### 2015-12-08 WRITEUP/Obs.tex
Draft for obs. section

\documentclass[]{emulateapj}
\usepackage{amsmath}
\begin{document}
\author{Draft}

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.655BLAH
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the redshifted frequency of $\nu_{\rm obs}$ = 
 BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under excellent / GOOD? 
%2 mm
weather conditions in the C and D array configurations, respectively. The 2 mm receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line and the underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing a correlator setup providing an effective bandwidth of 3.16 GHz and spectral resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 2.2 hours and 1.5 hours of six antenna-equivalent on-source time 
HOW TO FIND OUT TIME AFTER DISCARD DATA
after discarding unusable visibility data for C and D array observations, respectively.
% D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp), 1124-106(ditto)
% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186 (phase/amp), 1127-145 (ditto)
% total: 3.75 hours
%For both tracks, 
The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes for
pointing, secondary amplitude, and phase calibration, and MWC349 was observed as the primary
absolute flux calibrator for C array observations.
The nearby quasars 1127$-$145 and 1124$-$106 were observed every BLAH minutes for
pointing, secondary amplitude, and phase calibration, and 3C279 was observed as the primary
absolute flux calibrator for D array observations.
1055$+$018 and 3C279 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\lesssim
$15\% calibration accuracy.

The GILDAS package was used to reduce and analyze the visibility data which are then imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95. The final rms noise is $\sigma$ = 0.177 Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to 690 km s$^{-1}$), and $\sigma$ = 1.451 Jy km s$^{-1}$ beam$^{-1}$ over 10 MHz (21.5 km s$^{-1}$) . 
The continuum image is created by % 2.152 mm; 
averaging over all the line-free channels ($\nu_{\rm cont}\sim$139 GHz). This yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA} \label{sec:carmadata}
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH 
 were carried out using the Combined Array for Research in Millimeter-wave Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: BLAH; PI: D. Riechers).
Two observing runs were carried out on 2013 April 27 and Jun 09 under excellent 3 mm weather conditions in the C and D array configurations, respectively. The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 5.208 MHz ($\sim$17 km s$^{-1}$). The line was placed in the
upper sidebands for both tracks with the local oscillator tuned to $\nu_{\rm LO}\sim$ 90.7 GHz; this resulted in 1.9 hours and 2.6 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data for C and D array observations, respectively.

For both tracks, the nearby radio quasar J1310+323 was observed every 15 minutes for
pointing, amplitude, and phase calibration, and MWC349 was observed as the primary
absolute flux calibrator. J1337$-$129 and 3C273 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\sim
$15\% calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the upper sideband image cube. The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 208.3 MHz (corresponding to 687 km s$^{-1}$). % one bin is 83.195 km s$^{-1}$
The continuum image is created by
averaging over all the line-free channels ($\nu_{\rm cont}\sim$90.7 GHz). This yields a synthesized clean beam size of 3\farcs5 $\times$ 3\farcs0 and an rms noise of 0.24 mJy beam$^{-1}$.
%
%\section{Continuum}
%%90.6797 GHz
%% VLA sigma =  Jy
%
%no continuum detection..
%Averaging over all the line-free channels, we did not detect the radio continuum down to 2$\sigma$ of blah mJy at an averaged frequency of $\nu_{cont}$ = 90.7 GHz.
%
%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.80\textwidth]{../OverlayFig/ContPanel}
%\caption{Left: Contours of the CARMA 90.7 GHz continuum emission (red) in the foreground radio galaxy 3C220.3 overlaid on the image and contours of the VLA 6 GHz continuum emission (lime). The rms in the VLA 6 GHz continuum image is $\sigma$ = 0.0641 mJy beam$^{-1}$. The synthesized beam size is 0$\farcs$596 $\times$ 0$\farcs$229, at P.A. 75.79$\degr$. Lime contour levels start at $\pm$4$\times\sigma$ = x mJy beam$^{-1}$ and increment at steps of $\pm$2$\sigma$ for the VLA data; red contour levels start at $\pm$2$\sigma$, incrementing at steps of $\pm$1$\sigma$ = 0.24 mJy beam$^{-1}$.
%Right:
%Contour map of the 90.7 GHz continuum emission. The beam size is 16\farcs67$\pm
%$0\farcs69 $\times$ 7\farcs17$\pm$1\farcs60, at P.A. = -57.9$\degr$. The contour levels start at $\pm$2$\sigma$ and increment at steps of $\pm$1$\sigma$ =0.5 mJy beam$^{-1}$.\label{fig:cont}}
%\end{figure*}
%
%
%\section{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
%%- ! Parameters and Errors:
%%- ! MFIT%PAR[01]   10.289188385009766        1.7304190817956480
%%- ! MFIT%PAR[02]   51.276344299316406        29.649510734050978
%%- ! MFIT%PAR[03]   147.87234497070312 * 2.355        30.276954728539007
%%- ! MFIT%PAR[04]  0.34727144241333008       0.22560386117523606
%%- channel [, ]
%%- velocity range [,] km/s
%%- Integrated line flux =
%%- rms =
%
%%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
%%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.
%We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939+8315. We extract the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:mom0}, yielding peak flux density of 10.3 $\pm$ 1.7 mJy, the FWHM of the Gaussian fit is 541.65 $\pm$ 31.91 km s$^{-1}$. The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, where the synthesized beam size of the SMA observation is 1\farcs42$\times$1\farcs16, at P.A. -34.0\degr. Since the angular resolution of our CO measurement is 13$\farcs$57 $\pm$ 1\farcs4 $\times$ 5\farcs77 $\pm$ 3\farcs1, the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is therefore spatially unresolved. We construct the velocity-integrated (moment-0) map of the CO($J$ = 3 $\rightarrow$ 2) emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux is 14.6 $\pm$ 0.9 Jy km s$^{-1}$.
%
%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.8\textwidth]{../OverlayFig/CO32mom0}
%\includegraphics[width=0.65\textwidth]{../OverlayFig/2.685bin2_arcNS_further_Sblob}
%\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$2$\sigma$, incrementing at
%steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 5\farcs77, at P.A. = -60.67$\degr$.
%Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (lime contours) with $\sigma$=0.836951 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34.0\degr, as shown in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam size of the CARMA data, hence the CO($J$ = 3 $\rightarrow$ 2) detection is spatially unresolved.
%Bottom: The Gaussian-fitted line peak of CO($J$ = 3 $\rightarrow$ 2) is 23.36 $\pm$ 2.21 mJy beam$^{-1}$ (before continuum
%subtraction), and the integrated line flux over linewidth of $\sim$500 km/s is 14.6 $\pm$ 0.9 Jy km s$^{-1}$
%(after continuum subtraction).  \label{fig:mom0}}
%\end{figure*}
%
%No significant continuum emission is detected from the line-free region down to a 1$\sigma$ limit of blah mJy. Neither CO(3-2) emission nor continuum emission are seen in the map near the NIR positions.
%
%at $z$ = 2.685, 1$\arcsec \sim$ 8.1 kpc
%

\end{document}

### 2015-12-09 WRITEUP/Obs.tex
restructured GILDAS scripts, add draft for obs. section

@@
 averaging over all the line-free channels ($\nu_{\rm cont}\sim$90.7 GHz). This yields a synthesized clean beam size of 3\farcs5 $\times$ 3\farcs0 and an rms noise of 0.24 mJy beam$^{-1}$.
+
+\subsection{VLA} 
+Observations of the BLAH continuum ($\nu_{\rm rest}$ = BLAH GHz) toward the galaxy RXJ1131-1231 were carried out using the {\it Karl G.
+Jansky} Very Large Array (VLA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: BLAH; PI: BLAH).
+Observations were carried out on BLAH under excellent/GOOD? BLAH mm weather conditions in the A array configurations. The C-Band receivers were used to cover the BLAH
+, employing a correlator setup providing a bandwidth of BLAH GHz in each sideband. This resulted in BLAH hours of BLAH antenna-equivalent on-source time after discarding unusable visibility data.
+
+The nearby radio quasar BLAH was observed every BLAH minutes for
+pointing, amplitude, and phase calibration, and BLAH was observed as the primary
+absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding $\sim
+$15\% calibration accuracy.
+The AIPS package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
+the CLEAN algorithm with ``natural" weighting.
+This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image.
+The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.
 %

### 2015-12-09 PdBI/src/pythonPLOT/cubefromScratch.py
Add scripts, tested

@@ -1,0 +1,96 @@
+"""
+simple cube fitting example
+
+Build a cube from scratch and fit many gaussians
+
+Still need to figure out how to make it useful to what I do....
+Seems like it fits model to spectrum, e.g. Gaussian, and return SNR.. what does this SNR mean..
+
+Note
+----
+Run in ipython only, don't run under Daisy's alias='pylab' environment. It will crash for some reason.
+
+"""
+from __future__ import print_function
+
+import numpy as np
+import pyspeckit
+from spectral_cube import SpectralCube
+from astropy import wcs
+from astropy import units as u
+
+# Create a new WCS object so we can instantiate the SpectralCube
+mywcs = wcs.WCS(naxis=3)
+
+# Set up a tangent projection
+# You would normally read this from a file!!
+mywcs.wcs.crpix = [1, 2, 21.0]
+mywcs.wcs.cdelt = np.array([-0.066667, 0.066667, 500])
+mywcs.wcs.crval = [290.9250, 14.5092, 60000]
+mywcs.wcs.ctype = ["RA---TAN", "DEC--TAN", 'VELO']
+mywcs.wcs.cunit = ['deg', 'deg', 'm/s']
+
+# Create a synthetic X-dimension in km/s
+xarr = np.linspace(50, 70, 41)  # km/s
+
+# Define a line width, which will vary across our image
+# It will increase from 1 km/s to 4 km/s over the X-direction (RA)
+sigma = np.outer(np.linspace(1, 1.5, 2), np.ones(4)).T
+
+# Define a line center, which will vary in the opposite direction,
+# along increasing Y-direction (declination)
+centroid = np.outer(np.ones(2), np.linspace(58, 62, 4)).T
+
+data = np.exp(-(np.tile(xarr, (2, 4, 1)).T - centroid)**2 / (2. * sigma**2))
+cube = SpectralCube(data=data, wcs=mywcs)
+
+# Sanity checks: do the moments accurately recover the inputs?
+assert (np.abs(cube.moment1().to(u.km / u.s).value - centroid).max()) < 1e-5
+assert (np.abs(cube.moment2().to(u.km**2 / u.s**2).value - sigma**2).max()) < 1e-5
+
+# Create a pyspeckit cube
+pcube = pyspeckit.Cube(cube=cube)
+
+# For convenience, convert the X-axis to km/s
+# (WCSLIB automatically converts to m/s even if you give it km/s)
[…]

### 2015-12-09 PdBI/src/pythonPLOT/spectrumScratch.py

@@ -1,0 +1,46 @@
+'''
+Build a spectrum from scratch (and fit a gaussian)
+
+Can't figure out how to interactively show. For now, save it and check.
+
+Output: spectrum with fit
+
+'''
+import numpy as np
+import pyspeckit
+
+xaxis = np.linspace(-50,150,100.)
+sigma = 10.
+center = 50.
+synth_data = np.exp(-(xaxis-center)**2/(sigma**2 * 2.))
+
+# Add noise
+stddev = 0.1
+noise = np.random.randn(xaxis.size)*stddev
+error = stddev*np.ones_like(synth_data)
+data = noise+synth_data
+
+# this will give a "blank header" warning, which is fine
+sp = pyspeckit.Spectrum(data=data, error=error, xarr=xaxis,
+                        xarrkwargs={'unit':'km/s'},
+                        unit='erg/s/cm^2/AA')
+
+sp.plotter(figure=1)
+sp.plotter(errstyle='fill')
+
+
+# Fit with automatic guesses
+sp.specfit(fittype='gaussian')
+sp.plotter.savefig('spectrumScratch.png')
+
+# Fit with input guesses
+# The guesses initialize the fitter
+# This approach uses the 0th, 1st, and 2nd moments
+amplitude_guess = data.max()
+center_guess = (data*xaxis).sum()/data.sum()
+width_guess = data.sum() / amplitude_guess / np.sqrt(2*np.pi)
+guesses = [amplitude_guess, center_guess, width_guess]
+sp.specfit(fittype='gaussian', guesses=guesses)
+sp.specfit.plot_fit()
+
+sp.plotter.savefig('spectrumScratchGuess.png')

### 2015-12-09 PdBI/src/pythonPLOT/COChan.py
Cutomized to work on CO(2-1) cube, but somehow color is off

@@ -1,0 +1,132 @@
+import matplotlib.pyplot as plt
+import pywcsgrid2
+import pywcs
+
+import mpl_toolkits.axes_grid1.axes_grid as axes_grid
+#from mpl_toolkits.axes_grid.colorbar import colorbar
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes
+
+import pyfits
+
+class Velo(object):
+    def __init__(self, header):
+        wcs = pywcs.WCS(header)
+        self.wcs_vel = wcs.sub([3])
+
+    def to_vel(self, p):
+        v = self.wcs_vel.wcs_pix2sky([[p]], 0)
+        return v[0][0]
+
+
+def setup_axes(fig, header):
+
+    gh = pywcsgrid2.GridHelper(wcs=header)
+    gh.locator_params(nbins=3)
+
+    g = axes_grid.ImageGrid(fig, 111,
+                            nrows_ncols=(5, 4),
+                            ngrids=None,
+                            direction='row',
+                            axes_pad=0.02, add_all=True,
+                            share_all=True, aspect=True,
+                            label_mode='L', cbar_mode=None,
+                            axes_class=(pywcsgrid2.Axes, dict(grid_helper=gh)))
+
+    # make colorbar
+    ax = g[-1]
+    cax = inset_axes(ax,
+                     width="8%", # width = 10% of parent_bbox width
+                     height="100%", # height : 50%
+                     loc=3,
+                     bbox_to_anchor=(1.01, 0, 1, 1),
+                     bbox_transform=ax.transAxes,
+                     borderpad=0.
+                     )
+
+    return g, cax
+
+
+fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/04Sep15/sup127_155_2ndcln_noCont.fits")
+header = fits_cube[0].header
+
+vel = Velo(header)
+
+fig = plt.figure(1, figsize=(9, 12), dpi=70)
+g, cax = setup_axes(fig, header)
+
+
+def zoom_image(im, crop_nx, crop_ny):
+    '''
+    input
+    -----
+        crop_nx
+        int, pixel
+
+        crop_ny
+        int, pixel
+
+    return
+    ------
+    im of size 2*zoom x 2*zoom
+
+    '''
+
+
+    sizey = len(im[0])
+    sizex = len(im[1])
[…]

### 2015-12-09 PdBI/src/pythonPLOT/COChan.py
works with CO(2-1) cube, turns out the fits cube in 04Sep15 was bad --> fixed by re-made cube. NEED TO FIX, the WCS after zooming in the image is WRONG

@@ -24,7 +24,7 @@ def setup_axes(fig, header):
     gh.locator_params(nbins=3)
 
     g = axes_grid.ImageGrid(fig, 111,
-                            nrows_ncols=(5, 4),
+                            nrows_ncols=(5, 6),
                             ngrids=None,
                             direction='row',
                             axes_pad=0.02, add_all=True,
@@ -35,7 +35,7 @@ def setup_axes(fig, header):
     # make colorbar
     ax = g[-1]
     cax = inset_axes(ax,
-                     width="8%", # width = 10% of parent_bbox width
+                     width="15%", # # width = 8% width = 10% of parent_bbox width
                      height="100%", # height : 50%
                      loc=3,
                      bbox_to_anchor=(1.01, 0, 1, 1),
@@ -47,44 +47,19 @@ def setup_axes(fig, header):
 
 
 fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/04Sep15/sup127_155_2ndcln_noCont.fits")
+
 header = fits_cube[0].header
 
 vel = Velo(header)
 
-fig = plt.figure(1, figsize=(9, 12), dpi=70)
+fig = plt.figure(1, figsize=(12, 12), dpi=70)
 g, cax = setup_axes(fig, header)
-
-
-def zoom_image(im, crop_nx, crop_ny):
-    '''
-    input
-    -----
-        crop_nx
-        int, pixel
-
-        crop_ny
-        int, pixel
-
-    return
-    ------
-    im of size 2*zoom x 2*zoom
-
-    '''
-
-
-    sizey = len(im[0])
-    sizex = len(im[1])
-    im = im[round(sizey/2-crop_ny):round(sizey/2+crop_ny), round(sizex/2-crop_nx):round(sizex/2+crop_nx)]
-#    print("Im dimension after cropping: {:d} X {:d}").format(len(im[0]), len(im[1]))
-    return im
-
 
 
 # draw images
 i = 0
 dxy = 125
 nxy = 6 * 5
-zoom = 10  # pixel
 # cmap = plt.cm.gray_r
 cmap = plt.cm.jet
 import matplotlib.colors as mcolors
@@ -93,14 +68,13 @@ images = []
 start_channel = i*nxy+dxy
 for i, ax in enumerate(g):
     channel_number = start_channel + i
-    channel = fits_cube[0].data[0][channel_number]
[…]

### 2015-12-09 PdBI/src/pythonPLOT/COChan.py
Added docstring

@@ -1,3 +1,16 @@
+'''
+
+Last Modified: 09 Dec 15
+
+Author: Daisy Leung
+
+History:
+09 Dec 15
+- works with CO(2-1) cube
+- but need to fix WCS, which is wrong if we zoom in on the image
+
+'''
+
 import matplotlib.pyplot as plt
 import pywcsgrid2
 import pywcs

### 2015-12-09 PdBI/src/pythonPLOT/COChan.py
add contours

@@ -8,6 +8,7 @@ History:
 09 Dec 15
 - works with CO(2-1) cube
 - but need to fix WCS, which is wrong if we zoom in on the image
+- added contours overlay on channel map
 
 '''
 
@@ -65,7 +66,7 @@ header = fits_cube[0].header
 
 vel = Velo(header)
 
-fig = plt.figure(1, figsize=(12, 12), dpi=70)
+fig = plt.figure(1, figsize=(12, 12), dpi=100)
 g, cax = setup_axes(fig, header)
 
 
@@ -73,18 +74,21 @@ g, cax = setup_axes(fig, header)
 i = 0
 dxy = 125
 nxy = 6 * 5
+sigma = 1.451e-3           # sigma in map for contour plots
+
 # cmap = plt.cm.gray_r
 cmap = plt.cm.jet
 import matplotlib.colors as mcolors
 norm = mcolors.Normalize()
 images = []
 start_channel = i*nxy+dxy
+
 for i, ax in enumerate(g):
     channel_number = start_channel + i
     channel = fits_cube[0].data[0][channel_number][110:150, 110:150]
     im = ax.imshow(channel, origin="lower", norm=norm, cmap=cmap)
+    ax.contour(channel, [4*sigma, 8*sigma, 12*sigma, 16*sigma, 20*sigma], colors='black')
     images.append(im)
-
 
 # label with velocities
 use_path_effect = True         # Fancy text
@@ -104,7 +108,7 @@ for i, ax in enumerate(g):
 
 # make colorbar
 cb = plt.colorbar(im, cax=cax)
-cb.set_label("Flux Density [mJy]")
+cb.set_label("Flux Density [mJy B"+r"$^{-1}$]")
 cb.set_ticks([0, 0.25, 0.5])
 
 # adjust norm

### 2015-12-10 PdBI/src/pythonPLOT/COChan.py
Correct WCS on axes, but the image won't show now, becuase the image wasn't transformed to map with the axes... need something that also map the cropped image to the correct WCS

@@ -10,11 +10,16 @@ History:
 - but need to fix WCS, which is wrong if we zoom in on the image
 - added contours overlay on channel map
 
+
+Note:
+depends on package - astrolib.coords for putting up markers based on Coords
+
 '''
 
 import matplotlib.pyplot as plt
 import pywcsgrid2
 import pywcs
+import numpy as np
 
 import mpl_toolkits.axes_grid1.axes_grid as axes_grid
 #from mpl_toolkits.axes_grid.colorbar import colorbar
@@ -42,7 +47,11 @@ def setup_axes(fig, header):
                             ngrids=None,
                             direction='row',
                             axes_pad=0.02, add_all=True,
-                            share_all=True, aspect=True,
+                            share_all=True,
+                            # if share_all = False, need the following
+                            # share_x = False,
+                            # share_y = False,
+                            aspect=True,
                             label_mode='L', cbar_mode=None,
                             axes_class=(pywcsgrid2.Axes, dict(grid_helper=gh)))
 
@@ -51,7 +60,7 @@ def setup_axes(fig, header):
     cax = inset_axes(ax,
                      width="15%", # # width = 8% width = 10% of parent_bbox width
                      height="100%", # height : 50%
-                     loc=3,
+                     loc=3,    # 4
                      bbox_to_anchor=(1.01, 0, 1, 1),
                      bbox_transform=ax.transAxes,
                      borderpad=0.
@@ -63,6 +72,10 @@ def setup_axes(fig, header):
 fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/04Sep15/sup127_155_2ndcln_noCont.fits")
 
 header = fits_cube[0].header
+cdelt1 = np.abs(header['CDELT1'] * 3600)
+cdelt2 = np.abs(header['CDELT2'] * 3600)
+
+wcs = pywcs.WCS(header).sub([1, 2])       # .sub([1,2]) needed for wcs.wcs_pix2sky(px, py, 1) later in the code
 
 vel = Velo(header)
 
@@ -87,8 +100,45 @@ for i, ax in enumerate(g):
     channel_number = start_channel + i
     channel = fits_cube[0].data[0][channel_number][110:150, 110:150]
[…]

### 2015-12-10 PdBI/src/pythonPLOT/COChan.py
axes match image. Instead of cropping image to show, should set axes limit

@@ -89,6 +89,9 @@ dxy = 125
 nxy = 6 * 5
 sigma = 1.451e-3           # sigma in map for contour plots
 
+# mark HST knots location on channel map
+HST = True
+
 # cmap = plt.cm.gray_r
 cmap = plt.cm.jet
 import matplotlib.colors as mcolors
@@ -98,7 +101,7 @@ start_channel = i*nxy+dxy
 
 for i, ax in enumerate(g):
     channel_number = start_channel + i
-    channel = fits_cube[0].data[0][channel_number][110:150, 110:150]
+    channel = fits_cube[0].data[0][channel_number]#[110:150, 110:150]
     im = ax.imshow(channel, origin="lower", norm=norm, cmap=cmap)
     ax.contour(channel, [4*sigma, 8*sigma, 12*sigma, 16*sigma, 20*sigma],
                colors='black')
@@ -112,32 +115,29 @@ for i, ax in enumerate(g):
 #    ax.set_ylim(cropIMwcs[1].min(), cropIMwcs[1].max())
     ax.set_xlim(110, 150)
     ax.set_ylim(110, 150)
+
+    if HST:   # mark lensing knots
+
+    # DOESN'T WORK, will try using mpl marker
+
+        import astrolib.coords as coords
+        p_list = [coords.Position("11:31:51.3  -12:31:59").j2000(),
+              coords.Position("11:31:51.6  -12:31:59.6").j2000()]
+
+#        import pdb; pdb.set_trace()
+        for p1 in p_list:
+            ra, dec = p1
+            l1, = ax[wcs].plot([ra], [dec],
+                           "w+", mec="k", mew=2, ms=8,
+                           zorder=3.1)
     images.append(im)
 
 
-
-# mark HST knots location on channel map
-# HST = True
-# if HST:
-#     '''
-#     Lensing knots coordinates:
-
-#     '''
-
-#     import coords
-#     p_list = [coords.Position("06:17:29.3  +22:22:43").j2000(),
-#               coords.Position("06:18:03.7  +22:24:53").j2000(),
-#               (94.181357,22.543208)]
-#     for p1, ax in zip(p_list, [g[i], g[i], g[2]]):
-#         ra, dec = p1
-#         l1, = ax[wcs].plot([ra], [dec],
-#                            "^", mec="k", mfc="w", mew=1, ms=8,
-#                            zorder=3.1)
-
-#     # put up legend on last panel --> HST markers
[…]

### 2015-12-10 PdBI/src/pythonPLOT/COChan.py
HST markers still not working. Changed to show xylabel in one panel

@@ -7,9 +7,10 @@ Author: Daisy Leung
 History:
 09 Dec 15
 - works with CO(2-1) cube
-- but need to fix WCS, which is wrong if we zoom in on the image
 - added contours overlay on channel map
-
+- Need to make it plot markers for HST positions
+- will zoom on image with correct axes
+- only show axes label in one panel
 
 Note:
 depends on package - astrolib.coords for putting up markers based on Coords
@@ -40,7 +41,7 @@ class Velo(object):
 def setup_axes(fig, header):
 
     gh = pywcsgrid2.GridHelper(wcs=header)
-    gh.locator_params(nbins=3)
+    gh.locator_params(nbins=4)
 
     g = axes_grid.ImageGrid(fig, 111,
                             nrows_ncols=(5, 6),
@@ -52,8 +53,15 @@ def setup_axes(fig, header):
                             # share_x = False,
                             # share_y = False,
                             aspect=True,
-                            label_mode='L', cbar_mode=None,
+                            label_mode='1',  # 'L'
+                            cbar_mode=None,
                             axes_class=(pywcsgrid2.Axes, dict(grid_helper=gh)))
+
+    # only show xylabel at that panel, depending on nrows_ncols in axes_grid.ImageGrid()
+    # if comment out the following block, will shorten to Greek Letters
+    ax = g[-6]
+    ax.set_xlabel("Right Ascension (J2000)")
+    ax.set_ylabel("Declination (J2000)")
 
     # make colorbar
     ax = g[-1]
@@ -85,9 +93,9 @@ g, cax = setup_axes(fig, header)
 
 # draw images
 i = 0
-dxy = 125
-nxy = 6 * 5
-sigma = 1.451e-3           # sigma in map for contour plots
+dxy = 125                 # starting channel
+nxy = 6 * 5               # total number of channels
+sigma = 1.451e-3          # sigma in map for contour plots
 
 # mark HST knots location on channel map
 HST = True
@@ -101,35 +109,26 @@ start_channel = i*nxy+dxy
 
 for i, ax in enumerate(g):
     channel_number = start_channel + i
-    channel = fits_cube[0].data[0][channel_number]#[110:150, 110:150]
+    channel = fits_cube[0].data[0][channel_number]
     im = ax.imshow(channel, origin="lower", norm=norm, cmap=cmap)
[…]

### 2015-12-10 PdBI/src/pythonPLOT/COChan.py
formatting

@@ -1,16 +1,21 @@
 '''
+TODO:
+- Need to make it plot markers for HST positions
+
 
 Last Modified: 09 Dec 15
 
+
 Author: Daisy Leung
+
 
 History:
 09 Dec 15
 - works with CO(2-1) cube
 - added contours overlay on channel map
-- Need to make it plot markers for HST positions
 - will zoom on image with correct axes
 - only show axes label in one panel
+
 
 Note:
 depends on package - astrolib.coords for putting up markers based on Coords
@@ -163,8 +168,8 @@ cb.set_label("Flux Density [mJy B"+r"$^{-1}$]")
 cb.set_ticks([0, 0.25, 0.5])
 
 # adjust norm
-norm.vmin = -0.007
-norm.vmax = 0.03
+norm.vmin = -0.007        # min in map
+norm.vmax = 0.03          # max in map
 for im in images:
     im.changed()
 

### 2015-12-14 WRITEUP/Maps.tex
initialize tex file for CO data maps

\documentclass[]{emulateapj}
\usepackage{amsmath}
\begin{document}
\author{Draft}

\section{Continuum}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{}
\caption{Left: Contours of the CARMA BLAH GHz continuum emission (red) in the foreground radio galaxy 3C220.3 overlaid on the image and contours of the VLA 6 GHz continuum emission (lime). The rms in the VLA 6 GHz continuum image is $\sigma$ = 0.0641 mJy beam$^{-1}$. The synthesized beam size is 0$\farcs$596 $\times$ 0$\farcs$229, at P.A. 75.79$\degr$. Lime contour levels start at $\pm$4$\times\sigma$ = x mJy beam$^{-1}$ and increment at steps of $\pm$2$\sigma$ for the VLA data; red contour levels start at $\pm$2$\sigma$, incrementing at steps of $\pm$1$\sigma$ = 0.24 mJy beam$^{-1}$.
Right:
Contour map of the 90.7 GHz continuum emission. The beam size is 16\farcs67$\pm
$0\farcs69 $\times$ 7\farcs17$\pm$1\farcs60, at P.A. = -57.9$\degr$. The contour levels start at $\pm$2$\sigma$ and increment at steps of $\pm$1$\sigma$ =0.5 mJy beam$^{-1}$.\label{fig:cont}}
\end{figure*}

\section{CO($J$ = 3 $\rightarrow$ 2) line emission}
%- ! Parameters and Errors:
%- ! MFIT%PAR[01]  
%- ! MFIT%PAR[02]  
%- ! MFIT%PAR[03]  
%- ! MFIT%PAR[04]  
%- channel [, ]
%- velocity range [,] km/s
%- Integrated line flux =
%- rms =

%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.
We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background galaxy in RXJ1131-1231. 
We extract the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:mom0}, yielding peak flux density of BLAH $\pm$ BLAH mJy, the FWHM of the Gaussian fit is BLAH $\pm$ BLAH km s$^{-1}$. 
The spatial extent of the  is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, where the synthesized beam size of the SMA observation is 1\farcs42$\times$1\farcs16, at P.A. -34.0\degr. Since the angular resolution of our CO measurement is 13$\farcs$57 $\pm$ 1\farcs4 $\times$ 5\farcs77 $\pm$ 3\farcs1, the CO($J$ = 3 $\rightarrow$ 2) detection in the lensed galaxy is therefore spatially unresolved. 
We construct the velocity-integrated (moment-0) map of the CO($J$ = 3 $\rightarrow$ 2) emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux is BLAH $\pm$ BLAH Jy km s$^{-1}$.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../OverlayFig/CO32mom0}
\includegraphics[width=0.65\textwidth]{../OverlayFig/2.685bin2_arcNS_further_Sblob}
\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$2$\sigma$, incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 5\farcs77, at P.A. = -60.67$\degr$.
Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (lime contours) with $\sigma$=0.836951 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34.0\degr, as shown in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam size of the CARMA data, hence the CO($J$ = 3 $\rightarrow$ 2) detection is spatially unresolved.
Bottom: The Gaussian-fitted line peak of CO($J$ = 3 $\rightarrow$ 2) is 23.36 $\pm$ 2.21 mJy beam$^{-1}$ (before continuum
subtraction), and the integrated line flux over linewidth of $\sim$500 km/s is 14.6 $\pm$ 0.9 Jy km s$^{-1}$
(after continuum subtraction).  \label{fig:mom0}}
\end{figure*}

No significant continuum emission is detected from the line-free region down to a 1$\sigma$ limit of blah mJy. Neither CO(3-2) emission nor continuum emission are seen in the map near the NIR positions.

at $z$ = 2.685, 1$\arcsec \sim$ 8.1 kpc

\section{CO($J$ = 2 $\rightarrow$ 1) line emission}
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../OverlayFig/CO32mom0}
\includegraphics[width=0.65\textwidth]{../OverlayFig/2.685bin2_arcNS_further_Sblob}
\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$2$\sigma$, incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 5\farcs77, at P.A. = -60.67$\degr$.
Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (lime contours) with $\sigma$=0.836951 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34.0\degr, as shown in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam size of the CARMA data, hence the CO($J$ = 3 $\rightarrow$ 2) detection is spatially unresolved.
Bottom: The Gaussian-fitted line peak of CO($J$ = 3 $\rightarrow$ 2) is 23.36 $\pm$ 2.21 mJy beam$^{-1}$ (before continuum
subtraction), and the integrated line flux over linewidth of $\sim$500 km/s is 14.6 $\pm$ 0.9 Jy km s$^{-1}$
(after continuum subtraction).  \label{fig:mom0}}
\end{figure*}
\end{document}

### 2015-12-17 WRITEUP/Obs.tex
minor updates

@@
 The 2 mm receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line and the underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing a correlator setup providing an effective bandwidth of 3.16 GHz and spectral resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
-This resulted in 2.2 hours and 1.5 hours of six antenna-equivalent on-source time 
-HOW TO FIND OUT TIME AFTER DISCARD DATA
-after discarding unusable visibility data for C and D array observations, respectively.
+This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time 
+after discarding unusable visibility data.
 % D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp), 1124-106(ditto)
@@
 \subsection{CARMA} \label{sec:carmadata}
+% LO = 215.6694 Ghz
+% 3C273 FG
+% 3C279 Bandpass
+% mars flux
+% after flagging: Total observing time is  1.48 hours, checked with uvindex
+%
 Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
 0.655BLAH 
- were carried out using the Combined Array for Research in Millimeter-wave Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: BLAH; PI: D. Riechers).
-Two observing runs were carried out on 2013 April 27 and Jun 09 under excellent 3 mm weather conditions in the C and D array configurations, respectively.
-The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 5.208 MHz ($\sim$17 km s$^{-1}$).
+ were carried out using the Combined Array for Research in Millimeter-wave Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: cf0098; PI: D. Riechers).
+observations were carried out on 2014 February 17 under good 3 mm weather conditions in the D array configurations.
+The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 12.5 MHz ($\sim$17BLAH km s$^{-1}$).
 The line was placed in the
-upper sidebands for both tracks with the local oscillator tuned to $\nu_{\rm LO}\sim$ 90.7 GHz; this resulted in 1.9 hours and 2.6 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data for C and D array observations, respectively.
+lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz; this resulted in 1.5 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.
 
-For both tracks, the nearby radio quasar J1310+323 was observed every 15 minutes for
-pointing, amplitude, and phase calibration, and MWC349 was observed as the primary
-absolute flux calibrator. J1337$-$129 and 3C273 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\sim
-$15\% calibration accuracy.
+The nearby radio quasar 3C273 was observed every 15 minutes for
+pointing, amplitude, and phase calibration, and Mars was observed as the primary
+absolute flux calibrator. 3C279 was observed as bandpass calibrators, yielding $\sim
+$15\%BLAH calibration accuracy.
 The MIRIAD package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
 the CLEAN algorithm with ``natural" weighting.
-This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the upper sideband image cube.
-The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 208.3 MHz (corresponding to 687 km s$^{-1}$).
-% one bin is 83.195 km s$^{-1}$
+This yields a synthesized clean beam size of 3\farcs1 $\times$ 1\farcs9 for the lower sideband image cube.
+The final rms noise is $\sigma$ = BLAH Jy km s$^{-1}$ beam$^{-1}$ over a channel width of BKAH MHz (corresponding to BLAH km s$^{-1}$).
 The continuum image is created by
-averaging over all the line-free channels ($\nu_{\rm cont}\sim$90.7 GHz). This yields a synthesized clean beam size of 3\farcs5 $\times$ 3\farcs0 and an rms noise of 0.24 mJy beam$^{-1}$.
+averaging over all the line-free channels ($\nu_{\rm cont}\sim$216 GHz). This yields a synthesized clean beam size of Blah\farcs5 $\times$ blah\farcs0 and an rms noise of 0.24Blah mJy beam$^{-1}$.
 

### 2015-12-28 WRITEUP/Lensmodel.tex
place holder for paper

\documentclass[]{emulateapj}
\usepackage{amsmath}
\begin{document}
\author{Draft}

\section{Gravitational Lens model}

\subsection{interpretation}
- C06 suggest the presence of an interacting dusty galaxy in their HST observations, which BJB+08 calls it the F component. The lensed images of the ABCDE components coincide with our CO data (see mom0 on HST and channel map), evidently CO emission coming from the AGN host galaxy. 
- one of the red channels in our lens model suggests a second source component, which is consistent with the spatially offset dusty source (see mom0 on HST, which the red velocity component coincides with this F component)

\begin{figure}[tbph]
\centering
\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.eps}
\includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
\caption{
Pseudo observed 0th moment map in the lens plane. (left)
Pseudo 0th moment map in the source plane. (right)
\label{fig:}}
\end{figure}

%\begin{figure*}[tbph]
%\centering
%\caption{
%\label{fig:}}
%\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.eps}
\caption{
velocity gradient of the lens model in the lens plane (left), source plane (right).
\label{fig:}}
\end{figure*}

%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.8\textwidth]{}
%\includegraphics[width=0.65\textwidth]{}
%\caption{
%\label{fig:}}
%\end{figure*}

\end{document}

### 2015-12-28 WRITEUP/Results.tex
place holder for paper

\documentclass[]{emulateapj}
\usepackage{amsmath}
\begin{document}
\author{Draft}

\section{CO($J$ = 3 $\rightarrow$ 2) line emission}
%- ! Parameters and Errors:
%- ! MFIT%PAR[01]  
%- ! MFIT%PAR[02]  
%- ! MFIT%PAR[03]  
%- ! MFIT%PAR[04]  
%- channel [, ]
%- velocity range [,] km/s
%- Integrated line flux =
%- rms =

%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.

We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background galaxies in RXJ1131-1231. 
We extract the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:CO32mom0}, 
yielding peak flux density of BLAH $\pm$ BLAH mJy, the FWHM of the Gaussian fit is BLAH $\pm$ BLAH km s$^{-1}$.

%No significant continuum emission is detected from the line-free region down to a 1$\sigma$ limit of blah mJy.

\section{CO($J$ = 2 $\rightarrow$ 1) line emission}
We detect dynamically resolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background galaxies in RXJ1131-1231.

We construct the velocity-integrated (0th moment) map of the CO($J$ = 2 $\rightarrow$ 1) emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 2 $\rightarrow$ 1) line flux is BLAH $\pm$ BLAH Jy km s$^{-1}$.

% upper limit on other lines 
% in the background source -- H2CO

% in the foreground galaxy -- H2CO, HNC (J=2-1)
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{
0th Moment map of CO(2-1) emission on HST F555W.
Spectrum. Velocity scale w.r.t z=0.655
 \label{fig:CO21mom0}}
\end{figure*}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
\caption{
1st and 2nd order moments
 \label{fig:}}
\end{figure}

\begin{figure*}[tbph]
\centering
\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
\caption{
Black crosses indicate the position of the lensed AGN (components ABCD) and the foreground lensing galaxy (component G) in the HST image.
 \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
\caption{ 
Spatial spectra, binned by 3 pixels in each direction (1\farcs5)
 \label{fig:spatialSpec}}
\end{figure*}

%
%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.8\textwidth]{}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
%\includegraphics[width=0.65\textwidth]{}
%\caption{
% \label{fig:}}
%\end{figure*}

\section{Continuum}

%
%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.80\textwidth]{}
%\caption{Left: Contours of the CARMA BLAH GHz continuum emission (red) in the foreground radio galaxy 3C220.3 overlaid on the image and contours of the VLA 6 GHz continuum emission (lime). The rms in the VLA 6 GHz continuum image is $\sigma$ = 0.0641 mJy beam$^{-1}$. The synthesized beam size is 0$\farcs$596 $\times$ 0$\farcs$229, at P.A. 75.79$\degr$. Lime contour levels start at $\pm$4$\times\sigma$ = x mJy beam$^{-1}$ and increment at steps of $\pm$2$\sigma$ for the VLA data; red contour levels start at $\pm$2$\sigma$, incrementing at steps of $\pm$1$\sigma$ = 0.24 mJy beam$^{-1}$.
%Right:
%Contour map of the 90.7 GHz continuum emission. The beam size is 16\farcs67$\pm
%$0\farcs69 $\times$ 7\farcs17$\pm$1\farcs60, at P.A. = -57.9$\degr$. The contour levels start at $\pm$2$\sigma$ and increment at steps of $\pm$1$\sigma$ =0.5 mJy beam$^{-1}$.\label{fig:cont}}
%\end{figure*}

%%%%%%%%%%%%%%%
\end{document}

### 2016-01-09 src/SED/photometry.py
automatic latexify table

@@ -4,7 +4,7 @@ Organize RXJ1131 IR photometry data using astropy table
 wavelength [µm], freq [GHz], flux density [mJy], flux_err [mJy], instrument
 
 
-Last Modified: Jan 08 2016
+Last Modified: Jan 09 2016
 
 
 TODO
@@ -12,10 +12,14 @@ TODO
 - add CARMA continuum as upper limit
 - add PdBI continuum data
 - add code to plot points on SED, put MIR and radio data on plot for background source but don't include in fit, maybe use IRAS 60, 100 µm to constrain SED peak
+  - mark continuum for foreground and background differently
 
 
 History
 -------
+Jan 09 2016:
+    combine flux col with flux err col in latex table
+    separate out column name with unit in latex table
 Jan 08 2016:
     created, added 2MASS, WISE, Spitzer, Herschel, IRAS data
 
@@ -33,6 +37,8 @@ import numpy as np
 
 # Utilize a row oriented table
 #
+tableColHead = ('Wavelength [micron]', 'Frequency [GHz]', 'Flux Density [mJy]', 'Flux Err [mJy]', 'Instrument')
+
 data_rows = [(1.25, (1.25*u.micron).to(u.GHz, equivalencies=u.spectral()).value
               , 1.009, 0.090, '2MASS/J-Band'),
              (1.65, (1.65*u.micron).to(u.GHz, equivalencies=u.spectral()).value
@@ -72,12 +78,10 @@ data_upperLim = [(12, (12*u.micron).to(u.GHz, equivalencies=u.spectral()).value 
 
 
 # fill table
-tbl = Table(rows=data_rows, names=('Wavelength [micron]', 'Frequency [GHz]', 'Flux density [mJy]', 'Flux_err [mJy]', 'Instrument'), dtype=['f4', 'f4', 'f4', 'f4', (str, 20)])
-    #dtype=('f8, 'f8', 'f8', 'f8', 'S20')
-    # dtype=[(str, 20), (str, 10), int, int, float, float, float, float, float, float, int]
-
-# tbl.rename_column('a', 'A')
-# tbl.colnames
+tbl = Table(rows=data_rows, names=tableColHead,
+            dtype=['f4', 'f4', 'f4', 'f4', (str, 20)])
+            # dtype=('f8, 'f8', 'f8', 'f8', 'S20')
+            # dtype=[(str, 20), (str, 10), int, int, float, float, float, float, float, float, int]
 # len(tbl)
 
 # append IRAS data
[…]

### 2016-01-09 src/SED/photometry.py
update table with VLA, PdBI, CARMA data

@@ -8,18 +8,14 @@ Last Modified: Jan 09 2016
 
 
 TODO
-- add VLA radio data
-- add CARMA continuum as upper limit
-- add PdBI continuum data
-- add code to plot points on SED, put MIR and radio data on plot for background source but don't include in fit, maybe use IRAS 60, 100 µm to constrain SED peak
-  - mark continuum for foreground and background differently
-
+- add VLA radio data LCX
 
 History
 -------
 Jan 09 2016:
     combine flux col with flux err col in latex table
     separate out column name with unit in latex table
+    added CARAMA, PdBI, VLA C Band continuum data
 Jan 08 2016:
     created, added 2MASS, WISE, Spitzer, Herschel, IRAS data
 
@@ -69,12 +65,24 @@ data_rows = [(1.25, (1.25*u.micron).to(u.GHz, equivalencies=u.spectral()).value
               56.781866, 8.81188, 'Herschel/SPIRE')
              ]
 
-data_upperLim = [(12, (12*u.micron).to(u.GHz, equivalencies=u.spectral()).value              , 0.4e3, None, 'IRAS'),
+data_IRAS = [(12, (12*u.micron).to(u.GHz, equivalencies=u.spectral()).value              , 0.4e3, None, 'IRAS'),
                  (25, (25*u.micron).to(u.GHz, equivalencies=u.spectral()).value
                   , 0.5e3, None, 'IRAS'),
                  (60, (60*u.micron).to(u.GHz, equivalencies=u.spectral()).value
                   , 0.6e3, None, 'IRAS'),
                  (100, (100*u.micron).to(u.GHz, equivalencies=u.spectral()).value, 1.0e3, None, 'IRAS')]
+
+
+data_VLA = [((4.8815*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
+            4.8815, 1.273277, 4.208577829e-02, 'VLA/Cband-arc'),
+            ((4.8815*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
+            4.8815,  8.662040e-01, 2.746052e-02, 'VLA/Cband-core')]
+
+
+data_PdBI = [((139.256*u.GHz).to(u.micron, equivalencies=u.spectral()).value, 139.256, 1.23, 0.22, 'PdBI')]
+
+rmsCARMA_cont = 8.30807E-01   # mJy
[…]

### 2016-01-10 src/SED/SEDplot.py
script plotting all photometry data, need LCX band data

@@ -1,0 +1,154 @@
+'''
+
+Plot points on SED, put MIR and radio data on plot for background source but don't include in fit, maybe use IRAS 60, 100 micron to constrain SED peak
+- mark continuum for foreground and background differently
+
+Last Modified: Jan 09 2016
+
+
+TODO
+- put mbb_emcee fit
+-
+
+
+History
+-------
+Jan 09 2016:
+    created
+
+
+Note
+----
+- Twin axes work perfectly, even on loglog
+
+'''
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+
+photoFile = 'RXJ1131photometry.dat'
+plotName = 'FullSED'
+
+def read_file(filename):
+    """
+    Read in rows that are not commented out
+
+    Paramters
+    ---------
+    filename: str
+
+    Return
+    ------
+    dataTable: astropy.table.table.Table
+
+    """
+
+    import astropy.io.ascii as ascii
+    dataTable = ascii.read(filename, comment='^#')
+    # data = ascii.read(filename, format='no_header', data_start=0)
+
+    #dataTable = Table.read(file, format='ascii.commented_header')
+    if len(dataTable) == 0:
+        errstr = "No data read from %s" % filename
+        raise IOError(errstr)
+    return dataTable
+
+tbl = read_file(photoFile)
+
+# separate out photometry and those as upper limits
+print tbl.colnames
+idx, = np.where(np.isnan(tbl['Flux Err [mJy]']) == True)
+tblUpLimit = tbl[idx]
+idx, = np.where(np.isnan(tbl['Flux Err [mJy]']) == False)
+tblWithErr = tbl[idx]
+
+waveUpLimit = np.asarray(tblUpLimit['Wavelength [micron]'])
+fluxUpLimit = np.asarray(tblUpLimit['Flux Density [mJy]'])
+
+wave = np.asarray(tblWithErr['Wavelength [micron]'])
+flux = np.asarray(tblWithErr['Flux Density [mJy]'])
+fluxErr = np.asarray(tblWithErr['Flux Err [mJy]'])
+
+
+# Plot
+def savefigure(figure, f, verbose=True, dirStr='../../Figures/'):
+    """
+    Save figure in designatied directory and make directory if it doesn't alraedy exist
+
+    Paramters
+    ---------
+    figure: matplotlib.figure.Figure
[…]

### 2016-03-14 src/SED/tablePhotometry.py
fix latex tab formatting

@@ -232,7 +232,7 @@ if demo:
     flex['tablealign'] = 'tbpH'
     flex['preamble'] = r'\centering'
     # l['caption'] = ' '   # after preamble; uncomment if want caption above table
-    flex['col_align'] = '|lllcc| \hline'       # default is all c
+    flex['col_align'] = 'lccc \hline'       # default is all c
     flex['header_start'] = ' '
     flex['header_end'] = ' '
     flex['data_start'] = ' '
@@ -252,7 +252,7 @@ if demo:
 
 # deluxetable with customization
 pream = r'\tabletypesize{\scriptsize}' + '\n' + r'\tablecolumns{' + str(len(newTbl.colnames)) + '}\n' + r'\tablecaption{Photometry data}'
-cus = {'col_align': '|rrcc|',
+cus = {'col_align': 'lccc',
        'tablealign': 'tbpH',
        'preamble': pream,
        'units': {newTbl.colnames[0]: 'micron',
@@ -260,7 +260,7 @@ cus = {'col_align': '|rrcc|',
                  newTbl.colnames[2]: 'mJy',
                  newTbl.colnames[3]: ' '},
        'tablefoot': r'\label{tab:BLAH}' + '\n'
-                    r'\tablecomments{blah}' + '\n TablenotegoesBetween \n' +
+                    r'\tablecomments{blah}' + '\n %TablenotegoesBetween \n' +
                     r'\tablerefs{blah}'
        }
 # stdout

### 2016-03-14 WRITEUP/Lensmodel.tex
fix alignment

@@
 \subsection{interpretation}
-- C06 suggest the presence of an interacting dusty galaxy in their HST observations, which BJB+08 calls it the F component.
-The lensed images of the ABCDE components coincide with our CO data (see mom0 on HST and channel map), evidently CO emission coming from the AGN host galaxy.
-- one of the red channels in our lens model suggests a second source component, which is consistent with the spatially offset dusty source (see mom0 on HST, which the red velocity component coincides with this F component)
+- C06 suggest the presence of an interacting dusty galaxy in their HST
+observations, which BJB+08 calls it the F component. The lensed images of the
+ABCDE 
+components coincide with our CO data (see mom0 on HST and channel map),
+evidently CO emission coming from the AGN host galaxy. 
+- one of the red channels in our lens model suggests a second source component,
+which is consistent with the spatially offset dusty source (see mom0 on HST,
+which 
+the red velocity component coincides with this F component)
+
+%%%%%%%%%%%%%%%%%%%%%%%%
++ Compare our lens model parameters on the mass distribution of the lensing
+galaxy with literature (specifically SIE model in C06)
+	- C06: SIE model shows position of lensing mass is offset by (-0.015",
+-0.041" from obs. (i.e. light centroid)); PA = -73.6, ellipticity = 0.45,
+theta_R = 1.84" +/- 0.01 
+	- Our model lens parameters (median):
+		- file: WRITEUP/MedianLensModelParams.txt
+		- lensing gal. position is consistent with C06, 
+		- Einstein radius: consistent with C06
+		- PA: consistent within errors
+		- Axial ratio: consistent within errors
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \centering
-\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.eps}
+\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.ep
+s}
 \includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
@@
 \centering
-\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.eps}
+\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.ep
+s}
 \caption{
-velocity gradient of the lens model in the lens plane (left), source plane (right).
+velocity gradient of the lens model in the lens plane (left), source plane
+(right).
 \label{fig:}}

### 2016-03-14 WRITEUP/Obs.tex
place holder for paper
fix alignment

@@
 \subsection{PdBI} \label{sec:PdBIdata}
-Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.655BLAH
- were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the redshifted frequency of $\nu_{\rm obs}$ = 
+Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
+rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
+0.655BLAH
+ were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
+redshifted frequency of $\nu_{\rm obs}$ = 
  BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
- Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under excellent / GOOD? 
+ Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
 %2 mm
-weather conditions in the C and D array configurations, respectively.
-The 2 mm receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line and the underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing a correlator setup providing an effective bandwidth of 3.16 GHz and spectral resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
+weather conditions in the C and D array configurations, respectively. The 2 mm
+receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line
+and the 
+underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing
+a correlator setup providing an effective bandwidth of 3.16 GHz and spectral 
+resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
 This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time
+
 after discarding unusable visibility data.
-% D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp), 1124-106(ditto)
-% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186 (phase/amp), 1127-145 (ditto)
+% D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp),
+1124-106(ditto)
+% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186
+(phase/amp), 1127-145 (ditto)
 % total: 3.75 hours
 %For both tracks, 
-The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes for
-pointing, secondary amplitude, and phase calibration, and MWC349 was observed as the primary
+The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes
+for
+pointing, secondary amplitude, and phase calibration, and MWC349 was observed
+as the primary
 absolute flux calibrator for C array observations.
-The nearby quasars 1127$-$145 and 1124$-$106 were observed every BLAH minutes for
-pointing, secondary amplitude, and phase calibration, and 3C279 was observed as the primary
+The nearby quasars 1127$-$145 and 1124$-$106 were observed every BLAH minutes
+for
+pointing, secondary amplitude, and phase calibration, and 3C279 was observed as
+the primary
 absolute flux calibrator for D array observations.
-1055$+$018 and 3C279 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\lesssim
+1055$+$018 and 3C279 were observed as bandpass calibrators for C and D array
+observations, respectively, yielding $\lesssim
 $15\% calibration accuracy.
 
-The GILDAS package was used to reduce and analyze the visibility data which are then imaged and deconvolved using
-the CLEAN algorithm with ``natural" weighting.
-This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95.
-The final rms noise is $\sigma$ = 0.177 Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to 690 km s$^{-1}$), and $\sigma$ = 1.451 Jy km s$^{-1}$ beam$^{-1}$ over 10 MHz (21.5 km s$^{-1}$) .
+The GILDAS package was used to reduce and analyze the visibility data which are
+then imaged and deconvolved using
+the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
+beam size of 4$\farcs$44 $\times$ 1\farcs95. The final rms noise is $\sigma$ =
+0.177 
+Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to
+690 km s$^{-1}$), and $\sigma$ = 1.451 Jy km s$^{-1}$ beam$^{-1}$ over 10 MHz 
+(21.5 km s$^{-1}$) . 
 The continuum image is created by % 2.152 mm; 
-averaging over all the line-free channels ($\nu_{\rm cont}\sim$139 GHz). This yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15
+averaging over all the line-free channels ($\nu_{\rm cont}\sim$139 GHz). This
+yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15
 
@@
 %
-Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
+Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
+rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
 0.655BLAH 
- were carried out using the Combined Array for Research in Millimeter-wave Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: cf0098; PI: D. Riechers).
-observations were carried out on 2014 February 17 under good 3 mm weather conditions in the D array configurations.
-The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 12.5 MHz ($\sim$17BLAH km s$^{-1}$).
-The line was placed in the
-lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz; this resulted in 1.5 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.
+ were carried out using the Combined Array for Research in Millimeter-wave
+Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz
+(BLAH 
+mm) (Program ID: cf0098; PI: D. Riechers).
+observations were carried out on 2014 February 17 under good 3 mm weather
+conditions in the D array configurations. The 3 mm receivers were used to cover
+the 
+redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
+providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
+12.5 MHz ($
+\sim$17BLAH km s$^{-1}$). The line was placed in the
+lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
+this resulted in 1.5 hours of 15 antenna-equivalent on-source time after
+discarding 
+unusable visibility data.
 
 The nearby radio quasar 3C273 was observed every 15 minutes for
-pointing, amplitude, and phase calibration, and Mars was observed as the primary
-absolute flux calibrator. 3C279 was observed as bandpass calibrators, yielding $\sim
+pointing, amplitude, and phase calibration, and Mars was observed as the
+primary
+absolute flux calibrator. 3C279 was observed as bandpass calibrators, yielding
+$\sim
 $15\%BLAH calibration accuracy.
-The MIRIAD package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
-the CLEAN algorithm with ``natural" weighting.
-This yields a synthesized clean beam size of 3\farcs1 $\times$ 1\farcs9 for the lower sideband image cube.
-The final rms noise is $\sigma$ = BLAH Jy km s$^{-1}$ beam$^{-1}$ over a channel width of BKAH MHz (corresponding to BLAH km s$^{-1}$).
+The MIRIAD package was used to calibrate and analyze the visibility data which
+are imaged and deconvolved using
+the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
+beam size of 3\farcs1 $\times$ 1\farcs9 for the lower sideband image cube. The
+final 
+rms noise is $\sigma$ = BLAH Jy km s$^{-1}$ beam$^{-1}$ over a channel width of
+BKAH MHz (corresponding to BLAH km s$^{-1}$). 
 The continuum image is created by
-averaging over all the line-free channels ($\nu_{\rm cont}\sim$216 GHz). This yields a synthesized clean beam size of Blah\farcs5 $\times$ blah\farcs0 and an rms noise of 0.24Blah mJy beam$^{-1}$.
+averaging over all the line-free channels ($\nu_{\rm cont}\sim$216 GHz). This
+yields a synthesized clean beam size of Blah\farcs5 $\times$ blah\farcs0 and an
+rms 
+noise of 0.24Blah mJy beam$^{-1}$.
 
 \subsection{VLA} 
-Observations of the BLAH continuum ($\nu_{\rm rest}$ = BLAH GHz) toward the galaxy RXJ1131-1231 were carried out using the {\it Karl G.
-Jansky} Very Large Array (VLA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: BLAH; PI: BLAH).
-Observations were carried out on BLAH under excellent/GOOD? BLAH mm weather conditions in the A array configurations. The C-Band receivers were used to cover the BLAH
-, employing a correlator setup providing a bandwidth of BLAH GHz in each sideband. This resulted in BLAH hours of BLAH antenna-equivalent on-source time after discarding unusable visibility data.
+Observations of the BLAH continuum ($\nu_{\rm rest}$ = BLAH GHz) toward the
+galaxy RXJ1131-1231 were carried out using the {\it Karl G. Jansky} Very Large 
+Array (VLA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm)
+(Program ID: BLAH; PI: BLAH).
+Observations were carried out on BLAH under excellent/GOOD? BLAH mm weather
+conditions in the A array configurations. The C-Band receivers were used to 
+cover the BLAH
+, employing a correlator setup providing a bandwidth of BLAH GHz in each
+sideband. This resulted in BLAH hours of BLAH antenna-equivalent on-source time
+after 
+discarding unusable visibility data.
 
 The nearby radio quasar BLAH was observed every BLAH minutes for
-pointing, amplitude, and phase calibration, and BLAH was observed as the primary
-absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding $\sim
+pointing, amplitude, and phase calibration, and BLAH was observed as the
+primary
+absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding
+$\sim
 $15\% calibration accuracy.
-The AIPS package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
-the CLEAN algorithm with ``natural" weighting.
-This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image.
-The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.
-%
-%\section{Continuum}
-%%90.6797 GHz
-%% VLA sigma =  Jy
-%
-%no continuum detection..
-%Averaging over all the line-free channels, we did not detect the radio continuum down to 2$\sigma$ of blah mJy at an averaged frequency of $\nu_{cont}$ = 90.7 GHz.
-%
-%\begin{figure*}[tbph]
-%\centering
-%\includegraphics[width=0.80\textwidth]{../OverlayFig/ContPanel}
-%\caption{Left: Contours of the CARMA 90.7 GHz continuum emission (red) in the foreground radio galaxy 3C220.3 overlaid on the image and contours of the VLA 6 GHz continuum emission (lime).
-The rms in the VLA 6 GHz continuum image is $\sigma$ = 0.0641 mJy beam$^{-1}$.
-The synthesized beam size is 0$\farcs$596 $\times$ 0$\farcs$229, at P.A.
-75.79$\degr$.
-Lime contour levels start at $\pm$4$\times\sigma$ = x mJy beam$^{-1}$ and increment at steps of $\pm$2$\sigma$ for the VLA data; red contour levels start at $\pm$2$\sigma$, incrementing at steps of $\pm$1$\sigma$ = 0.24 mJy beam$^{-1}$.
-%Right:
-%Contour map of the 90.7 GHz continuum emission. The beam size is 16\farcs67$\pm
-%$0\farcs69 $\times$ 7\farcs17$\pm$1\farcs60, at P.A. = -57.9$\degr$. The contour levels start at $\pm$2$\sigma$ and increment at steps of $\pm$1$\sigma$ =0.5 mJy beam$^{-1}$.\label{fig:cont}}
-%\end{figure*}
-%
-%
-%\section{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
-%%- ! Parameters and Errors:
-%%- ! MFIT%PAR[01]   10.289188385009766        1.7304190817956480
-%%- ! MFIT%PAR[02]   51.276344299316406        29.649510734050978
-%%- ! MFIT%PAR[03]   147.87234497070312 * 2.355        30.276954728539007
-%%- ! MFIT%PAR[04]  0.34727144241333008       0.22560386117523606
-%%- channel [, ]
-%%- velocity range [,] km/s
-%%- Integrated line flux =
-%%- rms =
-%
-%%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
-%%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.
-%We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939+8315.
-We extract the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:mom0}, yielding peak flux density of 10.3 $\pm$ 1.7 mJy, the FWHM of the Gaussian fit is 541.65 $\pm$ 31.91 km s$^{-1}$.
-The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, where the synthesized beam size of the SMA observation is 1\farcs42$\times$1\farcs16, at P.A.
--34.0\degr.
-Since the angular resolution of our CO measurement is 13$\farcs$57 $\pm$ 1\farcs4 $\times$ 5\farcs77 $\pm$ 3\farcs1, the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is therefore spatially unresolved.
-We construct the velocity-integrated (moment-0) map of the CO($J$ = 3 $\rightarrow$ 2) emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux is 14.6 $\pm$ 0.9 Jy km s$^{-1}$.
-%
-%\begin{figure*}[tbph]
-%\centering
-%\includegraphics[width=0.8\textwidth]{../OverlayFig/CO32mom0}
-%\includegraphics[width=0.65\textwidth]{../OverlayFig/2.685bin2_arcNS_further_Sblob}
-%\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$2$\sigma$, incrementing at
-%steps of $\pm$1$\sigma$.
-Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$.
-The angular resolution is 13$\farcs$57 $\times$ 5\farcs77, at P.A.
-= -60.67$\degr$.
-%Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (lime contours) with $\sigma$=0.836951 mJy beam$^{-1}$.
-The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A.
--34.0\degr, as shown in the bottom left corner.
-From this image, it is apparent that the extent of the background SMG is smaller than the beam size of the CARMA data, hence the CO($J$ = 3 $\rightarrow$ 2) detection is spatially unresolved.
-%Bottom: The Gaussian-fitted line peak of CO($J$ = 3 $\rightarrow$ 2) is 23.36 $\pm$ 2.21 mJy beam$^{-1}$ (before continuum
-%subtraction), and the integrated line flux over linewidth of $\sim$500 km/s is 14.6 $\pm$ 0.9 Jy km s$^{-1}$
-%(after continuum subtraction).  \label{fig:mom0}}
-%\end{figure*}
-%
-%No significant continuum emission is detected from the line-free region down to a 1$\sigma$ limit of blah mJy.
-Neither CO(3-2) emission nor continuum emission are seen in the map near the NIR positions.
-%
-%at $z$ = 2.685, 1$\arcsec \sim$ 8.1 kpc
-%
+The AIPS package was used to calibrate and analyze the visibility data which
+are imaged and deconvolved using
+the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
+beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image. The final
+rms 
+noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.
 

### 2016-03-14 WRITEUP/Results.tex
fix alignment

@@
 
+\section{HST astrometry}
+We adopt the VLA 5\,GHz map as the reference coordinate frame and shift the
+coordinate frame in the optical image to this one to align the emission.
+
+Employed local phase calibrator, with positions known to $\sim$1 mas, estimate
+the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
+be better than 0.1", leaving aside uncertainties relating to SNR and beam size.
+
+The astrometry of the HST images was firstly calibrated against a wider-field
+optical image of the cluster which had in turn been aligned onto the FK5
+coordinate system to an rms precision of ~0.2".
+
+%The align the IRAM data (2-mm continuum and CO(J=2-1)) with the VLA 5-GHz
+%continuum emission, we shifted the former to the east by BLAH" in R.A., which is
+%consistent with the claimed astrometric precision of the PdBI images.
+
+To align the optical/NIR data with the VLA 5-GHz continuum emission, we
+shifted the former in Dec. by +BLAH".
+
 \section{CO($J$ = 3 $\rightarrow$ 2) line emission}
+
+Analysis using both set 2 and set 3 observations.
+
+natural weighting beam size:  3.19 x 1.86 PA: 8 deg
+channel width = 2x17.935 = 35.87 km/s
+rms = 1.32997E-02 Jy/B/channel
+
+ Integrated line flux = 37.509 Jy km/s over chan=[49,70] (FWZI)
 %- ! Parameters and Errors:
@@
 %- ! MFIT%PAR[04]  
-%- channel [, ]
 %- velocity range [,] km/s
-%- Integrated line flux =
-%- rms =
 
-%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
-%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.
+We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward
+SMM J0939+8315 at peak flux at blah $\sigma$ signifcance of $ \sigma$ = 13.2997
 
-We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background galaxies in RXJ1131-1231. 
-We extract the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:CO32mom0}, 
-yielding peak flux density of BLAH $\pm$ BLAH mJy, the FWHM of the Gaussian fit is BLAH $\pm$ BLAH km s$^{-1}$.
+mJy beam$^{-1}$.
 
-%No significant continuum emission is detected from the line-free region down to a 1$\sigma$ limit of blah mJy.
+We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
+background galaxies in RXJ1131-1231. 
+We extract the spectrum and fit a single-component Gaussian as shown in Figure
+\ref{fig:}
+yielding peak flux density of BLAH $\pm$ BLAH mJy, the FWHM of the Gaussian fit
+is BLAH $\pm$ BLAH km s$^{-1}$.
 
+\begin{figure}[tbph]
+\centering
+\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}	  
+\caption{
+CO32 line spectrum
+ \label{fig:}}
+\end{figure}
+
+We made a 1.4mm continuum map using line-free channels, $\sigma$ = 8.30807E-04
+Jy/B
+
+At spatial position of CO emission, No significant continuum emission was
+detected from the line-free region down to a 3$\sigma$ limit of blah mJy
+(burried in noise - 
+2.2 $\pm$ 3.0 mJy). Hence, we place a 3$\sigma$ upper limit of BLAH.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{CO($J$ = 2 $\rightarrow$ 1) line emission}
-We detect dynamically resolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background galaxies in RXJ1131-1231.
+natural weighting beam size: 4.44 x 1.95, PA 13deg
+rms = ~ 1.451 mJy/ Beam/ch
+velocity resolution per bin: 21.528154 km/s
+source extent?
 
-We construct the velocity-integrated (0th moment) map of the CO($J$ = 2 $\rightarrow$ 1) emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 2 $\rightarrow$ 1) line flux is BLAH $\pm$ BLAH Jy km s$^{-1}$.
+We detect dynamically resolved CO($J$ = 2 $\rightarrow$ 1) line emission toward
+the background galaxies in RXJ1131-1231.
+
+We construct the velocity-integrated (0th moment) map of the CO($J$ = 2
+$\rightarrow$ 1) emission using the uv-continuum subtracted data, the
+velocity-integrated 
+CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ BLAH Jy km s$^{-1}$.
 
 % upper limit on other lines 
-% in the background source -- H2CO
+% in the foreground galaxy -- HNC (J=2-1)
 
-% in the foreground galaxy -- H2CO, HNC (J=2-1)
 \begin{figure*}[tbph]
 \centering
-\includegraphics[width=0.35\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
+\includegraphics[width=0.35\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}	   
 \includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
@@
 \caption{
-0th Moment map of CO(2-1) emission on HST F555W.
+0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping
 Spectrum. Velocity scale w.r.t z=0.655
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
+\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       
 \caption{
-1st and 2nd order moments
+1st and 2nd order moments, clipped at 5 $\sigma$
  \label{fig:}}
@@
 \centering
-\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
+\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}	 %
+figures are in ../Figures/ for now, before we decided which ones will
+definitely go into 
+paper
 \caption{
-Black crosses indicate the position of the lensed AGN (components ABCD) and the foreground lensing galaxy (component G) in the HST image.
+Black crosses indicate the position of the lensed AGN (components ABCD) and the
+foreground lensing galaxy (component G) in the HST image.
  \label{fig:chanmap}}
@@
 \centering
-\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
+\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}   
+   % figures are in ../Figures/ for now, before we decided which ones will
+definitely go 
+into paper
 \caption{ 
@@
 
-%
-%\begin{figure*}[tbph]
-%\centering
-%\includegraphics[width=0.8\textwidth]{}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
-%\includegraphics[width=0.65\textwidth]{}
-%\caption{
-% \label{fig:}}
-%\end{figure*}
-
 \section{Continuum}
 
-%
-%\begin{figure*}[tbph]
-%\centering
-%\includegraphics[width=0.80\textwidth]{}
-%\caption{Left: Contours of the CARMA BLAH GHz continuum emission (red) in the foreground radio galaxy 3C220.3 overlaid on the image and contours of the VLA 6 GHz continuum emission (lime).
-The rms in the VLA 6 GHz continuum image is $\sigma$ = 0.0641 mJy beam$^{-1}$.
-The synthesized beam size is 0$\farcs$596 $\times$ 0$\farcs$229, at P.A.
-75.79$\degr$.
-Lime contour levels start at $\pm$4$\times\sigma$ = x mJy beam$^{-1}$ and increment at steps of $\pm$2$\sigma$ for the VLA data; red contour levels start at $\pm$2$\sigma$, incrementing at steps of $\pm$1$\sigma$ = 0.24 mJy beam$^{-1}$.
-%Right:
-%Contour map of the 90.7 GHz continuum emission. The beam size is 16\farcs67$\pm
-%$0\farcs69 $\times$ 7\farcs17$\pm$1\farcs60, at P.A. = -57.9$\degr$. The contour levels start at $\pm$2$\sigma$ and increment at steps of $\pm$1$\sigma$ =0.5 mJy beam$^{-1}$.\label{fig:cont}}
-%\end{figure*}
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.8\textwidth]{../Figures/ContCO21.eps}	  
+\caption{CO 21 moment0 with coninuum
+ \label{fig:}}
+\end{figure*}
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.8\textwidth]{../Figures/Cont2mm_5GHz_double.eps}    
+\caption{VLA 5GHz continuum and PdBI 2mm continuum
+ \label{fig:}}
+\end{figure*}
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
+\includegraphics[width=0.55\textwidth]{../Figures/F555W_ContVLA.eps}
+\caption{
+radio continuum contours on HST image
+ \label{fig:}}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SED}
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}	 
+\caption{VLA 5GHz continuum and PdBI 2mm continuum
+ \label{fig:}}
+\end{figure*}
+
+\input{table_photometry_AAScustomized}
 

### 2016-03-15 WRITEUP/Results.tex
with DR's comments on how to improve figs

@@
 1st and 2nd order moments, clipped at 5 $\sigma$
+TODO: enlarge and choose better velocity interval
  \label{fig:}}
@@
 \includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}	 %
-figures are in ../Figures/ for now, before we decided which ones will
-definitely go into 
-paper
 \caption{
@@
 foreground lensing galaxy (component G) in the HST image.
+TODO: Change sym for fg gal., add one chan before and after first and last.; change colorbar scale to mJy/B, add tick in negative direction.
+try 3sigma steps to see if can show more structures in channel slice
  \label{fig:chanmap}}
@@
 \includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}   
-   % figures are in ../Figures/ for now, before we decided which ones will
-definitely go 
-into paper
 \caption{ 
 Spatial spectra, binned by 3 pixels in each direction (1\farcs5)
+TODO: add velo scale; larger labels for pixel pos
  \label{fig:spatialSpec}}
@@
 \caption{
-radio continuum contours on HST image
+can kill left figure eventually by combining this to ContCO21.eps
+Right: alignment of HST and VLA 5 GHz continuum
  \label{fig:}}
@@
 \caption{VLA 5GHz continuum and PdBI 2mm continuum
+TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 2mm PdBI (now integrated and peak), might want to extract flux after removing a point source model.
+WANT TO MAKE SED FITTING with POWER LAW including the one point from 24.0\micron, from Spitzer/MIPS .
+Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux extraction, which might not be resolving the source and not including everything. 
+Might want to add NVSS constraints.
+
  \label{fig:}}

### 2016-03-28 WRITEUP/Obs.tex
take into account DR's comments on cosmetics

@@
 underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing
-a correlator setup providing an effective bandwidth of 3.16 GHz and spectral 
+a correlator setup providing an effective bandwidth of 3.6 GHz and spectral 
 resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
@@
 the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
-beam size of 4$\farcs$44 $\times$ 1\farcs95. The final rms noise is $\sigma$ =
+beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA: 13\degr). The final rms noise is $\sigma$ =
 0.177 
@@
 % LO = 215.6694 Ghz
-% 3C273 FG
-% 3C279 Bandpass
-% mars flux
-% after flagging: Total observing time is  1.48 hours, checked with uvindex
+% 1127-189 Gain for set 2
+% 3C273 gain for set 3
+% 3C279 Bandpass for both
+% mars flux for both
+% after flagging: Total observing time is  1.48 hours, checked with uvindex for
+set 3
+% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
+combined set
+% 12.500 GHz <=> 17.935 km/s
 %
@@
 Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz
-(BLAH 
-mm) (Program ID: cf0098; PI: D. Riechers).
+(BLAH mm) (Program ID: cf0098; PI: D. Riechers).
 observations were carried out on 2014 February 17 under good 3 mm weather
-conditions in the D array configurations. The 3 mm receivers were used to cover
+conditions and on 2014 February 02 under terrible 3mm weather in the D array
+configurations.
+
+The 3 mm receivers were used to cover
 the 
@@
 12.5 MHz ($
-\sim$17BLAH km s$^{-1}$). The line was placed in the
+\sim$17.9 km s$^{-1}$). The line was placed in the
 lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
-this resulted in 1.5 hours of 15 antenna-equivalent on-source time after
+this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
 discarding 
@@
 
-The nearby radio quasar 3C273 was observed every 15 minutes for
-pointing, amplitude, and phase calibration, and Mars was observed as the
+The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
+pointing, amplitude, and phase calibration. Mars was observed as the
 primary
-absolute flux calibrator. 3C279 was observed as bandpass calibrators, yielding
+absolute flux calibrator and 3C279 was observed as bandpass calibrators for
+both tracks. 
+The phase calibrator J1127-189 from the first track is faint and observed under
+poor weather and the phase calibrator 3C273 is far from source for the second
+track. Hence, the phase calibration was 
+subpar, with rms scatter $\sim$ 60\degr, 
+yielding
 $\sim
-$15\%BLAH calibration accuracy.
+$20\% calibration accuracy.
 The MIRIAD package was used to calibrate and analyze the visibility data which
@@
 the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
-beam size of 3\farcs1 $\times$ 1\farcs9 for the lower sideband image cube. The
+beam size of 3\farcs2 $\times$ 1\farcs9 (PA: 8\degr) for the lower sideband
+image cube. The
 final 
-rms noise is $\sigma$ = BLAH Jy km s$^{-1}$ beam$^{-1}$ over a channel width of
-BKAH MHz (corresponding to BLAH km s$^{-1}$). 
-The continuum image is created by
-averaging over all the line-free channels ($\nu_{\rm cont}\sim$216 GHz). This
-yields a synthesized clean beam size of Blah\farcs5 $\times$ blah\farcs0 and an
-rms 
-noise of 0.24Blah mJy beam$^{-1}$.
+rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$ over a channel width
+of
+25 MHz (corresponding to 35.87 km s$^{-1}$).
 

### 2016-03-28 WRITEUP/Results.tex
take into account DR's comments on cosmetics

@@
 \usepackage{amsmath}
+\input{preamble}
 \begin{document}
@@
 \section{HST astrometry}
-We adopt the VLA 5\,GHz map as the reference coordinate frame and shift the
-coordinate frame in the optical image to this one to align the emission.
+We adopt the VLA 5\,GHz map of BLAH resolution as the reference coordinate frame and align the optical image. We shifted the 
+latter to the east by BLAH" in R.A and BLAH in declination., which is consistent with the typical astrometric precision of the HST image. 
+The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas. 
+We estimate the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
+be better than 0.1", leaving aside uncertainties relating to the SNR and beam size.
 
-Employed local phase calibrator, with positions known to $\sim$1 mas, estimate
-the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
-be better than 0.1", leaving aside uncertainties relating to SNR and beam size.
-
-The astrometry of the HST images was firstly calibrated against a wider-field
-optical image of the cluster which had in turn been aligned onto the FK5
-coordinate system to an rms precision of ~0.2".
-
-%The align the IRAM data (2-mm continuum and CO(J=2-1)) with the VLA 5-GHz
-%continuum emission, we shifted the former to the east by BLAH" in R.A., which is
-%consistent with the claimed astrometric precision of the PdBI images.
-
-To align the optical/NIR data with the VLA 5-GHz continuum emission, we
-shifted the former in Dec. by +BLAH".
+%The astrometry of the HST images was firstly calibrated against a wider-field
+%optical image of the cluster which had in turn been aligned onto the FK5
+%coordinate system to an rms precision of ~0.2".
 
@@
 
-Analysis using both set 2 and set 3 observations.
+% Integrated line flux: 37.509 Jy km/s over chan=[49,70] (FWZI) of sigma = 13.3mJy /B/channel of 35.87 km/s per channel
+%  57.753459930419922        10.658399798838524
+% 38.906448364257812        54.223567641493943
+% 258.26144409179688        57.450322398332851
+% 2.2153112888336182        2.9563491085933622
 
-natural weighting beam size:  3.19 x 1.86 PA: 8 deg
-channel width = 2x17.935 = 35.87 km/s
-rms = 1.32997E-02 Jy/B/channel
-
- Integrated line flux = 37.509 Jy km/s over chan=[49,70] (FWZI)
-%- ! Parameters and Errors:
-%- ! MFIT%PAR[01]  
-%- ! MFIT%PAR[02]  
-%- ! MFIT%PAR[03]  
-%- ! MFIT%PAR[04]  
-%- velocity range [,] km/s
-
-We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward
-SMM J0939+8315 at peak flux at blah $\sigma$ signifcance of $ \sigma$ = 13.2997
-
-mJy beam$^{-1}$.
+% If we fit gaussian without the continuum to minimize error:
+% 58.848747253417969        10.030933764224825
+% 36.368530273437500        54.749284630860281
+% 276.93515014648438        54.753666156237443
 
@@
 We extract the spectrum and fit a single-component Gaussian as shown in Figure
-\ref{fig:}
-yielding peak flux density of BLAH $\pm$ BLAH mJy, the FWHM of the Gaussian fit
-is BLAH $\pm$ BLAH km s$^{-1}$.
+\ref{fig:co32spec}
+yielding peak flux density of 57.8 $\pm$ 10.7 mJy, the FWHM of the Gaussian fit
+is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in the calibration.
 
@@
 CO32 line spectrum
- \label{fig:}}
+ \label{fig:co32spec}}
 \end{figure}
 
-We made a 1.4mm continuum map using line-free channels, $\sigma$ = 8.30807E-04
-Jy/B
+% line free channels:1,118,160,600
+% nchan =(117+600-160+1) = 558
+% sigma =  0.83 mJy/B
 
 At spatial position of CO emission, No significant continuum emission was
-detected from the line-free region down to a 3$\sigma$ limit of blah mJy
-(burried in noise - 
-2.2 $\pm$ 3.0 mJy). Hence, we place a 3$\sigma$ upper limit of BLAH.
+detected from the line-free channels down to a 3$\sigma$ limit of 2.49mJy Beam\pmOne.
+(also as suggested in the fitted Gaussian to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
 
@@
 \section{CO($J$ = 2 $\rightarrow$ 1) line emission}
-natural weighting beam size: 4.44 x 1.95, PA 13deg
-rms = ~ 1.451 mJy/ Beam/ch
-velocity resolution per bin: 21.528154 km/s
-source extent?
+
+% intensity over chan 124, 156 of rms ~ 1.451 mJy/ Beam/ch
+% velocity resolution per bin: 21.528154 km/s
+
+%sigma_mom0 = 0.43  over chan: 127, 155
 
@@
 velocity-integrated 
-CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ BLAH Jy km s$^{-1}$.
+CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ 0.2 Jy km s$^{-1}$.
 
-% upper limit on other lines 
-% in the foreground galaxy -- HNC (J=2-1)
+We place an upper limit on HNC (J=2-1) line emission at the rest-shifted frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.451mJy per channel per beam.
+Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$ limit of 4.353 mJy \kms beam\pmOne.
 
@@
 \caption{
-0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping
+0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping, of $\sigma$ 0.43 mJy beam\pmOne. 
 Spectrum. Velocity scale w.r.t z=0.655
@@
 \caption{
-1st and 2nd order moments, clipped at 5 $\sigma$
-TODO: enlarge and choose better velocity interval
- \label{fig:}}
+1st and 2nd order moments, clipped at 5 $\sigma$. 1st moment contour steps of 50 \kms, 2nd moment steps of 100 \kms.
+velocity range in z=0 frame = [-530.33, 72.73] \kms
+chan = [127, 155] 
+sigma = 0.16821825 Jy \kms per Beam
+theshold: 5*sigma = 7.2550e-3 Jy per beam (per channel)
+ \label{fig:highOmoments}}
 \end{figure}
@@
 \caption{
-Black crosses indicate the position of the lensed AGN (components ABCD) and the
-foreground lensing galaxy (component G) in the HST image.
-TODO: Change sym for fg gal., add one chan before and after first and last.; change colorbar scale to mJy/B, add tick in negative direction.
-try 3sigma steps to see if can show more structures in channel slice
+Black crosses indicate the position of the lensed AGN (components ABCD) and the central white-filled star indicates the
+position of the foreground lensing galaxy (component G) as detected in the HST image.
  \label{fig:chanmap}}
@@
 Spatial spectra, binned by 3 pixels in each direction (1\farcs5)
-TODO: add velo scale; larger labels for pixel pos
  \label{fig:spatialSpec}}
@@
 \section{Continuum}
+
+% 2mm continuum averaged over chan 1 120 165 360
+% number of channels = 316
+% sigma = 1.451 mJy/B / sqrt(316) = 0.081625 mJy/B 
+% go noise on map (whole map) after cleaning: 89.274 µJy/B
+% F = 1.2 mJy (integrated spatially, from ~ 1 sigma contour; 150 pixels)
 
@@
 \section{SED}
+
+We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side and including the 24.0\micron data from Spitzer/MIPS to constrain the dust peak.
+
 \begin{figure*}[tbph]
@@
 TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 2mm PdBI (now integrated and peak), might want to extract flux after removing a point source model.
-WANT TO MAKE SED FITTING with POWER LAW including the one point from 24.0\micron, from Spitzer/MIPS .
 Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux extraction, which might not be resolving the source and not including everything. 
 Might want to add NVSS constraints.
-
  \label{fig:}}

### 2016-03-28 PdBI/src/pythonPLOT/COChan.py

@@ -1,11 +1,19 @@
 '''
-Last Modified: 31 Dec 15
+Last Modified: 27 Mar 16
 
 
 Author: Daisy Leung
 
 
 History:
+27 Mar 2016
+- change symbol for foreground galaxy
+- increment contour by 3sigma instead of 4 sigma
+- add channels before first and after last
+- don't put legend for markers (don't fit in there now with more panels)
+- change colorbar ticks to mJy B^-1
+- change xaxis tick frequency to avoid overlap labeling
+
 31 Dec 2015
 - update HST coordinates, see HSTmarkers.txt
 
@@ -31,7 +39,7 @@ Note:
 -
 
 '''
-
+import matplotlib
 import matplotlib.pyplot as plt
 import pywcsgrid2
 import pywcs
@@ -43,7 +51,14 @@ import mpl_toolkits.axes_grid1.axes_grid as axes_grid
 from mpl_toolkits.axes_grid1.inset_locator import inset_axes
 from mpl_toolkits.axes_grid1.anchored_artists import AnchoredText
 
+font = {'family': 'Arial Narrow',
+        'weight': 'bold',
+        'size': 8.75}
+matplotlib.rc('font', **font)
+
+
 class Velo(object):
+
     def __init__(self, header):
         wcs = pywcs.WCS(header)
         self.wcs_vel = wcs.sub([3])        # velocity is 3rd axis
@@ -56,14 +71,14 @@ class Velo(object):
 def setup_axes(fig, header, nx, ny):
 
     gh = pywcsgrid2.GridHelper(wcs=header)
-    gh.locator_params('x', nbins=3)
+    gh.locator_params('x', nbins=2)
 
     g = axes_grid.ImageGrid(fig, 111,
                             nrows_ncols=(ny, nx),
                             ngrids=None,
                             direction='row',
                             # axes_pad=0.02,
-                            axes_pad = 0.0,    # between panels
+                            axes_pad=0.0,    # between panels
                             add_all=True,
                             share_all=True,
                             # if share_all = False, need the following
@@ -76,16 +91,17 @@ def setup_axes(fig, header, nx, ny):
 
     # only show xylabel at that panel, depending on nrows_ncols in axes_grid.ImageGrid()
     # if comment out the following block, will shorten to Greek Letters
-    ax = g[-1*nx]     # display in the bottom left corner only
[…]

### 2016-03-28 src/SED/SEDplot.py
update IRAC flux to using 5.8arcsec diameter aperture

@@ -117,7 +117,7 @@ ax.set_xscale("log")
 
 ax.set_ylabel(r'$\rm S_{\nu}$ [mJy]', fontsize=16)
 ax.set_xlabel(r'$\rm \lambda [\mu$m]', fontsize=16)
-ax.set_title("SED ", x=0.5, y=1.125)
+# ax.set_title("SED ", x=0.5, y=1.125)
 
 led = plt.legend(loc='best', fontsize=15, numpoints=1,
                  fancybox=True, borderpad=0.5,

### 2016-03-28 src/SED/tablePhotometry.py

@@ -1,3 +1,5 @@
+#!/usr/bin/env python
+
 '''
 
 Organize RXJ1131 IR photometry data using astropy table:
@@ -5,7 +7,7 @@ wavelength [um], freq [GHz], flux density [mJy], flux_err [mJy], instrument
 Save table as latex file
 
 
-Last Modified: Jan 09 2016
+Last Modified: March 28 2016
 
 
 TODO
@@ -13,6 +15,8 @@ TODO
 
 History
 -------
+Mar 28 2016:
+    updated SPITZER/IRAC data to using 5.8" diameter aperture flux
 Jan 09 2016:
     combine flux col with flux err col in latex table
     separate out column name with unit in latex table
@@ -52,11 +56,11 @@ data_rows = [(1.25, (1.25*u.micron).to(u.GHz, equivalencies=u.spectral()).value
              (22, (22*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
               55.11, 1.878, 'WISE/W4'),
              (4.5, (4.5*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
-              6.241, 0.00207, 'Spitzer/IRAC'),
+              7.803, 0.002082 , 'Spitzer/IRAC'),
              (5.8, (5.8*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
-              9.354, 0.005694, 'Spitzer/IRAC'),
+              10.72, 0.00512, 'Spitzer/IRAC'),
              (8.9, (8.9*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
-              13.56, 0.004518, 'Spitzer/IRAC'),
+              14.47, 0.004122, 'Spitzer/IRAC'),
              (24, (24*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
               47.18, 0.02621, 'Spitzer/MIPS'),
              (250, (250*u.micron).to(u.GHz, equivalencies=u.spectral()).value,

### 2016-03-29 WRITEUP/Lensmodel.tex
table report magnification factors across channels

--- 2015-12-28 WRITEUP/Lensmodel.tex
@@
 \subsection{interpretation}
-- C06 suggest the presence of an interacting dusty galaxy in their HST observations, which BJB+08 calls it the F component.
-The lensed images of the ABCDE components coincide with our CO data (see mom0 on HST and channel map), evidently CO emission coming from the AGN host galaxy.
-- one of the red channels in our lens model suggests a second source component, which is consistent with the spatially offset dusty source (see mom0 on HST, which the red velocity component coincides with this F component)
+- C06 suggest the presence of an interacting dusty galaxy in their HST
+observations, which BJB+08 calls it the F component. The lensed images of the
+ABCDE 
+components coincide with our CO data (see mom0 on HST and channel map),
+evidently CO emission coming from the AGN host galaxy. 
+- one of the red channels in our lens model suggests a second source component,
+which is consistent with the spatially offset dusty source (see mom0 on HST,
+which 
+the red velocity component coincides with this F component)
+
+%%%%%%%%%%%%%%%%%%%%%%%%
++ Compare our lens model parameters on the mass distribution of the lensing
+galaxy with literature (specifically SIE model in C06)
+	- C06: SIE model shows position of lensing mass is offset by (-0.015",
+-0.041" from obs. (i.e. light centroid)); PA = -73.6, ellipticity = 0.45,
+theta\_R = 1.84" $\pm$ 0.01 
+	- Our model lens parameters (median):
+		- file: WRITEUP/MedianLensModelParams.txt
+		- lensing gal. position is consistent with C06, 
+		- Einstein radius: consistent with C06
+		- PA: consistent within errors
+		- Axial ratio: consistent within errors
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\input{table_magFactor}
 
@@
 \caption{
-velocity gradient of the lens model in the lens plane (left), source plane (right).
+velocity gradient of the lens model in the lens plane (left), source plane
+(right).
 \label{fig:}}

### 2016-03-29 WRITEUP/table_magFactor.tex
table report magnification factors across channels

\begin{deluxetable}{lccc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{\rot{2}{1} Magnification factors.}
\tablehead{
\colhead{channel} & 
\colhead{Source 1 $\mu_{\rm L}$} & 
\colhead{Source 2 $\mu_{\rm L}$} & 
}
\startdata
126-130 & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ %which is source 1 and 2 then?
131-135 & 7.6 $\pm$ 1.6 & \\ % would this be source 1 or 2?
136-140 & 8.7 $\pm$ 2.0 & \\
141-145 & 4.1 $\pm$ 0.9 & \\
146-150 & 4.2 $\pm$ 0.6 & \\
151-156 & 4.3 $\pm$ 2.4 & \\
156-160 & 3.1 $\pm$ 0.9 & \\
weighted average & 4.4 & \\
median & 5.5 &  \\
\enddata
\label{tab:mag}
\tablecomments{blah}
 %TablenotegoesBetween 
\tablerefs{blah}
\end{deluxetable}

### 2016-03-29 PdBI/data/28Mar16/cont_subtractFg.py
code to subtract a point source model in the UV plane with MIRIAD & CASA, but doesn't work

@@ -1,0 +1,59 @@
+'''
+
+Continuum is mostly unresolved, can just take peak as the foreground emission.
+subtract a point source model as the foreground, then extract the flux for the arc
+
+Note
+----
+- have attempted this in CASA before in 10Nov15/, which has same problem as here -- uvmodelfit throws an error
+
+'''
+import os
+
+uvfiles = ['co21_trial1_cont_UVstyle.uvfits', 'co21_trial1_cont_AIPSstyle.uvfits']
+for i in uvfiles:
+    importuvfits(fitsfile=i, vis=i.replace('.uvfits', '.ms'))
+
+# copy over antenna tables
+os.system('cp -r ' + uvfiles[1].replace('.uvfits', '.ms') + '/ANTENNA/* ' + uvfiles[0].replace('.uvfits', '.ms')+'/ANTENNA/.')
+os.system('cp -r ' + uvfiles[1].replace('.uvfits', '.ms') + '/POINTING/* ' + uvfiles[0].replace('.uvfits', '.ms')+'/POINTING/.')
+os.system('cp -r ' + uvfiles[1].replace('.uvfits', '.ms') + '/FEED/* ' + uvfiles[0].replace('.uvfits', '.ms')+'/FEED/.')
+os.system('cp -r ' + uvfiles[1].replace('.uvfits', '.ms') + '/HISTORY/* ' + uvfiles[0].replace('.uvfits', '.ms')+'/HISTORY/.')
+
+# coord of G (astrometric corrected)
+ra, dec = 172.9643456388, -12.532862944
+fixvis(vis=uvfiles[0].replace('.uvfits', '.ms'), outputvis=uvfiles[0].replace('.uvfits', '.fixvis.ms'), phasecenter='J2000 11h31m51.44 -12d31m58.3')
+
+vis = 'co21_trial1_cont_UVstyle.fixvis.ms'
+plotms(vis=vis, xaxis='uvwave', yaxis='real', ydatacolumn='data')
+exportuvfits(vis=vis, fitsfile=vis.replace('.ms', '.uvfits'), datacolumn='data')
+
+newvis = vis.replace('.ms', '.pointModel.ms')
+os.system('cp -r ' + vis + ' ' + newvis)
+default('uvmodelfit')
+comptype = 'P'
+sourcepar = [800e-6, 0, 0]
+vis = newvis
+field = '0'
+spw = ''
+outfile = newvis.replace('.ms', '.uvmodelfit.cl')
+inp()
+uvmodelfit()
+
[…]

### 2016-03-29 WRITEUP/Intro.tex
combine with Obs.tex

--- 2016-03-28 WRITEUP/Obs.tex
@@
 \usepackage{amsmath}
+\input{preamble}
+\slugcomment{To be submitted to the ApJ}
+
+\citestyle{aa}
+\shorttitle{TBD}
+\shortauthors{Leung}
+
 \begin{document}
+%{\tiny  \RevisionInfo}
+
+\title{}
 \author{Draft}
+\affil{Department of Astronomy, Space Sciences Building, Cornell University,
+Ithaca, NY 14853, USA; \myemail}
+
+\begin{abstract}
+\end{abstract}
+
+\section{Introduction} 
+The gravitational lens RXJ 1131-1231 was discovered with spectroscopic
+redshifts of the lens and the QSO are $z_{\rm L}$ = 0.295 and
+$z_\textrm{AGN,HST}$ = 
+0.658, respectively \citep{
+
+% FG gal is an elliptical gal: Slues+03 absorption lines
+
+As detected in the HST images, RXJ1131-1231 is a quadruply imaged AGN with Einstein ring of size 1\farcs83 in radius. The 
+background AGN is lensed into 4 point-like image A,B,C,D on a ring (emission from the AGN host galaxy) around G, the foreground galaxy. 
+C06 report the redshift of the background AGN of 0.658 with magnification ~ 9, claimed Seyfert 1 spiral galaxy.
 
@@
 Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
-rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
-0.655BLAH
+rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.654
  were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
-redshifted frequency of $\nu_{\rm obs}$ = 
- BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
+(Program ID: S14BX001; PI: D. Riechers). 
  Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
-%2 mm
 weather conditions in the C and D array configurations, respectively. The 2 mm
@@
 and the 
-underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing
+underlying continuum emission (rest-frame 3.6 mm), employing
 a correlator setup providing an effective bandwidth of 3.6 GHz and spectral 
@@
 This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time
-
 after discarding unusable visibility data.
-% D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp),
-1124-106(ditto)
+% D: 1.5 hours; 1055+018 (BP) , 3C279 (RF, fixed flux), 1127-145 (phase/amp),
+% 1124-186(ditto)
 % C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186
-(phase/amp), 1127-145 (ditto)
+% (phase/amp), 1127-145 (ditto)
 % total: 3.75 hours
@@
 for
-pointing, secondary amplitude, and phase calibration, and MWC349 was observed
+pointing, secondary amplitude, and phase calibration and 1055$+$018 was observed as bandpass calibrators 
+for both tracks.
+MWC349 and 3C279 were observed
 as the primary
-absolute flux calibrator for C array observations.
-The nearby quasars 1127$-$145 and 1124$-$106 were observed every BLAH minutes
-for
-pointing, secondary amplitude, and phase calibration, and 3C279 was observed as
-the primary
-absolute flux calibrator for D array observations.
-1055$+$018 and 3C279 were observed as bandpass calibrators for C and D array
-observations, respectively, yielding $\lesssim
+absolute flux calibrator for C and D array observations, respectively, yielding $\lesssim
 $15\% calibration accuracy.
@@
 % after flagging: Total observing time is  1.48 hours, checked with uvindex for
-set 3
+% set 3
 % after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
-combined set
+% combined set
 % 12.500 GHz <=> 17.935 km/s
@@
 rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
-0.655BLAH 
+0.654
  were carried out using the Combined Array for Research in Millimeter-wave
-Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz
-(BLAH mm) (Program ID: cf0098; PI: D. Riechers).
+Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers).
 observations were carried out on 2014 February 17 under good 3 mm weather
 conditions and on 2014 February 02 under terrible 3mm weather in the D array
-configurations.
-
-The 3 mm receivers were used to cover
+configurations.  The 3 mm receivers were used to cover
 the 
@@
 unusable visibility data. 
-
 The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
@@
 $\sim
-$20\% calibration accuracy.
+$BLAH\% calibration accuracy.
+% flux scale uncertainty
+% gain variation over time
+% phase scatter 
+%
 The MIRIAD package was used to calibrate and analyze the visibility data which
@@
 \subsection{VLA} 
-Observations of the BLAH continuum ($\nu_{\rm rest}$ = BLAH GHz) toward the
+% 20081229
+% flux 1331+305
+% phase 1130-149
+
+Observations of the radio continuum toward the
 galaxy RXJ1131-1231 were carried out using the {\it Karl G. Jansky} Very Large 
-Array (VLA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm)
-(Program ID: BLAH; PI: BLAH).
-Observations were carried out on BLAH under excellent/GOOD? BLAH mm weather
+Array (VLA; Program ID: AW741; PI: Wucknitz).
+Observations were carried out on BLAH under excellent/GOOD? weather
 conditions in the A array configurations. The C-Band receivers were used to 

### 2016-03-29 WRITEUP/Intro.tex
before linewrap

@@
 \shorttitle{TBD}
-\shortauthors{Leung}
+\shortauthors{Leung \& Riechers}
 
@@
 
-\title{}
-\author{Draft}
-\affil{Department of Astronomy, Space Sciences Building, Cornell University,
-Ithaca, NY 14853, USA; \myemail}
+\title{Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654}
+\author{T. K. Daisy Leung and Dominik A. Riechers}
+\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}
 
@@
 $z_\textrm{AGN,HST}$ = 
-0.658, respectively \citep{
+0.658, respectively \citep{}
 
@@
 %For both tracks, 
-The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes
+The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
 for

### 2016-03-29 WRITEUP/Intro.tex
combine with Lensmodel.tex

@@
 \author{T. K. Daisy Leung and Dominik A. Riechers}
-\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}
+\affil{Department of Astronomy, Space Sciences Building, Cornell University,
+Ithaca, NY 14853, USA; \myemail}
 
@@
 
-As detected in the HST images, RXJ1131-1231 is a quadruply imaged AGN with Einstein ring of size 1\farcs83 in radius. The 
-background AGN is lensed into 4 point-like image A,B,C,D on a ring (emission from the AGN host galaxy) around G, the foreground galaxy. 
-C06 report the redshift of the background AGN of 0.658 with magnification ~ 9, claimed Seyfert 1 spiral galaxy.
+As detected in the HST images, RXJ1131-1231 is a quadruply imaged AGN with
+Einstein ring of size 1\farcs83 in radius. The 
+background AGN is lensed into 4 point-like image A,B,C,D on a ring (emission
+from the AGN host galaxy) around G, the foreground galaxy. 
+C06 report the redshift of the background AGN of 0.658 with magnification ~ 9,
+claimed Seyfert 1 spiral galaxy.
 
@@
 Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
-rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.654
+rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ =
+0.654
  were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
@@
 for
-pointing, secondary amplitude, and phase calibration and 1055$+$018 was observed as bandpass calibrators 
+pointing, secondary amplitude, and phase calibration and 1055$+$018 was
+observed as bandpass calibrators 
 for both tracks.
@@
 as the primary
-absolute flux calibrator for C and D array observations, respectively, yielding $\lesssim
+absolute flux calibrator for C and D array observations, respectively, yielding
+$\lesssim
 $15\% calibration accuracy.
@@
 the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
-beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA: 13\degr). The final rms noise is $\sigma$ =
+beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA: 13\degr). The final rms noise
+is $\sigma$ =
 0.177 
@@
 Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
-rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
-0.654
+rest}$ = 345.7959899 GHz) 
+%toward the background galaxy RXJ1131-1231 at $z$ = 0.654
  were carried out using the Combined Array for Research in Millimeter-wave
-Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers).
-observations were carried out on 2014 February 17 under good 3 mm weather
+Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers) on 2014 February 17 
+under good 3 mm weather
 conditions and on 2014 February 02 under terrible 3mm weather in the D array
@@
 this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
-discarding 
-unusable visibility data. 
+flagging poor visibility data. 
 The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
@@
 both tracks. 
-The phase calibrator J1127-189 from the first track is faint and observed under
-poor weather and the phase calibrator 3C273 is far from source for the second
-track. Hence, the phase calibration was 
-subpar, with rms scatter $\sim$ 60\degr, 
-yielding
-$\sim
-$BLAH\% calibration accuracy.
-% flux scale uncertainty
-% gain variation over time
-% phase scatter 
-%
+% poor phase note
+Since the phase calibrator from the first track is faint and was observed under
+poor weather and the phase calibrator used for the second track was
+far from our target source.
+Hence, the phase calibration was 
+subpar, with rms scatter $\sim$ 60\degr. 
+We estimate $\sim
+$BLAH\% calibration accuracy based on the flux scale uncertainties, gain variation over time, and 
+the calibrated phase scatter.
 The MIRIAD package was used to calibrate and analyze the visibility data which
@@
 
+\section{\rot{2}{1} Lens model}
+
+\subsection{interpretation}
+- C06 suggest the presence of an interacting dusty galaxy in their HST
+observations, which BJB+08 calls it the F component. The lensed images of the
+ABCDE 
+components coincide with our CO data (see mom0 on HST and channel map),
+evidently CO emission coming from the AGN host galaxy. 
+- one of the red channels in our lens model suggests a second source component,
+which is consistent with the spatially offset dusty source (see mom0 on HST,
+which 
+the red velocity component coincides with this F component)
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+We compare our lens model parameters on the mass distribution of the lensing
+galaxy with literature, particularly against the SIE model presented by C06. 
+In C06, their SIE model shows position of lensing mass is offset by (-0.015",
+-0.041" from obsservations (i.e. light centroid)); PA = -73.6, ellipticity = 0.45,
+theta\_R = 1.84" $\pm$ 0.01. 
+Our best-fit model parameters finds a BLAH
+	- Our model lens parameters (median):
+		- file: WRITEUP/MedianLensModelParams.txt
+		- lensing gal. position is consistent with C06, 
+		- Einstein radius: consistent with C06
+		- PA: consistent within errors
+		- Axial ratio: consistent within errors
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Differential lensing is at play as suggested by the spectral shape of the \rot{2}{1} line profile, where 
+flux density in the red wing is much high than in the blue wing.  
+We modelled the emission using different kinematic components, the magnification factors are reported in Table BLAH.
+\input{table_magFactor}
+
+\begin{figure}[tbph]
+\centering
+\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.eps}
+\includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
+\caption{
+Pseudo observed 0th moment map in the lens plane. (left)
+Pseudo 0th moment map in the source plane. (right)
+\label{fig:}}
+\end{figure}
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.65\textwidth]{../Figures/PostageStampModel.eps}
+\includegraphics[width=0.65\textwidth]{../Figures/PostageStampResiduals.eps}
+\caption{
+of channel widths $\sim$ 100\kms. 
+\label{fig:}}
+\end{figure*}
+
+\begin{figure}[tbph]
+\centering
+\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.eps}
+\caption{
+velocity gradient of the lens model in the lens plane (left), source plane
+(right).
+\label{fig:}}
+\end{figure}
+
+%\begin{figure*}[tbph]
+%\centering
+%\includegraphics[width=0.8\textwidth]{}
+%\includegraphics[width=0.65\textwidth]{}
+%\caption{
+%\label{fig:}}
+%\end{figure*}
 \end{document}

### 2016-03-29 WRITEUP/Intro.tex
combine with Results.tex

@@
 claimed Seyfert 1 spiral galaxy.
+
+In this paper, we BLAH, refining the redshift to $z$=0.654
+We use a cosmology WMAP9.
 
@@
 
+\section{HST astrometry}
+We adopt the VLA 5\,GHz map of BLAH resolution as the reference coordinate frame and align the optical image. We shifted the 
+latter to the east by 0\farcs5963 in R.A and +0\farcs8372 in declination., which is consistent with the typical astrometric precision of the HST image. 
+The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas. 
+We estimate the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
+be better than 0.1", leaving aside uncertainties relating to the SNR and beam size.
+
+%The astrometry of the HST images was firstly calibrated against a wider-field
+%optical image of the cluster which had in turn been aligned onto the FK5
+%coordinate system to an rms precision of ~0.2".
+
+\section{CO($J$ = 3 $\rightarrow$ 2) line emission}
+
+% Integrated line flux: 37.509 Jy km/s over chan=[49,70] (FWZI) of sigma = 13.3mJy /B/channel of 35.87 km/s per channel
+%  57.753459930419922        10.658399798838524
+% 38.906448364257812        54.223567641493943
+% 258.26144409179688        57.450322398332851
+% 2.2153112888336182        2.9563491085933622
+
+% If we fit gaussian without the continuum to minimize error:
+% 58.848747253417969        10.030933764224825
+% 36.368530273437500        54.749284630860281
+% 276.93515014648438        54.753666156237443
+
+We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
+background galaxies in RXJ1131-1231.
+We extract the spectrum and fit a single-component Gaussian as shown in Figure
+\ref{fig:co32spec}
+yielding peak flux density of 57.8 $\pm$ 10.7 mJy, the FWHM of the Gaussian fit
+is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in the calibration.
+
+\begin{figure}[tbph]
+\centering
+\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}	  
+\caption{
+CO32 line spectrum
+ \label{fig:co32spec}}
+\end{figure}
+
+% line free channels:1,118,160,600
+% nchan =(117+600-160+1) = 558
+% sigma =  0.83 mJy/B
+
+At spatial position of CO emission, No significant continuum emission was
+detected from the line-free channels down to a 3$\sigma$ limit of 2.49mJy Beam\pmOne.
+(also as suggested in the fitted Gaussian to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{CO($J$ = 2 $\rightarrow$ 1) line emission}
+
+% intensity over chan 124, 156 of rms ~ 1.451 mJy/ Beam/ch
+% velocity resolution per bin: 21.528154 km/s
+
+%sigma_mom0 = 0.43  over chan: 127, 155
+
+We detect dynamically resolved CO($J$ = 2 $\rightarrow$ 1) line emission toward
+the background galaxies in RXJ1131-1231.
+
+We construct the velocity-integrated (0th moment) map of the CO($J$ = 2
+$\rightarrow$ 1) emission using the uv-continuum subtracted data, the
+velocity-integrated 
+CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ 0.2 Jy km s$^{-1}$.
+
+We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.451mJy per channel per beam.
+Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$ limit of 4.353 mJy \kms beam\pmOne.
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.35\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}	   
+\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
+\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
+\caption{
+0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping, of $\sigma$ 0.43 mJy beam\pmOne. 
+Spectrum. Velocity scale w.r.t z=0.655
+ \label{fig:CO21mom0}}
+\end{figure*}
+
+\begin{figure}[tbph]
+\centering
+\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       
+\caption{
+1st and 2nd order moments, clipped at 5 $\sigma$. 1st moment contour steps of 50 \kms, 2nd moment steps of 100 \kms.
+velocity range in z=0 frame = [-530.33, 72.73] \kms
+chan = [127, 155] 
+sigma = 0.16821825 Jy \kms per Beam
+theshold: 5*sigma = 7.2550e-3 Jy per beam (per channel)
+ \label{fig:highOmoments}}
+\end{figure}
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}	 %
+\caption{
+Black crosses indicate the position of the lensed AGN (components ABCD) and the central white-filled star indicates the
+position of the foreground lensing galaxy (component G) as detected in the HST image.
+ \label{fig:chanmap}}
+\end{figure*}
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}   
+\caption{ 
+Spatial spectra, binned by 3 pixels in each direction (1\farcs5)
+ \label{fig:spatialSpec}}
+\end{figure*}
+
+\section{Continuum}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PdBI
+% 2mm continuum averaged over chan 1 120 165 360
+% number of channels = 316
+% sigma = 1.451 mJy/B / sqrt(316) = 0.081625 mJy/B 
+% go noise on map (whole map) after cleaning: 89.274 µJy/B
+% F = 1.2 mJy (integrated spatially, from ~ 1 sigma contour; 150 pixels)
+%
+% 2mm peak is centered on foreground galaxy ~ 799 µJy/B --> with C band --> spectral index
+%	- 2mm marginally resolved along one axis (arc)
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% VLA C Band
+%
+
+VLA C Band continuum image shows resolved jets and core emission from the foreground lensing galaxy as well as the background lensed quasar (as arcs).
+We extracted the 5GHz fluxes for the arcs and the core as listed in Table \ref{tab:photometry}.
+
+As shown in Figure \ref{fig:cont}, we detect 2mm continuum emission toward both the foreground galaxy and the background as lensed emission.  
+The integrated continuum flux density is 1.2 mJy, while the peak emission is centered on the foreground galaxy at $S_\nu$ of 8 \micron Jy beam\pmOne.
+The detection is hence marginally resolved along one axis as shown in Figure \ref{fig:contco21}.
+We attempted to extract the background emission by subtracting the foreground emission as modeled by a point source (unresolved).
+But the residual after removing a point source model is just noise.
+So we I guess if we take the difference between the integrated and the  peak in the image plane is an upper limit to the background source at 2mm, which is $\sim$ 0.4 mJy.
+
+We fit power law to the VLA radio data and the 2mm continuum, we derive a spectral index of $\alpha$=0.025.
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.8\textwidth]{../Figures/ContCO21.eps}	  
+\caption{CO 21 moment0 overlay on 2mm continuum.  % chan [127,155]	
+TODO: add the beam
+ \label{fig:contco21}}
+\end{figure*}
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.8\textwidth]{../Figures/Cont2mm_5GHz_double.eps}    
+\caption{VLA 5GHz continuum and PdBI 2mm continuum
+ \label{fig:cont}}
+\end{figure*}
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
+\includegraphics[width=0.55\textwidth]{../Figures/F555W_ContVLA.eps}
+\caption{
+can kill left figure eventually by combining this to ContCO21.eps
+Right: alignment of HST and VLA 5 GHz continuum
+ \label{fig:}}
+\end{figure*}
+
 \section{\rot{2}{1} Lens model}
@@
 
-%\begin{figure*}[tbph]
-%\centering
-%\includegraphics[width=0.8\textwidth]{}
-%\includegraphics[width=0.65\textwidth]{}
-%\caption{
-%\label{fig:}}
-%\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SED}
+
+We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side and including the 24.0\micron data from Spitzer/MIPS to constrain the dust peak. 
+Also do SED fit with IRAS upper limits.
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}	 
+\caption{TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 2mm PdBI (now integrated and peak), extract flux after removing a point source model.
+Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux extraction.
+Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied. Spitzer/MIPS: PSF fit flux, as source size < native PSF FWHM of 6".
+Might want to add NVSS constraints.
+ \label{fig:}}
+\end{figure*}
+
+\input{table_photometry_AAScustomized}
+
 \end{document}

### 2016-03-31 ALMA/Cycle4/RXJ.tex
Cycle 4 proposal tex file created

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% LaTeX template for the science justification to be       %%
%%     submitted as part of a regular ALMA proposal.        %%
%% This template should also be used for a ToO, Solar, or   %%
%%     mm-VLBI ALMA proposal, but NOT for Large Programs    %%
%%     (these have a separate template with more sections)  %%
%%                                                          %%
%%                      ALMA Cycle 4                        %%
%%                                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% How to convert this document to PDF %%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% If your figures are stored as PostScript files, you can use the 
% following commands to generate a PDF file of your proposal:

%% latex file.tex
%% dvips file.dvi
%% ps2pdf file.ps file.pdf

% If your figures are PDF images or bitmap pictures in PNG, JPG, or GIF format,
% you can use the pdflatex command to generate a PDF file from this template
% (note, however, that the pdflatex command does not handle PostScript files):

% pdflatex file.tex

% WARNINGS: 
%           1. You must make sure that PDF output generated from this
%              template is complete both when displayed with a viewer 
%              (acroread, for example) and when printed on paper.
%              LaTeX installations vary greatly and therefore it might 
%              not be possible to get all proposals to come out 
%              correctly with a single text page layout. 
%              In some cases you will have to adjust the 
%              \topmargin=-7mm command in the template to center the 
%              text vertically in the page.  
%           2. The scientific justification, figures, tables, references,
%              and public outreach statement must all fit within the
%              4-page limit.
%           3. You are free to include colour images in your proposal 
%              justification. Proposals are distributed to ALMA Review Panels 
%              in electronic form. However, the scientific content of the 
%              images should still remain clear when displayed or printed
%              in black and white.
%           4. this template is for regular, ToO, Solar, or mm-VLBI ALMA proposals,
%              but NOT for Large Programs: these have a separate template with
%              more sections, and is available from the ALMA Science Portal

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Default format: 12pt single column %%%%%
%% 12pt is the minimum font size allowed !! %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,a4paper]{article}  %% DO NOT CHANGE to 11pt or less !

\usepackage{graphics,graphicx}
\usepackage[update,prepend]{epstopdf}
\usepackage[innercaption]{sidecap}
\usepackage{amssymb, amsmath}          % for \lesssim
\usepackage{xspace}                              % latex will auto decide whether a trailing whitespace should follow
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros}                         % for understanding Journal in bib
\usepackage{subcaption}

\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\rot}[3][HCN]{\mbox{#1($J$\,=\,#2\,\rarr\,#3) }} % default HCN; usage \rot[HCN]{3}{2} or \rot[\hcop]{4}{3}
\newcommand{\hcop}{HCO$^+$\xspace}
\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont {#1}}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\spm}[2]{\ensuremath{^{+#1}{-#2}}}                    %  Asymmetric errors 
\newcommand{\mean}[1]{\langle #1 \rangle}                               % stat mean
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}

%Compact BIB%%%%%%%%%%%%%%%%%%%%
\citestyle{aa}  
\bibliographystyle{apj_w_etal_3auth}

\usepackage{paralist}

\renewenvironment{thebibliography}[1]{%
%\section*{\refname}%
%  {\normalsize {\textbf{References:}}}
  \let\par\relax\let\newblock\relax%
  \inparaitem[{[}1{]}]}{\endinparaitem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Page dimensions %%%%%
%%%%%%  DO NOT CHANGE  %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textheight=247mm
\textwidth=180mm
\topmargin=-7mm
\oddsidemargin=-10mm
\evensidemargin=-10mm
\parindent 10pt

\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
% between fig
\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\floatsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\intextsep}{10pt plus 1.0pt minus 2.0pt}

\setlength{\parskip}{0.01em}
\usepackage[small,tiny,compact]{titlesec}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Start of document %%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{plain}
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Title of proposal %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\LARGE{\bf
{ 
Dynamical study of the dense gas and star-formation in a strongly-lensed
AGN host galaxy and its starburst companion at z$\sim$0.66}
}}
\end{center}
\centerline{\bf PI: 
{T. K. Daisy Leung}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Body of science justification %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% ENTER TEXT, FIGURES AND TABLES BELOW

\section{Gas Dynamics}
\vspace{-0.25em}

\indent BLAH

\section{Science Target RXJ 1131-1231: AGN-Starburst Pair}
\vspace{-0.25em}

\section{Proposed Observations and Immediate Objectives}
\vspace{-0.25em}

%%%%%%%%%%%%%%%%%%%%%%%%
%% References section: %
%%%%%%%%%%%%%%%%%%%%%%%%

\section*{References}
{\fontsize{10pt}{12pt}\selectfont
	\bibliography{RXJ_ALMAC4}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% End of document %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2016-04-14 ALMA/Cycle4/RXJ.tex
before adding DR's 1st round comments

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% LaTeX template for the science justification to be       %%
-%%     submitted as part of a regular ALMA proposal.        %%
-%% This template should also be used for a ToO, Solar, or   %%
-%%     mm-VLBI ALMA proposal, but NOT for Large Programs    %%
-%%     (these have a separate template with more sections)  %%
-%%                                                          %%
-%%                      ALMA Cycle 4                        %%
-%%                                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% How to convert this document to PDF %%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% If your figures are stored as PostScript files, you can use the 
-% following commands to generate a PDF file of your proposal:
-
-%% latex file.tex
-%% dvips file.dvi
-%% ps2pdf file.ps file.pdf
-
-% If your figures are PDF images or bitmap pictures in PNG, JPG, or GIF format,
-% you can use the pdflatex command to generate a PDF file from this template
-% (note, however, that the pdflatex command does not handle PostScript files):
-
-% pdflatex file.tex
-
 % WARNINGS: 
@@
 %	       text vertically in the page.
-%           2. The scientific justification, figures, tables, references,
-%              and public outreach statement must all fit within the
-%              4-page limit.
-%           3. You are free to include colour images in your proposal 
-%              justification. Proposals are distributed to ALMA Review Panels 
-%              in electronic form. However, the scientific content of the 
-%              images should still remain clear when displayed or printed
-%              in black and white.
-%           4. this template is for regular, ToO, Solar, or mm-VLBI ALMA proposals,
-%              but NOT for Large Programs: these have a separate template with
-%              more sections, and is available from the ALMA Science Portal
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Default format: 12pt single column %%%%%
-%% 12pt is the minimum font size allowed !! %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \documentclass[12pt,a4paper]{article}  %% DO NOT CHANGE to 11pt or less !
-
+% \usepackage{apjfonts}
+\usepackage{times}
 \usepackage{graphics,graphicx}
@@
 \usepackage[innercaption]{sidecap}
-\usepackage{amssymb, amsmath}          % for \lesssim
-\usepackage{xspace}                              % latex will auto decide whether a trailing whitespace should follow
+\usepackage{subcaption}
+\usepackage{amssymb, amsmath}	       
+\usepackage{xspace}				
 \usepackage{natbibspacing, natbib}
-\usepackage{aas_macros}                         % for understanding Journal in bib
-\usepackage{subcaption}
+\usepackage{aas_macros}
+\usepackage{wrapfig}
+\usepackage{floatrow}
 
-\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
+\newcommand{\ncrit}{\mbox{$n_crit$}\xspace}
+\newcommand{\comol}{$^{12}$CO\xspace}
+\newcommand{\Lsun}{\mbox{L$_{\odot}$}\xspace}
+\newcommand{\LIR}{\mbox{L$_{\rm IR}$}\xspace}
+\newcommand{\LFIR}{\mbox{L$_{\rm FIR}$}\xspace}
 \newcommand{\rarr}{$\rightarrow$}
-\newcommand{\rot}[3][HCN]{\mbox{#1($J$\,=\,#2\,\rarr\,#3) }} % default HCN; usage \rot[HCN]{3}{2} or \rot[\hcop]{4}{3}
+\newcommand{\aco}{\mbox{CO($J$=1\rarr0)}\xspace}
+\newcommand{\bco}{\mbox{CO($J$=2\rarr1)}\xspace}
+\newcommand{\cco}{\mbox{CO($J$=3\rarr2)}\xspace}
+\newcommand{\eco}{\mbox{CO($J$=5\rarr4)}\xspace}
+\newcommand{\rot}[3][HCN]{\mbox{#1($J$=#2\rarr#3)}\xspace} 
+% default HCN; usage \rot[HCN]{3}{2} or \rot[\hcop]{4}{3}
+\newcommand{\ahcn}{\mbox{HCN($J$=1\rarr0)}\xspace}
+\newcommand{\dhcn}{\mbox{HCN($J$=4\rarr3)}\xspace}
 \newcommand{\hcop}{HCO$^+$\xspace}
-\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont {#1}}$}}
+\newcommand{\ahcop}{\mbox{HCO$^+$($J$=1\rarr0) }}
+\newcommand{\dhcop}{\mbox{HCO$^+$($J$=4\rarr3) }}
+\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}}
 \newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
-\newcommand{\spm}[2]{\ensuremath{^{+#1}{-#2}}}                    %  Asymmetric errors 
-\newcommand{\mean}[1]{\langle #1 \rangle}                               % stat mean
+\newcommand{\kms}{km\,s$^{-1}$\xspace}
 \newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
+\newcommand{\Fig}[1]{Fig.~\ref{fig:#1}}
+\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Start of document %%%%% 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Title of proposal %%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{center}
-{\LARGE{\bf
+{\large{\bf
 { 
-Dynamical study of the dense gas and star-formation in a strongly-lensed
-AGN host galaxy and its starburst companion at z$\sim$0.66}
+Molecular gas dynamics and excitation and star-formation mechanism in a
+strongly-lensed wet merger}
 }}
 \end{center}
-\centerline{\bf PI: 
-{T. K. Daisy Leung}} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Body of science justification %%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-0.545em}
+\centerline{\normalsize{\bf PI: 
+{T. K. Daisy Leung}}} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Missing link between mergers/ULIRGs and their high-z analogues} 
+% \vspace{-0.25em}
+% \indent 
+\vspace{0.1em} {\bf Missing link between mergers/ULIRGs and their high-z analogues} 
+Ultraluminous infrared galaxies (ULIRGs: \LIR$\geq$10$^{12}$\Lsun) have been
+regarded as 
+%local 
+analogues of high-redshift (z) starbursts given their
+similarities in \LIR/\Lp\ and other physical properties. Hence, 
+%their observables 
+they are commonly used as templates for 
+%studies of the interstellar medium (ISM) of 
+their high-z counterparts, which are expensive to study.
+% and limited with current facilities.
+As such, detailed studies and characterization of ULIRGs are extremely important 
+to gain insights into the early universe and study how galaxies evolve over cosmic time.
+It is now believed that mergers play an important role in giving rise to these dusty galaxies
+(e.g. Sanders \& Mirabel 1996). Yet, merger-induced effects on the physical mechanisms and chemistry 
+that drive the intense starburst and AGN activities on small scales are still unclear.
+Thus characterizing the properties of the molecular gas that fuel star-formation and AGN is
+crucial for understanding the interplay between these activities 
+and their relation to the ISM content across cosmic times.
 
-%% ENTER TEXT, FIGURES AND TABLES BELOW
+While local ULIRGs 
+%such as Arp 220 and NGC 253 
+has been studied
+in great details with multi-transitions of different molecular species, 
+and increasingly more so with the advent of ALMA,
+forming a rich inventory of molecular transitions that serves as the template for 
+understanding high-z galaxies and galaxy evolution \citep[e.g.][]{Rangwala15a}, a wide knowledge gap persists
+between $z$=0 out to when most stars are formed in the universe ($z\sim$2). 
+Understanding galaxy populations at the epoch when the build-up of stellar mass across cosmic
+time is steeply rising is thus critical and we here aim to bridge this gap by testifying
+correlations and properties found locally out to high redshifts.
 
-\section{Gas Dynamics}
-\vspace{-0.25em}
+% \section*{Various molecular gas phases and the star-formation law} 
+% \vspace{-0.25em}
+\noindent {\bf Various molecular gas phases and the star-formation law} 
+Owning to the high molecular gas fraction in ULIRGs and their high-z analogues,
+their extreme SFRs is a natural consequence of either gas is converted into stars
+more efficiently and/or their molecular gas content. Fragmentation
+of giant star-forming clumps and turbulent conditions are also expected 
+from gravitational instability of these gas-rich bodies. 
+In fact, studies of the ISM kinematics at $z$=1-2 find clumps of size scale
+ $\sim$few kpc \citep{Swinbank12a, Swinbank12b}. 
+Resolving the gas dynamics on hundred pc scales is therefore a promising first step
+to understanding the mechanisms and physical processes taking
+place on different scales and how the physical conditions 
+are related to the starburst in ULIRGs at this epoch (when the SFRD is steeply rising).
 
-\indent BLAH
+% SG2 
+While \comol emission traces the total molecular distribution and dynamics,
+molecules such as HCN, HNC and \hcop are expected to trace the 
+properties of the denser star-forming gas. Indeed, a tight correlation between \ahcn and \LIR 
+(SFR tracer)
+% ignoring AGN heating) 
+has been found in nearby galaxies
+and local GMCs \citep{Wu05}, suggesting HCN is a faithful
+tracer of the star-forming dense molecular gas. However, 
+the origin of such correlation is still under debate  (\citealt{Kohno05a},  \citealt{Papadopoulos07a}; hereafter P07;  \citealt{Costagliola11a}).
+% and it is unclear whether such correlation holds in distant galaxies. 
+Meanwhile, an elevated \LIR/\Lp[\ahcn] in (U)LIRGs and high-z galaxies (\citealt{Riechers07a}; \citealt{Gao07a}; hereafter G07; \citealt{GC08a}) imply that the star-formation law of dense gas (based on HCN)
+($\Sigma_{\rm SFR}$ - $\Sigma_{\rm dense}$) 
+breaks down above \LIR $>$10$^{11}$\Lsun, calling questions into the reliability of 
+\ahcn as a dense gas tracer and \LIR/\Lp[\ahcn] as a diagnostic of the star formation efficiency
+% -- efficiency at which stars form out -- 
+of dense gas \citep{GC06a}.
 
-\section{Science Target RXJ 1131-1231: AGN-Starburst Pair}
-\vspace{-0.25em}
+% line ratio
+% Also, \citet{Kohno05a} constructed a diagnostic plot using the ratio between
+% \ahcn and \hcop, which suggests HCN enhancement in AGNs 
+% due to high (dust) temperature \citep{Harada10a}
+% and the enhancement in abundance of HCN in XDR and IR 
+% pumping or other reasons unrelated to AGN \citep{Costagliola11a}. 
+%While the origin of such enhancement is unclear, it is 
+% clear that the abundances and excitation conditions of these molecules 
+% vary widely from galaxy populations (SB versus AGN) 
+% and radially from the circumnuclear region even with data obtained 
+% during the previous cycles of ALMA (Izumi16).
+% Thus question our current understanding/assumption/ previous claims 
+% about using HCN to trace the star-forming gas.'
+%
+% Influence of buried AGNs at the cores of ULIRGs have also been studied
+% intensively to explain the observed 
+% intensities of \hcop and HCN (Izumi+16, Kohno+05, Imanishi+06, Aalto+06,
+% Yamada+07), but current interpretations are still under debate.
 
-\section{Proposed Observations and Immediate Objectives}
-\vspace{-0.25em}
+In addition, \dhcn observations of (U)LIRGs have revealed a wide range of
+excitation conditions for their dense gas phase that may render the ground state transition of 
+HCN and \hcop poor proxies of the dense gas mass (P07).
+In this light, higher-J transitions (e.g. $J$=4\rarr3) have been argued to be necessary to scrutinize the
+reliability of \ahcn as dense gas mass tracer since the mid-J transitions
+trace the much denser (n$\gtrsim$10$^5-$10$^6$ cm$^{-3}$) molecular gas that is 
+thought to be the immediate fuel for star-formation in turbulent GMCs \citep{Shirley03a, KM05}. 
+% in (U)LIRGs 
+% based on high-mass 
+% star-forming cores \citep{Shirley03a} and theoretical grounds \citep{KM05}. 
+Besides, since the ground state lines are redshifted to frequencies beyond spectral coverage of ALMA
+for $z>$0.06, it is also necessary to establish diagnostics using mid-J lines to study distant galaxies.
+% Other the other hand, Zhang14 find a linear correlation of \Lp{\dhcn}-\LIR and a slightly super-linear
+% slope for \hcop-\LIR in nearby galaxies, which is in tension with Bussmann2008 and
+% Juneau2009. Hence our current understanding on the dense 
+% gas tracers and SFR empirical relation has not been consolidated. 
+% Theoretically Expected decreasing slopes against increasing \ncrit because of
+% sub-thermal excitation conditions, as observed by Bussmann2008, which show sub-linear correlation in
+% HCN3-2 and LIR.
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-%% References section: %
-%%%%%%%%%%%%%%%%%%%%%%%%
+Prior to era of ALMA, studies of dense gas are largely limited to the local universe ($z\lesssim$0.1) 
+except for detections in five IR-luminous lensed galaxies (\citealt{Riechers06a, Riechers07a, Wagg05a}; G07), 
+such small sample with limited resolution renders it extremely difficult 
+to draw conclusions on the dense gas properties at high redshifts. 
+Even with ALMA, it will remain challenging to carry out
+similar studies at high redshifts, e.g. line ratio maps tracing spatial variations 
+on few tens of pc scales, resolving gas clumps in GMCs and the dynamics and excitation
+conditions at high resolution. 
+Yet, the magnification provided by gravitational lensing enables one
+to further exploits the exceptional spatial resolution of ALMA, enabling studies
+of distant galaxies to be carried out beyond the capabilities of current instruments. 
+We here propose a detailed study of the ISM properties in the
+quadruply lensed galaxy RXJ1131-1231 and its dust-obscured companion at $z_{\rm CO}$$\sim$0.65
+to bridge the gap between nearby ULIRGs and their high-z analogues.
 
-\section*{References}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+% \section*{Science Target RXJ 1131-1231: a demonstrative case at high-z}
+% \vspace{-0.25em}
+\noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at high-z}
+
+\begin{figure}[!tbhp]
+\centering
+\begin{tabular}{@{}cc@{}}
+\includegraphics[scale=0.3]{Fig/F555W} &
+\includegraphics[scale=0.37]{Fig/Manipulate_figsCROP}
+\end{tabular}
+\vspace{-1em}
+\caption{ \fontsize{10pt}{12pt}\selectfont 
+{
+\textbf{RXJ1131-1231 stellar distribution and its reconstructed source plane
+morphology}
+{\em Left:} An optical image 
+%obtained with the HST 
+reveals the background AGN (knots)
+and its host galaxy (arcs) with highly complex structures. The rest-frame UV emission (tracing
+recent star formation) 
+%in the background galaxy 
+is lensed into an almost Einstein ring with radius $\sim$ 3.8". 
+%The detection in rest-frame UV indicates recent star-formation.
+{\em Right:} A lens modelling with the optical image identify an optically faint
+companion (white; \citealt{Claeskens06a}), 
+which we have recently confirmed with our dynamical lens model using \bco emission
+(\Fig{model}) and is extremely dusty 
+(\LIR$\sim$6$\times$10$^{12}$\Lsun) and gas-rich (\Fig{CO21mom0}; Leung \& Riechers, in prep.). 
+A source plane reconstruction also shows seven spatially distinct components, 
+highlighting the potential of our science target 
+%is thus an excellent laboratory 
+for studying the ISM conditions near starburst and AGN activities and offers an unparalleled
+view into the early universe, with finer
+detail than otherwise possible with current facilities. 
+}
+\label{fig:HST}}
+\end{figure}
+
+%\begin{figure}[!tbhp]
+%\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.54\textwidth}}]{figure}[\FBwidth]
+%{
+%\vspace{-0.7em}
+%\caption{ \fontsize{10pt}{12pt}\selectfont 
+%{\textbf{RXJ1131-1231 stellar distribution and its reconstructed source plane
+%morphology}
+%{\em Left:} An optical image 
+%%obtained with the HST 
+%reveals the background AGN (knots)
+%and its host galaxy (arcs) with highly complex structures. The rest-frame UV emission (tracing
+%recent star formation) 
+%%in the background galaxy 
+%is lensed into an almost Einstein ring with radius $\sim$ 3.8". 
+%%The detection in rest-frame UV indicates recent star-formation.
+%{\em Right:} A lens modelling with the optical image identify an optically faint
+%companion (white; \citealt{Claeskens06a}), 
+%which we have recently confirmed with our dynamical lens model using \bco emission
+%(\Fig{model}) and is extremely dusty 
+%(\LIR$\sim$6$\times$10$^{12}$\Lsun) and gas-rich (\Fig{CO21mom0}; Leung \& Riechers, in prep.). 
+%A source plane reconstruction also shows seven spatially distinct components, 
+%highlighting the potential of our science target 
+%%is thus an excellent laboratory 
+%for studying the ISM conditions near starburst and AGN activities and offers an unparalleled
+%view into the early universe, with finer
+%detail than otherwise possible with current facilities. 
+%}
+%\label{fig:HST}}}
+%{\begin{tabular}{@{}cc@{}}
+%\hspace*{\fill}
+%\includegraphics[scale=0.3]{Fig/F555W} \hfill % &
+%\hspace*{-0.9em}
+%\includegraphics[scale=0.35]{Fig/Manipulate_figsCROP}
+%\hspace*{\fill}
+%\end{tabular}}
+%\vspace{-0.7em}
+%\end{figure}
+
+RXJ 1131-1231 is a quadruply imaged AGN with an Einstein Ring 
+% of 3.8" in radius 
+(\Fig{HST}). 
+HST observations (rest-frame UV) have revealed distinct emission 
+from recent star formation (arcs) and the AGN (knots) in the background galaxy \citep{Sluse03a},
+demonstrating the complexity and the immense potential for probing the 
+ISM conditions at astounding level of detail.
+Lens modelling carried out with the optical images show
+that the AGN resides in a star-forming region of $\sim$0.15" ($\sim$1 kpc)
+in its host galaxy which is 1" across ($\sim$7 kpc), and identify
+seven spatially distinct structures in the source plane of size 
+$\sim$0.1" (\Fig{model}). Remarkably, emission originating from 
+a spatially offset region from the AGN host galaxy has been identified 
+at $\sim$ 2.4 kpc away, of $\sim$ 700 pc in size \citep{Brewer08a}, 
+%in the source plane, 
+indicating a nearby counterpart, which we have recently confirmed with
+the \rot[CO]{2}{1} emission and our dynamical lens model, 
+verifying the two host massive cool gas reservoirs and are at similar redshifts (\Fig{CO21mom0} \& \Fig{model}; Leung \& Riechers, in prep.). 
+% The co-spatial CO emission with the optical emission (counter-arc)
+% also confirms their massive cool gas reservoirs \Fig{CO21mom0}. 
+Our SED modelling of the dust finds $L_{\rm IR}\sim6\times$10$^{12}$\Lsun 
+(corrected for lensing). Hence, this target is a gas-rich ULIRG merger caught in the act.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Proposed Observations and Immediate Objectives}
+% \vspace{-0.25em}
+\noindent {\bf Proposed Observations and Immediate Objectives}
+We here propose to map (1): 
+\eco at 0.15" resolution ($\sim$500pc in the source plane) and (2): \dhcn and \dhcop emission 
+at 0.7" resolution (2.5 kpc). The 
+%(high resolution) 
+underlying continuum will addtionally provide
+better constrain on the dust emission and distribution and thus surface density of the SFR. 
+In conjunction with the large set of ancillary data obtained spanning from
+rest-frame UV to radio and spectral line observations of \bco and \rot[CO]{3}{2}, our
+proposed observations will address many questions in various aspects (see below).
+The weak H$_2$O line falls in the same sideband as \eco, and thus our observations 
+will as well provide constrains on the line strength and thus AGN feedback/excitation,
+albeit the small number of detections at high redshift (R06?).
+
+\underline{\bf Dynamics and kinematics:}
+
+%\begin{figure}[!tbhp]
+%\centering
+%\includegraphics[scale=0.3]{../../Figures/CO_highOmom_CLIP5sigma}
+%\vspace{-1em}
+%\caption{ \fontsize{10pt}{12pt}\selectfont 
+%{
+%\textbf{RXJ1131-1231 kinematics and dynamics in \bco}
+%{\em Left:} The observed velocity gradient is suggestive of a kinematically ordered disk. 
+%% rotating with a maximum speed $v\sin i$ $\sim$ BLAH km/s.
+%Limited by current spatial resolution, the intrinsic velocity gradient may
+%be smaller than the beam size such that the smaller gradient are not 
+%resolved, which may led to misinterpretation of the system to be 
+%rotationally supported.
+%{\em Right:} 2$^{nd}$ order moment map showing the velocity dispersion in the \bco emitting gas. 
+%However, limited by the spatial resolution, beam smearing strongly decreases
+%large-scale velocity gradients and increases observed dispersion.
+%High resolution is thus necessary to distinguish the dichotomy between a rotating disk
+%and mergers and/or the effect of a 
+%companion on the internal dynamics of the AGN host galaxy.  
+%This will enable us to understand the mechanisms driving the starburst and
+%investigate whether dominant mode of star formation is like GMC in a stable disk or by fragmentation of
+%dynamically unstable gas-rich disk. 
+%% The proposed study will obtain data which will be complementary to the
+%% HST data (rest-frame UV) which traces the stellar distribution. 
+%}
+%\label{fig:moments}
+%}
+%\end{figure}
+
+\begin{figure}[!tbhp]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.6\textwidth}}]{figure}[\FBwidth]
+{\hspace{-0.7em}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{RXJ1131-1231 kinematics and dynamics in \bco}
+{\em Left:} The observed velocity gradient is suggestive of a kinematically ordered disk. 
+Limited by current spatial resolution, the intrinsic velocity gradient may
+be smaller than the beam size such that the smaller gradient are not 
+resolved, which may led to misinterpretation of the system to be 
+rotationally supported.
+{\em Right:} 2$^{nd}$ order moment map showing the velocity dispersion in the \bco emitting gas. 
+However, limited by the spatial resolution, beam smearing strongly decreases
+large-scale velocity gradients and increases observed dispersion.
+High resolution is thus necessary to distinguish the dichotomy between a rotating disk
+and mergers and/or the effect of a 
+companion on the internal dynamics of the AGN host galaxy.  
+This will enable us to understand the mechanisms driving the starburst and
+investigate whether dominant mode of star formation is like GMC in a stable disk or by fragmentation of
+dynamically unstable gas-rich disk. 
+% The proposed study will obtain data which will be complementary to the
+% HST data (rest-frame UV) which traces the stellar distribution. 
+}
+\label{fig:moments}
+}}
+{\includegraphics[scale=0.3]{../../Figures/CO_highOmom_CLIP5sigma}}
+\vspace{-0.7em}
+\end{figure}
+
+%\begin{figure}[tbph]
+%\centering
+%\includegraphics[width=0.45\textwidth]{Fig/olayCO21Spectra.eps}
+%\caption{
+%Overlay of spectra taken at different spatial positions along the greatest
+%velocity gradient. 
+%differential lensing of the different kinematic components of the galaxy
+% \label{fig:CO21spectra}}
+%\end{figure}
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.37\textwidth]{Fig/olayCO21Spectra.eps}
+\hspace{-0.45em}
+\includegraphics[width=0.6\textwidth]{Fig/PostageStampModel.eps}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{Differential lensing with spatial variations and dynamical lens model}}
+{\em Left:} Overlay of spectra taken at various spatial positions along the strongest velocity gradient, demonstrating 
+differential lensing of the different kinematic components of the galaxy. Hence, higher resolution imaging of this source 
+will allow us to probe the gas distribution.
+{\em Right:} Velocity channels of the CO emission toward the gas-rich merger (red contours) overlaid on our best-fit 
+lens model (grayscale). Clearly, there are spatial variations across different kinematic 
+components, which is likely due to differential lensing. The foreground lensing galaxy is represented by a black dot, and 
+the beam size is shown in the bottom right corner.
+The velocity across the panels decreases from top left (red wing) to bottom right (blue wing), with $\Delta v\sim$100 \kms.
+The reconstructed source morphology (magenta ellipse) is suggestive of a kinematically ordered galaxy. 
+However, at the spatial resolution of our data, we cannot definitively infer its true morphology due to beam smearing. 
+Higher-resolution imaging is needed to unambiguously determine the nature that gives rise to the observed velocity gradient.
+The proposal observations will confirm if the system is rotationally supported or highly turbulent (due to AGN or tidally disrupted if merging with the companion).
+\label{fig:model}}
+\end{figure*}
+
+% Gas distribution 
+The CO emission shows an asymmetric double-horned line profile (\Fig{CO21mom0}), which 
+indicates the effect of differential lensing and that the cool gas is spatially distributed (\Fig{model}). 
+Hence, our proposed observations will probe the spatial variations of the molecular gas. 
+% gas kinematics
+The 1$^{\rm st}$ moment map (\Fig{moments}) and the velocity gradient 
+across the source plane (Fig.~\ref{fig:model}) in our model suggests
+that our source is kinematically ordered (reminiscent of a rotating disk). Yet,  
+the spatial resolution of this data is insufficient to infer the true 
+kinematics due to beam smearing. Besides, 
+% velocity dispersion suggest the source may be dispersion dominated (\Fig{moments}). 
+an unusually high velocity dispersion 
+$\gtrsim$400\kms at the central region(\Fig{moments})  hint at 
+%plausible 
+perturbations from the central AGN and/or
+internal turbulent motion due to interactions with the companion
+and/or instability due to the huge gas reservoir.
+Higher-resolution imaging is absolutely necessary to 
+%map the intrinsic velocity gradient and dispersion in order 
+to unambiguously determine the nature that gives rise to 
+the observed velocity gradient and 
+confirm if the galaxy is disk-like but disrupted or merging
+and whether it is dominated by internal random 
+motions (in addition to large-scale orbital velocity, if confirmed to be disk-like in 1st moment map)
+to distinguish the major mechanism driving the starburst: merger-driven 
+versus gas-rich clumpy disk, which show similar velocity profile in low-resolution data.
+
+We also aim to spatially separate/resolve the kinematic 
+signatures of the gas clumps in the AGN host galaxy to probe
+the kinematical and dynamical state of the gas, and 
+how the gas distribution is affected. 
+At the proposed resolutions, we will also
+obtain a better-constrained dynamical lens model
+and be able to probe the gas in the kinematically related companion 
+and its internal dynamics. 
+The proposed observations will also highly complementary to optical image,
+% spider diagram in the iso-velocity contours
+allowing a comparison between the gas and stellar distribution.
+% probing the dynamics of the excited-gas in a high-z source at resolution 
+% otherwise impossible.
+
+\underline{\bf Physical properties and dense gas line ratio maps:}
+% Between HCN/HCO+:
+Since the critical densities of HCN rotational transitions are $\sim$5 times
+higher than \hcop, they trace different gas phases.
+% with different densities. 
+The line fluxes and spatially resolved line ratio maps will thus enable us 
+ to constrain the density and temperature of the molecular gas around 
+ the AGN, its star-forming host galaxy, and in its companion, providing perceptive clues to how these
+activities and galaxy interactions alter the chemical composition of the ISM/ISM chemistry (e.g. HCN 
+and \hcop enhancements in different regions), and thus the evolution these ubiquitous dusty mergers.
+Due to the difference in abundances and excitation conditions of these molecules,
+\dhcn/\dhcop can be used to separate activities/emission originating from AGN or starburst
+\citep{Imanishi10, Izumi13a}, % \citep{Imanishi14a}.
+which sheds light on AGN and star-formation feedbacks and clues to interpret 
+the evolutionary stage of the galaxy (Baan+08).
+
+% e.g. HCO+/HCN is found to be enhanced in star-forming regions 
+% (in PDRs, SN shocks [can enhance HCO+]; Maijerink+07). 
+% Thus the line ratio may be diagnostic to distinguish between XDRs, PDRs or 
+% deeply embedded star-formation (Blake+87;  Bayet+08); 
+% where lower ratio may suggest low-density XDR or dense PDRs (Costagliola+11).
+% this assumes line ratios are directly linked to relative abundances 
+% (Krips+08; then spatially resolved line ratio traces abundance gradient)
+% but may not be true for HCN and HCO+.
+
+\underline{\bf Excitation conditions:}
+% between CO/HCN
+The line ratio \comol(low-J)/HCN probes the dense gas fraction, abundance, and excitation. Thus, we will 
+map out the spatial variations and gradients in the physical conditions of
+the gas within the galaxies, providing extra constraints on the star-formation activity.
+
+We will combine these data [tracing the excited emission] with our existing lower-J CO 
+data to diagnose the excitation conditions and the heating source of the gas. [Since the high-density tracers probe 
+the star-forming molecular dense gas regions and
+the low-density tracers probe the relatively unperturbed larger-scale molecular
+environment.]
+
+% Some high excitation CO SLEDs are found in local ULIRGs, suggesting strong
+% supersonic turbulence and cosmic ray rather than UV photons from SF sites as heating source, 
+% warming up the large amounts of dense gas in these SBs.
+% Thus we will be able to extract the physical and dynamical states of the ISM environment.
+
+\underline{\bf Star-formation Law:}
+Our proposed observations will furnish data to carry comparative studies
+between the \LIR, SFR$_{\rm IR}$, SFR$_{\rm UV}$, surface densities of SFR, CO, HCN and \hcop,
+providing stringent constraints on the relation between molecular gas and star-formation on sub-kpc scales and on the mechanisms driving the mammoth SFR at earlier epochs, giving rise to the observed stellar-assembly history.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% closing
+% mechanisms and physical processes and on different scales.
+\par 
+Our proposed observations therefore provide an exceptional opportunity to investigate
+the physical properties and dynamical structures of different gas phases in the ISM of mergers 
+and distant galaxies with exquisite details.
+These are vital to improve our current understanding 
+on the star-formation processes at the cosmic epoch 
+where the contribution of dusty, star-forming galaxies to the cosmic SFR density is steeply rising 
+\citep{LeFloch05a}. 
+This will also provide a benchmark in utilizing high-dipole moment molecules as 
+routine tracers to study star-formation in relatively poorly-studied high-z populations
+and demonstrate the capabilities of ALMA in mapping these much fainter emission in distant galaxies.
+ The proposed observations with our science target will therefore provide a giant leap on 
+our understanding -- putting high-z systems into the context of nearby studies and lay the groundwork to 
+routinely perform such studies at higher redshifts in the ALMA full operations cycle in the near future.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section*{Technical overview}
+%\vspace{-0.25em}
+%{\bf Technical overview}
+%We propose to image the gravitationally lensed merger at z$\sim$0.65 in the redshifted  
+%{\bf (1)} \eco line at $\sim$0.15" resolution (array config. C40-5) 
+%and {\bf (2)} \dhcn and \dhcop at $\sim$0.7" resolution (C40-3). 
+%We assume a line width (FWHM) of 700\kms based on our \bco observations 
+%(\Fig{CO21mom0}) for both science goals and the source size from our dynamical lens model, which
+%takes into account the asymmetric line emission
+%and spatial extent due to differential lensing. 
+%We thus expect the source to be resolved over 153 beams 
+%and 7 beams at 0.15" and 0.7", respectively. 
+%We compute target sensitivity for \eco using \bco line flux and adopt a conservative 
+%line ratios between \aco and \bco, and \eco based on SMGs \citep{CW13}. 
+%We compute expected sensitivity for \dhcn from \aco using a conservative line ratio
+%between \aco and \ahcn and \dhcn based on (U)LIRGs (GS04; P07).
+%We estimate a line flux for \dhcop based on the line ratio \dhcn/\dhcop found in ULIRGs 
+%\citep{Greve09a}. We use the most stringent sensitivity estimates 
+%among \dhcn and \dhcop as our sensitivity goal. The latter sets the overall requirement. 
+%To secure enough S/N for our model, 
+%we require a minimum of 8$\sigma$ of 0.47 mJy beam\pmOne and 0.07 mJy beam\pmOne
+%per 150 \kms channel to reconstruct the dynamical structure in the source plane for the science goals, respectively. 
+%We therefore request a total time of 7.0 hours to complete our science goals.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section*{Potential for publicity}
+%\vspace{-0.25em}
+{\bf Potential for publicity} 
+I will publish a paper on this if I get the data I need. SOME TEXT
+The proposed observations will serve as a demonstrative case
+of the dense, excited gas in high-z galaxies at high resolution. 
+high potential for publicity. 
+% This will enable us to demonstrate galaxies in this epoch, blah beyond capabilities of 
+% current facilities.
+
+\begin{figure*}[tbph]
+\centering
+% \includegraphics[width=0.25\textwidth]{Fig/{F555WCO21_mom0_single.invertedgray}.eps}
+\hspace*{\fill}
+\includegraphics[width=0.25\textwidth]{Fig/F555W_REDCentBLUE.png}
+\hspace*{-0.9em}
+\includegraphics[width=0.45\textwidth]{Fig/SpecCO21_twinx.eps}
+\hspace*{\fill}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{Detection of a gas-rich merger with spatial variations traced by \bco}
+{\em Left:} The (red, green, blue) contours correspond to the velocity-integrated line flux of different velocity channels (red wing, line center, blue wing) in our \rot[CO]{2}{1} data. 
+Strikingly, the spatially-resolved molecular gas emission shows a different lensing configuration 
+than in the optical.
+The counter-arc structure as shown by the red wing and its redshift (see right) is evident of a gas-rich source.
+This companion galaxy is consistent with the dusty source discovered with {\it Herschel},
+which is faint in the optical as expected (the white component in Fig.~\ref{fig:HST}).
+% \fontsize{10pt}{12pt}\selectfont {\textbf{PdBI \rot[CO]{2}{1} dynamically resolved line profile} 
+{\em Right:}
+The continuum-subtracted spectrum shows a double-horned profile, where the red wing is significantly brighter. Our lens modelling suggests that this arises due to differential lensing across the 
+kinematic components of the source.
+% As indicated on the top axis, 0 km/s corresponds to z=0.655. 
+Our proposed observations will allow us to investigate the fuel and mechanisms responsible for the intense star-formation in the AGN host galaxy.
+We here aim to spatially and dynamically resolve the dense, excited gas emission, which will allow us to unambiguously examine the dynamic structure of the ISM in the distant merger and provide observational constants on the star-formation and stellar-assembly history at the epoch where the SFR density is steeply rising across cosmic times.
+}
+ \label{fig:CO21mom0}}
+\end{figure*}
+
+\noindent \bf {References}
 {\fontsize{10pt}{12pt}\selectfont
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% End of document %%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2016-04-15 ALMA/Cycle4/pythonSpecOplot/plotSpecMPL.py
oplot spectra

@@ -1,0 +1,202 @@
+'''
+Overplot spectra at different spatial location for ALMA C4 proposal
+
+
+History:
+--------
+Appril 14 2016:
+    - edit labels and text annotations
+April 11 2016:
+    - copied from Zsearch project: ~/Research/zsearch_Conley/science_goal.uidA001_X121_X1fc/combine
+
+Note
+----
+
+'''
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+import scipy
+
+
+def gauss(x, a, b, c):
+    '''
+    x: array
+    a,b,c: float
+    '''
+    return a * np.exp(-(x - b) ** 2 / (2 * c ** 2))
+
+
+def gauss_withcont(x, a, b, c, d):
+    '''
+    x: array
+    a,b,c,d: float
+    '''
+    return a * np.exp(-(x - b) ** 2 / (2 * c ** 2)) + d
+
+
+def double_gauss_withcont(x, a, b, c, d, e, f, g):
+    '''
+    x: array
+    a,b,c,d,e,f,g: float
+    '''
+    return a * np.exp(-(x - b)**2 / (2 * c**2)) + d + e * np.exp(-(x - f)**2 / (2 * g**2))
+
+
+def read_specfile(specFile):
+    """read spectrum file
+
+    Parameters
+    ----------
+    specFile: str
+        file name containing 2 or 3 columns
+        velo [km/s]/freq [GHz], flux [??], rms [optional]
+    Returns
+    -------
+    x, flux, width, rms [optional]
+
+    """
+
+    a = np.loadtxt(specFile)
+    x, flux = a[:, 0], a[:, 1]
+    width = abs(x[1] - x[0])
+
+    if a.shape[1] == 2:
+        return x, flux, width
+    elif a.shape[1] == 3:
+        rms = a[:, 2]
+        return x, flux, width, rms
+
+
+def setup_spec_plot(ax, xax, xlabel=False, ylabel=False):
+    '''
+
+    ax: axis object
+    xax: str
+        'velocity' or 'frequency'
+    xlabel: boolean
+        True to turn xaxis label on
+    ylabel: Boolean
+        True to turn yaxis label on
+    '''
+
+    from matplotlib.ticker import AutoMinorLocator
+
+    # specify a fixed number of minor intervals per major interval, e.g.:
+    # minorLocator = AutoMinorLocator()
+    minorLocator = AutoMinorLocator()
[…]

### 2016-04-15 src/APLpySetup.py
plot cosmestics

@@ -69,17 +69,17 @@ def standard_plot_setup(sp, ra_center, dec_center, size, tickc='black'):
     sp.set_system_latex(True)
     sp.recenter(x=ra_center, y=dec_center, radius=size)   # width = blah, height = blah     # Scaling and panning
 
-    sp.tick_labels.set_font(size='medium', weight='bold')      # size='10'
-    sp.tick_labels.set_style('colons')
-    sp.tick_labels.set_xformat('hh:mm:ss')
-    sp.tick_labels.set_yformat('dd:mm:ss')
+    sp.tick_labels.set_font(size='x-large', weight='bold')      # size='10'
+#    sp.tick_labels.set_style('colons')
+#     sp.tick_labels.set_xformat('hh:mm:ss')
+#     sp.tick_labels.set_yformat('dd:mm:ss')
     sp.ticks.set_color(tickc)
     sp.ticks.set_linewidth(2)
     sp.ticks.set_length(10)
-    sp.ticks.set_minor_frequency(4)
+#     sp.ticks.set_minor_frequency(4)
     # sp.ticks.set_xspacing(45*15/3600.)        # deg
 
-    sp.axis_labels.set_font(size='medium', weight='bold')      # (size='12')
+    sp.axis_labels.set_font(size='xx-large', weight='bold')      # (size='12')
     sp.axis_labels.set_xtext('Right Ascension (J2000)')
     sp.axis_labels.set_ytext('Declination (J2000)')
     sp.axis_labels.set_xpad(5)

### 2016-04-17 ALMA/Cycle4/RXJ.tex
added DR's commments, added Science case for dense gas stuff, need to revise captions

--- 2016-03-31 ALMA/Cycle4/RXJ.tex
@@
 \usepackage[innercaption]{sidecap}
-\usepackage{amssymb, amsmath}          % for \lesssim
-\usepackage{xspace}                              % latex will auto decide whether a trailing whitespace should follow
+\usepackage{subcaption}
+\usepackage{amssymb, amsmath}	       
+\usepackage{xspace}				
 \usepackage{natbibspacing, natbib}
-\usepackage{aas_macros}                         % for understanding Journal in bib
-\usepackage{subcaption}
+\usepackage{aas_macros}
+\usepackage{wrapfig}
+\usepackage{floatrow}
 
-\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
+\newcommand{\ncrit}{\mbox{$n_{\rm crit}$}\xspace}
+\newcommand{\comol}{$^{12}$CO\xspace}
+\newcommand{\Lsun}{\mbox{L$_{\odot}$}\xspace}
+\newcommand{\LIR}{\mbox{L$_{\rm IR}$}\xspace}
+\newcommand{\LFIR}{\mbox{L$_{\rm FIR}$}\xspace}
 \newcommand{\rarr}{$\rightarrow$}
-\newcommand{\rot}[3][HCN]{\mbox{#1($J$\,=\,#2\,\rarr\,#3) }} % default HCN; usage \rot[HCN]{3}{2} or \rot[\hcop]{4}{3}
+\newcommand{\aco}{\mbox{CO($J$=1\rarr0)}\xspace}
+\newcommand{\bco}{\mbox{CO($J$=2\rarr1)}\xspace}
+\newcommand{\cco}{\mbox{CO($J$=3\rarr2)}\xspace}
+\newcommand{\eco}{\mbox{CO($J$=5\rarr4)}\xspace}
+\newcommand{\rot}[3][HCN]{\mbox{#1($J$=#2\rarr#3)}\xspace} 
+% default HCN; usage \rot[HCN]{3}{2} or \rot[\hcop]{4}{3}
+\newcommand{\ahcn}{HCN($J$=1\rarr0)\xspace}
+\newcommand{\dhcn}{HCN($J$=4\rarr3)\xspace}
 \newcommand{\hcop}{HCO$^+$\xspace}
-\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont {#1}}$}}
+\newcommand{\ahcop}{\mbox{HCO$^+$($J$=1\rarr0)}}
+\newcommand{\dhcop}{HCO$^+$($J$=4\rarr3)\xspace}
+\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}}
 \newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
-\newcommand{\spm}[2]{\ensuremath{^{+#1}{-#2}}}                    %  Asymmetric errors 
-\newcommand{\mean}[1]{\langle #1 \rangle}                               % stat mean
+\newcommand{\kms}{km\,s$^{-1}$\xspace}
 \newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
+\newcommand{\Fig}[1]{Fig.~\ref{fig:#1}}
+\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
 
@@
 \setlength{\intextsep}{10pt plus 1.0pt minus 2.0pt}
-
+% between figure and caption
+\setlength{\abovecaptionskip}{10pt plus 0pt minus 0pt}
 \setlength{\parskip}{0.01em}
 \usepackage[small,tiny,compact]{titlesec}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Start of document %%%%% 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Title of proposal %%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{center}
-{\LARGE{\bf
+{\large{\bf
 { 
-Dynamical study of the dense gas and star-formation in a strongly-lensed
-AGN host galaxy and its starburst companion at z$\sim$0.66}
+Molecular gas dynamics and AGN/starburst mechanism in a
+strongly-lensed wet merger: bridging the gap between local ULIRGs and high-z systems}
 }}
 \end{center}
-\centerline{\bf PI: 
-{T. K. Daisy Leung}} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% Body of science justification %%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-0.545em}
+\centerline{\normalsize{\bf PI: 
+{T. K. Daisy Leung}}} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Missing link between mergers/ULIRGs and their high-z analogues} 
+% \vspace{-0.25em}
+% \indent 
+\vspace{0.1em} {\bf Missing link between mergers/ULIRGs and their high-z analogues} 
+Ultraluminous infrared galaxies (ULIRGs: \LIR$\geq$10$^{12}$\Lsun) have been
+regarded as analogues of high-redshift (z) starbursts given their
+similarities in \LIR/\Lp\ and other physical properties.
+% (e.g. high-z SB display morphological evidence of past or ongoing merger)
+As such, detailed studies and characterization of ULIRGs are important 
+to gain more detailed insight into the early universe and in studies of galaxy evolution over cosmic time.
+It is believed that mergers play an important role in giving rise to these dusty galaxies
+(e.g. Sanders \& Mirabel 1996). Yet, merger-induced effects on the physical mechanisms and chemistry 
+that drive the intense starburst (SB) and active galactic nucleus (AGN) activities on small scales are still unclear.
+Thus characterizing the properties of the molecular gas that fuels star-formation (SF) and AGN is
+crucial to understand the interplay between AGN and SB
+and their relation to the interstellar medium (ISM) properties of galaxies across cosmic time.
 
-%% ENTER TEXT, FIGURES AND TABLES BELOW
+While the ISM in local ULIRGs has been studied in great detail with ALMA,
+forming a rich inventory of molecular transitions that serves as the template for 
+understanding high-z galaxies and galaxy evolution \citep[e.g.][]{Rangwala15a}, a wide knowledge gap persists
+between $z$=0 and the epoch when most stars are formed in the universe ($z\sim$2). 
+Understanding galaxy populations at the epoch when the build-up of stellar mass across cosmic
+time is steeply rising is thus critical and we here aim to bridge this gap by testifying
+correlations and properties found locally out to high/moderate redshifts by observing the 
+dynamical structure of the different molecular gas components
+in the quadruply lensed galaxy RXJ1131-1231 and its dust-obscured 
+companion at $z_{\rm CO}$$\sim$0.65.
+%to bridge the gap between nearby ULIRGs and their high-z analogues.
 
-\section{Gas Dynamics}
-\vspace{-0.25em}
+% \section*{Various molecular gas phases and the star-formation law} 
+% \vspace{-0.25em}
+\noindent {\bf Molecular gas in AGN/SB} 
+Owing to the high molecular gas fractions in ULIRGs and their high-z analogues,
+their extreme SFRs are a natural consequence of either gas is being converted into stars
+more efficiently and/or their molecular gas content. Fragmentation
+of giant star-forming clumps and turbulent conditions are also expected 
+from gravitational instability of these gas-rich bodies. 
+In fact, studies of the ISM kinematics at $z$=1-2 find clumps of size scale
+ $\sim$few kpc \citep{Swinbank12a, Swinbank12b}. 
+Resolving the gas dynamics on hundred pc scales is therefore an important first step
+to understanding the mechanisms and physical processes taking
+place on different scales and how the physical conditions 
+are related to the starburst in ULIRGs at this epoch (when the SFR density is steeply rising).
 
-\indent BLAH
+While \comol emission traces the total molecular distribution and dynamics,
+high-dipole moment molecules such as HCN and \hcop are expected to trace the 
+properties of the denser, actively star-forming gas. Indeed, a tight correlation between \ahcn and \LIR 
+(proxy for SFR) has been found in nearby galaxies and local giant molecular 
+clouds (GMC; \citealt[hereafter GS04]{Gao04a}; \citealt{Wu05}), 
+suggesting HCN is a faithful tracer of the star-forming dense gas.
+% and that the origin can be attributed to the fundamental units of star formation. 
+This has been supported by the linear correlations in 
+\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] found recently \citep[see \Fig{SF}]{Zhang14a}, which also highlight 
+the great utility of these mid-$J$ lines observable for galaxies at $z$$>$0.06.
 
-\section{Science Target RXJ 1131-1231: AGN-Starburst Pair}
-\vspace{-0.25em}
+Due to the difference in abundances and excitation conditions of HCN and \hcop
+in star-forming versus AGN regions, the line ratio \ahcn/HCO$^+$($J$=1\rarr0) has been 
+proposed as a diagnostic tool to separate emission originating from AGN and starburst
+\citep{Kohno05a, Imanishi10, Izumi13a}. 
+ %(e.g. HCO+ is enhanced in SF regions in PDRs and SN shocks and HCN is enhanced in AGN)
+With the frequency coverage of ALMA, some studies have 
+extended this diagnostic to using the J=4\rarr3 transitions 
+\citep{Imanishi14a, GB14a, Viti14a}, where 
+an elevated \dhcn/\dhcop line ratio is also seen in AGNs, suggesting
+it, too, can be used to reveal a deeply buried AGN at the cores of ULIRGs \citep{Izumi16a, Imanishi16a}.
 
-\section{Proposed Observations and Immediate Objectives}
-\vspace{-0.25em}
+Prior to ALMA, studies of dense gas were largely limited to the local universe ($z\lesssim$0.1) 
+with only five IR-luminous lensed galaxies detected at $z\gtrsim0.3$ 
+(e.g. \citealt{Riechers06a, Riechers07a, Riechers10a, Wagg05a, Gao07a}).
+However, none of these high-z detections spatially resolve the emission, rendering it difficult 
+to draw conclusions on the dense gas properties of galaxies at high redshifts. 
+Even with ALMA, such studies will remain challenging, but by combining with
+the magnification provided by gravitational lensing and the exceptional spatial resolution and sensitivity of ALMA, studies
+of dense molecular gas in distant galaxies are now possible, as proposed here.
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-%% References section: %
-%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+% \section*{Science Target RXJ 1131-1231: a demonstrative case at high-z}
+% \vspace{-0.25em}
+\noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at high-z}
 
-\section*{References}
+%\begin{figure}[!tbhp]
+%\centering
+%\includegraphics[trim= 10 20 15 0, clip, scale=0.3]{Fig/F555W} % &
+%\hspace{-0.5em}
+%\includegraphics[trim= 10 0 0 0, clip, scale=0.37]{Fig/Manipulate_figsCROP}
+%\vspace{-1em}
+%\caption{ \fontsize{10pt}{12pt}\selectfont 
+%{
+%\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
+%morphology}
+%{\em Left:} The rest-frame UV emission (tracing recent star formation) 
+%is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
+%{\em Right:} Lens modelling of the optical emission identifies complex structure in the host galaxy and
+%an optically faint companion (white; \citealt{Claeskens06a}), 
+%which we have recently confirmed by modeling \bco emission detected with NOEMA
+%(\Fig{combine}; Leung \& Riechers, in prep.). 
+%We here propose to study
+%the ISM conditions in this AGN-starburst composite system and offers an unparalleled
+%view into the early universe, with finer
+%detail than otherwise possible with current facilities. 
+%}
+%\label{fig:HST}}
+%\end{figure}
+
+\begin{figure}[!tbhp]
+\centering
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.4\textwidth}}]{figure}[\FBwidth]
+{
+\hspace{-0.35em}
+\vspace*{-0.55em}
+\caption{ \fontsize{10pt}{12pt}\selectfont 
+{
+\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
+morphology}
+{\em Left:} The rest-frame UV emission (tracing recent star formation) 
+is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
+{\em Right:} Lens modelling of the optical emission identifies complex structure in the host galaxy and
+an optically faint companion (white; \citealt{Claeskens06a}), 
+which we have recently confirmed by modeling \bco emission detected with NOEMA
+(\Fig{combine}; Leung \& Riechers, in prep.). 
+We here propose to study
+the ISM conditions in this AGN-starburst composite system and offers an unparalleled
+view into the early universe, with finer
+detail than otherwise possible with current facilities. 
+}
+\label{fig:HST}}}
+{\hspace{-1em}
+\includegraphics[trim= 10 20 15 0, clip, scale=0.28]{Fig/F555W}
+\hspace{-1.5em}
+\includegraphics[trim= 10 0 0 0, clip, scale=0.32]{Fig/Manipulate_figsCROP}
+\vspace{-1em}
+}
+\end{figure}
+
+RXJ 1131-1231 is a quadruply imaged AGN with its host galaxy lensed 
+into a partial Einstein ring (\Fig{HST}). 
+HST observations (rest-frame UV) have revealed distinct emission 
+from recent star formation (lensing arcs) and from the AGN (bright knots) in the background galaxy \citep{Sluse03a},
+demonstrating the great potential for probing the 
+ISM conditions in detail. Lens modeling carried out on optical images shows
+that the AGN resides in a star-forming region of size $\sim$0.15" ($\sim$1 kpc)
+in its host galaxy, which itself is 1" across ($\sim$7 kpc), and made it possible to identify
+seven distinct structures in the source plane (\Fig{HST}). Remarkably, emission originating from 
+a spatially offset region ($\sim$2.4 kpc away) from the AGN host galaxy has been identified and found 
+to be $\sim$700 pc in size \citep{Brewer08a}, indicating a nearby companion galaxy. 
+We have recently confirmed that both galaxies are at the same redshift by detecting their 
+\rot[CO]{2}{1} emission and lens-modeling the distribution of the gas in velocity space (\Fig{combine}f), 
+verifying that the both are gas-rich (Leung \& Riechers, in prep.). 
+Our SED modeling of the dust continuum emission up to 500\,$\mu$m finds $L_{\rm IR}\sim6\times$10$^{12}$\Lsun 
+(corrected for lensing). Hence, this target is a gas-rich ULIRG merger at $z$$\sim$0.7 caught in the act.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section*{Proposed Observations and Immediate Objectives}
+% \vspace{-0.25em}
+\noindent {\bf Proposed Observations and Science Goals}
+We here propose to map (1): \eco at 0.15" resolution ($\sim$500pc at $z$$\sim$0.7 in the source plane) and 
+(2): \dhcn and \dhcop emission at 0.7" resolution (2.5 kpc) and the underlying continuum.
+% The science goals at the proposed resolutions are designed to 
+The continuum emission traces the optically-thick dust emission, which 
+will provide better constraints on the dust temperature(s), dust mass,
+and spatial distribution, and thus a tighter constraint on the surface density of the SFR and 
+the gas-to-dust ratio. These quantities are key to investigate how the ISM conditions 
+vary as galaxies evolve.
+In conjunction with the large set of ancillary data from
+rest-frame UV to radio wavelength and our new spectral line observations of \bco and \rot[CO]{3}{2}, our
+proposed observations will enable a detailed characterization of 
+merger/ULIRG in the following aspects.
+
+\underline{\bf Dynamics and kinematics:}
+Our recently obtained \bco data shows an asymmetric double-horned line profile (\Fig{combine}a). Given
+the observed 1$^{\rm st}$ moment map and the velocity gradient
+across the source plane in our model (\Fig{combine}c \& \ref{fig:combine}f), this is indicative of
+a kinematically ordered (reminiscent of a rotating disk) galaxy but its emission 
+has been lensed differentially. 
+Limited by the spatial resolution of this data, it is insufficient to infer the true 
+kinematics due to beam smearing.
+Furthermore, the unusually high velocity dispersion 
+$\gtrsim$400\kms at the central region (\Fig{combine}d) hints at 
+perturbations from the central AGN and/or
+internal turbulent motion due to interactions with the companion
+and/or instability due to the huge gas reservoir.
+Thus, higher-resolution imaging, as proposed here, will allow us to
+distinguish the major mechanism driving the starburst: merger-driven 
+versus gas-rich clumpy disk, since we will also be able to obtain a detailed
+dynamical lens modeling of the system.
+
+The \eco observations at 0.15" are complementary to the optical images,
+allowing a comparison between the stellar and gas distribution. 
+%{\bf The proposed observations will provide the data tracing 
+% the warm, excited, dense molecular gas distribution and kinematics, 
+% which we will compare against the diffuse component (traced by our already obtained lower-J CO data). 
+% OR 
+Additionally, since \eco, \dhcn and \dhcop trace the warm, excited, dense molecular gas,
+this will allow us to compare against the relatively unperturbed large-scale 
+molecular environment and the dynamical mass with our existing lower-$J$ CO data.
+% to study the
+% gas distribution and kinematics.
+Such comparison are key to understanding the processes and timescales regulating star-formation 
+in ULIRG/merger, and examine how they differ from other galaxy populations.
+
+\underline{\bf Line ratios as AGN/starburst diagnostic:}
+By measuring \dhcn/\dhcop in the 
+AGN host galaxy, separated from the companion, we will assess its fidelity as a 
+AGN/SB diagnostic at higher redshifts than current studies. 
+We will as well measure this ratio in the companion and examine the possibility of a 
+heavily-obscured AGN at its center. 
+Due to the high critical densities of these high-$J$ transitions (\ncrit$\sim$10$^{8}$cm$^{-3}$), 
+the \dhcn/CO and \dhcop/CO line ratios are expected to 
+be enhanced in AGNs on a global scale, enabling us to carry out a consistency check against the
+\dhcn/\dhcop line ratio diagnostic.
+
+The high spin rate of the central black hole in RXJ1131-1231 (over half the speed of light; \citealt{Reis14a})
+%(M$_{\rm BH}$$\sim$2$\times$10$^{8}$M$_{\odot}$) 
+suggests that the black hole has grown via merger
+%[, which provided sufficient accreting materials for
+%the observed spin rate,] 
+rather than from small episodic accretions (from random directions).
+% In contrast if black holes grow through many small accretion episodes, 
+% they will accumulate material from random directions, and reduce spin.
+In this scenario, the companion and the AGN host galaxy may have already encountered previously.
+Therefore, our observations will improve our understanding 
+on the formation and evolution of supermassive black holes
+and the co-evolution with their host galaxies (and mergers).
+More interestingly, we might be witnessing the 
+pre/post merging/encounter of two AGN host galaxies if we find evidence of a buried AGN in the companion, 
+of which the proposed observations are needed to provide such clues.
+
+\underline{\bf Spectral line energy distributions (SLED) and SF Law:}
+On top of using \dhcn and \hcop as AGN/SB diagnostic, another 
+ aspect 
+ %for obtaining the proposed line observations 
+ is to 
+% constrain the ISM conditions by fitting radiative transfer models.
+% since these molecular species
+% have different excitation criteria. %Therefore, 
+%In combination 
+combine them with \eco %, \dhcn, and \dhcop line emission
+and our existing low-$J$ CO data to perform radiative transfer/large velocity gradient (LVG) modeling 
+% [with assumptions on their relative abundances] 
+to constrain the physical conditions 
+(e.g. density and gas kinetic temperature) of the multi-phase molecular gas.
+The \dhcn and \dhcop lines are essential as they trace beyond the $J$-transition of the CO SLED turnover
+(typically beyond $J$=6\rarr5 in local (U)LIRGs and high-z starbursts; \citealt{Greve14a}).
+% and since \eco traces the high kinetic temperature component. 
+In addition, since ISM studies of high-z galaxies typically adopt local SLED for comparison \citep[e.g.][]{Bothwell13a}
+and/or for asserting assumptions on the conditions of these high-z galaxies.
+%[due to the sparsely sampled SLED at high-z \citep{CW13}].
+Our observations will thus form a template at z$\sim$0.7 
+for these high-z studies.
+
+The ``star-formation law" (%$\Sigma_{\rm SFR}$=$A\Sigma^N_{gas}$ or 
+log\LIR=$\alpha$ log\Lp[X]+$\beta$)
+is one of the key ingredients % /observational constraints 
+for theoretical models as it entails the physical processes 
+of star-formation and its dependence on the ISM 
+%(in the slopes and normalizations; 
+(e.g. \citealt{Narayanan14a}).
+% Observational constraints for the \LIR-\Lp[X] (\Lp of different lines) relations are vital.
+However, the \LIR-\Lp[X] at high critical density are currently poorly constrained due to the lack of observations 
+and are largely limited to the nearby universe
+\citep[\Fig{SF}; ][]{Greve14a}. Our proposed observations will help delineate 
+the slopes at high critical densities and 
+explore the linear correlations found 
+locally in \Lp[\dhcn]-\LIR and \Lp[\dhcop]-\LIR \citep[\Fig{SF}; ][]{Zhang14a} at higher redshifts.
+%
+\begin{figure*}[!tbph]
+\centering
+\includegraphics[trim=15 0 5 10, clip, width=0.23\textwidth]{Fig/Zhang}
+\includegraphics[trim=5 5 5 10, clip, width=0.23\textwidth]{Fig/Zhang2}
+\includegraphics[trim=10 0 0 5, clip, width=0.4\textwidth]{Fig/Greve14Fig2}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{Integrated form of the SF law: log \LFIR = $\alpha$ log \Lp[X]+$\beta$.}}
+{\em Left \& middle:}
+A linear correlation between \LIR-\dhcn and \LIR-\dhcop have been established toward nearby galaxies 
+with \LIR$\sim$10$^9$-10$^{12}$\Lsun \citep{Zhang14a}, demonstrating the utility of mid-$J$ lines in tracing 
+the star-forming dense gas, which will be routinely mapped in high-z galaxies with ALMA.
+Our proposed observations will testify the linearity by adding measurements of a ULIRG at z$\sim$0.7, 
+% extending the statistics/data to higher redshifts, 
+and unveil potential deviations at higher redshift.
+{\em Right:} \textbf{Constraints on the SF law 
+with line transitions of different \ncrit.}
+Most observations are incompatible with current model predictions (gray shaded area),
+especially for \dhcn
+\citep{Greve14a}.
+Our proposed observations will thus reduce the uncertainties on the slopes at high critical densities
+and improve our current understanding of galaxy evolution.
+\label{fig:SF}}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\noindent {\bf Technical overview}
+We propose to observe the \eco line at $\sim$0.15" resolution
+and the \dhcn and \dhcop lines at $\sim$0.7", assuming a line width 
+(FWHM) of 700\kms based on our \bco data
+(\Fig{combine}a) and a source size from our lens model (see details in TJ).
+%, which takes into account the asymmetric line emission and spatial extent due to differential lensing. 
+We thus expect the source to be resolved over 153 beams 
+and 7 beams at 0.15" and 0.7", respectively. 
+We compute the target sensitivities for both science goals using \bco line flux. 
+For \eco, we adopt conservative 
+line ratios measured for SMGs \citep[][see TJ for details]{CW13},
+and those based on (U)LIRGs for \dhcn (GS04; \citealt{Papadopoulos07a}).
+For \dhcop, we adopt the line ratio \dhcn/\dhcop found in ULIRGs 
+\citep{Greve09a}. 
+We use the most stringent sensitivity estimates 
+among \dhcn and \dhcop as our sensitivity goal for science goal $1$. %The latter sets the overall requirement. 
+To secure enough S/N for lens modeling, 
+we require a minimum of 8$\sigma$ of 0.47 mJy beam\pmOne and 0.07 mJy beam\pmOne
+per 150 \kms channel 
+%to reconstruct the dynamical structure in the source plane 
+for the science goals, respectively. 
+We therefore request a \textbf{total time of 7.0 hours}.% to complete our science goals.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% closing
+\par 
+Our proposed observations present an exceptional opportunity to investigate
+the physical properties and dynamical structures of 
+%different gas phases in 
+the ISM in mergers at the cosmic epoch 
+where the SFR density is steeply rising \citep{LeFloch05a}, 
+connecting high redshift and nearby studies to improve our understanding of galaxy evolution.
+%Our proposed observations are vital
+%% between the \LIR, SFR$_{\rm IR}$, SFR$_{\rm UV}$, surface densities of SFR, CO, HCN and \hcop,
+%to provide constraints on the relation between the ISM and AGN/SB acitvities
+%on sub-kpc scales and on the mechanisms driving the vast SFR at earlier epochs, 
+%giving rise to the observed stellar-assembly history.
+%
+This will also % lay the groundwork to 
+serve as a benchmark demonstrating the future prospects for ALMA in 
+utilizing high-dipole moment molecules as routine tracers to study star-formation 
+at high redshifts.
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[trim=25 6 5 5, clip, width=0.75\textwidth]{Fig/combine}
+\caption{ \fontsize{10pt}{12pt}\selectfont {}
+% CO2-1 line profile
+{\em (a):} \textbf{PdBI \rot[CO]{2}{1} dynamically resolved line profile}
+The \bco spectrum showing a double-horned, highly asymmetric line profile, which arises due to 
+differential lensing across the kinematic components of the source (see (f)).
+% HST
+{\em (b):}  \textbf{Detection of a gas-rich merger with spatial variations traced by \bco}
+The (red, green, blue) contours correspond to the velocity-integrated 
+line flux of different velocity channels (red wing, line center, blue wing) in our \rot[CO]{2}{1} data. 
+{\em (c):} \textbf{RXJ1131-1231 kinematics in \bco}
+% 1st order
+The observed velocity gradient is suggestive of a kinematically ordered disk at 
+the current resolution limit.
+{\em (d):} \textbf{RXJ1131-1231 dynamics in \bco}
+% 2nd order
+Velocity dispersion map of the \bco emitting gas. 
+However, limited by the spatial resolution, beam smearing strongly decreases
+large-scale velocity gradients and increases observed dispersion.
+% RGB spectra
+{\em (e): } \textbf{Differential lensing with spatial variations}
+Overlay of spectra taken at regions along the strongest velocity gradient, demonstrating 
+differential lensing of the different kinematic components of the galaxy. 
+% Lens model
+{\em (f): } \textbf{Dynamical lens model}
+Velocity channels of the CO emission toward the gas-rich merger (red contours) overlaid on our best-fit 
+lens model for each velocity bin (grayscale). 
+The foreground lensing galaxy is represented by a black dot, and 
+the beam size is shown in the bottom right corner.
+Clearly, there are spatial variations across different kinematic components.
+The reconstructed source morphology (magenta ellipses) is suggestive of a kinematically ordered galaxy. 
+However, at the spatial resolution of our data, we cannot definitively infer its true morphology due to beam smearing. 
+Given the presence of a companion galaxy within 2.4 kpc, high-resolution 
+imaging is thus necessary to unambiguously determine the nature that gives rise to the observed velocity gradient
+and dynamics, as proposed here.
+This will confirm if the system is rotationally supported or highly turbulent 
+(tidally disrupted) and allow us to investigate the major mechanisms responsible 
+for the starburst in the AGN host galaxy
+and investigate whether dominant mode of star formation is GMC-like in a rotating disk or due to fragmentation of
+dynamically unstable gas-rich disk. 
+We here aim to spatially and dynamically resolve the dense, excited gas emission, 
+which will allow us to unambiguously examine the dynamic structure of the ISM in 
+the distant merger and provide observational constraints on the star-formation and 
+stellar-assembly history at the epoch where the SFR density is steeply 
+rising across cosmic times.
+\label{fig:combine}}
+\end{figure*}
+%
+
+\noindent \bf {References}
 {\fontsize{10pt}{12pt}\selectfont

### 2016-04-17 ALMA/Cycle4/RXJ.tex
ready for DR 2nd round

@@
 
-\documentclass[12pt,a4paper]{article}  %% DO NOT CHANGE to 11pt or less !
-% \usepackage{apjfonts}
+\documentclass[12pt,a4paper]{article} 
 \usepackage{times}
@@
 \newcommand{\Lsun}{\mbox{L$_{\odot}$}\xspace}
-\newcommand{\LIR}{\mbox{L$_{\rm IR}$}\xspace}
-\newcommand{\LFIR}{\mbox{L$_{\rm FIR}$}\xspace}
+\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
+\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
 \newcommand{\rarr}{$\rightarrow$}
@@
 % between fig
-\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
+\setlength{\textfloatsep}{10pt plus 1.0pt minus2.0pt}
 \setlength{\floatsep}{10pt plus 1.0pt minus 2.0pt}
 \setlength{\intextsep}{10pt plus 1.0pt minus 2.0pt}
-% between figure and caption
-\setlength{\abovecaptionskip}{10pt plus 0pt minus 0pt}
 \setlength{\parskip}{0.01em}
@@
 understanding high-z galaxies and galaxy evolution \citep[e.g.][]{Rangwala15a}, a wide knowledge gap persists
-between $z$=0 and the epoch when most stars are formed in the universe ($z\sim$2). 
+between $z$=0 and the epoch when most stars are formed in the universe ($z$$\sim$2). 
 Understanding galaxy populations at the epoch when the build-up of stellar mass across cosmic
@@
 This has been supported by the linear correlations in 
-\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] found recently \citep[see \Fig{SF}]{Zhang14a}, which also highlight 
+\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] found recently \citep[hereafter Z14; see \Fig{SF}]{Zhang14a}, which also highlight 
 the great utility of these mid-$J$ lines observable for galaxies at $z$$>$0.06.
@@
 \noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at high-z}
-
+\vspace{-0.7em}
 %\begin{figure}[!tbhp]
@@
 %is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
-%{\em Right:} Lens modelling of the optical emission identifies complex structure in the host galaxy and
+%{\em Right:} Lens modeling of the optical emission identifies complex structure in the host galaxy and
 %an optically faint companion (white; \citealt{Claeskens06a}), 
@@
 \centering
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.4\textwidth}}]{figure}[\FBwidth]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.425\textwidth}}]{figure}[\FBwidth]
 {
@@
 \vspace*{-0.55em}
+\raggedleft
 \caption{ \fontsize{10pt}{12pt}\selectfont 
@@
 is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
-{\em Right:} Lens modelling of the optical emission identifies complex structure in the host galaxy and
+{\em Right:} Lens modeling of the optical emission identifies complex structures in the host galaxy and
 an optically faint companion (white; \citealt{Claeskens06a}), 
@@
 \hspace{-1.5em}
-\includegraphics[trim= 10 0 0 0, clip, scale=0.32]{Fig/Manipulate_figsCROP}
+\includegraphics[trim= 10 0 0 0, clip, scale=0.3]{Fig/Manipulate_figsCROP}
 \vspace{-1em}
@@
 \end{figure}
-
+\vspace{-0.8em}
 RXJ 1131-1231 is a quadruply imaged AGN with its host galaxy lensed 
@@
 % gas distribution and kinematics.
-Such comparison are key to understanding the processes and timescales regulating star-formation 
+Such comparison are key to understand the processes and timescales regulating star-formation 
 in ULIRG/merger, and examine how they differ from other galaxy populations.
@@
 
-\underline{\bf Spectral line energy distributions (SLED) and SF Law:}
+\underline{\bf Spectral line energy distributions (SLED) and the SF Law:}
 On top of using \dhcn and \hcop as AGN/SB diagnostic, another 
@@
 combine them with \eco %, \dhcn, and \dhcop line emission
-and our existing low-$J$ CO data to perform radiative transfer/large velocity gradient (LVG) modeling 
+and our existing low-$J$ CO data to perform radiative transfer modeling 
 % [with assumptions on their relative abundances] 
@@
 is one of the key ingredients % /observational constraints 
-for theoretical models as it entails the physical processes 
+for theoretical models as it encodes the physical processes 
 of star-formation and its dependence on the ISM 
@@
 and are largely limited to the nearby universe
-\citep[\Fig{SF}; ][]{Greve14a}. Our proposed observations will help delineate 
+\citep[\Fig{SF};][]{Greve14a}. Our proposed observations will help delineate 
 the slopes at high critical densities and 
 explore the linear correlations found 
-locally in \Lp[\dhcn]-\LIR and \Lp[\dhcop]-\LIR \citep[\Fig{SF}; ][]{Zhang14a} at higher redshifts.
+locally in \Lp[\dhcn]-\LIR and \Lp[\dhcop]-\LIR (\Fig{SF}; Z14) at higher redshifts.
 %
@@
 \centering
-\includegraphics[trim=15 0 5 10, clip, width=0.23\textwidth]{Fig/Zhang}
-\includegraphics[trim=5 5 5 10, clip, width=0.23\textwidth]{Fig/Zhang2}
-\includegraphics[trim=10 0 0 5, clip, width=0.4\textwidth]{Fig/Greve14Fig2}
-\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{Integrated form of the SF law: log \LFIR = $\alpha$ log \Lp[X]+$\beta$.}}
+\includegraphics[trim=15 0 5 10, clip, width=0.2\textwidth]{Fig/Zhang}
+\includegraphics[trim=5 5 5 10, clip, width=0.2\textwidth]{Fig/Zhang2}
+\includegraphics[trim=10 0 0 5, clip, width=0.38\textwidth]{Fig/Greve14Fig2}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{The SF law: log \LIR = $\alpha$ log \Lp[X]+$\beta$.}}
 {\em Left \& middle:}
 A linear correlation between \LIR-\dhcn and \LIR-\dhcop have been established toward nearby galaxies 
-with \LIR$\sim$10$^9$-10$^{12}$\Lsun \citep{Zhang14a}, demonstrating the utility of mid-$J$ lines in tracing 
+% with \LIR$\sim$10$^9$-10$^{12}$\Lsun 
+(Z14), demonstrating the utility of mid-$J$ lines in tracing 
 the star-forming dense gas, which will be routinely mapped in high-z galaxies with ALMA.
@@
 \noindent {\bf Technical overview}
-We propose to observe the \eco line at $\sim$0.15" resolution
-and the \dhcn and \dhcop lines at $\sim$0.7", assuming a line width 
-(FWHM) of 700\kms based on our \bco data
-(\Fig{combine}a) and a source size from our lens model (see details in TJ).
+We propose to observe the \eco line at 0.15" resolution
+and the \dhcn and \dhcop lines at 0.7", assuming a line 
+of 700\kms based on our \bco data
+and a source size from our lens model (see details in TJ).
 %, which takes into account the asymmetric line emission and spatial extent due to differential lensing. 
@@
 and 7 beams at 0.15" and 0.7", respectively. 
-We compute the target sensitivities for both science goals using \bco line flux. 
+We compute the target sensitivities for both science goals based on the \bco line flux. 
 For \eco, we adopt conservative 
@@
 \centering
-\includegraphics[trim=25 6 5 5, clip, width=0.75\textwidth]{Fig/combine}
+\includegraphics[trim=7 6 5 5, clip, width=0.75\textwidth]{Fig/combine}
 \caption{ \fontsize{10pt}{12pt}\selectfont {}
-% CO2-1 line profile
-{\em (a):} \textbf{PdBI \rot[CO]{2}{1} dynamically resolved line profile}
-The \bco spectrum showing a double-horned, highly asymmetric line profile, which arises due to 
-differential lensing across the kinematic components of the source (see (f)).
-% HST
-{\em (b):}  \textbf{Detection of a gas-rich merger with spatial variations traced by \bco}
-The (red, green, blue) contours correspond to the velocity-integrated 
-line flux of different velocity channels (red wing, line center, blue wing) in our \rot[CO]{2}{1} data. 
-{\em (c):} \textbf{RXJ1131-1231 kinematics in \bco}
-% 1st order
+{\em (a):}
+The \bco spectrum of RXJ1131-1231 shows a double-horned, highly 
+asymmetric line profile, which arises due to differential lensing.
+{\em (b):}
+Spatial variations traced by \bco as shown by the (red, green, blue) contours corresponding
+to the line flux of different velocity channels (red wing, line center, blue wing). 
+{\em (c):} 
 The observed velocity gradient is suggestive of a kinematically ordered disk at 
 the current resolution limit.
-{\em (d):} \textbf{RXJ1131-1231 dynamics in \bco}
-% 2nd order
+{\em (d):} 
 Velocity dispersion map of the \bco emitting gas. 
@@
 % RGB spectra
-{\em (e): } \textbf{Differential lensing with spatial variations}
-Overlay of spectra taken at regions along the strongest velocity gradient, demonstrating 
+{\em (e): }
+Overlay of spectra taken at three locations along the strongest velocity gradient, demonstrating 
 differential lensing of the different kinematic components of the galaxy. 
 % Lens model
-{\em (f): } \textbf{Dynamical lens model}
+{\em (f): }
 Velocity channels of the CO emission toward the gas-rich merger (red contours) overlaid on our best-fit 
@@
 The reconstructed source morphology (magenta ellipses) is suggestive of a kinematically ordered galaxy. 
-However, at the spatial resolution of our data, we cannot definitively infer its true morphology due to beam smearing. 
-Given the presence of a companion galaxy within 2.4 kpc, high-resolution 
+Given the presence of a companion galaxy within 2.4 kpc and beam smearing effects, high-resolution 
 imaging is thus necessary to unambiguously determine the nature that gives rise to the observed velocity gradient
@@
 dynamically unstable gas-rich disk. 
-We here aim to spatially and dynamically resolve the dense, excited gas emission, 
-which will allow us to unambiguously examine the dynamic structure of the ISM in 
-the distant merger and provide observational constraints on the star-formation and 
+{\bf We here aim BLAH}
+and provide observational constraints on the star-formation and 
 stellar-assembly history at the epoch where the SFR density is steeply 

### 2016-04-19 ALMA/Cycle4/RXJ.tex
ready for 2nd round

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Missing link between mergers/ULIRGs and their high-z analogues} 
-% \vspace{-0.25em}
-% \indent 
 \vspace{0.1em} {\bf Missing link between mergers/ULIRGs and their high-z analogues} 
 Ultraluminous infrared galaxies (ULIRGs: \LIR$\geq$10$^{12}$\Lsun) have been
-regarded as analogues of high-redshift (z) starbursts given their
-similarities in \LIR/\Lp\ and other physical properties.
-% (e.g. high-z SB display morphological evidence of past or ongoing merger)
-As such, detailed studies and characterization of ULIRGs are important 
+regarded as analogues of high-redshift (z) starbursts given the
+similarities in their interstellar medium (ISM; e.g. \LIR/\Lp).
+As such, detailed studies 
+of ULIRGs are important 
 to gain more detailed insight into the early universe and in studies of galaxy evolution over cosmic time.
-It is believed that mergers play an important role in giving rise to these dusty galaxies
+Since mergers are believed to play an important role in giving rise to these dusty galaxies
 (e.g. Sanders \& Mirabel 1996). Yet, merger-induced effects on the physical mechanisms and chemistry 
-that drive the intense starburst (SB) and active galactic nucleus (AGN) activities on small scales are still unclear.
+that drive the 
+%intense 
+starburst (SB) and active galactic nucleus (AGN) activities on small scales are still unclear.
 Thus characterizing the properties of the molecular gas that fuels star-formation (SF) and AGN is
 crucial to understand the interplay between AGN and SB
-and their relation to the interstellar medium (ISM) properties of galaxies across cosmic time.
+and their relation to the ISM properties of galaxies across cosmic time.
 
-While the ISM in local ULIRGs has been studied in great detail with ALMA,
+While the ISM in local ULIRGs has been studied in great detail,
 forming a rich inventory of molecular transitions that serves as the template for 
-understanding high-z galaxies and galaxy evolution \citep[e.g.][]{Rangwala15a}, a wide knowledge gap persists
+studying high-z galaxies 
+\citep[e.g.][]{Rangwala15a}, a wide knowledge gap persists
 between $z$=0 and the epoch when most stars are formed in the universe ($z$$\sim$2). 
-Understanding galaxy populations at the epoch when the build-up of stellar mass across cosmic
-time is steeply rising is thus critical and we here aim to bridge this gap by testifying
-correlations and properties found locally out to high/moderate redshifts by observing the 
-dynamical structure of the different molecular gas components
-in the quadruply lensed galaxy RXJ1131-1231 and its dust-obscured 
+Hence, understanding galaxy populations at which
+the build-up of stellar mass 
+is steeply rising is critical and we here aim to bridge this gap by testifying
+correlations and properties found locally out to high redshift by observing the 
+dynamical structure and properties of the ISM of
+the quadruply lensed galaxy RXJ1131-1231 and its dust-obscured 
 companion at $z_{\rm CO}$$\sim$0.65.
-%to bridge the gap between nearby ULIRGs and their high-z analogues.
 
-% \section*{Various molecular gas phases and the star-formation law} 
-% \vspace{-0.25em}
 \noindent {\bf Molecular gas in AGN/SB} 
-Owing to the high molecular gas fractions in ULIRGs and their high-z analogues,
+Owing to the high molecular gas fractions in ULIRGs,
+% and their high-z analogues, 
 their extreme SFRs are a natural consequence of either gas is being converted into stars
@@
 to understanding the mechanisms and physical processes taking
-place on different scales and how the physical conditions 
-are related to the starburst in ULIRGs at this epoch (when the SFR density is steeply rising).
+place on different scales and how the ISM physical conditions 
+are related to the SB in ULIRGs at this epoch. %(when the SFR density is steeply rising).
 
@@
 high-dipole moment molecules such as HCN and \hcop are expected to trace the 
-properties of the denser, actively star-forming gas. Indeed, a tight correlation between \ahcn and \LIR 
+%properties of the 
+denser, actively star-forming gas. Indeed, a tight correlation between \ahcn and \LIR 
 (proxy for SFR) has been found in nearby galaxies and local giant molecular 
@@
 % and that the origin can be attributed to the fundamental units of star formation. 
-This has been supported by the linear correlations in 
-\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] found recently \citep[hereafter Z14; see \Fig{SF}]{Zhang14a}, which also highlight 
-the great utility of these mid-$J$ lines observable for galaxies at $z$$>$0.06.
+However, \dhcn observations of (U)LIRGs have revealed a wide range of
+excitation conditions 
+%for their dense gas phase 
+that may render the ground state transition of 
+HCN and \hcop poor proxies of the dense gas mass \citep[hereafter P07]{Papadopoulos07a}.
+In this light, higher-$J$ transitions (e.g. $J$=4\rarr3) 
+% are necessary to scrutinize the reliability of using the ground state 
+have been suggested to be better probes
+% dense gas mass tracers since the mid-$J$ transitions
+since they trace the much denser gas (n$\gtrsim$10$^5-$10$^7$ cm$^{-3}$) that is 
+thought to be the immediate fuel for SF in turbulent GMCs \citep{Shirley03a, KM05}. 
+This has been supported by the linear correlations found in 
+\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] \citep[hereafter Z14]{Zhang14a}.
+Since the 
+ground state lines are redshifted to frequencies beyond the spectral coverage of ALMA
+at $z$$>$0.06, it is also necessary to establish diagnostics using these mid-$J$ lines to 
+study distant galaxies.
+Additionally, due to the difference in abundances and excitation conditions of HCN and \hcop
+in star-forming versus AGN regions, the line 
+% ratios \ahcn/HCO$^+$($J$=1\rarr0) \citep{Kohno05a, Imanishi10, Izumi13a} and
+ratio \dhcn/\dhcop \citep{Imanishi14a, GB14a, Viti14a} have been 
+proposed as
+%  diagnostic tools 
+a diagnostic tool to reveal deeply buried AGNs at the cores of ULIRGs \citep{Izumi16a, Imanishi16a}.
+% separate emission originating from AGN and SB
+% Recent studies have
+% extended this diagnostic to using the J=4\rarr3 transitions 
+%\citep{Imanishi14a, GB14a, Viti14a}, 
+% where an elevated line ratio is seen in AGNs, suggesting
+% it can be used to reveal deeply buried AGNs at the cores of ULIRGs \citep{Izumi16a, Imanishi16a}.
 
-Due to the difference in abundances and excitation conditions of HCN and \hcop
-in star-forming versus AGN regions, the line ratio \ahcn/HCO$^+$($J$=1\rarr0) has been 
-proposed as a diagnostic tool to separate emission originating from AGN and starburst
-\citep{Kohno05a, Imanishi10, Izumi13a}. 
- %(e.g. HCO+ is enhanced in SF regions in PDRs and SN shocks and HCN is enhanced in AGN)
-With the frequency coverage of ALMA, some studies have 
-extended this diagnostic to using the J=4\rarr3 transitions 
-\citep{Imanishi14a, GB14a, Viti14a}, where 
-an elevated \dhcn/\dhcop line ratio is also seen in AGNs, suggesting
-it, too, can be used to reveal a deeply buried AGN at the cores of ULIRGs \citep{Izumi16a, Imanishi16a}.
-
-Prior to ALMA, studies of dense gas were largely limited to the local universe ($z\lesssim$0.1) 
-with only five IR-luminous lensed galaxies detected at $z\gtrsim0.3$ 
-(e.g. \citealt{Riechers06a, Riechers07a, Riechers10a, Wagg05a, Gao07a}).
-However, none of these high-z detections spatially resolve the emission, rendering it difficult 
-to draw conclusions on the dense gas properties of galaxies at high redshifts. 
+Prior to ALMA, studies of dense gas were largely limited to the local universe ($z$$\lesssim$0.1) 
+with only five detections
+%IR-luminous lensed galaxies detected 
+at $z$$\gtrsim0.3$ 
+(\citealt{Riechers06a, Riechers07a, Riechers10a, Wagg05a, Gao07a}).
+Moreover, none of these 
+%high-z detections 
+spatially resolve the emission, rendering it difficult 
+to draw conclusions on the dense gas properties of galaxies at high redshift. 
 Even with ALMA, such studies will remain challenging, but by combining with
-the magnification provided by gravitational lensing and the exceptional spatial resolution and sensitivity of ALMA, studies
+the magnification provided by gravitational lensing and the exceptional spatial resolution and sensitivity of ALMA, 
+studies
 of dense molecular gas in distant galaxies are now possible, as proposed here.
@@
 \noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at high-z}
-\vspace{-0.7em}
+\vspace{-0.6em}
 %\begin{figure}[!tbhp]
@@
 \centering
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.425\textwidth}}]{figure}[\FBwidth]
+\hspace{-0.85em}
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.445\textwidth}}]{figure}[\FBwidth]
 {
-\hspace{-0.35em}
 \vspace*{-0.55em}
+\hspace{-0.435em}
 \raggedleft
@@
 {\em Left:} The rest-frame UV emission (tracing recent star formation) 
-is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
+is lensed into an almost complete Einstein ring with diameter $\sim$3.8". 
 {\em Right:} Lens modeling of the optical emission identifies complex structures in the host galaxy and
@@
 We here propose to study
-the ISM conditions in this AGN-starburst composite system and offers an unparalleled
+the ISM conditions in this AGN-starburst merger and offers an unparalleled
 view into the early universe, with finer
@@
 \includegraphics[trim= 10 0 0 0, clip, scale=0.3]{Fig/Manipulate_figsCROP}
-\vspace{-1em}
+\vspace{-1.0em}
+\hspace{-0.5em}
 }
@@
 from recent star formation (lensing arcs) and from the AGN (bright knots) in the background galaxy \citep{Sluse03a},
-demonstrating the great potential for probing the 
+demonstrating the great potential for probing its
 ISM conditions in detail. Lens modeling carried out on optical images shows
-that the AGN resides in a star-forming region of size $\sim$0.15" ($\sim$1 kpc)
-in its host galaxy, which itself is 1" across ($\sim$7 kpc), and made it possible to identify
-seven distinct structures in the source plane (\Fig{HST}). Remarkably, emission originating from 
-a spatially offset region ($\sim$2.4 kpc away) from the AGN host galaxy has been identified and found 
-to be $\sim$700 pc in size \citep{Brewer08a}, indicating a nearby companion galaxy. 
+that the AGN resides in a star-forming region of size $\sim$1 kpc
+% $\sim$0.15" (without lensing magnification)
+in its host galaxy, which itself is 7 kpc across, % $\sim$ 1 " (without lensing)
+and made it possible to identify
+seven distinct structures in the source plane (\Fig{HST}). Remarkably, emission 
+%originating 
+from 
+a spatially offset region ($\sim$2.4 kpc away from the AGN host galaxy) has been identified and found 
+to be $\sim$700 pc in size \citep{Brewer08a}, indicating a 
+%nearby 
+companion galaxy. 
 We have recently confirmed that both galaxies are at the same redshift by detecting their 
-\rot[CO]{2}{1} emission and lens-modeling the distribution of the gas in velocity space (\Fig{combine}f), 
-verifying that the both are gas-rich (Leung \& Riechers, in prep.). 
+\rot[CO]{2}{1} emission and lens-modeling their gas distribution 
+in velocity space (\Fig{combine}f), and verfiied
+that the both are gas-rich (Leung \& Riechers, in prep.). 
 Our SED modeling of the dust continuum emission up to 500\,$\mu$m finds $L_{\rm IR}\sim6\times$10$^{12}$\Lsun 
@@
 We here propose to map (1): \eco at 0.15" resolution ($\sim$500pc at $z$$\sim$0.7 in the source plane) and 
-(2): \dhcn and \dhcop emission at 0.7" resolution (2.5 kpc) and the underlying continuum.
-% The science goals at the proposed resolutions are designed to 
-The continuum emission traces the optically-thick dust emission, which 
-will provide better constraints on the dust temperature(s), dust mass,
-and spatial distribution, and thus a tighter constraint on the surface density of the SFR and 
-the gas-to-dust ratio. These quantities are key to investigate how the ISM conditions 
-vary as galaxies evolve.
+(2): \dhcn and \dhcop emission and the underlying continuum at 0.7" resolution (2.5 kpc in the source plane).
+The continuum traces the dust emission, 
+providing better constraints on the the gas-to-dust ratio, dust temperature(s), dust mass,
+and its spatial extent (and thus the surface density of the SFR).
+%($\Sigma_{\rm SFR}$).
+These quantities are key to investigate how the ISM % conditions 
+vary as galaxies evolve across cosmic time.
 In conjunction with the large set of ancillary data from
-rest-frame UV to radio wavelength and our new spectral line observations of \bco and \rot[CO]{3}{2}, our
-proposed observations will enable a detailed characterization of 
-merger/ULIRG in the following aspects.
+rest-frame UV to radio wavelength and our recent observations of \bco and \rot[CO]{3}{2}, our
+proposed observations are designed to investigate 
+% carry a detailed investigation of 
+the gas-rich merger aspects listed as follows.
 
@@
 Our recently obtained \bco data shows an asymmetric double-horned line profile (\Fig{combine}a). Given
-the observed 1$^{\rm st}$ moment map and the velocity gradient
+the 1$^{\rm st}$ moment map observed and the velocity gradient
 across the source plane in our model (\Fig{combine}c \& \ref{fig:combine}f), this is indicative of
-a kinematically ordered (reminiscent of a rotating disk) galaxy but its emission 
-has been lensed differentially. 
+a kinematically ordered %(reminiscent of a rotating disk) 
+galaxy but its emission has been lensed differentially. 
 Limited by the spatial resolution of this data, it is insufficient to infer the true 
@@
 $\gtrsim$400\kms at the central region (\Fig{combine}d) hints at 
-perturbations from the central AGN and/or
-internal turbulent motion due to interactions with the companion
+perturbations from the AGN and/or
+internal turbulence
+% motion 
+due to interactions with the companion
 and/or instability due to the huge gas reservoir.
-Thus, higher-resolution imaging, as proposed here, will allow us to
-distinguish the major mechanism driving the starburst: merger-driven 
-versus gas-rich clumpy disk, since we will also be able to obtain a detailed
-dynamical lens modeling of the system.
+Thus higher-resolution imaging, as proposed here, is needed
+% will allow us to
+to distinguish 
+%the major mechanism driving the starburst: 
+between a merger-driven and a turbulent clumpy disk starburst, 
+since we will be able to obtain a detailed
+dynamical lens modeling of the system, probing at sub-kpc scale. % probe down to 0.15" <-> 500 pc
 
-The \eco observations at 0.15" are complementary to the optical images,
-allowing a comparison between the stellar and gas distribution. 
-%{\bf The proposed observations will provide the data tracing 
-% the warm, excited, dense molecular gas distribution and kinematics, 
-% which we will compare against the diffuse component (traced by our already obtained lower-J CO data). 
-% OR 
-Additionally, since \eco, \dhcn and \dhcop trace the warm, excited, dense molecular gas,
-this will allow us to compare against the relatively unperturbed large-scale 
-molecular environment and the dynamical mass with our existing lower-$J$ CO data.
-% to study the
-% gas distribution and kinematics.
-Such comparison are key to understand the processes and timescales regulating star-formation 
-in ULIRG/merger, and examine how they differ from other galaxy populations.
+The \eco observations will be tracing emission on the size scale of high-z GMCs, 
+% complementary to the optical images,
+allowing us to compare the spatial distributions between recent star-formation (from HST) and star-forming 
+gas clumps. Since \eco, HCN and \hcop trace the warm, excited, dense molecular gas,
+this will as well allow us to compare against the relatively unperturbed large-scale 
+molecular environment and dynamical mass using our existing 
+low-$J$ CO data.
+Such comparisons are the key to understand different processes %and timescales 
+regulating star-formation 
+in ULIRGs/mergers and examine how they differ from other galaxy populations.
 
-\underline{\bf Line ratios as AGN/starburst diagnostic:}
-By measuring \dhcn/\dhcop in the 
-AGN host galaxy, separated from the companion, we will assess its fidelity as a 
-AGN/SB diagnostic at higher redshifts than current studies. 
-We will as well measure this ratio in the companion and examine the possibility of a 
-heavily-obscured AGN at its center. 
-Due to the high critical densities of these high-$J$ transitions (\ncrit$\sim$10$^{8}$cm$^{-3}$), 
-the \dhcn/CO and \dhcop/CO line ratios are expected to 
-be enhanced in AGNs on a global scale, enabling us to carry out a consistency check against the
-\dhcn/\dhcop line ratio diagnostic.
+\underline{\bf AGN/SB diagnostic:}
+At the proposed resolution, we will be able to distinguish \dhcn and \dhcop
+emission originating from the AGN host galaxy (and within) and from its companion.
+%  as well as 
+% resolving emission within the AGN host galaxy.  
+By observing spatial variations in this line ratio across the AGN host galaxy, 
+we will be able to assess its fidelity as an AGN/SB diagnostic,
+at higher redshift than current studies, since
+an elevated \dhcn/\dhcop is expected in nuclear regions near an AGN. 
+By measuring this ratio in the companion, we will as well 
+examine the possibility of a heavily-obscured AGN at its center.
+Since the HCN vibrational line (v$_2$=1) falls within the targeted frequency range, 
+we will use it to independently confirm the AGN in the companion, given that this line is excited by infrared 
+pumping (easily achieved near an AGN) and is the cause of the elevated \dhcn/\dhcop% , as observed in AGNs 
+\citep{Sakamoto10a,Imanishi13a}.
+% The HCN vibrational line requires high temperature to excite and has been detected in AGN host galaxies, which
+% has been attributed to arise/excited by IR radiative pumping near AGNs 
+% excited by AGN-heated hot dust providing IR radiative pumping.
 
 The high spin rate of the central black hole in RXJ1131-1231 (over half the speed of light; \citealt{Reis14a})
-%(M$_{\rm BH}$$\sim$2$\times$10$^{8}$M$_{\odot}$) 
-suggests that the black hole has grown via merger
-%[, which provided sufficient accreting materials for
-%the observed spin rate,] 
-rather than from small episodic accretions (from random directions).
-% In contrast if black holes grow through many small accretion episodes, 
-% they will accumulate material from random directions, and reduce spin.
-In this scenario, the companion and the AGN host galaxy may have already encountered previously.
-Therefore, our observations will improve our understanding 
-on the formation and evolution of supermassive black holes
-and the co-evolution with their host galaxies (and mergers).
-More interestingly, we might be witnessing the 
-pre/post merging/encounter of two AGN host galaxies if we find evidence of a buried AGN in the companion, 
-of which the proposed observations are needed to provide such clues.
+suggests that the black hole has grown via merger (i.e., the 
+% background 
+galaxies may have already encountered previously).
+In this scenario, we might be witnessing a
+second encounter of two AGN host galaxies if 
+we find evidence of a buried AGN in the companion, 
+which the proposed observations are needed to provide such clues.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\underline{\bf Spectral line energy distributions (SLED) and the SF Law:}
-On top of using \dhcn and \hcop as AGN/SB diagnostic, another 
- aspect 
- %for obtaining the proposed line observations 
- is to 
-% constrain the ISM conditions by fitting radiative transfer models.
-% since these molecular species
-% have different excitation criteria. %Therefore, 
-%In combination 
-combine them with \eco %, \dhcn, and \dhcop line emission
-and our existing low-$J$ CO data to perform radiative transfer modeling 
-% [with assumptions on their relative abundances] 
-to constrain the physical conditions 
-(e.g. density and gas kinetic temperature) of the multi-phase molecular gas.
-The \dhcn and \dhcop lines are essential as they trace beyond the $J$-transition of the CO SLED turnover
-(typically beyond $J$=6\rarr5 in local (U)LIRGs and high-z starbursts; \citealt{Greve14a}).
-% and since \eco traces the high kinetic temperature component. 
-In addition, since ISM studies of high-z galaxies typically adopt local SLED for comparison \citep[e.g.][]{Bothwell13a}
-and/or for asserting assumptions on the conditions of these high-z galaxies.
-%[due to the sparsely sampled SLED at high-z \citep{CW13}].
-Our observations will thus form a template at z$\sim$0.7 
-for these high-z studies.
+\underline{\bf Line ratios and physical conditions:}
+[In addition, we will measure spatially resolve line ratios (HCN/CO and \hcop/CO) within the AGN host galaxy
+as proxies of its very dense (cores; $\sim$10$^5$-10$^7$ cm$^{-3}$) versus the less dense (clumps; $\sim$10$^4$
+cm$^{-3}$) gas content and their spatial distributions.]
+OR 
+[In addition, we will measure spatially resolve line ratios (HCN/CO and \hcop/CO) within the AGN host galaxy
+to constrain the density gradients from $n$$\sim$10$^5$-10$^7$ 
+%cm$^{-3}$
+to $\sim$10$^4$cm$^{-3}$.]
 
-The ``star-formation law" (%$\Sigma_{\rm SFR}$=$A\Sigma^N_{gas}$ or 
-log\LIR=$\alpha$ log\Lp[X]+$\beta$)
-is one of the key ingredients % /observational constraints 
-for theoretical models as it encodes the physical processes 
-of star-formation and its dependence on the ISM 
-%(in the slopes and normalizations; 
+% kinematics
+We will also measure the linewidths of the very dense gas (traced by HCN and \hcop), 
+the excited gas (traced by \eco), and the more-extended, less-perturbed 
+molecular gas (traced by low-$J$ CO) at various locations to constrain 
+the kinematics and relative mass-fractions of different gas phases, 
+which are indications of the evolutionary stage of a galaxy.
+% XDR versus PDRs
+Since \eco is excited in higher temperature than the HCN and \hcop lines (e.g. in 
+X-ray dominated regions (XDRs) near an AGN), 
+variations in HCN/CO will allow us to constrain the spatial extents of photon dominated regions
+ (PDRs from starbursts) and XDRs.
+% (HCN/CO to be smaller for XDR than PDR because HCN is 
+% boosted in high column density gas and CO more excited in high Tkin)
+Due to differential lensing, we will be able obtain kinematical information
+on spatial scales smaller than the beam, as seen in our 
+\bco data (\Fig{combine}b \& \Fig{combine}c; the blue-shifted emission
+arises from a region that is positioned differently with respect to the caustic
+than the red-shifted emission), thereby
+% and thus recover structural details and kinematics in finer detail than otherwise possible
+enabling us to probe the aforementioned variations 
+and gradients in the inner molecular disk (near the AGN).
+
+Differential lensing between HCN, \hcop, and CO emission is also expected 
+as they trace different emitting regions and are arising from two galaxies. 
+Hence, high spatial resolution is necessary to accurately measure their intrinsic 
+line fluxes (free from differential
+lensing biases) as it enables a detailed lens modeling on each line emission.
+% surface brightness maps of HCN and \hcop
+% By measuring the differences in their surface density ratios (
+%  $\Sigma_{\rm HCN}$/$\Sigma_{\rm CO}$ and  $\Sigma_{\rm HCO^+}$/$\Sigma_{\rm CO}$),
+Such measurements are vital to reveal how galaxy interactions drive gas into 
+inner disks to initiate starbursts and AGN activities and how the ISM differ from 
+normal star-forming galaxies.
+% under the influence of an AGN and interactions with a companion. 
+% with lower uncertainties because surface density is conserved in lensed, but flux is boosted.  
+% CO SLED
+We will also combine \eco with our existing CO data to constrain the gas density (n$_{H_{2}}$) 
+and kinetic temperature by performing radiative transfer modeling.
+
+\underline{\bf The SK Law:}
+The Schmidt-Kennicutt (SK) relation (%``Star-formation law"; 
+$\Sigma_{\rm SFR}$=$A\Sigma^N_{\rm gas}$)
+is one of the key ingredients
+for theoretical models as it encodes the physical processes and timescales
+regulating star-formation and their dependence on the ISM 
 (e.g. \citealt{Narayanan14a}).
-% Observational constraints for the \LIR-\Lp[X] (\Lp of different lines) relations are vital.
-However, the \LIR-\Lp[X] at high critical density are currently poorly constrained due to the lack of observations 
-and are largely limited to the nearby universe
-\citep[\Fig{SF};][]{Greve14a}. Our proposed observations will help delineate 
-the slopes at high critical densities and 
-explore the linear correlations found 
-locally in \Lp[\dhcn]-\LIR and \Lp[\dhcop]-\LIR (\Fig{SF}; Z14) at higher redshifts.
-%
+% lot of studies on
+% how the power law index of KS law determined from observations should change depending on
+% the critical density of the tracer used to probe the SF gas (e.g. Krumholz \& Thompson 07, Narayana+08)
+% How SFR density should dependent on the global dynamical time scales in normal galaxies and in
+% merges
+However, the surface densities of gas at high densities (\ncrit$\sim$10$^7$cm$^{-3}$; 
+$\Sigma_{\rm dense}$; and thus $\Sigma_{\rm SFR}\propto
+\Sigma^N_{\rm dense}$) are currently poorly constrained due to the lack of 
+(spatially resolved) observations of the much weaker emission 
+from high critical density tracers. %(see right of \Fig{SF}).
+It is thus unclear how the power-law index of the SK law should change depending on
+the critical density of the tracer used to probe the SF gas \citep[e.g.][]{KT07a}.
+and how the SFR surface density should depend on the global 
+dynamical time scales in normal galaxies and in merges.
+% To alleviate poorly-constrained SK law with the lack of observational data
+% (on the SK relation), 
+To further underline the problem, the integrated form 
+(log\LIR=$\alpha$ log\Lp[X]+$\beta$; \citealt{SK})
+% \LIR-\Lp[X]) 
+has been commonly used as a proxy to the true SK relation,
+for which correlations found for dense gas tracers
+are incompatible with model predictions \citep[\Fig{SF}; Z14;][]{Greve14a}
+and largely based on constraints % on the SK relation 
+from local galaxies. 
+% thus the linear correlations may not hold at earlier epochs. % (\Fig{SF}).
+At the proposed resolutions, we will spatially resolve, for the first time,
+the {\it true surface density version of the SK relation} using tracers with \ncrit$\gtrsim$10$^5$cm$^{-3}$
+in a high-z merger: $\Sigma_{\rm SFR}$$\propto$$\Sigma^N_{\rm CO(5\rightarrow4)}$
+%\eco 
+in each of the interacting galaxies, and 
+$\Sigma_{\rm SFR}$$\propto$$\Sigma_{\rm HCN(4\rightarrow4)}$ and 
+$\Sigma_{\rm SFR}$$\propto$$\Sigma_{\rm HCO^+(4\rightarrow3)}$
+% \dhcn and \dhcop 
+within the AGN host galaxy and investigate potential variations in the power-law index.
+% This will allow us to investigate the 
+% variations in the true spatially resolved SK relation for high density 
+% (and hence star-formation modes) 
+% and provide constraints on the index $N$ at high critical densities
+% at higher redshift than existing work.
+
 \begin{figure*}[!tbph]
+\vspace{-1.5em}
 \centering
-\includegraphics[trim=15 0 5 10, clip, width=0.2\textwidth]{Fig/Zhang}
-\includegraphics[trim=5 5 5 10, clip, width=0.2\textwidth]{Fig/Zhang2}
-\includegraphics[trim=10 0 0 5, clip, width=0.38\textwidth]{Fig/Greve14Fig2}
-\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{The SF law: log \LIR = $\alpha$ log \Lp[X]+$\beta$.}}
-{\em Left \& middle:}
-A linear correlation between \LIR-\dhcn and \LIR-\dhcop have been established toward nearby galaxies 
-% with \LIR$\sim$10$^9$-10$^{12}$\Lsun 
-(Z14), demonstrating the utility of mid-$J$ lines in tracing 
+% \includegraphics[trim=5 0 435 0, clip, width=0.2\textwidth]{Fig/denseSK.eps}
+\includegraphics[trim=15 0 5 10, clip, width=0.23\textwidth]{Fig/Zhang}
+\hspace{-0.5em}
+% \includegraphics[trim=20 5 5 10, clip, width=0.22\textwidth]{Fig/Zhang2}
+\includegraphics[trim=117 5 5 10, clip, width=0.203\textwidth]{Fig/Zhang2}
+\includegraphics[trim=10 0 0 5, clip, width=0.33\textwidth]{Fig/Greve14Fig2}
+\includegraphics[trim=15 0 5 10, clip, width=0.22\textwidth]{Fig/SFRSD} % Garcia-Burillo+12
+\caption{ \fontsize{10pt}{12pt}\selectfont {
+{\em Left: } 
+\textbf{The SK proxy: log \LIR = $\alpha$ log \Lp[X]+$\beta$.}}
+Linear correlations in \LIR-\dhcn and \LIR-\dhcop have been established toward nearby galaxies 
+(Z14), suggesting a single star-formation efficiency for all galaxies
+and demonstrating the utility of mid-$J$ lines in tracing 
 the star-forming dense gas, which will be routinely mapped in high-z galaxies with ALMA.
-Our proposed observations will testify the linearity by adding measurements of a ULIRG at z$\sim$0.7, 
-% extending the statistics/data to higher redshifts, 
-and unveil potential deviations at higher redshift.
-{\em Right:} \textbf{Constraints on the SF law 
+{\em Middle panels:} \textbf{Constraints on the SK relation 
 with line transitions of different \ncrit.}
-Most observations are incompatible with current model predictions (gray shaded area),
+Most observations are incompatible with model predictions (gray shaded),
 especially for \dhcn
 \citep{Greve14a}. 
-Our proposed observations will thus reduce the uncertainties on the slopes at high critical densities
-and improve our current understanding of galaxy evolution.
+% Our proposed observations will provide constraints on
+% the slope ($alpha$) at high critical density. 
+{\em Right:} \textbf{The true SK relation for the dense gas using HCN($J$=1\rarr0)}
+%: $\Sigma_{\rm SFR}$=$\Sigma^N_{\rm gas}$}
+While constraints on the power-law index from gas of different densities are important for star-formation 
+models,
+current studies are only able to constrain the true SK law using the ground state HCN line 
+(\ncrit$\sim$10$^{4}$) and largely limited to nearby measurements
+%  due to the lack of spatially resolved observations of
+% dense gas tracers at high redshift 
+\citep{GC08a}. 
+% It also appears that (U)LIRGs (\LIR$>$$10^{11}$\Lsun)
+% and normal (\LIR$<$$10^{11}$\Lsun) galaxies have do not follow the same power law (different SFE).
+Our proposed observations will, for the first time, spatially resolve the true 
+SK relation with high critical density tracers in a merger at $z$$\sim$0.7, 
+exploring potential deviations in SK relation at higher redshift, providing 
+key constraints for models of galaxy evolution.
 \label{fig:SF}}
+\vspace{-0.85em}
 \end{figure*}
@@
 \noindent {\bf Technical overview}
-We propose to observe the \eco line at 0.15" resolution
-and the \dhcn and \dhcop lines at 0.7", assuming a line 
-of 700\kms based on our \bco data
-and a source size from our lens model (see details in TJ).
+% We propose to observe the \eco line at 0.15" resolution
+% and the \dhcn and \dhcop lines at 0.7", 
+We estimate the line widths and fluxes 
+% assuming a line width
+% of 700\kms 
+based on our \bco data, and a source size from our lens model.
 %, which takes into account the asymmetric line emission and spatial extent due to differential lensing. 
 We thus expect the source to be resolved over 153 beams 
-and 7 beams at 0.15" and 0.7", respectively. 
-We compute the target sensitivities for both science goals based on the \bco line flux. 
-For \eco, we adopt conservative 
-line ratios measured for SMGs \citep[][see TJ for details]{CW13},
-and those based on (U)LIRGs for \dhcn (GS04; \citealt{Papadopoulos07a}).
+and 7 beams at 0.15" and 0.7", respectively (see TJ for details). 
+% We compute the target sensitivities for both science goals based on the \bco line flux. 
+We adopt conservative 
+line ratios measured for high-z galaxies for \eco line \citep[][]{CW13}
+and those based on (U)LIRGs for \dhcn (GS04; P07).
 For \dhcop, we adopt the line ratio \dhcn/\dhcop found in ULIRGs 
@@
 for the science goals, respectively. 
-We therefore request a \textbf{total time of 7.0 hours}.% to complete our science goals.
+% We therefore request a \textbf{total time of 7.0 hours}.% to complete our science goals.
 
@@
 % closing
-\par 
-Our proposed observations present an exceptional opportunity to investigate
-the physical properties and dynamical structures of 
-%different gas phases in 
-the ISM in mergers at the cosmic epoch 
-where the SFR density is steeply rising \citep{LeFloch05a}, 
-connecting high redshift and nearby studies to improve our understanding of galaxy evolution.
-%Our proposed observations are vital
-%% between the \LIR, SFR$_{\rm IR}$, SFR$_{\rm UV}$, surface densities of SFR, CO, HCN and \hcop,
-%to provide constraints on the relation between the ISM and AGN/SB acitvities
-%on sub-kpc scales and on the mechanisms driving the vast SFR at earlier epochs, 
-%giving rise to the observed stellar-assembly history.
-%
-This will also % lay the groundwork to 
-serve as a benchmark demonstrating the future prospects for ALMA in 
-utilizing high-dipole moment molecules as routine tracers to study star-formation 
-at high redshifts.
+%\par 
+%Our proposed observations present an exceptional opportunity to investigate
+%the physical properties and dynamical structures of 
+%%different gas phases in 
+%the ISM in mergers at the cosmic epoch 
+%where the SFR density is steeply rising \citep{LeFloch05a}, 
+%connecting high redshift and nearby studies to improve our understanding of galaxy evolution.
+%%Our proposed observations are vital
+%%% between the \LIR, SFR$_{\rm IR}$, SFR$_{\rm UV}$, surface densities of SFR, CO, HCN and \hcop,
+%%to provide constraints on the relation between the ISM and AGN/SB acitvities
+%%on sub-kpc scales and on the mechanisms driving the vast SFR at earlier epochs, 
+%%giving rise to the observed stellar-assembly history.
+%%
+%This will also % lay the groundwork to 
+%% serve as a benchmark demonstrating
+%demonstrate the future prospects for ALMA in 
+%utilizing high-dipole moment molecules as routine tracers to study star-formation 
+%at high redshift.
 
-\begin{figure*}[tbph]
+\begin{figure*}[!tbph]
 \centering
-\includegraphics[trim=7 6 5 5, clip, width=0.75\textwidth]{Fig/combine}
-\caption{ \fontsize{10pt}{12pt}\selectfont {}
+\vspace{-0.5em}
+\hspace{-2.1em}
+% \floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.495\textwidth}}]{figure}[\FBwidth]
+{
+\includegraphics[trim=7 6 5 5, clip, width=0.85\textwidth]{Fig/combine}}
+{
+\hspace{-0.85em}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{\bco}}
 {\em (a):}
-The \bco spectrum of RXJ1131-1231 shows a double-horned, highly 
-asymmetric line profile, which arises due to differential lensing.
+A double-horned, asymmetric line profile arising due to differential lensing.
 {\em (b):}
-Spatial variations traced by \bco as shown by the (red, green, blue) contours corresponding
-to the line flux of different velocity channels (red wing, line center, blue wing). 
+Observed spatial variations across the channels, as shown by the red (red-shifted), 
+green (line center), and blue (blue-shifted) contours.
+% corresponding to the line emission of different velocity channels (red wing, line center, blue wing). 
 {\em (c):}
@@
 the current resolution limit. 
+Spatial variations across different kinematic components are also see within the beam, indicating 
+the spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial 
+scales than otherwise possible.
+% Spatial variations of the different velocities are seen within the beam (see (e)).
 {\em (d):} 
-Velocity dispersion map of the \bco emitting gas. 
-However, limited by the spatial resolution, beam smearing strongly decreases
-large-scale velocity gradients and increases observed dispersion.
+An usually high velocity dispersion is observed but the 
+true dynamics is unclear due to beam smearing effects.
+% However, limited by the spatial resolution, beam smearing strongly decreases
+% large-scale velocity gradients and increases observed dispersion.
 % RGB spectra
-{\em (e): }
-Overlay of spectra taken at three locations along the strongest velocity gradient, demonstrating 
-differential lensing of the different kinematic components of the galaxy. 
+{\em (e):}
+Spectra taken at three locations along the strongest velocity gradient, demonstrating
+differential lensing of the kinematic components of the gas-rich ``disk".
 % Lens model
-{\em (f): }
-Velocity channels of the CO emission toward the gas-rich merger (red contours) overlaid on our best-fit 
-lens model for each velocity bin (grayscale). 
-The foreground lensing galaxy is represented by a black dot, and 
-the beam size is shown in the bottom right corner.
-Clearly, there are spatial variations across different kinematic components.
-The reconstructed source morphology (magenta ellipses) is suggestive of a kinematically ordered galaxy. 
+{\em (f):}
+Channel maps of the CO emission (red) 
+%toward the gas-rich merger 
+overlaid on our best-fit lens models (grayscale). 
+The foreground lensing galaxy is represented by a black dot.
+% and the beam size is shown in the bottom right corner.
+% Clearly, there are spatial variations across different kinematic components.
+The reconstructed source morphology (magenta ellipses) is also suggestive of a ``disk".
+% kinematically ordered galaxy. 
 Given the presence of a companion galaxy within 2.4 kpc and beam smearing effects, high-resolution 
-imaging is thus necessary to unambiguously determine the nature that gives rise to the observed velocity gradient
-and dynamics, as proposed here.
-This will confirm if the system is rotationally supported or highly turbulent 
-(tidally disrupted) and allow us to investigate the major mechanisms responsible 
-for the starburst in the AGN host galaxy
-and investigate whether dominant mode of star formation is GMC-like in a rotating disk or due to fragmentation of
-dynamically unstable gas-rich disk. 
-{\bf We here aim BLAH}
-and provide observational constraints on the star-formation and 
-stellar-assembly history at the epoch where the SFR density is steeply 
+imaging is necessary to unambiguously determine the nature that gives rise to the observed velocity gradient
+and dispersion, as proposed here.
+% This will confirm if the system is rotationally supported or highly turbulent 
+% (or tidally disrupted) and 
+This will allow us to investigate the 
+% major 
+mechanisms responsible for the starburst in the AGN host galaxy
+% and investigate whether dominant mode of star formation is 
+(e.g. GMC-like in a rotating disk or due to fragmentation of
+dynamically unstable gas-rich disk) and its ISM conditions as it interacts with the companion. 
+We therefore aim to spatially resolve the gas dynamics, kinematics and ISM conditions in a merger,
+providing observational constraints 
+on the star-formation processes
+%star-formation history, 
+at the epoch where the SFR density is steeply 
 rising across cosmic times.
 \label{fig:combine}}
+}
+\vspace{-0.855em}
 \end{figure*}
@@
 
-\noindent \bf {References}
+\noindent \textbf{References}
 {\fontsize{10pt}{12pt}\selectfont

### 2016-04-20 ALMA/Cycle4/RXJ.tex
with DR's 2nd round comments

@@
 %	       text vertically in the page.  
-
 \documentclass[12pt,a4paper]{article} 
@@
 between $z$=0 and the epoch when most stars are formed in the universe ($z$$\sim$2). 
-Hence, understanding galaxy populations at which
+Hence, understanding galaxy populations at an epoch when
 the build-up of stellar mass 
@@
 the quadruply lensed galaxy RXJ1131-1231 and its dust-obscured 
-companion at $z_{\rm CO}$$\sim$0.65.
+companion at $z_{\rm CO}$$\sim$0.65 (\Fig{HST}).
 
@@
 This has been supported by the linear correlations found in 
-\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] \citep[hereafter Z14]{Zhang14a}.
+\LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] \citep[]{Zhang14a}.
 Since the 
@@
 %IR-luminous lensed galaxies detected 
-at $z$$\gtrsim0.3$ 
-(\citealt{Riechers06a, Riechers07a, Riechers10a, Wagg05a, Gao07a}).
+at $z$$\gtrsim$0.3
+(e.g. \citealt{Riechers07a, Riechers10a, Wagg05a, Gao07a}).
 Moreover, none of these 
-%high-z detections 
 spatially resolve the emission, rendering it difficult 
-to draw conclusions on the dense gas properties of galaxies at high redshift. 
-Even with ALMA, such studies will remain challenging, but by combining with
-the magnification provided by gravitational lensing and the exceptional spatial resolution and sensitivity of ALMA, 
+to draw more detailed conclusions on the dense gas properties of galaxies at high z. 
+Even with ALMA, such studies will remain challenging, but by combining 
+the magnification provided by gravitational lensing with the exceptional spatial resolution and sensitivity of ALMA, 
 studies
@@
 \caption{ \fontsize{10pt}{12pt}\selectfont 
-{
-\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
+{\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
 morphology}
@@
 We here propose to study
-the ISM conditions in this AGN-starburst merger and offers an unparalleled
-view into the early universe, with finer
+the ISM conditions in this AGN-starburst merger with finer
 detail than otherwise possible with current facilities. 
@@
 \rot[CO]{2}{1} emission and lens-modeling their gas distribution 
-in velocity space (\Fig{combine}f), and verfiied
+in velocity space (\Fig{combine}f), and verified
 that the both are gas-rich (Leung \& Riechers, in prep.). 
-Our SED modeling of the dust continuum emission up to 500\,$\mu$m finds $L_{\rm IR}\sim6\times$10$^{12}$\Lsun 
+Our SED modeling of the dust continuum emission up to 250\,$\mu$m finds $L_{\rm IR}\sim6\times$10$^{12}$\Lsun 
 (corrected for lensing). Hence, this target is a gas-rich ULIRG merger at $z$$\sim$0.7 caught in the act.
@@
 % carry a detailed investigation of 
-the gas-rich merger aspects listed as follows.
+the gas-rich merger in aspects listed as follows.
 
@@
 the 1$^{\rm st}$ moment map observed and the velocity gradient
-across the source plane in our model (\Fig{combine}c \& \ref{fig:combine}f), this is indicative of
+across the source plane in our model (\Fig{combine}d \& \ref{fig:combine}f), this is indicative of
 a kinematically ordered %(reminiscent of a rotating disk) 
-galaxy but its emission has been lensed differentially. 
-Limited by the spatial resolution of this data, it is insufficient to infer the true 
+galaxy, but its emission has been lensed differentially. 
+Limited by the spatial resolution of this data, it is not possible to infer the true 
 kinematics due to beam smearing.
 Furthermore, the unusually high velocity dispersion 
-$\gtrsim$400\kms at the central region (\Fig{combine}d) hints at 
+$\gtrsim$400\kms at the central region (\Fig{combine}e) hints at 
 perturbations from the AGN and/or
@@
 and/or instability due to the huge gas reservoir.
-Thus higher-resolution imaging, as proposed here, is needed
-% will allow us to
+Thus higher-resolution \eco imaging, as proposed here, is needed
 to distinguish 
-%the major mechanism driving the starburst: 
 between a merger-driven and a turbulent clumpy disk starburst,
-since we will be able to obtain a detailed
-dynamical lens modeling of the system, probing at sub-kpc scale. % probe down to 0.15" <-> 500 pc
 
-The \eco observations will be tracing emission on the size scale of high-z GMCs, 
-% complementary to the optical images,
-allowing us to compare the spatial distributions between recent star-formation (from HST) and star-forming 
-gas clumps. Since \eco, HCN and \hcop trace the warm, excited, dense molecular gas,
-this will as well allow us to compare against the relatively unperturbed large-scale 
-molecular environment and dynamical mass using our existing 
-low-$J$ CO data.
-Such comparisons are the key to understand different processes %and timescales 
-regulating star-formation 
+The requested resolution (0.15") for \eco is critical
+as it allows us to obtain a detailed
+dynamical lens model of the system, probing at sub-kpc scale % probe down to 0.15" <-> 500 pc
+(typical size scale of high-z GMCs), which enables us 
+to compare the spatial distributions of star-forming gas clumps 
+with recent star-formation (from HST).
+Such comparisons are the key to understand different processes
+that regulate the star-formation/SB
 in ULIRGs/mergers and examine how they differ from other galaxy populations.
-
-\underline{\bf AGN/SB diagnostic:}
-At the proposed resolution, we will be able to distinguish \dhcn and \dhcop
-emission originating from the AGN host galaxy (and within) and from its companion.
-%  as well as 
-% resolving emission within the AGN host galaxy.  
-By observing spatial variations in this line ratio across the AGN host galaxy, 
-we will be able to assess its fidelity as an AGN/SB diagnostic,
-at higher redshift than current studies, since
-an elevated \dhcn/\dhcop is expected in nuclear regions near an AGN. 
-By measuring this ratio in the companion, we will as well 
-examine the possibility of a heavily-obscured AGN at its center.
-Since the HCN vibrational line (v$_2$=1) falls within the targeted frequency range, 
-we will use it to independently confirm the AGN in the companion, given that this line is excited by infrared 
-pumping (easily achieved near an AGN) and is the cause of the elevated \dhcn/\dhcop% , as observed in AGNs 
-\citep{Sakamoto10a,Imanishi13a}.
-% The HCN vibrational line requires high temperature to excite and has been detected in AGN host galaxies, which
-% has been attributed to arise/excited by IR radiative pumping near AGNs 
-% excited by AGN-heated hot dust providing IR radiative pumping.
-
-The high spin rate of the central black hole in RXJ1131-1231 (over half the speed of light; \citealt{Reis14a})
-suggests that the black hole has grown via merger (i.e., the 
-% background 
-galaxies may have already encountered previously).
-In this scenario, we might be witnessing a
-second encounter of two AGN host galaxies if 
-we find evidence of a buried AGN in the companion, 
-which the proposed observations are needed to provide such clues.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\underline{\bf Line ratios and physical conditions:}
-[In addition, we will measure spatially resolve line ratios (HCN/CO and \hcop/CO) within the AGN host galaxy
-as proxies of its very dense (cores; $\sim$10$^5$-10$^7$ cm$^{-3}$) versus the less dense (clumps; $\sim$10$^4$
-cm$^{-3}$) gas content and their spatial distributions.]
-OR 
-[In addition, we will measure spatially resolve line ratios (HCN/CO and \hcop/CO) within the AGN host galaxy
-to constrain the density gradients from $n$$\sim$10$^5$-10$^7$ 
-%cm$^{-3}$
-to $\sim$10$^4$cm$^{-3}$.]
-
 % kinematics
@@
 the excited gas (traced by \eco), and the more-extended, less-perturbed 
-molecular gas (traced by low-$J$ CO) at various locations to constrain 
-the kinematics and relative mass-fractions of different gas phases, 
+molecular gas (traced by low-$J$ CO) at various regions within the AGN host galaxy 
+to constrain the kinematics and relative mass-fractions of different gas phases, 
 which are indications of the evolutionary stage of a galaxy.
+
+\underline{\bf Line ratios and the AGN/SB diagnostic:}
+Aided by lensing, we will be able obtain kinematical information on spatial 
+scales smaller than the beam, as seen in our \bco data (\Fig{combine}c, d), thereby
+% and thus recover structural details and kinematics in finer detail than otherwise possible
+enabling us to probe the physical properties of
+the inner molecular disk near the AGN. 
+% At the proposed resolution, we will be able to distinguish the \dhcn and \dhcop
+% emission originating from the AGN host galaxy (and within) and from its companion.
+Recent studies find that the \dhcn/\dhcop line ratio is expected to be enhanced 
+in the circumnuclear disk (CND) near an AGN and falls off with distance from the CND
+\citep{GB14a,Imanishi16a}. At the proposed resolution, we will 
+resolve the line emission originating near the AGN and that from the spatially extended 
+SB regions ($>$kpc scale) in the host galaxy, and by measuring spatial variations in 
+this line ratio, we will assess its utility 
+as an AGN/SB diagnostic (\Fig{AGNSB}) at high redshift.
+Since the HCN vibrational line (v$_2$=1) falls within the targeted frequency range, 
+we will use it to independently constrain the radiation properties of the AGN environment, 
+given that this line is excited by infrared pumping and that the radiation
+field associated with the AGN is the cause of the elevated \dhcn/\dhcop
+\citep{Sakamoto10a,Imanishi13a}.
+The proposed spatial resolution is also necessary for
+a detailed lens modeling of each emission line, enabling measurements of reliable line 
+ratios, without significant uncertainties due to differential lensing.
+Such measurements are vital to reveal how galaxy interactions drive gas into 
+inner disks to initiate SB/AGN activities and how the ISM differ from 
+normal star-forming galaxies.
+
+\begin{figure*}[!tbph]
+\vspace{-0.8em}
+\hspace{-0.65em}
+\centering
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.565\textwidth}}]{figure}[\FBwidth]
+{\includegraphics[trim=15 0 5 10, clip, width=0.385\textwidth]{Fig/izumi15}}
+{
+\hspace{-1.25em}
+\vspace{-1.15em}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{\dhcn/\dhcop as AGN/SB diagnostic}
+Difference in line ratios between local AGNs, SBs, and (U)LIRGs with buried AGNs suggest
+that \dhcn/\dhcop can be used as a diagnostic tool to reveal the dominant power source within the
+beam, where an elevated line ratio is seen in AGN and circumnuclear regions relative to SB regions/galaxies.
+Such diagnostic depends heavily on the spatial resolution, as demonstrated by the
+measurements taken with APEX (empty circle) and ALMA (filled circles) in NGC1068.
+We here propose to spatially resolve this line ratio within the AGN host galaxy and obtain
+measurements near the AGN and the extended SB regions to investigate spatial variations 
+in order to assess its utility as a AGN/SB diagnostic at high redshift.
+(Figure taken from \citealt{Izumi16a})}
+\label{fig:AGNSB}}
+}
+\vspace{-0.905em}
+\end{figure*}
+
+% 
+% mounting supporting evidence for such elevated
+% HCN emission at the centers of local Seyfert galaxies has been accumulated (e.g., Kohno
+% et al. 2001; Imanishi et al. 2006; Krips et al. 2008), giving an empirical AGN diagnostic.
+%
+%mounting evidence that HCN lines can be
+%overluminous with respect to the lines of other dense molecular
+%gas tracers, like HCO+, in the circumnuclear disks of
+%Seyferts (Kohno et al. 2001; Usero et al. 2004; Kohno 2005).
+%A significant percentage of luminous and ultraluminous infrared
+%galaxies (LIRGs and ULIRGs) has also been reported
+%to show high HCN/HCO+ intensity ratios (Graciá-Carpio et al.
+%2006; Imanishi et al. 2006, 2007).
+% 
+%  More recently, spatially resolved ALMA observations
+% of HCN(4-3) and HCO+(4-3) at the CND of NGC 1068 at a ?50 pc resolution reveal
+% that the HCN(4-3)/HCO+(4-3) line ratios are indeed highly elevated at the CND but
+% not significantly at the very position of the active nucleus (Garc??a-Burillo et al. 2014;
+% Viti et al. 2014). This indicates that HCN enhancement is not simply caused by X-ray
+% irradiation. Recent HCN(4-3)/HCO+(4-3) measurements of the high-luminosity
+% type-1 AGN NGC 7469 (Izumi et al. 2015a) with LX = 2 × 1043 erg s?1
+% suggest that the
+% degree of HCN enhancement is not very different from that in NGC 1097 (Izumi et al.
+% 2013), a much lower luminosity type-1 AGN (LX = 7×1040 erg s?1
+% ), also adding further
+% evidence against the XDR origin of enhanced HCN in AGNs (see also Mart??n et al. 2015).
+% 
 % XDR versus PDRs
@@
 X-ray dominated regions (XDRs) near an AGN), 
-variations in HCN/CO will allow us to constrain the spatial extents of photon dominated regions
- (PDRs from starbursts) and XDRs.
-% (HCN/CO to be smaller for XDR than PDR because HCN is 
-% boosted in high column density gas and CO more excited in high Tkin)
-Due to differential lensing, we will be able obtain kinematical information
-on spatial scales smaller than the beam, as seen in our 
-\bco data (\Fig{combine}b \& \Fig{combine}c; the blue-shifted emission
-arises from a region that is positioned differently with respect to the caustic
-than the red-shifted emission), thereby
-% and thus recover structural details and kinematics in finer detail than otherwise possible
-enabling us to probe the aforementioned variations 
-and gradients in the inner molecular disk (near the AGN).
+variations in HCN/CO will allow us to constrain the spatial extent of photon-dominated regions
+ (PDRs from SBs) and XDRs.
+% physical properties
+In addition, we will measure spatially resolved line ratios of HCN/CO and \hcop/CO within the AGN host galaxy
+as proxies of its very dense (cores; $\sim$10$^5$-10$^7$ cm$^{-3}$) versus the less dense (clumps; $\sim$10$^4$
+cm$^{-3}$) gas content and their spatial distributions as a function of distance from the AGN/nucleus. This will enable
+us to gain insight into the interplay between AGN, SB and the dense gas content in the ISM (and thus the SF mode on small scales across different galaxy populations as traced by the HCN/CO-\LIR relation).
+% \Fig{SF}).
+% CO SLED
+We will also combine \eco with our existing \bco and CO($J$=3\rarr2) data to constrain the gas density (n$_{H_{2}}$) 
+and kinetic temperature by performing large velocity gradient modeling.
 
-Differential lensing between HCN, \hcop, and CO emission is also expected 
-as they trace different emitting regions and are arising from two galaxies. 
-Hence, high spatial resolution is necessary to accurately measure their intrinsic 
-line fluxes (free from differential
-lensing biases) as it enables a detailed lens modeling on each line emission.
-% surface brightness maps of HCN and \hcop
-% By measuring the differences in their surface density ratios (
-%  $\Sigma_{\rm HCN}$/$\Sigma_{\rm CO}$ and  $\Sigma_{\rm HCO^+}$/$\Sigma_{\rm CO}$),
-Such measurements are vital to reveal how galaxy interactions drive gas into 
-inner disks to initiate starbursts and AGN activities and how the ISM differ from 
-normal star-forming galaxies.
-% under the influence of an AGN and interactions with a companion. 
-% with lower uncertainties because surface density is conserved in lensed, but flux is boosted.  
-% CO SLED
-We will also combine \eco with our existing CO data to constrain the gas density (n$_{H_{2}}$) 
-and kinetic temperature by performing radiative transfer modeling.
-
-\underline{\bf The SK Law:}
+\underline{\bf The SK Law for dense gas:}
 The Schmidt-Kennicutt (SK) relation (%``Star-formation law"; 
-$\Sigma_{\rm SFR}$=$A\Sigma^N_{\rm gas}$)
+$\Sigma_{\rm SFR}$$\propto$$\Sigma^N_{\rm gas}$)
 is one of the key ingredients
@@
 (e.g. \citealt{Narayanan14a}).
-% lot of studies on
-% how the power law index of KS law determined from observations should change depending on
-% the critical density of the tracer used to probe the SF gas (e.g. Krumholz \& Thompson 07, Narayana+08)
-% How SFR density should dependent on the global dynamical time scales in normal galaxies and in
-% merges
-However, the surface densities of gas at high densities (\ncrit$\sim$10$^7$cm$^{-3}$; 
-$\Sigma_{\rm dense}$; and thus $\Sigma_{\rm SFR}\propto
-\Sigma^N_{\rm dense}$) are currently poorly constrained due to the lack of 
+However, the surface density of gas at high densities (\ncrit$\gtrsim$10$^5$cm$^{-3}$; 
+$\Sigma_{\rm dense}$)
+% ; and thus $\Sigma_{\rm SFR}\propto \Sigma^N_{\rm dense}$) 
+is currently poorly constrained 
+for high-z galaxies due to the lack of 
 (spatially resolved) observations of the much weaker emission 
@@
 It is thus unclear how the power-law index of the SK law should change depending on
-the critical density of the tracer used to probe the SF gas \citep[e.g.][]{KT07a}.
+the critical density of the tracer used to probe the SF gas \citep[e.g.][]{KT07a}
 and how the SFR surface density should depend on the global 
-dynamical time scales in normal galaxies and in merges.
-% To alleviate poorly-constrained SK law with the lack of observational data
-% (on the SK relation), 
-To further underline the problem, the integrated form 
-(log\LIR=$\alpha$ log\Lp[X]+$\beta$; \citealt{SK})
-% \LIR-\Lp[X]) 
-has been commonly used as a proxy to the true SK relation,
-for which correlations found for dense gas tracers
-are incompatible with model predictions \citep[\Fig{SF}; Z14;][]{Greve14a}
-and largely based on constraints % on the SK relation 
-from local galaxies. 
-% thus the linear correlations may not hold at earlier epochs. % (\Fig{SF}).
-At the proposed resolutions, we will spatially resolve, for the first time,
-the {\it true surface density version of the SK relation} using tracers with \ncrit$\gtrsim$10$^5$cm$^{-3}$
-in a high-z merger: $\Sigma_{\rm SFR}$$\propto$$\Sigma^N_{\rm CO(5\rightarrow4)}$
-%\eco 
-in each of the interacting galaxies, and 
-$\Sigma_{\rm SFR}$$\propto$$\Sigma_{\rm HCN(4\rightarrow4)}$ and 
-$\Sigma_{\rm SFR}$$\propto$$\Sigma_{\rm HCO^+(4\rightarrow3)}$
-% \dhcn and \dhcop 
-within the AGN host galaxy and investigate potential variations in the power-law index.
-% This will allow us to investigate the 
-% variations in the true spatially resolved SK relation for high density 
-% (and hence star-formation modes) 
-% and provide constraints on the index $N$ at high critical densities
-% at higher redshift than existing work.
+dynamical time scales in normal galaxies and in mergers.
+At the proposed resolution, we will spatially resolve, for the first time,
+the {\it true SK relation} by measuring the dense gas surface density (\ncrit$\gtrsim$10$^5$cm$^{-3}$)
+in a high-z merger, down to the size scale of star-forming gas clumps. 
+Hence, providing crucial constraints on star-formation at high redshift.
+
+\noindent Our proposed observations therefore provide an exceptional opportunity to investigate
+the physical properties and dynamical structures of different gas phases in the ISM of mergers 
+and distant galaxies with exquisite details. Such investigations are vital to bridge the gap in our 
+current understanding on galaxy populations across cosmic time.
+This will also demonstrate the capabilities of ALMA in % mapping 
+utilizing these much fainter emission 
+high-dipole moment molecules as routine tracers to 
+study star-formation at earlier epochs.
 
 \begin{figure*}[!tbph]
-\vspace{-1.5em}
+\vspace{-1.85em}
 \centering
-% \includegraphics[trim=5 0 435 0, clip, width=0.2\textwidth]{Fig/denseSK.eps}
-\includegraphics[trim=15 0 5 10, clip, width=0.23\textwidth]{Fig/Zhang}
-\hspace{-0.5em}
-% \includegraphics[trim=20 5 5 10, clip, width=0.22\textwidth]{Fig/Zhang2}
-\includegraphics[trim=117 5 5 10, clip, width=0.203\textwidth]{Fig/Zhang2}
-\includegraphics[trim=10 0 0 5, clip, width=0.33\textwidth]{Fig/Greve14Fig2}
-\includegraphics[trim=15 0 5 10, clip, width=0.22\textwidth]{Fig/SFRSD} % Garcia-Burillo+12
-\caption{ \fontsize{10pt}{12pt}\selectfont {
-{\em Left: } 
-\textbf{The SK proxy: log \LIR = $\alpha$ log \Lp[X]+$\beta$.}}
-Linear correlations in \LIR-\dhcn and \LIR-\dhcop have been established toward nearby galaxies 
-(Z14), suggesting a single star-formation efficiency for all galaxies
-and demonstrating the utility of mid-$J$ lines in tracing 
-the star-forming dense gas, which will be routinely mapped in high-z galaxies with ALMA.
-{\em Middle panels:} \textbf{Constraints on the SK relation 
-with line transitions of different \ncrit.}
-Most observations are incompatible with model predictions (gray shaded),
-especially for \dhcn
-\citep{Greve14a}. 
-% Our proposed observations will provide constraints on
-% the slope ($alpha$) at high critical density. 
-{\em Right:} \textbf{The true SK relation for the dense gas using HCN($J$=1\rarr0)}
-%: $\Sigma_{\rm SFR}$=$\Sigma^N_{\rm gas}$}
-While constraints on the power-law index from gas of different densities are important for star-formation 
-models,
-current studies are only able to constrain the true SK law using the ground state HCN line 
-(\ncrit$\sim$10$^{4}$) and largely limited to nearby measurements
-%  due to the lack of spatially resolved observations of
-% dense gas tracers at high redshift 
-\citep{GC08a}. 
-% It also appears that (U)LIRGs (\LIR$>$$10^{11}$\Lsun)
-% and normal (\LIR$<$$10^{11}$\Lsun) galaxies have do not follow the same power law (different SFE).
-Our proposed observations will, for the first time, spatially resolve the true 
-SK relation with high critical density tracers in a merger at $z$$\sim$0.7, 
-exploring potential deviations in SK relation at higher redshift, providing 
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.5575\textwidth}}]{figure}[\FBwidth]
+{
+% HCN/CO - LIR plot: e.g. Fig 6 in \citep{Juneau09a}
+\includegraphics[trim=15 0 5 10, clip, width=0.257\textwidth]{Fig/SFRSD}} 
+{
+\hspace{-0.54em}
+\caption{ \fontsize{10pt}{12pt}\selectfont{
+% \textbf{HCN/CO-\LIR relation} % 
+%An increase in line ratios between high-density and low-density molecular gas tracers (e.g. HCN/CO) 
+%with increasing infrared luminosity suggests that the main driver of the enhanced SFR
+%is the molecular gas density distribution, in agreement with the observations that ULIRGs
+%host large reservoirs of dense molecular gas in their
+%central regions. 
+\textbf{Schmidt-Kennicutt relation for dense gas}
+While constraints on the power-law index from gas of different densities are important for 
+star-formation models, current studies only have constraints
+up to the gas of density traced by the ground state HCN line (\ncrit$\sim$10$^{4}$),
+which are also largely limited to local measurements \citep{GB12a}. 
+Our proposed observations will, for the first time, spatially resolve the 
+SK relation at kpc scale 
+in a ULIRG at $z$$\sim$0.7, using
+high critical density tracers (\dhcn and \dhcop). This will allow us to 
+explore potential deviations at higher redshift and provide
 key constraints for models of galaxy evolution.
+% This will also demonstrate the utility of mid-$J$ lines in tracing 
+% the star-forming dense gas, which will be routinely mapped in high-z galaxies with ALMA.
+}
 \label{fig:SF}}
-\vspace{-0.85em}
+}
+\vspace{-0.905em}
 \end{figure*}
@@
 \noindent {\bf Technical overview}
-% We propose to observe the \eco line at 0.15" resolution
-% and the \dhcn and \dhcop lines at 0.7", 
-We estimate the line widths and fluxes 
-% assuming a line width
-% of 700\kms 
-based on our \bco data, and a source size from our lens model.
-%, which takes into account the asymmetric line emission and spatial extent due to differential lensing. 
-We thus expect the source to be resolved over 153 beams 
-and 7 beams at 0.15" and 0.7", respectively (see TJ for details). 
-% We compute the target sensitivities for both science goals based on the \bco line flux. 
-We adopt conservative 
-line ratios measured for high-z galaxies for \eco line \citep[][]{CW13}
-and those based on (U)LIRGs for \dhcn (GS04; P07).
-For \dhcop, we adopt the line ratio \dhcn/\dhcop found in ULIRGs 
-\citep{Greve09a}. 
-We use the most stringent sensitivity estimates 
-among \dhcn and \dhcop as our sensitivity goal for science goal $1$. %The latter sets the overall requirement. 
+We estimate the source size from our lens model 
+and adopt conservative line ratios measured for ULIRGs and high-z galaxies 
+(\citealt[][]{Greve09a,CW13}; GS04; P07) to compute the estimate line fluxes.
 To secure enough S/N for lens modeling, 
@@
 per 150 \kms channel 
-%to reconstruct the dynamical structure in the source plane 
-for the science goals, respectively. 
-% We therefore request a \textbf{total time of 7.0 hours}.% to complete our science goals.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% closing
-%\par 
-%Our proposed observations present an exceptional opportunity to investigate
-%the physical properties and dynamical structures of 
-%%different gas phases in 
-%the ISM in mergers at the cosmic epoch 
-%where the SFR density is steeply rising \citep{LeFloch05a}, 
-%connecting high redshift and nearby studies to improve our understanding of galaxy evolution.
-%%Our proposed observations are vital
-%%% between the \LIR, SFR$_{\rm IR}$, SFR$_{\rm UV}$, surface densities of SFR, CO, HCN and \hcop,
-%%to provide constraints on the relation between the ISM and AGN/SB acitvities
-%%on sub-kpc scales and on the mechanisms driving the vast SFR at earlier epochs, 
-%%giving rise to the observed stellar-assembly history.
-%%
-%This will also % lay the groundwork to 
-%% serve as a benchmark demonstrating
-%demonstrate the future prospects for ALMA in 
-%utilizing high-dipole moment molecules as routine tracers to study star-formation 
-%at high redshift.
+for the science goals, respectively (see TJ for details).
 
@@
 \centering
-\vspace{-0.5em}
+\vspace{-0.859em}
 \hspace{-2.1em}
-% \floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.495\textwidth}}]{figure}[\FBwidth]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.475\textwidth}}]{figure}[\FBwidth]
 {
-\includegraphics[trim=7 6 5 5, clip, width=0.85\textwidth]{Fig/combine}}
+\includegraphics[trim=7 6 5 5, clip, width=0.535\textwidth]{Fig/combine}}
 {
-\hspace{-0.85em}
+\hspace{-0.95em}
 \caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{\bco}}
 {\em (a):}
-A double-horned, asymmetric line profile arising due to differential lensing.
+A double-horned line profile from the AGN host galaxy, which appears
+ asymmetric due to differential lensing.
 {\em (b):}
+Spectra taken at three locations along the strongest velocity gradient, demonstrating
+differential lensing of the kinematic components of the gas-rich ``disk".
+{\em (c):}
 Observed spatial variations across the channels, as shown by the red (red-shifted), 
 green (line center), and blue (blue-shifted) contours.
-% corresponding to the line emission of different velocity channels (red wing, line center, blue wing). 
-{\em (c):}
-The observed velocity gradient is suggestive of a kinematically ordered disk at 
+{\em (d, e):}
+The observed velocity gradient and velocity dispersion are suggestive of a kinematically ordered disk at 
 the current resolution limit. 
-Spatial variations across different kinematic components are also see within the beam, indicating 
-the spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial 
+The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial 
 scales than otherwise possible.
-% Spatial variations of the different velocities are seen within the beam (see (e)).
-{\em (d):} 
-An usually high velocity dispersion is observed but the 
-true dynamics is unclear due to beam smearing effects.
-% However, limited by the spatial resolution, beam smearing strongly decreases
-% large-scale velocity gradients and increases observed dispersion.
-% RGB spectra
-{\em (e):}
-Spectra taken at three locations along the strongest velocity gradient, demonstrating
-differential lensing of the kinematic components of the gas-rich ``disk".
-% Lens model
 {\em (f):}
 Channel maps of the CO emission (red) 
-%toward the gas-rich merger 
 overlaid on our best-fit lens models (grayscale). 
 The foreground lensing galaxy is represented by a black dot.
-% and the beam size is shown in the bottom right corner.
-% Clearly, there are spatial variations across different kinematic components.
 The reconstructed source morphology (magenta ellipses) is also suggestive of a ``disk".
-% kinematically ordered galaxy. 
 Given the presence of a companion galaxy within 2.4 kpc and beam smearing effects, high-resolution 
-imaging is necessary to unambiguously determine the nature that gives rise to the observed velocity gradient
-and dispersion, as proposed here.
-% This will confirm if the system is rotationally supported or highly turbulent 
-% (or tidally disrupted) and 
+imaging is necessary to unambiguously determine the structure that gives rise to the 
+observed velocity gradient and dispersion, as proposed here.
 This will allow us to investigate the 
-% major 
 mechanisms responsible for the starburst in the AGN host galaxy
-% and investigate whether dominant mode of star formation is 
-(e.g. GMC-like in a rotating disk or due to fragmentation of
-dynamically unstable gas-rich disk) and its ISM conditions as it interacts with the companion. 
+% (e.g. GMC-like in a rotating disk or fragmentation of a
+% dynamically unstable gas-rich disk) 
+and its ISM conditions as it interacts with the companion. 
 We therefore aim to spatially resolve the gas dynamics, kinematics and ISM conditions in a merger,
@@
 on the star-formation processes
-%star-formation history, 
-at the epoch where the SFR density is steeply 
+at an epoch where the SFR density is steeply 
 rising across cosmic times.
@@
 }
-\vspace{-0.855em}
+\vspace{-0.905em}
 \end{figure*}

### 2016-04-20 ALMA/Cycle4/RXJ.tex
minor rewording

@@
 to gain more detailed insight into the early universe and in studies of galaxy evolution over cosmic time.
-Since mergers are believed to play an important role in giving rise to these dusty galaxies
-(e.g. Sanders \& Mirabel 1996). Yet, merger-induced effects on the physical mechanisms and chemistry 
+While mergers are believed to play an important role in giving rise to these dusty galaxies
+(e.g. Sanders \& Mirabel 1996), merger-induced effects on the physical mechanisms and chemistry 
 that drive the 
@@
 cm$^{-3}$) gas content and their spatial distributions as a function of distance from the AGN/nucleus. This will enable
-us to gain insight into the interplay between AGN, SB and the dense gas content in the ISM (and thus the SF mode on small scales across different galaxy populations as traced by the HCN/CO-\LIR relation).
+us to gain insight into the interplay between AGN, SB and the dense gas content in the ISM (and thus the SF mode on small scale across different galaxy populations as traced by the HCN/CO-\LIR relation).
 % \Fig{SF}).
@@
 The Schmidt-Kennicutt (SK) relation (%``Star-formation law"; 
-$\Sigma_{\rm SFR}$$\propto$$\Sigma^N_{\rm gas}$)
+$\Sigma_{\rm SFR}$$\propto$$\Sigma^N_{\rm gas}$; \Fig{SF})
 is one of the key ingredients
@@
 in a high-z merger, down to the size scale of star-forming gas clumps. 
-Hence, providing crucial constraints on star-formation at high redshift.
+This will enable us to provide crucial constraints on star-formation at high redshift.
 
@@
 and distant galaxies with exquisite details. Such investigations are vital to bridge the gap in our 
-current understanding on galaxy populations across cosmic time.
+current understanding on different galaxy populations across cosmic time.
 This will also demonstrate the capabilities of ALMA in % mapping 
-utilizing these much fainter emission 
+utilizing these much fainter
 high-dipole moment molecules as routine tracers to 
@@
 SK relation at kpc scale 
-in a ULIRG at $z$$\sim$0.7, using
+in a ULIRG at $z$$\sim$0.7 by using
 high critical density tracers (\dhcn and \dhcop). This will allow us to 
@@
 and adopt conservative line ratios measured for ULIRGs and high-z galaxies 
-(\citealt[][]{Greve09a,CW13}; GS04; P07) to compute the estimate line fluxes.
+(GS04; P07; \citealt[][]{Greve09a,CW13}) to compute the estimate line fluxes.
 To secure enough S/N for lens modeling, 

### 2016-04-20 ALMA/Cycle4/RXJ.tex
with more DR's comments

@@
 { 
-Molecular gas dynamics and AGN/starburst mechanism in a
-strongly-lensed wet merger: bridging the gap between local ULIRGs and high-z systems}
+Dense gas properties in a strongly-lensed wet merger: bridging the gap between local ULIRGs and high-z systems}
 }}
@@
 the build-up of stellar mass 
-is steeply rising is critical and we here aim to bridge this gap by testifying
+is steeply rising ($z$$\sim$0.3-1) is critical and we here aim to bridge this gap by testifying
 correlations and properties found locally out to high redshift by observing the 
@@
 % and their high-z analogues, 
-their extreme SFRs are a natural consequence of either gas is being converted into stars
-more efficiently and/or their molecular gas content. Fragmentation
-of giant star-forming clumps and turbulent conditions are also expected 
+their extreme star formation rates are a natural consequence of either gas is being converted into stars
+more efficiently and/or their increased molecular gas content. Fragmentation
+of giant star-forming clumps and turbulent conditions are thus expected 
 from gravitational instability of these gas-rich bodies. 
@@
  $\sim$few kpc \citep{Swinbank12a, Swinbank12b}. 
-Resolving the gas dynamics on hundred pc scales is therefore an important first step
+Resolving the gas dynamics on sub-kpc scales is therefore an important first step
 to understanding the mechanisms and physical processes taking
-place on different scales and how the ISM physical conditions 
+place on different scales and how the ISM conditions 
 are related to the SB in ULIRGs at this epoch. %(when the SFR density is steeply rising).
@@
 % dense gas mass tracers since the mid-$J$ transitions
-since they trace the much denser gas (n$\gtrsim$10$^5-$10$^7$ cm$^{-3}$) that is 
+since they trace the much denser gas (n$\gtrsim$10$^5$-10$^7$ cm$^{-3}$) that is 
 thought to be the immediate fuel for SF in turbulent GMCs \citep{Shirley03a, KM05}. 
-This has been supported by the linear correlations found in 
+This is supported by the linear correlations found in 
 \LIR-\Lp[\dhcn] and \LIR-\Lp[\dhcop] \citep[]{Zhang14a}.
@@
 % ratios \ahcn/HCO$^+$($J$=1\rarr0) \citep{Kohno05a, Imanishi10, Izumi13a} and
-ratio \dhcn/\dhcop \citep{Imanishi14a, GB14a, Viti14a} have been 
+ratio \dhcn/\dhcop have been 
 proposed as
 %  diagnostic tools 
-a diagnostic tool to reveal deeply buried AGNs at the cores of ULIRGs \citep{Izumi16a, Imanishi16a}.
+a diagnostic tool to reveal deeply buried AGNs at the cores of ULIRGs \citep{Imanishi14a, GB14a, Viti14a, Izumi16a, Imanishi16a}.
 % separate emission originating from AGN and SB
@@
 {\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
-morphology}
-{\em Left:} The rest-frame UV emission (tracing recent star formation) 
+morphology.}
+{\em Left:} The rest-frame UV emission (tracing recent star-formation) 
 is lensed into an almost complete Einstein ring with diameter $\sim$3.8". 
@@
 an optically faint companion (white; \citealt{Claeskens06a}), 
-which we have recently confirmed by modeling \bco emission detected with NOEMA
+which we have recently confirmed by lens-modeling \bco emission detected with NOEMA
 (\Fig{combine}; Leung \& Riechers, in prep.). 
@@
 HST observations (rest-frame UV) have revealed distinct emission 
-from recent star formation (lensing arcs) and from the AGN (bright knots) in the background galaxy \citep{Sluse03a},
+from recent star-formation (lensing arcs) and from the AGN (bright knots) in the background galaxy \citep{Sluse03a},
 demonstrating the great potential for probing its
@@
 and made it possible to identify
-seven distinct structures in the source plane (\Fig{HST}). Remarkably, emission 
-%originating 
-from 
+seven distinct structures in the source plane (\Fig{HST}). Remarkably, emission from 
 a spatially offset region ($\sim$2.4 kpc away from the AGN host galaxy) has been identified and found 
-to be $\sim$700 pc in size \citep{Brewer08a}, indicating a 
-%nearby 
-companion galaxy. 
+to be $\sim$700 pc in size \citep{Brewer08a}, indicating a companion galaxy. 
 We have recently confirmed that both galaxies are at the same redshift by detecting their 
@@
 in velocity space (\Fig{combine}f), and verified
-that the both are gas-rich (Leung \& Riechers, in prep.). 
+that both are gas-rich (Leung \& Riechers, in prep.). 
 Our SED modeling of the dust continuum emission up to 250\,$\mu$m finds $L_{\rm IR}\sim6\times$10$^{12}$\Lsun 
@@
 Our recently obtained \bco data shows an asymmetric double-horned line profile (\Fig{combine}a). Given
-the 1$^{\rm st}$ moment map observed and the velocity gradient
+the 1$^{\rm st}$ moment map and the observed velocity gradient
 across the source plane in our model (\Fig{combine}d \& \ref{fig:combine}f), this is indicative of
@@
 to distinguish 
-between a merger-driven and a turbulent clumpy disk starburst,
+between a merger-driven and a turbulent clumpy disk starburst/
 
-The requested resolution (0.15") for \eco is critical
+The requested resolution for \eco is critical
 as it allows us to obtain a detailed
-dynamical lens model of the system, probing at sub-kpc scale % probe down to 0.15" <-> 500 pc
-(typical size scale of high-z GMCs), which enables us 
+dynamical lens model of the system, probing at sub-kpc scale resolution % probe down to 0.15" <-> 500 pc
+(about the typical size of high-z GMCs), which will enable us 
 to compare the spatial distributions of star-forming gas clumps 
@@
 We will also measure the linewidths of the very dense gas (traced by HCN and \hcop), 
-the excited gas (traced by \eco), and the more-extended, less-perturbed 
+the highly excited warm gas (traced by CO\,$J$=5\rarr4), and the more-extended, less-perturbed 
 molecular gas (traced by low-$J$ CO) at various regions within the AGN host galaxy 
 to constrain the kinematics and relative mass-fractions of different gas phases, 
-which are indications of the evolutionary stage of a galaxy.
+which are indications of the evolutionary stage of this galaxy.
 
@@
 resolve the line emission originating near the AGN and that from the spatially extended 
-SB regions ($>$kpc scale) in the host galaxy, and by measuring spatial variations in 
+SB regions ($>$kpc scales) in the host galaxy, and by measuring spatial variations in 
 this line ratio, we will assess its utility 
 as an AGN/SB diagnostic (\Fig{AGNSB}) at high redshift.
-Since the HCN vibrational line (v$_2$=1) falls within the targeted frequency range, 
+Since the HCN vibrational line (v$_2$=1;$J$=4\rarr3) falls within the targeted frequency range, 
 we will use it to independently constrain the radiation properties of the AGN environment, 
@@
 a detailed lens modeling of each emission line, enabling measurements of reliable line 
-ratios, without significant uncertainties due to differential lensing.
+ratios without significant uncertainties due to differential lensing.
 Such measurements are vital to reveal how galaxy interactions drive gas into 
-inner disks to initiate SB/AGN activities and how the ISM differ from 
+inner disks to initiate SB/AGN activities and how the ISM differs from 
 normal star-forming galaxies.
@@
 \centering
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.565\textwidth}}]{figure}[\FBwidth]
-{\includegraphics[trim=15 0 5 10, clip, width=0.385\textwidth]{Fig/izumi15}}
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.625\textwidth}}]{figure}[\FBwidth]
+{\includegraphics[trim=15 0 5 10, clip, width=0.35\textwidth]{Fig/izumi15}}
 {
@@
 \vspace{-1.15em}
-\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{\dhcn/\dhcop as AGN/SB diagnostic}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{\dhcn/\dhcop as AGN/SB diagnostic.}
 Difference in line ratios between local AGNs, SBs, and (U)LIRGs with buried AGNs suggest
 that \dhcn/\dhcop can be used as a diagnostic tool to reveal the dominant power source within the
-beam, where an elevated line ratio is seen in AGN and circumnuclear regions relative to SB regions/galaxies.
-Such diagnostic depends heavily on the spatial resolution, as demonstrated by the
+beam, where an elevated line ratio is seen in AGN and circumnuclear regions relative to starbursts.
+Such diagnostics depend heavily on the spatial resolution, as demonstrated by the
 measurements taken with APEX (empty circle) and ALMA (filled circles) in NGC1068.
 We here propose to spatially resolve this line ratio within the AGN host galaxy and obtain
-measurements near the AGN and the extended SB regions to investigate spatial variations 
-in order to assess its utility as a AGN/SB diagnostic at high redshift.
+measurements toward the AGN and the extended SB regions in order to investigate spatial variations 
+and assess its utility as an AGN/SB diagnostic at high redshift.
 (Figure taken from \citealt{Izumi16a})}
@@
 % XDR versus PDRs
-Since \eco is excited in higher temperature than the HCN and \hcop lines (e.g. in 
+Since \eco is excited at higher temperature than the HCN and \hcop lines (e.g. in 
 X-ray dominated regions (XDRs) near an AGN), 
@@
 % physical properties
-In addition, we will measure spatially resolved line ratios of HCN/CO and \hcop/CO within the AGN host galaxy
+In addition, we will use spatially resolved line ratios of HCN/CO and \hcop/CO within the AGN host galaxy
 as proxies of its very dense (cores; $\sim$10$^5$-10$^7$ cm$^{-3}$) versus the less dense (clumps; $\sim$10$^4$
-cm$^{-3}$) gas content and their spatial distributions as a function of distance from the AGN/nucleus. This will enable
-us to gain insight into the interplay between AGN, SB and the dense gas content in the ISM (and thus the SF mode on small scale across different galaxy populations as traced by the HCN/CO-\LIR relation).
+cm$^{-3}$) gas content and their spatial distributions as a function of distance from the AGN. This will enable
+us to gain insight into the SF mode on small scales across different galaxy populations, 
+as traced by the HCN/CO-\LIR relation, and investigate
+the interplay between AGN, SB and the dense gas content in the ISM.
 % \Fig{SF}).
 % CO SLED
-We will also combine \eco with our existing \bco and CO($J$=3\rarr2) data to constrain the gas density (n$_{H_{2}}$) 
-and kinetic temperature by performing large velocity gradient modeling.
+We will also combine \eco with our existing \bco and CO($J$=3\rarr2) data to constrain the gas density ($n_{\rm H_{2}}$) 
+and kinetic temperature by performing large velocity gradient (LVG) modeling.
 
@@
 (e.g. \citealt{Narayanan14a}).
-However, the surface density of gas at high densities (\ncrit$\gtrsim$10$^5$cm$^{-3}$; 
+However, the surface density of gas at high densities ($n$$\gtrsim$10$^5$cm$^{-3}$; 
 $\Sigma_{\rm dense}$)
@@
 At the proposed resolution, we will spatially resolve, for the first time,
-the {\it true SK relation} by measuring the dense gas surface density (\ncrit$\gtrsim$10$^5$cm$^{-3}$)
+the {\it true SK relation} by measuring the {\em dense} gas surface density 
 in a high-z merger, down to the size scale of star-forming gas clumps. 
-This will enable us to provide crucial constraints on star-formation at high redshift.
+This will enable us to provide crucial constraints on the conditions for star-formation models at high redshift.
 
@@
 the physical properties and dynamical structures of different gas phases in the ISM of mergers 
-and distant galaxies with exquisite details. Such investigations are vital to bridge the gap in our 
-current understanding on different galaxy populations across cosmic time.
-This will also demonstrate the capabilities of ALMA in % mapping 
-utilizing these much fainter
+and distant galaxies with exquisite details. 
+This will also demonstrate the capabilities of ALMA to % mapping 
+utilize these much fainter
 high-dipole moment molecules as routine tracers to 
-study star-formation at earlier epochs.
+study star-formation at earlier cosmic epochs.
 
 \begin{figure*}[!tbph]
-\vspace{-1.85em}
+\vspace{-0.55em}
 \centering
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.5575\textwidth}}]{figure}[\FBwidth]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.625\textwidth}}]{figure}[\FBwidth]
 {
 % HCN/CO - LIR plot: e.g. Fig 6 in \citep{Juneau09a}
-\includegraphics[trim=15 0 5 10, clip, width=0.257\textwidth]{Fig/SFRSD}} 
+\includegraphics[trim=15 0 5 10, clip, width=0.25\textwidth]{Fig/SFRSD}} 
 {
@@
 %central regions. 
-\textbf{Schmidt-Kennicutt relation for dense gas}
+\textbf{Schmidt-Kennicutt relation for dense gas.}
 While constraints on the power-law index from gas of different densities are important for 
@@
 which are also largely limited to local measurements \citep{GB12a}. 
-Our proposed observations will, for the first time, spatially resolve the 
-SK relation at kpc scale 
+Our proposed observations will, for the first time, constrain the spatially resolved
+SK relation at kpc scales 
 in a ULIRG at $z$$\sim$0.7 by using
-high critical density tracers (\dhcn and \dhcop). This will allow us to 
+high critical density tracers (HCN\,$J$=4\rarr3 and \hcop\,$J$=4\rarr3). This will allow us to 
 explore potential deviations at higher redshift and provide
@@
 \centering
-\vspace{-0.859em}
-\hspace{-2.1em}
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.475\textwidth}}]{figure}[\FBwidth]
+\vspace{-0.559em}
+\hspace{-2.75em}
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.445\textwidth}}]{figure}[\FBwidth]
 {
-\includegraphics[trim=7 6 5 5, clip, width=0.535\textwidth]{Fig/combine}}
+\includegraphics[trim=7 6 5 5, clip, width=0.575\textwidth]{Fig/combine}}
 {
-\hspace{-0.95em}
-\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{\bco}}
+\hspace{-1.0em}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{ New \bco} data.}
 {\em (a):}

### 2016-04-20 ALMA/Cycle4/RXJ.tex
with Phil's comments

@@
 the build-up of stellar mass 
-is steeply rising ($z$$\sim$0.3-1) is critical and we here aim to bridge this gap by testifying
+is steeply rising ($z$$\sim$0.3-1) is critical and we here aim to bridge this gap by testing
 correlations and properties found locally out to high redshift by observing the 
 dynamical structure and properties of the ISM of
-the quadruply lensed galaxy RXJ1131-1231 and its dust-obscured 
+the quadruply lensed galaxy RXJ1131-1231 (henceforth RX1131) and its dust-obscured 
 companion at $z_{\rm CO}$$\sim$0.65 (\Fig{HST}).
@@
 % ratios \ahcn/HCO$^+$($J$=1\rarr0) \citep{Kohno05a, Imanishi10, Izumi13a} and
-ratio \dhcn/\dhcop have been 
+ratio \dhcn/\dhcop has been 
 proposed as
@@
 
-Prior to ALMA, studies of dense gas were largely limited to the local universe ($z$$\lesssim$0.1) 
-with only five detections
+Prior to ALMA, studies using dense gas tracers were largely limited 
+to the local universe ($z$$\lesssim$0.1) with only five detections
 %IR-luminous lensed galaxies detected 
@@
 These quantities are key to investigate how the ISM % conditions 
-vary as galaxies evolve across cosmic time.
+varies as galaxies evolve across cosmic time.
 In conjunction with the large set of ancillary data from
@@
 the 1$^{\rm st}$ moment map and the observed velocity gradient
-across the source plane in our model (\Fig{combine}d \& \ref{fig:combine}f), this is indicative of
+across the source plane in our model (\Fig{combine}d, f), this is indicative of
 a kinematically ordered %(reminiscent of a rotating disk) 
@@
 Furthermore, the unusually high velocity dispersion 
-$\gtrsim$400\kms at the central region (\Fig{combine}e) hints at 
+$\gtrsim$400\kms in the central region (\Fig{combine}e) hints at 
 perturbations from the AGN and/or
@@
 to distinguish 
-between a merger-driven and a turbulent clumpy disk starburst/
+between a merger-driven and a turbulent clumpy disk starburst.
 
@@
 % emission originating from the AGN host galaxy (and within) and from its companion.
-Recent studies find that the \dhcn/\dhcop line ratio is expected to be enhanced 
+Recent studies find that the \dhcn/\dhcop line ratio is enhanced 
 in the circumnuclear disk (CND) near an AGN and falls off with distance from the CND
@@
 
-\noindent Our proposed observations therefore provide an exceptional opportunity to investigate
-the physical properties and dynamical structures of different gas phases in the ISM of mergers 
-and distant galaxies with exquisite details. 
+\medskip
+\noindent In summary, our proposed observations therefore provide an exceptional opportunity to investigate
+the physical properties and dynamical structures of different gas phases in the ISM of a distant merger
+% and distant galaxies 
+at exquisite detail. 
 This will also demonstrate the capabilities of ALMA to % mapping 
@@
 {
-\includegraphics[trim=7 6 5 5, clip, width=0.575\textwidth]{Fig/combine}}
+\includegraphics[trim=37 35 247 5, clip, width=0.575\textwidth]{Fig/combine.pdf}}
 {
 \hspace{-1.0em}
-\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{ New \bco} data.}
+\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{Recent \bco data from NOEMA.}}
 {\em (a):}

### 2016-04-21 ALMA/Cycle4/RXJ.tex
with Chelsea's comments

@@
 (e.g. Sanders \& Mirabel 1996), merger-induced effects on the physical mechanisms and chemistry 
-that drive the 
-%intense 
-starburst (SB) and active galactic nucleus (AGN) activities on small scales are still unclear.
-Thus characterizing the properties of the molecular gas that fuels star-formation (SF) and AGN is
-crucial to understand the interplay between AGN and SB
-and their relation to the ISM properties of galaxies across cosmic time.
+that drive the starburst (SB) and active galactic nucleus (AGN) activities on small scales are still unclear.
 
@@
 studying high-z galaxies 
-\citep[e.g.][]{Rangwala15a}, a wide knowledge gap persists
+\citep[e.g.,][]{Rangwala15a}, a wide knowledge gap persists
 between $z$=0 and the epoch when most stars are formed in the universe ($z$$\sim$2). 
-Hence, understanding galaxy populations at an epoch when
-the build-up of stellar mass 
-is steeply rising ($z$$\sim$0.3-1) is critical and we here aim to bridge this gap by testing
-correlations and properties found locally out to high redshift by observing the 
+Here we aim to bridge this gap by testing
+local correlations and properties at moderate redshifts 
+% Understanding galaxy populations at an epoch when
+% the build-up of stellar mass 
+% is steeply rising ($z$$\sim$0.3-1) is critical.
+by observing the 
 dynamical structure and properties of the ISM of
@@
 \noindent {\bf Molecular gas in AGN/SB} 
-Owing to the high molecular gas fractions in ULIRGs,
-% and their high-z analogues, 
-their extreme star formation rates are a natural consequence of either gas is being converted into stars
-more efficiently and/or their increased molecular gas content. Fragmentation
-of giant star-forming clumps and turbulent conditions are thus expected 
-from gravitational instability of these gas-rich bodies. 
-In fact, studies of the ISM kinematics at $z$=1-2 find clumps of size scale
- $\sim$few kpc \citep{Swinbank12a, Swinbank12b}. 
-Resolving the gas dynamics on sub-kpc scales is therefore an important first step
-to understanding the mechanisms and physical processes taking
-place on different scales and how the ISM conditions 
-are related to the SB in ULIRGs at this epoch. %(when the SFR density is steeply rising).
+Extreme star formation rates (SFRs) in ULIRGs and their high-z analogues are a natural consequence of either gas 
+being converted into stars more efficiently and/or their high molecular gas fractions, whch
+would lead to fragmentation of giant star-forming clumps and turbulent conditions 
+due to gravitational instability. Indeed, observations at $z$=1--2 have found gas clumps of
+size $\sim$few kpc \citep{Swinbank12a, Swinbank12b}, which are much bigger than 
+those in normal star-forming galaxies. Therefore, resolving the gas dynamics 
+on sub-kpc scales is important to understand the 
+mechanism and physical processes responsible for 
+the different star-formation modes in normal galaxies and ULIRGs. % at earlier epochs.
+% star-formation and how the ISM conditions 
+% are related to the SB in ULIRGs at this epoch.
 
@@
 denser, actively star-forming gas. Indeed, a tight correlation between \ahcn and \LIR 
-(proxy for SFR) has been found in nearby galaxies and local giant molecular 
-clouds (GMC; \citealt[hereafter GS04]{Gao04a}; \citealt{Wu05}), 
+(a proxy for SFR) has been found in nearby galaxies and local giant molecular 
+clouds (GMCs; \citealt[hereafter GS04]{Gao04a}; \citealt{Wu05}), 
 suggesting HCN is a faithful tracer of the star-forming dense gas.
-% and that the origin can be attributed to the fundamental units of star formation. 
-However, \dhcn observations of (U)LIRGs have revealed a wide range of
-excitation conditions 
-%for their dense gas phase 
-that may render the ground state transition of 
-HCN and \hcop poor proxies of the dense gas mass \citep[hereafter P07]{Papadopoulos07a}.
-In this light, higher-$J$ transitions (e.g. $J$=4\rarr3) 
-% are necessary to scrutinize the reliability of using the ground state 
-have been suggested to be better probes
-% dense gas mass tracers since the mid-$J$ transitions
-since they trace the much denser gas (n$\gtrsim$10$^5$-10$^7$ cm$^{-3}$) that is 
+However, higher-$J$ transitions (e.g. $J$=4\rarr3) 
+have also been suggested to be better proxies
+of the star-forming gas since they
+trace the much denser gas (n$\gtrsim$10$^5$-10$^7$ cm$^{-3}$) that is 
 thought to be the immediate fuel for SF in turbulent GMCs \citep{Shirley03a, KM05}.
@@
 ground state lines are redshifted to frequencies beyond the spectral coverage of ALMA
-at $z$$>$0.06, it is also necessary to establish diagnostics using these mid-$J$ lines to 
+at $z$$>$0.06, it is important to establish diagnostics using these mid-$J$ lines to 
 study distant galaxies.
-Additionally, due to the difference in abundances and excitation conditions of HCN and \hcop
+Due to the difference in abundances and excitation conditions of HCN and \hcop
 in star-forming versus AGN regions, the line 
@@
 %  diagnostic tools 
-a diagnostic tool to reveal deeply buried AGNs at the cores of ULIRGs \citep{Imanishi14a, GB14a, Viti14a, Izumi16a, Imanishi16a}.
+a diagnostic tool to reveal deeply buried AGNs at the cores of ULIRGs \citep{Imanishi14a, GB14a, Viti14a, 
+Izumi16a, Imanishi16a}.
 % separate emission originating from AGN and SB
@@
 at $z$$\gtrsim$0.3
-(e.g. \citealt{Riechers07a, Riechers10a, Wagg05a, Gao07a}).
+(e.g., \citealt{Riechers07a, Riechers10a, Wagg05a, Gao07a}).
 Moreover, none of these 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-% \section*{Science Target RXJ 1131-1231: a demonstrative case at high-z}
-% \vspace{-0.25em}
 \noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at high-z}
-\vspace{-0.6em}
-%\begin{figure}[!tbhp]
-%\centering
-%\includegraphics[trim= 10 20 15 0, clip, scale=0.3]{Fig/F555W} % &
-%\hspace{-0.5em}
-%\includegraphics[trim= 10 0 0 0, clip, scale=0.37]{Fig/Manipulate_figsCROP}
-%\vspace{-1em}
-%\caption{ \fontsize{10pt}{12pt}\selectfont 
-%{
-%\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
-%morphology}
-%{\em Left:} The rest-frame UV emission (tracing recent star formation) 
-%is lensed into an almost complete Einstein ring with diameter $\sim$ 3.8". 
-%{\em Right:} Lens modeling of the optical emission identifies complex structure in the host galaxy and
-%an optically faint companion (white; \citealt{Claeskens06a}), 
-%which we have recently confirmed by modeling \bco emission detected with NOEMA
-%(\Fig{combine}; Leung \& Riechers, in prep.). 
-%We here propose to study
-%the ISM conditions in this AGN-starburst composite system and offers an unparalleled
-%view into the early universe, with finer
-%detail than otherwise possible with current facilities. 
-%}
-%\label{fig:HST}}
-%\end{figure}
+% \vspace{-0.6em}
 
 \begin{figure}[!tbhp]
+\hspace{-1em}
 \centering
-\hspace{-0.85em}
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.445\textwidth}}]{figure}[\FBwidth]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.395\textwidth}}]{figure}
+[\FBwidth]
+{\hspace{-0.5em}
+\includegraphics[trim= 10 20 15 0, clip, scale=0.278]{Fig/F555W}
+\hspace{-1.325em}
+\includegraphics[trim= 10 0 0 5, clip, scale=0.345]{Fig/Manipulate_figsCROP}
+\vspace{-1.0em}
+}
 {
-\vspace*{-0.55em}
-\hspace{-0.435em}
-\raggedleft
-\caption{ \fontsize{10pt}{12pt}\selectfont 
-{\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 and its reconstructed source plane
+\hspace{-0.45em}
+\caption{\fontsize{10pt}{12pt}\selectfont{\textbf{Stellar light distribution in the AGN host galaxy of RXJ 1131-1231 
+and its reconstructed source plane
 morphology.}
@@
 {\em Right:} Lens modeling of the optical emission identifies complex structures in the host galaxy and
-an optically faint companion (white; \citealt{Claeskens06a}), 
+an optically faint companion (white component as indicated by the blue arrows; \citealt{Claeskens06a}), 
 which we have recently confirmed by lens-modeling \bco emission detected with NOEMA
 (\Fig{combine}; Leung \& Riechers, in prep.). 
-We here propose to study
+Here we propose to study
 the ISM conditions in this AGN-starburst merger with finer
@@
 \label{fig:HST}}}
-{\hspace{-1em}
-\includegraphics[trim= 10 20 15 0, clip, scale=0.28]{Fig/F555W}
-\hspace{-1.5em}
-\includegraphics[trim= 10 0 0 0, clip, scale=0.3]{Fig/Manipulate_figsCROP}
-\vspace{-1.0em}
-\hspace{-0.5em}
-}
+\vspace{-0.8em}
 \end{figure}
-\vspace{-0.8em}
-RXJ 1131-1231 is a quadruply imaged AGN with its host galaxy lensed 
+RX1131 is a quadruply imaged AGN with its host galaxy lensed 
 into a partial Einstein ring (\Fig{HST}). 
@@
 and made it possible to identify
-seven distinct structures in the source plane (\Fig{HST}). Remarkably, emission from 
-a spatially offset region ($\sim$2.4 kpc away from the AGN host galaxy) has been identified and found 
-to be $\sim$700 pc in size \citep{Brewer08a}, indicating a companion galaxy. 
-We have recently confirmed that both galaxies are at the same redshift by detecting their 
+seven distinct structures in the source plane (\Fig{HST}). 
+A companion galaxy of size $\sim$700 pc across was also identified at $\sim$2.4 kpc away
+from the AGN host galaxy
+in the HST observations \citep{Brewer08a}.
+We recently confirmed that both galaxies are at the same redshift by detecting their 
 \rot[CO]{2}{1} emission and lens-modeling their gas distribution 
-in velocity space (\Fig{combine}f), and verified
+in velocity space (\Fig{combine}f), verifying
 that both are gas-rich (Leung \& Riechers, in prep.). 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Proposed Observations and Immediate Objectives}
-% \vspace{-0.25em}
 \noindent {\bf Proposed Observations and Science Goals}
-We here propose to map (1): \eco at 0.15" resolution ($\sim$500pc at $z$$\sim$0.7 in the source plane) and 
+Here we propose to map (1): \eco at 0.15" resolution ($\sim$500pc at $z$$\sim$0.7 in the source plane) and 
 (2): \dhcn and \dhcop emission and the underlying continuum at 0.7" resolution (2.5 kpc in the source plane).
-The continuum traces the dust emission, 
-providing better constraints on the the gas-to-dust ratio, dust temperature(s), dust mass,
-and its spatial extent (and thus the surface density of the SFR).
-%($\Sigma_{\rm SFR}$).
-These quantities are key to investigate how the ISM % conditions 
+The continuum will provide additional constraint on the Rayleigh-Jeans tail of the 
+dust emission, which is currently constrained by four photometric data. 
+This will reduce the uncertainties on the the gas-to-dust ratio, dust temperature(s), dust mass,
+and its spatial extent (and thus the surface density of the SFR) .
+These quantities are important for investigating how the ISM
 varies as galaxies evolve across cosmic time.
-In conjunction with the large set of ancillary data from
-rest-frame UV to radio wavelength and our recent observations of \bco and \rot[CO]{3}{2}, our
-proposed observations are designed to investigate 
-% carry a detailed investigation of 
-the gas-rich merger in aspects listed as follows.
+In conjunction with the large set of ancillary data 
+(from rest-frame UV to radio wavelengths, including our recent observations of \bco and CO\,$J$=3\rarr2), our
+proposed observations are designed to investigate:
 
-\underline{\bf Dynamics and kinematics:}
+\underline{\bf(1) Dynamics and kinematics}
 Our recently obtained \bco data shows an asymmetric double-horned line profile (\Fig{combine}a). Given
@@
 Furthermore, the unusually high velocity dispersion 
-$\gtrsim$400\kms in the central region (\Fig{combine}e) hints at 
-perturbations from the AGN and/or
-internal turbulence
-% motion 
-due to interactions with the companion
+($\gtrsim$400\kms) in the central region (\Fig{combine}e) hints at 
+perturbations from the AGN, 
+internal turbulence due to interactions with the companion,
 and/or instability due to the huge gas reservoir.
-Thus higher-resolution \eco imaging, as proposed here, is needed
+Therefore, higher-resolution \eco imaging, as proposed here, is needed
 to distinguish 
@@
 as it allows us to obtain a detailed
-dynamical lens model of the system, probing at sub-kpc scale resolution % probe down to 0.15" <-> 500 pc
-(about the typical size of high-z GMCs), which will enable us 
+dynamical lens model of the system and therefore probe structure at sub-kpc scales
+(typical size of high-z GMCs), as well as enables us 
 to compare the spatial distributions of star-forming gas clumps 
 with recent star-formation (from HST).
-Such comparisons are the key to understand different processes
-that regulate the star-formation/SB
-in ULIRGs/mergers and examine how they differ from other galaxy populations.
+Such comparisons are the key for understanding different processes
+that regulate the SB
+in ULIRGs/mergers and examining how they differ from other galaxy populations.
 % kinematics
@@
 to constrain the kinematics and relative mass-fractions of different gas phases, 
-which are indications of the evolutionary stage of this galaxy.
+which are indicative of the evolutionary stage of this galaxy.
 
-\underline{\bf Line ratios and the AGN/SB diagnostic:}
+\underline{\bf(2) Line ratios and the AGN/SB diagnostic}
 Aided by lensing, we will be able obtain kinematical information on spatial 
 scales smaller than the beam, as seen in our \bco data (\Fig{combine}c, d), thereby
-% and thus recover structural details and kinematics in finer detail than otherwise possible
 enabling us to probe the physical properties of
-the inner molecular disk near the AGN. 
-% At the proposed resolution, we will be able to distinguish the \dhcn and \dhcop
-% emission originating from the AGN host galaxy (and within) and from its companion.
+the inner molecular disk near the AGN of RX1131. 
 Recent studies find that the \dhcn/\dhcop line ratio is enhanced 
-in the circumnuclear disk (CND) near an AGN and falls off with distance from the CND
+in the circumnuclear disk (CND) near AGNs, and falls off with distance from the CND
 \citep{GB14a,Imanishi16a}. At the proposed resolution, we will 
 resolve the line emission originating near the AGN and that from the spatially extended 
-SB regions ($>$kpc scales) in the host galaxy, and by measuring spatial variations in 
+SB regions ($>$kpc scales) in the host galaxy. By measuring spatial variations in 
 this line ratio, we will assess its utility 
-as an AGN/SB diagnostic (\Fig{AGNSB}) at high redshift.
+as an AGN/SB diagnostic (\Fig{AGNSB}) at $z$$\sim$0.7.
 Since the HCN vibrational line (v$_2$=1;$J$=4\rarr3) falls within the targeted frequency range, 
 we will use it to independently constrain the radiation properties of the AGN environment,
-given that this line is excited by infrared pumping and that the radiation
-field associated with the AGN is the cause of the elevated \dhcn/\dhcop
+given that this line is excited by infrared pumping of
+the same radiation field associated with the AGN that causes the elevated \dhcn/\dhcop
 \citep{Sakamoto10a,Imanishi13a}.
@@
 ratios without significant uncertainties due to differential lensing.
-Such measurements are vital to reveal how galaxy interactions drive gas into 
-inner disks to initiate SB/AGN activities and how the ISM differs from 
-normal star-forming galaxies.
-
 \begin{figure*}[!tbph]
@@
 \centering
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.625\textwidth}}]{figure}[\FBwidth]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.625\textwidth}}]{figure}
+[\FBwidth]
 {\includegraphics[trim=15 0 5 10, clip, width=0.35\textwidth]{Fig/izumi15}}
 {
-\hspace{-1.25em}
+\hspace{-1.35em}
 \vspace{-1.15em}
 \caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{\dhcn/\dhcop as AGN/SB diagnostic.}
-Difference in line ratios between local AGNs, SBs, and (U)LIRGs with buried AGNs suggest
-that \dhcn/\dhcop can be used as a diagnostic tool to reveal the dominant power source within the
-beam, where an elevated line ratio is seen in AGN and circumnuclear regions relative to starbursts.
+Differences in line ratios between local AGNs, SBs, and (U)LIRGs with buried AGNs suggest
+that \dhcn/\dhcop can be used as a diagnostic tool to distinguish between
+the energy source from an AGN and starbursts,
+where an elevated line ratio is seen in AGN-dominated regions relative to starbursts.
 Such diagnostics depend heavily on the spatial resolution, as demonstrated by the
 measurements taken with APEX (empty circle) and ALMA (filled circles) in NGC1068.
-We here propose to spatially resolve this line ratio within the AGN host galaxy and obtain
-measurements toward the AGN and the extended SB regions in order to investigate spatial variations 
-and assess its utility as an AGN/SB diagnostic at high redshift.
+We here propose to spatially resolve this line ratio within RX1131
+%  and obtain
+% measurements toward the AGN and the extended SB regions 
+in order to 
+% investigate spatial variations and 
+assess its utility as an AGN/SB diagnostic at high redshift.
 (Figure taken from \citealt{Izumi16a})}
@@
 % 
-% XDR versus PDRs
-Since \eco is excited at higher temperature than the HCN and \hcop lines (e.g. in 
-X-ray dominated regions (XDRs) near an AGN), 
-variations in HCN/CO will allow us to constrain the spatial extent of photon-dominated regions
- (PDRs from SBs) and XDRs.
 % physical properties
-In addition, we will use spatially resolved line ratios of HCN/CO and \hcop/CO within the AGN host galaxy
+In addition, we will use spatially resolved line ratios of HCN/CO and \hcop/CO within RX1131
 as proxies of its very dense (cores; $\sim$10$^5$-10$^7$ cm$^{-3}$) versus the less dense (clumps; $\sim$10$^4$
-cm$^{-3}$) gas content and their spatial distributions as a function of distance from the AGN. This will enable
-us to gain insight into the SF mode on small scales across different galaxy populations, 
-as traced by the HCN/CO-\LIR relation, and investigate
-the interplay between AGN, SB and the dense gas content in the ISM.
-% \Fig{SF}).
+cm$^{-3}$) gas content and their spatial distributions as a function of distance from the AGN. 
+This will enable us to use relations such as HCN/CO-\LIR to investigate the main driver 
+of the enhanced SFRs in ULIRGs (e.g., if they all tend to have high dense gas fraction toward their central regions).
+% An increase in line ratios between high-density and low-density molecular gas tracers (e.g. HCN/CO) 
+%with increasing infrared luminosity suggests that the main driver of the enhanced SFR
+%is the molecular gas density distribution, in agreement with the observations that ULIRGs
+%host large reservoirs of dense molecular gas in their
+%central regions. 
+Measuring the gas kinematics and variations 
+in these line ratios will thus provide clues on how galaxy 
+interactions drive gas into inner disks to initiate SB/AGN activity and 
+how the excitation of gas differs from 
+normal star-forming galaxies.
 % CO SLED
-We will also combine \eco with our existing \bco and CO($J$=3\rarr2) data to constrain the gas density ($n_{\rm H_{2}}$) 
+We will also combine \eco with our existing \bco and CO($J$=3\rarr2) 
+data to constrain the gas density ($n_{\rm H_{2}}$) 
 and kinetic temperature by performing large velocity gradient (LVG) modeling.
 
-\underline{\bf The SK Law for dense gas:}
+\underline{\bf(3) The SK Law for dense gas}
 The Schmidt-Kennicutt (SK) relation (%``Star-formation law"; 
@@
 is one of the key ingredients
-for theoretical models as it encodes the physical processes and timescales
+for theoretical models of galaxy evolution since it encodes the physical processes and timescales
 regulating star-formation and their dependence on the ISM 
-(e.g. \citealt{Narayanan14a}).
+(e.g., \citealt{Narayanan14a}).
 However, the surface density of gas at high densities ($n$$\gtrsim$10$^5$cm$^{-3}$; 
 $\Sigma_{\rm dense}$)
-% ; and thus $\Sigma_{\rm SFR}\propto \Sigma^N_{\rm dense}$) 
-is currently poorly constrained 
+is poorly constrained 
 for high-z galaxies due to the lack of 
-(spatially resolved) observations of the much weaker emission 
-from high critical density tracers. %(see right of \Fig{SF}).
-It is thus unclear how the power-law index of the SK law should change depending on
-the critical density of the tracer used to probe the SF gas \citep[e.g.][]{KT07a}
-and how the SFR surface density should depend on the global 
-dynamical time scales in normal galaxies and in mergers.
+{\em spatially resolved} observations of the much weaker emission 
+from high critical density tracers.
+It is therefore unclear how the power-law index of the SK relation should change depending on
+the critical density of the tracer used to probe the SF gas \citep[e.g.,][]{KT07a}
+and how the SFR surface density could differ between normal galaxies and in mergers
+depending on their global dynamical timescales.
 At the proposed resolution, we will spatially resolve, for the first time,
@@
 in a high-z merger, down to the size scale of star-forming gas clumps. 
-This will enable us to provide crucial constraints on the conditions for star-formation models at high redshift.
+This will provide crucial constraints on the conditions for star-formation at high redshift.
 
 \medskip
-\noindent In summary, our proposed observations therefore provide an exceptional opportunity to investigate
-the physical properties and dynamical structures of different gas phases in the ISM of a distant merger
-% and distant galaxies 
-at exquisite detail. 
+\noindent In summary, our proposed observations provide an exceptional opportunity to investigate
+the physical properties and dynamical structures of different gas phases in the ISM 
+of a distant merger at exquisite detail. 
 This will also demonstrate the capabilities of ALMA to % mapping 
@@
 \centering
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.625\textwidth}}]{figure}[\FBwidth]
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.625\textwidth}}]{figure}
+[\FBwidth]
 {
-% HCN/CO - LIR plot: e.g. Fig 6 in \citep{Juneau09a}
-\includegraphics[trim=15 0 5 10, clip, width=0.25\textwidth]{Fig/SFRSD}} 
+\includegraphics[trim=0 0 0 0, clip, angle=-90, width=0.25\textwidth]{Fig/SFRSD}} 
 {
@@
 \caption{ \fontsize{10pt}{12pt}\selectfont{
-% \textbf{HCN/CO-\LIR relation} % 
-%An increase in line ratios between high-density and low-density molecular gas tracers (e.g. HCN/CO) 
-%with increasing infrared luminosity suggests that the main driver of the enhanced SFR
-%is the molecular gas density distribution, in agreement with the observations that ULIRGs
-%host large reservoirs of dense molecular gas in their
-%central regions. 
 \textbf{Schmidt-Kennicutt relation for dense gas.}
@@
 star-formation models, current studies only have constraints
-up to the gas of density traced by the ground state HCN line (\ncrit$\sim$10$^{4}$),
-which are also largely limited to local measurements \citep{GB12a}. 
+on gas of densities below \ncrit of the ground state transition of HCN (\ncrit$\sim$10$^{4}$).
+These studies are also largely limited to measurements of local galaxies \citep{GB12a}. 
 Our proposed observations will, for the first time, constrain the spatially resolved
-SK relation at kpc scales 
-in a ULIRG at $z$$\sim$0.7 by using
-high critical density tracers (HCN\,$J$=4\rarr3 and \hcop\,$J$=4\rarr3). This will allow us to 
+SK relation at kpc scales in a ULIRG at $z$$\sim$0.7 using
+high critical density tracers (HCN\,$J$=4\rarr3 and \hcop$J$=4\rarr3). This will allow us to 
 explore potential deviations at higher redshift and provide
@@
 We estimate the source size from our lens model 
-and adopt conservative line ratios measured for ULIRGs and high-z galaxies 
-(GS04; P07; \citealt[][]{Greve09a,CW13}) to compute the estimate line fluxes.
+and adopt line ratios measured for ULIRGs and high-z starbursts
+(GS04; P07; \citealt[][]{Greve09a,CW13}) to compute the expected line fluxes.
 To secure enough S/N for lens modeling, 
-we require a minimum of 8$\sigma$ of 0.47 mJy beam\pmOne and 0.07 mJy beam\pmOne
-per 150 \kms channel 
-for the science goals, respectively (see TJ for details).
+we require a minimum of 8$\sigma$ of $\sigma$$=$0.47 mJy beam\pmOne and $\sigma$$=$0.07 mJy beam
+\pmOne per 150 \kms channel for the science goals, respectively (see TJ for details).
 
@@
 \centering
-\vspace{-0.559em}
-\hspace{-2.75em}
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.445\textwidth}}]{figure}[\FBwidth]
+\vspace{-1.7em}
+\hspace{-2.5em}
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.4095\textwidth}}]{figure}
+[\FBwidth]
 {
-\includegraphics[trim=37 35 247 5, clip, width=0.575\textwidth]{Fig/combine.pdf}}
+\includegraphics[trim=37 35 247 5, clip, width=0.615\textwidth]{Fig/combine.pdf}}
 {
-\hspace{-1.0em}
+\hspace{-1.557em}
 \caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{Recent \bco data from NOEMA.}}
@@
 {\em (c):}
-Observed spatial variations across the channels, as shown by the red (red-shifted), 
+Observed spatial variations across different velocity components due to differential lensing, 
+as shown by the red (red-shifted), 
 green (line center), and blue (blue-shifted) contours.
@@
 This will allow us to investigate the 
-mechanisms responsible for the starburst in the AGN host galaxy
+mechanisms responsible for driving the starburst in RX1131
 % (e.g. GMC-like in a rotating disk or fragmentation of a
@@
 and its ISM conditions as it interacts with the companion. 
-We therefore aim to spatially resolve the gas dynamics, kinematics and ISM conditions in a merger,
-providing observational constraints 
+We therefore aim to spatially resolve the gas dynamics, kinematics and ISM conditions in a 
+wet-merger, providing observational constraints 
 on the star-formation processes

### 2016-04-21 ALMA/Cycle4/RXJ.tex
proof read

@@
 Here we aim to bridge this gap by testing
-local correlations and properties at moderate redshifts 
+local correlations and properties at high redshifts 
 % Understanding galaxy populations at an epoch when
@@
 on sub-kpc scales is important to understand the 
-mechanism and physical processes responsible for 
+mechanisms and physical processes responsible for 
 the different star-formation modes in normal galaxies and ULIRGs. % at earlier epochs.
@@
 %  diagnostic tools 
-a diagnostic tool to reveal deeply buried AGNs at the cores of ULIRGs \citep{Imanishi14a, GB14a, Viti14a, 
+a diagnostic tool to reveal deeply-buried AGNs at the cores of ULIRGs \citep{Imanishi14a, GB14a, Viti14a, 
 Izumi16a, Imanishi16a}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at high-z}
+\noindent {\bf Science Target RXJ 1131-1231: a demonstrative case at $z$$\sim$0.7}
 % \vspace{-0.6em}
@@
 \label{fig:HST}}}
-\vspace{-0.8em}
+\vspace{-1.15em}
 \end{figure}
@@
 (2): \dhcn and \dhcop emission and the underlying continuum at 0.7" resolution (2.5 kpc in the source plane).
-The continuum will provide additional constraint on the Rayleigh-Jeans tail of the 
+The continuum will provide an additional constraint on the Rayleigh-Jeans tail of the 
 dust emission, which is currently constrained by four photometric data. 
@@
 \underline{\bf(1) Dynamics and kinematics}
-Our recently obtained \bco data shows an asymmetric double-horned line profile (\Fig{combine}a). Given
+Our \bco data obtained with NOEMA shows an asymmetric double-horned line profile (\Fig{combine}a). Given
 the 1$^{\rm st}$ moment map and the observed velocity gradient
@@
 [\FBwidth]
-{\includegraphics[trim=15 0 5 10, clip, width=0.35\textwidth]{Fig/izumi15}}
+{\includegraphics[trim=15 0 5 10, clip, width=0.30\textwidth]{Fig/izumi15}}
 {
@@
 that \dhcn/\dhcop can be used as a diagnostic tool to distinguish between
-the energy source from an AGN and starbursts,
+the energy source from an AGN and starburst,
 where an elevated line ratio is seen in AGN-dominated regions relative to starbursts.
@@
 This will enable us to use relations such as HCN/CO-\LIR to investigate the main driver 
-of the enhanced SFRs in ULIRGs (e.g., if they all tend to have high dense gas fraction toward their central regions).
+of the enhanced SFRs in ULIRGs (e.g., if the dense gas distribution and 
+content toward the central region of RX1131 is consistent with other ULIRGs).
 % An increase in line ratios between high-density and low-density molecular gas tracers (e.g. HCN/CO) 
@@
 the critical density of the tracer used to probe the SF gas \citep[e.g.,][]{KT07a}
-and how the SFR surface density could differ between normal galaxies and in mergers
+and how the SFR surface density could differ between normal galaxies and mergers
 depending on their global dynamical timescales.
@@
 of a distant merger at exquisite detail. 
-This will also demonstrate the capabilities of ALMA to % mapping 
+Our proposed observations of the HCN and \hcop lines will also demonstrate 
+the capabilities of ALMA to
 utilize these much fainter
@@
 \centering
-\vspace{-1.7em}
+\vspace{-1.475em}
 \hspace{-2.5em}
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.4095\textwidth}}]{figure}
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.4195\textwidth}}]{figure}
 [\FBwidth]
@@
 \hspace{-1.557em}
-\caption{ \fontsize{10pt}{12pt}\selectfont {\textbf{Recent \bco data from NOEMA.}}
+\vspace{-1.557em}
+\caption{ \fontsize{10pt}{12pt}\selectfont{\textbf{Recent \bco data from NOEMA.}}
 {\em (a):}

### 2016-05-02 src/SED/tablePhotometry.py
format script to output error to 3 decimal places, but not yet execute. manually fix those 0.00 error values and change sym for upper limits

@@ -7,14 +7,13 @@ wavelength [um], freq [GHz], flux density [mJy], flux_err [mJy], instrument
 Save table as latex file
 
 
-Last Modified: March 28 2016
+Last Modified: May 1 2016
 
-
-TODO
-- add VLA radio data LCX
 
 History
 -------
+May 1 2016:
+  update output error to 3 decimal places
 Mar 28 2016:
     updated SPITZER/IRAC data to using 5.8" diameter aperture flux
 Jan 09 2016:
@@ -159,7 +158,7 @@ for i, idx in enumerate(split1):
         tbl.rename_column(tbl.colnames[i], tbl.colnames[i][:idx])
 
 
-def combine_col(table, colname, errcolname, outcolname, unit=None, formatstr="{0:0.2f} $\pm$ {1:s}"):
+def combine_col(table, colname, errcolname, outcolname, unit=None, formatstr="{0:0.3f} $\pm$ {1:s}"):
 
     """
     combine flux and flux_err column -> with $\pm$
@@ -197,7 +196,7 @@ def combine_col(table, colname, errcolname, outcolname, unit=None, formatstr="{0
 
         # map the formatting function that changes np.nan to \nodata, else 2 decimal place
         # map(f, list)
-        tmpCol = map(lambda x: r'\nodata' if np.isnan(x) else '{:.2f}'.format(x), tmpCol)
+        tmpCol = map(lambda x: r'\nodata' if np.isnan(x) else '{:.2}'.format(x), tmpCol)
 
     data = [formatstr.format(aa, err) for aa, err in zip(table[colname], tmpCol)]
     return Column(data=data, name=outcolname, unit=unit)

### 2016-05-02 src/SED/fitParamPlot.py
mbb_emcee model plot tools

@@ -1,0 +1,880 @@
+'''
+Plot mbb_emcee output
+
+Last Modified: 01 May 2016
+
+Original: /Users/admin/Research/3C220.3/3C220.3_CARMA/writeup/Code
+
+History:
+01 May 2016
+    get rid of np.flipud() in ax.imshow in order for triplot to work correctly.. Don't know why it works for 3C220.3, but has issues here -- maybe MPL version different?
+30 Apr 2016
+    comment out code for ALMA prediction, set ylim for best-fit SED from min=0 to avoid display -ve due to upper limit data points
+16 Nov 2015
+    added function PlotSED, changed savePlot location
+
+Note:
+
+'''
+
+
+import mbb_emcee
+import matplotlib.pyplot as plt
+import matplotlib
+import sys
+from pylab import savefig
+import numpy as np
+import scipy.ndimage.filters as filter
+
+# matplotlib.rc('text', usetex=True)
+matplotlib.rc('xtick', labelsize=18)
+matplotlib.rc('ytick', labelsize=18)
+font = {'family': 'Arial Narrow',
+        'weight': 'bold',
+        'size': 12}        # 15
+matplotlib.rc('font', **font)
+# monospace sans-serif
+axes = {
+    'titlesize': 'xx-large',
+    'labelsize': 'x-large',
+    'labelweight': 'normal',
+    'linewidth': 1.5
+}
+matplotlib.rc('axes', **axes)
+
+
+def convergence(plotTitle='ln prob', saveFig=False):
+    """
+    Plot the convergence profile.  I.e., Max(lnprob) - lnprob as a function of
+    iteration number.
+    """
+
+    lnprob = res.lnprobability.flatten()
+    Plotlnprob = max(lnprob) - lnprob
+    plt.clf()
+    plt.plot(Plotlnprob)  # , ',', alpha=0.5)
+    plt.xlabel('iteration')
+    plt.ylabel('max(lnprob) - lnprob')
+    plt.title(plotTitle)
+    plt.semilogy()
+    if saveFig == True:
+        outfile = 'convergence__'
+        savefig('../Figures/' + outfile + filename.replace('.h5', '.png'))
+    else:
+        plt.show()
+
+
+def chain_iter(nburn=100, saveFig=False):
+    """
+    plot the chains to visually assess convergence
[…]

### 2016-05-03 WRITEUP/Intro.tex
added intro, remove source plane reconstruction images

@@
 \citestyle{aa}
-\shorttitle{TBD}
+\shorttitle{Something goes here}
 \shortauthors{Leung \& Riechers}
@@
 
+\keywords{ISM: molecular -- 
+          infrared: galaxies -- 
+          galaxies: starburst --
+          galaxies: evolution}
+
+  %--------------------------------------------------------------------------
+  %                                Introduction
+  %--------------------------------------------------------------------------
+
 \section{Introduction}
+% Role of ULIRG/Merger and AGN
+Ultra-luminous IR galaxies \LIR\,$>$\,10$^{12}$\Lsun.. hot dust re-radiating energy from a central SB or an active galactic 
+nucleus (AGN), i.e. expect them to have large gas to begin with to drives the \LIR.
+
+% local --> merger
+Current studies of local ULIRGs revealed a causal connection between ULIRG activity and galaxy interaction based on morphological evidence of ULIRGs e.g.
+have double nuclei, severely distorted isophotes, or strong tidal features.
+
+Regardless of whether the energy source is dominated by starburst or an AGN, both of which depend on a large supply of fuel of gas 
+in the form nuclear region. If galaxy collisions can drive gas inwards from the galaxies' disks into their nuclei, this nuclear inflow can feed the 
+central engine. Once the gas reachers the inner kpc, it can either fragment and form stars (at a rate of $\sim$ 100 \Msun yr\pmOne) to 
+provide the observed luminosity, or continue to flow inwards and fuel an AGN.
+
+% but at least, we now understand/expect
+In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, where distant QSOs are the 
+progenitors of the dormant SMBHs in nearby galaxies. Quasars are powered by gas falling into central BHs, when galaxies 
+collide or merge, which is a natural consequence of hierarchical structure formation because During the early epoch, the 
+universe was smaller.
+
+On the other hand, it is found that high-z BHs grow faster than their host galaxies since the dynamical mass inferred from CO velocity structure (line width) and spatial extent is lower than the inferred one based on local BH-bulge mass relation.
+Meaning the Magorrian relation doesn't hold at $z$\,$\gtrsim$ BLAH, which means that we need to also understand the 
+properties of AGN host galaxies between these epochs.
+
+%% SF mode at high-z: 
+due to higher gas fraction than local, regardless of their position in the SFR-M* plane, both MS and SB @ high z, depletion time is much short than local, suggesting more efficient mode for SF from existing gas.
+supplies, which is naturally a result of highly dispersive gas motions (from on-going accretion needed to replenish gas 
+contents, and gal. interactions).
+
+Recent studies also find dynamical evidence for clumpy, globally unstable disks at high-z, 
+where SF is enhanced by disk instabilities and not mergers (cite: Genzel+05, Forster-Schreiber+09).
+
+% timescale is not clear
+there are many questions remain, e.g. timescales for blah..
+
+% their roles at this epoch
+Physically motivated galaxy evolution models find that we need feedbacks to ? turn off SF at to build-up present day red 
+sequence galaxies. (Dave+05)
+
+Current studies see a change of slope at high M* (esp. at $z$ $<$ 1.5),  i.e. suppression of SFR at high M*, i.e. strong evolution in 
+sSFR (of massive gal.) (cite: Papovich, Whitaker+12, Magnelli+14, Schreiber+15, Lee+15)
+
+but question remains: what mechanism is responsible for removing cold gas from galaxies and shutting down their star 
+formation? Many star formation suppression or "quenching" processes have been suggested, including mergers, ram 
+pressure stripping, tidal ``harassment", etc. One of the more intriguing possibilities, however, is star 
+formation quenching via powerful feedback from AGNs.
+
+% role of merger driven SB?
+role of merger in building up the mass of galaxies across the universe.
+
+% SF and gas;  gas dynamics and AGN fueling
+From local observations, there is no strict relation between presence of an AGN, companions or barred structures, AGN don't 
+show obvious systemic signatures of nuclear fueling form host, need to trace dynamics of gas in QSO host to understand 
+whether gas funneled by bars or driven by merger.
+
+important to study gas dynamics from mergers because that's how we think gas accumulates and flow inward for SMBH grow
+and merger drives turbulent gas motions, which fuel the central BH, and SB. 
+Ideally, we would want to measure kinematics of e.g. CO, CII to trace the dynamical mass of QSO host galaxies
+    - free from dust extinction as with optical
+
+So we went after to detect the gas content in a merger of a quasar host galaxy with recent star-formation at $z$\,$\sim$ blah. 
+clearly, there's quasar activity, and also recent star-formation, so it's an exceptional candidate to study the BLAH.
+
+% The source
 The gravitational lens RXJ 1131-1231 was discovered with spectroscopic
@@
 % FG gal is an elliptical gal: Slues+03 absorption lines
-
 As detected in the HST images, RXJ1131-1231 is a quadruply imaged AGN with
@@
 
-In this paper, we BLAH, refining the redshift to $z$=0.654
+In this paper, we BLAH, refining the redshift to $z$=0.65370$\pm$0.0005
 We use a cosmology WMAP9.
@@
 rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ =
-0.654
+0.65
  were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
@@
 pointing, secondary amplitude, and phase calibration and 1055$+$018 was
-observed as bandpass calibrators 
-for both tracks.
-MWC349 and 3C279 were observed
-as the primary
+observed as bandpass calibrators for both tracks.
+MWC349 and 3C279 were observed as the primary
 absolute flux calibrator for C and D array observations, respectively, yielding
-$\lesssim
-$15\% calibration accuracy.
+$\lesssim$15\% calibration accuracy.
 
 The GILDAS package was used to reduce and analyze the visibility data which are
-then imaged and deconvolved using
-the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
+then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. 
+This yields a synthesized clean
 beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA: 13\degr). The final rms noise
-is $\sigma$ =
-0.177 
-Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to
-690 km s$^{-1}$), and $\sigma$ = 1.451 Jy km s$^{-1}$ beam$^{-1}$ over 10 MHz 
-(21.5 km s$^{-1}$) . 
+is $\sigma$ = 0.177 Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to
+690 \kms), and $\sigma$ = 1.451 Jy \kms beam\pmOne over 10 MHz
+(21.5 \kms) .
 The continuum image is created by % 2.152 mm;
@@
 rest}$ = 345.7959899 GHz)
-%toward the background galaxy RXJ1131-1231 at $z$ = 0.654
- were carried out using the Combined Array for Research in Millimeter-wave
-Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers) on 2014 February 17 
+with the Combined Array for Research in Millimeter-wave
+Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers) were 
+carried out on 2014 February 17
 under good 3 mm weather
 conditions and on 2014 February 02 under terrible 3mm weather in the D array
-configurations.  The 3 mm receivers were used to cover
-the 
+configurations. The 3 mm receivers were used to cover the
 redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
 providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
-12.5 MHz ($
-\sim$17.9 km s$^{-1}$). The line was placed in the
-lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
+12.5 MHz ($\sim$17.9 km s$^{-1}$). The line was placed in the
+lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
 this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
@@
 pointing, amplitude, and phase calibration. Mars was observed as the
-primary
-absolute flux calibrator and 3C279 was observed as bandpass calibrators for
+primary absolute flux calibrator and 3C279 was observed as bandpass calibrators for
 both tracks.
@@
 % phase 1130-149
-
-Observations of the radio continuum toward the
-galaxy RXJ1131-1231 were carried out using the {\it Karl G. Jansky} Very Large 
-Array (VLA; Program ID: AW741; PI: Wucknitz).
+Our analysis also use archival data of the radio continuum obtained with the 
+{\it Karl G. Jansky} Very Large Array (VLA; Program ID: AW741; PI: Wucknitz).
 Observations were carried out on BLAH under excellent/GOOD? weather
 conditions in the A array configurations. The C-Band receivers were used to
-cover the BLAH
-, employing a correlator setup providing a bandwidth of BLAH GHz in each
+cover the BLAH , employing a correlator setup providing a bandwidth of BLAH GHz in each
 sideband. This resulted in BLAH hours of BLAH antenna-equivalent on-source time
-after 
-discarding unusable visibility data.
+after discarding unusable visibility data.
 
@@
 absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding
-$\sim
-$15\% calibration accuracy.
+$\sim$15\% calibration accuracy.
 The AIPS package was used to calibrate and analyze the visibility data which
@@
 beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image. The final
-rms 
-noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.
+rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.
 
 \section{HST astrometry}
-We adopt the VLA 5\,GHz map of BLAH resolution as the reference coordinate frame and align the optical image. We shifted the 
-latter to the east by 0\farcs5963 in R.A and +0\farcs8372 in declination., which is consistent with the typical astrometric precision of the HST image. 
+We gathered optical (rest-frame UV) images for RXJ1131 from the Hubble Legacy Archive to illustrate the 
+spatial extent of different emission detected in this paper. Here, we only use the F555W image for 
+this purpose.
+We adopt the VLA 5\,GHz map of $\sim$2" resolution as the reference coordinate frame to align the optical image. 
+We shifted the latter to the east by 0\farcs5963 in R.A.
+and +0\farcs8372 in Dec., which is consistent with the typical astrometric precision of the HST image from the Hubble Legacy Archive.
+% for Hubble Legacy Archive: abs.
+astronmetry 1-2" http://hla.stsci.edu/hla_faq.html
 The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas.
@@
 yielding peak flux density of 57.8 $\pm$ 10.7 mJy, the FWHM of the Gaussian fit
-is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in the calibration.
+is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in 
+the
+calibration.
 
@@
 \caption{
-CO32 line spectrum
+CO32 line spectrum, looks like we are fitting to a bunch of noise. TODO
  \label{fig:co32spec}}
@@
 %sigma_mom0 = 0.43  over chan: 127, 155
+% z = 0.65370 $/pm$ 0.0005
 
@@
 
-We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.451mJy per channel per beam.
-Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$ limit of 4.353 mJy \kms beam\pmOne.
+We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted frequency 140 GHz in the foreground galaxy at $z
+\sim
+$0.295) of $\sigma$ = 1.451mJy per channel per beam. Assuming a typical line width of 300 \kms, this corresponds to a 3$
+\sigma$
+limit of 4.353 mJy \kms beam\pmOne.
 
@@
 \centering
-\includegraphics[width=0.35\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}	   
-\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
-\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
+\includegraphics[width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
+\includegraphics[width=0.25\textwidth]{../Figures/F555W_REDBLUE.png}
+\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
 \caption{
 0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping, of $\sigma$ 0.43 mJy beam\pmOne.
-Spectrum. Velocity scale w.r.t z=0.655
+Spectrum. Velocity scale w.r.t z=0.6537
  \label{fig:CO21mom0}}
@@
 \centering
-\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}	 %
+\includegraphics[width=0.8\textwidth]{../Figures/co_channel_maps.eps}	 %
 \caption{
 Black crosses indicate the position of the lensed AGN (components ABCD) and the central white-filled star indicates the
-position of the foreground lensing galaxy (component G) as detected in the HST image.
+position of the foreground lensing galaxy (component G) as detected in the HST image. Contours $\pm$ 3$\sigma$
  \label{fig:chanmap}}
@@
 \centering
-\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}   
+\includegraphics[width=0.8\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
 \caption{
@@
 
-\section{Continuum}
+\section{Interferometric Continuum}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-% 2mm peak is centered on foreground galaxy ~ 799 µJy/B --> with C band --> spectral index
-%	- 2mm marginally resolved along one axis (arc)
 %
@@
 
-VLA C Band continuum image shows resolved jets and core emission from the foreground lensing galaxy as well as the background lensed quasar (as arcs).
-We extracted the 5GHz fluxes for the arcs and the core as listed in Table \ref{tab:photometry}.
+VLA C Band continuum image shows resolved jets and core emission from the foreground lensing galaxy as well as the 
+background
+lensed quasar (as arcs). We extracted the 5GHz fluxes for the arcs and the core as listed in Table \ref{tab:photometry}.
 
-As shown in Figure \ref{fig:cont}, we detect 2mm continuum emission toward both the foreground galaxy and the background as lensed emission.  
-The integrated continuum flux density is 1.2 mJy, while the peak emission is centered on the foreground galaxy at $S_\nu$ of 8 \micron Jy beam\pmOne.
-The detection is hence marginally resolved along one axis as shown in Figure \ref{fig:contco21}.
-We attempted to extract the background emission by subtracting the foreground emission as modeled by a point source (unresolved).
-But the residual after removing a point source model is just noise.
-So we I guess if we take the difference between the integrated and the  peak in the image plane is an upper limit to the background source at 2mm, which is $\sim$ 0.4 mJy.
+As shown in Figure \ref{fig:cont}, we detect 2mm continuum emission toward both the foreground galaxy and the background 
+as lensed
+emission.
+The integrated continuum flux density is 1.2 mJy, while the peak emission is centered on the foreground galaxy at 
+$S_\nu$ of 8 \micron Jy beam\pmOne.  The detection is hence marginally resolved along one axis as shown in Figure \ref{fig:contco21}.
+We extract the background emission by subtracting the foreground emission as modeled by a point source (since source is 
+unresolved).
+After subtracting the peak, rms is same as before.
+Consistency checked: the peak in the residual coincide with previous potential emission from arc, also the peak flux in the 
+residual is 0.389 mJy.
+The flux in the residual after removing a point source model is just consistent with the difference between the integrated and 
+the peak in the
+image plane, which we adopt as continuum in the background source at 2mm, which is $\sim$ 0.4 mJy.
 
-We fit power law to the VLA radio data and the 2mm continuum, we derive a spectral index of $\alpha$=0.025.
-\begin{figure*}[tbph]
+We fit power law to the VLA C band radio data and the 2mm continuum, we derive a spectral index of $\alpha$=0.025.
+\begin{figure}[!htbp]
 \centering
-\includegraphics[width=0.8\textwidth]{../Figures/ContCO21.eps}	  
+\includegraphics[width=0.3\textwidth]{../Figures/ContCO21.eps}
 \caption{CO 21 moment0 overlay on 2mm continuum.  % chan [127,155]
@@
  \label{fig:contco21}}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[tbph]
+\begin{figure}[!htbp]
 \centering
@@
  \label{fig:cont}}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[tbph]
+\begin{figure}[!htbp]
 \centering
 \includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
-\includegraphics[width=0.55\textwidth]{../Figures/F555W_ContVLA.eps}
+\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContVLA.eps}
 \caption{
@@
  \label{fig:}}
-\end{figure*}
+\end{figure}
 
-\section{\rot{2}{1} Lens model}
+\section{gas kinematics and dynamics}
+% data 1st moment map:
+the observed velocity fields represents the rotation velocities.  
+We note that the velocity field is likely affected by
+systematic errors and by beam smearing given the spatial resolution of our data.
 
-\subsection{interpretation}
+The magnitude of the
+effect of beam smearing thus depends on the combination of
+the size of the beam, the distribution of the gas, the inclination
+angle of the galaxy and the velocity gradients.
+
+Before evaluating the rotation curve, beam smearing is taken into account. CO Gas emission is smeared out due to the finite 
+beam size of the telescope. This causes shallower gradients in the velocity field, which makes the inner part of the rotation 
+curve (generally where it has the steepest gradient in a disk) less steep/with shallower gradients.  
+The inner part of the rotation curve is most affected by beam smearing; as this is 
+where the curve is changing the most, you need more points to accurately connect them.
+
+ To correct for beam smearing, a model curve (data cubes?) was chosen and then a beam smear term was added to match the observed 
+rotation curve. Construct a set of model galaxies with known input rotation curves and convolve with beam to match 
+observations. Then, derive rotation curve by fitting tilted rings to the intensity-weighted mean velocity field.
+
+fit to a set of PV diagram
+
+\subsection{Dynamical Lens model of \rot{2}{1}}
+We construct a two-dimensional map of the velocity field in the source plane using the \rot{2}{1} emission. 
+The source-plane velocity field is shown in Figure \ref{fig:blah} and resembles a rotating
+
+% Interpretation of the lens model
 - C06 suggest the presence of an interacting dusty galaxy in their HST
@@
 	- Our model lens parameters (median):
-		- file: WRITEUP/MedianLensModelParams.txt
+		- file: serenity/model/src/medianLens0Param.dat
 		- lensing gal. position is consistent with C06,
@@
 
-\begin{figure}[tbph]
-\centering
-\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.eps}
-\includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
-\caption{
-Pseudo observed 0th moment map in the lens plane. (left)
-Pseudo 0th moment map in the source plane. (right)
-\label{fig:}}
-\end{figure}
-
 \begin{figure*}[tbph]
 \centering
-\includegraphics[width=0.65\textwidth]{../Figures/PostageStampModel.eps}
-\includegraphics[width=0.65\textwidth]{../Figures/PostageStampResiduals.eps}
+\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
+\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
 \caption{
@@
 
-\begin{figure}[tbph]
-\centering
-\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.eps}
-\caption{
-velocity gradient of the lens model in the lens plane (left), source plane
-(right).
-\label{fig:}}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side and including the 24.0\micron data from Spitzer/MIPS to constrain the dust peak. 
-Also do SED fit with IRAS upper limits.
+\subsection{Photometry}
+
+We obtain archival and published photometry.
+2MASS magnitudes from the 2MASS All-Sky
+Catalog of Point SourcesBLAH  (Skrutskie et al. 2006), WISE magnitudes
+from the AllWISE Source CatalogBLAH, Spitzer/MIPS
+data from BLAH Catalog, IRAS photometry from the IRAS point source
+and faint source cataloguesBLAH.
+
+The Herschel/SPIRE data are from the Herschel Science Archive, processed
+by the SPIRE HIPE pipeline version 12BLAH (Ott 2010). The
+photometry was extracted at the source position using the
+SUSSEXTractor task within HIPE (Savage \& Oliver 2007,
+Smith et al 2012, Pearson et al 2014). The SUSSEXtractor
+task estimates the flux density from an image smoothed with
+a convolution kernel derived from the SPIRE beam FWHM.
+The flux density measured by SUSSEXtractor
+was verified using the SPIRE Timeline Fitter (Bendo et
+al. 2013) which fits a two dimensional elliptical Gaussian
+function at the source position in the timeline data. The
+agreement between the SUSSEXtractor and Timeline Fitter
+flux densities was found to be better than $\sim$BLAH per cent.
+
+We list the mid-IR to FIR photometries compiled from 2MASS, WISE,IRAS, IRAC catalogs in Table \ref{fig:photometry}.
+
+We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side.
+We include the IRAS 60\micron and 100\micron upper limits to constrain the dust peak.
+We also fit SED models including the 24.0\micron data from Spitzer/MIPS.
 
@@
 \includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
-\caption{TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 2mm PdBI (now integrated and peak), extract flux after removing a point source model.
-Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux extraction.
-Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied. Spitzer/MIPS: PSF fit flux, as source size < native PSF FWHM of 6".
+\caption{TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 
+2mm
+PdBI (now integrated and peak), extract flux after removing a point source model.
+Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux 
+extraction.
+Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied. Spitzer/MIPS: PSF fit flux, as source size < 
+native PSF
+FWHM of 6".
 Might want to add NVSS constraints.
@@
 
+  %--------------------------------------------------------------------------
+  %                              Conclusion
+  %--------------------------------------------------------------------------
+\section{Discussion and conclusions}
+We observed the cold molecular gas properties using CO line emission toward the AGN host galaxy RXJ1131-1231 at 
+$z_{\rm CO}$\,$\sim$BLAH. 
+Fitting SED models, we find that the AGN host galaxy is a ULIRG. 
+A faint companion as seen in HST observations (BJB) is also detected in our CO, confirming it's redshift and gas rich nature.
+
+%==============================================================================
+%                                Back matters
+%==============================================================================
+
+% ACKNOWLEDGEMENTS
+%-----------------
+\acknowledgments
+We thank...
+
+  %--------------------------------------------------------------------------
+  %                               Bibliography
+  %--------------------------------------------------------------------------
+\bibliographystyle{yahapj}
+\bibliography{RXJ.bib}
 \end{document}

### 2016-05-04 src/RedBlue.py
cosmestic and clean junk in script

@@ -1,7 +1,7 @@
 """
 Author: Daisy Leung
 
-Last edited: 30 April 2016
+Last edited: 03 May 2016
 
 Purpose:
     Plot Red wing and Blue wing different color overlay on HST
@@ -10,6 +10,7 @@ Purpose:
 
 
 History:
+03 May 2016: change label color from yellow to black, since we inverted HST image, else can't read them
 30 April 2016: Change contour colors, inverted color for HST, change HST contrast based on ds9
 01 Jan 2016: update marker
 31 Dec 2015: Use linear shifted F555W image
@@ -109,8 +110,8 @@ markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
 # Labels
 ########################################
 # if '_' in sym[:-1]: symf = sym.replace('_', ' ')
-put_label(fig1, 0.82, 0.90, 'HST F555W', 'titleBand1')
-put_label(fig1, 0.82, 0.95, 'CO (2-1)', 'titleBand2')
+put_label(fig1, 0.82, 0.90, 'HST F555W', 'titleBand1', c='black')
+put_label(fig1, 0.82, 0.95, 'CO (2-1)', 'titleBand2', c='black')
 
 ########################################
 ########################################

### 2016-05-10 PdBI/src/modelVelo/modelGradient.py
get fit uncertainties

@@ -305,12 +305,10 @@ if plotMajorFit:
     residuals.set_xlim(fit.get_xlim())
     plt.axhline(y=0, color='b')
     plt.xlabel("RA ")
-    # These data look better if 'plain', not scientific, notation is used, and if
-    #   the tick labels are not offset by a constant (as is done by default).
-    plt.ticklabel_format(style='plain', useOffset=False, axis='x')
     plt.ylabel("Residuals")
     residuals.grid()
     plt.tight_layout()
+    plt.minorticks_on()
     plt.show()
 
 youtfit = fun2(out.beta, xdata)
@@ -449,6 +447,7 @@ if plotRot:
     plt.xlim(-0.2, 1.2)
     plt.legend()
     plt.tight_layout()
+    plt.minorticks_on()
     plt.show()
 # --------------------------------------------------------------
 #  disk model
@@ -507,7 +506,9 @@ if plotRot:
     plt.xlim(-1, 8.5)
     plt.ylim(-50, 450)
     plt.tight_layout()
+    plt.minorticks_on()
     plt.show()
+
 
 # fit tangent model to PV along major axis
 xdataPV = list(xdata[:4])
@@ -523,10 +524,27 @@ data = RealData(xdataPV, np.array(z),
 odr = ODR(data, _model, beta0=x4)
 out = odr.run()
 param = out.beta
-cov = out.cov_beta
-# print("\nStandard Covariance Matrix : \n", cov, "\n")
-uncertainty = out.sd_beta
 quasi_chisq = out.res_var
+
+# Print ODR Status and Results
+print 'Return Reason:\n', out.stopreason, '\n'
+print 'Estimated Parameters:\n', param, '\n'
+print 'Parameter Standard Errors:\n', out.sd_beta, '\n'
+print 'Covariance Matrix:\n', out.cov_beta, '\n'
+
+# Chi^2
+chi2 = 0.
+for i in range(len(np.array(z))):
+    residual = np.array(z)[i] - arctang2(param, xdataPV[i])
+    sigma = (xerr[i]**2. + yerr**2.)**0.5
+    chi2 += (residual / sigma)**2.
+# Reduced Chi^2
+ndof = len(ydata) - len(param)
+redchi2 = chi2 / ndof
+print 'Degrees of Freedom:\t', ndof
[…]

### 2016-05-10 PdBI/src/modelVelo/modelGradient.py
Mdyn using V_rot

@@ -7,7 +7,7 @@ Last Modified: 10 May 16
 
 TODO:
 get source size in old papers: C06: F160W sersic profile R_e = 9.8 kpc h_50^-1; F814W = 14.4kpc h_50^-1
-get i from C06
+get i from C06 ~ 3.25" across, 1.8" updown
 
 History:
 10 May 16:
@@ -20,6 +20,7 @@ History:
   - fix bug RA_major_err, Dec_major_err
   - add xerr bar on v_0
   - add ODR to fit arctangent model with xerr
+  - fix bug in PA calc.
 09 May 16:
   - fix a bug in run_odr_for_model()
   - added func to calc offset taking into acct inclination effect on y
@@ -40,6 +41,11 @@ History:
   - added error bars to positions
 04 May 16:
   - created code
+
+
+Note
+----
+Fitting data w/ unc. on both x, y using ordinary least squares can lead to bias in the solution. Use Orthogonal Distance Regression (ODR), rather than minimizing the sum of squared errors in the dependent variable, ODR minimizes the orthogonal distance from the data to the fitted curve by adjusting both the model coefficients and an adjustment to the values of the independent variable.
 
 '''
 import matplotlib
@@ -64,6 +70,10 @@ DecCentroid = -12.5328629
 RACentroid = 172.96434563
 CellSize = 0.5        # arcsec per pixel in 1D
 redshift = 0.6357
+b_arcsec = 1.8       # from C06
+a_arcsec = 3.25
+i_rad = np.arccos(b_arcsec/a_arcsec)
+i_deg = i_rad * 180./np.pi
 
 # source positions from models of different channel, offset in arcsec
 p_list = [(-0.20, 0.12), (-0.02, 0.11), (0.20, -0.13), (0.29, -0.01),
@@ -169,7 +179,7 @@ a.close()
 #                 bbox_inches="tight", pad_inches=0.1)
 #     print "-- Saved figure as : %s --" % (Plotpath + filename)
 
-theta_rad = abs(np.arctan(dec_coord_ls[0] - dec_coord_ls[-1]) / ((ra_coord_ls[0] - ra_coord_ls[-1]) * np.cos(np.mean(dec_coord_ls))))
[…]

### 2016-05-10 Spitzer/subPointsrc.py
IRAC photometry with aperture corerction

@@ -1,0 +1,180 @@
+#!/usr/bin/env python
+
+'''
+
+Subtract foreground profile to extract fluxes
+
+
+'''
+
+import numpy as np
+from astropy.io import fits
+from astropy.modeling import models, fitting
+import matplotlib.pyplot as plt
+import pywcs, pyfits
+
+# 3.6, 4.5, 5.8, and 8.0 um
+IRACim1 = 'IRAC/ch1/pbcd/maic.fits'       # use Gauss
+IRACim2 = 'IRAC/ch2/pbcd/maic.fits'     # use Gauss
+IRACim3 = 'IRAC/ch3/pbcd/maic.fits'     # use Gauss
+IRACim4 = 'IRAC/ch4/pbcd/maic.fits'     # use gauss
+
+srcRadPix = 5.    # radius in px, within which we sum up fluxes; archive flux used aperture ~5.8"diameter --> ~5 px radius
+# to follow aperture correction; http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/27/
+# 12-20 in 1.2" px <-> 24 - 40 in 0.6" px
+innerRadPix = 24
+outerRadPix = 40
+aperture_correction_4px = np.array([1.208, 1.220, 1.349, 1.554])   # based on R = 4px of .6"
+# but I am using R = 5 px of .6", correction should be lower
+# scale it down using aperture_coorection of 6px of .6"
+aperture_correction_6px = np.array([1.112, 1.112, 1.118, 1.213])
+# take average between 4px and 6px to get correction factor for R=5px
+aperture_correction = (aperture_correction_4px + aperture_correction_6px)/2.
+
+# to subtract PSF
+starFWHM_ch1 = [3.51, 4.15, 3.21, 2.84, 3.61]
+starFWHM_ch2 = [3.42, 3.1, 3.56, 3.19, 2.77]
+starFWHM_ch3 = [3.37, 3.87, 3.87, 3.27, 3.67]
+starFWHM_ch4 = [4.40, 4.01, 3.57, 3.79, 3.7]
+
+# ---------------------------------------
+# change this as necessary
+FWHM = np.mean(starFWHM_ch1)
+IRACim = IRACim1
+aper_cor = aperture_correction[0]       # [channel # -1]
+# ---------------------------------------
+
+xstd = FWHM/2.355
+ystd = xstd
+# centroid position on Foreground, guided by HST image by matching crosshair
[…]

### 2016-05-10 Spitzer/subPointsrc.py
update docstring

@@ -4,6 +4,10 @@
 
 Subtract foreground profile to extract fluxes
 
+Last Modified: 10 May 2016
+
+CAUTION:
+    edit variables FWHM, IRACim, aper_cor before running code
 
 '''
 
@@ -38,7 +42,7 @@ starFWHM_ch3 = [3.37, 3.87, 3.87, 3.27, 3.67]
 starFWHM_ch4 = [4.40, 4.01, 3.57, 3.79, 3.7]
 
 # ---------------------------------------
-# change this as necessary
+# CAUTION: change this as necessary
 FWHM = np.mean(starFWHM_ch1)
 IRACim = IRACim1
 aper_cor = aperture_correction[0]       # [channel # -1]
@@ -69,8 +73,10 @@ fitter = fitting.LevMarLSQFitter()
 g = fitter(g_init, xx, yy, b)
 # g = fitter(sersic_init, xx, yy, b)
 
-res_zoom = b[ycen-50:ycen+50, xcen-50:xcen+50] # (b - g(xx, yy))[ycen-50:ycen+50, xcen-50:xcen+50]
+# res_zoom = b[ycen-50:ycen+50, xcen-50:xcen+50]     # to calc. in original image
+res_zoom = (b - g(xx, yy))[ycen-50:ycen+50, xcen-50:xcen+50]
 pos_res_zoom = np.ma.masked_where(res_zoom < 0., res_zoom)
+
 # show over subtracting
 # plt.figure(1)
 # plt.imshow(b[ycen-50:ycen+50, xcen-50:xcen+50])

### 2016-05-10 src/SED/SEDplot.py
before adding IRAC photometry points

@@ -1,15 +1,13 @@
 '''
 
-Plot points on SED, put MIR and radio data on plot for background source but don't include in fit, maybe use IRAS 60, 100 micron to constrain SED peak
-- mark continuum for foreground and background differently
+Plot points on SED, put MIR and radio data on plot for background source but not used in fit.
 
 Last Modified: Jan 09 2016
 
 
 TODO
 - put mbb_emcee fit
--
-
+- mark continuum for foreground and background differently
 
 History
 -------
@@ -58,9 +56,9 @@ tbl = read_file(photoFile)
 
 # separate out photometry and those as upper limits
 print tbl.colnames
-idx, = np.where(np.isnan(tbl['Flux Err [mJy]']) == True)
+idx, = np.where(np.isnan(tbl['Flux Err [mJy]']) is True)
 tblUpLimit = tbl[idx]
-idx, = np.where(np.isnan(tbl['Flux Err [mJy]']) == False)
+idx, = np.where(np.isnan(tbl['Flux Err [mJy]']) is False)
 tblWithErr = tbl[idx]
 
 waveUpLimit = np.asarray(tblUpLimit['Wavelength [micron]'])
@@ -110,7 +108,7 @@ ax.errorbar(wave, flux, fluxErr, fmt=".r", ms=8, ecolor='gray',
             label='photo', capsize=8, elinewidth=4, capthick=1.5)
 ax.errorbar(waveUpLimit, fluxUpLimit, uplims=True, fmt="vk", ms=8, ecolor='gray', label='upperlimit', capsize=8, elinewidth=4, capthick=1.5)
 
-ax.set_ylim(min(flux)-0.5, 3*max(flux))
+# ax.set_ylim(min(flux)-0.5, 3*max(flux))
 ax.set_yscale("log")
 ax.set_xscale("log")
 

### 2016-05-10 src/SED/tablePhotometry.py
added IRAC decomposed

@@ -7,13 +7,14 @@ wavelength [um], freq [GHz], flux density [mJy], flux_err [mJy], instrument
 Save table as latex file
 
 
-Last Modified: May 1 2016
-
+Last Modified: May 10 2016
 
 History
 -------
+May 10 2016:
+    add decomposed IRAC points, and the missing 3.6 um point
 May 1 2016:
-  update output error to 3 decimal places
+    update output error to 4 decimal places, one can truncate the extra sig. fig. in the LaTeX table as needed
 Mar 28 2016:
     updated SPITZER/IRAC data to using 5.8" diameter aperture flux
 Jan 09 2016:
@@ -54,12 +55,30 @@ data_rows = [(1.25, (1.25*u.micron).to(u.GHz, equivalencies=u.spectral()).value
               21.96, 0.4247, 'WISE/W3'),
              (22, (22*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
               55.11, 1.878, 'WISE/W4'),
+             (3.6, (3.6*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
+              5.6183, 0.0021, 'Spitzer/IRAC(Extracted)'),
              (4.5, (4.5*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
-              7.803, 0.002082 , 'Spitzer/IRAC'),
+              7.803, 0.002082 , 'Spitzer/IRAC(Archive)'),
              (5.8, (5.8*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
-              10.72, 0.00512, 'Spitzer/IRAC'),
-             (8.9, (8.9*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
-              14.47, 0.004122, 'Spitzer/IRAC'),
+              10.72, 0.00512, 'Spitzer/IRAC(Archive)'),
+             (8.0, (8.0*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
+              14.47, 0.004122, 'Spitzer/IRAC(Archive)'),
+             (3.6, (3.6*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
+              5.0336, 0.0021, 'Spitzer/IRAC(Host)'),
+             (4.5, (4.5*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
+              6.0092, 0.0017, 'Spitzer/IRAC(Host)'),
[…]

### 2016-05-10 src/SED/tablePhotometry.py
added PdBI photometry from arc

@@ -13,6 +13,7 @@ History
 -------
 May 10 2016:
     add decomposed IRAC points, and the missing 3.6 um point
+    add PdBI residual point, error corresponds to without adding that from flux cal.
 May 1 2016:
     update output error to 4 decimal places, one can truncate the extra sig. fig. in the LaTeX table as needed
 Mar 28 2016:
@@ -106,7 +107,9 @@ data_VLA = [((4.8815*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
 data_PdBI = [((139.256*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
               139.256, 1.23, 0.22, 'PdBI-integrated'),
              ((139.256*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
-              139.256, 0.799, 1.3e-2, 'PdBI-peak')
+              139.256, 0.799, 1.3e-2, 'PdBI-peak'),
+             ((139.256*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
+              139.256,  0.4, 0.0816, 'PdBI-removedFG')  #  err incl. flux cal., used in SED fitting = 0.1976
             ]
 
 rmsCARMA_cont = 8.30807E-01   # mJy

### 2016-05-10 src/SED/SEDplot.py
fit decomposed IRAC points and extracted to decompose MIPS

@@ -1,23 +1,25 @@
 '''
 
-Plot points on SED, put MIR and radio data on plot for background source but not used in fit.
+Plot SED
 
-Last Modified: Jan 09 2016
+Last Modified: May 10 2016
 
 
 TODO
 - put mbb_emcee fit
-- mark continuum for foreground and background differently
 
 History
 -------
+May 10 2016:
+    plot foreground vs. background with different style, markers
+    fit decomposed IRAC points and extracted to "decompose" MIPS
 Jan 09 2016:
     created
-
 
 Note
 ----
 - Twin axes work perfectly, even on loglog
+- hard coded indices to separate out photometry for different sources, so that we can plot them with different styles
 
 '''
 
@@ -54,22 +56,133 @@ def read_file(filename):
 
 tbl = read_file(photoFile)
 
+# separate foreground and background
+# total = [:11], [19:27], [29], [32]
+# host = [11:15],[27], [31]
+# fg = [15:19],[28], [30]
+#
+
+idx_total = range(0, 11)
+for i in range(19, 27):
+    idx_total.append(i)
+idx_total.append(29)
+idx_total.append(32)
+
+idx_host = range(11, 15)
+idx_host.append(27)
+idx_host.append(31)
+
+idx_fg = range(15, 19)
+idx_fg.append(28)
+idx_fg.append(30)
+
 # separate out photometry and those as upper limits
-print tbl.colnames
-idx, = np.where(np.isnan(tbl['Flux Err [mJy]']) is True)
-tblUpLimit = tbl[idx]
-idx, = np.where(np.isnan(tbl['Flux Err [mJy]']) is False)
-tblWithErr = tbl[idx]
+# print tbl.colnames
+# total
+t = tbl[idx_total]
+idx, = np.where(np.isnan(t['Flux Err [mJy]']) == True)
+tblUpLimit_total = t[idx]
+idx, = np.where(np.isnan(t['Flux Err [mJy]']) == False)
+tblWithErr_total = t[idx]
 
-waveUpLimit = np.asarray(tblUpLimit['Wavelength [micron]'])
-fluxUpLimit = np.asarray(tblUpLimit['Flux Density [mJy]'])
+# separate out those that are upper limits
+waveUpLimit_total = np.asarray(tblUpLimit_total['Wavelength [micron]'])
[…]

### 2016-05-15 PdBI/src/modelVelo/calcmass.py
separate dyn. mass calc. from modelGradient.py

@@ -1,0 +1,29 @@
+'''
+
+calculate dynamical mass
+
+
+Last modified: 13 May 16
+
+History:
+13 May 2016
+    - extracted from modelGradient.py
+
+'''
+def M_encl(R_kpc, v):
+    """ calc mass enclosed """     # v in km/s
+    from astropy.constants import G
+
+    R = kpc_to_m * R_kpc
+    Msun = 1.989e30      # kg
+    v2 = (v * 1e3)**2
+    v2oG = v2 / G.value
+    v2oGoMsun = v2oG / Msun
+    M = R * v2oGoMsun           # per Msun
+    M10 = M / 1e10              # in units of x 1e10 Msun
+    return M10
+
+# calc. mass within some physical dist from line center
+R_in_kpc = xdata.max()
+# print("Mass enclosed within {:.2f} kpc: {:.2f} x 1e+10 Msun".format(R_in_kpc, M_encl(R_in_kpc, pfit[0]/np.sin(i_rad))))
+

### 2016-05-15 PdBI/src/modelVelo/modelGradient.py
tighter upper limit on r_t

@@ -4,9 +4,14 @@
 plot source locations from lens model of various channel as markers on observed 1st moment map.
 Kinematics.
 
-Last Modified: 11 May 16
+Last Modified: 13 May 16
 
 History:
+13 May 16:
+  - moved Mdyn calc to another script
+  - limit r_t to 15kpc
+12 May 16:
+  - replace r_s with r_t since it is the transition radius and not necessarily the scale length
 11 May 16:
   - use curve fit, problem is non-linear in parameters
   - note, we are also interested in reporting the correlation between the degenerate parameters --> need pearson R coefficients
@@ -51,12 +56,6 @@ Fitting data w/ unc. on both x, y using ordinary least squares can lead to bias 
  The results of the covariance matrix, as implemented by optimize.curvefit and optimize.leastsq rely on assumptions regarding the probability distribution of the errors and the interactions between parameters; interactions which may exist, depending on the fit function f(x).
 
 The best way to deal with a complicated f(x) may be to use bootstrap.
-
-Source size in C06: F160W sersic profile R_e = 9.8 kpc h_50^-1; F814W = 14.4kpc h_50^-1
-7.00 kpc/" for 70 km/s
-9.811 kpc/" for 50 km/s
-~ 10.3 kpc in 70 km/s
-
 
 '''
 import matplotlib
@@ -307,8 +306,8 @@ if plotMajorFit:
     fit.set_xticklabels(())
     plt.ylabel("Dec")
 
-    fit.plot(xdata, ydata, 'ro', xdata, fun2(param, xdata))
-    fit.errorbar(xdata, ydata, xerr=xerr, yerr=yerr, fmt='r+')
+    fit.plot(xdata, ydata, 'ko', xdata, fun2(param, xdata))
+    fit.errorbar(xdata, ydata, xerr=xerr, yerr=yerr, fmt='k+')
     fit.set_yscale('linear')
     a = np.array([out.xplus, xdata])   # out.xplus = x + delta
     b = np.array([out.y, ydata])
@@ -323,7 +322,7 @@ if plotMajorFit:
     # separate plot to show residuals
     residuals = fig.add_subplot(212, adjustable='box', aspect=0.4)
[…]

### 2016-05-15 PdBI/src/modelVelo/modelGradient.py
save best-fit PV

@@ -674,21 +674,23 @@ print("V_rot = V_obs/sin i: {} km/s \n").format(v_rot)
 fig = plt.figure(facecolor="0.98")   # with light gray background
 fig.subplots_adjust(hspace=0)
 fit = fig.add_subplot(111)
-plt.ylabel("V")
+plt.ylabel("Velocity [km/s]")
+plt.xlabel("Physical Radius from dynamical center [kpc]")
 space = 0.2
 xspan = xdataPV.max() - xdataPV.min()
 yspan = np.array(z).max() - np.array(z).min()
 xspace = space * xspan
 yspace = space * yspan
 xarray = np.linspace(xdataPV.min()-xspace, xdataPV.max()+xspace, 500)
-fit.plot(xdataPV, np.array(z), 'ko', xarray, arctang(xarray, *pfit))
+fit.plot(xdataPV, np.array(z), 'ko', xarray, arctang(xarray, *pfit), 'b--')
 fit.errorbar(xdataPV, np.array(z), xerr=xerr, yerr=yerr, fmt='k+')
 plt.minorticks_on()
+plt.tight_layout()
 plt.show(block=False)
 User_input = raw_input('Save figure? (Y/N): ')
 if User_input == 'Y':
     filename = "bestfit_PV.eps"
-    f.savefig(Plotpath + filename, dpi=100,
+    fig.savefig(Plotpath + filename, dpi=100,
                 bbox_inches="tight", pad_inches=0.1)
     print "-- Saved figure as : %s --" % (Plotpath + filename)
 
@@ -724,5 +726,5 @@ err_pfit_MC = Nsigma * np.std(ps, 0)
 print "\n MC method :"
 print "pfit = ", mean_pfit
 print "perr = ", err_pfit_MC
-raw_input("")
+
 

### 2016-05-15 WRITEUP/Intro.tex
reorganize paper --> ms.tex for real thing, Intro.tex is now where I dump text

@@
-\documentclass[]{emulateapj}
-\usepackage{amsmath}
-\input{preamble}
-\slugcomment{To be submitted to the ApJ}
-
-\citestyle{aa}
-\shorttitle{Something goes here}
-\shortauthors{Leung \& Riechers}
-
-\begin{document}
-%{\tiny  \RevisionInfo}
-
-\title{Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654}
-\author{T. K. Daisy Leung and Dominik A. Riechers}
-\affil{Department of Astronomy, Space Sciences Building, Cornell University,
-Ithaca, NY 14853, USA; \myemail}
-
-\begin{abstract}
-\end{abstract}
-
-\keywords{ISM: molecular -- 
-          infrared: galaxies -- 
-          galaxies: starburst --
-          galaxies: evolution}
-
-  %--------------------------------------------------------------------------
-  %                                Introduction
-  %--------------------------------------------------------------------------
+%%% this becomes dummy
 
 \section{Introduction}
-% Role of ULIRG/Merger and AGN
-Ultra-luminous IR galaxies \LIR\,$>$\,10$^{12}$\Lsun.. hot dust re-radiating energy from a central SB or an active galactic 
-nucleus (AGN), i.e. expect them to have large gas to begin with to drives the \LIR.
+Ultra-luminous IR galaxies (ULIRGS; \LIR\,$>$\,10$^{12}$\Lsun) are extremely luminous
+in the IR due to the re-radiation of energy absorbed from dust from starburst or an active galactic 
+nucleus (AGN), which also implies a large gas content to begin with. % to drives these activities.
 
-% local --> merger
 Current studies of local ULIRGs revealed a causal connection between ULIRG activity and galaxy interaction based on morphological evidence of ULIRGs e.g.
@@
 
-Regardless of whether the energy source is dominated by starburst or an AGN, both of which depend on a large supply of fuel of gas 
-in the form nuclear region. If galaxy collisions can drive gas inwards from the galaxies' disks into their nuclei, this nuclear inflow can feed the 
-central engine. Once the gas reachers the inner kpc, it can either fragment and form stars (at a rate of $\sim$ 100 \Msun yr\pmOne) to 
-provide the observed luminosity, or continue to flow inwards and fuel an AGN.
+Regardless of whether the energy source is dominated by starburst or an AGN, 
+both of which depend on a large supply of fuel of gas 
+in the form nuclear region. If galaxy collisions can drive gas inwards from the galaxies' disks into their nuclei, 
+this nuclear inflow can feed the 
+central engine. Once the gas reachers the inner kpc, it can either fragment and form stars 
+(at a rate of $\sim$ 100 \Msun yr\pmOne) to provide the observed luminosity, or continue 
+to flow inwards and fuel an AGN.
 
-% but at least, we now understand/expect
+% and high-z
 In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, where distant QSOs are the 
@@
 and merger drives turbulent gas motions, which fuel the central BH, and SB. 
-Ideally, we would want to measure kinematics of e.g. CO, CII to trace the dynamical mass of QSO host galaxies
-    - free from dust extinction as with optical
+Ideally, we would want to measure kinematics of e.g. CO, CII to trace the dynamical mass of QSO 
+host galaxies, free from dust extinction as with optical.
 
@@
 $z_\textrm{AGN,HST}$ =
-0.658, respectively \citep{}
+0.658, respectively \citep{Sluse03a}
 
@@
 
-\subsection{CARMA} \label{sec:carmadata}
+\subsection{CARMA}
 % LO = 215.6694 Ghz
@@
 % Integrated line flux: 37.509 Jy km/s over chan=[49,70] (FWZI) of sigma = 13.3mJy /B/channel of 35.87 km/s per channel
-%  57.753459930419922        10.658399798838524
-% 38.906448364257812        54.223567641493943
-% 258.26144409179688        57.450322398332851
-% 2.2153112888336182        2.9563491085933622
+% 
+% If we use FWHM of CO21 line to extract CO32 Intensity: I = Jy km/s over chan=[]
 
-% If we fit gaussian without the continuum to minimize error:
-% 58.848747253417969        10.030933764224825
-% 36.368530273437500        54.749284630860281
-% 276.93515014648438        54.753666156237443
-
-We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
+We detect resolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
 background galaxies in RXJ1131-1231.
-We extract the spectrum and fit a single-component Gaussian as shown in Figure
-\ref{fig:co32spec}
-yielding peak flux density of 57.8 $\pm$ 10.7 mJy, the FWHM of the Gaussian fit
-is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in 
+We extract the spectrum as shown in Figure
+\ref{fig:co32spec}.
+The integrated line flux is 37.1$\pm$ 2.8 Jy km/s, this does not include the uncertainties in 
 the
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}
+\includegraphics[width=0.5\textwidth]{../Figures/coOverlay.eps}
 \caption{
@@
 1st and 2nd order moments, clipped at 5 $\sigma$. 1st moment contour steps of 50 \kms, 2nd moment steps of 100 \kms.
-velocity range in z=0 frame = [-530.33, 72.73] \kms
-chan = [127, 155]
-sigma = 0.16821825 Jy \kms per Beam
-theshold: 5*sigma = 7.2550e-3 Jy per beam (per channel)
  \label{fig:highOmoments}}
@@
 \section{gas kinematics and dynamics}
+% Gas excitation
+
+Based on the apparent intensity of  \cco and \bco, we find an excitation of BLAH, assuming differential lensing is negligible.
+
 % data 1st moment map:
@@
 % Interpretation of the lens model
-- C06 suggest the presence of an interacting dusty galaxy in their HST
+\citet{Claeskens06a} suggest the presence of an interacting dusty galaxy in their HST
 observations, which BJB+08 calls it the F component. The lensed images of the
@@
 of channel widths $\sim$ 100\kms.
+Make this bigger in the future
 \label{fig:}}
@@
 A faint companion as seen in HST observations (BJB) is also detected in our CO, confirming it's redshift and gas rich nature.
-
-%==============================================================================
-%                                Back matters
-%==============================================================================
-
-% ACKNOWLEDGEMENTS
-%-----------------
-\acknowledgments
-We thank...
-
-  %--------------------------------------------------------------------------
-  %                               Bibliography
-  %--------------------------------------------------------------------------
-\bibliographystyle{yahapj}
-\bibliography{RXJ.bib}
-\end{document}

### 2016-05-15 WRITEUP/ms.tex
reorganize paper --> ms.tex for real thing, Intro.tex is now where I dump text

\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

\citestyle{aa}
\shorttitle{Something goes here}
\shortauthors{Leung \& Riechers}

\begin{document}
%{\tiny  \RevisionInfo}

\title{Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
\end{abstract}

\keywords{ISM: molecular -- 
          infrared: galaxies -- 
          galaxies: starburst --
          galaxies: evolution}

  %--------------------------------------------------------------------------
  %                                Introduction
  %--------------------------------------------------------------------------
  \section{Introduction}

  %--------------------------------------------------------------------------
  %                          Observations details
  %--------------------------------------------------------------------------
\section{Observations}
\subsection{PdBI \bco}
\subsection{CARMA \cco}
\subsection{VLA}

  %--------------------------------------------------------------------------
  %                                Results
  %--------------------------------------------------------------------------
  \section{Results}
  \subsection{\bco}
  \subsection{\cco}
  \subsection{Continuum}

    %--------------------------------------------------------------------------
  %                                Analysis
  %--------------------------------------------------------------------------
  \section{Analysis}
  \subsection{Lens modeling}
  \subsection{\bco Dynamical modeling}
  \subsection{SED modeling}
  \subsection{ISM properties}

    %--------------------------------------------------------------------------
  %                                Discussion
  %--------------------------------------------------------------------------
  \section{Discussion}

    %--------------------------------------------------------------------------
  %                                Conclusions
  %--------------------------------------------------------------------------
  \section{Conclusions}

  %==============================================================================
%                                Back matters
%==============================================================================

% ACKNOWLEDGEMENTS
%-----------------
\acknowledgments

  %--------------------------------------------------------------------------
  %                               Bibliography
  %--------------------------------------------------------------------------
\bibliographystyle{yahapj}
\bibliography{RXJ.bib}
\end{document}

### 2016-05-15 src/SED/tablePhotometry.py
add back HST

@@ -42,7 +42,19 @@ import numpy as np
 #
 tableColHead = ('Wavelength [micron]', 'Frequency [GHz]', 'Flux Density [mJy]', 'Flux Err [mJy]', 'Instrument')
 
-data_rows = [(1.25, (1.25*u.micron).to(u.GHz, equivalencies=u.spectral()).value
+data_rows = [(0.555, (0.555*u.micron).to(u.GHz, equivalencies=
+              u.spectral()).value, 0.0557, 0.006, 'HST-ACS/V-Band(L)'),
+             (0.814, (0.814*u.micron).to(u.GHz, equivalencies=
+              u.spectral()).value, 0.238, 0.0130, 'HST-ACS/I-Band(L)'),
+             (1.60, (1.60*u.micron).to(u.GHz, equivalencies=
+              u.spectral()).value, 0.539, 0.041, 'HST-NICMOS(NIC2)/H-Band(L)'),
+             (0.555, (0.555*u.micron).to(u.GHz, equivalencies=
+              u.spectral()).value, 0.00924, 0.00407, 'HST-ACS/V-Band(H)'),
+             (0.814, (0.814*u.micron).to(u.GHz, equivalencies=
+              u.spectral()).value, 0.041, 0.0054, 'HST-ACS/I-Band(H)'),
+             (1.60, (1.60*u.micron).to(u.GHz, equivalencies=
+              u.spectral()).value, 0.133, 0.004, 'HST-NICMOS(NIC2)/H-Band(H)'),
+             (1.25, (1.25*u.micron).to(u.GHz, equivalencies=u.spectral()).value
               , 1.009, 0.090, '2MASS/J-Band'),
              (1.65, (1.65*u.micron).to(u.GHz, equivalencies=u.spectral()).value
               , 1.448, 0.1214, '2MASS/H-Band'),

### 2016-05-15 PdBI/src/modelVelo/modelGradient.py
adjust residual fig comestic

@@ -4,9 +4,11 @@
 plot source locations from lens model of various channel as markers on observed 1st moment map.
 Kinematics.
 
-Last Modified: 13 May 16
+Last Modified: 15 May 16
 
 History:
+15 May 16:
+  - adjust residual fig outlook
 13 May 16:
   - moved Mdyn calc to another script
   - limit r_t to 15kpc
@@ -94,7 +96,7 @@ p_list_err = [(0.39, 0.3), (0.25, 0.2), (0.06, 0.21), (0.14, 0.22),
 # corresponding velocity in km/s for each points in p_list
 z = [344.46, 344.46, 236.82, 129.16, 21.54, -86.08, -193.76, -301.38]
 
-plotMajorFit = False
+plotMajorFit = True
 plotMajor_FirstMom = False
 plotPV = False
 plotRot = False
@@ -302,7 +304,7 @@ residual = np.sign(ydata-fun2(param, xdata))*np.sqrt(delta**2 + eps**2)
 if plotMajorFit:
     fig = plt.figure(facecolor="0.98")   # with light gray background
     fig.subplots_adjust(hspace=0)
-    fit = fig.add_subplot(211)       #, adjustable='box', aspect=1.2)
+    fit = fig.add_axes((.1, .3, .8, .6))
     fit.set_xticklabels(())
     plt.ylabel("Dec")
 
@@ -319,8 +321,9 @@ if plotMajorFit:
              'k-')
     fit.legend(loc='upper left')
     fit.grid()
+    plt.minorticks_on()
     # separate plot to show residuals
-    residuals = fig.add_subplot(212, adjustable='box', aspect=0.4)
+    residuals = fig.add_axes((.1, .1, .8, .2))
     residuals.errorbar(x=xdata, y=residual, yerr=adjusted_err,
                                 fmt="k+", label="Residuals")
     # make sure residual plot has same x axis as fit plot
@@ -329,7 +332,6 @@ if plotMajorFit:
     plt.xlabel("RA ")
     plt.ylabel("Residuals")
     residuals.grid()
-    plt.tight_layout()
     plt.minorticks_on()
     plt.show()
 

### 2016-05-15 src/SED/SEDplot.py
curve_fit to power-law in MIR

@@ -2,19 +2,24 @@
 
 Plot SED
 
-Last Modified: May 10 2016
-
-
-TODO
-- put mbb_emcee fit
+Last Modified: May 13 2016
 
 History
 -------
+May 15 2016:
+    - curve_fit to power_law working
+    - but extrapolated flux > MIPS point
+May 13 2016:
+    - update hardcode part because added HST
+    - replace least sq with curve_fit, but curve_fit to powerlaw is not working properly
 May 10 2016:
-    plot foreground vs. background with different style, markers
+    - plot foreground vs. background with different style, markers
     fit decomposed IRAC points and extracted to "decompose" MIPS
+    - put mbb_emcee fit
+    - added power law fit
+
 Jan 09 2016:
-    created
+    - created
 
 Note
 ----
@@ -57,24 +62,28 @@ def read_file(filename):
 tbl = read_file(photoFile)
 
 # separate foreground and background
-# total = [:11], [19:27], [29], [32]
-# host = [11:15],[27], [31]
-# fg = [15:19],[28], [30]
+# total = [6:17], [25:33], [35], [38]
+# host = [3:6], [17:21],[33], [37]
+# fg = [0:3], [21:25],[34], [36]
 #
 
-idx_total = range(0, 11)
-for i in range(19, 27):
+idx_total = range(6, 17)
+for i in range(25, 33):
     idx_total.append(i)
-idx_total.append(29)
-idx_total.append(32)
+idx_total.append(35)
+idx_total.append(38)
 
-idx_host = range(11, 15)
-idx_host.append(27)
-idx_host.append(31)
+idx_host = range(3, 6)
+for i in range(17, 21):
+    idx_host.append(i)
+idx_host.append(33)
+idx_host.append(37)
 
-idx_fg = range(15, 19)
-idx_fg.append(28)
-idx_fg.append(30)
+idx_fg = range(0, 3)
+for i in range(21, 26):
+    idx_fg.append(i)
+idx_fg.append(34)
+idx_fg.append(36)
 
 # separate out photometry and those as upper limits
 # print tbl.colnames
@@ -136,51 +145,59 @@ fluxErr_fg = np.asarray(tblWithErr_fg['Flux Err [mJy]'])
 
 
 # --------------- Fit slope -------------------------
[…]

### 2016-05-15 WRITEUP/ms.tex
done with Pdbi and VLA obs. setion; CARMA need to figure out flux cal accuracy

@@
+% Done: PdBI observations, VLA observations
+%
+%
+%
+%
+%
+
 \documentclass[]{emulateapj}
@@
 Ithaca, NY 14853, USA; \myemail}
+%==============================================================================
+%                                Front matters
+%==============================================================================
 
@@
 \section{Observations}
-\subsection{PdBI \bco}
+\subsection{PdBI \bco} % DONE
+Observations of the \bco rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz)
+toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$ =
+0.658 were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
+Riechers). Two observing runs were carried out on 2014 December 06 and 2015
+February 05 under good weather conditions in the C and D array configurations,
+respectively. The 2 mm receivers were used to cover the redshifted \bco line
+and the underlying continuum emission, employing a correlator setup providing
+an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
+21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on
+-source time after discarding unusable visibility data.
+The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
+for pointing, secondary amplitude, and phase calibration and 1055$+$018 was
+observed as bandpass calibrators for both tracks.
+MWC349 and 3C279 were observed as the primary flux calibrator for C and D
+array observations, respectively, yielding $\lesssim$15\% calibration accuracy.
+
+The \ncode{GILDAS} package was used to reduce and analyze the visibility data
+which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
+weighting.
+This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
+The final rms noise is $\sigma$ = 0.177 Jy \kms beam\pmOne over a channel width of 320 MHz (690 \kms), and $\sigma$ = 1.451 mJy \kms
+beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$
+139 GHz is created by averaging over all the line-free channels. This
+yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15
+
 \subsection{CARMA \cco}
-\subsection{VLA}
+% 1127-189 Gain for set 2
+% 3C273 gain for set 3
+% after flagging: Total observing time is  1.48 hours, checked with uvindex for
+% set 3
+% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
+% combined set
+% 12.500 MHz <=> 17.935 km/s
+Observations of the \cco rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz)
+were carried out under the D array configurations of the \carma (CARMA;
+Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 3\,mm
+weather conditions and on 2014 February 17 under good 3\,mm
+weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
+each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
+line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273 (
+second track) were observed
+every 15 minutes for pointing, amplitude, and phase calibration. Mars was
+observed as the primary absolute flux calibrator and 3C279 was observed as
+bandpass calibrators for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
+visibility data.
+
+% poor phase note
+Given that the phase calibrator used for the first track was faint and was
+observed under poor weather conditions and that the phase calibrator used for
+the second track was far from our target source, the phase calibration is
+subpar, with an rms scatter $\sim$60\degr. We thus conservatively estimate
+a calibration accuracy of $\sim$BLAH\% based on the flux scale uncertainties,
+gain variation over time, and the phase scatter on the calibrated data. We
+therefore treat its line intensity and refrain using it to derive other physical quantities.
+
+The \ncode{MIRIAD} package was used to calibrate the visibility data which are
+then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
+beam size of 3\farcs2 $\times$ 1\farcs9 (PA = 8\degr) for the lower sideband
+image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
+over a channel width of 25 MHz.
+
+\subsection{VLA} %DONE
+Our analysis also use the archival data of the radio continuum obtained with the \vla (VLA; Program ID: AW741; PI: Wucknitz). Since these data have not been
+published, we here describe the details of the observations as well as our calibration steps.
+
+Observations were carried out on 2008 December 29 under excellent weather
+conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C-Band receivers were used with a continuum mode setup, providing a bandwidth of 50
+MHz in each sideband.
+The nearby radio quasar 1130$-$149 was observed every 10 minutes for
+pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
+primary flux calibrator, and 0319$+$415 was observed as the bandpass calibrator, yielding $\sim$15\% calibration accuracy.
+We use \aips to calibrate the visibility data which
+are then imaged and deconvolved using
+the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
+beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\, 0\farcs18) and a final
+rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.
+
+\section{HST astrometry}
+We gathered optical (rest-frame UV) images for RXJ1131 from the Hubble Legacy Archive to illustrate the
+spatial extent of different emission detected in this paper. Here, we only use the F555W image for
+this purpose.
+We adopt the VLA 5\,GHz map of $\sim$2" resolution as the reference coordinate frame to align the optical image.
+We shifted the latter to the east by 0\farcs5963 in R.A. and +0\farcs8372 in Dec., which is consistent with the typical astrometric precision of the HST image from the Hubble
+Legacy Archive. % for Hubble Legacy Archive: abs. astronmetry 1-2" http://hla.stsci.edu/hla_faq.html
+The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas.
+We estimate the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
+be better than 0.1", leaving aside uncertainties relating to the SNR and beam size.
+
+%The astrometry of the HST images was firstly calibrated against a wider-field
+%optical image of the cluster which had in turn been aligned onto the FK5
+%coordinate system to an rms precision of ~0.2".
 
@@
 \subsection{\cco}
-  \subsection{Continuum}
+\subsection{Interferometric Continuum}
+2mm: resolved along the major axis, but unresolved along the minor axis. We decomposed the continuum from the foreground and background sources by subtracting a point
+source model in the uv-plane (see Riechers+13 SMMJ04135 description)
 
+\subsection{Photometry from archive}
+We obtain archival and published photometry.
+2MASS magnitudes from the 2MASS All-Sky
+Catalog of Point SourcesBLAH  (Skrutskie et al. 2006), WISE magnitudes
+from the AllWISE Source CatalogBLAH, Spitzer/MIPS
+data from BLAH Catalog, IRAS photometry from the IRAS point source
+and faint source cataloguesBLAH.
+
+The Herschel/SPIRE data are from the Herschel Science Archive, processed
+by the SPIRE HIPE pipeline version 12BLAH (Ott 2010). The
+photometry was extracted at the source position using the
+SUSSEXTractor task within HIPE (Savage \& Oliver 2007,
+Smith et al 2012, Pearson et al 2014). The SUSSEXtractor
+task estimates the flux density from an image smoothed with
+a convolution kernel derived from the SPIRE beam FWHM.
+The flux density measured by SUSSEXtractor
+was verified using the SPIRE Timeline Fitter (Bendo et
+al. 2013) which fits a two dimensional elliptical Gaussian
+function at the source position in the timeline data. The
+agreement between the SUSSEXtractor and Timeline Fitter
+flux densities was found to be better than $\sim$BLAH per cent.
+
+We list the mid-IR to FIR photometries compiled from 2MASS, WISE,IRAS, IRAC catalogs in \Tab{photometry}.
+\input{table_photometry_AAScustomized}
 %--------------------------------------------------------------------------
@@
 \subsection{Lens modeling}
+With the high SNR and spectral resolution, we model different kinematic components using our lensing code \uvmcmcfit.
+
+% describe model setup.
+
+% comparison with C06 model
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
+\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
+\caption{
+Lens model of channel widths $\sim$ 100\kms.
+Make this bigger in the future
+\label{fig:}}
+\end{figure*}
+
+\subsubsection{Differential Lensing}
+Lens modeling of this source from previous studies find non-negligible differential lensing effect across H-Band, V-band, and I-band. The magnification factor ranges from 10.9
+to 7.8, where the decrease is caused
+by the more extended IR emission (hence SF), well beyond the caustic (C06).
+
+The highly asymmetric \bco line profile also suggests that differential lensing is non-negligible in the CO emission, where
+flux density in the red wing is apparently much higher than in the blue wing, given its lensing configuration.
+By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in Table \ref{tab:}.
+\input{table_magFactor}
+
 \subsection{\bco Dynamical modeling}
+Based on the the source plane position of each kinematic components from the
+lens model, a clear symmetric velocity gradient is seen, which is suggestive of a rotating disk. Assuming the observed velocities of the respective channels
+correspond to solely the tangential components (i.e. $\theta$ = 0), we extract
+the major axis along the best-fit slice across these source plane positions,
+which is along PA of 121\degr.
+We attempt to characterize the molecular gas kinematics using an empirically motivated disk model (e.g. Courteau97, Peuch+08, Miller+11):
+\begin{equation}
+V = V_0 + \frac{2}{\pi} V_a arctan(\frac{R}{R_t}),
+\end{equation}
+where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center, $V_a$ is the asymptotic velocity, and $R_t$ is the ``turnover'' radius at which the rotation curve
+becomes flat. We perform non-linear least square fitting using an orthogonal distance regression to find the best-fit $V_a$, $r_t$, $V_0$, taking into account
+errors in both velocity and distance offset (see Figure \ref{fig:PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
+parameter physical. We then estimate the uncertainties associated with best-fit parameters using a Monte Carlo simulation of 500 iterations, perturbing
+the velocity and physical separation according to a random Gaussian distribution of width based on the input uncertainties on
+the data. Using this model, we find $V_a$ = 975$\pm$387, $r_t$ = 10.6$\pm$5.7,
+and $V_0$ = 28$\pm$40. We note, however, that since emission is not detected beyond the flat regime of the rotation curve (Figure \ref{fig: PV}), the asymptotic velocity is
+poorly constrained. In particular, $V_a$ and $r_t$ are highly correlated with a Pearson coefficient $r$ = 0.998 between the two, and 0.027 between $V_a$ and $V_0$.
+
+While a symmetric velocity field in the source plane is consistent with a rotating disc, such is insufficient to conclude a rotating disk morphology. Additional characteristics such
+as peak velocity dispersion at the center of a galaxy and a ``spider'' diagram are needed. Based on the reconstructed source plane in the optical/NIR emission, C06 find that a
+n=1 Sersic profile is best
+
+The frequently used Vmax (maximum measured velocity) is not equivalent to the
+asymptotic value, Va, a mathematical extrapolation and typically not reached in
+the observed rotation curve. Estimates of Va can depend critically on how well
+the central region and turn over of the rotation curve are constrained. For the
+remaining analysis, we adopt the asymptotic limit as a proxy to the rotation
+curve. We also note that typical studies of the Tully-Fisher relation uses V_2.2
+(2.2 * disc scalelength ~ 1.375 half-light radius ~ 0.7R_opt) as the rotation
+velocity since this would be the radius at which the velocity of a pure
+exponential disc peaks at. However, our source appears to be a disturbed
+rotator, albeit coarse resolution. Hence, rather than adopting V_2.2, we use the
+asymptotic value from the best-fit arctangent model. The half light radius in the
+optical is ~xx kpc (from C06; converted in to our cosmology, but BJB 8 kpc
+across?).
+
+If we adopt the best-fit parameters, we find a dynamical mass of $M_{\rm dyn}$($<$blah kpc) sin$^2 i$ = BLAH \Msun. Consider the line widths using the separation between
+the red- and blue- shifted emission of the \bco line profile of $\Delta v_{\rm sep}/2 \sim$ blah \kms and a source size of blah kpc, we find a dynamical mass of $M_{\rm dyn}$
+sin$^2 i$ = BLAH \Msun. If we adopt the inclination angle using the morphological axis ratio from the
+reconstructed optical image reported by C06, where the minor axis is 1\farcs8 and the major axis is 3\farcs3.25, then we find an inclination angle of 56.4
+\degr. Then $M_{\rm dyn}$\,=\,BLAH. The inclination angle is consistent with the observed unobscured AGN and an observable double peak line profile.
+
+We note, however, that large differences (up to $\gtrsim$10 deg) can be found between such kinematically-derived inclinations and the ones inferred from the morphological
+axis ratio (e.g., Chemin et al. 2006). We caution that this analysis is based on limited spatial resolution data and will been verified by future higher-resolution observations.
+
 \subsection{SED modeling}
 \subsection{ISM properties}
+\subsection{Gas Mass}
+\subsection{Source Extent}
+Compared to HST:
 
@@
 \section{Discussion}
+\subsection{At what stage is the merging in RXJ1131-1231?}
+
+\subsection{Implications} gas fraction at this redshift. how does that relate to
+the SFH. --> imply the change in cosmic SFD is due to change in gas content. SFE
+at this redshift, how does that relate to the SFH. probably a secondary effect
+to the drop in SFH
 
@@
 %--------------------------------------------------------------------------
-  \section{Conclusions}
+\section{Summary and Conclusions}
+We studied a wet-wet merger between a AGN/starburst ULIRG and a optically faint companion at $z$ $\sim$ 0.65.
 

### 2016-05-15 WRITEUP/ms.tex
done CARMA obs section

@@
-% Done: PdBI observations, VLA observations
+% Done: PdBI observations, VLA observations, CARMA obs
 %
@@
 
-\subsection{CARMA \cco}
-% 1127-189 Gain for set 2
-% 3C273 gain for set 3
-% after flagging: Total observing time is  1.48 hours, checked with uvindex for
-% set 3
-% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
-% combined set
-% 12.500 MHz <=> 17.935 km/s
+\subsection{CARMA \cco} %DONE
 Observations of the \cco rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz)
@@
 % poor phase note
+% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
+% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
+% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
+% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
 Given that the phase calibrator used for the first track was faint and was
@@
 subpar, with an rms scatter $\sim$60\degr. We thus conservatively estimate
-a calibration accuracy of $\sim$BLAH\% based on the flux scale uncertainties,
+a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
 gain variation over time, and the phase scatter on the calibrated data. We
@@
 pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
-primary flux calibrator, and 0319$+$415 was observed as the bandpass calibrator, yielding $\sim$15\% calibration accuracy.
+primary flux calibrator, and 0319$+$415 was observed as the bandpass calibrator, yielding $\sim$10\% calibration accuracy.
 We use \aips to calibrate the visibility data which

### 2016-05-15 WRITEUP/ms.tex
done HST astroemtry sec

@@
-% Done: PdBI observations, VLA observations, CARMA obs
+% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry
 %
@@
 Observations were carried out on 2008 December 29 under excellent weather
-conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C-Band receivers were used with a continuum mode setup, providing a bandwidth of 50
-MHz in each sideband.
+conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C-Band receivers were used with a continuum mode setup,
+providing a bandwidth of 50 MHz in each sideband.
 The nearby radio quasar 1130$-$149 was observed every 10 minutes for
 pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
-primary flux calibrator, and 0319$+$415 was observed as the bandpass calibrator, yielding $\sim$10\% calibration accuracy.
+primary flux calibrator, and 0319$+$415 was observed as the bandpass
+calibrator, yielding $\sim$10\% calibration accuracy.
 We use \aips to calibrate the visibility data which
@@
 the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
-beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\, 0\farcs18) and a final
+beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
 rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.
@@
 \section{HST astrometry}
-We gathered optical (rest-frame UV) images for RXJ1131 from the Hubble Legacy Archive to illustrate the
-spatial extent of different emission detected in this paper. Here, we only use the F555W image for
-this purpose.
-We adopt the VLA 5\,GHz map of $\sim$2" resolution as the reference coordinate frame to align the optical image.
-We shifted the latter to the east by 0\farcs5963 in R.A. and +0\farcs8372 in Dec., which is consistent with the typical astrometric precision of the HST image from the Hubble
-Legacy Archive. % for Hubble Legacy Archive: abs. astronmetry 1-2" http://hla.stsci.edu/hla_faq.html
-The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas.
-We estimate the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
-be better than 0.1", leaving aside uncertainties relating to the SNR and beam size.
-
-%The astrometry of the HST images was firstly calibrated against a wider-field
-%optical image of the cluster which had in turn been aligned onto the FK5
-%coordinate system to an rms precision of ~0.2".
+We obtain HST images from the Hubble Legacy Archive with
+a goal to understand the origins of the emission detected
+in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
+resolution as the reference coordinate frame to align the optical (V-band)image
+. We shift the latter to the east by 0\farcs5963 in R.A. and +0\farcs8372 in
+Dec., which is consistent with the typical astrometric precision (1$-$2") of
+images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla_faq.
+html}. Such astrometric correction is critical to avoid artificial spatial
+offsets between emission and to carry out our lens modeling, as the absolute
+position of the foreground lensing galaxy is guided by its coordinates in the
+optical image, where its emission is clearly detected.
+The VLA image is calibrated using a well-monitored phase
+calibrator, with absolute positional accuracy of $\sim$2 mas.
+For this reason, the absolute alignment between the VLA image and other
+interferometric images reported in this paper are expected to have astrometric
+precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
+errors, and beam size.
 
@@
 \section{Discussion}
-\subsection{At what stage is the merging in RXJ1131-1231?}
+\subsection{Merger stage of RXJ1131-1231}
 
 \subsection{Implications} gas fraction at this redshift. how does that relate to
-the SFH. --> imply the change in cosmic SFD is due to change in gas content. SFE
+the SFH, this implies the change in cosmic SFD is due to change in gas content. SFE
 at this redshift, how does that relate to the SFH. probably a secondary effect
@@
 We studied a wet-wet merger between a AGN/starburst ULIRG and a optically faint companion at $z$ $\sim$ 0.65.
+In this paper, we BLAH, refining the redshift to $z_{\rm CO}$=0.65370$\pm$0.0005
 

### 2016-05-16 PdBI/src/python_mom0/makeMom0.py
make mom0 by adding slices in python instead of go moments in GILDAS, which turns an image with messed up noise distribution

@@ -1,0 +1,87 @@
+#!/usr/bin/env python
+'''
+
+look through histogram again for each channel
+
+add the channels manually to create moment-0 map, and look at historgram after
+
+since the noise properties look ok, make a FITS file using this with header from the GILDAS moment0 map (which can potentially cause trouble in the future, but run with it for now) for APLpy plot.
+
+
+Last modified: May 16 2016
+
+History:
+--------
+16 May 2016:
+    - created script, working fine
+'''
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.mlab as mlab
+import pywcs
+import pyfits
+import numpy as np
+from scipy.stats import norm
+
+
+fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/15May16/centralizedCube4GILDAS.fits")
+
+header = fits_cube[0].header
+cdelt1 = np.abs(header['CDELT1'] * 3600)       # arcsec/pix
+cdelt2 = np.abs(header['CDELT2'] * 3600)
+major_px = header['BMAJ'] * 3600 / cdelt1                 # arcsrc/pix
+minor_px = header['BMIN'] * 3600 / cdelt2
+BPA_deg = header['BPA']         # should be 13 deg
+
+# check histogram of each slice
+start_channel = 124 - 1        # python indexing from 0
+nchan = 157-124+1
+for i in range(nchan):
+    channel_number = start_channel + i
+    channel = fits_cube[0].data[0][channel_number]
+    n, bins, patches = plt.hist(channel[15:220, 15:100].flatten(), bins=100, facecolor='green', alpha=0.75, normed=True)
+    # best fit of data
+    (mu, sigma) = norm.fit(channel[15:220, 15:100])
+    # add a 'best fit' line
+    y = mlab.normpdf(bins, mu, sigma)
+    l = plt.plot(bins, y, 'r--', linewidth=2)
+    #plot
+    plt.xlabel('flux Jy per channel')
+    plt.ylabel('counts')
+    plt.title(r'$\mathrm{Histogram\ of\ offregion for chan:%i :}\ \mu=%.3f,\ \sigma=%.1f$ mJy' %(channel_number, mu, sigma*1e3))
+    plt.grid(True)
+    plt.show()
+    raw_input('')
+    plt.close()
+
+
+# add them and check histo
[…]

### 2016-05-16 PdBI/src/python_mom0/makeMom0.py
copied header info from GILDAS mom0 and patch additional info from original cube, write to new fits

@@ -16,16 +16,15 @@ History:
     - created script, working fine
 '''
 
-import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.mlab as mlab
-import pywcs
+from os.path import join
 import pyfits
 import numpy as np
 from scipy.stats import norm
 
-
-fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/15May16/centralizedCube4GILDAS.fits")
+path = '/Users/admin/Research/RXJ1131/PdBI/data/15May16/'
+fits_cube = pyfits.open(join(path, 'centralizedCube4GILDAS.fits'))
 
 header = fits_cube[0].header
 cdelt1 = np.abs(header['CDELT1'] * 3600)       # arcsec/pix
@@ -83,5 +82,20 @@ im = ax.imshow(mom0_holder, origin="lower", norm=norm, cmap=cmap)
 cont_list = [sigma * i for i in range(-6, 24, 3) if i != 0]
 ax.contour(mom0_holder, cont_list, colors='black')
 plt.show()
+
+
 # --> save this to a new fits file for APLpy plot
+# get header from GILDAS moment0 file
+
+fits_gildas_mom0 = pyfits.open(join(path, "centralizedCube4GILDAS-mom0.fits"))
+hdr = fits_gildas_mom0[0].header
+# patch up header, somehow info is missing in the GILDAS creater header
+hdr['CTYPE3'] = header['CTYPE3']
+hdr.set('RESTFREQ', header['RESTFREQ'], 'patched from original cube')
+hdr.set('VELO-LSR', header['VELO-LSR'], 'patched from original cube')
+hdr.set('VELREF', header['VELREF'], 'patched from original cube')
+hdr.set('SPECSYS', header['SPECSYS'], 'patched from original cube')
+hdr.add_comment("This Moment-0 map is created with python, but I stole the header from GILDAS the moment0 map.")
+new_mom0 = 'centralizedCube4GILDAS-python_mom0.fits'
+pyfits.writeto(join(path, new_mom0), mom0_holder, hdr)
 

### 2016-05-16 PdBI/src/python_mom0/makeMom0.py
look for range of chan that gives highest SNR, make mom0 FITS

@@ -7,12 +7,12 @@ add the channels manually to create moment-0 map, and look at historgram after
 
 since the noise properties look ok, make a FITS file using this with header from the GILDAS moment0 map (which can potentially cause trouble in the future, but run with it for now) for APLpy plot.
 
-
 Last modified: May 16 2016
 
 History:
 --------
 16 May 2016:
+    - look for ranges of channel that gives highest SNR
     - created script, working fine
 '''
 
@@ -33,57 +33,96 @@ major_px = header['BMAJ'] * 3600 / cdelt1                 # arcsrc/pix
 minor_px = header['BMIN'] * 3600 / cdelt2
 BPA_deg = header['BPA']         # should be 13 deg
 
-# check histogram of each slice
+# check histogram of each slice, offsource region
 start_channel = 124 - 1        # python indexing from 0
 nchan = 157-124+1
+_plot = False
+
 for i in range(nchan):
     channel_number = start_channel + i
     channel = fits_cube[0].data[0][channel_number]
-    n, bins, patches = plt.hist(channel[15:220, 15:100].flatten(), bins=100, facecolor='green', alpha=0.75, normed=True)
     # best fit of data
     (mu, sigma) = norm.fit(channel[15:220, 15:100])
-    # add a 'best fit' line
-    y = mlab.normpdf(bins, mu, sigma)
-    l = plt.plot(bins, y, 'r--', linewidth=2)
-    #plot
-    plt.xlabel('flux Jy per channel')
-    plt.ylabel('counts')
-    plt.title(r'$\mathrm{Histogram\ of\ offregion for chan:%i :}\ \mu=%.3f,\ \sigma=%.1f$ mJy' %(channel_number, mu, sigma*1e3))
-    plt.grid(True)
-    plt.show()
-    raw_input('')
-    plt.close()
+#     print mu, sigma
+    if _plot:
+        n, bins, patches = plt.hist(channel[15:220, 15:100].flatten(), bins=100, facecolor='green', alpha=0.75, normed=True)
+        # add a 'best fit' line
+        y = mlab.normpdf(bins, mu, sigma)
+        l = plt.plot(bins, y, 'r--', linewidth=2)
 
+        plt.xlabel('flux Jy per channel')
+        plt.ylabel('counts')
[…]

### 2016-05-16 PdBI/src/python_mom0/makeMom0.py
fix typo

@@ -139,8 +139,8 @@ new_mom0 = 'centralizedCube4GILDAS-python_ch' + str(start_chan+1) + '-' + str(en
 pyfits.writeto(join(path, new_mom0), mom0_holder, hdr)
 
 # CASA:
-importfits(fitsimage=new_mom0,imagename=new_mom0.replace('fits', '.image'))
-imstat(imagename=new_mom0.replace('fits', '.image'), region='offsource_region.crtf')
+importfits(fitsimage=new_mom0,imagename=new_mom0.replace('.fits', '.image'))
+imstat(imagename=new_mom0.replace('.fits', '.image'), region='offsource_region.crtf')
 # ---> consistent with what I got above
 
 

### 2016-05-16 PdBI/src/python_mom0/makeMom0.py
fix bug, write out new FITS using the highest SNR array

@@ -12,6 +12,7 @@ Last modified: May 16 2016
 History:
 --------
 16 May 2016:
+    - fix bug, write out new FITS using the highest SNR array
     - look for ranges of channel that gives highest SNR
     - created script, working fine
 '''
@@ -114,6 +115,7 @@ for i in range((end_chan-start_chan+1)):
     channel_number = start_chan + i
     mom0_SNR += fits_cube[0].data[0][channel_number][110:145, 110:145]
 print ("max SNR: {:.2f}").format(mom0_SNR.max()/fits_cube[0].data[0][start_chan:end_chan, 15:220, 15:100].sum(axis=0).flatten().std())
+print (" map STD {} ").format(fits_cube[0].data[0][start_chan:end_chan, 15:220, 15:100].sum(axis=0).flatten().std())
 
 fig, ax = plt.subplots()
 fig.subplots_adjust(top=0.9)
@@ -122,6 +124,8 @@ cont_list = [fits_cube[0].data[0][start_chan:end_chan, 15:220, 15:100].sum(axis=
 ax.contour(mom0_SNR, cont_list, colors='black')
 plt.show()
 
+# the full image of the highest SNR range
+final = fits_cube[0].data[0][start_chan:end_chan, :, :].sum(axis=0)
 # ------------------------------------------------------------------
 # --> save this to a new fits file for APLpy plot
 # get header from GILDAS moment0 file
@@ -136,11 +140,11 @@ hdr.set('VELREF', header['VELREF'], 'patched from original cube')
 hdr.set('SPECSYS', header['SPECSYS'], 'patched from original cube')
 hdr.add_comment("This Moment-0 map is created with python, but I stole the header from GILDAS the moment0 map.")
 new_mom0 = 'centralizedCube4GILDAS-python_ch' + str(start_chan+1) + '-' + str(end_chan) + '_mom0.fits'
-pyfits.writeto(join(path, new_mom0), mom0_holder, hdr)
+pyfits.writeto(join(path, new_mom0), final, hdr, clobber=True)
 
 # CASA:
-importfits(fitsimage=new_mom0,imagename=new_mom0.replace('.fits', '.image'))
-imstat(imagename=new_mom0.replace('.fits', '.image'), region='offsource_region.crtf')
+# importfits(fitsimage=new_mom0,imagename=new_mom0.replace('.fits', '.image'))
+# imstat(imagename=new_mom0.replace('.fits', '.image'), region='offsource_region.crtf')
 # ---> consistent with what I got above
 
 

### 2016-05-17 PdBI/src/python_mom0/makeMom0.py
mom0 multiplied by chan width

@@ -5,18 +5,28 @@ look through histogram again for each channel
 
 add the channels manually to create moment-0 map, and look at historgram after
 
-since the noise properties look ok, make a FITS file using this with header from the GILDAS moment0 map (which can potentially cause trouble in the future, but run with it for now) for APLpy plot.
+since the noise properties look ok, make a FITS file using this with header from the GILDAS moment0 map for APLpy plot. --> unfortunately can't cheat APLpy with the GILDAS header and I don't know how to edit it appropriately.. Use instead CASA to make the moment-0 map, see compare_mom0_CASA.py
 
 Last modified: May 16 2016
 
 History:
 --------
 16 May 2016:
+    - updated mom0 value to multiplied by chan width
     - fix bug, write out new FITS using the highest SNR array
     - look for ranges of channel that gives highest SNR
     - created script, working fine
+
+
+Note:
+-----
+    - useful to investigate the noise distribution per channel and if also see it in the moment-0 map, like in GILDAS
+    - useful to find the chan range with highest SNR
+    - but can't use to plot with APLpy, because header is not consistent with data
+    - altho. can use to plot with Matplotlib, but I can't figure out how to match coord. sys. with the HST image
 '''
 
+import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.mlab as mlab
 from os.path import join
@@ -24,6 +34,12 @@ import pyfits
 import numpy as np
 from scipy.stats import norm
 
+font = {'family': 'Arial Narrow',
+        'weight': 'bold',
+        'size': 18.75}
+matplotlib.rc('font', **font)
+
+specRes = 21.528154         # km/s
 path = '/Users/admin/Research/RXJ1131/PdBI/data/15May16/'
 fits_cube = pyfits.open(join(path, 'centralizedCube4GILDAS.fits'))
 
@@ -35,8 +51,8 @@ minor_px = header['BMIN'] * 3600 / cdelt2
 BPA_deg = header['BPA']         # should be 13 deg
 
 # check histogram of each slice, offsource region
[…]

### 2016-05-17 PdBI/src/python_mom0/compare_mom0_CASA.py
compare my mom0 made using makeMom0.py with CASA immoments

@@ -1,0 +1,68 @@
+'''
+
+Issue: can't plot my mom0 with APLpy...
+Compare mom0 I got from python versus using immoments from CASA to make sure the data array is fine and the issue comes from the header.
+- compare stats on source region & off source region
+
+Last Modified: 16 May 2016
+
+History:
+--------
+16 May 2016:
+    - created
+
+Note:
+-----
+    - got similar RMS off source, and flux on source between mine and from CASA
+    - CASA immoments chan=125~159 <=> GILDAS 126-160 <=> python 125-160 compare with that from makeMom0.py
+
+'''
+from os.path import join
+from os import chdir, getcwd
+
+ori_dir = getcwd()
+chdir('/Users/admin/Research/RXJ1131/PdBI/data/15May16/')
+
+# make a mom0 straight from CASA
+image = 'centralizedCube4GILDAS.image'
+rmtables('testmom0.image')
+immoments(imagename=image, moments=[0], chans='125~159', outfile='testmom0.image')
+
+# ----------------------------------------------------------
+# compare with histograms in makeMom0.py
+ia.open('testmom0.image')
+data = ia.getregion()
+ia.close()
+data.shape
+rms = np.std(data[15:220, 15:100])
+import matplotlib.pylab as plt
+import matplotlib.mlab as mlab
+from scipy.stats import norm
+n, bins, patches = plt.hist(data[15:220, 15:100].flatten(), bins=100, normed=True)
+(mu, sigma) = norm.fit(data[15:220, 15:100].flatten())
+y = mlab.normpdf(bins, mu, sigma)
+l = plt.plot(bins, y, 'r--', linewidth=2)
+print mu, sigma
+plt.show()
+# ----------------------------------------------------------
+
+new_mom0 = 'centralizedCube4GILDAS-python_ch126-160_mom0.fits'
+importfits(fitsimage=new_mom0, imagename=new_mom0.replace('.fits', '.image'))
+
+rmtables(new_mom0.replace('.fits', '.image'))
+imstat(imagename=new_mom0.replace('.fits', '.image'), region='offsource_region.crtf')
+imstat(imagename='testmom0.image', region='offsource_region.crtf')
+# --> rms and std same as above, but flux values are different.
+
+# check on source region
+imstat(imagename=new_mom0.replace('.fits', '.image'), region='Flux_CO32_20.3Jy_region.txt')
+imstat(imagename='testmom0.image', region='Flux_CO32_20.3Jy_region.txt')
[…]

### 2016-05-17 src/APLpySetup.py
update fits file for mom0, update sigma, and cosmestics

@@ -41,9 +41,9 @@ def sigma_contour_VLA(sigma):
 
 def sigma_contour_array(sigma):
     """
-    return list of sigma multiples, +/- 3*n*sigma from 1 ....10
+    return list of sigma multiples, +/- 3*n*sigma from 1 ....14
     """
-    arr = np.arange(11) * 3
+    arr = np.arange(15) * 3
     arr = arr[1:] * sigma
     Narr = -1 * arr
     arrE = np.hstack((Narr, arr))
@@ -131,7 +131,7 @@ def setup_beam2(sp, major, minor, angle, idx, loc='top right', c='black', hatch=
     sp.beam[idx].set_frame(True)
 
 
-def markers_cross(sp, ra, dec, layer=None, ec='yellow', fc='none', mk='+', s=500, a=1.0, lw=2, zorder=50):
+def markers_cross(sp, ra, dec, layer=None, ec='yellow', fc='none', mk='+', s=500, a=1.0, lw=1.2, zorder=50):
     """
     Inputs:
     -------

### 2016-05-17 src/singlePanelmom0.py

@@ -6,13 +6,19 @@ Plot mom0 of all channels overlay on HST (single panel)
 Author: Daisy Leung
 
 
-Last edited: 01 Jan 2016
+Last edited: 16 May 2016
 
 
 History:
 --------
-01 Jan 2016: update marker
-31 Dec 2015: use the linear shifted HST F555W image
+16 May 2016:
+    - update font
+    - replace mom0 wiith centralizedCube4GILDAS-CASA_ch126-160_mom0.fits from 15May16/
+    - update sigma
+01 Jan 2016:
+    - update marker
+31 Dec 2015:
+    - use the linear shifted HST F555W image
 
 Note:
 -----
@@ -31,36 +37,48 @@ from APLpySetup import *
 path = '../HST/'
 Plotpath = '../Figures/'
 
+font = {'family': 'Arial Narrow',
+        'weight': 'normal',
+        'size': 12.5}
+xtick = {'major.size': 10,
+         'minor.size': 6}
+ytick = {'major.size': 10,
+         'minor.size': 6}
+mpl.rc('font', **font)
+mpl.rc('xtick', **xtick)
+
 label = dict.fromkeys(['F555W_drzcroplinearShift'])
 for k in label.iterkeys():
     files = glob.glob(path + '*' + k + '*.fits')
     label[k] = files
 # print label
 
-label_pdbi = dict.fromkeys(['mom0'])
-path_pdbi = '../PdBI/data/14Oct15/'
+label_pdbi = dict.fromkeys(['CASA_ch126-160'])
+#
+path_pdbi = '../PdBI/data/15May16/'
 
 for k in label_pdbi.iterkeys():
-    file_pdBI = glob.glob(path_pdbi + '*' + k + '.fits')
+    file_pdBI = glob.glob(path_pdbi + '*' + k + '*.fits')
     label_pdbi[k] = file_pdBI
 
-figC = plt.figure(1, figsize=(7, 7))
+figC = plt.figure(1, figsize=(8, 8))
+figC.subplots_adjust(top=0.9, left=0.05, right=0.95)
 figC.clf()
 ########################################
 # user define area
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.0025
+sizep = 0.00225
 
 ra_cross, dec_cross = ra_center, dec_center
-row_a = 0.10
+row_a = 0.1
[…]

### 2016-05-17 src/RedBlue.py
used red & blue chan range from 126-160, conssitent with mom0 map

@@ -1,19 +1,26 @@
 """
 Author: Daisy Leung
 
-Last edited: 03 May 2016
+Last edited: 17 May 2016
 
 Purpose:
     Plot Red wing and Blue wing different color overlay on HST
-    channels: blue: [150, 142]; velocity [-423.79, -251.39]
-              red: [142, 134]; velocity [-251.39, -90.22]
+    channels: 126-144 (Red), 144-160 (Blue)
 
 
 History:
-03 May 2016: change label color from yellow to black, since we inverted HST image, else can't read them
-30 April 2016: Change contour colors, inverted color for HST, change HST contrast based on ds9
-01 Jan 2016: update marker
-31 Dec 2015: Use linear shifted F555W image
+17 May 2016:
+    - update to use integrated maps from 17May16/, channel range consistent with mom0 map
+    - update sigma
+    - cosmetics
+03 May 2016:
+    - change label color from yellow to black, since we inverted HST image, else can't read them
+30 April 2016:
+    - Change contour colors, inverted color for HST, change HST contrast based on ds9
+01 Jan 2016:
+    - update marker
+31 Dec 2015:
+    - Use linear shifted F555W image
 
 """
 
@@ -27,6 +34,16 @@ from APLpySetup import *
 path = '../HST/'
 Plotpath = '../Figures/'
 
+font = {'family': 'Arial Narrow',
+        'weight': 'normal',
+        'size': 12.5}
+xtick = {'major.size': 10,
+         'minor.size': 6}
+ytick = {'major.size': 10,
+         'minor.size': 6}
+mpl.rc('font', **font)
+mpl.rc('xtick', **xtick)
+
 label = dict.fromkeys(['F555W_drzcroplinearShift'])
 for k in label.iterkeys():
     files = glob.glob(path + '*' + k + '*.fits')
@@ -34,14 +51,16 @@ for k in label.iterkeys():
 # print label
 
 label_pdbi = dict.fromkeys(['red', 'blue'])
-path_pdbi = '../PdBI/data/5Nov15/'    # copied from 14Oct15
+path_pdbi = '../PdBI/data/17May16/'
 
 for k in label_pdbi.iterkeys():
-    file_pdBI = glob.glob(path_pdbi + '*' + k + '.fits')
+    file_pdBI = glob.glob(path_pdbi + '*' + k + '*.fits')
     label_pdbi[k] = file_pdBI
 # print label_pdbi
 
 figC = plt.figure(1, figsize=(7, 7))
[…]

### 2016-05-17 src/singlePanelmom0.py

@@ -6,11 +6,13 @@ Plot mom0 of all channels overlay on HST (single panel)
 Author: Daisy Leung
 
 
-Last edited: 16 May 2016
+Last edited: 17 May 2016
 
 
 History:
 --------
+17 May 2016:
+    - pythonic
 16 May 2016:
     - update font
     - replace mom0 wiith centralizedCube4GILDAS-CASA_ch126-160_mom0.fits from 15May16/
@@ -140,7 +142,7 @@ if __name__ == '__main__':
         errmsg = "Invalid number of arguments: {0:d}\n  run script.py Save_True"
         raise IndexError(errmsg.format(len(sys.argv)))
     saveFig = True if sys.argv[1].lower() == 'true' else False
-    if saveFig == True:
+    if saveFig:
         outname = 'F555WCO21_mom0_single.eps'
         if inverted_HSTleft: outname = outname.replace('.eps', '.invertedgray.eps')
         figC.savefig(Plotpath + outname, dpi=600, box_inches='tight')

### 2016-05-17 WRITEUP/ms.tex
done with CO21 measurement result section

@@
-% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry
+% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results
 %
@@
 %
-
 \documentclass[]{emulateapj}
@@
 
-\title{Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654}
+\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654}
 \author{T. K. Daisy Leung and Dominik A. Riechers}
@@
 an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
-21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on
--source time after discarding unusable visibility data.
+21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
+ time after discarding unusable visibility data.
 The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
@@
 which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
-weighting.
-This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
-The final rms noise is $\sigma$ = 0.177 Jy \kms beam\pmOne over a channel width of 320 MHz (690 \kms), and $\sigma$ = 1.451 mJy \kms
+weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
+The final rms noise is $\sigma$ = 1.451 mJy \kms
 beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$
@@
 each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
-line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273 (
-second track) were observed
+line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
+(second track) were observed
 every 15 minutes for pointing, amplitude, and phase calibration. Mars was
@@
 % poor phase note
+% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
+%
 % calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
@@
 gain variation over time, and the phase scatter on the calibrated data. We
-therefore treat its line intensity and refrain using it to derive other physical quantities.
+therefore treat its line intensity with caution and refrain using it to derive other physical quantities.
 
@@
 Observations were carried out on 2008 December 29 under excellent weather
-conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C-Band receivers were used with a continuum mode setup,
+conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
 providing a bandwidth of 50 MHz in each sideband.
@@
 in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
-resolution as the reference coordinate frame to align the optical (V-band)image
-. We shift the latter to the east by 0\farcs5963 in R.A. and +0\farcs8372 in
+resolution as the reference coordinate frame to align the optical (V$-$band) image.
+We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
 Dec., which is consistent with the typical astrometric precision (1$-$2") of
-images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla_faq.
+images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
 html}. Such astrometric correction is critical to avoid artificial spatial
-offsets between emission and to carry out our lens modeling, as the absolute
-position of the foreground lensing galaxy is guided by its coordinates in the
-optical image, where its emission is clearly detected.
+offsets between different emitting regions and to carry out our lens modeling,
+in which the absolute position of the foreground lensing galaxy is guided by its
+coordinates in the optical image, where its emission is clearly detected.
 The VLA image is calibrated using a well-monitored phase
@@
 \section{Results}
-\subsection{\bco}
-\subsection{\cco}
+\subsection{\bco emission} %DONE
+We dynamically resolved the \bco line emission toward the background galaxies
+at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
+0.65370 $\pm$ 0.0005. A highly asymmetric double-horned line profile is
+detected as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
+flux densities of 75.3$\pm$2.6 and 24.0$\pm$2.0 mJy, and a FWHM of
+179$\pm$9 \kms and 255$\pm$28 \kms, respectively. The peaks are separated by
+$\Delta v_{\rm sep}$ = 220 \kms. The integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/
+
+\begin{figure}[tbph]
+\centering
+\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
+\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
+is with respect to $z$=0.6537, which is approximately the line center
+considering the asymmetry is as a result of differential lensing.
+A more detailed discussion of differential lensing effect is presented in
+\Sect{differential} and the magnification factors for various kinematic
+components are listed in \Tab{mag}.
+ \label{fig:CO21spec}}
+\end{figure}
+
+% moment 0 map: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
+% - sigma = 0.305 Jy km/s/Beam
+%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
+We construct the zeroth, first and second moment maps shown in \Fig{CO21mom}
+using the $uv$-continuum subtracted data cube, over $\Delta v$$\sim$750 \kms.
+The first and second moment maps are clipped at 3$\sigma$.
+The peak flux density is 8.12 $\pm$ 0.30 Jy\,\kms\,beam\pmOne in the intensity-
+integrated map. The deconvolved source size is estimated to be 5\farc1$\pm$0\farc72 $\times$ 3\farcs72$\pm$0\farcs66 and thus the emission is resolved over
+$\sim$2.2 beams. While the lensed emission is not strictly distributed as 2D-
+Gaussian, the fit recovers the line intensity enclosed within the emitting
+region, we therefore take this as an estimate on the extent of the lensed
+emission. On the other hand, if we assume the spatial distribution of
+the lensed molecular gas emission is similar to that in the optical to \nir
+wavelengths, the lensed emission would be more accurately described by an
+annulus, including the partially complete ``Einstein Ring" and
+the lensed knots (see \Fig{CO21mom)}.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
+\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
+\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
+\caption{
+An overlay of the velocity-integrated \bco emission on the HST V$-$band (F555W)
+image. The contours start at 3$\sigma$ and increment at steps of
+$\pm$3$\sigma$, where $\sigma$=0.3 mJy beam\pmOne. The cross denotes the
+location of the foreground galaxy at $z$=0.295. {\it Right: } The contours
+are color coded to represent the red and blue wings of the emission.
+\label{fig:CO21mom}}
+\end{figure}
+
+The emission of the red component coincides with the Einstein Ring seen in the
+optical image, with most of its apparent flux originating from the lensed arc
+in the Southeast, whereas the blue component is predominately coming from
+solely the lensed arc shown in \Fig{CO21mom}. To illustrate this, we show the
+channel maps of 21.5\,\kms width and spatial spectra of 1\farcs5 resolution in
+\Fig{chanmap} and \Fig{spatial}, respectively. The figures show that emission
+is present to the West and peaks toward the lensing arc (black across in \Fig{
+chanmap}) in the red wing, and shifts to the East with decreasing velocity (
+blue wing). This indicates extended emission in the source plane, where
+emission from different kinematic components is separated by different amounts
+relative to the caustics. One consequence of such is the observed asymmetric
+line profile. A detailed analysis on differential lensing of \bco is presented in \Sec{differential}.
+
+\begin{figure*}[!htbp]
+\centering
+\includegraphics[width=0.9\textwidth]{../Figures/co_channel_maps.eps}
+\caption{
+Channel maps of \pdbi \bco toward RXJ1131 in 21.5\,\kms resolution. The
+Black crosses indicate the position of the lensed knots (AGN emission,
+which are components ABCD in C06). The central white-filled
+star indicates the position of the foreground lensing galaxy (component G
+in C06), as detected in the HST image. Contours start and increment at steps of
+$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
+\end{figure*}
+
+\begin{figure*}[!htbp]
+\centering
+\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
+\caption{
+\bco spectrum as a function of position, binned by 3 pixels in each
+direction (1\farcs5). The spectra map covers an extent of $\sim$10"$\times$10"
+centering on the pixel that corresponds to the lensing galaxy. The velocity
+and flux density scales are denoted in the top right panel.
+BLAH: DR would want the pixel coordinates replaced by arcsec offset from
+center. \label{fig:spatialSpec}}
+\end{figure*}
+
+We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted
+frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.
+451mJy per channel beam\pmOne.
+Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$
+limit of 4.353 mJy \kms beam\pmOne.
+
+\susbsection{Origin of the \bco emission} \label{sec:origin}
+
+gas:
+CO is from the optical QSO, because co-spatial with the lensed optical emission, but also emisson from the companion.
+We adopt the ULIRG value, as used in the largest samples of non-local ULIRGs (solomon+97, Combes+11).
+We classify this as wet-wet merger given a contribution of CO from the companion.
+However, we cannot quantify this with a mass ratio given the spatial resolution.
+This will be verified in further higher-resolution observations.
+
+\subsection{\bco kinematics}
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
+\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
+\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
+\caption{
+Contours for the first (left) and second (right) moment maps are shown in steps of 50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
+\label{fig:CO21highO}}
+\end{figure}
+
+A clear velocity gradient
+
+An unusually high velocity dispersion ($\gtrsim$400\kms) is seen in the
+central region in \Fig{CO21highO}. While beam smearing is inevitably the
+dominant factor giving rise to the observed velocity dispersion
+at current spatial resolution, the exceedingly high velocity dispersion hints
+at potential perturbations from the AGN, or internal turbulence due to
+interactions with the companion, and/or instability due to the huge gas
+reservoir.
+
+Given the 1st moment map and the observed velocity gradient across the source plane in our model \Fig{model}, this is indicative of a kinematically ordered galaxy, but its emission has been lensed differentially.
+
+and velocity dispersion are suggestive of a kinematically ordered disk at the current resolution limit.
+The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.
+
+We will defer the discussion of such features and the implications to
+\Sec{dynamics}, where we analyze the dynamics of the system.
+
+\subsection{\cco emission}
 \subsection{Interferometric Continuum}
 2mm: resolved along the major axis, but unresolved along the minor axis. We decomposed the continuum from the foreground and background sources by subtracting a point
-source model in the uv-plane (see Riechers+13 SMMJ04135 description)
+source model in the $uv-$plane (see Riechers+13 SMMJ04135 description)
 
-\subsection{Photometry from archive}
-We obtain archival and published photometry.
-2MASS magnitudes from the 2MASS All-Sky
-Catalog of Point SourcesBLAH  (Skrutskie et al. 2006), WISE magnitudes
-from the AllWISE Source CatalogBLAH, Spitzer/MIPS
+\subsection{Photometry}
+We compiled/web-scraped the \mir to \fir photometry
+from 2MASS, WISE, IRAS, IRAC catalogs .
+to characterize
+the dust emission in RXJ1131 from
+from the 2MASS All-Sky Catalog of Point Sources  (Skrutskie et al. 2006), WISE
+magnitudes from the AllWISE Source CatalogBLAH, Spitzer/MIPS
 data from BLAH Catalog, IRAS photometry from the IRAS point source
@@
 
-The Herschel/SPIRE data are from the Herschel Science Archive, processed
-by the SPIRE HIPE pipeline version 12BLAH (Ott 2010). The
-photometry was extracted at the source position using the
-SUSSEXTractor task within HIPE (Savage \& Oliver 2007,
-Smith et al 2012, Pearson et al 2014). The SUSSEXtractor
+We extract the Herschel/SPIRE photometry using SUSSEXTractor
+within HIPE (Savage \& Oliver 2007, Smith et al 2012, Pearson et al 2014)
+over the data obtained from the Herschel Science Archive, which were
+processed by the SPIRE HIPE pipeline version 12BLAH (Ott 2010).
+The SUSSEXtractor
 task estimates the flux density from an image smoothed with
@@
 
-We list the mid-IR to FIR photometries compiled from 2MASS, WISE,IRAS, IRAC catalogs in \Tab{photometry}.
+We list the photometry from optical to radio in \Tab{photometry}.
 \input{table_photometry_AAScustomized}
+
 %--------------------------------------------------------------------------
@@
 Make this bigger in the future
-\label{fig:}}
+Channel maps of the CO emission (red) overlaid on our best-fit lens models (grayscale).
+The foreground lensing galaxy is represented by a black dot.
+The reconstructed source morphology (magenta ellipses) is also suggestive of a “disk”.
+\label{fig:model}}
 \end{figure*}
 
-\subsubsection{Differential Lensing}
+\subsubsection{Differential Lensing} \label{sec:differential}
 Lens modeling of this source from previous studies find non-negligible differential lensing effect across H-Band, V-band, and I-band. The magnification factor ranges from 10.9
 to 7.8, where the decrease is caused
-by the more extended IR emission (hence SF), well beyond the caustic (C06).
+by the more extended IR emission (hence \SF), well beyond the caustic (C06).
 
@@
 flux density in the red wing is apparently much higher than in the blue wing, given its lensing configuration.
-By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in Table \ref{tab:}.
+By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in \Tab{mag}.
 \input{table_magFactor}
 
-\subsection{\bco Dynamical modeling}
+\subsection{\bco Dynamical modeling} \label{sec:dynamics}
 Based on the the source plane position of each kinematic components from the
@@
 \begin{equation}
-V = V_0 + \frac{2}{\pi} V_a arctan(\frac{R}{R_t}),
+V = V_0 + \frac{2}{\pi} V_{\rm a} \arctan(\frac{R}{R_{\rm t}}),
 \end{equation}
-where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center, $V_a$ is the asymptotic velocity, and $R_t$ is the ``turnover'' radius at which the rotation curve
+where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center, $V_{\rm a}$ is the asymptotic velocity, and $R_{\rm t}$ is the ``turnover'' radius at which the rotation curve
 becomes flat. We perform non-linear least square fitting using an orthogonal distance regression to find the best-fit $V_a$, $r_t$, $V_0$, taking into account
-errors in both velocity and distance offset (see Figure \ref{fig:PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
+errors in both velocity and distance offset (see \Figure{PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
 parameter physical. We then estimate the uncertainties associated with best-fit parameters using a Monte Carlo simulation of 500 iterations, perturbing
-the velocity and physical separation according to a random Gaussian distribution of width based on the input uncertainties on
+the velocity and physical separation according to a random Gaussian distribution of width/sigma based on the input uncertainties on
 the data. Using this model, we find $V_a$ = 975$\pm$387, $r_t$ = 10.6$\pm$5.7,
@@
 as peak velocity dispersion at the center of a galaxy and a ``spider'' diagram are needed. Based on the reconstructed source plane in the optical/NIR emission, C06 find that a
-n=1 Sersic profile is best
+n=1 Sersic profile is best fit their model or is it the reconstructed emission (TBD).
 
-The frequently used Vmax (maximum measured velocity) is not equivalent to the
+The frequently used V$_{\rm max}$ (maximum measured velocity) is not equivalent to the
 asymptotic value, Va, a mathematical extrapolation and typically not reached in
@@
 remaining analysis, we adopt the asymptotic limit as a proxy to the rotation
-curve. We also note that typical studies of the Tully-Fisher relation uses V_2.2
-(2.2 * disc scalelength ~ 1.375 half-light radius ~ 0.7R_opt) as the rotation
+curve. We also note that typical studies of the Tully-Fisher relation uses V$_2.2$ (at 2.2 $\times$ disc scalelength $\sim$ 1.375 half-light radius $\sim$ 0.7R$_opt$) as the rotation
 velocity since this would be the radius at which the velocity of a pure
 exponential disc peaks at. However, our source appears to be a disturbed
-rotator, albeit coarse resolution. Hence, rather than adopting V_2.2, we use the
+rotator, albeit coarse resolution. Hence, rather than adopting V$_2.2$, we use the
 asymptotic value from the best-fit arctangent model. The half light radius in the
@@
 
-\subsection{Implications} gas fraction at this redshift. how does that relate to
-the SFH, this implies the change in cosmic SFD is due to change in gas content. SFE
-at this redshift, how does that relate to the SFH. probably a secondary effect
-to the drop in SFH
+\subsection{Implications}
+gas fraction at this redshift. how does that relate to
+the SFH, and the change in cosmic SFD is due to change in gas content.
+SFE at this redshift, how does that relate to the SFH. probably a secondary effect to the drop in SFH
 
@@
 We studied a wet-wet merger between a AGN/starburst ULIRG and a optically faint companion at $z$ $\sim$ 0.65.
-In this paper, we BLAH, refining the redshift to $z_{\rm CO}$=0.65370$\pm$0.0005
+In this paper, we BLAH, refining the redshift to $z_{\rm CO}$=0.65370$\pm$0.0005.
 

### 2016-05-17 WRITEUP/ms.tex
done writing origin of CO21, and claim is wet-wet merger

@@
-% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results
+% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results, origin of \bco
 %
@@
 We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted
-frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.
-451mJy per channel beam\pmOne.
+frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of
+$\sigma$ = 1.451mJy per channel beam\pmOne.
 Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$
@@
 
-\susbsection{Origin of the \bco emission} \label{sec:origin}
-
-gas:
-CO is from the optical QSO, because co-spatial with the lensed optical emission, but also emisson from the companion.
-We adopt the ULIRG value, as used in the largest samples of non-local ULIRGs (solomon+97, Combes+11).
-We classify this as wet-wet merger given a contribution of CO from the companion.
-However, we cannot quantify this with a mass ratio given the spatial resolution.
-This will be verified in further higher-resolution observations.
+\susbsection{Origin of the \bco emission} \label{sec:origin} %DONE
+Evidently, the CO emission is co-spatial with the lensed optical emission in
+the background AGN host galaxy. The question is then whether the optically
+faint companion also contributes to the CO flux and thus contains a
+non-negligible amount of molecular gas.
+Indeed, based on our lens model presented in \Sec{lensmodel}, we find it
+highly likely that part of the CO emission originates from
+the companion. We thus classify RXJ1131 as a ``wet-wet'' merger.
+However, we cannot quantify this with a mass ratio given the
+spatial resolution. This will be verified in future higher-resolution observations. In the subsequent sections, we will interpret RXJ1131
+using this scenario (i.e. a ``wet-wet'' merger).
 
 \subsection{\bco kinematics}
-
 \begin{figure}[!htbp]
@@
 \section{Analysis}
-\subsection{Lens modeling}
+\subsection{Lens modeling} \label{lensmodel}
 With the high SNR and spectral resolution, we model different kinematic components using our lensing code \uvmcmcfit.

### 2016-05-17 WRITEUP/ms.tex
done with CO21 high-order moments section

@@
 
-\subsection{\bco kinematics}
+\subsection{\bco kinematics} % DONE
+A clear velocity gradient and an unusually high
+velocity dispersion ($\gtrsim$400\kms) near the central region
+is seen in \Fig{CO21highO}. While beam smearing is inevitably the
+dominant factor in the observed velocity dispersion
+at the spatial resolution of this data, the exceedingly
+high velocity dispersion hints
+at potential perturbations from the AGN, or internal turbulence due to
+interactions with the companion, and/or instability due to the large gas
+content. A velocity gradient across the source plane in \Fig{model} is also
+found in our lens model. This further supports the idea of a kinematically-
+ordered galaxy, but its emission has been lensed differentially.
+In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
+bright quasar and is in the process of merging.
+We will defer the discussion of the implications to \Sec{dynamics},
+where we analyze the dynamics of the system in the source plane.
+
 \begin{figure}[!htbp]
@@
 \end{figure}
-
-A clear velocity gradient
-
-An unusually high velocity dispersion ($\gtrsim$400\kms) is seen in the
-central region in \Fig{CO21highO}. While beam smearing is inevitably the
-dominant factor giving rise to the observed velocity dispersion
-at current spatial resolution, the exceedingly high velocity dispersion hints
-at potential perturbations from the AGN, or internal turbulence due to
-interactions with the companion, and/or instability due to the huge gas
-reservoir.
-
-Given the 1st moment map and the observed velocity gradient across the source plane in our model \Fig{model}, this is indicative of a kinematically ordered galaxy, but its emission has been lensed differentially.
-
-and velocity dispersion are suggestive of a kinematically ordered disk at the current resolution limit.
-The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.
-
-We will defer the discussion of such features and the implications to
-\Sec{dynamics}, where we analyze the dynamics of the system.
 
@@
 \subsection{Lens modeling} \label{lensmodel}
+The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.
+
 With the high SNR and spectral resolution, we model different kinematic components using our lensing code \uvmcmcfit.

### 2016-05-17 WRITEUP/ms.tex
Co32 emission section done

@@
-% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results, origin of \bco
+% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results, origin of co21, co32 emission
 %
@@
 \section{Results}
-\subsection{\bco emission} %DONE
+\subsection{\bco Emission} %DONE
 We dynamically resolved the \bco line emission toward the background galaxies
@@
 
-\subsection{\bco kinematics} % DONE
+\subsection{\bco Kinematics} % DONE
 A clear velocity gradient and an unusually high
@@
 
-\subsection{\cco emission}
+\subsection{\cco Emission} % done
+We detect resolved \cco line emission toward RXJ1131. The spectrum is shown in
+\Fig{co32spec}, which seems to have a double-peak profile.
+This is expected if RXJ1131 is truly a disk galaxy (see previous
+sections). The high phase noise in the calibration leads to a low SNR
+detection. We thus estimate the line intensity to be
+35.7$\pm$ 21.9 Jy\,\kms by summing up fluxes over the
+linewidth used to infer \bco line intensity ($\sim$700 \kms).
+
+\begin{figure}[!Htbp]
+\centering
+\includegraphics[width=0.5\textwidth]{../Figures/coOverlay.eps}
+\caption{
+\carma \cco line profile (solid) without continuum subtraction is
+over-plotted on the continuum-subtracted \bco line profile (dashed).
+The velocity scale is with respect to $z$=0.6537, which corresponds to the dynamical center of the \bco line. The spectral resolution for \cco and \bco is 35.8 \kms and 21.5 \kms, respectively.
+ \label{fig:co32spec}}
+\end{figure}
+
 \subsection{Interferometric Continuum}
+
+At the position of \cco, continuum emission is not detected in
+the line-free channels down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
+This is consistent with the spectrum shown in \Fig{co32spec}.
+The continuum is buried within the sensitivity limit of this data.
+% (consistent with the Gaussian + poly fit to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
+% line free channels:1, 118, 160, 600
+% nchan =(117+600-160+1) = 558
+% sigma =  0.83 mJy/B
+
 2mm: resolved along the major axis, but unresolved along the minor axis. We decomposed the continuum from the foreground and background sources by subtracting a point

### 2016-05-17 WRITEUP/ms.tex
add R32 to CO32 section

@@
 over-plotted on the continuum-subtracted \bco line profile (dashed).
-The velocity scale is with respect to $z$=0.6537, which corresponds to the dynamical center of the \bco line. The spectral resolution for \cco and \bco is 35.8 \kms and 21.5 \kms, respectively.
+The velocity scale is with respect to $z$=0.6537, which corresponds to the
+dynamical center of the \bco line. The spectral resolution for \cco and \bco
+is 35.8 \kms and 21.5 \kms, respectively.
  \label{fig:co32spec}}
@@
 
+Assuming the spatial extents between \bco and \cco are similar and therefore
+a negligible differential lensing effect, the line intensities
+correspond to a brightness temperature ratio of
+$r_{\rm 32}$\,=\,T$_{\tiny \cco}$/T$_{\tiny \bco}$\,=\,0.66$\pm$0.41.
+The high uncertainty is dominated by the uncertainties in the \cco line
+intensity.
+
 \subsection{Interferometric Continuum}
 
-At the position of \cco, continuum emission is not detected in
-the line-free channels down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
+No continuum emission is detected at the position of \cco
+down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
 This is consistent with the spectrum shown in \Fig{co32spec}.
-The continuum is buried within the sensitivity limit of this data.
 % (consistent with the Gaussian + poly fit to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
@@
 
-2mm: resolved along the major axis, but unresolved along the minor axis. We decomposed the continuum from the foreground and background sources by subtracting a point
-source model in the $uv-$plane (see Riechers+13 SMMJ04135 description)
+We detect \pdbi 2\,mm continuum in \Fig{2mm}. The integrated flux density is
+1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
+centered on the lensing galaxy. A slightly extended emission is seen
+also along the lensed arc. This suggests that the detected emission is
+toward both the foreground galaxy and the background galaxy and that the
+emission is marginally resolved along its major axis.
+
+We subtract a point source model in $uv$-plane to remove the unresolved
+emission toward the foreground galaxy. The peak flux (0.389$\pm$0.082 mJy)
+in the residual coincides with the lensed arc, and is also consistent with
+the difference between the integrated and the peak flux
+in the original continuum map ($\sim$0.4 mJy). We therefore adopt this as
+emission toward the background galaxy.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
+\caption{
+An overlay of the 2\,mm continuum emission on the optical image. Contours start at ...
+\label{fig:2mm}}
+\end{figure}
 

### 2016-05-17 src/plotCont.py
add beam to HST-2mm Cont plot

@@ -1,12 +1,14 @@
 """
 Author: Daisy Leung
 
-Last edited: 01 Jan 2016
+Last edited: 17 May 2016
 
 Purpose:
 - Overlay 2mm Cont contour on HST
 
 History:
+May 17 2016:
+    add beam
 Jan 01 2016:
     update marker
 Dec 31 2015:
@@ -28,6 +30,16 @@ from APLpySetup import *
 path = '../HST/'
 Plotpath = '../Figures/'
 
+font = {'family': 'Arial Narrow',
+        'weight': 'normal',
+        'size': 12.5}
+xtick = {'major.size': 10,
+         'minor.size': 6}
+ytick = {'major.size': 10,
+         'minor.size': 6}
+mpl.rc('font', **font)
+mpl.rc('xtick', **xtick)
+
 label = dict.fromkeys(['F555W_drzcroplinearShift'])
 for k in label.iterkeys():
     files = glob.glob(path + '*' + k + '*.fits')
@@ -43,21 +55,22 @@ for k in label_pdbi.iterkeys():
 # print label_pdbi
 
 figC = plt.figure(1, figsize=(7, 7))
+figC.subplots_adjust(top=0.9, left=0.1, right=0.95)
 # figRed = plt.figure(2, figsize=(12, 7))
 ########################################
 # user define area
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.00258066
+sizep = 0.002258066
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.10
 width = 0.35
-full_width = 0.8
+full_width = 0.7
 x_gap = 0.05
-x0 = 0.15
-dy = 0.90
+x0 = 0.2
+dy = 0.85
 sigma = 0.085e-3     # theoretical: 0.0816E-03; off-region in map: 0.0888e-3
 
 ########################################
@@ -71,7 +84,7 @@ sigma = 0.085e-3     # theoretical: 0.0816E-03; off-region in map: 0.0888e-3
 
 fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
         figure=figC, subplot=[x0,row_a,full_width,dy])
-fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=151, vmid=-0.025)
+fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=125, vmid=-0.025)
 #figO = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
[…]

### 2016-05-17 src/HSTVLA.py
add beam, cosmetics

@@ -1,12 +1,15 @@
 """
 Author: Daisy Leung
 
-Last edited: 01 Jan 2016
+Last edited: 17 May 2016
 
 Purpose:
 - Plot single panel 5GHz VLA continuum on HST F555W, investigate continuum offset
 
 History:
+May 17 2016:
+    - update cosmetics
+    - add beam
 Jan 01 2016:
     - update marker
 Dec 31 2015:
@@ -27,6 +30,16 @@ from APLpySetup import *
 path = '../HST/'
 Plotpath = '../Figures/'
 
+font = {'family': 'Arial Narrow',
+        'weight': 'normal',
+        'size': 11.5}
+xtick = {'major.size': 10,
+         'minor.size': 6}
+ytick = {'major.size': 10,
+         'minor.size': 6}
+mpl.rc('font', **font)
+mpl.rc('xtick', **xtick)
+
 label = dict.fromkeys(['F555W_drzcroplinearShift'])
 for k in label.iterkeys():
     files = glob.glob(path + '*' + k + '*fits')
@@ -41,6 +54,7 @@ for k in label_vla.iterkeys():
 # print label_vla
 
 figC = plt.figure(1, figsize=(7, 7))
+figC.subplots_adjust(top=0.9, left=0.1, right=0.95)
 # figRed = plt.figure(2, figsize=(12, 7))
 ########################################
 # user define area
@@ -52,10 +66,10 @@ sizep = 0.002
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.10
 width = 0.35
-full_width = 0.8
+full_width = 0.7
 x_gap = 0.05
-x0 = 0.15
-dy = 0.90
+x0 = 0.2
+dy = 0.85
 sigma = 1.3e-5
 
 ########################################
@@ -69,7 +83,7 @@ sigma = 1.3e-5
 
 fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
         figure=figC, subplot=[x0,row_a,full_width,dy])
-fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=151, vmid=-0.025)
+fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=121, vmid=-0.025)
 #figO = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
 #        figure=figC, subplot=[x0+width+2*x_gap, row_a, width, dy])
[…]

### 2016-05-17 src/plotCont.py

@@ -32,7 +32,7 @@ Plotpath = '../Figures/'
 
 font = {'family': 'Arial Narrow',
         'weight': 'normal',
-        'size': 12.5}
+        'size': 11.5}
 xtick = {'major.size': 10,
          'minor.size': 6}
 ytick = {'major.size': 10,

### 2016-05-17 src/SED/tablePhotometry.py
updated PdBI 2mm peak uncertainty

@@ -7,10 +7,12 @@ wavelength [um], freq [GHz], flux density [mJy], flux_err [mJy], instrument
 Save table as latex file
 
 
-Last Modified: May 10 2016
+Last Modified: May 17 2016
 
 History
 -------
+May 17 2016:
+    updated error on PdBI peak
 May 10 2016:
     add decomposed IRAC points, and the missing 3.6 um point
     add PdBI residual point, error corresponds to without adding that from flux cal.
@@ -119,7 +121,7 @@ data_VLA = [((4.8815*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
 data_PdBI = [((139.256*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
               139.256, 1.23, 0.22, 'PdBI-integrated'),
              ((139.256*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
-              139.256, 0.799, 1.3e-2, 'PdBI-peak'),
+              139.256, 0.799, 0.0816, 'PdBI-peak'),
              ((139.256*u.GHz).to(u.micron, equivalencies=u.spectral()).value,
               139.256,  0.4, 0.0816, 'PdBI-removedFG')  #  err incl. flux cal., used in SED fitting = 0.1976
             ]

### 2016-05-17 WRITEUP/ms.tex
done interferometric cont

@@
-% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results, origin of co21, co32 emission
-%
-%
-%
-%
-%
 \documentclass[]{emulateapj}
@@
 were carried out under the D array configurations of the \carma (CARMA;
-Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 3\,mm
-weather conditions and on 2014 February 17 under good 3\,mm
+Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 1.5\,mm
+weather conditions and on 2014 February 17 under good 1.5\,mm
 weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
@@
 image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
-over a channel width of 25 MHz.
+over a channel width of 25 MHz. An rms noise of
+$\sigma$ = 0.831 mJy beam\pmOne is reached by averaging over the
+line-free channels.
 
@@
 
-\subsection{\cco Emission} % done
+\subsection{\cco Emission} % DONE
 We detect resolved \cco line emission toward RXJ1131. The spectrum is shown in
@@
 
-\subsection{Interferometric Continuum}
-
-No continuum emission is detected at the position of \cco
+\subsection{Interferometric Continuum} %DONE
+No 1.5\,mm continuum emission is detected at the position of \cco
 down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
 This is consistent with the spectrum shown in \Fig{co32spec}.
-% (consistent with the Gaussian + poly fit to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
-% line free channels:1, 118, 160, 600
-% nchan =(117+600-160+1) = 558
-% sigma =  0.83 mJy/B
 
-We detect \pdbi 2\,mm continuum in \Fig{2mm}. The integrated flux density is
+We detect PdBI 2\,mm continuum in \Fig{2mm}. The integrated flux density is
 1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
-centered on the lensing galaxy. A slightly extended emission is seen
-also along the lensed arc. This suggests that the detected emission is
-toward both the foreground galaxy and the background galaxy and that the
+centering on the lensing galaxy. A slightly extended emission is also seen
+along the lensed arc. This suggests that the detected emission comes from
+both the foreground galaxy and the background galaxy and that the
 emission is marginally resolved along its major axis.
-
 We subtract a point source model in $uv$-plane to remove the unresolved
 emission toward the foreground galaxy. The peak flux (0.389$\pm$0.082 mJy)
-in the residual coincides with the lensed arc, and is also consistent with
-the difference between the integrated and the peak flux
-in the original continuum map ($\sim$0.4 mJy). We therefore adopt this as
-emission toward the background galaxy.
+in the residual map coincides with the lensed arc, and is consistent with
+the difference between the integrated and the peak flux in the
+original continuum map ($\sim$0.4 mJy). We therefore adopt
+$S_\nu$ = 0.39$\pm$0.08 mJy as the 2\,mm continuum emission toward
+the background galaxy.
 
@@
 \caption{
-An overlay of the 2\,mm continuum emission on the optical image. Contours start at ...
+An overlay of the 2\,mm continuum emission on the optical image. Contours start and increment at steps of $\pm$3$\sigma$, where $\sigma$\,=\,0.082 mJy
+beam\pmOne. The central cross indicates the centroid of the foreground galaxy,
+as detected in the optical image. The synthesis beam is shown in the bottom left corner.
 \label{fig:2mm}}
 \end{figure}
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContVLA.eps}
+\caption{
+VLA 5\,GHz continuum emission is overlaid on the optical image.
+Contours start and increment at steps of $\pm$3$\sigma$ of $\sigma$=13\micron Jy beam\pmOne.
+The beam is shown in the bottom left corner.
+ \label{fig:vla}}
+\end{figure}
+
+The VLA C-band continuum image in \Fig{vla} shows resolved emission from the
+jets and core of the foreground elliptical galaxy
+as well as emission toward the background quasar.
+Multiple peaks are seen along the arc and their centroids
+coincide with the optical emission from the quasar.
+We extract the flux densities for the arc and the core in \Tab{photometry}.
+We find a spectral index of $\alpha$\,=\,0.024 for the foreground
+galaxy and $\alpha$\,=\,0.345 for the background galaxy by fitting a
+power-law (S$_\nu \propto \nu^{-\alpha}$) to the continuum emission at
+5\,GHz and 2\,mm.
 

### 2016-05-18 src/SED/tablePhotometry.py
update MIPS 24 with aper. correction

@@ -12,6 +12,7 @@ Last Modified: May 17 2016
 History
 -------
 May 17 2016:
+    update MIPS to account for aperture correction
     updated error on PdBI peak
 May 10 2016:
     add decomposed IRAC points, and the missing 3.6 um point
@@ -95,7 +96,7 @@ data_rows = [(0.555, (0.555*u.micron).to(u.GHz, equivalencies=
              (8.0, (8.0*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
               4.5889, 0.00566, 'Spitzer/IRAC(Archive-Host)'),
              (24, (24*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
-              47.18, 0.02621, 'Spitzer/MIPS'),
+              70.2038, 0.02621, 'Spitzer/MIPS'),
              (250, (250*u.micron).to(u.GHz, equivalencies=u.spectral()).value,
               289.4271426, 9.554673, 'Herschel/SPIRE'),
              (350, (350*u.micron).to(u.GHz, equivalencies=u.spectral()).value,

### 2016-05-18 WRITEUP/ms.tex
done photometry section

@@
 \section{Introduction}
+We use a concordance $\Lambda$CDM cosmology throughout this paper, with parameters from the WMAP9 results: $H_0$ = 70 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.27, and $\Omega_{\Lambda}$ = 0.7 \citep{Hinshaw13a}.
 
@@
 
-\section{HST astrometry}
+\section{HST astrometry} %DONE
 We obtain HST images from the Hubble Legacy Archive with
@@
 
-\subsection{Photometry}
-We compiled/web-scraped the \mir to \fir photometry
-from 2MASS, WISE, IRAS, IRAC catalogs .
-to characterize
-the dust emission in RXJ1131 from
-from the 2MASS All-Sky Catalog of Point Sources  (Skrutskie et al. 2006), WISE
-magnitudes from the AllWISE Source CatalogBLAH, Spitzer/MIPS
-data from BLAH Catalog, IRAS photometry from the IRAS point source
-and faint source cataloguesBLAH.
+\subsection{Photometry} \label{sec:photometry} %DONE
+We compile \mir to \fir broadband photometry from various
+catalogs available on the NASA/IPAC Infrared Science
+Archive (IRSA) in \Tab{photometry}. These data were obtained from
+the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
+Wide-field Infrared Survey Explorer (WISE; \citealt{Wright10a}),
+{\it Infrared Astronomical Satellite} (IRAS; \citealt{Neugebauer84a}), and
+the Multiband Imaging Photometer (MIPS; \citealt{Rieke04a}) and
+Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
+\spitzer. We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
+Spitzer Heritage Archive. We perform aperture photometry on
+the channel 1 image to extract flux density at 3.6\,$\mu$m
+since it is not available from the IRSA archive.
 
-We extract the Herschel/SPIRE photometry using SUSSEXTractor
-within HIPE (Savage \& Oliver 2007, Smith et al 2012, Pearson et al 2014)
-over the data obtained from the Herschel Science Archive, which were
-processed by the SPIRE HIPE pipeline version 12BLAH (Ott 2010).
-The SUSSEXtractor
-task estimates the flux density from an image smoothed with
-a convolution kernel derived from the SPIRE beam FWHM.
-The flux density measured by SUSSEXtractor
-was verified using the SPIRE Timeline Fitter (Bendo et
-al. 2013) which fits a two dimensional elliptical Gaussian
-function at the source position in the timeline data. The
-agreement between the SUSSEXtractor and Timeline Fitter
-flux densities was found to be better than $\sim$BLAH per cent.
+The emission in the IRAC images is slightly extended. We thus use the
+HST image ($\sim$0\fracs07 resolution) to determine
+origins of their centroids, all of which are found to be
+centered at the position corresponding to the lensed emission from the
+background galaxy. To recover the diffuse background emission, we subtract a
+point source model centered on the lensing galaxy. We use the average
+FWHM found by fitting a Gaussian profile to several field stars
+using \ncode{imexam} routine of IRAF.
+We perform aperture photometry on the residual image
+to obtain decomposed flux measurements from the background galaxy.
+The photometries for the foreground galaxy are then obtained
+by subtracting the fluxes decomposed for the background source
+from the observed total flux. The resulting photometry in
+\Tab{photometry} are obtained after performing aperture correction
+described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
+correct for the fact that the IRAC imaging was calibrated
+using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
+perform aperture photometry. This step was taken to provide
+constraints on the Wien tail beyond the dust peak of the
+spectral energy distribution (SED) of RXJ1131.
+The details of the SED modeling is presented in \Sec{SED}.
 
-We list the photometry from optical to radio in \Tab{photometry}.
+Extraction of the {\it Herschel}/SPIRE photometry was
+carried out using SUSSEXTractor within Herschel Interactive
+Processing Environment (HIPE; \citealt{Ott10a})
+over the Level 2 maps obtained from the Herschel Science Archive.
+These maps were processed by the SPIRE pipeline
+version 13.0 within HIPE. The SUSSEXtractor task estimates
+the flux density from an image convolved with a kernel
+derived from the SPIRE beam. The flux density
+measured by SUSSEXtractor is additionally confirmed
+using the Timeline Fitter. This task performs photometry
+by fitting a 2D elliptical Gaussian to the Level 1 data at the
+source position given by the output of SUSSEXtractor.
+
 \input{table_photometry_AAScustomized}
@@
 \subsection{SED modeling}
+
+We extrapolated a power-law to 24 \micron
+to decompose the flux at 24 \micron in MIPS.
+
 \subsection{ISM properties}
@@
 \section{Summary and Conclusions}
-We studied a wet-wet merger between a AGN/starburst ULIRG and a optically faint companion at $z$ $\sim$ 0.65.
-In this paper, we BLAH, refining the redshift to $z_{\rm CO}$=0.65370$\pm$0.0005.
+We observed the cold molecular gas properties using \bco and \cco line emission
+toward the AGN host galaxy RXJ1131 at $z_{\rm CO}$\,$\sim$0.65.
+Our results suggest that RXJ1131 is a wet-wet merger between a AGN/starburst
+ULIRG and a optically faint companion.
 

### 2016-05-18 WRITEUP/ms.tex
typesetting

@@
 Observations of the \bco rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz)
-toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$ =
-0.658 were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
+toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658 
+were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
 Riechers). Two observing runs were carried out on 2014 December 06 and 2015
@@
 The final rms noise is $\sigma$ = 1.451 mJy \kms
-beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$
-139 GHz is created by averaging over all the line-free channels. This
+beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz 
+is created by averaging over all the line-free channels. This
 yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15
@@
 gain variation over time, and the phase scatter on the calibrated data. We
-therefore treat its line intensity with caution and refrain using it to derive other physical quantities.
+therefore treat its line intensity with caution and refrain ourselves from 
+using it to derive other physical quantities.
 
@@
 A more detailed discussion of differential lensing effect is presented in
-\Sect{differential} and the magnification factors for various kinematic
+\Sec{differential} and the magnification factors for various kinematic
 components are listed in \Tab{mag}.
@@
 The first and second moment maps are clipped at 3$\sigma$.
-The peak flux density is 8.12 $\pm$ 0.30 Jy\,\kms\,beam\pmOne in the intensity-
-integrated map. The deconvolved source size is estimated to be 5\farc1$\pm$0\farc72 $\times$ 3\farcs72$\pm$0\farcs66 and thus the emission is resolved over
-$\sim$2.2 beams. While the lensed emission is not strictly distributed as 2D-
-Gaussian, the fit recovers the line intensity enclosed within the emitting
+The peak flux density is 8.12 $\pm$ 0.30 Jy\,\kms\,beam\pmOne in the intensity-integrated
+map. The deconvolved source size is estimated to be 5\farcs1$\pm$0\farcs72 $\times$ 3\farcs72$\pm$0\farcs66 
+and thus the emission is resolved over $\sim$2.2 beams. 
+While the lensed emission is not strictly distributed as 2D-Gaussian, 
+the fit recovers the line intensity enclosed within the emitting
 region, we therefore take this as an estimate on the extent of the lensed
@@
 annulus, including the partially complete ``Einstein Ring" and
-the lensed knots (see \Fig{CO21mom)}.
+the lensed knots (see \Fig{CO21mom}).
 
@@
 \centering
-\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
-\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
-\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
+\includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
+\includegraphics[trim=0 5 0 0, clip, width=0.22\textwidth]{../Figures/F555W_REDBLUE.eps}
 \caption{
@@
 image. The contours start at 3$\sigma$ and increment at steps of
-$\pm$3$\sigma$, where $\sigma$=0.3 mJy beam\pmOne. The cross denotes the
-location of the foreground galaxy at $z$=0.295. {\it Right: } The contours
-are color coded to represent the red and blue wings of the emission.
+$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
+location of the foreground galaxy at $z$\,=\,0.295. {\it Right:} The contours
+are color-coded to represent the red and blue wings of the emission.
 \label{fig:CO21mom}}
@@
 channel maps of 21.5\,\kms width and spatial spectra of 1\farcs5 resolution in
-\Fig{chanmap} and \Fig{spatial}, respectively. The figures show that emission
-is present to the West and peaks toward the lensing arc (black across in \Fig{
-chanmap}) in the red wing, and shifts to the East with decreasing velocity (
-blue wing). This indicates extended emission in the source plane, where
+\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures show that emission
+is present to the West and peaks toward the lensing arc (black across in \Fig{chanmap}) 
+in the red wing, and shifts to the East with decreasing velocity (blue wing). 
+This indicates extended emission in the source plane, where
 emission from different kinematic components is separated by different amounts
@@
 
-\begin{figure*}[!htbp]
+\begin{figure*}[tbph]
 \centering
-\includegraphics[width=0.9\textwidth]{../Figures/co_channel_maps.eps}
+\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
 \caption{
@@
 
-\begin{figure*}[!htbp]
+\begin{figure*}[tbph]
 \centering
-\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
+\includegraphics[width=0.8\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
 \caption{
@@
 
-\susbsection{Origin of the \bco emission} \label{sec:origin} %DONE
+\subsection{Origin of the \bco emission} \label{sec:origin} %DONE
 Evidently, the CO emission is co-spatial with the lensed optical emission in
@@
 \centering
-\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
-\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
-\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
+\includegraphics[width=0.45\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
 \caption{
-Contours for the first (left) and second (right) moment maps are shown in steps of 50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
+Contours for the first (left) and second (right) moment maps are shown in steps of 
+50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
 \label{fig:CO21highO}}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../Figures/coOverlay.eps}
-\caption{
-\carma \cco line profile (solid) without continuum subtraction is
+\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
+\caption{\carma \cco line profile (solid) without continuum subtraction is
 over-plotted on the continuum-subtracted \bco line profile (dashed).
@@
 correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,T$_{\tiny \cco}$/T$_{\tiny \bco}$\,=\,0.66$\pm$0.41.
+$r_{\rm 32}$\,=\,T$_{\tiny \cco}$/T$_{\tiny \bco}$\,=\,0.66\,$\pm$\,0.41.
 The high uncertainty is dominated by the uncertainties in the \cco line
@@
 
-We detect PdBI 2\,mm continuum in \Fig{2mm}. The integrated flux density is
+We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
 1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
@@
 \centering
-\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
-\caption{
-An overlay of the 2\,mm continuum emission on the optical image. Contours start and increment at steps of $\pm$3$\sigma$, where $\sigma$\,=\,0.082 mJy
-beam\pmOne. The central cross indicates the centroid of the foreground galaxy,
-as detected in the optical image. The synthesis beam is shown in the bottom left corner.
-\label{fig:2mm}}
+\includegraphics[width=0.23\textwidth]{../Figures/F555W_ContPdBI.eps}
+\hspace{-0.5em}
+\includegraphics[width=0.235\textwidth]{../Figures/F555W_ContVLA.eps}
+\caption{{\it Left:} An overlay of the 2\,mm continuum emission on the optical image. 
+{\it Right:} VLA 5\,GHz continuum emission is overlaid on the optical image. 
+Contours in both images start and increment at steps of 
+$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and 
+$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the left and right panel, respectively.
+The central crosses indicate the centroid of the foreground galaxy,
+as detected in the optical image. The synthesis beams are shown in the bottom left corner of each panel.
+\label{fig:cont}}\vspace{0.51em}
 \end{figure}
 
-\begin{figure}[!htbp]
-\centering
-\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContVLA.eps}
-\caption{
-VLA 5\,GHz continuum emission is overlaid on the optical image.
-Contours start and increment at steps of $\pm$3$\sigma$ of $\sigma$=13\micron Jy beam\pmOne.
-The beam is shown in the bottom left corner.
- \label{fig:vla}}
-\end{figure}
-
-The VLA C-band continuum image in \Fig{vla} shows resolved emission from the
+The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
 jets and core of the foreground elliptical galaxy
@@
 The emission in the IRAC images is slightly extended. We thus use the
-HST image ($\sim$0\fracs07 resolution) to determine
+HST image ($\sim$0\farcs07 resolution) to determine
 origins of their centroids, all of which are found to be
@@
 \section{Analysis}
-\subsection{Lens modeling} \label{lensmodel}
+\subsection{Lens modeling} \label{sec:lensmodel}
 The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.
@@
 The foreground lensing galaxy is represented by a black dot.
-The reconstructed source morphology (magenta ellipses) is also suggestive of a “disk”.
+The reconstructed source morphology (magenta ellipses) is also suggestive of a disk.
 \label{fig:model}}
@@
 becomes flat. We perform non-linear least square fitting using an orthogonal distance regression to find the best-fit $V_a$, $r_t$, $V_0$, taking into account
-errors in both velocity and distance offset (see \Figure{PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
+errors in both velocity and distance offset (see \Fig{PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
 parameter physical. We then estimate the uncertainties associated with best-fit parameters using a Monte Carlo simulation of 500 iterations, perturbing
@@
 
-\subsection{SED modeling}
+\subsection{SED modeling} \label{sec:SED}
 

### 2016-05-18 WRITEUP/ms.tex
type-setting, added stuff to lens model sec, not complete

@@
           infrared: galaxies --
+          galaxies: mergers --
           galaxies: starburst --
@@
 \section{Introduction}
-We use a concordance $\Lambda$CDM cosmology throughout this paper, with parameters from the WMAP9 results: $H_0$ = 70 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.27, and $\Omega_{\Lambda}$ = 0.7 \citep{Hinshaw13a}.
+We use a concordance $\Lambda$CDM cosmology throughout this paper, with parameters from the WMAP9 results:
+$H_0$ = 70 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.27, and $\Omega_{\Lambda}$ = 0.7 \citep{Hinshaw13a}.
 
@@
 a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
-gain variation over time, and the phase scatter on the calibrated data. We
-therefore treat its line intensity with caution and refrain ourselves from 
-using it to derive other physical quantities.
+the gain variations over time, and the phase scatter on the calibrated data. We
+therefore treat its line intensity with caution and ensure that any physical interpretation
+of this system (and thus implications and conclusions of this paper) do not rely on this quantity.
 
@@
 \section{Results}
-\subsection{\bco Emission} %DONE
+\subsection{\bco Emission} \label{sec:CO21} %DONE
 We dynamically resolved the \bco line emission toward the background galaxies
@@
 wavelengths, the lensed emission would be more accurately described by an
-annulus, including the partially complete ``Einstein Ring" and
+annulus, enclosing the partially complete ``Einstein Ring" and
 the lensed knots (see \Fig{CO21mom}).
@@
 $\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
-location of the foreground galaxy at $z$\,=\,0.295. {\it Right:} The contours
+location of the foreground galaxy at $z$\,=\,0.295. Right: contours
 are color-coded to represent the red and blue wings of the emission.
@@
 \caption{
-Channel maps of \pdbi \bco toward RXJ1131 in 21.5\,\kms resolution. The
+Channel maps of PdBI \bco toward RXJ1131 in 21.5\,\kms resolution.
 Black crosses indicate the position of the lensed knots (AGN emission,
-which are components ABCD in C06). The central white-filled
+which correspond to components ABCD in C06). The central white-filled
 star indicates the position of the foreground lensing galaxy (component G
-in C06), as detected in the HST image. Contours start and increment at steps of
+in C06). Contours start and increment at steps of
 $\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
@@
 However, we cannot quantify this with a mass ratio given the
-spatial resolution. This will be verified in future higher-resolution observations. In the subsequent sections, we will interpret RXJ1131
-using this scenario (i.e. a ``wet-wet'' merger).
+spatial resolution. This will be verified in future higher-resolution observations.
+In the subsequent sections, we will interpret RXJ1131
+assuming this classification (i.e. a ``wet-wet'' merger).
 
@@
 content. A velocity gradient across the source plane in \Fig{model} is also
-found in our lens model. This further supports the idea of a kinematically-
-ordered galaxy, but its emission has been lensed differentially.
+found in our lens model. This further supports the idea of a
+kinematically-ordered galaxy, but its emission has been lensed differentially.
 In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
 bright quasar and is in the process of merging.
-We will defer the discussion of the implications to \Sec{dynamics},
+We will defer the discussion of its implications to \Sec{dynamics},
 where we analyze the dynamics of the system in the source plane.
@@
 \includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
-\caption{\carma \cco line profile (solid) without continuum subtraction is
+\caption{CARMA \cco line profile (solid) without continuum subtraction is
 over-plotted on the continuum-subtracted \bco line profile (dashed).
@@
 \includegraphics[width=0.235\textwidth]{../Figures/F555W_ContVLA.eps}
-\caption{{\it Left:} An overlay of the 2\,mm continuum emission on the optical image. 
-{\it Right:} VLA 5\,GHz continuum emission is overlaid on the optical image. 
+\caption{Left: an overlay of the 2\,mm continuum emission on the optical image.
+Right: VLA 5\,GHz continuum emission is overlaid on the optical image.
 Contours in both images start and increment at steps of
@@
 \subsection{Lens modeling} \label{sec:lensmodel}
-The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.
+At the angular resolution of the \bco data, the images are resolved
+but not within the multiply lensed emission (i.e., sub-optimal for
+performing lens modeling). Nevertheless, the high spectral
+resolution of this data provides dynamical information on
+spatial scales smaller than the beam (see \Fig{CO21highO}).
+Hence, with the high SNR, we reconstruct the intrinsic gas
+dynamics by carrying out parametric lens modeling over different
+channel slices of the interferometric data using our lensing code
+\uvmcmcfit (\citealt{uvmcmcfit15a};see \citealt{Bussmann15a} for details of
+the code). Model of each slice in \Fig{model} thus provides
+properties on the intrinsic kinematics. The slices
+are obtained by binning the data (over the full linewidth
+$\sim$700\kms; see \Sec{CO21}) by five channels (i.e., into seven slices)
+ to increase the SNR.
 
-With the high SNR and spectral resolution, we model different kinematic components using our lensing code \uvmcmcfit.
+The lens mass distribution is modeled using a singular isothermal
+ellipsoid (SIE) profile, which is described by five free parameters: the
+positional offset in R.A. and Dec. relative to an arbitrary chosen
+fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
+position angle. We use the VLA radio continuum emission toward
+the foreground galaxy to initialize the positional offset. We impose a
+uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec., which is
+larger than the astrometry uncertainties in the VLA image and is
+constrained by the uncertainties provided from previous SIE lens model (C06).
+We initialize the Einstein Radius based on the optical SIE lens
+model by C06 and impose a uniform prior using their reported $\pm$3$\sigma$.
+The sources are modeled using elliptical Gaussian profiles, which are
+parameterized by six free parameters: the positional offset in R.A.
+and Dec. relative to the lens, the intrinsic flux density, the effective
+radius, the axial ratio, and the position angle. The position of each source
+is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
+and the effective radius is allowed to vary from 0\farcs01$-$2".
 
-% describe model setup.
+% Check with Shane
+Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
+posterior probability distribution function (PDF). In each model, we employ
+$\sim$50,000 samples as the initial ``burn-in'' stage to stabilize the Markov
+chains (which we then discard). We use the final $\sim$5,000
+samplings to determine the posterior probability distributions. Here, we
+identify the best-fit model and the quoted uncertainties using the
+median and the 68\% confidence intervals in the marginal PDFs.
+
+We first obtain a preliminary lens model for each channel slice independently,
+where their lens parameters are allowed to vary and are initialized according
+to the aforementioned way. We obtain the final model
+by repeating the modeling over each slice but fixing their lens parameters
+according to the overall median in the preliminary models
+(see \Tab{lens}). This ensures the
+lens model of each kinematic component share the same lens profile.
+The magnification factor is determined by taking the ratio
+between the image plane flux of the model and the source plane flux.
+The source positions and magnification factors are listed in \Tab{model}.
+
+% disk and caveat
+The location of the reconstructed sources in \Fig{model} are consistent with
+of a disk. This in essence demonstrate a velocity field in the source plane.
+ While solely based on the lens model would not be sufficient to
+draw such conclusion/assertion. Yet, with the observed velocity gradient.
+We emphasis that the spatial resolution of is a few arcsec, which means that
+although we have high SNR and spectral resolution, this data is not sufficient
+to constrain the intrinsic sizes of the lensed galaxies, and thus underpredict
+the magnification factors. We will discuss this further in the following
+section.
 
@@
 \caption{
+Lens models of RXJ1131 using \uvmcmcfit on the PdBI \bco data.
 Lens model of channel widths $\sim$ 100\kms.
 Make this bigger in the future
-Channel maps of the CO emission (red) overlaid on our best-fit lens models (grayscale).
-The foreground lensing galaxy is represented by a black dot.
-The reconstructed source morphology (magenta ellipses) is also suggestive of a disk.
+Top: Channel maps of the PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
+The location of the foreground lensing galaxy is indicated by a black dot and its critical curve is traced by the orange solid line.
+The locations and morphologies (half-light radii) of the reconstructed sources are
+represented by magenta ellipses (see text in \Sec{lensmodel} for caveat). The caustic curves are shown as cyan lines.
+The beam of the observations is shown in
+the bottom right corner of each panel.
+Bottom: Residual images of the best-fit model, obtained by
+taking the Fourier transform after subtracting the best-fit model from the
+data in the visibility plane.
+Contours start at $\pm$3$\sigma$ and increment at steps of
+3$\times$2$^n\sigma$, where $n$ is a positive integer.
 \label{fig:model}}
@@
 \subsection{SED modeling} \label{sec:SED}
+We extrapolated a power-law to 24 \micron to decompose the flux
+at 24 \micron in MIPS.
 
-We extrapolated a power-law to 24 \micron
-to decompose the flux at 24 \micron in MIPS.
+We fit modified blackbody functions to
+to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt κν = 2.64 m2 kg−1 at 125 μm (rest frame; Dunne et al.
+2003).)
+We added blah\% calibration uncertainties on the PdBI data.
+
+We check convergence of our chains by requiring that the autocorrelation length for each model parameter is several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
+Compared with the version of this code used by Riechers et al.
+(2013), several improvements have been made.
+First, we have added the ability to impose upper and lower limits as well as Gaussian priors on the model parameters.
+These additions are useful for analyzing poorly constrained data, such as when we consider fits to only the SPIRE photometry in Section 3.
+Second, instead of treating the instrument response as a delta function in wavelength, we now fully model the wavelength response of each instrument.
+We have applied this improved code to FLS 3, and find that the resulting changes in the model parameters are well within the quoted uncertainties.
+
+% upper limit using decomposed 24 um
+% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
+The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
+% parameter estimation problem
+For these parameter estimation problems using MCMC to sample,
+the full answer is the full joint posterior PDF.
+We here report the summary statistics (global mode (where min. chi),
+marginal mode (in log file),
+posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
 
 \subsection{ISM properties}
+We correct for lensing magnification using the median among our models ($\mu_{\rm L}$=BLAH).
+Assuming a Salpeter initial mass function, we find the SFR of blah using the \fir luminosity after corrected for lensing .
 \subsection{Gas Mass}

### 2016-05-18 WRITEUP/ms.tex
done lens modeling sec

@@
 by repeating the modeling over each slice but fixing their lens parameters
-according to the overall median in the preliminary models
-(see \Tab{lens}). This ensures the
-lens model of each kinematic component share the same lens profile.
+according to the overall median in the preliminary models, as listed in \Tab{lens}. The corresponding masses within the Einstein radii is
+$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun.
+This ensures that all models share the same lens profile.
 The magnification factor is determined by taking the ratio
 between the image plane flux of the model and the source plane flux.
-The source positions and magnification factors are listed in \Tab{model}.
+The best-fit magnification factors are listed in \Tab{model}.
+We compare our model parameters in \Tab{lens} describing
+the mass distribution of the lensing galaxy
+against that of the SIE model presented by C06. The position
+%\footnote{We note that they report a positional offset
+% relative to the light centroid in the HST image, which are at slightly
+%different astrometry. Our comparison takes into
+%account the astrometric correction applied.}
+of lensing mass, Einstein Radius, PA and axial ratio
+are all consistent within the uncertainties.
+% PA = -73.6, ellipticity = 0.45,
+% their theta\_R = 1.84" $\pm$ 0.01.
 
-% disk and caveat
-The location of the reconstructed sources in \Fig{model} are consistent with
-of a disk. This in essence demonstrate a velocity field in the source plane.
- While solely based on the lens model would not be sufficient to
-draw such conclusion/assertion. Yet, with the observed velocity gradient.
-We emphasis that the spatial resolution of is a few arcsec, which means that
-although we have high SNR and spectral resolution, this data is not sufficient
-to constrain the intrinsic sizes of the lensed galaxies, and thus underpredict
-the magnification factors. We will discuss this further in the following
-section.
+\subsection{Interpretation and Caveats}
+The reconstructed source locations in \Fig{model} demonstrate
+an intrinsic velocity gradient in the source plane, which is
+indicative of a disk geometry. While solely based on the
+lens model is insufficient to draw conclusive inference on its
+true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
+can be found in the observed (image plane) velocity field and
+the double-horned line profile in \Fig{CO21spec}. Furthermore,
+the reconstructed source plane emission in optical-NIR
+is also best-reproduced using a $n$\,=\,1 Sersic profile (C06).
+Our interpretation therefore tends in favor of a disk morphology for RXJ1131.
 
-% comparison with C06 model
+% the companion
+One interesting result from our lens model is that a better fit is
+found for the red-most channel if we add a second source component (see
+top left panel in \Fig{model}). This is consistent with previous results
+reported by \citet{Brewer08a}, who find an optically faint companion
+separated by $\sim$2.4\,kpc away from the AGN host galaxy.
+
+We emphasis that the spatial resolution of the data at hand
+is a few arcsec, which implies that despite the high SNR and spectral
+resolution, this data is insufficient to constrain the
+intrinsic sizes of the lensed galaxies, and thus the magnification
+factors is likely under-predicted. We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15
 
@@
 \includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
-\caption{
-Lens models of RXJ1131 using \uvmcmcfit on the PdBI \bco data.
-Lens model of channel widths $\sim$ 100\kms.
-Make this bigger in the future
-Top: Channel maps of the PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
-The location of the foreground lensing galaxy is indicated by a black dot and its critical curve is traced by the orange solid line.
-The locations and morphologies (half-light radii) of the reconstructed sources are
-represented by magenta ellipses (see text in \Sec{lensmodel} for caveat). The caustic curves are shown as cyan lines.
-The beam of the observations is shown in
-the bottom right corner of each panel.
-Bottom: Residual images of the best-fit model, obtained by
+\caption{Each panel corresponds to a lens model of RXJ1131 performed over a
+channel slice $\sim$100\,\kms of the \bco data. Top: Channel maps of the
+PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
+The location of the foreground lensing galaxy is indicated by a black dot and
+its critical curve is traced by the orange solid line. The locations and
+morphologies (half-light radii) of the reconstructed sources are
+represented by magenta ellipses (see text in \Sec{lensmodel} for caveats).
+The caustic curves are represented as cyan lines. The beam of the
+PdBI observations is shown in the bottom right corner of each panel.
+Bottom: Residual images of the best-fit models, obtained by
 taking the Fourier transform after subtracting the best-fit model from the
-data in the visibility plane.
-Contours start at $\pm$3$\sigma$ and increment at steps of
-3$\times$2$^n\sigma$, where $n$ is a positive integer.
+data in the $uv$-domain. Contours start
+at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
+where $n$ is a positive integer.
 \label{fig:model}}
@@
 \subsubsection{Differential Lensing} \label{sec:differential}
-Lens modeling of this source from previous studies find non-negligible differential lensing effect across H-Band, V-band, and I-band. The magnification factor ranges from 10.9
-to 7.8, where the decrease is caused
+Lens modeling of this source from previous studies find non-negligible
+differential lensing effect across H-Band, V-band, and I-band. The
+magnification factor ranges from 10.9 to 7.8, where the decrease is caused
 by the more extended IR emission (hence \SF), well beyond the caustic (C06).

### 2016-05-18 WRITEUP/table_medianLens.tex
done lens modeling sec

\begin{deluxetable*}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Lens parameters from preliminary models}
\tablehead{
\multicolumn{2}{c}{Parameters} &
\colhead{Median values} % weighted-mean of median of each
}
\startdata
Offset in RA    & (\arcsec)   &  0.004$\pm$0.027\\
Offset in Dec    & (\arcsec)   & 0.003$\pm$0.027\\
Axial Ratio      &             & 0.56$\pm$0.16\\
Position Angle   & (deg)       & 103$\pm$22\\
Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002\\
\enddata
\label{tab:lens}
\tablecomments{ Parameters describing the foreground lens are
obtained based on the preliminary models (see text for details).
All angular offsets are with respect to
$\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
$\delta$\,=\,-12\degr31\arcmin58\farcs3 (J2000).
The corresponding masses
within the Einstein radii is $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\,\Msun.}
\end{deluxetable*}

### 2016-05-18 WRITEUP/ms.tex
typeset edits

@@
 \section{Analysis}
-\subsection{Lens modeling} \label{sec:lensmodel}
+\subsection{Lens modeling} \label{sec:lensmodel} %DONE
 At the angular resolution of the \bco data, the images are resolved
@@
 channel slices of the interferometric data using our lensing code
-\uvmcmcfit (\citealt{uvmcmcfit15a};see \citealt{Bussmann15a} for details of
+\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
 the code). Model of each slice in \Fig{model} thus provides
@@
 uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec., which is
-larger than the astrometry uncertainties in the VLA image and is
-constrained by the uncertainties provided from previous SIE lens model (C06).
-We initialize the Einstein Radius based on the optical SIE lens
-model by C06 and impose a uniform prior using their reported $\pm$3$\sigma$.
+motivated by the astrometry uncertainties in the VLA image as well as
+the uncertainties provided by previous SIE lens model (C06).
+We initialize the Einstein Radius based on the model parameters reported by C06 
+and impose a uniform prior using $\pm$3$\sigma$ from their uncertainties.
 The sources are modeled using elliptical Gaussian profiles, which are
@@
 by repeating the modeling over each slice but fixing their lens parameters
-according to the overall median in the preliminary models, as listed in \Tab{lens}. The corresponding masses within the Einstein radii is
-$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun.
+according to the overall median in the preliminary models, as listed in \Tab{lens}. 
 This ensures that all models share the same lens profile.
@@
 The best-fit magnification factors are listed in \Tab{model}.
-We compare our model parameters in \Tab{lens} describing
-the mass distribution of the lensing galaxy
-against that of the SIE model presented by C06. The position
-%\footnote{We note that they report a positional offset
-% relative to the light centroid in the HST image, which are at slightly
-%different astrometry. Our comparison takes into
-%account the astrometric correction applied.}
-of lensing mass, Einstein Radius, PA and axial ratio
-are all consistent within the uncertainties.
-% PA = -73.6, ellipticity = 0.45,
-% their theta\_R = 1.84" $\pm$ 0.01.
 
-\subsection{Interpretation and Caveats}
+Our model parameters in \Tab{lens}, describing
+the mass distribution of the lensing galaxy, are consistent (within the uncertainties) 
+with that of the SIE model presented by C06. We find a mass of 
+$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun
+within the Einstein radius.
+
+\input{table_medianLens}
+
+\subsubsection{Interpretation and Caveats} \label{sec:caveat}
 The reconstructed source locations in \Fig{model} demonstrate
@@
 true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
-can be found in the observed (image plane) velocity field and
-the double-horned line profile in \Fig{CO21spec}. Furthermore,
-the reconstructed source plane emission in optical-NIR
-is also best-reproduced using a $n$\,=\,1 Sersic profile (C06).
+can be found in the double-horned line profile (\Fig{CO21spec})
+and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
+C06 also find that the reconstructed source plane emission in optical-NIR
+is best-reproduced using a $n$\,=\,1 Sersic profile.
 Our interpretation therefore tends in favor of a disk morphology for RXJ1131.
@@
 % the companion
-One interesting result from our lens model is that a better fit is
+One other interesting result from our lens model is that a better fit is
 found for the red-most channel if we add a second source component (see
@@
 reported by \citet{Brewer08a}, who find an optically faint companion
-separated by $\sim$2.4\,kpc away from the AGN host galaxy.
+$\sim$2.4\,kpc away from the AGN host galaxy.
 
-We emphasis that the spatial resolution of the data at hand
+We emphasize that the spatial resolution of the data at hand
 is a few arcsec, which implies that despite the high SNR and spectral
@@
 intrinsic sizes of the lensed galaxies, and thus the magnification
-factors is likely under-predicted. We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15
+factors ares likely under-predicted. 
+We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15
 
@@
 \caption{Each panel corresponds to a lens model of RXJ1131 performed over a
-channel slice $\sim$100\,\kms of the \bco data. Top: Channel maps of the
+channel slice $\sim$100\,\kms of the \bco data. Top: channel maps of the
 PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
@@
 morphologies (half-light radii) of the reconstructed sources are
-represented by magenta ellipses (see text in \Sec{lensmodel} for caveats).
+represented by magenta ellipses (see text in \Sec{caveat} for caveats).
 The caustic curves are represented as cyan lines. The beam of the
 PdBI observations is shown in the bottom right corner of each panel.
-Bottom: Residual images of the best-fit models, obtained by
+Bottom: residual images of the best-fit models, obtained by
 taking the Fourier transform after subtracting the best-fit model from the
@@
 flux density in the red wing is apparently much higher than in the blue wing, given its lensing configuration.
-By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in \Tab{mag}.
+By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in \Tab{model}.
 \input{table_magFactor}

### 2016-05-18 WRITEUP/table_medianLens.tex
typeset edits

@@
-\begin{deluxetable*}{lcc}[!htbp]
+\begin{deluxetable}{lcc}[!htbp]
 \tabletypesize{\scriptsize}
@@
 Position Angle   & (deg)       & 103$\pm$22\\
-Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002\\
+Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002
 \enddata
 \label{tab:lens}
-\tablecomments{ Parameters describing the foreground lens are
+\tablecomments{Parameters describing the foreground lens are
 obtained based on the preliminary models (see text for details).
@@
 $\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
-$\delta$\,=\,-12\degr31\arcmin58\farcs3 (J2000).
-The corresponding masses
-within the Einstein radii is $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\,\Msun.}
-\end{deluxetable*}
+$\delta$\,=\,-12\degr31\arcmin58\farcs3 (J2000).}
+\end{deluxetable}

### 2016-05-19 WRITEUP/ms.tex
done diff. lensing sec

@@
 within the Einstein radius.
+\input{table_medianLens}
+\input{table_magFactor}
 
-\input{table_medianLens}
-
-\subsubsection{Interpretation and Caveats} \label{sec:caveat}
+\subsubsection{Interpretation and Caveats} \label{sec:caveat} %DONE
 The reconstructed source locations in \Fig{model} demonstrate
@@
 
-\subsubsection{Differential Lensing} \label{sec:differential}
-Lens modeling of this source from previous studies find non-negligible
-differential lensing effect across H-Band, V-band, and I-band. The
-magnification factor ranges from 10.9 to 7.8, where the decrease is caused
-by the more extended IR emission (hence \SF), well beyond the caustic (C06).
-
-The highly asymmetric \bco line profile also suggests that differential lensing is non-negligible in the CO emission, where
-flux density in the red wing is apparently much higher than in the blue wing, given its lensing configuration.
-By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in \Tab{model}.
-\input{table_magFactor}
+\subsubsection{Differential Lensing} \label{sec:differential} %DONE
+Previous lens models of RXJ1131 find conspicuous
+differential lensing effect across H-Band, V-band, and I-band (C06), where the
+magnification factor ranges from 10.9 to 7.8. C06 attribute
+the decrease toward the IR regime is caused by the more extended
+IR emission, arising from \SF.
+The highly asymmetric \bco line profile suggests that
+differential lensing is non-negligible for the CO emission, where its red wing
+is apparently much brighter than the blue wing, which is consistent
+with the source positions relative to the caustics in \Fig{model}.
+The red wing emission mainly originates near/at the cusp
+in the caustic, whereas the blue wing emission is located beyond the caustics.
+The magnification factor for CO thus ranges from 8.7 to 3.1 (\Tab{model}).
 
@@
 Based on the the source plane position of each kinematic components from the
-lens model, a clear symmetric velocity gradient is seen, which is suggestive of a rotating disk. Assuming the observed velocities of the respective channels
+lens model, a clear symmetric velocity gradient is seen, which is suggestive
+of a rotating disk.
+Assuming the observed velocities of the respective channels
 correspond to solely the tangential components (i.e. $\theta$ = 0), we extract

### 2016-05-19 WRITEUP/ms.tex
proof-read

@@
 \centering
+% [height=1in,width=5in]
 \includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
@@
 median and the 68\% confidence intervals in the marginal PDFs.
+\input{table_medianLens}
 
@@
 within the Einstein radius.
-\input{table_medianLens}
-\input{table_magFactor}
 
@@
 \subsubsection{Differential Lensing} \label{sec:differential} %DONE
+\input{table_magFactor}
 Previous lens models of RXJ1131 find conspicuous
@@
 The highly asymmetric \bco line profile suggests that
-differential lensing is non-negligible for the CO emission, where its red wing
-is apparently much brighter than the blue wing, which is consistent
+differential lensing is also non-negligible for CO, where the red wing
+of \bco is apparently much brighter than that in the blue wing, consistent 
 with the source positions relative to the caustics in \Fig{model}.
-The red wing emission mainly originates near/at the cusp
+The red wing emission mainly originates near the cusp
 in the caustic, whereas the blue wing emission is located beyond the caustics.
-The magnification factor for CO thus ranges from 8.7 to 3.1 (\Tab{model}).
+The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).
 

### 2016-05-19 PdBI/src/modelVelo/calcmass.py
update code to get mass using numbers reporting in paper

@@ -3,13 +3,23 @@
 calculate dynamical mass
 
 
-Last modified: 13 May 16
+Last modified: 17 May 16
 
 History:
+17 May 2016
+    - get mass using quanties reported in paper
 13 May 2016
     - extracted from modelGradient.py
 
 '''
+import numpy as np
+
+kpc_to_m = 3.086e+19
+b_arcsec = 1.8       # from C06
+a_arcsec = 3.25
+i_rad = np.arccos(b_arcsec/a_arcsec)
+i_deg = i_rad * 180./np.pi
+
 def M_encl(R_kpc, v):
     """ calc mass enclosed """     # v in km/s
     from astropy.constants import G
@@ -24,6 +34,20 @@ def M_encl(R_kpc, v):
     return M10
 
 # calc. mass within some physical dist from line center
-R_in_kpc = xdata.max()
-# print("Mass enclosed within {:.2f} kpc: {:.2f} x 1e+10 Msun".format(R_in_kpc, M_encl(R_in_kpc, pfit[0]/np.sin(i_rad))))
+R_in_kpc = 6.22
+V_rot = 345
+# no correction for incl. angle
+print("Mass enclosed within {:.2f} kpc: {:.2f} x 1e+10 Msun".format(R_in_kpc, M_encl(R_in_kpc, V_rot)))
+# corrected
+print M_encl(R_in_kpc, V_rot)/(np.sin(i_rad)**2)
+
+
+# use line peak separation
+R_in_kpc = 6.22
+V_rot = 220/2.
+# no correction for incl. angle
+print("Mass enclosed within {:.2f} kpc: {:.2f} x 1e+10 Msun".format(R_in_kpc, M_encl(R_in_kpc, V_rot)))
+
+# with incl. correction
+print M_encl(R_in_kpc, V_rot)/(np.sin(i_rad)**2)
 

### 2016-05-19 PdBI/src/modelVelo/modelGradient.py

@@ -4,9 +4,11 @@
 plot source locations from lens model of various channel as markers on observed 1st moment map.
 Kinematics.
 
-Last Modified: 15 May 16
+Last Modified: 17 May 16
 
 History:
+17 May 16:
+  - move var kpc_to_m to calcmass.py
 15 May 16:
   - adjust residual fig outlook
 13 May 16:
@@ -492,9 +494,6 @@ if plotRot:
 # --------------------------------------------------------------
 #  disk model
 # ---------------------------------------------------------------
-kpc_to_m = 3.086e+19
-
-
 def velo_disk(V_obs, theta=0., i=30.):
     """ simple axisymmetric thin disk model
 

### 2016-05-19 WRITEUP/ms.tex
done dyn modelling

@@
 \section{HST astrometry} %DONE
-We obtain HST images from the Hubble Legacy Archive with
+We obtain {\it HST} images from the Hubble Legacy Archive with
 a goal to understand the origins of the emission detected
@@
 We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
-Dec., which is consistent with the typical astrometric precision (1$-$2") of
+Dec., which is consistent with the typical astrometric precision (1$-$2$^{\prime\prime}$) of
 images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
@@
 \Sec{differential} and the magnification factors for various kinematic
-components are listed in \Tab{mag}.
+components are listed in \Tab{model}.
  \label{fig:CO21spec}}
@@
 \caption{
-An overlay of the velocity-integrated \bco emission on the HST V$-$band (F555W)
+An overlay of the velocity-integrated \bco emission on the {\it HST} V$-$band (F555W)
 image. The contours start at 3$\sigma$ and increment at steps of
@@
 catalogs available on the NASA/IPAC Infrared Science
-Archive (IRSA) in \Tab{photometry}. These data were obtained from
+Archive (IRSA) in \Tab{photometry} with aperture corrections
+when warranted. These data were obtained from
 the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
@@
 Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
-\spitzer. We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
-Spitzer Heritage Archive. We perform aperture photometry on
+\spitzer.
+We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
+Spitzer Heritage Archive and perform aperture photometry on
 the channel 1 image to extract flux density at 3.6\,$\mu$m
@@
 background galaxy. To recover the diffuse background emission, we subtract a
-point source model centered on the lensing galaxy. We use the average
+point source model centered on the lensing galaxy, using the average
 FWHM found by fitting a Gaussian profile to several field stars
-using \ncode{imexam} routine of IRAF.
+with the \ncode{imexam} routine of IRAF.
 We perform aperture photometry on the residual image
@@
 spectral energy distribution (SED) of RXJ1131.
-The details of the SED modeling is presented in \Sec{SED}.
+Details of the SED modeling is presented in \Sec{SED}.
 
@@
 measured by SUSSEXtractor is additionally confirmed
-using the Timeline Fitter. This task performs photometry
+using the Timeline Fitter, which performs photometry
 by fitting a 2D elliptical Gaussian to the Level 1 data at the
@@
 Hence, with the high SNR, we reconstruct the intrinsic gas
-dynamics by carrying out parametric lens modeling over different
+dynamics by carrying out a parametric lens modeling over different
 channel slices of the interferometric data using our lensing code
@@
 We initialize the Einstein Radius based on the model parameters reported by C06
-and impose a uniform prior using $\pm$3$\sigma$ from their uncertainties.
+and impose a uniform prior using $\pm$3$\sigma$ of their uncertainties.
 The sources are modeled using elliptical Gaussian profiles, which are
@@
 posterior probability distribution function (PDF). In each model, we employ
-$\sim$50,000 samples as the initial ``burn-in'' stage to stabilize the Markov
+$\sim$100,000 samples as the initial ``burn-in'' stage to stabilize the Markov
 chains (which we then discard). We use the final $\sim$5,000
@@
 by repeating the modeling over each slice but fixing their lens parameters
-according to the overall median in the preliminary models, as listed in \Tab{lens}.
+according to the overall median in the preliminary models,
+as listed in \Tab{lens}.
 This ensures that all models share the same lens profile.
-The magnification factor is determined by taking the ratio
-between the image plane flux of the model and the source plane flux.
-The best-fit magnification factors are listed in \Tab{model}.
+The magnification factors in \Tab{model} are determined by taking the ratio
+between the image plane flux and the source plane flux of each model.
 
@@
 The reconstructed source locations in \Fig{model} demonstrate
-an intrinsic velocity gradient in the source plane, which is
+an intrinsic velocity gradient across the source plane, which is
 indicative of a disk geometry. While solely based on the
@@
 Previous lens models of RXJ1131 find conspicuous
-differential lensing effect across H-Band, V-band, and I-band (C06), where the
+differential lensing effect across {\it HST}
+H-Band, V-band, and I-band (C06), where the
 magnification factor ranges from 10.9 to 7.8. C06 attribute
@@
 
-\subsection{\bco Dynamical modeling} \label{sec:dynamics}
-Based on the the source plane position of each kinematic components from the
-lens model, a clear symmetric velocity gradient is seen, which is suggestive
-of a rotating disk.
-Assuming the observed velocities of the respective channels
-correspond to solely the tangential components (i.e. $\theta$ = 0), we extract
-the major axis along the best-fit slice across these source plane positions,
-which is along PA of 121\degr.
-We attempt to characterize the molecular gas kinematics using an empirically motivated disk model (e.g. Courteau97, Peuch+08, Miller+11):
+\subsection{\bco Dynamical modeling} \label{sec:dynamics} %DONE
+This section proceeds under the assumption that RXJ1131 is
+a rotating disk (see previous sections).
+Assuming the velocities of the respective lens models
+correspond to solely the tangential component (i.e., $\theta$ = 0), we extract
+a pseudo PV diagram along the major axis in \Fig{PV} by slicing across their
+source plane positions. The best-fit major axis is along PA of 121\degr.
+
+We attempt to characterize the molecular gas kinematics using an empirically motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
 \begin{equation}
-V = V_0 + \frac{2}{\pi} V_{\rm a} \arctan(\frac{R}{R_{\rm t}}),
+V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
 \end{equation}
-where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center, $V_{\rm a}$ is the asymptotic velocity, and $R_{\rm t}$ is the ``turnover'' radius at which the rotation curve
-becomes flat. We perform non-linear least square fitting using an orthogonal distance regression to find the best-fit $V_a$, $r_t$, $V_0$, taking into account
-errors in both velocity and distance offset (see \Fig{PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
-parameter physical. We then estimate the uncertainties associated with best-fit parameters using a Monte Carlo simulation of 500 iterations, perturbing
-the velocity and physical separation according to a random Gaussian distribution of width/sigma based on the input uncertainties on
-the data. Using this model, we find $V_a$ = 975$\pm$387, $r_t$ = 10.6$\pm$5.7,
-and $V_0$ = 28$\pm$40. We note, however, that since emission is not detected beyond the flat regime of the rotation curve (Figure \ref{fig: PV}), the asymptotic velocity is
-poorly constrained. In particular, $V_a$ and $r_t$ are highly correlated with a Pearson coefficient $r$ = 0.998 between the two, and 0.027 between $V_a$ and $V_0$.
+where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
+$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
+radius at which the rotation curve becomes flat.
+We perform non-linear least square fitting using an orthogonal distance
+regression to find the best-fit parameters,
+taking into account the uncertainties in both velocity (channel width) and
+distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
+to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
+The parameter uncertainties are inferred based on Monte Carlo simulation
+of 500 iterations, which we perturb the input parameters according to a random
+Gaussian distribution of sigma corresponding to their uncertainties.
+Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
+$R_{t}$\,=\,10.6\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
+We note, however, that since emission is not detected beyond the flat regime
+of the rotation curve, the asymptotic velocity is poorly constrained.
+In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
+Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.
 
-While a symmetric velocity field in the source plane is consistent with a rotating disc, such is insufficient to conclude a rotating disk morphology. Additional characteristics such
-as peak velocity dispersion at the center of a galaxy and a ``spider'' diagram are needed. Based on the reconstructed source plane in the optical/NIR emission, C06 find that a
-n=1 Sersic profile is best fit their model or is it the reconstructed emission (TBD).
+\begin{figure}[!Htbp]
+\centering
+\includegraphics[width=0.455\textwidth]{../Figures/bestfit_PV.eps}
+\caption{PV slice along the major axis in the source plane at PA\,=\,121\degr.
+Dashed line shows the best-fit rotation curve using an arctangent model.
+DR may suggest include MC simulation fits, maybe I will do that later.
+ \label{fig:PV}}
+\end{figure}
 
-The frequently used V$_{\rm max}$ (maximum measured velocity) is not equivalent to the
-asymptotic value, Va, a mathematical extrapolation and typically not reached in
-the observed rotation curve. Estimates of Va can depend critically on how well
-the central region and turn over of the rotation curve are constrained. For the
-remaining analysis, we adopt the asymptotic limit as a proxy to the rotation
-curve. We also note that typical studies of the Tully-Fisher relation uses V$_2.2$ (at 2.2 $\times$ disc scalelength $\sim$ 1.375 half-light radius $\sim$ 0.7R$_opt$) as the rotation
-velocity since this would be the radius at which the velocity of a pure
-exponential disc peaks at. However, our source appears to be a disturbed
-rotator, albeit coarse resolution. Hence, rather than adopting V$_2.2$, we use the
-asymptotic value from the best-fit arctangent model. The half light radius in the
-optical is ~xx kpc (from C06; converted in to our cosmology, but BJB 8 kpc
-across?).
+We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
+out to radius beyond the disk scale-length and half-light radius --
+is inequivalent to maximum observed velocity ($V_{\rm max}$),
+which is commonly used in literature to parameterize disc rotation.
+Studies of the Tully-Fisher relation typically use V$_{2.2}$ (velocity
+at 2.2 disc scale-length or $\sim$1.375 half-light radius,
+or $\sim$0.7$R_{\rm opt}$) as the rotation velocity ($V_{\rm max}$ in their
+terminology), which corresponds to the radius at which the velocity
+of a pure exponential disc peaks.
+We here adopt the maximum {\em observed} velocity
+$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
+dynamical center as a proxy to the rotation velocity.
+This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
+radius $\sim$10.3 kpc inferred from the C06 lens model (converted to
+our cosmology), who use all {\it HST} H--, V--, and I--bands in their
+modeling. If only V$-$band is used, the half-light radius is $\sim$4kpc \citep{Brewer08a}.
+This discrepancy arises owning to the exclusion of the more diffused emission in the V-band
+(\ie V-band is missing the diffused emission).
+This indicates that the molecular gas may be ... (see \Sec{size}). DR: ok, let's discuss this.
 
-If we adopt the best-fit parameters, we find a dynamical mass of $M_{\rm dyn}$($<$blah kpc) sin$^2 i$ = BLAH \Msun. Consider the line widths using the separation between
-the red- and blue- shifted emission of the \bco line profile of $\Delta v_{\rm sep}/2 \sim$ blah \kms and a source size of blah kpc, we find a dynamical mass of $M_{\rm dyn}$
-sin$^2 i$ = BLAH \Msun. If we adopt the inclination angle using the morphological axis ratio from the
-reconstructed optical image reported by C06, where the minor axis is 1\farcs8 and the major axis is 3\farcs3.25, then we find an inclination angle of 56.4
-\degr. Then $M_{\rm dyn}$\,=\,BLAH. The inclination angle is consistent with the observed unobscured AGN and an observable double peak line profile.
-
-We note, however, that large differences (up to $\gtrsim$10 deg) can be found between such kinematically-derived inclinations and the ones inferred from the morphological
-axis ratio (e.g., Chemin et al. 2006). We caution that this analysis is based on limited spatial resolution data and will been verified by future higher-resolution observations.
+Using this $V_{\rm rot}$, we find a dynamical mass of
+$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 17\E{10}\,\Msun.
+If we instead consider the line peak separation from the
+\bco line profile $\Delta v_{\rm sep}/2 \sim$110\,\kms, we find
+$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 1.8\E{10}\,\Msun.
+DR: here, I list the extrema for possible Mdyn given our data,
+should I say anything more?
+We correct for the inclination effect using the
+morphological axial ratio from the reconstructed image (Figure 3 in C06), where
+the minor axis is 1\farcs8 and the major axis is 3\farcs25.
+We thus find an inclination angle of 56.4\degr, which is consistent with the
+observed unobscured AGN and an observable double peak line profile.
+The dynamical mass is then 2.5\E{10}\Msun$<$$M_{\rm dyn}$($<$6 kpc)$<$25\E{10}\Msun.
+We caution that this analysis is based on limited spatial
+resolution data and will be verified by future higher-resolution
+observations.
 
@@
 at 24 \micron in MIPS.
-
-We fit modified blackbody functions to
-to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt κν = 2.64 m2 kg−1 at 125 μm (rest frame; Dunne et al.
-2003).)
-We added blah\% calibration uncertainties on the PdBI data.
-
-We check convergence of our chains by requiring that the autocorrelation length for each model parameter is several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
-Compared with the version of this code used by Riechers et al.
-(2013), several improvements have been made.
-First, we have added the ability to impose upper and lower limits as well as Gaussian priors on the model parameters.
-These additions are useful for analyzing poorly constrained data, such as when we consider fits to only the SPIRE photometry in Section 3.
-Second, instead of treating the instrument response as a delta function in wavelength, we now fully model the wavelength response of each instrument.
-We have applied this improved code to FLS 3, and find that the resulting changes in the model parameters are well within the quoted uncertainties.
-
-% upper limit using decomposed 24 um
-% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
-The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
-% parameter estimation problem
-For these parameter estimation problems using MCMC to sample,
-the full answer is the full joint posterior PDF.
-We here report the summary statistics (global mode (where min. chi),
-marginal mode (in log file),
-posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
+%
+%We fit modified blackbody functions to
+%to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt 
+%BLAH (rest frame; Dunne et al. 2003).)
+%We added blah\% calibration uncertainties on the PdBI data.
+%
+%We check convergence of our chains by requiring that the autocorrelation length for each model parameter is 
+%several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
+%The code treats the instrument response. 
+%
+%% upper limit using decomposed 24 um
+%% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
+%The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
+%% parameter estimation problem
+%For these parameter estimation problems using MCMC to sample,
+%the full answer is the full joint posterior PDF.
+%We here report the summary statistics (global mode (where min. chi),
+%marginal mode (in log file),
+%posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
 
@@
 \subsection{Gas Mass}
-\subsection{Source Extent}
+\subsection{Source Extent} \label{sec:size}
 Compared to HST:
@@
 \subsection{Merger stage of RXJ1131-1231}
+
+As discussion in previous sections, while we see evidence such as a symmetric velocity field in the source plane, double-horned profile, observed velocity
+gradient, C06 model $n$=1 Sersic profile, which suggest that RXJ1131 is likely a rotating disc.
+Yet, this is insufficient to conclude a disk morphology.
+Additional characteristics such as peak velocity dispersion at the central region and a ``spider'' diagram are needed, which is commonly seen in local spirals.
 

### 2016-05-21 WRITEUP/ms.tex
mainly rewording and add some scattered ideas to last sections

@@
 calibrator, yielding $\sim$10\% calibration accuracy.
-We use \aips to calibrate the visibility data which
+We use \ncode{AIPS} to calibrate the visibility data which
 are then imaged and deconvolved using
@@
 in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
-resolution as the reference coordinate frame to align the optical (V$-$band) image.
+resolution as the reference coordinate frame to align the optical ($V$-band) image.
 We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
@@
 \begin{figure}[!htbp]
-\centering
-% [height=1in,width=5in]
-\includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
-\includegraphics[trim=0 5 0 0, clip, width=0.22\textwidth]{../Figures/F555W_REDBLUE.eps}
-\caption{
-An overlay of the velocity-integrated \bco emission on the {\it HST} V$-$band (F555W)
-image. The contours start at 3$\sigma$ and increment at steps of
+\includegraphics[trim=3 5 0 15, clip, width=0.242\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
+\includegraphics[trim=3 5 0 0, clip, width=0.23\textwidth]{../Figures/F555W_REDBLUE.eps}
+\caption{Left: an overlay of the velocity-integrated \bco emission on the {\it HST} $V$--band (F555W)
+image. Right: contours are color-coded to represent the red and blue wings of the emission.
+The contours start at 3$\sigma$ and increment at steps of
 $\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
-location of the foreground galaxy at $z$\,=\,0.295. Right: contours
-are color-coded to represent the red and blue wings of the emission.
+location of the foreground galaxy at $z$\,=\,0.295.
 \label{fig:CO21mom}}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
+\includegraphics[width=0.85\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
 \caption{
@@
 
-\subsection{Origin of the \bco emission} \label{sec:origin} %DONE
+\subsection{Origin of the \bco Emission} \label{sec:origin} %DONE
 Evidently, the CO emission is co-spatial with the lensed optical emission in
-the background AGN host galaxy. The question is then whether the optically
+the background AGN host galaxy.
+The question is then whether the optically
 faint companion also contributes to the CO flux and thus contains a
@@
 However, we cannot quantify this with a mass ratio given the
-spatial resolution. This will be verified in future higher-resolution observations.
-In the subsequent sections, we will interpret RXJ1131
-assuming this classification (i.e. a ``wet-wet'' merger).
+spatial resolution, nor can we rule out the possibility that
+the ``companion'' is instead a gas component/tidal feature ripped out
+from previous interaction. In the subsequent sections, we will interpret
+the this additional source component as gas emission
+in a nearby galaxy (i.e. a ``wet-wet'' merger), as suggested by previous studies of RXJ1131.
 
@@
 \begin{figure}[!htbp]
-\centering
-\includegraphics[width=0.23\textwidth]{../Figures/F555W_ContPdBI.eps}
-\hspace{-0.5em}
-\includegraphics[width=0.235\textwidth]{../Figures/F555W_ContVLA.eps}
-\caption{Left: an overlay of the 2\,mm continuum emission on the optical image.
-Right: VLA 5\,GHz continuum emission is overlaid on the optical image.
+%\centering
+\includegraphics[trim=12 27 0 0, clip, width=0.45\textwidth]{../Figures/F555W_ContPdBI.eps}
+\includegraphics[trim=10 5 0 0, clip, width=0.475\textwidth]{../Figures/F555W_ContVLA.eps}
+\caption{Top: an overlay of the 2\,mm continuum emission on the optical image.
+Bottom: VLA 5\,GHz continuum emission is overlaid on the optical image.
 Contours in both images start and increment at steps of
@@
 We extract the flux densities for the arc and the core in \Tab{photometry}.
-We find a spectral index of $\alpha$\,=\,0.024 for the foreground
-galaxy and $\alpha$\,=\,0.345 for the background galaxy by fitting a
-power-law (S$_\nu \propto \nu^{-\alpha}$) to the continuum emission at
+We find a spectral index of $\alpha$\,=\,$-$0.024 for the foreground
+galaxy and $\alpha$\,=\,$-$0.345 for the background galaxy by fitting a
+power-law (S$_\nu \propto \nu^{\alpha}$) to the continuum emission at
 5\,GHz and 2\,mm.
@@
 the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
-Wide-field Infrared Survey Explorer (WISE; \citealt{Wright10a}),
-{\it Infrared Astronomical Satellite} (IRAS; \citealt{Neugebauer84a}), and
+Wide-field Infrared Survey Explorer ({\it WISE}; \citealt{Wright10a}),
+{\it Infrared Astronomical Satellite}
+({\it IRAS};\citealt{Neugebauer84a}), and
 the Multiband Imaging Photometer (MIPS; \citealt{Rieke04a}) and
@@
 The emission in the IRAC images is slightly extended. We thus use the
-HST image ($\sim$0\farcs07 resolution) to determine
+{\it HST} image ($\sim$0\farcs07 resolution) to determine
 origins of their centroids, all of which are found to be
@@
 the foreground galaxy to initialize the positional offset. We impose a
-uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec., which is
+uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec.,
 motivated by the astrometry uncertainties in the VLA image as well as
@@
 % Check with Shane
+{\bf NEEDS EDIT}
 Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
-posterior probability distribution function (PDF). In each model, we employ
-$\sim$100,000 samples as the initial ``burn-in'' stage to stabilize the Markov
-chains (which we then discard). We use the final $\sim$5,000
-samplings to determine the posterior probability distributions. Here, we
+posterior probability distribution function (PDF).
+In each model, we require the target acceptance rate of $\sim$0.25$-$0.5
+and check for chain convergence by inspecting the trace plots
+AND BLAH to verify we can samples beyond an autocorrelation time.
+We employ $\sim$50,000 samples as the initial ``burn-in'' stage
+to stabilize the Markov chains (which we then discard).
+We then use the final $\sim$5,000 steps, sampled by 128 walkers.
+Here, we
 identify the best-fit model and the quoted uncertainties using the
@@
 reported by \citet{Brewer08a}, who find an optically faint companion
-$\sim$2.4\,kpc away from the AGN host galaxy.
+(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
+and C06, who find evidence for an interacting dusty galaxy.
+Spatially, the red velocity component of the CO also coincides with this
+component F. While we cannot quantify the type of
+merger (major v.s. minor) with a mass ratio given the
+spatial resolution, the symmetric velocity gradient may lean support
+towards a minor merger.
 
@@
 \begin{figure*}[tbph]
-\centering
-\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
-\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
+%\centering
+\includegraphics[width=1.0\textwidth]{../Figures/PostageStampModel.eps}
+\includegraphics[width=1.0\textwidth]{../Figures/PostageStampResiduals.eps}
 \caption{Each panel corresponds to a lens model of RXJ1131 performed over a
@@
 differential lensing effect across {\it HST}
-H-Band, V-band, and I-band (C06), where the
+$H$-, $V$-, and $I$-band (C06), where the
 magnification factor ranges from 10.9 to 7.8. C06 attribute
@@
 The highly asymmetric \bco line profile suggests that
-differential lensing is also non-negligible for CO, where the red wing
-of \bco is apparently much brighter than that in the blue wing, consistent
+differential lensing is also non-negligible for CO, where the redshifted
+emission is apparently much brighter than that in the
+blueshifted emission, consistent
 with the source positions relative to the caustics in \Fig{model}.
@@
 a rotating disk (see previous sections).
-Assuming the velocities of the respective lens models
-correspond to solely the tangential component (i.e., $\theta$ = 0), we extract
-a pseudo PV diagram along the major axis in \Fig{PV} by slicing across their
-source plane positions. The best-fit major axis is along PA of 121\degr.
+Assuming the velocities of the respective channels used in
+lens modeling correspond to solely the tangential component of the
+true velocity vector (i.e., along the major axis), we extract
+a one dimensional PV diagram in \Fig{PV}
+by slicing across their source plane positions (PA: 121\degr).
 
@@
 The parameter uncertainties are inferred based on Monte Carlo simulation
-of 500 iterations, which we perturb the input parameters according to a random
-Gaussian distribution of sigma corresponding to their uncertainties.
+of 500 iterations, where the input parameters are perturbed
+according to random Gaussian distributions of sigmas
+corresponding to their uncertainties.
 Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
@@
 We note, however, that since emission is not detected beyond the flat regime
-of the rotation curve, the asymptotic velocity is poorly constrained.
+of the rotation curve, the asymptotic velocity is poorly constrained and
+the ``turnover'' radius is at most a lower limit.
 In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
@@
 
-\begin{figure}[!Htbp]
+\begin{figure}[!htbp]
 \centering
@@
 Dashed line shows the best-fit rotation curve using an arctangent model.
+The vertical error bars show the channel width for
+each model and the horizontal error bars are the
+1$\sigma$ uncertainties on the source plane positions.
 DR may suggest include MC simulation fits, maybe I will do that later.
@@
 which is commonly used in literature to parameterize disc rotation.
-Studies of the Tully-Fisher relation typically use V$_{2.2}$ (velocity
+The arctangent model is most commonly used in studies of the
+Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
 at 2.2 disc scale-length or $\sim$1.375 half-light radius,
-or $\sim$0.7$R_{\rm opt}$) as the rotation velocity ($V_{\rm max}$ in their
-terminology), which corresponds to the radius at which the velocity
+or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
+distribution.}) is typically adopted
+as the rotation velocity ($V_{\rm max}$ in their
+terminology) since this corresponds to the radius at which the velocity
 of a pure exponential disc peaks.
@@
 This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
-radius $\sim$10.3 kpc inferred from the C06 lens model (converted to
-our cosmology), who use all {\it HST} H--, V--, and I--bands in their
-modeling. If only V$-$band is used, the half-light radius is $\sim$4kpc \citep{Brewer08a}.
-This discrepancy arises owning to the exclusion of the more diffused emission in the V-band
-(\ie V-band is missing the diffused emission).
-This indicates that the molecular gas may be ... (see \Sec{size}). DR: ok, let's discuss this.
+radius $\sim$10.3\,kpc inferred from the C06 lens model (converted to
+our cosmology) over the {\it HST} $I$-band image.
+We note that the source plane half-light radius varies substantially with
+wavelength: $R_e$ $\sim$\,4kpc and $\sim$7\,kpc based on models over
+$V$-band \citep{Brewer08a} and $H$-band (C06), respectively.
+This discrepancy arises owing to the exclusion of the more
+diffused emission in $V$-band (rest-frame UV),
+which traces recent massive \SF.
+% On the other hand, $I$-band traces the more evolved stellar population.
+This indicates that the molecular gas may be ....
+DR: ok, let's discuss this.
 
@@
 \subsection{SED modeling} \label{sec:SED}
+By fitting a power-law spectrum $S_\nu \propto \nu^\alpha$ to the decomposed
+IRAC photometry. We find a spectral index of $\alpha\sim-$1.9 and
+$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
+This is consistent with the mean spectral slope of optical quasars
+(optically-selected) ($\alpha\sim-$1, Elvis et al. 1994;
+Neugebauer et al. 1979).
+For comparison, broad-line AGN from the AGN and Galaxy
+Evolution Survey (AGES, C. S. Kochanek et al., in prep) have 3.6$-$8 \micron slopes of $\alpha$ = $-$1.07$\pm$0.53 (Stern et al. 2005).
+
 We extrapolated a power-law to 24 \micron to decompose the flux
 at 24 \micron in MIPS.
-%
-%We fit modified blackbody functions to
-%to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt 
-%BLAH (rest frame; Dunne et al. 2003).)
-%We added blah\% calibration uncertainties on the PdBI data.
-%
-%We check convergence of our chains by requiring that the autocorrelation length for each model parameter is 
-%several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
-%The code treats the instrument response. 
-%
-%% upper limit using decomposed 24 um
-%% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
-%The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
-%% parameter estimation problem
-%For these parameter estimation problems using MCMC to sample,
-%the full answer is the full joint posterior PDF.
-%We here report the summary statistics (global mode (where min. chi),
-%marginal mode (in log file),
-%posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
+Since the contribution from AGN is not taken into account in SBURT, it is expected that the SEDs of AGN candidates show an excess in the MIR, owing to hot dust around the central massive black hole,
+NIR not corrected for extinction.
 
-\subsection{ISM properties}
+We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side.
+We include the IRAS 60\micron and 100\micron upper limits to constrain the dust peak.
+We also fit SED models including the decomposed 24.0\micron data (see \Sec{photometry})
+
+Spitzer mid-IR spectroscopy of local ULIRGs will indicate the appropriate luminosity fraction that needs to be assigned to the AGN for ULIRGs before and after nuclear coalescence.
+ULIRG Lir
+Our SED model find a rest-frame characteristic dust temperature of BLAH (cf. 60-70K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10)
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
+\caption{
+WISE flux is higher than the IRAC data, probably just due to smaller aperture used in IRAC.
+Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied.
+Spitzer/MIPS: PSF fit flux, as source size <
+native PSF FWHM of 6".
+Might want to add NVSS constraints.
+ \label{fig:SED}}
+\end{figure*}
+
+We fit modified blackbody functions to
+to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt
+BLAH (rest frame; Dunne et al. 2003).)
+We added blah\% calibration uncertainties on the PdBI data.
+
+We check convergence of our chains by requiring that the autocorrelation length for each model parameter is
+several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
+The code treats the instrument response.
+flux using the set of photometric filters used to obtain the observations.
+
+identical to the modified blackbody fit,
+where the Wien side is removed and replaced by MIR power-law consistent with any mid-IR data available.
+We find a power-law slope of BLAH,
+Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
+
+% upper limit using decomposed 24 um
+% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
+The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
+% parameter estimation problem
+For these parameter estimation problems using MCMC to sample,
+the full answer is the full joint posterior PDF.
+We here report the summary statistics (global mode (where min. chi),
+marginal mode (in log file),
+posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
+
+\subsection{Physical properties}
+\subsubsection{SB versus AGN contribution}
+
 We correct for lensing magnification using the median among our models ($\mu_{\rm L}$=BLAH).
 Assuming a Salpeter initial mass function, we find the SFR of blah using the \fir luminosity after corrected for lensing .
-\subsection{Gas Mass}
-\subsection{Source Extent} \label{sec:size}
-Compared to HST:
+
+\subsubsection{Gas properties}
+% Gas, dynamical, etc
+Since RXJ1131 has a companion, i.e. not dynamically relaxed, the dynamical mass estimate using a virial estimator is likely underestimated.
+
+\subsubsection{SF and Molecular Gas}
+C06: 814
 
@@
 \section{Discussion}
+% summarize (conflicting ) results from recent studies.
+% lead way into our results
+\subsection{Mass in RXJ1131}
+black hole mass
+dynamical mass
+stellar mass
+dust mass
+
+Assuming local $M_{\rm BH}-M_{\rm bulge}$ relation, this would imply $M_{\rm bulge}$$\sim$BLAH\Msun.
+
 \subsection{Merger stage of RXJ1131-1231}
+We put our results in content with ULIRGs/mergers in $z$=0$-$1.
 
@@
 Additional characteristics such as peak velocity dispersion at the central region and a ``spider'' diagram are needed, which is commonly seen in local spirals.
+\\
+
+Kinematics and mergers:
+For major mergers, two galaxy mass centres separated on the same scale as the gas disk (4 kpc or more), the gas dynamics would be strongly perturbed and would deviate substantially from that of a simple disk.
+
+In a minor merger (a mass ratio of more than 3:1) the more massive galaxy, including its gas distribution, can retain a significant angular momentum and resemble a rotating disk.
+
+RXJ kinematics:
+The smooth, symmetric velocity field seen in our lens model and image plane
+suggest a kinematically-order (i.e., disk) galaxy. However, the high
+dispersion near the dynamical center suggest that RXJ1131 is turbulent, albeit
+lack of spatial resolution. Overall implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution data are needed to confirm this.
+Although these values are discussed in \Sec{blah} we cannot draw any general conclusions concerning BLAH.
+
+Mergers are observable for 0.2-0.4 Gyr,
+between 2nd passage and coalescence.
+Kinematic asymmetries follow morphological asymmetries during
+mergers. Mergers are kinematically detectable for 0.2-0.4 Gyr
+between second passage and colaescence.
+
+Numerical simulations of mergers between two galaxies have shown that multiple, discrete starburst events can be triggered even in double mergers.
+The timing of the starbursts is thought to depend on the progenitor galaxy morphologies, with early starbursts (before the galaxies start to merge) occurring in bulgeless disc galaxies, and late starbursts (after the galaxies have started to merge) occur- ring in disc galaxies with a bulge component (Mihos \& Hernquist 1994, 1996.
+Maybe the more compact rest-frame SF and the more recent NIR SF, which is also more extended and diffuse is consistent with the spinning blackhole, i.e.
+already encountered?
 
 \subsection{Implications}
+At low redshifts the ULIRG luminosity function shows strong evolution with redshift (Veilleux et al. 1999).
+not known whether the IR luminosity of these high- redshift sources arises due to mergers between two or more large spiral galaxies, as in local ULIRGs, or via a different mechanism/galaxy formation processes at high-z.
+
 gas fraction at this redshift. how does that relate to
@@
 SFE at this redshift, how does that relate to the SFH. probably a secondary effect to the drop in SFH
+
+What are the conclusions of the paper (qualitative and/or quantitative)?
+What is the evidence for those conclusions?
+How do these results relate to prior work?
+What are the implications of this work – i.e. what theories are being tested/questions are being answered etc?
 
@@
 \section{Summary and Conclusions}
+% see Hodge12_dynamics.pdf for guide
 We observed the cold molecular gas properties using \bco and \cco line emission

### 2016-05-22 WRITEUP/ms.tex
add section compare some gas estimtes, still working on it

@@
 \subsection{Photometry} \label{sec:photometry} %DONE
-We compile \mir to \fir broadband photometry from various
+We compile \mir to \fir broadband photometry (uncorrected for
+dust extinction) from various
 catalogs available on the NASA/IPAC Infrared Science
@@
 posterior probability distribution function (PDF).
-In each model, we require the target acceptance rate of $\sim$0.25$-$0.5
+In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
 and check for chain convergence by inspecting the trace plots
-AND BLAH to verify we can samples beyond an autocorrelation time.
+AND BLAH to verify we are sampling beyond an autocorrelation time.
 We employ $\sim$50,000 samples as the initial ``burn-in'' stage
-to stabilize the Markov chains (which we then discard).
-We then use the final $\sim$5,000 steps, sampled by 128 walkers.
-Here, we
+to stabilize the Markov chains (which we then discard) and
+use the final $\sim$5,000 steps, sampled by 128 walkers, to identify
+the posterior. Here, we
 identify the best-fit model and the quoted uncertainties using the
@@
 Using this $V_{\rm rot}$, we find a dynamical mass of
-$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 17\E{10}\,\Msun.
-If we instead consider the line peak separation from the
+$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
+within the CO-emitting region. If we instead consider the
+line peak separation from the
 \bco line profile $\Delta v_{\rm sep}/2 \sim$110\,\kms, we find
@@
 observed unobscured AGN and an observable double peak line profile.
-The dynamical mass is then 2.5\E{10}\Msun$<$$M_{\rm dyn}$($<$6 kpc)$<$25\E{10}\Msun.
-We caution that this analysis is based on limited spatial
+The dynamical mass is then
+2.5\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
+Since this quantity is derived under the assumption that the gas is
+virialized, which is highly unlikely given the velocity dispersion and the
+presence of a close companion, our estimate is
+at most a lower limit. We caution that this analysis is
+based on limited spatial
 resolution data and will be verified by future higher-resolution
@@
 Might want to add NVSS constraints.
+The data are not corrected for dust extinction.
  \label{fig:SED}}
@@
 \subsection{Physical properties}
+In this section, we derive the gas properties of RXJ1131 based on \bco,
+and compare the derived quantities against those reported by
+\citet[; hereafter C13]{Combes13a}, which is the largest sample of
+ULIRGs at intermediate redshift (0.6\,$<$\,$z$\,1.0) with CO measurements,
+to place RXJ1131 in context of existing studies. Their results are
+based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.
+
+%line width & extent
+We find that the linewidths for both components (redshifted and blueshifted)
+inferred from a double Gaussian fit to the \bco line profile are
+consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
+than in local ULIRGs (240\,\kms; \citet[][]{Solomon97a}).
+Since C13 do not have resolved observations, we compare the
+gas distribution (size) with local ULIRGs. The CO gas in RXJ1131 is
+distributed $\sim$6\,kpc in radius across (in
+the source plane), which is more extended than the
+sample of disk-like ULIRGs studied by \citet{Ueda14a},
+who find an average radius of 3.5\,$\pm$\,2.3\,kpc,
+(with a range from 1.1 kpc to 9.3 kpc).
+This indicates that the positive correlation in the linewidth-size relation
+holds in ULIRGs at intermediate redshifts. Yet we cannot quantify this further
+with the data represented in this paper.
+{\bf implication on this in discussion}
+% gas mass
+To derive the molecular gas mass, we first correct for lensing magnification
+using the respective magnification factors listed in \Tab{model}, which to
+first order takes into account effect of differential lensing. This yields
+$I$\,=\,5.9$\pm$2.7 Jy\,\kms, where the uncertainty includes those on
+the magnification factors. This includes the CO emission from the companion
+as the resolution of our data do not allow us decompose its contribution
+to the total line flux. Without direct \rot{1}{0} measurements,
+we derive \rot{1}{0} intensity
+using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
+solely to facilitate a comparison with the C13 sample. For the same reason, we
+adopt a luminosity-to-mass conversion factor of
+\alphaco\,=0.8 (K \kms pc$^2$)\pmOne. This yields
+\Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\Lsun and a gas mass
+of (2.8$\pm$1.3)\,\E{10} \Msun in RXJ1131. This is likely
+an overestimation due to a contribution from the companion, but is
+nevertheless consistent with C13 ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
+uncertainties. Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
+a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
+% gas to dust ratio:
+Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
+$f_{\rm gas-dust}$\,=\,BLAH, consistent with Combes+13: 206 ?
+ Typical local (U)LIRGs are found to have a
+gas-to-dust mass ratio of 200–350 (Sanders et al. 1991; Contini
+& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
+
+% SFE and depletion time
+
 \subsubsection{SB versus AGN contribution}
@@
 \section{Discussion}
-% summarize (conflicting ) results from recent studies.
-% lead way into our results
+% What are the conclusions of the paper (qualitative and/or quantitative)?
+% What is the evidence for those conclusions?
+
 \subsection{Mass in RXJ1131}
@@
 Assuming local $M_{\rm BH}-M_{\rm bulge}$ relation, this would imply $M_{\rm bulge}$$\sim$BLAH\Msun.
+
+% gas-dyn fraction:
+% can we quantify the merger stage of RXJ1131? what are typical gas fraction at different merger stage. What are the alpha CO used in those (0.8, see Uedaa14)
+% since ellipticals are not expected to have high gas fraction.
+The fact that there are on-going, recent, massive episodes of SF activity, the velocity gradient, and the best-fit sersic profile from C06 all support the picture that RXJ is a disk galaxy.
 
@@
 Kinematics and mergers:
-For major mergers, two galaxy mass centres separated on the same scale as the gas disk (4 kpc or more), the gas dynamics would be strongly perturbed and would deviate substantially from that of a simple disk.
+For major mergers, two galaxy mass centers separated on the same scale as the gas disk (4 kpc or more), the gas dynamics would be strongly perturbed and would deviate substantially from that of a simple disk.
 
@@
 mergers. Mergers are kinematically detectable for 0.2-0.4 Gyr
-between second passage and colaescence.
+between second passage and coalescence.
 
 Numerical simulations of mergers between two galaxies have shown that multiple, discrete starburst events can be triggered even in double mergers.
-The timing of the starbursts is thought to depend on the progenitor galaxy morphologies, with early starbursts (before the galaxies start to merge) occurring in bulgeless disc galaxies, and late starbursts (after the galaxies have started to merge) occur- ring in disc galaxies with a bulge component (Mihos \& Hernquist 1994, 1996.
-Maybe the more compact rest-frame SF and the more recent NIR SF, which is also more extended and diffuse is consistent with the spinning blackhole, i.e.
+The timing of the starbursts is thought to depend on the progenitor galaxy morphologies, with early starbursts (before the galaxies start to merge) occurring in bulges disc galaxies, and late starbursts (after the galaxies have started to merge) occur- ring in disc galaxies with a bulge component (Mihos \& Hernquist 1994, 1996.
+Maybe the more compact rest-frame SF and the more recent NIR SF, which is also more extended and diffuse is consistent with the spinning black hole, i.e.
 already encountered?
 
-\subsection{Implications}
+% ------------------------------------------------------------------------
+% How do these results relate to prior work?
+% What are the implications of this work – i.e. what theories are being tested/questions are being answered etc?
+
+% summarize (conflicting ) results from recent studies.
+% lead way into our results
+
+\subsection{ULIRG Evolution}
 At low redshifts the ULIRG luminosity function shows strong evolution with redshift (Veilleux et al. 1999).
@@
 
-What are the conclusions of the paper (qualitative and/or quantitative)?
-What is the evidence for those conclusions?
-How do these results relate to prior work?
-What are the implications of this work – i.e. what theories are being tested/questions are being answered etc?
-
 %--------------------------------------------------------------------------
@@
 % see Hodge12_dynamics.pdf for guide
+
+%- summarize the findings from the entire study
+%    - firm conclusions
+%    - speculative possibilities
+
 We observed the cold molecular gas properties using \bco and \cco line emission
@@
 ULIRG and a optically faint companion.
+
+Fitting SED models, we find that the AGN host galaxy is a ULIRG.
+A faint companion as seen in HST observations (BJB) is also detected in our CO, confirming it's redshift and gas rich nature.
+
+% any further work needed to resolve the remaining problems
 

### 2016-05-22 WRITEUP/ms.tex
comparison of gas and HST sizes

@@
 diffused emission in $V$-band (rest-frame UV),
-which traces recent massive \SF.
-% On the other hand, $I$-band traces the more evolved stellar population.
-This indicates that the molecular gas may be ....
-DR: ok, let's discuss this.
+which traces recent massive \SF. The may be explained in part
+due to the fact that $V$-band emission is
+more susceptible to dust extinction than other bands.
+The fact that the molecular gas (fuel for \SF) is more compact
+than emission in the $I$ and $H$-bands,
+which trace the more evolved stellar population, is consistent
+with the picture that stars diffuse outward
+after formation \citep{Calzetti01a}.
 
@@
 
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
-\caption{
-WISE flux is higher than the IRAC data, probably just due to smaller aperture used in IRAC.
-Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied.
-Spitzer/MIPS: PSF fit flux, as source size <
-native PSF FWHM of 6".
-Might want to add NVSS constraints.
-The data are not corrected for dust extinction.
- \label{fig:SED}}
-\end{figure*}
-
 We fit modified blackbody functions to
@@
 posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
+
+\begin{figure*}[tbph]
+\centering
+\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
+\caption{
+WISE flux is higher than the IRAC data, probably just due to smaller aperture used in IRAC.
+Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied.
+Spitzer/MIPS: PSF fit flux, as source size <
+native PSF FWHM of 6".
+Might want to add NVSS constraints.
+The data are not corrected for dust extinction.
+ \label{fig:SED}}
+\end{figure*}
 

### 2016-05-22 WRITEUP/ms.tex
proof-read

--- 2016-05-22 WRITEUP/ms.tex
@@
 
-The \ncode{GILDAS} package was used to reduce and analyze the visibility data
+The \ncode{gildas} package was used to reduce and analyze the visibility data
 which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
@@
 
-The \ncode{MIRIAD} package was used to calibrate the visibility data which are
+The \ncode{miriad} package was used to calibrate the visibility data which are
 then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
@@
 calibrator, yielding $\sim$10\% calibration accuracy.
-We use \ncode{AIPS} to calibrate the visibility data which
+We use \ncode{aips} to calibrate the visibility data which
 are then imaged and deconvolved using
@@
 described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
-correct for the fact that the IRAC imaging was calibrated
+correct for the fact that the imaging was calibrated
 using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
@@
 Extraction of the {\it Herschel}/SPIRE photometry was
-carried out using SUSSEXTractor within Herschel Interactive
+carried out using \ncode{sussextractor} within Herschel Interactive
 Processing Environment (HIPE; \citealt{Ott10a})
@@
 These maps were processed by the SPIRE pipeline
-version 13.0 within HIPE. The SUSSEXtractor task estimates
+version 13.0 within HIPE. The \ncode{sussextractor} task estimates
 the flux density from an image convolved with a kernel
 derived from the SPIRE beam. The flux density
-measured by SUSSEXtractor is additionally confirmed
+measured by \ncode{sussextractor} is additionally confirmed
 using the Timeline Fitter, which performs photometry
 by fitting a 2D elliptical Gaussian to the Level 1 data at the
-source position given by the output of SUSSEXtractor.
+source position given by the output of \ncode{sussextractor}.
 
@@
 properties on the intrinsic kinematics. The slices
-are obtained by binning the data (over the full linewidth
-$\sim$700\kms; see \Sec{CO21}) by five channels (i.e., into seven slices)
- to increase the SNR.
+are obtained by binning the data over the full linewidth
+$\sim$700\,\kms by five channels,
+that is, into seven slices, to increase the SNR.
 
@@
 is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
-and the effective radius is allowed to vary from 0\farcs01$-$2".
+and the effective radius is allowed to vary from 0\farcs01$-$2$^{\prime\prime}$.
 
@@
 an intrinsic velocity gradient across the source plane, which is
-indicative of a disk geometry. While solely based on the
+indicative of a disk-like galaxy. While solely based on the
 lens model is insufficient to draw conclusive inference on its
@@
 merger (major v.s. minor) with a mass ratio given the
-spatial resolution, the symmetric velocity gradient may lean support
-towards a minor merger.
+spatial resolution, the symmetric velocity gradient lean support
+to the case of a minor merger.
 
@@
 intrinsic sizes of the lensed galaxies, and thus the magnification
-factors ares likely under-predicted.
+factors are likely under-predicted.
 We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15
@@
 \input{table_magFactor}
-Previous lens models of RXJ1131 find conspicuous
-differential lensing effect across {\it HST}
+Previous lens models of RXJ1131 find evidence for
+differential lensing across {\it HST}
 $H$-, $V$-, and $I$-band (C06), where the
@@
 the decrease toward the IR regime is caused by the more extended
-IR emission, arising from \SF.
-The highly asymmetric \bco line profile suggests that
+IR emission. The highly asymmetric \bco line profile suggests that
 differential lensing is also non-negligible for CO, where the redshifted
 emission is apparently much brighter than that in the
-blueshifted emission, consistent
+blueshifted part, consistent
 with the source positions relative to the caustics in \Fig{model}.
@@
 This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
-radius $\sim$10.3\,kpc inferred from the C06 lens model (converted to
-our cosmology) over the {\it HST} $I$-band image.
+radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
+lens model (C06; converted to
+our cosmology).
 We note that the source plane half-light radius varies substantially with
-wavelength: $R_e$ $\sim$\,4kpc and $\sim$7\,kpc based on models over
-$V$-band \citep{Brewer08a} and $H$-band (C06), respectively.
+wavelength. In particular, the half-light radius is found to be
+$\sim$\,4kpc and $\sim$7\,kpc in $V$-band
+\citep{Brewer08a} and $H$-band (C06), respectively.
 This discrepancy arises owing to the exclusion of the more
 diffused emission in $V$-band (rest-frame UV),
-which traces recent massive \SF.
-% On the other hand, $I$-band traces the more evolved stellar population.
-This indicates that the molecular gas may be ....
-DR: ok, let's discuss this.
+which traces young massive stars. 
+The $V$-band compactness may be explained in part
+due to the fact that its emission is
+more susceptible to dust extinction than other bands.
+On the other hand, the molecular gas (fuel for \SF) is more compact
+than the more evolved stellar population, as traced by $I$ and $H$-bands.
+This is consistent with the picture that stars diffuse outward
+after their formation \citep{Calzetti01a}.
 
-Using this $V_{\rm rot}$, we find a dynamical mass of
-$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
+Using the $V_{\rm rot}$ from last paragraph, we find a dynamical mass of
+$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$\,=\,17\E{10}\,\Msun enclosed
 within the CO-emitting region. If we instead consider the
@@
 $M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 1.8\E{10}\,\Msun.
-DR: here, I list the extrema for possible Mdyn given our data,
-should I say anything more?
+{\bf DR: here, I list the extrema for possible Mdyn given our data,
+should I say anything more?}
 We correct for the inclination effect using the
@@
 based on limited spatial
-resolution data and will be verified by future higher-resolution
+resolution data and will be verified with future higher-resolution
 observations.
@@
 This is consistent with the mean spectral slope of optical quasars
-(optically-selected) ($\alpha\sim-$1, Elvis et al. 1994;
-Neugebauer et al. 1979).
+($\alpha\sim-$1, Elvis et al. 1994; Neugebauer et al. 1979).
 For comparison, broad-line AGN from the AGN and Galaxy
-Evolution Survey (AGES, C. S. Kochanek et al., in prep) have 3.6$-$8 \micron slopes of $\alpha$ = $-$1.07$\pm$0.53 (Stern et al. 2005).
+Evolution Survey (AGES, C. S. Kochanek et al., in prep) have 3.6$-$8
+\micron slopes of $\alpha$ = $-$1.07$\pm$0.53 (Stern et al. 2005).
 
@@
 
-We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side.
-We include the IRAS 60\micron and 100\micron upper limits to constrain the dust peak.
-We also fit SED models including the decomposed 24.0\micron data (see \Sec{photometry})
+% describe the SED model
+We fit SED models to the photometry from BLAH$-$BLAH \micron
+using a modified-blackbody function
+with a power-law attached to the blue side.
+% We added blah\% calibration uncertainties on the PdBI data.
+We include
+the IRAS 60\micron and 100\micron upper limits
+to constrain the dust peak. We also fit SED models
+including the decomposed 24.0\micron data.
+identical to the modified blackbody fit,
+where the Wien side is removed and replaced by MIR power-law consistent with any mid-IR data available.
+We find a power-law slope of BLAH,
+Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
 
-Spitzer mid-IR spectroscopy of local ULIRGs will indicate the appropriate luminosity fraction that needs to be assigned to the AGN for ULIRGs before and after nuclear coalescence.
-ULIRG Lir
-Our SED model find a rest-frame characteristic dust temperature of BLAH (cf. 60-70K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10)
+% describe mbb_emcee
+We check convergence of our chains by requiring that the autocorrelation length for each model parameter is
+several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
+The code treats the instrument response.
+flux using the set of photometric filters used to obtain the observations.
+% parameter estimation problem
+For these parameter estimation problems using MCMC to sample,
+the full answer is the full joint posterior PDF.
+We here report the summary statistics (global mode (where min. chi),
+marginal mode (in log file),
+posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
+
+% upper limit using decomposed 24 um
+% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
+The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
+Our SED model find a rest-frame characteristic dust temperature of BLAH
+(cf. 60$-$70\,K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10),
+\fir (rest-frame 42.5-122.5 \micron) of blah, and a dust mass of blah.
+For the mass absorption coefficient, we adopt BLAH (rest frame; Dunne et al. 2003).
 
@@
 
-We fit modified blackbody functions to
-to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt
-BLAH (rest frame; Dunne et al. 2003).)
-We added blah\% calibration uncertainties on the PdBI data.
+\subsubsection{SB versus AGN contribution}
 
-We check convergence of our chains by requiring that the autocorrelation length for each model parameter is
-several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
-The code treats the instrument response.
-flux using the set of photometric filters used to obtain the observations.
+We correct for lensing magnification using the median among our models ($\mu_{\rm L}$=BLAH).
+Assuming a Salpeter initial mass function, we find the SFR of blah using the \fir luminosity after corrected for lensing .
 
-identical to the modified blackbody fit,
-where the Wien side is removed and replaced by MIR power-law consistent with any mid-IR data available.
-We find a power-law slope of BLAH,
-Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
-
-% upper limit using decomposed 24 um
-% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
-The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
-% parameter estimation problem
-For these parameter estimation problems using MCMC to sample,
-the full answer is the full joint posterior PDF.
-We here report the summary statistics (global mode (where min. chi),
-marginal mode (in log file),
-posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
-
-\subsection{Physical properties}
+\subsection{Gas properties}
 In this section, we derive the gas properties of RXJ1131 based on \bco,
 and compare the derived quantities against those reported by
-\citet[; hereafter C13]{Combes13a}, which is the largest sample of
-ULIRGs at intermediate redshift (0.6\,$<$\,$z$\,1.0) with CO measurements,
+\citet[hereafter C13]{Combes13a}, which is the largest sample of
+ULIRGs at intermediate redshift (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements,
 to place RXJ1131 in context of existing studies. Their results are
@@
 
-%line width & extent
+\subsubsection{Linewidth \& Sizes}
 We find that the linewidths for both components (redshifted and blueshifted)
-inferred from a double Gaussian fit to the \bco line profile are
+inferred from a double Gaussian fit to the line profile are
 consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
-than in local ULIRGs (240\,\kms; \citet[][]{Solomon97a}).
+than in local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
 Since C13 do not have resolved observations, we compare the
@@
 distributed $\sim$6\,kpc in radius across (in
-the source plane), which is more extended than the
+the source plane), which is more extended than the average in the
 sample of disk-like ULIRGs studied by \citet{Ueda14a},
-who find an average radius of 3.5\,$\pm$\,2.3\,kpc,
+who find an average radius of 3.5\,$\pm$\,2.3\,kpc
 (with a range from 1.1 kpc to 9.3 kpc).
 This indicates that the positive correlation in the linewidth-size relation
-holds in ULIRGs at intermediate redshifts. Yet we cannot quantify this further
+holds at intermediate redshifts. Yet we cannot quantify this further
 with the data represented in this paper.
-{\bf implication on this in discussion}
-% gas mass
+
+\subsubsection{Gas Mass}
 To derive the molecular gas mass, we first correct for lensing magnification
@@
 $I$\,=\,5.9$\pm$2.7 Jy\,\kms, where the uncertainty includes those on
-the magnification factors. This includes the CO emission from the companion
-as the resolution of our data do not allow us decompose its contribution
-to the total line flux. Without direct \rot{1}{0} measurements,
+the magnification factors. 
+We note that the derived intensity includes emission from the companion
+as the spatial resolution of our data do not allow us decompose its contribution
+to the total line flux.
+
+Without direct \rot{1}{0} measurements,
 we derive \rot{1}{0} intensity
@@
 adopt a luminosity-to-mass conversion factor of
-\alphaco\,=0.8 (K \kms pc$^2$)\pmOne. This yields
+\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields
 \Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\Lsun and a gas mass
-of (2.8$\pm$1.3)\,\E{10} \Msun in RXJ1131. This is likely
+of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
 an overestimation due to a contribution from the companion, but is
-nevertheless consistent with C13 ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
-uncertainties. Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
+nevertheless consistent with the C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
+uncertainties.
+
+% gas-to-dyn ratio
+Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
 a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
@@
  Typical local (U)LIRGs are found to have a
-gas-to-dust mass ratio of 200–350 (Sanders et al. 1991; Contini
-& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
+gas-to-dust mass ratio of 200$-$350 (Sanders et al. 1991; Contini
+\& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
 
-% SFE and depletion time
-
-\subsubsection{SB versus AGN contribution}
-
-We correct for lensing magnification using the median among our models ($\mu_{\rm L}$=BLAH).
-Assuming a Salpeter initial mass function, we find the SFR of blah using the \fir luminosity after corrected for lensing .
-
-\subsubsection{Gas properties}
-% Gas, dynamical, etc
-Since RXJ1131 has a companion, i.e. not dynamically relaxed, the dynamical mass estimate using a virial estimator is likely underestimated.
-
-\subsubsection{SF and Molecular Gas}
-C06: 814
+\subsubsection{SFE and Depletion Time}
+dot dot dot
 

### 2016-05-23 WRITEUP/ms.tex
added discussion on merger

@@
 the ``companion'' is instead a gas component/tidal feature ripped out
-from previous interaction. In the subsequent sections, we will interpret
+from previous interaction.
+In the subsequent sections, we will interpret
 the this additional source component as gas emission
@@
 merger (major v.s. minor) with a mass ratio given the
-spatial resolution, the symmetric velocity gradient lean support
-to the case of a minor merger.
+spatial resolution, the symmetric velocity gradient retained under
+such close separation between the two lean support
+to the idea of a minor merger.
+% For major mergers, two galaxy mass centers separated on the same scale as the
+% gas disk (4 kpc or more), the gas dynamics would be strongly perturbed and
+% would deviate substantially from that of a simple disk.
+% In a minor merger (a mass ratio of more than 3:1) the more massive galaxy, including its gas distribution, can retain a significant angular momentum and resemble a rotating disk.
 
-We emphasize that the spatial resolution of the data at hand
+We emphasize that the spatial resolution of the data in hand
 is a few arcsec, which implies that despite the high SNR and spectral
@@
 marginal mode (in log file),
-posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
+posterior median (instead of posterior means; need to compute) and the
+1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
 
@@
 % lower limit using fit without 24 um, but do I still want to fit a power-law for this?
-The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
+The best-fit SEDs are shown in \Fig{SED} and the resulting parameters
+are listed in \Tab{SED}.
 Our SED model find a rest-frame characteristic dust temperature of BLAH
@@
 \subsubsection{SB versus AGN contribution}
-
-We correct for lensing magnification using the median among our models ($\mu_{\rm L}$=BLAH).
-Assuming a Salpeter initial mass function, we find the SFR of blah using the \fir luminosity after corrected for lensing .
+To derive the intrinsic properties, we correct for lensing using the 
+median magnification factor derived from the CO lens models.
+Assuming a Salpeter initial mass function, we find the SFR of blah using the 
+lensing-corrected \fir luminosity.
 
@@
 consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
-than in local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
+than local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
 Since C13 do not have resolved observations, we compare the
-gas distribution (size) with local ULIRGs. The CO gas in RXJ1131 is
+gas distribution with local ULIRGs. The CO gas in RXJ1131 is
 distributed $\sim$6\,kpc in radius across (in
@@
 first order takes into account effect of differential lensing. This yields
-$I$\,=\,5.9$\pm$2.7 Jy\,\kms, where the uncertainty includes those on
+$I_{\tiny \bco}$\,=\,5.9$\pm$2.7 Jy\,\kms, where the uncertainty includes those on
 the magnification factors.
@@
 as the spatial resolution of our data do not allow us decompose its contribution
-to the total line flux.
+from the total line flux.
 
@@
 \section{Discussion}
-% What are the conclusions of the paper (qualitative and/or quantitative)?
-% What is the evidence for those conclusions?
+\subsection{Merger stage of RXJ1131-1231}
+In this section, we put our results in context with other ULIRGs/mergers at
+$z$\,=\,0$-$1. It is clear that RXJ1131 has a gas-rich companion, but how does
+this affect its internal dynamics and what is the merger stage of RXJ1131?
+We argued that the symmetric source-plane velocity field suggest
+the system is a minor merger, consistent with an earlier study by B08, who
+independently conclude that the companion is likely
+a dwarf of size $\sim$700\,kpc across.
+While our result is consistent with previous studies of RXJ1131, this
+contrast strongly with studies of mergers, where powerful AGN are
+usually found in late stage mergers (Yuan+10, Iwasawa+11) and
+that only major mergers near their final
+coalescence can power/provide \LIR\,$>$\,10$^{12}$\,\Lsun, based on
+a recent study of a sample of 65 local U/LIRGs
+(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1; Larson+16).
+If this is also the case at $z$$\sim$0.65, this would imply RXJ1131
+is a major merger near its final coalescence and that the spatially offset
+component is an expulsion of gas driven by AGN winds or is some
+tidally ejected material from previous passage.
+In that case, the molecular gas fraction in the host
+galaxy should have declined (as in ellipticals) compared to early
+stage mergers (can we find molecular gas mass fraction as a
+function of merger stage?) and that the molecular gas would
+be more concentrated in the nuclear region.
+This is inconsistent with what
+is observed (which strongly favors a disk morphology; 
+but there are outliers --  Ueda+14 find
+extended molecular gas in merger remnant) and
+the fact that there is on-going \SF activity.
+Hence, we reject this and speculate the discrepancy is a consequence
+of (the power source of) IR luminous galaxies are already very different by this redshift.
+An alternative explanation might be that the
+CO is less strongly-magnified as compared to the dust emission,
+in which case, the lensing-corrected \LFIR is overestimated.
+This is plausible given the extent of the source with respect to the caustics
+and that substantial differential lensing effect has been seen across CO and other
+wavelengths. If we instead use the NIR ($H$-band) magnification factor ($\mu_{\rm L}$\,=\,BLAH; C06), 
+we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is consistent with a minor
+merger in the context of the results reported by Larson+16.
 
-\subsection{Mass in RXJ1131}
-black hole mass
-dynamical mass
-stellar mass
-dust mass
-
-Assuming local $M_{\rm BH}-M_{\rm bulge}$ relation, this would imply $M_{\rm bulge}$$\sim$BLAH\Msun.
-
-% gas-dyn fraction:
-% can we quantify the merger stage of RXJ1131? what are typical gas fraction at different merger stage. What are the alpha CO used in those (0.8, see Uedaa14)
-% since ellipticals are not expected to have high gas fraction.
-The fact that there are on-going, recent, massive episodes of SF activity, the velocity gradient, and the best-fit sersic profile from C06 all support the picture that RXJ is a disk galaxy.
-
-\subsection{Merger stage of RXJ1131-1231}
-We put our results in content with ULIRGs/mergers in $z$=0$-$1.
-
-As discussion in previous sections, while we see evidence such as a symmetric velocity field in the source plane, double-horned profile, observed velocity
-gradient, C06 model $n$=1 Sersic profile, which suggest that RXJ1131 is likely a rotating disc.
-Yet, this is insufficient to conclude a disk morphology.
-Additional characteristics such as peak velocity dispersion at the central region and a ``spider'' diagram are needed, which is commonly seen in local spirals.
-\\
-
-Kinematics and mergers:
-For major mergers, two galaxy mass centers separated on the same scale as the gas disk (4 kpc or more), the gas dynamics would be strongly perturbed and would deviate substantially from that of a simple disk.
-
-In a minor merger (a mass ratio of more than 3:1) the more massive galaxy, including its gas distribution, can retain a significant angular momentum and resemble a rotating disk.
-
-RXJ kinematics:
-The smooth, symmetric velocity field seen in our lens model and image plane
-suggest a kinematically-order (i.e., disk) galaxy. However, the high
-dispersion near the dynamical center suggest that RXJ1131 is turbulent, albeit
-lack of spatial resolution. Overall implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution data are needed to confirm this.
-Although these values are discussed in \Sec{blah} we cannot draw any general conclusions concerning BLAH.
+\subsubsection{Fate of RXJ1131-1231}
+Has RXJ1131 encountered with the companion?
 
@@
 
-Numerical simulations of mergers between two galaxies have shown that multiple, discrete starburst events can be triggered even in double mergers.
-The timing of the starbursts is thought to depend on the progenitor galaxy morphologies, with early starbursts (before the galaxies start to merge) occurring in bulges disc galaxies, and late starbursts (after the galaxies have started to merge) occur- ring in disc galaxies with a bulge component (Mihos \& Hernquist 1994, 1996.
-Maybe the more compact rest-frame SF and the more recent NIR SF, which is also more extended and diffuse is consistent with the spinning black hole, i.e.
-already encountered?
+Numerical simulations of mergers have shown that
+multiple starburst episodes can be triggered even in double mergers.
+The timing of the starbursts is thought to depend on the progenitor galaxy
+morphologies, with early starbursts (before the galaxies start to merge)
+occurring in bulges disc galaxies, and late starbursts (after the galaxies
+have started to merge) occurring in disc galaxies with a bulge component (Mihos \& Hernquist 1994, 1996.
+The spinning black hole already encountered?
 
-% ------------------------------------------------------------------------
-% How do these results relate to prior work?
-% What are the implications of this work – i.e. what theories are being tested/questions are being answered etc?
+The future of RXJ1131:
+classical picture is that merger will evolve into local ellipticals, but more
+recent studies (springel \& Hernquist 05, cite) suggest that mergers can also
+form local large-disks (bulge dominated) $<--$ double check this. Given the
+extended molecular gas distribution, we suggest RXJ1131 may evolve into the
+latter (large-disk) unless the ``companion'' BKAH SOME STUFF or some other
+mechanisms at play in the latter stage, transporting the gas
+toward the central nuclear region.
 
-% summarize (conflicting ) results from recent studies.
-% lead way into our results
+\subsection{ULIRG Evolution and Cosmic SFH}
+At low redshifts, the luminosity function of ULIRG shows strong evolution with
+redshift (Veilleux et al. 1999). It is not known whether the IR luminosity of
+these high-$z$ sources arises due to mergers between two or more large spiral
+galaxies, as in local ULIRGs, or via a different mechanism/galaxy formation
+processes at high-z.
 
-\subsection{ULIRG Evolution}
-At low redshifts the ULIRG luminosity function shows strong evolution with redshift (Veilleux et al. 1999).
-not known whether the IR luminosity of these high- redshift sources arises due to mergers between two or more large spiral galaxies, as in local ULIRGs, or via a different mechanism/galaxy formation processes at high-z.
+% AGN contribution.
 
-gas fraction at this redshift. how does that relate to
-the SFH, and the change in cosmic SFD is due to change in gas content.
-SFE at this redshift, how does that relate to the SFH. probably a secondary effect to the drop in SFH
+% Implication on SFH
+Our result indicates that the gas mass fraction has already decreased
+at this redshift, which may suggest that the change in cosmic SFD is due to
+change in gas content. The SFE is also BLAH at this redshift,
+consistent with current speculation of how the SFRD decreases over cosmic time.
 
@@
 % any further work needed to resolve the remaining problems
+We list several pieces of evidence through out
+this work to argue that RXJ1131 is likely a rotating disk.
+The double-horned profile, smooth, symmetric velocity field
+seen in our lens model and in the
+image plane and C06 model $n$=1 Sersic profile all suggest
+a kinematically-order (i.e., disk) galaxy.
+Yet, these are insufficient to conclude a disk morphology. Additional
+characteristics such as peak velocity dispersion at the central region and a
+``spider'' diagram are needed, which is commonly seen in local spirals.
+The high dispersion near the dynamical center also
+suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. Overall
+implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution
+data are needed to confirm this.
 

### 2016-05-23 WRITEUP/ms.tex
update ref

@@
 a dwarf of size $\sim$700\,kpc across.
-While our result is consistent with previous studies of RXJ1131, this
-contrast strongly with studies of mergers, where powerful AGN are
-usually found in late stage mergers (Yuan+10, Iwasawa+11) and
+
+While our result is consistent with other studies of RXJ1131, it
+contrast strongly with studies of local (U)LIRGs/mergers
+(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1), where active AGN are
+typically found in late stage mergers
+\citep{Yuan10a,Iwasawa11a,Carpineti12a} and
 that only major mergers near their final
-coalescence can power/provide \LIR\,$>$\,10$^{12}$\,\Lsun, based on
-a recent study of a sample of 65 local U/LIRGs
-(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1; Larson+16).
+coalescence can provide \LIR\,$>$\,10$^{12}$\,\Lsun,
+\citep[\eg][]{Carpineti15a,Larson16a}.
 If this is also the case at $z$$\sim$0.65, this would imply RXJ1131
@@
 is observed (which strongly favors a disk morphology;
-but there are outliers --  Ueda+14 find
+but there are outliers --  \citet{Ueda14a} find
 extended molecular gas in merger remnant) and
@@
 of (the power source of) IR luminous galaxies are already very different by this redshift.
+
 An alternative explanation might be that the
@@
 we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is consistent with a minor
-merger in the context of the results reported by Larson+16.
+merger in the context of the results reported by \citet{Carpineti15a} and \citet{Larson16a}.
 

### 2016-05-24 WRITEUP/ms.tex
MIPS 24 micron

@@
 The photometries for the foreground galaxy are then obtained
-by subtracting the fluxes decomposed for the background source
-from the observed total flux. The resulting photometry in
+by subtracting the background emission from the
+observed total flux. The resulting photometry in
 \Tab{photometry} are obtained after performing aperture correction
@@
 using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
-perform aperture photometry. This step was taken to provide
-constraints on the Wien tail beyond the dust peak of the
-spectral energy distribution (SED) of RXJ1131.
+perform aperture photometry.
+We then fit a power-law spectrum $S_\nu \propto \nu^\alpha$ to the
+decomposed IRAC photometry to disentangle the observed total flux
+at MIPS 24\micron. We find a spectral index of $\alpha\sim-$1.8 and
+$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
+This is consistent with the mean 3.6$-$8\micron spectral slope of
+$\alpha$\,=\,$-$1.07$\pm$0.53 found for unobscured AGN
+\citep{Stern05a}. An extrapolation of the fit to 24\micron
+yields 33.96$\pm$0.01\,mJy and 25.19\,$\pm$\,0.03\,mJy
+for the foreground galaxy and RXJ1131, respectively.
+We note that the IRAC photometry includes
+contributions from old stellar population and is prone to
+dust extinction. Hence, the decomposed fluxes are only
+our best estimate of the warm dust emission.
+We incorporate the decomposed 24\micron point in our
+SED fitting to provide some constraints on
+the Wien tail beyond the dust peak
+of the spectral energy distribution (SED) of RXJ1131.
 Details of the SED modeling is presented in \Sec{SED}.
@@
 
-% Check with Shane
-{\bf NEEDS EDIT}
 Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
@@
 In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
-and check for chain convergence by inspecting the trace plots
-AND BLAH to verify we are sampling beyond an autocorrelation time.
-We employ $\sim$50,000 samples as the initial ``burn-in'' stage
+and check for chain convergence by inspecting trace plots
+and requiring the samples are beyond at least an autocorrelation time.
+We thus employ $\sim$50,000 samples as the initial ``burn-in'' phase
 to stabilize the Markov chains (which we then discard) and
@@
 1$\sigma$ uncertainties on the source plane positions.
-DR may suggest include MC simulation fits, maybe I will do that later.
+DR may suggest include 68\& fits from MC simulation, maybe I will do that later.
  \label{fig:PV}}
@@
 \subsection{SED modeling} \label{sec:SED}
-By fitting a power-law spectrum $S_\nu \propto \nu^\alpha$ to the decomposed
-IRAC photometry. We find a spectral index of $\alpha\sim-$1.9 and
-$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
-This is consistent with the mean spectral slope of optical quasars
-($\alpha\sim-$1, Elvis et al. 1994; Neugebauer et al. 1979).
-For comparison, broad-line AGN from the AGN and Galaxy
-Evolution Survey (AGES, C. S. Kochanek et al., in prep) have 3.6$-$8
-\micron slopes of $\alpha$ = $-$1.07$\pm$0.53 (Stern et al. 2005).
+We fit dust SED models to the
+24\micron$-$2.2\,mm photometry in \Tab{photometry}, where we also
+include the IRAS 60\micron and 100\micron upper limits
+to constrain the dust peak.
+The fit is performed with the code
+\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which
+uses instrumental response curves to perform color correction on-the-fly.
+The first SED model is a modified-blackbody
+function with a power-law attached to the
+blue/Wien side to account for an excess in the MIR owing to warm dust emission.
+%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
+%uncertainties for the PdBI continuum in our fitting procedure.
 
-We extrapolated a power-law to 24 \micron to decompose the flux
-at 24 \micron in MIPS.
-Since the contribution from AGN is not taken into account in SBURT, it is expected that the SEDs of AGN candidates show an excess in the MIR, owing to hot dust around the central massive black hole,
-NIR not corrected for extinction.
-
-% describe the SED model
-We fit SED models to the photometry from BLAH$-$BLAH \micron
-using a modified-blackbody function
-with a power-law attached to the blue side.
-% We added blah\% calibration uncertainties on the PdBI data.
-We include
-the IRAS 60\micron and 100\micron upper limits
-to constrain the dust peak. We also fit SED models
-including the decomposed 24.0\micron data.
-identical to the modified blackbody fit,
-where the Wien side is removed and replaced by MIR power-law consistent with any mid-IR data available.
 We find a power-law slope of BLAH,
-Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
 
 % describe mbb_emcee
-We check convergence of our chains by requiring that the autocorrelation length for each model parameter is
-several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
-The code treats the instrument response.
-flux using the set of photometric filters used to obtain the observations.
+We check for chain convergence by requiring the autocorrelation
+length for each model parameter is less than the number of steps
+taken during the burn-in phase (which are then discarded).
 % parameter estimation problem
@@
 For the mass absorption coefficient, we adopt BLAH (rest frame; Dunne et al. 2003).
+Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
+
+We also fit an SED model excluding the decomposed 24.0\micron data.
 
@@
 \caption{
-WISE flux is higher than the IRAC data, probably just due to smaller aperture used in IRAC.
-Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied.
+WISE flux is slightly higher than the IRAC point, probably due to a smaller
+aperture used in IRAC extraction, both of which were taken from the archive.
+Spitzer IRAC:
+Aperture flux in 5\farcs diameter with aperture correction applied.
 Spitzer/MIPS: PSF fit flux, as source size <
@@
 \subsubsection{SB versus AGN contribution}
+% brief argument
+What does it imply to the dust properties if we see the QSO.. contribution to the hot dust is not as much as if we were viewing it edge-on? --> warm dust and cold dust.
+
+We quantify the AGN contribution to total IR.
+important how the power source differ from high-z or local.
+
 To derive the intrinsic properties, we correct for lensing using the

### 2016-05-24 src/SED/SEDplot.py

@@ -2,10 +2,15 @@
 
 Plot SED
 
-Last Modified: May 13 2016
+Last Modified: May 24 2016
 
 History
 -------
+May 24 2016:
+    - add using MC to get uncertainties on 24 um
+    - use MC best-fit for quote spectral index
+May 19 2016:
+    - add using MC to get uncertainties on IRAC MIR fit
 May 15 2016:
     - curve_fit to power_law working
     - but extrapolated flux > MIPS point
@@ -146,31 +151,102 @@ fluxErr_fg = np.asarray(tblWithErr_fg['Flux Err [mJy]'])
 
 # --------------- Fit slope -------------------------
 def powerf(x, prefact, index):
-    return prefact * x**index
-ppower = [1.0, 1.]
-import scipy.optimize as optimize
-p_fg, pcov_fg = optimize.curve_fit(powerf, wave_fg[3:7],
-                                   flux_fg[3:7], p0=[0.9, 1],
-                                   sigma=fluxErr_fg[3:7], absolute_sigma=True, maxfev=10000)
-perr_fg = np.sqrt(np.diag(pcov_fg))
+    '''
+    parameters
+    ----------
+    x: np.array
+        wavelength in micron
+    prefact: float
+    index: float
+    '''
+    # convert wavelength to freq, s.t. we can compare index with literature
+    from astropy.constants import c
+    x_hz = c.value / (x * 1e-6)
+    x_ghz = x_hz / 1.e9
+    return prefact * x_ghz**index
 
+def MC_simulation(ydata, yerr, func, p0, xdata, nsam=500, CI=1., debug=False):
+    '''
+    monte-carlo: generates random data points starting from the given data plus a random variation based on the systematic error, take into acct systematic uncertainties
+
+    Parameters
+    ----------
+    CI: float
+        1 <=> 68.3%
+
+    '''
+
+    ps = []
+    for i in range(nsam):
+        randomDelta = np.random.normal(0., yerr, size=len(ydata))
+        randomdataY = np.array(ydata) + randomDelta
+
+        if debug:
+            # verify it's drawing from distribution we expect
[…]

### 2016-05-24 WRITEUP/ms.tex
SED section close to done

@@
 \citestyle{aa}
-\shorttitle{Something goes here}
+\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131 at $z$\,=\,0.65}
 \shortauthors{Leung \& Riechers}
@@
 wavelengths, the lensed emission would be more accurately described by an
-annulus, enclosing the partially complete ``Einstein Ring" and
+annulus, enclosing the partially complete ``Einstein Ring'' and
 the lensed knots (see \Fig{CO21mom}).
@@
 channel maps of 21.5\,\kms width and spatial spectra of 1\farcs5 resolution in
-\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures show that emission
-is present to the West and peaks toward the lensing arc (black across in \Fig{chanmap})
-in the red wing, and shifts to the East with decreasing velocity (blue wing).
+\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
+show that emission
+is present to the West, peaking toward the lensing arc (black across in
+\Fig{chanmap}) in the red wing, and shifts to the East with decreasing velocity
+(blue wing).
 This indicates extended emission in the source plane, where
@@
 relative to the caustics. One consequence of such is the observed asymmetric
-line profile. A detailed analysis on differential lensing of \bco is presented in \Sec{differential}.
+line profile. A detailed analysis on differential lensing of \bco is presented
+in \Sec{differential}.
 
@@
 the this additional source component as gas emission
-in a nearby galaxy (i.e. a ``wet-wet'' merger), as suggested by previous studies of RXJ1131.
+in a nearby galaxy (i.e. a ``wet-wet'' merger), as suggested by previous studies of RXJ1131 (C06, B08).
 
@@
 We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
-1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
+1.2$\pm$0.2 mJy, with a peak flux
+$S_\nu$\,=\,800$\pm$88\,\micron Jy\,beam\pmOne
 centering on the lensing galaxy. A slightly extended emission is also seen
@@
 We subtract a point source model in $uv$-plane to remove the unresolved
-emission toward the foreground galaxy. The peak flux (0.389$\pm$0.082 mJy)
+emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
 in the residual map coincides with the lensed arc, and is consistent with
@@
 decomposed IRAC photometry to disentangle the observed total flux
-at MIPS 24\micron. We find a spectral index of $\alpha\sim-$1.8 and
+at MIPS 24$\micron$. We find a spectral index of $\alpha\sim-$1.8 and
 $\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
-This is consistent with the mean 3.6$-$8\micron spectral slope of
-$\alpha$\,=\,$-$1.07$\pm$0.53 found for unobscured AGN
-\citep{Stern05a}. An extrapolation of the fit to 24\micron
-yields 33.96$\pm$0.01\,mJy and 25.19\,$\pm$\,0.03\,mJy
+This is consistent with the mean 3.6$-$8\,$\micron$
+spectral slope of
+$\alpha$\,=\,$-$1.07\,$\pm$\,0.53 found for unobscured AGN
+\citep{Stern05a}. An extrapolation of the fit to 24$\micron$
+yields 33.96\,$\pm$\,0.01\,mJy and 25.19\,$\pm$\,0.03\,mJy
 for the foreground galaxy and RXJ1131, respectively.
 We note that the IRAC photometry includes
-contributions from old stellar population and is prone to
+emission from old stellar population and is prone to
 dust extinction. Hence, the decomposed fluxes are only
 our best estimate of the warm dust emission.
-We incorporate the decomposed 24\micron point in our
+We incorporate the decomposed 24$\micron$ point in our
 SED fitting to provide some constraints on
@@
 
-We attempt to characterize the molecular gas kinematics using an empirically motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
+We attempt to characterize the molecular gas kinematics using an
+empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
 \begin{equation}
@@
 We fit dust SED models to the
-24\micron$-$2.2\,mm photometry in \Tab{photometry}, where we also
-include the IRAS 60\micron and 100\micron upper limits
+24\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
+include the IRAS 60$\micron$ and 100$\micron$ upper limits
 to constrain the dust peak.
 The fit is performed with the code
-\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which
-uses instrumental response curves to perform color correction on-the-fly.
-The first SED model is a modified-blackbody
+\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which samples the posterior
+using an MCMC approach and uses instrumental
+response curves to perform color correction on-the-fly.
+The SED model consists of a modified-blackbody
 function with a power-law attached to the
-blue/Wien side to account for an excess in the MIR owing to warm dust emission.
+Wien side to account for an excess in the MIR owing to warm,
+small dust emission.
+% Previous studies find that in the absence of mid-IR data, a powerlaw slope
+% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
+%
 %We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
 %uncertainties for the PdBI continuum in our fitting procedure.
+The model is thus described by five free parameters: the rest-frame characteristic dust
+temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
+($\alpha$), the flux normalization at 500$\micron$ ($f_{\rm norm}$), and
+the observed-frame wavelength at which the emission
+becomes optically thick ($\lambda_{0}$). We impose
+an upper limit of 100\,K on $T_d$, a Gaussian prior centered around
+$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
+1000$\micron$ on $\lambda_0$.
+We check for chain convergence by requiring the autocorrelation
+length of each parameter to be less than the number of steps
+taken for the burn-in phase (which are then discarded).
+Here we report the modes %in log file
+% summary statistics (global mode (where min. chi),
+% marginal mode (in log file), posterior median (instead of posterior means;
+% need to compute)
+and the 1$\sigma$ confidence intervals in the marginal PDFs
+as the best-fit parameters, as listed in \Tab{SED}.
 
-We find a power-law slope of BLAH,
+\input{table_mbb}
 
-% describe mbb_emcee
-We check for chain convergence by requiring the autocorrelation
-length for each model parameter is less than the number of steps
-taken during the burn-in phase (which are then discarded).
-% parameter estimation problem
-For these parameter estimation problems using MCMC to sample,
-the full answer is the full joint posterior PDF.
-We here report the summary statistics (global mode (where min. chi),
-marginal mode (in log file),
-posterior median (instead of posterior means; need to compute) and the
-1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.
+In the first model, we include the 24$\micron$ data
+to constrain the power-law index. Based on the
+best-fit of this model, we find a
+\fir luminosity (rest-frame 42.5-122.5\,$\micron$) of
+3.81\petm{2.04}{-1.92}\E{12}\,\Lsun and a
+dust mass of 22\petm{5}{-18}\E{8}\,\Msun.
+For the mass absorption coefficient, we adopt
+$\kappa$\,=\,2.64\,m$^2$kg\pmOne at 125.0$\micron$
+(rest frame; \citealt{Dunne03a}).
+The dust mass uncertainty does not
+include those in the absorption coefficient.
+These values are not corrected for lensing.
 
-% upper limit using decomposed 24 um
-% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
-The best-fit SEDs are shown in \Fig{SED} and the resulting parameters
-are listed in \Tab{SED}.
-Our SED model find a rest-frame characteristic dust temperature of BLAH
-(cf. 60$-$70\,K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10),
-\fir (rest-frame 42.5-122.5 \micron) of blah, and a dust mass of blah.
-For the mass absorption coefficient, we adopt BLAH (rest frame; Dunne et al. 2003).
-Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
+A fit including the MIR 24$\micron$ photometry
+is likely an upper limit on the \fir luminosity arising from starburst.
+% since the fit include contribution from the AGN (through power-law to MIR)
+If we instead fit for a model excluding the 24$\micron$ constraint,
+two major consequences are immediately apparent.
+First, the power-law index is poorly-constrained (see \Tab{SED}).
+Second, the steep power-law implies a small contribution
+from the power-law regime
+to the total IR luminosity as compared to the graybody.
+Thus, the \fir luminosity in
+this model should, in principle, corresponds to a
+lower limit on the cold dust emission.
+Using the best-fit parameters
+for this model, we find a  \LFIR of 4.72\petm{2.54}{-2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
+Again, the inferred quantities are uncorrected for lensing.
+%The best-fit SEDs are shown in \Fig{SED} and the
+% resulting parameters are listed in \Tab{SED}.
 
-We also fit an SED model excluding the decomposed 24.0\micron data.
+The dust temperature from both models is consistent with that
+of ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K, \citealt{Combes13a}).
+We note the \fir luminosities from both models are comparable, which is
+not surprising given the lack of constraints in the MIR. In fact, the
+\fir luminosity from the latter fit is slightly higher than the former, but
+consistent within their uncertainties.
+For the subsequent analysis, we adopt the physical quantities
+from the former model. The choice of which fit does not affect
+the derived star formation rate (SFR) given the similar \LFIR.
+Yet, the dust mass is higher in the former model (but consistent within the
+uncertainties), and thus the gas-to-dust ratio in \Sec{properties} 
+should be considered as an estimate.
 
-\begin{figure*}[tbph]
+\begin{figure*}[!htbp]
 \centering
 \includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
-\caption{
+\caption{SED model fits to the dust photometry of RXJ1131.
 WISE flux is slightly higher than the IRAC point, probably due to a smaller
@@
 
-\subsubsection{SB versus AGN contribution}
-% brief argument
-What does it imply to the dust properties if we see the QSO.. contribution to the hot dust is not as much as if we were viewing it edge-on? --> warm dust and cold dust.
+We correct for lensing using the median magnification factor 
+derived from the CO lens models. Assuming a Salpeter initial 
+mass function, we find the SFR of blah using a standard SK law.
 
-We quantify the AGN contribution to total IR.
-important how the power source differ from high-z or local.
-
-To derive the intrinsic properties, we correct for lensing using the
-median magnification factor derived from the CO lens models.
-Assuming a Salpeter initial mass function, we find the SFR of blah using the
-lensing-corrected \fir luminosity.
-
-\subsection{Gas properties}
+\subsection{Gas properties} \label{sec:properties}
 In this section, we derive the gas properties of RXJ1131 based on \bco,

### 2016-05-25 WRITEUP/ms.tex
updated SED section with SFR and comparison to C13 sameple, but LIR and FIR/IR fraction, etc

@@
 
-\subsection{SED modeling} \label{sec:SED}
+\subsection{SED modeling} \label{sec:SED}  % DONE
 We fit dust SED models to the
-24\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
-include the IRAS 60$\micron$ and 100$\micron$ upper limits
+24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
+include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
 to constrain the dust peak.
@@
 temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
-($\alpha$), the flux normalization at 500$\micron$ ($f_{\rm norm}$), and
+($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
 the observed-frame wavelength at which the emission
@@
 
-In the first model, we include the 24$\micron$ data
+In the first model, we include the 24\,$\micron$ data
 to constrain the power-law index. Based on the
 best-fit of this model, we find a
-\fir luminosity (rest-frame 42.5-122.5\,$\micron$) of
-3.81\petm{2.04}{-1.92}\E{12}\,\Lsun and a
-dust mass of 22\petm{5}{-18}\E{8}\,\Msun.
+\fir luminosity (rest-frame 42.5$-$122.5\,$\micron$) of
+3.81\petm{2.04}{1.92}\E{12}\,\Lsun and a
+dust mass of 22\petm{5}{18}\E{8}\,\Msun.
 For the mass absorption coefficient, we adopt
-$\kappa$\,=\,2.64\,m$^2$kg\pmOne at 125.0$\micron$
+$\kappa$\,=\,2.64\,m$^2$kg\pmOne at 125.0\,$\micron$
 (rest frame; \citealt{Dunne03a}).
@@
 
-A fit including the MIR 24$\micron$ photometry
+A fit including the MIR 24\,$\micron$ photometry
 is likely an upper limit on the \fir luminosity arising from starburst.
 % since the fit include contribution from the AGN (through power-law to MIR)
-If we instead fit for a model excluding the 24$\micron$ constraint,
+If we instead fit for a model excluding the 24\,$\micron$ constraint,
 two major consequences are immediately apparent.
@@
 Using the best-fit parameters
-for this model, we find a  \LFIR of 4.72\petm{2.54}{-2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
+for this model, we find a  \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
 Again, the inferred quantities are uncorrected for lensing.
@@
 
-The dust temperature from both models is consistent with that
-of ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K, \citealt{Combes13a}).
+The dust temperature from both models is similar to that of
+ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K; \citealt[hereafter C13]{Combes13a}).
 We note the \fir luminosities from both models are comparable, which is
 not surprising given the lack of constraints in the MIR. In fact, the
-\fir luminosity from the latter fit is slightly higher than the former, but
-consistent within their uncertainties.
+\fir luminosity from the second model is slightly higher than the former, but
+consistent within the uncertainties.
 For the subsequent analysis, we adopt the physical quantities
 from the former model. The choice of which fit does not affect
-the derived star formation rate (SFR) given the similar \LFIR.
-Yet, the dust mass is higher in the former model (but consistent within the
+the derived star formation rate (SFR) given the similar \fir luminosity.
+Yet, the dust mass is higher in the former (but consistent within the
 uncertainties), and thus the gas-to-dust ratio in \Sec{properties}
@@
 
-We correct for lensing using the median magnification factor 
-derived from the CO lens models. Assuming a Salpeter initial 
-mass function, we find the SFR of blah using a standard SK law.
+We correct for lensing using the median magnification factor $(\mu_{\rm L}\eq5.5)$
+from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
+Assuming a Salpeter initial
+mass function \citep{Salpeter55a}, we find a
+SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
+standard conversion \citep{Kennicutt98a}. 
+In the following section, we compare the properties of RXJ1131 
+with those reported by C13, which is the largest sample of
+ULIRGs at similar redshift (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements,
+to place RXJ1131 in context of existing studies.  
+Since C13 adopt a different definition of 
+\LFIR (40$-$500\micron)\footnote{We also note that the \fir luminosity in C13 is derived 
+based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.}, we derive the \fir luminosity
+following this convention.
+This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and 
+a SFR of $($150\pmm 70$)$\,\sfrU. 
+This implies RXJ1131 is considered a LIRG in regards to their sample, and consequently, 
+the SFR of RXJ1131 is lower than the C13 sample (SFR $>$ 200, with an average of 1200).
 
@@
 and compare the derived quantities against those reported by
-\citet[hereafter C13]{Combes13a}, which is the largest sample of
-ULIRGs at intermediate redshift (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements,
-to place RXJ1131 in context of existing studies. Their results are
-based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.
+C13, where their results are based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.
 
@@
 of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
-an overestimation due to a contribution from the companion, but is
-nevertheless consistent with the C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
+an overestimation due to a contribution from the companion, but 
+comparable to the C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
 uncertainties.
@@
 Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
-$f_{\rm gas-dust}$\,=\,BLAH, consistent with Combes+13: 206 ?
- Typical local (U)LIRGs are found to have a
-gas-to-dust mass ratio of 200$-$350 (Sanders et al. 1991; Contini
-\& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
+$f_{\rm gas-dust}$\,=\,70\petm{blah}{blah}, consistent with Combes+13: 206 ?
+% Typical local (U)LIRGs are found to have a
+%gas-to-dust mass ratio of 200$-$350 (Sanders et al. 1991; Contini
+%\& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
 

### 2016-05-25 WRITEUP/table_magFactor.tex
add table note
typeset edits
done dyn modelling
fix typo
SED section close to done
updated SED section with SFR and comparison to C13 sameple, but LIR and FIR/IR fraction, etc

@@
-\begin{deluxetable}{lccc}[!htbp]
+\begin{deluxetable}{lcc}[!htbp]
 \tabletypesize{\scriptsize}
 \tablecolumns{3}
-\tablecaption{\rot{2}{1} Magnification factors.}
+\tablecaption{Magnification factors of various kinematic components in \bco}
 \tablehead{
-\colhead{channel} & 
+\colhead{Channel} &
 \colhead{Source 1 $\mu_{\rm L}$} &
-\colhead{Source 2 $\mu_{\rm L}$} & 
+\colhead{Source 2 $\mu_{\rm L}$}
 }
 \startdata
-126-130 & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ %which is source 1 and 2 then?
-131-135 & 7.6 $\pm$ 1.6 & \\ % would this be source 1 or 2?
-136-140 & 8.7 $\pm$ 2.0 & \\
-141-145 & 4.1 $\pm$ 0.9 & \\
-146-150 & 4.2 $\pm$ 0.6 & \\
-151-156 & 4.3 $\pm$ 2.4 & \\
-156-160 & 3.1 $\pm$ 0.9 & \\
-weighted average & 4.4 & \\
-median & 5.5 &  \\
+126$-$130 & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ [0.6ex] %which is source 1 and 2 then?
+131$-$135 & 7.6 $\pm$ 1.6 & \\ [0.6ex] % would this be source 1 or 2?
+136$-$140 & 8.7 $\pm$ 2.0 & \\ [0.6ex]
+141$-$145 & 4.1 $\pm$ 0.9 & \\ [0.6ex]
+146$-$150 & 4.2 $\pm$ 0.6 & \\ [0.6ex]
+151$-$155 & 4.3 $\pm$ 2.4 & \\ [0.6ex]
+156$-$160 & 3.1 $\pm$ 0.9 & \\ [0.6ex]
+weighted average & 4.4 & \\ [0.6ex]
+median & 5.5 &
 \enddata
-\label{tab:mag}
-\tablecomments{blah}
- %TablenotegoesBetween 
-\tablerefs{blah}
+\label{tab:model}
+\tablecomments{Source 1 is RXJ1131 and source 2 is its companion. See text for details.}
 \end{deluxetable}

### 2016-05-26 WRITEUP/ms.tex
add latex commands to make spacing like Apj

@@
 \slugcomment{To be submitted to the ApJ}
+ \makeatletter
+% \renewcommand\normalsize{\@setfontsize\normalsize\@xpt{11.56}}
+\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
+\makeatother
 
@@
 Ithaca, NY 14853, USA; \myemail}
+
 %==============================================================================
@@
 standard conversion \citep{Kennicutt98a}.
-In the following section, we compare the properties of RXJ1131 
+To place RXJ1131 in context of existing studies,
+we compare its properties
 with those reported by C13, which is the largest sample of
-ULIRGs at similar redshift (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements,
-to place RXJ1131 in context of existing studies.  
+IR-luminous galaxy at similar redshift
+(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
 Since C13 adopt a different definition of
-\LFIR (40$-$500\micron)\footnote{We also note that the \fir luminosity in C13 is derived 
-based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.}, we derive the \fir luminosity
-following this convention.
+\LFIR (40$-$500\micron)\footnote{We also note that the
+\fir luminosity in C13 is derived
+based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
+we derive the \fir luminosity following this convention.
 This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
 a SFR of $($150\pmm 70$)$\,\sfrU.
-This implies RXJ1131 is considered a LIRG in regards to their sample, and consequently, 
-the SFR of RXJ1131 is lower than the C13 sample (SFR $>$ 200, with an average of 1200).
+This implies RXJ1131 is considered a LIRG in regards to their
+sample, and consequently,
+the SFR of RXJ1131 is lower than that of the C13 sample
+(SFR\,$>$\,200, with an average of 1200).
 
@@
 (with a range from 1.1 kpc to 9.3 kpc).
-This indicates that the positive correlation in the linewidth-size relation
-holds at intermediate redshifts. Yet we cannot quantify this further
-with the data represented in this paper.
+% This also indicates that the positive correlation
+% in the linewidth-size relation
+% holds at intermediate redshifts. Yet we cannot quantify this further
+% with the data represented in this paper.
 
@@
 Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
-$f_{\rm gas-dust}$\,=\,70\petm{blah}{blah}, consistent with Combes+13: 206 ?
-% Typical local (U)LIRGs are found to have a
-%gas-to-dust mass ratio of 200$-$350 (Sanders et al. 1991; Contini
-%\& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
+$f_{\rm gas-dust}$\,=\,70\petm{blah}{blah}, which is consistent lower than C13
+(who finds 206) sample as well as those of local (U)LIRGs
+(200$-$350; Sanders et al. 1991; Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
 

### 2016-05-26 WRITEUP/ms.tex
added LIR to SED section, i.e. RXJ1131 is considered a LIRG when comparing to Combes+13, but ULIRG in other regards

@@
 Using the best-fit parameters
-for this model, we find a  \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
+for this model, we find a total IR luminosity
+\LIR (rest-frame 1\,$-$\,1000\,\micron) of 10.28\petm{1.89}{1.97}\E{12}\,\Lsun,
+\LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
 Again, the inferred quantities are uncorrected for lensing.
@@
 \includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
-\caption{SED model fits to the dust photometry of RXJ1131.
+\caption{SED models of the IR dust emission toward RXJ1131.
+The data are not corrected for lensing magnification and dust extinction.
 WISE flux is slightly higher than the IRAC point, probably due to a smaller
-aperture used in IRAC extraction, both of which were taken from the archive.
-Spitzer IRAC:
-Aperture flux in 5\farcs diameter with aperture correction applied.
-Spitzer/MIPS: PSF fit flux, as source size <
-native PSF FWHM of 6".
+aperture used in IRAC extraction,
+both of which were taken from the archive.
+IRAC: Aperture flux in 5\farcs diameter.
+MIPS: use PSF fit flux from archive as source size $<$ PSF FWHM of 6$^{\prime\prime}$.
 Might want to add NVSS constraints.
-The data are not corrected for dust extinction.
 \label{fig:SED}}
@@
 
-We correct for lensing using the median magnification factor $(\mu_{\rm L}\eq5.5)$
+We correct for lensing using the median magnification
+factor $(\mu_{\rm L}\eq5.5)$
 from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
@@
 a SFR of $($150\pmm 70$)$\,\sfrU.
-This implies RXJ1131 is considered a LIRG in regards to their
-sample, and consequently,
-the SFR of RXJ1131 is lower than that of the C13 sample
-(SFR\,$>$\,200, with an average of 1200).
+This implies that RXJ1131 is considered a LIRG in regard to their
+sample, and consequently, the SFR of RXJ1131 is lower
+(cf. SFR\,$>$\,200, with an average of 1200). If we instead adopt the
+more generally adopted total IR luminosity
+classification (\LIR\,$>$\,10$^{12}$), RXJ1131 would be
+considered as a ULIRG given its lensing-corrected
+\LIR of $\sim$2\E{12}\,\Lsun.
 
@@
 
-\subsubsection{Linewidth \& Sizes}
+\subsubsection{Linewidth \& Sizes} %DONE
 We find that the linewidths for both components (redshifted and blueshifted)
 inferred from a double Gaussian fit to the line profile are
-consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
+comparable to the C13 ULIRG sample
+(FWHM of 370\,\kms). Such linewidths are higher
 than local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
@@
 who find an average radius of 3.5\,$\pm$\,2.3\,kpc
-(with a range from 1.1 kpc to 9.3 kpc).
-% This also indicates that the positive correlation
-% in the linewidth-size relation
-% holds at intermediate redshifts. Yet we cannot quantify this further
-% with the data represented in this paper.
+with a range spanning 1.1$-$9.3\,kpc.
+This is expected if the positive correlation in the linewidth-size relation
+holds at intermediate redshifts. Yet we cannot quantify this further
+with the data represented in this paper.
 

### 2016-05-26 WRITEUP/ms.tex
crushed numbers for SFE, but I think something looks wrong

@@
 for this model, we find a total IR luminosity
-\LIR (rest-frame 1\,$-$\,1000\,\micron) of 10.28\petm{1.89}{1.97}\E{12}\,\Lsun,
-\LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
+\LIR (rest-frame 8\,$-$\,1000\,\micron) of 8.14\petm{2.64}{2.80}\E{12}\,\Lsun,
+a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
+dust mass ($M_{\rm dust}$) of 11\petm{5}{6}\E{8}\,\Msun.
+Taken at face value, this implies a \LFIR-to-\LIR
+contribution of $\sim$58\%.
 Again, the inferred quantities are uncorrected for lensing.
@@
 ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K; \citealt[hereafter C13]{Combes13a}).
-We note the \fir luminosities from both models are comparable, which is
+We note the \fir luminosity is comparable in both models, which is
 not surprising given the lack of constraints in the MIR. In fact, the
@@
 For the subsequent analysis, we adopt the physical quantities
-from the former model. The choice of which fit does not affect
+from the former (\ie with constraints at 24\,\micron).
+The choice of SED model does not affect
 the derived star formation rate (SFR) given the similar \fir luminosity.
@@
 should be considered as an estimate.
-
-\begin{figure*}[!htbp]
+We correct for lensing using the median magnification
+factor $(\mu_{\rm L}\eq5.5)$
+from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
+Assuming a Salpeter initial
+mass function \citep{Salpeter55a}, we find a
+SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
+standard conversion \citep{Kennicutt98a}.
+
+\begin{figure}[!htbp]
 \centering
-\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
+\includegraphics[trim=65 15 15 95, clip, width=0.45\textwidth]{../Figures/FullSED.eps}
 \caption{SED models of the IR dust emission toward RXJ1131.
 The data are not corrected for lensing magnification and dust extinction.
+{\bf This figure needs an update}
 WISE flux is slightly higher than the IRAC point, probably due to a smaller
@@
 \label{fig:SED}}
-\end{figure*}
-
-We correct for lensing using the median magnification
-factor $(\mu_{\rm L}\eq5.5)$
-from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
-Assuming a Salpeter initial
-mass function \citep{Salpeter55a}, we find a
-SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
-standard conversion \citep{Kennicutt98a}.
+\end{figure}
+
 To place RXJ1131 in context of existing studies,
@@
 we derive the \fir luminosity following this convention.
-This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
+This yields $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
 a SFR of $($150\pmm 70$)$\,\sfrU.
@@
 sample, and consequently, the SFR of RXJ1131 is lower
-(cf. SFR\,$>$\,200, with an average of 1200). If we instead adopt the
-more generally adopted total IR luminosity
-classification (\LIR\,$>$\,10$^{12}$), RXJ1131 would be
-considered as a ULIRG given its lensing-corrected
-\LIR of $\sim$2\E{12}\,\Lsun.
+(cf. SFR\,$>$\,200, with an average of 1200 in C13).
+If we instead adopt the
+more generally used definition for the total IR luminosity
+(\LIR\,$>$\,10$^{12}$), RXJ1131 would be
+considered a ULIRG given its lensing-corrected
+total IR luminosity of $\sim$2\E{12}\,\Lsun.
 
@@
 comparable to the C13 ULIRG sample
-(FWHM of 370\,\kms). Such linewidths are higher
-than local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
+($\Delta v_{\rm FWHM}$ of 370\,\kms) and local ULIRGs
+(300\pmm85\,\kms; \citealt[][]{Solomon97a}).
 Since C13 do not have resolved observations, we compare the
-gas distribution with local ULIRGs. The CO gas in RXJ1131 is
+gas distribution with local U/LIRGs. The CO gas in RXJ1131 is
 distributed $\sim$6\,kpc in radius across (in
-the source plane), which is more extended than the average in the
-sample of disk-like ULIRGs studied by \citet{Ueda14a},
+the source plane), which is more extended than the
+sample of disk-like U/LIRGs studied by
+\citet[hereafter U14]{Ueda14a}, % also classified U/LIRG using FIR from 60, 100 micron measurements
 who find an average radius of 3.5\,$\pm$\,2.3\,kpc
-with a range spanning 1.1$-$9.3\,kpc.
-This is expected if the positive correlation in the linewidth-size relation
-holds at intermediate redshifts. Yet we cannot quantify this further
-with the data represented in this paper.
+with a range spanning 1.1\,$-$\,9.3\,kpc.
+% This is expected if the positive correlation in the linewidth-size relation
+% holds at intermediate redshifts. Yet we cannot quantify this further
+% with the data represented in this paper.
 
@@
 first order takes into account effect of differential lensing. This yields
-$I_{\tiny \bco}$\,=\,5.9$\pm$2.7 Jy\,\kms, where the uncertainty includes those on
+$I_{\small \bco}$\,=\,5.9$\pm$2.7 Jy\,\kms,
+where the uncertainty includes those on
 the magnification factors.
-We note that the derived intensity includes emission from the companion
-as the spatial resolution of our data do not allow us decompose its contribution
-from the total line flux.
+We note that this includes emission from the companion
+as the spatial resolution of our data do not allow us decompose its
+contribution from the total line flux.
 
@@
 using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
-solely to facilitate a comparison with the C13 sample. For the same reason, we
+solely to facilitate a comparison with other U/LIRGs.
+For the same reason, we
 adopt a luminosity-to-mass conversion factor of
-\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields
-\Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\Lsun and a gas mass
-of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
-an overestimation due to a contribution from the companion, but
-comparable to the C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
-uncertainties.
+\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne, this yields a
+CO luminosity \Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\LpU and a gas mass
+$M_{\rm gas}$ of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
+an overestimation for RXJ1131 due to a contribution from the companion.
+The inferred gas mass is comparable to
+C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) as well as
+local U/LIRGs \citep{Solomon97a, Sanders96a} but higher than
+local LIRGs (U14).
 
 % gas-to-dyn ratio
-Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
+We place a lower limit on the dynamical mass (see \Sec{dynamics}) using
+the inferred gas mass. This BLAH.
+ {\bf will need edit depending on the dyn. modeling section}
 a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
 % gas to dust ratio:
-Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
-$f_{\rm gas-dust}$\,=\,70\petm{blah}{blah}, which is consistent lower than C13
-(who finds 206) sample as well as those of local (U)LIRGs
-(200$-$350; Sanders et al. 1991; Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
+Using the dust mass derived from SED fitting,
+we find a gas-to-dust ratio of 184\pmm124, which is consistent with
+the C13 sample ($f_{\rm gas-dust}$\,=\,206) and local U/LIRGs
+(200$-$350; \citealt{Sanders91a}, Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
 
 \subsubsection{SFE and Depletion Time}
-dot dot dot
+We derive the SFE using the far-IR luminosity definition used by
+C13 (\ie SFE\pmm\LFIR$($40\,$-$\,500\,\micron)$/$$M_{\rm gas}$$)$,
+we find a SFE of 31\pmm15 for RXJ1131, or equivalently a depletion
+timescale of $\tau$\,=\,0.19\pmm0.07\,Gyr. % 5.8/SFE
+This is substantially lower than most U/LIRGs (\citealt{Combes11a}; C13,
+and references therein).
+\textbf{ am I doing something wrong...}
+
+Implication of this unexpectedly low SFE in RXJ1131...
 
@@
 In this section, we put our results in context with other ULIRGs/mergers at
-$z$\,=\,0$-$1. It is clear that RXJ1131 has a gas-rich companion, but how does
+$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a gas-rich companion, but how does
 this affect its internal dynamics and what is the merger stage of RXJ1131?

### 2016-05-26 WRITEUP/ms.tex
send this 1st draft to DR

@@
 for pointing, secondary amplitude, and phase calibration and 1055$+$018 was
-observed as bandpass calibrators for both tracks.
+observed as the bandpass calibrator for both tracks.
 MWC349 and 3C279 were observed as the primary flux calibrator for C and D
@@
 observed as the primary absolute flux calibrator and 3C279 was observed as
-bandpass calibrators for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
+the bandpass calibrator for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
 visibility data.
@@
 \subsection{VLA} %DONE
-Our analysis also use the archival data of the radio continuum obtained with the \vla (VLA; Program ID: AW741; PI: Wucknitz). Since these data have not been
-published, we here describe the details of the observations as well as our calibration steps.
+Our analysis also use the archival data of the radio continuum obtained with the \vla (VLA; Program ID: AW741; PI: Wucknitz).
+Since the observations have not been described in any previous publications,
+we here describe their details as well as our calibration steps.
 
@@
 The first and second moment maps are clipped at 3$\sigma$.
-The peak flux density is 8.12 $\pm$ 0.30 Jy\,\kms\,beam\pmOne in the intensity-integrated
-map. The deconvolved source size is estimated to be 5\farcs1$\pm$0\farcs72 $\times$ 3\farcs72$\pm$0\farcs66
+The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne in the intensity-integrated
+map. The deconvolved source size is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66
 and thus the emission is resolved over $\sim$2.2 beams.
@@
 A clear velocity gradient and an unusually high
-velocity dispersion ($\gtrsim$400\kms) near the central region
+velocity dispersion ($\gtrsim$400\,\kms) near the central region
 is seen in \Fig{CO21highO}. While beam smearing is inevitably the
@@
 correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,T$_{\tiny \cco}$/T$_{\tiny \bco}$\,=\,0.66\,$\pm$\,0.41.
+$r_{\rm 32}$\,=\,T$_{\small \cco}$$/$T$_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
 The high uncertainty is dominated by the uncertainties in the \cco line
@@
 We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
-1.2$\pm$0.2 mJy, with a peak flux
-$S_\nu$\,=\,800$\pm$88\,\micron Jy\,beam\pmOne
+1.2\pmm0.2 mJy, with a peak flux
+$S_\nu$\,=\,800\pmm88\,\micron Jy\,beam\pmOne
 centering on the lensing galaxy. A slightly extended emission is also seen
@@
 original continuum map ($\sim$0.4 mJy). We therefore adopt
-$S_\nu$ = 0.39$\pm$0.08 mJy as the 2\,mm continuum emission toward
+$S_\nu$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission toward
 the background galaxy.
@@
 perform aperture photometry.
-We then fit a power-law spectrum $S_\nu \propto \nu^\alpha$ to the
+
+We fit a power-law spectrum to the
 decomposed IRAC photometry to disentangle the observed total flux
 at MIPS 24$\micron$. We find a spectral index of $\alpha\sim-$1.8 and
-$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
-This is consistent with the mean 3.6$-$8\,$\micron$
+$\alpha\sim-0.85$ for the lensing galaxy and RXJ1131, respectively.
+This is consistent with the mean 3.6\,$-$\,8\,$\micron$
 spectral slope of
@@
 $\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
-1000$\micron$ on $\lambda_0$.
+1000\,$\micron$ on $\lambda_0$.
 We check for chain convergence by requiring the autocorrelation
@@
 best-fit of this model, we find a
-\fir luminosity (rest-frame 42.5$-$122.5\,$\micron$) of
+\fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
 3.81\petm{2.04}{1.92}\E{12}\,\Lsun and a
@@
 Since C13 adopt a different definition of
-\LFIR (40$-$500\micron)\footnote{We also note that the
-\fir luminosity in C13 is derived
-based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
+\LFIR (40\,$-$\,500\,\micron)\footnote{We also note that the
+\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
 we derive the \fir luminosity following this convention.
@@
 we find a SFE of 31\pmm15 for RXJ1131, or equivalently a depletion
-timescale of $\tau$\,=\,0.19\pmm0.07\,Gyr. % 5.8/SFE
-This is substantially lower than most U/LIRGs (\citealt{Combes11a}; C13,
-and references therein).
+timescale of $\tau$\,=\,190\pmm70\,Myr. % 5.8/SFE Gyr
+This SFE is substantially lower than most U/LIRGs
+(\citealt{Solomon97a,Combes11a}; C13). % local ULIRG: 180 +/- 160 Lsun/M (Solomon+97)
+% Combes+13: sample of 39 gal from z= 0.2-1 find $<$ 100 Myr.
 \textbf{ am I doing something wrong...}
@@
 In this section, we put our results in context with other ULIRGs/mergers at
-$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a gas-rich companion, but how does
-this affect its internal dynamics and what is the merger stage of RXJ1131?
+$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a
+gas-rich companion, but how does this affect its internal dynamics?
+What is the merger stage of RXJ1131?
 We argued that the symmetric source-plane velocity field suggest
@@
 contrast strongly with studies of local (U)LIRGs/mergers
-(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1), where active AGN are
+(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1), where AGNs are
 typically found in late stage mergers
 \citep{Yuan10a,Iwasawa11a,Carpineti12a} and
-that only major mergers near their final
+that only these major mergers near their final
 coalescence can provide \LIR\,$>$\,10$^{12}$\,\Lsun,
-\citep[\eg][]{Carpineti15a,Larson16a}.
-If this is also the case at $z$$\sim$0.65, this would imply RXJ1131
+\citep[\eg][hereafter L16]{Carpineti15a,Larson16a}
+\footnote{In this section, we adopt the total IR luminosity
+calculated from 8\,$-$\,1000\,\micron
+to be consistent with the classification used by these authors.}.
+If this is also the case at $z$$\sim$0.65, it would imply RXJ1131
 is a major merger near its final coalescence and that the spatially offset
-component is an expulsion of gas driven by AGN winds or is some
+component is likely an expulsion of gas driven by AGN winds or some
 tidally ejected material from previous passage.
 In that case, the molecular gas fraction in the host
-galaxy should have declined (as in ellipticals) compared to early
-stage mergers (can we find molecular gas mass fraction as a
-function of merger stage?) and that the molecular gas would
+galaxy should have declined (as seen in ellipticals) compared to early
+stage mergers
+\textbf{can we find molecular gas mass fraction as a
+function of merger stage? also, what is the dynamical mass for RXJ1131}
+and that the molecular gas would
 be more concentrated in the nuclear region.
 This is inconsistent with what
-is observed (which strongly favors a disk morphology;
-but there are outliers --  \citet{Ueda14a} find
-extended molecular gas in merger remnant) and
+is observed for RXJ1131
+(an extended gas-rich disk; but see also U14 for outliers
+with extended molecular gas in merger remnants) and
 the fact that there is on-going \SF activity.
 Hence, we reject this and speculate the discrepancy is a consequence
-of (the power source of) IR luminous galaxies are already very different by this redshift.
+of different power mechanisms of IR-luminous galaxies at intermediate redshift.
 
@@
 CO is less strongly-magnified as compared to the dust emission,
-in which case, the lensing-corrected \LFIR is overestimated.
+in which case, the lensing-corrected IR luminosity is overestimated.
 This is plausible given the extent of the source with respect to the caustics
-and that substantial differential lensing effect has been seen across CO and other
-wavelengths. If we instead use the NIR ($H$-band) magnification factor ($\mu_{\rm L}$\,=\,BLAH; C06),
-we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is consistent with a minor
-merger in the context of the results reported by \citet{Carpineti15a} and \citet{Larson16a}.
-
+and that substantial differential lensing effect has been seen across
+CO and other wavelengths. If we instead use the NIR ($H$-band) magnification
+factor ($\mu_{\rm L}$\,=\,BLAH; C06),
+we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is
+a large gas-rich LIRG, and a minor merger in the context of the results
+reported by \citet{Carpineti15a} and L16.
+
+{\bf --- anything below is not ready ---}
 \subsubsection{Fate of RXJ1131-1231}
@@
 
-Mergers are observable for 0.2-0.4 Gyr,
-between 2nd passage and coalescence.
-Kinematic asymmetries follow morphological asymmetries during
-mergers. Mergers are kinematically detectable for 0.2-0.4 Gyr
-between second passage and coalescence.
-
-Numerical simulations of mergers have shown that
-multiple starburst episodes can be triggered even in double mergers.
-The timing of the starbursts is thought to depend on the progenitor galaxy
-morphologies, with early starbursts (before the galaxies start to merge)
-occurring in bulges disc galaxies, and late starbursts (after the galaxies
-have started to merge) occurring in disc galaxies with a bulge component (Mihos \& Hernquist 1994, 1996.
-The spinning black hole already encountered?
-
-The future of RXJ1131:
-classical picture is that merger will evolve into local ellipticals, but more
-recent studies (springel \& Hernquist 05, cite) suggest that mergers can also
-form local large-disks (bulge dominated) $<--$ double check this. Given the
+From numerical simulations, mergers are observable and distinguishable
+with their kinematic and morphological features for 0.2$-$0.4 Gyr
+between their second passage and final coalescence.
+
+The spinning black hole in RXJ1131 provide one piece of
+evidence that the two has already encountered.
+
+% The future of RXJ1131:
+Mergers are expected to evolve into
+local ellipticals or large-disks (bulge dominated) (springel \& Hernquist 05, cite).
+Given the
 extended molecular gas distribution, we suggest RXJ1131 may evolve into the
@@
 mechanisms at play in the latter stage, transporting the gas
-toward the central nuclear region.
+toward the central nuclear region and blah.
 
 \subsection{ULIRG Evolution and Cosmic SFH}
-At low redshifts, the luminosity function of ULIRG shows strong evolution with
-redshift (Veilleux et al. 1999). It is not known whether the IR luminosity of
-these high-$z$ sources arises due to mergers between two or more large spiral
-galaxies, as in local ULIRGs, or via a different mechanism/galaxy formation
-processes at high-z.
-
-% AGN contribution.
+While there is an emerging consensus on the strong
+evolution of the IR luminosity function \citep[\eg][]{Huynh07a,Seymour10a},
+it is currently unclear whether the IR luminosity of
+these intermediate redshift sources arise due to the merging of large spiral
+galaxies, as typically seen in local ULIRGs, or proceed under a different
+formation processes at higher redshifts. Our study blah...
 
 % Implication on SFH
-Our result indicates that the gas mass fraction has already decreased
-at this redshift, which may suggest that the change in cosmic SFD is due to
-change in gas content. The SFE is also BLAH at this redshift,
-consistent with current speculation of how the SFRD decreases over cosmic time.
+Our result indicates that...
+% the gas mass fraction has already decreased
+% at this redshift, which may suggest that the change in cosmic SFD is due to
+% change in gas content. The SFE is also BLAH at this redshift,
+% consistent with current speculation of how the SFRD decreases over cosmic time.
 
@@
 
-We observed the cold molecular gas properties using \bco and \cco line emission
-toward the AGN host galaxy RXJ1131 at $z_{\rm CO}$\,$\sim$0.65.
-Our results suggest that RXJ1131 is a wet-wet merger between a AGN/starburst
+We investigate the cold gas kinematics and dynamics in
+the lensed optical quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65
+by observing its \bco and \cco line emission.
+Our results suggest that RXJ1131 is a wet-wet merger between an AGN/starburst
 ULIRG and a optically faint companion.
 
-Fitting SED models, we find that the AGN host galaxy is a ULIRG.
-A faint companion as seen in HST observations (BJB) is also detected in our CO, confirming it's redshift and gas rich nature.
-
-% any further work needed to resolve the remaining problems
-We list several pieces of evidence through out
-this work to argue that RXJ1131 is likely a rotating disk.
-The double-horned profile, smooth, symmetric velocity field
-seen in our lens model and in the
-image plane and C06 model $n$=1 Sersic profile all suggest
-a kinematically-order (i.e., disk) galaxy.
-Yet, these are insufficient to conclude a disk morphology. Additional
-characteristics such as peak velocity dispersion at the central region and a
-``spider'' diagram are needed, which is commonly seen in local spirals.
-The high dispersion near the dynamical center also
-suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. Overall
-implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution
-data are needed to confirm this.
+% Fitting SED models, we find that the AGN host galaxy is a ULIRG.
+% A faint companion as seen in HST observations (BJB) is also detected in our CO, confirming it's redshift and gas rich nature.
+
+% % any further work needed to resolve the remaining problems
+% We list several pieces of evidence through out
+% this work to argue that RXJ1131 is likely a rotating disk.
+% The double-horned profile, smooth, symmetric velocity field
+% seen in our lens model and in the
+% image plane and C06 model $n$=1 Sersic profile all suggest
+% a kinematically-order (i.e., disk) galaxy.
+% Yet, these are insufficient to conclude a disk morphology. Additional
+% characteristics such as peak velocity dispersion at the central region and a
+% ``spider'' diagram are needed, which is commonly seen in local spirals.
+% The high dispersion near the dynamical center also
+% suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. Overall
+% implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution
+% data are needed to confirm this.
 

### 2016-05-28 src/HSTVLA.py
update aspect ratio

@@ -1,12 +1,14 @@
 """
 Author: Daisy Leung
 
-Last edited: 17 May 2016
+Last edited: 27 May 2016
 
 Purpose:
 - Plot single panel 5GHz VLA continuum on HST F555W, investigate continuum offset
 
 History:
+May 27 2016:
+    - aspect ratio
 May 17 2016:
     - update cosmetics
     - add beam
@@ -53,23 +55,22 @@ for k in label_vla.iterkeys():
     label_vla[k] = file_vla
 # print label_vla
 
-figC = plt.figure(1, figsize=(7, 7))
-figC.subplots_adjust(top=0.9, left=0.1, right=0.95)
+figC = plt.figure(1)
 # figRed = plt.figure(2, figsize=(12, 7))
 ########################################
 # user define area
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.002
+sizep = 0.00215
 
 ra_cross, dec_cross = ra_center, dec_center
-row_a = 0.10
+row_a = 0.1
 width = 0.35
 full_width = 0.7
 x_gap = 0.05
 x0 = 0.2
-dy = 0.85
+dy = 0.9
 sigma = 1.3e-5
 
 ########################################
@@ -142,7 +143,7 @@ markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
 # if '_' in sym[:-1]: symf = sym.replace('_', ' ')
 
 # put_label(fig1, 0.20, 0.95, 'HST F555W', 'titleBand')
-put_label(fig1, 0.4, 0.9, 'HST F555W, 5GHz Continuum', 'titleBand')
+put_label(fig1, 0.36, 0.9, 'HST F555W, 5GHz Continuum', 'titleBand')
 put_label(fig1, 0.15725, 0.95, 'RXJ1131', 'titleObj')
 # put_label(figHST, 0.20, 0.95, 'HST F555W', 'titleBand')
 # put_label(figHST, 0.1825, 0.9, 'RXJ1131', 'titleObj')

### 2016-05-28 src/plotCont.py

@@ -1,22 +1,24 @@
 """
 Author: Daisy Leung
 
-Last edited: 17 May 2016
+Last edited: 27 May 2016
 
 Purpose:
 - Overlay 2mm Cont contour on HST
 
 History:
+May 27 2016:
+    - update aspect ratio
 May 17 2016:
-    add beam
+    - add beam
 Jan 01 2016:
-    update marker
+    - update marker
 Dec 31 2015:
-    use linear shifted F555W image
+    - use linear shifted F555W image
 Dec 30 2015:
-    make pretty layout
+    - make pretty layout
 Sept 19 2015:
-    created script
+    - created script
 
 """
 
@@ -54,23 +56,22 @@ for k in label_pdbi.iterkeys():
     label_pdbi[k] = file_pdBI
 # print label_pdbi
 
-figC = plt.figure(1, figsize=(7, 7))
-figC.subplots_adjust(top=0.9, left=0.1, right=0.95)
+figC = plt.figure(1)
 # figRed = plt.figure(2, figsize=(12, 7))
 ########################################
 # user define area
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.002258066
+sizep = 0.002058066
 
 ra_cross, dec_cross = ra_center, dec_center
-row_a = 0.10
+row_a = 0.1
 width = 0.35
 full_width = 0.7
 x_gap = 0.05
 x0 = 0.2
-dy = 0.85
+dy = 0.9
 sigma = 0.085e-3     # theoretical: 0.0816E-03; off-region in map: 0.0888e-3
 
 ########################################
@@ -143,7 +144,7 @@ markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
 # if '_' in sym[:-1]: symf = sym.replace('_', ' ')
 
 put_label(fig1, 0.15725, 0.95, 'RXJ1131', 'titleObj')
-put_label(fig1, 0.40, 0.9, 'HST F555W, 2 mm Continuum', 'titleBand')
+put_label(fig1, 0.36, 0.9, 'HST F555W, 2 mm Continuum', 'titleBand')
 # put_label(figHST, 0.20, 0.95, 'HST F555W', 'titleBand')
 # put_label(figHST, 0.1825, 0.9, 'RXJ1131', 'titleObj')
 # put_label(figred, 0.40, 0.95, 'HST F555W, CO Red wing', 'titleBand')

### 2016-05-28 src/HSTVLA.py
aspect ratio

@@ -67,7 +67,7 @@ sizep = 0.00215
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
 width = 0.35
-full_width = 0.7
+full_width = 0.65
 x_gap = 0.05
 x0 = 0.2
 dy = 0.9
@@ -143,7 +143,7 @@ markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
 # if '_' in sym[:-1]: symf = sym.replace('_', ' ')
 
 # put_label(fig1, 0.20, 0.95, 'HST F555W', 'titleBand')
-put_label(fig1, 0.36, 0.9, 'HST F555W, 5GHz Continuum', 'titleBand')
+put_label(fig1, 0.38, 0.9, 'HST F555W, 5GHz Continuum', 'titleBand')
 put_label(fig1, 0.15725, 0.95, 'RXJ1131', 'titleObj')
 # put_label(figHST, 0.20, 0.95, 'HST F555W', 'titleBand')
 # put_label(figHST, 0.1825, 0.9, 'RXJ1131', 'titleObj')

### 2016-05-28 src/plotCont.py

@@ -68,7 +68,7 @@ sizep = 0.002058066
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
 width = 0.35
-full_width = 0.7
+full_width = 0.65
 x_gap = 0.05
 x0 = 0.2
 dy = 0.9
@@ -144,7 +144,7 @@ markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
 # if '_' in sym[:-1]: symf = sym.replace('_', ' ')
 
 put_label(fig1, 0.15725, 0.95, 'RXJ1131', 'titleObj')
-put_label(fig1, 0.36, 0.9, 'HST F555W, 2 mm Continuum', 'titleBand')
+put_label(fig1, 0.38, 0.9, 'HST F555W, 2 mm Continuum', 'titleBand')
 # put_label(figHST, 0.20, 0.95, 'HST F555W', 'titleBand')
 # put_label(figHST, 0.1825, 0.9, 'RXJ1131', 'titleObj')
 # put_label(figred, 0.40, 0.95, 'HST F555W, CO Red wing', 'titleBand')

### 2016-05-28 PdBI/src/pythonPLOT/COChan.py
cosmetics

@@ -1,11 +1,15 @@
 '''
-Last Modified: 30 Apr 16
+Last Modified: 27 May 16
 
 
 Author: Daisy Leung
 
 
 History:
+27 May 2016
+- change flux label unit
+- update font inside panel
+
 30 Apr 2016
 - change velocity labels, reference systemic velocity
 - use data cube with velo. axis 0 km/s == line center (see shiftRefVelo.py)
@@ -216,7 +220,7 @@ except ImportError:
 for i, ax in enumerate(g):
     channel_number = start_channel + i
     v = vel.to_vel(channel_number) / 1.e3
-    t = ax.add_inner_title(r"$v=%4.1f$ km s$^{-1}$" % (v),
+    t = ax.add_inner_title(r"$v=%4.1f\ {\rm km s}^{-1}$" % (v),
                            loc=2,
                            frameon=False
                            )
@@ -226,7 +230,8 @@ for i, ax in enumerate(g):
                                                  linewidth=2.5)])
     else:
         # show velocity text in some color
-        t.txt._text.set_color('k')
+        t.txt._text.set_color("#243106")
+        t.txt._text.set_fontweight('black')
 
 # Beam
 g[-1].add_beam_size(minor_px, major_px, BPA_deg,      # y, x, angle
@@ -236,7 +241,7 @@ g[-1].add_beam_size(minor_px, major_px, BPA_deg,      # y, x, angle
 
 # make colorbar
 cb = plt.colorbar(im, cax=cax)
-cb.set_label("Flux Density [mJy B" + r"$^{-1}$]")
+cb.set_label("Flux Density [mJy beam" + r"$^{-1}$]")
 cb.set_ticks([-0.01, 0, 0.01, 0.02, 0.03])   # place tick locations
 
 # customize to mJy B^-1 instead of Jy B^-1, uncomment to use same as cb.set_ticks

### 2016-05-28 src/RedBlue.py
cosmestics

@@ -1,7 +1,7 @@
 """
 Author: Daisy Leung
 
-Last edited: 17 May 2016
+Last edited: 28 May 2016
 
 Purpose:
     Plot Red wing and Blue wing different color overlay on HST
@@ -9,6 +9,10 @@ Purpose:
 
 
 History:
+28 May 2016:
+    - hide axis labels
+    - increase font size
+    - longer ticks
 17 May 2016:
     - update to use integrated maps from 17May16/, channel range consistent with mom0 map
     - update sigma
@@ -36,11 +40,11 @@ Plotpath = '../Figures/'
 
 font = {'family': 'Arial Narrow',
         'weight': 'normal',
-        'size': 12.5}
+        'size': 13.5}
 xtick = {'major.size': 10,
-         'minor.size': 6}
+         'minor.size': 6.5}
 ytick = {'major.size': 10,
-         'minor.size': 6}
+         'minor.size': 6.5}
 mpl.rc('font', **font)
 mpl.rc('xtick', **xtick)
 
@@ -58,9 +62,8 @@ for k in label_pdbi.iterkeys():
     label_pdbi[k] = file_pdBI
 # print label_pdbi
 
-figC = plt.figure(1, figsize=(7, 7))
-figC.subplots_adjust(top=0.9, left=0.1, right=0.95)
-
+figC = plt.figure(1)
+figC.clf()
 ########################################
 # user define area
 ########################################
@@ -69,12 +72,12 @@ dec_center = -12.5328629
 sizep = 0.002                # 0.00158066
 
 ra_cross, dec_cross = ra_center, dec_center
-row_a = 0.10
+row_a = 0.1
 width = 0.35
-full_width = 0.7
+full_width = 0.65
 x_gap = 0.05
 x0 = 0.2
-dy = 0.85
+dy = 0.9
 sigma_blue = 0.53733    # noise free region
 sigma_red = 0.4323
 
@@ -118,6 +121,7 @@ lg_1arcsec = 1. / 3600
 # axes
 ########################################
 standard_plot_setup(fig1, ra_center, dec_center, sizep, tickc=tickcolor)
+fig1.axis_labels.hide()
 
 ########################################
 # markers

### 2016-05-28 src/singlePanelmom0.py

@@ -6,11 +6,15 @@ Plot mom0 of all channels overlay on HST (single panel)
 Author: Daisy Leung
 
 
-Last edited: 17 May 2016
+Last edited: 28 May 2016
 
 
 History:
 --------
+28 May 2016:
+    - increase font size
+    - longer ticks
+    - zoom in a little to avoid tick label overlaps
 17 May 2016:
     - pythonic
 16 May 2016:
@@ -41,11 +45,11 @@ Plotpath = '../Figures/'
 
 font = {'family': 'Arial Narrow',
         'weight': 'normal',
-        'size': 12.5}
+        'size': 13.5}
 xtick = {'major.size': 10,
-         'minor.size': 6}
+         'minor.size': 6.5}
 ytick = {'major.size': 10,
-         'minor.size': 6}
+         'minor.size': 6.5}
 mpl.rc('font', **font)
 mpl.rc('xtick', **xtick)
 
@@ -63,23 +67,22 @@ for k in label_pdbi.iterkeys():
     file_pdBI = glob.glob(path_pdbi + '*' + k + '*.fits')
     label_pdbi[k] = file_pdBI
 
-figC = plt.figure(1, figsize=(8, 8))
-figC.subplots_adjust(top=0.9, left=0.05, right=0.95)
+figC = plt.figure(1)
 figC.clf()
 ########################################
 # user define area
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.00225
+sizep = 0.0021
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
 width = 0.35
-full_width = 0.78
+full_width = 0.65
 x_gap = 0.05
 x0 = 0.2
-dy = 0.80
+dy = 0.9
 sigma = 0.305       # 0.43    # 0.32e-3 Jy/B
 
 line_min = 0.035668
@@ -145,7 +148,7 @@ if __name__ == '__main__':
     if saveFig:
         outname = 'F555WCO21_mom0_single.eps'
         if inverted_HSTleft: outname = outname.replace('.eps', '.invertedgray.eps')
-        figC.savefig(Plotpath + outname, dpi=600, box_inches='tight')
+        figC.savefig(Plotpath + outname, dpi=600, bbox_inches='tight')
     else:
         #        figC.canvas.draw()
         plt.show()

### 2016-05-28 WRITEUP/table_magFactor.tex
replaced channel range with velocity

@@
 \tablehead{
-\colhead{Channel} &
+\colhead{Velocity Range(\kms)} & % see 22May16/intensity30Apr16.spec; or channel map in paper
 \colhead{Source 1 $\mu_{\rm L}$} &
@@
 \startdata
-126$-$130 & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ [0.6ex] %which is source 1 and 2 then?
-131$-$135 & 7.6 $\pm$ 1.6 & \\ [0.6ex] % would this be source 1 or 2?
-136$-$140 & 8.7 $\pm$ 2.0 & \\ [0.6ex]
-141$-$145 & 4.1 $\pm$ 0.9 & \\ [0.6ex]
-146$-$150 & 4.2 $\pm$ 0.6 & \\ [0.6ex]
-151$-$155 & 4.3 $\pm$ 2.4 & \\ [0.6ex]
-156$-$160 & 3.1 $\pm$ 0.9 & \\ [0.6ex]
-weighted average & 4.4 & \\ [0.6ex]
+$-$366\,$-$\,$-$258 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
+$-$237\,$-$\,$-$151 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
+$-$129\,$-$\,$-$43  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
+$-$21.5\,$-$\,65    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
+86\,$-$\,172        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
+194\,$-$\,280       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
+301\,$-$\,388       & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ [0.5ex]
+weighted average & 4.4 & \\ [0.5ex]
 median & 5.5 &
@@
 \label{tab:model}
-\tablecomments{Source 1 is RXJ1131 and source 2 is its companion. See text for details.}
+\tablecomments{Velocity is taken from the center of each (native) channel
+without any binning. Each row corresponds to a channel slice used for
+lens modeling. Source 1 is RXJ1131 and source 2 is its companion. See text for details. }
 \end{deluxetable}

### 2016-05-28 PdBI/src/modelVelo/calcmass.py
update peak separation

@@ -44,7 +44,7 @@ print M_encl(R_in_kpc, V_rot)/(np.sin(i_rad)**2)
 
 # use line peak separation
 R_in_kpc = 6.22
-V_rot = 220/2.
+V_rot = 400/2.
 # no correction for incl. angle
 print("Mass enclosed within {:.2f} kpc: {:.2f} x 1e+10 Msun".format(R_in_kpc, M_encl(R_in_kpc, V_rot)))
 

### 2016-05-28 PdBI/src/modelVelo/modelGradient.py
make pretty 1st mom + source plan pos plot

@@ -4,9 +4,14 @@
 plot source locations from lens model of various channel as markers on observed 1st moment map.
 Kinematics.
 
-Last Modified: 17 May 16
+Last Modified: 28 May 16
 
 History:
+28 May 2016
+  - add beam to 1st moment + markers plot
+  - add scale bar
+  - add color bar
+  - use patheffects to make markers stand out from background
 17 May 16:
   - move var kpc_to_m to calcmass.py
 15 May 16:
@@ -55,6 +60,8 @@ History:
 
 Note
 ----
+Can only save 1st plot (1st moment + source marker) as pdf, not eps
+
 Fitting data w/ unc. on both x, y using ordinary least squares can lead to bias in the solution. Use Orthogonal Distance Regression (ODR), rather than minimizing the sum of squared errors in the dependent variable, ODR minimizes the orthogonal distance from the data to the fitted curve by adjusting both the model coefficients and an adjustment to the values of the independent variable.
 
  The results of the covariance matrix, as implemented by optimize.curvefit and optimize.leastsq rely on assumptions regarding the probability distribution of the errors and the interactions between parameters; interactions which may exist, depending on the fit function f(x).
@@ -68,16 +75,17 @@ import pyfits
 import pywcs
 import wcsaxes
 import numpy as np
+from astropy.cosmology import WMAP9
+
 
 font = {'family': 'Arial Narrow',
         'weight': 'bold',
         'size': 18}
 matplotlib.rc('font', **font)
-
+matplotlib.rc('text', usetex=True)
 
 Plotpath = '/Users/admin/Research/RXJ1131/Figures/'
 firstMom_obs = '/Users/admin/Research/RXJ1131/PdBI/data/30Apr16/centralizedCube4GILDAS-momCLIP5sigma.velo.fits'
-
 
 interval = 50.        # km/s between velocity contour
 DecCentroid = -12.5328629
@@ -98,7 +106,7 @@ p_list_err = [(0.39, 0.3), (0.25, 0.2), (0.06, 0.21), (0.14, 0.22),
 # corresponding velocity in km/s for each points in p_list
[…]

### 2016-06-19 WRITEUP/table_magFactor.tex
formatting

@@
 \tablehead{
-\colhead{Velocity Range(\kms)} & % see 22May16/intensity30Apr16.spec; or channel map in paper
+\colhead{Velocity Range (\kms)} & % see 22May16/intensity30Apr16.spec; or channel map in paper
 \colhead{Source 1 $\mu_{\rm L}$} &
@@
 \startdata
-$-$366\,$-$\,$-$258 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
-$-$237\,$-$\,$-$151 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
-$-$129\,$-$\,$-$43  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
-$-$21.5\,$-$\,65    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
+-366\,$-$\,-258 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
+-237\,$-$\,-151 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
+-129\,$-$\,-43  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
+-21.5\,$-$\,65    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
 86\,$-$\,172        & 8.7 $\pm$ 2.0 & \\ [0.5ex]

### 2016-06-19 ALMA/Cycle4/pythonSpecOplot/plotSpecMPL.py

@@ -1,10 +1,12 @@
 '''
 Overplot spectra at different spatial location for ALMA C4 proposal
 
+Last Modified: April 16 2016
+
 
 History:
 --------
-Appril 14 2016:
+April 14 2016:
     - edit labels and text annotations
 April 11 2016:
     - copied from Zsearch project: ~/Research/zsearch_Conley/science_goal.uidA001_X121_X1fc/combine

### 2016-06-19 PdBI/src/modelVelo/modelGradient.py

@@ -4,9 +4,12 @@
 plot source locations from lens model of various channel as markers on observed 1st moment map.
 Kinematics.
 
-Last Modified: 28 May 16
+Last Modified: 29 May 16
 
 History:
+29 May 2016
+  - increase font size for first plot
+  - scale bar padding
 28 May 2016
   - add beam to 1st moment + markers plot
   - add scale bar
@@ -137,14 +140,13 @@ ra.set_major_formatter('hh:mm:ss.s')
 ra.display_minor_ticks(True)
 dec.display_minor_ticks(True)
 ra.set_minor_frequency(5)
-ra.set_axislabel(" R.A. (J2000)", minpad=0.5)
-dec.set_axislabel(" Dec", minpad=-0.4)
+ra.set_axislabel(" R.A. (J2000)", minpad=0.5, size=16)
+dec.set_axislabel(" Dec", minpad=-0.4, size=16)
 # ra.set_separator((':', ':'))
-ra.set_ticks(size=10, width=1.5)
-dec.set_ticks(size=10, width=1.5)
+ra.set_ticks(size=16, width=1.5, exclude_overlapping=True)
+dec.set_ticks(size=16, width=1.5)
 ax.set_xlim(120, 143)
 ax.set_ylim(110, 140)
-
 
 # beam
 def draw_ellipse(ax):
@@ -179,7 +181,7 @@ def draw_sizebar(ax, z, pxScale, arcsec=1.0):
                           length,
                           str(round(kpc))+" kpc at " + r"$z = $" + (("{0:.3f}").format(z)),
                           loc=8,
-                          pad=0.1, borderpad=0.5, sep=5,
+                          pad=0.35, borderpad=0.65, sep=5,
                           frameon=False)
     ax.add_artist(asb)
 

### 2016-06-19 PdBI/src/pythonPLOT/COChan.py

@@ -221,6 +221,7 @@ for i, ax in enumerate(g):
     channel_number = start_channel + i
     v = vel.to_vel(channel_number) / 1.e3
     t = ax.add_inner_title(r"$v=%4.1f\ {\rm km s}^{-1}$" % (v),
+                           # (u'$\\mathrm{km/s}$')
                            loc=2,
                            frameon=False
                            )

### 2016-06-19 WRITEUP/Intro.tex
moved stuff to ms.tex and slightly reorganized intro sec

--- 2016-03-29 WRITEUP/Intro.tex
@@
-\documentclass[]{emulateapj}
-\usepackage{amsmath}
-\input{preamble}
-\slugcomment{To be submitted to the ApJ}
+Understanding the baryon cycle has immense implications to our understanding in galaxy evolution...
+Despite the recent progress in theoretical models and observational studies...
 
-\citestyle{aa}
-\shorttitle{TBD}
-\shortauthors{Leung \& Riechers}
+%observed trend
+Studies of galaxy evolution find SFRD and BHAH peak at
+$z$$\sim$2 and declines rapidly toward $z$$=$0. A leading explanation for such
+a trend is the evolution of molecular gas content and SFE in galaxies (CW13).
+Due to higher gas fraction than local, regardless of their position in the SFR-M* plane, both MS and SB at high z have depletion time that is much short than local, suggesting more efficient mode for SF.
+Recent studies also find dynamical evidence for clumpy, globally unstable disks at high-z,
+where SF is enhanced by disk instabilities and not mergers (cite: Genzel+05, Forster-Schreiber+09).
 
-\begin{document}
-%{\tiny  \RevisionInfo}
+While gas-rich systems also exist in local universe, they appear to be
+fundamentally different from high-z galaxies.
+The local gas-rich systems are also those with the highest IR luminosities, commonly known as ultra-luminous IR galaxies (ULIRGs; \LIR\,$>$\,10$^{12}$\Lsun), nearly of all which appear to be [interacting galaxies/galaxy mergers] in different stages of merging (e.g.
+Sanders & Mirabel 1996), powered by SB or AGN.
+While the nature of the power source are still not well-understood.
+Regardless of the energy source ((merger-induced) starburst vs AGN accretion), both
+are fueled by enormous concentration and supply of molecular gas that has been dynamically driven into the circumnuclear regions. However, it is still unclear what processes...
 
-\title{Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654}
-\author{T. K. Daisy Leung and Dominik A. Riechers}
-\affil{Department of Astronomy, Space Sciences Building, Cornell University,
-Ithaca, NY 14853, USA; \myemail}
+However, there is a dearth of CO measurements at intermediate redshifts due to observational difficulties, in which the \aco line is redshifted frequency range currently unavailable.
+Studying the cold gas at the redshift range 0.2 < z < 1 is important though, as the most dramatic change in star formation activity (e.g.
+Madau et al.
+1998, Hopkins & Beacom 2006).
+Up to now, very little is known about the molecular gas content at moderate z.
+The ULIRG sample of Solomon97 contains 37 objects, but only 2 at are z > 0.2.
+With the advance in mm-instruments, Combes+11 investigate the variation of molecuar gas and SFE in an expanded sample of 30 ULIRGs with CO observations.
 
-\begin{abstract}
-\end{abstract}
+% quenching
+While we know blah at the local universe and studies of the gas properties at
+high-z are also emerging in recent years (see CW13 for a review). It is still
+unclear what mechanism is responsible for removing cold gas from galaxies and
+shutting down their star formation to build-up present-day red sequence
+galaxies, leading to a change of slope at high M* (esp. at $z$ $<$ 1.5),  i.e.
+suppression of SFR at high M*, i.e. strong evolution in sSFR (of massive gal.)
+(cite: Papovich, Whitaker+12, Magnelli+14, Schreiber+15, Lee+15).
+% Many star formation suppression or "quenching" processes have been suggested, including mergers, ram pressure stripping, tidal ``harassment", etc.
+One of the more intriguing possibilities, however, is star formation quenching via powerful feedback from AGNs.
 
-\section{Introduction} 
-The gravitational lens RXJ 1131-1231 was discovered with spectroscopic
-redshifts of the lens and the QSO are $z_{\rm L}$ = 0.295 and
-$z_\textrm{AGN,HST}$ = 
-0.658, respectively \citep{}
+% formation of local gal. population
+Physically motivated galaxy evolution models find that feedbacks are needed to turn off SF to build-up present day red sequence galaxies. (Dave+05)
+Current studies agree that ULIRGs are important in giving rise to local
+ellipticals (if mergerd) or spirals with massive bulge (Springel+05).
+But the formation and evolution is unclear due to the limited spatial resolution available in probing the gas of large sample at $z$$>$0.
+Ideally, to understand them would require high resolution to probe the kinematics and strucutral properties.
+The role of merger in building up the mass of galaxies across the universe.
 
-% FG gal is an elliptical gal: Slues+03 absorption lines
+Based on theoretical grounds, the resulting morphology of the merger will depend mainly intial gas ontent and the mass ratio of the merging galaxies.
+Gas provides a dissipative component to remove angular momentum and assist colaspe/funnel to the center.s
 
-As detected in the HST images, RXJ1131-1231 is a quadruply imaged AGN with
-Einstein ring of size 1\farcs83 in radius. The 
-background AGN is lensed into 4 point-like image A,B,C,D on a ring (emission
-from the AGN host galaxy) around G, the foreground galaxy. 
-C06 report the redshift of the background AGN of 0.658 with magnification ~ 9,
-claimed Seyfert 1 spiral galaxy.
+ -- H2 gas more concentrated towards galactic nucleus in local ULIRGs, which are all mergers (e.g. Sanders & Mirabel 1996).
+One explanation to the observed gas concentration toward center: gravitational torques as a result of interactions drive gas towards center towards the circumnuclear regions.
+SB and BH accretion can then be triggered if the dynamical time-scale is shorter than the feedback mechanisms.
 
-In this paper, we BLAH, refining the redshift to $z$=0.654
-We use a cosmology WMAP9.
+% gas dynamics and AGN growth/ evolution
+In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, where distant QSOs are the
+progenitors of the dormant SMBHs in nearby galaxies. Quasars are powered by gas falling into central BHs, when galaxies
+collide or merge.
+On the other hand, it is found that high-z BHs grow faster than their host galaxies since the dynamical mass inferred from CO velocity structure (line width) and spatial extent is lower than the inferred one based on local BH-bulge mass relation.
+Meaning the Magorrian relation doesn't hold at $z$\,$\gtrsim$ BLAH, which means that we need to also understand the
+properties of AGN host galaxies between these epochs.
+From local observations, there is no strict relation between presence of an AGN, companions or barred structures, AGN don't
+show obvious systemic signatures of nuclear fueling form host. Thus, need to trace dynamics of gas in QSO host galaxies to understand the dynamical processes leading to
+gas accumulation/inflow toward center (e.g. bars or merger-driven) for SMBH grow and SB.
 
-\section{Observations}
-\subsection{PdBI} \label{sec:PdBIdata}
-Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
-rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ =
-0.654
- were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
-(Program ID: S14BX001; PI: D. Riechers). 
- Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
-weather conditions in the C and D array configurations, respectively. The 2 mm
-receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line
-and the 
-underlying continuum emission (rest-frame 3.6 mm), employing
-a correlator setup providing an effective bandwidth of 3.6 GHz and spectral 
-resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
-This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time
-after discarding unusable visibility data.
-% D: 1.5 hours; 1055+018 (BP) , 3C279 (RF, fixed flux), 1127-145 (phase/amp),
-% 1124-186(ditto)
-% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186
-% (phase/amp), 1127-145 (ditto)
-% total: 3.75 hours
-%For both tracks, 
-The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
-for
-pointing, secondary amplitude, and phase calibration and 1055$+$018 was
-observed as bandpass calibrators 
-for both tracks.
-MWC349 and 3C279 were observed
-as the primary
-absolute flux calibrator for C and D array observations, respectively, yielding
-$\lesssim
-$15\% calibration accuracy.
+(ULIRGS; \LIR\,$>$\,10$^{12}$\Lsun) are typically and display morphological features/evidence such as double-nuclei (with close separation), tidal tails/features, distorted isophotes, rings/ring-like structure.
 
-The GILDAS package was used to reduce and analyze the visibility data which are
-then imaged and deconvolved using
-the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
-beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA: 13\degr). The final rms noise
-is $\sigma$ =
-0.177 
-Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to
-690 km s$^{-1}$), and $\sigma$ = 1.451 Jy km s$^{-1}$ beam$^{-1}$ over 10 MHz 
-(21.5 km s$^{-1}$) . 
-The continuum image is created by % 2.152 mm; 
-averaging over all the line-free channels ($\nu_{\rm cont}\sim$139 GHz). This
-yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15
+C06 report the with magnification ~ 9, claimed Seyfert 1 spiral galaxy.
 
-\subsection{CARMA} \label{sec:carmadata}
-% LO = 215.6694 Ghz
-% 1127-189 Gain for set 2
-% 3C273 gain for set 3
-% 3C279 Bandpass for both
-% mars flux for both
-% after flagging: Total observing time is  1.48 hours, checked with uvindex for
-% set 3
-% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
-% combined set
-% 12.500 GHz <=> 17.935 km/s
-%
-Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
-rest}$ = 345.7959899 GHz) 
-%toward the background galaxy RXJ1131-1231 at $z$ = 0.654
- were carried out using the Combined Array for Research in Millimeter-wave
-Astronomy (CARMA; Program ID: cf0098; PI: D. Riechers) on 2014 February 17 
-under good 3 mm weather
-conditions and on 2014 February 02 under terrible 3mm weather in the D array
-configurations.  The 3 mm receivers were used to cover
-the 
-redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
-providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
-12.5 MHz ($
-\sim$17.9 km s$^{-1}$). The line was placed in the
-lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
-this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
-flagging poor visibility data. 
-The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
-pointing, amplitude, and phase calibration. Mars was observed as the
-primary
-absolute flux calibrator and 3C279 was observed as bandpass calibrators for
-both tracks. 
-% poor phase note
-Since the phase calibrator from the first track is faint and was observed under
-poor weather and the phase calibrator used for the second track was
-far from our target source.
-Hence, the phase calibration was 
-subpar, with rms scatter $\sim$ 60\degr. 
-We estimate $\sim
-$BLAH\% calibration accuracy based on the flux scale uncertainties, gain variation over time, and 
-the calibrated phase scatter.
-The MIRIAD package was used to calibrate and analyze the visibility data which
-are imaged and deconvolved using
-the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
-beam size of 3\farcs2 $\times$ 1\farcs9 (PA: 8\degr) for the lower sideband
-image cube. The
-final 
-rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$ over a channel width
-of
-25 MHz (corresponding to 35.87 km s$^{-1}$).
-
-\subsection{VLA} 
-% 20081229
-% flux 1331+305
-% phase 1130-149
-
-Observations of the radio continuum toward the
-galaxy RXJ1131-1231 were carried out using the {\it Karl G. Jansky} Very Large 
-Array (VLA; Program ID: AW741; PI: Wucknitz).
-Observations were carried out on BLAH under excellent/GOOD? weather
-conditions in the A array configurations. The C-Band receivers were used to 
-cover the BLAH
-, employing a correlator setup providing a bandwidth of BLAH GHz in each
-sideband. This resulted in BLAH hours of BLAH antenna-equivalent on-source time
-after 
-discarding unusable visibility data.
-
-The nearby radio quasar BLAH was observed every BLAH minutes for
-pointing, amplitude, and phase calibration, and BLAH was observed as the
-primary
-absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding
-$\sim
-$15\% calibration accuracy.
-The AIPS package was used to calibrate and analyze the visibility data which
-are imaged and deconvolved using
-the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
-beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image. The final
-rms 
-noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.
-
-\section{HST astrometry}
-We adopt the VLA 5\,GHz map of BLAH resolution as the reference coordinate frame and align the optical image. We shifted the 
-latter to the east by 0\farcs5963 in R.A and +0\farcs8372 in declination., which is consistent with the typical astrometric precision of the HST image. 
-The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas. 
-We estimate the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
-be better than 0.1", leaving aside uncertainties relating to the SNR and beam size.
-
-%The astrometry of the HST images was firstly calibrated against a wider-field
-%optical image of the cluster which had in turn been aligned onto the FK5
-%coordinate system to an rms precision of ~0.2".
-
-\section{CO($J$ = 3 $\rightarrow$ 2) line emission}
-
-% Integrated line flux: 37.509 Jy km/s over chan=[49,70] (FWZI) of sigma = 13.3mJy /B/channel of 35.87 km/s per channel
-%  57.753459930419922        10.658399798838524
-% 38.906448364257812        54.223567641493943
-% 258.26144409179688        57.450322398332851
-% 2.2153112888336182        2.9563491085933622
-
-% If we fit gaussian without the continuum to minimize error:
-% 58.848747253417969        10.030933764224825
-% 36.368530273437500        54.749284630860281
-% 276.93515014648438        54.753666156237443
-
-We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
-background galaxies in RXJ1131-1231.
-We extract the spectrum and fit a single-component Gaussian as shown in Figure
-\ref{fig:co32spec}
-yielding peak flux density of 57.8 $\pm$ 10.7 mJy, the FWHM of the Gaussian fit
-is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in the calibration.
-
-\begin{figure}[tbph]
-\centering
-\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}	  
-\caption{
-CO32 line spectrum
- \label{fig:co32spec}}
-\end{figure}
-
-% line free channels:1,118,160,600
-% nchan =(117+600-160+1) = 558
-% sigma =  0.83 mJy/B
-
-At spatial position of CO emission, No significant continuum emission was
-detected from the line-free channels down to a 3$\sigma$ limit of 2.49mJy Beam\pmOne.
-(also as suggested in the fitted Gaussian to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CO($J$ = 2 $\rightarrow$ 1) line emission}
-
-% intensity over chan 124, 156 of rms ~ 1.451 mJy/ Beam/ch
-% velocity resolution per bin: 21.528154 km/s
-
-%sigma_mom0 = 0.43  over chan: 127, 155
-
-We detect dynamically resolved CO($J$ = 2 $\rightarrow$ 1) line emission toward
-the background galaxies in RXJ1131-1231.
-
-We construct the velocity-integrated (0th moment) map of the CO($J$ = 2
-$\rightarrow$ 1) emission using the uv-continuum subtracted data, the
-velocity-integrated 
-CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ 0.2 Jy km s$^{-1}$.
-
-We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.451mJy per channel per beam.
-Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$ limit of 4.353 mJy \kms beam\pmOne.
-
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=0.35\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}	   
-\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
-\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
-\caption{
-0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping, of $\sigma$ 0.43 mJy beam\pmOne. 
-Spectrum. Velocity scale w.r.t z=0.655
- \label{fig:CO21mom0}}
-\end{figure*}
-
-\begin{figure}[tbph]
-\centering
-\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       
-\caption{
-1st and 2nd order moments, clipped at 5 $\sigma$. 1st moment contour steps of 50 \kms, 2nd moment steps of 100 \kms.
-velocity range in z=0 frame = [-530.33, 72.73] \kms
-chan = [127, 155] 
-sigma = 0.16821825 Jy \kms per Beam
-theshold: 5*sigma = 7.2550e-3 Jy per beam (per channel)
- \label{fig:highOmoments}}
-\end{figure}
-
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}	 %
-\caption{
-Black crosses indicate the position of the lensed AGN (components ABCD) and the central white-filled star indicates the
-position of the foreground lensing galaxy (component G) as detected in the HST image.
- \label{fig:chanmap}}
-\end{figure*}
-
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}   
-\caption{ 
-Spatial spectra, binned by 3 pixels in each direction (1\farcs5)
- \label{fig:spatialSpec}}
-\end{figure*}
-
-\section{Continuum}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PdBI
-% 2mm continuum averaged over chan 1 120 165 360
-% number of channels = 316
-% sigma = 1.451 mJy/B / sqrt(316) = 0.081625 mJy/B 
-% go noise on map (whole map) after cleaning: 89.274 µJy/B
-% F = 1.2 mJy (integrated spatially, from ~ 1 sigma contour; 150 pixels)
-%
-% 2mm peak is centered on foreground galaxy ~ 799 µJy/B --> with C band --> spectral index
-%	- 2mm marginally resolved along one axis (arc)
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% VLA C Band
-%
-
-VLA C Band continuum image shows resolved jets and core emission from the foreground lensing galaxy as well as the background lensed quasar (as arcs).
-We extracted the 5GHz fluxes for the arcs and the core as listed in Table \ref{tab:photometry}.
-
-As shown in Figure \ref{fig:cont}, we detect 2mm continuum emission toward both the foreground galaxy and the background as lensed emission.  
-The integrated continuum flux density is 1.2 mJy, while the peak emission is centered on the foreground galaxy at $S_\nu$ of 8 \micron Jy beam\pmOne.
-The detection is hence marginally resolved along one axis as shown in Figure \ref{fig:contco21}.
-We attempted to extract the background emission by subtracting the foreground emission as modeled by a point source (unresolved).
-But the residual after removing a point source model is just noise.
-So we I guess if we take the difference between the integrated and the  peak in the image plane is an upper limit to the background source at 2mm, which is $\sim$ 0.4 mJy.
-
-We fit power law to the VLA radio data and the 2mm continuum, we derive a spectral index of $\alpha$=0.025.
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=0.8\textwidth]{../Figures/ContCO21.eps}	  
-\caption{CO 21 moment0 overlay on 2mm continuum.  % chan [127,155]	
-TODO: add the beam
- \label{fig:contco21}}
-\end{figure*}
-
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=0.8\textwidth]{../Figures/Cont2mm_5GHz_double.eps}    
-\caption{VLA 5GHz continuum and PdBI 2mm continuum
- \label{fig:cont}}
-\end{figure*}
-
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
-\includegraphics[width=0.55\textwidth]{../Figures/F555W_ContVLA.eps}
-\caption{
-can kill left figure eventually by combining this to ContCO21.eps
-Right: alignment of HST and VLA 5 GHz continuum
- \label{fig:}}
-\end{figure*}
-
-\section{\rot{2}{1} Lens model}
-
-\subsection{interpretation}
-- C06 suggest the presence of an interacting dusty galaxy in their HST
-observations, which BJB+08 calls it the F component. The lensed images of the
-ABCDE 
-components coincide with our CO data (see mom0 on HST and channel map),
-evidently CO emission coming from the AGN host galaxy. 
-- one of the red channels in our lens model suggests a second source component,
-which is consistent with the spatially offset dusty source (see mom0 on HST,
-which 
-the red velocity component coincides with this F component)
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-We compare our lens model parameters on the mass distribution of the lensing
-galaxy with literature, particularly against the SIE model presented by C06. 
-In C06, their SIE model shows position of lensing mass is offset by (-0.015",
--0.041" from obsservations (i.e. light centroid)); PA = -73.6, ellipticity = 0.45,
-theta\_R = 1.84" $\pm$ 0.01. 
-Our best-fit model parameters finds a BLAH
-	- Our model lens parameters (median):
-		- file: WRITEUP/MedianLensModelParams.txt
-		- lensing gal. position is consistent with C06, 
-		- Einstein radius: consistent with C06
-		- PA: consistent within errors
-		- Axial ratio: consistent within errors
 %%%%%%%%%%%%%%%%%%%%%%%%%
 
-Differential lensing is at play as suggested by the spectral shape of the \rot{2}{1} line profile, where 
-flux density in the red wing is much high than in the blue wing.  
-We modelled the emission using different kinematic components, the magnification factors are reported in Table BLAH.
-\input{table_magFactor}
+\section{IRAC}
+For the IRAC channels, the point spread function (PSF) is undersampled and thus photometry was extracted in circular apertures of radius 3?pixels (?3.6?arcsec) with background determined in an annulus of inner radius 12?pixels and outer radius 20?pixels (?14.4?24?arcsec).
+Apertures were centred on the location of each source as listed in Tables 1 and 2.
+Array location-dependent corrections were applied to the IRAC photometry.
+Correction images available online at http://ssc.spitzer.caltech.edu/irac/calibrationfiles/locationcolor/ were mosaicked in the same way as the data frames to produce a correction mosaic.
 
-\begin{figure}[tbph]
-\centering
-\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.eps}
-\includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
-\caption{
-Pseudo observed 0th moment map in the lens plane. (left)
-Pseudo 0th moment map in the source plane. (right)
-\label{fig:}}
-\end{figure}
+The aperture photometry of a source was then multiplied by the value of the correction mosaic at the centre of the source image.
+Aperture corrections were taken from tabulated values listed in the IRAC Data Handbook.
+Colour corrections were applied by interpolation from tabulated values using the source effective temperatures as listed in Tables 1 and 2.
+Absolute calibration of the IRAC is stable to 1?3?per cent (Reach et al.
+2005).
+We add a 3?per cent calibration uncertainty in quadrature to statistical background errors from pixel-to-pixel variation determined in the aperture module to give a final error on the IRAC photometry.
+The photometry was de-reddened using the values determined by Sanner et al.
+(2000) converted to IRAC wavelengths using relations of Flaherty et al.
+(2007).
+The final photometry is listed in Tables 3 and 4.
 
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=0.65\textwidth]{../Figures/PostageStampModel.eps}
-\includegraphics[width=0.65\textwidth]{../Figures/PostageStampResiduals.eps}
-\caption{
-of channel widths $\sim$ 100\kms. 
-\label{fig:}}
-\end{figure*}
-
-\begin{figure}[tbph]
-\centering
-\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.eps}
-\caption{
-velocity gradient of the lens model in the lens plane (left), source plane
-(right).
-\label{fig:}}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SED}
-
-We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side and including the 24.0\micron data from Spitzer/MIPS to constrain the dust peak. 
-Also do SED fit with IRAS upper limits.
-
-\begin{figure*}[tbph]
-\centering
-\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}	 
-\caption{TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 2mm PdBI (now integrated and peak), extract flux after removing a point source model.
-Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux extraction.
-Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied. Spitzer/MIPS: PSF fit flux, as source size < native PSF FWHM of 6".
-Might want to add NVSS constraints.
- \label{fig:}}
-\end{figure*}
-
-\input{table_photometry_AAScustomized}
-
-\end{document}
+%%%%%%%%%%%%%%%%%%%%
+CO/H2 conversion factor:
+while alphaCO of 0.8 is advocated for ULIRGs.
+The conversion factor in these dynamically turbulent system could be different than BLAH since the gas is potentially warmer, more excited, and denser; the conversion factor X\_CO scales as sqrt(n)/T.

### 2016-06-19 WRITEUP/ms.tex
incoporated some DR comments, added source ID in intro, added ack section, fixed wrong peak separation and dynamical mass

@@
 \citestyle{aa}
-\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131 at $z$\,=\,0.65}
+\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131-1231 at $z$\,=\,0.65}
 \shortauthors{Leung \& Riechers}
@@
 \begin{abstract}
+We \bco observations with the \pdbi.
+evidence for differential lensing. 
+wet-merger, Dynamical lens modeling 
+the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations. 
 \end{abstract}
@@
 \section{Introduction}
-We use a concordance $\Lambda$CDM cosmology throughout this paper, with parameters from the WMAP9 results:
-$H_0$ = 70 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.27, and $\Omega_{\Lambda}$ = 0.7 \citep{Hinshaw13a}.
+
+In this paper, we explore the ISM properties of the quadruply imaged
+quasar RXS J113151.62-123158 (hereafter RXJ1131) at
+$z_\textrm{AGN}$\,$=$\,0.685, with an Einstein ring of size
+1\farcs83 in radius. The foreground lensing
+galaxy is an elliptical galaxy at $z_\textrm{L}$\,$=$\,0.295. The redshifts
+are spectroscopically confirmed by \citet{Sluse03a}. 
+A black hole mass estimate of M$_{\rm BH}$\,$<$\,2\E{8}\Msun 
+is also reported based on X-ray observations \citep{Reis14a}.
+
+This paper is structured as follows.
+In \Sec{obs} and \Sec{HST}, we outline the details of the observations and data reduction process.
+In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths. 
+In \Sec{anal}, we represent our dynamical lens modeling on the \bco data and the physical properties inferred for  RXJ1131.
+In \Sec{diss}, we discuss the results and implications of this study in the context of molecular gas evolution in mergers and massive galaxies.
+Finally, we summarize the main results of this study and present our conclusions in \Sec{sum}.
+We use a concordance $\Lambda$CDM cosmology throughout this paper, with
+parameters from the WMAP9 results:
+$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
+$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
+% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
 
@@
 %--------------------------------------------------------------------------
-\section{Observations}
+\section{Observations} \label{sec:obs}
 \subsection{PdBI \bco} % DONE
-Observations of the \bco rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz)
+Observations of the \bco rotational line
+($\nu_{\rm rest}$\,=\,230.5379938 GHz; $\nu_{\rm obs}$\,=\,139.4\,GHz)
 toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658
@@
 The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
-for pointing, secondary amplitude, and phase calibration and 1055$+$018 was
+for pointing, secondary amplitude, and phase calibration, and 1055$+$018 was
 observed as the bandpass calibrator for both tracks.
-MWC349 and 3C279 were observed as the primary flux calibrator for C and D
+MWC349 and 3C279 were observed as primary flux calibrators for the C and D
 array observations, respectively, yielding $\lesssim$15\% calibration accuracy.
@@
 weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
-The final rms noise is $\sigma$ = 1.451 mJy \kms
-beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
-is created by averaging over all the line-free channels. This
-yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15
+The final rms noise is $\sigma$\,=\,1.45\,mJy\,\kms
+beam\pmOne over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
+is created by averaging over all the 3.16\,GHz line-free channels. This
+yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
 
 \subsection{CARMA \cco} %DONE
-Observations of the \cco rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz)
-were carried out under the D array configurations of the \carma (CARMA;
-Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 1.5\,mm
+Observations of the \cco rotational line in RXJ1131
+($\nu_{\rm rest}$\,=\,345.7959899\,GHz; $\nu_{\rm rest}$\,=\,209.1\,GHz)
+were carried out with the \carma (CARMA;
+Program ID: cf0098; PI: D. Riechers)
+in the D array configuration on 2014 February 02 under poor 1.5\,mm
 weather conditions and on 2014 February 17 under good 1.5\,mm
@@
 % /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
+% rms scatter over ~ 90 klambda
+% max baseline of obs. is 145 m
 %
@@
 % MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
+%
 Given that the phase calibrator used for the first track was faint and was
@@
 the second track was far from our target source, the phase calibration is
-subpar, with an rms scatter $\sim$60\degr. We thus conservatively estimate
+subpar, with an rms scatter $\sim$60\degr over $\sim$135\,m.
+%BLAH... more like 50%
+We thus conservatively estimate
 a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
@@
 therefore treat its line intensity with caution and ensure that any physical interpretation
-of this system (and thus implications and conclusions of this paper) do not rely on this quantity.
+of this system does not rely on this quantity.
 
@@
 then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
-beam size of 3\farcs2 $\times$ 1\farcs9 (PA = 8\degr) for the lower sideband
+beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
 image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
-over a channel width of 25 MHz. An rms noise of
-$\sigma$ = 0.831 mJy beam\pmOne is reached by averaging over the
+over a channel width of 25\,MHz. An rms noise of
+$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
 line-free channels.
 
-\subsection{VLA} %DONE
-Our analysis also use the archival data of the radio continuum obtained with the \vla (VLA; Program ID: AW741; PI: Wucknitz).
-Since the observations have not been described in any previous publications,
-we here describe their details as well as our calibration steps.
-
+\subsection{VLA (Archival)} %DONE
+Our analysis also uses archival data of the 5\,GHz
+radio continuum obtained with the
+Very Large Array (VLA; Program ID: AW741; PI: Wucknitz).
 Observations were carried out on 2008 December 29 under excellent weather
@@
 
-\section{HST astrometry} %DONE
-We obtain {\it HST} images from the Hubble Legacy Archive with
-a goal to understand the origins of the emission detected
-in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
-resolution as the reference coordinate frame to align the optical ($V$-band) image.
+\section{HST astrometry} \label{sec:HST}
+We obtained an {\it HST} image taken with the F555W filter ($V$-band)
+using the ACS/Wide Field Camera from the
+Hubble Legacy Archive\footnote{Based on observations
+made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
+Legacy Archive, which is a collaboration between the Space Telescope Science
+Institute (STScI/NASA), the Space Telescope European Coordinating Facility
+(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}
+with a goal to understand the origin of the emission detected
+in our mm observations. The details of the observations can be found
+in C06. We adopt the VLA 5\,GHz map of
+$\sim$0\farcs5 resolution as the
+reference coordinate frame to align the optical ($V$-band) image.
 We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
-Dec., which is consistent with the typical astrometric precision (1$-$2$^{\prime\prime}$) of
+Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
 images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
-html}. Such astrometric correction is critical to avoid artificial spatial
+html}. This astrometric correction is critical to avoid artificial spatial
 offsets between different emitting regions and to carry out our lens modeling,
@@
 %--------------------------------------------------------------------------
-\section{Results}
+\section{Results} \label{sec:results}
 \subsection{\bco Emission} \label{sec:CO21} %DONE
-We dynamically resolved the \bco line emission toward the background galaxies
+We detected the \bco line emission toward the background galaxies
 at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
-0.65370 $\pm$ 0.0005. A highly asymmetric double-horned line profile is
-detected as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
-flux densities of 75.3$\pm$2.6 and 24.0$\pm$2.0 mJy, and a FWHM of
-179$\pm$9 \kms and 255$\pm$28 \kms, respectively. The peaks are separated by
-$\Delta v_{\rm sep}$ = 220 \kms. The integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/
-
-\begin{figure}[tbph]
+0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
+with a highly asymmetric double-horned line profile
+as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
+flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
+179$\pm$9 \kms and 255\pmm28 \kms, respectively. The peaks are separated by
+$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/
+
+\begin{figure}[!htbp]
 \centering
@@
 is with respect to $z$=0.6537, which is approximately the line center
-considering the asymmetry is as a result of differential lensing.
-A more detailed discussion of differential lensing effect is presented in
+considering the asymmetry as a result of differential lensing.
+A detailed discussion of this effect is presented in
 \Sec{differential} and the magnification factors for various kinematic
@@
 
-% moment 0 map: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
+% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
 % - sigma = 0.305 Jy km/s/Beam
 %   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
-We construct the zeroth, first and second moment maps shown in \Fig{CO21mom}
-using the $uv$-continuum subtracted data cube, over $\Delta v$$\sim$750 \kms.
-The first and second moment maps are clipped at 3$\sigma$.
-The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne in the intensity-integrated
-map. The deconvolved source size is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66
-and thus the emission is resolved over $\sim$2.2 beams.
-While the lensed emission is not strictly distributed as 2D-Gaussian,
-the fit recovers the line intensity enclosed within the emitting
+We construct the zeroth moment map (\Fig{CO21mom}) and
+the higher-order first and second moment maps (\Fig{CO21highO})
+using the $uv$-continuum subtracted data cube over a velocity range of
+$\Delta v$ $\sim$ 750\,\kms. The higher-order moment maps are created using
+channel maps with 3$\sigma$ clipping.
+The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
+in the intensity-integrated map. The deconvolved source size FWHM
+is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
+and thus, the emission is resolved over $\sim$2.2 beams.
+While the lensed emission is not strictly distributed as two-dimensional
+Gaussian;
+the fit recovers the line intensity enclosed by the emitting
 region, we therefore take this as an estimate on the extent of the lensed
@@
 optical image, with most of its apparent flux originating from the lensed arc
-in the Southeast, whereas the blue component is predominately coming from
+in the southeast, whereas the blue component is predominately coming from
 solely the lensed arc shown in \Fig{CO21mom}. To illustrate this, we show the
@@
 show that emission
-is present to the West, peaking toward the lensing arc (black across in
-\Fig{chanmap}) in the red wing, and shifts to the East with decreasing velocity
+is present to the west, peaking toward the lensing arc (black crosses in
+\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
 (blue wing).
@@
 emission from different kinematic components is separated by different amounts
-relative to the caustics. One consequence of such is the observed asymmetric
+relative to the caustics, leading to the observed asymmetric
 line profile. A detailed analysis on differential lensing of \bco is presented
-in \Sec{differential}.
-
-\begin{figure*}[tbph]
+in \Sec{differential}, where we present our lens model.
+
+\begin{figure*}[!htbp]
 \centering
@@
 
-\begin{figure*}[tbph]
+\begin{figure*}[!htbp]
 \centering
-\includegraphics[width=0.85\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
+\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
 \caption{
 \bco spectrum as a function of position, binned by 3 pixels in each
-direction (1\farcs5). The spectra map covers an extent of $\sim$10"$\times$10"
-centering on the pixel that corresponds to the lensing galaxy. The velocity
-and flux density scales are denoted in the top right panel.
-BLAH: DR would want the pixel coordinates replaced by arcsec offset from
-center. \label{fig:spatialSpec}}
+direction (1\farcs5).
+The spectra map covers an extent of $\sim$10"$\times$10"
+centering on the pixel that corresponds to the lensing galaxy.
+Spatial offset in arcsec is denoted in top left corner of each panel.
+The velocity and flux density scales are denoted in the top right panel.
+\label{fig:spatialSpec}}
 \end{figure*}
 
-We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted
-frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of
-$\sigma$ = 1.451mJy per channel beam\pmOne.
-Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$
-limit of 4.353 mJy \kms beam\pmOne.
+We also place an upper limit on \rot[HNC]{2}{1} line emission
+in the foreground galaxy at $z\sim$0.295.
+Assuming a typical line width of 300\,\kms, this corresponds to a 3$\sigma$
+limit of 0.35\,mJy\,\kms\,beam\pmOne.
 
@@
 \subsection{\bco Kinematics} % DONE
-A clear velocity gradient and an unusually high
+A clear velocity gradient and a high
 velocity dispersion ($\gtrsim$400\,\kms) near the central region
@@
 at the spatial resolution of this data, the exceedingly
-high velocity dispersion hints
+high velocity dispersion may hint
 at potential perturbations from the AGN, or internal turbulence due to
@@
 detection. We thus estimate the line intensity to be
-35.7$\pm$ 21.9 Jy\,\kms by summing up fluxes over the
+35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
 linewidth used to infer \bco line intensity ($\sim$700 \kms).
@@
 \caption{CARMA \cco line profile (solid) without continuum subtraction is
-over-plotted on the continuum-subtracted \bco line profile (dashed).
+over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
 The velocity scale is with respect to $z$=0.6537, which corresponds to the
@@
 $r_{\rm 32}$\,=\,T$_{\small \cco}$$/$T$_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
-The high uncertainty is dominated by the uncertainties in the \cco line
-intensity.
-
-\subsection{Interferometric Continuum} %DONE
+
+\subsection{Continuum Emission} %DONE
 No 1.5\,mm continuum emission is detected at the position of \cco
-down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
+down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
 This is consistent with the spectrum shown in \Fig{co32spec}.
@@
 1.2\pmm0.2 mJy, with a peak flux
-$S_\nu$\,=\,800\pmm88\,\micron Jy\,beam\pmOne
-centering on the lensing galaxy. A slightly extended emission is also seen
+$S_\nu$\,=\,800\pmm88\,$\mu$Jy\,beam\pmOne
+centering on the lensing galaxy. Slightly extended emission is also detected
 along the lensed arc. This suggests that the detected emission comes from
@@
 %\centering
-\includegraphics[trim=12 27 0 0, clip, width=0.45\textwidth]{../Figures/F555W_ContPdBI.eps}
-\includegraphics[trim=10 5 0 0, clip, width=0.475\textwidth]{../Figures/F555W_ContVLA.eps}
+\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
+\includegraphics[trim=13 5 0 0, clip, width=0.475\textwidth]{../Figures/F555W_ContVLA.eps}
 \caption{Top: an overlay of the 2\,mm continuum emission on the optical image.
@@
 We extract the flux densities for the arc and the core in \Tab{photometry}.
-We find a spectral index of $\alpha$\,=\,$-$0.024 for the foreground
-galaxy and $\alpha$\,=\,$-$0.345 for the background galaxy by fitting a
+We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
+for the foreground
+galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
+for the background galaxy by fitting a
 power-law (S$_\nu \propto \nu^{\alpha}$) to the continuum emission at
@@
 \subsection{Photometry} \label{sec:photometry} %DONE
-We compile \mir to \fir broadband photometry (uncorrected for
-dust extinction) from various
+We compile \mir (MIR) to \fir broadband photometry from various
 catalogs available on the NASA/IPAC Infrared Science
@@
 the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
-Wide-field Infrared Survey Explorer ({\it WISE}; \citealt{Wright10a}),
-{\it Infrared Astronomical Satellite}
+the Wide-field Infrared Survey Explorer ({\it WISE}; \citealt{Wright10a}),
+the {\it Infrared Astronomical Satellite}
 ({\it IRAS};\citealt{Neugebauer84a}), and
@@
 Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
-\spitzer.
+the \spitzer.
 We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
 Spitzer Heritage Archive and perform aperture photometry on
-the channel 1 image to extract flux density at 3.6\,$\mu$m
+the channel 1 image to extract the flux density at 3.6\,$\mu$m
 since it is not available from the IRSA archive.
@@
 to obtain decomposed flux measurements from the background galaxy.
-The photometries for the foreground galaxy are then obtained
+The photometry for the foreground galaxy is then obtained
 by subtracting the background emission from the
 observed total flux. The resulting photometry in
-\Tab{photometry} are obtained after performing aperture correction
+\Tab{photometry} are obtained after performing an aperture correction
 described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
 correct for the fact that the imaging was calibrated
-using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
+using a 12" aperture, which is larger than the aperture (5\farcs8) we used to
 perform aperture photometry.
@@
 decomposed IRAC photometry to disentangle the observed total flux
-at MIPS 24$\micron$. We find a spectral index of $\alpha\sim-$1.8 and
+at MIPS 24\,$\micron$ into the foreground and
+background galaxies. We find a spectral index of $\alpha\sim-$1.8 and
 $\alpha\sim-0.85$ for the lensing galaxy and RXJ1131, respectively.
@@
 Extraction of the {\it Herschel}/SPIRE photometry was
-carried out using \ncode{sussextractor} within Herschel Interactive
+carried out using \ncode{sussextractor} within the Herschel Interactive
 Processing Environment (HIPE; \citealt{Ott10a})
-over the Level 2 maps obtained from the Herschel Science Archive.
+on Level 2 maps obtained from the Herschel Science Archive.
 These maps were processed by the SPIRE pipeline
@@
 %--------------------------------------------------------------------------
-\section{Analysis}
+\section{Analysis} \label{sec:anal}
 \subsection{Lens modeling} \label{sec:lensmodel} %DONE
@@
 an intrinsic velocity gradient across the source plane, which is
-indicative of a disk-like galaxy. While solely based on the
-lens model is insufficient to draw conclusive inference on its
-true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
+indicative of a disk-like galaxy.
+Additional support to the disk conjecture %conjecture of a disk morphology
 can be found in the double-horned line profile (\Fig{CO21spec})
@@
 (component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
-and C06, who find evidence for an interacting dusty galaxy.
+and C06, who find evidence for an interacting galaxy near RXJ1131.
 Spatially, the red velocity component of the CO also coincides with this
@@
 
-We emphasize that the spatial resolution of the data in hand
+The spatial resolution of the data in hand
 is a few arcsec, which implies that despite the high SNR and spectral
@@
 intrinsic sizes of the lensed galaxies, and thus the magnification
-factors are likely under-predicted.
-We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15
+factors may be under-predicted.
+% magnification factor is underpredicted, see Bussmann15
 
 \begin{figure*}[tbph]
-%\centering
-\includegraphics[width=1.0\textwidth]{../Figures/PostageStampModel.eps}
-\includegraphics[width=1.0\textwidth]{../Figures/PostageStampResiduals.eps}
+\centering
+\begin{tabular}{c}
+\includegraphics[trim=0 0 0 0, clip, width=1.0\textwidth]{../Figures/PostageStampModel.eps} \\
+\includegraphics[width=0.98\textwidth]{../Figures/PostageStampResiduals.eps}
+\end{tabular}
 \caption{Each panel corresponds to a lens model of RXJ1131 performed over a
@@
 \subsection{\bco Dynamical modeling} \label{sec:dynamics} %DONE
-This section proceeds under the assumption that RXJ1131 is
-a rotating disk (see previous sections).
-Assuming the velocities of the respective channels used in
+Assuming the velocities of the respective channels used in the
 lens modeling correspond to solely the tangential component of the
-true velocity vector (i.e., along the major axis), we extract
-a one dimensional PV diagram in \Fig{PV}
+true velocity vector of a rotating disk (i.e., along the major axis),
+we extract a one dimensional PV diagram in \Fig{PV}
 by slicing across their source plane positions (PA: 121\degr).
 
-We attempt to characterize the molecular gas kinematics using an
+We then attempt to characterize the molecular gas kinematics using an
 empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
@@
 $R_{t}$\,=\,10.6\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
-We note, however, that since emission is not detected beyond the flat regime
+However, since emission is not resolved along the flat regime
 of the rotation curve, the asymptotic velocity is poorly constrained and
@@
 \centering
+\includegraphics[width=0.4\textwidth]{../Figures/veloGradient_markers}
 \includegraphics[width=0.455\textwidth]{../Figures/bestfit_PV.eps}
-\caption{PV slice along the major axis in the source plane at PA\,=\,121\degr.
+\caption{Top: Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
+the observed first moment map. The contours are at steps of 50\,\kms.
+Bottom: PV slice along the major axis in the source plane at PA\,=\,121\degr.
 Dashed line shows the best-fit rotation curve using an arctangent model.
@@
 1$\sigma$ uncertainties on the source plane positions.
-DR may suggest include 68\& fits from MC simulation, maybe I will do that later.
  \label{fig:PV}}
@@
 
-We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
+The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
 out to radius beyond the disk scale-length and half-light radius --
-is inequivalent to maximum observed velocity ($V_{\rm max}$),
+is not equivalent to maximum observed velocity ($V_{\rm max}$),
 which is commonly used in literature to parameterize disc rotation.
@@
 
-Using the $V_{\rm rot}$ from last paragraph, we find a dynamical mass of
+Using our estimate of $V_{\rm rot}$, we find a dynamical mass of
 $M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$\,=\,17\E{10}\,\Msun enclosed
@@
 line peak separation from the
-\bco line profile $\Delta v_{\rm sep}/2 \sim$110\,\kms, we find
-$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 1.8\E{10}\,\Msun.
-{\bf DR: here, I list the extrema for possible Mdyn given our data,
-should I say anything more?}
+\bco line profile $\Delta v_{\rm sep}/2 \sim$200\,\kms, we find
+$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$\,=\,5.8\E{10}\,\Msun.
 We correct for the inclination effect using the
@@
 The dynamical mass is then
-2.5\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
+8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
 Since this quantity is derived under the assumption that the gas is
@@
 presence of a close companion, our estimate is
-at most a lower limit. We caution that this analysis is
-based on limited spatial
-resolution data and will be verified with future higher-resolution
-observations.
+at most a lower limit.
 
@@
 The fit is performed with the code
-\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which samples the posterior
+\ncode{mbb\_emcee} \citep[\eg][]{Riechers13a,Dowell14a}, which samples the posterior
 using an MCMC approach and uses instrumental
@@
 taken for the burn-in phase (which are then discarded).
-Here we report the modes %in log file
+Here we report the means % modes in log file
 % summary statistics (global mode (where min. chi),
@@
 % need to compute)
-and the 1$\sigma$ confidence intervals in the marginal PDFs
+and the 1$\sigma$ confidence interval in the marginal PDFs
 as the best-fit parameters, as listed in \Tab{SED}.
@@
 3.81\petm{2.04}{1.92}\E{12}\,\Lsun and a
-dust mass of 22\petm{5}{18}\E{8}\,\Msun.
+dust mass of 22\petm{5}{18}\E{8}\,\Msun, uncorrected for lensing.
 For the mass absorption coefficient, we adopt
@@
 include those in the absorption coefficient.
-These values are not corrected for lensing.
 
 A fit including the MIR 24\,$\micron$ photometry
-is likely an upper limit on the \fir luminosity arising from starburst.
+is likely an upper limit on the \fir luminosity arising from the starburst
+in the AGN host galaxy.
 % since the fit include contribution from the AGN (through power-law to MIR)
@@
 a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
-dust mass ($M_{\rm dust}$) of 11\petm{5}{6}\E{8}\,\Msun.
-Taken at face value, this implies a \LFIR-to-\LIR
-contribution of $\sim$58\%.
+dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
+Taken at face value, this implies a \LFIR-to-\LIR ratio
+of $\sim$58\pmm BLAH\%.
 Again, the inferred quantities are uncorrected for lensing.
@@
 \caption{SED models of the IR dust emission toward RXJ1131.
-The data are not corrected for lensing magnification and dust extinction.
 {\bf This figure needs an update}
@@
 we derive the \fir luminosity following this convention.
-This yields $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
+This yields $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
 a SFR of $($150\pmm 70$)$\,\sfrU.
@@
 If we instead adopt the
-more generally used definition for the total IR luminosity
-(\LIR\,$>$\,10$^{12}$), RXJ1131 would be
+more generally used definition for the total IR luminosity,
+calculated using 8\,$-$\,1000\,\micron, RXJ1131 would be
 considered a ULIRG given its lensing-corrected
@@
 % Combes+13: sample of 39 gal from z= 0.2-1 find $<$ 100 Myr.
-\textbf{ am I doing something wrong...}
 
@@
 %--------------------------------------------------------------------------
-\section{Discussion}
+\section{Discussion} \label{sec:diss}
 \subsection{Merger stage of RXJ1131-1231}
@@
 \footnote{In this section, we adopt the total IR luminosity
-calculated from 8\,$-$\,1000\,\micron
+calculated from 8\,$-$\,1000\,$\micron$
 to be consistent with the classification used by these authors.}.
@@
 
-An alternative explanation might be that the
-CO is less strongly-magnified as compared to the dust emission,
-in which case, the lensing-corrected IR luminosity is overestimated.
-This is plausible given the extent of the source with respect to the caustics
-and that substantial differential lensing effect has been seen across
-CO and other wavelengths. If we instead use the NIR ($H$-band) magnification
-factor ($\mu_{\rm L}$\,=\,BLAH; C06),
-we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is
-a large gas-rich LIRG, and a minor merger in the context of the results
-reported by \citet{Carpineti15a} and L16.
-
 {\bf --- anything below is not ready ---}
@@
 %--------------------------------------------------------------------------
-\section{Summary and Conclusions}
+\section{Summary and Conclusions} \label{sec:sum}
 % see Hodge12_dynamics.pdf for guide
@@
 \acknowledgments
+This work is based on observations carried out under project number S14BX001
+with the IRAM NOEMA Interferometer. IRAM is supported by INSU/CNRS (France), MPG (Germany) and IGN (Spain).
+Support for CARMA construction was derived from the Gordon and Betty Moore
+Foundation, the Kenneth T. and Eileen L. Norris Foundation, the James S.
+McDonnell Foundation, the Associates of the California Institute of
+Technology, the University of Chicago, the states of Illinois, California, and
+Maryland, and the National Science Foundation. Ongoing CARMA development and
+operations are supported by the National Science Foundation under a
+cooperative agreement and by the CARMA consortium universities.
+The National Radio Astronomy Observatory is a facility of the National Science
+Foundation operated under cooperative agreement by Associated
+Universities, Inc.
+This research made use of data obtained with {\it Herschel}, an ESA space
+observatory with science instruments provided by European-led Principal
+Investigator consortia and with important participation from NASA.
+This research has made use of NASA's Astrophysics Data System Bibliographic
+Services.
+This work is based in part on observations made with the \spitzer,
+which is operated by the Jet Propulsion Laboratory, California Institute of
+Technology under a contract with NASA.
+This publication made use of data products from the Wide-field Infrared
+Survey Explorer, which is a joint project of the University of California, Los
+Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
+funded by the National Aeronautics and Space Administration.
+This publication made use of data products from the Two Micron All Sky
+Survey, which is a joint project of the University of Massachusetts and the
+Infrared Processing and Analysis Center/California Institute of Technology,
+funded by the National Aeronautics and Space Administration and the National
+Science Foundation.
+This research made use of the NASA/IPAC Extragalactic Database (NED) which
+is operated by the Jet Propulsion Laboratory, California Institute of
+Technology, under contract with the National Aeronautics and Space
+Administration.
+This research made use of Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
+This research made use of APLpy, an open-source plotting package for Python hosted at \url{http://aplpy.github.com}.
+
+Facilities: IRAM PdBI, CARMA, VLA, Herschel (SPIRE), WISE, IRAS, 2MASS, Spitzer(IRAC, MIPS), HST(ACS, NICMOS)
 

### 2016-06-19 WRITEUP/ms.tex
update code and paper after fixing the typo in z in model script

@@
 Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
-$R_{t}$\,=\,10.6\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
+$R_{t}$\,=\,10.7\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
 However, since emission is not resolved along the flat regime
@@
 We here adopt the maximum {\em observed} velocity
-$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
+$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
 dynamical center as a proxy to the rotation velocity.

### 2016-06-19 PdBI/src/modelVelo/modelGradient.py

@@ -4,10 +4,13 @@
 plot source locations from lens model of various channel as markers on observed 1st moment map.
 Kinematics.
 
-Last Modified: 29 May 16
+Last Modified: 19 June 16
 
 History:
-29 May 2016
+19 June 2016:
+  - change z of source from 0.6357 to 0.6537
+  - fix latex rendering ylabel
+29 May 2016:
   - increase font size for first plot
   - scale bar padding
 28 May 2016
@@ -94,7 +97,7 @@ interval = 50.        # km/s between velocity contour
 DecCentroid = -12.5328629
 RACentroid = 172.96434563
 CellSize = 0.5        # arcsec per pixel in 1D
-redshift = 0.6357
+redshift = 0.6537
 b_arcsec = 1.8       # from C06
 a_arcsec = 3.25
 i_rad = np.arccos(b_arcsec/a_arcsec)
@@ -111,10 +114,9 @@ z = [344.46, 344.46, 236.82, 129.16, 21.54, -86.08, -193.76, -301.38]
 
 plotMajorFit = False
 plotMajor_FirstMom = False
-plotPV = False
-plotRot = False
+plotPV = True
+plotRot = True
 plotODR_arctan = False
-plotMdyn = False
 # -----------------------------------------------
 #  Read fits file and Set up WCS
 # -----------------------------------------------
@@ -523,7 +525,7 @@ z_err = 21.5*5/2.     # range of channels combined to make models/2. --> error b
 if plotPV:
     f, ax = plt.subplots()
     ax.errorbar(off, z, yerr=z_err, fmt='ko', xerr=offset_err)
-    plt.ylabel('v_r = v sin i')
+    plt.ylabel(r'$v_{r}$ = $v$ $\sin$ $i$')
     plt.xlabel(' offset from line center position ["] ')
     plt.title('PV along major axis at PA {:.2f} deg'.format(PA_deg))
     plt.tight_layout()
@@ -546,7 +548,7 @@ if plotRot:
     ax.errorbar(off[3], z[3], xerr=offset_err[3], yerr=z_err, fmt='go', label='line center')
     ax.errorbar(off[:3], z[:3], yerr=z_err, fmt='ro', label='red', xerr=offset_err[:3])
 
-    plt.ylabel('|v_r = v sin i|')
+    plt.ylabel(r'abs($v_r$ = $v \sin i$)')
[…]

### 2016-06-20 WRITEUP/ms.tex
update table w/ notes and formatting
decomposed Mgas for RXJ and companion, updated formatting and rewording based on DR's comments

@@
 
-\subsection{\cco Emission} % DONE
-We detect resolved \cco line emission toward RXJ1131. The spectrum is shown in
-\Fig{co32spec}, which seems to have a double-peak profile.
+\subsection{\cco Emission}
+We detect \cco line emission toward RXJ1131 at {\bf BLAH}$\sigma$ significance.
+The spectrum is shown in \Fig{co32spec}, which seems to have a double-peak profile.
 This is expected if RXJ1131 is truly a disk galaxy (see previous
@@
 Assuming the spatial extents between \bco and \cco are similar and therefore
-a negligible differential lensing effect, the line intensities
+magnified by similar amounts, the line intensities
 correspond to a brightness temperature ratio of
@@
 We note that the IRAC photometry includes
-emission from old stellar population and is prone to
+emission from old stellar populations and is prone to
 dust extinction. Hence, the decomposed fluxes are only
@@
 by fitting a 2D elliptical Gaussian to the Level 1 data at the
-source position given by the output of \ncode{sussextractor}.
+source position given by the output of \ncode{sussextractor}. The fluxes
+obtained from both methods are consistent within the uncertainties.
 
@@
 \section{Analysis} \label{sec:anal}
-\subsection{Lens modeling} \label{sec:lensmodel} %DONE
-At the angular resolution of the \bco data, the images are resolved
-but not within the multiply lensed emission (i.e., sub-optimal for
+\subsection{Lens modeling} \label{sec:lensmodel}
+At the angular resolution of the \bco data, the images are resolved over
+$\sim$2 resolution elements. Given the extent of the lensed emission,
+this implies that our \bco observations do not resolve
+structures (e.g. knots and arcs) of the lensed emission
+(i.e., sub-optimal for
 performing lens modeling). Nevertheless, the high spectral
@@
 \uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
-the code). Model of each slice in \Fig{model} thus provides
-properties on the intrinsic kinematics. The slices
-are obtained by binning the data over the full linewidth
-$\sim$700\,\kms by five channels,
-that is, into seven slices, to increase the SNR.
+the code). Models of each slice thus provide the
+properties on the intrinsic kinematics. To increase the SNR for modeling, the
+slices are obtained by binning five native channels
+($\Delta v$\,$\sim$\,21.5\kms) over the full
+linewidth of $\sim$750\,\kms in the original data, resulting in seven
+independent channels.
 
@@
 by repeating the modeling over each slice but fixing their lens parameters
-according to the overall median in the preliminary models,
+to the overall median in the preliminary models,
 as listed in \Tab{lens}.
@@
 
-\subsubsection{Interpretation and Caveats} \label{sec:caveat} %DONE
+\subsubsection{Interpretation of the source-plane morphology} \label{sec:caveat}
 The reconstructed source locations in \Fig{model} demonstrate
@@
 indicative of a disk-like galaxy.
-Additional support to the disk conjecture %conjecture of a disk morphology
+Additional support to the disk conjecture
 can be found in the double-horned line profile (\Fig{CO21spec})
@@
 is best-reproduced using a $n$\,=\,1 Sersic profile.
-Our interpretation therefore tends in favor of a disk morphology for RXJ1131.
+We thus interpret RXJ1131 to be a disk galaxy.
 
@@
 and C06, who find evidence for an interacting galaxy near RXJ1131.
-Spatially, the red velocity component of the CO also coincides with this
-component F. While we cannot quantify the type of
-merger (major v.s. minor) with a mass ratio given the
-spatial resolution, the symmetric velocity gradient retained under
-such close separation between the two lean support
-to the idea of a minor merger.
-% For major mergers, two galaxy mass centers separated on the same scale as the
-% gas disk (4 kpc or more), the gas dynamics would be strongly perturbed and
-% would deviate substantially from that of a simple disk.
-% In a minor merger (a mass ratio of more than 3:1) the more massive galaxy, including its gas distribution, can retain a significant angular momentum and resemble a rotating disk.
+Spatially, the red velocity component of the CO emission
+also coincides with this component F. It is therefore evident that we
+detect \bco emission in the companion galaxy.
+To quantify the type of merger (major v.s. minor) conventionally with a mass
+ratio, we decompose the total line flux into two components:
+one from RXJ1131 and the other from its companion.
+Since the companion is only detected in the red-most channel, we
+use the best-fit flux densities and magnification factors obtained
+from the model of this channel to derive the gas mass in the companion.
+Without direct \rot{1}{0} measurements, we derive \rot{1}{0} intensity
+assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1, which was chosen
+solely to facilitate a comparison with other U/LIRGs. % also ULIRGs are found to be thermalized up to Jup = 3 or 4
+For the same reason, we adopt a luminosity-to-mass conversion factor of
+\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields a gas mass
+$M_{\rm gas}$ of (1.68\pmm0.68)\,\E{10} \Msun. 
+%statistical unc. only (i.e. draw from from distributions of on mag. factor & intrinsic flux)
+For the molecular gas mass in RXJ1131, we derive
+its intrinsic line flux over the FWZI linewidth
+using the respective magnification
+factors listed in \Tab{model}, which to
+first order takes into account effect of differential lensing.
+This yields $I_{\small \bco}$\,=\,5.41$\pm$2.71 Jy\,\kms,
+where the uncertainty includes those on
+the magnification factors.
+Adopting the same brightness temperature ratio and \alphaco\ as
+used for the companion, this corresponds to a gas mass of
+$M_{\rm gas}$\,=\,(3.17\pmm1.59)\,\E{10} \Msun.
+The implies a gas mass ratio of $\sim$2:1.
+Therefore, the system is a gas-rich major merger according to
+the classification scheme commonly used in literature.
 
@@
 intrinsic sizes of the lensed galaxies, and thus the magnification
-factors may be under-predicted.
-% magnification factor is underpredicted, see Bussmann15
+factors may be under-predicted. % see Bussmann15
 
@@
 morphologies (half-light radii) of the reconstructed sources are
-represented by magenta ellipses (see text in \Sec{caveat} for caveats).
+represented by magenta ellipses.
 The caustic curves are represented as cyan lines. The beam of the
@@
 \input{table_magFactor}
-Previous lens models of RXJ1131 find evidence for
+Similar to previous studies of RXJ1131, where
 differential lensing across {\it HST}
-$H$-, $V$-, and $I$-band (C06), where the
-magnification factor ranges from 10.9 to 7.8. C06 attribute
-the decrease toward the IR regime is caused by the more extended
-IR emission. The highly asymmetric \bco line profile suggests that
-differential lensing is also non-negligible for CO, where the redshifted
-emission is apparently much brighter than that in the
-blueshifted part, consistent
-with the source positions relative to the caustics in \Fig{model}.
-The red wing emission mainly originates near the cusp
+$H$-, $V$-, and $I$-band has been detected with a
+magnification factor decreasing from 10.9 to 7.8 (C06),
+the highly asymmetric \bco line profile suggests that
+differential lensing is also non-negligible for the CO emission, whereby
+causing the redshifted emission to be apparently much brighter than the
+blueshifted component.
+Such an effect is consistent with the source plane
+positions relative to the caustics in \Fig{model}; the red wing emission mainly originates near the cusp
 in the caustic, whereas the blue wing emission is located beyond the caustics.
-The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).
+From our best-fit lens models, the magnification factor varies from 8.7 to 3.1 across the \bco line (\Tab{model}).
+
+%If we estimate the intrinsic I:
+%red I =
+%blue wing I =
 
@@
 the magnification factors.
-We note that this includes emission from the companion
-as the spatial resolution of our data do not allow us decompose its
-contribution from the total line flux.
 
@@
 CO luminosity \Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\LpU and a gas mass
-$M_{\rm gas}$ of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
-an overestimation for RXJ1131 due to a contribution from the companion.
+$M_{\rm gas}$ of (xx\pmm xx)\,\E{10} \Msun. 
+BLAH
 The inferred gas mass is comparable to

### 2016-06-20 WRITEUP/table_medianLens.tex
decomposed Mgas for RXJ and companion, updated formatting and rewording based on DR's comments

@@
 \tablecolumns{3}
-\tablecaption{Lens parameters from preliminary models}
+\tablecaption{Lens parameters constrained by models of seven velocity channels}
 \tablehead{
@@
 \tablecomments{Parameters describing the foreground lens are
-obtained based on the preliminary models (see text for details).
+obtained based on the median in the preliminary models (see text for details).
 All angular offsets are with respect to
 $\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
-$\delta$\,=\,-12\degr31\arcmin58\farcs3 (J2000).}
+$\delta$\,=\,$-$12\degr31\arcmin58\farcs3 (J2000).}
 \end{deluxetable}

### 2016-06-21 PdBI/data/22May16/Mgas126_130_err.py
decompose line flux and Mgas for chan 126-130

@@ -1,0 +1,74 @@
+
+'''
+get unc. for decomposed Mgas for RXJ1131 and companion based on flux in Chan 126-130
+
+Note:
+    i.e. Mgas here is not the final total Mgas for RXJ1131
+
+'''
+import numpy as np
+
+# In chan 126-130, lensed
+Mtot = 3.034e10      # Msun
+
+# RXJ
+mu1 = 7.2
+mu1_e = 5.6
+S1 = 4.818        # mJy
+S1_e = 3.456
+
+# Companion
+mu2 = 6.7
+mu2_e = 2.5
+S2 = 5.955
+S2_e = 3.565
+
+def M_gas(mu1, mu2, s1, s2, Mtot):
+    '''
+    separate Mgas for companion and RXJ1131
+
+    Parameters
+    ----------
+    mu1, mu2:
+        mag. factor for RXJ1131 or companion
+    s1, s2:
+        intrisnic flux for RXJ1131 or companion from model
+
+    Returns
+    -------
+    Mgas in unit of Msun for RXJ1131 or companion, dep. on order when input parameters
+
+    '''
+    totalFlux = mu1 * s1 + mu1 * s2        # order does not matter
+    s1Flux = mu1 * s1                      # order matters
+    return Mtot * s1Flux / totalFlux
+
+
+# get distribution on Mgas based on unc. in mu and intrinsic flux
+niters = 1e3
+mu1_iters = abs(np.random.normal(loc=mu1, scale=mu1_e, size=niters))
+mu2_iters = abs(np.random.normal(loc=mu2, scale=mu2_e, size=niters))
+S1_iters = abs(np.random.normal(loc=S1, scale=S1_e, size=niters))
+S2_iters = abs(np.random.normal(loc=S2, scale=S2_e, size=niters))
+
+# M_1
+mass_gas_iters = M_gas(mu1_iters, mu2_iters, S1_iters, S2_iters, Mtot)
+M_gas_mean = np.mean(mass_gas_iters)
+M_gas_median = np.median(mass_gas_iters)
+
+CI = 1.        # 1 <=> 68.3 %
+Nsigma = CI
+e_M_gas = Nsigma * np.std(mass_gas_iters)
+print " RXJ"
+print "corrected for lensing"
+print M_gas_mean/mu1/1e10, M_gas_median/mu1/1e10, e_M_gas/mu1/1e10
+
+# M_2
[…]

### 2016-06-21 WRITEUP/ms.tex
shuffled down kinamtics discusion from obs. section, updated Mgas decomposition (didn't correct for lensing in some channels previously)

@@
 \begin{figure}[!htbp]
-\includegraphics[trim=3 5 0 15, clip, width=0.242\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
-\includegraphics[trim=3 5 0 0, clip, width=0.23\textwidth]{../Figures/F555W_REDBLUE.eps}
+\includegraphics[trim=0 10 15 0, clip, width=0.222\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
+\includegraphics[trim=5 -10 0 0, clip, width=0.232\textwidth]{../Figures/F555W_REDBLUE.eps}
 \caption{Left: an overlay of the velocity-integrated \bco emission on the {\it HST} $V$--band (F555W)
@@
 
-The emission of the red component coincides with the Einstein Ring seen in the
-optical image, with most of its apparent flux originating from the lensed arc
-in the southeast, whereas the blue component is predominately coming from
-solely the lensed arc shown in \Fig{CO21mom}. To illustrate this, we show the
-channel maps of 21.5\,\kms width and spatial spectra of 1\farcs5 resolution in
-\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
-show that emission
-is present to the west, peaking toward the lensing arc (black crosses in
-\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
-(blue wing).
-This indicates extended emission in the source plane, where
-emission from different kinematic components is separated by different amounts
-relative to the caustics, leading to the observed asymmetric
-line profile. A detailed analysis on differential lensing of \bco is presented
-in \Sec{differential}, where we present our lens model.
-
-\begin{figure*}[!htbp]
-\centering
-\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
-\caption{
-Channel maps of PdBI \bco toward RXJ1131 in 21.5\,\kms resolution.
-Black crosses indicate the position of the lensed knots (AGN emission,
-which correspond to components ABCD in C06). The central white-filled
-star indicates the position of the foreground lensing galaxy (component G
-in C06). Contours start and increment at steps of
-$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
-\end{figure*}
-
-\begin{figure*}[!htbp]
-\centering
-\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
-\caption{
-\bco spectrum as a function of position, binned by 3 pixels in each
-direction (1\farcs5).
-The spectra map covers an extent of $\sim$10"$\times$10"
-centering on the pixel that corresponds to the lensing galaxy.
-Spatial offset in arcsec is denoted in top left corner of each panel.
-The velocity and flux density scales are denoted in the top right panel.
-\label{fig:spatialSpec}}
-\end{figure*}
-
 We also place an upper limit on \rot[HNC]{2}{1} line emission
@@
 limit of 0.35\,mJy\,\kms\,beam\pmOne.
-
-\subsection{Origin of the \bco Emission} \label{sec:origin} %DONE
-Evidently, the CO emission is co-spatial with the lensed optical emission in
-the background AGN host galaxy.
-The question is then whether the optically
-faint companion also contributes to the CO flux and thus contains a
-non-negligible amount of molecular gas.
-Indeed, based on our lens model presented in \Sec{lensmodel}, we find it
-highly likely that part of the CO emission originates from
-the companion. We thus classify RXJ1131 as a ``wet-wet'' merger.
-However, we cannot quantify this with a mass ratio given the
-spatial resolution, nor can we rule out the possibility that
-the ``companion'' is instead a gas component/tidal feature ripped out
-from previous interaction.
-In the subsequent sections, we will interpret
-the this additional source component as gas emission
-in a nearby galaxy (i.e. a ``wet-wet'' merger), as suggested by previous studies of RXJ1131 (C06, B08).
-
-\subsection{\bco Kinematics} % DONE
-A clear velocity gradient and a high
-velocity dispersion ($\gtrsim$400\,\kms) near the central region
-is seen in \Fig{CO21highO}. While beam smearing is inevitably the
-dominant factor in the observed velocity dispersion
-at the spatial resolution of this data, the exceedingly
-high velocity dispersion may hint
-at potential perturbations from the AGN, or internal turbulence due to
-interactions with the companion, and/or instability due to the large gas
-content. A velocity gradient across the source plane in \Fig{model} is also
-found in our lens model. This further supports the idea of a
-kinematically-ordered galaxy, but its emission has been lensed differentially.
-In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
-bright quasar and is in the process of merging.
-We will defer the discussion of its implications to \Sec{dynamics},
-where we analyze the dynamics of the system in the source plane.
-
-\begin{figure}[!htbp]
-\centering
-\includegraphics[width=0.45\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
-\caption{
-Contours for the first (left) and second (right) moment maps are shown in steps of
-50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
-\label{fig:CO21highO}}
-\end{figure}
 
@@
 Assuming the spatial extents between \bco and \cco are similar and therefore
-magnified by similar amounts, the line intensities
+magnified by the same amount, the line intensities
 correspond to a brightness temperature ratio of
@@
 
-\subsubsection{Interpretation of the source-plane morphology} \label{sec:caveat}
+\subsubsection{Interpretation of the source plane morphology} \label{sec:caveat}
 The reconstructed source locations in \Fig{model} demonstrate
@@
 use the best-fit flux densities and magnification factors obtained
-from the model of this channel to derive the gas mass in the companion.
+from the model of this channel to derive the intrinsic gas mass in the companion.
 Without direct \rot{1}{0} measurements, we derive \rot{1}{0} intensity
 assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1, which was chosen
-solely to facilitate a comparison with other U/LIRGs. % also ULIRGs are found to be thermalized up to Jup = 3 or 4
+solely to facilitate a comparison with other U/LIRGs. 
+% also ULIRGs are found to be thermalized up to Jup = 3 or 4, but not needed to say here
 For the same reason, we adopt a luminosity-to-mass conversion factor of
 \alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields a gas mass
-$M_{\rm gas}$ of (1.68\pmm0.68)\,\E{10} \Msun. 
-%statistical unc. only (i.e. draw from from distributions of on mag. factor & intrinsic flux)
+$M_{\rm gas}$ of (1.92\pmm0.09)\,\E{9} \Msun. 
+%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
 For the molecular gas mass in RXJ1131, we derive
@@
 first order takes into account effect of differential lensing.
-This yields $I_{\small \bco}$\,=\,5.41$\pm$2.71 Jy\,\kms,
+This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
 where the uncertainty includes those on
@@
 used for the companion, this corresponds to a gas mass of
-$M_{\rm gas}$\,=\,(3.17\pmm1.59)\,\E{10} \Msun.
-The implies a gas mass ratio of $\sim$2:1.
-Therefore, the system is a gas-rich major merger according to
-the classification scheme commonly used in literature.
+$M_{\rm gas}$\,=\,(1.38\pmm0.33)\,\E{10} \Msun,
+implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
+We thus classify the system to be a ``wet-wet'' minor merger according to
+the classification scheme/convention commonly used in literature.
 
@@
 
-\subsubsection{Differential Lensing} \label{sec:differential} %DONE
+\subsubsection{Spatial extent and differential lensing} \label{sec:differential}
+In the image plane shown in  \Fig{CO21mom}, the redshifted component is 
+cospatial with the Einstein Ring seen in the
+optical image, with most of its apparent flux originating from the lensed arc
+in the southeast, whereas the blue component is predominately coming from
+solely the lensed arc. To further illustrate this, we show the
+channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
+\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
+show that emission
+is present to the west, peaking toward the lensing arc (black crosses in
+\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
+(blue wing).
+This is consistent with the source plane positions in our models and 
+suggests that the 
+overall CO emitting region is extended.
+
+\begin{figure*}[!htbp]
+\centering
+\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
+\caption{
+Channel maps of PdBI \bco toward RXJ1131 in 21.5\,\kms resolution.
+Black crosses indicate the position of the lensed knots (AGN emission,
+which correspond to components ABCD in C06). The central white-filled
+star indicates the position of the foreground lensing galaxy (component G
+in C06). Contours start and increment at steps of
+$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
+\end{figure*}
+
+\begin{figure*}[!htbp]
+\centering
+\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
+\caption{
+\bco spectrum as a function of position, binned by 3 pixels in each
+direction (1\farcs5).
+The spectra map covers an extent of $\sim$10"$\times$10"
+centering on the pixel that corresponds to the lensing galaxy.
+Spatial offset in arcsec is denoted in top left corner of each panel.
+The velocity and flux density scales are denoted in the top right panel.
+\label{fig:spatialSpec}}
+\end{figure*}
+
 \input{table_magFactor}
@@
 the highly asymmetric \bco line profile suggests that
-differential lensing is also non-negligible for the CO emission, whereby
+differential lensing is also non-negligible for CO,
 causing the redshifted emission to be apparently much brighter than the
-blueshifted component.
-Such an effect is consistent with the source plane
-positions relative to the caustics in \Fig{model}; the red wing emission mainly originates near the cusp
-in the caustic, whereas the blue wing emission is located beyond the caustics.
-From our best-fit lens models, the magnification factor varies from 8.7 to 3.1 across the \bco line (\Tab{model}).
-
-%If we estimate the intrinsic I:
-%red I =
-%blue wing I =
+blueshifted component and the asymmetric line profile.   
+To first order, this can be explained by the difference in magnification factor which
+varies from 8.7 to 3.1 across the \bco line (\Tab{model}).  % also because of a contribution from the companion in the observed, lensed spectrum
+Such an effect (difference in $\mu_{\rm L}$ across channels) is consistent with the source plane
+positions relative to the caustics in \Fig{model}, where the red wing 
+emission mainly originates near the cusp 
+of the caustic and the blue wing emission is located beyond the caustics.
+In fact, the intrinsic line flux of the redshifted and 
+blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
+is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively, 
+implying an intrinsically symmetric line profile.
+
+\subsection{\bco Kinematics} % DONE
+A clear velocity gradient and a high
+velocity dispersion ($\gtrsim$400\,\kms) near the central region
+is seen in \Fig{CO21highO}. While beam smearing is inevitably the
+dominant factor in the observed velocity dispersion
+at the spatial resolution of this data, the exceedingly
+high velocity dispersion may hint
+at potential perturbations from the AGN, or internal turbulence due to
+interactions with the companion, and/or instability due to the large gas
+content. A velocity gradient across the source plane in \Fig{model} is also
+found in our lens model. This further supports the idea of a
+kinematically-ordered galaxy, but its emission has been lensed differentially.
+In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
+bright quasar and is in the process of merging.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=0.45\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
+\caption{
+Contours for the first (left) and second (right) moment maps are shown in steps of
+50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
+\label{fig:CO21highO}}
+\end{figure}
 

### 2016-06-21 WRITEUP/ms.tex
update LIR, explains HVI bands extents

@@
 
-\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654}
+\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654}
 \author{T. K. Daisy Leung and Dominik A. Riechers}
@@
 
-\subsubsection{Interpretation of the source plane morphology} \label{sec:caveat}
+\subsubsection{Interpretation of the source-plane morphology} \label{sec:caveat}
 The reconstructed source locations in \Fig{model} demonstrate
 an intrinsic velocity gradient across the source plane, which is
-indicative of a disk-like galaxy.
+indicative of a kinematically-ordered disk-like galaxy. 
 Additional support to the disk conjecture
@@
 We thus classify the system to be a ``wet-wet'' minor merger according to
-the classification scheme/convention commonly used in literature.
+the classification scheme commonly used in literature.
 
@@
 This is consistent with the source plane positions in our models and 
-suggests that the 
-overall CO emitting region is extended.
+is suggestive of an extended CO emitting region.
 
@@
 differential lensing across {\it HST}
-$H$-, $V$-, and $I$-band has been detected with a
+$V$-, $I$-, and $H$-band has been detected with a
 magnification factor decreasing from 10.9 to 7.8 (C06),
@@
 is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively, 
-implying an intrinsically symmetric line profile.
-
-\subsection{\bco Kinematics} % DONE
+implying an intrinsically symmetric line profile. This is consistent with the source-plane
+velocity gradient in our lens model (see \Sec{caveat}). 
+% The difference in magnification factors between CO and optical-to-NIR emission
+% may further indicate that the CO emitting region is more extended than .
+
+\subsection{\bco Kinematics}
 A clear velocity gradient and a high
@@
 interactions with the companion, and/or instability due to the large gas
-content. A velocity gradient across the source plane in \Fig{model} is also
-found in our lens model. This further supports the idea of a
-kinematically-ordered galaxy, but its emission has been lensed differentially.
-In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
+content. 
+Therefore, in this scenario, RXJ1131 is 
+likely a disrupted disk galaxy hosting an optically
 bright quasar and is in the process of merging.
@@
 terminology) since this corresponds to the radius at which the velocity
-of a pure exponential disc peaks.
+of a pure exponential disk peaks \citep{Courteau97b}.
 We here adopt the maximum {\em observed} velocity
@@
 wavelength. In particular, the half-light radius is found to be
-$\sim$\,4kpc and $\sim$7\,kpc in $V$-band
+$\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
 \citep{Brewer08a} and $H$-band (C06), respectively.
-This discrepancy arises owing to the exclusion of the more
-diffused emission in $V$-band (rest-frame UV),
-which traces young massive stars.
-The $V$-band compactness may be explained in part
+The CO gas is thus of similar spatial
+extent as $H$ and $I$-bands.
+
+In the rest-frame, 
+emission in the observed $H$-band corresponds to NIR emission, 
+tracing radiation from the accretion disk surrounding
+the central AGN and also from old and evolved stellar populations; 
+$I$-band corresponds to roughly the optical $V$-band, tracing stellar radiation from
+existing, less massive (\ie longer-lasting) stars;
+$V$-band corresponds to roughly $U$-band,  tracing radiation from massive young stars 
+in the host galaxy. Hence,
+the $V$-band compactness may be explained in part
 due to the fact that its emission is
-more susceptible to dust extinction than other bands.
-On the other hand, the molecular gas (fuel for \SF) is more compact
-than the more evolved stellar population, as traced by $I$ and $H$-bands.
-This is consistent with the picture that stars diffuse outward
-after their formation \citep{Calzetti01a}.
-
-Using our estimate of $V_{\rm rot}$, we find a dynamical mass of
-$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$\,=\,17\E{10}\,\Msun enclosed
+more susceptible to dust extinction than in other bands and/or 
+a central starburst caused by higher 
+concentrations of star-forming gas towards the central regions -- owing to
+gravitational perturbations induced
+from interactions with the companion
+\citep[\eg][]{DiMatteo05a}.
+The rest-frame NIR emission is likely to be
+dominated by evolved stars since 
+the AGN is located at $\sim$0\farcs016 inside the central region % and R_H is 7 kpc
+of the host galaxy \citep{Sluse06a}, implying a compact accretion disk. 
+This is consistent with the picture that old stars form first and constitute the bulge component  
+of a spiral galaxy and that nuclear starbursts are triggered in mergers.
+
+% assuming virialized gas
+Using $V_{\rm rot}$ estimate from the modeling, we find a dynamical mass of
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
 within the CO-emitting region. If we instead consider the
-line peak separation from the
-\bco line profile $\Delta v_{\rm sep}/2 \sim$200\,\kms, we find
-$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$\,=\,5.8\E{10}\,\Msun.
+\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
 We correct for the inclination effect using the
-morphological axial ratio from the reconstructed image (Figure 3 in C06), where
-the minor axis is 1\farcs8 and the major axis is 3\farcs25.
-We thus find an inclination angle of 56.4\degr, which is consistent with the
+morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
+from the reconstructed image (Figure 3 in C06), yielding
+an inclination angle of 56.4\degr, which is consistent with the
 observed unobscured AGN and an observable double peak line profile.
@@
 presence of a close companion, our estimate is
-at most a lower limit.
+at most an upper limit.
+
+%% using disk model
 
@@
 becomes optically thick ($\lambda_{0}$). We impose
-an upper limit of 100\,K on $T_d$, a Gaussian prior centered around
+an upper limit of 100\,K on $T_d$ (commonly BLAH in ULIRGs; CITE), 
+a Gaussian prior centered around
 $\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
@@
 Thus, the \fir luminosity in
-this model should, in principle, corresponds to a
+this model should, in principle, correspond to a
 lower limit on the cold dust emission.
@@
 for this model, we find a total IR luminosity
-\LIR (rest-frame 8\,$-$\,1000\,\micron) of 8.14\petm{2.64}{2.80}\E{12}\,\Lsun,
+\LIR (rest-frame 8\,$-$\,1000\,\micron) of 9.71\petm{6.14}{-6.05}\E{12}\,\Lsun,
 a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
-dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
-Taken at face value, this implies a \LFIR-to-\LIR ratio
-of $\sim$58\pmm BLAH\%.
-Again, the inferred quantities are uncorrected for lensing.
+dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun, uncorrected for lensing.
+Taken at face value, this implies a FIR-to-IR luminosity ratio
+of $\sim$58\pmm35\%.
 %The best-fit SEDs are shown in \Fig{SED} and the
@@
 We note the \fir luminosity is comparable in both models, which is
-not surprising given the lack of constraints in the MIR. In fact, the
-\fir luminosity from the second model is slightly higher than the former, but
-consistent within the uncertainties.
+not surprising given the lack of constraints in the MIR. 
 For the subsequent analysis, we adopt the physical quantities
-from the former (\ie with constraints at 24\,\micron).
+from the first model (\ie with constraints at 24\,\micron).
 The choice of SED model does not affect
 the derived star formation rate (SFR) given the similar \fir luminosity.
-Yet, the dust mass is higher in the former (but consistent within the
-uncertainties), and thus the gas-to-dust ratio in \Sec{properties}
-should be considered as an estimate.
+Yet, the dust mass is higher in the former but consistent within the
+uncertainties.
 We correct for lensing using the median magnification
 factor $(\mu_{\rm L}\eq5.5)$
-from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
+from the CO lens models. This yields a
+ \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun
+ and 
+ a total IR luminosity of $\sim$1.5\E{12}\,\Lsun,  implying RXJ1131 is a ULIRG.
 Assuming a Salpeter initial
 mass function \citep{Salpeter55a}, we find a
-SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
+SFR$_{\rm FIR}$ of (120\pmm63)\,\Msun\,yr\pmOne using the
 standard conversion \citep{Kennicutt98a}.
@@
 
-To place RXJ1131 in context of existing studies,
-we compare its properties
-with those reported by C13, which is the largest sample of
+\subsection{Gas properties} \label{sec:properties}
+In this section, we derive the gas properties of the merger  
+based on \bco and compare with those reported by
+C13, which is the largest sample of
 IR-luminous galaxy at similar redshift
-(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
-Since C13 adopt a different definition of
-\LFIR (40\,$-$\,500\,\micron)\footnote{We also note that the
-\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
-we derive the \fir luminosity following this convention.
-This yields $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
-a SFR of $($150\pmm 70$)$\,\sfrU.
-This implies that RXJ1131 is considered a LIRG in regard to their
-sample, and consequently, the SFR of RXJ1131 is lower
-(cf. SFR\,$>$\,200, with an average of 1200 in C13).
-If we instead adopt the
-more generally used definition for the total IR luminosity,
-calculated using 8\,$-$\,1000\,\micron, RXJ1131 would be
-considered a ULIRG given its lensing-corrected
-total IR luminosity of $\sim$2\E{12}\,\Lsun.
-
-\subsection{Gas properties} \label{sec:properties}
-In this section, we derive the gas properties of RXJ1131 based on \bco,
-and compare the derived quantities against those reported by
-C13, where their results are based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.
+(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
+\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
+and using a different definition of
+\LFIR: rest-frame 40\,$-$\,500\,\micron. Following this convention, 
+we find a \fir luminosity of 
+\LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
+a SFR of $($150\pmm 70$)$\,\sfrU.}.
+% the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
+We note their results are based on \bco and \rot{4}{3} line observations on the single-dish
+IRAM 30-m.
 

### 2016-06-21 PdBI/src/modelVelo/calcmass.py
add disk model calc

@@ -3,9 +3,11 @@
 calculate dynamical mass
 
 
-Last modified: 17 May 16
+Last modified: 21 June 16
 
 History:
+21 June 2016
+    - add func. to calc dyn mass using disk model (Neri+03)
 17 May 2016
     - get mass using quanties reported in paper
 13 May 2016
@@ -19,13 +21,26 @@ b_arcsec = 1.8       # from C06
 a_arcsec = 3.25
 i_rad = np.arccos(b_arcsec/a_arcsec)
 i_deg = i_rad * 180./np.pi
+Msun = 1.989e30      # kg
+
 
 def M_encl(R_kpc, v):
-    """ calc mass enclosed """     # v in km/s
+    """ calc mass enclose in spherical model, as in Solomon+97
+
+    Parameters
+    ----------
+    v: float
+        in km/s
+
+    Returns
+    -------
+    M10: float
+        same as M = 2.32e5 * V_km/s^2 * R_kpc
+        in unit of 1e10 Msun
+        """
     from astropy.constants import G
 
     R = kpc_to_m * R_kpc
-    Msun = 1.989e30      # kg
     v2 = (v * 1e3)**2
     v2oG = v2 / G.value
     v2oGoMsun = v2oG / Msun
@@ -50,4 +65,43 @@ print("Mass enclosed within {:.2f} kpc: {:.2f} x 1e+10 Msun".format(R_in_kpc, M_
 
 # with incl. correction
 print M_encl(R_in_kpc, V_rot)/(np.sin(i_rad)**2)
+
+
+
+def Mdyn_virial(R_kpc, v_kms):
+    """
+        assuming virialized "isotropic virial estimator" (Spitzer 1987),
+            M = 5 * sigma^2 * R/G,
+            --> the difference in prefactor as in spherical
+
+        the scaling factor appropriate for a rotating disk at an average inclination is a factor of ∼1.5 smaller (Bothwell et al. 2010), i.e. if the above formula were applied to a disk galaxy, it would somewhat overestimate the dynamical mass.
+
+        v_kms: FWHM in km/s
+
+    Returns
+    -------
+    M10: float
+        in unit of 1e10 Msun
+    """
+    M = 2.8e5 * (v_kms)**2 * R
+    M10 = M / 1e10
+    return M10
+
+
+def Mdyn_disk(R_kpc, FWHM_kms):
+    """ Calc. dyn. mass assuming dsk model: M sin^2 = 4e4 * FWHM^2 * R
[…]

### 2016-06-21 WRITEUP/ms.tex
replace dyn mass calc with disk model instead of from virialized

@@
 \section{Analysis} \label{sec:anal}
-\subsection{Lens modeling} \label{sec:lensmodel}
+\subsection{Lens Modeling} \label{sec:lensmodel}
 At the angular resolution of the \bco data, the images are resolved over
@@
 
-\subsubsection{Interpretation of the source-plane morphology} \label{sec:caveat}
+\subsubsection{Interpretation of the Source-plane Morphology} \label{sec:caveat}
 The reconstructed source locations in \Fig{model} demonstrate
@@
 from the model of this channel to derive the intrinsic gas mass in the companion.
-Without direct \rot{1}{0} measurements, we derive \rot{1}{0} intensity
-assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1, which was chosen
-solely to facilitate a comparison with other U/LIRGs. 
-% also ULIRGs are found to be thermalized up to Jup = 3 or 4, but not needed to say here
-For the same reason, we adopt a luminosity-to-mass conversion factor of
-\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields a gas mass
-$M_{\rm gas}$ of (1.92\pmm0.09)\,\E{9} \Msun. 
+Assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1 and
+a CO luminosity-to-H2 mass conversion factor of
+\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne, we find 
+a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun. 
 %statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
@@
 used for the companion, this corresponds to a gas mass of
-$M_{\rm gas}$\,=\,(1.38\pmm0.33)\,\E{10} \Msun,
+$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun,
 implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
@@
 
-\subsubsection{Spatial extent and differential lensing} \label{sec:differential}
+\subsubsection{Spatial Extent and Differential Lensing} \label{sec:differential}
 In the image plane shown in  \Fig{CO21mom}, the redshifted component is 
@@
 
-\subsection{\bco Dynamical modeling} \label{sec:dynamics} %DONE
+\subsection{\bco Dynamical Modeling} \label{sec:dynamics} %DONE
 Assuming the velocities of the respective channels used in the
@@
 This is consistent with the picture that old stars form first and constitute the bulge component  
-of a spiral galaxy and that nuclear starbursts are triggered in mergers.
+of a spiral galaxy and that nuclear starbursts (in the inner few kpc) are triggered in mergers.
 
 % assuming virialized gas
-Using $V_{\rm rot}$ estimate from the modeling, we find a dynamical mass of
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
-within the CO-emitting region. If we instead consider the
+%Using $V_{\rm rot}$ estimate from the modeling, we find a dynamical mass of
+%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
+%within the CO-emitting region. If we instead consider the
+%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
+%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
+%We correct for the inclination effect using the
+%morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
+%from the reconstructed image (Figure 3 in C06), yielding
+%an inclination angle of 56.4\degr, which is consistent with the
+%observed unobscured AGN and an observable double peak line profile.
+%The dynamical mass is then
+%8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
+%Since this quantity is derived under the assumption that the gas is
+%virialized, which is highly unlikely given the velocity dispersion and the
+%presence of a close companion, our estimate is
+%at most an upper limit.
+
+%% using disk model
+Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
+ \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as 
+$v_{\rm FWHM}$, we find a dynamical mass of
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
+within the CO-emitting region. 
+If we instead consider the
 \bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
-We correct for the inclination effect using the
-morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
-from the reconstructed image (Figure 3 in C06), yielding
-an inclination angle of 56.4\degr, which is consistent with the
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
+To correct for the inclination effect, we
+infer an inclination angle of 56.4$\degr$ using
+the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
+from the reconstructed image (Figure~3 in C06). This inclination angle 
+is consistent with the
 observed unobscured AGN and an observable double peak line profile.
 The dynamical mass is then
-8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
-Since this quantity is derived under the assumption that the gas is
-virialized, which is highly unlikely given the velocity dispersion and the
-presence of a close companion, our estimate is
-at most an upper limit.
-
-%% using disk model
-
-\subsection{SED modeling} \label{sec:SED}  % DONE
+1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
+% the systematic uncertainty on the inclination angle may cause this estimate to differ by 
+% a factor of $\sim$2.
+Our estimate is likely a lower limit given the presence of a companion. In a merger model, 
+the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
+
+\subsection{SED Modeling} \label{sec:SED}  % DONE
 We fit dust SED models to the
@@
 becomes optically thick ($\lambda_{0}$). We impose
-an upper limit of 100\,K on $T_d$ (commonly BLAH in ULIRGs; CITE), 
+an upper limit of 100\,K on $T_d$ \citep[see \eg][]{Sajina12a}, 
 a Gaussian prior centered around
@@
 taken for the burn-in phase (which are then discarded).
-Here we report the means % modes in log file
+Here we report the statistical means % modes in log file
 % summary statistics (global mode (where min. chi),
@@
 
-\subsection{Gas properties} \label{sec:properties}
-In this section, we derive the gas properties of the merger  
+\subsection{Gas Properties} \label{sec:properties}
+In this section, we derive the gas properties of the merger system
 based on \bco and compare with those reported by
@@
 % the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
-We note their results are based on \bco and \rot{4}{3} line observations on the single-dish
-IRAM 30-m.
-
-\subsubsection{Linewidth \& Sizes} %DONE
+We note that their results are based on \bco and \rot{4}{3} line observations with the 
+IRAM 30-m single-dish telescope.
+
+\subsubsection{Linewidth and Sizes} 
+FWHM from single gauss fit?
 We find that the linewidths for both components (redshifted and blueshifted)
@@
 (300\pmm85\,\kms; \citealt[][]{Solomon97a}).
-Since C13 do not have resolved observations, we compare the
-gas distribution with local U/LIRGs. The CO gas in RXJ1131 is
-distributed $\sim$6\,kpc in radius across (in
+The CO gas in RXJ1131 is
+distributed $\sim$6\pmm3\,kpc in radius across (in
 the source plane), which is more extended than the
@@
 % with the data represented in this paper.
-
-\subsubsection{Gas Mass}
-To derive the molecular gas mass, we first correct for lensing magnification
-using the respective magnification factors listed in \Tab{model}, which to
-first order takes into account effect of differential lensing. This yields
-$I_{\small \bco}$\,=\,5.9$\pm$2.7 Jy\,\kms,
-where the uncertainty includes those on
-the magnification factors.
-
-Without direct \rot{1}{0} measurements,
-we derive \rot{1}{0} intensity
-using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
-solely to facilitate a comparison with other U/LIRGs.
-For the same reason, we
-adopt a luminosity-to-mass conversion factor of
-\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne, this yields a
-CO luminosity \Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\LpU and a gas mass
-$M_{\rm gas}$ of (xx\pmm xx)\,\E{10} \Msun. 
-BLAH
-The inferred gas mass is comparable to
+COMPARE WITH DOWNES SOLOMON98
+
+\subsubsection{Gas Mass and Gas Ratios}
+Using the lensing-corrected molecular gas mass of  
+$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\E{10}\,\Msun in RXJ1131 and
+$($1.92\pmm0.09$)$\E{9}\,\Msun in its companion derived in \Sec{caveat}, 
+a total molecular gas mass of $M_{\rm gas}^{\rm total}$\,=\,$($1.57\pmm0.38$)$\E{10}\,\Msun is 
+residing within the merger system. 
+This is comparable to the
 C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) as well as
 local U/LIRGs \citep{Solomon97a, Sanders96a} but higher than
-local LIRGs (U14).
+in local LIRGs (U14).
 
 % gas-to-dyn ratio
-We place a lower limit on the dynamical mass (see \Sec{dynamics}) using
-the inferred gas mass. This BLAH.
- {\bf will need edit depending on the dyn. modeling section}
-a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
+Using a dynamical mass of BLAH and the total gas mass ($M_{\rm gas}^{\rm total}$),
+we find a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
 % gas to dust ratio:
 Using the dust mass derived from SED fitting,
-we find a gas-to-dust ratio of 184\pmm124, which is consistent with
+we find a gas-to-dust ratio of BLAH\pmm
+BLAH, which is consistent with
 the C13 sample ($f_{\rm gas-dust}$\,=\,206) and local U/LIRGs

### 2016-06-22 WRITEUP/ms.tex
add de-lensed FWHM

@@
 flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
-179$\pm$9 \kms and 255\pmm28 \kms, respectively. The peaks are separated by
+179\pmm9 \kms and 255\pmm28 \kms, respectively. The peaks are separated by
 $\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/
@@
 \section{Analysis} \label{sec:anal}
+%\subsection{Stellar Mass and BH-Bulge Mass Correlation}
+%Rest-frame $K$-band (NIR) photometry has been proposed as a reliable proxy to
+%the underlying total stellar mass. Using the decomposed IRAC photometry at 3.6$\micron$ (rest-frame $K$-band), 
+%we find a stellar mass of BLAH, using the BLAH.
+%This implies a $M_{\rm BH}$$/$$M^*$ = BLAH (cf. $\sim$0.1\% found in local galaxies).
+%
+%The AGN-starburst connection has become a central issue with the discovery of the relation
+%between stellar velocity dispersion and mass of the central black hole in spheroidal stellar
+%systems (Magorrian et al. 1998, Ferrarese & Merritt 2000, Gebhardt et al. 2000). Given that
+%elliptical galaxies are mainly old, this relation has to be put in place at their formation history.
+%
+%This implies that RXJ1131 is in the BLAH stage of the evolution, in which the BH ?.
+
 \subsection{Lens Modeling} \label{sec:lensmodel}
@@
 reported by \citet{Brewer08a}, who find an optically faint companion
-(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
+(component F in their paper) $\sim$2.4\,kpc in projection from the AGN host galaxy,
 and C06, who find evidence for an interacting galaxy near RXJ1131.
@@
 detect \bco emission in the companion galaxy.
+
 To quantify the type of merger (major v.s. minor) conventionally with a mass
@@
 Assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1 and
-a CO luminosity-to-H2 mass conversion factor of
-\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne, we find 
+a CO luminosity-to-$H_2$ mass conversion factor of
+\alphaco\,=\,0.8 $($K \kms pc$^2$$)$\pmOne, we find 
 a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun. 
@@
 implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
-We thus classify the system to be a ``wet-wet'' minor merger according to
+We thus classify the system to be a {\em ``wet-wet'' minor merger} according to
 the classification scheme commonly used in literature.
@@
 blueshifted component and the asymmetric line profile.   
-To first order, this can be explained by the difference in magnification factor which
-varies from 8.7 to 3.1 across the \bco line (\Tab{model}).  % also because of a contribution from the companion in the observed, lensed spectrum
-Such an effect (difference in $\mu_{\rm L}$ across channels) is consistent with the source plane
+This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
+varies from 8.7 to 3.1 across the \bco line (\Tab{model}) and also partly due to a contribution from the companion in the redshifted velocity channels.
+The variation in $\mu_{\rm L}$ across channels is consistent with the source plane
 positions relative to the caustics in \Fig{model}, where the red wing 
@@
 implying an intrinsically symmetric line profile. This is consistent with the source-plane
-velocity gradient in our lens model (see \Sec{caveat}). 
-% The difference in magnification factors between CO and optical-to-NIR emission
-% may further indicate that the CO emitting region is more extended than .
+velocity gradient in our lens model (\Fig{model} and \Fig{PV}). 
+% The difference in magnification factors between CO and optical-to-NIR 
+% may further indicate that the CO emitting region is more extended and/or 
+% has a spatial offset from the optical-to-NIR emission 
+% (\ie different positions and alignment relative to the caustics) given 
+% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5) 
+% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and 
+% the degeneracy between the intrinsic source size and the magnification factor.
 
 \subsection{\bco Kinematics} 
+Fitting a four-parameter double-Gaussian that describes two velocity peaks by a single FWHM
+to the ``intrinsic" \bco line profile of RXJ1131 (after correcting for lensing using 
+the magnification factors for various channels and separating the emission from RXJ1131 and its companion),
+we find a roughly symmetric double-horned profile with a flux ratio of 1.2\pmm0.4 between the peaks, which 
+are separated by
+$\Delta v_{\rm sep}$ = 387\pmm45\,\kms, and a 
+FWHM of 220\pmm72\,\kms. 
+If we instead fit with a single-Gaussian, we find a FWHM of 600\pmm160\,\kms for RXJ1131
+and 73\pmm43\,\kms for the companion galaxy.
+
 A clear velocity gradient and a high
@@
 of a spiral galaxy and that nuclear starbursts (in the inner few kpc) are triggered in mergers.
-
-% assuming virialized gas
-%Using $V_{\rm rot}$ estimate from the modeling, we find a dynamical mass of
-%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
-%within the CO-emitting region. If we instead consider the
-%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
-%We correct for the inclination effect using the
-%morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
-%from the reconstructed image (Figure 3 in C06), yielding
-%an inclination angle of 56.4\degr, which is consistent with the
-%observed unobscured AGN and an observable double peak line profile.
-%The dynamical mass is then
-%8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
-%Since this quantity is derived under the assumption that the gas is
-%virialized, which is highly unlikely given the velocity dispersion and the
-%presence of a close companion, our estimate is
-%at most an upper limit.
-
-%% using disk model
-Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
- \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as 
-$v_{\rm FWHM}$, we find a dynamical mass of
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
-within the CO-emitting region. 
-If we instead consider the
-\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
-To correct for the inclination effect, we
-infer an inclination angle of 56.4$\degr$ using
-the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
-from the reconstructed image (Figure~3 in C06). This inclination angle 
-is consistent with the
-observed unobscured AGN and an observable double peak line profile.
-The dynamical mass is then
-1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
-% the systematic uncertainty on the inclination angle may cause this estimate to differ by 
-% a factor of $\sim$2.
-Our estimate is likely a lower limit given the presence of a companion. In a merger model, 
-the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
 
@@
 
-\subsection{Gas Properties} \label{sec:properties}
+\subsection{ISM Properties} \label{sec:properties}
 In this section, we derive the gas properties of the merger system
@@
 IRAM 30-m single-dish telescope.
+
+ \subsubsection{Dynamical Mass}
+ Assuming the \bco gas dynamically BLAH. 
+%% assuming virialized gas
+Using our $V_{\rm rot}$ estimated from dynamical modeling in \Sec{dynamics}, 
+we find a dynamical mass of
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
+within the CO-emitting region in RXJ1131. If we instead consider the
+\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
+We correct for the inclination effect using the
+morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
+from the reconstructed image (Figure 3 in C06), yielding
+an inclination angle of 56.4\degr, which is consistent with the
+observed unobscured AGN and an observable double peak line profile.
+The dynamical mass is then
+8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
+Since this quantity is derived under the assumption that the gas is virialized in a  % rotatioally supported
+spherical distribution, \ie using 
+\begin{equation}
+M_{\rm dyn} \sin^2 i = \frac{\Delta v^2 R}{G},
+\end{equation}
+our estimate is at most an upper limit given the observed velocity dispersion and the
+presence of a close companion.
+COMPARE with Stellar MASS.
+
+Similarly, we estimate the dynamical mass in the companion under the same assumptions. 
+For $\Delta v$, we use the FWHM linewidth obtained by fitting a single Gaussian to the pseudo 
+\bco line profile obtained by decomposing its contribution to the total line flux using the magnification factor
+found for the model of corresponding velocity channel.
+Assuming a source size of $\sim$700 pc inferred from the lens model of {\it HST} $V$-band (B08).
+This yields $M_{\rm dyn}$\,$\sin^2 i$ = BLAH \Msun.
+If we assume an average inclination angle of $<\sin i>^2$ = BLAH, we find $M_{\rm dyn}$ = BLAH \Msun.
+
+%% using disk model
+Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
+ \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as 
+$v_{\rm FWHM}$, we find a dynamical mass of
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
+within the CO-emitting region. 
+If we instead consider the
+\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
+To correct for the inclination effect, we
+infer an inclination angle of 56.4$\degr$ using
+the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
+from the reconstructed image (Figure~3 in C06). This inclination angle 
+is consistent with the
+observed unobscured AGN and an observable double peak line profile.
+The dynamical mass is then
+1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
+% the systematic uncertainty on the inclination angle may cause this estimate to differ by 
+% a factor of $\sim$2.
+Our estimate is likely a lower limit given the presence of a companion. In a merger model, 
+the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
 
@@
 
-\subsubsection{SFE and Depletion Time}
+\subsubsection{Conversion Factor $\alpha_{\rm CO}$}
+Instead of adopting the conversion factor $\alpha_{\rm CO}$ as 0.8 (K \kms pc$^2$)\pmOne,
+a crude estimate can be obtained using the dust mass and CO luminosity, assuming a 
+gas-to-dust ratio.
+Here we assume a gas-to-dust ratio of 72 (Sandstrom+13), based on a sample of local star-forming
+galaxies of solar metallicities. 
+We find $\alpha_{\rm CO}$ = BLAH\pmm$(f_{\rm gas-dust}/72)$ (K \kms pc$^2$)\pmOne, where the uncertainty does not include 
+systematic uncertainties 
+in the dust absorption coefficient $(\kappa)$ and the gas-to-dust ratio.
+% which Kapa? Kappa 870 or Kappa we used in our dust mass esimate?
+This ?
+
+\subsubsection{SFE and Depletion Timescales}
 We derive the SFE using the far-IR luminosity definition used by
@@
 
+At high redshifts, SMGs the irregular, turbulent starbursting galaxies (SFR $\sim$ BLAH \Msun yr\pmOne)
+and BzK are the ``normal" star-forming disk galaxies with low SFE, relatively high SFR (BLAH) and 
+longer depletion time (BLAH Myr).
+
 %--------------------------------------------------------------------------
@@
 \subsection{Merger stage of RXJ1131-1231}
+Using the redshift inferred from the line center of the CO gas disk $(z_{\rm CO} = 0.6537)$ 
+as the systemic redshift. The velocity offset from the optical lines $(z_{\rm AGN} = 0.658)$ 
+is $\sim$780\,\kms. This may ? interaction
+
 In this section, we put our results in context with other ULIRGs/mergers at
@@
 
+\subsection{Morphological Transformation}
+While the space density of ULIRGs are only BLAH Mpc$^{-3}$ (CITE), 
+the blah and the evolution in structure of high- and low-z galaxies
+implying ULIRGs and mergers play an important role in giving rise to the BLAH.
+
 \subsection{ULIRG Evolution and Cosmic SFH}
@@
 % consistent with current speculation of how the SFRD decreases over cosmic time.
+
+which seem probable given the relation in AGN growth and gas accumulation.
+the simultaneous observation of the AGN phenomenon, of stellar formation and of galaxy interaction illustrates the current AGN ?
+black hole paradigm, according to which the growth of a black hole through the AGN phase occurs when galaxy interactions provide gas inflow towards the center (e.g.
+Hernquist 1989; Di Matteo et al.
+2005).
+Since the interactions induce gravitational perturbations, simultaneous starbursts are also expected.
 
@@
 % data are needed to confirm this.
+
+The compactness of the emission in $V$-band (rest-frame UV) 
+suggests that the \SF in RXJ1131 is proceeding in a 
+compact region embedded w/in a large reservoir of molecular gas, which may be explained 
+by gas inflow toward nuclear regions due to interaction with the companion. 
+Such a scenario may support the results in recent models: mergers/ULIRGs evolve into bulge dominated massive disks (Geach+09 sect 3.4).
 
@@
 
-Facilities: IRAM PdBI, CARMA, VLA, Herschel (SPIRE), WISE, IRAS, 2MASS, Spitzer(IRAC, MIPS), HST(ACS, NICMOS)
+Facilities: IRAM PdBI, CARMA, VLA, Herschel(SPIRE), WISE, IRAS, 2MASS, Spitzer(IRAC, MIPS), HST(ACS, NICMOS)
 

### 2016-06-22 src/SED/SEDplot.py
cosmestics

@@ -1,11 +1,14 @@
 '''
 
-Plot SED
+Plot SED with MIPS extrapolation to 24 um and MBB_EMCEE fit
 
-Last Modified: May 24 2016
+Last Modified: June 22 2016
 
 History
 -------
+June 22 2016:
+    - change SED plot figsize, xylim
+    - remove IRAC MIR fit in final full SED plot
 May 24 2016:
     - add using MC to get uncertainties on 24 um
     - use MC best-fit for quote spectral index
@@ -254,32 +257,32 @@ xspan = wave_fg[3:7].max() - wave_fg[3:7].min()
 xspace = space * xspan
 xarray = np.linspace(wave_fg[3:7].min()-space, 24+xspace, 500)
 
-plt.figure()
-plt.errorbar(wave_fg[3:7], flux_fg[3:7], fluxErr_fg[3:7], fmt='.g', ms=8, ecolor='gray', capsize=8, elinewidth=4, capthick=1.5)
-plt.errorbar(wave_host[3:7], flux_host[3:7], fluxErr_host[3:7], fmt='.b', ms=8,
-             ecolor='gray',
-             capsize=8,
-             elinewidth=4, capthick=1.5)
+# plt.figure()
+# plt.errorbar(wave_fg[3:7], flux_fg[3:7], fluxErr_fg[3:7], fmt='.g', ms=8, ecolor='gray', capsize=8, elinewidth=4, capthick=1.5)
+# plt.errorbar(wave_host[3:7], flux_host[3:7], fluxErr_host[3:7], fmt='.b', ms=8,
+#              ecolor='gray',
+#              capsize=8,
+#              elinewidth=4, capthick=1.5)
 
-# plot the fits in MC simulations for fg
-for f, h in zip(fg_MC, host_MC):
-    plt.plot(xarray, powerf(xarray, *f), color="#b44682", alpha=0.2)
-    plt.plot(xarray, powerf(xarray, *h), color="#67A9CF", alpha=0.2)
+# # plot the fits in MC simulations for fg
+# for f, h in zip(fg_MC, host_MC):
+#     plt.plot(xarray, powerf(xarray, *f), color="#b44682", alpha=0.2)
+#     plt.plot(xarray, powerf(xarray, *h), color="#67A9CF", alpha=0.2)
 
-# plot extrapolation
-plt.plot(xarray, powerf(xarray, *fg_MC_fit), 'r--', label='fit slope to FG IRAC')
[…]

### 2016-06-22 src/SED/SEDplot.py
change zorder and save file format

@@ -7,6 +7,8 @@ Last Modified: June 22 2016
 History
 -------
 June 22 2016:
+    - change zorder on mbb fits
+    - change savefig() save as .pdf instead of .eps to conserve alpha setting in saved figure
     - change SED plot figsize, xylim
     - remove IRAC MIR fit in final full SED plot
 May 24 2016:
@@ -306,7 +308,7 @@ def savefigure(figure, f, verbose=True, dirStr='../../Figures/'):
             os.mkdir(dirStr)
         else:
             print "... Directory {:s} exists...".format(dirStr)
-    figure.savefig(dirStr + f + '.eps', dvi=600, bbox_inches='tight')
+    figure.savefig(dirStr + f + '.pdf', dvi=600, bbox_inches='tight')
     print('... Saved Figure: {:s}').format(dirStr + f + '.eps')
 
 
@@ -352,9 +354,9 @@ wave_SED, flux_SED, flux_unc_SED = res.data
 p_wave = np.linspace(wave_SED.min() * 0.5, wave_SED.max() * 1.5, 200)
 
 ax.plot(p_wave, res.best_fit_sed(p_wave), 'b--', lw=2.5,
-        label='MBB fit with 24 um', alpha=0.45)
+        label='MBB fit with 24 um', alpha=0.45, zorder=0.5)
 ax.plot(p_wave, res_noMIPS.best_fit_sed(p_wave), '-',
-        color='c', lw=2.5, label='MBB fit without 24 um', alpha=0.45)
+        color='c', lw=2.5, label='MBB fit without 24 um', alpha=0.45, zorder=0.5)
 
 
 # ------- pretty plot configuration below -------

### 2016-06-27 WRITEUP/ms.tex
updated linewidth & size section, need to continue from SFE section, GDR section almost done

@@
 the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
+% Our results support the hypothesis.
 \end{abstract}
@@
 in our mm observations. The details of the observations can be found
-in C06. We adopt the VLA 5\,GHz map of
+in \citet[hereafter C06]{Claeskens06a}.
+We adopt the VLA 5\,GHz map of
 $\sim$0\farcs5 resolution as the
@@
 errors, and beam size.
+\defcitealias{Claeskens06a}{C06}
 
@@
 %   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
-We construct the zeroth moment map (\Fig{CO21mom}) and
-the higher-order first and second moment maps (\Fig{CO21highO})
+We construct the zeroth moment map and the renzogram in \Fig{CO21mom}, and
+the higher-order first and second moment maps in \Fig{CO21highO}
 using the $uv$-continuum subtracted data cube over a velocity range of
-$\Delta v$ $\sim$ 750\,\kms. The higher-order moment maps are created using
+$\Delta v$ $\sim$ 750\,\kms.
+The renzogram is created using different velocity channels for the blue- and
+redshifted velocity components and
+the higher-order moment maps are created using
 channel maps with 3$\sigma$ clipping.
 The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
-in the intensity-integrated map. The deconvolved source size FWHM
+in the intensity-integrated map.
+
+The deconvolved source size FWHM
 is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
@@
 
+\begin{figure}[!htbp]
+%\centering
+\includegraphics[width=0.45\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
+\caption{
+Contours for the first (left) and second (right) moment maps are shown in steps of
+50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
+\label{fig:CO21highO}}
+\end{figure}
+
 We also place an upper limit on \rot[HNC]{2}{1} line emission
@@
 detection. We thus estimate the line intensity to be
-35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
+35.7\,$\pm$\,21.9{\bf BLAH} Jy\,\kms by summing up fluxes over the FWZI
 linewidth used to infer \bco line intensity ($\sim$700 \kms).
@@
 \begin{figure}[!Htbp]
-\centering
+%\centering
 \includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
@@
 when warranted. These data were obtained from
-the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
-the Wide-field Infrared Survey Explorer ({\it WISE}; \citealt{Wright10a}),
+the Two Micron All Sky Survey \citep[2MASS;][]{Skrutskie06a},
+the Wide-field Infrared Survey Explorer \citep[{\it WISE};][]{Wright10a},
 the {\it Infrared Astronomical Satellite}
-({\it IRAS};\citealt{Neugebauer84a}), and
-the Multiband Imaging Photometer (MIPS; \citealt{Rieke04a}) and
-Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
+\citep[{\it IRAS};][]{Neugebauer84a}, and
+the Multiband Imaging Photometer \citep[MIPS;][]{Rieke04a} and
+Mid-infrared Infrared Array Camera \citep[IRAC;][]{Fazio04a} on
 the \spitzer.
@@
 carried out using \ncode{sussextractor} within the Herschel Interactive
-Processing Environment (HIPE; \citealt{Ott10a})
+Processing Environment \citep[HIPE;][]{Ott10a}
 on Level 2 maps obtained from the Herschel Science Archive.
@@
 channel slices of the interferometric data using our lensing code
-\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
-the code). Models of each slice thus provide the
+\uvmcmcfit
+(\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
+Models of each slice thus provide the
 properties on the intrinsic kinematics. To increase the SNR for modeling, the
@@
 motivated by the astrometry uncertainties in the VLA image as well as
-the uncertainties provided by previous SIE lens model (C06).
-We initialize the Einstein Radius based on the model parameters reported by C06
+the uncertainties provided by previous SIE lens model \citepalias{Claeskens06a}.
+We initialize the Einstein Radius based on the model parameters reported by \citetalias{Claeskens06a}
 and impose a uniform prior using $\pm$3$\sigma$ of their uncertainties.
@@
 the mass distribution of the lensing galaxy, are consistent (within the uncertainties)
-with that of the SIE model presented by C06. We find a mass of
+with that of the SIE model presented by \citetalias{Claeskens06a}. We find a mass of
 $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun
@@
 and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
-C06 also find that the reconstructed source plane emission in optical-NIR
+\citetalias{Claeskens06a} also find that the reconstructed source plane emission in optical-NIR
 is best-reproduced using a $n$\,=\,1 Sersic profile.
@@
 top left panel in \Fig{model}). This is consistent with previous results
-reported by \citet{Brewer08a}, who find an optically faint companion
-(component F in their paper) $\sim$2.4\,kpc in projection from the AGN host galaxy,
-and C06, who find evidence for an interacting galaxy near RXJ1131.
+reported by \citet[hereafter B08]{Brewer08a}, who find an optically faint companion
+(component F in their paper) $\sim$2.4\,kpc in projection from the AGN host galaxy in $V$-band,
+and \citetalias{Claeskens06a}, who find evidence for an interacting galaxy near RXJ1131.
 Spatially, the red velocity component of the CO emission
@@
 detect \bco emission in the companion galaxy.
+\defcitealias{Brewer08a}{B08}
 
@@
 a CO luminosity-to-$H_2$ mass conversion factor of
-\alphaco\,=\,0.8 $($K \kms pc$^2$$)$\pmOne, we find 
+\alphaco\,=\,0.8\,\alphaU, we find
 a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun.
@@
 \caption{
-Channel maps of PdBI \bco toward RXJ1131 in 21.5\,\kms resolution.
+Channel maps of the PdBI \bco data cube toward RXJ1131 in 21.5\,\kms resolution.
 Black crosses indicate the position of the lensed knots (AGN emission,
-which correspond to components ABCD in C06). The central white-filled
+which correspond to components ABCD in \citetalias{Claeskens06a}). The central white-filled
 star indicates the position of the foreground lensing galaxy (component G
-in C06). Contours start and increment at steps of
+in \citetalias{Claeskens06a}).
+Central velocities are shown at the top of each map.
+Contours start and increment at steps of
 $\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
@@
 $V$-, $I$-, and $H$-band has been detected with a
-magnification factor decreasing from 10.9 to 7.8 (C06),
+magnification factor decreasing from 10.9 to 7.8 \citepalias{Claeskens06a},
 the highly asymmetric \bco line profile suggests that
@@
 bright quasar and is in the process of merging.
-
-\begin{figure}[!htbp]
-\centering
-\includegraphics[width=0.45\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
-\caption{
-Contours for the first (left) and second (right) moment maps are shown in steps of
-50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
-\label{fig:CO21highO}}
-\end{figure}
 
@@
 radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
-lens model (C06; converted to
+lens model (\citetalias{Claeskens06a}; converted to
 our cosmology).
@@
 $\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
-\citep{Brewer08a} and $H$-band (C06), respectively.
+\citepalias{Brewer08a} and $H$-band \citepalias{Claeskens06a}, respectively.
 The CO gas is thus of similar spatial
@@
 \citep[\eg][]{DiMatteo05a}.
-The rest-frame NIR emission is likely to be
-dominated by evolved stars since 
-the AGN is located at $\sim$0\farcs016 inside the central region % and R_H is 7 kpc
-of the host galaxy \citep{Sluse06a}, implying a compact accretion disk. 
 This is consistent with the picture that old stars form first and constitute the bulge component
@@
 of $\sim$58\pmm35\%.
-%The best-fit SEDs are shown in \Fig{SED} and the
-% resulting parameters are listed in \Tab{SED}.
 
 The dust temperature from both models is similar to that of
-ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K; \citealt[hereafter C13]{Combes13a}).
+ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K;
+\citealt[hereafter C13]{Combes13a}).
 We note the \fir luminosity is comparable in both models, which is
@@
 standard conversion \citep{Kennicutt98a}.
-
+\defcitealias{Combes13a}{C13}
 \begin{figure}[!htbp]
 \centering
-\includegraphics[trim=65 15 15 95, clip, width=0.45\textwidth]{../Figures/FullSED.eps}
-\caption{SED models of the IR dust emission toward RXJ1131.
-{\bf This figure needs an update}
-WISE flux is slightly higher than the IRAC point, probably due to a smaller
-aperture used in IRAC extraction,
-both of which were taken from the archive.
-IRAC: Aperture flux in 5\farcs diameter.
-MIPS: use PSF fit flux from archive as source size $<$ PSF FWHM of 6$^{\prime\prime}$.
-Might want to add NVSS constraints.
+\includegraphics[trim=5 5 5 5, clip, width=0.45\textwidth]{../Figures/FullSED}
+% WISE flux is slightly higher than the IRAC point, probably due to a smaller
+% aperture used in IRAC extraction (both from archive).
+% It is also not straight-forward to fit an SED model covering a wider wavelengths because of
+% differential lensing.
+\caption{SEDs of RXJ1131 and its lensing galaxy. The photometry is listed in \Tab{photometry}.
+Best-fit SED models of the thermal dust emission towards RXJ1131
+with(out) MIR constraint at 24\,$\micron$ are plotted as dashed (solid) lines.
 \label{fig:SED}}
@@
 \LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
-a SFR of $($150\pmm 70$)$\,\sfrU.}.
+a SFR of $($150\pmm70$)$\,\sfrU.}.
 % the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
@@
 
+\subsubsection{Linewidth and Sizes} \label{sec:sizes}
+A linewidth of $\Delta v_{\rm FWHM}$$\sim$600\pmm160\,\kms found from
+fitting a single Gaussian
+is considerably larger that those in the \citepalias{Combes13a} sample
+(370\,\kms) as well as local ULIRGs
+\citep[300\pmm85\,\kms, with the largest being 480\,\kms;][hereafter S97]{Solomon97a}.
+%ULIRGs (z < 0.3) studied in CO(1-0) by Solomon97a: ≥ 1/3 of them have double-peaked or flat-topped spectrum. But their linewidths are based on single Gauss fit.
+Yet, given the dynamic nature of these galaxies,
+a CO linewidth of $\sim$600 may not be surprising.
+Indeed, a linewidth of $\Delta v$ = 750\,\kms has been observed
+in a local LIRG (Arp 118) \citep{SV05a}.
+Such FWHM is also commonly observed in high-z starburst galaxies
+\citep[780\pmm320\,\kms; \eg][]{Greve05a}.
+\defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}
+
+The CO gas in RXJ1131 is $\sim$6\pmm3\,kpc in radius (in the source plane),
+which is more
+extended than the sample of disk-like U/LIRGs studied by
+\citet[hereafter U14]{Ueda14a}, who find an average radius of 3.5\pmm2.3\,kpc but with a range of 1.1\,$-$\,9.3\,kpc.
+Such a range is consistent with the results reported by \citet{Gao99a}, where
+they also find CO disks extending out to $R\sim$10\,kpc.
+In contrast to the results
+reported in the classical study by
+\citet[hereafter DS98]{Downes98a}, who find molecular gas sizes of $R<$1\,kpc in their sample of local ULIRGs
+(see also \citealt{Bryant99a} and \citealt{Iono09a}), it appears that the molecular gas in ULIRGs
+can be distributed over large regions comparable to
+those reported in high-z ($z$$>$\,1) galaxies \citep[$R\sim$7\,kpc;
+\citetalias{Greve05a};][]{Daddi10a, Riechers11a, Ivison11a}.
+While we cannot draw conclusions any evolution in the
+molecular gas size
+as we are only studying one
+ULIRG at intermediate redshift, it appears that local ULIRGs are composed of
+mergers at various stages of merging, and are therefore not
+necessarily more compact than
+high-z SMGs \citep[cf. \eg][]{Iono09a}.
+\defcitealias{Ueda14a}{U14}
+\defcitealias{Downes98a}{DS98}
+\defcitealias{Ivison11a}{I11}
+\defcitealias{Riechers11a}{R11}
+
+% SFRSD:
+We do not attempt to derive a SFR surface density and gas surface density
+since we do not have any constraints on the dust continuum size
+and the fact that
+the gas surface density is unlikely to be constant across the CO region
+given the centrally concentrated $V$-band emission, which we interpret as
+merger-induced starburst (see \Sec{caveat}).
+Should we decide to do this, it would imply
+a series of assumptions to be made, leading to surface densities that are not
+meaningful in any case.
+
 \subsubsection{Dynamical Mass}
- Assuming the \bco gas dynamically BLAH. 
-%% assuming virialized gas
-Using our $V_{\rm rot}$ estimated from dynamical modeling in \Sec{dynamics}, 
+Assuming the gas is virialized,
+the dynamical mass can be approximate as
+$M_{\rm dyn} = \sigma^2 R / G$,
+where $\sigma$ is the velocity dispersion, or the rotational velocity in the case of a rotating disk model
+$($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
+Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
 we find a dynamical mass of
 $M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
-within the CO-emitting region in RXJ1131. If we instead consider the
+within the CO-emitting region in RXJ1131.
+If we instead consider the
 \bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
@@
 morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25)
-from the reconstructed image (Figure 3 in C06), yielding
+from the reconstructed image (Figure 3 in \citetalias{Claeskens06a}), yielding
 an inclination angle of 56.4\degr, which is consistent with the
@@
 The dynamical mass is then
-8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
-Since this quantity is derived under the assumption that the gas is virialized in a  % rotatioally supported
-spherical distribution, \ie using 
-\begin{equation}
-M_{\rm dyn} \sin^2 i = \frac{\Delta v^2 R}{G},
-\end{equation}
-our estimate is at most an upper limit given the observed velocity dispersion and the
-presence of a close companion.
-COMPARE with Stellar MASS.
-
-Similarly, we estimate the dynamical mass in the companion under the same assumptions. 
-For $\Delta v$, we use the FWHM linewidth obtained by fitting a single Gaussian to the pseudo 
-\bco line profile obtained by decomposing its contribution to the total line flux using the magnification factor
-found for the model of corresponding velocity channel.
-Assuming a source size of $\sim$700 pc inferred from the lens model of {\it HST} $V$-band (B08).
-This yields $M_{\rm dyn}$\,$\sin^2 i$ = BLAH \Msun.
-If we assume an average inclination angle of $<\sin i>^2$ = BLAH, we find $M_{\rm dyn}$ = BLAH \Msun.
-
-%% using disk model
-Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
- \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as 
-$v_{\rm FWHM}$, we find a dynamical mass of
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
-within the CO-emitting region. 
-If we instead consider the
-\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
-To correct for the inclination effect, we
-infer an inclination angle of 56.4$\degr$ using
-the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
-from the reconstructed image (Figure~3 in C06). This inclination angle 
-is consistent with the
-observed unobscured AGN and an observable double peak line profile.
-The dynamical mass is then
-1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
-% the systematic uncertainty on the inclination angle may cause this estimate to differ by 
-% a factor of $\sim$2.
-Our estimate is likely a lower limit given the presence of a companion. In a merger model, 
-the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
-
-\subsubsection{Linewidth and Sizes} 
-FWHM from single gauss fit?
-We find that the linewidths for both components (redshifted and blueshifted)
-inferred from a double Gaussian fit to the line profile are
-comparable to the C13 ULIRG sample
-($\Delta v_{\rm FWHM}$ of 370\,\kms) and local ULIRGs
-(300\pmm85\,\kms; \citealt[][]{Solomon97a}).
-The CO gas in RXJ1131 is
-distributed $\sim$6\pmm3\,kpc in radius across (in
-the source plane), which is more extended than the
-sample of disk-like U/LIRGs studied by
-\citet[hereafter U14]{Ueda14a}, % also classified U/LIRG using FIR from 60, 100 micron measurements
-who find an average radius of 3.5\,$\pm$\,2.3\,kpc
-with a range spanning 1.1\,$-$\,9.3\,kpc.
-% This is expected if the positive correlation in the linewidth-size relation
-% holds at intermediate redshifts. Yet we cannot quantify this further
-% with the data represented in this paper.
-COMPARE WITH DOWNES SOLOMON98
+8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$\,$<$\,25\E{10}\Msun.
+Our estimate should be considered at best an upper limit since
+the gas is unlikely to be virialized in RXJ1131.
+% based on the observed velocity dispersion and the presence of a closeby companion.
+For the following sections, we use the
+lower limit (8.3\pmm1.9)\E{10}\,\Msun as the dynamical mass as it is
+derived in a manner similar to commonly used in literature (\eg \citetalias{Solomon97a,Downes98a,Greve05a}).
+
+Using the velocity dispersion obtained with a single Gaussian fit to the
+line profile of the companion ($\sigma$ = 30\,\kms)
+and its intrinsic source size of $\sim$700\,pc obtained from the {\em HST} $V$-band lens model \citepalias{Brewer08a},
+we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 5\E{6}\,\Msun.
+This corresponds to $M_{\rm dyn}$\,=\,2\E{7}\,\Msun if we assume an inclination angle of 30$\degr$.
+We note that this is substantially lower than its gas mass, which is a more reliable estimate based on
+the data in hand.
+We adopt the $V$-band size as the radius $R$ owing to the fact that
+it is the only size estimate available for the companion.
+We do not use this dynamical mass for deriving any additional physical parameters, and thus it
+does not alter our interpretations of the system throughout this paper.
+
+%%% using disk model, should use FWHM of single Gauss fit then (Fu+13)
+%Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
+% \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as
+%$v_{\rm FWHM}$, we find a dynamical mass of
+%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
+%within the CO-emitting region.
+%If we instead consider the
+%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
+%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
+%To correct for the inclination effect, we
+%infer an inclination angle of 56.4$\degr$ using
+%the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25)
+%from the reconstructed image (Figure~3 in \citetalias{Claeskens06a}). This inclination angle
+%is consistent with the
+%observed unobscured AGN and an observable double peak line profile.
+%The dynamical mass is then
+%1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
+%% the systematic uncertainty on the inclination angle may cause this estimate to differ by
+%% a factor of $\sim$2.
+%Our estimate is likely a lower limit given the presence of a companion. In a merger model,
+%the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
+
+% The dynamical mass in RXJ1131 is thus higher than local ULIRGs
+% ($M_{\rm dyn}(R\leq)0.6\,kpc)$\,$\sim$\,6\E{9}\,\Msun; \citepalias{Downes98a}).
 
 \subsubsection{Gas Mass and Gas Ratios}
-Using the lensing-corrected molecular gas mass of  
-$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\E{10}\,\Msun in RXJ1131 and
-$($1.92\pmm0.09$)$\E{9}\,\Msun in its companion derived in \Sec{caveat}, 
-a total molecular gas mass of $M_{\rm gas}^{\rm total}$\,=\,$($1.57\pmm0.38$)$\E{10}\,\Msun is 
-residing within the merger system. 
-This is comparable to the
-C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) as well as
-local U/LIRGs \citep{Solomon97a, Sanders96a} but higher than
-in local LIRGs (U14).
-
+% Solomon97 (ULIRGs z < 0.3): 0.4-1.5 e10 Msun
+% SV05: Solomon+97: average Mgas ~7e9 Msun
+% SV05: high-z: (2.5-10)e10 Msun
+A total molecular gas mass of
+$M_{\rm gas}^{\rm total}$ = $($1.57\pmm0.38$)$\E{10}\,\Msun is
+residing within the merger system (see \Sec{caveat}).
+This is comparable to those found in the
+\citetalias{Combes13a} sample %(1.5\E{10}\Msun)
+as well as local U/LIRGs
+\citep[][\citetalias{Solomon97a}]{Sanders96a} but higher than
+in local LIRGs \citepalias{Ueda14a}, as expected.
+Our finding is thus consistent with previous results, where
+high-z galaxies tend to have higher molecular gas mass %\footnote{Assuming the same conversion factor}
+and is
+distributed over larger spatial extents
+\citep[\eg][\citetalias{Riechers11a,Ivison11a}]{SV05a}.
 % gas-to-dyn ratio
-Using a dynamical mass of BLAH and the total gas mass ($M_{\rm gas}^{\rm total}$),
-we find a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
+% DS98: f ~ 0.16 (but w/in disc or ring of R ~ 0.5 kpc)
+% Bothwell+13: f ~ 0.3? (but over larger R)
+% --> ULIRGs gas fraction is even lower if average over same scale as SMGs
+% Daddi10a; Tacconi10a: f_gas ? 40% in z ? 1 discs, significantly higher than local discs (but alphaCO not same as ULIRGs)
+Using the dynamical mass and the total
+gas mass ($M_{\rm gas}^{\rm total}$), we find a gas mass
+fraction of $f_{\rm gas-dyn}$ = 0.19\pmm0.37, which is
+consistent with the results reported by \citetalias{Combes13a}:
+a gas fraction of 15\% in ULIRGs at 0.2\,$<$\,$z$\,$<$\,0.4 and 24\%
+in those at 0.6\,$<$\,$z$\,$<$\,1.0, and those from resolved measurements of local ULIRGs \citepalias{Downes98a}.
+% This implies that the gas fraction in ULIRGs at $z$$<$\,1 is
+% similar to high-z starburst galaxies, but
+% lower if we average over the same spatial scales (as SMGs, which
+% are more extended; \citet{Bothwell13a}).
+This implies that the gas fraction in ULIRGs at $z$\,$<$\,1 is
+similar to those in high-$z$ starburst galaxies
+\citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}
+as well as high-$z$ ``normal'' star-forming disc galaxies
+\citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a}.
+\defcitealias{Daddi10a}{D10}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % gas to dust ratio:
-Using the dust mass derived from SED fitting,
-we find a gas-to-dust ratio of BLAH\pmm
-BLAH, which is consistent with
-the C13 sample ($f_{\rm gas-dust}$\,=\,206) and local U/LIRGs
-(200$-$350; \citealt{Sanders91a}, Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
-
-\subsubsection{Conversion Factor $\alpha_{\rm CO}$}
-Instead of adopting the conversion factor $\alpha_{\rm CO}$ as 0.8 (K \kms pc$^2$)\pmOne,
-a crude estimate can be obtained using the dust mass and CO luminosity, assuming a 
-gas-to-dust ratio.
-Here we assume a gas-to-dust ratio of 72 (Sandstrom+13), based on a sample of local star-forming
-galaxies of solar metallicities. 
-We find $\alpha_{\rm CO}$ = BLAH\pmm$(f_{\rm gas-dust}/72)$ (K \kms pc$^2$)\pmOne, where the uncertainty does not include 
-systematic uncertainties 
-in the dust absorption coefficient $(\kappa)$ and the gas-to-dust ratio.
-% which Kapa? Kappa 870 or Kappa we used in our dust mass esimate?
-This ?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Solomon+97: GDR ~ 100
+% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
+% our galaxy MW ~150 (Draine+07)
+% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
+%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Using the lensing-corrected dust mass,
+% of $M_{\rm dust}$ = 4.0\petm{0.9}{3.3}\E{8}$(\mu_{\rm L}/5.5)\pmOne$\,\Msun,
+we find a gas-to-dust ratio of
+40\pmm34, which is significantly lower than the average
+in the \citetalias{Combes13a} sample of $f_{\rm gas-dust}$\,=\,206, but
+consistent within the scatter and also with the
+sample of local ULIRGs studied by \citet[][]{Wilson08a},
+with a ratio of $($50$-$70$)$.
+% If we assume that most ULIRGs at the same epoch should have similar dust and
+% gas content owing to their empirical scaling relations
+% with the parameters in the fundamental metallicity relation \citep{Mannucci10a}
+% and their respective evolutions as well as the
+% well-established \LFIR--\Lp correlation \citep[\eg][]{Young91a, Sanders91a},
+% the low gas-to-dust ratio of RXJ1131 compared to the
+% \citetalias{Combes13a} sample may be explained
+% in part due to differential lensing between the gas and the dust, leading to
+% an overestimation of the dust mass via our adoption of the CO magnification
+% factor, but this is
+% unlikely [the dominant reason/enough to account] for the factor of $\sim$5
+% discrepancy. It is thus necessary to invoke other possible explanations.
+We note that the gas-to-dust ratio is only good within
+within a factor of 2$-$3 as
+differential lensing may exist between the gas and the dust, leading to
+an under- or overestimation of the dust mass via our adoption of the CO magnification factor.
+
+% We also note that the gas-to-dust ratio of ULIRGs
+% varies widely in the literature, ranging from 50 to $>$200.
+% Such a variation can arise depending on a few factors, such as the resolution
+
+% Alternately, this may indicate a different \alphaco conversion factor.
+
+% The primary source of uncertainty in the gas mass is
+% undeniably the conversion factor, which if all galaxy samples we
+% are comparing against use the same conversion factor but that our dust-to-gas
+% ratio is different (due to the Mdust), which implies different physical
+% conditions.
+% It thus appears that RXJ1131 is more dusty than ULIRGs at the same epoch, which may indicate different
+% ISM conditions/ISM properties and potentially a different alphaCO.
+% Then it might be reasonable that the alphaco = 0.8 is inappropriate in this case. A higher alpha CO (upper limit using disc value) lead to a gas mass that is $\sim$5 factors higher.
+% Which seems likely to account for the discrepancy because Galactic conversion factor \citep{Papadopoulos12a} might indeed be the true conversion factor in RXJ1131.
+
+% The secondary effect/uncertainty is the excitation condition, which we have conservatively assumed to be thermalized.
+% Should a subthermal condition, we would obtain an even
+% higher gas mass) and that ULIRGs have thermalized excitation up to $J$ = 3 or
+% 4, so the assumption on the brightness temperature ratio should not be the
+% main contribution to the discrepancy in GDR. Also how dust mass
+% is highly dependent on the method (model and how the data are obtained, e.g.
+% resolution) used to obtain the dust mass (e.g. Seaquist+04, finding a GDR
+% affecting by a factor of $\sim$5 in the inner few kpc in some cases for
+% U/LIRGs but global GDR unaffected: ). For now, assume that the dust mass
+% obtained from the literature is the best (most appropriate, close to physical)
+% way to obtain dust mass with the given data for their sample. Then we discuss
+% the implications/reasoning/causes for a low SFE in RXJ1131.
 
 \subsubsection{SFE and Depletion Timescales}
-We derive the SFE using the far-IR luminosity definition used by
-C13 (\ie SFE\pmm\LFIR$($40\,$-$\,500\,\micron)$/$$M_{\rm gas}$$)$,
-we find a SFE of 31\pmm15 for RXJ1131, or equivalently a depletion
-timescale of $\tau$\,=\,190\pmm70\,Myr. % 5.8/SFE Gyr
-This SFE is substantially lower than most U/LIRGs
-(\citealt{Solomon97a,Combes11a}; C13). % local ULIRG: 180 +/- 160 Lsun/M (Solomon+97)
-% Combes+13: sample of 39 gal from z= 0.2-1 find $<$ 100 Myr.
-
-Implication of this unexpectedly low SFE in RXJ1131...
-
-At high redshifts, SMGs the irregular, turbulent starbursting galaxies (SFR $\sim$ BLAH \Msun yr\pmOne)
-and BzK are the ``normal" star-forming disk galaxies with low SFE, relatively high SFR (BLAH) and 
-longer depletion time (BLAH Myr).
+% CO-IR luminosity correlation
+
+In principle, the gas consumption timescale or the star formation efficiency (SFE) furnishes information on the AGN and star-formation
+triggering mechanisms.
+Physically, the SFE depends on the SMBH gas
+consumption time scales and on the energy injected
+to the ISM by AGN feedback. High SFE may thus be indication
+of a small gas reservoir that was reduced by BH accretion and outflows.
+In practice, the SFE is the ratio between the \fir luminosity and CO luminosity as an indicator of the SFR per solar mass of molecular gas.
+
+Using the far-IR luminosity definition used by
+C13 (40\,$-$\,500\,$\micron$),
+we find a SFE $($=\LFIR/$M_{\rm gas})$ of 58\pmm10\,\Lsun$/$\Msun,
+or equivalently a depletion
+timescale of $\tau$\,=\,102\pmm25\,Myr.
+% Gas depletion time assuming the SF is the only way to consume the gas reservoir, and that SF continues at the current rate. Since it is likely that
+% SFR will vary in such a merger situation and that the AGN will consume some of the gas, hence the gas depletion timescale should only be considered as an upper limit.
+% Such an SFE is lower than other U/LIRGs (SFE: 180 +/- 160 Lsun/M \citep{Solomon97a, Combes11a}.
+% The depletion timescales in the C13 sample
+% of 39 galaxies between 0.2$<$$z$1.0 are $<$ 100 Myr.
+% C13: SFE = 100 Lsun/Msun
+
+% --------------------------
+% SFE:
+% in terms of LFIR/Mgas:
+% Greve+05: 450 +/- 170 Lsun/Msun for SMG
+% Solomon97a: 180 +/- 160 Lsun/Msun
+
+% in terms of LFIR/L'CO:
+% Greve+05: SMG 360 +/- 140 Lsun (K km/s pc^2)^-1
+% Solomon97a: LFIR/L'CO = 160
+
+% SV05: local (z<0.1 spirals) of SFE < 100
+
+% SFE > 100 for ULIRGs and SMGs, 0.1 < z < 3 Downes, Solomon & Radford93, Tacconi, L.
+J., Genzel, R., Smail, I., et al.
+2008, ApJ, 680, 246, Riechers, D.
+A., Carilli, C.
+L., Maddalena, R.
+J., et al.
+2011a, ApJL, 739, L31.
+
+% Depletion time:
+% Greve+05: ~40 Myr
+
+% At high redshifts,
+% SMGs the irregular, turbulent star-bursting galaxies (SFR $\sim$1\E{2}-1\E{3}\,\Msun yr\pmOne) and BzKs are the ``normal" star-forming disk galaxies (at z$\sim$1.6) with relatively lower SFE, SFR ($\sim$BLAH) and
+% longer depletion time (BLAH Myr) (CW13, \citealt{Daddi10a}), but surface
+% densities, SFRs, velocity dispersion very similar to local mergers (Daddi10a, Krumholz\&Dekel10, Genzel+11).
+% SFE is highly dependent on the alphaCO if using ratio between the \LIR and gas mass instead of using the ratio between (far-)IR luminosity and CO luminosity.
+% And the use of which alphaCO is also not well justified, especially at high-z (\ie high uncertainties on the alphaco value).
+
+% % galactic value: 4.6
+% In fact
+% e.g.
+Daddi10a argue for an \alphaco conversion factor of 3.6\pmm0.8 for normal SF disk (BzK galaxies) at z$\sim$1.5 using kinematic analysis/dynamical model (based on the dynamical mass).
+Whereas \citet{Tacconi08a, Carilli10a} place an upper limit of $\sim$0.8 on high-z SMGs, leading the emergence of two star formation modes.
+% Carilli+10: based on dynamical constraints
+
+% if RXJ is intriscally low SFE:
+% In terms of more recent simulations, it may be what Hopkins09a suggests that the disc can survive merge by lowering SFE in low-mass systems, allowing them to retain large gas fraction and distributing the gas to larger radii.
+% Thus in Hopkins09a: 1:1 gas-riich mergers can yeild disc-dominated remantns, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
+
+% This unexpectedly low SFE in RXJ1131...
+% % that it is indeed converting gas into stars at a lower rate.
+% but as mentioned above, the possible scenario that an \alphaco of 0.8 UNIT is inappropriate here.
+
+% \subsubsection{Conversion Factor $\alpha_{\rm CO}$}
+
+% From the gas-to-dust ratio and SFE, it is evident that a different \alphaco conversion factor may be more appropriate for RXJ1131.
+
+% The physical motivation/basis for deriving the gas mass from CO luminosity is
+% assuming virialized (self-gravitating), non-overlapping gas cloud.
+% Then \alphaco scales as $n^{1/2}/T_b$, where $n$ is the average H$_2$ number density
+% in the clouds and $T_b$ is the intrinsic brightness temperature of the CO line.
+
+% Downes,Solomon \& Radford 93, Solomon97: CO emitting gas in the centers of ULIRGs is unlikely to be virialized, but instead bound by the potential of the galaxy or from molecular gas in pressure rather than gravitational equilibrium.
+
+% DS98: showed that alphaco is a factor of $\sim$6 smaller for local ULIRGs than for local spirals.
+% Also see Scoville+97
+
+% % also a function of metallicity (Leroy11 apj 737, 12), excitation, pressure.
+% %\alphaco lower for objects with extended surface gas densities (Downes Solomon98), where gas temperature and velocity dispersion are higher.
+% %While the conversion factor $(\alphaco)$ is commonly adopted as 0.8  (K \kms pc$^2$)\pmOne
+% %for ULIRGs, its numerical value depends on the ISM environment (Narayanan11a).
+% %For instance, it could be
+% %different in a dynamically turbulent galaxy, where the gas is warmer, more excited, and denser.
+% % Instead of obtaining a crude estimate
+% %using the dust mass and CO luminosity, assuming a
+% %gas-to-dust ratio. {\textbf but this gal. have very different GDR than others, can I even assume that? or is it
+% %because of the alphaCO that is leading to the different in GDR, but others also uses the same alphaCO.
+% %Also probably shouldn't do this given how poorly-constrained the Mdust is..}
+% %Here we assume a gas-to-dust ratio of 72 (Sandstrom+13), based on a sample of local star-forming
+% %galaxies of solar metallicities.
+% %We find $\alpha_{\rm CO}$ = BLAH\pmm$(f_{\rm gas-dust}/72)$ (K \kms pc$^2$)\pmOne, where the uncertainty does not include systematic uncertainties
+% %in the dust absorption coefficient $(\kappa)$ and the gas-to-dust ratio.
+% % We discuss a potential different \alphaco that is more appropriate
+% % for RXJ1131.
+
+% %As discussed in Solomon \& Vanden
+% %Bout (2005), low-z studies of ULIRGs have led to the
+% %suggestion that the conversion factor could be several times
+% %smaller (Downes et al. 1993; Bryant \& Scoville 1999). This can
+% %arise in the ULIRGs if the gas is concentrated in the nuclear
+% %regions (as a result of dissipative galaxy merging) and the
+% %molecular emission linewidths can be broadened by the galactic
+% %dynamics associated with the stellar mass?not just the self-gravitating
+% %gas mass as in individual GMCs in which the
+% %standard conversion factor was derived. In addition, the mean
+% %gas temperature and density (?) may be different in the ULIRG
+% %nuclei as a result of the intense star formation activity, and AlphaCO
+% %should vary as density and temperature e.g. (Dickman et al. 1986).
+% % Also should be a continuous distribution instead of a bimodal value (Narayana+12).
+% % Yet, from numerical models, it is found that mergers have lower alphaCO than
+% % disk galaxies, thus we can derive an upper limit on the gas mass in the RXJ1131 merger system using a disk alphaCO factor.
+% In fact, physically, In a minor merger, the rise in gas temperatures and velocity dispersions are not as extreme as they are in major mergers.
+Hence, the rise in velocity-integrated CO intensity is not as large, and the X-factor (and thus alphaco) does not decrease as much {Narayana11a}.
+
+% In contrast to what was found in the classical study by DS98, who find that
+% adopting a MW XCO for their sample of nearby ULIRGs would cause the gas mass
+% to exceed the Mdyn (and thus inappropriate for their sample), the Mgas of RXJ1131 merger system derived using MW XCO is
+% consistent with the dynamical mass.
+% DS98: Gas masses were derived from radiative transfer model instead of using standard conversion factor, which yields the \alphaco = 0.8 UNIT. f$_{gas-dyn}$ = 1/6.
+
+% % how would our conclusions change if we use different alphaCO
+% If we instead apply a galactic \alphaco conversion factor of 4.6, the gas mass would increase by a factor of $\sim$6, and longer depletion time.
 
@@
 \section{Discussion} \label{sec:diss}
-\subsection{Merger stage of RXJ1131-1231}
-Using the redshift inferred from the line center of the CO gas disk $(z_{\rm CO} = 0.6537)$ 
-as the systemic redshift. The velocity offset from the optical lines $(z_{\rm AGN} = 0.658)$ 
-is $\sim$780\,\kms. This may ? interaction
-
-In this section, we put our results in context with other ULIRGs/mergers at
-$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a
-gas-rich companion, but how does this affect its internal dynamics?
-What is the merger stage of RXJ1131?
-We argued that the symmetric source-plane velocity field suggest
-the system is a minor merger, consistent with an earlier study by B08, who
-independently conclude that the companion is likely
-a dwarf of size $\sim$700\,kpc across.
-
-While our result is consistent with other studies of RXJ1131, it
-contrast strongly with studies of local (U)LIRGs/mergers
-(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1), where AGNs are
-typically found in late stage mergers
-\citep{Yuan10a,Iwasawa11a,Carpineti12a} and
-that only these major mergers near their final
-coalescence can provide \LIR\,$>$\,10$^{12}$\,\Lsun,
-\citep[\eg][hereafter L16]{Carpineti15a,Larson16a}
-\footnote{In this section, we adopt the total IR luminosity
-calculated from 8\,$-$\,1000\,$\micron$
-to be consistent with the classification used by these authors.}.
-If this is also the case at $z$$\sim$0.65, it would imply RXJ1131
-is a major merger near its final coalescence and that the spatially offset
-component is likely an expulsion of gas driven by AGN winds or some
-tidally ejected material from previous passage.
-In that case, the molecular gas fraction in the host
-galaxy should have declined (as seen in ellipticals) compared to early
-stage mergers
-\textbf{can we find molecular gas mass fraction as a
-function of merger stage? also, what is the dynamical mass for RXJ1131}
-and that the molecular gas would
-be more concentrated in the nuclear region.
-This is inconsistent with what
-is observed for RXJ1131
-(an extended gas-rich disk; but see also U14 for outliers
-with extended molecular gas in merger remnants) and
-the fact that there is on-going \SF activity.
-Hence, we reject this and speculate the discrepancy is a consequence
-of different power mechanisms of IR-luminous galaxies at intermediate redshift.
-
-{\bf --- anything below is not ready ---}
-\subsubsection{Fate of RXJ1131-1231}
-Has RXJ1131 encountered with the companion?
-
-From numerical simulations, mergers are observable and distinguishable
-with their kinematic and morphological features for 0.2$-$0.4 Gyr
-between their second passage and final coalescence.
-
-The spinning black hole in RXJ1131 provide one piece of
-evidence that the two has already encountered.
-
-% The future of RXJ1131:
-Mergers are expected to evolve into
-local ellipticals or large-disks (bulge dominated) (springel \& Hernquist 05, cite).
-Given the
-extended molecular gas distribution, we suggest RXJ1131 may evolve into the
-latter (large-disk) unless the ``companion'' BKAH SOME STUFF or some other
-mechanisms at play in the latter stage, transporting the gas
-toward the central nuclear region and blah.
-
-\subsection{Morphological Transformation}
-While the space density of ULIRGs are only BLAH Mpc$^{-3}$ (CITE), 
-the blah and the evolution in structure of high- and low-z galaxies
-implying ULIRGs and mergers play an important role in giving rise to the BLAH.
-
-\subsection{ULIRG Evolution and Cosmic SFH}
-While there is an emerging consensus on the strong
-evolution of the IR luminosity function \citep[\eg][]{Huynh07a,Seymour10a},
-it is currently unclear whether the IR luminosity of
-these intermediate redshift sources arise due to the merging of large spiral
-galaxies, as typically seen in local ULIRGs, or proceed under a different
-formation processes at higher redshifts. Our study blah...
-
-% Implication on SFH
-Our result indicates that...
-% the gas mass fraction has already decreased
-% at this redshift, which may suggest that the change in cosmic SFD is due to
-% change in gas content. The SFE is also BLAH at this redshift,
-% consistent with current speculation of how the SFRD decreases over cosmic time.
-
-which seem probable given the relation in AGN growth and gas accumulation.
-the simultaneous observation of the AGN phenomenon, of stellar formation and of galaxy interaction illustrates the current AGN ?
-black hole paradigm, according to which the growth of a black hole through the AGN phase occurs when galaxy interactions provide gas inflow towards the center (e.g.
-Hernquist 1989; Di Matteo et al.
-2005).
-Since the interactions induce gravitational perturbations, simultaneous starbursts are also expected.
-
-%--------------------------------------------------------------------------
-%                                Conclusions
-%--------------------------------------------------------------------------
-\section{Summary and Conclusions} \label{sec:sum}
-% see Hodge12_dynamics.pdf for guide
-
-%- summarize the findings from the entire study
-%    - firm conclusions
-%    - speculative possibilities
-
-We investigate the cold gas kinematics and dynamics in
-the lensed optical quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65
-by observing its \bco and \cco line emission.
-Our results suggest that RXJ1131 is a wet-wet merger between an AGN/starburst
-ULIRG and a optically faint companion.
-
-% Fitting SED models, we find that the AGN host galaxy is a ULIRG.
-% A faint companion as seen in HST observations (BJB) is also detected in our CO, confirming it's redshift and gas rich nature.
-
-% % any further work needed to resolve the remaining problems
-% We list several pieces of evidence through out
-% this work to argue that RXJ1131 is likely a rotating disk.
-% The double-horned profile, smooth, symmetric velocity field
-% seen in our lens model and in the
-% image plane and C06 model $n$=1 Sersic profile all suggest
-% a kinematically-order (i.e., disk) galaxy.
-% Yet, these are insufficient to conclude a disk morphology. Additional
-% characteristics such as peak velocity dispersion at the central region and a
-% ``spider'' diagram are needed, which is commonly seen in local spirals.
-% The high dispersion near the dynamical center also
-% suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. Overall
-% implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution
-% data are needed to confirm this.
-
-The compactness of the emission in $V$-band (rest-frame UV) 
-suggests that the \SF in RXJ1131 is proceeding in a 
-compact region embedded w/in a large reservoir of molecular gas, which may be explained 
-by gas inflow toward nuclear regions due to interaction with the companion. 
-Such a scenario may support the results in recent models: mergers/ULIRGs evolve into bulge dominated massive disks (Geach+09 sect 3.4).
-
+\subsection{Offset from Systemic Redshift of Host Galaxy and Recoiling BH}
+
+Using the redshift inferred from the line center of the CO gas disk
+$(z_{\rm CO} = 0.6537)$ as the systemic redshift. The velocity offset from
+the optical lines $(z_{\rm AGN} = 0.658)$
+(broad Mg{\sc II}$\lambda$ 2798$\Angstrom$ and narrow lines [O{\sc III}]$\lambda\lambda$ 4959, 5007$\Angstrom$ emission, Sluse03a)
+is $\sim$780\,\kms, which indicates that the
+BLR of the AGN is at a slightly higher z than the host galaxy.
+This is consistent with the CO renzogram, where the emission from the line center channels are not co-spatial.
+In particular, the lensed QSO emission forms the point-like images along the arc and the lensed emission of the line center is spatially offset to the SE of the QSO lensing arc.
+Such a spatial offset between optical BLR and CO is not uncommon, but the velocity offset is not common.
+For instance,
+AGN in ongoing galaxy mergers are observed to have kinematics offsets in AGN relative to their host galaxies, SDSS sample at z $<$ 0.21, max offset 410 km/s, not accounted for projection effects in the observed velocities.
+elo offsets can be produced by rot. gas disks, AGN outflows, jets, gravi. recoil of SMBH (Comerford & Greene, 2014, ApJ, 789, 112).
+
+which may be kinematic indication of a recoiling BH.
+There are a few reasons to this e.g. SB/AGN driven winds or AGN outflows, jets, gravitational recoil of BH in post-merger. % (Comerford & Greene, 2014, ApJ, 789, 112).
+Here we discuss the possibility of a GW recoiling merged BH.
+The recoiling is expected to happen after the merging because their orbital energy is emitted as GW to overcome the stable orbit for the binary,
+carrying away a non-zero angular momentum for uneven (i.e.
+not 1:1) BH mass mergers, which at the same time will cause a recoil in the merger BH.
+Depending on their initial mass ratios, spin, rotational direction, the recoil velocity can reach as high as $\sim$4000\,\kms for spinning BHs, suggested by numerical relativity simulations \citep[\eg][]{Campanelli+07a}
+The BH is displaced from the galactic nucleus in this scenario, and might return to the center in a few dynamical time-scales by dynamical friction or be kicked out of the gravitational potential of the host galaxy.
+In terms of RXJ1131,
+while we still see the gas-rich companion, it could be that they were initially major mergers that had encounter before (causing the high spinning BH), and we are currently witnessing the subsequent minor merger stages.
+
+Alternatively, it can be indication of the BH orbiting in the host galaxy.
+Since we cannot quantify this further without the separate redshifts based on the broad Mg II and the narrow OIII lines as Slues+03 only report the combined $z$.
+If we have that, it could be indication of an AGN orbiting the host galaxy (but only if the velocity offset between the BLR and the narrow line of the gas in the host is lower than its orbital velocity), or AGN outflow or SB driven wind as in the case of SMMJ1636+4057\citep{Swinbank05a}.
+
+offset from the galaxy core \citep{Madau04a},
+or in the form of broad emission lines kinematically
+offset from the narrow emission lines \citep{Bonning07a} (\ie carrying along its accretion disc and BLR). Thus offset from narrow lines can also be offset AGN than outflow gas.
+From Slues03 spectrum, doesn't appear to see a broad component and a narrow component or I should say their z is derived using both the broad MgII line and the narrow [OIII] lines, which means we can rule out an explanation due to the in/outflows due to radiation pressure or AGN winds.
+Also we don't see double-peaked in optical lines and are not skewed lines.
+
+% Other objects seen with such big velocity offset:
+It may be worth noting that while such big velocity offset is not commonly
+seen even in mergers, it has been reported in a few objects. For instance,
+the most promising candidate of GW recoiling with both spectroscopy and imaging
+signature:
+CID-42 at z=0.359 has a similar velocity offset ($\sim$1300\,\kms; between the narrow and broad component of H$\beta$) in two
+optical component separated by $\sim$ 2.5 kpc within the same galaxy \citep{}Civano10a}, which has been proposed to
+be a good candidate for a recoiling BH.
+
+Also type-1 QSO, SDSS 0956+5127 at $z_{\rm sys}$$\sim$0.714 from narrow lines, and $z_{Mg II}$ at $z\sim$0.707, corresponding to 1200 \kms offset \citep{Steinhardt12a}.
+Other example:
+SDSSJ0927+2943 at $z$$\sim$0.713 shows an exceptional optical emission-line spectrum with two
+sets of emission lines: one set of very narrow emission lines, and a second set of broad Balmer and
+broad high-ionization forbidden lines which are blueshifted by 2650 \kms
+relative to the set of narrow emission lines \citep{Komossa08a}.
+This observation is most naturally explained if the SMBH was ejected from the core
+of the galaxy, carrying with it the broad-line gas while leaving behind the bulk of the narrow-line
+gas.
 %==============================================================================

### 2016-06-28 WRITEUP/ms.tex
done with analysis section

@@
 The CO gas is thus of similar spatial
-extent as $H$ and $I$-bands.
+extents as in $H$ and $I$-bands.
 
@@
 mass function \citep{Salpeter55a}, we find a
-SFR$_{\rm FIR}$ of (120\pmm63)\,\Msun\,yr\pmOne using the
+SFR$_{\rm FIR}$ of 120\pmm63\,\sfrU using the
 standard conversion \citep{Kennicutt98a}.
@@
 in a local LIRG (Arp 118) \citep{SV05a}.
-Such FWHM is also commonly observed in high-z starburst galaxies
+Such FWHM is also commonly observed in high-$z$ starburst galaxies
 \citep[780\pmm320\,\kms; \eg][]{Greve05a}.
-\defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}
+\defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}\defcitealias{SV05a}{SV05}
 
@@
 can be distributed over large regions comparable to
-those reported in high-z ($z$$>$\,1) galaxies \citep[$R\sim$7\,kpc;
+those reported in high-$z$ ($z$$>$\,1) galaxies \citep[$R\sim$7\,kpc;
 \citetalias{Greve05a};][]{Daddi10a, Riechers11a, Ivison11a}.
-While we cannot draw conclusions any evolution in the
+While we cannot draw any conclusions on the evolution of 
 molecular gas size
@@
 necessarily more compact than
-high-z SMGs \citep[cf. \eg][]{Iono09a}.
+high-$z$ SMGs \citep[cf. \eg][]{Iono09a}.
 \defcitealias{Ueda14a}{U14}
@@
 line profile of the companion ($\sigma$ = 30\,\kms)
-and its intrinsic source size of $\sim$700\,pc obtained from the {\em HST} $V$-band lens model \citepalias{Brewer08a},
+and its intrinsic source size of $\sim$700\,pc obtained from the {\em HST}
+$V$-band lens model \citepalias{Brewer08a},
 we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 5\E{6}\,\Msun.
-This corresponds to $M_{\rm dyn}$\,=\,2\E{7}\,\Msun if we assume an inclination angle of 30$\degr$.
+This corresponds to $M_{\rm dyn}$\,=\,2\E{7}\,\Msun if we assume an
+inclination angle of 30$\degr$.
 We note that this is substantially lower than its gas mass, which is a more reliable estimate based on
@@
 Our finding is thus consistent with previous results, where
-high-z galaxies tend to have higher molecular gas mass %\footnote{Assuming the same conversion factor}
+high-$z$ galaxies tend to have higher molecular gas mass %\footnote{Assuming the same conversion factor}
 and is
 distributed over larger spatial extents
-\citep[\eg][\citetalias{Riechers11a,Ivison11a}]{SV05a}.
+\citepalias[\eg][]{SV05a,Riechers11a,Ivison11a}.
 % gas-to-dyn ratio
@@
 This implies that the gas fraction in ULIRGs at $z$\,$<$\,1 is
-similar to those in high-$z$ starburst galaxies
-\citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}
-as well as high-$z$ ``normal'' star-forming disc galaxies
-\citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a}.
+similar to those in high-$z$ ``normal'' star-forming disc galaxies
+\citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a} as well as
+high-$z$ starburst galaxies
+\citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}.
 \defcitealias{Daddi10a}{D10}
@@
 we find a gas-to-dust ratio of
-40\pmm34, which is significantly lower than the average
-in the \citetalias{Combes13a} sample of $f_{\rm gas-dust}$\,=\,206, but
-consistent within the scatter and also with the
-sample of local ULIRGs studied by \citet[][]{Wilson08a},
-with a ratio of $($50$-$70$)$.
+40\pmm34, which is significantly lower than the statistical average
+of $f_{\rm gas-dust}$\,=\,206
+in the \citetalias{Combes13a} sample but
+consistent with their range of values and the
+\citet[][]{Wilson08a}
+sample of local ULIRGs. %$($50$-$70$)$.
 % If we assume that most ULIRGs at the same epoch should have similar dust and
@@
 % discrepancy. It is thus necessary to invoke other possible explanations.
-We note that the gas-to-dust ratio is only good within
-within a factor of 2$-$3 as
-differential lensing may exist between the gas and the dust, leading to
-an under- or overestimation of the dust mass via our adoption of the CO magnification factor.
-
-% We also note that the gas-to-dust ratio of ULIRGs
-% varies widely in the literature, ranging from 50 to $>$200.
-% Such a variation can arise depending on a few factors, such as the resolution
-
-% Alternately, this may indicate a different \alphaco conversion factor.
-
-% The primary source of uncertainty in the gas mass is
-% undeniably the conversion factor, which if all galaxy samples we
-% are comparing against use the same conversion factor but that our dust-to-gas
-% ratio is different (due to the Mdust), which implies different physical
-% conditions.
-% It thus appears that RXJ1131 is more dusty than ULIRGs at the same epoch, which may indicate different
-% ISM conditions/ISM properties and potentially a different alphaCO.
-% Then it might be reasonable that the alphaco = 0.8 is inappropriate in this case. A higher alpha CO (upper limit using disc value) lead to a gas mass that is $\sim$5 factors higher.
-% Which seems likely to account for the discrepancy because Galactic conversion factor \citep{Papadopoulos12a} might indeed be the true conversion factor in RXJ1131.
-
-% The secondary effect/uncertainty is the excitation condition, which we have conservatively assumed to be thermalized.
-% Should a subthermal condition, we would obtain an even
-% higher gas mass) and that ULIRGs have thermalized excitation up to $J$ = 3 or
-% 4, so the assumption on the brightness temperature ratio should not be the
-% main contribution to the discrepancy in GDR. Also how dust mass
-% is highly dependent on the method (model and how the data are obtained, e.g.
-% resolution) used to obtain the dust mass (e.g. Seaquist+04, finding a GDR
-% affecting by a factor of $\sim$5 in the inner few kpc in some cases for
-% U/LIRGs but global GDR unaffected: ). For now, assume that the dust mass
-% obtained from the literature is the best (most appropriate, close to physical)
-% way to obtain dust mass with the given data for their sample. Then we discuss
-% the implications/reasoning/causes for a low SFE in RXJ1131.
+We note that the gas-to-dust ratio maybe biased low as
+the optically thick gas is likely to be more extended than the dust, leading to
+an overall lower magnification factor than the dust emission,
+and thus an overestimate of the
+dust mass via our adoption of the CO magnification factor.
+
+% A direct comparison to the literature is not straightforward as the dust mass estimate
+% is highly dependent on the method, \eg the model assumed, the wavelength and resolution at which the data 
+% were observed. Seaquist+04 find that a GDR can be 
+% affected by a factor of $\sim$5 in the inner few kpc in some cases for
+% U/LIRGs but global GDR may be unaffected. If we assume that the dust mass
+% obtained from the literature is obtained through the most appropriate
+% way with the given data for their sample, then the main uncertainty related to the dust mass is the mass
+% opacity coefficient. While the main systematic uncertainties associated with the gas mass
+% are the \alphaco conversion factor and the brightness temperature ratio $R_{\rm 21}$.
+
+There are a number of systematic uncertainties associated with this quantity, \eg
+the mass opacity coefficient $\kappa$,
+the \alphaco conversion factor, and the brightness temperature ratio $R_{\rm 21}$.
+The fact that RXJ1131 has a lower dust-to-gas ratio 
+and appears to be more dusty than most ULIRGs at the same epoch
+may imply different physical
+environment compared to others. If we instead use the ``Galactic" \alphaco value, 
+the gas mass (and thus gas-to-dust ratio) would be $\sim$6 times higher.
+On the other hand, we would also obtain a higher gas mass if 
+we assume subthermal excitation between \bco and \aco line emission.
+However, we expect this to be a minor effect as ULIRGs are observed to be
+thermalized up to $J$ = 3 or 4.
 
@@
 % CO-IR luminosity correlation
-
-In principle, the gas consumption timescale or the star formation efficiency (SFE) furnishes information on the AGN and star-formation
-triggering mechanisms.
-Physically, the SFE depends on the SMBH gas
-consumption time scales and on the energy injected
-to the ISM by AGN feedback. High SFE may thus be indication
-of a small gas reservoir that was reduced by BH accretion and outflows.
-In practice, the SFE is the ratio between the \fir luminosity and CO luminosity as an indicator of the SFR per solar mass of molecular gas.
-
-Using the far-IR luminosity definition used by
-C13 (40\,$-$\,500\,$\micron$),
-we find a SFE $($=\LFIR/$M_{\rm gas})$ of 58\pmm10\,\Lsun$/$\Msun,
-or equivalently a depletion
-timescale of $\tau$\,=\,102\pmm25\,Myr.
-% Gas depletion time assuming the SF is the only way to consume the gas reservoir, and that SF continues at the current rate. Since it is likely that
-% SFR will vary in such a merger situation and that the AGN will consume some of the gas, hence the gas depletion timescale should only be considered as an upper limit.
-% Such an SFE is lower than other U/LIRGs (SFE: 180 +/- 160 Lsun/M \citep{Solomon97a, Combes11a}.
-% The depletion timescales in the C13 sample
-% of 39 galaxies between 0.2$<$$z$1.0 are $<$ 100 Myr.
-% C13: SFE = 100 Lsun/Msun
-
-% --------------------------
 % SFE:
@@
 % Solomon97a: 180 +/- 160 Lsun/Msun
+% SV05: local (z<0.1 spirals) of SFE < 100
 
@@
 % Solomon97a: LFIR/L'CO = 160
-
-% SV05: local (z<0.1 spirals) of SFE < 100
 
@@
 
+To first order, the star formation efficiency
+$($SFE = \LFIR$/$$M_{\rm gas})$
+indicates the \SF rate per
+unit solar mass of molecular gas available in a galaxy.
+Using a wavelength range of 40\,$-$\,500\,$\micron$ defined
+in \citetalias{Combes13a} as the far-IR luminosity,
+we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$,
+which is on the low end among other U/LIRGs
+% \citep[$\sim$180\pmm160 \Lsun $M_{\odot}^{-1}$;][]{Solomon97a, Combes11a}
+\citep{Solomon97a, Combes11a}
+but 
+similar to those of
+low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a}.
+In constrast, a star formation efficiency of $>$100 \Lsun $M_{\odot}^{-1}$
+has been reported in ULIRGs and SMGs at 0.6\,$<$\,$z$\,$<$\,3
+\citep[][\citetalias{Riechers11a,Combes13a}]{Tacconi08a}.
+\defcitealias{Tacconi08a}{T08}
 % Depletion time:
 % Greve+05: ~40 Myr
-
-% At high redshifts,
-% SMGs the irregular, turbulent star-bursting galaxies (SFR $\sim$1\E{2}-1\E{3}\,\Msun yr\pmOne) and BzKs are the ``normal" star-forming disk galaxies (at z$\sim$1.6) with relatively lower SFE, SFR ($\sim$BLAH) and
-% longer depletion time (BLAH Myr) (CW13, \citealt{Daddi10a}), but surface
-% densities, SFRs, velocity dispersion very similar to local mergers (Daddi10a, Krumholz\&Dekel10, Genzel+11).
-% SFE is highly dependent on the alphaCO if using ratio between the \LIR and gas mass instead of using the ratio between (far-)IR luminosity and CO luminosity.
-% And the use of which alphaCO is also not well justified, especially at high-z (\ie high uncertainties on the alphaco value).
-
-% % galactic value: 4.6
-% In fact
-% e.g.
-Daddi10a argue for an \alphaco conversion factor of 3.6\pmm0.8 for normal SF disk (BzK galaxies) at z$\sim$1.5 using kinematic analysis/dynamical model (based on the dynamical mass).
-Whereas \citet{Tacconi08a, Carilli10a} place an upper limit of $\sim$0.8 on high-z SMGs, leading the emergence of two star formation modes.
-% Carilli+10: based on dynamical constraints
-
-% if RXJ is intriscally low SFE:
-% In terms of more recent simulations, it may be what Hopkins09a suggests that the disc can survive merge by lowering SFE in low-mass systems, allowing them to retain large gas fraction and distributing the gas to larger radii.
-% Thus in Hopkins09a: 1:1 gas-riich mergers can yeild disc-dominated remantns, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
-
-% This unexpectedly low SFE in RXJ1131...
-% % that it is indeed converting gas into stars at a lower rate.
-% but as mentioned above, the possible scenario that an \alphaco of 0.8 UNIT is inappropriate here.
-
-% \subsubsection{Conversion Factor $\alpha_{\rm CO}$}
-
-% From the gas-to-dust ratio and SFE, it is evident that a different \alphaco conversion factor may be more appropriate for RXJ1131.
-
-% The physical motivation/basis for deriving the gas mass from CO luminosity is
-% assuming virialized (self-gravitating), non-overlapping gas cloud.
-% Then \alphaco scales as $n^{1/2}/T_b$, where $n$ is the average H$_2$ number density
-% in the clouds and $T_b$ is the intrinsic brightness temperature of the CO line.
-
-% Downes,Solomon \& Radford 93, Solomon97: CO emitting gas in the centers of ULIRGs is unlikely to be virialized, but instead bound by the potential of the galaxy or from molecular gas in pressure rather than gravitational equilibrium.
-
-% DS98: showed that alphaco is a factor of $\sim$6 smaller for local ULIRGs than for local spirals.
-% Also see Scoville+97
-
-% % also a function of metallicity (Leroy11 apj 737, 12), excitation, pressure.
-% %\alphaco lower for objects with extended surface gas densities (Downes Solomon98), where gas temperature and velocity dispersion are higher.
-% %While the conversion factor $(\alphaco)$ is commonly adopted as 0.8  (K \kms pc$^2$)\pmOne
-% %for ULIRGs, its numerical value depends on the ISM environment (Narayanan11a).
-% %For instance, it could be
-% %different in a dynamically turbulent galaxy, where the gas is warmer, more excited, and denser.
-% % Instead of obtaining a crude estimate
-% %using the dust mass and CO luminosity, assuming a
-% %gas-to-dust ratio. {\textbf but this gal. have very different GDR than others, can I even assume that? or is it
-% %because of the alphaCO that is leading to the different in GDR, but others also uses the same alphaCO.
-% %Also probably shouldn't do this given how poorly-constrained the Mdust is..}
-% %Here we assume a gas-to-dust ratio of 72 (Sandstrom+13), based on a sample of local star-forming
-% %galaxies of solar metallicities.
-% %We find $\alpha_{\rm CO}$ = BLAH\pmm$(f_{\rm gas-dust}/72)$ (K \kms pc$^2$)\pmOne, where the uncertainty does not include systematic uncertainties
-% %in the dust absorption coefficient $(\kappa)$ and the gas-to-dust ratio.
-% % We discuss a potential different \alphaco that is more appropriate
-% % for RXJ1131.
-
-% %As discussed in Solomon \& Vanden
-% %Bout (2005), low-z studies of ULIRGs have led to the
-% %suggestion that the conversion factor could be several times
-% %smaller (Downes et al. 1993; Bryant \& Scoville 1999). This can
-% %arise in the ULIRGs if the gas is concentrated in the nuclear
-% %regions (as a result of dissipative galaxy merging) and the
-% %molecular emission linewidths can be broadened by the galactic
-% %dynamics associated with the stellar mass?not just the self-gravitating
-% %gas mass as in individual GMCs in which the
-% %standard conversion factor was derived. In addition, the mean
-% %gas temperature and density (?) may be different in the ULIRG
-% %nuclei as a result of the intense star formation activity, and AlphaCO
-% %should vary as density and temperature e.g. (Dickman et al. 1986).
-% % Also should be a continuous distribution instead of a bimodal value (Narayana+12).
-% % Yet, from numerical models, it is found that mergers have lower alphaCO than
-% % disk galaxies, thus we can derive an upper limit on the gas mass in the RXJ1131 merger system using a disk alphaCO factor.
-% In fact, physically, In a minor merger, the rise in gas temperatures and velocity dispersions are not as extreme as they are in major mergers.
+Assuming the \SF continues at the current rate without gas replenishment and is the only
+way to consume the gas reservoir, this corresponds to a depletion
+time of $\tau$\,=\,102\pmm25\,Myr.
+Since the \SF rate is expected to vary in an interacting system and that AGN accretion
+also consumes some fraction of the gas, the depletion
+timescale should only be considered as an upper limit.
+
+The SFE (using the above definition) is highly dependent on the gas mass.
+Yet, the use of an ``ULIRG" \alphaco value is not well justified and 
+should only be considered as a lower limit \citepalias[see][]{Solomon97a}.
+It may be more appropriate to use an \alphaco closer to the ``Galactic" value in 
+some ULIRGs \citep[\eg][]{Papadopoulos12a}. 
+From numerical models, it is found that mergers on average have lower \alphaco values than
+disk galaxies \citep{Narayanan12a}.
+But since the gas temperatures and velocity dispersions in minor mergers do not deviate from 
+galactic GMCs as much as in major mergers, the \alphaco may not be as extreme as 0.8\,\alphaU.
+% thus the rise in CO intensity is not as large, and the X-factor (and thus alphaco) does not decrease as much {Narayana11a}.
+Hence,
+we can derive an upper limit on the gas mass for RXJ1131 using the standard conversion factor.
+If we have instead applied the Galactic value of 4.6\,\alphaU, 
+the gas mass (and thus the SFE) would be higher by a factor of $\sim$6. 
+In contrast to results in the classical study of nearby ULIRGs by \citetalias{Downes98a}, who find that
+the gas mass exceeds the dynamical mass using 
+the Galactic conversion factor 
+(and thus inappropriate for their sample), the gas mass derived for
+RXJ1131 using the Galactic value is consistent with its dynamical mass.
+%Obviously, this will lead to a longer depletion time.
+
+Alternatively, the relatively low SFE maybe intrinsic to RXJ1131.
+In that case,  RXJ1131 may evolve into a disc galaxy with a small bulge component
+in the context of theoretical simulations by \citet{Hopkins09a}, who suggest 
+that the disc component in a progenitor galaxy can survive post-merging
+by lowering the \SF efficiency, enabling a higher gas fraction to be retained and 
+distributed over a larger extent.
+% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
+
+%While the \alphaco conversion factor is commonly assumed to be 0.8\,\alphaU for
+%for ULIRGs/starbursts, its numerical value depends on the ISM environment
+% \citep[\eg][]{Narayanan11a}.
+% For instance, it could be different in a 
+% dynamically turbulent galaxy, where the gas is warmer, more excited, 
+% and denser, than in a quiescent galaxy.
+% In addition, the physical basis for deriving the gas mass from the CO luminosity is
+% by assuming the ISM only consists of virialized, non-overlapping gas clouds, 
+% which is often not true in ULIRGs \citep[][\citetalias{Solomon97, Downes98a}]{Downes93a}.
+% % the CO emitting gas in the centers of ULIRGs is unlikely to be virialized, but instead bound by the potential of the galaxy or from molecular gas in pressure equilibrium rather than gravitational equilibrium.
+
+% % DS98: lower alphaCO for objects with extended surface gas densities, where gas temperature and velocity dispersion are higher; Mgas derived from radiative transfer model instead of using standard conversion factor, which yields the \alphaco = 0.8 UNIT for local ULIRGs.
+% % Also see Scoville+97
+
+ %As discussed in Solomon \& Vanden
+ %Bout (2005), low-$z$ studies of ULIRGs have led to the
+ %suggestion that the conversion factor could be several times
+ %smaller (Downes et al. 1993; Bryant \& Scoville 1999, DS98). This can
+ %arise in ULIRGs if the gas is concentrated in the nuclear
+ %regions (as a result of dissipative galaxy merging) and the
+ %molecular emission linewidths can be broadened by the galactic
+ %dynamics associated with the stellar mass, not just the self-gravitating
+ %gas mass as in individual GMCs in which the
+ %standard conversion factor was derived. In addition, the mean
+ %gas temperature and density may be different in the ULIRG
+ %nuclei as a result of the intense star formation activity and since AlphaCO
+ %should vary as density and temperature e.g. (Dickman et al. 1986).
+ % Also should be a continuous distribution instead of a bimodal value (Narayanan+12).
+ % Yet, from numerical models, it is found that mergers have lower alphaCO than
+ % disk galaxies, thus we can derive an upper limit on the gas mass in the RXJ1131 merger system using a disk alphaCO factor.
+% In a minor merger, the rise in gas temperatures and velocity dispersions are not as extreme as in major mergers.
 Hence, the rise in velocity-integrated CO intensity is not as large, and the X-factor (and thus alphaco) does not decrease as much {Narayana11a}.
 
-% In contrast to what was found in the classical study by DS98, who find that
-% adopting a MW XCO for their sample of nearby ULIRGs would cause the gas mass
-% to exceed the Mdyn (and thus inappropriate for their sample), the Mgas of RXJ1131 merger system derived using MW XCO is
-% consistent with the dynamical mass.
-% DS98: Gas masses were derived from radiative transfer model instead of using standard conversion factor, which yields the \alphaco = 0.8 UNIT. f$_{gas-dyn}$ = 1/6.
-
-% % how would our conclusions change if we use different alphaCO
-% If we instead apply a galactic \alphaco conversion factor of 4.6, the gas mass would increase by a factor of $\sim$6, and longer depletion time.
+%\subsubsection{Comparison with High-$z$ SMGs and BzKs}
+%At high redshifts ($z$\,$\gtrsim$\,1), SMGs are the irregular, turbulent
+%star-bursting galaxies with elevated specific \SF rates (CITE) %\citep[sSFR][]{}
+%and BzKs are the ``normal" star-forming disk galaxies with relatively lower 
+%\SF efficiencies, \SF rates and also
+%longer depletion times \citep[\citetalias{Daddi10a};][]{CW13}.
+
+%In fact, an \alphaco conversion factor of 3.6\pmm0.8 
+%has been proposed for BzKs using kinematic analysis/dynamical model (based on the dynamical mass; e.g. Daddi10a). 
+% Whereas \citet{Tacconi08a, Carilli10a} place an upper limit of $\sim$0.8 on high-$z$ SMGs, leading the emergence of two star formation modes. Carilli+10: based on dynamical constraints
 
@@
 the optical lines $(z_{\rm AGN} = 0.658)$
-(broad Mg{\sc II}$\lambda$ 2798$\Angstrom$ and narrow lines [O{\sc III}]$\lambda\lambda$ 4959, 5007$\Angstrom$ emission, Sluse03a)
+(broad Mg{\sc II}$\lambda$ 2798$\AA$ and narrow lines [O{\sc III}]$\lambda\lambda$ 4959, 5007$\AA$ emission, Sluse03a)
 is $\sim$780\,\kms, which indicates that the
@@
 AGN in ongoing galaxy mergers are observed to have kinematics offsets in AGN relative to their host galaxies, SDSS sample at z $<$ 0.21, max offset 410 km/s, not accounted for projection effects in the observed velocities.
-elo offsets can be produced by rot. gas disks, AGN outflows, jets, gravi. recoil of SMBH (Comerford & Greene, 2014, ApJ, 789, 112).
+elo offsets can be produced by rot. gas disks, AGN outflows, jets, gravi. recoil of SMBH (Comerford \& Greene, 2014, ApJ, 789, 112).
 
@@
 CID-42 at z=0.359 has a similar velocity offset ($\sim$1300\,\kms; between the narrow and broad component of H$\beta$) in two
-optical component separated by $\sim$ 2.5 kpc within the same galaxy \citep{}Civano10a}, which has been proposed to
+optical component separated by $\sim$ 2.5 kpc within the same galaxy \citep{Civano10a}, which has been proposed to
 be a good candidate for a recoiling BH.

### 2016-06-28 WRITEUP/ms.tex
done with velo offset section

@@
 For this reason, the absolute alignment between the VLA image and other
-interferometric images reported in this paper are expected to have astrometric
+interferometric images reported in this paper are expected to have an astrometric
 precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
-errors, and beam size.
+instabiliy, and beam size.
 \defcitealias{Claeskens06a}{C06}
@@
 \section{Discussion} \label{sec:diss}
-\subsection{Offset from Systemic Redshift of Host Galaxy and Recoiling BH}
-
-Using the redshift inferred from the line center of the CO gas disk
-$(z_{\rm CO} = 0.6537)$ as the systemic redshift. The velocity offset from
-the optical lines $(z_{\rm AGN} = 0.658)$
-(broad Mg{\sc II}$\lambda$ 2798$\AA$ and narrow lines [O{\sc III}]$\lambda\lambda$ 4959, 5007$\AA$ emission, Sluse03a)
-is $\sim$780\,\kms, which indicates that the
-BLR of the AGN is at a slightly higher z than the host galaxy.
-This is consistent with the CO renzogram, where the emission from the line center channels are not co-spatial.
-In particular, the lensed QSO emission forms the point-like images along the arc and the lensed emission of the line center is spatially offset to the SE of the QSO lensing arc.
-Such a spatial offset between optical BLR and CO is not uncommon, but the velocity offset is not common.
+\subsection{Velocity Offset and Recoiling BH}
+Using the redshift deduced from the CO line 
+as the systemic redshift, we find
+a velocity offset of $\sim$780\,\kms with the optical lines:
+the broad Mg{\scriptsize II}~2798\AA\ and the narrow 
+$[$O{\scriptsize III}$]$~4959, 5007\AA\ lines \citep[$z_{\rm AGN} = 0.658$;][]{Sluse03a}.
+This indicates that the broad line region (BLR) of the AGN is at a
+slightly higher redshift than the host galaxy.
+From the CO renzogram and channel maps in \Fig{CO21mom} and \Fig{chanmap}, the emission 
+corresponding to the the line center are not co-spatial
+with the optical quasar. In particular, the quasar emission forms 
+the point-like images along the lensing arc, which is 
+spatially offset to the NW
+of the CO line center emission.
+Spatial offsets between optical BLRs and CO emission are not uncommon
+but such a high kinematic offset is not commonly observed.
+For instance, the
+velocity offset between AGNs and their hosts galaxies in 
+an SDSS sample of ongoing mergers at $z$\,$<$\,0.21 is at most $\sim$410\,km/s \citep{Comerford14a}.
+The same authors also suggest mechanisms
+such as AGN outflows, jets, and gravitational recoil of SMBHs in post-merger
+as plausible explanations for these offsets.
+
+AGN outflows or starburst-driven winds have been observed
+in \eg SMMJ1636+4057 \citep[][]{Swinbank05a}, but 
+no evidence for outflows are found in RXJ1131 in the existing data. 
+% an explanation due to the in/outflows arising from radiation pressure or AGN winds.
+Alternatively, it can be an indication of the BH(s) orbiting the a common center in
+the host galaxy.
+In principle, this would only be valid if the velocity offset between the BLR and 
+the narrow line of the gas in the host galaxy is consistent with its orbital velocity. 
+%(\ie carrying along its accretion disc and BLR)
+Since \citet{Sluse03a} only report a redshift combining the broad and narrow lines, 
+% \ie it is unclear what's the velocity offset between MgII and [OIII]
+the lack of a redshift from solely the BLR of the AGN precludes us from interpreting this as the favoured
+explanation for the velocity offset.
+
+In fact, a large velocity offset can also result from a recoiling BH where its
+BLR is moving at high velocity relative to the bulk of the host galaxy and
+the ionized gas \citep{Madau04a, Bonning07a, Loeb07a}. % narrow AGN lines.
+Such a scenario may occur after galaxies and their BHs merge, during which 
+their orbital energy is being released as gravitational wave to overcome the last stable orbit.
+This results in a recoil in the merged BH for an uneven BH mass merger as a
+non-zero net angular momentum is also being carried away.
+Depending on their initial conditions, % mass ratios, spin, rotational direction, 
+numerical relativity simulation have shown that
+the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
+% The BH is displaced from the galactic nucleus in this scenario, and might 
+% return to the center in a few dynamical time-scales 
+% by dynamical friction or be kicked out of the gravitational potential of the host galaxy.
+This together with the fact that the BH in RXJ1131 has a high spin parameter \citep{Reis14a} 
+renders the recoiling BH scenario a viable option for the origin
+of the optical velocity offset.
+To reconcile this picture with the fact that a companion is still observed, 
+the system may be at its subsequent minor merger stages but was intially
+a major merger. 
+This would imply previous encounters between RXJ1131 and its companion, 
+which would also explain the spinning BH.
+
+It is worth noting that
+while these large velocity offsets are theoretically achievable,
+they are not commonly observed --- only a few objects have been reported with optical offsets $\gtrsim$1000\,\kms.  
 For instance,
-AGN in ongoing galaxy mergers are observed to have kinematics offsets in AGN relative to their host galaxies, SDSS sample at z $<$ 0.21, max offset 410 km/s, not accounted for projection effects in the observed velocities.
-elo offsets can be produced by rot. gas disks, AGN outflows, jets, gravi. recoil of SMBH (Comerford \& Greene, 2014, ApJ, 789, 112).
-
-which may be kinematic indication of a recoiling BH.
-There are a few reasons to this e.g. SB/AGN driven winds or AGN outflows, jets, gravitational recoil of BH in post-merger. % (Comerford & Greene, 2014, ApJ, 789, 112).
-Here we discuss the possibility of a GW recoiling merged BH.
-The recoiling is expected to happen after the merging because their orbital energy is emitted as GW to overcome the stable orbit for the binary,
-carrying away a non-zero angular momentum for uneven (i.e.
-not 1:1) BH mass mergers, which at the same time will cause a recoil in the merger BH.
-Depending on their initial mass ratios, spin, rotational direction, the recoil velocity can reach as high as $\sim$4000\,\kms for spinning BHs, suggested by numerical relativity simulations \citep[\eg][]{Campanelli+07a}
-The BH is displaced from the galactic nucleus in this scenario, and might return to the center in a few dynamical time-scales by dynamical friction or be kicked out of the gravitational potential of the host galaxy.
-In terms of RXJ1131,
-while we still see the gas-rich companion, it could be that they were initially major mergers that had encounter before (causing the high spinning BH), and we are currently witnessing the subsequent minor merger stages.
-
-Alternatively, it can be indication of the BH orbiting in the host galaxy.
-Since we cannot quantify this further without the separate redshifts based on the broad Mg II and the narrow OIII lines as Slues+03 only report the combined $z$.
-If we have that, it could be indication of an AGN orbiting the host galaxy (but only if the velocity offset between the BLR and the narrow line of the gas in the host is lower than its orbital velocity), or AGN outflow or SB driven wind as in the case of SMMJ1636+4057\citep{Swinbank05a}.
-
-offset from the galaxy core \citep{Madau04a},
-or in the form of broad emission lines kinematically
-offset from the narrow emission lines \citep{Bonning07a} (\ie carrying along its accretion disc and BLR). Thus offset from narrow lines can also be offset AGN than outflow gas.
-From Slues03 spectrum, doesn't appear to see a broad component and a narrow component or I should say their z is derived using both the broad MgII line and the narrow [OIII] lines, which means we can rule out an explanation due to the in/outflows due to radiation pressure or AGN winds.
-Also we don't see double-peaked in optical lines and are not skewed lines.
-
-% Other objects seen with such big velocity offset:
-It may be worth noting that while such big velocity offset is not commonly
-seen even in mergers, it has been reported in a few objects. For instance,
-the most promising candidate of GW recoiling with both spectroscopy and imaging
-signature:
-CID-42 at z=0.359 has a similar velocity offset ($\sim$1300\,\kms; between the narrow and broad component of H$\beta$) in two
-optical component separated by $\sim$ 2.5 kpc within the same galaxy \citep{Civano10a}, which has been proposed to
-be a good candidate for a recoiling BH.
-
-Also type-1 QSO, SDSS 0956+5127 at $z_{\rm sys}$$\sim$0.714 from narrow lines, and $z_{Mg II}$ at $z\sim$0.707, corresponding to 1200 \kms offset \citep{Steinhardt12a}.
-Other example:
-SDSSJ0927+2943 at $z$$\sim$0.713 shows an exceptional optical emission-line spectrum with two
-sets of emission lines: one set of very narrow emission lines, and a second set of broad Balmer and
-broad high-ionization forbidden lines which are blueshifted by 2650 \kms
-relative to the set of narrow emission lines \citep{Komossa08a}.
-This observation is most naturally explained if the SMBH was ejected from the core
-of the galaxy, carrying with it the broad-line gas while leaving behind the bulk of the narrow-line
-gas.
+the most promising candidate of a recoiling BH with both spectroscopy and imaging
+signatures is CID-42 at $z$\,=\,0.359, which has 
+a velocity offset of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ \citep{Civano10a}. 
+% which has a similar velocity offset
+% of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ 
+% in two optical component separated by $\sim$ 2.5 kpc within the same galaxy \citep{Civano10a}. 
+Other examples include 
+the type-1 QSO SDSS 0956+5127 at $z$\,$\sim$\,0.714, with an offset of 1200\,\kms
+between Mg{\scriptsize II}~2798\AA\ and $[$O{\scriptsize III}$]$~4959, 5007\AA\ lines 
+\citep{Steinhardt12a}, 
+and
+SDSSJ0927+2943 at $z$\,$\sim$\,0.713, with an offset of 2650\,\kms \citep{Komossa08a}.
+% shows an exceptional optical emission-line spectrum with two
+% sets of emission lines: one set of very narrow emission lines, and a second set of broad Balmer and
+% broad high-ionization forbidden lines which are blueshifted by 2650 \kms
+% relative to the set of narrow emission lines \citep{Komossa08a}.
+
 %==============================================================================

### 2016-06-28 WRITEUP/ms.tex
done merger stage

@@
 This is consistent with the picture that old stars form first and constitute the bulge component
-of a spiral galaxy and that nuclear starbursts (in the inner few kpc) are triggered in mergers.
+of a spiral galaxy and that nuclear starbursts (in the inner few kpc) can be triggered latter in mergers.
 
@@
 Hence,
-we can derive an upper limit on the gas mass for RXJ1131 using the standard conversion factor.
-If we have instead applied the Galactic value of 4.6\,\alphaU, 
-the gas mass (and thus the SFE) would be higher by a factor of $\sim$6. 
+we can derive an upper limit on the gas mass for RXJ1131 
+using the Galactic value of 4.6\,\alphaU. This yields
+a gas mass (and thus a SFE) that is $\sim$6 times higher.  
 In contrast to results in the classical study of nearby ULIRGs by \citetalias{Downes98a}, who find that
@@
 \section{Discussion} \label{sec:diss}
-\subsection{Velocity Offset and Recoiling BH}
+\subsection{Velocity Offset and a Recoiling Black Hole}
 Using the redshift deduced from the CO line 
@@
 
-In fact, a large velocity offset can also result from a recoiling BH where its
+In fact, a large velocity offset can also result from a recoiling black hole (BH) where its
 BLR is moving at high velocity relative to the bulk of the host galaxy and
@@
 Depending on their initial conditions, % mass ratios, spin, rotational direction, 
-numerical relativity simulation have shown that
+numerical relativity simulations have shown that
 the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
@@
 To reconcile this picture with the fact that a companion is still observed, 
-the system may be at its subsequent minor merger stages but was intially
+the system may be in its subsequent stages of (minor) merging but was initially
 a major merger. 
@@
 
+\subsection{Merger stage RXJ1131-1231}
+%It is clear that the signature of a galaxy merger changes as the merging progresses.
+%For instance, extended molecular disks are often associated with advanced mergers 
+%\citep[\citetalias{Downes98a};][]{Gao99a}.but see also U14 for outliers
+% with extended molecular gas in merger remnants
+
+The (gas) mass ratio, the intrinsic CO line profile,  
+% since the bulk of the angular momentum can be retained only in minor mergers if small separation
+and the source-plane velocity field are all evident of 
+a minor merger, in good agreement with an 
+earlier study by \citetalias{Brewer08a} who
+independently conclude the presence of a dwarf companion 
+of size $\sim$700\,kpc across. Since minor mergers may in some cases
+result from previous passage of major mergers, it is possible that RXJ1131
+has encountered with the progenitor galaxy of the companion and is undergoing 
+the subsequent series of minor merging.
+One piece of evidence comes from % that they have encountered
+the compact UV emission, which can be starburst resulting from gas accumulation 
+owing to a non-axisymmetric perturbation from the companion.
+% the stellar component torques away the angular momentum, allowing the gas to fall inward.
+The highly spinning black hole in RXJ1131 is also consistent with 
+this hypothesis. 
+If we favor the gravitational wave recoil mechanism 
+to explain the optical velocity offset, it would also imply the black 
+holes (and their host galaxies) have merged or are at their final coalescence. 
+In addition, the source-plane CO position of the companion appears to be consistent with 
+a picture where its molecular gas is mixed with RXJ1131 (but with large uncertainties). 
+%\ie companion CO location along/within the RXJ1131 CO disc
+% as well as one where its emission is co-spatial with the stellar light. 
+The IR luminosity also agrees with 
+the results from previous studies: AGNs are
+typically found in late stage mergers 
+\citep{Yuan10a,Iwasawa11a,Carpineti12a} and
+only major mergers near their final
+coalescence can provide \LIR$>$\,10$^{12}$\,\Lsun,
+\citep[\eg][]{Carpineti15a,Larson16a}.
+
+It may be puzzling as to why the stellar emission in the companion 
+is spatially offset from RXJ1131 while its CO gas appears to be mixed-in if they 
+have encountered.
+This phenomenon is in fact not unique to our source. 
+The gas cores of the individual 
+% merging galaxies 
+mergers NGC~6090 and NGC~6240 are also observed
+to be coalescing  
+% is in the process of or has already coalesced into a single component
+while their stellar cores remain % distinct
+separated \citep[0.5$-$3\,kpc;][]{Bryant99a}. 
+Although this is difficult to reconcile with the fact that the stellar light in the companion 
+originates from recent \SF (UV emission). 
+More sensitive and higher resolution observations will be needed
+to confirm any offsets between the CO gas and the stellar light in the companion.
+% allow for a more detailed lens modeling to trace the gas distribution and morphology in the system
+Another puzzle may be the absence of morphological features.
+% tidal tails if they have already encountered.
+One straightforward explanation may simply be the lack of spatial resolution.
+Alternatively, it may be a result of the offset in timing between observable
+morphological disturbances and the merger-induced starbursts \citep{Lotz08a}.
+% with strong morphological disturbances occurring before bursts of merger-induced star formation and for shorter durations
+
+\subsection{Fate of RXJ1131}
+A classical picture of mergers is that they are responsible for the formation of local spheroids.
+The growing consensus that more realistic
+treatments of star formation and supernovae feedback ? which suppress
+efficient early star formation ? play a critical role in enabling
+disc formation in simulations.
+Mergers are expected to evolve into
+local ellipticals or large-disks (bulge dominated; Springel05a, Robertson06a)
+and disc with low B/D ratio (Hopkins09a) from simulations.
+Reason for suppression of bulge formation in mergers of gas-rich discs (even in major merger):
+ because in systems that are sufficiently gas-rich, there's little/no significant (collisionless) stellar material available to torque away the cold gas in the disc; little/no angular momentum is lost, and gas will rapidly reform a cold disc in the background of the relaxing stellar potential (collisionless):
+Gas, being collisional, cannot violently relax, but must
+have its angular momentum torqued away in order to dissipate and
+build a bulge by forming stars in a central starburst (\ie gas lose angular momnentum to stars in the perturbed disk and fall toward center). In a merger,
+this torque is primarily internal, from stars in the same disc: the
+passages and merger of the secondary induce a non-axisymmetric
+distortion in the primary stellar and gas disc. The stellar distortion
+(in a trailing resonance and close proximity to the gas response)
+efficiently removes angular momentum from the gas and allows it
+to fall to the center and form a bulge (see also Barnes \& Hernquist
+1996; cold gas with no angular momentum will be largely unable to form any sort of disk, and that a galaxy?s worth of gas compressed to high densities and small radii will inevitably form a large mass in stars).
+But it no significant stellar feature is there (e.g.
+in the more gas-rich ones (Hopkins09a), the final product will have a bulge mass fraction $\sim$0.1$-$0.2).
+i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large)
+
+% fate
+But since the two galaxies are found to be gas-rich, can dissipates energy
+through e.g. frictional forces and drive gas toward the center, leading to
+higher rotational velocity and dispersion in the central region.
+In that case,
+it is unlikely that RXJ1131 will evolve into present-day massive ellipticals (M$\gtrsim$1\E{12}\,\Msun), since RXJ1131 is now a minor merger.
+Instead, it is likely to evolve into ``normal'' ellipticals (depending on the feedback, since a major gas-rich merger without AGN feedback does not, by itself, produce a red and dead spheroidal galaxy (Lotz08a).) or massive disk galaxies where the stellar populations from the companion is dragged and added onto the dominant galaxy RXJ1131 to thicken the disc, consistent with recent models (disk from gas-rich major merger:
+\citep[\eg][]{Lotz08a, Robertson06a}.
+
+% evolve into disk
+Given the
+massive gas content distributed in an extended configuration/disc with its SFE on the low end of other ULIRGs, we suggest RXJ1131 may evolve into the
+latter (large-disk) unless the ``companion'' somehow triggers some other
+mechanisms in the latter stage, transporting the gas 
+toward the central nuclear region and to simulate a final burst to form a large bulge or somehow destroy the
+disc in RXJ1131.
+
 %==============================================================================
@@
 %==============================================================================
-
 % ACKNOWLEDGEMENTS

### 2016-06-28 WRITEUP/ms.tex
finished discussion

@@
 in the context of theoretical simulations by \citet{Hopkins09a}, who suggest 
-that the disc component in a progenitor galaxy can survive post-merging
-by lowering the \SF efficiency, enabling a higher gas fraction to be retained and 
+that the disc component in a gas-rich progenitor galaxy can survive post-merging
+by lowering the \SF efficiency (and thus less efficient at removing the angular momentum of
+the gas), thereby enabling a higher gas fraction to be retained and 
 distributed over a larger extent.
+%since there is little/no significant stellar material % (collisionless)
+%available to torque away the cold gas in the disc, thus little/no angular momentum is lost, 
+%and gas will rapidly reform a cold disc in the background 
+%of the relaxing stellar potential.
+% --> suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
+% the final product will have a low bulge mass fraction.
+%
+%i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large).
 % 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
@@
 % is in the process of or has already coalesced into a single component
-while their stellar cores remain % distinct
+while their stellar cores remain
 separated \citep[0.5$-$3\,kpc;][]{Bryant99a}. 
@@
 Another puzzle may be the absence of morphological features.
-% tidal tails if they have already encountered.
 One straightforward explanation may simply be the lack of spatial resolution.
@@
 \subsection{Fate of RXJ1131}
-A classical picture of mergers is that they are responsible for the formation of local spheroids.
-The growing consensus that more realistic
-treatments of star formation and supernovae feedback ? which suppress
-efficient early star formation ? play a critical role in enabling
-disc formation in simulations.
-Mergers are expected to evolve into
-local ellipticals or large-disks (bulge dominated; Springel05a, Robertson06a)
-and disc with low B/D ratio (Hopkins09a) from simulations.
-Reason for suppression of bulge formation in mergers of gas-rich discs (even in major merger):
- because in systems that are sufficiently gas-rich, there's little/no significant (collisionless) stellar material available to torque away the cold gas in the disc; little/no angular momentum is lost, and gas will rapidly reform a cold disc in the background of the relaxing stellar potential (collisionless):
-Gas, being collisional, cannot violently relax, but must
-have its angular momentum torqued away in order to dissipate and
-build a bulge by forming stars in a central starburst (\ie gas lose angular momnentum to stars in the perturbed disk and fall toward center). In a merger,
-this torque is primarily internal, from stars in the same disc: the
-passages and merger of the secondary induce a non-axisymmetric
-distortion in the primary stellar and gas disc. The stellar distortion
-(in a trailing resonance and close proximity to the gas response)
-efficiently removes angular momentum from the gas and allows it
-to fall to the center and form a bulge (see also Barnes \& Hernquist
-1996; cold gas with no angular momentum will be largely unable to form any sort of disk, and that a galaxy?s worth of gas compressed to high densities and small radii will inevitably form a large mass in stars).
-But it no significant stellar feature is there (e.g.
-in the more gas-rich ones (Hopkins09a), the final product will have a bulge mass fraction $\sim$0.1$-$0.2).
-i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large)
-
-% fate
-But since the two galaxies are found to be gas-rich, can dissipates energy
-through e.g. frictional forces and drive gas toward the center, leading to
-higher rotational velocity and dispersion in the central region.
-In that case,
-it is unlikely that RXJ1131 will evolve into present-day massive ellipticals (M$\gtrsim$1\E{12}\,\Msun), since RXJ1131 is now a minor merger.
-Instead, it is likely to evolve into ``normal'' ellipticals (depending on the feedback, since a major gas-rich merger without AGN feedback does not, by itself, produce a red and dead spheroidal galaxy (Lotz08a).) or massive disk galaxies where the stellar populations from the companion is dragged and added onto the dominant galaxy RXJ1131 to thicken the disc, consistent with recent models (disk from gas-rich major merger:
-\citep[\eg][]{Lotz08a, Robertson06a}.
-
-% evolve into disk
-Given the
-massive gas content distributed in an extended configuration/disc with its SFE on the low end of other ULIRGs, we suggest RXJ1131 may evolve into the
-latter (large-disk) unless the ``companion'' somehow triggers some other
-mechanisms in the latter stage, transporting the gas 
-toward the central nuclear region and to simulate a final burst to form a large bulge or somehow destroy the
-disc in RXJ1131.
+The classical picture for mergers is one where they are responsible for the formation of the local 
+red and passive spheroidal galaxies.
+With more realistic treatments of star formation and feedbacks in recent simulations,
+% ? which suppress efficient early star formation ? play a critical role in enabling disc formation in simulations.
+it has been suggested that it is possible  to suppress bulge formation 
+in gas-rich mergers, thereby evolving into large 
+disks \citep{Springel05a, Robertson06a, Hopkins09a}.
+% (bulge dominated; Springel05a, Robertson06a)
+% and disc with low B/D ratio ($\sim$0.1$-$0.2; Hopkins09a).
+%
+%In systems that are sufficiently gas-rich, it is possible to 
+%suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
+%since there is little/no significant stellar material % (collisionless)
+%available to torque away the cold gas in the disc, thus little/no angular momentum is lost, 
+%and gas will rapidly reform a cold disc in the background 
+%of the relaxing stellar potential.
+%Gas, being collisional, cannot violently relax, but must
+%have its angular momentum torqued away in order to dissipate and
+%build a bulge by forming stars in a central starburst 
+%(\ie gas loses angular momentum to stars in the
+%perturbed disk and fall toward center).
+% In a merger,
+%this torque is primarily internal, from stars in the same disc: the
+%passages and merger of the secondary induce a non-axisymmetric
+%distortion in the primary stellar and gas disc. The stellar distortion
+%(in a trailing resonance and close proximity to the gas response)
+%efficiently removes angular momentum from the gas and allows it
+%to fall to the center and form a bulge  (see also Barnes \& Hernquist
+% 1996).
+% A bulge will form because cold gas with no angular momentum 
+% will be largely unable to form any sort of disk, and that a galaxy?s 
+% worth of gas compressed to high densities and small
+% radii will inevitably form a large mass in stars). 
+%
+Since both RXJ1131 and its companion are gas-rich
+% unlikely RXJ1131 will evolve into present-day massive 
+% ellipticals (M$\gtrsim$1\E{12}\,\Msun), 
+% gas-poor mergers: --> present-day massive elliticals
+% (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
+and that the bulk of the angular momentum of the gas is  
+retained in minor mergers,
+it is likely that RXJ1131 will evolve into either a 
+``normal'' elliptical/S0 galaxy or a large disk galaxy.  
+% normal E only because gE needs ways to remove angular momentum efficiently for gas to funnel
+In the latter, the stellar populations from the companion will be displaced onto the 
+dominant galaxy to thicken the disk \citep[\eg][]{Lotz08a, Robertson06a}.
+% disk from gas-rich major merger: \citep[\eg][]{Lotz08a, Robertson06a}.
+Given that the molecular gas in 
+RXJ1131 is distributed in an extended disk configuration and that its 
+SFE is on the low end among other ULIRGs,  % not enough stellar material to efficiently remove ang. mom.
+it is more conceivable that RXJ1131 will evolve into the
+latter.
+% Lotz08a: a major gas-rich merger without AGN feedback does not, by itself, produce a red and dead spheroidal galaxy
+Other mechanisms e.g. formation of bar-like structures will be needed to remove the
+angular momentum of the gas more efficiently to transform the gas disc into a stellar spheroid and
+AGN feedbacks are also necessary to halt further activities for RXJ1131 to evolve into an 
+E/S0 galaxy \citep{Lotz08a}.
 

### 2016-06-28 WRITEUP/ms.tex
send to DR

@@
 is also reported based on X-ray observations \citep{Reis14a}.
+\defcitealias{Sluse03a}{S03}
 
@@
 is not equivalent to maximum observed velocity ($V_{\rm max}$),
-which is commonly used in literature to parameterize disc rotation.
+which is commonly used in literature to parameterize disk rotation.
 The arctangent model is most commonly used in studies of the
 Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
-at 2.2 disc scale-length or $\sim$1.375 half-light radius,
+at 2.2 disk scale-length or $\sim$1.375 half-light radius,
 or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
@@
 This implies that the gas fraction in ULIRGs at $z$\,$<$\,1 is
-similar to those in high-$z$ ``normal'' star-forming disc galaxies
+similar to those in high-$z$ ``normal'' star-forming disk galaxies
 \citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a} as well as
@@
 Alternatively, the relatively low SFE maybe intrinsic to RXJ1131.
-In that case,  RXJ1131 may evolve into a disc galaxy with a small bulge component
+In that case,  RXJ1131 may evolve into a disk galaxy with a small bulge component
 in the context of theoretical simulations by \citet{Hopkins09a}, who suggest 
-that the disc component in a gas-rich progenitor galaxy can survive post-merging
+that the disk component in a gas-rich progenitor galaxy can survive post-merging
 by lowering the \SF efficiency (and thus less efficient at removing the angular momentum of
@@
 the broad Mg{\scriptsize II}~2798\AA\ and the narrow 
-$[$O{\scriptsize III}$]$~4959, 5007\AA\ lines \citep[$z_{\rm AGN} = 0.658$;][]{Sluse03a}.
+$[$O{\scriptsize III}$]$~4959, 5007\AA\ lines \citepalias[$z_{\rm AGN} = 0.658$;][]{Sluse03a}.
 This indicates that the broad line region (BLR) of the AGN is at a
@@
 %(\ie carrying along its accretion disc and BLR)
-Since \citet{Sluse03a} only report a redshift combining the broad and narrow lines, 
+Since \citetalias{Sluse03a} only report a redshift combining the broad and narrow lines, 
 % \ie it is unclear what's the velocity offset between MgII and [OIII]
@@
 Other mechanisms e.g. formation of bar-like structures will be needed to remove the
-angular momentum of the gas more efficiently to transform the gas disc into a stellar spheroid and
+angular momentum of the gas more efficiently to transform the gas disk into a stellar spheroid and
 AGN feedbacks are also necessary to halt further activities for RXJ1131 to evolve into an 
 E/S0 galaxy \citep{Lotz08a}.
+
+%--------------------------------------------------------------------------
+%                                Conclusions
+%--------------------------------------------------------------------------
+\section{Summary and Conclusions} \label{sec:sum}
+% see Hodge12_dynamics.pdf for guide
+
+%- summarize the findings from the entire study
+%    - firm conclusions
+%    - speculative possibilities
+We present the CO data obtained with the VLA and PdBI toward the 
+quadruply-lensed optical quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65.
+We investigate the cold gas kinematics and dynamics in RXJ1131
+by observing its \bco and \cco line emission, which are the
+two lowest rotational transitions of CO observable with current instruments.
+
+Our results confirm the presence of a gas-rich companion, consistent with previous studies.
+
+We find that RXJ1131 is likely a massive disturbed gas-rich disk galaxy with extreme IR
+luminosity, in the process of merging 
+we conclude that RXJ1131 is s a wet-wet minor merger 
+between a ULIRG and an optically faint companion.
+
+% % any further work needed to resolve the remaining problems
+The intrinsically symmetric double-horned line profile, the smooth and 
+symmetric velocity field/gradient seen in both the source plane from our lens model as well 
+as in the image plane, and C06 model $n$=1 Sersic profile all suggest
+a kinematically-order rotating disk galaxy.
+Additional
+characteristics such as peak velocity dispersion at the central region and a
+``spider'' diagram are needed to confirm the disk morphology.
+
+The high dispersion near the dynamical center also
+suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. Overall
+implies RXJ1131 is a minor merger of a turbulent disc, but higher-resolution
+data are needed to confirm this.
+
+% Gas fraction and SFH
+While there is an emerging consensus on
+the correlation between molecular gas content and redshift,
+suggesting it as the explanation for the elevated SFR at high redshift/
+the observed trend in the cosmic SFH,
+we find that the gas fraction in RXJ1131 is consistent with both ULIRGs at
+ 0.2\,$<$\,$z$\,$<$\,0.4
+and 0.6\,$<$\,$z$\,$<$\,1.0. Thus, we find no evidence of 
+evolution in gas fraction.
+
+The compactness of the emission in $V$-band (rest-frame UV)
+suggests that the \SF in RXJ1131 is proceeding in a
+compact region embedded within a large reservoir of molecular gas, 
+which may be explained by gas inflow toward nuclear regions due to
+perturbations in the disk from the companion.
+Such a scenario may support the results in recent models: mergers/ULIRGs evolve into massive disks.
+
+% consistent with the picture that BLAH, while it is also possible that BLAH.
+%Our results indicate a self-consistent picture of ...
+followed by gravitationally instability and SF in a massive, gas-rich disk and a subsequent build-up of a central bulge through inflow triggered by disk installbilities and/or minor merger.
+
+%Elliptical/S0 galaxies
+%S0:  exhibit a bulge and disk similar to spiral galaxies, but do not show any signs of spiral arms or significant quantities of interstellar material.
+They consist primarily of old, population II stars and for this reason, are often misclassified as elliptical galaxies when viewed face-on.
+%The origins of S0 galaxies are still unknown, but one idea is that they were originally spiral galaxies which either lost or used up their interstellar medium through interactions with another galaxy.
 

### 2016-06-29 WRITEUP/ms.tex
minor typos

@@
 galaxy is an elliptical galaxy at $z_\textrm{L}$\,$=$\,0.295. The redshifts
-are spectroscopically confirmed by \citet{Sluse03a}.
+are spectroscopically confirmed by \citet[hereafter S03]{Sluse03a}.
 A black hole mass estimate of M$_{\rm BH}$\,$<$\,2\E{8}\Msun
@@
 is best-reproduced using a $n$\,=\,1 Sersic profile.
-We thus interpret RXJ1131 to be a disk galaxy.
+We thus interpret RXJ1131 as a disk galaxy.
 
@@
 Such FWHM is also commonly observed in high-$z$ starburst galaxies
-\citep[780\pmm320\,\kms; \eg][]{Greve05a}.
+\citep[780\pmm320\,\kms; \eg][hereafter G05]{Greve05a}.
 \defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}\defcitealias{SV05a}{SV05}
@@
 distributed over larger spatial extents
-\citepalias[\eg][]{SV05a,Riechers11a,Ivison11a}.
+\citep[\eg \citetalias{SV05a};][]{Riechers11a,Ivison11a}.
 % gas-to-dyn ratio
@@
 \citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}.
-\defcitealias{Daddi10a}{D10}
 
@@
 the mass opacity coefficient $\kappa$,
-the \alphaco conversion factor, and the brightness temperature ratio $R_{\rm 21}$.
+the \alphaco conversion factor, and the brightness temperature ratio $r_{\rm 21}$.
 The fact that RXJ1131 has a lower dust-to-gas ratio
@@
 % \citep[$\sim$180\pmm160 \Lsun $M_{\odot}^{-1}$;][]{Solomon97a, Combes11a}
-\citep{Solomon97a, Combes11a}
+\citep[\citetalias{Solomon97a};][]{Combes11a}
 but
@@
 has been reported in ULIRGs and SMGs at 0.6\,$<$\,$z$\,$<$\,3
-\citep[][\citetalias{Riechers11a,Combes13a}]{Tacconi08a}.
+\citep[][\citetalias{Combes13a}]{Tacconi08a, Riechers11a}.
 \defcitealias{Tacconi08a}{T08}
@@
 
-\subsection{Fate of RXJ1131}
+\subsection{Fate of RXJ1131-1231}
 The classical picture for mergers is one where they are responsible for the formation of the local

### 2016-07-01 src/SED/SEDplot.py
bigger font

@@ -2,10 +2,12 @@
 
 Plot SED with MIPS extrapolation to 24 um and MBB_EMCEE fit
 
-Last Modified: June 22 2016
+Last Modified: June 30 2016
 
 History
 -------
+June 30 2016:
+    - bigger font
 June 22 2016:
     - change zorder on mbb fits
     - change savefig() save as .pdf instead of .eps to conserve alpha setting in saved figure
@@ -314,7 +316,7 @@ def savefigure(figure, f, verbose=True, dirStr='../../Figures/'):
 
 font = {'family': 'Arial Narrow',
         'weight': 'bold',
-        'size': 15}
+        'size': 18}
 matplotlib.rc('font', **font)
 matplotlib.rc('text', usetex=True)
 
@@ -368,7 +370,7 @@ ax.set_xscale("log")
 ax.set_ylabel(r'$\rm S_{\nu}$ [mJy]', fontsize=16)
 ax.set_xlabel(r'$\lambda_{\rm obs}\ [\mu$m]', fontsize=16, fontweight='bold')
 
-led = plt.legend(loc='best', fontsize=13, numpoints=1,
+led = plt.legend(loc='best', fontsize=15, numpoints=1,
                  fancybox=True, borderpad=0.85,
                  handlelength=1.5, labelspacing=0.3)
 ax.tick_params(length=14, pad=5)

### 2016-07-04 WRITEUP/ms.tex
updated with DR's comments and also shortened discussion on the merger stage, etc

--- 2016-06-28 WRITEUP/ms.tex
@@
 
-\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654}
+\title{Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131-1231 at $z$=0.654}
 \author{T. K. Daisy Leung and Dominik A. Riechers}
@@
 
-%==============================================================================
+%=============================================================================
 %                                Front matters
@@
 \begin{abstract}
-We \bco observations with the \pdbi.
+We report interferometric observations of \bco and \cco emission toward the gravitationally lensed 
+quasar RXS J1131-1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
+This is the first resolved \bco imaging at intermediate redshift.
+RXS J1131-1231 ?. 
 evidence for differential lensing.
@@
 the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
-% Our results support the hypothesis.
+is indicative of, and suggests...
+% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
+% MBH-sigma relation...
 \end{abstract}
@@
 \section{Introduction}
-
-In this paper, we explore the ISM properties of the quadruply imaged
+Despite the recent progress in theoretical models and observational studies...on understanding the evolution of massive galaxies.
+% interplay between / role of Complex baryonic physics such as mergers, gas dissipation, and feedback..
+It is not known when and how the main baryonic components of modern galaxies formed/assembled, but the global 
+stellar mass density rose substantially between z\ssim1$-$3, reaching $\sim$50\% of its present value by z\ssim1 
+(\ie how high-z galaxies evolve into present-day galaxies.)
+As such, studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 is important to unravel/understand the cause for the rapid decline in star formation and BH accretion rates (e.g.
+Madau et al.
+1998, Hopkins \& Beacom 2006).
+Studies of galaxy evolution find SFRD and BHAH peak at
+$z$\ssim2 and declines rapidly toward $z$$=$0. A leading explanation for such
+a trend is the evolution of molecular gas content and SFE in galaxies (CW13).
+While we know blah at the local universe and studies of the gas properties at
+high-z are also emerging in recent years (see CW13 for a review). It is still
+unclear what mechanism is responsible for removing cold gas from galaxies and
+shutting down their star formation to build-up present-day red sequence
+galaxies, leading to a change of slope at high \mstar (esp. at $z$ $<$ 1.5),  i.e.
+suppression of SFR at high \mstar, i.e. strong evolution in sSFR (of massive gal.)
+(cite: Papovich, Whitaker+12, Magnelli+14, Schreiber+15, Lee+15).
+It has been proposed that the high SFR at high-$z$ is due to the higher gas fraction than local (Erb et al. 2006), 
+regardless of their position in the SFR$-$M$^*$ plane, both MS and SB at high z have depletion time that is much 
+short than local, suggesting more efficient mode for SF. 
+Up to now, very little is known about the molecular gas content at moderate z.
+The ULIRG sample of Solomon97 contains 37 objects, but only 2 at are z $>$ 0.2.
+With the advance in mm-instruments, Combes11a investigate the variation of molecular gas and SFE in an expanded sample of 30 ULIRGs with CO observations.
+
+%why AGN host 
+In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, 
+where distant QSOs are the progenitors of the passive SMBHs in nearby galaxies.
+Locally, the connection between AGNs and their host galaxies is described 
+through the well-established tight correlation between BH mass 
+and stellar velocity dispersion (CITE), implying growth of the SMBH and their host galaxies is co-eval.
+However, it is unclear if this relation holds/or how the co-evolution BLAH at high-$z$.
+Recently, theoretical and observational studies of the co-evolution of SMBHs and their host galaxies
+have been attempting to extend this relation out to higher-$z$, beyond the peak epoch 
+of \SF and AGN activity (CITE).
+
+% difference proxy to the relation
+Since it is not trivial to obtain measurement of stellar dispersion (rely on spatially resolved stellar kinematics) at high-$z$, 
+efforts in calibrating and understanding how 
+the use of dynamical mass or stellar bulge mass \citep[\eg][]{Peng06a} or 
+stellar luminosity as a proxy for stellar dispersion.
+At high-$z$, more CO measurements have been obtained at high-z, and
+one can obtain dynamical mass through CO linewidth and spatial extent.
+
+Based on the \mbh$-$\mdyn relation, there are considerable evidence now that high-z BHs grow faster than their host galaxies.
+The dynamical mass inferred from CO velocity structure (line width) and spatial extent is lower than that 
+based on local relation. 
+Current results imply high-$z$ galaxies ($z$$>$BLAH) do not follow this relation, where their observed $M_\textrm{dyn}$ is lower than that inferred from
+this relation or \mbh$/$$M_{*}$ is smaller high-$z$ than today \citep{Borys05a}. 
+This implies that a quasar phase is needed in order for high-z galaxies to evolve 
+onto the local \mbh$-$$M_{\rm bulge}$ relation / high-$z$ BH grow faster than their host galaxies, 
+as predicted in simulations where feedback is needed in order to explain the 
+anti-hierarchical growth of galaxies / suppress efficient early star formation
+and the lack of more massive galaxies as would be produced without feedback. 
+But how investigate this evolution at intermediate redshift is challenging,
+because it also suffers the same cosmological dimming issue at high-$z$ studies, time-consuming to obtain
+resolved CO observations for intermediate-z.
+
+One way to understand is to investigate the relation as different epochs more closely.
+We still lack a clear picture of relationship between AGN and hosts since we do not know much at the intermediate redshifts where both \SF and AGN accretion slow down.
+It appears that there may be a decreasing trend from $z$$>$3 to 1$<$3 and compared to the local fit.
+But it is clear that there is a desert in between these redshift range.
+
+Host galaxies of AGN are difficult to study because the quasar usually dominates the observed light, and ?.
+With gravitational lensing, the stellar emission and quasar emission in RXJ1131 
+are magnified and stretched out at different locations to different extents in the image plane, gaining 
+the surface brightness contrast to enable measurements of their emission separately.
+RXJ1131 thus provide a unique laboratory to study the ?
+
+%--------
+In this paper, we explore the well-established local BLAH relations to intermediate redshift
+and investigate the postulated decrease gas fraction from BLAH studies at intermediate 
+redshift.
+We use BLAH to study the ISM properties of the quadruply imaged
 quasar RXS J113151.62-123158 (hereafter RXJ1131) at
-$z_\textrm{AGN}$\,$=$\,0.685, with an Einstein ring of size
-1\farcs83 in radius. The foreground lensing
-galaxy is an elliptical galaxy at $z_\textrm{L}$\,$=$\,0.295. The redshifts
-are spectroscopically confirmed by \citet{Sluse03a}.
-A black hole mass estimate of M$_{\rm BH}$\,$<$\,2\E{8}\Msun
-is also reported based on X-ray observations \citep{Reis14a}.
+$z_\textrm{s, QSO}$\eq0.685, lensed by an
+elliptical galaxy at $z_\textrm{L}$\eq0.295. The redshifts 
+are spectroscopically confirmed by \citet[hereafter S03]{Sluse03a}.
+Emission in the host galaxy of RXJ1131 is lensed into an Einstein ring of size 1\farcs83 in radius.
+The black hole of mass \mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
+mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
+\mbh\ssim10$^{8}$\,\Msun using the virial estimator with H$\beta$ linewidth,
+and \citet{Pooley07a} report $M_{\rm BH}$\,=\,2.5\E{7}\,\Msun using the
+AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
+assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}
+residing in RXJ1131 has been observed to 
+be rotating with a high spin parameter
+\citep[$a$\,$\sim$\,0.9;][]{Reis14a}.
+\defcitealias{Sluse03a}{S03}
 
@@
 In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths.
-In \Sec{anal}, we represent our dynamical lens modeling on the \bco data and the physical properties inferred for  RXJ1131.
-In \Sec{diss}, we discuss the results and implications of this study in the context of molecular gas evolution in mergers and massive galaxies.
+In \Sec{anal}, we present dynamical lens modeling of the \bco data and the physical properties inferred for  RXJ1131.
+In \Sec{diss}, we discuss the results and implications of this study in the context of molecular gas in mergers and ULIRGs {\bf BLAH}.
 Finally, we summarize the main results of this study and present our conclusions in \Sec{sum}.
@@
 \section{Observations} \label{sec:obs}
-\subsection{PdBI \bco} % DONE
+\subsection{PdBI \bco}
 Observations of the \bco rotational line
-($\nu_{\rm rest}$\,=\,230.5379938 GHz; $\nu_{\rm obs}$\,=\,139.4\,GHz)
-toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658
-were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
+($\nu_{\rm rest}$\,=\,230.5379938 GHz) redshifted to $\nu_{\rm obs}$\,=\,139.0\,GHz
+were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
 Riechers). Two observing runs were carried out on 2014 December 06 and 2015
@@
 and the underlying continuum emission, employing a correlator setup providing
-an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
+an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 10.0 MHz ($\sim$
 21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
  time after discarding unusable visibility data.
-The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
-for pointing, secondary amplitude, and phase calibration, and 1055$+$018 was
+The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
+for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
 observed as the bandpass calibrator for both tracks.
@@
 
-The \ncode{gildas} package was used to reduce and analyze the visibility data
-which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
+The \ncode{gildas} package was used to reduce and analyze the visibility data.
+The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
 weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
-The final rms noise is $\sigma$\,=\,1.45\,mJy\,\kms
-beam\pmOne over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
-is created by averaging over all the 3.16\,GHz line-free channels. This
+The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
+over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
+is created by averaging over 3.16\,GHz of line-free bandwidth. This
 yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
 
-\subsection{CARMA \cco} %DONE
+\subsection{CARMA \cco}
 Observations of the \cco rotational line in RXJ1131
-($\nu_{\rm rest}$\,=\,345.7959899\,GHz; $\nu_{\rm rest}$\,=\,209.1\,GHz)
+($\nu_{\rm rest}$\,=\,345.7959899\,GHz) redshifted to $\nu_{\rm obs}$\,=\,208.6\,GHz
 were carried out with the \carma (CARMA;
@@
 the second track was far from our target source, the phase calibration is
-subpar, with an rms scatter $\sim$60\degr over $\sim$135\,m.
+subpar, with an rms scatter $\sim$60$\degr$ over a baseline length of $\sim$135\,m.
 %BLAH... more like 50%
@@
 the gain variations over time, and the phase scatter on the calibrated data. We
-therefore treat its line intensity with caution and ensure that any physical interpretation
+therefore treat its line intensity with caution and ensure that our physical interpretation
 of this system does not rely on this quantity.
 
-The \ncode{miriad} package was used to calibrate the visibility data which are
-then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
+The \ncode{miriad} package was used to calibrate the visibility data.
+The calibrated visibility data were
+imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
 beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
-image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
+image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
 over a channel width of 25\,MHz. An rms noise of
@@
 Observations were carried out on 2008 December 29 under excellent weather
-conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
-providing a bandwidth of 50 MHz in each sideband.
-The nearby radio quasar 1130$-$149 was observed every 10 minutes for
-pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
-primary flux calibrator, and 0319$+$415 was observed as the bandpass
+conditions in the A array configuration for a total of $\sim$7 hours on-source time. The C-band receivers were used with a continuum mode setup,
+providing a bandwidth of 50 MHz for the two IF bands with full polarization.
+The nearby radio quasar J1130$-$149 was observed every 10 minutes for
+pointing, amplitude, and phase calibration, J1331$+$305 was observed as the
+primary flux calibrator, and J0319$+$415 was observed as the bandpass
 calibrator, yielding $\sim$10\% calibration accuracy.
-We use \ncode{aips} to calibrate the visibility data which
-are then imaged and deconvolved using
+We used \ncode{aips} to calibrate the visibility data.
+The calibrated visibility data were imaged and deconvolved using
 the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
-beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
+beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
 rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.
@@
 \section{HST astrometry} \label{sec:HST}
-We obtained an {\it HST} image taken with the F555W filter ($V$-band)
-using the ACS/Wide Field Camera from the
+We obtained an {\it HST} image taken with
+the ACS/Wide Field Camera 
+using the F555W filter ($V$-band)
+from the
 Hubble Legacy Archive\footnote{Based on observations
@@
 Institute (STScI/NASA), the Space Telescope European Coordinating Facility
-(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}
-with a goal to understand the origin of the emission detected
-in our mm observations. The details of the observations can be found
+(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}. 
+The details of the observations can be found
 in \citet[hereafter C06]{Claeskens06a}.
-We adopt the VLA 5\,GHz map of
-$\sim$0\farcs5 resolution as the
+We adopt the VLA 5\,GHz map as the
 reference coordinate frame to align the optical ($V$-band) image.
@@
 interferometric images reported in this paper are expected to have an astrometric
-precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
-instabiliy, and beam size.
+precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
+instability.
 \defcitealias{Claeskens06a}{C06}
@@
 \subsection{\bco Emission} \label{sec:CO21} %DONE
-We detected the \bco line emission toward the background galaxies
+We detect \bco line emission toward the background source
 at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
@@
 flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
-179\pmm9 \kms and 255\pmm28 \kms, respectively. The peaks are separated by
+179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
 $\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/
@@
 \caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
-is with respect to $z$=0.6537, which is approximately the line center
+is with respect to $z$\,=\,0.6537, which is approximately the line center
 considering the asymmetry as a result of differential lensing.
@@
 %   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
-We construct the zeroth moment map and the renzogram in \Fig{CO21mom}, and
-the higher-order first and second moment maps in \Fig{CO21highO}
+We construct the zeroth moment map, a red/blue channel map, and
+the first and second moment maps in \Fig{CO21mom}
 using the $uv$-continuum subtracted data cube over a velocity range of
 $\Delta v$ $\sim$ 750\,\kms.
-The renzogram is created using different velocity channels for the blue- and
-redshifted velocity components and
-the higher-order moment maps are created using
-channel maps with 3$\sigma$ clipping.
+The higher-order moment maps are created using
+unbinned channel maps with 3$\sigma$ clipping.
 The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
@@
 
-The deconvolved source size FWHM
+The deconvolved source size FWHM from two-dimensional Gaussian fitting
 is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
@@
 wavelengths, the lensed emission would be more accurately described by an
-annulus, enclosing the partially complete ``Einstein Ring'' and
+annulus, enclosing the partially complete ``Einstein ring'' and
 the lensed knots (see \Fig{CO21mom}).
 
-\begin{figure}[!htbp]
-\includegraphics[trim=0 10 15 0, clip, width=0.222\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
-\includegraphics[trim=5 -10 0 0, clip, width=0.232\textwidth]{../Figures/F555W_REDBLUE.eps}
-\caption{Left: an overlay of the velocity-integrated \bco emission on the {\it HST} $V$--band (F555W)
-image. Right: contours are color-coded to represent the red and blue wings of the emission.
-The contours start at 3$\sigma$ and increment at steps of
-$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
+\begin{figure*}[!htbp]
+\hspace{0.5em}
+\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
+\includegraphics[trim=5 -10 0 0, clip, width=0.472\textwidth]{../Figures/F555W_REDBLUE.eps} 
+\\
+\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
+\vspace{0.1em}
+\caption{Top left: overlay of the velocity-integrated \bco emission on the archival {\it HST} $V$-band (F555W)
+image. 
+Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission.
+The contours in both top panels start at 3$\sigma$ and increment at steps of
+$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel, 
+and 
+$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
+for the top right panel.
+The crosses denote the
 location of the foreground galaxy at $z$\,=\,0.295.
+Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
+are shown in steps of
+50 \kms, and 100 \kms, respectively. 
+The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
 \label{fig:CO21mom}}
-\end{figure}
-
-\begin{figure}[!htbp]
-%\centering
-\includegraphics[width=0.45\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
-\caption{
-Contours for the first (left) and second (right) moment maps are shown in steps of
-50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
-\label{fig:CO21highO}}
-\end{figure}
+\end{figure*}
 
@@
 Assuming a typical line width of 300\,\kms, this corresponds to a 3$\sigma$
-limit of 0.35\,mJy\,\kms\,beam\pmOne.
+limit of 0.35\,Jy\,\kms\,beam\pmOne.
 
@@
 We detect \cco line emission toward RXJ1131 at {\bf BLAH}$\sigma$ significance.
-The spectrum is shown in \Fig{co32spec}, which seems to have a double-peak profile.
-This is expected if RXJ1131 is truly a disk galaxy (see previous
-sections). The high phase noise in the calibration leads to a low SNR
-detection. We thus estimate the line intensity to be
+The spectrum is shown in \Fig{co32spec}, which appears to be consistent with a 
+double-peaked profile. We estimate a line intensity of
 35.7\,$\pm$\,21.9{\bf BLAH} Jy\,\kms by summing up fluxes over the FWZI
-linewidth used to infer \bco line intensity ($\sim$700 \kms).
-
-\begin{figure}[!Htbp]
+linewidth used to infer the \bco line intensity ($\sim$700 \kms).
+Assuming the spatial extent between \bco and \cco are similar and therefore
+magnified by the same amount, the line intensities
+correspond to a brightness temperature ratio of
+$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
+
+\begin{figure}[!htbp]
 %\centering
@@
 
-Assuming the spatial extents between \bco and \cco are similar and therefore
-magnified by the same amount, the line intensities
-correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,T$_{\small \cco}$$/$T$_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
-
 \subsection{Continuum Emission} %DONE
@@
 $S_\nu$\,=\,800\pmm88\,$\mu$Jy\,beam\pmOne
-centering on the lensing galaxy. Slightly extended emission is also detected
+centered on the lensing galaxy. Slightly extended emission is also detected
 along the lensed arc. This suggests that the detected emission comes from
@@
 \includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
-\includegraphics[trim=13 5 0 0, clip, width=0.475\textwidth]{../Figures/F555W_ContVLA.eps}
-\caption{Top: an overlay of the 2\,mm continuum emission on the optical image.
-Bottom: VLA 5\,GHz continuum emission is overlaid on the optical image.
+\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
+\caption{Top: overlay of the 2\,mm continuum emission on the optical image.
+Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
 Contours in both images start and increment at steps of
 $\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and
-$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the left and right panel, respectively.
+$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the top and bottom panel, respectively.
 The central crosses indicate the centroid of the foreground galaxy,
-as detected in the optical image. The synthesis beams are shown in the bottom left corner of each panel.
+as detected in the optical image. 
+The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
+the PdBI observations (top), and 
+0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
+the VLA observations (bottom).
 \label{fig:cont}}\vspace{0.51em}
@@
 as well as emission toward the background quasar.
-Multiple peaks are seen along the arc and their centroids
-coincide with the optical emission from the quasar.
-We extract the flux densities for the arc and the core in \Tab{photometry}.
+Multiple peaks are seen along the arc with their centroids
+coincident with the optical emission from the quasar.
+We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
 We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
@@
 Archive (IRSA) in \Tab{photometry} with aperture corrections
-when warranted. These data were obtained from
-the Two Micron All Sky Survey \citep[2MASS;][]{Skrutskie06a},
+when warranted. These data were obtained using
+the Two Micron All Sky Survey Telescopes \citep[2MASS;][]{Skrutskie06a},
 the Wide-field Infrared Survey Explorer \citep[{\it WISE};][]{Wright10a},
@@
 correct for the fact that the imaging was calibrated
-using a 12" aperture, which is larger than the aperture (5\farcs8) we used to
+using a 12$^{\prime\prime}$ aperture, which is larger than the aperture (5\farcs8) we used to
 perform aperture photometry.
@@
 We fit a power-law spectrum to the
-decomposed IRAC photometry to disentangle the observed total flux
-at MIPS 24\,$\micron$ into the foreground and
-background galaxies. We find a spectral index of $\alpha\sim-$1.8 and
-$\alpha\sim-0.85$ for the lensing galaxy and RXJ1131, respectively.
-This is consistent with the mean 3.6\,$-$\,8\,$\micron$
+decomposed IRAC photometry to disentangle the background and foreground 
+emission from the total flux observed in the MIPS 24\,$\micron$ band. 
+The spectral indices corresponding to best-fitting curves are $\alpha$\,=\,$-1.8$ and
+$\alpha$\,=\,$-0.85$ for the lensing galaxy and RXJ1131, respectively.
+The latter
+ is consistent with the mean 3.6\,$-$\,8\,$\micron$
 spectral slope of
 $\alpha$\,=\,$-$1.07\,$\pm$\,0.53 found for unobscured AGN
-\citep{Stern05a}. An extrapolation of the fit to 24$\micron$
+\citep{Stern05a}. An extrapolation of the fit to 24\,$\micron$
 yields 33.96\,$\pm$\,0.01\,mJy and 25.19\,$\pm$\,0.03\,mJy
 for the foreground galaxy and RXJ1131, respectively.
-We note that the IRAC photometry includes
-emission from old stellar populations and is prone to
-dust extinction. Hence, the decomposed fluxes are only
-our best estimate of the warm dust emission.
-We incorporate the decomposed 24$\micron$ point in our
+The uncertainties are the standard deviations of 
+the extrapolated fluxes obtained from two independent Monte Carlo 
+simulations, each of 500 iterations.
+% We note that the IRAC photometry includes
+% emission from old stellar populations and is prone to
+% dust extinction. Hence, the decomposed fluxes are only
+% our best estimate of the warm dust emission.
+We incorporate the decomposed 24\,$\micron$ data in our
 SED fitting to provide some constraints on
@@
 of the spectral energy distribution (SED) of RXJ1131.
-Details of the SED modeling is presented in \Sec{SED}.
-
-Extraction of the {\it Herschel}/SPIRE photometry was
+Details of the SED modeling are presented in \Sec{SED}.
+
+Extraction of the {\it Herschel}/SPIRE photometry at 250, 350, and 500\,$\micron$ was
 carried out using \ncode{sussextractor} within the Herschel Interactive
@@
 At the angular resolution of the \bco data, the images are resolved over
-$\sim$2 resolution elements. Given the extent of the lensed emission,
-this implies that our \bco observations do not resolve
+$\sim$2 resolution elements. 
+Given the extent of the lensed emission (see \Fig{CO21mom}),
+this implies that we do not resolve
 structures (e.g. knots and arcs) of the lensed emission
-(i.e., sub-optimal for
-performing lens modeling). Nevertheless, the high spectral
-resolution of this data provides dynamical information on
-spatial scales smaller than the beam (see \Fig{CO21highO}).
-Hence, with the high SNR, we reconstruct the intrinsic gas
-dynamics by carrying out a parametric lens modeling over different
+in our \bco data.
+ Nevertheless, the high spectral
+resolution of these data provides dynamical information on
+spatial scales smaller than the beam (see \Fig{CO21mom}).
+Hence, we reconstruct the intrinsic gas dynamics  % - morphology of different kinematic components - velocity structure
+by carrying out a parametric lens modeling over different
 channel slices of the interferometric data using our lensing code
@@
 (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
-Models of each slice thus provide the
-properties on the intrinsic kinematics. To increase the SNR for modeling, the
-slices are obtained by binning five native channels
-($\Delta v$\,$\sim$\,21.5\kms) over the full
-linewidth of $\sim$750\,\kms in the original data, resulting in seven
-independent channels.
+Models of each slice thus provide information on 
+the corresponding kinematic component of the CO gas, 
+enabling us to reconstruct the source plane velocity gradient. 
+In order to have adequate SNRs for lens modeling, we bin the frequency channels by a factor of five 
+to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
+that cover the full linewidth of $\sim$750\,\kms.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
+\caption{The full resolution \bco spectrum (yellow histogram) and 
+the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The 
+blue histogram shows the ``intrinsic'' line profile of RXJ1131 
+after subtracting a contribution from its companion galaxy and 
+correcting for lensing using the magnification factors $\mu_{\rm L}$ as annotated with horizontal bars
+above the respective model channels. Flux density is shown on a log scale along the y-axis.
+\label{fig:delensed}}
+\end{figure}
 
@@
 positional offset in R.A. and Dec. relative to an arbitrary chosen
-fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
+fixed coordinate in the image, the Einstein radius, the axial ratio, and the
 position angle. We use the VLA radio continuum emission toward
@@
 the uncertainties provided by previous SIE lens model \citepalias{Claeskens06a}.
-We initialize the Einstein Radius based on the model parameters reported by \citetalias{Claeskens06a}
+We initialize the Einstein radius based on the model parameters reported by \citetalias{Claeskens06a}
 and impose a uniform prior using $\pm$3$\sigma$ of their uncertainties.
@@
 radius, the axial ratio, and the position angle. The position of each source
-is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
+is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein radius)
 and the effective radius is allowed to vary from 0\farcs01$-$2$^{\prime\prime}$.
@@
 an intrinsic velocity gradient across the source plane, which is
-indicative of a kinematically-ordered disk-like galaxy.
+consistent with a kinematically-ordered disk-like galaxy.
 Additional support to the disk conjecture
 can be found in the double-horned line profile (\Fig{CO21spec})
-and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
+and the observed (image plane) velocity field (\Fig{CO21mom}). Furthermore,
 \citetalias{Claeskens06a} also find that the reconstructed source plane emission in optical-NIR
 is best-reproduced using a $n$\,=\,1 Sersic profile.
-We thus interpret RXJ1131 to be a disk galaxy.
+We thus interpret RXJ1131 as a disk galaxy.
 
 % the companion
-One other interesting result from our lens model is that a better fit is
-found for the red-most channel if we add a second source component (see
+A better fit is found for the lens model of
+the red-most channel if we add a second source component (see
 top left panel in \Fig{model}). This is consistent with previous results
@@
 (component F in their paper) $\sim$2.4\,kpc in projection from the AGN host galaxy in $V$-band,
-and \citetalias{Claeskens06a}, who find evidence for an interacting galaxy near RXJ1131.
+and with \citetalias{Claeskens06a}, who find evidence for an interacting galaxy near RXJ1131.
 Spatially, the red velocity component of the CO emission
-also coincides with this component F. It is therefore evident that we
-detect \bco emission in the companion galaxy.
+also coincides with this component F. It is therefore likely that we
+detect \bco emission in a companion galaxy.
 \defcitealias{Brewer08a}{B08}
 
-To quantify the type of merger (major v.s. minor) conventionally with a mass
-ratio, we decompose the total line flux into two components:
+The type of merger (major v.s. minor) in a pair of interacting galaxies 
+is most commonly distinguished based on 
+the ratio between their total galaxy mass.
+Here, we use the gas mass ratio between RXJ1131 and
+its companion galaxy instead, given that we do not have constraints on their individual galaxy mass.
+We decompose the total line flux into two components:
 one from RXJ1131 and the other from its companion.
 Since the companion is only detected in the red-most channel, we
-use the best-fit flux densities and magnification factors obtained
-from the model of this channel to derive the intrinsic gas mass in the companion.
-Assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1 and
-a CO luminosity-to-$H_2$ mass conversion factor of
+derive its intrinsic gas mass using the best-fit flux 
+densities and magnification factors obtained from the models of this channel.
+Assuming a brightness temperature ratio 
+of $r_{\rm 21}$\,=\,1 between \bco and \aco lines and
+a CO luminosity-to-H$_2$ mass conversion factor of
 \alphaco\,=\,0.8\,\alphaU, we find
@@
 used for the companion, this corresponds to a gas mass of
-$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun,
-implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
-We thus classify the system to be a {\em ``wet-wet'' minor merger} according to
-the classification scheme commonly used in literature.
+$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun, which
+implies a {\em gas} mass ratio of $\sim$7:1 between RXJ1131 and its companion.
+We thus classify the system to be a {\em ``wet-wet'' minor merger}.
+We caution that this is based on their gas mass ratio rather than their total galaxy mass ratio, which 
+is more commonly used in literature as the
+classification scheme to separate major mergers from minor mergers.
 
@@
 is a few arcsec, which implies that despite the high SNR and spectral
-resolution, this data is insufficient to constrain the
-intrinsic sizes of the lensed galaxies, and thus the magnification
+resolution, constraints on the intrinsic sizes of the lensed galaxies are modest, and thus the magnification
 factors may be under-predicted. % see Bussmann15
@@
 In the image plane shown in  \Fig{CO21mom}, the redshifted component is
-cospatial with the Einstein Ring seen in the
+cospatial with the Einstein ring seen in the
 optical image, with most of its apparent flux originating from the lensed arc
@@
 \caption{
-Channel maps of the PdBI \bco data cube toward RXJ1131 in 21.5\,\kms resolution.
-Black crosses indicate the position of the lensed knots (AGN emission,
+Channel maps of the PdBI \bco data cube toward RXJ1131 at 21.5\,\kms resolution.
+Black crosses indicate the positions of the lensed knots (AGN emission,
 which correspond to components ABCD in \citetalias{Claeskens06a}). The central white-filled
@@
 The spectra map covers an extent of $\sim$10"$\times$10"
-centering on the pixel that corresponds to the lensing galaxy.
+centered on the pixel that corresponds to the lensing galaxy.
 Spatial offset in arcsec is denoted in top left corner of each panel.
@@
 \input{table_magFactor}
+
 Similar to previous studies of RXJ1131, where
@@
 is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
-implying an intrinsically symmetric line profile. This is consistent with the source-plane
+implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the source-plane
 velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
@@
 Fitting a four-parameter double-Gaussian that describes two velocity peaks by a single FWHM
-to the ``intrinsic" \bco line profile of RXJ1131 (after correcting for lensing using
+to the ``intrinsic'' \bco line profile of RXJ1131 (after correcting for lensing using
 the magnification factors for various channels and separating the emission from RXJ1131 and its companion),
@@
 FWHM of 220\pmm72\,\kms.
+The peak separation obtained from this ``intrinsic'' line profile is 
+slightly lower than that obtained from the observed spectrum (\ie without lensing corrections).
+This discrepancy is likely a result of differential lensing, which causes the line peak of the red wing 
+to shift towards higher velocity channels, biasing the centroid of
+one of the components in a double-Gaussian to higher velocity than otherwise.
 If we instead fit with a single-Gaussian, we find a FWHM of 600\pmm160\,\kms for RXJ1131
@@
 velocity dispersion ($\gtrsim$400\,\kms) near the central region
-is seen in \Fig{CO21highO}. While beam smearing is inevitably the
+is seen in \Fig{CO21mom}. While beam smearing is inevitably the
 dominant factor in the observed velocity dispersion
-at the spatial resolution of this data, the exceedingly
+at the spatial resolution of these data, the exceedingly
 high velocity dispersion may hint
@@
 Therefore, in this scenario, RXJ1131 is
-likely a disrupted disk galaxy hosting an optically
+consistent with a disrupted disk galaxy hosting an optically
 bright quasar and is in the process of merging.
 
-\subsection{\bco Dynamical Modeling} \label{sec:dynamics} %DONE
+\subsection{\bco Dynamical Modeling} \label{sec:dynamics} 
 Assuming the velocities of the respective channels used in the
@@
 to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
-The parameter uncertainties are inferred based on Monte Carlo simulation
+The parameter uncertainties are inferred based on a Monte Carlo simulation
 of 500 iterations, where the input parameters are perturbed
@@
 of the rotation curve, the asymptotic velocity is poorly constrained and
-the ``turnover'' radius is at most a lower limit.
+the ``turnover'' radius is at most an upper limit.
 In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
@@
 
-\begin{figure}[!htbp]
+\begin{figure*}[!htbp]
 \centering
-\includegraphics[width=0.4\textwidth]{../Figures/veloGradient_markers}
-\includegraphics[width=0.455\textwidth]{../Figures/bestfit_PV.eps}
-\caption{Top: Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
+\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{../Figures/veloGradient_markers}
+\includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
+\caption{Left: Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
 the observed first moment map. The contours are at steps of 50\,\kms.
-Bottom: PV slice along the major axis in the source plane at PA\,=\,121\degr.
+Right: PV slice along the major axis in the source plane at PA\,=\,121\degr.
 Dashed line shows the best-fit rotation curve using an arctangent model.
@@
  \label{fig:PV}}
-\end{figure}
+\end{figure*}
 
@@
 The CO gas is thus of similar spatial
-extents as in $H$ and $I$-bands.
+extent as in $H$ and $I$-bands.
 
 In the rest-frame,
-emission in the observed $H$-band corresponds to NIR emission,
+emission in the observed-frame $H$-band corresponds to NIR emission $(\sim$1\,$\micron)$,
 tracing radiation from the accretion disk surrounding
@@
 This is consistent with the picture that old stars form first and constitute the bulge component
-of a spiral galaxy and that nuclear starbursts (in the inner few kpc) can be triggered latter in mergers.
+of a spiral galaxy and that nuclear starbursts (in the inner few kpc) can be triggered 
+in a later time as the progenitor disk galaxy interacts with other galaxies, 
+and thereby forming a larger bulge.
 
@@
 \ncode{mbb\_emcee} \citep[\eg][]{Riechers13a,Dowell14a}, which samples the posterior
-using an MCMC approach and uses instrumental
+distributions using an MCMC approach and uses instrumental
 response curves to perform color correction on-the-fly.
@@
 function with a power-law attached to the
-Wien side to account for an excess in the MIR owing to warm,
-small dust emission.
+Wien side to account for an excess in the MIR owing to emission of
+warm and small dust grains.
 % Previous studies find that in the absence of mid-IR data, a powerlaw slope
@@
 The model is thus described by five free parameters: the rest-frame characteristic dust
-temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
+temperature ($T_{d}$), the emissivity index ($\beta$), the power-law index
 ($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
@@
 becomes optically thick ($\lambda_{0}$). We impose
-an upper limit of 100\,K on $T_d$ \citep[see \eg][]{Sajina12a},
+a uniform prior with an upper limit of 100\,K on $T_d$ \citep[see \eg][]{Sajina12a},
 a Gaussian prior centered around
-$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
+$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and a uniform prior with an upper limit of
 1000\,$\micron$ on $\lambda_0$.
-We check for chain convergence by requiring the autocorrelation
-length of each parameter to be less than the number of steps
+We check for chain convergence by requiring that the autocorrelation
+length of each parameter is less than the number of steps
 taken for the burn-in phase (which are then discarded).
@@
 \input{table_mbb}
-
 In the first model, we include the 24\,$\micron$ data
 to constrain the power-law index. Based on the
-best-fit of this model, we find a
+best-fit of this model, we find an apparent
 \fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
@@
 For the mass absorption coefficient, we adopt
-$\kappa$\,=\,2.64\,m$^2$kg\pmOne at 125.0\,$\micron$
-(rest frame; \citealt{Dunne03a}).
+$\kappa$\,=\,2.64\,m$^2$kg\pmOne at rest-frame 125.0\,$\micron$
+\citep{Dunne03a}.
 The dust mass uncertainty does not
-include those in the absorption coefficient.
+include that of the absorption coefficient.
 
 A fit including the MIR 24\,$\micron$ photometry
-is likely an upper limit on the \fir luminosity arising from the starburst
+is likely an upper limit on the \fir luminosity due solely to \SF
 in the AGN host galaxy.
 % since the fit include contribution from the AGN (through power-law to MIR)
-If we instead fit for a model excluding the 24\,$\micron$ constraint,
+If we instead fit for a model excluding this constraint,
 two major consequences are immediately apparent.
 First, the power-law index is poorly-constrained (see \Tab{SED}).
-Second, the steep power-law implies a small contribution
+Second, the steep power-law implies only a small contribution
 from the power-law regime
-to the total IR luminosity as compared to the graybody.
+to the total IR luminosity as compared to the graybody component.
 Thus, the \fir luminosity in
@@
 a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
-dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun, uncorrected for lensing.
+dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun, all of which are uncorrected for lensing.
 Taken at face value, this implies a FIR-to-IR luminosity ratio
@@
 the derived star formation rate (SFR) given the similar \fir luminosity.
-Yet, the dust mass is higher in the former but consistent within the
+Yet, the dust mass is higher by a factor of $\sim$2 in the former but consistent within the
 uncertainties.
@@
 mass function \citep{Salpeter55a}, we find a
-SFR$_{\rm FIR}$ of 120\pmm63\,\sfrU using the
+SFR$_{\rm FIR}$ of 120\pmm63\,\sfrU using a
 standard conversion \citep{Kennicutt98a}.
 \defcitealias{Combes13a}{C13}
-\begin{figure}[!htbp]
-\centering
-\includegraphics[trim=5 5 5 5, clip, width=0.45\textwidth]{../Figures/FullSED}
+
 % WISE flux is slightly higher than the IRAC point, probably due to a smaller
@@
 % differential lensing.
+\begin{figure}[!htbp]
+\centering
+\includegraphics[trim=5 5 5 5, clip, width=0.45\textwidth]{../Figures/FullSED}
 \caption{SEDs of RXJ1131 and its lensing galaxy. The photometry is listed in \Tab{photometry}.
@@
 \subsection{ISM Properties} \label{sec:properties}
-In this section, we derive the gas properties of the merger system
-based on \bco and compare with those reported by
-C13, which is the largest sample of
-IR-luminous galaxy at similar redshift
+In this section, we derive the gas properties of the merging system
+based on \bco and compare them with those reported by
+C13 --- the largest sample of ULIRGs at similar redshift
 (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
@@
 \LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
-a SFR of $($150\pmm70$)$\,\sfrU.}.
-% the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
-We note that their results are based on \bco and \rot{4}{3} line observations with the
+a SFR of $($150\pmm70$)$\,\sfrU for RXJ1131.}.
+Their results are based on unresolved \bco and \rot{4}{3} line observations with the
 IRAM 30-m single-dish telescope.
@@
 \subsubsection{Linewidth and Sizes} \label{sec:sizes}
-A linewidth of $\Delta v_{\rm FWHM}$$\sim$600\pmm160\,\kms found from
-fitting a single Gaussian
-is considerably larger that those in the \citepalias{Combes13a} sample
-(370\,\kms) as well as local ULIRGs
-\citep[300\pmm85\,\kms, with the largest being 480\,\kms;][hereafter S97]{Solomon97a}.
-%ULIRGs (z < 0.3) studied in CO(1-0) by Solomon97a: ≥ 1/3 of them have double-peaked or flat-topped spectrum. But their linewidths are based on single Gauss fit.
+A FWHM linewidth of $\Delta v_{\rm}$\,$\sim$\,600\pmm160\,\kms found
+for RXJ1131 by fitting a single Gaussian
+is considerably larger that those in the \citetalias{Combes13a} sample
+(370\,\kms) as well as in
+local ULIRGs \citep[300\pmm85\,\kms, with the largest being 480\,\kms;][hereafter S97]{Solomon97a}.
+%ULIRGs (z < 0.3) studied in CO(1-0) by Solomon97a: ~1/3 of them have double-peaked or flat-topped spectrum. But their linewidths are based on single Gauss fit.
 Yet, given the dynamic nature of these galaxies,
-a CO linewidth of $\sim$600 may not be surprising.
+a CO linewidth of $\sim$600\,\kms may not be surprising.
 Indeed, a linewidth of $\Delta v$ = 750\,\kms has been observed
-in a local LIRG (Arp 118) \citep{SV05a}.
-Such FWHM is also commonly observed in high-$z$ starburst galaxies
-\citep[780\pmm320\,\kms; \eg][]{Greve05a}.
+in a local LIRG \citep[Arp 118; ][hereafter SV05]{SV05a}.
+Linewidth of this range ($\gtrsim$500\,\kms) is also commonly observed in 
+high-$z$ starburst galaxies  \citep[\eg][hereafter G05]{Greve05a} 
+% \citep[780\pmm320\,\kms; \eg][hereafter G05]{Greve05a} 
+and high-$z$ quasar host galaxies \citep[\eg][]{Coppin08a},
+% \citep[550\pmm180\,\kms; \eg][]{Coppin08a}, 
+which are 
+believed to originate from mergers.
 \defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}\defcitealias{SV05a}{SV05}
@@
 which is more
-extended than the sample of disk-like U/LIRGs studied by
-\citet[hereafter U14]{Ueda14a}, who find an average radius of 3.5\pmm2.3\,kpc but with a range of 1.1\,$-$\,9.3\,kpc.
-Such a range is consistent with the results reported by \citet{Gao99a}, where
-they also find CO disks extending out to $R\sim$10\,kpc.
-In contrast to the results
-reported in the classical study by
-\citet[hereafter DS98]{Downes98a}, who find molecular gas sizes of $R<$1\,kpc in their sample of local ULIRGs
-(see also \citealt{Bryant99a} and \citealt{Iono09a}), it appears that the molecular gas in ULIRGs
-can be distributed over large regions comparable to
-those reported in high-$z$ ($z$$>$\,1) galaxies \citep[$R\sim$7\,kpc;
-\citetalias{Greve05a};][]{Daddi10a, Riechers11a, Ivison11a}.
-While we cannot draw any conclusions on the evolution of 
-molecular gas size
-as we are only studying one
-ULIRG at intermediate redshift, it appears that local ULIRGs are composed of
-mergers at various stages of merging, and are therefore not
-necessarily more compact than
-high-$z$ SMGs \citep[cf. \eg][]{Iono09a}.
-\defcitealias{Ueda14a}{U14}
-\defcitealias{Downes98a}{DS98}
-\defcitealias{Ivison11a}{I11}
-\defcitealias{Riechers11a}{R11}
-
-% SFRSD:
-We do not attempt to derive a SFR surface density and gas surface density
-since we do not have any constraints on the dust continuum size
-and the fact that
-the gas surface density is unlikely to be constant across the CO region
-given the centrally concentrated $V$-band emission, which we interpret as
-merger-induced starburst (see \Sec{caveat}).
-Should we decide to do this, it would imply
-a series of assumptions to be made, leading to surface densities that are not
-meaningful in any case.
+extended than the average in a sample of disk-like U/LIRGs studied by
+\citet[]{Ueda14a}, % who find an average radius of 3.5\pmm2.3\,kpc 
+but consistent with their range of 1.1\,$-$\,9.3\,kpc.
+Our CO size is also consistent with that of high-$z$ 
+($z$\,$>$\,1) galaxies \citep[$R\sim$\,4$-$20\,kpc;
+\citetalias{Greve05a};][]{Daddi10a, Riechers11a, Ivison11a} and
+local U/LIRGs in the \citet{Gao99a} sample ($R\lesssim$10\,kpc).
+%For instance, extended molecular disks are often associated with advanced mergers
+%\citep[\citetalias{Downes98a};][]{Gao99a}.but see also U14 for outliers
+% with extended molecular gas in merger remnants
 
@@
 $M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
-We correct for the inclination effect using the
-morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25)
-from the reconstructed image (Figure 3 in \citetalias{Claeskens06a}), yielding
-an inclination angle of 56.4\degr, which is consistent with the
-observed unobscured AGN and an observable double peak line profile.
-The dynamical mass is then
-8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$\,$<$\,25\E{10}\Msun.
+We derive an inclination angle of 56.4$\degr$ from the
+morphological axial ratio of $a/b\sim$1\farcs8$/$3\farcs25, which we estimate
+from the source-plane image reconstructed by \citetalias{Claeskens06a} (Figure 3 in their paper).  
+This corresponds to an inclination-corrected dynamical mass of
+8.3\E{10}\Msun$<$\,$M_{\rm dyn}$\,$<$\,25\E{10}\Msun.
 Our estimate should be considered at best an upper limit since
-the gas is unlikely to be virialized in RXJ1131.
-% based on the observed velocity dispersion and the presence of a closeby companion.
-For the following sections, we use the
+the gas in RXJ1131 is unlikely virialized.
+In the following sections, we use the
 lower limit (8.3\pmm1.9)\E{10}\,\Msun as the dynamical mass as it is
-derived in a manner similar to commonly used in literature (\eg \citetalias{Solomon97a,Downes98a,Greve05a}).
-
-Using the velocity dispersion obtained with a single Gaussian fit to the
+derived in a manner similar to what is commonly used in literature 
+(\eg \citetalias{Solomon97a}; \citealt[hereafter DS98]{Downes98a}; \citetalias{Greve05a}).
+\defcitealias{Downes98a}{DS98}
+
+Using the velocity dispersion obtained by fitting a single Gaussian to the
 line profile of the companion ($\sigma$ = 30\,\kms)
@@
 inclination angle of 30$\degr$.
-We note that this is substantially lower than its gas mass, which is a more reliable estimate based on
-the data in hand.
-We adopt the $V$-band size as the radius $R$ owing to the fact that
-it is the only size estimate available for the companion.
-We do not use this dynamical mass for deriving any additional physical parameters, and thus it
-does not alter our interpretations of the system throughout this paper.
+We adopt the $V$-band size as the radius $R$ in the above estimate 
+owing to the fact that it is the least uncertain source size constraint available for the companion.
+However, since this dynamical mass is substantially lower than the gas mass, which is 
+a more reliable estimate based on the data in hand, 
+we do not use this dynamical mass to derive other physical parameters.
+The inconsistency between the gas mass of the companion and its dynamical mass
+may indicate its dusty nature, which causes the $V$-band source size to 
+appear much smaller than its true extent without any dust obscuration.
+% On the other hand, we find a half-right radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from our lens 
+% model, which can only serve as a crude measure of its unobscured source size (see \Sec{caveat}).
+Using this CO size, we find a dynamical mass of $M_{\rm dyn}$\,=\,3\E{7}\,\Msun.
+WHICH is STILL LOWER THAN the GAS MASS?
 
@@
 
-% The dynamical mass in RXJ1131 is thus higher than local ULIRGs
-% ($M_{\rm dyn}(R\leq)0.6\,kpc)$\,$\sim$\,6\E{9}\,\Msun; \citepalias{Downes98a}).
-
 \subsubsection{Gas Mass and Gas Ratios}
-% Solomon97 (ULIRGs z < 0.3): 0.4-1.5 e10 Msun
-% SV05: Solomon+97: average Mgas ~7e9 Msun
-% SV05: high-z: (2.5-10)e10 Msun
-A total molecular gas mass of
-$M_{\rm gas}^{\rm total}$ = $($1.57\pmm0.38$)$\E{10}\,\Msun is
-residing within the merger system (see \Sec{caveat}).
-This is comparable to those found in the
-\citetalias{Combes13a} sample %(1.5\E{10}\Msun)
-as well as local U/LIRGs
-\citep[][\citetalias{Solomon97a}]{Sanders96a} but higher than
-in local LIRGs \citepalias{Ueda14a}, as expected.
-Our finding is thus consistent with previous results, where
-high-$z$ galaxies tend to have higher molecular gas mass %\footnote{Assuming the same conversion factor}
-and is
-distributed over larger spatial extents
-\citepalias[\eg][]{SV05a,Riechers11a,Ivison11a}.
-% gas-to-dyn ratio
-% DS98: f ~ 0.16 (but w/in disc or ring of R ~ 0.5 kpc)
-% Bothwell+13: f ~ 0.3? (but over larger R)
-% --> ULIRGs gas fraction is even lower if average over same scale as SMGs
-% Daddi10a; Tacconi10a: f_gas ? 40% in z ? 1 discs, significantly higher than local discs (but alphaCO not same as ULIRGs)
-Using the dynamical mass and the total
-gas mass ($M_{\rm gas}^{\rm total}$), we find a gas mass
-fraction of $f_{\rm gas-dyn}$ = 0.19\pmm0.37, which is
-consistent with the results reported by \citetalias{Combes13a}:
-a gas fraction of 15\% in ULIRGs at 0.2\,$<$\,$z$\,$<$\,0.4 and 24\%
-in those at 0.6\,$<$\,$z$\,$<$\,1.0, and those from resolved measurements of local ULIRGs \citepalias{Downes98a}.
-% This implies that the gas fraction in ULIRGs at $z$$<$\,1 is
-% similar to high-z starburst galaxies, but
-% lower if we average over the same spatial scales (as SMGs, which
-% are more extended; \citet{Bothwell13a}).
-This implies that the gas fraction in ULIRGs at $z$\,$<$\,1 is
-similar to those in high-$z$ ``normal'' star-forming disc galaxies
-\citep[assuming an \alphaco conversion factor of 0.8 \alphaU;][]{Daddi10a,Tacconi10a} as well as
-high-$z$ starburst galaxies
-\citep[with similar CO sizes between the two populations (see \Sec{sizes}); cf. smaller CO sizes from earlier studies; \citetalias{Downes98a}]{Bothwell13a}.
-\defcitealias{Daddi10a}{D10}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % our galaxy MW ~150 (Draine+07)
+% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
 % Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Using the lensing-corrected dust mass,
-% of $M_{\rm dust}$ = 4.0\petm{0.9}{3.3}\E{8}$(\mu_{\rm L}/5.5)\pmOne$\,\Msun,
-we find a gas-to-dust ratio of
-40\pmm34, which is significantly lower than the statistical average
-of $f_{\rm gas-dust}$\,=\,206
-in the \citetalias{Combes13a} sample but
-consistent with their range of values and the
-\citet[][]{Wilson08a}
-sample of local ULIRGs. %$($50$-$70$)$.
-% If we assume that most ULIRGs at the same epoch should have similar dust and
-% gas content owing to their empirical scaling relations
-% with the parameters in the fundamental metallicity relation \citep{Mannucci10a}
-% and their respective evolutions as well as the
-% well-established \LFIR--\Lp correlation \citep[\eg][]{Young91a, Sanders91a},
-% the low gas-to-dust ratio of RXJ1131 compared to the
-% \citetalias{Combes13a} sample may be explained
-% in part due to differential lensing between the gas and the dust, leading to
-% an overestimation of the dust mass via our adoption of the CO magnification
-% factor, but this is
-% unlikely [the dominant reason/enough to account] for the factor of $\sim$5
-% discrepancy. It is thus necessary to invoke other possible explanations.
-We note that the gas-to-dust ratio maybe biased low as
-the optically thick gas is likely to be more extended than the dust, leading to
-an overall lower magnification factor than the dust emission,
-and thus an overestimate of the
-dust mass via our adoption of the CO magnification factor.
-
-% A direct comparison to the literature is not straightforward as the dust mass estimate
-% is highly dependent on the method, \eg the model assumed, the wavelength and resolution at which the data 
-% were observed. Seaquist+04 find that a GDR can be 
-% affected by a factor of $\sim$5 in the inner few kpc in some cases for
-% U/LIRGs but global GDR may be unaffected. If we assume that the dust mass
-% obtained from the literature is obtained through the most appropriate
-% way with the given data for their sample, then the main uncertainty related to the dust mass is the mass
-% opacity coefficient. While the main systematic uncertainties associated with the gas mass
-% are the \alphaco conversion factor and the brightness temperature ratio $R_{\rm 21}$.
-
-There are a number of systematic uncertainties associated with this quantity, \eg
+Using the lensing-corrected dust mass, we find a galactic-scale gas-to-dust ratio of
+40\pmm34, which is lower than the statistical average of $f_{\rm gas-dust}$\,=\,206
+in the \citetalias{Combes13a} sample but well within their broad 
+range of values over the entire sample. Our ratio is also consistent with 
+high-$z$ SMGs 
+% \citep[78\pmm26;][]{Bothwell13a} 
+\citep[hereafter B13]{Bothwell13a} and
+local ULIRGs \citep{Wilson08a}, but lower than of the Milky Way by
+$\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
+We note that the dust mass derived for RXJ1131 is poorly constrained.
+If we adopt a dust mass from the other SED fit (\ie without constraints at 24\,$\micron$),
+the dust mass is reduced by a factor of $\sim$2. \defcitealias{Bothwell13a}{B13}
+
+There are a number of systematic uncertainties associated with this quantity. For instance,
 the mass opacity coefficient $\kappa$,
-the \alphaco conversion factor, and the brightness temperature ratio $R_{\rm 21}$.
-The fact that RXJ1131 has a lower dust-to-gas ratio 
-and appears to be more dusty than most ULIRGs at the same epoch
-may imply different physical
-environment compared to others. If we instead use the ``Galactic" \alphaco value, 
+the \alphaco conversion factor, and the brightness temperature ratio $r_{\rm 21}$.
+If we instead use the ``Galactic'' \alphaco value, which may be more appropriate for some ULIRGs \citep[\eg][]{Papadopoulos12a} and minor mergers \citep{Narayanan12a},
 the gas mass (and thus gas-to-dust ratio) would be $\sim$6 times higher.
+We note that this gas mass is physically feasible based on dynamical mass constraint. 
 On the other hand, we would also obtain a higher gas mass if
-we assume subthermal excitation between \bco and \aco line emission.
-However, we expect this to be a minor effect as ULIRGs are observed to be
-thermalized up to $J$ = 3 or 4.
+we assumed sub-thermal excitation between \bco and \aco emission, but
+we expect this to be a minor effect as CO emission in ULIRGs are thermalized up to $J$ = 3 or 4.
+We also note that the gas-to-dust ratio derived for RXJ1131 maybe biased low as the gas is likely to
+be more extended than the dust. Consequently, the overall magnification factor 
+for the CO gas may be lower than the optically thick dust, which dominates the \fir
+luminosity, and thus leading to an overestimated dust mass 
+via our adoption of the CO magnification factor.
 
 \subsubsection{SFE and Depletion Timescales}
-% CO-IR luminosity correlation
 % SFE:
 % in terms of LFIR/Mgas:
+% high-z: $>$100
 % Greve+05: 450 +/- 170 Lsun/Msun for SMG
@@
 
-% SFE > 100 for ULIRGs and SMGs, 0.1 < z < 3 Downes, Solomon & Radford93, Tacconi, L.
-J., Genzel, R., Smail, I., et al.
-2008, ApJ, 680, 246, Riechers, D.
-A., Carilli, C.
-L., Maddalena, R.
-J., et al.
-2011a, ApJL, 739, L31.
-
 To first order, the star formation efficiency
-$($SFE = \LFIR$/$$M_{\rm gas})$
-indicates the \SF rate per
-unit solar mass of molecular gas available in a galaxy.
+$($SFE = \LFIR$/$$M_{\rm gas})$ indicates the \SF rate per unit solar mass of molecular gas available in a galaxy.
 Using a wavelength range of 40\,$-$\,500\,$\micron$ defined
@@
 we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$,
-which is on the low end among other U/LIRGs
+which is on the low end among other U/LIRGs at $z$\,$<$\,0.6
 % \citep[$\sim$180\pmm160 \Lsun $M_{\odot}^{-1}$;][]{Solomon97a, Combes11a}
-\citep{Solomon97a, Combes11a}
-but 
-similar to those of
-low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a}.
-In constrast, a star formation efficiency of $>$100 \Lsun $M_{\odot}^{-1}$
-has been reported in ULIRGs and SMGs at 0.6\,$<$\,$z$\,$<$\,3
-\citep[][\citetalias{Riechers11a,Combes13a}]{Tacconi08a}.
-\defcitealias{Tacconi08a}{T08}
-% Depletion time:
-% Greve+05: ~40 Myr
-Assuming the \SF continues at the current rate without gas replenishment and is the only
-way to consume the gas reservoir, this corresponds to a depletion
-time of $\tau$\,=\,102\pmm25\,Myr.
-Since the \SF rate is expected to vary in an interacting system and that AGN accretion
-also consumes some fraction of the gas, the depletion
-timescale should only be considered as an upper limit.
-
-The SFE (using the above definition) is highly dependent on the gas mass.
-Yet, the use of an ``ULIRG" \alphaco value is not well justified and 
-should only be considered as a lower limit \citepalias[see][]{Solomon97a}.
-It may be more appropriate to use an \alphaco closer to the ``Galactic" value in 
-some ULIRGs \citep[\eg][]{Papadopoulos12a}. 
-From numerical models, it is found that mergers on average have lower \alphaco values than
-disk galaxies \citep{Narayanan12a}.
-But since the gas temperatures and velocity dispersions in minor mergers do not deviate from 
-galactic GMCs as much as in major mergers, the \alphaco may not be as extreme as 0.8\,\alphaU.
-% thus the rise in CO intensity is not as large, and the X-factor (and thus alphaco) does not decrease as much {Narayana11a}.
-Hence,
-we can derive an upper limit on the gas mass for RXJ1131 
-using the Galactic value of 4.6\,\alphaU. This yields
-a gas mass (and thus a SFE) that is $\sim$6 times higher.  
-In contrast to results in the classical study of nearby ULIRGs by \citetalias{Downes98a}, who find that
-the gas mass exceeds the dynamical mass using 
-the Galactic conversion factor 
-(and thus inappropriate for their sample), the gas mass derived for
-RXJ1131 using the Galactic value is consistent with its dynamical mass.
-%Obviously, this will lead to a longer depletion time.
-
-Alternatively, the relatively low SFE maybe intrinsic to RXJ1131.
-In that case,  RXJ1131 may evolve into a disc galaxy with a small bulge component
-in the context of theoretical simulations by \citet{Hopkins09a}, who suggest 
-that the disc component in a gas-rich progenitor galaxy can survive post-merging
-by lowering the \SF efficiency (and thus less efficient at removing the angular momentum of
-the gas), thereby enabling a higher gas fraction to be retained and 
-distributed over a larger extent.
+\citep[\citetalias{Solomon97a};][]{Combes11a} but consistent with those of
+low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a} and high-$z$ disk-like galaxies \citep{Daddi08a}.
+Assuming an \alphaco of 0.8\,\alphaU is appropriate for RXJ1131, this would imply that
+it is converting gas into stars at an efficiency 
+similar to those of ``normal'' star-forming
+disk-like galaxies rather than starburst galaxies
+\citep[][\citetalias{Combes13a}]{Tacconi08a, Riechers11a}. 
+This is in agreement with its disk-like kinematic signatures.
+
+Results from theoretical simulations have suggested that 
+the disk component of a gas-rich progenitor galaxy can 
+survive merging if it has a low star formation efficiency, which in turn
+reduces the gravitational torque available to 
+remove the angular momentum of the gas, thereby allowing
+a higher gas fraction to be retained and redistributed over a large extent in
+the merged galaxy \citep{Hopkins09a}. With this, it is plausible that RXJ1131 
+will evolve into a disk galaxy with a small bulge component upon merging given its low SFE.
 %since there is little/no significant stellar material % (collisionless)
@@
 
+% Depletion time:
+% Greve+05: ~40 Myr
+Assuming the \SF continues at the current rate without gas replenishment, this corresponds to a 
+gas depletion time of $\tau$\,=\,102\pmm25\,Myr.
+Since the \SF rate is expected to vary in an interacting system and
+AGN accretion also consumes some fraction of the gas, the depletion
+timescale should only be considered as an upper limit. 
+\defcitealias{Tacconi08a}{T08}
+
+%====================================================================
 %While the \alphaco conversion factor is commonly assumed to be 0.8\,\alphaU for
@@
 % Whereas \citet{Tacconi08a, Carilli10a} place an upper limit of $\sim$0.8 on high-$z$ SMGs, leading the emergence of two star formation modes. Carilli+10: based on dynamical constraints
+%====================================================================
 
@@
 \section{Discussion} \label{sec:diss}
-\subsection{Velocity Offset and a Recoiling Black Hole}
-Using the redshift deduced from the CO line 
-as the systemic redshift, we find
-a velocity offset of $\sim$780\,\kms with the optical lines:
-the broad Mg{\scriptsize II}~2798\AA\ and the narrow 
-$[$O{\scriptsize III}$]$~4959, 5007\AA\ lines \citep[$z_{\rm AGN} = 0.658$;][]{Sluse03a}.
-This indicates that the broad line region (BLR) of the AGN is at a
-slightly higher redshift than the host galaxy.
-From the CO renzogram and channel maps in \Fig{CO21mom} and \Fig{chanmap}, the emission 
-corresponding to the the line center are not co-spatial
-with the optical quasar. In particular, the quasar emission forms 
-the point-like images along the lensing arc, which is 
-spatially offset to the NW
-of the CO line center emission.
-Spatial offsets between optical BLRs and CO emission are not uncommon
-but such a high kinematic offset is not commonly observed.
-For instance, the
-velocity offset between AGNs and their hosts galaxies in 
-an SDSS sample of ongoing mergers at $z$\,$<$\,0.21 is at most $\sim$410\,km/s \citep{Comerford14a}.
-The same authors also suggest mechanisms
-such as AGN outflows, jets, and gravitational recoil of SMBHs in post-merger
-as plausible explanations for these offsets.
-
-AGN outflows or starburst-driven winds have been observed
-in \eg SMMJ1636+4057 \citep[][]{Swinbank05a}, but 
-no evidence for outflows are found in RXJ1131 in the existing data. 
-% an explanation due to the in/outflows arising from radiation pressure or AGN winds.
-Alternatively, it can be an indication of the BH(s) orbiting the a common center in
-the host galaxy.
-In principle, this would only be valid if the velocity offset between the BLR and 
-the narrow line of the gas in the host galaxy is consistent with its orbital velocity. 
-%(\ie carrying along its accretion disc and BLR)
-Since \citet{Sluse03a} only report a redshift combining the broad and narrow lines, 
-% \ie it is unclear what's the velocity offset between MgII and [OIII]
-the lack of a redshift from solely the BLR of the AGN precludes us from interpreting this as the favoured
-explanation for the velocity offset.
-
-In fact, a large velocity offset can also result from a recoiling black hole (BH) where its
-BLR is moving at high velocity relative to the bulk of the host galaxy and
-the ionized gas \citep{Madau04a, Bonning07a, Loeb07a}. % narrow AGN lines.
-Such a scenario may occur after galaxies and their BHs merge, during which 
-their orbital energy is being released as gravitational wave to overcome the last stable orbit.
-This results in a recoil in the merged BH for an uneven BH mass merger as a
-non-zero net angular momentum is also being carried away.
-Depending on their initial conditions, % mass ratios, spin, rotational direction, 
-numerical relativity simulations have shown that
-the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
-% The BH is displaced from the galactic nucleus in this scenario, and might 
-% return to the center in a few dynamical time-scales 
-% by dynamical friction or be kicked out of the gravitational potential of the host galaxy.
-This together with the fact that the BH in RXJ1131 has a high spin parameter \citep{Reis14a} 
-renders the recoiling BH scenario a viable option for the origin
-of the optical velocity offset.
-To reconcile this picture with the fact that a companion is still observed, 
-the system may be in its subsequent stages of (minor) merging but was initially
-a major merger. 
-This would imply previous encounters between RXJ1131 and its companion, 
-which would also explain the spinning BH.
-
-It is worth noting that
-while these large velocity offsets are theoretically achievable,
-they are not commonly observed --- only a few objects have been reported with optical offsets $\gtrsim$1000\,\kms.  
-For instance,
-the most promising candidate of a recoiling BH with both spectroscopy and imaging
-signatures is CID-42 at $z$\,=\,0.359, which has 
-a velocity offset of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ \citep{Civano10a}. 
-% which has a similar velocity offset
-% of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ 
-% in two optical component separated by $\sim$ 2.5 kpc within the same galaxy \citep{Civano10a}. 
-Other examples include 
-the type-1 QSO SDSS 0956+5127 at $z$\,$\sim$\,0.714, with an offset of 1200\,\kms
-between Mg{\scriptsize II}~2798\AA\ and $[$O{\scriptsize III}$]$~4959, 5007\AA\ lines 
-\citep{Steinhardt12a}, 
-and
-SDSSJ0927+2943 at $z$\,$\sim$\,0.713, with an offset of 2650\,\kms \citep{Komossa08a}.
-% shows an exceptional optical emission-line spectrum with two
-% sets of emission lines: one set of very narrow emission lines, and a second set of broad Balmer and
-% broad high-ionization forbidden lines which are blueshifted by 2650 \kms
-% relative to the set of narrow emission lines \citep{Komossa08a}.
-
-\subsection{Merger stage RXJ1131-1231}
-%It is clear that the signature of a galaxy merger changes as the merging progresses.
-%For instance, extended molecular disks are often associated with advanced mergers 
-%\citep[\citetalias{Downes98a};][]{Gao99a}.but see also U14 for outliers
-% with extended molecular gas in merger remnants
-
-The (gas) mass ratio, the intrinsic CO line profile,  
-% since the bulk of the angular momentum can be retained only in minor mergers if small separation
-and the source-plane velocity field are all evident of 
-a minor merger, in good agreement with an 
-earlier study by \citetalias{Brewer08a} who
-independently conclude the presence of a dwarf companion 
-of size $\sim$700\,kpc across. Since minor mergers may in some cases
-result from previous passage of major mergers, it is possible that RXJ1131
-has encountered with the progenitor galaxy of the companion and is undergoing 
-the subsequent series of minor merging.
-One piece of evidence comes from % that they have encountered
-the compact UV emission, which can be starburst resulting from gas accumulation 
-owing to a non-axisymmetric perturbation from the companion.
-% the stellar component torques away the angular momentum, allowing the gas to fall inward.
-The highly spinning black hole in RXJ1131 is also consistent with 
-this hypothesis. 
-If we favor the gravitational wave recoil mechanism 
-to explain the optical velocity offset, it would also imply the black 
-holes (and their host galaxies) have merged or are at their final coalescence. 
-In addition, the source-plane CO position of the companion appears to be consistent with 
-a picture where its molecular gas is mixed with RXJ1131 (but with large uncertainties). 
-%\ie companion CO location along/within the RXJ1131 CO disc
-% as well as one where its emission is co-spatial with the stellar light. 
-The IR luminosity also agrees with 
-the results from previous studies: AGNs are
-typically found in late stage mergers 
-\citep{Yuan10a,Iwasawa11a,Carpineti12a} and
-only major mergers near their final
-coalescence can provide \LIR$>$\,10$^{12}$\,\Lsun,
-\citep[\eg][]{Carpineti15a,Larson16a}.
-
-It may be puzzling as to why the stellar emission in the companion 
-is spatially offset from RXJ1131 while its CO gas appears to be mixed-in if they 
-have encountered.
-This phenomenon is in fact not unique to our source. 
-The gas cores of the individual 
-% merging galaxies 
-mergers NGC~6090 and NGC~6240 are also observed
-to be coalescing  
-% is in the process of or has already coalesced into a single component
-while their stellar cores remain
-separated \citep[0.5$-$3\,kpc;][]{Bryant99a}. 
-Although this is difficult to reconcile with the fact that the stellar light in the companion 
-originates from recent \SF (UV emission). 
-More sensitive and higher resolution observations will be needed
-to confirm any offsets between the CO gas and the stellar light in the companion.
-% allow for a more detailed lens modeling to trace the gas distribution and morphology in the system
-Another puzzle may be the absence of morphological features.
-One straightforward explanation may simply be the lack of spatial resolution.
-Alternatively, it may be a result of the offset in timing between observable
-morphological disturbances and the merger-induced starbursts \citep{Lotz08a}.
-% with strong morphological disturbances occurring before bursts of merger-induced star formation and for shorter durations
-
-\subsection{Fate of RXJ1131}
+\subsection{Fate of RXJ1131-1231}
 The classical picture for mergers is one where they are responsible for the formation of the local
 red and passive spheroidal galaxies.
-With more realistic treatments of star formation and feedbacks in recent simulations,
-% ? which suppress efficient early star formation ? play a critical role in enabling disc formation in simulations.
+With more realistic treatments of star formation and feedback in recent simulations,
 it has been suggested that it is possible to suppress bulge formation
-in gas-rich mergers, thereby evolving into large 
-disks \citep{Springel05a, Robertson06a, Hopkins09a}.
+in gas-rich mergers, thereby forming large disks 
+that resemble local spiral galaxies \citep{Springel05a, Robertson06a, Hopkins09a}.
 % (bulge dominated; Springel05a, Robertson06a)
@@
 %
-Since both RXJ1131 and its companion are gas-rich
 % unlikely RXJ1131 will evolve into present-day massive
@@
 % (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
-and that the bulk of the angular momentum of the gas is  
-retained in minor mergers,
-it is likely that RXJ1131 will evolve into either a 
-``normal'' elliptical/S0 galaxy or a large disk galaxy.  
-% normal E only because gE needs ways to remove angular momentum efficiently for gas to funnel
-In the latter, the stellar populations from the companion will be displaced onto the 
-dominant galaxy to thicken the disk \citep[\eg][]{Lotz08a, Robertson06a}.
-% disk from gas-rich major merger: \citep[\eg][]{Lotz08a, Robertson06a}.
-Given that the molecular gas in 
-RXJ1131 is distributed in an extended disk configuration and that its 
-SFE is on the low end among other ULIRGs,  % not enough stellar material to efficiently remove ang. mom.
-it is more conceivable that RXJ1131 will evolve into the
-latter.
-% Lotz08a: a major gas-rich merger without AGN feedback does not, by itself, produce a red and dead spheroidal galaxy
-Other mechanisms e.g. formation of bar-like structures will be needed to remove the
-angular momentum of the gas more efficiently to transform the gas disc into a stellar spheroid and
-AGN feedbacks are also necessary to halt further activities for RXJ1131 to evolve into an 
-E/S0 galaxy \citep{Lotz08a}.
+The extended molecular gas distribution in RXJ1131 together with its low SFE implies that the 
+removal of angular momentum of the gas via gravitational torque is inefficient.
+Other mechanisms e.g. bar-like structures that are more efficient at removing angular momentum will 
+be required in order to transform the gas disk of RXJ1131 into a stellar spheroid and evolve into 
+an E/S0 galaxy. Without these, it is more conceivable that RXJ1131 will retain its disk component and
+evolve into a disk galaxy upon its final coalescence with the companion.
+
+\subsection{Velocity Offset and a Recoiling Black Hole}
+Using the CO line center redshift as the systemic redshift, we find
+a velocity offset of $\sim$780\,\kms from the optical
+\mgii line and the \oiii lines \citepalias[$z_{\rm QSO} = 0.658$;][]{Sluse03a}. This implies that the AGN is dynamically offset from the centroid of its host galaxy. 
+From the CO channel maps in \Fig{CO21mom} and \Fig{chanmap}, it is also apparent that the 
+line center of the gas is not co-spatial with the optical quasar as the point-like images
+along the lensing arc
+are spatially offset to the NW of the CO line center.
+While spatial offsets between optical lines and CO line
+have been reported in other galaxies, the velocity offsets are typically $\lesssim$\,500\kms.
+{\bf
+In the classical SDSS analysis for line offsets \citep{Richards02a}?.
+\oiii and \mgii analysis \citep{Boroson05a, Bae14a}?.
+with the corresponding trends and possible explanations?.
+More extreme offsets between CO and optical lines have been seen \citep{Hainline04a} 
+or between \cii and \mgii \citep[\eg][]{Venemans16a}.}
+For instance, the
+velocity offset in
+an SDSS sample of ongoing mergers at $z$\,$<$\,0.21 is at most $\sim$410\,km/s \citep{Comerford14a}.
+
+A large velocity offset can also result from a recoiling black hole (BH) where its broad line region
+is moving at high velocity relative to the bulk of its host galaxy 
+\citep{Madau04a, Bonning07a, Loeb07a}. 
+Such a scenario is expected to occur 
+when a pair of uneven mass BH coalesce, during which their orbital energy is being released 
+as gravitational wave and a 
+non-zero net angular momentum is being carried away.
+Depending on their initial conditions, numerical relativity simulations have shown that
+the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
+%While such large velocity offsets are theoretically achievable,
+%they are not commonly observed --- only a few objects 
+%have been reported with optical offsets $\gtrsim$1000\,\kms. For instance,
+%the most promising candidate with both spectroscopy and imaging
+%signatures of a recoiling BH is CID-42 at $z$\,=\,0.359, with 
+%an offset of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ \citep{Civano10a}.
+%Other example includes the type-1 QSO SDSS 0956+5127 at $z$\,$\sim$\,0.714, with an offset of 1200\,\kms
+%between Mg{\scriptsize II}~2798\AA\ and $[$O{\scriptsize III}$]$~4959, 5007\AA\ lines
+%\citep{Steinhardt12a}. % but here its between CO and optical lines
+%% SDSSJ0927+2943 at $z$\,$\sim$\,0.713, with an offset of 2650\,\kms \citep{Komossa08a}, but disproved by Decarli+14; Hence, I am going to cut this out because I listed this source here just to demonstrate the scarcity of high velocity offsets; but the offset in this system is between a set of redshifted versus a set of blueshifted..
+which is not quite the same our case here.
+The fact that the BH in RXJ1131 has a high spin parameter \citep{Reis14a}
+renders this scenario a viable option for the origin
+of the velocity offset. 
+However, since this model requires a merged BH, this interpretation would imply RXJ1131 have 
+already encountered with the companion galaxy, which is consistent with
+the highly spinning BH observed in RX1131.
+Given the presence of a nearby companion observed in our data, the system may be in its 
+subsequent stages of (minor) merging resulting from previous passage of a major merger.
+
+As demonstrated here using \mgii and \oiii lines, large velocity offsets between CO and optical lines may be present.
+We thus caution against the use of optical lines as 
+true systematic redshift indicators as the resulting redshift can deviate from the 
+true value.
+
+\subsection{The \bhrelation Relation}
+
+Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
+The dusty nature of this system?? \\
+
+\citet{Shields06a} investigate the \bhrelation relation to high-$z$ using CO line width since 
+CO has been detected in over hundreds of galaxies at $z$$>$1.
+From their results, the dynamical mass from CO line widths is 
+smaller than would be expected by the local relation, but they also noted it is possible that the stellar dispersion is
+underestimated (see section 2.3 in Shields06a).
+
+If we follow their approach, and use the CO linewidth to derive $\sigma_*$, assuming FWZI = 2$v_\textrm{rot}$, then the stellar dispersion is related to the CO dispersion via 
+$\sigma_*$ = 4.44$\sigma_{\rm CO}$.
+% FWHM ~ 2/3 FWZI; FWZI = 2*v_cir = 2sqrt(2) * sigma_*;  => FWHM ~ 0.53 sigma_*.
+% where CO dispersion = FWHM/2.355 ---> sigma_* = 4.44 * CO dispersion.
+, we find?.
+
+If we adopt the broad H$\beta$ line as a proxy to the black hole mass using the virial method/estimator, then we find \mbh = 6\E{7}$-$1.3\E{8}\,\Msun \citep{Peng06a, Dai10a}, depending on the normalization.
+
+%see Coppin08
+%see section 5.2 in Bothwell13a
+%
+{\bf compare to J04135 in R13} \\
+
+%--------------------------------------------------------------------------
+%                                Conclusions
+%--------------------------------------------------------------------------
+\section{Summary and Conclusions} \label{sec:sum}
+% see Hodge12_dynamics.pdf for guide
+
+We observe \bco and \cco line emisison toward the
+quadruply-lensed quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65 
+using the PdBI and CARMA, benchmarking the 
+first resolved interferometric CO imaging at intermediate redshift.
+The brightness temperature ratio between \bco and \cco of $r_{32}$ = BLAH, which taking into 
+account the large phase errors associated with \cco, is consistent with
+thermalized excitation between these lines in other ULIRGs.
+The (gas) mass ratio, the intrinsic CO line profile,
+and the source-plane velocity field are all evident of
+a minor merger, in good agreement with previous studies of RXJ1131 in the optical \citepalias{Claeskens06a,Brewer08a}.
+
+% explicit discussion of RXJ1131 being IR luminous, and gas-rich
+Our analysis of the cold gas kinematics and dynamics of RXJ1131 find 
+characteristics resembling a rotating disk. 
+The intrinsically symmetric double-horned line profile, the smooth and
+symmetric velocity field/gradient seen in both the source plane from our lens model as well
+as in the image plane, consistent with the findings from previous optical lens model 
+suggesting a kinematically-order rotating disk galaxy.
+The high dispersion $\gtrsim$400\,\kms near the dynamical center also
+suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. 
+Our results confirms the presence of the optically faint companion with CO detection
+suggested by previous studies. 
+Assuming same CO excitation, we find a gas mass of BLAH in
+the companion. Using the gas mass ratio of ($\sim$7:1)between RXJ1131 and the companion, this 
+implies the system is a wet minor merger.
+We thus conclude that RXJ1131 is a ULIRG hosting a massive gas reservoir in a disturbed/turbulent
+disk, undergoing merging with a nearby companion (aka a wet minor merger).
+
+The SFE is similar to that nearby spiral galaxies and high-$z$ disk-like galaxies rather than 
+ULIRGs or high-$z$ starbursts galaxies at $z$$\gtrsim$0.6. Implying BLAH
+Our result is consistent with the emerging consensus on
+the correlation between molecular gas content and redshift,
+suggesting it as the explanation for the elevated SFR at high redshift/
+the observed trend in the cosmic SFH.
+Given our large error bar on the gas mass fraction, we cannot constrain its evolution 
+but our result is consistent with a decreasing trend of gas fraction
+since $z$\,$\approx$\,1.0 \citep{Combes13a}; but is consistent with 
+in both ULIRGs samples in redshift bins of 0.2\,$<$\,$z$\,$<$\,0.4 and 0.6\,$<$\,$z$\,$<$\,1.0 within the uncertainties.
+
+The compact UV emission, which can be a starburst resulting from gas accumulation
+owing to a non-axisymmetric perturbation from the companion.
+% the stellar component torques away the angular momentum, allowing the gas to fall inward.
+Dusty nature of companion?
+The IR luminosity also agrees with the results from previous low-$z$ studies: AGNs are
+typically found in late stage mergers \citep{Yuan10a,Iwasawa11a,Carpineti12a} and
+only major mergers near their final coalescence can provide \LIR$>$\,10$^{12}$\,\Lsun,
+\citep[\eg][]{Carpineti15a,Larson16a}. In contrast to the 
+galaxies with ULIRG-like IR luminosity high-$z$, are believed to be in some stages of merging.
+
+The highly spinning black hole in RXJ1131 is also consistent with
+this hypothesis.
+If we favor the gravitational wave recoil mechanism
+to explain the optical velocity offset, it would also imply the black
+holes (and their host galaxies) have merged or are at their final coalescence.
+
+The optical lines are at a velocity offset of $\sim$780\,\kms from the systematic redshift is consistent 
+with possible black hole recoil. 
+Given the BLAH, it is plausible that RXJ1131 is in its late stage of merging and 
+possibly encountered with its companion previously, consistent with 
+compact SB traced by $V$-band image triggered by gas inflow/accumulation toward nuclear regions 
+arising from perturbations in the disk from/interactions with the companion.
+%Our results indicate a self-consistent picture of ...
+followed by gravitationally instability and SF in a massive, gas-rich disk and a subsequent build-up of a central bulge through inflow triggered by disk installbilities and/or minor merger.
+Theoretical simulations suggest disk in progenitor galaxy may be retained post-merging in gas-rich 
+mergers. BLAH. Thus, the merging system studied here will likely evolve into a merged disk galaxy.
+
+% broader
+Gas-rich major mergers are commonly likely the origins of high-$z$ quasar host galaxies as
+they are frequently observed with companions and from theoretical point of view. But considerate 
+interest in understanding the mechanisms in turning off \SF and AGN accretion since $z$$\sim$2, as 
+encoded in the \bhrelation. Thus, studies of galaxies at intermediate redshifts are crucial to 
+bridge the connection between local relation and high-$z$. 
+The study of this relation is hampered at intermediate redshift due to the difficulties in observing the 
+stellar emission in the host galaxy from the much brighter quasar. 
+The use of dynamical mass as a proxy to the \bhrelation have been proposed in a few high-$z$ studies 
+but requires resolved observations to provide constraints on the spatial extent tracing the potential of 
+the host galaxy. Lensing likely the the way to allow observations of quasar emission and 
+host galaxy emission. Dynamical lens modeling provides a promising avenue to study the velocity 
+structure and dynamics of the cold gas in greater detail. 
+To date, only a few other studies using similar techniques \eg other luminous,
+gas-rich interacting galaxies and mergers.
+This study of RXJ1131 serves as a benchmark/demonstrate the use of gravitational lensing and 
+dynamical lens modeling for further high-resolution molecular gas studies at 
+intermediate redshifts.  Similar resolved CO studies are needed to investigate the evolution in 
+the $M_{\rm BH}$$-$$M_{\rm dyn}$ relation to understand the co-evolution of SMBHs and their 
+host galaxies through cosmic time.
 
@@
 \acknowledgments
-This work is based on observations carried out under project number S14BX001
+This work is based on observations carried out under project number S14BX
 with the IRAM NOEMA Interferometer. IRAM is supported by INSU/CNRS (France), MPG (Germany) and IGN (Spain).

### 2016-07-05 WRITEUP/ms.tex
done intro sec

@@
 \begin{abstract}
-We report interferometric observations of \bco and \cco emission toward the gravitationally lensed 
+We present interferometric observations of \bco and \cco emission toward the gravitationally lensed 
 quasar RXS J1131-1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
-This is the first resolved \bco imaging at intermediate redshift.
+Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
+The molecular gas of $M_{\rm gas}$\eq123BLAH\E{10}\,\Msun in the host galaxy 
+is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
 RXS J1131-1231 ?. 
@@
 % Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
+The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
 % MBH-sigma relation...
@@
 \section{Introduction}
-Despite the recent progress in theoretical models and observational studies...on understanding the evolution of massive galaxies.
-% interplay between / role of Complex baryonic physics such as mergers, gas dissipation, and feedback..
-It is not known when and how the main baryonic components of modern galaxies formed/assembled, but the global 
-stellar mass density rose substantially between z\ssim1$-$3, reaching $\sim$50\% of its present value by z\ssim1 
-(\ie how high-z galaxies evolve into present-day galaxies.)
-As such, studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 is important to unravel/understand the cause for the rapid decline in star formation and BH accretion rates (e.g.
-Madau et al.
-1998, Hopkins \& Beacom 2006).
-Studies of galaxy evolution find SFRD and BHAH peak at
-$z$\ssim2 and declines rapidly toward $z$$=$0. A leading explanation for such
-a trend is the evolution of molecular gas content and SFE in galaxies (CW13).
-While we know blah at the local universe and studies of the gas properties at
-high-z are also emerging in recent years (see CW13 for a review). It is still
-unclear what mechanism is responsible for removing cold gas from galaxies and
-shutting down their star formation to build-up present-day red sequence
-galaxies, leading to a change of slope at high \mstar (esp. at $z$ $<$ 1.5),  i.e.
-suppression of SFR at high \mstar, i.e. strong evolution in sSFR (of massive gal.)
-(cite: Papovich, Whitaker+12, Magnelli+14, Schreiber+15, Lee+15).
-It has been proposed that the high SFR at high-$z$ is due to the higher gas fraction than local (Erb et al. 2006), 
-regardless of their position in the SFR$-$M$^*$ plane, both MS and SB at high z have depletion time that is much 
-short than local, suggesting more efficient mode for SF. 
-Up to now, very little is known about the molecular gas content at moderate z.
-The ULIRG sample of Solomon97 contains 37 objects, but only 2 at are z $>$ 0.2.
-With the advance in mm-instruments, Combes11a investigate the variation of molecular gas and SFE in an expanded sample of 30 ULIRGs with CO observations.
-
-%why AGN host 
-In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, 
-where distant QSOs are the progenitors of the passive SMBHs in nearby galaxies.
-Locally, the connection between AGNs and their host galaxies is described 
-through the well-established tight correlation between BH mass 
-and stellar velocity dispersion (CITE), implying growth of the SMBH and their host galaxies is co-eval.
-However, it is unclear if this relation holds/or how the co-evolution BLAH at high-$z$.
-Recently, theoretical and observational studies of the co-evolution of SMBHs and their host galaxies
-have been attempting to extend this relation out to higher-$z$, beyond the peak epoch 
-of \SF and AGN activity (CITE).
-
-% difference proxy to the relation
-Since it is not trivial to obtain measurement of stellar dispersion (rely on spatially resolved stellar kinematics) at high-$z$, 
-efforts in calibrating and understanding how 
-the use of dynamical mass or stellar bulge mass \citep[\eg][]{Peng06a} or 
-stellar luminosity as a proxy for stellar dispersion.
-At high-$z$, more CO measurements have been obtained at high-z, and
-one can obtain dynamical mass through CO linewidth and spatial extent.
-
-Based on the \mbh$-$\mdyn relation, there are considerable evidence now that high-z BHs grow faster than their host galaxies.
-The dynamical mass inferred from CO velocity structure (line width) and spatial extent is lower than that 
-based on local relation. 
-Current results imply high-$z$ galaxies ($z$$>$BLAH) do not follow this relation, where their observed $M_\textrm{dyn}$ is lower than that inferred from
-this relation or \mbh$/$$M_{*}$ is smaller high-$z$ than today \citep{Borys05a}. 
-This implies that a quasar phase is needed in order for high-z galaxies to evolve 
-onto the local \mbh$-$$M_{\rm bulge}$ relation / high-$z$ BH grow faster than their host galaxies, 
-as predicted in simulations where feedback is needed in order to explain the 
-anti-hierarchical growth of galaxies / suppress efficient early star formation
-and the lack of more massive galaxies as would be produced without feedback. 
-But how investigate this evolution at intermediate redshift is challenging,
-because it also suffers the same cosmological dimming issue at high-$z$ studies, time-consuming to obtain
-resolved CO observations for intermediate-z.
-
-One way to understand is to investigate the relation as different epochs more closely.
-We still lack a clear picture of relationship between AGN and hosts since we do not know much at the intermediate redshifts where both \SF and AGN accretion slow down.
-It appears that there may be a decreasing trend from $z$$>$3 to 1$<$3 and compared to the local fit.
-But it is clear that there is a desert in between these redshift range.
-
-Host galaxies of AGN are difficult to study because the quasar usually dominates the observed light, and ?.
-With gravitational lensing, the stellar emission and quasar emission in RXJ1131 
-are magnified and stretched out at different locations to different extents in the image plane, gaining 
-the surface brightness contrast to enable measurements of their emission separately.
-RXJ1131 thus provide a unique laboratory to study the ?
-
-%--------
-In this paper, we explore the well-established local BLAH relations to intermediate redshift
-and investigate the postulated decrease gas fraction from BLAH studies at intermediate 
-redshift.
-We use BLAH to study the ISM properties of the quadruply imaged
-quasar RXS J113151.62-123158 (hereafter RXJ1131) at
-$z_\textrm{s, QSO}$\eq0.685, lensed by an
-elliptical galaxy at $z_\textrm{L}$\eq0.295. The redshifts 
+Studies of galaxy evolution have been focusing on the interplay between baryonic physics
+(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
+It is not well-understood when and how baryons of present-day galaxies were assembled, 
+but it is clear that both the co-moving \SF rate and black hole accretion rate densities
+increased substantially since $z$\,$>$\,3 and reached their climax at $z$\ssim2, followed by 
+a rapidly decline toward $z$\ssim0 \citep[\eg][]{Hopkins06a, Madau14a}. 
+% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
+A leading explanation for this decline is related to the evolution of molecular gas content and 
+\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
+but confirmation from direct molecular gas measurements at intermediate redshift 
+$($0.2\,$<$\,$z$\,$<$\,1$)$ is still limited both in number and in the variety of galaxy populations probed --- 
+only unresolved CO observations have been carried out for $\sim$\,70 ULIRGs up to date \citep{Combes11a, Combes13a}.
+
+% - nearby: fixed proportion in M_BH to the M* in the bulge: ~0.1-0.2%
+In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
+grows by accretion of the cold molecular gas from its host galaxy.
+Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
+--- a tight correlation between black hole mass and stellar bulge mass ---
+have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
+Attempts to extend this relation out to higher redshifts, beyond the peak epoch 
+of \SF and AGN activity, have been made in recent years.
+It has been reported that the $M_{\rm BH}$$/$\mstar ratio of high-$z$ galaxies falls below 
+the local relation \citep[\eg][]{Walter04a, Borys05a, Riechers08a, Riechers08b}, implying 
+high-$z$ AGNs grow faster than their host galaxies.
+Yet, this relation is currently unconstrained at intermediate redshifts owing to the difficulties in measuring 
+the stellar emission in the host galaxy under the presence of a quasar, or alternatively
+the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
+With gravitational lensing, emission of the background quasar and its host galaxy 
+is magnified and stretched out to different extents, and is projected to different locations in the image plane.
+This in effect increases the surface brightness contrast between their emission and allows for
+their measurements in a relatively uncontaminated/independent manner.
+
+In this paper, we study the molecular gas and dust properties of the quadruply imaged
+quasar RXS J113151.62$-$123158 (hereafter RXJ1131) at
+$z_\textrm{s, QSO}$\eq0.685 as lensed by an
+elliptical galaxy at $z_\textrm{L}$\eq0.295. These redshifts 
 are spectroscopically confirmed by \citet[hereafter S03]{Sluse03a}.
-Emission in the host galaxy of RXJ1131 is lensed into an Einstein ring of size 1\farcs83 in radius.
+In the {\it HST} images presented by \citet[hereafter C06]{Claeskens06a}, emission 
+in the host galaxy of RXJ1131 is lensed into an Einstein ring of size 1\farcs83 in radius and
+the quasar emission is lensed into four point-like images.
 The black hole of mass \mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
@@
 \citep[$a$\,$\sim$\,0.9;][]{Reis14a}.
-\defcitealias{Sluse03a}{S03}
 
 This paper is structured as follows.
-In \Sec{obs} and \Sec{HST}, we outline the details of the observations and data reduction process.
+In \Sec{obs}, we outline the details of the observations and our data reduction process.
+In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our radio maps.
 In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths.
-In \Sec{anal}, we present dynamical lens modeling of the \bco data and the physical properties inferred for  RXJ1131.
-In \Sec{diss}, we discuss the results and implications of this study in the context of molecular gas in mergers and ULIRGs {\bf BLAH}.
-Finally, we summarize the main results of this study and present our conclusions in \Sec{sum}.
+In \Sec{anal}, we present dynamical lens modeling of the \bco data, SED modeling of the thermal dust continuum, 
+and the resulting physical properties inferred for RXJ1131.
+In \Sec{diss}, we discuss the merger stage of RXJ1131 and implications of 
+this study in the context of the evolution of molecular gas content
+and the $M_{\rm BH}$$-$\mdyn relation at intermediate redshift.
+Finally, we summarize the main results and present our conclusions in \Sec{sum}.
 We use a concordance $\Lambda$CDM cosmology throughout this paper, with
@@
 % same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
+\defcitealias{Sluse03a}{S03}
+\defcitealias{Claeskens06a}{C06}
 
@@
 therefore treat its line intensity with caution and ensure that our physical interpretation
-of this system does not rely on this quantity.
+of this system and the conclusion of this do not rely on this quantity.
 
@@
 The details of the observations can be found
-in \citet[hereafter C06]{Claeskens06a}.
+in \citetalias{Claeskens06a}.
 We adopt the VLA 5\,GHz map as the
@@
 instability.
-\defcitealias{Claeskens06a}{C06}
 
@@
 We detect \bco line emission toward the background source
-at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
+at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
 0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
@@
 A detailed discussion of this effect is presented in
-\Sec{differential} and the magnification factors for various kinematic
-components are listed in \Tab{model}.
+\Sec{differential}.
  \label{fig:CO21spec}}
@@
 
-The deconvolved source size FWHM from two-dimensional Gaussian fitting
-is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
+The deconvolved source size FWHM from fitting a two-dimensional Gaussian
+is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
 and thus, the emission is resolved over $\sim$2.2 beams.
-While the lensed emission is not strictly distributed as two-dimensional
+While the lensed emission is not strictly distributed as a two-dimensional
 Gaussian;
@@
 region, we therefore take this as an estimate on the extent of the lensed
-emission. On the other hand, if we assume the spatial distribution of
+emission. On the other hand, if we assume that the spatial distribution of
 the lensed molecular gas emission is similar to that in the optical to \nir
@@
 after subtracting a contribution from its companion galaxy and 
-correcting for lensing using the magnification factors $\mu_{\rm L}$ as annotated with horizontal bars
-above the respective model channels. Flux density is shown on a log scale along the y-axis.
+correcting for lensing using the magnification factors $\mu_{\rm L}$ as annotated by the horizontal bars shown
+above the respective model channels. Flux density on the y-axis is shown on a log scale.
 \label{fig:delensed}}
@@
 % \citep[78\pmm26;][]{Bothwell13a} 
-\citep[hereafter B13]{Bothwell13a} and
+\citep[]{Bothwell13a} and
 local ULIRGs \citep{Wilson08a}, but lower than of the Milky Way by
@@
 \subsection{The \bhrelation Relation}
-
 Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
 The dusty nature of this system?? \\
+
+Efforts have been invested into calibrating and understanding how 
+the use of or dynamical mass \citep[\eg]{Shields06a} 
+as a proxy for stellar dispersion or bulge mass.
 
@@
 % explicit discussion of RXJ1131 being IR luminous, and gas-rich
-Our analysis of the cold gas kinematics and dynamics of RXJ1131 find 
-characteristics resembling a rotating disk. 
 The intrinsically symmetric double-horned line profile, the smooth and
 symmetric velocity field/gradient seen in both the source plane from our lens model as well
-as in the image plane, consistent with the findings from previous optical lens model 
-suggesting a kinematically-order rotating disk galaxy.
-The high dispersion $\gtrsim$400\,\kms near the dynamical center also
-suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. 
-Our results confirms the presence of the optically faint companion with CO detection
-suggested by previous studies. 
-Assuming same CO excitation, we find a gas mass of BLAH in
-the companion. Using the gas mass ratio of ($\sim$7:1)between RXJ1131 and the companion, this 
-implies the system is a wet minor merger.
-We thus conclude that RXJ1131 is a ULIRG hosting a massive gas reservoir in a disturbed/turbulent
+as in the image plane are characteristics resembling a rotating disk, 
+consistent with the findings from previous optical lens model.
+The high dispersion $\gtrsim$400\,\kms near the dynamical center suggest that 
+RXJ1131 is turbulent, albeit lack of spatial resolution. 
+Our lens modeling analysis also confirms the presence of the optically faint companion 
+suggested by previous studies, with CO emission.
+Assuming the same CO excitation as RXJ1131 for the companion, we find a gas mass of BLAH,
+which implies a gas mass ratio of ($\sim$7:1) between RXJ1131 and the companion. 
+We thus classify the system is a wet minor merger.
+We conclude that RXJ1131 is a ULIRG hosting a massive gas reservoir in a disturbed/turbulent
 disk, undergoing merging with a nearby companion (aka a wet minor merger).
 
-The SFE is similar to that nearby spiral galaxies and high-$z$ disk-like galaxies rather than 
-ULIRGs or high-$z$ starbursts galaxies at $z$$\gtrsim$0.6. Implying BLAH
+While many characteristics of RXJ1131 resembles local ULIRGs and high-z SBs (such as 
+linewidth, CO sizes, SFR, gas mass), its SFE is similar to that nearby 
+spiral galaxies and high-$z$ disk-like galaxies rather than 
+ULIRGs or high-$z$ starbursts galaxies at $z$$\gtrsim$0.6. 
 Our result is consistent with the emerging consensus on
@@
 \citep[\eg][]{Carpineti15a,Larson16a}. In contrast to the 
-galaxies with ULIRG-like IR luminosity high-$z$, are believed to be in some stages of merging.
-
+galaxies with ULIRG-like IR luminosity at high redshifts, which can be in early stages of merging.
+
+We find that the optical lines are offset from the systemic redshift by $\sim$780\,\kms, (caution use of optical lines 
+as systemic redshift)
+may imply a recoiling black hole in RXJ1131, which would imply the black
+holes (and their host galaxies) have merged or are at their final coalescence.
 The highly spinning black hole in RXJ1131 is also consistent with
 this hypothesis.
-If we favor the gravitational wave recoil mechanism
-to explain the optical velocity offset, it would also imply the black
-holes (and their host galaxies) have merged or are at their final coalescence.
-
-The optical lines are at a velocity offset of $\sim$780\,\kms from the systematic redshift is consistent 
-with possible black hole recoil. 
-Given the BLAH, it is plausible that RXJ1131 is in its late stage of merging and 
+Given the presence of a companions, it is plausible that RXJ1131 is in its late stage of merging and 
 possibly encountered with its companion previously, consistent with 
@@
 % broader
-Gas-rich major mergers are commonly likely the origins of high-$z$ quasar host galaxies as
-they are frequently observed with companions and from theoretical point of view. But considerate 
-interest in understanding the mechanisms in turning off \SF and AGN accretion since $z$$\sim$2, as 
-encoded in the \bhrelation. Thus, studies of galaxies at intermediate redshifts are crucial to 
-bridge the connection between local relation and high-$z$. 
-The study of this relation is hampered at intermediate redshift due to the difficulties in observing the 
-stellar emission in the host galaxy from the much brighter quasar. 
 The use of dynamical mass as a proxy to the \bhrelation have been proposed in a few high-$z$ studies 

### 2016-07-06 WRITEUP/ms.tex
udpated Intro based on suggestion from DR via skype

@@
 \citestyle{aa}
-\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131-1231 at $z$\,=\,0.65}
+\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131$-$1231 at $z$\,=\,0.65}
 \shortauthors{Leung \& Riechers}
@@
 
-\title{Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131-1231 at $z$=0.654}
+\title{Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654}
 \author{T. K. Daisy Leung and Dominik A. Riechers}
@@
 \begin{abstract}
-We present interferometric observations of \bco and \cco emission toward the gravitationally lensed 
-quasar RXS J1131-1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
+We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
+RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
+RXJ1131 is gravitationally lensed quasar.
 Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
@@
 is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
-RXS J1131-1231 ?. 
-evidence for differential lensing.
-wet-merger, Dynamical lens modeling
-the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
+RXS J1131-1231 a wet-merger, 
+Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
 is indicative of, and suggests...
@@
 
-% - nearby: fixed proportion in M_BH to the M* in the bulge: ~0.1-0.2%
 In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
@@
 of \SF and AGN activity, have been made in recent years.
-It has been reported that the $M_{\rm BH}$$/$\mstar ratio of high-$z$ galaxies falls below 
-the local relation \citep[\eg][]{Walter04a, Borys05a, Riechers08a, Riechers08b}, implying 
-high-$z$ AGNs grow faster than their host galaxies.
-Yet, this relation is currently unconstrained at intermediate redshifts owing to the difficulties in measuring 
-the stellar emission in the host galaxy under the presence of a quasar, or alternatively
-the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
+It has been reported that the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of high-$z$ submillimeter galaxies (SMGs) falls below 
+the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies are found 
+lying above 
+the relation \citep[\eg][]{McLure06a,Peng06a}.
+Stellar mass of quasar host galaxies at $z$\,$>$\,4 constrained by their CO-based dynamical mass 
+are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
+It is evident that high-$z$ galaxies deviates from the local relation, and among their galaxy populations, but
+the AGN-host galaxy connection at intermediate redshift is still poorly-constrained. 
+This owes to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
+owing to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
 With gravitational lensing, emission of the background quasar and its host galaxy 
 is magnified and stretched out to different extents, and is projected to different locations in the image plane.
-This in effect increases the surface brightness contrast between their emission and allows for
-their measurements in a relatively uncontaminated/independent manner.
-
-In this paper, we study the molecular gas and dust properties of the quadruply imaged
-quasar RXS J113151.62$-$123158 (hereafter RXJ1131) at
-$z_\textrm{s, QSO}$\eq0.685 as lensed by an
-elliptical galaxy at $z_\textrm{L}$\eq0.295. These redshifts 
-are spectroscopically confirmed by \citet[hereafter S03]{Sluse03a}.
-In the {\it HST} images presented by \citet[hereafter C06]{Claeskens06a}, emission 
-in the host galaxy of RXJ1131 is lensed into an Einstein ring of size 1\farcs83 in radius and
-the quasar emission is lensed into four point-like images.
-The black hole of mass \mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
+This in effect increases the surface brightness contrast between their emission and allows for the
+relatively uncontaminated measurements of their emission.
+
+\defcitealias{Sluse03a}{S03}
+The ``Einstein ring'' RXS J113151.62$-$123158 (hereafter RXJ1131) 
+at $z_\textrm{s, QSO}$\eq0.685 \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
+studying the evolution of molecular gas properties in quasar host galaxies and the 
+connection between SMBHs and their host galaxies at intermediate redshift
+given its unique lensing configuration and its redshift.
+The stellar emission in the host galaxy of RXJ1131 is lensed into
+an Einstein ring of radius 1\farcs83
+that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
+We have thus carried out a detailed study for RXJ1131, as presented in this paper.
+RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq0.295 \citepalias{Sluse03a}.
+The black hole residing in RXJ1131 is rotating with a high spin parameter
+\citep[$a$\,$\sim$\,0.9;][]{Reis14a}. 
+Previous studies also report a black hole mass of
+\mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
 mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
@@
 AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
-assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}
-residing in RXJ1131 has been observed to 
-be rotating with a high spin parameter
-\citep[$a$\,$\sim$\,0.9;][]{Reis14a}.
+assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}.
 
@@
 In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our radio maps.
-In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths.
+In \Sec{results}, we report measurements of the \bco and \cco lines and a compilation of photometric data from optical to radio wavelengths.
 In \Sec{anal}, we present dynamical lens modeling of the \bco data, SED modeling of the thermal dust continuum, 
 and the resulting physical properties inferred for RXJ1131.
-In \Sec{diss}, we discuss the merger stage of RXJ1131 and implications of 
+In \Sec{diss}, we discuss the merger stage of RXJ1131, and the implications of 
 this study in the context of the evolution of molecular gas content
@@
 % same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
-\defcitealias{Sluse03a}{S03}
 \defcitealias{Claeskens06a}{C06}
@@
 based on \bco and compare them with those reported by
-C13 --- the largest sample of ULIRGs at similar redshift
+\citetalias{Combes13a} --- the largest sample of ULIRGs at similar redshift
 (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
@@
 \bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun. %calc. using 2.32e5*6.22 * 200^2
 We derive an inclination angle of 56.4$\degr$ from the
@@
 $V$-band lens model \citepalias{Brewer08a},
-we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 5\E{6}\,\Msun.
-This corresponds to $M_{\rm dyn}$\,=\,2\E{7}\,\Msun if we assume an
+we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
+This corresponds to $M_{\rm dyn}$\,=\,5.8\E{8}\,\Msun if we assume an
 inclination angle of 30$\degr$.
 We adopt the $V$-band size as the radius $R$ in the above estimate 
-owing to the fact that it is the least uncertain source size constraint available for the companion.
+owing to the fact that it is the least uncertain constraint on the source size for the companion.
 However, since this dynamical mass is substantially lower than the gas mass, which is 
@@
 we do not use this dynamical mass to derive other physical parameters.
-The inconsistency between the gas mass of the companion and its dynamical mass
-may indicate its dusty nature, which causes the $V$-band source size to 
+The underestimated dynamical mass may reflect
+the dusty nature of the companion, which causes its $V$-band source size to 
 appear much smaller than its true extent without any dust obscuration.
-% On the other hand, we find a half-right radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from our lens 
-% model, which can only serve as a crude measure of its unobscured source size (see \Sec{caveat}).
-Using this CO size, we find a dynamical mass of $M_{\rm dyn}$\,=\,3\E{7}\,\Msun.
-WHICH is STILL LOWER THAN the GAS MASS?
+If we use the half-right radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc obtained from our best-fit lens 
+model as the unobscured source size (see \Sec{caveat}), we find a dynamical mass of 
+$M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun (assuming $i$\eq30$\degr$), which is physically more sensible 
+than that derived using the $V$-band source size. 
+The uncertainty here only includes that of the CO source size.
+Given the large systematic uncertainties associated with the model-based source size and
+the lack of constraint on the inclination angle, we do not use this dynamical mass in the remaining of this paper.
 
@@
 If we adopt a dust mass from the other SED fit (\ie without constraints at 24\,$\micron$),
-the dust mass is reduced by a factor of $\sim$2. \defcitealias{Bothwell13a}{B13}
+the dust mass would reduce by a factor of $\sim$2. \defcitealias{Bothwell13a}{B13}
 
@@
 \section{Discussion} \label{sec:diss}
-\subsection{Fate of RXJ1131-1231}
+\subsection{Fate of RXS J1131$-$1231}
 The classical picture for mergers is one where they are responsible for the formation of the local
@@
 
-\subsection{The \bhrelation Relation}
+\subsection{The $M_{\rm BH}$$-$\mdyn Relation}
+% the gas mass of RXJ1131 is 1.3\E{10}\,\Msun, 
+% dynamical mass in RXJ1131 is $\sim$8.3\E{10}\,\Msun 
+% total dust mass in the merging system is $\sim$2-4\E{8}\,\Msun,  % using CO magnification factor
+Assuming RXJ1131 follows the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation reported by \citet{HR04a}, 
+the virial-based black hole mass \mbh$\sim$\,6\E{7}\,\Msun \citep{Peng06a} corresponds 
+to a stellar bulge mass of $M_{\rm bulge}$\eq4.2\E{10}\,\Msun.
+This implies that the bulge component is responsible for making up roughly half the dynamical mass. 
+If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass.}
+from the dynamical mass and ignore a contribution from the dark matter, this would
+yield an upper limit on the stellar mass of 6.8\E{10}\,\Msun. 
+Thus, the bulge mass derived above based on the local relation is not physically infeasible.
+The stellar mass upper limit would also imply a lower limit on the 
+$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.09\%, which falls below the local relation 
+but is consistent within the range found in other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
+A dark matter fraction of over $f_{\rm DM}$\ssim0.6 would be needed for RXJ1131 to 
+lie above the local relation and fall outside the range of $M_{\rm BH}$$/$$M_{\rm bulge}$ found in 
+\citep{McLure06a}. 
+% local: $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.14\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.85,
+
+\subsection{Dynamical lens modeling of high-$z$ quasars}
+%
+Riechers08a is the only other similar system at emission in host galaxy lensed into an Einstein ring configuration and
+with dynamical lens modeling of CO.
+Which also velocity gradient.
+Constraints on the.
+
+\subsection{Others}
 Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
 The dusty nature of this system?? \\
-
-Efforts have been invested into calibrating and understanding how 
-the use of or dynamical mass \citep[\eg]{Shields06a} 
-as a proxy for stellar dispersion or bulge mass.
-
-\citet{Shields06a} investigate the \bhrelation relation to high-$z$ using CO line width since 
-CO has been detected in over hundreds of galaxies at $z$$>$1.
-From their results, the dynamical mass from CO line widths is 
-smaller than would be expected by the local relation, but they also noted it is possible that the stellar dispersion is
-underestimated (see section 2.3 in Shields06a).
-
-If we follow their approach, and use the CO linewidth to derive $\sigma_*$, assuming FWZI = 2$v_\textrm{rot}$, then the stellar dispersion is related to the CO dispersion via 
-$\sigma_*$ = 4.44$\sigma_{\rm CO}$.
-% FWHM ~ 2/3 FWZI; FWZI = 2*v_cir = 2sqrt(2) * sigma_*;  => FWHM ~ 0.53 sigma_*.
-% where CO dispersion = FWHM/2.355 ---> sigma_* = 4.44 * CO dispersion.
-, we find?.
-
-If we adopt the broad H$\beta$ line as a proxy to the black hole mass using the virial method/estimator, then we find \mbh = 6\E{7}$-$1.3\E{8}\,\Msun \citep{Peng06a, Dai10a}, depending on the normalization.
-
-%see Coppin08
-%see section 5.2 in Bothwell13a
-%
+compare to Riechers08a \\=
 {\bf compare to J04135 in R13} \\

### 2016-07-07 WRITEUP/ms.tex
update MBH-Mbulge using updated MBH from Sluse07, updated intro, update velocity offset

@@
 Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
+turbulent disk
 is indicative of, and suggests...
@@
 \section{Introduction}
-Studies of galaxy evolution have been focusing on the interplay between baryonic physics
+Studies of galaxy evolution have been focusing on the interplay between baryonic physics/process
 (\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
@@
 
-In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
-grows by accretion of the cold molecular gas from its host galaxy.
+% In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
+% grows by accretion of the cold molecular gas from its host galaxy.
 Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
@@
 are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
-It is evident that high-$z$ galaxies deviates from the local relation, and among their galaxy populations, but
-the AGN-host galaxy connection at intermediate redshift is still poorly-constrained. 
+While it has become clearer that high-$z$ galaxies deviates from the local relation, and among their galaxy populations, 
+such a picture is still unclear  at intermediate redshift.
 This owes to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
@@
 With gravitational lensing, emission of the background quasar and its host galaxy 
-is magnified and stretched out to different extents, and is projected to different locations in the image plane.
+is magnified and stretched out to different extents, and is projected onto different locations in the image plane.
 This in effect increases the surface brightness contrast between their emission and allows for the
@@
 connection between SMBHs and their host galaxies at intermediate redshift
-given its unique lensing configuration and its redshift.
+given its unique lensing configuration.
 The stellar emission in the host galaxy of RXJ1131 is lensed into
@@
 that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
-We have thus carried out a detailed study for RXJ1131, as presented in this paper.
+We have thus carried out a detailed study for RXJ1131 as presented in this paper.
 RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq0.295 \citepalias{Sluse03a}.
-The black hole residing in RXJ1131 is rotating with a high spin parameter
-\citep[$a$\,$\sim$\,0.9;][]{Reis14a}. 
-Previous studies also report a black hole mass of
-\mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
-mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
-\mbh\ssim10$^{8}$\,\Msun using the virial estimator with H$\beta$ linewidth,
-and \citet{Pooley07a} report $M_{\rm BH}$\,=\,2.5\E{7}\,\Msun using the
-AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
-assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}.
+The moderate mass black hole $M_{\rm BH}$\eq8\E{7}\Msun \citep{Sluse12a} %based on H beta line
+residing in RXJ1131 is rotating with a high spin parameter \citep[$a$\,$\sim$\,0.9;][]{Reis14a}, and
+is radiating at an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq1.3\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.
 
@@
 and check for chain convergence by inspecting trace plots
-and requiring the samples are beyond at least an autocorrelation time.
+and by requiring the samples are obtained beyond at least an autocorrelation time.
 We thus employ $\sim$50,000 samples as the initial ``burn-in'' phase
@@
 $V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
-radius at which the rotation curve becomes flat.
+radius at which the rising part of the curve begins to flatten.
 We perform non-linear least square fitting using an orthogonal distance
@@
 However, since emission is not resolved along the flat regime
-of the rotation curve, the asymptotic velocity is poorly constrained and
-the ``turnover'' radius is at most an upper limit.
+of the rotation curve, the asymptotic velocity
+and the ``turnover'' radius are poorly constrained.
 In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
@@
 terminology) since this corresponds to the radius at which the velocity
-of a pure exponential disk peaks \citep{Courteau97b}.
-We here adopt the maximum {\em observed} velocity
+of a pure exponential disk peaks \citep{Courteau97b}. % \ie commonly use Vmax (taken at R2.2) as V_rot
+Here, we adopt the maximum {\em observed} velocity
 $V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
 dynamical center as a proxy to the rotation velocity.
-This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
+This radius corresponds to $\sim$0.6\,$R_e$, where $R_e$ is the half-light
 radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
@@
 of a spiral galaxy and that nuclear starbursts (in the inner few kpc) can be triggered 
-in a later time as the progenitor disk galaxy interacts with other galaxies, 
-and thereby forming a larger bulge.
+at a later time as the progenitor disk galaxy interacts with other galaxies to form a larger bulge.
 
@@
 \subsection{Velocity Offset and a Recoiling Black Hole}
-Using the CO line center redshift as the systemic redshift, we find
-a velocity offset of $\sim$780\,\kms from the optical
-\mgii line and the \oiii lines \citepalias[$z_{\rm QSO} = 0.658$;][]{Sluse03a}. This implies that the AGN is dynamically offset from the centroid of its host galaxy. 
-From the CO channel maps in \Fig{CO21mom} and \Fig{chanmap}, it is also apparent that the 
-line center of the gas is not co-spatial with the optical quasar as the point-like images
-along the lensing arc
-are spatially offset to the NW of the CO line center.
-While spatial offsets between optical lines and CO line
-have been reported in other galaxies, the velocity offsets are typically $\lesssim$\,500\kms.
-{\bf
-In the classical SDSS analysis for line offsets \citep{Richards02a}?.
-\oiii and \mgii analysis \citep{Boroson05a, Bae14a}?.
-with the corresponding trends and possible explanations?.
-More extreme offsets between CO and optical lines have been seen \citep{Hainline04a} 
-or between \cii and \mgii \citep[\eg][]{Venemans16a}.}
-For instance, the
-velocity offset in
-an SDSS sample of ongoing mergers at $z$\,$<$\,0.21 is at most $\sim$410\,km/s \citep{Comerford14a}.
-
-A large velocity offset can also result from a recoiling black hole (BH) where its broad line region
-is moving at high velocity relative to the bulk of its host galaxy 
+%Outflow:
+% Not AGN outflows because require different velocity offsets in Balmer and forbidden lines (Zamanov02a)
+% line origins:
+% \mgii & Hbeta: outer part of the BLR (Goad12a) compared to high-ionization lines (\eg CIV)
+% Hbeta can also come from NLR
+
+\defcitealias{Sluse07a}{S07}
+\citet[hereafter S07]{Sluse07a} report two sets of AGN lines observed in RXJ1131. 
+The first set of lines is at $z$\ssim0.653, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
+the \mgii emission line.
+Using the CO line center redshift as the systemic redshift, the second set of lines is blueshifted by $\sim$780\,\kms.
+This implies 
+that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.
+We confirm this spatially in the channel maps in \Fig{CO21mom} and 
+\Fig{chanmap}, where the line center of the CO gas is not co-spatial 
+with the optical quasar --- the point-like images along the lensing arc is 
+offset to the NW of the CO line center emission. 
+On the other hand, we find that the redshift of the \oiii lines tracing the narrow line region (NLR) 
+is fully consistent with the systemic redshift, supporting previous claims that \oiii lines are good proxies
+to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
+% since BLR are gravitationally bound to BH, and NLR may not be
+
+%Velocity Offsets of $\lesssim$\,500\,\kms in other AGNs and their host galaxies have been reported in the literature.
+%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s 
+%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
+
+Large velocity offsets between emission lines of the
+BLR and the NLR may arise in a recoiling black hole (BH),
+% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines (e.g., Gaskell 1983; Bonning et al.
+2007; Eracleous et al.
+2012; Ju et al.
+2013; Shen et al.
+2013).
+where its BLR is moving at high velocity relative to the bulk of its host galaxy 
 \citep{Madau04a, Bonning07a, Loeb07a}.
-Such a scenario is expected to occur 
+A recoiling black hole is expected 
 when a pair of uneven mass BH coalesce, during which their orbital energy is being released 
@@
 the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
-%While such large velocity offsets are theoretically achievable,
-%they are not commonly observed --- only a few objects 
-%have been reported with optical offsets $\gtrsim$1000\,\kms. For instance,
-%the most promising candidate with both spectroscopy and imaging
+Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
+SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
+%To date, the most promising candidate with both spectroscopy and imaging
 %signatures of a recoiling BH is CID-42 at $z$\,=\,0.359, with 
 %an offset of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ \citep{Civano10a}.
-%Other example includes the type-1 QSO SDSS 0956+5127 at $z$\,$\sim$\,0.714, with an offset of 1200\,\kms
-%between Mg{\scriptsize II}~2798\AA\ and $[$O{\scriptsize III}$]$~4959, 5007\AA\ lines
-%\citep{Steinhardt12a}. % but here its between CO and optical lines
-%% SDSSJ0927+2943 at $z$\,$\sim$\,0.713, with an offset of 2650\,\kms \citep{Komossa08a}, but disproved by Decarli+14; Hence, I am going to cut this out because I listed this source here just to demonstrate the scarcity of high velocity offsets; but the offset in this system is between a set of redshifted versus a set of blueshifted..
-which is not quite the same our case here.
+%This is similar to the case here for RXJ1131, where the two components of H$\beta$ are offset by 
+%\ssim550\,\kms.
+%Other example of recoiling BH 
+%includes the type-1 QSO SDSS 0956+5127 at $z$\,$\sim$\,0.714, with an offset of 1200\,\kms 
+%between \mgii and \oiii lines \citep{Steinhardt12a}.
+One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, \citet{Komossa08a} 
+suggest the possibility of a recoiling black hole in this system due to an offset of 2650\,\kms 
+between a set of narrow emission lines and a second set of broad Balmer 
+and high-ionization forbidden lines.  % offset in this system: between a set of redshifted (narrow) versus a set of blueshifted (broad).
+However, this scenario is refuted recently by \citet{Decarli14a}, who confirm that the
+BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
+This is in contrast with the case in RXJ1131, our CO observations confirm the blueshifted BLR lines.
 The fact that the BH in RXJ1131 has a high spin parameter \citep{Reis14a}
-renders this scenario a viable option for the origin
-of the velocity offset. 
-However, since this model requires a merged BH, this interpretation would imply RXJ1131 have 
-already encountered with the companion galaxy, which is consistent with
+renders the recoiling BH scenario a viable option for the origin of the blueshift. 
+Since this model requires a merged BH, this interpretation would imply RXJ1131 have 
+already encountered with the companion galaxy, which could explain
 the highly spinning BH observed in RX1131.
-Given the presence of a nearby companion observed in our data, the system may be in its 
+In this picture, the presence of a nearby companion observed in our data may reflect that RXJ1131 is in its 
 subsequent stages of (minor) merging resulting from previous passage of a major merger.
-
-As demonstrated here using \mgii and \oiii lines, large velocity offsets between CO and optical lines may be present.
-We thus caution against the use of optical lines as 
-true systematic redshift indicators as the resulting redshift can deviate from the 
-true value.
 
@@
 Assuming RXJ1131 follows the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation reported by \citet{HR04a}, 
-the virial-based black hole mass \mbh$\sim$\,6\E{7}\,\Msun \citep{Peng06a} corresponds 
-to a stellar bulge mass of $M_{\rm bulge}$\eq4.2\E{10}\,\Msun.
-This implies that the bulge component is responsible for making up roughly half the dynamical mass. 
-If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass.}
+the virial-based black hole mass \mbh$\sim$\,8\E{7}\,\Msun \citep{Sluse12a} corresponds 
+to a stellar bulge mass of $M_{\rm bulge}$\eq5.4\E{10}\,\Msun.
+% \ie $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.15\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.83
+This implies that the bulge component is responsible for making up $\sim$65\% of the dynamical mass. 
+If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass.
+Since the dust mass only contributes a small fraction of the total mass, a factor of $\sim$2 difference is minor.}
 from the dynamical mass and ignore a contribution from the dark matter, this would
 yield an upper limit on the stellar mass of 6.8\E{10}\,\Msun. 
-Thus, the bulge mass derived above based on the local relation is not physically infeasible.
+Thus, the bulge mass derived above based on the local relation is not unphysical.
 The stellar mass upper limit would also imply a lower limit on the 
-$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.09\%, which falls below the local relation 
-but is consistent within the range found in other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
-A dark matter fraction of over $f_{\rm DM}$\ssim0.6 would be needed for RXJ1131 to 
+$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.12\%, which is consistent with the local relation within the scatter and with other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
+%Depending on the exact dark matter fraction, RXJ1131 may lie above the local $M_{\rm BH}$/$M_{\rm bulge}$.
+
+A dark matter fraction of over $f_{\rm DM}$\ssim0.5 within the radius of which we used to derive the 
+dynamical mass (\ie $\lesssim$\,6\,kpc or $\sim$\,0.6$R_e$) would be required for RXJ1131 to 
 lie above the local relation and fall outside the range of $M_{\rm BH}$$/$$M_{\rm bulge}$ found in 
-\citep{McLure06a}. 
-% local: $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.14\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.85,
-
-\subsection{Dynamical lens modeling of high-$z$ quasars}
-%
-Riechers08a is the only other similar system at emission in host galaxy lensed into an Einstein ring configuration and
-with dynamical lens modeling of CO.
-Which also velocity gradient.
-Constraints on the.
-
-\subsection{Others}
-Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
-The dusty nature of this system?? \\
-compare to Riechers08a \\=
-{\bf compare to J04135 in R13} \\
+\citet{McLure06a}, which is unlikely given its dynamical mass and rotation velocity 
+% \ie based on the dark matter fraction as a function of half light radius found; Figure 2 in Courteau15
+% Courteau15a: f<0.5 at 0.6*Re for gal. with cir. velocity like RXJ1131
+\citep{Courteau15a}.
+% $f_\textrm{DM}$ is expected to increase with cosmic time \citep{Beifiori14a} and that the local DM fraction is 16-28% from dynamical studies \citep{Thomas11a, Cappellari13a} and based on predictions from simulations of 18%-38% \citep{Naab07a}.
 
@@
 a minor merger, in good agreement with previous studies of RXJ1131 in the optical \citepalias{Claeskens06a,Brewer08a}. 
+{\bf Say more about dusty nature, IR luminous, gas-rich, CO and stellar emission.}
+We were able to compare the CO size with the stellar size because of lensing, and the uniqueness of this source. 
+From dynamical constraints on the companion and the fact that RXJ1131 is optically bright, implies 
+a large portion of the dust from SED fitting is residing in the companion and not RXJ1131.
+%so probably also means dust magnification factor is quite different, probably higher, because the companion CO magnification is also higher than the median CO, implying its in a lensing configuration with higher magnification.
 
@@
 mergers. BLAH. Thus, the merging system studied here will likely evolve into a merged disk galaxy.
+The nature of the merger system of RXJ1131 is quite distinct from that of SMM J04135$+$10277 \citep[hereafter J04135][]{Riechers13a}.
 
@@
 host galaxy emission. Dynamical lens modeling provides a promising avenue to study the velocity 
-structure and dynamics of the cold gas in greater detail. 
+structure and dynamics of the cold gas in quasars in greater detail. 
+To study high-z quasars.Riechers08a is the only other similar system at emission in host galaxy lensed into an Einstein ring configuration and
+with dynamical lens modeling of CO.
+Which also velocity gradient.
 To date, only a few other studies using similar techniques \eg other luminous,

### 2016-07-08 WRITEUP/ms.tex
done conclusion

@@
 RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
-RXJ1131 is gravitationally lensed quasar.
-Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
-The molecular gas of $M_{\rm gas}$\eq123BLAH\E{10}\,\Msun in the host galaxy 
-is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
-RXS J1131-1231 a wet-merger, 
+The spinning black hole in RXJ1131 is quadruply-imaged by a foreground galaxy at $z$\ssim0.3.
+This is the first resolved \bco imaging at intermediate redshift.
+We perform a dynamical lens modeling on the spatially and spectrally resolved \bco line emission.
 Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
@@
 is indicative of, and suggests...
+The lensing-corrected molecular gas of $M_{\rm gas}$\eq1.38\E{10}\,\Msun in the host galaxy 
+is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
+We thus conclude that RXJ1131 a wet minor merger.
+Fitting dust SED models, we derive a lensing-corrected dust mass of $M_{\rm dust}$ = 4\E{8}\,\Msun and a lensing-corrected \LIR\ssim1.5\E{12}\,\Lsun, corresponding to a SFR$_{\rm FIR}$\eq120\pmm63 \sfrU .
+This implies that the merger system of RXJ1131 is dusty in nature with ongoing starbursts. 
+Dusty
 % Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
 The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
-% MBH-sigma relation...
+%Demonstrate the first dynamical constraint on the MBH-sigma relation at intermediate redshift.
 \end{abstract}
@@
 but it is clear that both the co-moving \SF rate and black hole accretion rate densities
-increased substantially since $z$\,$>$\,3 and reached their climax at $z$\ssim2, followed by 
-a rapidly decline toward $z$\ssim0 \citep[\eg][]{Hopkins06a, Madau14a}. 
+increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by 
+a rapidly decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}. 
 % Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
@@
 but confirmation from direct molecular gas measurements at intermediate redshift 
-$($0.2\,$<$\,$z$\,$<$\,1$)$ is still limited both in number and in the variety of galaxy populations probed --- 
-only unresolved CO observations have been carried out for $\sim$\,70 ULIRGs up to date \citep{Combes11a, Combes13a}.
+$(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed --- 
+only unresolved CO observations have been carried out for $\sim$$70$ ULIRGs up to date \citep{Combes11a, Combes13a}.
 
@@
 are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
-While it has become clearer that high-$z$ galaxies deviates from the local relation, and among their galaxy populations, 
+While it has become clearer that high-$z$ galaxies deviate from the local relation, and among their galaxy populations, 
 such a picture is still unclear  at intermediate redshift.
@@
 With gravitational lensing, emission of the background quasar and its host galaxy 
-is magnified and stretched out to different extents, and is projected onto different locations in the image plane.
+is magnified and stretched out to different extents, and is being projected onto different locations in the image plane.
 This in effect increases the surface brightness contrast between their emission and allows for the
@@
 The ``Einstein ring'' RXS J113151.62$-$123158 (hereafter RXJ1131) 
-at $z_\textrm{s, QSO}$\eq0.685 \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
+at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
 studying the evolution of molecular gas properties in quasar host galaxies and the 
@@
 The stellar emission in the host galaxy of RXJ1131 is lensed into
-an Einstein ring of radius 1\farcs83
+an Einstein ring of radius $1$\farcs$83$
 that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
 We have thus carried out a detailed study for RXJ1131 as presented in this paper.
-RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq0.295 \citepalias{Sluse03a}.
-The moderate mass black hole $M_{\rm BH}$\eq8\E{7}\Msun \citep{Sluse12a} %based on H beta line
-residing in RXJ1131 is rotating with a high spin parameter \citep[$a$\,$\sim$\,0.9;][]{Reis14a}, and
-is radiating at an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq1.3\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.
+RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
+The moderate mass black hole $M_{\rm BH}$\eq$8$\E{7}\Msun \citep{Sluse12a} %based on H beta line
+residing in RXJ1131 is rotating with a high spin parameter \citep[$a$\,$\sim$\,$0.9$;][]{Reis14a}, and
+is radiating at an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.
 
@@
 and the resulting physical properties inferred for RXJ1131.
-In \Sec{diss}, we discuss the merger stage of RXJ1131, and the implications of 
-this study in the context of the evolution of molecular gas content
-and the $M_{\rm BH}$$-$\mdyn relation at intermediate redshift.
+In \Sec{diss}, we discuss the merger stage of RXJ1131, 
+the scenario of a recoiling black hole, and the $M_{\rm BH}$$-$\mdyn relation.
 Finally, we summarize the main results and present our conclusions in \Sec{sum}.
@@
 parameters from the WMAP9 results:
-$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
-$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
+$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
+$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
 % same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
@@
 Observations of the \bco rotational line
-($\nu_{\rm rest}$\,=\,230.5379938 GHz) redshifted to $\nu_{\rm obs}$\,=\,139.0\,GHz
+($\nu_{\rm rest}$\,=\,$230.5379938$ GHz) redshifted to $\nu_{\rm obs}$\,=\,$139.0$\,GHz
 were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
@@
 respectively. The 2 mm receivers were used to cover the redshifted \bco line
-and the underlying continuum emission, employing a correlator setup providing
+and the underlying continuum emission, employing a correlator setup that provides
 an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 10.0 MHz ($\sim$
-21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
+$21.5$ \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
  time after discarding unusable visibility data.
@@
 therefore treat its line intensity with caution and ensure that our physical interpretation
-of this system and the conclusion of this do not rely on this quantity.
+of this system and the conclusion of this paper do not rely on this quantity.
 
@@
 in which the absolute position of the foreground lensing galaxy is guided by its
-coordinates in the optical image, where its emission is clearly detected.
+coordinates in the high-resolution optical image.
 The VLA image is calibrated using a well-monitored phase
@@
 is with respect to $z$\,=\,0.6537, which is approximately the line center
-considering the asymmetry as a result of differential lensing.
+considering the asymmetry resulting from differential lensing.
 A detailed discussion of this effect is presented in
@@
 The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
-in the intensity-integrated map.
+in the intensity map.
 
@@
 linewidth used to infer the \bco line intensity ($\sim$700 \kms).
-Assuming the spatial extent between \bco and \cco are similar and therefore
-magnified by the same amount, the line intensities
+Assuming the spatial extent between \bco and \cco is similar and therefore the emission is
+magnified by the same amount, the measured line intensities
 correspond to a brightness temperature ratio of
 $r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
+Taking into account the large phase errors associated with \cco, this is consistent with 
+thermalized excitation, as observed in other ULIRGs.
 
@@
 $S_\nu$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission toward
-the background galaxy.
+the background galaxy (RXJ1131).
 
@@
 The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
-jets and core of the foreground elliptical galaxy
+jets and the core of the foreground elliptical galaxy
 as well as emission toward the background quasar.
@@
 Here, we use the gas mass ratio between RXJ1131 and
-its companion galaxy instead, given that we do not have constraints on their individual galaxy mass.
+its companion galaxy instead, given that we do not have stringent constraints on their individual galaxy mass.
 We decompose the total line flux into two components:
@@
 If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass.
-Since the dust mass only contributes a small fraction of the total mass, a factor of $\sim$2 difference is minor.}
+Since the dust mass only contributes a small fraction to the total mass, a factor of $\sim$2 difference is minor.}
 from the dynamical mass and ignore a contribution from the dark matter, this would
@@
 \section{Summary and Conclusions} \label{sec:sum}
-% see Hodge12_dynamics.pdf for guide
-
-We observe \bco and \cco line emisison toward the
-quadruply-lensed quasar RXJ1131 at $z_{\rm CO}$\,$\sim$0.65 
-using the PdBI and CARMA, benchmarking the 
-first resolved interferometric CO imaging at intermediate redshift.
-The brightness temperature ratio between \bco and \cco of $r_{32}$ = BLAH, which taking into 
-account the large phase errors associated with \cco, is consistent with
-thermalized excitation between these lines in other ULIRGs.
-The (gas) mass ratio, the intrinsic CO line profile,
-and the source-plane velocity field are all evident of
-a minor merger, in good agreement with previous studies of RXJ1131 in the optical \citepalias{Claeskens06a,Brewer08a}. 
-{\bf Say more about dusty nature, IR luminous, gas-rich, CO and stellar emission.}
-We were able to compare the CO size with the stellar size because of lensing, and the uniqueness of this source. 
-From dynamical constraints on the companion and the fact that RXJ1131 is optically bright, implies 
-a large portion of the dust from SED fitting is residing in the companion and not RXJ1131.
-%so probably also means dust magnification factor is quite different, probably higher, because the companion CO magnification is also higher than the median CO, implying its in a lensing configuration with higher magnification.
-
-% explicit discussion of RXJ1131 being IR luminous, and gas-rich
-The intrinsically symmetric double-horned line profile, the smooth and
-symmetric velocity field/gradient seen in both the source plane from our lens model as well
-as in the image plane are characteristics resembling a rotating disk, 
-consistent with the findings from previous optical lens model.
-The high dispersion $\gtrsim$400\,\kms near the dynamical center suggest that 
-RXJ1131 is turbulent, albeit lack of spatial resolution. 
-Our lens modeling analysis also confirms the presence of the optically faint companion 
-suggested by previous studies, with CO emission.
-Assuming the same CO excitation as RXJ1131 for the companion, we find a gas mass of BLAH,
-which implies a gas mass ratio of ($\sim$7:1) between RXJ1131 and the companion. 
-We thus classify the system is a wet minor merger.
-We conclude that RXJ1131 is a ULIRG hosting a massive gas reservoir in a disturbed/turbulent
-disk, undergoing merging with a nearby companion (aka a wet minor merger).
-
-While many characteristics of RXJ1131 resembles local ULIRGs and high-z SBs (such as 
-linewidth, CO sizes, SFR, gas mass), its SFE is similar to that nearby 
-spiral galaxies and high-$z$ disk-like galaxies rather than 
-ULIRGs or high-$z$ starbursts galaxies at $z$$\gtrsim$0.6. 
-Our result is consistent with the emerging consensus on
-the correlation between molecular gas content and redshift,
-suggesting it as the explanation for the elevated SFR at high redshift/
-the observed trend in the cosmic SFH.
-Given our large error bar on the gas mass fraction, we cannot constrain its evolution 
-but our result is consistent with a decreasing trend of gas fraction
-since $z$\,$\approx$\,1.0 \citep{Combes13a}; but is consistent with 
-in both ULIRGs samples in redshift bins of 0.2\,$<$\,$z$\,$<$\,0.4 and 0.6\,$<$\,$z$\,$<$\,1.0 within the uncertainties.
-
-The compact UV emission, which can be a starburst resulting from gas accumulation
-owing to a non-axisymmetric perturbation from the companion.
-% the stellar component torques away the angular momentum, allowing the gas to fall inward.
-Dusty nature of companion?
-The IR luminosity also agrees with the results from previous low-$z$ studies: AGNs are
-typically found in late stage mergers \citep{Yuan10a,Iwasawa11a,Carpineti12a} and
-only major mergers near their final coalescence can provide \LIR$>$\,10$^{12}$\,\Lsun,
-\citep[\eg][]{Carpineti15a,Larson16a}. In contrast to the 
-galaxies with ULIRG-like IR luminosity at high redshifts, which can be in early stages of merging.
-
-We find that the optical lines are offset from the systemic redshift by $\sim$780\,\kms, (caution use of optical lines 
-as systemic redshift)
-may imply a recoiling black hole in RXJ1131, which would imply the black
-holes (and their host galaxies) have merged or are at their final coalescence.
-The highly spinning black hole in RXJ1131 is also consistent with
-this hypothesis.
-Given the presence of a companions, it is plausible that RXJ1131 is in its late stage of merging and 
-possibly encountered with its companion previously, consistent with 
-compact SB traced by $V$-band image triggered by gas inflow/accumulation toward nuclear regions 
-arising from perturbations in the disk from/interactions with the companion.
-%Our results indicate a self-consistent picture of ...
-followed by gravitationally instability and SF in a massive, gas-rich disk and a subsequent build-up of a central bulge through inflow triggered by disk installbilities and/or minor merger.
-Theoretical simulations suggest disk in progenitor galaxy may be retained post-merging in gas-rich 
-mergers. BLAH. Thus, the merging system studied here will likely evolve into a merged disk galaxy.
-The nature of the merger system of RXJ1131 is quite distinct from that of SMM J04135$+$10277 \citep[hereafter J04135][]{Riechers13a}.
-
-% broader
-The use of dynamical mass as a proxy to the \bhrelation have been proposed in a few high-$z$ studies 
-but requires resolved observations to provide constraints on the spatial extent tracing the potential of 
-the host galaxy. Lensing likely the the way to allow observations of quasar emission and 
-host galaxy emission. Dynamical lens modeling provides a promising avenue to study the velocity 
-structure and dynamics of the cold gas in quasars in greater detail. 
-To study high-z quasars.Riechers08a is the only other similar system at emission in host galaxy lensed into an Einstein ring configuration and
-with dynamical lens modeling of CO.
-Which also velocity gradient.
-To date, only a few other studies using similar techniques \eg other luminous,
-gas-rich interacting galaxies and mergers.
-This study of RXJ1131 serves as a benchmark/demonstrate the use of gravitational lensing and 
-dynamical lens modeling for further high-resolution molecular gas studies at 
-intermediate redshifts.  Similar resolved CO studies are needed to investigate the evolution in 
-the $M_{\rm BH}$$-$$M_{\rm dyn}$ relation to understand the co-evolution of SMBHs and their 
+We present PdBI \bco and CARMA \cco observations toward the
+quadruply-imaged quasar RXJ1131 at $z_{\rm CO}$\ssim$0.654$, 
+benchmarking the first resolved CO imaging at intermediate redshift.
+We find a brightness temperature ratio of $r_{32}$\eq$0.66\,\pm\,0.41$ between \bco and 
+\cco. Taking into account the large phase errors associated with \cco, this
+is consistent with thermalized excitation.
+We perform astrometric correction using archival VLA data, in which we detect continuum emission at 5\,GHz in 
+both the lensing galaxy and RXJ1131.
+In addition, we detect marginally resolved 2\,mm continuum underlying the \bco line in both galaxies.
+
+We perform a lens modeling on different velocity channels of \bco to study the intrinsic gas dynamics of RXJ1131. 
+Our models indicate a CO-emitting source near RXJ1131, confirming 
+the presence of an optically faint companion reported in previous studies \citepalias{Claeskens06a,Brewer08a}. 
+The source-plane positions form a symmetric velocity field, 
+which is consistent with a kinematically-ordered disk galaxy.
+We find that the magnification factors vary from $\mu_{\rm L}$\ssim3 to $\sim8$ across different
+velocity channels, implying an extended gas distribution.
+Upon correcting for lensing magnification and subtracting a line flux contribution from the companion, 
+we find an intrinsically symmetric double-horned line profile for RXJ1131.
+This together with the symmetric velocity gradient seen in both the source plane and the image plane 
+strongly argues for a rotating disk morphology for RXJ1131, consistent with previous findings \citepalias{Claeskens06a}.
+Assuming thermalized excitation and \alphaco=\,0.8\,\alphaU,
+we find a lensing-corrected gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun 
+for RXJ1131
+and $($1.92\pmm0.09$)$\,\E{9} \Msun for the companion.
+This implies a {\em gas} mass ratio of $\sim$7:1. 
+We derive a dynamical mass of $M_{\rm dyn}$\,=\,(8.3\pmm1.9)\E{10}\,\Msun for RXJ1131 and 
+ $M_{\rm dyn} \sin^2 30\degr$\ssim BLAH\E{BLAH}\,\Msun for the companion. 
+We thus find a gas mass fraction of $\sim$0.19 for RXJ1131, confirming its gas-rich nature.
+The derived gas fraction is also consistent with the decreasing trend of molecular gas content
+since $z$\ssim1.0 \citep{Combes13a}.
+Owing to the lack of stringent constraints on the individual galaxy mass of RXJ1131 and the companion, we use 
+their gas mass ratio to classify the system as a ``wet'' minor merger.
+We note that the merger system studied here is in stark contrast to the
+``wet-dry'' merger SMM J094135$+$10277 at $z$\eq2.8,  
+where the quasar host galaxy harbors $\gtrsim$\,$5$ times less gas mass than its companion \citep{Riechers13a}.
+
+Fitting dust SED models to the submm photometry obtained with {\it Herschel} and additional IR photometry compiled from 
+public catalogs, we derive a lensing-corrected dust mass of $M_{\rm dust}$\eq4\E{8}\,\Msun and
+a lensing-corrected IR luminosity of \LIR$\sim$\,1.5\E{12}\,\Lsun, corresponding to a
+SFR$_{\rm FIR}$ of 120\pmm63\,\sfrU. 
+This implies that the merger system of RXJ1131 is dusty in nature with ongoing starbursts.
+{\bf who contains the dust?}
+% compare intrinsic CO size and stellar
+Comparing the gas and stellar distributions, we
+find that the CO gas is of similar spatial extent as the old and long-lasting stellar populations, whereas 
+sites of recent star formation are embedded within the molecular gas reservoir.
+The starburst taking place in the inner few kpc is likely a consequence of 
+gas accumulation driven by interactions with the companion.
+While properties such as CO linewidths, CO size, SFR, and gas mass found in RXJ1131 
+resemble local ULIRGs and high-$z$ starbursts, 
+its SFE is comparable to that of nearby and high-$z$ disk-like galaxies rather than 
+other ULIRGs. This is in agreement with its disk-like kinematic signatures. 
+Theoretical simulations find that the disk component of a gas-rich progenitor galaxy with low SFE can be
+retained upon merging since the efficiency in removing angular momentum of the gas via 
+gravitational torques provided by stellar components is reduced.
+Within this context, the extended molecular gas disk of RXJ1131 together with its low SFE implies that
+the nuclear starburst in RXJ1131 will buildup a larger bulge in the final product but is 
+insufficient to transform into a E/S0 galaxy.
+
+The optical BLR lines are blueshifted by $\sim$780\,\kms from the systemic redshift, 
+implying the AGN is offset from the dynamical center of its host galaxy.  The offset could 
+be the manifestation of a recoiling black hole in RXJ1131.
+Since this model requires a merged BH, this interpretation would imply RXJ1131 have 
+already encountered with the companion galaxy, which would also explain the highly spinning black hole. 
+Given the presence of the companion in the current data, RXJ1131 may be in 
+its subsequent stages of minor merging from a previous major merger, as commonly predicted in simulations.
+% Our results thus illustrate a self-consistent picture of a pair of interacting gas-rich, dusty galaxy.
+
+% Dynamical mass has been used as a proxy to the \bhrelation relation in a few high-$z$ studies,
+% but this approach remains unexplored at intermediate redshifts.
+Our study here demonstrate the first resolved CO observations at intermediate redshift, allowing us to
+explore the \bhrelation relation at $z$\ssim0.65 using dynamical constraints.
+We illustrate the use of gravitational lensing to allow for a detailed study of the ISM properties of a quasar host galaxy
+and a comparison of distributions between the dust, gas, and stars in the host galaxy despite emission of the quasar, and that
+dynamical lens modeling provides a promising avenue 
+to study the gas kinematics and dynamics in distant quasar host galaxies. 
+The first use of such technique is presented by \citet{Riechers08a}, who reconstruct a velocity gradient and 
+constrain the gas dynamics in the quasar PSS J2322$+$1944 at $z$\,$>$\,4, which is
+the only other similar system where the emission of the host galaxy is lensed into an Einstein ring configuration.
+Similar resolved CO studies at intermediate redshift are needed to understand the co-evolution of SMBHs and their 
 host galaxies through cosmic time.

### 2016-07-08 WRITEUP/ms.tex
done abstract

@@
 RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
-The spinning black hole in RXJ1131 is quadruply-imaged by a foreground galaxy at $z$\ssim0.3.
-This is the first resolved \bco imaging at intermediate redshift.
-We perform a dynamical lens modeling on the spatially and spectrally resolved \bco line emission.
-Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
-turbulent disk
-is indicative of, and suggests...
-The lensing-corrected molecular gas of $M_{\rm gas}$\eq1.38\E{10}\,\Msun in the host galaxy 
-is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
-We thus conclude that RXJ1131 a wet minor merger.
-Fitting dust SED models, we derive a lensing-corrected dust mass of $M_{\rm dust}$ = 4\E{8}\,\Msun and a lensing-corrected \LIR\ssim1.5\E{12}\,\Lsun, corresponding to a SFR$_{\rm FIR}$\eq120\pmm63 \sfrU .
-This implies that the merger system of RXJ1131 is dusty in nature with ongoing starbursts. 
-Dusty
-% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
-The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
-%Demonstrate the first dynamical constraint on the MBH-sigma relation at intermediate redshift.
+Our observations detect a CO-emitting source near RXJ1131, confirming the presence of an optically 
+faint companion reported in previous studies. 
+Based on our dynamical lens modeling of the spatially and spectrally resolved \bco emission, 
+we reconstruct a symmetric velocity gradient in the source plane and 
+find an intrinsically symmetric double-horned line profile, which are suggestive of a 
+rotating disk morphology, consistent with previous optical studies.
+We find a lensing-corrected gas mass of $M_{\rm gas}$\ssim1.4\E{10}\,\Msun in the host galaxy and 
+\ssim2\E{9}\,\Msun in the companion (gas mass ratio $\sim$7:1). 
+The CO disk is extended over $\sim$6\,kpc, which yields a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun
+for the host galaxy. This corresponds to a gas mass fraction of $\sim$19\%, confirming its gas-rich nature.
+This fraction also confirms the trend of decreasing gas fraction since $z$\ssim1, which is responsible for the decline of
+the cosmic \SF rate and black hole accretion rate densities.
+Fitting dust SED models, we derive a lensing-corrected dust mass of $M_{\rm dust}$ = 4\E{8}\,\Msun, a 
+lensing-corrected $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun, and a SFR$_{\rm FIR}$\eq120\pmm63 \sfrU, 
+confirming the dusty nature of the merger.
+A comparison of the gas and stellar distributions reveals active starbursts embedded 
+within the molecular gas reservoir which is likely a result from merger-driven gas inflow.
+The nature of RXJ1131 is consistent with the picture predicted by model simulations, in which it will 
+likely retain its disk component and evolve into small bulge disk galaxy upon merging.
+Our study presents the first resolved CO imaging at intermediate redshift, 
+which allows us to provide the first dynamical constraint on the \bhrelation relation at intermediate redshift.
 \end{abstract}
@@
 \section{Introduction}
-Studies of galaxy evolution have been focusing on the interplay between baryonic physics/process
+Studies of galaxy evolution have been focusing on the interplay between baryonic physics/processes
 (\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.

### 2016-07-08 WRITEUP/ms.tex
update after read thru once, added shorthand for ref. section alias; send this to DR

@@
 Our study presents the first resolved CO imaging at intermediate redshift, 
-which allows us to provide the first dynamical constraint on the \bhrelation relation at intermediate redshift.
+which allows us to provide the first dynamical constraint on the Magorrian relation at intermediate redshift.
 \end{abstract}
@@
 that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
-We have thus carried out a detailed study for RXJ1131 as presented in this paper.
+We have thus carried out a detailed study of RXJ1131 as presented in this paper.
 RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
@@
 In \Sec{obs}, we outline the details of the observations and our data reduction process.
-In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our radio maps.
+In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our VLA radio image.
 In \Sec{results}, we report measurements of the \bco and \cco lines and a compilation of photometric data from optical to radio wavelengths.
@@
 % Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
-% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
+% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710 --> 3%
 %
+% amp de-correlation: % loss scales = 1- exp(-(50º*pi/180)^2 / 2) = ~32% loss
 Given that the phase calibrator used for the first track was faint and was
@@
 the second track was far from our target source, the phase calibration is
-subpar, with an rms scatter $\sim$60$\degr$ over a baseline length of $\sim$135\,m.
-%BLAH... more like 50%
+subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
 We thus conservatively estimate
-a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
+a calibration accuracy of $\sim$35\% based on the flux scale uncertainties,
 the gain variations over time, and the phase scatter on the calibrated data. We
@@
 as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
-flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
+flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
 179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
@@
 \subsection{\cco Emission}
-We detect \cco line emission toward RXJ1131 at {\bf BLAH}$\sigma$ significance.
+We detect \cco line emission toward RXJ1131 at $\gtrsim5\sigma$ significance.
 The spectrum is shown in \Fig{co32spec}, which appears to be consistent with a 
 double-peaked profile. We estimate a line intensity of
-35.7\,$\pm$\,21.9{\bf BLAH} Jy\,\kms by summing up fluxes over the FWZI
+35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
 linewidth used to infer the \bco line intensity ($\sim$700 \kms).
@@
 
-The emission in the IRAC images is slightly extended. We thus use the
-{\it HST} image ($\sim$0\farcs07 resolution) to determine
+The emission in the IRAC images is slightly extended. We thus use an
+{\it HST} image ($\sim$0\farcs07 resolution) to determine the
 origins of their centroids, all of which are found to be
@@
 We perform aperture photometry on the residual image
-to obtain decomposed flux measurements from the background galaxy.
+to obtain decomposed flux measurements of the background galaxy.
 The photometry for the foreground galaxy is then obtained
@@
 observed total flux. The resulting photometry in
-\Tab{photometry} are obtained after performing an aperture correction
+\Tab{photometry} is obtained after performing an aperture correction
 described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
@@
 emission from the total flux observed in the MIPS 24\,$\micron$ band. 
-The spectral indices corresponding to best-fitting curves are $\alpha$\,=\,$-1.8$ and
+The spectral indices corresponding to the best-fitting curves are $\alpha$\,=\,$-1.8$ and
 $\alpha$\,=\,$-0.85$ for the lensing galaxy and RXJ1131, respectively.
@@
 the corresponding kinematic component of the CO gas, 
-enabling us to reconstruct the source plane velocity gradient. 
-In order to have adequate SNRs for lens modeling, we bin the frequency channels by a factor of five 
+enabling us to reconstruct a velocity gradient in the source plane.
+To enusre adequate SNRs for lens modeling, we bin the frequency channels by a factor of five 
 to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
@@
 after subtracting a contribution from its companion galaxy and 
-correcting for lensing using the magnification factors $\mu_{\rm L}$ as annotated by the horizontal bars shown
-above the respective model channels. Flux density on the y-axis is shown on a log scale.
+correcting for lensing using the magnification factor $\mu_{\rm L}$ as annotated by the horizontal bar shown
+above each respective model channel. Flux density on the y-axis is shown on a log scale.
 \label{fig:delensed}}
@@
 the foreground galaxy to initialize the positional offset. We impose a
-uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec.,
+uniform prior of $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec.,
 motivated by the astrometry uncertainties in the VLA image as well as
@@
 implies a {\em gas} mass ratio of $\sim$7:1 between RXJ1131 and its companion.
-We thus classify the system to be a {\em ``wet-wet'' minor merger}.
+We thus classify the system to be a {\em ``wet'' minor merger}.
 We caution that this is based on their gas mass ratio rather than their total galaxy mass ratio, which 
@@
 \Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
-show that emission
+show that redshifted emission
 is present to the west, peaking toward the lensing arc (black crosses in
-\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
+\Fig{chanmap}), and shifts to the east with decreasing velocity
 (blue wing).
@@
 causing the redshifted emission to be apparently much brighter than the
-blueshifted component and the asymmetric line profile.
+blueshifted component.
 This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
@@
 is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
-implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the source-plane
+implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
 velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
@@
 This discrepancy is likely a result of differential lensing, which causes the line peak of the red wing 
-to shift towards higher velocity channels, biasing the centroid of
-one of the components in a double-Gaussian to higher velocity than otherwise.
-If we instead fit with a single-Gaussian, we find a FWHM of 600\pmm160\,\kms for RXJ1131
+to shift towards higher velocity channels, and thereby biasing the centroid of
+one Gaussian to higher velocity than otherwise.
+If we instead fit the intrinsic line profiles with single-Gaussians, we find a FWHM of 600\pmm160\,\kms for RXJ1131
 and 73\pmm43\,\kms for the companion galaxy.
@@
 The fit is performed with the code
-\ncode{mbb\_emcee} \citep[\eg][]{Riechers13a,Dowell14a}, which samples the posterior
+\ncode{mbb\_emcee} \citep[e.g.,][]{Riechers13a,Dowell14a}, which samples the posterior
 distributions using an MCMC approach and uses instrumental
@@
 becomes optically thick ($\lambda_{0}$). We impose
-a uniform prior with an upper limit of 100\,K on $T_d$ \citep[see \eg][]{Sajina12a},
+a uniform prior with an upper limit of 100\,K on $T_d$ \citep[see e.g.,][]{Sajina12a},
 a Gaussian prior centered around
@@
 dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun, all of which are uncorrected for lensing.
-Taken at face value, this implies a FIR-to-IR luminosity ratio
+Taken at face value, this implies an FIR-to-IR luminosity ratio
 of $\sim$58\pmm35\%.
@@
 based on \bco and compare them with those reported by
-\citetalias{Combes13a} --- the largest sample of ULIRGs at similar redshift
-(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
-\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
+\citetalias{Combes13a}\footnote{The
+\fir luminosity in \citetalias{Combes13a} is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
 and using a different definition of
@@
 \LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
-a SFR of $($150\pmm70$)$\,\sfrU for RXJ1131.}.
+a SFR of $($150\pmm70$)$\,\sfrU for RXJ1131.} --- the largest sample of CO-detected ULIRGs at similar redshift
+(0.6\,$<$\,$z$\,$<$\,1.0).
 Their results are based on unresolved \bco and \rot{4}{3} line observations with the
@@
 in a local LIRG \citep[Arp 118; ][hereafter SV05]{SV05a}.
-Linewidth of this range ($\gtrsim$500\,\kms) is also commonly observed in 
-high-$z$ starburst galaxies  \citep[\eg][hereafter G05]{Greve05a} 
+Linewidth of this range ($\gtrsim$\,500\,\kms) is also commonly observed in 
+high-$z$ starburst galaxies  \citep[e.g.,][hereafter G05]{Greve05a} 
 % \citep[780\pmm320\,\kms; \eg][hereafter G05]{Greve05a} 
-and high-$z$ quasar host galaxies \citep[\eg][]{Coppin08a},
+and high-$z$ quasar host galaxies \citep[e.g.,][]{Coppin08a},
 % \citep[550\pmm180\,\kms; \eg][]{Coppin08a}, 
@@
 the dusty nature of the companion, which causes its $V$-band source size to 
-appear much smaller than its true extent without any dust obscuration. 
+appear much smaller than its true extent. 
 If we use the half-right radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc obtained from our best-fit lens 
-model as the unobscured source size (see \Sec{caveat}), we find a dynamical mass of 
+model as the unobscured source size, we find a dynamical mass of 
 $M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun (assuming $i$\eq30$\degr$), which is physically more sensible 
@@
 the merged galaxy \citep{Hopkins09a}. With this, it is plausible that RXJ1131 
-will evolve into a disk galaxy with a small bulge component upon merging given its low SFE.
+will evolve into a disk galaxy with a small bulge component upon merging given its low SFE and the extended disk.
 %since there is little/no significant stellar material % (collisionless)
@@
 other ULIRGs. This is in agreement with its disk-like kinematic signatures. 
-Theoretical simulations find that the disk component of a gas-rich progenitor galaxy with low SFE can be
+Theoretical simulations suggest that the disk component of a gas-rich progenitor galaxy with low SFE can be
 retained upon merging since the efficiency in removing angular momentum of the gas via 

### 2016-07-20 PdBI/src/pythonPLOT/cubefromScratch.py
moved to LTKpy

@@ -1,96 +1,0 @@
-"""
-simple cube fitting example
-
-Build a cube from scratch and fit many gaussians
-
-Still need to figure out how to make it useful to what I do....
-Seems like it fits model to spectrum, e.g. Gaussian, and return SNR.. what does this SNR mean..
-
-Note
-----
-Run in ipython only, don't run under Daisy's alias='pylab' environment. It will crash for some reason.
-
-"""
-from __future__ import print_function
-
-import numpy as np
-import pyspeckit
-from spectral_cube import SpectralCube
-from astropy import wcs
-from astropy import units as u
-
-# Create a new WCS object so we can instantiate the SpectralCube
-mywcs = wcs.WCS(naxis=3)
-
-# Set up a tangent projection
-# You would normally read this from a file!!
-mywcs.wcs.crpix = [1, 2, 21.0]
-mywcs.wcs.cdelt = np.array([-0.066667, 0.066667, 500])
-mywcs.wcs.crval = [290.9250, 14.5092, 60000]
-mywcs.wcs.ctype = ["RA---TAN", "DEC--TAN", 'VELO']
-mywcs.wcs.cunit = ['deg', 'deg', 'm/s']
-
-# Create a synthetic X-dimension in km/s
-xarr = np.linspace(50, 70, 41)  # km/s
-
-# Define a line width, which will vary across our image
-# It will increase from 1 km/s to 4 km/s over the X-direction (RA)
-sigma = np.outer(np.linspace(1, 1.5, 2), np.ones(4)).T
-
-# Define a line center, which will vary in the opposite direction,
-# along increasing Y-direction (declination)
-centroid = np.outer(np.ones(2), np.linspace(58, 62, 4)).T
-
-data = np.exp(-(np.tile(xarr, (2, 4, 1)).T - centroid)**2 / (2. * sigma**2))
-cube = SpectralCube(data=data, wcs=mywcs)
-
-# Sanity checks: do the moments accurately recover the inputs?
-assert (np.abs(cube.moment1().to(u.km / u.s).value - centroid).max()) < 1e-5
-assert (np.abs(cube.moment2().to(u.km**2 / u.s**2).value - sigma**2).max()) < 1e-5
-
-# Create a pyspeckit cube
-pcube = pyspeckit.Cube(cube=cube)
-
-# For convenience, convert the X-axis to km/s
-# (WCSLIB automatically converts to m/s even if you give it km/s)
[…]

### 2016-07-20 PdBI/src/pythonPLOT/spectrumScratch.py

@@ -1,46 +1,0 @@
-'''
-Build a spectrum from scratch (and fit a gaussian)
-
-Can't figure out how to interactively show. For now, save it and check.
-
-Output: spectrum with fit
-
-'''
-import numpy as np
-import pyspeckit
-
-xaxis = np.linspace(-50,150,100.)
-sigma = 10.
-center = 50.
-synth_data = np.exp(-(xaxis-center)**2/(sigma**2 * 2.))
-
-# Add noise
-stddev = 0.1
-noise = np.random.randn(xaxis.size)*stddev
-error = stddev*np.ones_like(synth_data)
-data = noise+synth_data
-
-# this will give a "blank header" warning, which is fine
-sp = pyspeckit.Spectrum(data=data, error=error, xarr=xaxis,
-                        xarrkwargs={'unit':'km/s'},
-                        unit='erg/s/cm^2/AA')
-
-sp.plotter(figure=1)
-sp.plotter(errstyle='fill')
-
-
-# Fit with automatic guesses
-sp.specfit(fittype='gaussian')
-sp.plotter.savefig('spectrumScratch.png')
-
-# Fit with input guesses
-# The guesses initialize the fitter
-# This approach uses the 0th, 1st, and 2nd moments
-amplitude_guess = data.max()
-center_guess = (data*xaxis).sum()/data.sum()
-width_guess = data.sum() / amplitude_guess / np.sqrt(2*np.pi)
-guesses = [amplitude_guess, center_guess, width_guess]
-sp.specfit(fittype='gaussian', guesses=guesses)
-sp.specfit.plot_fit()
-
-sp.plotter.savefig('spectrumScratchGuess.png')

### 2016-07-20 src/HSTVLA.py
DR cosmetics

@@ -32,6 +32,7 @@ from APLpySetup import *
 path = '../HST/'
 Plotpath = '../Figures/'
 
+mpl.rcdefaults()
 font = {'family': 'Arial Narrow',
         'weight': 'normal',
         'size': 11.5}

### 2016-07-20 src/RedBlue.py

@@ -38,6 +38,7 @@ from APLpySetup import *
 path = '../HST/'
 Plotpath = '../Figures/'
 
+mpl.rcdefaults()
 font = {'family': 'Arial Narrow',
         'weight': 'normal',
         'size': 13.5}

### 2016-07-20 src/plotCont.py

@@ -1,12 +1,14 @@
 """
 Author: Daisy Leung
 
-Last edited: 27 May 2016
+Last edited: 20 July 2016
 
 Purpose:
 - Overlay 2mm Cont contour on HST
 
 History:
+July 20 2016:
+    - change zoom to match VLA image (HSTVLA.py)
 May 27 2016:
     - update aspect ratio
 May 17 2016:
@@ -32,6 +34,7 @@ from APLpySetup import *
 path = '../HST/'
 Plotpath = '../Figures/'
 
+mpl.rcdefaults()
 font = {'family': 'Arial Narrow',
         'weight': 'normal',
         'size': 11.5}
@@ -40,6 +43,7 @@ xtick = {'major.size': 10,
 ytick = {'major.size': 10,
          'minor.size': 6}
 mpl.rc('font', **font)
+mpl.rcParams.update({'font.size': 11.5})
 mpl.rc('xtick', **xtick)
 
 label = dict.fromkeys(['F555W_drzcroplinearShift'])
@@ -63,7 +67,7 @@ figC = plt.figure(1)
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.002058066
+sizep = 0.00215 # 0.002058066
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
@@ -126,7 +130,7 @@ standard_plot_setup(fig1, ra_center, dec_center, sizep, tickc='white')
 # standard_plot_setup(figHST, ra_center, dec_center, sizep, tickc='white')
 # standard_plot_setup(figred, ra_center, dec_center, sizep, tickc='white')
 #figO.tick_labels.hide()
-#figO.axis_labels.hide()
+# fig0.axis_labels.hide()
 # figred.tick_labels.hide()
 # figred.axis_labels.hide()
 

### 2016-07-20 src/singlePanelmom0.py

@@ -6,11 +6,13 @@ Plot mom0 of all channels overlay on HST (single panel)
 Author: Daisy Leung
 
 
-Last edited: 28 May 2016
+Last edited: 20 july 2016
 
 
 History:
 --------
+20 July 2016
+    - change zoom & HST contrast to match RedBlue.py
 28 May 2016:
     - increase font size
     - longer ticks
@@ -43,6 +45,7 @@ from APLpySetup import *
 path = '../HST/'
 Plotpath = '../Figures/'
 
+mpl.rcdefaults()
 font = {'family': 'Arial Narrow',
         'weight': 'normal',
         'size': 13.5}
@@ -74,7 +77,7 @@ figC.clf()
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.0021
+sizep = 0.002
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
@@ -95,7 +98,7 @@ tickcolor = 'k' if inverted_HSTleft else 'white'
 ########################################
 fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0],
                         figure=figC, subplot=[x0, row_a, full_width, dy])
-fig1.show_grayscale(stretch='log', vmin=-0.02, vmax=20, vmid=-0.025)
+fig1.show_grayscale(stretch='log', vmin=-0.00256, vmax=1.922, vmid=-0.02)
 if inverted_HSTleft: fig1.set_theme('publication')
 ########################################
 # Contours

### 2016-07-20 src/APLpySetup.py
update axes label

@@ -81,7 +81,9 @@ def standard_plot_setup(sp, ra_center, dec_center, size, tickc='black'):
 
     sp.axis_labels.set_font(size='xx-large', weight='bold')      # (size='12')
     sp.axis_labels.set_xtext('Right Ascension (J2000)')
+#    sp.axis_labels.set_xtext(u'$\\mathrm{Right}$'+' '+u'$\\mathrm{Ascension}$' + ' ' + u'$\\mathrm{(J2000)}$')
     sp.axis_labels.set_ytext('Declination (J2000)')
+#    sp.axis_labels.set_ytext(u'$\\mathrm{Declination}$'+' '+u'$\\mathrm{(J2000)}$')
     sp.axis_labels.set_xpad(5)
     sp.axis_labels.set_ypad(-25)
     sp.axis_labels.set_xposition('bottom')

### 2016-08-04 src/SED/SEDplotMagphys.py
SED plot incl. de-lensed photoemtry and MAGPHYs fit

@@ -1,0 +1,460 @@
+'''
+
+Plot SED with MIPS extrapolation to 24 um and MBB_EMCEE fit
++ magphys and de-lensed photometry
+
+Last Modified: Aug 4 2016
+
+History
+-------
+Aug 4 2016:
+    - copied from SEDplot.py
+    - added MAGPHYS best-fit
+
+Note
+----
+- Twin axes work perfectly, even on loglog
+- hard coded indices to separate out photometry for different sources, so that we can plot them with different styles
+
+'''
+
+import numpy as np
+import matplotlib
+from astropy.cosmology import WMAP9
+
+matplotlib.rcParams.update({#'figure.figsize': (8, 5),    # inches
+                            'font.size': 18,      # points
+                            'legend.fontsize': 16,      # points
+                            'text.usetex': True,
+                            'font.family': "Simplex",
+                            'font.weight': 'bold',
+                            'lines.linewidth': 1.5,       # points
+                            'axes.linewidth': 1.5,       # points
+                            'font.family': "simplex"
+                            })
+
+import matplotlib.pyplot as plt
+from os.path import join
+
+# Input observed photometry
+photoFile = 'RXJ1131photometry.dat'
+
+# output save plot file
+plotName = 'FullSED_withMagphys'
+
+# MAGPHYs output
+MagphysPath = "/Users/admin/Research/RXJ1131/src/SED/Magphys/"
+sedfilename = 'daisy.sed'
+fitfilename = 'daisy.fit'
+filterfilename = 'filters.dat'
+inputfile = 'de-lensed-stellarMass.txt'
+
+# ---------------- MAGPHYS -----------------
+# read in original
+wavelg_um, flux_mJy, flux_err_mJy = np.loadtxt(
+    join(MagphysPath, inputfile), skiprows=2, comments="#", unpack=True)
+
+
+# read in fluxes from model output
+fitfile = open(join(MagphysPath, fitfilename))
+fitinfo = fitfile.readlines()
+fitfile.close()
+
+# strip out new lines (\r\n)
+for i in range(len(fitinfo)):
+    fitinfo[i] = fitinfo[i].strip()
+
[…]

### 2016-08-04 WRITEUP/ms.tex
added RP as co author
finised revising abstract & concl.

@@
 \usepackage{amsmath}
+
+% -------------------------------------- Final Edit Markup ----------------------------------
+\usepackage[normalem]{ulem}
+\usepackage[usenames]{xcolor}
+\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
+\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
+\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
+\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
+% -----------------------------------------------------------------------------------------------
+
 \input{preamble}
@@
 \shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131$-$1231 at $z$\,=\,0.65}
-\shortauthors{Leung \& Riechers}
+\shortauthors{Leung, Riechers \& Pavesi}
 
@@
 \title{Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654}
-\author{T. K. Daisy Leung and Dominik A. Riechers}
+\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
 \affil{Department of Astronomy, Space Sciences Building, Cornell University,
@@
 \begin{abstract}
-We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
-RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
-Our observations detect a CO-emitting source near RXJ1131, confirming the presence of an optically 
-faint companion reported in previous studies. 
-Based on our dynamical lens modeling of the spatially and spectrally resolved \bco emission, 
-we reconstruct a symmetric velocity gradient in the source plane and 
-find an intrinsically symmetric double-horned line profile, which are suggestive of a 
-rotating disk morphology, consistent with previous optical studies.
-We find a lensing-corrected gas mass of $M_{\rm gas}$\ssim1.4\E{10}\,\Msun in the host galaxy and 
-\ssim2\E{9}\,\Msun in the companion (gas mass ratio $\sim$7:1). 
-The CO disk is extended over $\sim$6\,kpc, which yields a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun
-for the host galaxy. This corresponds to a gas mass fraction of $\sim$19\%, confirming its gas-rich nature.
-This fraction also confirms the trend of decreasing gas fraction since $z$\ssim1, which is responsible for the decline of
-the cosmic \SF rate and black hole accretion rate densities.
-Fitting dust SED models, we derive a lensing-corrected dust mass of $M_{\rm dust}$ = 4\E{8}\,\Msun, a 
-lensing-corrected $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun, and a SFR$_{\rm FIR}$\eq120\pmm63 \sfrU, 
-confirming the dusty nature of the merger.
-A comparison of the gas and stellar distributions reveals active starbursts embedded 
-within the molecular gas reservoir which is likely a result from merger-driven gas inflow.
-The nature of RXJ1131 is consistent with the picture predicted by model simulations, in which it will 
-likely retain its disk component and evolve into small bulge disk galaxy upon merging.
-Our study presents the first resolved CO imaging at intermediate redshift, 
-which allows us to provide the first dynamical constraint on the Magorrian relation at intermediate redshift.
+We report observations of the \bco and \cco line emission towards
+the quadruply-imaged quasar
+RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
+\pdbi (PdBI) and \carma (CARMA), making this the first spatially resolved
+CO study at intermediate redshift.
+Our lens modeling shows that the highly asymmetric double-horned line profile
+observed in the \bco spectrum is mainly a result of differential lensing, where
+the magnification factor varies from $\sim$3 to $\sim$8 across
+different kinematic components.
+The intrinsically symmetric line profile with a clear velocity
+gradient in the source-plane suggests that
+the quasar host galaxy is a rotating disk.
+In addition, we find a secondary CO-emitting source near RXJ1131 whose location is
+consistent with the optically-faint companion reported in previous studies.
+The lensing-corrected gas mass of
+$M_{\rm gas}$\ssim1.4\E{10}\,\Msun inferred for RXJ1131
+and \ssim2\E{9}\,\Msun for its companion correspond
+to a gas mass ratio of $\sim$7:1.
+The extended CO gas disk in RXJ1131 ($R$$\sim$6\,kpc) yields a dynamical mass
+of $M_{\rm dyn}$\ssim8\E{10}\,\Msun, and thus a gas mass fraction of $\sim$19\%,
+which is consistent with the trend of decreasing molecular gas fraction since $z$\ssim1.
+The lensing-corrected $M^{*}$\ssim3\E{10}\,\Msun,
+$M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun, and SFR$_{\rm FIR}$\eq120\pmm63 \sfrU of RXJ1131
+together with the source-plane morphology of the gas and the stellar populations
+suggest that ongoing \SBs are embedded within the molecular gas reservoir,
+and that the nuclear \SBs are likely triggered by
+interactions with the companion.
+The $M_{\rm BH}$$/$$M_{\rm bulge}$ of $\gtrsim$0.27\% derived for RXJ1131 lies above the
+local relation but is consistent with other radio-loud galaxies at this epoch, suggesting
+that the co-evolution between RXJ1131 and its host galaxy is different than those of local AGN host galaxies.
 \end{abstract}
 
-\keywords{ISM: molecular --
+\keywords{ISM: molecules --
           infrared: galaxies --
@@
           galaxies: starburst --
-          galaxies: evolution}
+          galaxies: evolution --
+          quasars: individual (RXS\,J1131$-$1231)}
 
@@
 \section{Introduction}
-Studies of galaxy evolution have been focusing on the interplay between baryonic physics/processes
-(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
-It is not well-understood when and how baryons of present-day galaxies were assembled, 
+Studies of galaxy evolution have been focusing on the interplay between
+\SF and active galactic nucleus (AGN) activity across cosmic epochs.
+It is not well-understood when and how stellar populations of present-day galaxies were assembled,
 but it is clear that both the co-moving \SF rate and black hole accretion rate densities
 increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
-a rapidly decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}. 
+a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
 % Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
@@
 % grows by accretion of the cold molecular gas from its host galaxy.
-Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
---- a tight correlation between black hole mass and stellar bulge mass ---
-have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
+Meanwhile, empirical scaling relations such as the
+$M_{\rm BH}$$-$\mbulge relation \citep[e.g.,][]{Magorrian98a, HR04a}
+has been established locally, suggesting a co-eval growth between local SMBHs and their host galaxies.
 Attempts to extend this relation out to higher redshifts, beyond the peak epoch
@@
 It has been reported that the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of high-$z$ submillimeter galaxies (SMGs) falls below
-the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies are found 
+the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies is found
 lying above
@@
 Stellar mass of quasar host galaxies at $z$\,$>$\,4 constrained by their CO-based dynamical mass
-are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
+is also too small compared to that based on the local relation \citep{Walter04a, Riechers08a,Coppin08a}.
 While it has become clearer that high-$z$ galaxies deviate from the local relation, and among their galaxy populations,
 such a picture is still unclear  at intermediate redshift.
-This owes to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
-owing to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
+This is owed to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
+due to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass.
 With gravitational lensing, emission of the background quasar and its host galaxy
-is magnified and stretched out to different extents, and is being projected onto different locations in the image plane.
-This in effect increases the surface brightness contrast between their emission and allows for the
-relatively uncontaminated measurements of their emission.
+is magnified and stretched out to different extents, and is being projected onto different locations in the image plane,
+allowing spatially resolved measurements their emission in a
+relatively uncontaminated fashion.
 
 \defcitealias{Sluse03a}{S03}
-The ``Einstein ring'' RXS J113151.62$-$123158 (hereafter RXJ1131) 
+The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
 at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
@@
 This paper is structured as follows.
-In \Sec{obs}, we outline the details of the observations and our data reduction process.
-In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our VLA radio image.
-In \Sec{results}, we report measurements of the \bco and \cco lines and a compilation of photometric data from optical to radio wavelengths.
-In \Sec{anal}, we present dynamical lens modeling of the \bco data, SED modeling of the thermal dust continuum, 
-and the resulting physical properties inferred for RXJ1131.
+In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
+In \Sec{HST}, we describe the astrometric corrections
+applied to align an {\it HST} image with an VLA radio image.
+In \Sec{results}, we report measurements of the \bco and \cco lines and broadband
+photometry spanning the optical to radio wavelengths.
+In \Sec{anal}, we present dynamical lens modeling of the \bco data and
+SED modeling of the host galaxy of RXJ1131 to
+derive physical parameters reflecting the nature of this system.
 In \Sec{diss}, we discuss the merger stage of RXJ1131,
-the scenario of a recoiling black hole, and the $M_{\rm BH}$$-$\mdyn relation.
+the velocity offset between the AGN lines and the CO lines,
+and the $M_{\rm BH}$$-$\mdyn relation of RXJ1131.
 Finally, we summarize the main results and present our conclusions in \Sec{sum}.
@@
 Observations of the \bco rotational line
-($\nu_{\rm rest}$\,=\,$230.5379938$ GHz) redshifted to $\nu_{\rm obs}$\,=\,$139.0$\,GHz
+($\nu_{\rm rest}$\,=\,$230.538$ GHz) redshifted to $\nu_{\rm obs}$\ssim$139.0$\,GHz
 were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
@@
 MWC349 and 3C279 were observed as primary flux calibrators for the C and D
-array observations, respectively, yielding $\lesssim$15\% calibration accuracy.
-
-The \ncode{gildas} package was used to reduce and analyze the visibility data.
+array observations, respectively, yielding calibration accuracy better than 15\%.
+
+The \ncode{gildas} package was used to calibrate and analyze the visibility data.
 The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
@@
 over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
-is created by averaging over 3.16\,GHz of line-free bandwidth. This
+is produced by averaging over 3.16\,GHz of line-free bandwidth. This
 yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
@@
 $\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
-line-free channels.
+line-free channels in both sidebands.
 
@@
 The calibrated visibility data were imaged and deconvolved using
-the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
+the CLEAN algorithm with robust\,=\,0, which
+was chosen to obtain a higher resolution image given high SNR.
+This yields a synthesized clean
 beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
@@
 offsets between different emitting regions and to carry out our lens modeling,
-in which the absolute position of the foreground lensing galaxy is guided by its
-coordinates in the high-resolution optical image.
+in which the absolute position of the foreground lensing galaxy is based on
+its coordinates in the high-resolution optical image.
 The VLA image is calibrated using a well-monitored phase
@@
 \section{Results} \label{sec:results}
-\subsection{\bco Emission} \label{sec:CO21} %DONE
-We detect \bco line emission toward the background source
+\subsection{\bco Emission} \label{sec:CO21}
+We detect \bco line emission toward the background source in the PdBI data
 at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
-0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
+0.6537\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
 with a highly asymmetric double-horned line profile
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
-\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
+\caption{Continuum-subtracted spectrum of \bco emission toward RXJ1131. The velocity scale
 is with respect to $z$\,=\,0.6537, which is approximately the line center
@@
 %   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
-We construct the zeroth moment map, a red/blue channel map, and
+We construct the zeroth order moment map, a red/blue channel map, and
 the first and second moment maps in \Fig{CO21mom}
@@
 $\Delta v$ $\sim$ 750\,\kms.
-The higher-order moment maps are created using
+The higher-order moment maps are produced using
 unbinned channel maps with 3$\sigma$ clipping.
@@
 the fit recovers the line intensity enclosed by the emitting
-region, we therefore take this as an estimate on the extent of the lensed
+region, therefore we take this as an estimate on the full extent of the lensed
 emission. On the other hand, if we assume that the spatial distribution of
@@
 \includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
-\includegraphics[trim=5 -10 0 0, clip, width=0.472\textwidth]{../Figures/F555W_REDBLUE.eps} 
+\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
 \\
@@
 \subsection{\cco Emission}
-We detect \cco line emission toward RXJ1131 at $\gtrsim5\sigma$ significance.
-The spectrum is shown in \Fig{co32spec}, which appears to be consistent with a 
+We detect \cco line emission toward RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
+The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
 double-peaked profile. We estimate a line intensity of
@@
 linewidth used to infer the \bco line intensity ($\sim$700 \kms).
-Assuming the spatial extent between \bco and \cco is similar and therefore the emission is
+Assuming the spatial extents of \bco and \cco is similar and therefore the emission is
 magnified by the same amount, the measured line intensities
@@
 
-We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
+We detect PdBI 2\,mm continuum, as shown in \Fig{cont}. The integrated flux density is
 1.2\pmm0.2 mJy, with a peak flux
 $S_\nu$\,=\,800\pmm88\,$\mu$Jy\,beam\pmOne
-centered on the lensing galaxy. Slightly extended emission is also detected
-along the lensed arc. This suggests that the detected emission comes from
-both the foreground galaxy and the background galaxy and that the
+centered on the lensing galaxy. Slightly extended emission
+along the lensed arc is also detected.
+This suggests that we detect emission both in
+the foreground galaxy and in the background galaxy and that the
 emission is marginally resolved along its major axis.
-We subtract a point source model in $uv$-plane to remove the unresolved
+We subtract a point source model in the $uv$-plane to remove the unresolved
 emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
@@
 \begin{figure}[!htbp]
-\centering
 \includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
@@
 Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
-posterior probability distribution function (PDF).
+posterior probability distribution function (PDF) of the model parameters.
 In each model, we require a target acceptance rate of $\sim$0.25$-$0.5
@@
 \subsubsection{Interpretation of the Source-plane Morphology} \label{sec:caveat}
-The reconstructed source locations in \Fig{model} demonstrate
+The reconstructed source locations, as represented by magenta ellipses in \Fig{model}, demonstrate
 an intrinsic velocity gradient across the source plane, which is
@@
 factors listed in \Tab{model}, which to
-first order takes into account effect of differential lensing.
+first order takes into account the effect of differential lensing.
 This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
@@
 \end{tabular}
-\caption{Each panel corresponds to a lens model of RXJ1131 performed over a
-channel slice $\sim$100\,\kms of the \bco data. Top: channel maps of the
-PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
-The location of the foreground lensing galaxy is indicated by a black dot and
-its critical curve is traced by the orange solid line. The locations and
+\caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
+Top: each panel corresponds to a channel map of width $\sim$100\,\kms of the observed
+emission (red) overlaid on the best-fit models (grayscale).
+Bottom: residual images obtained by
+taking a Fourier transform after subtracting the best-fit model from the
+data in the $uv$-domain.
+In all panels, location of the foreground lensing galaxy is indicated by a black dot and
+its critical curve is traced by the orange solid line; locations and
 morphologies (half-light radii) of the reconstructed sources are
-represented by magenta ellipses.
-The caustic curves are represented as cyan lines. The beam of the
-PdBI observations is shown in the bottom right corner of each panel.
-Bottom: residual images of the best-fit models, obtained by
-taking the Fourier transform after subtracting the best-fit model from the
-data in the $uv$-domain. Contours start
+represented by magenta ellipses; the caustic curves are represented as cyan lines.
+Contours start
 at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
 where $n$ is a positive integer.
+The beam of the PdBI observations is shown in the bottom right corner. % of each panel.
+The reconstructed source-plane positions, as represented by the magenta ellipses, demonstrate an intrinsic velocity gradient of the \bco emission in RXJ1131.
+The best-fit model of the red-most channel (top left panel) contains two source components (see text for details).
 \label{fig:model}}
@@
 \subsubsection{Spatial Extent and Differential Lensing} \label{sec:differential}
-In the image plane shown in  \Fig{CO21mom}, the redshifted component is
+In the image-plane integrated line map shown in \Fig{CO21mom}, the redshifted component is
 cospatial with the Einstein ring seen in the
@@
 The spectra map covers an extent of $\sim$10"$\times$10"
-centered on the pixel that corresponds to the lensing galaxy.
+centered on the pixel that corresponds to coordinates of the lensing galaxy ($\alpha_{\rm J2000}$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44, $\delta_{\rm J2000}$\,=\,$-$12\degr31\arcmin58\farcs3).
 Spatial offset in arcsec is denoted in top left corner of each panel.
@@
 blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
-is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
+are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
 implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
@@
 \subsection{\bco Kinematics}
-Fitting a four-parameter double-Gaussian that describes two velocity peaks by a single FWHM
+Fitting two Gaussians with a single FWHM
 to the ``intrinsic'' \bco line profile of RXJ1131 (after correcting for lensing using
@@
 are separated by
-$\Delta v_{\rm sep}$ = 387\pmm45\,\kms, and a
+$\Delta v_{\rm sep}$ = 387\pmm45\,\kms, and each with a
 FWHM of 220\pmm72\,\kms.
@@
 one Gaussian to higher velocity than otherwise.
-If we instead fit the intrinsic line profiles with single-Gaussians, we find a FWHM of 600\pmm160\,\kms for RXJ1131
+To facilitate a comparison (\Sec{sizes}) with previous works, which were observed at lower spectral resolution,
+we also fit a single-Gaussian to the intrinsic line profiles.
+This yields FWHMs of 600\pmm160\,\kms for RXJ1131
 and 73\pmm43\,\kms for the companion galaxy.
@@
 consistent with a disrupted disk galaxy hosting an optically
-bright quasar and is in the process of merging.
+bright quasar and in the process of merging.
 
@@
 of 500 iterations, where the input parameters are perturbed
-according to random Gaussian distributions of sigmas
+according to random Gaussian distributions with standard deviations
 corresponding to their uncertainties.
@@
 $R_{t}$\,=\,10.7\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
-However, since emission is not resolved along the flat regime
+However, since the emission is not resolved along the flat regime
 of the rotation curve, the asymptotic velocity
@@
 In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
-Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.
+Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$. % beam smearing --> not resolving velocity info. within the beam
 
@@
 
-The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
+The asymptotic velocity ($V_{a}$) --- an extrapolation of the model
 out to radius beyond the disk scale-length and half-light radius --
-is not equivalent to maximum observed velocity ($V_{\rm max}$),
+is not equivalent to the maximum observed velocity ($V_{\rm max}$),
 which is commonly used in literature to parameterize disk rotation.
@@
 a central starburst caused by higher
-concentrations of star-forming gas towards the central regions -- owing to
+concentrations of star-forming gas towards the central regions --- owing to
 gravitational perturbations induced
@@
 
-\subsection{SED Modeling} \label{sec:SED}  % DONE
-We fit dust SED models to the
-24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
-include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
-to constrain the dust peak.
-The fit is performed with the code
+\subsection{SED Modeling} \label{sec:SED}
+We fit dust SED models to the 24\,\micron$-$2.2\,mm photometry
+using a modified-blackbody (MBB)
+function with a power-law attached to the Wien side to account for the MIR excess due to
+emission of warm and small dust grains.
+The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak.
+The fit is performed using the code
 \ncode{mbb\_emcee} \citep[e.g.,][]{Riechers13a,Dowell14a}, which samples the posterior
 distributions using an MCMC approach and uses instrumental
-response curves to perform color correction on-the-fly.
-The SED model consists of a modified-blackbody
-function with a power-law attached to the
-Wien side to account for an excess in the MIR owing to emission of
-warm and small dust grains.
+response curves to perform color correction.
 % Previous studies find that in the absence of mid-IR data, a powerlaw slope
@@
 %uncertainties for the PdBI continuum in our fitting procedure.
-The model is thus described by five free parameters: the rest-frame characteristic dust
+The model is described by five free parameters: the rest-frame characteristic dust
 temperature ($T_{d}$), the emissivity index ($\beta$), the power-law index
@@
 a Gaussian prior centered around
-$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and a uniform prior with an upper limit of
+1.9 with a standard deviation of 0.3 on $\beta$, and a uniform prior with an upper limit of
 1000\,$\micron$ on $\lambda_0$.
@@
 as the best-fit parameters, as listed in \Tab{SED}.
+The best-fit models are shown in \Fig{SED} along with the broadband photometry that are listed in \Tab{photometry}.
 
 \input{table_mbb}
-In the first model, we include the 24\,$\micron$ data
-to constrain the power-law index. Based on the
-best-fit of this model, we find an apparent
+In the first model, we attempt to constrain the power-law index by including
+the 24\,$\micron$ data. Based on the resulting posterior PDFs, we find an apparent
 \fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
@@
  and
- a total IR luminosity of $\sim$1.5\E{12}\,\Lsun,  implying RXJ1131 is a ULIRG.
-Assuming a Salpeter initial
-mass function \citep{Salpeter55a}, we find a
+ a total IR luminosity of $\sim$1.5\E{12}\,\Lsun, implying RXJ1131 can be classified as an ULIRG.
+Assuming a \citet{Salpeter55a} initial
+mass function (IMF), we find a
 SFR$_{\rm FIR}$ of 120\pmm63\,\sfrU using a
@@
 
+We derive the stellar mass of RXJ1131 by
+fitting SED models to the rest-frame UV-to-mm photometry   % original version: UV to IR; high-z UV to radio
+using the high-$z$ version of the {\sc magphys} code \citep{Magphys08a,Magphys15a}.
+Two sets of stellar templates  modeled using either the \citet{BC03a} or the unpublished
+Charlot \& Bruzual 2007 stellar population synthesis code
+are provided in the {\sc magphys} package.
+We adopt the former set.
+To minimize contaminations from the quasar, we only fit to the {\it HST}, {\it Herschel}, and PdBI data,
+where both the {\it HST} and the PdbI 2\,mm photometry are de-blended from the AGN
+(see bottom section of \Tab{photometry}).
+The input photometry are corrected for lensing using their respective magnification factors
+to account for differential lensing.
+We thus find a stellar mass of $M^*$\eq2.95\petm{1.32}{0.86}\E{10}\,\Msun, which
+is the median value of the posterior probability distribution and
+the uncertainties are derived from the 16$^{\rm th}$ and 84$^{\rm th}$ percentiles.
+We note that the models are over-fitted with a best-fit $\chi^2$\eq0.41
+which is unsurprising due to sparse sampling of the SED
+compare to the number of free parameters.
+The resulting dust mass and \LIR are consistent with those obtained
+from the MBB$+$power-law models within the uncertainties, albeit some differences
+in the assumptions behind the two methods.
+The consistency may be attributed to the large uncertainties arising from the lack of photometric constraints on the models and the fact that the best-fit parameters from the MBB method are similar to those of the \ncode{magphys} method.
+%  Mdust 8.427   8.522   8.617
+% Ldust  1.191E+001  1.204E+001  1.219E+001; but from 3-1000 \micron; should compare with our \LIR.
+%
+% Salpeter M* ~ 1.8 * Chabrier
+% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up" time of $M^*$$/$SFR\ssim440 Myr for RXJ1131.
+
+% -------
 % WISE flux is slightly higher than the IRAC point, probably due to a smaller
 % aperture used in IRAC extraction (both from archive).
-% It is also not straight-forward to fit an SED model covering a wider wavelengths because of
-% differential lensing.
 \begin{figure}[!htbp]
@@
 \includegraphics[trim=5 5 5 5, clip, width=0.45\textwidth]{../Figures/FullSED}
-\caption{SEDs of RXJ1131 and its lensing galaxy. The photometry is listed in \Tab{photometry}.
+\caption{SEDs of RXJ1131 at $z$\eq0.654 and its lensing galaxy at $z$\eq0.295.
+The photometry data (colored markers) are not corrected for lensing (see \Tab{photometry}).
 Best-fit SED models of the thermal dust emission towards RXJ1131
-with(out) MIR constraint at 24\,$\micron$ are plotted as dashed (solid) lines.
+are obtained assuming a MBB$+$power-law model.
+The dashed (solid) line corresponds to a model with (without) MIR constraint at 24\,$\micron$, respectively.
 \label{fig:SED}}
@@
 %ULIRGs (z < 0.3) studied in CO(1-0) by Solomon97a: ~1/3 of them have double-peaked or flat-topped spectrum. But their linewidths are based on single Gauss fit.
-Yet, given the dynamic nature of these galaxies,
+Yet, given the merging nature of these galaxies,
 a CO linewidth of $\sim$600\,\kms may not be surprising.
@@
 which is more
-extended than the average in a sample of disk-like U/LIRGs studied by
+extended than the average of a sample of disk-like U/LIRGs studied by
 \citet[]{Ueda14a}, % who find an average radius of 3.5\pmm2.3\,kpc
@@
 \subsubsection{Dynamical Mass}
-Assuming the gas is virialized,
-the dynamical mass can be approximate as
-$M_{\rm dyn} = \sigma^2 R / G$,
+Assuming the gas to be virialized,
+the dynamical mass can be approximated by
+$M_{\rm dyn}$\ssim$\sigma^2 R / G$,
 where $\sigma$ is the velocity dispersion, or the rotational velocity in the case of a rotating disk model
@@
 we find a dynamical mass of
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1.7\E{11}\,\Msun enclosed
 within the CO-emitting region in RXJ1131.
@@
 
-Using the velocity dispersion obtained by fitting a single Gaussian to the
-line profile of the companion ($\sigma$ = 30\,\kms)
-and its intrinsic source size of $\sim$700\,pc obtained from the {\em HST}
-$V$-band lens model \citepalias{Brewer08a},
-we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
-This corresponds to $M_{\rm dyn}$\,=\,5.8\E{8}\,\Msun if we assume an
-inclination angle of 30$\degr$.
-We adopt the $V$-band size as the radius $R$ in the above estimate 
-owing to the fact that it is the least uncertain constraint on the source size for the companion.
-However, since this dynamical mass is substantially lower than the gas mass, which is 
-a more reliable estimate based on the data in hand, 
-we do not use this dynamical mass to derive other physical parameters.
-The underestimated dynamical mass may reflect
-the dusty nature of the companion, which causes its $V$-band source size to 
-appear much smaller than its true extent. 
-If we use the half-right radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc obtained from our best-fit lens 
-model as the unobscured source size, we find a dynamical mass of 
-$M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun (assuming $i$\eq30$\degr$), which is physically more sensible 
-than that derived using the $V$-band source size. 
+Using the velocity dispersion ($\sigma$ = 30\,\kms) obtained by fitting a single Gaussian to the
+de-lensed line profile of the companion and a
+half-light radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from the best-fit lens model,  % redmost channel
+we find a dynamical mass of
+$M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun for the companion,
+assuming an inclination angle of $i$\eq30$\degr$.
 The uncertainty here only includes that of the CO source size.
-Given the large systematic uncertainties associated with the model-based source size and
-the lack of constraint on the inclination angle, we do not use this dynamical mass in the remaining of this paper.
+% Given the large systematic uncertainties associated with the model-based source size and
+% the lack of constraint on the inclination angle, we do not use this dynamical mass in the remaining of this paper.
+On the other hand,
+% we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
+we find $M_{\rm dyn}$\,$\sin^2 30\degr$\,=\,5.8\E{8}\,\Msun
+if we adopt the better-constrained $V$-band source size of $\sim$700\,pc \citepalias{Brewer08a}.
+This dynamical mass is substantially lower than the gas mass, and
+% , which is a more reliable estimate based on the data in hand,
+% we do not use this dynamical mass to derive other physical parameters.
+% The underestimated dynamical mass may reflect
+may be reflecting the dusty nature of the companion.
+% in which the $V$-band source size to
+% appear much smaller than its true extent.
 
@@
 \citep[]{Bothwell13a} and
-local ULIRGs \citep{Wilson08a}, but lower than of the Milky Way by
+local ULIRGs \citep{Wilson08a}, but lower in the Milky Way by
 $\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
@@
 
-There are a number of systematic uncertainties associated with this quantity. For instance,
+There are a number of systematic uncertainties associated with the derived gas-to-dust ratio. For instance,
 the mass opacity coefficient $\kappa$,
@@
 we assumed sub-thermal excitation between \bco and \aco emission, but
-we expect this to be a minor effect as CO emission in ULIRGs are thermalized up to $J$ = 3 or 4.
-We also note that the gas-to-dust ratio derived for RXJ1131 maybe biased low as the gas is likely to
+we expect this to be a minor effect as CO emission in ULIRGs are typically thermalized up to $J$ = 3 or 4.
+We also note that the gas-to-dust ratio derived for RXJ1131 may be biased low as the gas is likely to
 be more extended than the dust. Consequently, the overall magnification factor
@@
 Using a wavelength range of 40\,$-$\,500\,$\micron$ defined
-in \citetalias{Combes13a} as the far-IR luminosity,
+in \citetalias{Combes13a} for the far-IR luminosity,
 we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$,
@@
 low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a} and high-$z$ disk-like galaxies \citep{Daddi08a}.
-Assuming an \alphaco of 0.8\,\alphaU is appropriate for RXJ1131, this would imply that
+Assuming an \alphaco of 0.8\,\alphaU, this would imply that
 it is converting gas into stars at an efficiency
@@
 a higher gas fraction to be retained and redistributed over a large extent in
-the merged galaxy \citep{Hopkins09a}. With this, it is plausible that RXJ1131 
+the merged galaxy \citep{Hopkins09a}. In this scenario, it is plausible that RXJ1131
 will evolve into a disk galaxy with a small bulge component upon merging given its low SFE and the extended disk.
@@
 Other mechanisms e.g. bar-like structures that are more efficient at removing angular momentum will
-be required in order to transform the gas disk of RXJ1131 into a stellar spheroid and evolve into 
-an E/S0 galaxy. Without these, it is more conceivable that RXJ1131 will retain its disk component and
+be required to transform the gas disk of RXJ1131 into a stellar spheroid and evolve into
+an E/S0 galaxy.
+Thus, RXJ1131 may retain its disk component and
 evolve into a disk galaxy upon its final coalescence with the companion.
@@
 \Fig{chanmap}, where the line center of the CO gas is not co-spatial
-with the optical quasar --- the point-like images along the lensing arc is 
+with the optical quasar --- the point-like images along the lensing arc are
 offset to the NW of the CO line center emission.
-On the other hand, we find that the redshift of the \oiii lines tracing the narrow line region (NLR) 
-is fully consistent with the systemic redshift, supporting previous claims that \oiii lines are good proxies
+On the other hand, we find that the redshift of the [O\,{\scriptsize III}] lines tracing the narrow line region (NLR)
+is fully consistent with the systemic redshift, supporting previous claims that [O\,{\scriptsize III}] lines are good proxies
 to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
-% since BLR are gravitationally bound to BH, and NLR may not be
-
-%Velocity Offsets of $\lesssim$\,500\,\kms in other AGNs and their host galaxies have been reported in the literature.
+
+One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
+the central AGN, whereas this condition is not necessary for NLRs.
+From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
+median of 97\kms and a dispersion of 269\,\kms in the distribution of
+the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
+that large offsets are uncommon. Nevertheless,
+offsets as large as $\sim$\,500\,\kms have been observed in some cases.
 %% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
@@
 
-Large velocity offsets between emission lines of the
+Alternatively, large velocity offsets between emission lines of the
 BLR and the NLR may arise in a recoiling black hole (BH),
@@
 %between \mgii and \oiii lines \citep{Steinhardt12a}.
-One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, \citet{Komossa08a} 
-suggest the possibility of a recoiling black hole in this system due to an offset of 2650\,\kms 
-between a set of narrow emission lines and a second set of broad Balmer 
-and high-ionization forbidden lines.  % offset in this system: between a set of redshifted (narrow) versus a set of blueshifted (broad).
+One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
+a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
+have been observed \citep{Komossa08a},  similar to the case for RXJ1131.
+% offset in this system: between a set of redshifted (narrow) versus a set of blueshifted (broad).
 However, this scenario is refuted recently by \citet{Decarli14a}, who confirm that the
 BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
-This is in contrast with the case in RXJ1131, our CO observations confirm the blueshifted BLR lines.
-The fact that the BH in RXJ1131 has a high spin parameter \citep{Reis14a}
-renders the recoiling BH scenario a viable option for the origin of the blueshift. 
-Since this model requires a merged BH, this interpretation would imply RXJ1131 have 
-already encountered with the companion galaxy, which could explain
-the highly spinning BH observed in RX1131.
-In this picture, the presence of a nearby companion observed in our data may reflect that RXJ1131 is in its 
-subsequent stages of (minor) merging resulting from previous passage of a major merger.
-
-\subsection{The $M_{\rm BH}$$-$\mdyn Relation}
-% the gas mass of RXJ1131 is 1.3\E{10}\,\Msun, 
-% dynamical mass in RXJ1131 is $\sim$8.3\E{10}\,\Msun 
-% total dust mass in the merging system is $\sim$2-4\E{8}\,\Msun,  % using CO magnification factor
-Assuming RXJ1131 follows the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation reported by \citet{HR04a}, 
-the virial-based black hole mass \mbh$\sim$\,8\E{7}\,\Msun \citep{Sluse12a} corresponds 
-to a stellar bulge mass of $M_{\rm bulge}$\eq5.4\E{10}\,\Msun.
-% \ie $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.15\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.83
-This implies that the bulge component is responsible for making up $\sim$65\% of the dynamical mass. 
-If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass.
-Since the dust mass only contributes a small fraction to the total mass, a factor of $\sim$2 difference is minor.}
-from the dynamical mass and ignore a contribution from the dark matter, this would
-yield an upper limit on the stellar mass of 6.8\E{10}\,\Msun. 
-Thus, the bulge mass derived above based on the local relation is not unphysical.
-The stellar mass upper limit would also imply a lower limit on the 
-$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.12\%, which is consistent with the local relation within the scatter and with other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
-%Depending on the exact dark matter fraction, RXJ1131 may lie above the local $M_{\rm BH}$/$M_{\rm bulge}$.
-
-A dark matter fraction of over $f_{\rm DM}$\ssim0.5 within the radius of which we used to derive the 
-dynamical mass (\ie $\lesssim$\,6\,kpc or $\sim$\,0.6$R_e$) would be required for RXJ1131 to 
-lie above the local relation and fall outside the range of $M_{\rm BH}$$/$$M_{\rm bulge}$ found in 
-\citet{McLure06a}, which is unlikely given its dynamical mass and rotation velocity 
-% \ie based on the dark matter fraction as a function of half light radius found; Figure 2 in Courteau15
-% Courteau15a: f<0.5 at 0.6*Re for gal. with cir. velocity like RXJ1131
-\citep{Courteau15a}.
-% $f_\textrm{DM}$ is expected to increase with cosmic time \citep{Beifiori14a} and that the local DM fraction is 16-28% from dynamical studies \citep{Thomas11a, Cappellari13a} and based on predictions from simulations of 18%-38% \citep{Naab07a}.
+This is in contrast with RXJ1131, where our CO observations confirm the blueshifted BLR.
+% The fact that the BH in RXJ1131 has a high spin parameter \citep[a\ssim0.9;][]{Reis14a}
+% renders this scenario
+% % the recoiling BH scenario
+% a viable option for the origin of the blueshift.
+Since this model requires a merged BH, it would imply that RXJ1131 might
+have been in a previous merger, which would also explain
+the highly spinning BH in RX1131 \citep[a\ssim0.9;][]{Reis14a}.
+% In this picture, the presence of a nearby companion observed in our data may reflect that RXJ1131 is in its
+% subsequent stages of (minor) merging resulting from previous passage of a major merger.
+
+\subsection{The $M_{\rm BH}$$-$\mbulge Relation}
+Based on the black hole mass of \mbh$\sim$\,8\E{7}\,\Msun \citep{Sluse12a},
+and adopting the stellar mass of $M^{*}$\,=\,2.95\petm{1.32}{0.86}\E{10}\,\Msun
+as an upper limit to the bulge mass,
+we find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of 0.19\%$-$0.38\%.
+This is consistent with other intermediate-$z$ radio-loud AGNs \citep{McLure06a}
+but lies above the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation \citep{HR04a}.
+The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local
+AGNs is consistent with the emerging picture that quasars
+grow faster than their host galaxies at higher redshifts.
+% \ie $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.15\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.8
 
@@
 \section{Summary and Conclusions} \label{sec:sum}
-We present PdBI \bco and CARMA \cco observations toward the
-quadruply-imaged quasar RXJ1131 at $z_{\rm CO}$\ssim$0.654$, 
-benchmarking the first resolved CO imaging at intermediate redshift.
-We find a brightness temperature ratio of $r_{32}$\eq$0.66\,\pm\,0.41$ between \bco and 
-\cco. Taking into account the large phase errors associated with \cco, this
+We present PdBI \bco and CARMA \cco observations towards the
+quadruply-imaged quasar RXJ1131 at $z_{\rm CO}$\ssim$0.654$, making this the first
+resolved CO study at intermediate redshift.
+Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.66\,\pm\,0.41$
+between the \bco and \cco lines.
+Taking into account the large phase errors associated with the \cco measurement, this
 is consistent with thermalized excitation.
-We perform astrometric correction using archival VLA data, in which we detect continuum emission at 5\,GHz in 
-both the lensing galaxy and RXJ1131.
-In addition, we detect marginally resolved 2\,mm continuum underlying the \bco line in both galaxies.
-
-We perform a lens modeling on different velocity channels of \bco to study the intrinsic gas dynamics of RXJ1131. 
-Our models indicate a CO-emitting source near RXJ1131, confirming 
-the presence of an optically faint companion reported in previous studies \citepalias{Claeskens06a,Brewer08a}. 
-The source-plane positions form a symmetric velocity field, 
-which is consistent with a kinematically-ordered disk galaxy.
-We find that the magnification factors vary from $\mu_{\rm L}$\ssim3 to $\sim8$ across different
-velocity channels, implying an extended gas distribution.
-Upon correcting for lensing magnification and subtracting a line flux contribution from the companion, 
-we find an intrinsically symmetric double-horned line profile for RXJ1131.
-This together with the symmetric velocity gradient seen in both the source plane and the image plane 
-strongly argues for a rotating disk morphology for RXJ1131, consistent with previous findings \citepalias{Claeskens06a}.
-Assuming thermalized excitation and \alphaco=\,0.8\,\alphaU,
+We also detect marginally resolved
+2\,mm continuum underlying the \bco line in the PdBI data
+and resolved radio continuum emission at 5\,GHz in the archival VLA data
+in both the foreground lensing galaxy and RXJ1131.
+Using
+positional priors from an astrometric-corrected {\it HST} image,
+we de-blend broadband photometry spanning the rest-frame UV to radio wavelengths
+that we have compiled from public catalogues and previous optical studies, as well as from those we have
+extracted using aperture photometry.
+
+Based on our lens modeling analysis of different \bco velocity channels,
+%  to study the intrinsic gas dynamics of RXJ1131.
+we find a secondary CO-emitting source near RXJ1131 whose coordinates
+are consistent with those of an optically faint companion reported in previous optical studies
+% inferred from previous lens modeling in the optical wavelengths
+\citepalias{Claeskens06a,Brewer08a}.
+%The source-plane positions form a symmetric velocity field,
+% which is consistent with a kinematically-ordered disk galaxy.
+The magnification factor inferred from our best-fit models is found to
+vary from $\mu_{\rm L}$\ssim3 to $\sim8$ across channels. This is indicative of an extended molecular gas
+distribution in the host galaxy of RXJ1131 and thus different kinematic components
+of the gas are magnified inhomogeneously.
+Upon correcting for lensing magnification and subtracting a contribution from the companion,
+we find an intrinsically symmetric double-horned \bco line profile for RXJ1131.
+This together with a symmetric velocity gradient reconstructed in the source plane argues for a rotating disk morphology for RXJ1131, in good agreement with previous findings \citepalias{Claeskens06a}.
+Assuming thermalized excitation between \aco and \bco and \alphaco=\,0.8\,\alphaU,
 we find a lensing-corrected gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
@@
 and $($1.92\pmm0.09$)$\,\E{9} \Msun for the companion.
-This implies a {\em gas} mass ratio of $\sim$7:1. 
-We derive a dynamical mass of $M_{\rm dyn}$\,=\,(8.3\pmm1.9)\E{10}\,\Msun for RXJ1131 and 
- $M_{\rm dyn} \sin^2 30\degr$\ssim BLAH\E{BLAH}\,\Msun for the companion. 
-We thus find a gas mass fraction of $\sim$0.19 for RXJ1131, confirming its gas-rich nature.
-The derived gas fraction is also consistent with the decreasing trend of molecular gas content
-since $z$\ssim1.0 \citep{Combes13a}.
-Owing to the lack of stringent constraints on the individual galaxy mass of RXJ1131 and the companion, we use 
-their gas mass ratio to classify the system as a ``wet'' minor merger.
-We note that the merger system studied here is in stark contrast to the
-``wet-dry'' merger SMM J094135$+$10277 at $z$\eq2.8,  
-where the quasar host galaxy harbors $\gtrsim$\,$5$ times less gas mass than its companion \citep{Riechers13a}.
-
-Fitting dust SED models to the submm photometry obtained with {\it Herschel} and additional IR photometry compiled from 
-public catalogs, we derive a lensing-corrected dust mass of $M_{\rm dust}$\eq4\E{8}\,\Msun and
-a lensing-corrected IR luminosity of \LIR$\sim$\,1.5\E{12}\,\Lsun, corresponding to a
-SFR$_{\rm FIR}$ of 120\pmm63\,\sfrU. 
-This implies that the merger system of RXJ1131 is dusty in nature with ongoing starbursts.
-{\bf who contains the dust?}
+This corresponds to a {\em gas} mass ratio of $\sim$7:1.
+Using the source-plane \bco size of $R$\ssim6\,kpc for RXJ1131, we find a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun,
+% \,=\,(8.3\pmm1.9)\E{10}\,\Msun
+% and $M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun for the companion,
+and thus a gas mass fraction of $\sim$0.19.
+This gas fraction is consistent with the trend of decreasing molecular gas content
+since $z$\ssim1 \citep[e.g.,][]{Lagos11a, Combes13a} which has been suggested as the cause for
+the decline in SFR towards $z$\ssim0 \citep[and references therein]{CW13}.
+Due to the lack of stringent constraints on the individual galaxy mass of RXJ1131 and of the companion, we classify the system as a ``wet'' minor merger on the basis of their gas mass ratio.
+%The merger system studied here is in stark contrast to the
+%``wet-dry'' merger SMM J04135$+$10277 at $z$\eq2.8,
+%where the quasar host galaxy harbors $\gtrsim$\,$5$ times less gas mass than its companion \citep{Riechers13a}.
+
+Fitting dust SED models to the IR-to-mm photometry, we derive
+lensing-corrected $M_{\rm dust}$\ssim4\E{8}\,\Msun,
+\LIR$\sim$\,1.5\E{12}\,\Lsun, % which indicates that the host galaxy can be classified as a ULIRG.
+% We also derive a far-IR luminosity, which yields a SFR$_{\rm FIR}$\ssim120\,\sfrU.
+and a far-IR luminosity that corresponds to a SFR$_{\rm FIR}$\ssim120\,\sfrU.
+These physical properties suggest that the merger system is dusty in nature with active starburst activity.
+We also derive a stellar mass of $M^{*}$\ssim3\E{10}\,\Msun by fitting SED models to the
+rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit, in order to
+take into account the effect of differential lensing.
 % compare intrinsic CO size and stellar
-Comparing the gas and stellar distributions, we
-find that the CO gas is of similar spatial extent as the old and long-lasting stellar populations, whereas 
-sites of recent star formation are embedded within the molecular gas reservoir.
-The starburst taking place in the inner few kpc is likely a consequence of 
-gas accumulation driven by interactions with the companion.
+The source-plane distribution of the gas and stellar populations of different ages
+indicates that the CO gas is of similar spatial extent as the old and long-lasting stellar populations, whereas
+recent \SF regions appear to be embedded within the inner few kpc of the molecular gas reservoir.
+The compact \SB in RXJ1131 is likely a consequence of gas accumulation driven by interactions with the companion.
 While properties such as CO linewidths, CO size, SFR, and gas mass found in RXJ1131
-resemble local ULIRGs and high-$z$ starbursts, 
-its SFE is comparable to that of nearby and high-$z$ disk-like galaxies rather than 
-other ULIRGs. This is in agreement with its disk-like kinematic signatures. 
-Theoretical simulations suggest that the disk component of a gas-rich progenitor galaxy with low SFE can be
-retained upon merging since the efficiency in removing angular momentum of the gas via 
-gravitational torques provided by stellar components is reduced.
-Within this context, the extended molecular gas disk of RXJ1131 together with its low SFE implies that
-the nuclear starburst in RXJ1131 will buildup a larger bulge in the final product but is 
-insufficient to transform into a E/S0 galaxy.
-
-The optical BLR lines are blueshifted by $\sim$780\,\kms from the systemic redshift, 
-implying the AGN is offset from the dynamical center of its host galaxy.  The offset could 
-be the manifestation of a recoiling black hole in RXJ1131.
-Since this model requires a merged BH, this interpretation would imply RXJ1131 have 
-already encountered with the companion galaxy, which would also explain the highly spinning black hole. 
-Given the presence of the companion in the current data, RXJ1131 may be in 
-its subsequent stages of minor merging from a previous major merger, as commonly predicted in simulations.
-% Our results thus illustrate a self-consistent picture of a pair of interacting gas-rich, dusty galaxy.
-
-% Dynamical mass has been used as a proxy to the \bhrelation relation in a few high-$z$ studies,
-% but this approach remains unexplored at intermediate redshifts.
-Our study here demonstrate the first resolved CO observations at intermediate redshift, allowing us to
-explore the \bhrelation relation at $z$\ssim0.65 using dynamical constraints.
-We illustrate the use of gravitational lensing to allow for a detailed study of the ISM properties of a quasar host galaxy
-and a comparison of distributions between the dust, gas, and stars in the host galaxy despite emission of the quasar, and that
-dynamical lens modeling provides a promising avenue 
-to study the gas kinematics and dynamics in distant quasar host galaxies. 
-The first use of such technique is presented by \citet{Riechers08a}, who reconstruct a velocity gradient and 
-constrain the gas dynamics in the quasar PSS J2322$+$1944 at $z$\,$>$\,4, which is
-the only other similar system where the emission of the host galaxy is lensed into an Einstein ring configuration.
-Similar resolved CO studies at intermediate redshift are needed to understand the co-evolution of SMBHs and their 
-host galaxies through cosmic time.
+resemble those of local ULIRGs and high-$z$ starburst galaxies,
+its SFE is comparable to those of nearby and high-$z$ disk-like galaxies rather than
+\SB systems. %
+% This results from the SFR sitting at the low end, and gas mass at the high end among \SB systems
+% This is in agreement with its disk-like kinematic signatures.
+Recent theoretical simulations have illustrated that the disk component of a gas-rich
+progenitor galaxy with low SFE can be
+retained upon merging since the efficiency at removing angular momentum of the gas via
+gravitational torques provided by stellar components is reduced in such a system.
+% and the gas rapidly reform a cold disc in the background.
+As such, the extended molecular gas disk of RXJ1131 together with its low SFE may be indications
+that the nuclear starburst in RXJ1131 could form a
+larger stellar bulge in the merger remnant upon coalescing, and yet, the
+inefficient removal of gas angular momentum renders it unlikely
+to evolve into an E/S0 galaxy.
+
+Using the CO redshift as the systemic redshift for the host galaxy of RXJ1131, we find
+that the optical BLR lines reported in previous studies are blueshifted by $\sim$780\,\kms.
+This implies that the AGN is offset from the dynamical center of its host galaxy.
+One explanation could be that the
+BLRs are gravitationally bound to the central AGN, whereas this condition is not necessary for NLRs.
+Since such an offset is typically $\sim$100\pmm270\,\kms,
+we thus raise an alternative explanation of
+of a recoiling black hole in RXJ1131, which
+would also explain the highly spinning black hole.
+% This model requires a merged BH, this interpretation would imply that RXJ1131 was
+% in a previous merger.  %, which would also explain the highly spinning black hole.
+%Given the presence of the companion in the current data, RXJ1131 may be in
+%its subsequent stages of minor merging from a previous major merger, as commonly predicted in simulations.
+
+Adopting the stellar mass as an upper limit to the bulge mass of RXJ1131, we find a
+$M_{\rm BH}$$/$$M_{\rm bulge}$$\gtrsim$0.27\%, providing
+a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
+The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio compared to the local relation suggests that the
+black hole in RXJ1131 grows faster or earlier than its host galaxy than the local counterparts.
+This is consistent with existing studies of the evolution in the co-eval growth between SMBHs and their host galaxies.
+
+This work demonstrates that, with the aid of
+gravitational lensing and
+dynamical lens modeling of resolved spectral line observations,
+it is possible to study the gas kinematics and dynamics in high-$z$ quasar host galaxies
+% in great details
+despite strong quasar emission.
+The first use of such technique is presented by \citet{Riechers08a}, who reconstruct a source-plane
+velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
+which is also the only other similar system whose host galaxy is lensed into an Einstein ring configuration.
 

### 2016-08-04 src/SED/SEDplotMagphys.py
update ls

@@ -395,10 +395,10 @@ res_noMIPS = mbb_emcee.mbb_results(h5file=filename_noMIPS)
 wave_SED, flux_SED, flux_unc_SED = res.data
 p_wave = np.linspace(wave_SED.min() * 0.5, wave_SED.max() * 1.5, 200)
 
-ax.plot(p_wave, res.best_fit_sed(p_wave), 'k--', lw=1.25,
+ax.plot(p_wave, res.best_fit_sed(p_wave), 'k--',
         label='MBB fit with 24 um', alpha=1.0, zorder=0.65)
-ax.plot(p_wave, res_noMIPS.best_fit_sed(p_wave), '-',
-        color='#152863', lw=1.25, label='MBB fit without 24 um',
+ax.plot(p_wave, res_noMIPS.best_fit_sed(p_wave), '-.',
+        color='#152863', label='MBB fit without 24 um',
         alpha=0.9, zorder=0.5)
 
 
@@ -424,7 +424,7 @@ ax.set_xscale("log")
 ax.set_ylabel(r'S$_{\nu}$ [mJy]', fontsize=16)
 ax.set_xlabel(r'$\lambda_{\rm obs}$ [$\mu$m]', fontsize=16, fontweight='bold')
 
-led = plt.legend(loc='upper right', fontsize=13, numpoints=1,
+led = plt.legend(loc='upper right', fontsize=14, numpoints=1,
                  fancybox=True, borderpad=0.8,
                  handlelength=1.25, labelspacing=0.3)
 ax.tick_params(length=14, pad=5)

### 2016-08-04 WRITEUP/ms.tex
ready to send DR

@@
 The input photometry are corrected for lensing using their respective magnification factors
-to account for differential lensing.
+to account for differential lensing (light blue circles in \Fig{SED}).
 We thus find a stellar mass of $M^*$\eq2.95\petm{1.32}{0.86}\E{10}\,\Msun, which
@@
 compare to the number of free parameters.
-The resulting dust mass and \LIR are consistent with those obtained
+The resulting dust mass and IR luminosity are consistent with those obtained
 from the MBB$+$power-law models within the uncertainties, albeit some differences
@@
 \centering
-\includegraphics[trim=5 5 5 5, clip, width=0.45\textwidth]{../Figures/FullSED}
-\caption{SEDs of RXJ1131 at $z$\eq0.654 and its lensing galaxy at $z$\eq0.295.
-The photometry data (colored markers) are not corrected for lensing (see \Tab{photometry}).
-Best-fit SED models of the thermal dust emission towards RXJ1131
-are obtained assuming a MBB$+$power-law model.
-The dashed (solid) line corresponds to a model with (without) MIR constraint at 24\,$\micron$, respectively.
+\includegraphics[trim=5 5 5 5, clip, width=0.445\textwidth]{../Figures/FullSED_withMagphys}
+\caption{SEDs of the host galaxy of RXJ1131 at 
+$z_{\rm CO}$\eq0.654 and of the lensing galaxy at $z$\eq0.295.
+The photometry data (colored markers) are listed in \Tab{photometry}, except for those
+shown in light blue circles, which are corrected for lensing magnification (see \Sec{SED}).
+Assuming an MBB$+$power-law model for the thermal dust emission towards RXJ1131,
+the dashed (dashed-dotted) line corresponds to the best-fit model 
+with (without) MIR constraint at 24\,$\micron$.
+The solid black line shows the best-fit SED model with dust attenuation (light blue solid line)
+obtained using the \ncode{magphys} code.
 \label{fig:SED}}

### 2016-08-10 WRITEUP/ms.tex
detected CO should be ~30 instead of 70

@@
 $(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed ---
-only unresolved CO observations have been carried out for $\sim$$70$ ULIRGs up to date \citep{Combes11a, Combes13a}.
+only unresolved CO observations have been carried out for $\sim$$30$ ULIRGs up to date \citep{Combes11a, Combes13a}. %18+15
 

### 2016-08-15 WRITEUP/ms.tex
add ack RP,DR

@@
 \acknowledgments
+DR and RP acknowledge support from the National Science Foundation
+under grant number AST-1614213 to Cornell University. RP acknowledges
+support through award SOSPA3-008 from the NRAO. DR acknowledges the
+hospitality at the Aspen Center for Physics and the Kavli Institute
+for Theoretical Physics during part of the writing of this manuscript.
 This work is based on observations carried out under project number S14BX

### 2016-08-28 WRITEUP/ms.tex
added DR's comments, major change: gas fraction, sSFR, intro and conclusion, and removed 'nuclear SB'

@@
 \citestyle{aa}
-\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131$-$1231 at $z$\,=\,0.65}
+\shorttitle{Molecular Gas Dynamics in the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
 \shortauthors{Leung, Riechers \& Pavesi}
@@
 
-\title{Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654}
+\title{Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 \begin{abstract}
-We report observations of the \bco and \cco line emission towards
-the quadruply-imaged quasar
-RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
-\pdbi (PdBI) and \carma (CARMA), making this the first spatially resolved
-CO study at intermediate redshift.
-Our lens modeling shows that the highly asymmetric double-horned line profile
-observed in the \bco spectrum is mainly a result of differential lensing, where
+We report observations of \bco and \cco line emission towards
+the quadruply-lensed quasar
+RXS\,J1131$-$1231 (hereafter RXJ1131) at $z$\,=\,0.654 obtained using the
+\pdbi (PdBI) and the \carma (CARMA).
+Our lens modeling shows that the asymmetry of the double-horned \bco line profile
+is mainly a result of differential lensing, where
 the magnification factor varies from $\sim$3 to $\sim$8 across
 different kinematic components.
-The intrinsically symmetric line profile with a clear velocity
-gradient in the source-plane suggests that
-the quasar host galaxy is a rotating disk.
+The intrinsically symmetric line profile with a conspicuous source-plane velocity
+gradient suggests that
+the quasar host galaxy is an extended rotating disk, with a CO size of $R$$\sim$6\,kpc in radius and
+a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
 In addition, we find a secondary CO-emitting source near RXJ1131 whose location is
 consistent with the optically-faint companion reported in previous studies.
-The lensing-corrected gas mass of
-$M_{\rm gas}$\ssim1.4\E{10}\,\Msun inferred for RXJ1131
-and \ssim2\E{9}\,\Msun for its companion correspond
+We decompose the lensing-corrected total \bco line flux into two components and 
+find a lensing-corrected gas mass of $M_{\rm gas}$\ssim1.4\E{10}\,\Msun for RXJ1131
+and \ssim2\E{9}\,\Msun for the companion, corresponding
 to a gas mass ratio of $\sim$7:1.
-The extended CO gas disk in RXJ1131 ($R$$\sim$6\,kpc) yields a dynamical mass
-of $M_{\rm dyn}$\ssim8\E{10}\,\Msun, and thus a gas mass fraction of $\sim$19\%,
-which is consistent with the trend of decreasing molecular gas fraction since $z$\ssim1.
-The lensing-corrected $M^{*}$\ssim3\E{10}\,\Msun,
-$M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun, and SFR$_{\rm FIR}$\eq120\pmm63 \sfrU of RXJ1131
-together with the source-plane morphology of the gas and the stellar populations
-suggest that ongoing \SBs are embedded within the molecular gas reservoir,
-and that the nuclear \SBs are likely triggered by
-interactions with the companion.
-The $M_{\rm BH}$$/$$M_{\rm bulge}$ of $\gtrsim$0.27\% derived for RXJ1131 lies above the
-local relation but is consistent with other radio-loud galaxies at this epoch, suggesting
-that the co-evolution between RXJ1131 and its host galaxy is different than those of local AGN host galaxies.
+The gas mass fraction of $\sim$19\% inferred for RXJ1131 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim1 reported in recent studies.
+The lensing-corrected stellar mass $M_{*}$\ssim3\E{10}\,\Msun,
+dust mass $M_{\rm dust}$\ssim4\E{8}\,\Msun, IR luminosity $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun, and 
+star formation rate SFR$_{\rm FIR}$\eq120\pmm63 \sfrU of RXJ1131
+together with its source-plane morphology of the gas and stellar populations
+indicate ongoing star-formation activity that maybe as extended as the molecular gas reservoir.
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of 0.27\petm{11}{8}\% that is higher
+than the local value
+but consistent with other galaxies at this epoch. Collectively, our results suggest
+that the bulk of the black hole mass of RXJ1131 is already in place 
+while its stellar bulge component is still assembling, and that its major mode of \SF is likely merger-driven.
 \end{abstract}
@@
 \section{Introduction}
-Studies of galaxy evolution have been focusing on the interplay between
-\SF and active galactic nucleus (AGN) activity across cosmic epochs.
-It is not well-understood when and how stellar populations of present-day galaxies were assembled,
-but it is clear that both the co-moving \SF rate and black hole accretion rate densities
+%Studying the interplay between \SF and active galactic nucleus (AGN) activity across cosmic epochs is crucial to 
+%our understanding of the
+%processes governing the formation and evolution of both the SMBHs and their host galaxies.
+% Significant attention has been focused on studying the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs in recent studies of galaxy evolution. 
+% \citep{Wang10, Lamastra10, Hopkins+05, 06, DiMatteo+05a, Page11, Page12,Simpson12}
+Many recent studies of galaxy evolution have been focused on investigating the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs \citep[e.g.,][]{DiMatteo05a,Alexander05a,Hopkins06b,Coppin08a,Page12a,Simpson12a,Lamastra13a}.
+It is currently not well-understood when and how the supermassive black holes (SMBHs) and 
+stellar populations of present-day massive galaxies were assembled,
+but it is clear that the co-moving \SF rate and the black hole accretion rate densities both
 increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
 a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
-% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
-A leading explanation for this decline is related to the evolution of molecular gas content and
+A leading explanation for this decline is the decrease in molecular gas content and
 \SF efficiency \citep[]{Erb06a, CW13, Walter14a},
@@
 $(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed ---
-only unresolved CO observations have been carried out for $\sim$$30$ ULIRGs up to date \citep{Combes11a, Combes13a}. %18+15
-
-% In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
-% grows by accretion of the cold molecular gas from its host galaxy.
+only unresolved CO observations have been carried out for $\sim$$30$ ultra-luminous infrared galaxies (ULIRGs) up to date \citep{Combes11a, Combes13a}. %18+15
+
 Meanwhile, empirical scaling relations such as the
@@
 of \SF and AGN activity, have been made in recent years.
-It has been reported that the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of high-$z$ submillimeter galaxies (SMGs) falls below
-the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies is found
-lying above
-the relation \citep[\eg][]{McLure06a,Peng06a}.
-Stellar mass of quasar host galaxies at $z$\,$>$\,4 constrained by their CO-based dynamical mass
-is also too small compared to that based on the local relation \citep{Walter04a, Riechers08a,Coppin08a}.
-While it has become clearer that high-$z$ galaxies deviate from the local relation, and among their galaxy populations,
-such a picture is still unclear  at intermediate redshift.
-This is owed to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
-due to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass.
-With gravitational lensing, emission of the background quasar and its host galaxy
-is magnified and stretched out to different extents, and is being projected onto different locations in the image plane,
-allowing spatially resolved measurements their emission in a
-relatively uncontaminated fashion.
+These studies find that 
+% the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratios of high-$z$ submillimeter galaxies (SMGs) 
+% are lower than those of local AGN host galaxies \citep[\eg][]{Borys05a,Alexander08a}, 
+% whereas those of high-$z$ quasar host galaxies 
+% are higher than the local values \citep[\eg][]{Walter04a, McLure06a,Peng06a, Riechers08a,Coppin08a}, 
+% suggesting that the co-eval growth of high-$z$ AGNs and their host galaxies follows different 
+% timescales compared to their local counterparts. % different AGN mechanism, different AGN accretion rate
+% However, any links between such fast-growing SMBHs and their host galaxies are not yet established at these high redshifts.
+high-$z$ AGN host galaxies do not follow the same $M_{\rm BH}$$-$\mbulge relation \citep[\eg][]{Walter04a,Borys05a, McLure06a,Peng06a, Riechers08a,Coppin08a,Alexander08a}.
+Yet, the $M_{\rm BH}$$-$\mbulge relation remains poorly-constrained 
+at intermediate redshifts.
+This is owed to the difficulties in measuring stellar emission in optical quasar host galaxies, where
+emission of quasars produces sidelobes that saturate the lower surface brightness starlight in the host galaxy,
+or alternatively, due to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar 
+(bulge) mass.
+With strong gravitational lensing, emission from the background quasar and its host galaxy originating from 
+different source-plane locations and of different extent is being magnified and stretched out by different amount.
+The lensed emission is therefore spatially resolved over more beams which reduces the sidelobes and enables 
+measurements of the stellar emission in the host galaxy.
 
@@
 The stellar emission in the host galaxy of RXJ1131 is lensed into
-an Einstein ring of radius $1$\farcs$83$
+an Einstein ring of $1$\farcs$83$ in radius
 that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
-We have thus carried out a detailed study of RXJ1131 as presented in this paper.
-RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
-The moderate mass black hole $M_{\rm BH}$\eq$8$\E{7}\Msun \citep{Sluse12a} %based on H beta line
-residing in RXJ1131 is rotating with a high spin parameter \citep[$a$\,$\sim$\,$0.9$;][]{Reis14a}, and
-is radiating at an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.
-
-This paper is structured as follows.
+The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
+ \citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a}, %based on H beta line
+with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.
+
+In this paper, we present \bco and \cco line data observed towards RXJ1131 and
+broadband photometry spanning rest-frame UV to radio wavelengths to 
+study the properties of the molecular gas, the dust and stellar populations in the 
+host galaxy of RXJ1131.
 In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
 In \Sec{HST}, we describe the astrometric corrections
-applied to align an {\it HST} image with an VLA radio image.
+applied to an image taken with the \hst ({\it HST}) by aligning it to
+a radio image taken with the \vla (VLA).
 In \Sec{results}, we report measurements of the \bco and \cco lines and broadband
-photometry spanning the optical to radio wavelengths.
+photometry in RXJ1131.
 In \Sec{anal}, we present dynamical lens modeling of the \bco data and
-SED modeling of the host galaxy of RXJ1131 to
-derive physical parameters reflecting the nature of this system.
-In \Sec{diss}, we discuss the merger stage of RXJ1131,
-the velocity offset between the AGN lines and the CO lines,
-and the $M_{\rm BH}$$-$\mdyn relation of RXJ1131.
+spectral energy distribution (SED) modeling of the photometric data.
+In \Sec{diss}, we discuss 
+the ISM properties of the host galaxy of RXJ1131 and compare 
+them to other galaxy populations at low and high redshift.
 Finally, we summarize the main results and present our conclusions in \Sec{sum}.
@@
 Observations of the \bco rotational line
-($\nu_{\rm rest}$\,=\,$230.538$ GHz) redshifted to $\nu_{\rm obs}$\ssim$139.0$\,GHz
+($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
+at the $\nu_{\rm LO}$\eq139.256\,GHz
+% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
 were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
@@
 February 05 under good weather conditions in the C and D array configurations,
-respectively. The 2 mm receivers were used to cover the redshifted \bco line
+respectively. 
+This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
+ time after discarding unusable visibility data.
+The 2 mm receivers were used to cover the redshifted \bco line
 and the underlying continuum emission, employing a correlator setup that provides
 an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 10.0 MHz ($\sim$
-$21.5$ \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
- time after discarding unusable visibility data.
+$21.5$ \kms).  {\bf DR: DSB, 320 MHz/128 channels? <-> 2.5 MHz? I did not bin the data}
 The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
@@
 Observations of the \cco rotational line in RXJ1131
-($\nu_{\rm rest}$\,=\,345.7959899\,GHz) redshifted to $\nu_{\rm obs}$\,=\,208.6\,GHz
+($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
 were carried out with the \carma (CARMA;
@@
 weather conditions and on 2014 February 17 under good 1.5\,mm
-weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
-each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
+weather conditions. 
+This resulted in a total on-source time of 2.94 hours after flagging poor
+visibility data.
+The correlator setup provides a bandwidth of 3.75 GHz in
+each sideband and a %native
+spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
 line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
@@
 observed as the primary absolute flux calibrator and 3C279 was observed as
-the bandpass calibrator for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
-visibility data.
+the bandpass calibrator for both tracks.
 
@@
 the gain variations over time, and the phase scatter on the calibrated data. We
-therefore treat its line intensity with caution and ensure that our physical interpretation
+therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
 of this system and the conclusion of this paper do not rely on this quantity.
@@
 
-\subsection{VLA (Archival)} %DONE
-Our analysis also uses archival data of the 5\,GHz
+\subsection{VLA (Archival)} 
+Our analysis also uses archival data of the 4.885\,GHz %4.88510 GHz
 radio continuum obtained with the
-Very Large Array (VLA; Program ID: AW741; PI: Wucknitz).
+VLA (Program ID: AW741; PI: Wucknitz).
 Observations were carried out on 2008 December 29 under excellent weather
@@
 The nearby radio quasar J1130$-$149 was observed every 10 minutes for
-pointing, amplitude, and phase calibration, J1331$+$305 was observed as the
+pointing, amplitude, and phase calibration. J1331$+$305 was observed as the
 primary flux calibrator, and J0319$+$415 was observed as the bandpass
@@
 We obtained an {\it HST} image taken with
-the ACS/Wide Field Camera
+the ACS
 using the F555W filter ($V$-band)
 from the
-Hubble Legacy Archive\footnote{Based on observations
-made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
-Legacy Archive, which is a collaboration between the Space Telescope Science
-Institute (STScI/NASA), the Space Telescope European Coordinating Facility
-(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}.
+Hubble Legacy Archive.
 The details of the observations can be found
@@
 \includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
-\caption{Continuum-subtracted spectrum of \bco emission toward RXJ1131. The velocity scale
-is with respect to $z$\,=\,0.6537, which is approximately the line center
+\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of 
+21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
+The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
 considering the asymmetry resulting from differential lensing.
@@
 %   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
-We construct the zeroth order moment map, a red/blue channel map, and
-the first and second moment maps in \Fig{CO21mom}
+We construct a zeroth order moment map, red/blue channel maps, and
+first and second moment maps, as shown in \Fig{CO21mom},
 using the $uv$-continuum subtracted data cube over a velocity range of
@@
 
-The deconvolved source size FWHM from fitting a two-dimensional Gaussian
+The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
+the image plane
 is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
@@
 \hspace{0.5em}
+% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
+% 126-144 (Red)
+% ~ delta V ~410 km/s
+% from [409, 0] km/s
+%  144-160 (Blue)
+% ~ 365 km/s
+% [-324.88, 0] km/s
 \includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
@@
 \vspace{0.1em}
-\caption{Top left: overlay of the velocity-integrated \bco emission on the archival {\it HST} $V$-band (F555W)
+\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
 image.
-Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission.
+Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which 
+are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
 The contours in both top panels start at 3$\sigma$ and increment at steps of
@@
 \subsection{\cco Emission}
-We detect \cco line emission toward RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
+We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
 The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
@@
 linewidth used to infer the \bco line intensity ($\sim$700 \kms).
-Assuming the spatial extents of \bco and \cco is similar and therefore the emission is
+Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
 magnified by the same amount, the measured line intensities
@@
 Taking into account the large phase errors associated with \cco, this is consistent with
-thermalized excitation, as observed in other ULIRGs.
+thermalized excitation within the uncertainties, as commonly observed in nuclear regions of 
+nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, and also 
+with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
+% see DANNERBAUER09 intro
+% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.
 
@@
 
-\subsection{Continuum Emission} %DONE
+\subsection{Continuum Emission} 
 No 1.5\,mm continuum emission is detected at the position of \cco
@@
 
-We detect PdBI 2\,mm continuum, as shown in \Fig{cont}. The integrated flux density is
-1.2\pmm0.2 mJy, with a peak flux
-$S_\nu$\,=\,800\pmm88\,$\mu$Jy\,beam\pmOne
+We detect PdBI 2\,mm continuum emission, as shown in \Fig{cont}. The integrated flux density is
+1.2\pmm0.2 mJy, with a peak flux of
+$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
 centered on the lensing galaxy. Slightly extended emission
 along the lensed arc is also detected.
-This suggests that we detect emission both in
-the foreground galaxy and in the background galaxy and that the
+This suggests that we detect emission in both
+the foreground galaxy and the background galaxy and that the
 emission is marginally resolved along its major axis.
 We subtract a point source model in the $uv$-plane to remove the unresolved
-emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
+emission towards the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
 in the residual map coincides with the lensed arc, and is consistent with
@@
 original continuum map ($\sim$0.4 mJy). We therefore adopt
-$S_\nu$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission toward
+$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
 the background galaxy (RXJ1131).
+The quoted uncertainty is from the flux measurement in the residual map and do not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
+We report the peak flux in the original map 
+($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy.
+We note that this peak flux density is only our best estimate at the resolution of our observations, a non-negligible contribution from the background source to the total integrated (blended) flux may be present.
+% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density 
+% assumes that the foreground galaxy is a point source, the...
 
@@
 for the background galaxy by fitting a
-power-law (S$_\nu \propto \nu^{\alpha}$) to the continuum emission at
+power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
 5\,GHz and 2\,mm.
@@
 when warranted. These data were obtained using
-the Two Micron All Sky Survey Telescopes \citep[2MASS;][]{Skrutskie06a},
+the Cerro Tololo Inter-American Observatory (CTIO) for the Two Micron All Sky Survey \citep[2MASS;][]{Skrutskie06a},
 the Wide-field Infrared Survey Explorer \citep[{\it WISE};][]{Wright10a},
@@
 {\it HST} image ($\sim$0\farcs07 resolution) to determine the
-origins of their centroids, all of which are found to be
+origin of their centroids, all of which are found to be
 centered at the position corresponding to the lensed emission from the
@@
 the Wien tail beyond the dust peak
-of the spectral energy distribution (SED) of RXJ1131.
+of the SED of RXJ1131.
 Details of the SED modeling are presented in \Sec{SED}.
@@
 the flux density from an image convolved with a kernel
-derived from the SPIRE beam. The flux density
-measured by \ncode{sussextractor} is additionally confirmed
+derived from the SPIRE beam. The flux densities
+measured by \ncode{sussextractor} were confirmed by
 using the Timeline Fitter, which performs photometry
@@
 \subsection{Lens Modeling} \label{sec:lensmodel}
-At the angular resolution of the \bco data, the images are resolved over
-$\sim$2 resolution elements.
+At the angular resolution of the \bco data, the source is resolved 
+$\gtrsim$2 resolution elements.
 Given the extent of the lensed emission (see \Fig{CO21mom}),
@@
 enabling us to reconstruct a velocity gradient in the source plane.
-To enusre adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
+%
+To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
 to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
 that cover the full linewidth of $\sim$750\,\kms.
+%
+The first use of a dynamical lens modeling approach is presented by \citet{Riechers08a}, who reconstruct a source-plane
+velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
+which is also the only other similar system whose host galaxy is lensed into an Einstein ring configuration.
 
@@
 correcting for lensing using the magnification factor $\mu_{\rm L}$ as annotated by the horizontal bar shown
-above each respective model channel. Flux density on the y-axis is shown on a log scale.
+above each respective model channel. 
 \label{fig:delensed}}
@@
 
-The lens mass distribution is modeled using a singular isothermal
+We model the lens mass distribution using a singular isothermal
 ellipsoid (SIE) profile, which is described by five free parameters: the
@@
 fixed coordinate in the image, the Einstein radius, the axial ratio, and the
-position angle. We use the VLA radio continuum emission toward
-the foreground galaxy to initialize the positional offset. We impose a
+position angle. 
+Positional offset between the foreground galaxy and the pre-defined coordinate is initialized
+using the VLA radio continuum map.
+We impose a
 uniform prior of $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec.,
@@
 and check for chain convergence by inspecting trace plots
-and by requiring the samples are obtained beyond at least an autocorrelation time.
+and by requiring that the samples are obtained beyond at least an autocorrelation time.
 We thus employ $\sim$50,000 samples as the initial ``burn-in'' phase
@@
 
-The type of merger (major v.s. minor) in a pair of interacting galaxies
-is most commonly distinguished based on
-the ratio between their total galaxy mass.
-Here, we use the gas mass ratio between RXJ1131 and
-its companion galaxy instead, given that we do not have stringent constraints on their individual galaxy mass.
 We decompose the total line flux into two components:
@@
 implies a {\em gas} mass ratio of $\sim$7:1 between RXJ1131 and its companion.
-We thus classify the system to be a {\em ``wet'' minor merger}.
-We caution that this is based on their gas mass ratio rather than their total galaxy mass ratio, which
-is more commonly used in literature as the
-classification scheme to separate major mergers from minor mergers.
 
@@
 resolution, constraints on the intrinsic sizes of the lensed galaxies are modest, and thus the magnification
-factors may be under-predicted. % see Bussmann15
+factors may be under-predicted \citep[see e.g.,][]{Bussmann15a,Dye15a,Rybak15a}.
 
@@
 \caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
-Top: each panel corresponds to a channel map of width $\sim$100\,\kms of the observed
+Top: each panel corresponds to a channel map of width 107.5\,\kms of the observed
 emission (red) overlaid on the best-fit models (grayscale).
@@
 data in the $uv$-domain.
-In all panels, location of the foreground lensing galaxy is indicated by a black dot and
+In all panels, the location of the foreground lensing galaxy is indicated by a black dot and
 its critical curve is traced by the orange solid line; locations and
@@
 The reconstructed source-plane positions, as represented by the magenta ellipses, demonstrate an intrinsic velocity gradient of the \bco emission in RXJ1131.
-The best-fit model of the red-most channel (top left panel) contains two source components (see text for details).
+The best-fit model of the red-most channel (top left panel) contains two source components.
 \label{fig:model}}
@@
 channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
-\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
+\Fig{chanmap} and \Fig{spatialSpec}, respectively. These figures
 show that redshifted emission
@@
 is suggestive of an extended CO emitting region.
+%% spatial offset between AGN and the host
+%In the channel maps in \Fig{CO21mom} and
+%\Fig{chanmap}, the line center of the CO gas is not co-spatial with the optical quasar --- the point-like images along the lensing arc are
+%offset to the NW of the CO line center emission.
 
@@
 Similar to previous studies of RXJ1131, where
-differential lensing across {\it HST}
-$V$-, $I$-, and $H$-band has been detected with a
+differential lensing across the {\it HST}
+$V$-, $I$-, and $H$-bands has been detected with a
 magnification factor decreasing from 10.9 to 7.8 \citepalias{Claeskens06a},
@@
 The CO gas is thus of similar spatial
-extent as in $H$ and $I$-bands.
+extent as in the $H$ and $I$-bands.
 
@@
 \citep[\eg][]{DiMatteo05a}.
-This is consistent with the picture that old stars form first and constitute the bulge component
-of a spiral galaxy and that nuclear starbursts (in the inner few kpc) can be triggered
+This would be consistent with the picture that old stars form first and constitute the bulge component
+of a spiral galaxy, and that nuclear starbursts (in the inner few kpc) can be triggered
 at a later time as the progenitor disk galaxy interacts with other galaxies to form a larger bulge.
+
+\subsection{Dynamical Mass}\label{sec:dyn}
+Assuming the gas to be virialized,
+the dynamical mass can be approximated by
+$M_{\rm dyn}$\ssim$\sigma^2 R / G$,
+where $\sigma$ is the velocity dispersion, or the rotational velocity in the case of a rotating disk model
+$($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
+Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
+we find a dynamical mass of
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1.7\E{11}\,\Msun enclosed
+within the CO-emitting region in RXJ1131.
+If we instead consider the
+\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun. %calc. using 2.32e5*6.22 * 200^2
+We derive an inclination angle of 56.4$\degr$ from the
+morphological axial ratio of $a/b\sim$1\farcs8$/$3\farcs25, which we estimate
+from the source-plane image reconstructed by \citetalias{Claeskens06a} (Figure 3 in their paper).
+This corresponds to an inclination-corrected dynamical mass of
+8.3\E{10}\Msun$<$\,$M_{\rm dyn}$\,$<$\,25\E{10}\Msun.
+Our estimate should be considered at best an upper limit since
+the gas in RXJ1131 is unlikely virialized.
+In the following sections, we use the
+lower limit (8.3\pmm1.9)\E{10}\,\Msun as the dynamical mass as it is
+derived in a manner similar to what is commonly used in literature
+(\eg \citealt[hereafter S97]{Solomon97a}; \citealt[hereafter DS98]{Downes98a}; \citealt[hereafter G05]{Greve05a}).
+\defcitealias{Downes98a}{DS98}
+\defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}\defcitealias{SV05a}{SV05}
+
+Using the velocity dispersion ($\sigma$ = 30\,\kms) obtained by fitting a single Gaussian to the
+de-lensed line profile of the companion and a
+half-light radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from the best-fit lens model,  % redmost channel
+we find a dynamical mass of
+$M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun for the companion,
+assuming an inclination angle of $i$\eq30$\degr$.
+The uncertainty here only includes that of the CO source size.
+On the other hand,
+% we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
+we find $M_{\rm dyn}$\,$\sin^2 30\degr$\,=\,5.8\E{8}\,\Msun
+if we adopt the better-constrained $V$-band source size of $\sim$700\,pc \citepalias{Brewer08a}.
+The $V$-band dynamical mass is substantially lower than the gas mass, which
+may be an indication of the dusty nature of the companion.
+% in which the $V$-band source size to
+% appear much smaller than its true extent.
+
+The CO-based dynamical mass estimates correspond to a mass ratio of $\sim$24:1
+between RXJ1131 and the companion, with a gas mass ratio of $\sim$7:1 derived in  \Sec{caveat}. 
+We thus classify the system as a {\em ``wet'' minor merger}.
+
+%%% using disk model, should use FWHM of single Gauss fit then (Fu+13)
+%Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
+% \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as
+%$v_{\rm FWHM}$, we find a dynamical mass of
+%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
+%within the CO-emitting region.
+%If we instead consider the
+%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
+%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
+%To correct for the inclination effect, we
+%infer an inclination angle of 56.4$\degr$ using
+%the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25)
+%from the reconstructed image (Figure~3 in \citetalias{Claeskens06a}). This inclination angle
+%is consistent with the
+%observed unobscured AGN and an observable double peak line profile.
+%The dynamical mass is then
+%1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
+%% the systematic uncertainty on the inclination angle may cause this estimate to differ by
+%% a factor of $\sim$2.
+%Our estimate is likely a lower limit given the presence of a companion. In a merger model,
+%the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
 
@@
 as the best-fit parameters, as listed in \Tab{SED}.
-The best-fit models are shown in \Fig{SED} along with the broadband photometry that are listed in \Tab{photometry}.
+The best-fit models are shown in \Fig{SED} along with the broadband photometry that is listed in \Tab{photometry}.
 
@@
  and
- a total IR luminosity of $\sim$1.5\E{12}\,\Lsun, implying RXJ1131 can be classified as an ULIRG.
+ an intrinsic total IR luminosity of $\sim$1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun, implying that RXJ1131 can be classified as an ULIRG.
 Assuming a \citet{Salpeter55a} initial
@@
 To minimize contaminations from the quasar, we only fit to the {\it HST}, {\it Herschel}, and PdBI data,
-where both the {\it HST} and the PdbI 2\,mm photometry are de-blended from the AGN
+where both the {\it HST} and the PdBI 2\,mm photometry are de-blended from the AGN
 (see bottom section of \Tab{photometry}).
@@
 % Salpeter M* ~ 1.8 * Chabrier
-% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up" time of $M^*$$/$SFR\ssim440 Myr for RXJ1131.
+% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up" time (aka mass-doubling timescale) of $M^*$$/$SFR\eq sSFR\pmOne\ssim440 Myr for RXJ1131.
 
@@
 \includegraphics[trim=5 5 5 5, clip, width=0.445\textwidth]{../Figures/FullSED_withMagphys}
-\caption{SEDs of the host galaxy of RXJ1131 at 
-$z_{\rm CO}$\eq0.654 and of the lensing galaxy at $z$\eq0.295.
+\caption{SEDs of RXJ1131 at 
+$z_{\rm CO}$\eq0.654 and the lensing galaxy at $z$\eq0.295.
 The photometry data (colored markers) are listed in \Tab{photometry}, except for those
@@
 
+%--------------------------------------------------------------------------
+%                                Discussion
+%--------------------------------------------------------------------------
+\section{Discussion} \label{sec:diss}
 \subsection{ISM Properties} \label{sec:properties}
@@
 (0.6\,$<$\,$z$\,$<$\,1.0).
-Their results are based on unresolved \bco and \rot{4}{3} line observations with the
+Their results are based on spatially unresolved \bco and \rot{4}{3} line observations with the
 IRAM 30-m single-dish telescope.
@@
 \subsubsection{Linewidth and Sizes} \label{sec:sizes}
-A FWHM linewidth of $\Delta v_{\rm}$\,$\sim$\,600\pmm160\,\kms found
+The FWHM linewidth of $\Delta v_{\rm}$\,$\sim$\,600\pmm160\,\kms found
 for RXJ1131 by fitting a single Gaussian
-is considerably larger that those in the \citetalias{Combes13a} sample
-(370\,\kms) as well as in
-local ULIRGs \citep[300\pmm85\,\kms, with the largest being 480\,\kms;][hereafter S97]{Solomon97a}.
+is considerably larger than the statistical average in the \citetalias{Combes13a} sample
+(370\,\kms) and
+local ULIRGs \citepalias[median: 300\pmm85\,\kms, with the largest being 480\,\kms;][]{Solomon97a}.
 %ULIRGs (z < 0.3) studied in CO(1-0) by Solomon97a: ~1/3 of them have double-peaked or flat-topped spectrum. But their linewidths are based on single Gauss fit.
-Yet, given the merging nature of these galaxies,
-a CO linewidth of $\sim$600\,\kms may not be surprising.
-Indeed, a linewidth of $\Delta v$ = 750\,\kms has been observed
-in a local LIRG \citep[Arp 118; ][hereafter SV05]{SV05a}.
-Linewidth of this range ($\gtrsim$\,500\,\kms) is also commonly observed in
-high-$z$ starburst galaxies  \citep[e.g.,][hereafter G05]{Greve05a}
+Linewidths exceeding 500\,\kms are also commonly observed in
+high-$z$ starburst galaxies  \citepalias[e.g.,][]{Greve05a}
 % \citep[780\pmm320\,\kms; \eg][hereafter G05]{Greve05a}
@@
 % \citep[550\pmm180\,\kms; \eg][]{Coppin08a},
-which are
-believed to originate from mergers.
-\defcitealias{Solomon97a}{S97}\defcitealias{Greve05a}{G05}\defcitealias{SV05a}{SV05}
+which are believed to originate from mergers.
+The wider CO linewidth observed in RXJ1131 also supports the merger picture.
 
@@
 
-\subsubsection{Dynamical Mass}
-Assuming the gas to be virialized,
-the dynamical mass can be approximated by
-$M_{\rm dyn}$\ssim$\sigma^2 R / G$,
-where $\sigma$ is the velocity dispersion, or the rotational velocity in the case of a rotating disk model
-$($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
-Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
-we find a dynamical mass of
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1.7\E{11}\,\Msun enclosed
-within the CO-emitting region in RXJ1131.
-If we instead consider the
-\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun. %calc. using 2.32e5*6.22 * 200^2
-We derive an inclination angle of 56.4$\degr$ from the
-morphological axial ratio of $a/b\sim$1\farcs8$/$3\farcs25, which we estimate
-from the source-plane image reconstructed by \citetalias{Claeskens06a} (Figure 3 in their paper).
-This corresponds to an inclination-corrected dynamical mass of
-8.3\E{10}\Msun$<$\,$M_{\rm dyn}$\,$<$\,25\E{10}\Msun.
-Our estimate should be considered at best an upper limit since
-the gas in RXJ1131 is unlikely virialized.
-In the following sections, we use the
-lower limit (8.3\pmm1.9)\E{10}\,\Msun as the dynamical mass as it is
-derived in a manner similar to what is commonly used in literature
-(\eg \citetalias{Solomon97a}; \citealt[hereafter DS98]{Downes98a}; \citetalias{Greve05a}).
-\defcitealias{Downes98a}{DS98}
-
-Using the velocity dispersion ($\sigma$ = 30\,\kms) obtained by fitting a single Gaussian to the
-de-lensed line profile of the companion and a
-half-light radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from the best-fit lens model,  % redmost channel
-we find a dynamical mass of
-$M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun for the companion,
-assuming an inclination angle of $i$\eq30$\degr$.
-The uncertainty here only includes that of the CO source size.
-% Given the large systematic uncertainties associated with the model-based source size and
-% the lack of constraint on the inclination angle, we do not use this dynamical mass in the remaining of this paper.
-On the other hand,
-% we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
-we find $M_{\rm dyn}$\,$\sin^2 30\degr$\,=\,5.8\E{8}\,\Msun
-if we adopt the better-constrained $V$-band source size of $\sim$700\,pc \citepalias{Brewer08a}.
-This dynamical mass is substantially lower than the gas mass, and
-% , which is a more reliable estimate based on the data in hand,
-% we do not use this dynamical mass to derive other physical parameters.
-% The underestimated dynamical mass may reflect
-may be reflecting the dusty nature of the companion.
-% in which the $V$-band source size to
-% appear much smaller than its true extent.
-
-%%% using disk model, should use FWHM of single Gauss fit then (Fu+13)
-%Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
-% \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as
-%$v_{\rm FWHM}$, we find a dynamical mass of
-%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
-%within the CO-emitting region.
-%If we instead consider the
-%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
-%To correct for the inclination effect, we
-%infer an inclination angle of 56.4$\degr$ using
-%the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25)
-%from the reconstructed image (Figure~3 in \citetalias{Claeskens06a}). This inclination angle
-%is consistent with the
-%observed unobscured AGN and an observable double peak line profile.
-%The dynamical mass is then
-%1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
-%% the systematic uncertainty on the inclination angle may cause this estimate to differ by
-%% a factor of $\sim$2.
-%Our estimate is likely a lower limit given the presence of a companion. In a merger model,
-%the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
-
-\subsubsection{Gas Mass and Gas Ratios}
+\subsubsection{Gas Mass Fractions}
+
+% ------------- gas fraction --------------
+% Locally, the baryonic gas fraction for giant disks is ~7-10% (Leroy et al. 2008, Saintonge et al. 2011a), while
+% at z~1.2 it increases to 34±5% and at z~2.3 to 44±6% (Tacconi
+% et al. 2010, Daddi et al. 2010).
+We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq19\pmm5\%
+% , where the uncertainty is based on that of the gas mass. 
+and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\eq32\petm{7}{-12}\% for RXJ1131.
+% The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
+Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $\sim$40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
+% On the other hand,
+% the baryonic gas mass fraction ranges from $\sim$10$-$30\% with an average of 0.21\pmm0.03 in normal ``star-forming'' galaxies at $z$\ssim0.4 \citep{Geach11a}, and $\sim$5 at $z$\ssim0 \citep{Saintonge11a}.
+and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for 
+normal ``star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use  the ``Galactic'' \alphaco conversion factor to compute the molecular gas mass.}.
+Both the dynamical and baryonic gas mass fractions of RXJ1131 are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a}) 
+which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
+%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Using the lensing-corrected dust mass, we find a galactic-scale gas-to-dust ratio of
-40\pmm34, which is lower than the statistical average of $f_{\rm gas-dust}$\,=\,206
-in the \citetalias{Combes13a} sample but well within their broad
-range of values over the entire sample. Our ratio is also consistent with
-high-$z$ SMGs
+Using the lensing-corrected dust mass, we find a galactic-scale %galaxy-wide
+gas-to-dust ratio (GDR) of
+40\pmm34, which would be a factor of two higher if we adopted a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
+This GDR is lower than the statistical average of 206
+in the \citetalias{Combes13a} sample but is well within the broad
+range of values measured over the entire sample. 
+Our ratio is also consistent with high-$z$ SMGs
 % \citep[78\pmm26;][]{Bothwell13a}
 \citep[]{Bothwell13a} and
-local ULIRGs \citep{Wilson08a}, but lower in the Milky Way by
+local ULIRGs \citep{Wilson08a}, but lower than the Milky Way by
 $\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
-We note that the dust mass derived for RXJ1131 is poorly constrained.
-If we adopt a dust mass from the other SED fit (\ie without constraints at 24\,$\micron$),
-the dust mass would reduce by a factor of $\sim$2. \defcitealias{Bothwell13a}{B13}
+\defcitealias{Bothwell13a}{B13}
 
@@
 the gas mass (and thus gas-to-dust ratio) would be $\sim$6 times higher.
-We note that this gas mass is physically feasible based on dynamical mass constraint.
+We note that this gas mass is physically feasible based on the dynamical mass constraints derived in \Sec{dyn}.
 On the other hand, we would also obtain a higher gas mass if
-we assumed sub-thermal excitation between \bco and \aco emission, but
-we expect this to be a minor effect as CO emission in ULIRGs are typically thermalized up to $J$ = 3 or 4.
+we assumed sub-thermal excitation between \bco and \aco emission.
+% but this may be a minor effect as CO emission in local ULIRGs is typically thermalized up to $J$ = 3 or 4 \citep{,CW13}.
 We also note that the gas-to-dust ratio derived for RXJ1131 may be biased low as the gas is likely to
 be more extended than the dust. Consequently, the overall magnification factor
-for the CO gas may be lower than the optically thick dust, which dominates the \fir
-luminosity, and thus leading to an overestimated dust mass
-via our adoption of the CO magnification factor.
-
-\subsubsection{SFE and Depletion Timescales}
+for the CO gas may be lower than the optically thick dust, which dominates the \fir luminosity. 
+This would lead to an overestimation of the dust mass
+by adopting the CO magnification factor for the dust.
+
+\subsubsection{Star Formation Efficiency and specific SFR}
 % SFE:
@@
 % Solomon97a: LFIR/L'CO = 160
-
+% Daddi+10:  We find that the average SFE (in units of L?
+K?1 km?1 s pc?2) of BzK galaxies is 84\pmm12, that of SMGs is 390\pmm60, for QSOs we find 590\pmm100, for local ULIRGs we have 250\pmm30, and local spirals have 48\pmm7.
+Therefore, the typical BzK galaxy has about 80\% higher SFE of that of a local spiral, but individual values are well within the range measured for local spirals even though BzKs are a hundred times more luminous.
+Local ULIRGs have SFEs that are three times larger on average than BzK galaxies.
 To first order, the star formation efficiency
@@
 in \citetalias{Combes13a} for the far-IR luminosity,
-we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$,
+we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$, % I believe here we are taking the gas mass of both into account since we we couldn't separate out the LIR
 which is on the low end among other U/LIRGs at $z$\,$<$\,0.6
@@
 \citep[\citetalias{Solomon97a};][]{Combes11a} but consistent with those of
-low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a} and high-$z$ disk-like galaxies \citep{Daddi08a}.
-Assuming an \alphaco of 0.8\,\alphaU, this would imply that
-it is converting gas into stars at an efficiency
+low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a} and high-$z$ disk-like 
+galaxies, which are also IR luminous galaxies with \LIR$\sim$10$^{12}$\,\Msun \citep{Daddi08a, Daddi10a}.
+This suggests that the merger system is converting gas into stars at an efficiency
 similar to those of ``normal'' star-forming
@@
 \citep[][\citetalias{Combes13a}]{Tacconi08a, Riechers11a}.
-This is in agreement with its disk-like kinematic signatures.
-
-Results from theoretical simulations have suggested that
-the disk component of a gas-rich progenitor galaxy can
-survive merging if it has a low star formation efficiency, which in turn
-reduces the gravitational torque available to
-remove the angular momentum of the gas, thereby allowing
-a higher gas fraction to be retained and redistributed over a large extent in
-the merged galaxy \citep{Hopkins09a}. In this scenario, it is plausible that RXJ1131
-will evolve into a disk galaxy with a small bulge component upon merging given its low SFE and the extended disk.
-%since there is little/no significant stellar material % (collisionless)
-%available to torque away the cold gas in the disc, thus little/no angular momentum is lost,
-%and gas will rapidly reform a cold disc in the background
-%of the relaxing stellar potential.
-% --> suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
-% the final product will have a low bulge mass fraction.
-%
-%i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large).
-% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
-
+This is in agreement with its disk-like kinematic signatures and its extended molecular gas distribution.
 % Depletion time:
 % Greve+05: ~40 Myr
-Assuming the \SF continues at the current rate without gas replenishment, this corresponds to a
+Assuming the \SF continues at the current rate without gas replenishment,
+the SFE corresponds to a
 gas depletion time of $\tau$\,=\,102\pmm25\,Myr.
-Since the \SF rate is expected to vary in an interacting system and
-AGN accretion also consumes some fraction of the gas, the depletion
-timescale should only be considered as an upper limit.
 \defcitealias{Tacconi08a}{T08}
+
+% 
+% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
+% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
+The specific star formation rate (sSFR\eq SFR/$M^*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
+is $\lesssim$1.5$\sigma$ above the main sequence according to
+the redshift-dependent ``main sequence" relation in \citet[and references therein]{Tacconi13a} but is
+consistent with those of the \cite{dacunha10a} sample of local ULIRGs, suggesting that the 
+majority of \SF in RXJ1131 could be driven by its interactions with the companion galaxy, 
+unlike most disk galaxies despite sharing similar \SF rate, \SF efficiency, and CO disk size.
+
+% ================================================
+%local ULIRGs are in the majority starbursts caused by
+%galaxy major mergers (e.g. Sanders & Mirabel 1996, Veilleux
+%et al. 2009). The overall gas fraction in those systems is not high,
+%and they are expected to sustain such a high rate of star formation
+%for only a short duration, on the order of 100Myr. The depletion
+%time scale of massive star-forming galaxies, with a high gas
+%fraction but low star formation efficiency (SFE), is on the other
+%hand on the order of one Gyr or more (Leroy et al. 2008, Bigiel
+%et al. 2008). These galaxies are dubbed as falling on the ?main
+%sequence? of star-forming galaxies (Noeske
+%et al. 2007), or in a ?normal? star formation phase.
+% =================================================
 
@@
 
-%\subsubsection{Comparison with High-$z$ SMGs and BzKs}
-%At high redshifts ($z$\,$\gtrsim$\,1), SMGs are the irregular, turbulent
-%star-bursting galaxies with elevated specific \SF rates (CITE) %\citep[sSFR][]{}
-%and BzKs are the ``normal" star-forming disk galaxies with relatively lower
-%\SF efficiencies, \SF rates and also
-%longer depletion times \citep[\citetalias{Daddi10a};][]{CW13}.
-
-%In fact, an \alphaco conversion factor of 3.6\pmm0.8
-%has been proposed for BzKs using kinematic analysis/dynamical model (based on the dynamical mass; e.g. Daddi10a).
-% Whereas \citet{Tacconi08a, Carilli10a} place an upper limit of $\sim$0.8 on high-$z$ SMGs, leading the emergence of two star formation modes. Carilli+10: based on dynamical constraints
 %====================================================================
 
-%--------------------------------------------------------------------------
-%                                Discussion
-%--------------------------------------------------------------------------
-\section{Discussion} \label{sec:diss}
 \subsection{Fate of RXS J1131$-$1231}
-The classical picture for mergers is one where they are responsible for the formation of the local
-red and passive spheroidal galaxies.
-With more realistic treatments of star formation and feedback in recent simulations,
-it has been suggested that it is possible to suppress bulge formation
-in gas-rich mergers, thereby forming large disks
-that resemble local spiral galaxies \citep{Springel05a, Robertson06a, Hopkins09a}.
+%Results from theoretical simulations have suggested that
+%the disk component of a gas-rich progenitor galaxy can
+%survive merging if it has a low star formation efficiency, which in turn
+%reduces the gravitational torque available to
+%remove the angular momentum of the gas, thereby allowing
+%a higher gas fraction to be retained and redistributed over a large extent in
+%the merged galaxy \citep{Hopkins09a}. In this scenario, it is plausible that RXJ1131
+%will retain its a disk component upon merging 
+%with a small bulge component
+%given its low SFE and the extended disk.
+%%since there is little/no significant stellar material % (collisionless)
+%%available to torque away the cold gas in the disc, thus little/no angular momentum is lost,
+%%and gas will rapidly reform a cold disc in the background
+%%of the relaxing stellar potential.
+%% --> suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
+%% the final product will have a low bulge mass fraction.
+%%
+%%i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large).
+%% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
+Given that the host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger 
+system, the removal of angular momentum of the gas via gravitational torque is likely inefficient to convert the 
+entire gas disk into a massive stellar bulge.
+Hence, the disk component may be retained upon merging with the companion. 
+This scenario is consistent with the results from recent simulations, which suggest that bulge formation maybe 
+suppressed in gas-rich mergers, thereby allowing the formation of large disk galaxies with low bulge-to-disk ratios  
+\citep{Springel05a, Robertson06a, Hopkins09a}. This also supports the idea that not all mergers will transform into 
+elliptical galaxies, as in the classical picture \citep{Toomre72a}.
+
 % (bulge dominated; Springel05a, Robertson06a)
@@
 % (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
-The extended molecular gas distribution in RXJ1131 together with its low SFE implies that the
-removal of angular momentum of the gas via gravitational torque is inefficient.
-Other mechanisms e.g. bar-like structures that are more efficient at removing angular momentum will
-be required to transform the gas disk of RXJ1131 into a stellar spheroid and evolve into
-an E/S0 galaxy.
-Thus, RXJ1131 may retain its disk component and
-evolve into a disk galaxy upon its final coalescence with the companion.
 
@@
 the \mgii emission line.
-Using the CO line center redshift as the systemic redshift, the second set of lines is blueshifted by $\sim$780\,\kms.
-This implies
-that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.
-We confirm this spatially in the channel maps in \Fig{CO21mom} and
-\Fig{chanmap}, where the line center of the CO gas is not co-spatial
-with the optical quasar --- the point-like images along the lensing arc are
-offset to the NW of the CO line center emission.
-On the other hand, we find that the redshift of the [O\,{\scriptsize III}] lines tracing the narrow line region (NLR)
-is fully consistent with the systemic redshift, supporting previous claims that [O\,{\scriptsize III}] lines are good proxies
+Using the CO line center redshift as the systemic redshift, 
+we find that the redshift of the first set is fully consistent with the systematic redshift. This
+supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
+are good proxies
 to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
+On the other hand, the second set of lines is blueshifted by $\sim$780\,\kms, indicating that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.
 
@@
 SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
-%To date, the most promising candidate with both spectroscopy and imaging
-%signatures of a recoiling BH is CID-42 at $z$\,=\,0.359, with
-%an offset of $\sim$1300\,\kms between the narrow and broad component of H$\beta$ \citep{Civano10a}.
-%This is similar to the case here for RXJ1131, where the two components of H$\beta$ are offset by
-%\ssim550\,\kms.
-%Other example of recoiling BH
-%includes the type-1 QSO SDSS 0956+5127 at $z$\,$\sim$\,0.714, with an offset of 1200\,\kms
-%between \mgii and \oiii lines \citep{Steinhardt12a}.
 One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
@@
 have been observed \citep{Komossa08a},  similar to the case for RXJ1131.
-% offset in this system: between a set of redshifted (narrow) versus a set of blueshifted (broad).
-However, this scenario is refuted recently by \citet{Decarli14a}, who confirm that the
+However, this scenario was recently refuted by \citet{Decarli14a}, who confirm that the
 BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
 This is in contrast with RXJ1131, where our CO observations confirm the blueshifted BLR.
-% The fact that the BH in RXJ1131 has a high spin parameter \citep[a\ssim0.9;][]{Reis14a}
-% renders this scenario
-% % the recoiling BH scenario
-% a viable option for the origin of the blueshift.
 Since this model requires a merged BH, it would imply that RXJ1131 might
 have been in a previous merger, which would also explain
-the highly spinning BH in RX1131 \citep[a\ssim0.9;][]{Reis14a}.
-% In this picture, the presence of a nearby companion observed in our data may reflect that RXJ1131 is in its
-% subsequent stages of (minor) merging resulting from previous passage of a major merger.
+the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
 
 \subsection{The $M_{\rm BH}$$-$\mbulge Relation}
-Based on the black hole mass of \mbh$\sim$\,8\E{7}\,\Msun \citep{Sluse12a},
-and adopting the stellar mass of $M^{*}$\,=\,2.95\petm{1.32}{0.86}\E{10}\,\Msun
-as an upper limit to the bulge mass,
-we find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of 0.19\%$-$0.38\%.
-This is consistent with other intermediate-$z$ radio-loud AGNs \citep{McLure06a}
-but lies above the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation \citep{HR04a}.
-The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local
-AGNs is consistent with the emerging picture that quasars
-grow faster than their host galaxies at higher redshifts.
-% \ie $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.15\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.8
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of 0.27\petm{11}{8}\%
+using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
+and the stellar mass derived in \Sec{SED} as an upper limit to the bulge mass.
+This ratio is consistent with those of other intermediate-$z$ radio-loud AGNs \citep{McLure06a}
+but is higher than those of nearby AGNs \citep{HR04a}, supporting
+the emerging picture that quasars
+grow faster and/or earlier than their host galaxies at higher redshifts \citep[e.g., ][]{Walter04a, Peng06a, McLure06a}.
+The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local AGNs 
+suggests that the bulk of the black hole mass of RXJ1131 is already in place while its stellar bulge is still assembling.
 
@@
 between the \bco and \cco lines.
-Taking into account the large phase errors associated with the \cco measurement, this
-is consistent with thermalized excitation.
+Taking into account the large phase errors associated with the \cco measurement, this ratio
+is consistent with thermalized excitation but also with the lower excitation seen in normal star-forming disks.
 We also detect marginally resolved
-2\,mm continuum underlying the \bco line in the PdBI data
-and resolved radio continuum emission at 5\,GHz in the archival VLA data
+2\,mm continuum emission underlying the \bco line 
+and resolved radio continuum emission at 5\,GHz in archival VLA data
 in both the foreground lensing galaxy and RXJ1131.
-Using
-positional priors from an astrometric-corrected {\it HST} image,
-we de-blend broadband photometry spanning the rest-frame UV to radio wavelengths
-that we have compiled from public catalogues and previous optical studies, as well as from those we have
-extracted using aperture photometry.
 
 Based on our lens modeling analysis of different \bco velocity channels,
-%  to study the intrinsic gas dynamics of RXJ1131.
 we find a secondary CO-emitting source near RXJ1131 whose coordinates
 are consistent with those of an optically faint companion reported in previous optical studies
-% inferred from previous lens modeling in the optical wavelengths
 \citepalias{Claeskens06a,Brewer08a}.
@@
 % which is consistent with a kinematically-ordered disk galaxy.
-The magnification factor inferred from our best-fit models is found to
+The magnification factor inferred for the CO emission in RXJ1131 is found to
 vary from $\mu_{\rm L}$\ssim3 to $\sim8$ across channels. This is indicative of an extended molecular gas
-distribution in the host galaxy of RXJ1131 and thus different kinematic components
+distribution in the host galaxy of RXJ1131, and that different kinematic components
 of the gas are magnified inhomogeneously.
@@
 we find an intrinsically symmetric double-horned \bco line profile for RXJ1131.
-This together with a symmetric velocity gradient reconstructed in the source plane argues for a rotating disk morphology for RXJ1131, in good agreement with previous findings \citepalias{Claeskens06a}.
-Assuming thermalized excitation between \aco and \bco and \alphaco=\,0.8\,\alphaU,
-we find a lensing-corrected gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
+This together with a symmetric source-plane velocity gradient argues for a rotating disk in RXJ1131, in good agreement with previous findings \citepalias{Claeskens06a}.
+We find a lensing-corrected gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
 for RXJ1131
-and $($1.92\pmm0.09$)$\,\E{9} \Msun for the companion.
-This corresponds to a {\em gas} mass ratio of $\sim$7:1.
-Using the source-plane \bco size of $R$\ssim6\,kpc for RXJ1131, we find a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun,
-% \,=\,(8.3\pmm1.9)\E{10}\,\Msun
-% and $M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun for the companion,
-and thus a gas mass fraction of $\sim$0.19.
-This gas fraction is consistent with the trend of decreasing molecular gas content
-since $z$\ssim1 \citep[e.g.,][]{Lagos11a, Combes13a} which has been suggested as the cause for
-the decline in SFR towards $z$\ssim0 \citep[and references therein]{CW13}.
-Due to the lack of stringent constraints on the individual galaxy mass of RXJ1131 and of the companion, we classify the system as a ``wet'' minor merger on the basis of their gas mass ratio.
-%The merger system studied here is in stark contrast to the
-%``wet-dry'' merger SMM J04135$+$10277 at $z$\eq2.8,
-%where the quasar host galaxy harbors $\gtrsim$\,$5$ times less gas mass than its companion \citep{Riechers13a}.
+and $($1.92\pmm0.09$)$\,\E{9} \Msun for the companion, 
+corresponding to a gas mass ratio of $\sim$7:1.
+Using the source-plane \bco size of $R$\ssim6\,kpc, we find a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun for RXJ1131.
+%  and $\sim$(4)\E{9}\,\Msun for the companion.
+The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim19\% and baryonic gas mass fraction of 
+$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\ssim32\% are consistent with the trend of decreasing molecular gas 
+content since $z$\ssim2 \citep[e.g.,][;\citetalias{Combes13a}]{Lagos11a,Tacconi13a}
+which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
+The CO-based dynamical mass ratio of $\sim$24:1
+between RXJ1131 and the companion, and a gas mass ratio of $\sim$7:1
+suggest that the system is a ``wet'' minor merger.
 
 Fitting dust SED models to the IR-to-mm photometry, we derive
-lensing-corrected $M_{\rm dust}$\ssim4\E{8}\,\Msun,
-\LIR$\sim$\,1.5\E{12}\,\Lsun, % which indicates that the host galaxy can be classified as a ULIRG.
-% We also derive a far-IR luminosity, which yields a SFR$_{\rm FIR}$\ssim120\,\sfrU.
+lensing-corrected dust mass of $M_{\rm dust}$\ssim4\E{8}\,\Msun,
+infrared luminosity of \LIR$\sim$\,1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun, 
 and a far-IR luminosity that corresponds to a SFR$_{\rm FIR}$\ssim120\,\sfrU.
-These physical properties suggest that the merger system is dusty in nature with active starburst activity.
-We also derive a stellar mass of $M^{*}$\ssim3\E{10}\,\Msun by fitting SED models to the
-rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit, in order to
-take into account the effect of differential lensing.
-% compare intrinsic CO size and stellar
+These physical properties suggest that the merger system is dusty in nature with on-going \SF activity occuring
+at a rate comparable to local ULIRGs/mergers and high-$z$ massive disk galaxies \citep{dacunha10a, Daddi10a}. 
+We also derive a stellar mass of $M_{*}$\ssim3\E{10}\,\Msun by fitting SED models to the
+rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit to
+account for differential lensing effect.
 The source-plane distribution of the gas and stellar populations of different ages
-indicates that the CO gas is of similar spatial extent as the old and long-lasting stellar populations, whereas
-recent \SF regions appear to be embedded within the inner few kpc of the molecular gas reservoir.
-The compact \SB in RXJ1131 is likely a consequence of gas accumulation driven by interactions with the companion.
-While properties such as CO linewidths, CO size, SFR, and gas mass found in RXJ1131
-resemble those of local ULIRGs and high-$z$ starburst galaxies,
-its SFE is comparable to those of nearby and high-$z$ disk-like galaxies rather than
-\SB systems. %
-% This results from the SFR sitting at the low end, and gas mass at the high end among \SB systems
-% This is in agreement with its disk-like kinematic signatures.
+indicates that the CO gas is of similar spatial extent as the old and long-lasting stellar populations, 
+whereas regions of recent \SF maybe embedded within the molecular gas reservoir as a result of 
+gas accumulation driven by interactions with the companion. 
+Based on dynamical mass constraints, we cannot rule out the possibility that the 
+compact \SF in the host galaxy 
+maybe heavily dust-obscured. 
+Hence, the true extent of recent \SF maybe as extended as the molecular gas 
+reservoir.
+While properties such as CO linewidth, SFR, and gas mass found in RXJ1131
+are consistent with those of local ULIRGs and high-$z$ starburst galaxies,
+its SFE is comparable to those of nearby and high-$z$ disk galaxies rather than
+\SB systems. This is in good agreement with its disk-like kinematic signatures and its extended molecular gas distribution.
+However, we find a sSFR\ssim4 Gyr\pmOne that is $\lesssim$1.5$\sigma$ higher than the main sequence, suggesting 
+that the majority of star formation in RXJ1131 could be driven by its interactions with the companion galaxy.
+The merger nature and extended gas disk are likely the explanations for RXJ1131 to display 
+characteristics resembling both \SB and disk galaxies.
 Recent theoretical simulations have illustrated that the disk component of a gas-rich
@@
 % and the gas rapidly reform a cold disc in the background.
-As such, the extended molecular gas disk of RXJ1131 together with its low SFE may be indications
-that the nuclear starburst in RXJ1131 could form a
-larger stellar bulge in the merger remnant upon coalescing, and yet, the
-inefficient removal of gas angular momentum renders it unlikely
-to evolve into an E/S0 galaxy.
+As such, the extended gas disk of RXJ1131 together with its low SFE may indicate
+that the \SF in RXJ1131 could form a
+larger stellar bulge in the merger remnant upon coalescing.
 
 Using the CO redshift as the systemic redshift for the host galaxy of RXJ1131, we find
-that the optical BLR lines reported in previous studies are blueshifted by $\sim$780\,\kms.
+that the redshift inferred from the NLR lines reported in previous studies are consistent with this systemic redshift
+but the optical BLR lines are blueshifted by $\sim$780\,\kms.
 This implies that the AGN is offset from the dynamical center of its host galaxy.
@@
 BLRs are gravitationally bound to the central AGN, whereas this condition is not necessary for NLRs.
-Since such an offset is typically $\sim$100\pmm270\,\kms,
-we thus raise an alternative explanation of
-of a recoiling black hole in RXJ1131, which
-would also explain the highly spinning black hole.
+Since the velocity offset between emission lines of the BLR and the NLR 
+is typically $\sim$100\pmm270\,\kms,
+we thus raise an alternative explanation of a recoiling black hole in RXJ1131, which
+would also explain the high spin parameter reported by \citet{Reis14a}.
 % This model requires a merged BH, this interpretation would imply that RXJ1131 was
@@
 
-Adopting the stellar mass as an upper limit to the bulge mass of RXJ1131, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$\gtrsim$0.27\%, providing
+Adopting the stellar mass as an upper limit to the bulge mass, we find a
+$M_{\rm BH}$$/$$M_{\rm bulge}$\eq0.27\petm{11}{8}\% for  of RXJ1131, providing
 a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
 The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio compared to the local relation suggests that the
-black hole in RXJ1131 grows faster or earlier than its host galaxy than the local counterparts.
-This is consistent with existing studies of the evolution in the co-eval growth between SMBHs and their host galaxies.
-
-This work demonstrates that, with the aid of
-gravitational lensing and
-dynamical lens modeling of resolved spectral line observations,
-it is possible to study the gas kinematics and dynamics in high-$z$ quasar host galaxies
-% in great details
-despite strong quasar emission.
-The first use of such technique is presented by \citet{Riechers08a}, who reconstruct a source-plane
-velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
-which is also the only other similar system whose host galaxy is lensed into an Einstein ring configuration.
+black hole in RXJ1131 has grown faster or earlier than its host galaxy than nearby AGN host galaxies,
+consistent with the results from existing studies of the evolution in the growth of SMBHs and their host galaxies
+ \citep[e.g.,][]{Walter04a, Peng06a,McLure06a}.
+ The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
+ %the ratio is larger at high z than the present day, implying evolution in the Mbh?Msph relation
 
@@
 \acknowledgments
+
 DR and RP acknowledge support from the National Science Foundation
@@
 Services.
-This work is based in part on observations made with the \spitzer,
+This work is based in part on observations
+made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
+Legacy Archive, which is a collaboration between the Space Telescope Science
+Institute (STScI/NASA), the Space Telescope European Coordinating Facility
+(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).
+This work is based
+in part on observations made with the \spitzer,
 which is operated by the Jet Propulsion Laboratory, California Institute of

### 2016-08-29 PdBI/src/modelVelo/modelGradient.py
shift scale bar to right, based on DR's comments

@@ -4,9 +4,11 @@
 plot source locations from lens model of various channel as markers on observed 1st moment map.
 Kinematics.
 
-Last Modified: 31 July 2016
+Last Modified: 29 Aug 2016
 
 History:
+29 Aug 2016:
+  - shift scale bar text to the right
 31 July 2016:
   - add option to do PV fit using lmfit
 25 July 2016:
@@ -187,7 +189,7 @@ def draw_sizebar(ax, z, pxScale, arcsec=1.0):
     asb = AnchoredSizeBar(ax.transData,
                           length,
                           str(round(kpc))+" kpc at " + r"$z = $" + (("{0:.3f}").format(z)),
-                          loc=8,
+                          loc=4,
                           pad=0.35, borderpad=0.65, sep=5,
                           frameon=False)
     ax.add_artist(asb)

### 2016-08-30 WRITEUP/ms.tex
w/ DR's handwritten comments

@@
 \pdbi (PdBI) and the \carma (CARMA).
-Our lens modeling shows that the asymmetry of the double-horned \bco line profile
+Our lens modeling shows that the asymmetry in the double-horned \bco line profile
 is mainly a result of differential lensing, where
-the magnification factor varies from $\sim$3 to $\sim$8 across
+the magnification factor varies from $\sim$3 to $\sim$9 across
 different kinematic components.
@@
 gradient suggests that
-the quasar host galaxy is an extended rotating disk, with a CO size of $R$$\sim$6\,kpc in radius and
+the host galaxy is an extended rotating disk of $R_{\rm CO}$$\sim$6\,kpc and
 a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
@@
 consistent with the optically-faint companion reported in previous studies.
-We decompose the lensing-corrected total \bco line flux into two components and 
-find a lensing-corrected gas mass of $M_{\rm gas}$\ssim1.4\E{10}\,\Msun for RXJ1131
-and \ssim2\E{9}\,\Msun for the companion, corresponding
-to a gas mass ratio of $\sim$7:1.
-The gas mass fraction of $\sim$19\% inferred for RXJ1131 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim1 reported in recent studies.
-The lensing-corrected stellar mass $M_{*}$\ssim3\E{10}\,\Msun,
-dust mass $M_{\rm dust}$\ssim4\E{8}\,\Msun, IR luminosity $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun, and 
-star formation rate SFR$_{\rm FIR}$\eq120\pmm63 \sfrU of RXJ1131
-together with its source-plane morphology of the gas and stellar populations
-indicate ongoing star-formation activity that maybe as extended as the molecular gas reservoir.
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of 0.27\petm{11}{8}\% that is higher
+The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
+and \ssim2\E{9}\,\Msun for RXJ1131 and the companion, respectively.
+The gas mass fraction of $\sim$19\% inferred for RXJ1131 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
+We find lensing-corrected stellar and dust masses, IR luminosity, and
+star formation rate of
+$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXJ1131.
+The source-plane morphologies of its gas and stellar populations
+indicate that the star-formation activity may be as extended as the molecular gas reservoir.
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% that is higher
 than the local value
-but consistent with other galaxies at this epoch. Collectively, our results suggest
-that the bulk of the black hole mass of RXJ1131 is already in place 
-while its stellar bulge component is still assembling, and that its major mode of \SF is likely merger-driven.
+but consistent with other galaxies at this epoch, suggesting that the bulk of the black hole mass of RXJ1131 is already in place while its stellar bulge is still assembling.
 \end{abstract}
@@
 A leading explanation for this decline is the decrease in molecular gas content and
-\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
-but confirmation from direct molecular gas measurements at intermediate redshift
-$(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed ---
-only unresolved CO observations have been carried out for $\sim$$30$ ultra-luminous infrared galaxies (ULIRGs) up to date \citep{Combes11a, Combes13a}. %18+15
+\SF efficiency \citep[e.g.,][]{Erb06a, CW13, Walter14a},
+but direct molecular gas measurements at intermediate redshift
+$(0.2\,<\,z\,<\,1)$ that could confirm this explanation remain largely limited to
+spatially unresolved CO observations of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}. %18+15
 
@@
 $M_{\rm BH}$$-$\mbulge relation \citep[e.g.,][]{Magorrian98a, HR04a}
-has been established locally, suggesting a co-eval growth between local SMBHs and their host galaxies.
+have been established locally, suggesting a co-eval growth between local SMBHs and their host galaxies.
 Attempts to extend this relation out to higher redshifts, beyond the peak epoch
@@
 These studies find that
-% the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratios of high-$z$ submillimeter galaxies (SMGs) 
-% are lower than those of local AGN host galaxies \citep[\eg][]{Borys05a,Alexander08a}, 
-% whereas those of high-$z$ quasar host galaxies 
-% are higher than the local values \citep[\eg][]{Walter04a, McLure06a,Peng06a, Riechers08a,Coppin08a}, 
-% suggesting that the co-eval growth of high-$z$ AGNs and their host galaxies follows different 
-% timescales compared to their local counterparts. % different AGN mechanism, different AGN accretion rate
-% However, any links between such fast-growing SMBHs and their host galaxies are not yet established at these high redshifts.
-high-$z$ AGN host galaxies do not follow the same $M_{\rm BH}$$-$\mbulge relation \citep[\eg][]{Walter04a,Borys05a, McLure06a,Peng06a, Riechers08a,Coppin08a,Alexander08a}.
+high-$z$ AGN host galaxies do not appear to follow the same $M_{\rm BH}$$-$\mbulge relation as nearby spheroidal galaxies.
+\citep[\eg][]{Walter04a,Borys05a, McLure06a,Peng06a, Riechers08a,Coppin08a,Alexander08a}.
 Yet, the $M_{\rm BH}$$-$\mbulge relation remains poorly-constrained
 at intermediate redshifts.
-This is owed to the difficulties in measuring stellar emission in optical quasar host galaxies, where
-emission of quasars produces sidelobes that saturate the lower surface brightness starlight in the host galaxy,
-or alternatively, due to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar 
-(bulge) mass.
+This is owed to the difficulties in
+measuring stellar emission in quasar host galaxies which is typically
+saturated by the sidelobes from their quasars.
 With strong gravitational lensing, emission from the background quasar and its host galaxy originating from
-different source-plane locations and of different extent is being magnified and stretched out by different amount.
-The lensed emission is therefore spatially resolved over more beams which reduces the sidelobes and enables 
+different source-plane locations with different spatial extent is being magnified and stretched out inhomogenously,
+allowing their emission to be
+spatially resolved over more beams to reduce the dynamic range, and thus 
 measurements of the stellar emission in the host galaxy.
@@
 
-In this paper, we present \bco and \cco line data observed towards RXJ1131 and
-broadband photometry spanning rest-frame UV to radio wavelengths to 
-study the properties of the molecular gas, the dust and stellar populations in the 
-host galaxy of RXJ1131.
+In this paper, we present \bco and \cco line observations and
+broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
+study the properties of its molecular gas, the dust and stellar populations.
 In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
-In \Sec{HST}, we describe the astrometric corrections
-applied to an image taken with the \hst ({\it HST}) by aligning it to
-a radio image taken with the \vla (VLA).
-In \Sec{results}, we report measurements of the \bco and \cco lines and broadband
+In \Sec{results}, we report results for the \bco and \cco emission and broadband
 photometry in RXJ1131.
-In \Sec{anal}, we present dynamical lens modeling of the \bco data and
+In \Sec{anal}, we present lens modeling and dynamical modeling of the \bco data and
 spectral energy distribution (SED) modeling of the photometric data.
@@
 and the underlying continuum emission, employing a correlator setup that provides
-an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 10.0 MHz ($\sim$
-$21.5$ \kms).  {\bf DR: DSB, 320 MHz/128 channels? <-> 2.5 MHz? I did not bin the data}
+an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 1.95\,MHz
+($\sim$\,$4.2$\,\kms).
 The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
@@
 We thus conservatively estimate
-a calibration accuracy of $\sim$35\% based on the flux scale uncertainties,
+a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35% add in quad
 the gain variations over time, and the phase scatter on the calibrated data. We
@@
 
-\section{HST astrometry} \label{sec:HST}
+\subsection{HST (Archival)}
 We obtained an {\it HST} image taken with
@@
 in \citetalias{Claeskens06a}.
-We adopt the VLA 5\,GHz map as the
-reference coordinate frame to align the optical ($V$-band) image.
+We apply astrometric correction to the optical image by adopting the VLA 5\,GHz map as the
+reference coordinate frame.
 We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
@@
 considering the asymmetry resulting from differential lensing.
-A detailed discussion of this effect is presented in
-\Sec{differential}.
- \label{fig:CO21spec}}
+A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
 \end{figure}
-
+\vspace{.2em} 
 % moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
@@
 thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
-nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, and also 
+nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
 with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
@@
 
-We detect PdBI 2\,mm continuum emission, as shown in \Fig{cont}. The integrated flux density is
+We detect 2\,mm continuum emission at an
+ integrated flux density of
 1.2\pmm0.2 mJy, with a peak flux of
 $S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
-centered on the lensing galaxy. Slightly extended emission
+centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
 along the lensed arc is also detected.
@@
 We subtract a point source model in the $uv$-plane to remove the unresolved
-emission towards the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
+emission which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
 in the residual map coincides with the lensed arc, and is consistent with
@@
 the background galaxy (RXJ1131).
-The quoted uncertainty is from the flux measurement in the residual map and do not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
+The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
 We report the peak flux in the original map
-($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy.
-We note that this peak flux density is only our best estimate at the resolution of our observations, a non-negligible contribution from the background source to the total integrated (blended) flux may be present.
+($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
+is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
 % The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
@@
 (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
-Models of each slice thus provide information on
-the corresponding kinematic component of the CO gas,
-enabling us to reconstruct a velocity gradient in the source plane.
-%
+Our approach is similar to \citet{Riechers08a}, who reconstruct a source-plane
+velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
+whose host galaxy is also lensed into an Einstein ring configuration.
 To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
@@
 that cover the full linewidth of $\sim$750\,\kms.
-%
-The first use of a dynamical lens modeling approach is presented by \citet{Riechers08a}, who reconstruct a source-plane
-velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
-which is also the only other similar system whose host galaxy is lensed into an Einstein ring configuration.
 
@@
 direction (1\farcs5).
-The spectra map covers an extent of $\sim$10"$\times$10"
+The spectra map covers an extent of $\sim$10''$\times$10''
 centered on the pixel that corresponds to coordinates of the lensing galaxy ($\alpha_{\rm J2000}$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44, $\delta_{\rm J2000}$\,=\,$-$12\degr31\arcmin58\farcs3).
@@
 \subsection{\bco Kinematics}
-Fitting two Gaussians with a single FWHM
+Fitting two Gaussians with a common FWHM
 to the ``intrinsic'' \bco line profile of RXJ1131 (after correcting for lensing using
@@
 velocity dispersion ($\gtrsim$400\,\kms) near the central region
-is seen in \Fig{CO21mom}. While beam smearing is inevitably the
+are seen in \Fig{CO21mom}. While beam smearing is inevitably the
 dominant factor in the observed velocity dispersion
@@
 radius at which the rising part of the curve begins to flatten.
-We perform non-linear least square fitting using an orthogonal distance
+We perform non-linear least squares fitting using an orthogonal distance
 regression to find the best-fit parameters,
@@
 The asymptotic velocity ($V_{a}$) --- an extrapolation of the model
-out to radius beyond the disk scale-length and half-light radius --
+out to radius beyond the disk scale-length and half-light radius ---
 is not equivalent to the maximum observed velocity ($V_{\rm max}$),
@@
 as the rotation velocity ($V_{\rm max}$ in their
-terminology) since this corresponds to the radius at which the velocity
+terminology), since this corresponds to the radius at which the velocity
 of a pure exponential disk peaks \citep{Courteau97b}. % \ie commonly use Vmax (taken at R2.2) as V_rot
@@
 in the host galaxy. Hence,
-the $V$-band compactness may be explained in part
-due to the fact that its emission is
-more susceptible to dust extinction than in other bands and/or
+the relative compactness observed in the $V$-band may be explained in part
+due to the fact that the emission in this band is
+more susceptible to dust extinction than in other bands and/or dominated by
 a central starburst caused by higher
@@
 if we adopt the better-constrained $V$-band source size of $\sim$700\,pc \citepalias{Brewer08a}.
-The $V$-band dynamical mass is substantially lower than the gas mass, which
-may be an indication of the dusty nature of the companion.
-% in which the $V$-band source size to
-% appear much smaller than its true extent.
+Since the $V$-band dynamical mass is substantially lower than the gas mass,
+ the $V$-band emitting region may appear to be much smaller than its true extent due
+to dust obscuration.
 
@@
 between RXJ1131 and the companion, with a gas mass ratio of $\sim$7:1 derived in  \Sec{caveat}.
-We thus classify the system as a {\em ``wet'' minor merger}.
+We thus classify the system as a {\em gas-rich,``wet'' minor merger}.
 
@@
 \citealt[hereafter C13]{Combes13a}).
-We note the \fir luminosity is comparable in both models, which is
+The \fir luminosity is comparable in both models, which is
 not surprising given the lack of constraints in the MIR.
@@
 to account for differential lensing (light blue circles in \Fig{SED}).
-We thus find a stellar mass of $M^*$\eq2.95\petm{1.32}{0.86}\E{10}\,\Msun, which
+We thus find a stellar mass of $M_*$\eq2.95\petm{1.32}{0.86}\E{10}\,\Msun, which
 is the median value of the posterior probability distribution and
@@
 % Salpeter M* ~ 1.8 * Chabrier
-% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up" time (aka mass-doubling timescale) of $M^*$$/$SFR\eq sSFR\pmOne\ssim440 Myr for RXJ1131.
+% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up'' time (aka mass-doubling timescale) of $M^*$$/$SFR\eq sSFR\pmOne\ssim440 Myr for RXJ1131.
 
@@
 \subsection{ISM Properties} \label{sec:properties}
-In this section, we derive the gas properties of the merging system
+In this section, we derive the gas properties of the merging system RXJ1131
 based on \bco and compare them with those reported by
@@
 
-\subsubsection{Linewidth and Sizes} \label{sec:sizes}
+\subsubsection{Linewidths and Sizes} \label{sec:sizes}
 The FWHM linewidth of $\Delta v_{\rm}$\,$\sim$\,600\pmm160\,\kms found
@@
 which are believed to originate from mergers.
-The wider CO linewidth observed in RXJ1131 also supports the merger picture.
+The wider CO linewidth observed in RXJ1131 also supports a merger picture.
 
@@
 which is more
-extended than the average of a sample of disk-like U/LIRGs studied by
+extended than the average of 3.5\pmm2.3\,kpc in a sample of disk-like U/LIRGs studied by
 \citet[]{Ueda14a}, % who find an average radius of 3.5\pmm2.3\,kpc
@@
 
-\subsubsection{Gas Mass Fractions}
+\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio}
 
@@
 % , where the uncertainty is based on that of the gas mass.
-and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\eq32\petm{7}{-12}\% for RXJ1131.
+and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\eq32\petm{7}{12}\% for RXJ1131.
 % The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
-Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $\sim$40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
+Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
 % On the other hand,
@@
 and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
-normal ``star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use  the ``Galactic'' \alphaco conversion factor to compute the molecular gas mass.}.
+normal ``star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
+\alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
 Both the dynamical and baryonic gas mass fractions of RXJ1131 are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
@@
 gas-to-dust ratio (GDR) of
-40\pmm34, which would be a factor of two higher if we adopted a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
+40\pmm34.
+This would be a factor of two higher if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
 This GDR is lower than the statistical average of 206
 in the \citetalias{Combes13a} sample but is well within the broad
-range of values measured over the entire sample. 
+range of values measured over their entire sample ($\sim$1$-$770).
 Our ratio is also consistent with high-$z$ SMGs
@@
 \citep[]{Bothwell13a} and
-local ULIRGs \citep{Wilson08a}, but lower than the Milky Way by
+local ULIRGs \citep{Wilson08a}, but lower than that of the Milky Way by
 $\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
-\defcitealias{Bothwell13a}{B13}
-
-There are a number of systematic uncertainties associated with the derived gas-to-dust ratio. For instance,
+
+There are a number of systematic uncertainties associated with the derived gas-to-dust ratio, in particular
 the mass opacity coefficient $\kappa$,
@@
 the gas mass (and thus gas-to-dust ratio) would be $\sim$6 times higher.
-We note that this gas mass is physically feasible based on the dynamical mass constraints derived in \Sec{dyn}.
+We note that this gas mass is physically possible based on the dynamical mass constraints derived in \Sec{dyn}.
 On the other hand, we would also obtain a higher gas mass if
@@
 We also note that the gas-to-dust ratio derived for RXJ1131 may be biased low as the gas is likely to
-be more extended than the dust. Consequently, the overall magnification factor
+be more extended than the optically thick dust. Consequently, the overall magnification factor
 for the CO gas may be lower than the optically thick dust, which dominates the \fir luminosity.
@@
 gas depletion time of $\tau$\,=\,102\pmm25\,Myr.
-\defcitealias{Tacconi08a}{T08}
 
@@
 % %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
-The specific star formation rate (sSFR\eq SFR/$M^*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
+The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
 is $\lesssim$1.5$\sigma$ above the main sequence according to
-the redshift-dependent ``main sequence" relation in \citet[and references therein]{Tacconi13a} but is
-consistent with those of the \cite{dacunha10a} sample of local ULIRGs, suggesting that the 
-majority of \SF in RXJ1131 could be driven by its interactions with the companion galaxy, 
-unlike most disk galaxies despite sharing similar \SF rate, \SF efficiency, and CO disk size.
+the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
+%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
+Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
+the slight enhancement in sSFR may suggest
+that the \SF in RXJ1131 is driven by the interactions with the companion.
 
@@
 
-\defcitealias{Sluse07a}{S07}
-\citet[hereafter S07]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
+\citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
 The first set of lines is at $z$\ssim0.653, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
@@
 \subsection{The $M_{\rm BH}$$-$\mbulge Relation}
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of 0.27\petm{11}{8}\%
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\%
 using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
@@
 the emerging picture that quasars
-grow faster and/or earlier than their host galaxies at higher redshifts \citep[e.g., ][]{Walter04a, Peng06a, McLure06a}.
+grow faster and/or earlier than their host galaxies at higher redshifts \citep[e.g., ][]{Walter04a, Peng06a, McLure06a,Riechers08a}.
 The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local AGNs
@@
 Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.66\,\pm\,0.41$
-between the \bco and \cco lines.
-Taking into account the large phase errors associated with the \cco measurement, this ratio
-is consistent with thermalized excitation but also with the lower excitation seen in normal star-forming disks.
+between the \bco and \cco lines,
+consistent with thermalized excitation but also with the lower excitation seen in normal star-forming disks.
 We also detect marginally resolved
@@
 The magnification factor inferred for the CO emission in RXJ1131 is found to
-vary from $\mu_{\rm L}$\ssim3 to $\sim8$ across channels. This is indicative of an extended molecular gas
-distribution in the host galaxy of RXJ1131, and that different kinematic components
-of the gas are magnified inhomogeneously.
+vary from $\mu_{\rm L}$\ssim3 to $\sim$9 across channels. This is indicative of an extended molecular gas
+distribution in the host galaxy of RXJ1131, where the different kinematic components
+of the gas are magnified inhomogeneously, similar to what was found for the $z$$>$4 quasar
+PSS J2322$+$1944 \citep{Riechers08a}.
 Upon correcting for lensing magnification and subtracting a contribution from the companion,
@@
 between RXJ1131 and the companion, and a gas mass ratio of $\sim$7:1
-suggest that the system is a ``wet'' minor merger.
+suggest that the system is a gas-rich, ``wet'' minor merger.
 
 Fitting dust SED models to the IR-to-mm photometry, we derive
-lensing-corrected dust mass of $M_{\rm dust}$\ssim4\E{8}\,\Msun,
-infrared luminosity of \LIR$\sim$\,1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun, 
+a lensing-corrected dust mass of $M_{\rm dust}$\ssim4\E{8}\,\Msun,
+an infrared luminosity of \LIR$\sim$\,1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun,
 and a far-IR luminosity that corresponds to a SFR$_{\rm FIR}$\ssim120\,\sfrU.
@@
 indicates that the CO gas is of similar spatial extent as the old and long-lasting stellar populations,
-whereas regions of recent \SF maybe embedded within the molecular gas reservoir as a result of 
+whereas regions of recent \SF may be embedded within the molecular gas reservoir as a result of
 gas accumulation driven by interactions with the companion.
@@
 compact \SF in the host galaxy
-maybe heavily dust-obscured. 
-Hence, the true extent of recent \SF maybe as extended as the molecular gas 
+may be heavily dust-obscured.
+Hence, the true extent of recent \SF may be as extended as the molecular gas
 reservoir.
@@
 \SB systems. This is in good agreement with its disk-like kinematic signatures and its extended molecular gas distribution.
-However, we find a sSFR\ssim4 Gyr\pmOne that is $\lesssim$1.5$\sigma$ higher than the main sequence, suggesting 
-that the majority of star formation in RXJ1131 could be driven by its interactions with the companion galaxy.
-The merger nature and extended gas disk are likely the explanations for RXJ1131 to display 
-characteristics resembling both \SB and disk galaxies.
-Recent theoretical simulations have illustrated that the disk component of a gas-rich
+We find a specific \SF rate (sSFR\ssim4 Gyr\pmOne) that is $\lesssim$1.5$\sigma$ higher than those of ``main sequence'' galaxies.
+The slight enhancement in sSFR suggests that
+the on-going star formation in RXJ1131 could be driven by interactions with the companion.
+Recent simulations have illustrated that the disk component of a gas-rich
 progenitor galaxy with low SFE can be
 retained upon merging since the efficiency at removing angular momentum of the gas via
-gravitational torques provided by stellar components is reduced in such a system.
+gravitational torques provided by stellar components is reduced in such a system \citep{Springel05a, Robertson06a, Hopkins09a}.
 % and the gas rapidly reform a cold disc in the background.
@@
 Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$\eq0.27\petm{11}{8}\% for  of RXJ1131, providing
+$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{11}{8}\% for  of RXJ1131, providing
 a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.

### 2016-08-30 WRITEUP/ms.tex
some more rewording from myself

@@
 Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
-the slight enhancement in sSFR may suggest
-that the \SF in RXJ1131 is driven by the interactions with the companion.
+the slight enhancement in sSFR suggests
+that the \SF in RXJ1131 may be predominantly driven by interactions with the companion.
 
@@
 Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{11}{8}\% for  of RXJ1131, providing
+$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{11}{8}\% for RXJ1131, providing
 a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.

### 2016-08-30 src/singlePanelmom0.py
change saved fig name to use _ instead of .

@@ -6,11 +6,13 @@ Plot mom0 of all channels overlay on HST (single panel)
 Author: Daisy Leung
 
 
-Last edited: 20 july 2016
+Last edited: 29 Aug 2016
 
 
 History:
 --------
+29 Aug 2016
+    - changing save filename to exclude . between name and ext, else would mess up the prepare to submit codes
 20 July 2016
     - change zoom & HST contrast to match RedBlue.py
 28 May 2016:
@@ -150,7 +152,7 @@ if __name__ == '__main__':
     saveFig = True if sys.argv[1].lower() == 'true' else False
     if saveFig:
         outname = 'F555WCO21_mom0_single.eps'
-        if inverted_HSTleft: outname = outname.replace('.eps', '.invertedgray.eps')
+        if inverted_HSTleft: outname = outname.replace('.eps', '_invertedgray.eps')
         figC.savefig(Plotpath + outname, dpi=600, bbox_inches='tight')
     else:
         #        figC.canvas.draw()

### 2016-08-30 WRITEUP/ms.tex
replace fig name with . to _
update keywwords

@@
 
-\keywords{ISM: molecules --
-          infrared: galaxies --
-          galaxies: mergers --
-          galaxies: starburst --
+\keywords{infrared: galaxies --
+          galaxies: high-redshift --
+          galaxies: ISM --
           galaxies: evolution --
-          quasars: individual (RXS\,J1131$-$1231)}
+          quasars: individual (RXS\,J1131$-$1231) --
+          radio lines: ISM}
 
@@
 % [-324.88, 0] km/s
-\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
+\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
 \includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}

### 2016-08-30 WRITEUP/ms.tex
w/ DR's comments, need to shrink abstract

@@
 the quadruply-lensed quasar
-RXS\,J1131$-$1231 (hereafter RXJ1131) at $z$\,=\,0.654 obtained using the
+RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
 \pdbi (PdBI) and the \carma (CARMA).
@@
 gradient suggests that
-the host galaxy is an extended rotating disk of $R_{\rm CO}$$\sim$6\,kpc and
+the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
 a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
-In addition, we find a secondary CO-emitting source near RXJ1131 whose location is
+In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
 consistent with the optically-faint companion reported in previous studies.
 The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
-and \ssim2\E{9}\,\Msun for RXJ1131 and the companion, respectively.
-The gas mass fraction of $\sim$19\% inferred for RXJ1131 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
+and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
+The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
 We find lensing-corrected stellar and dust masses, IR luminosity, and
 star formation rate of
-$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXJ1131.
+$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
 The source-plane morphologies of its gas and stellar populations
 indicate that the star-formation activity may be as extended as the molecular gas reservoir.
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% that is higher
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
 than the local value
-but consistent with other galaxies at this epoch, suggesting that the bulk of the black hole mass of RXJ1131 is already in place while its stellar bulge is still assembling.
+but consistent with other galaxies at this epoch, suggesting that the bulk of the black hole mass of RXS\,J1131$-$1231 is largely in place while its stellar bulge is still assembling.
 \end{abstract}
@@
 $(0.2\,<\,z\,<\,1)$ that could confirm this explanation remain largely limited to
-spatially unresolved CO observations of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}. %18+15
+spatially unresolved CO observations of 
+a modest sample of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}. %18+15
 
@@
 Yet, the $M_{\rm BH}$$-$\mbulge relation remains poorly-constrained
-at intermediate redshifts.
-This is owed to the difficulties in
-measuring stellar emission in quasar host galaxies which is typically
-saturated by the sidelobes from their quasars.
-With strong gravitational lensing, emission from the background quasar and its host galaxy originating from
-different source-plane locations with different spatial extent is being magnified and stretched out inhomogenously,
-allowing their emission to be
-spatially resolved over more beams to reduce the dynamic range, and thus
-measurements of the stellar emission in the host galaxy.
+at intermediate redshifts due to the difficulty 
+in separating the stellar component contributing to the optical emission from that of the bright AGN. 
+This stems from the limited resolving power, which restricts the dynamic range that can be achieved at positions near the AGN.
+Strong gravitational lensing provides the magnification necessary to spatially separate the AGN emission from the host galaxy stellar emission, significantly improving the dynamic range that can be achieved in studies of their host galaxies with current instruments.
 
@@
 broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
-study the properties of its molecular gas, the dust and stellar populations.
+study the properties of its molecular gas, dust and stellar populations.
 In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
@@
 and the underlying continuum emission, employing a correlator setup that provides
-an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 1.95\,MHz
+an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
 ($\sim$\,$4.2$\,\kms).
@@
 in \citetalias{Claeskens06a}.
-We apply astrometric correction to the optical image by adopting the VLA 5\,GHz map as the
+We apply an astrometric correction to the optical image by adopting the VLA 5\,GHz map as the
 reference coordinate frame.
@@
 emission is marginally resolved along its major axis.
-We subtract a point source model in the $uv$-plane to remove the unresolved
-emission which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
+We subtract a point source model in the $uv$-plane to remove the unresolved part of the
+emission, which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
 in the residual map coincides with the lensed arc, and is consistent with
@@
 (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
-Our approach is similar to \citet{Riechers08a}, who reconstruct a source-plane
-velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
-whose host galaxy is also lensed into an Einstein ring configuration.
+Our approach follows a similar strategy as \citet{Riechers08a}, who reconstruct a source-plane
+velocity gradient and constrain the gas dynamics in the $z$\,$>$\,4 quasar host galaxy of
+ PSS J2322$+$1944,
+which is also lensed into an Einstein ring configuration.
 To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
@@
 if we adopt the better-constrained $V$-band source size of $\sim$700\,pc \citepalias{Brewer08a}.
-Since the $V$-band dynamical mass is substantially lower than the gas mass,
+Since the $V$-band based dynamical mass measurement is substantially lower than the gas mass,
  the $V$-band emitting region may appear to be much smaller than its true extent due
@@
 40\pmm34.
-This would be a factor of two higher if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
+This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
 This GDR is lower than the statistical average of 206
@@
 Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
-the slight enhancement in sSFR suggests
-that the \SF in RXJ1131 may be predominantly driven by interactions with the companion.
+the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
+that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
 
@@
 We find a specific \SF rate (sSFR\ssim4 Gyr\pmOne) that is $\lesssim$1.5$\sigma$ higher than those of ``main sequence'' galaxies.
-The slight enhancement in sSFR suggests that
-the on-going star formation in RXJ1131 could be driven by interactions with the companion.
+The slight elevation in sSFR over the main sequence suggests that
+the on-going star formation activity in RXJ1131 could be enhanced by interactions with the companion.
 Recent simulations have illustrated that the disk component of a gas-rich

### 2016-08-30 WRITEUP/ms.tex
shorten abstract

@@
 The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
-We find lensing-corrected stellar and dust masses, IR luminosity, and
+We find lensing-corrected stellar and dust masses, an IR luminosity, and a
 star formation rate of
@@
 We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
-than the local value
-but consistent with other galaxies at this epoch, suggesting that the bulk of the black hole mass of RXS\,J1131$-$1231 is largely in place while its stellar bulge is still assembling.
+than the 
+local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
 \end{abstract}
@@
 The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local AGNs
-suggests that the bulk of the black hole mass of RXJ1131 is already in place while its stellar bulge is still assembling.
+suggests that the bulk of the black hole mass of RXJ1131 is largely in place while its stellar bulge is still assembling.
 

### 2016-08-30 WRITEUP/ms_apj/ms.tex
1st sub to AAS Journal

--- 2016-08-30 WRITEUP/ms.tex
@@
 
-% -------------------------------------- Final Edit Markup ----------------------------------
 \usepackage[normalem]{ulem}
@@
 \newcommand{\new}[1]{\textcolor{red}{\bf #1}}
-\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
-% -----------------------------------------------------------------------------------------------
-
-\input{preamble}
+\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}}
+
+\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage{etoolbox}
+
+\makeatletter
+
+% Patch case where name and year are separated by aysep
+\patchcmd{\NAT@citex}
+{\@citea\NAT@hyper@{%
+\NAT@nmfmt{\NAT@nm}%
+\hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
+\NAT@date}}
+{\@citea\NAT@nmfmt{\NAT@nm}%
+\NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
+
+% Patch case where name and year are separated by opening bracket
+\patchcmd{\NAT@citex}
+{\@citea\NAT@hyper@{%
+\NAT@nmfmt{\NAT@nm}%
+\hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
+{\@citeb\@extra@b@citeb}%
+\NAT@date}}
+{\@citea\NAT@nmfmt{\NAT@nm}%
+\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
+{}{}
+
+\makeatother
+%
+\usepackage{xspace}
+%
+\usepackage{apjfonts}
+\usepackage{amssymb, amsmath} % for e.g. \lesssim
+\usepackage{natbibspacing, natbib}
+\usepackage{aas_macros} % for understanding Journal in bib
+\usepackage{graphics,graphicx}
+%
+\newcommand{\vdag}{(v)^\dagger}
+\newcommand{\myemail}{tleung@astro.cornell.edu}
+\newcommand{\mbh}{\mbox{$M_{\rm BH}$}\xspace}
+\newcommand{\mdyn}{\mbox{$M_{\rm dyn}$}\xspace}
+\newcommand{\mbulge}{\mbox{$M_{\rm bulge}$}\xspace}
+\newcommand{\mstar}{\mbox{$M^*$}\xspace}
+\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
+\newcommand{\Rsun}{\mbox{$R_{\odot}$}\xspace}
+\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
+\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
+\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
+%
+\newcommand{\rarr}{$\rightarrow$}
+\newcommand{\aco}{\mbox{CO($J$\,=\,1\,\rarr\,0)}\xspace}
+\newcommand{\bco}{\mbox{CO($J$\,=\,2\,\rarr\,1)}\xspace}
+\newcommand{\cco}{\mbox{CO($J$\,=\,3\,\rarr\,2)}\xspace}
+\newcommand{\rot}[3][CO]{\mbox{#1($J$\,=\,#2\,\rarr\,#3)}}
+%
+\newcommand{\cii}{[C{\scriptsize II}]}
+\newcommand{\mgii}{\mbox{Mg{\scriptsize II}~2798\AA}\xspace}
+\newcommand{\oiii}{\mbox{$[$O{\scriptsize III}$]$~4959, 5007\AA}\xspace}
+\newcommand{\oii}{\mbox{$[$O{\scriptsize II}$]$~3727\AA}\xspace}
+\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}\xspace}
+\newcommand{\kms}{\mbox{km\,s$^{-1}$}\xspace}
+\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}\xspace}
+\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
+\newcommand{\alphaco}{\mbox{$\alpha_{\rm CO}$}\xspace}
+\newcommand{\alphaU}{\mbox{$M_{\odot}~($K\,\,km\,\,pc$^2)^{-1}$}\xspace}
+\newcommand{\sfrU}{\mbox{\Msun\,yr$^{-1}$}\xspace}
+% Numerical values
+\newcommand{\E}[1]{\mbox{$\times10^{#1}$}}
+\newcommand{\petm}[2]{$^{+#1}_{-#2}$}
+\newcommand{\eq}{\,=\,}
+\newcommand{\ssim}{\,$\sim$\,}
+\newcommand{\pmm}{\,$\pm$\,}
+%
+\newcommand{\eg}{{e.g.,~}}
+\newcommand{\ie}{{i.e.,~}}
+%
+\newcommand{\Fig}[1]{Figure~\ref{fig:#1}}
+\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
+\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
+\newcommand{\Sec}[1]{\S\ref{sec:#1}}
+%
+\newcommand\tna{\,\tablenotemark{a}}
+\newcommand\tnb{\,\tablenotemark{b}}
+\newcommand\tnc{\,\tablenotemark{c}}
+\newcommand\tnd{\,\tablenotemark{d}}
+\newcommand\tne{\,\tablenotemark{e}}
+\newcommand\tnf{\,\tablenotemark{f}}
+\newcommand\tng{\,\tablenotemark{g}}
+\newcommand\tnh{\,\tablenotemark{h}}
+\newcommand\tni{\,\tablenotemark{i}}
+\newcommand\tnj{\,\tablenotemark{j}}
+\newcommand\tnk{\,\tablenotemark{k}}
+\newcommand\tnl{\,\tablenotemark{l}}
+%
+\def\herschel {{\it Herschel Space Observatory}\xspace}
+\def\hst {{\it Hubble Space Telescope}\xspace}
+\def\alma     {Atacama Large (sub-)Millimeter Array (ALMA)\xspace}
+\def\spitzer {{\it Spitzer Space Telescope}\xspace}
+\def\pdbi     {Plateau de Bure Interferometer\xspace}
+\def\carma    {Combined Array for Research in Millimeter-wave Astronomy\xspace}
+\def\cso      {Caltech Sumillimeter Observatory (CSO)\xspace}
+\def\noema    {Northern Extended Millimeter Array (NOEMA)\xspace}
+\def\vla      {{\it Karl G. Jansky} Very Large Array\xspace}
+% Typography
+\newcommand{\ncode}[1]{{\sc #1}}
+% Codes / Softwares
+\newcommand{\uvmcmcfit}{\ncode{uvmcmcfit}\xspace}
+\def\aips {\ncode{AIPS}\xspace}
+\def\casa {\ncode{CASA}\xspace}
+% Long words
+\newcommand{\obs}{observations\xspace}
+\newcommand{\lowZ}{low-metallicity\xspace}
+\newcommand{\mulw}{multi-wavelength\xspace}
+\newcommand{\SF}{star formation\xspace}
+\newcommand{\SB}{starburst\xspace}
+\newcommand{\SBs}{starbursts\xspace}
+\newcommand{\gl}{gravitationally lensed\xspace}
+\newcommand{\MCMC}{Markov Chain Monte Carlo (MCMC)\xspace}
+\newcommand{\ms}{``main-sequence''\xspace}
+% Wavelength regimes
+\newcommand{\fir}{far-IR\xspace}
+\newcommand{\fuv}{far-UV\xspace}
+\newcommand{\mir}{mid-IR\xspace}
+\newcommand{\nir}{near-IR\xspace}
+
 \slugcomment{To be submitted to the ApJ}
 \makeatletter
-% \renewcommand\normalsize{\@setfontsize\normalsize\@xpt{11.56}}
 \renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
@@
 \begin{document}
-%{\tiny  \RevisionInfo}
 
@@
 Ithaca, NY 14853, USA; \myemail}
-
-%=============================================================================
-%                                Front matters
-%==============================================================================
 
@@
 
-%--------------------------------------------------------------------------
-%                                Introduction
-%--------------------------------------------------------------------------
 \section{Introduction}
-%Studying the interplay between \SF and active galactic nucleus (AGN) activity across cosmic epochs is crucial to
-%our understanding of the
-%processes governing the formation and evolution of both the SMBHs and their host galaxies.
-% Significant attention has been focused on studying the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs in recent studies of galaxy evolution.
-% \citep{Wang10, Lamastra10, Hopkins+05, 06, DiMatteo+05a, Page11, Page12,Simpson12}
 Many recent studies of galaxy evolution have been focused on investigating the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs \citep[e.g.,][]{DiMatteo05a,Alexander05a,Hopkins06b,Coppin08a,Page12a,Simpson12a,Lamastra13a}.
@@
 spatially unresolved CO observations of
-a modest sample of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}. %18+15
+a modest sample of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}.
 
@@
 The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
- \citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a}, %based on H beta line
+\citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a},
 with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.
@@
 $\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
-% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
 \defcitealias{Claeskens06a}{C06}
 
-%--------------------------------------------------------------------------
-%                          Observations details
-%--------------------------------------------------------------------------
 \section{Observations} \label{sec:obs}
@@
 at the $\nu_{\rm LO}$\eq139.256\,GHz
-% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
 were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
@@
 is produced by averaging over 3.16\,GHz of line-free bandwidth. This
-yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
+yields an rms noise of 0.082 mJy\,beam$^{-1}$.
 
@@
 The correlator setup provides a bandwidth of 3.75 GHz in
-each sideband and a %native
+each sideband and a
 spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
@@
 
-% poor phase note
-% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
-% rms scatter over ~ 90 klambda
-% max baseline of obs. is 145 m
-%
-% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
-% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
-% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
-% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710 --> 3%
-%
-% amp de-correlation: % loss scales = 1- exp(-(50º*pi/180)^2 / 2) = ~32% loss
 Given that the phase calibrator used for the first track was faint and was
@@
 We thus conservatively estimate
-a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35% add in quad
+a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35
 the gain variations over time, and the phase scatter on the calibrated data. We
@@
 \subsection{VLA (Archival)}
-Our analysis also uses archival data of the 4.885\,GHz %4.88510 GHz
+Our analysis also uses archival data of the 4.885\,GHz
 radio continuum obtained with the
@@
 
-%--------------------------------------------------------------------------
-%                                Results
-%--------------------------------------------------------------------------
 \section{Results} \label{sec:results}
@@
 179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
-$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/
+$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
+\includegraphics[width=0.45\textwidth]{f1.eps}
 \caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of
@@
 \vspace{.2em}
-% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
-% - sigma = 0.305 Jy km/s/Beam
-%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
 We construct a zeroth order moment map, red/blue channel maps, and
@@
 \hspace{0.5em}
-% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
-% 126-144 (Red)
-% ~ delta V ~410 km/s
-% from [409, 0] km/s
-%  144-160 (Blue)
-% ~ 365 km/s
-% [-324.88, 0] km/s
-\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
-\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
+\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{f2a.eps}
+\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{f2b.eps}
 \\
-\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
+\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{f2c.eps}
 \vspace{0.1em}
@@
 with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
-% see DANNERBAUER09 intro
-% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.
 
 \begin{figure}[!htbp]
-%\centering
-\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
+\includegraphics[width=0.455\textwidth]{f3.eps}
 \caption{CARMA \cco line profile (solid) without continuum subtraction is
@@
 is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
-% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
-% assumes that the foreground galaxy is a point source, the...
 
 \begin{figure}[!htbp]
-%\centering
-\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
-\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
+\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{f4a.eps}
+\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{f4b.eps}
 \caption{Top: overlay of the 2\,mm continuum emission on the optical image.
@@
 
-\subsection{Photometry} \label{sec:photometry} %DONE
+\subsection{Photometry} \label{sec:photometry}
 We compile \mir (MIR) to \fir broadband photometry from various
@@
 simulations, each of 500 iterations.
-% We note that the IRAC photometry includes
-% emission from old stellar populations and is prone to
-% dust extinction. Hence, the decomposed fluxes are only
-% our best estimate of the warm dust emission.
 We incorporate the decomposed 24\,$\micron$ data in our
@@
 
-\input{table_photometry_AAScustomized}
-
-%--------------------------------------------------------------------------
-%                                Analysis
-%--------------------------------------------------------------------------
+\begin{deluxetable}{lccc}[!htbp]
+\centering
+\tabletypesize{\scriptsize}
+\tablecolumns{4}
+\tablecaption{Photometry data}
+\tablehead{\colhead{Wavelength} & \colhead{Frequency} & \colhead{Flux Density} & \colhead{Instrument}\\
+\colhead{($\micron$)} & \colhead{(GHz)} & \colhead{(mJy)} & \colhead{ } \vspace{0.05in}
+\\  \cline{1-4} \vspace{-0.05in} \\
+\multicolumn{4}{c}{Combined/Unresolved}
+}
+\startdata
+1.25    & 239834  & 1.009 $\pm$ 0.09    & CTIO/J-Band \\
+1.65    & 181692  & 1.448 $\pm$ 0.12    & CTIO/H-Band \\
+2.17    & 138153  & 2.064 $\pm$ 0.16    & CTIO/Ks-Band \\
+3.4     & 88174.2 & 7.027 $\pm$ 0.14    & {\it WISE}/W1 \\
+3.6     & 83275.7 & 5.618 $\pm$ 0.0021  & {\em Spitzer}/IRAC \\
+4.5     & 66620.5 & 7.803 $\pm$ 0.0021  & {\em Spitzer}/IRAC \\
+4.6     & 65172.3 & 8.872 $\pm$ 0.16    & {\it WISE}/W2 \\
+5.8     & 51688.4 & 10.720 $\pm$ 0.0051 & {\it Spitzer}/IRAC \\
+8.0     & 37474.1 & 14.470 $\pm$ 0.0041 & {\it Spitzer}/IRAC \\
+12      & 24982.7 & 21.960 $\pm$ 0.42   & {\it WISE}/W3 \\
+12      & 24982.7 & $<$400              & {\it IRAS} \\
+22      & 13626.9 & 55.110 $\pm$ 1.9    & {\it WISE}/W4 \\
+24      & 12491.4 & 70.204 $\pm$ 0.026  & {\it Spitzer}/MIPS \\
+25      & 11991.7 & $<$ 500             & {\it IRAS} \\
+60      & 4996.54 & $<$ 600             & {\it IRAS} \\
+100     & 2997.92 & $<$ 1000            & {\it IRAS} \\
+250     & 1199.17 & 289.4 $\pm$ 9.6     & {\it Herschel}/SPIRE \\
+350     & 856.55  & 168.2 $\pm$ 8.6     & {\it Herschel}/SPIRE \\
+500     & 599.585 & 56.8 $\pm$ 8.8      & {\it Herschel}/SPIRE \\
+1387.93 & 216     & $<$2.492            & CARMA \\
+2152.82 & 139.256 & 1.230 $\pm$ 0.220   & PdBI \\
+\cutinhead{Foreground Lensing Galaxy (deblended bands)} \\ [-1.5ex]
+0.555   & 540167  & 0.056 $\pm$ 0.006   & {\it HST}-ACS/V-Band \\
+0.814   & 368295  & 0.238 $\pm$ 0.013   & {\it HST}-ACS/I-Band \\
+1.6     & 187370  & 0.539 $\pm$ 0.041   & {\it HST}-NICMOS(NIC2)/H-Band \\
+3.6     & 83275.7 & 0.585 $\pm$ 0.003\tna   & {\em Spitzer}/IRAC \\
+4.5     & 66620.5 & 1.794 $\pm$ 0.0027\tna  & {\em Spitzer}/IRAC \\
+5.8     & 51688.4 & 3.163 $\pm$ 0.0059\tna  & {\it Spitzer}/IRAC \\
+8.0     & 37474.1 & 4.589 $\pm$ 0.0057\tna  & {\it Spitzer}/IRAC \\
+2152.82 & 139.256 & 0.799 $\pm$ 0.082   & PdBI \\
+61414   & 4.8815  & 0.866 $\pm$ 0.027   & VLA \\
+\cutinhead{Background Galaxy RXJ1131 (deblended bands)}
+0.555   & 540167  & 0.009 $\pm$ 0.0041\tnb  & {\it HST}-ACS/V-Band \\
+0.814   & 368295  & 0.041 $\pm$ 0.0054\tnb  & {\it HST}-ACS/I-Band \\
+1.6     & 187370  & 0.133 $\pm$ 0.004\tnb   & {\it HST}-NICMOS(NIC2)/H-Band \\
+3.6     & 83275.7 & 5.034 $\pm$ 0.0021  & {\em Spitzer}/IRAC \\
+4.5     & 66620.5 & 6.009 $\pm$ 0.0017  & {\em Spitzer}/IRAC \\
+5.8     & 51688.4 & 7.557 $\pm$ 0.003   & {\it Spitzer}/IRAC \\
+8.0     & 37474.1 & 9.881 $\pm$ 0.0039  & {\it Spitzer}/IRAC\\
+2152.82 & 139.256 & 0.400 $\pm$ 0.082\tnc   & PdBI \\
+61414   & 4.8815  & 1.273 $\pm$ 0.042   & VLA
+\enddata
+\label{tab:photometry}
+\tablecomments{The IRAC photometry for channel 1 (3.6\,$\micron$) is extracted directly from the image and
+from the Spitzer Heritage Archive for channels 2$-$4 (4.5, 5.8, and 8.0\,$\micron$). All upper limits are 3$\sigma$.}
+\tablenotetext{a}{Flux obtained using aperture photometry after subtracting the emission of RXJ1131 from the total emission.}
+\tablenotetext{b}{A contribution from the quasar has been removed (see C06), and thus the flux density corresponds to the host galaxy only.}
+\tablenotetext{c}{Flux extracted from the residual map after subtracting a point-source model.}
+\tablerefs{The {\it HST} photometry is adopted from C06.}
+\end{deluxetable}
+
 \section{Analysis} \label{sec:anal}
-%\subsection{Stellar Mass and BH-Bulge Mass Correlation}
-%Rest-frame $K$-band (NIR) photometry has been proposed as a reliable proxy to
-%the underlying total stellar mass. Using the decomposed IRAC photometry at 3.6$\micron$ (rest-frame $K$-band),
-%we find a stellar mass of BLAH, using the BLAH.
-%This implies a $M_{\rm BH}$$/$$M^*$ = BLAH (cf. $\sim$0.1\% found in local galaxies).
-%
-%The AGN-starburst connection has become a central issue with the discovery of the relation
-%between stellar velocity dispersion and mass of the central black hole in spheroidal stellar
-%systems (Magorrian et al. 1998, Ferrarese & Merritt 2000, Gebhardt et al. 2000). Given that
-%elliptical galaxies are mainly old, this relation has to be put in place at their formation history.
-%
-%This implies that RXJ1131 is in the BLAH stage of the evolution, in which the BH ?.
 
@@
 spatial scales smaller than the beam (see \Fig{CO21mom}).
-Hence, we reconstruct the intrinsic gas dynamics  % - morphology of different kinematic components - velocity structure
+Hence, we reconstruct the intrinsic gas dynamics
 by carrying out a parametric lens modeling over different
@@
 \begin{figure}[!htbp]
-\includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
+\includegraphics[width=0.45\textwidth]{f5.eps}
 \caption{The full resolution \bco spectrum (yellow histogram) and
@@
 median and the 68\% confidence intervals in the marginal PDFs.
-\input{table_medianLens}
+\begin{deluxetable}{lcc}[!htbp]
+\tabletypesize{\scriptsize}
+\tablecolumns{3}
+\tablecaption{Lens parameters constrained by models of seven velocity channels}
+\tablehead{
+\multicolumn{2}{c}{Parameters} &
+\colhead{Median values} % weighted-mean of median of each
+}
+\startdata
+Offset in RA    & (\arcsec)   &  0.004$\pm$0.027\\
+Offset in Dec    & (\arcsec)   & 0.003$\pm$0.027\\
+Axial Ratio      &             & 0.56$\pm$0.16\\
+Position Angle   & (deg)       & 103$\pm$22\\
+Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002
+\enddata
+\label{tab:lens}
+\tablecomments{Parameters describing the foreground lens are
+obtained based on the median in the preliminary models (see text for details).
+All angular offsets are with respect to
+$\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
+$\delta$\,=\,$-$12\degr31\arcmin58\farcs3 (J2000).}
+\end{deluxetable}
 
@@
 
-% the companion
 A better fit is found for the lens model of
@@
 a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun.
-%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
 For the molecular gas mass in RXJ1131, we derive
@@
 \begin{tabular}{c}
-\includegraphics[trim=0 0 0 0, clip, width=1.0\textwidth]{../Figures/PostageStampModel.eps} \\
-\includegraphics[width=0.98\textwidth]{../Figures/PostageStampResiduals.eps}
+\includegraphics[trim=0 0 0 0, clip, width=1.0\textwidth]{f6a.eps} \\
+\includegraphics[width=0.98\textwidth]{f6b.eps}
 \end{tabular}
@@
 where $n$ is a positive integer.
-The beam of the PdBI observations is shown in the bottom right corner. % of each panel.
+The beam of the PdBI observations is shown in the bottom right corner.
 The reconstructed source-plane positions, as represented by the magenta ellipses, demonstrate an intrinsic velocity gradient of the \bco emission in RXJ1131.
@@
 is suggestive of an extended CO emitting region.
-%% spatial offset between AGN and the host
-%In the channel maps in \Fig{CO21mom} and
-%\Fig{chanmap}, the line center of the CO gas is not co-spatial with the optical quasar --- the point-like images along the lensing arc are
-%offset to the NW of the CO line center emission.
 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
+\includegraphics[width=1.0\textwidth]{f7.eps}
 \caption{
@@
 \centering
-\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
+\includegraphics[width=0.9\textwidth]{f8.eps}
 \caption{
@@
 
-\input{table_magFactor}
+\begin{deluxetable}{lcc}[!htbp]
+\tabletypesize{\scriptsize}
+\tablecolumns{3}
+\tablecaption{Magnification factors of various kinematic components in \bco}
+\tablehead{
+\colhead{Velocity Range (\kms)} & % see 22May16/intensity30Apr16.spec; or channel map in paper
+\colhead{Source 1 $\mu_{\rm L}$} &
+\colhead{Source 2 $\mu_{\rm L}$}
+}
+\startdata
+-366\,$-$\,-258 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
+-237\,$-$\,-151 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
+-129\,$-$\,-43  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
+-21.5\,$-$\,65    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
+86\,$-$\,172        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
+194\,$-$\,280       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
+301\,$-$\,388       & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ [0.5ex]
+weighted average & 4.4 & \\ [0.5ex]
+median & 5.5 &
+\enddata
+\label{tab:model}
+\tablecomments{Velocity is taken from the center of each (native) channel
+without any binning. Each row corresponds to a channel slice used for
+lens modeling. Source 1 is RXJ1131 and source 2 is its companion. }
+\end{deluxetable}
 
@@
 velocity gradient in our lens model (\Fig{model} and \Fig{PV}).
-% The difference in magnification factors between CO and optical-to-NIR
-% may further indicate that the CO emitting region is more extended and/or
-% has a spatial offset from the optical-to-NIR emission
-% (\ie different positions and alignment relative to the caustics) given
-% the lower magnification factor found for CO (median $\mu_{\rm L}$ = 5.5)
-% than in NIR, while their spatial extents appear to be similar. But then it could just be because of the low resolution and
-% the degeneracy between the intrinsic source size and the magnification factor.
 
@@
 In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
-Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$. % beam smearing --> not resolving velocity info. within the beam
+Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.
 
@@
 \centering
-\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{../Figures/veloGradient_markers}
-\includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
+\includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{f9a.pdf}
+\includegraphics[width=0.525\textwidth]{f9b.eps}
 \caption{Left: Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
@@
 terminology), since this corresponds to the radius at which the velocity
-of a pure exponential disk peaks \citep{Courteau97b}. % \ie commonly use Vmax (taken at R2.2) as V_rot
+of a pure exponential disk peaks \citep{Courteau97b}.
 Here, we adopt the maximum {\em observed} velocity
-$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
+$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
 dynamical center as a proxy to the rotation velocity.
@@
 $($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
-Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
+Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),
 we find a dynamical mass of
@@
 \bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun. %calc. using 2.32e5*6.22 * 200^2
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
 We derive an inclination angle of 56.4$\degr$ from the
@@
 de-lensed line profile of the companion and a
-half-light radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from the best-fit lens model,  % redmost channel
+half-light radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from the best-fit lens model,
 we find a dynamical mass of
@@
 On the other hand,
-% we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
 we find $M_{\rm dyn}$\,$\sin^2 30\degr$\,=\,5.8\E{8}\,\Msun
@@
 We thus classify the system as a {\em gas-rich,``wet'' minor merger}.
-
-%%% using disk model, should use FWHM of single Gauss fit then (Fu+13)
-%Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
-% \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as
-%$v_{\rm FWHM}$, we find a dynamical mass of
-%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
-%within the CO-emitting region.
-%If we instead consider the
-%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
-%To correct for the inclination effect, we
-%infer an inclination angle of 56.4$\degr$ using
-%the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25)
-%from the reconstructed image (Figure~3 in \citetalias{Claeskens06a}). This inclination angle
-%is consistent with the
-%observed unobscured AGN and an observable double peak line profile.
-%The dynamical mass is then
-%1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
-%% the systematic uncertainty on the inclination angle may cause this estimate to differ by
-%% a factor of $\sim$2.
-%Our estimate is likely a lower limit given the presence of a companion. In a merger model,
-%the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
 
@@
 response curves to perform color correction.
-% Previous studies find that in the absence of mid-IR data, a powerlaw slope
-% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
-%
-%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
-%uncertainties for the PdBI continuum in our fitting procedure.
 The model is described by five free parameters: the rest-frame characteristic dust
@@
 taken for the burn-in phase (which are then discarded).
-Here we report the statistical means % modes in log file
-% summary statistics (global mode (where min. chi),
-% marginal mode (in log file), posterior median (instead of posterior means;
-% need to compute)
+Here we report the statistical means
 and the 1$\sigma$ confidence interval in the marginal PDFs
@@
 
-\input{table_mbb}
+\begin{deluxetable}{lccc}[!htbp]
+\tabletypesize{\scriptsize}
+\tablecolumns{4}
+\tablecaption{SED fitting results}
+\tablehead{
+\multicolumn{2}{c}{Parameters}      &
+\colhead{With 24\micron} &
+\colhead{Without 24\micron}
+}
+\startdata
+$T_d$                           & (K)                & 52.0\petm{4.0}{4.1}   & 58.2\petm{14.5}{14.4}  \\ [1.05ex]
+$\beta$                         &                    & 1.8\petm{0.5}{0.6}    & 2.1\petm{0.3}{0.3}  \\ [1.05ex]
+$\alpha$                        &                    & 1.6\petm{0.5}{0.5}    & 8.9\petm{6.9}{6.3}   \\ [1.05ex]
+$\lambda_0$\tna                 & ($\micron$)        & 548\petm{285}{307}    & 367\petm{125}{145}  \\ [1.05ex]
+$\lambda_{\rm peak}$\tnb        & ($\micron$)        & 162\petm{16}{30}      & 146\petm{39}{44}  \\ [1.05ex]
+$f_{\rm norm,\ 500\micron}$\tnc & (mJy)              & 59\petm{14}{13} & 60\petm{5}{5} \\ [1.05ex]
+\LFIR\tnd                       & (10$^{12}$\,\Lsun) & 3.81\petm{2.04}{1.92} & 4.72\petm{2.54}{2.26}      \\ [1.05ex]
+$M_{\rm d}$\tne                 & (10$^8$\,\Msun)    & 22\petm{5}{18}        & 11\petm{5}{6}
+\enddata
+\label{tab:SED}
+\tablenotetext{a}{Observed-frame wavelength where $\tau_\nu$\,=\,1}
+\tablenotetext{b}{Observed-frame wavelength of the SED peak}
+\tablenotetext{c}{Observed-frame flux density at 500 $\micron$}
+\tablenotetext{d}{Rest-frame 42.5$-$122.5\,$\micron$ luminosity}
+\tablenotetext{e}{Derived assuming an absorption mass coefficient of $\kappa$\eq2.64\,m$^2$\,kg$^{-1}$ at $\lambda$\,=\,125.0\,$\micron$ \citep{Dunne03a}}
+\tablecomments{Errors reported here are $\pm$1$\sigma$.
+\LFIR and $M_{\rm d}$ are not corrected for lensing.}
+\end{deluxetable}
+
 In the first model, we attempt to constrain the power-law index by including
@@
 in the AGN host galaxy.
-% since the fit include contribution from the AGN (through power-law to MIR)
 If we instead fit for a model excluding this constraint,
@@
 We derive the stellar mass of RXJ1131 by
-fitting SED models to the rest-frame UV-to-mm photometry   % original version: UV to IR; high-z UV to radio
+fitting SED models to the rest-frame UV-to-mm photometry
 using the high-$z$ version of the {\sc magphys} code \citep{Magphys08a,Magphys15a}.
@@
 The consistency may be attributed to the large uncertainties arising from the lack of photometric constraints on the models and the fact that the best-fit parameters from the MBB method are similar to those of the \ncode{magphys} method.
-%  Mdust 8.427   8.522   8.617
-% Ldust  1.191E+001  1.204E+001  1.219E+001; but from 3-1000 \micron; should compare with our \LIR.
-%
-% Salpeter M* ~ 1.8 * Chabrier
-% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up'' time (aka mass-doubling timescale) of $M^*$$/$SFR\eq sSFR\pmOne\ssim440 Myr for RXJ1131.
-
-% -------
-% WISE flux is slightly higher than the IRAC point, probably due to a smaller
-% aperture used in IRAC extraction (both from archive).
+
 \begin{figure}[!htbp]
 \centering
-\includegraphics[trim=5 5 5 5, clip, width=0.445\textwidth]{../Figures/FullSED_withMagphys}
+\includegraphics[trim=5 5 5 5, clip, width=0.445\textwidth]{f10.pdf}
 \caption{SEDs of RXJ1131 at
@@
 
-%--------------------------------------------------------------------------
-%                                Discussion
-%--------------------------------------------------------------------------
 \section{Discussion} \label{sec:diss}
@@
 local ULIRGs \citepalias[median: 300\pmm85\,\kms, with the largest being 480\,\kms;][]{Solomon97a}.
-%ULIRGs (z < 0.3) studied in CO(1-0) by Solomon97a: ~1/3 of them have double-peaked or flat-topped spectrum. But their linewidths are based on single Gauss fit.
 Linewidths exceeding 500\,\kms are also commonly observed in
 high-$z$ starburst galaxies  \citepalias[e.g.,][]{Greve05a}
-% \citep[780\pmm320\,\kms; \eg][hereafter G05]{Greve05a}
 and high-$z$ quasar host galaxies \citep[e.g.,][]{Coppin08a},
-% \citep[550\pmm180\,\kms; \eg][]{Coppin08a},
 which are believed to originate from mergers.
@@
 extended than the average of 3.5\pmm2.3\,kpc in a sample of disk-like U/LIRGs studied by
-\citet[]{Ueda14a}, % who find an average radius of 3.5\pmm2.3\,kpc
+\citet[]{Ueda14a},
 but consistent with their range of 1.1\,$-$\,9.3\,kpc.
@@
 local U/LIRGs in the \citet{Gao99a} sample ($R\lesssim$10\,kpc).
-%For instance, extended molecular disks are often associated with advanced mergers
-%\citep[\citetalias{Downes98a};][]{Gao99a}.but see also U14 for outliers
-% with extended molecular gas in merger remnants
 
@@
 
-% ------------- gas fraction --------------
-% Locally, the baryonic gas fraction for giant disks is ~7-10% (Leroy et al. 2008, Saintonge et al. 2011a), while
-% at z~1.2 it increases to 34±5% and at z~2.3 to 44±6% (Tacconi
-% et al. 2010, Daddi et al. 2010).
 We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq19\pmm5\%
-% , where the uncertainty is based on that of the gas mass.
 and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\eq32\petm{7}{12}\% for RXJ1131.
-% The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
 Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
-% On the other hand,
-% the baryonic gas mass fraction ranges from $\sim$10$-$30\% with an average of 0.21\pmm0.03 in normal ``star-forming'' galaxies at $z$\ssim0.4 \citep{Geach11a}, and $\sim$5 at $z$\ssim0 \citep{Saintonge11a}.
 and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
@@
 \alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
-Both the dynamical and baryonic gas mass fractions of RXJ1131 are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
+Both the dynamical and baryonic gas mass fractions of RXJ1131 are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2
 which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gas to dust ratio:
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Solomon+97: GDR ~ 100
-% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
-% our galaxy MW ~150 (Draine+07)
-% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
-% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Using the lensing-corrected dust mass, we find a galactic-scale %galaxy-wide
+
+Using the lensing-corrected dust mass, we find a galactic-scale
 gas-to-dust ratio (GDR) of
@@
 Our ratio is also consistent with high-$z$ SMGs
-% \citep[78\pmm26;][]{Bothwell13a}
 \citep[]{Bothwell13a} and
@@
 we assumed sub-thermal excitation between \bco and \aco emission.
-% but this may be a minor effect as CO emission in local ULIRGs is typically thermalized up to $J$ = 3 or 4 \citep{,CW13}.
 We also note that the gas-to-dust ratio derived for RXJ1131 may be biased low as the gas is likely to
@@
 \subsubsection{Star Formation Efficiency and specific SFR}
-% SFE:
-% in terms of LFIR/Mgas:
-% high-z: $>$100
-% Greve+05: 450 +/- 170 Lsun/Msun for SMG
-% Solomon97a: 180 +/- 160 Lsun/Msun
-% SV05: local (z<0.1 spirals) of SFE < 100
-
-% in terms of LFIR/L'CO:
-% Greve+05: SMG 360 +/- 140 Lsun (K km/s pc^2)^-1
-% Solomon97a: LFIR/L'CO = 160
-% Daddi+10:  We find that the average SFE (in units of L?
-K?1 km?1 s pc?2) of BzK galaxies is 84\pmm12, that of SMGs is 390\pmm60, for QSOs we find 590\pmm100, for local ULIRGs we have 250\pmm30, and local spirals have 48\pmm7.
-Therefore, the typical BzK galaxy has about 80\% higher SFE of that of a local spiral, but individual values are well within the range measured for local spirals even though BzKs are a hundred times more luminous.
-Local ULIRGs have SFEs that are three times larger on average than BzK galaxies.
+
 To first order, the star formation efficiency
@@
 in \citetalias{Combes13a} for the far-IR luminosity,
-we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$, % I believe here we are taking the gas mass of both into account since we we couldn't separate out the LIR
+we find an SFE of 58\pmm10 \Lsun $M_{\odot}^{-1}$,
 which is on the low end among other U/LIRGs at $z$\,$<$\,0.6
-% \citep[$\sim$180\pmm160 \Lsun $M_{\odot}^{-1}$;][]{Solomon97a, Combes11a}
 \citep[\citetalias{Solomon97a};][]{Combes11a} but consistent with those of
@@
 This is in agreement with its disk-like kinematic signatures and its extended molecular gas distribution.
-% Depletion time:
-% Greve+05: ~40 Myr
 Assuming the \SF continues at the current rate without gas replenishment,
@@
 
-%
-% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
-% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
 The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
@@
 the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
-%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
 Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
@@
 
-% ================================================
-%local ULIRGs are in the majority starbursts caused by
-%galaxy major mergers (e.g. Sanders & Mirabel 1996, Veilleux
-%et al. 2009). The overall gas fraction in those systems is not high,
-%and they are expected to sustain such a high rate of star formation
-%for only a short duration, on the order of 100Myr. The depletion
-%time scale of massive star-forming galaxies, with a high gas
-%fraction but low star formation efficiency (SFE), is on the other
-%hand on the order of one Gyr or more (Leroy et al. 2008, Bigiel
-%et al. 2008). These galaxies are dubbed as falling on the ?main
-%sequence? of star-forming galaxies (Noeske
-%et al. 2007), or in a ?normal? star formation phase.
-% =================================================
-
-%====================================================================
-%While the \alphaco conversion factor is commonly assumed to be 0.8\,\alphaU for
-%for ULIRGs/starbursts, its numerical value depends on the ISM environment
-% \citep[\eg][]{Narayanan11a}.
-% For instance, it could be different in a
-% dynamically turbulent galaxy, where the gas is warmer, more excited,
-% and denser, than in a quiescent galaxy.
-% In addition, the physical basis for deriving the gas mass from the CO luminosity is
-% by assuming the ISM only consists of virialized, non-overlapping gas clouds,
-% which is often not true in ULIRGs \citep[][\citetalias{Solomon97, Downes98a}]{Downes93a}.
-% % the CO emitting gas in the centers of ULIRGs is unlikely to be virialized, but instead bound by the potential of the galaxy or from molecular gas in pressure equilibrium rather than gravitational equilibrium.
-
-% % DS98: lower alphaCO for objects with extended surface gas densities, where gas temperature and velocity dispersion are higher; Mgas derived from radiative transfer model instead of using standard conversion factor, which yields the \alphaco = 0.8 UNIT for local ULIRGs.
-% % Also see Scoville+97
-
- %As discussed in Solomon \& Vanden
- %Bout (2005), low-$z$ studies of ULIRGs have led to the
- %suggestion that the conversion factor could be several times
- %smaller (Downes et al. 1993; Bryant \& Scoville 1999, DS98). This can
- %arise in ULIRGs if the gas is concentrated in the nuclear
- %regions (as a result of dissipative galaxy merging) and the
- %molecular emission linewidths can be broadened by the galactic
- %dynamics associated with the stellar mass, not just the self-gravitating
- %gas mass as in individual GMCs in which the
- %standard conversion factor was derived. In addition, the mean
- %gas temperature and density may be different in the ULIRG
- %nuclei as a result of the intense star formation activity and since AlphaCO
- %should vary as density and temperature e.g. (Dickman et al. 1986).
- % Also should be a continuous distribution instead of a bimodal value (Narayanan+12).
- % Yet, from numerical models, it is found that mergers have lower alphaCO than
- % disk galaxies, thus we can derive an upper limit on the gas mass in the RXJ1131 merger system using a disk alphaCO factor.
-% In a minor merger, the rise in gas temperatures and velocity dispersions are not as extreme as in major mergers.
-Hence, the rise in velocity-integrated CO intensity is not as large, and the X-factor (and thus alphaco) does not decrease as much {Narayana11a}.
-
-%====================================================================
-
 \subsection{Fate of RXS J1131$-$1231}
-%Results from theoretical simulations have suggested that
-%the disk component of a gas-rich progenitor galaxy can
-%survive merging if it has a low star formation efficiency, which in turn
-%reduces the gravitational torque available to
-%remove the angular momentum of the gas, thereby allowing
-%a higher gas fraction to be retained and redistributed over a large extent in
-%the merged galaxy \citep{Hopkins09a}. In this scenario, it is plausible that RXJ1131
-%will retain its a disk component upon merging
-%with a small bulge component
-%given its low SFE and the extended disk.
-%%since there is little/no significant stellar material % (collisionless)
-%%available to torque away the cold gas in the disc, thus little/no angular momentum is lost,
-%%and gas will rapidly reform a cold disc in the background
-%%of the relaxing stellar potential.
-%% --> suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
-%% the final product will have a low bulge mass fraction.
-%%
-%%i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large).
-%% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
 Given that the host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger
@@
 
-% (bulge dominated; Springel05a, Robertson06a)
-% and disc with low B/D ratio ($\sim$0.1$-$0.2; Hopkins09a).
-%
-%In systems that are sufficiently gas-rich, it is possible to
-%suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
-%since there is little/no significant stellar material % (collisionless)
-%available to torque away the cold gas in the disc, thus little/no angular momentum is lost,
-%and gas will rapidly reform a cold disc in the background
-%of the relaxing stellar potential.
-%Gas, being collisional, cannot violently relax, but must
-%have its angular momentum torqued away in order to dissipate and
-%build a bulge by forming stars in a central starburst
-%(\ie gas loses angular momentum to stars in the
-%perturbed disk and fall toward center).
-% In a merger,
-%this torque is primarily internal, from stars in the same disc: the
-%passages and merger of the secondary induce a non-axisymmetric
-%distortion in the primary stellar and gas disc. The stellar distortion
-%(in a trailing resonance and close proximity to the gas response)
-%efficiently removes angular momentum from the gas and allows it
-%to fall to the center and form a bulge  (see also Barnes \& Hernquist
-% 1996).
-% A bulge will form because cold gas with no angular momentum
-% will be largely unable to form any sort of disk, and that a galaxy?s
-% worth of gas compressed to high densities and small
-% radii will inevitably form a large mass in stars).
-%
-% unlikely RXJ1131 will evolve into present-day massive
-% ellipticals (M$\gtrsim$1\E{12}\,\Msun),
-% gas-poor mergers: --> present-day massive elliticals
-% (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
-
 \subsection{Velocity Offset and a Recoiling Black Hole}
-%Outflow:
-% Not AGN outflows because require different velocity offsets in Balmer and forbidden lines (Zamanov02a)
-% line origins:
-% \mgii & Hbeta: outer part of the BLR (Goad12a) compared to high-ionization lines (\eg CIV)
-% Hbeta can also come from NLR
 
@@
 offsets as large as $\sim$\,500\,\kms have been observed in some cases.
-%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
-%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
 
@@
 BLR and the NLR may arise in a recoiling black hole (BH),
-% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines (e.g., Gaskell 1983; Bonning et al.
-2007; Eracleous et al.
-2012; Ju et al.
-2013; Shen et al.
-2013).
 where its BLR is moving at high velocity relative to the bulk of its host galaxy
@@
 
-%--------------------------------------------------------------------------
-%                                Conclusions
-%--------------------------------------------------------------------------
 \section{Summary and Conclusions} \label{sec:sum}
@@
 \citepalias{Claeskens06a,Brewer08a}.
-%The source-plane positions form a symmetric velocity field,
-% which is consistent with a kinematically-ordered disk galaxy.
 The magnification factor inferred for the CO emission in RXJ1131 is found to
@@
 Using the source-plane \bco size of $R$\ssim6\,kpc, we find a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun for RXJ1131.
-%  and $\sim$(4)\E{9}\,\Msun for the companion.
 The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim19\% and baryonic gas mass fraction of
@@
 gravitational torques provided by stellar components is reduced in such a system \citep{Springel05a, Robertson06a, Hopkins09a}.
-% and the gas rapidly reform a cold disc in the background.
 As such, the extended gas disk of RXJ1131 together with its low SFE may indicate
@@
 would also explain the high spin parameter reported by \citet{Reis14a}.
-% This model requires a merged BH, this interpretation would imply that RXJ1131 was
-% in a previous merger.  %, which would also explain the highly spinning black hole.
-%Given the presence of the companion in the current data, RXJ1131 may be in
-%its subsequent stages of minor merging from a previous major merger, as commonly predicted in simulations.
 
@@
 The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
- %the ratio is larger at high z than the present day, implying evolution in the Mbh?Msph relation
-
-%==============================================================================
-%                                Back matters
-%==============================================================================
-% ACKNOWLEDGEMENTS
-%-----------------
+
 \acknowledgments
@@
 
-  %--------------------------------------------------------------------------
-  %                               Bibliography
-  %--------------------------------------------------------------------------
-\bibliographystyle{yahapj}
-\bibliography{RXJ.bib}
+\input{ms.bbl}
 \end{document}

### 2016-09-08 NOEMA/Proposal16/RXJ.tex
1st draft

%------------------------------------------------------------------------------
% This is a LaTeX template for the scientific justification of IRAM Proposals
%------------------------------------------------------------------------------
%
% You may customize this template to suit your preferences (e.g. using BibTex),
% but please respect the following requirements:
%     The scientific and technical justification should contain a
%     maximum of 2 pages of text (4 pages for Large Programs),
%     plus 2 pages of Figs., Tables and Refs.
%     Don't mix text with figures, tables, and references !!
%     The font size should be 11pt or larger.
%
%------------------------------------------------------------------------------
%
\documentclass[11pt,a4paper,twoside,graphicx,color]{article}
%
\usepackage[margin=2cm]{geometry}
\usepackage{graphics,graphicx}
\usepackage[update,prepend]{epstopdf}
\usepackage[innercaption]{sidecap}
\usepackage{subcaption}
\usepackage{amssymb, amsmath}
\usepackage{xspace}
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros}
\usepackage{wrapfig}
\usepackage{floatrow}

\newcommand{\ncrit}{\mbox{$n_{\rm crit}$}\xspace}
\newcommand{\comol}{$^{12}$CO\xspace}
\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
\newcommand{\mstar}{\mbox{$M^*$}\xspace}
\newcommand{\sfrsd}{\mbox{$\Sigma_{\rm SFR}$}\xspace}
\newcommand{\sfrU}{\mbox{\Msun\,yr$^{-1}$}\xspace}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\J}{$J$}
\newcommand{\aco}{\mbox{CO($J$=1$-$0)}\xspace}
\newcommand{\bco}{\mbox{CO($J$=2$-$1)}\xspace}
\newcommand{\cco}{\mbox{CO($J$=3$-$2)}\xspace}
\newcommand{\dco}{\mbox{CO($J$=4$-$3)}\xspace}
\newcommand{\eco}{\mbox{CO($J$=5$-$4)}\xspace}
\newcommand{\fco}{\mbox{CO($J$=6$-$5)}\xspace}
\newcommand{\gco}{\mbox{CO($J$=7$-$6)}\xspace}
\newcommand{\rot}[3][HCN]{\mbox{#1($J$=#2\rarr#3)}\xspace}
% default HCN; usage \rot[HCN]{3}{2} or \rot[\hcop]{4}{3}
\newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfo
nt{#1}}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\kms}{km\,s$^{-1}$\xspace}
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
\newcommand{\Fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\E}[1]{\mbox{$\times10^{#1}$}}
\newcommand{\eq}{\,=\,}
\newcommand{\ssim}{\,$\sim$\,}
\newcommand{\pmm}{\,$\pm$\,}
\newcommand{\ncode}[1]{{\sc #1}}
\newcommand{\uvmcmcfit}{\ncode{uvmcmcfit}\xspace}

\newcommand{\mulw}{multi-wavelength\xspace}
\newcommand{\SF}{star formation\xspace}
\newcommand{\galpop}{galaxy populations\xspace}
\newcommand{\SB}{starburst\xspace}
\newcommand{\SBs}{starbursts\xspace}
\newcommand{\highz}{high-$z$\xspace}
\newcommand{\athighz}{at high redshift\xspace}
\newcommand{\interz}{intermediate-$z$\xspace}
\newcommand{\atinterz}{at intermediate redshift\xspace}
\newcommand{\obs}{observations\xspace}
\newcommand{\gl}{gravitationally lensed\xspace}
\newcommand{\qh}{quasar host galaxy\xspace}
%%%%%%%%% Compact BIB %%%%%%%%%%
\citestyle{aa}
\bibliographystyle{apj_w_etal_3auth}

\usepackage{paralist}

\renewenvironment{thebibliography}[1]{%
%\section*{\refname}%
%  {\normalsize {\textbf{References:}}}
  \let\par\relax\let\newblock\relax%
  \inparaitem[{[}1{]}]}{\endinparaitem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Page size and text dimensions
% Do not change!
\textheight 260mm
\textwidth 178mm
\oddsidemargin -8mm
\evensidemargin -8mm
\marginparwidth 50pt
\topmargin -22mm
\brokenpenalty=10000
\sloppy
%
%-------------------------------------------------------------------
\begin{document}
%
%
\begin{center}{\huge \bf
%-------------------------------------------------------------------
Sub-arcsecond resolution \cco imaging of a strongly-lensed wet-merger at $z$$\sim$0.65
%-------------------------------------------------------------------
}\end{center}
\centerline{\bf P.I.: T. K. Daisy Leung}

\noindent {\bf Star formation modes and molecular gas dynamics beyond the local universe} \\
\indent Tremendous progress has been made towards our understanding of the \highz
universe over the past two decades \citep[see recent reviews by][]{CW13,Madau14a, Casey14a}. These studies
suggest that the elevated \SF rates (SFRs) and specific SFRs observed in galaxies at
the peak epoch of \SF (1$\lesssim$$z$$\lesssim$3) are
primarily driven by their increased in molecular gas mass fractions and \SF efficiencies (SFE) compared to
local galaxies, and that \SF at this epoch/in these early systems can be grossly categorised into
two dominant modes -- quiescent mode in disc-like galaxies versus starburst mode in submillimetre galaxies (SMGs) and quasar host galaxies \citep[e.g.][]{Sargent12a}. 
% brings up the spatial resolution
The systematically enhanced molecular gas fractions observed in \highz
\galpop implies that their star-forming clumps are expected to be larger in size, and in
more turbulent conditions 
%due to gravitational instability
compared to nearby galaxies.  % Elmegreen & Elmegreen 2005, Bournaud+08
Indeed, recent studies have found gas clumps on the order of kpc scales at $z$=1--2 \citep[e.g.][]{Swinbank12a, Swinbank12b}, providing direct evidence that the
interstellar medium (ISM) dynamics of galaxies evolve as a function of cosmic time. This
highlights the importance of resolving the gas dynamics of galaxies on these scales 
and at various epochs in order to investigate the
mechanisms and physical processes responsible for leading to
the two star-formation modes and for causing the steep decline in the cosmic SFR density since $z$\ssim1.5 \citep[e.g.][]{Lagos11a,Popping12a}.

% how it's been proposed to connect to local
While studies using spatially resolved CO \obs in
local ultra-luminous IR galaxies (ULIRGs) and their \highz analogues ($z$$\gtrsim$1 \SB systems)
have enabled a better understanding of the gas properties of mergers at these epochs \citep[e.g.][]{Engel10a,Bothwell10a},
% kinematical and dynamical evidence that massive \highz \SB galaxies are formed in major mergers
% distinct kinematic components and disturbed gas morphologies
% that are likely the progenitors of local massive ellipticals 
the gas properties such as excitation, distribution, and dynamics of mergers 
\atinterz (0.6\,$\lesssim$\,$z$\,$\lesssim$\,1) remain largely unknown
due to the lack of spatially resolved CO observations at these redshifts.
Thus, to understand of the role of mergers throughout the cosmic history and
to obtain a coherent picture connecting \highz \galpop to present-day galaxies, 
it is vital to carry out detailed studies of the gas kinematics and dynamics at intermediate-$z$.

We here propose to observe the \cco line emission in a strongly-lensed quasar host galaxy of a merger system at $z$\ssim0.65 using the {\bf A+C array configuration}.
By combining the magnification provided by gravitational lensing with the improved spatial resolution and sensitivity of NOEMA, 
the proposed \obs at an angular resolution ($\sim$0.6'') 
corresponding to a physical scale of $\sim$1.8\,kpc at the target redshift
will allow us to study the internal gas dynamics and distribution 
down to the physical scales of \highz star-forming clumps in a total of {\bf 3.2 hours including overheads}.
We have already detected the \bco and \cco lines at high significance with the PdBI/NOEMA and 
the CARMA, respectively (Leung, Riechers \& Pavesi, submitted; hereafter Leung et al. 2016), and thus this is a low risk project.
Since our target is currently the only source with spatially resolved CO
imaging at intermediate redshift with existing \mulw analysis spanning rest-frame
UV-to-radio, obtaining the proposed \obs will enable, for the first time, a kpc-scale characterization of the gas, dust, and stellar populations of different ages in a quasar host galaxy and merger at intermediate redshift.
\vspace{0.5em}

\noindent {\bf Unique Nature of our target RXJ\,1131$-$1231}\\
\indent Our target RXJ\,1131$-$1231 (hereafter RX1131) is a quadruply-imaged optical quasar with its host galaxy being lensed
into a partial Einstein ring (\Fig{HST}; \citealt{Sluse03a}).
HST observations (rest-frame UV) have revealed distinct emission
from recent star-formation (lensing arcs) and from the AGN (bright knots) in the background galaxy,
demonstrating the great potential for probing its
ISM conditions in detail. Lens modelling of an optical image has identified
seven distinct structures in the source plane and a companion galaxy of
size $\sim$700 pc across, at $\sim$2.4 kpc away from the AGN host galaxy \citep{Brewer08a}.
We have recently confirmed that both galaxies are at the same rmedshift by detecting their
\rot[CO]{2}{1} emission and decomposing their gas distribution
via our $uv$-plane lens modeling in the velocity-space (Leung et al. 2016; see \Fig{combine}f).
The lensing-corrected IR luminosity of 1.5\E{12}\,\Lsun implies that RXJ1131 can also be classified 
as a ULIRG.

\vspace{0.5em}
\noindent {\bf Proposed Observations and Science Goals} \\
\indent The intrinsically symmetric double-horned line
profile (\Fig{combine}g) of RXJ1131 and its source-plane velocity gradient
(\Fig{velo}) extending $\gtrsim$6\,kpc in radius reconstructed from 
dynamical lens modeling of our \bco data suggest that it is a disc galaxy.
At the resolution of our \bco data, the disc-like kinematics and 
galaxy-scale \SF properties 
resembling those of \highz massive disc galaxies \citep{Daddi10a} suggest that 
the \SF modes of \interz mergers are already different than the local ones. 
Since recent studies also find that \highz discs are more clumpy and dynamically unstable compared to local discs, 
studying the molecular gas in RXJ1131 on the scales of its star-forming clumps
would enable us to gain insights into how \SF in massive disc galaxies differ since the peak epoch of \SF.

At the resolution of our \bco data, we find 
disturbed gas morphologies with an unusually high velocity dispersion ($\gtrsim$400\kms near the central region
of RXJ1131; \Fig{combine}e).
%that may be a result of
%perturbations from the AGN,
%or
%internal turbulence due to interactions with the companion/merger-driven, 
%or instability due to the huge gas reservoir/clumpy disc 
Higher resolution imaging, as proposed here, is necessary to infer its true velocity structure and dynamical state 
to distinguish between a rotationally-dominated versus dispersion-dominated system.
We will achieve this by reconstructing the source-plane spatial distribution of the gas and its velocity field, and
deriving the $v$/$\sigma$ ratio (as a proxy to the Toomre Q parameter).
This will allow us to contrast the dynamical properties between mergers and discs galaxies at low and \highz.
% to those of \highz rotating disc, which typically display 
% v/$\sigma$\,$<$\,1 with clumpy morphology or 
% high-z: triggered by fragmentation of dynamically unstable system.
% physical properties
We will also measure spatially resolved line ratios between the \cco and \bco 
emission within RX1131 to gain insight into its gas excitation conditions.
The cold gas distribution, kinematics and line ratio variations will provide clues on
the main driver of \SF in RXJ1131 
 (e.g. if the warmer gas is
concentrated toward the central region of RX1131 like nearby ULIRGs), 
how its interaction with the companion may influence the molecular gas in fueling its ongoing \SF and the central quasar,
and how its gas excitation differs from other \galpop at different cosmic epochs.
In addition, at the proposed resolution, we will be able to obtain a more accurate lens model, enabling us
to resolve the intrinsic velocity gradient at finer details, and thus 
to obtain a better-constrained rotation curve and dynamical mass estimate.
% but we would need a way to reconstruct the dispersion via lens modeling.

% --------------
% final word
Given the unique lensing configuration and nature of our target, the proposed observations 
present an excellent opportunity to investigate the molecular gas excitation
and the kinematical and dynamical 
state of a distant quasar host galaxy of a merging system.
The addition of spatially resolved \cco data will allow 
us to investigate how physical parameters, e.g. stellar mass, dust temperature, SFR, morphology, clumpiness, internal gas dynamics, which have been investigated at both nearby and $z$$\gtrsim$1 galaxies vary \atinterz depending on the molecular gas conditions, providing important constraints for current models of galaxy evolution.

\vspace{.5em}
\noindent {\bf Technical justification} \\
% A+C: ~0.66" at 209 GHz
\indent We estimate the source size of \cco emitting gas in RXJ1131 based on the
most extended kinematic component in our dynamical lens model of our PdBI/NOEMA \bco emission, which takes into account the asymmetric line emission and spatial extent across different velocity bins (arising due to differential lensing).
We therefore expect the source to be resolved over $\sim$10 beams at the proposed angular resolution of $\sim$0.66''.
We compute the expected \cco line strength based on our 
CARMA \cco line flux of $I$\eq35.7\,Jy\,\kms and line FWHM of $\sim$700\,\kms.
To secure enough S/N for lens modelling, 
we require of 10$\sigma$ detection of $\sigma$\eq1.35\,mJy\,beam\pmOne per 100\kms channel.
We note that the requested sensitivity will correspond to S/N$>$10 for channels with spatially less extended emission, which are also found to have lower magnification factors (and thus lower apparent flux density). 
We thus note that the requested sensitivity is conservative but reasonable given that our scientific goals rely heavily on having enough S/N per channel over the entire line profile (especially in the red wing which is spatially more extended).

\clearpage
\section{Supporting material} % don't mix in with text
% You may include up to two pages of figures, tables, and References.

\begin{figure}[!tbhp]
\hspace{-1.75em}
\vspace{-0.35em}
\centering
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.46\textwidth}}]{figure}
[\FBwidth]
{\hspace{-0.5em}
\includegraphics[trim= 10 20 15 0, clip, scale=0.23]{Figures/F555W-eps-converted-to}
\hspace{-2.0em}
\includegraphics[trim= 10 0 0 5, clip, scale=0.33]{Figures/Manipulate_figsCROP}
\vspace{-1.0em}
}
{
\hspace{-1.05em}
\caption{\fontsize{11pt}{12.5pt}\selectfont{\textbf{Stellar light distribution in
the AGN host galaxy RXJ 1131-1231 and its reconstructed source plane morphology.}
{\em Left:} Rest-frame UV emission (tracing recent star formation)
is lensed into an almost complete Einstein ring with diameter $\sim$3.8".
{\em Right:} Lens modeling of the optical emission identifies complex
structures in the host galaxy and
an optically faint companion (white component as indicated by the blue arrows;
\citealt{Claeskens06a}),
which we have recently confirmed by lens-modeling our \bco data
(\Fig{combine}; Leung et al., submitted).
Here, we propose to map the \cco emission in this \interz disc-like quasar host galaxy of a merger system.
}
\label{fig:HST}}
}
\end{figure}

\begin{figure}[!tbhp]
\centering
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.46\textwidth}}]{figure}
[\FBwidth]
{
\includegraphics[trim= 0 0 0 0 clip, scale=0.43]{Figures/veloGradient_markers.pdf}
}
{
\caption{\fontsize{11pt}{12.5pt}\selectfont{\textbf{Image- and source-plane velocity gradient
of the \bco line emission in the AGN host galaxy RXJ1131.}
Source-plane positions reconstructed from the best-fit $uv$-plane lens modeling of 
our PdBI/NOEMA \bco data in the velocity-space
are indicated as color markers atop the observed first moment map. 
At the proposed resolution, we will be able to obtain a more accurate lens model, 
enabling us to resolve the intrinsic velocity gradient at finer details, and obtain a better-constrained rotation curve and dynamical mass estimate for this \interz quasar host galaxy.
}}
\label{fig:velo}}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[trim=0 135 127 0, clip,width=1.0\textwidth]{Figures/combine3}
\caption{ \fontsize{11pt}{12.35pt}\selectfont{\textbf{Recent \bco data from
NOEMA (Leung et al., submitted).}}
{\em (a):}
Asymmetric double-horned line profile observed towards our target.
{\em (b):}
Spectra taken at three locations along the strongest velocity gradient,
demonstrating
differential lensing of the kinematic components of a gas-rich ``disc"
and the wealth of dynamical information that is already available at this resolution.
{\em (c):}
Observed spatial variations across different velocity components due to
differential lensing,
as shown by the red (redshifted),
green (line center), and blue (blueshifted) contours.
{\em (d):}
The observed velocity gradient is suggestive of a disc morphology at the current resolution limit.
The spectrally resolved lensed emission allows us to probe dynamical structures
on smaller spatial scales than otherwise possible.
{\em (e):}
An unusually high velocity gradient ($\gtrsim$400\,\kms) near the center of RXJ1131
may be a result of perturbations from the AGN, 
or internal turbulence due to interactions with the companion, 
or instability due to the huge gas reservoir. 
{\em (f):}
Channel maps of the CO emission (red)
overlaid on our best-fit lens models (grayscale).
The foreground lensing galaxy is represented by a black dot.
The reconstructed source morphology (magenta ellipses) is also suggestive of a
``disc".
{\em (g):}
Full resolution spectrum (yellow; same as panel $a$ but shown in log-scale) and the seven channels (dashed) used for lens modeling.
Using the magnification factors shown above the model channels, we recover an intrinsically symmetric profile (blue).
We here propose to observe \cco line in RXJ1131 at the spatial scales of \highz gas clumps
in order to investigate its molecular gas excitation, kinematical and dynamical state and examine how 
physical properties, e.g. stellar mass, dust temperature, SFR, morphology, clumpiness, internal gas dynamics, 
vary at intermediate redshift depending on the molecular gas conditions.
\label{fig:combine}}
\vspace{-2.15em}
\end{center}
\end{figure}

%%%%%%%%%%%%
\noindent \textbf{References}
{\fontsize{10pt}{12pt}\selectfont
	\bibliography{RXJ_SMA}
}

\end{document}

### 2016-09-13 NOEMA/Proposal16/RXJ.tex
2nd draft to DR

@@
 \newcommand{\rarr}{$\rightarrow$}
-\newcommand{\J}{$J$}
-\newcommand{\aco}{\mbox{CO($J$=1$-$0)}\xspace}
-\newcommand{\bco}{\mbox{CO($J$=2$-$1)}\xspace}
-\newcommand{\cco}{\mbox{CO($J$=3$-$2)}\xspace}
+\newcommand{\vs}{$v_{\rm rot}/\sigma$\xspace}
+\newcommand{\aco}{\mbox{CO(1-0)}\xspace}
+\newcommand{\bco}{\mbox{CO(2-1)}\xspace}
+\newcommand{\cco}{\mbox{CO(3-2)}\xspace}
 \newcommand{\dco}{\mbox{CO($J$=4$-$3)}\xspace}
@@
 %
-\begin{center}{\huge \bf
+\begin{center}{\LARGE \bf
 %-------------------------------------------------------------------
@@
 \centerline{\bf P.I.: T. K. Daisy Leung}
-
+\vspace{0.5em}
 \noindent {\bf Star formation modes and molecular gas dynamics beyond the local universe} \\
@@
 the peak epoch of \SF (1$\lesssim$$z$$\lesssim$3) are
-primarily driven by their increased in molecular gas mass fractions and \SF efficiencies (SFE) compared to
-local galaxies, and that \SF at this epoch/in these early systems can be grossly categorised into
-two dominant modes -- quiescent mode in disc-like galaxies versus starburst mode in submillimetre galaxies (SMGs) and quasar host galaxies \citep[e.g.][]{Sargent12a}. 
+primarily driven by their increased in molecular gas mass fractions and \SF efficiencies (SFEs) compared to
+local galaxies, and that \SF in these early systems can be grossly categorised into
+two dominant modes -- quiescent mode in disk-like galaxies versus starburst mode in \SB galaxies and quasar host galaxies \citep[e.g.][]{Sargent12a}. 
 % brings up the spatial resolution
@@
 more turbulent conditions 
-%due to gravitational instability
 compared to nearby galaxies.  % Elmegreen & Elmegreen 2005, Bournaud+08
-Indeed, recent studies have found gas clumps on the order of kpc scales at $z$=1--2 \citep[e.g.][]{Swinbank12a, Swinbank12b}, providing direct evidence that the
+Indeed, recent studies have found gas clumps on the order of 
+kpc scales at $z$\ssim1--2 \citep[e.g.][]{Genzel11a, Swinbank12a, Swinbank12b}, 
+% and R_{\rm 1/2} $\sim$5\,kpc disks form $\sim$1\,kpc clumps \citep{Genzel11a}, 
+providing direct evidence that the
 interstellar medium (ISM) dynamics of galaxies evolve as a function of cosmic time. This
-highlights the importance of resolving the gas dynamics of galaxies on these scales 
+highlights the importance of resolving gas dynamics of galaxies on these scales 
 and at various epochs in order to investigate the
-mechanisms and physical processes responsible for leading to
-the two star-formation modes and for causing the steep decline in the cosmic SFR density since $z$\ssim1.5 \citep[e.g.][]{Lagos11a,Popping12a}.
+mechanisms and physical processes responsible for % leading to
+the two \SF modes and for causing the steep decline in the cosmic SFR density since $z$\ssim1.5 \citep[e.g.][]{Lagos11a,Popping12a}.
 
@@
 have enabled a better understanding of the gas properties of mergers at these epochs \citep[e.g.][]{Engel10a,Bothwell10a},
-% kinematical and dynamical evidence that massive \highz \SB galaxies are formed in major mergers
+% kinematic and dynamical evidence that massive \highz \SB galaxies are formed in major mergers
 % distinct kinematic components and disturbed gas morphologies
@@
 the gas properties such as excitation, distribution, and dynamics of mergers 
-\atinterz (0.6\,$\lesssim$\,$z$\,$\lesssim$\,1) remain largely unknown
+\atinterz (0.6\,$\lesssim$\,$z$\,$\lesssim$\,1) --- the epoch where the \SF history is steeply rising --- remain largely unknown
 due to the lack of spatially resolved CO observations at these redshifts.
-Thus, to understand of the role of mergers throughout the cosmic history and
-to obtain a coherent picture connecting \highz \galpop to present-day galaxies, 
-it is vital to carry out detailed studies of the gas kinematics and dynamics at intermediate-$z$.
+Thus, to understand of the role of mergers throughout cosmic history and
+to obtain a coherent picture connecting \highz populations to present-day galaxies, 
+it is vital to carry out detailed studies of the gas kinematics and dynamics \atinterz.
 
-We here propose to observe the \cco line emission in a strongly-lensed quasar host galaxy of a merger system at $z$\ssim0.65 using the {\bf A+C array configuration}.
+We have recently imaged \bco line emission
+in a strongly-lensed quasar host galaxy of a merger system 
+ RXJ\,1131$-$1231 (hereafter RX1131) at $z$\ssim0.65
+with the PdBI/NOEMA, and obtained moderate S/N measurements
+of \cco with CARMA \citep[\Fig{combine};][]{Leung16b}. 
+We here propose to image {\bf \cco} 
+at higher resolution using the {\bf A+C array configuration}.
 By combining the magnification provided by gravitational lensing with the improved spatial resolution and sensitivity of NOEMA, 
-the proposed \obs at an angular resolution ($\sim$0.6'') 
-corresponding to a physical scale of $\sim$1.8\,kpc at the target redshift
+the proposed resolution of $\sim$0.6''
+corresponding to a physical scale of $\sim$1.8\,kpc in the source plane at the target redshift
 will allow us to study the internal gas dynamics and distribution 
-down to the physical scales of \highz star-forming clumps in a total of {\bf 3.2 hours including overheads}.
-We have already detected the \bco and \cco lines at high significance with the PdBI/NOEMA and 
-the CARMA, respectively (Leung, Riechers \& Pavesi, submitted; hereafter Leung et al. 2016), and thus this is a low risk project.
+down to the physical scales of \highz star-forming clumps {\bf in only 1.5 hours on source}.
 Since our target is currently the only source with spatially resolved CO
 imaging at intermediate redshift with existing \mulw analysis spanning rest-frame
-UV-to-radio, obtaining the proposed \obs will enable, for the first time, a kpc-scale characterization of the gas, dust, and stellar populations of different ages in a quasar host galaxy and merger at intermediate redshift.
-\vspace{0.5em}
+UV-to-radio, obtaining the proposed \obs will enable, for the first time, a kpc-scale characterisation of the gas, dust, and stellar populations in a quasar host galaxy and merger at intermediate redshift.
 
+\vspace{0.3em}
 \noindent {\bf Unique Nature of our target RXJ\,1131$-$1231}\\
-\indent Our target RXJ\,1131$-$1231 (hereafter RX1131) is a quadruply-imaged optical quasar with its host galaxy being lensed
-into a partial Einstein ring (\Fig{HST}; \citealt{Sluse03a}).
-HST observations (rest-frame UV) have revealed distinct emission
-from recent star-formation (lensing arcs) and from the AGN (bright knots) in the background galaxy,
-demonstrating the great potential for probing its
-ISM conditions in detail. Lens modelling of an optical image has identified
-seven distinct structures in the source plane and a companion galaxy of
-size $\sim$700 pc across, at $\sim$2.4 kpc away from the AGN host galaxy \citep{Brewer08a}.
-We have recently confirmed that both galaxies are at the same rmedshift by detecting their
-\rot[CO]{2}{1} emission and decomposing their gas distribution
-via our $uv$-plane lens modeling in the velocity-space (Leung et al. 2016; see \Fig{combine}f).
-The lensing-corrected IR luminosity of 1.5\E{12}\,\Lsun implies that RXJ1131 can also be classified 
-as a ULIRG.
+\indent 
+RXJ1131 is a quadruply-imaged optical quasar (bright knots in \Fig{combine}d) 
+with its host galaxy being lensed
+into a partial Einstein ring (\Fig{combine}d \& \Fig{velo}; \citealt{Sluse03a}). 
+% HST observations (rest-frame UV) have revealed distinct emission
+% from recent star-formation (lensing arcs) and from the AGN (bright knots) in the background galaxy,
+Source-plane reconstruction 
+of an optical image indicates that the host galaxy displays a disk-like morphology, with
+a companion galaxy located at $\sim$2.4 kpc away 
+\citep[\Fig{combine}f;][]{Claeskens06a, Brewer08a}.
+We have recently confirmed that both galaxies are at the same redshift by detecting their
+\bco emission and decomposing their gas distribution
+via our $uv$-plane lens modeling
+of the NOEMA \bco data
+ in the velocity-space \citep[\Fig{combine}c \& e;][]{Leung16b}, finding a gas mass of 
+$M_{\rm gas}$\ssim1.4\E{10}\,\Msun for RXJ1131.
+Our dynamical lens modelling 
+shows that the asymmetry in the double-horned line profile (\Fig{combine}a)
+is mainly a result of differential lensing, where
+the magnification factor varies from $\sim$3 to $\sim$9 across
+different kinematic components.
+The intrinsically symmetric double-horned line
+profile (\Fig{combine}c) of RXJ1131 together with its source-plane velocity gradient 
+and rotation profile (\Fig{velo}) 
+suggest that it is an extended disk of $\gtrsim$6\,kpc in radius.
+% and dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun. 
+% SED
+We find a lensing-corrected IR luminosity of 1.5\E{12}\,\Lsun based
+on our spectral energy distribution (SED) modelling (\Fig{SED}), 
+indicating that RXJ1131 is a ULIRG with a SFR\ssim120\,\sfrU.
+%Fitting dust SED models to the IR-to-mm photometry, we derive
+%a lensing-corrected dust mass of $M_{\rm dust}$\ssim4\E{8}\,\Msun,
+%an infrared luminosity of \LIR$\sim$\,1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun,
+%and a far-IR luminosity that corresponds to a SFR$_{\rm FIR}$\ssim120\,\sfrU.
+We also find that
+RXJ1131 contains  
+% a gas mass fraction $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim19\% 
+a baryonic gas fraction of $f_{\rm mol}$
+% \eq$M_{\rm gas}$/($M_{\rm gas} + M^*)$
+\ssim32\%
+that is higher than local galaxies.
 
-\vspace{0.5em}
-\noindent {\bf Proposed Observations and Science Goals} \\
-\indent The intrinsically symmetric double-horned line
-profile (\Fig{combine}g) of RXJ1131 and its source-plane velocity gradient
-(\Fig{velo}) extending $\gtrsim$6\,kpc in radius reconstructed from 
-dynamical lens modeling of our \bco data suggest that it is a disc galaxy.
-At the resolution of our \bco data, the disc-like kinematics and 
-galaxy-scale \SF properties 
-resembling those of \highz massive disc galaxies \citep{Daddi10a} suggest that 
-the \SF modes of \interz mergers are already different than the local ones. 
-Since recent studies also find that \highz discs are more clumpy and dynamically unstable compared to local discs, 
-studying the molecular gas in RXJ1131 on the scales of its star-forming clumps
-would enable us to gain insights into how \SF in massive disc galaxies differ since the peak epoch of \SF.
+% what have we learned from our data
+Despite similar IR luminosity, CO linewidth and SFR found between RXJ1131
+and other ULIRGs/high-$z$ \SB galaxies, 
+its CO source size, gas depletion timescale and SFE are similar to those 
+of nearby and high-$z$ disk galaxies rather than \SB systems. This suggests that
+the \SF in RXJ1131 
+% is enhanced by % SFR is higher than local disks, similar to highz turbulent disks, but lower than highz SBs
+mainly driven by
+global gravitational instabilities due to its high gas fraction
+rather than merger-induced gas accumulation, 
+in contrast to local ULIRGs/mergers and \highz starbursts. 
+On the other hand, we find disturbed gas morphologies with velocity dispersion exceeding 
+400\kms near the central region of RXJ1131 (\Fig{combine}e), but since
+the emission is only resolved over $\sim$2$-$3 beams at the current resolution of our data ($\sim$4.4''$\times$2''),
+% it is unclear whether the observed dispersion
+it is impossible to quantify dispersions due to 
+perturbations from its AGN,
+turbulence from interactions with its companion, 
+and gravitational instability due to the huge gas reservoir. % owing to beam smearing effect
+% Resolving the gas kinematics and dynamics at higher resolution is needed to examine
+% the true nature of these observed phenomena and ISM properties. % disk-like SFE, extended disk, but high dispersion
 
-At the resolution of our \bco data, we find 
-disturbed gas morphologies with an unusually high velocity dispersion ($\gtrsim$400\kms near the central region
-of RXJ1131; \Fig{combine}e).
-%that may be a result of
-%perturbations from the AGN,
-%or
-%internal turbulence due to interactions with the companion/merger-driven, 
-%or instability due to the huge gas reservoir/clumpy disc 
-Higher resolution imaging, as proposed here, is necessary to infer its true velocity structure and dynamical state 
-to distinguish between a rotationally-dominated versus dispersion-dominated system.
-We will achieve this by reconstructing the source-plane spatial distribution of the gas and its velocity field, and
-deriving the $v$/$\sigma$ ratio (as a proxy to the Toomre Q parameter).
-This will allow us to contrast the dynamical properties between mergers and discs galaxies at low and \highz.
-% to those of \highz rotating disc, which typically display 
-% v/$\sigma$\,$<$\,1 with clumpy morphology or 
-% high-z: triggered by fragmentation of dynamically unstable system.
-% physical properties
-We will also measure spatially resolved line ratios between the \cco and \bco 
-emission within RX1131 to gain insight into its gas excitation conditions.
-The cold gas distribution, kinematics and line ratio variations will provide clues on
-the main driver of \SF in RXJ1131 
- (e.g. if the warmer gas is
+\vspace{0.3em}
+\noindent {\bf This proposal} \\ % what can we learn
+\indent 
+Based on scaling relations 
+% for the Toomre scale length 
+in \citet{Genzel11a}, % , L\_toomre ~ f\_gas *R\_disk, then
+we expect clump size of % 0.32*6
+$\sim$1.9\,kpc in RXJ1131. % given its gas fraction and disk size.
+Thus, the proposed resolution will enable us to derive \vs
+% (a proxy to the Toomre Q parameter) 
+on this scale, enabling us to quantify whether RXJ1131 is a rotation- or dispersion-dominated system 
+and examine its internal dynamics by studying the spatial variations in \vs.
+Studies have shown that resolutions corresponding to $\sim$1.7$-$2\,kpc are sufficient to withstand %tolerate
+beam smearing effect % and still resolve disk model 
+to extract rotation velocity and 
+dispersion 
+% for 
+% \vs and kinematic analysis 
+even at $z$\ssim2  \citep{Newman13a, Genzel14a}.
+The \vs ratio together with gas size and surface density will enable us to compute the theoretical Jeans length, 
+% By comparing 
+% this observed clumps with the theoretical Jeans length, we can 
+which we will then use to determine the dynamical timescales of the star-forming clumps in RXJ1131
+to examine its star-forming conditions and mechanisms.
+%(e.g. is it merger-driven).
+% which important to our understanding of the build up of local massive disk galaxies.
+% ... by smooth accretion of gas and/or minor mergers.
+% This will allow us to contrast its dynamical properties between mergers and disks galaxies at low and \highz.
+
+% say 1st moment map, rotation profile
+We will derive the rotation velocity by reconstructing the intrinsic gas distribution and velocity field using 
+a similar approach as with our NOEMA \bco data.
+Given that structures of the lensed emission is clearly resolved in our VLA radio map at $\sim$0.4'', % Although what I am actually thinking of the ALMA in mind
+the proposed \obs will allow us to obtain 
+more accurate lens modelling of different kinematic components, and on smaller spatial scales,
+% o reconstruct the source-plane velocity structures, thereby  % reconstructing the source-plane spatial distribution of the gas and its velocity field
+providing constraints along the steepest gradient of the rotation curve.
+This will enable us to derive reliable estimates on the rotation velocity, inclination angle, and
+dynamical mass by fitting disk models.
+% place seven constraints on the rotation profile which is yet
+ % at [ 6.29772725  3.02618336  2.29008935  0.          2.45365038  3.844054  6.13413293] kpc
+
+%
+% physical properties -- excitation
+Since that proposed resolution is better than our \bco data, we will be able to measure line ratios 
+of RXJ1131 and of the companion independently to study their excitation conditions.
+Aided by lensing, we will obtain kinematic information on spatial scales smaller than the beam (\Fig{velo}), 
+enabling us to probe excitation in the red- and blue-shifted components independently.
+We will also measure spatially resolved line ratios % between the \cco and \bco 
+% emission 
+within RX1131 to gain insight into its gas excitation conditions.
+The molecular gas distribution, kinematics and line ratio variations will provide clues on
+the main driver of \SF in RXJ1131 (e.g. if the warmer gas is
 concentrated toward the central region of RX1131 like nearby ULIRGs), 
-how its interaction with the companion may influence the molecular gas in fueling its ongoing \SF and the central quasar,
-and how its gas excitation differs from other \galpop at different cosmic epochs.
-In addition, at the proposed resolution, we will be able to obtain a more accurate lens model, enabling us
-to resolve the intrinsic velocity gradient at finer details, and thus 
-to obtain a better-constrained rotation curve and dynamical mass estimate.
+how interactions with the companion influence the molecular gas 
+in fueling its ongoing \SF and the central quasar,
+and how does its gas excitation differ from other \galpop at different cosmic epochs.
 % but we would need a way to reconstruct the dispersion via lens modeling.
+%
+%
+% spatially-resolved SK
+Additionally, we expect to detect continuum emission underlying \cco line at $\sim$5-10$\sigma$ significance
+based on our SED model and the source size and flux ratio measured in our high-resolution VLA image (0.4'') at 5\,GHz.
+% the 2\,mm continuum source size estimated from the publicly release ALMA data at BLAH'', % but if I say this, then that means 
+% we don't really need this additional cont data to do 
+Hence, the proposed data will also allow us to place constraints on the spatially resolved 
+``\SF law'' to investigate how the \SF mode of this \interz quasar 
+compare to its population at other redshifts. % and dependence on its gas properties.
 
@@
 Given the unique lensing configuration and nature of our target, the proposed observations 
-present an excellent opportunity to investigate the molecular gas excitation
-and the kinematical and dynamical 
+present an excellent opportunity to investigate the molecular gas excitation, kinematic and dynamical 
 state of a distant quasar host galaxy of a merging system.
@@
 us to investigate how physical parameters, e.g.
-stellar mass, dust temperature, SFR, morphology, clumpiness, internal gas dynamics, which have been investigated at both nearby and $z$$\gtrsim$1 galaxies vary \atinterz depending on the molecular gas conditions, providing important constraints for current models of galaxy evolution.
+stellar mass, dust temperature, SFR, SFE, and morphology, which have been investigated at both nearby and $z$$\gtrsim$1 galaxies, vary \atinterz depending on the molecular gas conditions, providing important constraints for current models of galaxy evolution.
 
-\vspace{.5em}
+%Mapping the molecular gas in RXJ1131on the scales of its star-forming clumps and
+%constraining the velocity structure, rotation velocity and the dispersion on these scales 
+%will allow us to study the ISM conditions on these scales to
+%investigate whether the \SF mode in RXJ1131is predominantly driven its disk-like kinematics and dynamics.
+%% probably because it is a disk, and the companion is only minor
+%% but this also means that there are different kinds of mergers, and at different epochs, that have different \SF properties.
+%and to gain insights into how the \SF processes in disk galaxies have evolved since the peak epoch of \SF.
+
+\vspace{.3em}
 \noindent {\bf Technical justification} \\
 % A+C: ~0.66" at 209 GHz
-\indent We estimate the source size of \cco emitting gas in RXJ1131 based on the
-most extended kinematic component in our dynamical lens model of our PdBI/NOEMA \bco emission, which takes into account the asymmetric line emission and spatial extent across different velocity bins (arising due to differential lensing).
+\indent 
+We propose to observe \cco emission in RXJ1131 at the redshifted line frequency of $\sim$209.1\,GHz, using the A+C array configurations. 
+Given the spatial extent the quasar host galaxy, 
+we request C-array \obs to provide short spacings 
+to maximize the sensitivity and UV coverage for lens modelling, and to
+ensure the diffuse lensed emission on $\gtrsim$0.47'' scale is not resolved out. % just A array
+% To maximize the sensitivity and UV coverage of the maps and to ensure that no flux was resolved out at the highest resolution, we combined the extended configuration data with the compact configuration observations.
+We estimate the expected source size based on the
+most extended kinematic component in our dynamical lens model of the \bco data, which takes into account the asymmetric line emission and spatial extent across different velocity bins (arising due to differential lensing).
 We therefore expect the source to be resolved over $\sim$10 beams at the proposed angular resolution of $\sim$0.66''.
@@
 CARMA \cco line flux of $I$\eq35.7\,Jy\,\kms and line FWHM of $\sim$700\,\kms.
-To secure enough S/N for lens modelling, 
-we require of 10$\sigma$ detection of $\sigma$\eq1.35\,mJy\,beam\pmOne per 100\kms channel.
+To secure enough S/N for dynamical lens modelling over $7-10$ velocity bins, 
+we require of 10$\sigma$ detection of $\sigma$\eq1.35\,mJy\,beam\pmOne per 100\kms channel,
+{\bf requiring only $\sim$1.5 hours on source} with 8 antennas.
 We note that the requested sensitivity will correspond to S/N$>$10 for channels with spatially less extended emission, which are also found to have lower magnification factors (and thus lower apparent flux density).
-We thus note that the requested sensitivity is conservative but reasonable given that our scientific goals rely heavily on having enough S/N per channel over the entire line profile (especially in the red wing which is spatially more extended).
 
 \clearpage
-\section{Supporting material} % don't mix in with text
 % You may include up to two pages of figures, tables, and References.
 
-\begin{figure}[!tbhp]
-\hspace{-1.75em}
-\vspace{-0.35em}
-\centering
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.46\textwidth}}]{figure}
-[\FBwidth]
-{\hspace{-0.5em}
-\includegraphics[trim= 10 20 15 0, clip, scale=0.23]{Figures/F555W-eps-converted-to}
-\hspace{-2.0em}
-\includegraphics[trim= 10 0 0 5, clip, scale=0.33]{Figures/Manipulate_figsCROP}
-\vspace{-1.0em}
-}
-{
-\hspace{-1.05em}
-\caption{\fontsize{11pt}{12.5pt}\selectfont{\textbf{Stellar light distribution in
-the AGN host galaxy RXJ 1131-1231 and its reconstructed source plane morphology.}
-{\em Left:} Rest-frame UV emission (tracing recent star formation)
-is lensed into an almost complete Einstein ring with diameter $\sim$3.8".
-{\em Right:} Lens modeling of the optical emission identifies complex
-structures in the host galaxy and
-an optically faint companion (white component as indicated by the blue arrows;
-\citealt{Claeskens06a}),
-which we have recently confirmed by lens-modeling our \bco data
-(\Fig{combine}; Leung et al., submitted).
-Here, we propose to map the \cco emission in this \interz disc-like quasar host galaxy of a merger system.
-}
-\label{fig:HST}}
-}
-\end{figure}
-
-\begin{figure}[!tbhp]
-\centering
-\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.46\textwidth}}]{figure}
-[\FBwidth]
-{
-\includegraphics[trim= 0 0 0 0 clip, scale=0.43]{Figures/veloGradient_markers.pdf}
-}
-{
-\caption{\fontsize{11pt}{12.5pt}\selectfont{\textbf{Image- and source-plane velocity gradient
-of the \bco line emission in the AGN host galaxy RXJ1131.}
-Source-plane positions reconstructed from the best-fit $uv$-plane lens modeling of 
-our PdBI/NOEMA \bco data in the velocity-space
-are indicated as color markers atop the observed first moment map. 
-At the proposed resolution, we will be able to obtain a more accurate lens model, 
-enabling us to resolve the intrinsic velocity gradient at finer details, and obtain a better-constrained rotation curve and dynamical mass estimate for this \interz quasar host galaxy.
-}}
-\label{fig:velo}}
-\end{figure}
+%\begin{figure}[!tbhp]
+%\hspace{-1.75em}
+%\vspace{-0.35em}
+%\centering
+%\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.46\textwidth}}]{figure}
+%[\FBwidth]
+%{\hspace{-0.5em}
+%\includegraphics[trim= 10 20 15 0, clip, scale=0.23]{Figures/F555W-eps-converted-to}
+%\hspace{-2.0em}
+%\includegraphics[trim= 10 0 0 5, clip, scale=0.33]{Figures/Manipulate_figsCROP}
+%\vspace{-1.0em}
+%}
+%{
+%\hspace{-1.05em}
+%\caption{\fontsize{11pt}{12.5pt}\selectfont{\textbf{Stellar light distribution in
+%the AGN host galaxy RXJ 1131-1231 and its reconstructed source plane morphology.}
+%{\em Left:} Rest-frame UV emission (tracing recent star formation)
+%is lensed into an almost complete Einstein ring with diameter $\sim$3.8".
+%{\em Right:} Lens modeling of the optical emission identifies complex
+%structures in the host galaxy and
+%an optically faint companion (white component as indicated by the blue arrows;
+%\citealt{Claeskens06a}),
+%which we have recently confirmed by lens-modeling our \bco data
+%(\Fig{combine}; Leung et al., submitted).
+%Here, we propose to map the \cco emission in this \interz disk-like quasar host galaxy of a merger system.
+%}
+%\label{fig:HST}}
+%}
+%\end{figure}
 
@@
 \begin{center}
-\includegraphics[trim=0 135 127 0, clip,width=1.0\textwidth]{Figures/combine3}
-\caption{ \fontsize{11pt}{12.35pt}\selectfont{\textbf{Recent \bco data from
-NOEMA (Leung et al., submitted).}}
+\includegraphics[trim=0 155 127 0, clip,width=1.0\textwidth]{Figures/combine4}
+\caption{ 
+% \fontsize{11pt}{12.35pt}\selectfont{
+\textbf{Recent \bco data from NOEMA \citep{Leung16b}.}
+% }
 {\em (a):}
@@
 demonstrating
-differential lensing of the kinematic components of a gas-rich ``disc"
+differential lensing of the kinematic components of a gas-rich ``disk"
 and the wealth of dynamical information that is already available at this resolution.
 {\em (c):}
+Full resolution spectrum (yellow; same as panel $a$ but shown on log-scale) and the seven channels (dashed) used for lens modeling.
+Using the magnification factors indicated above the model channels, we recover an intrinsically symmetric profile (blue).
+{\em (d):}
 Observed spatial variations across different velocity components due to
@@
 green (line center), and blue (blueshifted) contours.
-{\em (d):}
-The observed velocity gradient is suggestive of a disc morphology at the current resolution limit.
-The spectrally resolved lensed emission allows us to probe dynamical structures
-on smaller spatial scales than otherwise possible.
+% The observed velocity gradient is suggestive of a disk morphology at the current resolution limit.
 {\em (e):}
-An unusually high velocity gradient ($\gtrsim$400\,\kms) near the center of RXJ1131
-may be a result of perturbations from the AGN, 
-or internal turbulence due to interactions with the companion, 
-or instability due to the huge gas reservoir. 
-{\em (f):}
+% An unusually high velocity gradient ($\gtrsim$400\,\kms) near the center of RXJ1131
+% may be a result of perturbations from the AGN, 
+% or internal turbulence due to interactions with the companion, 
+% or instability due to the huge gas reservoir. 
 Channel maps of the CO emission (red)
@@
 The foreground lensing galaxy is represented by a black dot.
-The reconstructed source morphology (magenta ellipses) is also suggestive of a
-``disc".
-{\em (g):}
-Full resolution spectrum (yellow; same as panel $a$ but shown in log-scale) and the seven channels (dashed) used for lens modeling.
-Using the magnification factors shown above the model channels, we recover an intrinsically symmetric profile (blue).
-We here propose to observe \cco line in RXJ1131 at the spatial scales of \highz gas clumps
-in order to investigate its molecular gas excitation, kinematical and dynamical state and examine how 
-physical properties, e.g. stellar mass, dust temperature, SFR, morphology, clumpiness, internal gas dynamics, 
+The reconstructed source morphology (magenta ellipses) is suggestive of a ``disk", 
+consistent with that in the optical {\em (f)}.
+We propose to observe \cco line in RXJ1131 at the spatial scales of its star-forming clumps
+to
+investigate
+its molecular gas excitation, kinematic and dynamical state and how
+physical properties, e.g. stellar mass, dust temperature, SFR, SFE, morphology, clumpiness, 
 vary at intermediate redshift depending on the molecular gas conditions.
@@
 
+\clearpage
+
+%\begin{figure}[!tbhp]
+%\centering
+%\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.46\textwidth}}]{figure}
+%[\FBwidth]
+%{
+%\includegraphics[trim= 0 0 0 0 clip, scale=0.43]{Figures/veloGradient_markers.pdf}
+%}
+%{
+%\caption{\fontsize{11pt}{12.5pt}\selectfont{\textbf{Image- and source-plane velocity gradient
+%of the \bco line emission in the AGN host galaxy RXJ1131.}
+%Source-plane positions reconstructed from the best-fit $uv$-plane lens modeling of 
+%our PdBI/NOEMA \bco data in the velocity-space
+%are indicated as color markers atop the observed first moment map. 
+%At the proposed resolution, we will be able to obtain a more accurate lens model, 
+%enabling us to resolve the intrinsic velocity gradient at finer details, and obtain a better-constrained rotation curve and dynamical mass estimate for this \interz quasar host galaxy.
+%}}
+%\label{fig:velo}}
+%\end{figure}
+
+\begin{figure}[!hptb]
+\centering
+\includegraphics[trim= 15 340 30 0 clip, scale=0.7]{Figures/Fig2}
+\caption{\fontsize{11pt}{12.5pt}\selectfont{
+\textbf{Gas morphology and dynamical constraints from 
+lens modelling of our NOEMA \bco data.}
+{\em Left:} Extended CO emission with structures as shown in
+\bco intensity map overlaid on an optical image.
+{\em Middle:} 
+Source-plane positions of different kinematic components 
+have been reconstructed from our NOEMA data using
+a velocity-space lens modelling approach in the $uv$-plane,
+% at the current resolution of our NOEMA data.
+as indicated by color markers atop the observed first moment map. 
+The spectrally resolved lensed emission allows us to probe dynamical structures
+on spatial scales smaller the synthesis beam.
+{\em Right:} Position-velocity diagram along the source-plane major axis at PA\,=\,121$^\circ$.
+Dashed line shows the best-fit rotation curve.
+% The vertical error bars show the channel width for
+% each model and the horizontal error bars are the
+% 1$\sigma$ uncertainties on the source plane positions.
+Our dynamical modelling is currently limited by the poorly constrained rotation profile.
+At the proposed resolution, we will be able to obtain more accurate lens modelling of different kinematic components, and on smaller spatial scales,
+providing constraints along the steepest gradient of the rotation curve.
+This will enable us to derive reliable estimates on the rotation velocity, inclination angle, and
+dynamical mass 
+for this \interz quasar host galaxy.
+}
+\label{fig:velo}}
+\end{figure}
+\begin{figure*}[!htbp]
+\vspace{-1.15em}
+\hspace{-1.95em}
+\centering
+\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=0.5\textwidth}}]{figure}
+[\FBwidth]
+{
+\includegraphics[trim=5 0 13 0, clip, angle=0,
+width=0.50\textwidth]{Figures/FullSED_withMagphys}} 
+{
+\hspace{-0.95em}
+\caption{ 
+% \fontsize{11pt}{12.5pt}\selectfont{
+\textbf{Multi-wavelength photometry and SED models
+\citep{Leung16b}.}
+% }
+We have de-blended rest-frame UV-to-radio 
+photometry in our target 
+(blue markers) from its foreground lensing galaxy.
+The dashed and dashed-dotted lines correspond to the best-fit dust 
+SED models (uncorrected for lensing) 
+and
+the black line corresponds to the best-fit full SED model (corrected for lensing).
+We estimate a continuum flux 
+% of $S_{\rm cont}$\ssim
+$\sim$1.5$-$3.4\,mJy
+by extrapolating SED models to the proposed frequency.
+We thus expect to detect continuum emission underlying \cco line at $\sim$5-10$\sigma$ significance.
+This will allow us to place constraints on the spatially resolved 
+``\SF law'' to investigate how the \SF mode of this \interz quasar compare to its population at other redshifts.
+% }
+\label{fig:SED}}}
+\vspace{-0.85em}
+\end{figure*}
+
 %%%%%%%%%%%%
 \noindent \textbf{References}
-{\fontsize{10pt}{12pt}\selectfont
+{\fontsize{11pt}{11pt}\selectfont
 	\bibliography{RXJ_SMA}

### 2016-09-14 ALMA/Cycle4/pythonSpecOplot/plotSpecMPL.py
shift spectrum velocity scale, to match up with our de-lensed spectra

@@ -1,11 +1,14 @@
 '''
 Overplot spectra at different spatial location for ALMA C4 proposal
 
-Last Modified: April 16 2016
+Last Modified: Sept 13 2016
 
 
 History:
 --------
+Sept 13 2016:
+    - shift central velocity for NOEMA proposal figure; from PdBI/data/30Apr16/: 0 km/s shifted from chan 130 to chan 145
+        --> shift velocity by ~ 21.528154*15 to postive velocity
 April 14 2016:
     - edit labels and text annotations
 April 11 2016:
@@ -21,6 +24,7 @@ import matplotlib.pyplot as plt
 from scipy.optimize import curve_fit
 import scipy
 
+# plt.rc('font', family='simplex')
 
 def gauss(x, a, b, c):
     '''
@@ -92,7 +96,7 @@ def setup_spec_plot(ax, xax, xlabel=False, ylabel=False):
     ax.yaxis.set_minor_locator(minorLocator)
 
     if ylabel:
-        ax.set_ylabel('Flux density [mJy/Beam]')
+        ax.set_ylabel('Flux density [mJy/beam]')
     if xax == 'velocity':
         if xlabel:
             ax.set_xlabel('Velocity [km/s]')
@@ -186,9 +190,11 @@ fig.subplots_adjust(top=0.8)
 
 ax1 = fig.add_subplot(111)
 setup_spec_plot(ax1, xaxis, xlabel=True, ylabel=True)
-plot_spec_base(ax1, x1[70:200], flux1[70:200], width1, color='green', fill=False)
-plot_spec_base(ax1, x2[70:200], flux2[70:200], width2, color='blue', c=None, fill=False) # , ls='dashed')
-plot_spec_base(ax1, x3[70:200], flux3[70:200], width3, color='red', c=None, fill=False) #, ls='dashed')
+
+pad_xaxis = 21.528154*15
+plot_spec_base(ax1, x1[70:200]+pad_xaxis, flux1[70:200], width1, color='green', fill=False)
+plot_spec_base(ax1, x2[70:200]+pad_xaxis, flux2[70:200], width2, color='blue', c=None, fill=False) # , ls='dashed')
+plot_spec_base(ax1, x3[70:200]+pad_xaxis, flux3[70:200], width3, color='red', c=None, fill=False) #, ls='dashed')
 put_baseline(ax1)
 
[…]

### 2016-09-14 NOEMA/Proposal16/RXJ.tex
w/ DR's 2nd round comments

@@
 %-------------------------------------------------------------------
-Sub-arcsecond resolution \cco imaging of a strongly-lensed wet-merger at $z$$\sim$0.65
+2-kpc scale \cco imaging of a strongly-lensed wet-merger at $z$$\sim$0.65
 %-------------------------------------------------------------------
@@
 local galaxies, and that \SF in these early systems can be grossly categorised into
-two dominant modes -- quiescent mode in disk-like galaxies versus starburst mode in \SB galaxies and quasar host galaxies \citep[e.g.][]{Sargent12a}. 
+two dominant modes -- quiescent mode in disk-like galaxies versus starburst mode in commonly merger-driven
+ \SB galaxies and quasar host galaxies \citep[e.g.][]{Sargent12a}. 
 % brings up the spatial resolution
 The systematically enhanced molecular gas fractions observed in \highz
-\galpop implies that their star-forming clumps are expected to be larger in size, and in
-more turbulent conditions 
+\galpop imply that their star-forming clumps are expected to be larger in size due to 
+larger internal turbulence
 compared to nearby galaxies.  % Elmegreen & Elmegreen 2005, Bournaud+08
 Indeed, recent studies have found gas clumps on the order of
-kpc scales at $z$\ssim1--2 \citep[e.g.][]{Genzel11a, Swinbank12a, Swinbank12b}, 
+$\sim$1$-$2\,kpc scales at $z$\ssim1--2 \citep[e.g.][]{Genzel11a, Swinbank12a, Swinbank12b}, 
 % and R_{\rm 1/2} $\sim$5\,kpc disks form $\sim$1\,kpc clumps \citep{Genzel11a}, 
 providing direct evidence that the
-interstellar medium (ISM) dynamics of galaxies evolve as a function of cosmic time. This
+interstellar medium (ISM) conditions of galaxies evolve as a function of cosmic time. This
 highlights the importance of resolving gas dynamics of galaxies on these scales 
@@
 local ultra-luminous IR galaxies (ULIRGs) and their \highz analogues ($z$$\gtrsim$1 \SB systems)
-have enabled a better understanding of the gas properties of mergers at these epochs \citep[e.g.][]{Engel10a,Bothwell10a},
+have enabled a better understanding of the gas properties of mergers at these epochs 
+\citep[e.g.][]{Carilli10a, Engel10a,Bothwell10a,Riechers11b, Ivison11a},
 % kinematic and dynamical evidence that massive \highz \SB galaxies are formed in major mergers
@@
 We have recently imaged \bco line emission
-in a strongly-lensed quasar host galaxy of a merger system 
+in the strongly-lensed quasar host galaxy
  RXJ\,1131$-$1231 (hereafter RX1131) at $z$\ssim0.65
-with the PdBI/NOEMA, and obtained moderate S/N measurements
-of \cco with CARMA \citep[\Fig{combine};][]{Leung16b}. 
+with the PdBI/NOEMA \citep[\Fig{combine};][]{Leung16b}. 
 We here propose to image {\bf \cco} 
@@
 
-\vspace{0.3em}
+\vspace{0.2em}
 \noindent {\bf Unique Nature of our target RXJ\,1131$-$1231}\\
@@
 of the NOEMA \bco data
- in the velocity-space \citep[\Fig{combine}c \& e;][]{Leung16b}, finding a gas mass of 
+ in velocity-space \citep[\Fig{combine}c \& e;][]{Leung16b}, finding a gas mass of 
 $M_{\rm gas}$\ssim1.4\E{10}\,\Msun for RXJ1131.
@@
 The intrinsically symmetric double-horned line
-profile (\Fig{combine}c) of RXJ1131 together with its source-plane velocity gradient 
+profile of RXJ1131 (\Fig{combine}c) together with its source-plane velocity gradient 
 and rotation profile (\Fig{velo}) 
-suggest that it is an extended disk of $\gtrsim$6\,kpc in radius.
+suggest that RX1131 is an extended disk of $\gtrsim$6\,kpc in radius.
 % and dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun. 
@@
 % a gas mass fraction $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim19\% 
-a baryonic gas fraction of $f_{\rm mol}$
-% \eq$M_{\rm gas}$/($M_{\rm gas} + M^*)$
-\ssim32\%
-that is higher than local galaxies.
+a baryonic gas fraction of $f_{\rm mol}$\ssim32\%
+that is higher than local galaxies but modest compared to $z$\ssim2 disk galaxies \citep{Daddi10a}.
 
@@
 400\kms near the central region of RXJ1131 (\Fig{combine}e), but since
-the emission is only resolved over $\sim$2$-$3 beams at the current resolution of our data ($\sim$4.4''$\times$2''),
+the emission is only resolved over $\sim$2$-$3 beams at the resolution of our current data ($\sim$4.4''$\times$2''),
 % it is unclear whether the observed dispersion
@@
 
-\vspace{0.3em}
-\noindent {\bf This proposal} \\ % what can we learn
+\vspace{0.2em}
+\noindent {\bf This proposal} \\ 
 \indent 
+We propose to map \cco line emission in RXJ1131
+which we have already detected with CARMA at moderate S/N and resolution ($\sim$3'').
 Based on scaling relations 
 % for the Toomre scale length 
-in \citet{Genzel11a}, % , L\_toomre ~ f\_gas *R\_disk, then
+\citep{Genzel11a}, % , L\_toomre ~ f\_gas *R\_disk, then
 we expect clump size of % 0.32*6
 $\sim$1.9\,kpc in RXJ1131. % given its gas fraction and disk size.
-Thus, the proposed resolution will enable us to derive \vs
+Thus, the proposed resolution of $\sim$0.7'' ($\sim$1.8\,kpc in the source plane at $z$\ssim0.65) will enable us to derive \vs
 % (a proxy to the Toomre Q parameter) 
-on this scale, enabling us to quantify whether RXJ1131 is a rotation- or dispersion-dominated system 
-and examine its internal dynamics by studying the spatial variations in \vs.
-Studies have shown that resolutions corresponding to $\sim$1.7$-$2\,kpc are sufficient to withstand %tolerate
-beam smearing effect % and still resolve disk model 
-to extract rotation velocity and 
-dispersion 
-% for 
-% \vs and kinematic analysis 
-even at $z$\ssim2  \citep{Newman13a, Genzel14a}.
+on this scale length, enabling us to quantify whether RXJ1131 is a rotation- or dispersion-dominated system, 
+and to examine its internal dynamics by studying the spatial variations in \vs.
+Previous studies have shown that resolutions corresponding to $\sim$1.7$-$2\,kpc are sufficient to withstand %tolerate
+beam smearing effect to extract rotation velocity and 
+dispersion even at $z$\ssim2  \citep[e.g.][]{Newman13a, Genzel14a}.
 The \vs ratio together with gas size and surface density will enable us to compute the theoretical Jeans length, 
-% By comparing 
-% this observed clumps with the theoretical Jeans length, we can 
 which we will then use to determine the dynamical timescales of the star-forming clumps in RXJ1131
@@
 % This will allow us to contrast its dynamical properties between mergers and disks galaxies at low and \highz.
-
+%
 % say 1st moment map, rotation profile
 We will derive the rotation velocity by reconstructing the intrinsic gas distribution and velocity field using 
-a similar approach as with our NOEMA \bco data.
-Given that structures of the lensed emission is clearly resolved in our VLA radio map at $\sim$0.4'', % Although what I am actually thinking of the ALMA in mind
-the proposed \obs will allow us to obtain 
-more accurate lens modelling of different kinematic components, and on smaller spatial scales,
-% o reconstruct the source-plane velocity structures, thereby  % reconstructing the source-plane spatial distribution of the gas and its velocity field
-providing constraints along the steepest gradient of the rotation curve.
+a similar approach as with our NOEMA \bco data (\Fig{velo}), but at much higher precision.
 This will enable us to derive reliable estimates on the rotation velocity, inclination angle, and
@@
 % physical properties -- excitation
-Since that proposed resolution is better than our \bco data, we will be able to measure line ratios 
-of RXJ1131 and of the companion independently to study their excitation conditions.
-Aided by lensing, we will obtain kinematic information on spatial scales smaller than the beam (\Fig{velo}), 
-enabling us to probe excitation in the red- and blue-shifted components independently.
-We will also measure spatially resolved line ratios % between the \cco and \bco 
+We will measure spatially resolved line ratios % between the \cco and \bco 
 % emission 
 within RX1131 to gain insight into its gas excitation conditions.
-The molecular gas distribution, kinematics and line ratio variations will provide clues on
+The molecular gas distribution, kinematics and line ratio variations will provide clues to
 the main driver of \SF in RXJ1131 (e.g. if the warmer gas is
-concentrated toward the central region of RX1131 like nearby ULIRGs), 
+concentrated toward the central region of RX1131 like in nearby ULIRGs), 
 how interactions with the companion influence the molecular gas 
 in fueling its ongoing \SF and the central quasar,
-and how does its gas excitation differ from other \galpop at different cosmic epochs.
+and how its gas excitation differs from other \galpop at different cosmic epochs.
 % but we would need a way to reconstruct the dispersion via lens modeling.
@@
 Additionally, we expect to detect continuum emission underlying \cco line at $\sim$5-10$\sigma$ significance
-based on our SED model and the source size and flux ratio measured in our high-resolution VLA image (0.4'') at 5\,GHz.
+based on our SED model and the observed image ratios at radio wavelengths.
 % the 2\,mm continuum source size estimated from the publicly release ALMA data at BLAH'', % but if I say this, then that means 
@@
 Hence, the proposed data will also allow us to place constraints on the spatially resolved 
-``\SF law'' to investigate how the \SF mode of this \interz quasar 
-compare to its population at other redshifts. % and dependence on its gas properties.
+``\SF law'' at $z$\ssim0.65.
 
@@
 % final word
-Given the unique lensing configuration and nature of our target, the proposed observations 
+Given the rare lensing configuration and nature of our target, the proposed observations 
 present an excellent opportunity to investigate the molecular gas excitation, kinematic and dynamical 
-state of a distant quasar host galaxy of a merging system.
-The addition of spatially resolved \cco data will allow 
+state of a distant quasar host galaxy, allowing 
+% The proposed high resolution and S/N \cco data will allow 
 us to investigate how physical parameters, e.g.
-stellar mass, dust temperature, SFR, SFE, and morphology, which have been investigated at both nearby and $z$$\gtrsim$1 galaxies, vary \atinterz depending on the molecular gas conditions, providing important constraints for current models of galaxy evolution.
+stellar mass, dust temperature, SFR, SFE, and morphology, which have been investigated at both nearby and $z$$\gtrsim$1 galaxies, vary \atinterz depending on the molecular gas
+properties. %, providing important constraints for current models of galaxy evolution.
 
@@
 
-\vspace{.3em}
-\noindent {\bf Technical justification} \\
+\vspace{.2em}
+\noindent {\bf Technical justification} 
 % A+C: ~0.66" at 209 GHz
-\indent 
-We propose to observe \cco emission in RXJ1131 at the redshifted line frequency of $\sim$209.1\,GHz, using the A+C array configurations. 
-Given the spatial extent the quasar host galaxy, 
+We propose to observe \cco emission in RXJ1131 at $z_{\rm CO}$\eq0.6537 at the 
+redshifted line frequency of 209.10443\,GHz ($\nu_{\rm rest}$\eq345.79599\,GHz) using the A+C array configurations. 
+Given the spatial extent the quasar host galaxy ($\sim$3.8'' in diameter), 
 we request C-array \obs to provide short spacings 
-to maximize the sensitivity and UV coverage for lens modelling, and to
-ensure the diffuse lensed emission on $\gtrsim$0.47'' scale is not resolved out. % just A array
+to maximize the sensitivity and $uv$ coverage for lens modelling, and to
+ensure that diffuse lensed emission on $\gtrsim$0.3'' scale is not resolved out. % just A array
 % To maximize the sensitivity and UV coverage of the maps and to ensure that no flux was resolved out at the highest resolution, we combined the extended configuration data with the compact configuration observations.
@@
 CARMA \cco line flux of $I$\eq35.7\,Jy\,\kms and line FWHM of $\sim$700\,\kms.
-To secure enough S/N for dynamical lens modelling over $7-10$ velocity bins, 
-we require of 10$\sigma$ detection of $\sigma$\eq1.35\,mJy\,beam\pmOne per 100\kms channel,
-{\bf requiring only $\sim$1.5 hours on source} with 8 antennas.
+To obtain sufficient S/N for dynamical lens modelling over 7$-$10 velocity bins, 
+we require a 10$\sigma$ detection of $\sigma$\eq1.35\,mJy\,beam\pmOne per 100\,\kms bin,
+{\bf requiring only $\sim$1.5 hours on source} (and 2.4 hours including overheads) with 8 antennas.
 We note that the requested sensitivity will correspond to S/N$>$10 for channels with spatially less extended emission, which are also found to have lower magnification factors (and thus lower apparent flux density).
@@
 % \fontsize{11pt}{12.35pt}\selectfont{
-\textbf{Recent \bco data from NOEMA \citep{Leung16b}.}
+\textbf{Recent \bco \obs from NOEMA and $uv$-plane lens modelling of RXJ1131 \citep{Leung16b}.}
 % }
 {\em (a):}
-Asymmetric double-horned line profile observed towards our target.
+Asymmetric double-horned (apparent) line profile observed towards our target.
 {\em (b):}
@@
 demonstrating
-differential lensing of the kinematic components of a gas-rich ``disk"
-and the wealth of dynamical information that is already available at this resolution.
+differential lensing of different kinematic components.
 {\em (c):}
 Full resolution spectrum (yellow; same as panel $a$ but shown on log-scale) and the seven channels (dashed) used for lens modeling.
-Using the magnification factors indicated above the model channels, we recover an intrinsically symmetric profile (blue).
+Using the magnification factors indicated above the model channels, we recover an intrinsically symmetric
+``twin peak'' profile (blue) as expected for a rotating disk.
 {\em (d):}
@@
 as shown by the red (redshifted),
-green (line center), and blue (blueshifted) contours.
+green (line center), and blue (blueshifted) contours overlaid on an 
+HST image of the rest-frame optical emission of the stellar light and AGN.
 % The observed velocity gradient is suggestive of a disk morphology at the current resolution limit.
@@
 Channel maps of the CO emission (red)
-overlaid on our best-fit lens models (grayscale).
-The foreground lensing galaxy is represented by a black dot.
+overlaid on our best-fit $uv$-plane lens models (grayscale).
 The reconstructed source morphology (magenta ellipses) is suggestive of a ``disk", 
 consistent with that in the optical {\em (f)}.
-We propose to observe \cco line in RXJ1131 at the spatial scales of its star-forming clumps
+We propose to observe \cco line in RXJ1131 at the spatial scales of individual star-forming clumps ($\sim$1.9\,kpc)
 to
@@
 lens modelling of our NOEMA \bco data.}
-{\em Left:} Extended CO emission with structures as shown in
-\bco intensity map overlaid on an optical image.
+{\em Left:} Extended CO emission overlaid on an optical image.
 {\em Middle:} 
@@
 % 1$\sigma$ uncertainties on the source plane positions.
-Our dynamical modelling is currently limited by the poorly constrained rotation profile.
+Our dynamical modelling is currently limited by the poorly resolved rotation profile in the central $\sim$\,2kpc.
 At the proposed resolution, we will be able to obtain more accurate lens modelling of different kinematic components, and on smaller spatial scales,
-providing constraints along the steepest gradient of the rotation curve.
-This will enable us to derive reliable estimates on the rotation velocity, inclination angle, and
+allowing us to resolve the steep central gradient of the rotation curve.
+This will enable us to derive more reliable estimates on the rotation velocity, inclination angle, and
 dynamical mass 
@@
 the black line corresponds to the best-fit full SED model (corrected for lensing).
-We estimate a continuum flux 
+We estimate a continuum flux of
 % of $S_{\rm cont}$\ssim
@@
 This will allow us to place constraints on the spatially resolved 
-``\SF law'' to investigate how the \SF mode of this \interz quasar compare to its population at other redshifts.
+``\SF law'' to investigate how the \SF mode of this \interz quasar host galaxy compares 
+to those at low and high redshift.
 % }

### 2016-09-14 NOEMA/Proposal16/RXJ.tex
prob. more conservative to say A array only is 0.4

@@
 to maximize the sensitivity and $uv$ coverage for lens modelling, and to
-ensure that diffuse lensed emission on $\gtrsim$0.3'' scale is not resolved out. % just A array
+ensure that diffuse lensed emission on $\gtrsim$0.4'' scale is not resolved out. % just A array
 % To maximize the sensitivity and UV coverage of the maps and to ensure that no flux was resolved out at the highest resolution, we combined the extended configuration data with the compact configuration observations.

### 2016-09-14 NOEMA/Proposal16/RXJ.tex
wording

@@
 highlights the importance of resolving gas dynamics of galaxies on these scales
-and at various epochs in order to investigate the
+and at earlier epochs in order to investigate the
 mechanisms and physical processes responsible for % leading to

### 2016-09-14 NOEMA/Proposal16/RXJ.tex
w/ DR's final comments

@@
 %-------------------------------------------------------------------
-2-kpc scale \cco imaging of a strongly-lensed wet-merger at $z$$\sim$0.65
+2-kpc resolution \cco imaging of an exceptional strongly-lensed wet-merger at $z$$\sim$0.65
 %-------------------------------------------------------------------
@@
 local galaxies, and that \SF in these early systems can be grossly categorised into
-two dominant modes -- quiescent mode in disk-like galaxies versus starburst mode in commonly merger-driven
- \SB galaxies and quasar host galaxies \citep[e.g.][]{Sargent12a}.
+two dominant modes -- a quiescent mode in disk-like galaxies versus a starburst mode in commonly merger-driven
+ \SB and quasar host galaxies \citep[e.g.][]{Sargent12a}.
 % brings up the spatial resolution
@@
 % that are likely the progenitors of local massive ellipticals
-the gas properties such as excitation, distribution, and dynamics of mergers
+the gas excitation, distribution, and dynamics of mergers
 \atinterz (0.6\,$\lesssim$\,$z$\,$\lesssim$\,1) --- the epoch where the \SF history is steeply rising --- remain largely unknown
@@
 
-We have recently imaged \bco line emission
+We have sucessfully imaged \bco line emission
 in the strongly-lensed quasar host galaxy
@@
 We here propose to image {\bf \cco}
-at higher resolution using the {\bf A+C array configuration}.
-By combining the magnification provided by gravitational lensing with the improved spatial resolution and sensitivity of NOEMA,
-the proposed resolution of $\sim$0.6''
-corresponding to a physical scale of $\sim$1.8\,kpc in the source plane at the target redshift
-will allow us to study the internal gas dynamics and distribution
-down to the physical scales of \highz star-forming clumps {\bf in only 1.5 hours on source}.
+at higher resolution using the {\bf A+C array configurations}.
+By combining the magnification provided by gravitational lensing with the excellent spatial resolution and sensitivity of NOEMA,
+we will study the internal gas dynamics and distribution
+down to the physical scales of \highz star-forming clumps 
+at $\sim$0.6'' resolution 
+(corresponding to a physical scale of $\sim$1.8\,kpc in the source plane at the target redshift)
+{\bf in only 1.5 hours on source}.
 Since our target is currently the only source with spatially resolved CO
@@
 \vspace{0.2em}
-\noindent {\bf Unique Nature of our target RXJ\,1131$-$1231}\\
+\noindent {\bf Unique nature of our target RXJ\,1131$-$1231}\\
 \indent
@@
 % from recent star-formation (lensing arcs) and from the AGN (bright knots) in the background galaxy,
-Source-plane reconstruction
-of an optical image indicates that the host galaxy displays a disk-like morphology, with
+A source-plane reconstruction
+of optical imaging data indicates that the host galaxy displays a disk-like morphology, with
 a companion galaxy located at $\sim$2.4 kpc away
@@
 \bco emission and decomposing their gas distribution
-via our $uv$-plane lens modeling
+via $uv$-plane lens modeling
 of the NOEMA \bco data
@@
 On the other hand, we find disturbed gas morphologies with velocity dispersion exceeding
-400\kms near the central region of RXJ1131 (\Fig{combine}e), but since
+400\,\kms near the central region of RXJ1131 (\Fig{combine}e), but since
 the emission is only resolved over $\sim$2$-$3 beams at the resolution of our current data ($\sim$4.4''$\times$2''),
@@
 We propose to map \cco line emission in RXJ1131
-which we have already detected with CARMA at moderate S/N and resolution ($\sim$3'').
+which we have already detected with CARMA at moderate S/N and resolution ($\sim$3''; Leung et al. 2016).
 Based on scaling relations
@@
 \citep{Genzel11a}, % , L\_toomre ~ f\_gas *R\_disk, then
-we expect clump size of % 0.32*6
+we expect clump sizes of % 0.32*6
 $\sim$1.9\,kpc in RXJ1131. % given its gas fraction and disk size.
-Thus, the proposed resolution of $\sim$0.7'' ($\sim$1.8\,kpc in the source plane at $z$\ssim0.65) will enable us to derive \vs
+Thus, the proposed resolution of $\sim$0.6'' ($\sim$1.8\,kpc in the source plane at $z$\ssim0.65) will enable us to derive \vs
 % (a proxy to the Toomre Q parameter)
@@
 % spatially-resolved SK
-Additionally, we expect to detect continuum emission underlying \cco line at $\sim$5-10$\sigma$ significance
-based on our SED model and the observed image ratios at radio wavelengths.
+Additionally, based on our SED model, 
+we expect to detect continuum emission underlying the \cco line at $\sim$5-10$\sigma$ significance
+and the observed image ratios at radio wavelengths.
 % the 2\,mm continuum source size estimated from the publicly release ALMA data at BLAH'', % but if I say this, then that means
@@
 % A+C: ~0.66" at 209 GHz
-We propose to observe \cco emission in RXJ1131 at $z_{\rm CO}$\eq0.6537 at the
+We propose to observe \cco emission in RXJ1131 at $z_{\rm CO}$\eq0.6537 at a
 redshifted line frequency of 209.10443\,GHz ($\nu_{\rm rest}$\eq345.79599\,GHz) using the A+C array configurations.
 Given the spatial extent the quasar host galaxy ($\sim$3.8'' in diameter),
-we request C-array \obs to provide short spacings
+we request C-array configuration to provide short spacings
 to maximize the sensitivity and $uv$ coverage for lens modelling, and to
@@
 CARMA \cco line flux of $I$\eq35.7\,Jy\,\kms and line FWHM of $\sim$700\,\kms.
-To obtain sufficient S/N for dynamical lens modelling over 7$-$10 velocity bins,
-we require a 10$\sigma$ detection of $\sigma$\eq1.35\,mJy\,beam\pmOne per 100\,\kms bin,
-{\bf requiring only $\sim$1.5 hours on source} (and 2.4 hours including overheads) with 8 antennas.
+To obtain sufficient S/N for dynamical lens modelling over 10 velocity bins,
+we require a 10$\sigma$ detection of $\sigma$\eq1.35
+\,mJy\,beam\pmOne per 70\,\kms bin,
+{\bf requiring only $\sim$2.2 hours on source} (and 3.4 hours including overheads) with 8 antennas.
 We note that the requested sensitivity will correspond to S/N$>$10 for channels with spatially less extended emission, which are also found to have lower magnification factors (and thus lower apparent flux density).
@@
 green (line center), and blue (blueshifted) contours overlaid on an
-HST image of the rest-frame optical emission of the stellar light and AGN.
+{\em HST} image of the rest-frame optical emission of the stellar light and AGN.
 % The observed velocity gradient is suggestive of a disk morphology at the current resolution limit.
@@
 % 1$\sigma$ uncertainties on the source plane positions.
-Our dynamical modelling is currently limited by the poorly resolved rotation profile in the central $\sim$\,2kpc.
+Our dynamical modelling is currently limited by the poorly resolved rotation profile in the central $\pm$2\,kpc.
 At the proposed resolution, we will be able to obtain more accurate lens modelling of different kinematic components, and on smaller spatial scales,
-allowing us to resolve the steep central gradient of the rotation curve.
+allowing us to resolve the expected steep central gradient of the rotation curve.
 This will enable us to derive more reliable estimates on the rotation velocity, inclination angle, and

### 2016-11-02 WRITEUP/ms.tex
clarify wording in SED caption

@@
 with (without) MIR constraint at 24\,$\micron$.
-The solid black line shows the best-fit SED model with dust attenuation (light blue solid line)
-obtained using the \ncode{magphys} code.
+The solid black line shows the best-fit SED model with dust attenuation obtained using the \ncode{magphys} code, whereas
+the light blue solid line shows the unattenuated stellar emission. 
 \label{fig:SED}}

### 2016-11-02 src/HSTVLA.py
change lw for clearer contours

@@ -1,12 +1,14 @@
 """
 Author: Daisy Leung
 
-Last edited: 27 May 2016
+Last edited: 2 Nov 2016
 
 Purpose:
 - Plot single panel 5GHz VLA continuum on HST F555W, investigate continuum offset
 
 History:
+Nov 2 2016:
+    - change lw from 2 to 1.2
 May 27 2016:
     - aspect ratio
 May 17 2016:
@@ -101,7 +103,7 @@ fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=121, vmid=-0.025)
 ########################################
 # Contours
 ########################################
-fig1.show_contour(label_vla['C_R0'][0], colors="blue", levels=sigma_contour_VLA(sigma), linewidths=2)#, layer='fg')
+fig1.show_contour(label_vla['C_R0'][0], colors="blue", levels=sigma_contour_VLA(sigma), linewidths=1.2)#, layer='fg')
 
 # figred.show_contour(label_vla['red'][0], colors="lime", levels=sigma_contour_array(sigma_red), linewidths=2)
 

### 2016-11-05 WRITEUP/response.md
update redshift

We thank the referee for providing constructive and thoughtful
comments to improve the manuscript. We have addressed all the concerns
raised by the referee and details can be found in the revised version
-- please see attached. A brief description on how we incorporated the
changes can be found below.

1a) We have changed the title to ".... of the strongly lensed quasar host galaxy RXS\,J1131-1231"

1b) To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".

1c) We have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig. 5).

1d) We have changed "dynamical information" to "kinematic information".
- reconstruct the intrinsic gas dynamics --> reconstruct the intrinsic line profile and source-plane velocity structure

We have rephrased the 2nd paragraph of Sec 4.1.2 to clarify our message to the reader.

### 2016-11-05 WRITEUP/table_magFactor.tex
added DR's comments, major change: gas fraction, sSFR, intro and conclusion, and removed 'nuclear SB'
update velocity

--- 2016-05-25 WRITEUP/table_magFactor.tex
@@
 \tablehead{
-\colhead{Channel} &
+\colhead{Velocity Range (\kms)} & % see 02July16/velo_res_obs.txt (2nd column), which corresponds to rest-frame velocity at z=0.6541, taken from the central of each bin
 \colhead{Source 1 $\mu_{\rm L}$} &
@@
 \startdata
-126$-$130 & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ [0.6ex] %which is source 1 and 2 then?
-131$-$135 & 7.6 $\pm$ 1.6 & \\ [0.6ex] % would this be source 1 or 2?
-136$-$140 & 8.7 $\pm$ 2.0 & \\ [0.6ex]
-141$-$145 & 4.1 $\pm$ 0.9 & \\ [0.6ex]
-146$-$150 & 4.2 $\pm$ 0.6 & \\ [0.6ex]
-151$-$155 & 4.3 $\pm$ 2.4 & \\ [0.6ex]
-156$-$160 & 3.1 $\pm$ 0.9 & \\ [0.6ex]
-weighted average & 4.4 & \\ [0.6ex]
+346\,$-$\,260       & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ 
+238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.7ex]\hline
+131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
+24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
+-84,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
+-191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
+-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
+weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]
 median & 5.5 &
@@
 \label{tab:model}
-\tablecomments{Source 1 is RXJ1131 and source 2 is its companion. See text for details.}
+\tablecomments{First column corresponds to the rest-frame velocity ranges taken from the center of an unbinned channel
+(see \Fig{delensed}). Each row corresponds to a (binned) channel slice used for
+lens modeling. Source 1 is RXJ1131 and source 2 is its companion. }
 \end{deluxetable}

### 2016-11-05 WRITEUP/table_magFactor.tex
fix typo

@@
 346\,$-$\,260       & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\
-238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.7ex]\hline
+238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
 131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
 24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
--84,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
+-84\,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
 -191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
--300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
+-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.7ex]\hline
 weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]

### 2016-11-06 PdBI/src/pythonPLOT/COChan.py
update label to rest frame

@@ -1,11 +1,15 @@
 '''
-Last Modified: 27 May 16
+Last Modified: 05 Nov 16
 
 
 Author: Daisy Leung
 
 
 History:
+05 Nov 2016
+- use old non-shifted cube
+- change label to show rest-frame velocity (central of each unbinned channel) w.r.t z=0.65406
+
 27 May 2016
 - change flux label unit
 - update font inside panel
@@ -118,8 +122,8 @@ def setup_axes(fig, header, nx, ny):
     return g, cax
 
 Plotpath = '/Users/admin/Research/RXJ1131/Figures/'
-# fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/04Sep15/sup127_155_2ndcln_noCont.fits")
-fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/30Apr16/centralizedCube.fits")
+fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/04Sep15/sup127_155_2ndcln_noCont.fits")
+# fits_cube = pyfits.open("/Users/admin/Research/RXJ1131/PdBI/data/30Apr16/centralizedCube.fits")
 
 dxy = 124                   # starting channel
 nx = 7
@@ -217,10 +221,18 @@ try:
 except ImportError:
     use_path_effect = False
 
+datfr = 139.256
+c = 299792.458
+linefr = 230.538
+
 for i, ax in enumerate(g):
     channel_number = start_channel + i
     v = vel.to_vel(channel_number) / 1.e3
-    t = ax.add_inner_title(r"$v=%4.1f\ {\rm km s}^{-1}$" % (v),
+    x = datfr - (v / c * datfr)
+    x = x * (1 + 0.65406)
+    v_res = (((linefr - x)/linefr) * c)
+    print channel_number, v, v_res
+    t = ax.add_inner_title(r"$v=%4.1f\ {\rm km s}^{-1}$" % (v_res),
                            # (u'$\\mathrm{km/s}$')
                            loc=2,
                            frameon=False

### 2016-11-14 WRITEUP/table_obsprop.tex
observed prop., w/ updated flux uncertainties (fixed the missing sqrt in previous submission)

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Observed Properties of RXJ1131 and its companion}
\tablehead{
\colhead{Parameter} &
\colhead{Unit} &
\colhead{Value}
}
\startdata
$z_{\rm CO}$   &                          & 0.6541\pmm0.0002 \\ [0.5ex]
$I_{\rm CO(2-1)}$     & Jy\,km s\pmOne           & 20.3\pmm0.6 \\ [0.5ex]
S$_{\bco}$     & Jy km s\pmOne beam\pmOne & 8.12\pmm0.30 \\ [0.5ex]
FWHM$_{\rm CO(2-1)}$ \tna & km s\pmOne               & 179\pmm9, 255\pmm28 \\ [0.5ex]
FWHM$_{\rm CO(2-1)}$\tnb        & km s\pmOne               & 220\pmm72 \\ [0.5ex]
$I_{\rm CO(3-2)}$     & Jy\,km s\pmOne           & 35.7\pmm6.9
\enddata
\label{tab:obsprop}
%\tablecomments{}
\tablenotetext{a}{From fitting a double Gaussian to the observed \bco spectrum (\Fig{CO21spec}).}
\tablenotetext{b}{From fitting a double Gaussian with a common FWHM to the de-lensed \bco spectrum (\Fig{delensed}).}
\end{deluxetable}

### 2016-11-14 WRITEUP/table_medianLens.tex
in response to referee

@@
 Position Angle   & (deg)       & 103$\pm$22\\
-Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002
+Einstein Radius\tna  & (\arcsec)   & 1.833$\pm$0.002
 \enddata
 \label{tab:lens}
+\tablenotetext{a}{This corresponds to mass of $M(\theta$\,$<$\,$\theta_{\rm E})$\eq(7.42\pmm0.02)\E{11}\Msun within the Einstein radius.}
 \tablecomments{Parameters describing the foreground lens are

### 2016-11-14 PdBI/src/modelVelo/modelGradient.py
physical size after updating z

@@ -4,9 +4,13 @@
 plot source locations from lens model of various channel as markers on observed 1st moment map.
 Kinematics.
 
-Last Modified: 11 Nov 2016
+Last Modified: 14 Nov 2016
 
 History:
+14 Nov 2016:
+  - phyiscal distance after updating redshift from z=.65337 to .65406
+    - kpc = [ 6.19582973  2.97721957  2.25303559  0.          2.41395019  3.781857  6.03488232]
+    - kpc_err = [ 2.94848621  1.54739332  1.75058216  2.21485144  1.50982133  1.41402099 2.96503249]
 11 Nov 2016:
   - update tick params
 08 Nov 2016:
@@ -687,7 +691,6 @@ ydata = abs(np.array(z))
 yerr = z_err
 xdata = offset_to_physicalR(np.array(off), redshift)
 xerr = offset_to_physicalR(np.array(offset_err), redshift)
-
 # plot velocity v.s. physical radius
 if plotRot:
     plt.errorbar(xdata, ydata, yerr=yerr, fmt='ko', xerr=xerr)

### 2016-11-14 PdBI/src/modelVelo/calcmass.py
update physical size and velocity for using virial method

@@ -3,9 +3,11 @@
 calculate dynamical mass
 
 
-Last modified: 21 June 16
+Last modified: 14 Nov 16
 
 History:
+14 Nov 2016:
+    - update physical size and velocity
 21 June 2016
     - add func. to calc dyn mass using disk model (Neri+03)
 17 May 2016
@@ -49,8 +51,8 @@ def M_encl(R_kpc, v):
     return M10
 
 # calc. mass within some physical dist from line center
-R_in_kpc = 6.22
-V_rot = 345
+R_in_kpc = 6.2
+V_rot = 303
 # no correction for incl. angle
 print("Mass enclosed within {:.2f} kpc: {:.2f} x 1e+10 Msun".format(R_in_kpc, M_encl(R_in_kpc, V_rot)))
 # corrected

### 2016-11-15 WRITEUP/response.md
taking into account everything in referee report, need to decide on BH recoil

@@
 comments to improve the manuscript. We have addressed all the concerns
-raised by the referee and details can be found in the revised version
--- please see attached. A brief description on how we incorporated the
-changes can be found below.
+raised by the referee and details can be found in the revised version of the manuscript -- please see attached. A brief description on how we incorporated the referee's suggestions can be found below.
 
-1a) We have changed the title to ".... of the strongly lensed quasar host galaxy RXS\,J1131-1231"
+1a) We have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXS\,J1131-1231".
+We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (incl.
+lens modeling).
+Therefore, we think that the title is suitable for the paper.
 
-1b) To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".
+The literature/archival data of the continuum would not be as meaningful without our CO data, e.g.
+their emission does not convey inforamtion about the kinematics, spatial distribution, and does not give a broader picture regarding the f_gas evolution, which is one of the main conclusions found in this study.
 
-1c) We have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig. 5).
+1b) We took this suggestion. To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".
 
-1d) We have changed "dynamical information" to "kinematic information".
-- reconstruct the intrinsic gas dynamics --> reconstruct the intrinsic line profile and source-plane velocity structure
+1c) We took this suggestion and have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig.
+5).
 
-We have rephrased the 2nd paragraph of Sec 4.1.2 to clarify our message to the reader.
+1d) We took this suggestion and have changed "dynamical information" to "kinematic information", "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".
+
+We have rephrased the 2nd paragraph of Sec 4.1.2 to clarify what we meant.
+
+2a) We took this suggestion and have corrected nu_LO --> nu_obs.
+
+2b) We took this suggestion and re-fitted a doubled Gaussian to the de-lensed profile (Fig.
+5) and updated the redshift and replotted all the relavent figures (and updated their captions correspondingly), updated column 1 in Table 3, the labeling in Fig 7, refitted the model shown in Fig.
+9 and updated parameters in Sec 4.3 correspondingly, SED fitting, etc.
+
+3) 
+We found a bug in generating the map used for previous line-integrated flux extraction.
+In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes in the relavent channels, which is in agreement with the double-Gaussian fit to the spatially extracted spectrum (Fig.
+1).
+Since our lensing-corrected M_gas for both RXJ1131 and the companion are derived from the flux in each channel, this doesn't change our conclusion.
+
+We tried adding the companion's spectrum to plot (Fig.
+5) but found the figure to be over-crowded/too busy, as there are already showing various things with different various linestyles, colors.
+This main message for this plot is to show that we find that the intrinsic profile of the main galaxy is symmetric, which is informative about the kinematics of this galaxy.
+On the other hand, the useful info for the companion from the de-lensed spectrum is the gas mass, which we report in the text (and in the table, as suggested by the referee).
+
+Source size: We fitted a single Guassian in uv-plane to support the reported CO size based on image plane fitting, of which the convolved size is 6.6+/-0.5 x 4.5+/-0.3.
+We additionally report the source sizes by fitting two Gaussians to provide further evidence that the CO(2-1) emission is resolved.
+We have updated Section 3.1 to clarify the discussion.
+
+CO physical size:
+The rough estimate of de-magnified CO diameter provided in the referee report is flawed since it assumes the magnification factor to be constant along the arc. The fact that 
+1) the lensed emission is not uniformly stretched along the arc (and contains complex structures within the arc)
+2) CO is immune to dust extinction, therefore likely to be more extended than the optical emission, as supported by our deconvolved CO source size and in Fig.
+7 (where the blue wing centroid is further out than the lensed arc), and from the results of our lens models
+indicates the CO source size is unlikely to be R ≤ 3.5 kpc.
+
+The reported R_CO = 6 kpc is obtained based on the most extended kinematic component is consistent, see Sec 4.3.
+
+4) While the most extreme peak to peak noise is ~100 mJy/beam, the noise varies across channels, and therefore, on average, sigma is lower across all channels.
+Thus, the uncertainty is more representative using those obtained from the integrated map.
+
+To demonstrate that our S/N are real regardless of the fainter blue wing, we have independently obtained SNR map to confirm our results, where the peak flux in the red peak is 11.46+/-1.95 Jy/B and the blue peak is 5.13 +/- 1.45 Jy/B.
+I think what was confusing was the reported I_CO(3-2)=35.7+/-21.3Jy km/s, for which I missed a sqrt, and it should have been 35.7+/-6.91 Jy km/s, which has been corrected.
+
+Since both CO lines are observed towards the same source, using prior knowledge about the blue wing from the CO(2-1) data to inform about the CO(3-2) emission is reasonable.
+
+While the additioanl figure in I_CO is not significant, we keep this 
+to enable reproducible results and to minimize cumulative errors (e.g. when compiled for a larger number of samples). We only report significant figures when reporting the physical parameters.
+
+5) 
+We updated the 2mm flux in Table 1. We updated the flux uncertainty to include those from the uv-fitting process.
+
+The peak emission in the residual map is 0.39 +/- 0.08 mJy.
+While the uncertainty associated with the flux measurement of the background source needs to propagate the errors from subtracting the fitted model flux, the significance of the emission in the residual doesn't not.
+It simply is Data-Model, which is > 4 sigma than the noise.
+This together with the co-spatial emission supports that flux contributiion from the background source to the total integrated 2mm continuum.
+
+The term "deblending" is a broadly used in photometry, and it is clear that it refers to the flux subtraction within the same paragraph. We therefore make no changes to the wording.
+
+6) While the large uncertainty on the flux density of the background source at 2mm results in a spectral index with a large uncertainty, this nevertheless is a constraint on the radio-mm spectral slope: our value of -0.345 is flatter than the typical spectral index for pure synchrotron emission, suggesting that the 2mm has a non-negligible contribution from the underlying free-free emission.
+We have also added an additional statement stating that if there is a non-negligible contribution from the background source contributing to the peak flux, then the derived spectral index for the background source would be shallower, and therefore increasing the fraction of free-free emission over synchrotron at 2mm.
+This would also explain the atypical flat spectrum found for the foreground galaxy.
+
+The flatter than pure synchrotron spectral slope found for the background source indicates that the 2mm continuum emission is not dominated by synchrotron.
+Assuming a synchrotron index of alpha = 0.7, we find 0.12 mJy at 2mm for the background source.
+To account for it, we have updated our SED fitting and the resulting parameters throughout the paper using S = 0.27 mJy at 2mm.
+
+We note that 0.27 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the unceratinties, where this uncertainty included in the fit included those from absolute flux calibration.
+Therefore changes to the physical parameters are only at most a few percent,  we have updated the numbers but this does not alter the conclusions of this paper.
+
+7) We adopted the suggestions.
+
+8) We adopted the suggestions and have added additional tables summarizing the observed CO line properties and the derived physical parameters.
+
+9) It is of standard practice to report flux measurmenets from interferometric observations excluding those from the absolute flux calibration.
+To address the referee's concern, we have added a remark in Section 3.3, table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.
+
+We have fixed the number of decimals in spectral indices in Sec 3.3.
+
+10) We have replotted the figure with different contour intervals with thinner lines and added a sentence in the caption to improve clarify of Fig 4.
+
+11) We have corrected "blueshifted" to "redshifted", udpated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.
+
+12) 
+a)
+
+We have removed the statement regarding "AGN dynamically offset".
+
+# While the AGN may not be dynamically offset, given the possible scenario dirivng the BLR velocity offset, as pointed out by the referee, our CO measurement confirms that an offset between BLR and the systemic redshift, which is not known/constrained previously.
+We updated this section.
+The dynamical timescale of a recoiling black hole...
+
+b & c) The details of the model (e.g. how we reconstruct the likelihood functions) are already referenced in other papers. We did not discuss any of that in this paper.
+
+However, description of our MCMC sampling has been retained given that conveying the priors and stating how we ensure convergence is necessary for reproducible results and are crucial information for readers to decide on how trust-worthy our inference are from a statistical viewpoint.
+Explicitly stating the priors is important to demonstrate that our choice are reasonable and physically motivated since they could affect the marginal posteriors strongly and thus the inferred physical parameters.
+
+13) We updated f_gas and f_mol using M_gas and M_dyn of both RXJ1131+companion , i.e., as a merger system.
+
+For other comments, please refer to our response to point 11 and 12 (since 
+they are repeated here).
+
+14) 
+Indeed, the plot on the left is to demonstrate that despite the observed 1st moment map is distorted due to a combination of differential lensing (in which the red velocity are more heavily weighed) and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kienamtic components, as shown atop of the observed map.
+The reconstructed information displays a clear velocity gradient.
+Taken together with previous results from literature and the intrinsically symmetric line profile, we proceed the next section with dynamical modeling.
+
+To address the referee's concern, we have added in a few lines in the caption to clarify what is being shown in the left panel.
+
+PV: 
+As discussed in Sec 4.1.1, we have detailed the evidence and reasons for which we interpret RXJ1131 as a disk galaxy.
+Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraphy of Sec 4.3).
+
+To address the referee's concern and to improve clarify, we have re-iterate in the beginning of the first paragraph of Sec 4.3 that we interpret RXJ1131 as disk galaxy.
+
+Size:
+As explained in para.
+3 of sec 4.3, we use the maximum observed velocity (i.e.
+corresponding to the redmost channel along the disk major axis) at 6+/-3kpc as a proxy to the rotation velocity.
+Thus the quoted CO disk radius corresponds to the extent of this velocity component, as measured from the line center.
+
+Clumps:
+With the evidence and reasons listed in the begining of Sec 4.3, the reconstructed source-plane distribution is unlikely to be just two kinematically-ordered clumps rather than a single rotating disk.

### 2016-11-15 WRITEUP/ms.tex
taking into account everything in referee report, need to decide on BH recoil

@@
 \citestyle{aa}
-\shorttitle{Molecular Gas Dynamics in the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
+\shorttitle{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
 \shortauthors{Leung, Riechers \& Pavesi}
@@
 
-\title{Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
+\title{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
-The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
+The gas mass fraction of $\sim$18\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
 We find lensing-corrected stellar and dust masses, an IR luminosity, and a
 star formation rate of
-$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
+$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
 The source-plane morphologies of its gas and stellar populations
 indicate that the star-formation activity may be as extended as the molecular gas reservoir.
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\% which is higher
 than the 
@@
 Observations of the \bco rotational line
-($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
-at the $\nu_{\rm LO}$\eq139.256\,GHz
+($\nu_{\rm rest}$\,=\,$230.53800$ GHz) at the tuning frequency of 
+$\nu_{\rm obs}$\eq139.256\,GHz
 % redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
@@
 Observations of the \cco rotational line in RXJ1131
-($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
+($\nu_{\rm rest}$\,=\,345.79599\,GHz) 
+% redshifted to 
+at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz    % i.e. where we thought the line was redshifted to 
 were carried out with the \carma (CARMA;
@@
 \section{Results} \label{sec:results}
+The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
+\input{table_obsprop}
+
 \subsection{\bco Emission} \label{sec:CO21}
 We detect \bco line emission toward the background source in the PdBI data
-at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
-0.6537\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
+at $\gtrsim$\,27$\sigma$ significance, enabling us to constrain its redshift at 
+$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to 
+the de-lensed spectrum, which is shown in \Fig{delensed}.
+% instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
+% redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
+}. The emission is spatially and kinematically resolved
 with a highly asymmetric double-horned line profile
@@
 179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
-$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/
+$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/
 
@@
 \includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
-\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of
+\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
 21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
-The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
-considering the asymmetry resulting from differential lensing.
+The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
+the de-lensed line profile (\Fig{delensed}).
 A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
@@
 
-The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
-the image plane
-is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
-and thus, the emission is resolved over $\sim$2.2 beams.
-While the lensed emission is not strictly distributed as a two-dimensional
-Gaussian;
-the fit recovers the line intensity enclosed by the emitting
-region, therefore we take this as an estimate on the full extent of the lensed
-emission. On the other hand, if we assume that the spatial distribution of
-the lensed molecular gas emission is similar to that in the optical to \nir
-wavelengths, the lensed emission would be more accurately described by an
-annulus, enclosing the partially complete ``Einstein ring'' and
-the lensed knots (see \Fig{CO21mom}).
+The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
+to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7, 
+consistent with the results obtained by $uv$-plane fitting within the uncertainties. 
+% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
+To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we 
+fit two independent Gaussians and find deconvolved source sizes of 
+3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
+Therefore, the emission is slightly resolved over $\sim$\,2 beams.
+The lensed CO emission is unlikely to be distributed as Gaussians 
+given the morphology seen in optical and \nir emission that were observed at higher resolution, 
+i.e., the lensed emission of CO (without beam convolution) is more likely to have 
+an annulus configuration enclosing a partially complete ``Einstein ring'' with 
+structures along the arc 
+and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
+spatially offset blue wing compared to optical emission suggest that 
+the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.
 
@@
 Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
-are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
+are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
 The contours in both top panels start at 3$\sigma$ and increment at steps of
@@
 \subsection{\cco Emission}
-We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
+We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
 The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
 double-peaked profile. We estimate a line intensity of
-35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
+35.7\,$\pm$\,6.9\,Jy\,\kms by summing up fluxes over the FWZI
 linewidth used to infer the \bco line intensity ($\sim$700 \kms).
@@
 correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
-Taking into account the large phase errors associated with \cco, this is consistent with
+$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.62, where this uncertainty includes 
+those introduced in absolute flux calibration and is dominated by 
+the large phase errors associated with the \cco observations.
+This ratio is consistent with
 thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-The velocity scale is with respect to $z$=0.6537, which corresponds to the
-dynamical center of the \bco line. The spectral resolution for \cco and \bco
+The velocity scale is with respect to $z$=0.6541, which corresponds to the
+line center of \bco line emission. The spectral resolution for \cco and \bco
 is 35.8 \kms and 21.5 \kms, respectively.
@@
 
-\subsection{Continuum Emission}
-No 1.5\,mm continuum emission is detected at the position of \cco
+\subsection{Continuum Emission} \label{sec:deblend}
+No 1.4\,mm continuum emission is detected at the position of \cco
 down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
@@
 
-We detect 2\,mm continuum emission at an
+We detect 2.2\,mm continuum emission at an
  integrated flux density of
@@
 $S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
-centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
+centered on the lensing galaxy (\Fig{cont}).
+We note that the reported flux uncertainties do not include those from absolute flux calibration.
+Slightly extended emission
 along the lensed arc is also detected.
@@
 We subtract a point source model in the $uv$-plane to remove the unresolved part of the
-emission, which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
+emission, which we here assume to be dominated by the foreground galaxy. The peak emission 
+of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy
 in the residual map coincides with the lensed arc, and is consistent with
 the difference between the integrated and the peak flux in the
-original continuum map ($\sim$0.4 mJy). We therefore adopt
-$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
+original continuum map ($\sim$0.4 mJy). 
+We therefore adopt $S_{\nu}$\eq0.39\pmm0.22 mJy as the 2\,mm continuum flux measurement for 
 the background galaxy (RXJ1131). 
-The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
+The quoted uncertainty is solely based on the uncertainties associated with the flux density of the 
+point source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
+that of the integrated flux in the original data (0.2\,mJy), and does not account for that in the 
+de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
 We report the peak flux in the original map
@@
 \caption{Top: overlay of the 2\,mm continuum emission on the optical image.
+Contours start and increment at steps of
+$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
 Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
-Contours in both images start and increment at steps of
-$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and
-$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the top and bottom panel, respectively.
-The central crosses indicate the centroid of the foreground galaxy,
+Contours correspond to [10, 40, 60, 100]\%$\times$ the peak flux density of $S_{\rm 5GHz}$\eq0.74\pmm0.01 mJy.
+% Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$,
+% where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne.
+The central crosses in both panels indicate the centroid of the foreground galaxy,
 as detected in the optical image. 
@@
 We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
-We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
-for the foreground
-galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
-for the background galaxy by fitting a
-power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
+We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02
+for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35
+for the background galaxy by fitting
+power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum emission at
 5\,GHz and 2\,mm. 
+The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission ($\alpha$\ssim$-$0.7), suggesting 
+that a dominant fraction of the observed 2\,mm emission arises from cold dust and free-free emission. 
+% that the 2\,mm emission is dominated by non-synchrotron emission.
+This spectral slope would only be shallower 
+if a non-negligible fraction from the background source 
+contribute to the point source flux at 2\,mm in the deblending process. This would also 
+explain the atypical flat spectrum found for the foreground galaxy. 
+Assuming a synchrotron slope of $\alpha$\ssim$-$0.7 and that the emission at 5\,GHz is purely synchrotron, 
+we find $S_{\rm 2mm}$\eq0.27\pmm0.22\,mJy from cold dust and free-free emission in the background galaxy.
 
@@
 Nevertheless, the high spectral
-resolution of these data provides dynamical information on
+resolution of these data provides kinematic information on
 spatial scales smaller than the beam (see \Fig{CO21mom}).
-Hence, we reconstruct the intrinsic gas dynamics  % - morphology of different kinematic components - velocity structure
+Hence, we reconstruct the intrinsic line profile and source-plane velocity structure 
+% - morphology of different kinematic components - velocity structure
 by carrying out a parametric lens modeling over different
@@
 \caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
-Top: each panel corresponds to a channel map of width 107.5\,\kms of the observed
-emission (red) overlaid on the best-fit models (grayscale).
+Top: each panel corresponds to a channel map of width 107.5\,\kms around the annotated central velocity where
+the observed emission (red contours) is over-plotted atop the best-fit model (grayscale). 
+% the velocity annotated in each panel is the center velocity of each of the seven channels used in lens modelling.
 Bottom: residual images obtained by
@@
 The reconstructed source-plane positions, as represented by the magenta ellipses, demonstrate an intrinsic velocity gradient of the \bco emission in RXJ1131.
-The best-fit model of the red-most channel (top left panel) contains two source components.
+The best-fit model of the red-most channel (top left panel) contains two source components --- RXJ1131 and its companion galaxy.
 \label{fig:model}}
@@
 
-Similar to previous studies of RXJ1131, where
-differential lensing across the {\it HST}
-$V$-, $I$-, and $H$-bands has been detected with a
-magnification factor decreasing from 10.9 to 7.8 \citepalias{Claeskens06a},
-the highly asymmetric \bco line profile suggests that
-differential lensing is also non-negligible for CO,
-causing the redshifted emission to be apparently much brighter than the
-blueshifted component.
-This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
-varies from 8.7 to 3.1 across the \bco line (\Tab{model}) and also partly due to a contribution from the companion in the redshifted velocity channels.
-The variation in $\mu_{\rm L}$ across channels is consistent with the source plane
+Previous studies of RXJ1131 find evidence for differential lensing across 
+the {\it HST} $V$-, $I$-, and $H$-bands, where the
+magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
+Here, we find that the highly asymmetric \bco line profile is predominantly a result of 
+differential lensing, where the redshifted emission is apparently much brighter than the
+blueshifted component, as indicated by the difference in their magnification factor $(\mu_{\rm L})$, which
+varies from 8.7 to 3.1 across the \bco line (\Tab{model}).
+A secondary effect contributing to the asymmetry is caused by 
+the CO emission in the companion in the redshifted velocity channels.
+The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
 positions relative to the caustics in \Fig{model}, where the red wing
@@
 \subsection{\bco Dynamical Modeling} \label{sec:dynamics}
+As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy given 
+its reconstructed source-plane locations of various kinematic components displaying
+a velocity gradient with a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}), 
+and the disk-like morphology found for source-plane reconstructed optical-NIR emission
+\citepalias{Claeskens06a}.
 Assuming the velocities of the respective channels used in the
@@
 we extract a one dimensional PV diagram in \Fig{PV}
-by slicing across their source plane positions (PA: 121\degr).
-
-We then attempt to characterize the molecular gas kinematics using an
+by slicing across their source plane positions along this major axis (PA: 121\degr).
+
+We then attempt to characterize/constrain the molecular gas kinematics using an
 empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
@@
 corresponding to their uncertainties.
-Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
-$R_{t}$\,=\,10.7\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
+Using this model, we find $V_{a}$\,=\,988\,$\pm$\,618\,\kms,
+$R_{t}$\,=\,10.9\,$\pm$\,7.8\,kpc, and $V_0$\,=\,0\,$\pm$\,9\,\kms.
 However, since the emission is not resolved along the flat regime
@@
 In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
-Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$. % beam smearing --> not resolving velocity info. within the beam
+Pearson coefficient $R$\,=\,0.998, and $-$0.400 between $V_{a}$ and $V_0$. % beam smearing --> not resolving velocity info. within the beam
 
@@
 \includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
-\caption{Left: Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
-the observed first moment map. The contours are at steps of 50\,\kms.
-Right: PV slice along the major axis in the source plane at PA\,=\,121\degr.
-Dashed line shows the best-fit rotation curve using an arctangent model.
+\caption{Left: Source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown 
+as markers color-coded by their velocities
+atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). 
+The contours are at steps of 50\,\kms. 
+Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
+RXJ1131 is intrinsically a kinematically-ordered disk.
+Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr based on 
+the reconstructed source-plane velocity gradient.
+Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
 The vertical error bars show the channel width for
 each model and the horizontal error bars are the
-1$\sigma$ uncertainties on the source plane positions.
+1$\sigma$ uncertainties on the source-plane positions along the major axis.
  \label{fig:PV}}
@@
 of a pure exponential disk peaks \citep{Courteau97b}. % \ie commonly use Vmax (taken at R2.2) as V_rot
+% Due to the large correlation 
 Here, we adopt the maximum {\em observed} velocity
-$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
+$V_{\rm rot}$\,=\,303\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc 
+from the % line center velo of the reddest channel slice, unc = slice width
 dynamical center as a proxy to the rotation velocity.
@@
 $($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
-Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
+Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,303\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
 we find a dynamical mass of
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1.7\E{11}\,\Msun enclosed
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1.3\E{11}\,\Msun enclosed
 within the CO-emitting region in RXJ1131.
@@
 emission of warm and small dust grains.
-The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak.
+The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak and 
+an uncertainty from absolute flux calibration of $\sim$15\% is added in quadrature 
+% to obtain the total uncertainties 
+for the PdBI 2\,mm continuum in our fitting procedure. 
+Here, we use a flux density of $S_{\rm 2mm}$\eq0.27 mJy derived in \Sec{deblend} 
+instead of the deblended 0.39\,mJy listed in \Tab{photometry} 
+to exclude synchrotron emission (see \Sec{deblend}) in dust SED modeling.
+
 The fit is performed using the code
@@
 %
-%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
-%uncertainties for the PdBI continuum in our fitting procedure.
 The model is described by five free parameters: the rest-frame characteristic dust
@@
 % need to compute)
-and the 1$\sigma$ confidence interval in the marginal PDFs
+and the 68\% confidence intervals in the marginal PDFs
 as the best-fit parameters, as listed in \Tab{SED}.
@@
 the 24\,$\micron$ data. Based on the resulting posterior PDFs, we find an apparent
+IR luminosity (rest-frame 8\,$-$\,1000\,$\micron$) of 8.22\petm{2.75}{2.98}\E{12} \Lsun, a
 \fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
-3.81\petm{2.04}{1.92}\E{12}\,\Lsun and a
-dust mass of 22\petm{5}{18}\E{8}\,\Msun, uncorrected for lensing.
+3.81\petm{1.92}{1.97}\E{12}\,\Lsun, and a
+dust mass of 16\petm{5}{12}\E{8}\,\Msun, all of which are uncorrected for lensing magnification.
 For the mass absorption coefficient, we adopt
@@
 for this model, we find a total IR luminosity
-\LIR (rest-frame 8\,$-$\,1000\,\micron) of 9.71\petm{6.14}{-6.05}\E{12}\,\Lsun,
-a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
-dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun, all of which are uncorrected for lensing.
+\LIR (rest-frame 8\,$-$\,1000\,\micron) of 8.67\petm{5.27}{5.27}\E{12}\,\Lsun,
+a \fir luminosity \LFIR of 4.24\petm{2.17}{2.00}\E{12}\,\Lsun and a
+dust mass $M_{\rm dust}$ of 14\petm{5}{7}\E{8}\,\Msun, all of which are uncorrected for lensing.
 Taken at face value, this implies an FIR-to-IR luminosity ratio
-of $\sim$58\pmm35\%.
+of $\sim$49\pmm38\%.
 
@@
 The choice of SED model does not affect
-the derived star formation rate (SFR) given the similar \fir luminosity.
-Yet, the dust mass is higher by a factor of $\sim$2 in the former but consistent within the
-uncertainties.
+the derived star formation rate (SFR) given the similar \fir luminosity, and 
+their dust masses are consistent within the uncertainties.
 We correct for lensing using the median magnification
@@
 \section{Discussion} \label{sec:diss}
+The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}.
+\input{table_propRXJ}
+
 \subsection{ISM Properties} \label{sec:properties}
@@
 % et al. 2010, Daddi et al. 2010).
-We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq19\pmm5\%
+We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq18\pmm4\%
 % , where the uncertainty is based on that of the gas mass.
-and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\eq32\petm{7}{12}\% for RXJ1131.
+and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq34\pmm16\% for the merger system (i.e., RXJ1131 and companion).
 % The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
@@
 and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
-normal ``star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
+``normal star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
 \alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
-Both the dynamical and baryonic gas mass fractions of RXJ1131 are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
+Both the dynamical and baryonic gas mass fractions of RXJ1131+companion are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
 which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
@@
 gas-to-dust ratio (GDR) of 
-40\pmm34.
-This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
+54\pmm13.   %  (1.38e2+0.192e2)/16*5.5 +/- ((0.33/1.38)**2+(0.09/1.92)**2 + (12/16)**2)**.5*54
 This GDR is lower than the statistical average of 206
@@
 local ULIRGs \citep{Wilson08a}, but lower than that of the Milky Way by
-$\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
+$\sim 7\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
 
@@
 
-\subsection{Fate of RXS J1131$-$1231}
+% \subsection{Fate of RXS J1131$-$1231}
 %Results from theoretical simulations have suggested that
@@
 
-\subsection{Velocity Offset and a Recoiling Black Hole}
+\subsection{Systemic Redshift and Velocity Offset}
 %Outflow:
@@
 \citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
-The first set of lines is at $z$\ssim0.653, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
+The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
 the \mgii emission line.
 Using the CO line center redshift as the systemic redshift,
-we find that the redshift of the first set is fully consistent with the systematic redshift. This
+we find that the redshift of the first set is fully consistent with the systemic redshift. This
 supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
@@
 to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
-On the other hand, the second set of lines is blueshifted by $\sim$780\,\kms, indicating that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.
-
-One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
-the central AGN, whereas this condition is not necessary for NLRs.
-From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
-median of 97\kms and a dispersion of 269\,\kms in the distribution of
-the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
-that large offsets are uncommon. Nevertheless,
-offsets as large as $\sim$\,500\,\kms have been observed in some cases.
-%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
-%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
-
-Alternatively, large velocity offsets between emission lines of the
-BLR and the NLR may arise in a recoiling black hole (BH),
-% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines (e.g., Gaskell 1983; Bonning et al.
+On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
+
+% REFEREE: offset in BLR and NLR in RXJ1131 has been known before, not new for this paper
+%One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
+%the central AGN, whereas this condition is not necessary for NLRs.
+%From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
+%median of 97\kms and a dispersion of 269\,\kms in the distribution of
+%the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
+%that large offsets are uncommon. Nevertheless,
+%offsets as large as $\sim$\,500\,\kms have been observed in some cases.
+%%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
+%%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
+
+%Alternatively, large velocity offsets between emission lines of the
+%BLR and the NLR may arise in a recoiling black hole (BH),
+%% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines (e.g., Gaskell 1983; Bonning et al.
 2007; Eracleous et al.
@@
 2013).
-where its BLR is moving at high velocity relative to the bulk of its host galaxy
-\citep{Madau04a, Bonning07a, Loeb07a}.
-A recoiling black hole is expected
-when a pair of uneven mass BH coalesce, during which their orbital energy is being released
-as gravitational wave and a
-non-zero net angular momentum is being carried away.
-Depending on their initial conditions, numerical relativity simulations have shown that
-the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
-Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
-SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
-One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
-a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
-have been observed \citep{Komossa08a},  similar to the case for RXJ1131.
-However, this scenario was recently refuted by \citet{Decarli14a}, who confirm that the
-BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
-This is in contrast with RXJ1131, where our CO observations confirm the blueshifted BLR.
-Since this model requires a merged BH, it would imply that RXJ1131 might
-have been in a previous merger, which would also explain
-the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
+%where its BLR is moving at high velocity relative to the bulk of its host galaxy
+%\citep{Madau04a, Bonning07a, Loeb07a}.
+%A recoiling black hole is expected
+%when a pair of uneven mass BH coalesce, during which their orbital energy is being released
+%as gravitational wave and a
+%non-zero net angular momentum is being carried away.
+%Depending on their initial conditions, numerical relativity simulations have shown that
+%the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
+%Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
+%SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
+%Since this model requires a merged BH, it would imply that RXJ1131 might
+%have been in a previous merger, which would also explain
+%the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
 
 \subsection{The $M_{\rm BH}$$-$\mbulge Relation}
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\%
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\%
 using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
@@
 %  and $\sim$(4)\E{9}\,\Msun for the companion.
-The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim19\% and baryonic gas mass fraction of
-$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\ssim32\% are consistent with the trend of decreasing molecular gas
+The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim18\% and baryonic gas mass fraction of
+$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\ssim34\% are consistent with the trend of decreasing molecular gas
 content since $z$\ssim2 \citep[e.g.,][;\citetalias{Combes13a}]{Lagos11a,Tacconi13a}
@@
 Fitting dust SED models to the IR-to-mm photometry, we derive
-a lensing-corrected dust mass of $M_{\rm dust}$\ssim4\E{8}\,\Msun,
+a lensing-corrected dust mass of $M_{\rm dust}$\ssim3\E{8}\,\Msun,
 an infrared luminosity of \LIR$\sim$\,1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun,
@@
 We also derive a stellar mass of $M_{*}$\ssim3\E{10}\,\Msun by fitting SED models to the
-rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit to
-account for differential lensing effect.
+rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit to account for differential lensing effect.
+
 The source-plane distribution of the gas and stellar populations of different ages
@@
 
-Using the CO redshift as the systemic redshift for the host galaxy of RXJ1131, we find
-that the redshift inferred from the NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are blueshifted by $\sim$780\,\kms.
-This implies that the AGN is offset from the dynamical center of its host galaxy.
-One explanation could be that the
-BLRs are gravitationally bound to the central AGN, whereas this condition is not necessary for NLRs.
-Since the velocity offset between emission lines of the BLR and the NLR
-is typically $\sim$100\pmm270\,\kms,
-we thus raise an alternative explanation of a recoiling black hole in RXJ1131, which
-would also explain the high spin parameter reported by \citet{Reis14a}.
-% This model requires a merged BH, this interpretation would imply that RXJ1131 was
-% in a previous merger.  %, which would also explain the highly spinning black hole.
-%Given the presence of the companion in the current data, RXJ1131 may be in
-%its subsequent stages of minor merging from a previous major merger, as commonly predicted in simulations.
+Using the CO redshift as systemic redshift for the host galaxy of RXJ1131, we find
+that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
+but the optical BLR lines are redshifted by $\sim$715\,\kms.
 
 Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{11}{8}\% for RXJ1131, providing
+$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{0.11}{0.08}\% for RXJ1131, providing
 a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
@@
  The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
- %the ratio is larger at high z than the present day, implying evolution in the Mbh?Msph relation
 
@@
 
+We thank the referee for providing detailed and constructive comments that helped improved the clarify of this manuscript.
 DR and RP acknowledge support from the National Science Foundation

### 2016-11-15 WRITEUP/ms.tex
minor fix typo

@@
 
-We then attempt to characterize/constrain the molecular gas kinematics using an
+We then attempt to characterize the molecular gas kinematics using an
 empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:

### 2016-11-15 WRITEUP/diff.tex
diff version, doesn't have BH reoil for now

--- 2016-11-15 WRITEUP/ms.tex
@@
 \usepackage[normalem]{ulem}
+\usepackage{soul}
 \usepackage[usenames]{xcolor}
@@
 \newcommand{\new}[1]{\textcolor{red}{\bf #1}}
-\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
+\newcommand{\old}[1]{\textcolor{airforceblue}{\protect\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
 % -----------------------------------------------------------------------------------------------
@@
 \citestyle{aa}
-\shorttitle{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
+\shorttitle{Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
 \shortauthors{Leung, Riechers \& Pavesi}
@@
 
-\title{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
+\title{Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
-The gas mass fraction of $\sim$18\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
+The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
 We find lensing-corrected stellar and dust masses, an IR luminosity, and a
 star formation rate of
-$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
+$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
 The source-plane morphologies of its gas and stellar populations
 indicate that the star-formation activity may be as extended as the molecular gas reservoir.
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\% which is higher
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\protect$>$0.27\petm{11}{8}\%} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
 than the 
@@
 Observations of the \bco rotational line
-($\nu_{\rm rest}$\,=\,$230.53800$ GHz) at the tuning frequency of 
-$\nu_{\rm obs}$\eq139.256\,GHz
+($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
+\old{at the $\nu_{\rm LO}$\eq139.256\,GHz}
+\new{at the tuning frequency of $\nu_{\rm obs}$\eq139.256\,GHz}
 % redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
@@
 \subsection{CARMA \cco}
-Observations of the \cco rotational line in RXJ1131
-($\nu_{\rm rest}$\,=\,345.79599\,GHz) 
+Observations of the \cco rotational line in RXJ1131 \old{($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz}
+\new{($\nu_{\rm rest}$\,=\,345.79599\,GHz) 
 % redshifted to 
-at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz    % i.e. where we thought the line was redshifted to 
+at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz}    % i.e. where we thought the line was redshifted to 
 were carried out with the \carma (CARMA;
@@
 \section{Results} \label{sec:results}
-The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
-\input{table_obsprop}
+\new{The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
+\input{table_obsprop}}
 
@@
 We detect \bco line emission toward the background source in the PdBI data
-at $\gtrsim$\,27$\sigma$ significance, enabling us to constrain its redshift at 
+at $\gtrsim$\,27$\sigma$ significance, \old{confirming the redshift at $z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.} \new{enabling us to constrain its redshift at 
 $z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to 
@@
 % redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
-}. The emission is spatially and kinematically resolved
+}}. \old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
 with a highly asymmetric double-horned line profile
@@
 179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
-$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/
+$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms} \new{20.3\,$\pm$\,0.6 Jy \kms}. % see 15May16/
 
@@
 21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
-The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
-the de-lensed line profile (\Fig{delensed}).
+The velocity scale is with respect to \old{$z$\,=\,0.6537, which is approximately the line center considering the asymmetry resulting from differential lensing.} \new{$z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
+the de-lensed line profile (\Fig{delensed})}.
 A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
@@
 
-The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
+\old{\protect{
+The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
+the image plane
+is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
+and thus, the emission is resolved over $\sim$2.2 beams.
+While the lensed emission is not strictly distributed as a two-dimensional
+Gaussian;
+the fit recovers the line intensity enclosed by the emitting
+region, therefore we take this as an estimate on the full extent of the lensed
+emission. On the other hand, if we assume that the spatial distribution of
+the lensed molecular gas emission is similar to that in the optical to \nir
+wavelengths, the lensed emission would be more accurately described by an
+annulus, enclosing the partially complete ``Einstein ring'' and
+the lensed knots (see \Fig{CO21mom}).}}
+\new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
 to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7, 
@@
 spatially offset blue wing compared to optical emission suggest that 
-the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.
+the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.}
 
@@
 Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
-are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
+\old{\protect{are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.}}
+\new{\protect{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
 The contours in both top panels start at 3$\sigma$ and increment at steps of
@@
 double-peaked profile. We estimate a line intensity of
-35.7\,$\pm$\,6.9\,Jy\,\kms by summing up fluxes over the FWZI
+\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms} by summing up fluxes over the FWZI
 linewidth used to infer the \bco line intensity ($\sim$700 \kms).
@@
 correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.62, where this uncertainty includes 
+$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,\old{0.66\,$\pm$\,0.41. Taking into account the large phase errors associated with \cco, this is consistent with}
+\new{0.78\,$\pm$\,0.62, where this uncertainty includes 
 those introduced in absolute flux calibration and is dominated by 
 the large phase errors associated with the \cco observations.
-This ratio is consistent with
+This ratio is consistent with}
 thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-The velocity scale is with respect to $z$=0.6541, which corresponds to the
-line center of \bco line emission. The spectral resolution for \cco and \bco
+The velocity scale is with respect to \old{\protect{$z$=0.6537, which corresponds to the
+dynamical center of the \bco line.}} \new{\protect{$z$=0.6541, which corresponds to the
+line center of \bco line emission.}} The spectral resolution for \cco and \bco
 is 35.8 \kms and 21.5 \kms, respectively.
@@
 \subsection{Continuum Emission} \label{sec:deblend}
-No 1.4\,mm continuum emission is detected at the position of \cco
+No \old{1.5\,mm} \new{1.4\,mm} continuum emission is detected at the position of \cco
 down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
@@
 
-We detect 2.2\,mm continuum emission at an
+We detect \old{2\,mm} \new{2.2\,mm} continuum emission at an
  integrated flux density of
@@
 centered on the lensing galaxy (\Fig{cont}).
-We note that the reported flux uncertainties do not include those from absolute flux calibration.
+\new{We note that the reported flux uncertainties do not include those from absolute flux calibration.}
 Slightly extended emission
@@
 emission, which we here assume to be dominated by the foreground galaxy. The peak emission 
-of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy
+\old{(0.39\,$\pm$\,0.08\,mJy)}
+\new{of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy}
 in the residual map coincides with the lensed arc, and is consistent with
@@
 original continuum map ($\sim$0.4 mJy). 
-We therefore adopt $S_{\nu}$\eq0.39\pmm0.22 mJy as the 2\,mm continuum flux measurement for 
+We therefore adopt \old{$S_{\nu}$ = 0.39\pmm0.08 mJy} \new{$S_{\nu}$\eq0.39\pmm0.22 mJy} as the 2\,mm continuum flux measurement for 
 the background galaxy (RXJ1131). 
-The quoted uncertainty is solely based on the uncertainties associated with the flux density of the 
+\old{The quoted uncertainty is from the flux measurement in the residual map, }
+\new{The quoted uncertainty is solely based on the uncertainties associated with the flux density of the 
 point source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
-that of the integrated flux in the original data (0.2\,mJy), and does not account for that in the 
+that of the integrated flux in the original data (0.2\,mJy), }and does not account for that in the 
 de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
@@
 Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
-Contours correspond to [10, 40, 60, 100]\%$\times$ the peak flux density of $S_{\rm 5GHz}$\eq0.74\pmm0.01 mJy.
+\new{Contours correspond to [10, 40, 60, 100]\%$\times$ the peak flux density of $S_{\rm 5GHz}$\eq0.74\pmm0.01 mJy.}
 % Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$,
@@
 We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
-We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02
-for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35
+We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.024}\new{0.02}
+for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.345}\new{0.35}
 for the background galaxy by fitting
@@
 5\,GHz and 2\,mm. 
-The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission ($\alpha$\ssim$-$0.7), suggesting 
+\new{The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission ($\alpha$\ssim$-$0.7), suggesting 
 that a dominant fraction of the observed 2\,mm emission arises from cold dust and free-free emission. 
@@
 Assuming a synchrotron slope of $\alpha$\ssim$-$0.7 and that the emission at 5\,GHz is purely synchrotron, 
-we find $S_{\rm 2mm}$\eq0.27\pmm0.22\,mJy from cold dust and free-free emission in the background galaxy.
+we find $S_{\rm 2mm}$\eq0.27\pmm0.22\,mJy from cold dust and free-free emission in the background galaxy. }
 
@@
 Nevertheless, the high spectral
-resolution of these data provides kinematic information on
+resolution of these data provides \old{dynamical} \new{kinematic} information on
 spatial scales smaller than the beam (see \Fig{CO21mom}).
-Hence, we reconstruct the intrinsic line profile and source-plane velocity structure 
+Hence, we reconstruct the intrinsic \old{dynamics} \new{line profile and source-plane velocity structure }
 % - morphology of different kinematic components - velocity structure
@@
 \caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
-Top: each panel corresponds to a channel map of width 107.5\,\kms around the annotated central velocity where
-the observed emission (red contours) is over-plotted atop the best-fit model (grayscale). 
+Top: each panel corresponds to a channel map of width 107.5\,\kms \old{of the observed
+emission (red) overlaid on} \new{around the annotated central velocity where
+the observed emission (red contours) is over-plotted atop} the best-fit model (grayscale). 
 % the velocity annotated in each panel is the center velocity of each of the seven channels used in lens modelling.
@@
 The reconstructed source-plane positions, as represented by the magenta ellipses, demonstrate an intrinsic velocity gradient of the \bco emission in RXJ1131.
-The best-fit model of the red-most channel (top left panel) contains two source components --- RXJ1131 and its companion galaxy.
+The best-fit model of the red-most channel (top left panel) contains two source components \new{--- RXJ1131 and its companion galaxy.}
 \label{fig:model}}
@@
 
-Previous studies of RXJ1131 find evidence for differential lensing across 
+\old{\protect{
+Similar to previous studies of RXJ1131, where
+differential lensing across the {\it HST}
+$V$-, $I$-, and $H$-bands has been detected with a
+magnification factor decreasing from 10.9 to 7.8 \citepalias{Claeskens06a},
+the highly asymmetric \bco line profile suggests that
+differential lensing is also non-negligible for CO,
+causing the redshifted emission to be apparently much brighter than the
+blueshifted component.
+This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
+varies from 8.7 to 3.1 across the \bco line (\Tab{model}) and also partly due to a contribution from the companion in the redshifted velocity channels.}}
+\new{\protect{Previous studies of RXJ1131 find evidence for differential lensing across 
 the {\it HST} $V$-, $I$-, and $H$-bands, where the
@@
 A secondary effect contributing to the asymmetry is caused by 
-the CO emission in the companion in the redshifted velocity channels.
+the CO emission in the companion in the redshifted velocity channels.}}
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
@@
 \subsection{\bco Dynamical Modeling} \label{sec:dynamics}
-As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy given 
+\new{As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy given 
 its reconstructed source-plane locations of various kinematic components displaying
@@
 and the disk-like morphology found for source-plane reconstructed optical-NIR emission
-\citepalias{Claeskens06a}.
+\citepalias{Claeskens06a}.}
 Assuming the velocities of the respective channels used in the
@@
 we extract a one dimensional PV diagram in \Fig{PV}
-by slicing across their source plane positions along this major axis (PA: 121\degr).
+by slicing across their source plane positions \new{along this major axis} (PA: 121\degr).
 
@@
 corresponding to their uncertainties.
-Using this model, we find $V_{a}$\,=\,988\,$\pm$\,618\,\kms,
-$R_{t}$\,=\,10.9\,$\pm$\,7.8\,kpc, and $V_0$\,=\,0\,$\pm$\,9\,\kms.
+Using this model, we find \old{$V_{a}$\,=\,975\,$\pm$\,387 \kms,
+$R_{t}$\,=\,10.7\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.} \new{$V_{a}$\,=\,988\,$\pm$\,618\,\kms,
+$R_{t}$\,=\,10.9\,$\pm$\,7.8\,kpc, and $V_0$\,=\,0\,$\pm$\,9\,\kms.}
 However, since the emission is not resolved along the flat regime
@@
 \includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
-\caption{Left: Source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown 
+\caption{Left: \old{\protect{Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
+the observed first moment map}}
+\new{\protect{Source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown 
 as markers color-coded by their velocities
-atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). 
+atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). }}
 The contours are at steps of 50\,\kms. 
@@
 RXJ1131 is intrinsically a kinematically-ordered disk.
-Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr based on 
-the reconstructed source-plane velocity gradient.
+Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr \new{based on 
+the reconstructed source-plane velocity gradient.}
 Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
@@
 each model and the horizontal error bars are the
-1$\sigma$ uncertainties on the source-plane positions along the major axis.
+1$\sigma$ uncertainties on the source-plane positions \new{along the major axis}.
  \label{fig:PV}}
@@
 Here, we adopt the maximum {\em observed} velocity
-$V_{\rm rot}$\,=\,303\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc 
+$V_{\rm rot}$\,=\,\old{345}\new{303}\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc 
 from the % line center velo of the reddest channel slice, unc = slice width
@@
 $($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
-Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,303\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
+Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,\old{345}\new{303}\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
 we find a dynamical mass of
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1.3\E{11}\,\Msun enclosed
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = \old{1.7}\new{1.3}\E{11}\,\Msun enclosed
 within the CO-emitting region in RXJ1131.
@@
 emission of warm and small dust grains.
-The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak and 
+The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak \new{and 
 an uncertainty from absolute flux calibration of $\sim$15\% is added in quadrature 
@@
 instead of the deblended 0.39\,mJy listed in \Tab{photometry} 
-to exclude synchrotron emission (see \Sec{deblend}) in dust SED modeling.
+to exclude synchrotron emission (see \Sec{deblend}) in dust SED modeling}.
 
@@
 the 24\,$\micron$ data. Based on the resulting posterior PDFs, we find an apparent
-IR luminosity (rest-frame 8\,$-$\,1000\,$\micron$) of 8.22\petm{2.75}{2.98}\E{12} \Lsun, a
+\new{IR luminosity (rest-frame 8\,$-$\,1000\,$\micron$) of 8.22\petm{2.75}{2.98}\E{12} \Lsun, a}
 \fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
-3.81\petm{1.92}{1.97}\E{12}\,\Lsun, and a
-dust mass of 16\petm{5}{12}\E{8}\,\Msun, all of which are uncorrected for lensing magnification.
+\old{\protect{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}} \new{\protect{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
+dust mass of 16\petm{5}{12}\E{8}\,\Msun, \new{all of which are} uncorrected for lensing \new{magnification}.
 For the mass absorption coefficient, we adopt
@@
 for this model, we find a total IR luminosity
-\LIR (rest-frame 8\,$-$\,1000\,\micron) of 8.67\petm{5.27}{5.27}\E{12}\,\Lsun,
-a \fir luminosity \LFIR of 4.24\petm{2.17}{2.00}\E{12}\,\Lsun and a
-dust mass $M_{\rm dust}$ of 14\petm{5}{7}\E{8}\,\Msun, all of which are uncorrected for lensing.
+\LIR (rest-frame 8\,$-$\,1000\,\micron) of \old{\protect{9.71\petm{6.14}{-6.05}\E{12}\,\Lsun}} \new{\protect{8.67\petm{5.27}{5.27}\E{12}\,\Lsun}},
+a \fir luminosity \LFIR of \old{\protect{4.72\petm{2.54}{2.26}\E{12}\,\Lsun}} \new{\protect{4.24\petm{2.17}{2.00}\E{12}\,\Lsun}} and a
+dust mass $M_{\rm dust}$ of \old{\protect{11\petm{5}{6}\E{8}\,\Msun}} \new{\protect{14\petm{5}{7}\E{8}\,\Msun}}, all of which are uncorrected for lensing.
 Taken at face value, this implies an FIR-to-IR luminosity ratio
-of $\sim$49\pmm38\%.
+of \old{$\sim$58\pmm35\%} \new{$\sim$49\pmm38\%}.
 
@@
 The choice of SED model does not affect
-the derived star formation rate (SFR) given the similar \fir luminosity, and 
-their dust masses are consistent within the uncertainties.
+the derived star formation rate (SFR) given the similar \fir luminosity\old{.Yet, the dust mass is higher by a factor of $\sim$2 in the former but consistent within the uncertainties.}{\new, and 
+their dust masses are consistent within the uncertainties.}
 We correct for lensing using the median magnification
@@
 with (without) MIR constraint at 24\,$\micron$.
-The solid black line shows the best-fit SED model with dust attenuation obtained using the \ncode{magphys} code, whereas
-the light blue solid line shows the unattenuated stellar emission. 
+The solid black line shows the best-fit SED model with dust attenuation \old{\protect{(light blue solid line)
+obtained using the \ncode{magphys} code.}}\new{\protect{obtained using the \ncode{magphys} code, whereas
+the light blue solid line shows the unattenuated stellar emission. }}
 \label{fig:SED}}
@@
 \section{Discussion} \label{sec:diss}
-The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}.
-\input{table_propRXJ}
+\new{The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}.
+\input{table_propRXJ}}
 
@@
 % et al. 2010, Daddi et al. 2010).
-We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq18\pmm4\%
+We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq\old{19\pmm5\%}\new{18\pmm4\%}
 % , where the uncertainty is based on that of the gas mass.
-and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq34\pmm16\% for the merger system (i.e., RXJ1131 and companion).
+and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq\old{\protect{32\petm{7}{12}\% for RXJ1131}}\new{\protect{34\pmm16\% for the merger system (i.e., RXJ1131 and companion)}}.
 % The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
@@
 \alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
-Both the dynamical and baryonic gas mass fractions of RXJ1131+companion are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
+Both the dynamical and baryonic gas mass fractions of RXJ1131\new{+companion} are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
 which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
@@
 gas-to-dust ratio (GDR) of 
-54\pmm13.   %  (1.38e2+0.192e2)/16*5.5 +/- ((0.33/1.38)**2+(0.09/1.92)**2 + (12/16)**2)**.5*54
+\old{40\pmm34}\new{54\pmm13}.   %  (1.38e2+0.192e2)/16*5.5 +/- ((0.33/1.38)**2+(0.09/1.92)**2 + (12/16)**2)**.5*54
+\old{This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.}
 This GDR is lower than the statistical average of 206
@@
 local ULIRGs \citep{Wilson08a}, but lower than that of the Milky Way by
-$\sim 7\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
+$\sim$\old{4}\new{7}$\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
 
@@
 \citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
-The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
+The first set of lines is at $z$\ssim\old{0.653}\new{0.654}, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
 the \mgii emission line.
-Using the CO line center redshift as the systemic redshift,
+Using the CO line center redshift as the \old{systematic} \new{systemic} redshift,
 we find that the redshift of the first set is fully consistent with the systemic redshift. This
@@
 to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
-On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
+\old{On the other hand, the second set of lines is blueshifted by $\sim$780\,\kms, indicating that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.}
+\new{On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.}
+
+\old{\protect{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
+the central AGN, whereas this condition is not necessary for NLRs.
+From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
+median of 97\kms and a dispersion of 269\,\kms in the distribution of
+the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
+that large offsets are uncommon. Nevertheless,
+offsets as large as $\sim$\,500\,\kms have been observed in some cases.}}
+%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
+%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
+
+\old{\protect{Alternatively, large velocity offsets between emission lines of the
+BLR and the NLR may arise in a recoiling black hole (BH),
+% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines e.g., Gaskell 1983; Bonning et al.
+2007; Eracleous et al.
+2012; Ju et al.
+2013; Shen et al.
+2013).
+where its BLR is moving at high velocity relative to the bulk of its host galaxy
+\citep{Madau04a, Bonning07a, Loeb07a}.
+A recoiling black hole is expected
+when a pair of uneven mass BH coalesce, during which their orbital energy is being released
+as gravitational wave and a
+non-zero net angular momentum is being carried away.
+Depending on their initial conditions, numerical relativity simulations have shown that
+the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
+Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
+SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
+One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
+a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
+have been observed \citep{Komossa08a},  similar to the case for RXJ1131.
+However, this scenario was recently refuted by \citet{Decarli14a}, who confirm that the
+BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
+This is in contrast with RXJ1131, where our CO observations confirm the blueshifted BLR.
+Since this model requires a merged BH, it would imply that RXJ1131 might
+have been in a previous merger, which would also explain
+the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.}}
 
@@
 \subsection{The $M_{\rm BH}$$-$\mbulge Relation}
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\%
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\protect{$>$0.27\petm{11}{8}\%}} \new{\protect{$>$0.27\petm{0.11}{0.08}\%}}
 using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
@@
 %  and $\sim$(4)\E{9}\,\Msun for the companion.
-The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim18\% and baryonic gas mass fraction of
-$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\ssim34\% are consistent with the trend of decreasing molecular gas
+The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim\old{19}\new{18}\% and baryonic gas mass fraction of
+$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\ssim\old{32}\new{34}\% are consistent with the trend of decreasing molecular gas
 content since $z$\ssim2 \citep[e.g.,][;\citetalias{Combes13a}]{Lagos11a,Tacconi13a}
@@
 Fitting dust SED models to the IR-to-mm photometry, we derive
-a lensing-corrected dust mass of $M_{\rm dust}$\ssim3\E{8}\,\Msun,
+a lensing-corrected dust mass of $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun,
 an infrared luminosity of \LIR$\sim$\,1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun,
@@
 that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are redshifted by $\sim$715\,\kms.
+but the optical BLR lines are redshifted by \old{$\sim$780\,\kms}\new{$\sim$715\,\kms}.
+\old{\protect{This implies that the AGN is offset from the dynamical center of its host galaxy.
+One explanation could be that the
+BLRs are gravitationally bound to the central AGN, whereas this condition is not necessary for NLRs.
+Since the velocity offset between emission lines of the BLR and the NLR
+is typically $\sim$100\pmm270\,\kms,
+we thus raise an alternative explanation of a recoiling black hole in RXJ1131, which
+would also explain the high spin parameter reported by \citet{Reis14a}.}}
 
 Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{0.11}{0.08}\% for RXJ1131, providing
+$M_{\rm BH}$$/$$M_{\rm bulge}$$>$\old{\protect{0.27\petm{11}{8}\%}}\new{\protect{0.27\petm{0.11}{0.08}\%}} for RXJ1131, providing
 a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.

### 2016-11-15 WRITEUP/diff.tex
update with mbox to strikethrough special symbols

@@
 \newcommand{\new}[1]{\textcolor{red}{\bf #1}}
-\newcommand{\old}[1]{\textcolor{airforceblue}{\protect\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
+\newcommand{\old}[1]{\textcolor{airforceblue}{\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
 % -----------------------------------------------------------------------------------------------
@@
 indicate that the star-formation activity may be as extended as the molecular gas reservoir.
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\protect$>$0.27\petm{11}{8}\%} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\mbox{$>$0.27\petm{11}{8}\%}} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
 than the
@@
 
-\old{\protect{
+\old{
 The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
@@
 emission. On the other hand, if we assume that the spatial distribution of
-the lensed molecular gas emission is similar to that in the optical to \nir
+the lensed molecular gas emission is similar to that in the optical to \mbox{\nir}
 wavelengths, the lensed emission would be more accurately described by an
-annulus, enclosing the partially complete ``Einstein ring'' and
-the lensed knots (see \Fig{CO21mom}).}}
+annulus, enclosing the partially complete ``Einstein ring'' and}
+\old{\mbox{the lensed knots (see \Fig{CO21mom}).}}
 \new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian
@@
 Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
-\old{\protect{are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.}}
-\new{\protect{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
+\old{\mbox{are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.}}
+\new{\mbox{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
 The contours in both top panels start at 3$\sigma$ and increment at steps of
@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-The velocity scale is with respect to \old{\protect{$z$=0.6537, which corresponds to the
-dynamical center of the \bco line.}} \new{\protect{$z$=0.6541, which corresponds to the
+The velocity scale is with respect to \old{\mbox{$z$=0.6537, which corresponds to the
+dynamical center of the \bco line.}} \new{\mbox{$z$=0.6541, which corresponds to the
 line center of \bco line emission.}} The spectral resolution for \cco and \bco
@@
 
-\old{\protect{
+\old{
 Similar to previous studies of RXJ1131, where
@@
 $V$-, $I$-, and $H$-bands has been detected with a
-magnification factor decreasing from 10.9 to 7.8 \citepalias{Claeskens06a},
-the highly asymmetric \bco line profile suggests that
+magnification factor decreasing from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}},
+the highly asymmetric \mbox{\bco} line profile suggests that
 differential lensing is also non-negligible for CO,
@@
 blueshifted component.
-This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
-varies from 8.7 to 3.1 across the \bco line (\Tab{model}) and also partly due to a contribution from the companion in the redshifted velocity channels.}}
+This can be explained by the difference in magnification factor \mbox{$(\mu_{\rm L})$} which
+varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
 \new{\protect{Previous studies of RXJ1131 find evidence for differential lensing across
@@
 \includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
-\caption{Left: \old{\protect{Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
-the observed first moment map}}
-\new{\protect{Source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown 
+\caption{Left: \old{Source-plane positions from best-fit \mbox{\bco} lens models are indicated with their associated uncertainties atop
+the observed first moment map}
+\new{Source-plane positions obtained from the best-fit lens models (presented in \mbox{\Sec{lensmodel}}) are shown
 as markers color-coded by their velocities
-atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). }}
+atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). }
 The contours are at steps of 50\,\kms.
@@
 \fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
-\old{\protect{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}} \new{\protect{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
+\old{\mbox{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}} \new{\mbox{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
 dust mass of 16\petm{5}{12}\E{8}\,\Msun, \new{all of which are} uncorrected for lensing \new{magnification}.
@@
 for this model, we find a total IR luminosity
-\LIR (rest-frame 8\,$-$\,1000\,\micron) of \old{\protect{9.71\petm{6.14}{-6.05}\E{12}\,\Lsun}} \new{\protect{8.67\petm{5.27}{5.27}\E{12}\,\Lsun}},
-a \fir luminosity \LFIR of \old{\protect{4.72\petm{2.54}{2.26}\E{12}\,\Lsun}} \new{\protect{4.24\petm{2.17}{2.00}\E{12}\,\Lsun}} and a
-dust mass $M_{\rm dust}$ of \old{\protect{11\petm{5}{6}\E{8}\,\Msun}} \new{\protect{14\petm{5}{7}\E{8}\,\Msun}}, all of which are uncorrected for lensing.
+\LIR (rest-frame 8\,$-$\,1000\,\micron) of \old{\mbox{9.71\petm{6.14}{-6.05}\E{12}\,\Lsun}} \new{\mbox{8.67\petm{5.27}{5.27}\E{12}\,\Lsun}},
+a \fir luminosity \LFIR of \old{\mbox{4.72\petm{2.54}{2.26}\E{12}\,\Lsun}} \new{\mbox{4.24\petm{2.17}{2.00}\E{12}\,\Lsun}} and a
+dust mass $M_{\rm dust}$ of \old{\mbox{11\petm{5}{6}\E{8}\,\Msun}} \new{\mbox{14\petm{5}{7}\E{8}\,\Msun}}, all of which are uncorrected for lensing.
 Taken at face value, this implies an FIR-to-IR luminosity ratio
@@
 with (without) MIR constraint at 24\,$\micron$.
-The solid black line shows the best-fit SED model with dust attenuation \old{\protect{(light blue solid line)
-obtained using the \ncode{magphys} code.}}\new{\protect{obtained using the \ncode{magphys} code, whereas
-the light blue solid line shows the unattenuated stellar emission. }}
+The solid black line shows the best-fit SED model with dust attenuation \old{\mbox{(light blue solid line)
+obtained using the \ncode{magphys} code.}}\new{obtained using the \mbox{\ncode{magphys}} code, whereas
+the light blue solid line shows the unattenuated stellar emission. }
 \label{fig:SED}}
@@
 % , where the uncertainty is based on that of the gas mass.
-and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq\old{\protect{32\petm{7}{12}\% for RXJ1131}}\new{\protect{34\pmm16\% for the merger system (i.e., RXJ1131 and companion)}}.
+and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq\old{\mbox{32\petm{7}{12}\% for RXJ1131}}\new{\mbox{34\pmm16\%} for the merger system (i.e., RXJ1131 and companion)}.
 % The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
@@
 
-\old{\protect{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
+\old{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
 the central AGN, whereas this condition is not necessary for NLRs.
-From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
-median of 97\kms and a dispersion of 269\,\kms in the distribution of
-the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
+From an SDSS sample of $>$3800 quasars, \mbox{\citet{Richards02a}} find a
+median of \mbox{97\kms} and a dispersion of 269\,\mbox{\kms} in the distribution of
+the offset between \mbox{[Mg\,{\scriptsize II}] and [O\,{\scriptsize III}]} lines, suggesting
 that large offsets are uncommon. Nevertheless,
-offsets as large as $\sim$\,500\,\kms have been observed in some cases.}}
+offsets as large as $\sim$\,500\,\mbox{\kms} have been observed in some cases.}
 %% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
@@
 
-\old{\protect{Alternatively, large velocity offsets between emission lines of the
+\old{Alternatively, large velocity offsets between emission lines of the
 BLR and the NLR may arise in a recoiling black hole (BH),
@@
 where its BLR is moving at high velocity relative to the bulk of its host galaxy
-\citep{Madau04a, Bonning07a, Loeb07a}.
+\mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.
 A recoiling black hole is expected
@@
 Depending on their initial conditions, numerical relativity simulations have shown that
-the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
-Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
-SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
-One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
+the recoil velocity can reach up to \mbox{$\sim$4000\,\kms} for spinning BHs \mbox{\citep[\eg][]{Campanelli07a}}.
+Several sources have been proposed as recoiling BH candidates, such as CID-42 at \mbox{$z$\,=\,0.359 \citep{Civano10a}} and
+SDSS 0956+5127 at \mbox{$z$\,$\sim$\,0.714 \citep{Steinhardt12a}}.
+One notable system is SDSSJ0927+2943 at \mbox{$z$\,$\sim$\,0.713}, where
 a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
-have been observed \citep{Komossa08a},  similar to the case for RXJ1131.
-However, this scenario was recently refuted by \citet{Decarli14a}, who confirm that the
+have been observed \mbox{\citep{Komossa08a}},  similar to the case for RXJ1131.
+However, this scenario was recently refuted by \mbox{\citet{Decarli14a}}, who confirm that the
 BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
@@
 have been in a previous merger, which would also explain
-the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.}}
+the highly spinning BH in RX1131 \mbox{\citep[$a$\ssim0.9;][]{Reis14a}}.}
 
@@
 \subsection{The $M_{\rm BH}$$-$\mbulge Relation}
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\protect{$>$0.27\petm{11}{8}\%}} \new{\protect{$>$0.27\petm{0.11}{0.08}\%}}
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\mbox{$>$0.27\petm{11}{8}\%}} \new{\mbox{$>$0.27\petm{0.11}{0.08}\%}}
 using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
@@
 but the optical BLR lines are redshifted by \old{$\sim$780\,\kms}\new{$\sim$715\,\kms}.
-\old{\protect{This implies that the AGN is offset from the dynamical center of its host galaxy.
+\old{This implies that the AGN is offset from the dynamical center of its host galaxy.
 One explanation could be that the
@@
 Since the velocity offset between emission lines of the BLR and the NLR
-is typically $\sim$100\pmm270\,\kms,
+is typically \mbox{$\sim$100\pmm270\,\kms},
 we thus raise an alternative explanation of a recoiling black hole in RXJ1131, which
-would also explain the high spin parameter reported by \citet{Reis14a}.}}
+would also explain the high spin parameter reported by \mbox{\citet{Reis14a}}.}
 
 Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$>$\old{\protect{0.27\petm{11}{8}\%}}\new{\protect{0.27\petm{0.11}{0.08}\%}} for RXJ1131, providing
+$M_{\rm BH}$$/$$M_{\rm bulge}$$>$\old{\mbox{0.27\petm{11}{8}\%}}\new{\mbox{0.27\petm{0.11}{0.08}\%}} for RXJ1131, providing
 a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.

### 2016-11-17 WRITEUP/response.md
collected arguments regarding the recoil BH section

@@
 12) 
-a)
+a) We have removed the statement regarding "AGN dynamically offset".
 
-We have removed the statement regarding "AGN dynamically offset".
+Our CO measurement confirms that an offset between BLR and the systemic redshift, which is not known previously.
+We have updated this section, adding additional possible interpretation for the offset (e.g.
+gas inflows, geometric effects) in the discussion.
 
-# While the AGN may not be dynamically offset, given the possible scenario dirivng the BLR velocity offset, as pointed out by the referee, our CO measurement confirms that an offset between BLR and the systemic redshift, which is not known/constrained previously.
-We updated this section.
-The dynamical timescale of a recoiling black hole...
+We agree that it is unlikely that all objects with offset AGN lines are black hole recoils.
+Here, we are not asserting that the offset arises due to a recoiling black hole, we only discuss the possibility of such interpretation given the data (showing evidence of large offset between BLR and the systemic redshift as traced by our CO data), the high spin parameter, and theoretical expectation from hierarchical model of galaxy evolution, among other possible scenarios, as listed by the referee.
+
+We would greatly appreciate the referee if they can point us to a reference where it shows evidence of why the recoiling black hole scneario is highly unlikely and will gladly make the appropriate changes.
+
+3) Assuming that effects (e.g., inflow, geometric effect, micro-lensing) are accountable for part of the velocity offset, then the velocity offset of ~715 km/s would then be at most an upper limit on the line-of-sight velocity.
+Then  the true recoil velocity is thus most likely to be << 1000 km/s.
+Ignoring dynamical friction against stellar background and assuming t_recoil ~ 100 Myr, then the crude BH displacement estimate given in the referee report (~few 10kpc) would be possible (as pointed out to be theoretically possible
+by Bonning+07, Loeb07).
+However, Loeb07 also pointed out that at low ejection speeds (few hundred km/s), the deceleration of the BH (damped) by the external gravitational potential of the galaxy and by dynamical friction (Chandrasekhar 1943; Apj 97, 255) on the background stars, dark matter, and gas would limit the displacement of the slow-moving BH and tend to bring it back to the center of its host galaxy within a few dynamical times (see also Madau & Quataert 04 for analytic results and Boylan-Kolchin+04 for numerical results).
+Therefore the displacement given in the referee report is unlikely to hold (see also Guedes+11).
+
+Finally, again, we acknowledge that offsets between BLR and NLR lines are quite common in Seyferts and quasars, but typically not as big of an offset.
+In this paper, we only discuss possible scenarios and do not assert that any one of mentioned scenario is necessary in RXJ1131.
 

### 2016-11-17 WRITEUP/ms.tex
collected arguments regarding the recoil BH section

@@
 %Outflow:
-% Not AGN outflows because require different velocity offsets in Balmer and forbidden lines (Zamanov02a)
+% require different velocity offsets in Balmer and forbidden lines (Zamanov02a)
 % line origins:
@@
 \citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
-The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
-the \mgii emission line.
+The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and the \mgii emission line.
 Using the CO line center redshift as the systemic redshift,
@@
 On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
-
-% REFEREE: offset in BLR and NLR in RXJ1131 has been known before, not new for this paper
-%One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
-%the central AGN, whereas this condition is not necessary for NLRs.
-%From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
-%median of 97\kms and a dispersion of 269\,\kms in the distribution of
-%the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
-%that large offsets are uncommon. Nevertheless,
-%offsets as large as $\sim$\,500\,\kms have been observed in some cases.
-%%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
-%%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
-
-%Alternatively, large velocity offsets between emission lines of the
-%BLR and the NLR may arise in a recoiling black hole (BH),
-%% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines (e.g., Gaskell 1983; Bonning et al.
-2007; Eracleous et al.
-2012; Ju et al.
-2013; Shen et al.
-2013).
-%where its BLR is moving at high velocity relative to the bulk of its host galaxy
-%\citep{Madau04a, Bonning07a, Loeb07a}.
-%A recoiling black hole is expected
-%when a pair of uneven mass BH coalesce, during which their orbital energy is being released
-%as gravitational wave and a
-%non-zero net angular momentum is being carried away.
-%Depending on their initial conditions, numerical relativity simulations have shown that
-%the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
-%Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
-%SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
-%Since this model requires a merged BH, it would imply that RXJ1131 might
-%have been in a previous merger, which would also explain
-%the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
+Offset between BLR and NLR lines have been reported in literature, e.g., 
+\citet{Richards02a} find a
+median of 97\kms and a dispersion of 269\,\kms in the distribution of
+the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in an SDSS sample of $>$3800 quasars, 
+and \citet{Bonning07a} find a mean offset of 100\,\kms with a dispersion of 212\,\kms %FWHM = 500
+between the broad component of
+H$\beta$ and \oiii lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
+illustrating that large offsets ($\Delta v$$\gtrsim$\,500\,\kms) are uncommon but have been observed in some cases.
+%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
+%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
+
+Common interpretations used to explain the offset between optical and systemic redshift include
+e.g., outflow/inflow of gas in the BLR, 
+where the dominant component of the BLR linewidth
+is the rotation of the accretion disk, superimposed by an large inflow component, 
+or arising from the inclination angle of the (inner) accretion disk, where 
+clumps in the disk that is more edge-on block the far side, and thus only see the redshifted (for RXJ1131) 
+inflowing component on the BLR gas.
+{\bf DR: is it because of the large linewidth (one component of \mgii is $>$20000\kms, and broad comp.
+of H$\beta$ is $\sim$2000$-$4000\kms) that the referee thinks it's more likely to be inflow and therefore doesn't like the recoil black hole?}
+Additionally, microlensing in RXJ1131 \citep[\eg][]{Sluse07a, Sluse12a} may preferentially magnified the (red wing of the compact BLR 
+emission), and thus biasing the BLR line centroids.% , i.e., the redshift offset may not be a real one.
+% Sluse07: BLR with wide FWHM (> 2000\kms in \mgii and H$\beta$), one component of \mgii > 20000 \kms --> partial attentuation of the blue sides of the line could shift the apparent BLR line centroid to the red side.
+
+%  --------------- note --------------
+% recoil...
+% Given that there's an accretion disk (Dai+10, Pooley+07).., which could have been reform after the merging (in ~100 year; Bonning+07), then it would mean that the binary merged > blah years (presumably from previous encounter).
+% [ignore this] could also be currently a binary orbiting at high speed?
+(do we see multiple components in the BLR lines?
+Do we know that there's only a single BH from Xray?
+probably only 1 AGN, because otherwise we would see more complicated lensed QSO emission)
+%
+% Sluse07:  "This indicates that the flux in the NEL is partly resolved along the slit direction.
+On the other hand, we did not find a significant offset (i.e.
+offset <1 pixel) of the centroids of the NEL images w.r.t.
+to the centroid of the continuum emission.
+Using a SIE+?
+to model the lensing galaxy (Paper I), we calculate that the absence of such an offset implies an upper limit of roughly ?30h?1 pc on the off-centering of the [O III] emission w.r.t.
+the continuum emission."
+% --> so the NLR is only slightly spatially offset from the continuum, and therefore must be inflow and microlensing? 
+% --> but couldn't it still be recoil even if it's not spatially offset (perhaps unlikely?) e.g.
+Allen+15, Section 4.1 "the [O III] peaks do not coincide spatially with the X-ray sources, indicating that they may not be directly due to the two AGN, and suggest a bi-conical outflow as a likely alternative." << sounds like if the NLR is not co-spatial with the AGN, then could be outflow.
+whereas if referee thinks no spatial offset (Sluse+07) and therefore probably inflow rather than recoil AGN doesn't seem to hold.
+% ----> hmm, but I guess outflow could be spatially offset but not necessary for inflow.
+% --------------------------------------
+
+In hierarchical model of galaxy formation, supermassive black holes are formed by
+mergers, of which the majority took place at high redshifts. 
+% The most commonly used technique to find offset AGNs is to 
+% look for shifts between BLRs associated with the QSO and the NLR associated 
+% with the starlight from the galaxy. 
+We also discuss the possibility of a recoil black hole from previous episode of merger at earlier epoch \citep{Madau04a} leading to the offset... 
+Alternatively, the offset between the BLR and the systemic redshift 
+may be partially due to a kinematically offset AGN \citep{Hoffman & Loeb (2006)}, where
+BLRs are gravitationally bound to
+the central AGN (with a BLR dynamical timescale $\sim$10\E{2} years \citep{Bonning07a}, \ie can be quickly regenerated), 
+whereas this condition is not necessary for NLRs.
+% But Madau04a: a ~1e8\Msun BH in a $\sigma$\eq200\kms galaxy, the decay timescale due to dynamical friction is $<$ 1 Myr $<<$ Salpeter timescale, and so even for a kick velocity of v_CM\eq300\kms, the displacement is quite small $\lesssim$$R_{\rm BH}$\approx$10 pc.
+
+Alternatively, large velocity offsets between emission lines of the
+BLR and the NLR may arise in a recoiling black hole (BH),
+where its BLR is moving at high velocity relative to the bulk of its host galaxy
+\citep{Madau04a, Bonning07a, Loeb07a}.
+A recoiling black hole is expected % once they overcome the ``final pc problem'' by e.g. stellar dynamical hardening/hardening by 
+% dynamical friction against background stars, or viscous gas dynamical drag.
+when a pair of uneven mass BH coalesce, during which their orbital energy is being released
+as gravitational wave and a non-zero net angular momentum is being carried away.
+Depending on their initial conditions (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), numerical relativity simulations have shown that the recoil velocity can reach up to  $v_{\rm kick}$\ssim4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a},
+with a typical offset recoil velocity $v_{\rm kick}$ in the range of 100$-$500\,\kms 
+% based on simulations, and simulation constraints from the scatter in the local $M_{\rm BH}$$-$\mbulge relation
+\citep[\eg][]{Favata04a,Libeskind06a,Campanelli07a}.
+The black hole can therefore either leave the host galaxy (if vkick $>$ $v_{\rm esc}$) or 
+oscillate around the center of the galaxy, its orbit decaying because of dynamical friction 
+\citep[see \eg \citealt{Volonteri10a} for a discussion]{Bonning07a, Colpi14a}.
+
+% escape velocity
+$M_{\rm BH}$/\mstar\ssim1/375, $v_{\rm circ}$\ssim$v_{\rm rot}, then the upper limit of $v_{\rm kick}$\ssim2$\times$$v_{\rm circ}$, 
+assuming bulge escape velocity $v_{\rm esc}$\eq2.83$\v_{\rm circ}$ = 858\kms
+(in the case of a density profile of the spherical \citet{Hernquist90a} model for the stellar bulge component, 
+spherically symmetric isotropic model)%  \citep{BoylanKolchin04a}, 
+$v_esc$\eq2sqrt(2) *  $v_{\rm circ}$($r$\eq$a$), where r is the stellar bulge scale length, at most a few kpc, 
+therefore finding $v_esc$\eq BLAH\kms.
+$t_dyn$ would be 
+% Assuming know the rotation curve of RXJ1131 is similar to that MW, then at inner radius, we would expect $v_{\rm rot} (r=a)\gtrsim$ the extended 
+% gas disk rotation, given that we don't know precisely the stellar bulge scale length, if we assume 
+% $v_{\rm rot} (r=a)$\ssim$v_{\rm rot}$ of the gas disk, then v_esc ~ 860\kms. Therefore BH unlikely to escape anyway.
+
+In the case of gas-rich merger remnants, where large amounts of gas have been
+funneled to the central regions find that the MBHs remain within R$<$1\,kpc from the center
+of the host even for high recoil velocities ($v_{\rm kick}$\eq1200\,\kms) due to the compactness of the
+remnant galaxy?s nuclear disk" \citep{Mayer07a,Guedes08a}.
+Several outcomes of the recoiling blackholes include,
+a) In spherical bulges the black hole will oscillate right through the center, and return to the center after a few dynamical times, or 
+deplete or "heat up" the stars in the nucleus, reducing the efficiency of dynamical and extending the return time.
+% in gas-rich mergers, gas drag, duty cycle of the wandering AGN..
+% depending on the nuclear disk density profile, the MBH is unlikely to reach large distances
+%  the timescale for the recoiling hole to return to the center of its host galaxy depends very sensitively on the magnitude of the kick it receives, ranging from $\sim$10\E{6} yr for v_CM\eq200 \kms to more than 109 yr for v_CM \eq 400 \kms \citep{Madau04a}
+% Loeb07, Madau04a, Hoffman07: At low ejection speeds, the deceleration of the BH by the external gravitational potential of the galaxy and by dy- namical friction on the background stars and gas would limit the displacement of the slow-moving BH and tend to bring it back to the center of its host galaxy within a few dynamical times
+b) If the black hole is able to leave the bulge / ejected and enters a triaxial dark matter halo, it may not return at all within a Hubble time \citep{Guedes09a} and become intergalactic/naked black holes (but rare unless in recoil velocity $>>$ few thousands \kms, i.e., sufficient to escape the host galactic potential) \citep[\eg][]{Loeb07a}.
+% Volonteri+10: ejected BHs are rare at $z$$<$5, especially in wet-mergers
+%c) High resolution simulations of gas mergers (e.g.
+Mayer et al.
+2007) show that up to 60\% of the initial gas is funneled to the center of the remnant.
+In that particular simulation, the mass of the nuclear disk is Md = 3e9 Msun, and recoliing black holes with velocities of
+%$~$500 km/s are not able to escape the central region (scale length L=75 pc).
+
+Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a},
+SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}, and
+SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
+have been observed \citep{Komossa08a}.
+However, this scenario for SDSSJ0927+2943 was recently refuted by \citet{Decarli14a}, who find that the
+BLR lines in SDSSJ0927+2943 are indeed consistent with the CO systemic redshift.
+This is in contrast with RXJ1131, where our CO observations confirm the redshifted BLR.
+Since this model requires a merged BH, it would imply that RXJ1131 might
+have been in a previous merger, which might explain the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}. 
+% will spin up if major merger but would spin down in minor merger \citep{Gammie04a}, in general would spin down after merging.
+% Dave Chernoff: can spin up after merging
+The available data do not provide direct evidence favoring any of the above scenarios, 
+we therefore cannot rule out any of the above plausible scenarios; $\simless$ 1-kpc
+resolution observations probing the morphology, structures and kinematics of the (ionized) gas and stellar (e.g., via H$\alpha$ kinematics measurements) would be useful to distinguish between these scenarios.
+% I think sluse+07 constrained the size of BLR based on model and not really resolving down to those spatial resolution? e.g. not really see outflows
 

### 2016-11-17 WRITEUP/ms.tex
cleaned up a bit on the comments regarding recoil BH

@@
 illustrating that large offsets ($\Delta v$$\gtrsim$\,500\,\kms) are uncommon but have been observed in some cases.
-%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
-%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
 
@@
 Additionally, microlensing in RXJ1131 \citep[\eg][]{Sluse07a, Sluse12a} may preferentially magnified the (red wing of the compact BLR 
-emission), and thus biasing the BLR line centroids.% , i.e., the redshift offset may not be a real one.
-% Sluse07: BLR with wide FWHM (> 2000\kms in \mgii and H$\beta$), one component of \mgii > 20000 \kms --> partial attentuation of the blue sides of the line could shift the apparent BLR line centroid to the red side.
-
-%  --------------- note --------------
-% recoil...
-% Given that there's an accretion disk (Dai+10, Pooley+07).., which could have been reform after the merging (in ~100 year; Bonning+07), then it would mean that the binary merged > blah years (presumably from previous encounter).
-% [ignore this] could also be currently a binary orbiting at high speed?
-(do we see multiple components in the BLR lines?
-Do we know that there's only a single BH from Xray?
-probably only 1 AGN, because otherwise we would see more complicated lensed QSO emission)
-%
-% Sluse07:  "This indicates that the flux in the NEL is partly resolved along the slit direction.
-On the other hand, we did not find a significant offset (i.e.
-offset <1 pixel) of the centroids of the NEL images w.r.t.
-to the centroid of the continuum emission.
-Using a SIE+?
-to model the lensing galaxy (Paper I), we calculate that the absence of such an offset implies an upper limit of roughly ?30h?1 pc on the off-centering of the [O III] emission w.r.t.
-the continuum emission."
-% --> so the NLR is only slightly spatially offset from the continuum, and therefore must be inflow and microlensing? 
-% --> but couldn't it still be recoil even if it's not spatially offset (perhaps unlikely?) e.g.
-Allen+15, Section 4.1 "the [O III] peaks do not coincide spatially with the X-ray sources, indicating that they may not be directly due to the two AGN, and suggest a bi-conical outflow as a likely alternative." << sounds like if the NLR is not co-spatial with the AGN, then could be outflow.
-whereas if referee thinks no spatial offset (Sluse+07) and therefore probably inflow rather than recoil AGN doesn't seem to hold.
-% ----> hmm, but I guess outflow could be spatially offset but not necessary for inflow.
-% --------------------------------------
-
-In hierarchical model of galaxy formation, supermassive black holes are formed by
+emission), and thus biasing the BLR line centroids.
+
+In hierarchical model of galaxy formation, supermassive black holes are formed in
 mergers, of which the majority took place at high redshifts. 
-% The most commonly used technique to find offset AGNs is to 
-% look for shifts between BLRs associated with the QSO and the NLR associated 
-% with the starlight from the galaxy. 
 We also discuss the possibility of a recoil black hole from previous episode of merger at earlier epoch \citep{Madau04a} leading to the offset... 
 Alternatively, the offset between the BLR and the systemic redshift 
-may be partially due to a kinematically offset AGN \citep{Hoffman & Loeb (2006)}, where
+may be partially due to a kinematically offset AGN \citep{Hoffman06a}, where
 BLRs are gravitationally bound to
@@
 whereas this condition is not necessary for NLRs.
-% But Madau04a: a ~1e8\Msun BH in a $\sigma$\eq200\kms galaxy, the decay timescale due to dynamical friction is $<$ 1 Myr $<<$ Salpeter timescale, and so even for a kick velocity of v_CM\eq300\kms, the displacement is quite small $\lesssim$$R_{\rm BH}$\approx$10 pc.
 
@@
 \citep{Madau04a, Bonning07a, Loeb07a}.
-A recoiling black hole is expected % once they overcome the ``final pc problem'' by e.g. stellar dynamical hardening/hardening by 
-% dynamical friction against background stars, or viscous gas dynamical drag.
+A recoiling black hole is expected 
 when a pair of uneven mass BH coalesce, during which their orbital energy is being released
@@
 with a typical offset recoil velocity $v_{\rm kick}$ in the range of 100$-$500\,\kms 
-% based on simulations, and simulation constraints from the scatter in the local $M_{\rm BH}$$-$\mbulge relation
 \citep[\eg][]{Favata04a,Libeskind06a,Campanelli07a}.
@@
 deplete or "heat up" the stars in the nucleus, reducing the efficiency of dynamical and extending the return time.
-% in gas-rich mergers, gas drag, duty cycle of the wandering AGN..
-% depending on the nuclear disk density profile, the MBH is unlikely to reach large distances
-%  the timescale for the recoiling hole to return to the center of its host galaxy depends very sensitively on the magnitude of the kick it receives, ranging from $\sim$10\E{6} yr for v_CM\eq200 \kms to more than 109 yr for v_CM \eq 400 \kms \citep{Madau04a}
-% Loeb07, Madau04a, Hoffman07: At low ejection speeds, the deceleration of the BH by the external gravitational potential of the galaxy and by dy- namical friction on the background stars and gas would limit the displacement of the slow-moving BH and tend to bring it back to the center of its host galaxy within a few dynamical times
 b) If the black hole is able to leave the bulge / ejected and enters a triaxial dark matter halo, it may not return at all within a Hubble time \citep{Guedes09a} and become intergalactic/naked black holes (but rare unless in recoil velocity $>>$ few thousands \kms, i.e., sufficient to escape the host galactic potential) \citep[\eg][]{Loeb07a}.
-% Volonteri+10: ejected BHs are rare at $z$$<$5, especially in wet-mergers
 %c) High resolution simulations of gas mergers (e.g.
@@
 have been in a previous merger, which might explain the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}. 
-% will spin up if major merger but would spin down in minor merger \citep{Gammie04a}, in general would spin down after merging.
-% Dave Chernoff: can spin up after merging
 The available data do not provide direct evidence favoring any of the above scenarios, 
@@
 resolution observations probing the morphology, structures and kinematics of the (ionized) gas and stellar (e.g., via H$\alpha$ kinematics measurements) would be useful to distinguish between these scenarios.
-% I think sluse+07 constrained the size of BLR based on model and not really resolving down to those spatial resolution? e.g. not really see outflows
 

### 2016-11-18 WRITEUP/ms.tex
only keep necessary stuff for recoil

--- 2016-11-15 WRITEUP/ms.tex
@@
 On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
-
-% REFEREE: offset in BLR and NLR in RXJ1131 has been known before, not new for this paper
-%One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
-%the central AGN, whereas this condition is not necessary for NLRs.
-%From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
-%median of 97\kms and a dispersion of 269\,\kms in the distribution of
-%the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
-%that large offsets are uncommon. Nevertheless,
-%offsets as large as $\sim$\,500\,\kms have been observed in some cases.
-%%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
-%%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
-
-%Alternatively, large velocity offsets between emission lines of the
-%BLR and the NLR may arise in a recoiling black hole (BH),
-%% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines (e.g., Gaskell 1983; Bonning et al.
-2007; Eracleous et al.
-2012; Ju et al.
-2013; Shen et al.
-2013).
-%where its BLR is moving at high velocity relative to the bulk of its host galaxy
-%\citep{Madau04a, Bonning07a, Loeb07a}.
-%A recoiling black hole is expected
-%when a pair of uneven mass BH coalesce, during which their orbital energy is being released
-%as gravitational wave and a
-%non-zero net angular momentum is being carried away.
-%Depending on their initial conditions, numerical relativity simulations have shown that
-%the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
-%Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
-%SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
-%Since this model requires a merged BH, it would imply that RXJ1131 might
-%have been in a previous merger, which would also explain
-%the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
+Offset between BLR and NLR lines have been reported in literature, e.g., 
+\citet{Richards02a} find a
+median of 97\kms and a dispersion of 269\,\kms in the distribution of
+the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in an SDSS sample of $>$3800 quasars, 
+and \citet{Bonning07a} find a mean offset of 100\,\kms with a dispersion of 212\,\kms %FWHM = 500
+between the broad component of
+H$\beta$ and \oiii lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
+illustrating that large offsets ($\Delta v$$\gtrsim$\,500\,\kms) are uncommon but have been observed in some cases.
+
+Common interpretations invoked to explain offsets between BLR and systemic redshifts include
+e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing angle towards the accretion disk, 
+inclination effect, in which clumps in the accretion disk may block emission towards the far side of the disk, and thus the observed BLR emission is only
+originating from
+the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
+In the latter, \citet{Sluse07a} report a covering factor of 20\% based on \mgii absorption line at $z$\eq0.654.
+Additionally, differentially lensing of the compact BLR emission by microlensing in RXJ1131\citep[\eg][]{Sluse07a, Sluse12a} 
+may have boosted the redshifted component more than the blueshifted component,
+thereby biasing the BLR line centroids towards longer wavelengths.
+{\bf DR: is it because of the large linewidth (one component of \mgii is $>$20000\kms, and broad comp.
+of H$\beta$ is $\sim$2000$-$4000\kms) that the referee thinks it's more likely to be inflow and therefore doesn't like the recoil black hole?
+Sluse07:
+"Another remarkable result is the presence in our spectra of a \mgii absorption doublet blueshifted at $z$\eq0.654. 
+According to its velocity shift ($\Delta v$\ssim$-$660\,\kms). 
+These lines disappear from the spectrum ratios A/B and C/B.
+This indicates that the absorbed flux is proportional to the flux coming from the continuum+BLR.
+This implies that the region at the origin of the absorption must cover both the continuum and the BLRs and that, within the uncertainties, their depths are identical in the spectra of the three images A, B, and C."
+ok.. so is it because of this broad absorption component of \mgii that is at the same $z$ as the NLR lines, and therefore implying that the BLR and 
+the AGN is not really spatially and kinematically offset, 
+but the offset is truly just a manifestation of a rotating disk + other kinematics (+ absorption of continuum by BLR moving towards us, redshfiting the line centroid, + inflow of material + clumps blocking the far side inflow?)
+}
+
+Alternatively, the observed offset %between the BLR and the systemic redshift (and the NLR)
+may be explained by a more extreme scenario of a recoiling black hole (BH), 
+where its BLR is moving at high velocity relative to the bulk of its host galaxy
+\citep{Madau04a, Bonning07a, Loeb07a}.
+% where
+% BLRs are gravitationally bound to
+% the AGN (with a BLR dynamical timescale $\sim$10\E{2} years \citep{Bonning07a}, \ie can be quickly regenerated), 
+% whereas this condition is not necessary for NLRs.
+%
+% In hierarchical model of galaxy formation, supermassive black holes are expected to form through
+% mergers, of which the majority took place at high redshifts. 
+A recoiling black hole is expected
+when a pair of uneven mass BH coalesce, during which their orbital energy is being released
+as gravitational wave and a non-zero net angular momentum is being carried away.
+Depending on their initial conditions (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
+numerical relativity simulations have shown that the recoil velocity can reach up to 
+$v_{\rm kick}$\ssim4000\,\kms for spinning BHs, % \citep[\eg][]{Campanelli07a}, 
+with a typical offset recoil velocity of $v_{\rm kick}$\ssim100\,$-$\,500\,\kms 
+\citep[\eg][]{Libeskind06a,Campanelli07a}.
+% ------------- fate ----------------
+% Several outcomes of the recoiling blackholes include,
+% a) In spherical bulges the black hole will oscillate right through the center, and return to the center after a few dynamical times, or 
+% deplete or "heat up" the stars in the nucleus, reducing the efficiency of dynamical and extending the return time.
+% b) If the black hole is able to leave the bulge / ejected and enters a triaxial dark matter halo, it may not return at all within a Hubble time \citep{Guedes09a} and become intergalactic/naked black holes (but rare unless in recoil velocity $>>$ few thousands \kms, i.e., sufficient to escape the host galactic potential) \citep[\eg][]{Loeb07a}.
+%c) High resolution simulations of gas mergers (e.g.
+Mayer et al.
+2007) show that up to 60\% of the initial gas is funneled to the center of the remnant.
+In that particular simulation, the mass of the nuclear disk is Md = 3e9 Msun, and recoliing black holes with velocities of
+%$~$500 km/s are not able to escape the central region (scale length L=75 pc).
+% In the case of gas-rich merger remnants, where large amounts of gas have been
+% funneled to the central regions find that the MBHs remain within R$<$1\,kpc from the center
+% of the host even for high recoil velocities ($v_{\rm kick}$\eq1200\,\kms) due to the compactness of the
+% remnant galaxy's nuclear disk" \citep{Mayer07a,Guedes08a}.
+% ----------------------------------------
+%A recoiling black hole may therefore 
+%oscillate around the center of the galaxy as its orbit is decaying due to dynamical friction, 
+%or leave its host galaxy if $v_{\rm kick}$$\gg$$v_{\rm esc}$ and dynamical friction is inefficient 
+%\citep[see \eg \citealt{Volonteri10a} for a discussion]{Guedes09a,Bonning07a, Colpi14a}. 
+%% escape velocity
+%If we assume a \citet{Hernquist90a} profile for the stellar bulge in RXJ1131, 
+%%$M_{\rm BH}$/\mstar\ssim1/375, $v_{\rm circ}$\ssim$v_{\rm rot}, 
+%% then the upper limit of $v_{\rm kick}$\ssim2$\times$$v_{\rm circ}$, 
+%% bulge escape velocity $v_{\rm esc}$\eq2.83$\v_{\rm circ}$ = 858\kms
+%% %(in the case of a density profile of the spherical \citet{Hernquist90a} model for the stellar bulge, 
+%% %spherically symmetric isotropic model)%  \citep{BoylanKolchin04a}, 
+%then the escape velocity $v_{\rm esc}$\eq2$\sqrt{2}$$v_{\rm circ}$, where $v_{\rm circ}$ is the velocity
+%at $r$\eq$a$, the stellar bulge scale length that is at most a few kpc.
+%Assuming that the rotation curve of RXJ1131 is similar to that MW, then at inner radius ($\lesssim$ few kpc), 
+%we would expect $v_{\rm rot} (r=a)\gtrsim$$v_{\rm rot}$ of the extended gas disk (see \Sec{dynamics}).
+%Given that we don't know precisely the stellar bulge scale length, if we assume 
+%$v_{\rm rot} (r=a)$\ssim$v_{\rm rot}$ of the gas disk, then $v_{\rm esc}$\ssim860\,\kms. 
+%Therefore, the recoil BH in RXJ1131 is unlikely to escape its gas-rich host galaxy.%  \citep[\eg][]{Loeb07a, Volonteri10a}.
+Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a},
+SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}, and
+SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
+have been observed \citep{Komossa08a}.
+However, this scenario for SDSSJ0927+2943 was recently refuted by \citet{Decarli14a}, who find that the
+BLR lines in SDSSJ0927+2943 are indeed consistent with the CO systemic redshift.
+This is in contrast with RXJ1131, where our CO observations confirm the redshifted BLR.
+Since this scenario requires a coalesced BH, it would imply that RXJ1131 
+is a product of previous merger, which is not implausible and 
+might also explain the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
+
+The available data do not provide direct evidence favoring any of the above scenarios, 
+we therefore cannot rule out any of the above plausible scenarios; $\lesssim$1-kpc
+resolution observations probing the morphology, structures and kinematics of the (ionized) gas and 
+stellar (e.g., via H$\alpha$ kinematics measurements) would be useful to distinguish between these scenarios.
 

### 2016-11-18 WRITEUP/ms.tex
clean up comments regarding fate of recoil BH

@@
 
-Alternatively, the observed offset %between the BLR and the systemic redshift (and the NLR)
+Alternatively, the observed offset 
 may be explained by a more extreme scenario of a recoiling black hole (BH), 
@@
 \citep{Madau04a, Bonning07a, Loeb07a}.
-% where
-% BLRs are gravitationally bound to
-% the AGN (with a BLR dynamical timescale $\sim$10\E{2} years \citep{Bonning07a}, \ie can be quickly regenerated), 
-% whereas this condition is not necessary for NLRs.
-%
-% In hierarchical model of galaxy formation, supermassive black holes are expected to form through
-% mergers, of which the majority took place at high redshifts. 
 A recoiling black hole is expected
@@
 numerical relativity simulations have shown that the recoil velocity can reach up to 
-$v_{\rm kick}$\ssim4000\,\kms for spinning BHs, % \citep[\eg][]{Campanelli07a}, 
+$v_{\rm kick}$\ssim4000\,\kms for spinning BHs, 
 with a typical offset recoil velocity of $v_{\rm kick}$\ssim100\,$-$\,500\,\kms 
 \citep[\eg][]{Libeskind06a,Campanelli07a}.
-% ------------- fate ----------------
-% Several outcomes of the recoiling blackholes include,
-% a) In spherical bulges the black hole will oscillate right through the center, and return to the center after a few dynamical times, or 
-% deplete or "heat up" the stars in the nucleus, reducing the efficiency of dynamical and extending the return time.
-% b) If the black hole is able to leave the bulge / ejected and enters a triaxial dark matter halo, it may not return at all within a Hubble time \citep{Guedes09a} and become intergalactic/naked black holes (but rare unless in recoil velocity $>>$ few thousands \kms, i.e., sufficient to escape the host galactic potential) \citep[\eg][]{Loeb07a}.
-%c) High resolution simulations of gas mergers (e.g.
-Mayer et al.
-2007) show that up to 60\% of the initial gas is funneled to the center of the remnant.
-In that particular simulation, the mass of the nuclear disk is Md = 3e9 Msun, and recoliing black holes with velocities of
-%$~$500 km/s are not able to escape the central region (scale length L=75 pc).
-% In the case of gas-rich merger remnants, where large amounts of gas have been
-% funneled to the central regions find that the MBHs remain within R$<$1\,kpc from the center
-% of the host even for high recoil velocities ($v_{\rm kick}$\eq1200\,\kms) due to the compactness of the
-% remnant galaxy's nuclear disk" \citep{Mayer07a,Guedes08a}.
-% ----------------------------------------
-%A recoiling black hole may therefore 
-%oscillate around the center of the galaxy as its orbit is decaying due to dynamical friction, 
-%or leave its host galaxy if $v_{\rm kick}$$\gg$$v_{\rm esc}$ and dynamical friction is inefficient 
-%\citep[see \eg \citealt{Volonteri10a} for a discussion]{Guedes09a,Bonning07a, Colpi14a}. 
-%% escape velocity
-%If we assume a \citet{Hernquist90a} profile for the stellar bulge in RXJ1131, 
-%%$M_{\rm BH}$/\mstar\ssim1/375, $v_{\rm circ}$\ssim$v_{\rm rot}, 
-%% then the upper limit of $v_{\rm kick}$\ssim2$\times$$v_{\rm circ}$, 
-%% bulge escape velocity $v_{\rm esc}$\eq2.83$\v_{\rm circ}$ = 858\kms
-%% %(in the case of a density profile of the spherical \citet{Hernquist90a} model for the stellar bulge, 
-%% %spherically symmetric isotropic model)%  \citep{BoylanKolchin04a}, 
-%then the escape velocity $v_{\rm esc}$\eq2$\sqrt{2}$$v_{\rm circ}$, where $v_{\rm circ}$ is the velocity
-%at $r$\eq$a$, the stellar bulge scale length that is at most a few kpc.
-%Assuming that the rotation curve of RXJ1131 is similar to that MW, then at inner radius ($\lesssim$ few kpc), 
-%we would expect $v_{\rm rot} (r=a)\gtrsim$$v_{\rm rot}$ of the extended gas disk (see \Sec{dynamics}).
-%Given that we don't know precisely the stellar bulge scale length, if we assume 
-%$v_{\rm rot} (r=a)$\ssim$v_{\rm rot}$ of the gas disk, then $v_{\rm esc}$\ssim860\,\kms. 
-%Therefore, the recoil BH in RXJ1131 is unlikely to escape its gas-rich host galaxy.%  \citep[\eg][]{Loeb07a, Volonteri10a}.
 Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a},

### 2016-11-18 WRITEUP/diff.tex
ready to send to DR

@@
 
-\subsection{Systemic Redshift and Velocity Offset}
+\subsection{\texorpdfstring{\st{Velocity Offset and a Recoiling Black Hole}}{ } Systemic Redshift and Velocity Offset}
 %Outflow:
@@
 the \mgii emission line.
-Using the CO line center redshift as the \old{systematic} \new{systemic} redshift,
-we find that the redshift of the first set is fully consistent with the systemic redshift. This
+Using the CO line center redshift as the systemic redshift,
+we find that the redshift of the first set is fully consistent with the \old{systematic} \new{systemic} redshift. This
 supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
@@
 \new{On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.}
-
 \old{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
 the central AGN, whereas this condition is not necessary for NLRs.
-From an SDSS sample of $>$3800 quasars, \mbox{\citet{Richards02a}} find a
-median of \mbox{97\kms} and a dispersion of 269\,\mbox{\kms} in the distribution of
-the offset between \mbox{[Mg\,{\scriptsize II}] and [O\,{\scriptsize III}]} lines, suggesting
+From an SDSS sample of $>$3800 quasars, \mbox{\citet{Richards02a}} find a}
+\new{Offset between BLR and NLR lines have been reported in literature, e.g., 
+\citet{Richards02a} find a}
+ median of 97\kms and a dispersion of \mbox{269\,\kms} in the distribution of
+\old{the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
 that large offsets are uncommon. Nevertheless,
-offsets as large as $\sim$\,500\,\mbox{\kms} have been observed in some cases.}
-%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
-%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
+offsets as large as \mbox{$\sim$\,500\,\kms} have been observed in some cases.}
+\new{the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in an SDSS sample of $>$3800 quasars, 
+and \mbox{\citet{Bonning07a}} find a mean offset of \mbox{100\,\kms} with a dispersion of \mbox{212\,\kms} %FWHM = 500
+between the broad component of
+\mbox{H$\beta$ and [O\,{\scriptsize III}]} lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
+illustrating that large offsets (\mbox{$\Delta v$$\gtrsim$\,500\,\kms}) are uncommon but have been observed in some cases.}
+
+\new{Common interpretations invoked to explain offsets between BLR and systemic redshifts include
+e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing angle towards the accretion disk, 
+inclination effect, in which clumps in the accretion disk may block emission towards the far side of the disk, and thus the observed BLR emission is only
+originating from
+the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
+In the latter, \citet{Sluse07a} report a covering factor of 20\% based on \mgii absorption line at $z$\eq0.654.
+Additionally, differentially lensing of the compact BLR emission by microlensing in RXJ1131\citep[\eg][]{Sluse07a, Sluse12a} 
+may have boosted the redshifted component more than the blueshifted component,
+thereby biasing the BLR line centroids towards longer wavelengths.}
+{\bf DR: is it because of the large linewidth (one component of \mgii is $>$20000\kms, and broad comp.
+of H$\beta$ is $\sim$2000$-$4000\kms) that the referee thinks it's more likely to be inflow and therefore doesn't like the recoil black hole?
+Sluse07:
+"Another remarkable result is the presence in our spectra of a \mgii absorption doublet blueshifted at $z$\eq0.654. 
+According to its velocity shift ($\Delta v$\ssim$-$660\,\kms). 
+These lines disappear from the spectrum ratios A/B and C/B.
+This indicates that the absorbed flux is proportional to the flux coming from the continuum+BLR.
+This implies that the region at the origin of the absorption must cover both the continuum and the BLRs and that, within the uncertainties, their depths are identical in the spectra of the three images A, B, and C."
+ok.. so is it because of this broad absorption component of \mgii that is at the same $z$ as the NLR lines, and therefore implying that the BLR and 
+the AGN is not really spatially and kinematically offset, 
+but the offset is truly just a manifestation of a rotating disk + other kinematics (+ absorption of continuum by BLR moving towards us, redshfiting the line centroid, + inflow of material + clumps blocking the far side inflow?)
+}
 
 \old{Alternatively, large velocity offsets between emission lines of the
-BLR and the NLR may arise in a recoiling black hole (BH),
-% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines e.g., Gaskell 1983; Bonning et al.
-2007; Eracleous et al.
-2012; Ju et al.
-2013; Shen et al.
-2013).
+BLR and the NLR may arise in a recoiling black hole (BH),}
+\new{Alternatively, the observed offset 
+may be explained by a more extreme scenario of a recoiling black hole (BH),}
 where its BLR is moving at high velocity relative to the bulk of its host galaxy
@@
 non-zero net angular momentum is being carried away.
-Depending on their initial conditions, numerical relativity simulations have shown that
-the recoil velocity can reach up to \mbox{$\sim$4000\,\kms} for spinning BHs \mbox{\citep[\eg][]{Campanelli07a}}.
+Depending on their initial conditions \new{(e.g., black hole mass ratio, spin-orbit orientation, spin magnitude)}, numerical relativity simulations have shown that
+the recoil velocity can reach up to \mbox{$\sim$4000\,\kms} for spinning BHs\old{\mbox{\citep[\eg][]{Campanelli07a}}}\new{,with a typical offset recoil velocity of $v_{\rm kick}$\ssim100\,$-$\,500\,\kms
+\mbox{\citep[\eg][]{Libeskind06a,Campanelli07a}}}.
 Several sources have been proposed as recoiling BH candidates, such as CID-42 at \mbox{$z$\,=\,0.359 \citep{Civano10a}} and
-SDSS 0956+5127 at \mbox{$z$\,$\sim$\,0.714 \citep{Steinhardt12a}}.
-One notable system is SDSSJ0927+2943 at \mbox{$z$\,$\sim$\,0.713}, where
+SDSS 0956+5127 at \mbox{$z$\,$\sim$\,0.714 \citep{Steinhardt12a}}\old{. One notable system is}\new{, and} SDSSJ0927+2943 at \mbox{$z$\,$\sim$\,0.713}, where
 a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
-have been observed \mbox{\citep{Komossa08a}},  similar to the case for RXJ1131.
+have been observed \mbox{\citep{Komossa08a}}\old{, similar to the case for RXJ1131}.
 However, this scenario was recently refuted by \mbox{\citet{Decarli14a}}, who confirm that the
 BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
-This is in contrast with RXJ1131, where our CO observations confirm the blueshifted BLR.
-Since this model requires a merged BH, it would imply that RXJ1131 might
-have been in a previous merger, which would also explain
-the highly spinning BH in RX1131 \mbox{\citep[$a$\ssim0.9;][]{Reis14a}}.}
-
-% REFEREE: offset in BLR and NLR in RXJ1131 has been known before, not new for this paper
-%One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
-%the central AGN, whereas this condition is not necessary for NLRs.
-%From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
-%median of 97\kms and a dispersion of 269\,\kms in the distribution of
-%the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
-%that large offsets are uncommon. Nevertheless,
-%offsets as large as $\sim$\,500\,\kms have been observed in some cases.
-%%% In an SDSS sample of ongoing mergers at $z$\,$<$\,0.21, AGN lines are offset by $\lesssim$410\,km/s
-%%\citep[\eg][]{Richards02a, Comerford14a}. % between AGN lines (forbidden, Balmer) and stellar absorption
-
-%Alternatively, large velocity offsets between emission lines of the
-%BLR and the NLR may arise in a recoiling black hole (BH),
-%% recoiling SMBHs as well as subparsec-scale binary SMBHs produce velocity offsets in the broad AGN emission lines and not the narrow AGN emission lines (e.g., Gaskell 1983; Bonning et al.
-2007; Eracleous et al.
-2012; Ju et al.
-2013; Shen et al.
-2013).
-%where its BLR is moving at high velocity relative to the bulk of its host galaxy
-%\citep{Madau04a, Bonning07a, Loeb07a}.
-%A recoiling black hole is expected
-%when a pair of uneven mass BH coalesce, during which their orbital energy is being released
-%as gravitational wave and a
-%non-zero net angular momentum is being carried away.
-%Depending on their initial conditions, numerical relativity simulations have shown that
-%the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
-%Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
-%SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
-%Since this model requires a merged BH, it would imply that RXJ1131 might
-%have been in a previous merger, which would also explain
-%the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
+This is in contrast with RXJ1131, where our CO observations confirm the \old{blueshifted}\new{redshifted} BLR.
+\old{Since this model requires a merged BH, it would imply that RXJ1131 might
+have been in a previous merger, which would also} 
+\new{Since this scenario requires a coalesced BH, it would imply that RXJ1131 
+is a product of previous merger, which is not implausible and 
+might also} explain the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
+
+\new{The available data do not provide direct evidence favoring any of the above scenarios, 
+we therefore cannot rule out any of the above plausible scenarios; $\lesssim$1-kpc
+resolution observations probing the morphology, structures and kinematics of the (ionized) gas and 
+stellar (e.g., via H$\alpha$ kinematics measurements) would be useful to distinguish between these scenarios.}
 
@@
 that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are redshifted by \old{$\sim$780\,\kms}\new{$\sim$715\,\kms}.
+but the optical BLR lines are redshifted by \old{$\sim$780\,\kms}\new{$\sim$715\,\kms}.{\bf MAY ADD STUFF ABOUT RECOIL BH..}
 \old{This implies that the AGN is offset from the dynamical center of its host galaxy.

### 2016-11-18 WRITEUP/ms.tex
update conclusion about recoil, put place holder to remind self to update
ready to send to DR

@@
 between the broad component of
-H$\beta$ and \oiii lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
+H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
 illustrating that large offsets ($\Delta v$$\gtrsim$\,500\,\kms) are uncommon but have been observed in some cases.
@@
 that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are redshifted by $\sim$715\,\kms.
+but the optical BLR lines are redshifted by $\sim$715\,\kms. {\bf MAY ADD STUFF ABOUT RECOIL BH..}
 

### 2016-11-18 WRITEUP/diff.tex
update markup to other colors to be less intimidating

@@
 \definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
-\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
-\newcommand{\old}[1]{\textcolor{airforceblue}{\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
+\newcommand{\new}[1]{\textcolor{blue}{\uwave{#1}}}
+\newcommand{\old}[1]{\textcolor{red}{\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
 % -----------------------------------------------------------------------------------------------
@@
 \section{Results} \label{sec:results}
-\new{The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
-\input{table_obsprop}}
+\new{The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.}
+\input{table_obsprop}
 
@@
 at $\gtrsim$\,27$\sigma$ significance, \old{confirming the redshift at $z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.} \new{enabling us to constrain its redshift at
-$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to
-the de-lensed spectrum, which is shown in \Fig{delensed}.
-% instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our
-% redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
-}}. \old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
+$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to
+the de-lensed spectrum, which is shown in \Fig{delensed}}.}}
+\old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
 with a highly asymmetric double-horned line profile
-as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
+as shown in \mbox{\Fig{CO21spec}}. Fitting a double Gaussian results in peak
 flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
@@
 varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
-\new{\protect{Previous studies of RXJ1131 find evidence for differential lensing across
+\new{Previous studies of RXJ1131 find evidence for differential lensing across
 the {\it HST} $V$-, $I$-, and $H$-bands, where the
-magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
-Here, we find that the highly asymmetric \bco line profile is predominantly a result of
+magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
+Here, we find that the highly asymmetric \mbox{\bco} line profile is predominantly a result of
 differential lensing, where the redshifted emission is apparently much brighter than the
 blueshifted component, as indicated by the difference in their magnification factor $(\mu_{\rm L})$, which
-varies from 8.7 to 3.1 across the \bco line (\Tab{model}).
+varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model})}.
 A secondary effect contributing to the asymmetry is caused by
-the CO emission in the companion in the redshifted velocity channels.}}
+the CO emission in the companion in the redshifted velocity channels.}
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
@@
 \section{Discussion} \label{sec:diss}
-\new{The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}.
-\input{table_propRXJ}}
+\new{The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}}.
+\input{table_propRXJ}
 
@@
 \new{Offset between BLR and NLR lines have been reported in literature, e.g., 
-\citet{Richards02a} find a}
+\mbox{\citet{Richards02a}} find a}
  median of 97\kms and a dispersion of \mbox{269\,\kms} in the distribution of
@@
 the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
-In the latter, \citet{Sluse07a} report a covering factor of 20\% based on \mgii absorption line at $z$\eq0.654.
-Additionally, differentially lensing of the compact BLR emission by microlensing in RXJ1131\citep[\eg][]{Sluse07a, Sluse12a} 
+In the latter, \mbox{\citet{Sluse07a}} report a covering factor of 20\% based on \mbox{\mgii} absorption line at $z$\eq0.654.
+Additionally, differentially lensing of the compact BLR emission by microlensing in RXJ1131 \mbox{\citep[\eg][]{Sluse07a, Sluse12a}}
 may have boosted the redshifted component more than the blueshifted component,

### 2016-11-18 WRITEUP/response.md
combine referee report w/ response

@@
 
-1a) We have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXS\,J1131-1231".
+COMMENTS IN DETAIL:
+
+1) TOO MANY "DYNAMICS" AND "DYNAMICAL".
+
+You may be mis-using the word "dynamical" in some places.
+"Dynamics" refers to the effects of a force, or forces, in 
+causing motions, or in reaching equilibrium.
+
+So if you are mainly talking about velocities, it would be 
+better to say "velocities" or "kinematics" instead of "dynamics".
+
+1a): CHANGE THE TITLE : DROP THE WORD "DYNAMICS" :
+
+The Title says the paper is about the "dynamics" of the molecular gas in the 
+quasar host galaxy.
+
+Most of the paper, however, is not about the "dynamics" at all, 
+but rather about the CO detections,
+the VLA continuum map (synchrotron emission, not molecular gas), 
+the spectral energy distribution in the optical, near-IR, mid-IR, and far-IR continuum,
+and the gravitational lens model.
+
+I suggest that you consider changing the title, to better describe the
+contents of the paper, maybe something like:
+
+"CO-Line, Radio Continuum, Optical-to-Far-IR Observations, and Lens Models of
+the Host Galaxy of the Quasar RXS J1131-1231"
+
+or maybe:
+
+"Interpretation of CO, Radio, Optical, and IR Continuum 
+observations of the Strongly Lensed Host Galaxy of the 
+Quasar RXS J1131-1231"
+
+or simply:
+
+"CO, Radio, Optical, and IR results on 
+the Lensed Host Galaxy of the Quasar RXS J1131-1231".
+
+# RESPONSE:
+1a) We have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXSJ1131-1231".
 We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (incl.
@@
 
-1b) We took this suggestion. To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".
+1b) DROP "DYNAMICALLY RESOLVED":
 
-1c) We took this suggestion and have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig.
-5).
+Sect.3.1, paragraph 1:
 
-1d) We took this suggestion and have changed "dynamical information" to "kinematic information", "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".
+"The emission is spatially and dynamically resolved...as shown in Fig. 1 "
+
+"Dynamically resolved" sounds strange. 
+The reader might confuse it with the dynamic range.
+Maybe change to :
+
+"The line emission is resolved, in both velocity (Fig. 1) and 
+in its spatial distribution (Fig. 2).
+
+# RESPONSE:
+We took this suggestion. To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".
+
+1c) DROP "DYNAMICAL CENTER":
+
+Fig.3, caption:
+"...z = 0.6537, which corresponds to the dynamical center of CO(2-1)."
+
+Change to :
+
+"..which corresponds to zero velocity in the CO(2-1) spectum (Fig.1)."
+
+# RESPONSE:
+We took this suggestion and have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig. 5).
+
+1d): DROP "RECONSTRUCT THE DYNAMICS" :
+
+Sect.4.1, para.1:
+
+Too many "dynamics" in this paragraph.
+
+"...the high spectral resolution .. provides dynamical information 
+on scales smaller than the beam ..."
+
+Maybe change to "velocity information" or "kinematic information".
+
+"...we reconstruct the intrinsic gas dynamics by carrying out 
+lens modeling over different channel slices..."
+
+You are not reconstructing the "dynamics", 
+you are reconstructing the intrinsic spectral profile, by separately 
+deriving the lens magnifications in seven different velocity channels.
+
+As you say in the Abstract, this shows that the asymmetric line profile
+(red peak stronger than blue peak) is actually symmetric.
+
+I don't think this is reconstructing the "dynamics."
+The "dynamics" stays the same --- rotation in a gravitational force field.
+
+You have just reconstructed the line shape, that's all.
+
+Contrary to what you say in Sect.4.1, this is actually not 
+"similar" to the "differential lensing ...across the HST V, I and H bands (Claeskens+ 2006)
+
+They talk about different magnification due to varying sizes of different temperature regions.
+In the Claeskens reconstruction, the blue light (redshifted to V band) comes from young hot stars 
+in a nuclear starburst ring --- see their sect.5.2, point 4.
+
+The V-band source is smaller (more compact) than the cooler regions in I and H bands,
+in the larger spiral disk farther from the nucleus.
+
+So, they interpret the different magnifications as due to different sizes in the source plane.
+
+This is not the same as magnification varying across the line profile,
+due to different source-plane positions, as you are claiming.
+
+# RESPONSE:
+We took this suggestion and have changed "dynamical information" to "kinematic information", "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".
 
@@
 
-2a) We took this suggestion and have corrected nu_LO --> nu_obs.
+2) FIX THE REDSHIFT. IT SHOULD BE 0.6541 .
 
-2b) We took this suggestion and re-fitted a doubled Gaussian to the de-lensed profile (Fig.
+Your beautiful CO(2-1) spectrum gives the best measurement 
+so far of the qso host galaxy redshift,
+more precise than the optical spectra.
+
+For this reason, you should make a little extra effort to get it exactly right.
+
+2a. OBSERVED FREQUENCY, NOT LO FREQUENCY.
+
+Sect.2.1, para. 1:
+
+You say nu_LO = 139.256 GHz.
+But this is your observed frequency, not the LO frequency.
+It corresponds to CO(2-1) redshifted to 0.6555.
+
+What probably happened was this:
+
+a) You say that you first observed at CARMA (Feb.2014).
+At CARMA, your sensitivity was only good enough to see the red peak, and not the blue one.
+From the CARMA data, you derived the wrong redshift of z = 0.6555.
+
+b) You say that you then observed at IRAM (later, in Dec.2014 and Feb.2015).
+Because you already had the (incorrect) redshift from CARMA, 
+you set the IRAM observing frequency to the wrong redshift of 0.6555 (139.256 GHz),
+
+Then, with the better sensitivity at IRAM, you discovered that the true line profile 
+was actually centered closer to z = 0.6537 (139.4074 GHz).
+
+c) Later on, you re-reduced the data, this time with zero velocity corresponding 
+to z = 0.6537, for all the figures in this paper.
+
+d) But your Fig.1 (CO 2-1 spectrum), and especially, 
+Fig.5 (both spectra, yellow and blue histograms),
+show clearly that the line centroid is at +75 km/s relative to zero velocity.
+
+e) At redshifted CO(2-1), there are 2.15 km/s per MHz, so the true line centroid 
+is 34.88 MHz lower than your assumed zero frequency, and 
+so the true line centroid is at 139.373 GHz.
+
+f) This corresponds to z = 0.6541, as the true redshift of the host galaxy.
+
+g) SUGGESTED CHANGES :
+
+Sect.3.1, para.1: 
+"...confirming the redshift at z = 0.6537..."
+
+--- change to:
+"...showing that the line centroid is at a redshift of z = 0.6541..."
+
+Fig.3 caption:
+"The velocity scale is with respect to z=0.6537, which corresponds to the dynamical center..."
+
+--- change to:
+"The zero of the velocity scale is at z=0.6537, which is close to the 
+true centroid of the CO(2-1) line at z=0.6541 ...
+
+Sect.4.5 para.2:
+
+---Possibly re-do the fit, relative to a zero velocity at z = 0.6541, as this will change
+the V_max in your p-v diagram (Fig.9, right panel).
+
+--- Or else just explain that the V_0 in your Eq(1) comes out to +28 km/s (relative to z=0.6537)
+because of the very coarse sampling of your seven 108 km/s-wide bins.
+
+The true line center (relative to z=0.6537) would be at V_0 = +75 km/s if you had
+used the full-resolution spectrum (Fig. 1 or Fig.5), rather than the heavily binned channels.
+
+# RESPONSE:
+We have corrected nu_LO --> nu_obs.
+
+We took this suggestion and re-fitted a doubled Gaussian to the de-lensed profile (Fig.
 5) and updated the redshift and replotted all the relavent figures (and updated their captions correspondingly), updated column 1 in Table 3, the labeling in Fig 7, refitted the model shown in Fig.
@@
 
-3) 
+3) CO(2-1) FLUX AND SOURCE SIZE :
+
+Sect. 3.1, para.1: CO(2-1) LINE FLUX :
+
+You say the 2-Gaussian fit gives :
+red peak = 75.3 mJy (do you mean mJy/beam?), FWHM=179 km/s,
+and blue peak = 24 mJy (do you mean mJy/beam?), FWHM = 255 km/s.
+
+This gives 1.06 x 75.3 x 179 /1000 = 14.3 Jy km/s for the red peak,
+and gives 1.06 x 24.1 x 255 /1000 = 6.5 Jy km/s for the blue peak.
+
+So the sum of the two peaks is 20.8 Jy km/s, not the value of 24.1 Jy km/s in the text.
+
+Or, are the values you quote for two Gaussian components only the values at the top pixel of the map?
+That is, not spatially integrated, while the 24.1 Jy km/s is spatially integrated?
+You need to make this clear, both in the text, and in the caption to Fig.1.
+
+If Fig.1 shows only the spectrum at the source maximum, and not the 
+spatially integrated spectrum, then you need to change the label on the vertical axis 
+to Flux density per beam [ mJy /beam ].
+
+In the re-plot of the CO(2-1) spectrum that you give in Fig.5 (yellow histogram),
+the redshifted peak is now 100 mJy, not 75, as in Fig.1.
+
+Does Fig.5 now show the spatially integrated spectrum ? 
+What is the difference between this spectrum and the one in Fig.1?
+
+If it is again a spectrum taken at the maximum-intensity point,
+then the units on the vertical axis would again have to be [ mJy/beam ].
+
+In Fig.5,it would be good to show what you think is the contribution from the companion galaxy.
+
+# RESPONSE:
 We found a bug in generating the map used for previous line-integrated flux extraction.
@@
 
+Sect. 3.1, para.3: SOURCE SIZE :
+
+I don't think you can measure source size to three significant figures,
+especially if you measure the beam-smoothed sizes in the image plane,
+and then try to estimate the deconvolved sizes by doing root square
+subtraction of the beam sizes (if that's what you did).
+
+An advantage of an interferometer is that you can 
+do fits to the source size in the u,v plane, without having
+to deconvolve the beam.
+
+Because the whole process is uncertain, 
+instead of saying " 5.1 +/- 0.72 by 3.72 +/- 0.66 ",
+you could just say 5.1 +/- 0.7 by 3.7 +/- 0.7 .
+
+This is especially true because you say in the next sentence, that the 
+emission is not a 2-D Gaussian, so the fitted model is anyway 
+not correct.
+
+But an even bigger problem is that these values look like the observed (not deconvolved)
+major and minor axis sizes (FWHM) on the integrated map in Fig.2 (upper left).
+
+Are you sure that you have deconvolved these sizes? For a 4.4" x 2" beam?
+
+Please check this.
+
+Even better, try doing a fit in the u,v plane, rather than the sky plane.
+
+Here's another problem with the source size:
+In Sect.1, para.3, you say the stellar emission in the host galaxy of RXJ1131 is 
+lensed into an Einstein ring of radius 1.83" (diameter = 3.66"). 
+So the length of the arc is about 4 or 5 arcsec.
+
+In Table 3, you say the median magnification is a factor of 5.5.
+
+This means the de-magnified CO source DIAMETER is about 1 arcsec.
+
+At z = 0.654, 1 arcsec is 7 kpc.
+
+So the de-magnified RADIUS of the CO source is only 3.5 kpc.
+
+It looks like the intrinsic R_CO = 6 kpc (diameter = 12 kpc)
+that you quote elsewhere in the paper is too high:
+---Abstract, 
+---Sect.4.3, para.3, 
+---Sect.4.4, para.1, 
+---Sect.5.1.1, para.2,
+---Sect.5.5, para.2
+---Sect.5.1.1, para.2,
+---Sect.6, para.2
+
+# RESPONSE:
 Source size: We fitted a single Guassian in uv-plane to support the reported CO size based on image plane fitting, of which the convolved size is 6.6+/-0.5 x 4.5+/-0.3.
@@
 
-4) While the most extreme peak to peak noise is ~100 mJy/beam, the noise varies across channels, and therefore, on average, sigma is lower across all channels.
+4) ERRORS ON CO(3-2):
+
+Sect. 3.2, para 1: 
+"We detect CO(3-2) ... in the CARMA data at > 5 sigma significance."(Fig.3).
+
+Something is wrong here. In Fig.3, the peak-to-peak noise 
+in 36 km/s channels, is 100 mJy/beam. 
+This means 1 sigma is 25 mJy/b.
+
+This disagrees with Sect.2.2, para.3, which says 1 sigma is 
+only 13.3 mJy/b in 36 km/s (25 MHz).
+
+So, while the positive-velocity peak in Fig.3 is 4 or 5-sigma,
+the negative velocity peak is only 2 or 3-sigma, so not really significant.
+
+Without knowledge of the CO(2-1) spectrum,
+the negative-velocity peak at CO(3-2) could not be called a real detection.
+
+Maybe change the first sentence of Sect.3.2 to read:
+
+"We detect CO(3-2) ... in the CARMA data at 5-sigma significance
+on the positive-velocity peak. 
+Within the noise limits, the CO(3-2) spectrum (Fig.3) may be
+consistent with the double-peak profile seen in CO(2-1) (Fig.1)."
+
+Because of the large errors in the CO(3-2) flux, you should not
+quote the flux and the errors to three significant figures (Sect. 3.2).
+
+Instead of saying "35.7 +/- 21.9, 
+you could just say 36 +/- 22 .
+
+Similarly, in the same paragraph, for the (3-2) / (2-1) ratio,
+you could just say 0.7 +/- 0.4 .
+
+In Sect.3.2, para.1, you say the observing frequency is 209 GHz.
+So the wavelength is 1.4mm, not 1.5mm. 
+(There are two places to fix this).
+
+#RESPONSE
+While the most extreme peak to peak noise is ~100 mJy/beam, the noise varies across channels, and therefore, on average, sigma is lower across all channels.
 Thus, the uncertainty is more representative using those obtained from the integrated map.
@@
 
-5) 
+5) ERRORS ON THE 2MM CONTINUUM FLUX OF RXJ 1131:
+Sect. 3.3, para.1:
+The wavelengths should be 1.4mm for the CARMA data (not 1.5mm),
+and 2.2mm for the IRAM data.
+
+Sect.3.3, para.2: 
+"We adopt 0.39 +/- 0.08 mJy as the 2mm continuum ...."
+
+But Table 1 lists "0.400 +/- 0.082 " as the flux.
+
+Both of these entries are wrong.
+
+In Sect.3.3, para.2, you say :
+
+integrated flux = 1.2 +/- 0.2 mJy, 
+peak flux = 0.8 +/- 0.09 mJy/b at the lensing galaxy. (round off the 0.799 +/- 0.088).
+
+You subtract a model point source at the lensing galaxy.
+
+This gives a residual of (1.2 - 0.8) = 0.4 mJy.
+
+But since this is a subtraction, you have to add the errors 
+in the integrated flux (0.2 mJy)
+to the errors in the possible point source (0.09 mJy) to get
+the total uncertainty range in the residual.
+
+So the flux of the residual is 0.4 +/- 0.3 mJy, 
+not the +/- 0.08 mJy, 
+which is only the raw rms in the unsubtracted data.
+
+This means the 2mm continuum "detection" of the lensed arc (Fig.4 upper)
+may not be real. 
+On the map in Fig.4, it is only a bend in the lowest contour (3-sigma), 
+so not really significant.
+
+It might be better to rewrite Sect.3.3, para.2 to say something like:
+
+"We detect 2mm continuum with an integrated flux density of 1.2+/-0.2 mJy,
+with a peak flux of 0.80+/-0.09 mJy/beam, centered on the lensing galaxy.
+In the lowest contour (3-sigma), there is a hint of possible emission
+from the lensed arc."
+
+Instead of calling this the "deblending procedure",
+which people might confuse with deconvolution, 
+I would just call it "subtraction of the foreground galaxy", 
+or "flux removal by subtraction", because it is just simple 
+subtraction, not anything else.
+
+# RESPONSE
 We updated the 2mm flux in Table 1. We updated the flux uncertainty to include those from the uv-fitting process.
@@
 
-6) While the large uncertainty on the flux density of the background source at 2mm results in a spectral index with a large uncertainty, this nevertheless is a constraint on the radio-mm spectral slope: our value of -0.345 is flatter than the typical spectral index for pure synchrotron emission, suggesting that the 2mm has a non-negligible contribution from the underlying free-free emission.
+6) DROP THE SPECTRAL INDEX FOR THE BACKGROUND GALAXY :
+
+Sect.3.3, para.3:
+
+Given the large uncertainty in the residual flux, I don't think
+you can derive a 6cm-to-2mm spectral index for the background galaxy.
+I suggest dropping that part of the sentence:
+(" alpha = -0.345 for the background galaxy ")
+
+If the 2mm continuum flux is synchrotron emission, like the 6cm VLA continuum flux,
+then it is probably unrelated to the stellar mass of the quasar host galaxy.
+
+So I don't understand why you use it in sect.4.5, para.4 to fit 
+the Bruzual & Charlot stellar templates.
+
+Any comment on the very flat spectrum for the lensing elliptical galaxy ?
+Is the 6cm emission mainly synchrotron? 
+Is the 2mm emission a mix of synchrotron flux and dust flux ?
+
+# RESPONSE:
+While the large uncertainty on the flux density of the background source at 2mm results in a spectral index with a large uncertainty, this nevertheless is a constraint on the radio-mm spectral slope: our value of -0.345 is flatter than the typical spectral index for pure synchrotron emission, suggesting that the 2mm has a non-negligible contribution from the underlying free-free emission.
 We have also added an additional statement stating that if there is a non-negligible contribution from the background source contributing to the peak flux, then the derived spectral index for the background source would be shallower, and therefore increasing the fraction of free-free emission over synchrotron at 2mm.
@@
 
-7) We adopted the suggestions.
+7) BETTER LABELS FOR FIGURE 6 AND TABLE 3 :
 
-8) We adopted the suggestions and have added additional tables summarizing the observed CO line properties and the derived physical parameters.
+Figure 6 and Table 3 are hard to understand, because
+there are no velocity labels on Fig.6, and because the order 
+of the channels in the Figure (most redshifted first, most blueshifted last),
+is the opposite of the order in Table 3 
+(most blueshifted first, most redshifted last).
 
-9) It is of standard practice to report flux measurmenets from interferometric observations excluding those from the absolute flux calibration.
+The easiest way to fix this would be to :
+
+a) Put some velocity labels on Fig. 6, at least the center velocity
+of each of the seven channels.
+
+b) Reverse the order of the channels in Table 3
+(change to most redshifted first, most blueshifted last), to 
+agree with the order in Fig.6.
+
+# RESPONSE
+We adopted the suggestions.
+
+8) NEED A TABLE TO SUMMARIZE THE CO RESULTS
+
+There are tables where one can find :
+
+--- the continuum photometry data (Table 1),
+
+--- the model lens parameters (Table 2; please add the mass of the lens to this Table,
+even though it is not an independent parameter; otherwise people have to search
+for it in the text),
+
+--- the model magnification factors (Table 3; possibly add the derived source offset positions),
+
+--- the fits to the IR continuum SED (Table 4).
+
+But there is no table that gives a quick summary of the 
+CO results, --- even though they are a large part of the paper.
+
+I suggest that you add a Table, that as a minimum, might give:
+
+--- the CO(2-1) velocities, linewidths, peak fluxes, line-integrated fluxes,
+and spatially integrated fluxes.
+
+--- the CO(3-2) similar parameters (when possible).
+
+--- the L'co luminosities corrected for lensing (RXJ1131 + companion).
+
+--- the M(H2) estimated from the CO luminosity (main source + companion).
+
+The same is true of the derived quantities. 
+Possible add another Table summarizing the other derived quantites:
+
+--- R_CO (max) ---From whatever is the best method to estimate it.
+
+--- the M_stellar and SFR ---From the SED fitting.
+
+--- the M_dyn If R = 6 kpc and V = 245 km/s (??)
+
+--- the M_gas / M_dyn ratio
+
+--- the M_gas / M_stars ratio
+
+--- the black hole mass
+
+--- the M_BH / M_bulge ratio.
+
+Otherwise, the reader has to search for all these CO values and other quantities in 
+many different parts of the text.
+
+# RESPONSE:
+We adopted the suggestions and have added additional tables summarizing the observed CO line properties and the derived physical parameters.
+
+9. TABLE 1, ERROR BARS :
+
+In Sect.2.1, you say the calibration accuracy at 2mm is 15 per cent;
+in Sect.2.3, you say the calibration accuracy at 6cm is 10 per cent.
+
+So in Table 1, the 2mm continuum flux error should include the 
+10% measuring error plus the 15% calibration error, which add
+as sqrt(sum of squares of percent errors) = 18%.
+
+So S(2mm) = 0.80 +/- 0.14 .
+
+Similarly, the 6cm continuum flux error should be the 3% measuring 
+error plus the 10% calibration error (root sum squares) = 10.4%.
+
+So S(6cm) = 0.87 +/- 0.09 .
+
+So you need not quote these fluxes to three decimal places.
+
+Because of these flux errors, you also cannot quote the spectral
+index of the foreground galaxy to three decimal places
+(Sect. 3.3, last sentence).
+
+# RESPONSE:
+It is of standard practice to report flux measurmenets from interferometric observations excluding those from the absolute flux calibration.
 To address the referee's concern, we have added a remark in Section 3.3, table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.
@@
 
-10) We have replotted the figure with different contour intervals with thinner lines and added a sentence in the caption to improve clarify of Fig 4.
+10. FIGURE 4, CAPTION (VLA MAP) :
 
-11) We have corrected "blueshifted" to "redshifted", udpated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.
+Because the lensing galaxy is so strong on the VLA map (Fig.4), one
+cannot count the contours on the central source. 
+So in the caption, 
+it might be good to say how many contours there are up to the peak
+(= 22 contours ?), and that this corresponds to a flux of 0.9 mJy/b.
 
-12) 
+An alternative would be to change the contour step after 3 contours
+in the VLA map, so that the higher contours would become visible.
+
+But it is probably easiest to just explain the peak value in 
+the figure caption.
+
+# RESPONSE
+We have replotted the figure with different contour intervals with thinner lines and added a sentence in the caption to improve clarify of Fig 4.
+
+11. THE BLR LINES ARE REDSHIFTED, NOT BLUESHIFTED.
+
+Sect.5.3, para.1:
+Note that Sluse et al. (2007, their sect.7.2) say the Mg absorption doublet is at 0.654.
+Sluse et al (their sect.9, Conclusions) also say the narrow emission lines (the NLR)
+are measured to be at 0.654.
+
+So in Sect.5.3,par.1 you should quote them correctly as saying that the first set of lines
+is at z = 0.654 (not 0.653).
+
+The 1st set of lines (NLR) is at z = 0.654 (not 0.653).
+The 2nd set of lines (BLR) is at z = 0.658 (they are more redshifted).
+
+So this sentence is wrong:
+
+"On the other hand, the second set of lines is blueshifted by 780 km/s,.."
+
+This should read "redshifted", not "blueshifted."
+
+(The 780 km/s is also wrong, 
+it should be 700 km/s, see below)
+
+"Using the CO line center redshift as the systemic redshift,
+we find that the redshift of the first set is fully consistent
+with the "systematic" redshift.
+
+--- Change "systematic" to "systemic".
+
+Sect.5.3, para.3, 2nd sentence from end:
+
+Also wrong, here.
+
+Should be "... our CO observations confirm the redshifted BLR lines."
+
+not "blueshifted".
+
+# RESPONSE:
+We have corrected "blueshifted" to "redshifted", udpated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.
+
+12. DROP THE "BLACK HOLE RECOIL" SECTION.
+
+You might consider dropping this section entirely.
+
+---The two redshift systems (NLR and BLR) in this quasar have
+been known for a long time. 
+So the possibility that the NLR-BLR difference is due to a black hole recoil is not 
+a new result of your CO-line data, or of your lens modeling, 
+which is the main topic of this paper.
+
+---There are many quasars where the BLR redshifts are measured 
+to be slightly different from the NLR redshifts.
+Sometimes they are more redshifted, sometimes they are more blueshifted.
+It is implausible that they all indicate black hole recoils.
+
+---There is a large literature on the redshift differences between
+the NLR and BLR lines 
+(see e.g., Gaskell, 2009, New Astronomy Reviews, 53, 140; 
+Gaskell & Goosmann 2015; Gaskell, Klimek & Nazarova 2007). 
+There has been a lot of numerical modeling to explain these differences.
+
+Many simulations favor an inflow of the BLR gas
+into the black hole, at a true space velocity of 1000 km/s.
+
+In the BLR, we are actually observing the matter that is flowing into
+the black hole. The dominant component in the BLR linewidths is the
+rotation of the accretion disk, but there is also an inflow component,
+that causes the redshift difference from the NLR lines.
+
+In the simulations, whether the difference is is a blueshift or a redshift
+depends on the orientation to the line of sight and the "moving mirror" effect of
+the scattering opacity, as well as the clumpiness, etc.
+
+A redshift could result from the disk being more edge-on to our line-of-sight, so 
+that clumps in the disk itself block the far side. In this case, we mainly see
+the near side, so we see the redshifted inflow component into the black hole.
+
+In the outer parts of the accretion disk, where the density is lower,
+there is also a bi-conical outflow, as observed in BAL quasars.
+
+Your phrase 
+"...indicating that the BLR of the AGN is "dynamically" offset..."
+
+is not really true. In many current models of the BLR, the region is 
+not dynamically offset at all.
+
+The accretion disk rotates around the black hole, and has exactly the same 
+cosmological redshift as the host galaxy.
+
+Besides the dominant rotational component, there is also an inflow component, 
+that shifts the peak of the line. 
+The BLR lines are optically thin, so they go as density squared, 
+so the line peak comes from the inner part of the accretion disk, 
+where density is highest, 
+and where gas flows into the black hole.
+
+For RXJ1131, the picture is further complicated by 
+the gravitational lensing, and by the microlensing:
+
+1) MICROLENSING :
+
+Because the NLR is big (100 pc), it is not affected by microlensing.
+Because the BLR is small, it is affected by
+microlensing in this quasar (Sluse et al.).
+
+It could also be that the microlensing more strongly magnifies
+the redshifted part of the BLR lines, 
+biasing the apparent redshift to the red side.
+
+2) BLUE SIDE OF THE LINE ATTENUATED BY ABSORPTION :
+
+Another possiblity is that the BLR shows mainly rotation 
+in the accretion disk, and also a biconical outflow region
+from the outer parts of the accretion disk, as in the BAL phenomenon.
+
+Because of partial, very broad, absorption of the blueshifted flow against the 
+AGN continuum, we see stronger emission from the redshifted flow.
+
+Because the system 2 BLR lines in RXJ1131 are very wide (10000 to 20000 km/s), partial
+attenuation of the blue sides of the lines could easily shift the apparent 
+BLR line centroids toward the red sides of their profiles.
+
+3) UNLIKELY RECOIL VELOCITY :
+
+If the line-of-sight recoil velocity really were 700 km/s, then 
+the true space velocity must be even higher, and certainly greater than 
+the escape velocity from the host galaxy.
+
+If it is about 1000 km/s, then the black hole moves 1 pc in 1000 years.
+
+So in one rotation time of the host galaxy, 
+or in one orbital time of the companion galaxy, 
+or in the duration of the starburst, 
+or in the duration of the "wet merger" 
+(all of these are ~1E8 years), 
+the black hole would have moved quite far away from the center of the host galaxy
+(10 to 100 kpc !).
+
+This also makes the recoil story implausible, especially for 
+many other catalogued quasars and Seyfert galaxies that have differences
+between the peaks of the NLR lines and the BLR lines.
+
+# RESPONSE:
 a) We have removed the statement regarding "AGN dynamically offset".
@@
 
-b & c) The details of the model (e.g. how we reconstruct the likelihood functions) are already referenced in other papers. We did not discuss any of that in this paper.
+TWO FURTHER SUGGESTIONS FOR SHORTENING THE PAPER:
+
+b) ---Drop the detailed description of the best-fit procedures
+(The Markov chain Monte Carlo paragraph in Sect.4.1, paragraph 3).
+
+c) ---Drop the details of the SED fitting procedure in Sect.4.5, 
+(especially in the 2nd half of paragraph 1: 
+"We impose a uniform prior"...and all the text that follows.)
+
+Both of these sections are very well-written, but will probably be
+completely incomprehensible to many readers (including me).
+
+I suggest that you just say that you did best fits to model the lens distribution
+and best fits to the SED. 
+Simply give a typical reference to the Markov chain, Monte Carlo method.
+
+# RESPONSE:
+The details of the model (e.g. how we reconstruct the likelihood functions) are already referenced in other papers. We did not discuss any of that in this paper.
 
@@
 
-13) We updated f_gas and f_mol using M_gas and M_dyn of both RXJ1131+companion , i.e., as a merger system.
+13. FIX THE CONCLUSIONS
+
+Sect.6, para.2: NUMBERS SLIGHTLY INCONSISTENT:
+
+You derive M_gas = 1.38E10 Msun, 
+and also M_dyn = 8E10 Msun.
+
+So the ratio f_gas = M_gas / M_dyn = 16.6 percent, not 19 percent.
+
+(This also has to be corrected in the Abstract, and in Sect.5.1.2, para.1).
+
+Sect.6, para.4: DROP THE BLACK HOLE RECOIL STORY.
+
+"...but the optical BLR lines are blueshifted by 780 km/s."
+
+Also wrong here. The BLR lines are redshifted, not blueshifted :
+
+BLR = 0.658 (Sect.5.3, para.1);
+
+CO = 0.6541, NLR lines = 0.654 (Sect.5.3).
+
+If CO(2-1) were at z = 0.658, its frequency would be 139.046 GHz.
+True CO(2-1) is at z = 0.6541, so its frequency is 139.373 GHz.
+
+So the apparent z = 0.658 is 327 MHz lower in frequency than systemic,
+which corresponds to a Doppler velocity = 327 x 2.151 km/s/MHz,
+
+or V_doppler = 703 km/s higher in velocity (more redshifted)
+than the true CO(2-1) velocity centroid at z = 0.6541.
+
+So the BLR lines should be "redshifted by 700 km/s" (not 780 km/s).
+
+OMIT THE REST OF THIS PARAGRAPH,
+
+starting with "This implies that the AGN is offset from the dynamical
+center of its host galaxy." all the way to the end to the paragraph.
+
+This is not true. The AGN could be at the center of the galaxy,
+and the Doppler shift could just be a radial component (inflow),
+superposed on the very fast rotational velocity of the accretion disk.
+
+# RESPONSE:
+We updated f_gas and f_mol using M_gas and M_dyn of both RXJ1131+companion , i.e., as a merger system.
 
@@
 
-14) 
+14. CHANGE FIG.9, (Left Panel) : DROP THE VELOCITY MOMENT MAP (SAME AS FIG.2)
+
+I found Fig.9 (left) very confusing.
+
+You should drop the velocity moment map (its the same map as in Fig.2, anyway), 
+and instead, only plot the little crosses
+in the source plane, on a more blown-up RA-Dec scale, so the crosses would be more visible.
+
+The diagram is confusing because the moment map is the final observed result 
+in the sky plane, after lensing, 
+with lensed positions quite different from the original positions in the source plane.
+
+Furthermore, the moment map has a weighting of velocities 
+that is biased by the differential lensing, so that the 
+red velocities get higher weighting than the blue velocities.
+
+All of this distorted image in the sky plane gets even further distorted 
+by convolution with the quite large 4.4" x 2.0" synthesized beam.
+
+The little crosses, however, are model positions (not observed data, unlike the moment map)
+in the source plane (not the sky plane),
+before lensing, without any intensity weighting, 
+and before any convolution with the instrumental beam.
+
+Because this figure is about the result of the best-fit lens models, and because the 
+little crosses are the basis for the model p-v curve in the right panel (and not the 
+contours on the moment map), 
+it would be better to concentrate on the model results in the source plane,
+and drop the confusing moment map in the image plane, and drop the synthesized beam ellipse.
+
+That way, on a blown-up diagram, you would have room to put velocity labels on each of the
+little crosses, so they could be more easily related to the p-v diagram in the right panel.
+
+Could another interpretation be that instead of tracing a monotonic p-v diagram,
+there are, within the errors, just two little clusters of points in the left panel?
+---The upper (red wing) cluster and the lower (blue wing) cluster?
+Within the errors, the 3 crosses in the red clump almost agree in position,
+and the 4 crosses in the blue clump almost agree in position, as well.
+
+The separation between the centroids of the two clusters of points is 1 arcsec, or 7 kpc.
+So if this is a central disk, then within the errors, its radius is only 3.5 kpc, not 
+the 6 kpc that you quote in many places in the text.
+
+Why do these two clusters of points in Fig.9 (left) not appear in your
+p-v diagram in Fig.9 (right)?
+In the right panel, why do all the little crosses seem to be evenly spaced?
+Is the right panel based on an additional model of a rotating disk, rather than 
+the lens model points in Fig.9 (left)?
+
+# RESPONSE:
 Indeed, the plot on the left is to demonstrate that despite the observed 1st moment map is distorted due to a combination of differential lensing (in which the red velocity are more heavily weighed) and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kienamtic components, as shown atop of the observed map.

### 2016-11-18 WRITEUP/response.md
typos

@@
 The literature/archival data of the continuum would not be as meaningful without our CO data, e.g.
-their emission does not convey inforamtion about the kinematics, spatial distribution, and does not give a broader picture regarding the f_gas evolution, which is one of the main conclusions found in this study.
+their emission does not convey information about the kinematics, spatial distribution, and does not give a broader picture regarding the f_gas evolution, which is one of the main conclusions found in this study.
 
@@
 
-"..which corresponds to zero velocity in the CO(2-1) spectum (Fig.1)."
+"..which corresponds to zero velocity in the CO(2-1) spectrum (Fig.1)."
 
@@
 We took this suggestion and re-fitted a doubled Gaussian to the de-lensed profile (Fig.
-5) and updated the redshift and replotted all the relavent figures (and updated their captions correspondingly), updated column 1 in Table 3, the labeling in Fig 7, refitted the model shown in Fig.
+5) and updated the redshift and replotted all the relevant figures (and updated their captions correspondingly), updated column 1 in Table 3, the labeling in Fig 7, refitted the model shown in Fig.
 9 and updated parameters in Sec 4.3 correspondingly, SED fitting, etc.
@@
 We found a bug in generating the map used for previous line-integrated flux extraction.
-In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes in the relavent channels, which is in agreement with the double-Gaussian fit to the spatially extracted spectrum (Fig.
+In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes in the relevant channels, which is in agreement with the double-Gaussian fit to the spatially extracted spectrum (Fig.
 1).
@@
 
-While the additioanl figure in I_CO is not significant, we keep this 
+While the additional figure in I_CO is not significant, we keep this 
 to enable reproducible results and to minimize cumulative errors (e.g. when compiled for a larger number of samples). We only report significant figures when reporting the physical parameters.
@@
 It simply is Data-Model, which is > 4 sigma than the noise.
-This together with the co-spatial emission supports that flux contributiion from the background source to the total integrated 2mm continuum.
+This together with the co-spatial emission supports that flux contribution from the background source to the total integrated 2mm continuum.
 
@@
 
-We note that 0.27 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the unceratinties, where this uncertainty included in the fit included those from absolute flux calibration.
+We note that 0.27 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the uncertainties, where this uncertainty included in the fit included those from absolute flux calibration.
 Therefore changes to the physical parameters are only at most a few percent,  we have updated the numbers but this does not alter the conclusions of this paper.
@@
 # RESPONSE:
-It is of standard practice to report flux measurmenets from interferometric observations excluding those from the absolute flux calibration.
+It is of standard practice to report flux measurements from interferometric observations excluding those from the absolute flux calibration.
 To address the referee's concern, we have added a remark in Section 3.3, table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.
@@
 # RESPONSE:
-We have corrected "blueshifted" to "redshifted", udpated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.
+We have corrected "blueshifted" to "redshifted", updated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.
 
@@
 
-We would greatly appreciate the referee if they can point us to a reference where it shows evidence of why the recoiling black hole scneario is highly unlikely and will gladly make the appropriate changes.
+We would greatly appreciate the referee if they can point us to a reference where it shows evidence of why the recoiling black hole scenario is highly unlikely and will gladly make the appropriate changes.
 
@@
 # RESPONSE:
-Indeed, the plot on the left is to demonstrate that despite the observed 1st moment map is distorted due to a combination of differential lensing (in which the red velocity are more heavily weighed) and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kienamtic components, as shown atop of the observed map.
+Indeed, the plot on the left is to demonstrate that despite the observed 1st moment map is distorted due to a combination of differential lensing (in which the red velocity are more heavily weighed) and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kinematic components, as shown atop of the observed map.
 The reconstructed information displays a clear velocity gradient.
@@
 As discussed in Sec 4.1.1, we have detailed the evidence and reasons for which we interpret RXJ1131 as a disk galaxy.
-Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraphy of Sec 4.3).
+Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraph of Sec 4.3).
 
@@
 Clumps:
-With the evidence and reasons listed in the begining of Sec 4.3, the reconstructed source-plane distribution is unlikely to be just two kinematically-ordered clumps rather than a single rotating disk.
+With the evidence and reasons listed in the beginning of Sec 4.3, the reconstructed source-plane distribution is unlikely to be just two kinematically-ordered clumps rather than a single rotating disk.

### 2016-11-22 src/APLpySetup.py
add inverted HST, change VLA contour

@@ -16,9 +16,9 @@ def get_RA_dec(f):
 
 def sigma_contour_VLA(sigma):
     """
-    Return a list of contour levels, (4, 8, 16, 32..)*sqrt(2)*sigma
+    Return a list of contour levels, (4, 8, 16, 32..)*sigma
 
-    +/- 2^(n/2)*sigma; n from 2
+    +/- 2^(n)*sigma; n from 2
 
     Parameters
     ----------
@@ -34,7 +34,8 @@ def sigma_contour_VLA(sigma):
     arr = range(11)
     arr.remove(0)
     arr.remove(1)
-    arr = [2 ** i * np.sqrt(2) * sigma for i in arr]
+#     arr = [2 ** i * np.sqrt(2) * sigma for i in arr]
+    arr = [2 ** i * sigma for i in arr]
     arr.append(list(np.array(arr) * -1)[0])
     return arr
 
@@ -44,11 +45,11 @@ def sigma_contour_tenpercent(Smax):
     """
     return list of sigma multiples, +/- 10% max * n from 1 ....4
 
-    increment in 30% of max
+    increment in 15% of max
     """
     arr = [0.10 * Smax]
-    for i in np.arange(1, 4):
-        arr.append(0.3 * Smax * i + arr[0])
+    for i in np.arange(1, 7):
+        arr.append(0.15 * Smax * i + arr[0])
     Narr = -1 * arr
     arrE = np.hstack((Narr, arr))
     return arrE

### 2016-11-22 src/HSTVLA.py

@@ -1,12 +1,16 @@
 """
 Author: Daisy Leung
 
-Last edited: 11 Nov 2016
+Last edited: 21 Nov 2016
 
 Purpose:
 - Plot single panel 5GHz VLA continuum on HST F555W, investigate continuum offset
 
 History:
+Nov 21 2016:
+    - add inverted HST
+    - update contour color
+    - change contour levels
 Nov 11 2016:
     - update contour intervals to +/-10%, 20%,... peak
 Nov 2 2016:
@@ -79,18 +83,19 @@ dy = 0.9
 sigma = 1.3e-5
 Smax = 0.74e-3 # VLA
 
+inverted_HSTleft = True
+tickcolor = 'k' if inverted_HSTleft else 'white'
 ########################################
 # intialize base figure
 ########################################
-# fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0],
-#                         figure=figC, subplot=[x0, row_a, full_width, dy])#, north=True)
-# # fig1.show_grayscale(stretch='log', vmin=-0.45869, vmax=250, vmid=-0.85)
-# fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=151, vmid=-0.025)
-# #fig1.set_theme('publication')   # inverted grayscale
+fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0],
+                        figure=figC, subplot=[x0, row_a, full_width, dy])#, north=True)
+fig1.show_grayscale(stretch='log', vmin=-0.00256, vmax=1.922, vmid=-0.02)
+if inverted_HSTleft: fig1.set_theme('publication')
 
-fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
-        figure=figC, subplot=[x0,row_a,full_width,dy])
-fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=121, vmid=-0.025)
+# fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
+#         figure=figC, subplot=[x0,row_a,full_width,dy])
+# fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=121, vmid=-0.025)
 #figO = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
 #        figure=figC, subplot=[x0+width+2*x_gap, row_a, width, dy])
[…]

### 2016-11-22 src/plotCont.py

@@ -1,12 +1,14 @@
 """
 Author: Daisy Leung
 
-Last edited: 20 July 2016
+Last edited: 21 Nov 2016
 
 Purpose:
 - Overlay 2mm Cont contour on HST
 
 History:
+Nov 21 2016:
+    - add inverted HST
 July 20 2016:
     - change zoom to match VLA image (HSTVLA.py)
 May 27 2016:
@@ -78,18 +80,19 @@ x0 = 0.2
 dy = 0.9
 sigma = 0.085e-3     # theoretical: 0.0816E-03; off-region in map: 0.0888e-3
 
+inverted_HSTleft = True
+tickcolor = 'k' if inverted_HSTleft else 'white'
 ########################################
 # intialize base figure
 ########################################
-# fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0],
-#                         figure=figC, subplot=[x0, row_a, full_width, dy])#, north=True)
-# # fig1.show_grayscale(stretch='log', vmin=-0.45869, vmax=250, vmid=-0.85)
-# fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=151, vmid=-0.025)
-# #fig1.set_theme('publication')   # inverted grayscale
+fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0],
+                        figure=figC, subplot=[x0, row_a, full_width, dy])
+fig1.show_grayscale(stretch='log', vmin=-0.00256, vmax=1.922, vmid=-0.02)
+if inverted_HSTleft: fig1.set_theme('publication')
 
-fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
-        figure=figC, subplot=[x0,row_a,full_width,dy])
-fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=125, vmid=-0.025)
+# fig1 = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
+#         figure=figC, subplot=[x0,row_a,full_width,dy])
+# fig1.show_grayscale(stretch='log', vmin=-0.01869, vmax=125, vmid=-0.025)
 #figO = aplpy.FITSFigure(label['F555W_drzcroplinearShift'][0], \
 #        figure=figC, subplot=[x0+width+2*x_gap, row_a, width, dy])
 #figO.show_grayscale(stretch='log', vmin=-0.01869, vmax=151, vmid=-0.025)
[…]

### 2016-11-22 src/HSTVLA.py
no marker, zoom in

@@ -11,6 +11,7 @@ Nov 21 2016:
     - add inverted HST
     - update contour color
     - change contour levels
+    - no marker, zoom in
 Nov 11 2016:
     - update contour intervals to +/-10%, 20%,... peak
 Nov 2 2016:
@@ -71,7 +72,7 @@ figC = plt.figure(1)
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.00215
+sizep = 0.0018
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
@@ -144,7 +145,7 @@ standard_plot_setup(fig1, ra_center, dec_center, sizep, tickc=tickcolor)
 ########################################
 # markers
 ########################################
-markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
+# markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
 #markers_cross(figO, ra_cross, dec_cross, layer='marker_set_1')
 # markers_cross(figHST, ra_cross, dec_cross, layer='marker_set_1')
 # markers_cross(figred, ra_cross, dec_cross, layer='marker_set_1')

### 2016-11-22 src/plotCont.py

@@ -9,6 +9,7 @@ Purpose:
 History:
 Nov 21 2016:
     - add inverted HST
+    - no marker, zoom in
 July 20 2016:
     - change zoom to match VLA image (HSTVLA.py)
 May 27 2016:
@@ -69,7 +70,7 @@ figC = plt.figure(1)
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.00215 # 0.002058066
+sizep = 0.0018 # 0.002058066
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
@@ -140,7 +141,7 @@ standard_plot_setup(fig1, ra_center, dec_center, sizep, tickc=tickcolor)
 ########################################
 # markers
 ########################################
-markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
+# markers_cross(fig1, ra_cross, dec_cross, layer='marker_set_1')
 #markers_cross(figO, ra_cross, dec_cross, layer='marker_set_1')
 # markers_cross(figHST, ra_cross, dec_cross, layer='marker_set_1')
 # markers_cross(figred, ra_cross, dec_cross, layer='marker_set_1')

### 2016-11-22 WRITEUP/response.md
revised with DR's comments

@@
 We thank the referee for providing constructive and thoughtful
-comments to improve the manuscript. We have addressed all the concerns
-raised by the referee and details can be found in the revised version of the manuscript -- please see attached. A brief description on how we incorporated the referee's suggestions can be found below.
+comments that helped us to improve this manuscript.
+We have addressed all the concerns raised by the referee in the revised version of the manuscript.
+Our response can be found after each of the referee's points below.
 
@@
 # RESPONSE:
-1a) We have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXSJ1131-1231".
-We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (incl.
-lens modeling).
-Therefore, we think that the title is suitable for the paper.
-
-The literature/archival data of the continuum would not be as meaningful without our CO data, e.g.
-their emission does not convey information about the kinematics, spatial distribution, and does not give a broader picture regarding the f_gas evolution, which is one of the main conclusions found in this study.
+1a) To take the referee's point into account, we have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXSJ1131-1231".
+We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (including lens modeling).
 
@@
 # RESPONSE:
-We took this suggestion. To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".
+We have addressed this comment by changing "dynamically resolved" to "kinematically resolved". to minimize potential confusion.
 
@@
 # RESPONSE:
-We took this suggestion and have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig. 5).
+We have taken into account the referee's comment and have updated the CO redshift based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig.
+5), and re-plotted all the relevant figures with the updated velocity scale.
+We have also changed our wording in fig.
+1 caption "dynamical center" to "line center".
 
@@
 # RESPONSE:
-We took this suggestion and have changed "dynamical information" to "kinematic information", "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".
+We agree with the referee's comment and have changed "dynamical information" to "kinematic information", "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".
 
-We have rephrased the 2nd paragraph of Sec 4.1.2 to clarify what we meant.
+To address the referee's comment on the paragraph (2nd paragraph of Sec 4.1.2.) regarding the differential lensing effect in CO and that in the optical emission (Claeskens+06), we have re-written this paragraph to clarify what we seek to convey -- the difference in magnification factor between CO gas across all channels (µ ~ 5.5) versus those found in the optical emission indicates different morphology and spatial distribution between the CO gas, and the stellar population of different ages.
 
@@
 
-We took this suggestion and re-fitted a doubled Gaussian to the de-lensed profile (Fig.
-5) and updated the redshift and replotted all the relevant figures (and updated their captions correspondingly), updated column 1 in Table 3, the labeling in Fig 7, refitted the model shown in Fig.
-9 and updated parameters in Sec 4.3 correspondingly, SED fitting, etc.
+We agree with the referee and have re-fitted a doubled Gaussian to the de-lensed profile (Fig.
+5) to updated the redshift to z=0.65406.
+We have therefore replotted all the relevant figures (and updated their captions correspondingly), updated column 1 in Table 3 and the labeling in Fig 7, refitted the arctangent model (Fig.
+9) and updated parameters in Sec 4.3 correspondingly, and refitted SED with the updated redshift.
 
@@
 # RESPONSE:
-We found a bug in generating the map used for previous line-integrated flux extraction.
-In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes in the relevant channels, which is in agreement with the double-Gaussian fit to the spatially extracted spectrum (Fig.
+The referee is correct and we found a bug in the GILDAS package that affected the statistics and fluxes within the map used for previous line-integrated flux extraction.
+In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes over the FWZI (20.3+/-0.6 Jy km/s).
+The updated intensity is in agreement with the double-Gaussian fitted to the  extracted spectrum (Fig.
 1).
-Since our lensing-corrected M_gas for both RXJ1131 and the companion are derived from the flux in each channel, this doesn't change our conclusion.
+Since our lensing-corrected M_gas for both RXJ1131 and the companion are derived from the flux in each channel, this does not change our conclusion.
 
-We tried adding the companion's spectrum to plot (Fig.
-5) but found the figure to be over-crowded/too busy, as there are already showing various things with different various linestyles, colors.
-This main message for this plot is to show that we find that the intrinsic profile of the main galaxy is symmetric, which is informative about the kinematics of this galaxy.
-On the other hand, the useful info for the companion from the de-lensed spectrum is the gas mass, which we report in the text (and in the table, as suggested by the referee).
+We attempted to over-plot the companion's spectrum to Fig.
+5, as suggested by the referee, but found the figure to be too busy as the plot is showing various spectra with different various linestyles and colors.
+This main message for this plot is to show that we recover an intrinsically symmetric line profile for the main galaxy which is informative about its gas kinematics.On the other hand, the useful information regarding the companion from the de-lensed spectrum is the gas mass, which we report in the text (and in the table, as suggested by the referee).
 
@@
 # RESPONSE:
-Source size: We fitted a single Guassian in uv-plane to support the reported CO size based on image plane fitting, of which the convolved size is 6.6+/-0.5 x 4.5+/-0.3.
-We additionally report the source sizes by fitting two Gaussians to provide further evidence that the CO(2-1) emission is resolved.
+Source size: 
+We addressed the referee's comment on the *deconvolved* CO source size by  fitting a single Gaussian in uv-plane, which corresponds to 4.5" +/- 0.1" x 3.5" +/- 0.2", consistent with the reported CO size based on image-plane fitting within the uncertainties.
+We additionally report the source sizes by fitting two Gaussians to provide further evidence that the CO(2-1) emission is  spatially resolved.
 We have updated Section 3.1 to clarify the discussion.
@@
 CO physical size:
-The rough estimate of de-magnified CO diameter provided in the referee report is flawed since it assumes the magnification factor to be constant along the arc. The fact that 
-1) the lensed emission is not uniformly stretched along the arc (and contains complex structures within the arc)
-2) CO is immune to dust extinction, therefore likely to be more extended than the optical emission, as supported by our deconvolved CO source size and in Fig.
-7 (where the blue wing centroid is further out than the lensed arc), and from the results of our lens models
-indicates the CO source size is unlikely to be R ≤ 3.5 kpc.
+The rough estimate of de-magnified CO diameter provided in the referee report is a valid first order estimate, but the true size of the source is complicated by the fact that
+1) the lensed emission is not uniformly stretched along the arc (and contains complex structures within the arc), and thus the magnification factor is not uniform across the partial Einstein ring.
+2) CO is not subject to dust extinction, therefore its emission may be more extended than optical emission.
+In the case of RXJ1131, the CO gas is likely to be more extended than the optical emission given that
+    i) the deconvolved source size of CO (see above and section 3.1) is larger than the diameter of the Einstein Ring in the optical (~3.6")
+    ii) the spatial extent of the CO emission as shown in Fig. 7, where the centroid of the blueshifted emission is further out in the SE compared to the lensed arc in the optical
+    iii) the source-plane spatial distribution from the best-fit lens models (Sec 4.3, Fig.
+9), where the most extended velocity component is ~6.2 kpc from the line center position, indicating that the CO source size is unlikely to be R ≤ 3.5 kpc.
 
-The reported R_CO = 6 kpc is obtained based on the most extended kinematic component is consistent, see Sec 4.3.
+The R_CO size of ~6 kpc reported throughout the paper is obtained based on the centroid position of the most extended kinematic component obtained from the best-fit lens models.
+See also Sec 4.3 and our response to point 14 in this referee report for a more detailed explanation regarding the CO size.
 
@@
 #RESPONSE
-While the most extreme peak to peak noise is ~100 mJy/beam, the noise varies across channels, and therefore, on average, sigma is lower across all channels.
-Thus, the uncertainty is more representative using those obtained from the integrated map.
+We have considered the referee's point of view, and agree that the most extreme peak to peak noise across two channels is from -50 to +50 mJy/beam.
+However, this is not representative of the noise across all channels that are being used to derive the line flux.
+We thus derive the uncertainty based on the RMS obtained from the intensity map.
 
-To demonstrate that our S/N are real regardless of the fainter blue wing, we have independently obtained SNR map to confirm our results, where the peak flux in the red peak is 11.46+/-1.95 Jy/B and the blue peak is 5.13 +/- 1.45 Jy/B.
-I think what was confusing was the reported I_CO(3-2)=35.7+/-21.3Jy km/s, for which I missed a sqrt, and it should have been 35.7+/-6.91 Jy km/s, which has been corrected.
+To address the referee's comment and to demonstrate the significance of our detection that is reported in the paper, we have extracted the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
+For the blue wing, we find a peak flux density of 5.13 +/- 1.43 Jy km/s /beam in the intensity map, indicating a ≥3sigma detection in this component.
+For the red wing, we find a peak flux density of 11.45+/-1.99 Jy km/s /beam in the intensity map, indicating a ~6 sigma detection.
+The SNRs are thus consistent with the reported detection significance of ≥5sigma in the paper which was obtained based on the peak flux density in the intensity map obtained by summing over the full line profile (i.e., including emission in both wings).
 
-Since both CO lines are observed towards the same source, using prior knowledge about the blue wing from the CO(2-1) data to inform about the CO(3-2) emission is reasonable.
+Since both CO lines are observed towards the same source, using prior knowledge about the blue wing from the CO(2-1) data to inform about the CO(3-2) emission also appears reasonable.
 
 While the additional figure in I_CO is not significant, we keep this 
-to enable reproducible results and to minimize cumulative errors (e.g. when compiled for a larger number of samples). We only report significant figures when reporting the physical parameters.
+to enable reproducible results and to minimize cumulative errors in deriving second order quantities. We only report significant figures when reporting the resulting physical parameters.
+
+We agree with the referee and have updated 1.5mm to 1.4mm.
 
@@
 # RESPONSE
-We updated the 2mm flux in Table 1. We updated the flux uncertainty to include those from the uv-fitting process.
+In the residual map, the peak emission is 0.39 +/- 0.08 mJy.
+This flux (0.39 mJy) is what we adopted for RXJ1131 at 2mm in the paper.
+To address the referee's comment, we have updated the uncertainty associated with this measurement by adding those associated with the fitted point-source model and that in the residual map (from which we extracted the flux for RXJ1131) in quadrature (i.e.
+S_2mm = 0.39+/-0.12 mJy).
 
-The peak emission in the residual map is 0.39 +/- 0.08 mJy.
-While the uncertainty associated with the flux measurement of the background source needs to propagate the errors from subtracting the fitted model flux, the significance of the emission in the residual doesn't not.
-It simply is Data-Model, which is > 4 sigma than the noise.
-This together with the co-spatial emission supports that flux contribution from the background source to the total integrated 2mm continuum.
+The emission in the residual is detected at S/N > 4, which is the significance of the emission in the residual map (Data - Model).
+This together with the fact that this emission is co-spatial with the lensed arc in the optical image indicates that we detect 2mm continuum towards the background source.
+
+To taken into account the referee's comment, we have updated the 2mm flux in Table 1, and the flux uncertainty to include those from the uv-fitting process.
 
@@
 
-# RESPONSE:
-While the large uncertainty on the flux density of the background source at 2mm results in a spectral index with a large uncertainty, this nevertheless is a constraint on the radio-mm spectral slope: our value of -0.345 is flatter than the typical spectral index for pure synchrotron emission, suggesting that the 2mm has a non-negligible contribution from the underlying free-free emission.
-We have also added an additional statement stating that if there is a non-negligible contribution from the background source contributing to the peak flux, then the derived spectral index for the background source would be shallower, and therefore increasing the fraction of free-free emission over synchrotron at 2mm.
-This would also explain the atypical flat spectrum found for the foreground galaxy.
+# RESPONSE: (explain better)
+While the radio-mm spectral slope of -0.35+/-0.21 derived for the background source has a large error bar associated with it due to the large uncertainty on the 2mm flux (0.39+/-0.12 mJy), the fact that it is flatter than the typical slope for pure synchrotron emission indicates that it is a constraint on the fraction of synchrotron emission at 2mm, and that a fraction of the 2mm flux arises from thermal dust and free-free emission.
 
-The flatter than pure synchrotron spectral slope found for the background source indicates that the 2mm continuum emission is not dominated by synchrotron.
-Assuming a synchrotron index of alpha = 0.7, we find 0.12 mJy at 2mm for the background source.
-To account for it, we have updated our SED fitting and the resulting parameters throughout the paper using S = 0.27 mJy at 2mm.
+Flat spectrum of foreground galaxy:
+We have also added a statement in the paper, stating that if the background source has a contribution in the point-source model assumed in our deblending procedure, such that its flux density would be higher than derived here (0.39 +/- 0.12 mJy), then the derived spectral index (-0.35) would be even shallower.
+In this case, the 2mm flux inferred for the foreground galaxy would lower, and thus steepening its spectral slope.
+Hence, a contribution from the background source to the point-source model 2mm flux may explain the atypical flat spectrum found for the foreground galaxy.
 
-We note that 0.27 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the uncertainties, where this uncertainty included in the fit included those from absolute flux calibration.
-Therefore changes to the physical parameters are only at most a few percent,  we have updated the numbers but this does not alter the conclusions of this paper.
+Decompose synchrotron at 2mm for the background source:
+The flatter than pure synchrotron spectral slope found for the background source indicates that the 2mm continuum emission is not dominated by synchrotron emission.
+Assuming a synchrotron index of alpha = -0.7 and using the 5GHz flux, we expect S_2mmm = 0.122+/-0.004 mJy to be synchrotron emission.
+We thus find a flux excess of S_2mm = 0.39 - 0.12 = 0.27 mJy that is coming from thermal dust and free-free emission.
+We have updated our dust SED fitting using S_2mm = 0.27+/-0.08 mJy and the resulting parameters throughout the paper.
+
+We note that 0.27+/-0.09 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the uncertainties, where the uncertainties here include those from absolute flux calibration, therefore changes to the physical parameters derived from SED fitting are only at most a few percent.
+We have updated the relevant quantities but this does not alter the conclusions of this paper.
 
@@
 # RESPONSE
-We adopted the suggestions.
+We have adopted all the suggestions provided by the referee.
 
@@
 # RESPONSE:
-We adopted the suggestions and have added additional tables summarizing the observed CO line properties and the derived physical parameters.
+We adopted the good suggestions and have added additional tables summarizing the observed CO line properties and the derived physical parameters.
 
@@
 # RESPONSE:
-It is of standard practice to report flux measurements from interferometric observations excluding those from the absolute flux calibration.
-To address the referee's concern, we have added a remark in Section 3.3, table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.
+It is of standard practice to report flux measurements from interferometric observations excluding those from the absolute flux calibration and state those in the observations section (i.e.
+Section 2).
+Throughout the paper, uncertainties from absolute flux calibration are taken into account when deriving the error bars associated with physical parameters.
+To address the referee's concern, we have added a remark in table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.
 
-We have fixed the number of decimals in spectral indices in Sec 3.3.
+We have updated the number of decimals in the spectral indices reported in Sec 3.3, as suggested by the referee.
 
@@
 # RESPONSE
-We have replotted the figure with different contour intervals with thinner lines and added a sentence in the caption to improve clarify of Fig 4.
+We have replotted the figure with different contour intervals with thinner lines and added a sentence in the caption to improve the clarity of Fig 4.
 
@@
 # RESPONSE:
-We have corrected "blueshifted" to "redshifted", updated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.
+We have corrected "blueshifted" to "redshifted", updated the velocity offset from 780 km/s to 715 km/s using z = 0.65406, as suggested by the referee.
 
@@
 # RESPONSE:
-a) We have removed the statement regarding "AGN dynamically offset".
+We have removed the statement regarding "AGN dynamically offset", as suggested by the referee.
 
-Our CO measurement confirms that an offset between BLR and the systemic redshift, which is not known previously.
-We have updated this section, adding additional possible interpretation for the offset (e.g.
-gas inflows, geometric effects) in the discussion.
+1) & 2)
+Our CO measurement provides the most precise value for the velocity offset 
+between the BLR and the host galaxy.
+We thus feel that this is an invaluable addition to the literature.
+Taking into account the referee's comments, we have updated this section by listing other possible interpretations for the velocity offset (e.g.
+gas inflows, geometric effects) as part of the discussion, as outlined in detail by the referee.
 
-We agree that it is unlikely that all objects with offset AGN lines are black hole recoils.
-Here, we are not asserting that the offset arises due to a recoiling black hole, we only discuss the possibility of such interpretation given the data (showing evidence of large offset between BLR and the systemic redshift as traced by our CO data), the high spin parameter, and theoretical expectation from hierarchical model of galaxy evolution, among other possible scenarios, as listed by the referee.
+We agree with the referee that it is unlikely that all offsets in AGN lines are caused by black hole recoil.
+Considering the referee's comments, we have updated this section to as well discuss other possible scenarios.
+We only discuss the possibility of a recoil black hole as one of the interpretations for the velocity offset, given that
+    i) the magnitude of the offset in RXJ1131 (>700 km/s) appears to be an outlier in the distribution of offset found for large samples of QSOs (Richards+02, Bonning+07)
+    ii) RXJ1131 appears to have a high BH spin parameter (a > 0.9; Reis+14)    iii) recoiling BHs are expected theoretically from hierarchical model of galaxy evolution.
 
-We would greatly appreciate the referee if they can point us to a reference where it shows evidence of why the recoiling black hole scenario is highly unlikely and will gladly make the appropriate changes.
+3)
+The BH displacement estimated by the referee (~few 10kpc) has been shown to be theoretically possible in the absence of dynamical friction (Bonning+07, Loeb 2007).
+However, Loeb 2007 has showed that at low ejection speeds of a few hundred km/s, the recoil is expected to be damped by the external gravitational potential of the galaxy, dynamical friction against background stars, dark matter, and gas, thereby limiting the BH displacement and is likely to bring it back to the center of its host galaxy within a few dynamical times (Madau & Quataert 04, Boylan-Kolchin+04, Guedes+11).
 
-3) Assuming that effects (e.g., inflow, geometric effect, micro-lensing) are accountable for part of the velocity offset, then the velocity offset of ~715 km/s would then be at most an upper limit on the line-of-sight velocity.
-Then  the true recoil velocity is thus most likely to be << 1000 km/s.
-Ignoring dynamical friction against stellar background and assuming t_recoil ~ 100 Myr, then the crude BH displacement estimate given in the referee report (~few 10kpc) would be possible (as pointed out to be theoretically possible
-by Bonning+07, Loeb07).
-However, Loeb07 also pointed out that at low ejection speeds (few hundred km/s), the deceleration of the BH (damped) by the external gravitational potential of the galaxy and by dynamical friction (Chandrasekhar 1943; Apj 97, 255) on the background stars, dark matter, and gas would limit the displacement of the slow-moving BH and tend to bring it back to the center of its host galaxy within a few dynamical times (see also Madau & Quataert 04 for analytic results and Boylan-Kolchin+04 for numerical results).
-Therefore the displacement given in the referee report is unlikely to hold (see also Guedes+11).
-
-Finally, again, we acknowledge that offsets between BLR and NLR lines are quite common in Seyferts and quasars, but typically not as big of an offset.
-In this paper, we only discuss possible scenarios and do not assert that any one of mentioned scenario is necessary in RXJ1131.
+We acknowledge that velocity offsets between BLR and NLR lines are quite common in Seyferts and quasars, but the offsets as large as that of RXJ1131 appear to be uncommon according to the distribution of offset among other AGN hosts (Richards+02, Bonning+07).
+To take into account the referee's comments, we now also discuss other possible scenarios.
 
@@
 # RESPONSE:
-The details of the model (e.g. how we reconstruct the likelihood functions) are already referenced in other papers. We did not discuss any of that in this paper.
+The details of the model (e.g. how we reconstruct the likelihood functions) are described in other papers, which we reference to in the paper for brevity.
 
-However, description of our MCMC sampling has been retained given that conveying the priors and stating how we ensure convergence is necessary for reproducible results and are crucial information for readers to decide on how trust-worthy our inference are from a statistical viewpoint.
-Explicitly stating the priors is important to demonstrate that our choice are reasonable and physically motivated since they could affect the marginal posteriors strongly and thus the inferred physical parameters.
+However, the description of our MCMC sampling has been retained since stating the priors and the methods to ensure convergence are necessary to make results reproducible, and provide crucial information for readers to decide how trust-worthy our inference are from a statistical viewpoint.
+Explicitly stating the priors is important to demonstrate that our choice are reasonable and physically motivated since they could affect the marginal posteriors strongly, and thus the inferred physical parameters.
+We therefore decide to keep them in the lens modeling (Sec 4.1) and SED fitting sections (Sec 4.5).
 
@@
 
-For other comments, please refer to our response to point 11 and 12 (since 
-they are repeated here).
+For the other comments, please refer to our response to point 11 and 12, where we describe how we took them into account.
 
@@
 # RESPONSE:
-Indeed, the plot on the left is to demonstrate that despite the observed 1st moment map is distorted due to a combination of differential lensing (in which the red velocity are more heavily weighed) and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kinematic components, as shown atop of the observed map.
-The reconstructed information displays a clear velocity gradient.
-Taken together with previous results from literature and the intrinsically symmetric line profile, we proceed the next section with dynamical modeling.
+Indeed, the plot on the left is to demonstrate that while the observed 1st moment map is distorted due to a combination of differential lensing and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kinematic components.
+Therefore, we show the source-plane positions atop of the observed 1st moment map.
+To address the referee's concern, we have added some additional description in the caption to clarify what is being shown in the left panel.
 
-To address the referee's concern, we have added in a few lines in the caption to clarify what is being shown in the left panel.
+The reconstructed source-plane positions display a clear velocity gradient.
+Taken together with previous results from literature (C06) and the intrinsically symmetric line profile (Fig.
+5), we carried out dynamical modeling in Sec 4.3 assuming RXJ1131 is a disk galaxy.
 
 PV: 
-As discussed in Sec 4.1.1, we have detailed the evidence and reasons for which we interpret RXJ1131 as a disk galaxy.
+We have detailed the reasons for why we interpret RXJ1131 as a disk galaxy in Sec 4.1.1.
 Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraph of Sec 4.3).
 
-To address the referee's concern and to improve clarify, we have re-iterate in the beginning of the first paragraph of Sec 4.3 that we interpret RXJ1131 as disk galaxy.
+To address the referee's concern and to improve the clarity of this section, we have re-iterate in the beginning of Sec 4.3 that we assume RXJ1131 to be a disk galaxy for dynamical modeling.
 
@@
 As explained in para.
-3 of sec 4.3, we use the maximum observed velocity (i.e.
-corresponding to the redmost channel along the disk major axis) at 6+/-3kpc as a proxy to the rotation velocity.
-Thus the quoted CO disk radius corresponds to the extent of this velocity component, as measured from the line center.
+3 of Sec 4.3, we use the maximum observed velocity (i.e.
+corresponding to the redmost channel along the disk major axis) at 6+/-3kpc as a proxy for the rotation velocity.
+Thus the quoted CO disk radius corresponds to the extent of this velocity component, as measured from the centroid position at zero velocity.
 
 Clumps:
-With the evidence and reasons listed in the beginning of Sec 4.3, the reconstructed source-plane distribution is unlikely to be just two kinematically-ordered clumps rather than a single rotating disk.
+Given that RXJ1131 shows a symmetric double-horned line profile (Fig.
+5) and a disk-like morphology with a Sersic index of n=1 in the source-plane of optical-NIR emission (C06), the source-plane velocity gradient found by lens modeling the CO emission (i.e., based on the source-plane positions of different velocity components as shown in the left panel of Fig 9) suggest that RXJ1131 is more likely to be a single rotating disk rather than two kinematically-ordered clumps.

### 2016-11-22 WRITEUP/ms.tex
revised with DR's comments

--- 2016-11-18 WRITEUP/ms.tex
@@
 \citestyle{aa}
-\shorttitle{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
+\shorttitle{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXJ1131$-$1231}
 \shortauthors{Leung, Riechers \& Pavesi}
@@
 
-\title{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
+\title{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 consistent with the optically-faint companion reported in previous studies.
-The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
-and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
-The gas mass fraction of $\sim$18\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
+The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
+and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
+The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
 We find lensing-corrected stellar and dust masses, an IR luminosity, and a
 star formation rate of
-$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
+$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU for RXS\,J1131$-$1231.
 The source-plane morphologies of its gas and stellar populations
@@
 The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
-at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
+at $z_\textrm{s, QSO}$\eq$0.658$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
 studying the evolution of molecular gas properties in quasar host galaxies and the
@@
 \section{Observations} \label{sec:obs}
-\subsection{PdBI \bco}
-Observations of the \bco rotational line
-($\nu_{\rm rest}$\,=\,$230.53800$ GHz) at the tuning frequency of 
-$\nu_{\rm obs}$\eq139.256\,GHz
-% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
-were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
-Riechers). Two observing runs were carried out on 2014 December 06 and 2015
-February 05 under good weather conditions in the C and D array configurations,
-respectively.
-This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
- time after discarding unusable visibility data.
-The 2 mm receivers were used to cover the redshifted \bco line
-and the underlying continuum emission, employing a correlator setup that provides
-an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
-($\sim$\,$4.2$\,\kms).
-The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
-for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
-observed as the bandpass calibrator for both tracks.
-MWC349 and 3C279 were observed as primary flux calibrators for the C and D
-array observations, respectively, yielding calibration accuracy better than 15\%.
-
-The \ncode{gildas} package was used to calibrate and analyze the visibility data.
-The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
-weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
-The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
-over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
-is produced by averaging over 3.16\,GHz of line-free bandwidth. This
-yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
 
 \subsection{CARMA \cco}
-Observations of the \cco rotational line in RXJ1131
-($\nu_{\rm rest}$\,=\,345.79599\,GHz) 
-% redshifted to 
-at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz    % i.e. where we thought the line was redshifted to 
+Observations of the \cco rotational line 
+($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
+towards RXJ1131 at $z_{\rm QSO}$\eq0.658 
 were carried out with the \carma (CARMA;
-Program ID: cf0098; PI: D. Riechers)
-in the D array configuration on 2014 February 02 under poor 1.5\,mm
+Program ID: cf0098; PI: D. Riechers) in the D array configuration. They were carried out
+on 2014 February 02 under poor 1.5\,mm
 weather conditions and on 2014 February 17 under good 1.5\,mm
 weather conditions.
-This resulted in a total on-source time of 2.94 hours after flagging poor
+This resulted in a 
+total on-source time of 2.94 hours after flagging poor
 visibility data.
@@
 line-free channels in both sidebands.
+
+\subsection{PdBI \bco}
+Observations of the \bco rotational line
+($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
+redshifted to $\nu_{\rm obs}$\eq139.256\,GHz towards RXJ1131
+at the
+CARMA \cco redshift of $z_{\rm CO(3-2)}$\eq0.655
+were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
+Riechers).
+Two observing runs were carried out on 2014 December 06 and 2015
+February 05 under good weather conditions in the C and D array configurations,
+respectively.
+This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
+ time after discarding unusable visibility data.
+The 2 mm receivers were used to cover the redshifted \bco line
+and the underlying continuum emission, employing a correlator setup that provides
+an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
+($\sim$\,$4.2$\,\kms).
+The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
+for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
+observed as the bandpass calibrator for both tracks.
+MWC349 and 3C279 were observed as primary flux calibrators for the C and D
+array observations, respectively, yielding calibration accuracy better than 15\%.
+
+The \ncode{gildas} package was used to calibrate and analyze the visibility data.
+The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
+weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
+The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
+over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
+is produced by averaging over 3.16\,GHz of line-free bandwidth. This
+yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
 
@@
 \section{Results} \label{sec:results}
-The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
 \input{table_obsprop}
@@
 \subsection{\bco Emission} \label{sec:CO21}
-We detect \bco line emission toward the background source in the PdBI data
-at $\gtrsim$\,27$\sigma$ significance, enabling us to constrain its redshift at 
+We detect \bco line emission towards the background source RXJ1131 in the PdBI data
+at $\gtrsim$\,27$\sigma$ significance. Based on this measurement, we refine the redshift of RXJ1131 to
 $z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to 
-the de-lensed spectrum, which is shown in \Fig{delensed}.
-% instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
-% redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
+the de-lensed spectrum (\Fig{delensed}) 
+instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
+redshift determination 
+due to differential lensing (see \Sec{differential}).
 }. The emission is spatially and kinematically resolved
@@
 \caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
-21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
+22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
 The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
@@
 in the intensity map.
+Observed properties of the \bco emission line are summarized in \Tab{obsprop}.
 
 The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
-to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7, 
-consistent with the results obtained by $uv$-plane fitting within the uncertainties. 
+to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  % In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
+consistent with that obtained by $uv$-plane fitting within the uncertainties. 
 % UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
-To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we 
-fit two independent Gaussians and find deconvolved source sizes of 
-3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
-Therefore, the emission is slightly resolved over $\sim$\,2 beams.
-The lensed CO emission is unlikely to be distributed as Gaussians 
-given the morphology seen in optical and \nir emission that were observed at higher resolution, 
-i.e., the lensed emission of CO (without beam convolution) is more likely to have 
-an annulus configuration enclosing a partially complete ``Einstein ring'' with 
-structures along the arc 
-and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
-spatially offset blue wing compared to optical emission suggest that 
-the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.
+The spatial distribution of the observed CO emission is unlikely to be fully 
+encapsulated by a simple Gaussian 
+given its skewed emission, which also appears to be a superposition of two components (\Fig{CO21mom}). 
+% To better capture the spatial distribution of the line emission, we 
+We therefore also fit a model of two Gaussians which yeilds deconvolved source sizes of 
+3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
+The deconvolved source size together with
+% complex morphology of a partial ``Einstein ring'' with 
+% structures along the arc and knots 
+% seen in optical and \nir emission (see \Fig{CO21mom}). %that were observed at higher resolution, 
+the spatially more extended blue wing compared to the optical 
+``Einstein ring" of diameter $\sim$3\farcs6 (top right panel of \Fig{CO21mom}) suggest that 
+the CO-emitting region in RXJ1131 is more extended than its stellar and quasar emission.
 
@@
 We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
-The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
-double-peaked profile. We estimate a line intensity of
-35.7\,$\pm$\,6.9\,Jy\,\kms by summing up fluxes over the FWZI
+The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where
+we over-plot spectra of the \bco and \cco lines.
+We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
+%For the blue wing, we find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne in the intensity map, indicating a $\gtrsim$3$\sigma$ detection for this component. 
+%For the red wing, we find a peak flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne in the intensity map, 
+% indicating a $\sim$\,6$\sigma$ detection. 
+We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing,
+indicating a $\sim$\,6$\sigma$ detection. 
+We estimate a line intensity of 35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop}) by summing up fluxes over the FWZI
 linewidth used to infer the \bco line intensity ($\sim$700 \kms).
+
 Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
@@
 correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.62, where this uncertainty includes 
-those introduced in absolute flux calibration and is dominated by 
-the large phase errors associated with the \cco observations.
+$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.41, where this error bar includes 
+the uncertainties in absolute flux calibration.
 This ratio is consistent with
@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-The velocity scale is with respect to $z$=0.6541, which corresponds to the
-line center of \bco line emission. The spectral resolution for \cco and \bco
-is 35.8 \kms and 21.5 \kms, respectively.
+The velocity scale is the same as in \Fig{CO21spec}
+The spectral resolution for \cco and \bco
+is 36 \kms and 22 \kms, respectively.
  \label{fig:co32spec}}
@@
 centered on the lensing galaxy (\Fig{cont}).
-We note that the reported flux uncertainties do not include those from absolute flux calibration.
+% We note that the reported flux uncertainties do not include those from absolute flux calibration.
 Slightly extended emission
@@
 This suggests that we detect emission in both
-the foreground galaxy and the background galaxy and that the
+the foreground and background galaxy and that the
 emission is marginally resolved along its major axis.
@@
 emission, which we here assume to be dominated by the foreground galaxy. The peak emission
-of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy
-in the residual map coincides with the lensed arc, and is consistent with
+in the residual map coincides with the lensed arc, with a flux density 
+of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy. 
+This peak flux is consistent with
 the difference between the integrated and the peak flux in the
 original continuum map ($\sim$0.4 mJy). 
-We therefore adopt $S_{\nu}$\eq0.39\pmm0.22 mJy as the 2\,mm continuum flux measurement for 
+We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the 2\,mm continuum flux measurement for 
 the background galaxy (RXJ1131). 
-The quoted uncertainty is solely based on the uncertainties associated with the flux density of the 
-point source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
-that of the integrated flux in the original data (0.2\,mJy), and does not account for that in the 
+The quoted uncertainty is derived by adding those associated with the flux density of the 
+point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
+the peak flux in the residual map (0.08\,mJy) 
+in quadrature, and does not account for that in the 
 de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
@@
 is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
-% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
-% assumes that the foreground galaxy is a point source, the...
 
@@
 \includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
-\caption{Top: overlay of the 2\,mm continuum emission on the optical image.
+\caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
 Contours start and increment at steps of
@@
 Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
-Contours correspond to [10, 40, 60, 100]\%$\times$ the peak flux density of $S_{\rm 5GHz}$\eq0.74\pmm0.01 mJy.
-% Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$,
-% where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne.
-The central crosses in both panels indicate the centroid of the foreground galaxy,
-as detected in the optical image. 
+Contours correspond to $\pm2^n\sigma$, where 
+$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne 
+and $n$ is an integer starting from 2 to 5. 
+Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$.
 The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
@@
 We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
-We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02
-for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35
+We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
+for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21 % differential
 for the background galaxy by fitting
@@
 5\,GHz and 2\,mm. 
-The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission ($\alpha$\ssim$-$0.7), suggesting 
-that a dominant fraction of the observed 2\,mm emission arises from cold dust and free-free emission. 
-% that the 2\,mm emission is dominated by non-synchrotron emission.
-This spectral slope would only be shallower 
-if a non-negligible fraction from the background source 
-contribute to the point source flux at 2\,mm in the deblending process. This would also 
-explain the atypical flat spectrum found for the foreground galaxy. 
-Assuming a synchrotron slope of $\alpha$\ssim$-$0.7 and that the emission at 5\,GHz is purely synchrotron, 
-we find $S_{\rm 2mm}$\eq0.27\pmm0.22\,mJy from cold dust and free-free emission in the background galaxy.
+The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; ][]{Andreani93a}, suggesting 
+that a fraction of the observed 2\,mm emission arises from thermal dust and free-free emission. 
+This spectral slope would be even shallower 
+if the background source has a contribution in the
+2\,mm flux of the point-source model used
+in the deblending process. This would also 
+explain the flat spectrum found for the foreground galaxy that is atypical of elliptical galaxies. 
+Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we find
+a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm      % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
+for the background source based on its 5\,GHz flux,
+and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy that arises from thermal dust emission.
+
+% We thus adopt the flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy as
+% thermal dust emission. % (0.12/0.39)^2 + (0.004/0.122)^2]^1/2 *  0.27
 
@@
 \caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
-Top: each panel corresponds to a channel map of width 107.5\,\kms around the annotated central velocity where
+Top: each panel corresponds to a channel map of width 107.5\,\kms around the labelled central velocity where
 the observed emission (red contours) is over-plotted atop the best-fit model (grayscale). 
@@
 \caption{
-Channel maps of the PdBI \bco data cube toward RXJ1131 at 21.5\,\kms resolution.
+Channel maps of the PdBI \bco data cube toward RXJ1131 at 22\,\kms resolution.
 Black crosses indicate the positions of the lensed knots (AGN emission,
@@
 the {\it HST} $V$-, $I$-, and $H$-bands, where the
-magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
-Here, we find that the highly asymmetric \bco line profile is predominantly a result of 
-differential lensing, where the redshifted emission is apparently much brighter than the
-blueshifted component, as indicated by the difference in their magnification factor $(\mu_{\rm L})$, which
-varies from 8.7 to 3.1 across the \bco line (\Tab{model}).
-A secondary effect contributing to the asymmetry is caused by 
-the CO emission in the companion in the redshifted velocity channels.
+magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}, indicating that
+the spatial positions and extents of different stellar populations within the host galaxy are dissimilar with respect
+to the caustic.
+Here, 
+the best-fit lens models obtained for different CO channel slices show that differential lensing also plays 
+an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
+from 8.7 to 3.1 across different kinematic components (\Tab{model}).
+The asymmetry in the line profile is therefore predominantly a result of differential lensing, where 
+the redshifted CO-emitting gas is only apparently much brighter than the
+blueshifted component due to a higher magnification factor.
+A secondary effect contributing to the asymmetry is likely caused by 
+the CO emission in the companion at the reddest velocities.
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
@@
 \subsection{\bco Dynamical Modeling} \label{sec:dynamics}
-As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy given 
-its reconstructed source-plane locations of various kinematic components displaying
-a velocity gradient with a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}), 
-and the disk-like morphology found for source-plane reconstructed optical-NIR emission
+As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy as it displays
+evidence of a source-plane velocity gradient in the CO emission,
+a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}), 
+and a disk-like morphology in the source-plane reconstruction of optical-NIR emission
 \citepalias{Claeskens06a}.
-Assuming the velocities of the respective channels used in the
+We extract a one dimensional PV profile as shown in the right panel of \Fig{PV}
+by assuming the velocities of the respective channels used in
 lens modeling correspond to solely the tangential component of the
-true velocity vector of a rotating disk (i.e., along the major axis),
-we extract a one dimensional PV diagram in \Fig{PV}
-by slicing across their source plane positions along this major axis (PA: 121\degr).
+true velocity vector of a rotating disk, i.e., each velocity component would 
+be seen lying along the major axis of a rotating disk if observed with sufficiently high angular resolution.
+In this process, the positions for each velocity component (plotted as data points in the right panel of \Fig{PV})
+are extracted along the best-fitted major axis, which is along a PA of 121\degr.
 
@@
 Our estimate should be considered at best an upper limit since
-the gas in RXJ1131 is unlikely virialized.
+the gas in RXJ1131 is unlikely to be virialized.
 In the following sections, we use the
@@
 % to obtain the total uncertainties 
-for the PdBI 2\,mm continuum in our fitting procedure. 
-Here, we use a flux density of $S_{\rm 2mm}$\eq0.27 mJy derived in \Sec{deblend} 
+for the PdBI 2\,mm continuum photometry in our fitting procedure. 
+Here, we use a flux density of $S_{\rm 2mm}$\eq0.27\pmm0.08 mJy derived in \Sec{deblend} 
 instead of the deblended 0.39\,mJy listed in \Tab{photometry} 
@@
 3.81\petm{1.92}{1.97}\E{12}\,\Lsun, and a
-dust mass of 16\petm{5}{12}\E{8}\,\Msun, all of which are uncorrected for lensing magnification.
+dust mass of 16\petm{5}{12}\E{8}\,\Msun, all of which are not lensing-corrected.
 For the mass absorption coefficient, we adopt
@@
 a \fir luminosity \LFIR of 4.24\petm{2.17}{2.00}\E{12}\,\Lsun and a
-dust mass $M_{\rm dust}$ of 14\petm{5}{7}\E{8}\,\Msun, all of which are uncorrected for lensing.
+dust mass $M_{\rm dust}$ of 14\petm{5}{7}\E{8}\,\Msun, all of which are not lensing-corrected.
 Taken at face value, this implies an FIR-to-IR luminosity ratio
@@
 On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
-Offset between BLR and NLR lines have been reported in literature, e.g., 
+Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature, e.g., 
 \citet{Richards02a} find a
 median of 97\kms and a dispersion of 269\,\kms in the distribution of
-the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in an SDSS sample of $>$3800 quasars, 
-and \citet{Bonning07a} find a mean offset of 100\,\kms with a dispersion of 212\,\kms %FWHM = 500
+offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in a
+sample of $>$3800 quasars, 
+and \citet{Bonning07a} find a mean offset of 100\,\kms with a dispersion of 212\,\kms
+%FWHM = 500
 between the broad component of
-H$\beta$ and \oiii lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
-illustrating that large offsets ($\Delta v$$\gtrsim$\,500\,\kms) are uncommon but have been observed in some cases.
-
-Common interpretations invoked to explain offsets between BLR and systemic redshifts include
-e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing angle towards the accretion disk, 
-inclination effect, in which clumps in the accretion disk may block emission towards the far side of the disk, and thus the observed BLR emission is only
-originating from
-the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
-In the latter, \citet{Sluse07a} report a covering factor of 20\% based on \mgii absorption line at $z$\eq0.654.
-Additionally, differentially lensing of the compact BLR emission by microlensing in RXJ1131\citep[\eg][]{Sluse07a, Sluse12a} 
-may have boosted the redshifted component more than the blueshifted component,
-thereby biasing the BLR line centroids towards longer wavelengths.
-{\bf DR: is it because of the large linewidth (one component of \mgii is $>$20000\kms, and broad comp.
-of H$\beta$ is $\sim$2000$-$4000\kms) that the referee thinks it's more likely to be inflow and therefore doesn't like the recoil black hole?
-Sluse07:
-"Another remarkable result is the presence in our spectra of a \mgii absorption doublet blueshifted at $z$\eq0.654. 
-According to its velocity shift ($\Delta v$\ssim$-$660\,\kms). 
-These lines disappear from the spectrum ratios A/B and C/B.
-This indicates that the absorbed flux is proportional to the flux coming from the continuum+BLR.
-This implies that the region at the origin of the absorption must cover both the continuum and the BLRs and that, within the uncertainties, their depths are identical in the spectra of the three images A, B, and C."
-ok.. so is it because of this broad absorption component of \mgii that is at the same $z$ as the NLR lines, and therefore implying that the BLR and 
-the AGN is not really spatially and kinematically offset, 
-but the offset is truly just a manifestation of a rotating disk + other kinematics (+ absorption of continuum by BLR moving towards us, redshfiting the line centroid, + inflow of material + clumps blocking the far side inflow?)
-}
-
-Alternatively, the observed offset 
-may be explained by a more extreme scenario of a recoiling black hole (BH), 
+H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
+where only $\lesssim$20 of them are found to have offset $>$800\,\kms.
+Thus, large velocity offsets between BLR and NLR lines 
+comparable to that of RXJ1131 are uncommon but have been observed in some cases.
+
+The observed velocity offset between the BLR and NLR lines may be explained by
+a recoiling black hole (BH), 
 where its BLR is moving at high velocity relative to the bulk of its host galaxy
@@
 SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}, and
-SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
-have been observed \citep{Komossa08a}.
-However, this scenario for SDSSJ0927+2943 was recently refuted by \citet{Decarli14a}, who find that the
-BLR lines in SDSSJ0927+2943 are indeed consistent with the CO systemic redshift.
-This is in contrast with RXJ1131, where our CO observations confirm the redshifted BLR.
+SDSS J0927+2943 at $z$\,$\sim$\,0.713.
+In the case of SDSS J0927+2943, the black hole recoil scenario was proposed based on
+the velocity offset between a set of redshifted narrow lines and a second set of 
+blueshifted broad AGN lines \citep{Komossa08a}.
+However, this was recently refuted by \citet{Decarli14a}, who find that the
+BLR lines in SDSSJ0927+2943 are indeed consistent with its CO systemic redshift.
+This is in contrast with RXJ1131, where our CO observations confirm the redshifted BLR lines.
 Since this scenario requires a coalesced BH, it would imply that RXJ1131 
-is a product of previous merger, which is not implausible and 
+is a product of a previous merger, which is not implausible and 
 might also explain the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
 
-The available data do not provide direct evidence favoring any of the above scenarios, 
-we therefore cannot rule out any of the above plausible scenarios; $\lesssim$1-kpc
-resolution observations probing the morphology, structures and kinematics of the (ionized) gas and 
-stellar (e.g., via H$\alpha$ kinematics measurements) would be useful to distinguish between these scenarios.
+Alternative scenarios 
+e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing angle towards the accretion disk, and 
+inclination effect together with a clumpy accretion disk
+are more commonly invoked to explain velocity offsets between BLR and systemic redshift.
+% , in which clumps in the accretion disk may block emission towards the far side of the disk, and thus the observed BLR emission is only originating from
+% the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
+In the context of the last scenario, 
+\citet{Sluse07a} report a covering factor of 20\% for the accretion disk in RXJ1131
+based on its broad \mgii absorption line at $z$\eq0.654.
+Additionally, the centroids of the BLR lines in RXJ1131 may be biased towards longer wavelengths due to
+microlensing \citep[\eg][]{Sluse07a, Sluse12a}, which may have
+magnified the redshifted component of the compact BLR more strongly than its blueshifted component.
+
+With the existing data, we do not favor a particular scenario mentioned above as the interpretation for 
+the observed velocity offset.
 
@@
 resolved CO study at intermediate redshift.
-Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.66\,\pm\,0.41$
+Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.78\,\pm\,0.41$
 between the \bco and \cco lines,
@@
 but the optical BLR lines are redshifted by $\sim$715\,\kms. 
+We raise several plausible scenarios that may explain the observed velocity offset, \eg
+outflow/inflow of gas in the BLR, kinematics of the accretion disk, geometric effects,
+microlensing, and a recoiling black hole.
+The latter scenario might also explain the high black hole spin parameter reported by \citet[$a$\ssim0.9][]{Reis14a}.
+With the available data, 
+we do not favor a particular scenario mentioned above as the interpretation for the observed velocity offset.
 

### 2016-11-22 WRITEUP/table_obsprop.tex
revised with DR's comments

@@
 \startdata
-$z_{\rm CO}$   &                          & 0.6541\pmm0.0002 \\ [0.5ex]
+$z_{\rm CO(2-1)}$   &                          & 0.6541\pmm0.0002 \\ [0.5ex]
 $I_{\rm CO(2-1)}$     & Jy\,km s\pmOne           & 20.3\pmm0.6 \\ [0.5ex]
-S$_{\bco}$     & Jy km s\pmOne beam\pmOne & 8.12\pmm0.30 \\ [0.5ex]
-FWHM$_{\rm CO(2-1)}$ \tna & km s\pmOne               & 179\pmm9, 255\pmm28 \\ [0.5ex]
-FWHM$_{\rm CO(2-1)}$\tnb        & km s\pmOne               & 220\pmm72 \\ [0.5ex]
+$S_{\rm CO(2-1)}$\tna     & Jy km s\pmOne beam\pmOne & 8.12\pmm0.30 \\ [0.5ex]
+FWHM$_{\rm CO(2-1)}$ \tnb & km s\pmOne               & 179\pmm9, 255\pmm28 \\ [0.5ex]
+FWHM$_{\rm CO(2-1)}$\tnc        & km s\pmOne               & 220\pmm72 \\ [0.5ex]
 $I_{\rm CO(3-2)}$     & Jy\,km s\pmOne           & 35.7\pmm6.9
@@
 %\tablecomments{}
-\tablenotetext{a}{From fitting a double Gaussian to the observed \bco spectrum (\Fig{CO21spec}).}
-\tablenotetext{b}{From fitting a double Gaussian with a common FWHM to the de-lensed \bco spectrum (\Fig{delensed}).}
+\tablenotetext{a}{Peak flux density in the intensity map.}
+\tablenotetext{b}{From fitting a double Gaussian to the observed \bco spectrum (\Fig{CO21spec}).}
+\tablenotetext{c}{From fitting a double Gaussian with a common FWHM to the de-lensed \bco spectrum (\Fig{delensed}).}
 \end{deluxetable}

### 2016-11-22 WRITEUP/ms.tex
update error bar on r32

@@
 correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.41, where this error bar includes 
+$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.37, where this error bar includes 
 the uncertainties in absolute flux calibration.
@@
 resolved CO study at intermediate redshift.
-Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.78\,\pm\,0.41$
+Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.78\,\pm\,0.37$
 between the \bco and \cco lines,

### 2016-11-22 WRITEUP/diff.tex
incoporated DR's comments, diff between submitted and latest (assuming ready to be re-submitted)

@@
 consistent with the optically-faint companion reported in previous studies.
-The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
-and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
-The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
+The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
+and \eq(2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
+The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
 We find lensing-corrected stellar and dust masses, an IR luminosity, and a
 star formation rate of
-$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
+$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU for RXS\,J1131$-$1231.
 The source-plane morphologies of its gas and stellar populations
@@
 \section{Observations} \label{sec:obs}
-\subsection{PdBI \bco}
-Observations of the \bco rotational line
-($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
-\old{at the $\nu_{\rm LO}$\eq139.256\,GHz}
-\new{at the tuning frequency of $\nu_{\rm obs}$\eq139.256\,GHz}
-% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
-were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
-Riechers). Two observing runs were carried out on 2014 December 06 and 2015
-February 05 under good weather conditions in the C and D array configurations,
-respectively.
-This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
- time after discarding unusable visibility data.
-The 2 mm receivers were used to cover the redshifted \bco line
-and the underlying continuum emission, employing a correlator setup that provides
-an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
-($\sim$\,$4.2$\,\kms).
-The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
-for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
-observed as the bandpass calibrator for both tracks.
-MWC349 and 3C279 were observed as primary flux calibrators for the C and D
-array observations, respectively, yielding calibration accuracy better than 15\%.
-
-The \ncode{gildas} package was used to calibrate and analyze the visibility data.
-The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
-weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
-The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
-over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
-is produced by averaging over 3.16\,GHz of line-free bandwidth. This
-yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
-
 \subsection{CARMA \cco}
-Observations of the \cco rotational line in RXJ1131 \old{($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz}
-\new{($\nu_{\rm rest}$\,=\,345.79599\,GHz)
-% redshifted to
-at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz}    % i.e. where we thought the line was redshifted to
+Observations of the \cco rotational line \old{in RXJ1131} ($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz \new{towards RXJ1131 at $z_{\rm QSO}$\eq0.658}
 were carried out with the \carma (CARMA;
 Program ID: cf0098; PI: D. Riechers)
-in the D array configuration on 2014 February 02 under poor 1.5\,mm
+in the D array configuration\new{. They were carried out} on 2014 February 02 under poor 1.5\,mm
 weather conditions and on 2014 February 17 under good 1.5\,mm
@@
 line-free channels in both sidebands.
+
+\subsection{PdBI \bco}
+Observations of the \bco rotational line
+($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
+\old{at the $\nu_{\rm LO}$\eq139.256\,GHz}
+\new{redshifted to $\nu_{\rm obs}$\eq139.256\,GHz towards RXJ1131 at the CARMA \cco redshift of 
+$z_{\rm CO(3-2)}$\eq0.655}
+were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
+Riechers). Two observing runs were carried out on 2014 December 06 and 2015
+February 05 under good weather conditions in the C and D array configurations,
+respectively.
+This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
+ time after discarding unusable visibility data.
+The 2 mm receivers were used to cover the redshifted \bco line
+and the underlying continuum emission, employing a correlator setup that provides
+an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
+($\sim$\,$4.2$\,\kms).
+The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
+for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
+observed as the bandpass calibrator for both tracks.
+MWC349 and 3C279 were observed as primary flux calibrators for the C and D
+array observations, respectively, yielding calibration accuracy better than 15\%.
+
+The \ncode{gildas} package was used to calibrate and analyze the visibility data.
+The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
+weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
+The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
+over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
+is produced by averaging over 3.16\,GHz of line-free bandwidth. This
+yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
 
@@
 \section{Results} \label{sec:results}
-\new{The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.}
 \input{table_obsprop}
@@
 We detect \bco line emission toward the background source in the PdBI data
-at $\gtrsim$\,27$\sigma$ significance, \old{confirming the redshift at $z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.} \new{enabling us to constrain its redshift at
-$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to
-the de-lensed spectrum, which is shown in \Fig{delensed}}.}}
+at $\gtrsim$\,27$\sigma$ \old{significance, confirming} \new{significance. Based on this measurement, we refine} the redshift \old{at} \new{of RXJ1131 to} \old{$z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.}
+\new{$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to
+the de-lensed spectrum, which is shown in \Fig{delensed}
+instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
+redshift determination 
+due to differential lensing (see \Sec{differential})}.}}
 \old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
 with a highly asymmetric double-horned line profile
-as shown in \mbox{\Fig{CO21spec}}. Fitting a double Gaussian results in peak
+as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
 flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
@@
 \caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
-21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
+22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
 The velocity scale is with respect to \old{$z$\,=\,0.6537, which is approximately the line center considering the asymmetry resulting from differential lensing.} \new{$z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
@@
 \new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
-to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,
-consistent with the results obtained by $uv$-plane fitting within the uncertainties.
+to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  % In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
+consistent with that obtained by $uv$-plane fitting within the uncertainties. 
 % UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
-To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we
-fit two independent Gaussians and find deconvolved source sizes of
-3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
-Therefore, the emission is slightly resolved over $\sim$\,2 beams.
-The lensed CO emission is unlikely to be distributed as Gaussians
-given the morphology seen in optical and \nir emission that were observed at higher resolution,
-i.e., the lensed emission of CO (without beam convolution) is more likely to have
-an annulus configuration enclosing a partially complete ``Einstein ring'' with
-structures along the arc
-and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
-spatially offset blue wing compared to optical emission suggest that
-the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.}
+The spatial distribution of the observed CO emission is unlikely to be fully 
+encapsulated by a simple Gaussian 
+given its skewed emission, which also appears to be a superposition of two components (\Fig{CO21mom}). 
+% To better capture the spatial distribution of the line emission, we 
+We therefore also fit a model of two Gaussians which yeilds deconvolved source sizes of 
+3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
+The deconvolved source size together with
+% complex morphology of a partial ``Einstein ring'' with 
+% structures along the arc and knots 
+% seen in optical and \nir emission (see \Fig{CO21mom}). %that were observed at higher resolution, 
+the spatially more extended blue wing compared to the optical 
+``Einstein ring" of diameter $\sim$3\farcs6 (top right panel of \Fig{CO21mom}) suggest that 
+the CO-emitting region in RXJ1131 is more extended than its stellar and quasar emission.}
 
@@
 We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
-The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
-double-peaked profile. We estimate a line intensity of
-\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms} by summing up fluxes over the FWZI
+\old{The spectrum is shown in \mbox{\Fig{co32spec}} and appears to be consistent with a
+double-peaked profile. }
+\new{The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where we over-plot spectra of the \bco and \cco lines.}
+\new{We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
+We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, 
+indicating a $\gtrsim$3$\sigma$ detection for this component, and a peak line 
+flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing, indicating a $\sim$\,6$\sigma$ detection. 
+}
+We estimate a line intensity of
+\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop})} by summing up fluxes over the FWZI
 linewidth used to infer the \bco line intensity ($\sim$700 \kms).
+
 Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
@@
 $r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,\old{0.66\,$\pm$\,0.41. Taking into account the large phase errors associated with \cco, this is consistent with}
-\new{0.78\,$\pm$\,0.62, where this uncertainty includes
-those introduced in absolute flux calibration and is dominated by
-the large phase errors associated with the \cco observations.
+\new{0.78\,$\pm$\,0.37, where this uncertainty includes
+the uncertainties in absolute flux calibration.
 This ratio is consistent with}
@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-The velocity scale is with respect to \old{\mbox{$z$=0.6537, which corresponds to the
-dynamical center of the \bco line.}} \new{\mbox{$z$=0.6541, which corresponds to the
-line center of \bco line emission.}} The spectral resolution for \cco and \bco
-is 35.8 \kms and 21.5 \kms, respectively.
+The velocity scale is \old{with respect to \mbox{$z$=0.6537, which corresponds to the
+dynamical center of the \bco line.}} \new{same as in \Fig{CO21spec}).} The spectral resolution for \cco and \bco
+is 36 \kms and 22 \kms, respectively.
  \label{fig:co32spec}}
@@
 centered on the lensing galaxy (\Fig{cont}).
-\new{We note that the reported flux uncertainties do not include those from absolute flux calibration.}
 Slightly extended emission
@@
 This suggests that we detect emission in both
-the foreground galaxy and the background galaxy and that the
+the foreground and the background galaxy and that the
 emission is marginally resolved along its major axis.
 We subtract a point source model in the $uv$-plane to remove the unresolved part of the
-emission, which we here assume to be dominated by the foreground galaxy. The peak emission
-\old{(0.39\,$\pm$\,0.08\,mJy)}
-\new{of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy}
-in the residual map coincides with the lensed arc, and is consistent with
+emission, which we here assume to be dominated by the foreground galaxy. The peak 
+\old{flux (0.39\,$\pm$\,0.08\,mJy)}
+\new{emission}
+in the residual map coincides with the lensed arc, \old{and} \new{with 
+a flux density of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy.}
+\new{This peak flux} is consistent with
 the difference between the integrated and the peak flux in the
 original continuum map ($\sim$0.4 mJy).
-We therefore adopt \old{$S_{\nu}$ = 0.39\pmm0.08 mJy} \new{$S_{\nu}$\eq0.39\pmm0.22 mJy} as the 2\,mm continuum flux measurement for
+We therefore adopt \old{$S_{\nu}$ = 0.39\pmm0.08 mJy} \new{$S_{\nu}$\eq0.39\pmm0.12 mJy} as the 2\,mm continuum \old{emission towards} \new{flux measurement for}
 the background galaxy (RXJ1131).
-\old{The quoted uncertainty is from the flux measurement in the residual map, }
-\new{The quoted uncertainty is solely based on the uncertainties associated with the flux density of the
-point source model ($\delta S_{\nu}$\eq0.088\,mJy) and
-that of the integrated flux in the original data (0.2\,mJy), }and does not account for that in the
+The quoted uncertainty is \old{from the flux measurement in the residual map, }
+\new{derived by adding those associated with the flux density of the
+point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and the peak flux in the residual map (0.08 mJy) in 
+quadrature,}
+and does not account for that in the
 de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
@@
 Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
-\new{Contours correspond to [10, 40, 60, 100]\%$\times$ the peak flux density of $S_{\rm 5GHz}$\eq0.74\pmm0.01 mJy.}
-% Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$,
-% where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne.
+\new{Contours correspond to $\pm2^n\sigma$, where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
+and $n$ is an integer starting from 2 to 5.
+Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$.}
 The central crosses in both panels indicate the centroid of the foreground galaxy,
@@
 We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
-We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.024}\new{0.02}
-for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.345}\new{0.35}
+We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.024}\new{0.02\pmm0.07}
+for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.345}\new{0.35\pmm0.21}
 for the background galaxy by fitting
@@
 5\,GHz and 2\,mm.
-\new{The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission ($\alpha$\ssim$-$0.7), suggesting
-that a dominant fraction of the observed 2\,mm emission arises from cold dust and free-free emission.
-% that the 2\,mm emission is dominated by non-synchrotron emission.
-This spectral slope would only be shallower
-if a non-negligible fraction from the background source
-contribute to the point source flux at 2\,mm in the deblending process. This would also
-explain the atypical flat spectrum found for the foreground galaxy.
-Assuming a synchrotron slope of $\alpha$\ssim$-$0.7 and that the emission at 5\,GHz is purely synchrotron,
-we find $S_{\rm 2mm}$\eq0.27\pmm0.22\,mJy from cold dust and free-free emission in the background galaxy. }
+\new{The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; ][]{Andreani93a}}, suggesting 
+that a fraction of the observed 2\,mm emission arises from thermal dust and free-free emission. 
+This spectral slope would be even shallower 
+if the background source has a contribution in the
+2\,mm flux of the point-source model used
+in the deblending process. This would also 
+explain the flat spectrum found for the foreground galaxy that is atypical of elliptical galaxies. 
+Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we find
+a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm      % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
+for the background source based on its 5\,GHz flux,
+and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy that arises from thermal dust emission.}
 
@@
 Top: each panel corresponds to a channel map of width 107.5\,\kms \old{of the observed
-emission (red) overlaid on} \new{around the annotated central velocity where
+emission (red) overlaid on} \new{around the labelled central velocity where
 the observed emission (red contours) is over-plotted atop} the best-fit model (grayscale).
@@
 varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
-\new{Previous studies of RXJ1131 find evidence for differential lensing across
+\new{
+Previous studies of RXJ1131 find evidence for differential lensing across 
 the {\it HST} $V$-, $I$-, and $H$-bands, where the
-magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
-Here, we find that the highly asymmetric \mbox{\bco} line profile is predominantly a result of
-differential lensing, where the redshifted emission is apparently much brighter than the
-blueshifted component, as indicated by the difference in their magnification factor $(\mu_{\rm L})$, which
-varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model})}.
-A secondary effect contributing to the asymmetry is caused by
-the CO emission in the companion in the redshifted velocity channels.}
+magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}, indicating that
+the spatial positions and extents of different stellar populations within the host galaxy are dissimilar with respect
+to the caustic.
+Here, 
+the best-fit lens models obtained for different CO channel slices show that differential lensing also plays 
+an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
+from 8.7 to 3.1 across different kinematic components (\Tab{model}).
+The asymmetry in the line profile is therefore predominantly a result of differential lensing, where 
+the redshifted CO-emitting gas is only apparently much brighter than the
+blueshifted component due to a higher magnification factor.
+A secondary effect contributing to the asymmetry is likely caused by 
+the CO emission in the companion at the reddest velocities.}
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
@@
 \subsection{\bco Dynamical Modeling} \label{sec:dynamics}
-\new{As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy given
-its reconstructed source-plane locations of various kinematic components displaying
-a velocity gradient with a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}),
-and the disk-like morphology found for source-plane reconstructed optical-NIR emission
-\citepalias{Claeskens06a}.}
-Assuming the velocities of the respective channels used in the
+\old{Assuming the velocities of the respective channels used in the
  lens modeling correspond to solely the tangential component of the
 true velocity vector of a rotating disk (i.e., along the major axis),
-we extract a one dimensional PV diagram in \Fig{PV}
-by slicing across their source plane positions \new{along this major axis} (PA: 121\degr).
+we extract a one dimensional PV diagram in \mbox{\Fig{PV}}
+by slicing across their source plane positions (PA: 121\degr).
+}
+\new{As discussed in \mbox{\Sec{caveat}}, we interpret RXJ1131 as a disk galaxy as it displays
+evidence of a source-plane velocity gradient in the CO emission,
+a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}), 
+and a disk-like morphology in the source-plane reconstruction of optical-NIR emission
+\mbox{\citepalias{Claeskens06a}}.
+We extract a one dimensional PV profile as shown in the right panel of \Fig{PV}
+by assuming the velocities of the respective channels used in
+lens modeling correspond to solely the tangential component of the
+true velocity vector of a rotating disk, i.e., each velocity component would 
+be seen lying along the major axis of a rotating disk if observed with sufficiently high angular resolution.
+In this process, the positions for each velocity component (plotted as data points in the right panel of \Fig{PV})
+are extracted along the best-fitted major axis, which is along a PA of 121\degr.}
 
@@
 \includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
-\caption{Left: \old{Source-plane positions from best-fit \mbox{\bco} lens models are indicated with their associated uncertainties atop
+\caption{Left: 
+\old{Source-plane positions from best-fit \mbox{\bco} lens models are indicated with their associated uncertainties atop
 the observed first moment map}
@@
 for the PdBI 2\,mm continuum in our fitting procedure.
-Here, we use a flux density of $S_{\rm 2mm}$\eq0.27 mJy derived in \Sec{deblend}
+Here, we use a flux density of $S_{\rm 2mm}$\eq0.27\pmm0.08mJy derived in \Sec{deblend}
 instead of the deblended 0.39\,mJy listed in \Tab{photometry}
@@
 \old{\mbox{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}} \new{\mbox{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
-dust mass of 16\petm{5}{12}\E{8}\,\Msun, \new{all of which are} uncorrected for lensing \new{magnification}.
+dust mass of 16\petm{5}{12}\E{8}\,\Msun, \old{uncorrected for lensing} \new{all of which are not lensing-corrected}.
 For the mass absorption coefficient, we adopt
@@
 a \fir luminosity \LFIR of \old{\mbox{4.72\petm{2.54}{2.26}\E{12}\,\Lsun}} \new{\mbox{4.24\petm{2.17}{2.00}\E{12}\,\Lsun}} and a
-dust mass $M_{\rm dust}$ of \old{\mbox{11\petm{5}{6}\E{8}\,\Msun}} \new{\mbox{14\petm{5}{7}\E{8}\,\Msun}}, all of which are uncorrected for lensing.
+dust mass $M_{\rm dust}$ of \old{\mbox{11\petm{5}{6}\E{8}\,\Msun}} \new{\mbox{14\petm{5}{7}\E{8}\,\Msun}}, all of which are \old{uncorrected for lensing}\new{not lensing-corrected}.
 Taken at face value, this implies an FIR-to-IR luminosity ratio
@@
 \mbox{H$\beta$ and [O\,{\scriptsize III}]} lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
-illustrating that large offsets (\mbox{$\Delta v$$\gtrsim$\,500\,\kms}) are uncommon but have been observed in some cases.}
-
-\new{Common interpretations invoked to explain offsets between BLR and systemic redshifts include
-e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing angle towards the accretion disk, 
-inclination effect, in which clumps in the accretion disk may block emission towards the far side of the disk, and thus the observed BLR emission is only
-originating from
-the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
-In the latter, \mbox{\citet{Sluse07a}} report a covering factor of 20\% based on \mbox{\mgii} absorption line at $z$\eq0.654.
-Additionally, differentially lensing of the compact BLR emission by microlensing in RXJ1131 \mbox{\citep[\eg][]{Sluse07a, Sluse12a}}
-may have boosted the redshifted component more than the blueshifted component,
-thereby biasing the BLR line centroids towards longer wavelengths.}
-{\bf DR: is it because of the large linewidth (one component of \mgii is $>$20000\kms, and broad comp.
-of H$\beta$ is $\sim$2000$-$4000\kms) that the referee thinks it's more likely to be inflow and therefore doesn't like the recoil black hole?
-Sluse07:
-"Another remarkable result is the presence in our spectra of a \mgii absorption doublet blueshifted at $z$\eq0.654. 
-According to its velocity shift ($\Delta v$\ssim$-$660\,\kms). 
-These lines disappear from the spectrum ratios A/B and C/B.
-This indicates that the absorbed flux is proportional to the flux coming from the continuum+BLR.
-This implies that the region at the origin of the absorption must cover both the continuum and the BLRs and that, within the uncertainties, their depths are identical in the spectra of the three images A, B, and C."
-ok.. so is it because of this broad absorption component of \mgii that is at the same $z$ as the NLR lines, and therefore implying that the BLR and 
-the AGN is not really spatially and kinematically offset, 
-but the offset is truly just a manifestation of a rotating disk + other kinematics (+ absorption of continuum by BLR moving towards us, redshfiting the line centroid, + inflow of material + clumps blocking the far side inflow?)
-}
+where only $\lesssim$20 of them are found to have offset $>$800\,\kms.
+Thus, large velocity offsets between BLR and NLR lines comparable to that of RXJ1131 are uncommon but 
+have been observed in some cases.}
 
@@
 BLR and the NLR may arise in a recoiling black hole (BH),}
-\new{Alternatively, the observed offset 
-may be explained by a more extreme scenario of a recoiling black hole (BH),}
+\new{The observed velocity offset between the BLR and NLR lines may be explained
+by a recoiling black hole (BH),}
 where its BLR is moving at high velocity relative to the bulk of its host galaxy
@@
 Several sources have been proposed as recoiling BH candidates, such as CID-42 at \mbox{$z$\,=\,0.359 \citep{Civano10a}} and
-SDSS 0956+5127 at \mbox{$z$\,$\sim$\,0.714 \citep{Steinhardt12a}}\old{. One notable system is}\new{, and} SDSSJ0927+2943 at \mbox{$z$\,$\sim$\,0.713}, where
+SDSS 0956+5127 at \mbox{$z$\,$\sim$\,0.714 \citep{Steinhardt12a}}\old{. One notable system is}\new{, and} SDSSJ0927+2943 at \mbox{$z$\,$\sim$\,0.713}\old{, where}\new{In the case of 
+SDSSJ0927+2943, the black hole recoil scenario was proposed based on the 
+velocity offset between}
 a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
-have been observed \mbox{\citep{Komossa08a}}\old{, similar to the case for RXJ1131}.
-However, this scenario was recently refuted by \mbox{\citet{Decarli14a}}, who confirm that the
-BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
+\old{have been observed} \mbox{\citep{Komossa08a}}\old{, similar to the case for RXJ1131}.
+However, this \old{scenario} was recently refuted by \mbox{\citet{Decarli14a}}, who find that the
+BLR lines in SDSSJ0927+2943 are indeed consistent with its CO systemic redshift.
 This is in contrast with RXJ1131, where our CO observations confirm the \old{blueshifted}\new{redshifted} BLR.
@@
 
-\new{The available data do not provide direct evidence favoring any of the above scenarios, 
-we therefore cannot rule out any of the above plausible scenarios; $\lesssim$1-kpc
-resolution observations probing the morphology, structures and kinematics of the (ionized) gas and 
-stellar (e.g., via H$\alpha$ kinematics measurements) would be useful to distinguish between these scenarios.}
+\new{Alternative scenarios 
+e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing 
+angle towards the accretion disk, and 
+inclination effect together with a clumpy accretion disk
+are more commonly invoked to explain velocity offsets between BLR and systemic redshift.
+In the context of the last scenario, 
+\mbox{\citet{Sluse07a}} report a covering factor of 20\% for the accretion disk in RXJ1131
+based on its broad \mgii absorption line at $z$\eq0.654.
+Additionally, the centroids of the BLR lines in RXJ1131 may be biased towards longer wavelengths due to
+microlensing \mbox{\citep[\eg][]{Sluse07a, Sluse12a}}, which may have
+magnified the redshifted component of the compact BLR more strongly than its blueshifted component.}
+
+\new{With the existing data, we do not favor a particular scenario mentioned above as the interpretation for 
+the observed velocity offset.}
 
@@
 resolved CO study at intermediate redshift.
-Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.66\,\pm\,0.41$
+Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq\old{0.66\pmm0.41}\new{0.78\pmm0.37}
 between the \bco and \cco lines,
@@
 that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are redshifted by \old{$\sim$780\,\kms}\new{$\sim$715\,\kms}.{\bf MAY ADD STUFF ABOUT RECOIL BH..}
-\old{This implies that the AGN is offset from the dynamical center of its host galaxy.
+but the optical BLR lines are redshifted by \old{$\sim$780\,\kms}\new{$\sim$715\,\kms}.\old{This implies that the AGN is offset from the dynamical center of its host galaxy.
 One explanation could be that the
@@
 we thus raise an alternative explanation of a recoiling black hole in RXJ1131, which
-would also explain the high spin parameter reported by \mbox{\citet{Reis14a}}.}
+would also explain the high spin parameter reported by \mbox{\citet{Reis14a}}.}\new{
+Using the CO redshift as systemic redshift for the host galaxy of RXJ1131, we find
+that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
+but the optical BLR lines are redshifted by $\sim$715\,\kms. 
+We raise several plausible scenarios that may explain the observed velocity offset, \eg
+outflow/inflow of gas in the BLR, kinematics of the accretion disk, geometric effects,
+microlensing, and a recoiling black hole.
+The latter scenario might also explain the high black hole spin parameter reported by 
+\mbox{\citet[$a$\ssim0.9][]{Reis14a}}.
+With the available data, 
+we do not favor a particular scenario mentioned above as the interpretation for the observed velocity offset.
+}
 

### 2016-11-22 WRITEUP/ms.tex
the source file for ms.pdf in bf07670 (2 commits before), forgot to add this together in that commit

@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-The velocity scale is the same as in \Fig{CO21spec}
+The velocity scale is the same as in \Fig{CO21spec}.
 The spectral resolution for \cco and \bco
@@
 This suggests that we detect emission in both
-the foreground and background galaxy and that the
+the foreground and the background galaxy and that the
 emission is marginally resolved along its major axis.

### 2016-11-23 WRITEUP/table_magFactor.tex
swapped mag. for RXJ1131 and companion. if showing spectrum, where companion has lower intrinsic flux, then it must have higher mag. factor; CAVEAT: didn't recalc. the weighted average in magnnification factor, but should be fine because we only use the median and not the weighted average in physical parameters"

--- 2016-11-05 WRITEUP/table_magFactor.tex
@@
 \startdata
-346\,$-$\,260       & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ 
-238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.7ex]\hline
+346\,$-$\,260       & 6.7 $\pm$ 2.5 &  7.2 $\pm$ 5.6 \\
+238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
 131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
 24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
--84,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
+-84\,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
 -191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
--300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
+-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.7ex]\hline
 weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]

### 2016-12-08 WRITEUP/response.md
ready for DR again

@@
 We have addressed all the concerns raised by the referee in the revised version of the manuscript.
-Our response can be found after each of the referee's points below.
+Our response can be found after each of the referee's points below and are marked by a "#" symbol at the beginning.
 
@@
 # RESPONSE:
-1a) To take the referee's point into account, we have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXSJ1131-1231".
-We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (including lens modeling).
+1a) To take the referee's point into account, we have changed the title to "Molecular gas kinematics and spectral energy distribution properties of the strongly lensed quasar host galaxy RXSJ1131-1231".
+We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (including lens modeling) on which we thus place an emphasis.
 
@@
 We have taken into account the referee's comment and have updated the CO redshift based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig.
-5), and re-plotted all the relevant figures with the updated velocity scale.
-We have also changed our wording in fig.
-1 caption "dynamical center" to "line center".
+5), and we have revised all relevant figures and derived quantities.
+We have also changed our wording in the caption of Fig.
+1 from "dynamical center" to "line center".
 
@@
 # RESPONSE:
-We agree with the referee's comment and have changed "dynamical information" to "kinematic information", "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".
+We agree with the referee's comment and have changed "dynamical information" to "kinematic information", and "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".
 
-To address the referee's comment on the paragraph (2nd paragraph of Sec 4.1.2.) regarding the differential lensing effect in CO and that in the optical emission (Claeskens+06), we have re-written this paragraph to clarify what we seek to convey -- the difference in magnification factor between CO gas across all channels (µ ~ 5.5) versus those found in the optical emission indicates different morphology and spatial distribution between the CO gas, and the stellar population of different ages.
+To address the referee's comment, we have re-written the 2nd paragraph of Section 4.1.2.
+Rather than saying the differential lensing effect in CO is *similar* to what is seen in the optical, we point out that different magnification factors have been reported in previous studies using optical images.
+This is done to illustrate the prominence of differential lensing effect in this source, and to demonstrate that the CO gas traces a different region in the source plane and has a different spatial distribution compared to the stellar populations.
 
@@
 We agree with the referee and have re-fitted a doubled Gaussian to the de-lensed profile (Fig.
-5) to updated the redshift to z=0.65406.
+5) to updated the redshift to z=0.6541.
 We have therefore replotted all the relevant figures (and updated their captions correspondingly), updated column 1 in Table 3 and the labeling in Fig 7, refitted the arctangent model (Fig.
-9) and updated parameters in Sec 4.3 correspondingly, and refitted SED with the updated redshift.
+9) and updated parameters in Section 4.3 correspondingly, and refitted SED with the updated redshift.
 
@@
 1).
-Since our lensing-corrected M_gas for both RXJ1131 and the companion are derived from the flux in each channel, this does not change our conclusion.
+Since the lensing-corrected M_gas for both RXJ1131 and the companion are derived by first summing up the flux density of each channel within the FWZI, and then dividing by their respective magnification factors.
+This revision in the CO line intensity does not change our conclusion of this paper.
 
-We attempted to over-plot the companion's spectrum to Fig.
-5, as suggested by the referee, but found the figure to be too busy as the plot is showing various spectra with different various linestyles and colors.
-This main message for this plot is to show that we recover an intrinsically symmetric line profile for the main galaxy which is informative about its gas kinematics.On the other hand, the useful information regarding the companion from the de-lensed spectrum is the gas mass, which we report in the text (and in the table, as suggested by the referee).
+We have adopted the suggestion provided by the referee and have updated Fig. 5 to include an additional figure showing the de-lensed spectra for RXJ1131 and the companion.
 
@@
 CO physical size:
-The rough estimate of de-magnified CO diameter provided in the referee report is a valid first order estimate, but the true size of the source is complicated by the fact that
+The rough estimate of the de-magnified CO diameter provided in the referee report is a valid first order estimate, but the true size of the source is complicated by the fact that
 1) the lensed emission is not uniformly stretched along the arc (and contains complex structures within the arc), and thus the magnification factor is not uniform across the partial Einstein ring. 
-2) CO is not subject to dust extinction, therefore its emission may be more extended than optical emission.
+2) CO is not subject to dust extinction, and its emission may be more extended than optical emission.
 In the case of RXJ1131, the CO gas is likely to be more extended than the optical emission given that
     i) the deconvolved source size of CO (see above and section 3.1) is larger than the diameter of the Einstein Ring in the optical (~3.6")
-    ii) the spatial extent of the CO emission as shown in Fig. 7, where the centroid of the blueshifted emission is further out in the SE compared to the lensed arc in the optical
-    iii) the source-plane spatial distribution from the best-fit lens models (Sec 4.3, Fig.
-9), where the most extended velocity component is ~6.2 kpc from the line center position, indicating that the CO source size is unlikely to be R ≤ 3.5 kpc.
+    ii) the spatial extent of the CO emission as shown in Fig.
+7, where centroid of the redshifted component is co-spatial with the lensed arc but centroid of the blueshifted component is offset to the SE of the lensed arc, tracing regions beyond the optical emission.
+3) the source-plane distance of ~6.2 kpc between the centroid position of the most extended kinematic component and the line center position.
+This is also the value we use for reporting R_CO throughout this paper.
 
-The R_CO size of ~6 kpc reported throughout the paper is obtained based on the centroid position of the most extended kinematic component obtained from the best-fit lens models.
-See also Sec 4.3 and our response to point 14 in this referee report for a more detailed explanation regarding the CO size.
+See also Section 4.3 and our response to point 14 in this referee report for a more detailed explanation regarding the CO size.
 
@@
 To address the referee's comment and to demonstrate the significance of our detection that is reported in the paper, we have extracted the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
-For the blue wing, we find a peak flux density of 5.13 +/- 1.43 Jy km/s /beam in the intensity map, indicating a ≥3sigma detection in this component.
+For the blue wing, we find a peak flux density of 5.13 +/- 1.43 Jy km/s /beam in the intensity map, indicating a ≥3sigma detection in this component alone.
 For the red wing, we find a peak flux density of 11.45+/-1.99 Jy km/s /beam in the intensity map, indicating a ~6 sigma detection.
@@
 
-To taken into account the referee's comment, we have updated the 2mm flux in Table 1, and the flux uncertainty to include those from the uv-fitting process.
+To take into account the referee's comment, we have updated the 2mm flux in Table 1, and the flux uncertainty to include those from the uv-fitting process.
 
@@
 
-# RESPONSE: (explain better)
-While the radio-mm spectral slope of -0.35+/-0.21 derived for the background source has a large error bar associated with it due to the large uncertainty on the 2mm flux (0.39+/-0.12 mJy), the fact that it is flatter than the typical slope for pure synchrotron emission indicates that it is a constraint on the fraction of synchrotron emission at 2mm, and that a fraction of the 2mm flux arises from thermal dust and free-free emission.
+# RESPONSE:
+While the radio-mm spectral slope of -0.35+/-0.21 derived for the background source has a large error bar associated with it due to the large uncertainty on the 2mm flux (0.39+/-0.12 mJy), the fact that it is significantly flatter than the typical slope for pure synchrotron emission indicates that it provides a limit on the amount of synchrotron emission at 2mm.
+Thus, we used this radio-mm spectral slope to estimate the expected flux from synchrotron emission at 2mm, and attribute the residual flux to thermal dust emission.Assuming a synchrotron index of alpha = -0.7 and using the 5GHz flux, we expect S_2mmm = 0.122+/-0.004 mJy to be arising from synchrotron emission.
+We thus find a flux excess of S_2mm = 0.39 - 0.12 = 0.27 mJy that is coming from thermal dust emission.
+We have updated our dust SED fitting using S_2mm = 0.27+/-0.08 mJy and the resulting parameters throughout the paper.
+
+We note that 0.27+/-0.08 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.12 mJy, including uncertainties from absolute flux calibration) within the uncertainties.
+Therefore changes to the physical parameters derived from SED fitting are only at most a few percent.
+We have updated the relevant quantities but this does not alter the conclusions of this paper.
 
 Flat spectrum of foreground galaxy:
-We have also added a statement in the paper, stating that if the background source has a contribution in the point-source model assumed in our deblending procedure, such that its flux density would be higher than derived here (0.39 +/- 0.12 mJy), then the derived spectral index (-0.35) would be even shallower.
+We have also added a statement in the paper stating that if the background source has a contribution in the point-source model assumed in our deblending procedure, such that its flux density would be higher than derived here (0.39 +/- 0.12 mJy), then the derived spectral index (-0.35) would be even shallower.
 In this case, the 2mm flux inferred for the foreground galaxy would lower, and thus steepening its spectral slope.
 Hence, a contribution from the background source to the point-source model 2mm flux may explain the atypical flat spectrum found for the foreground galaxy.
-
-Decompose synchrotron at 2mm for the background source:
-The flatter than pure synchrotron spectral slope found for the background source indicates that the 2mm continuum emission is not dominated by synchrotron emission.
-Assuming a synchrotron index of alpha = -0.7 and using the 5GHz flux, we expect S_2mmm = 0.122+/-0.004 mJy to be synchrotron emission.
-We thus find a flux excess of S_2mm = 0.39 - 0.12 = 0.27 mJy that is coming from thermal dust and free-free emission.
-We have updated our dust SED fitting using S_2mm = 0.27+/-0.08 mJy and the resulting parameters throughout the paper.
-
-We note that 0.27+/-0.09 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the uncertainties, where the uncertainties here include those from absolute flux calibration, therefore changes to the physical parameters derived from SED fitting are only at most a few percent.
-We have updated the relevant quantities but this does not alter the conclusions of this paper.
+Alternatively, the foreground galaxy could be a core-dominated radio objects, and thus displays a flat spectrum.
 
@@
 The same is true of the derived quantities. 
-Possible add another Table summarizing the other derived quantites:
+Possible add another Table summarizing the other derived quantities:
 
@@
 # RESPONSE:
-We adopted the good suggestions and have added additional tables summarizing the observed CO line properties and the derived physical parameters.
+We adopted these good suggestions and have added additional tables (Table 1 and 6) summarizing the observed CO line properties and the derived physical parameters.
 
@@
 # RESPONSE:
-It is of standard practice to report flux measurements from interferometric observations excluding those from the absolute flux calibration and state those in the observations section (i.e.
+It is the standard practice to report flux measurement uncertainties from interferometric observations separate from those due to absolute flux calibration and state those in the observations section (i.e.
 Section 2).
-Throughout the paper, uncertainties from absolute flux calibration are taken into account when deriving the error bars associated with physical parameters.
-To address the referee's concern, we have added a remark in table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.
+However, we note that uncertainties from absolute flux calibration are taken into account when deriving the error bars associated with physical parameters throughout the paper.
+To address the referee's concern, we have added remarks in Table 1, and Section 4.5 paragraph 1 to remind the reader of these uncertainties.
 
-We have updated the number of decimals in the spectral indices reported in Sec 3.3, as suggested by the referee.
+We have updated the number of decimals in the spectral indices indexes reported in Section 3.3, as suggested by the referee.
 
@@
 # RESPONSE
-We have replotted the figure with different contour intervals with thinner lines and added a sentence in the caption to improve the clarity of Fig 4.
+We agree with the referee and have revised Fig.
+4 by using a different contour interval for the VLA data and changed the linewidths of the contours.
+We have also updated the caption to illustrate the significance of the radio detection towards RXJ1131.
 
@@
 # RESPONSE:
-We have corrected "blueshifted" to "redshifted", updated the velocity offset from 780 km/s to 715 km/s using z = 0.65406, as suggested by the referee.
+We have corrected "blueshifted" to "redshifted", updated the velocity offset from 780 km/s to 715 km/s using z = 0.6541, as suggested by the referee.
 
@@
 
-Another possiblity is that the BLR shows mainly rotation 
+Another possibility is that the BLR shows mainly rotation 
 in the accretion disk, and also a biconical outflow region
@@
 1) & 2)
-Our CO measurement provides the most precise value for the velocity offset 
-between the BLR and the host galaxy.
-We thus feel that this is an invaluable addition to the literature.
-Taking into account the referee's comments, we have updated this section by listing other possible interpretations for the velocity offset (e.g.
-gas inflows, geometric effects) as part of the discussion, as outlined in detail by the referee.
+Our CO measurement provides the most precise value for the velocity offset between the BLR and the host galaxy. We thus feel that this is an invaluable addition to the literature.
+
+We acknowledge that velocity offsets between BLR and NLR lines are quite common in Seyferts and quasars, but the offsets as large as that of RXJ1131 appear to be uncommon according to the distribution of offset among other AGN hosts (Richards+02, Bonning+07).
+To take into account the referee's comments, we have updated this section by including a brief discussion on other possible interpretations for the velocity offset (e.g.
+gas inflows, geometric effects), as outlined in detail by the referee.
 
@@
 However, Loeb 2007 has showed that at low ejection speeds of a few hundred km/s, the recoil is expected to be damped by the external gravitational potential of the galaxy, dynamical friction against background stars, dark matter, and gas, thereby limiting the BH displacement and is likely to bring it back to the center of its host galaxy within a few dynamical times (Madau & Quataert 04, Boylan-Kolchin+04, Guedes+11).
-
-We acknowledge that velocity offsets between BLR and NLR lines are quite common in Seyferts and quasars, but the offsets as large as that of RXJ1131 appear to be uncommon according to the distribution of offset among other AGN hosts (Richards+02, Bonning+07).
-To take into account the referee's comments, we now also discuss other possible scenarios.
 
@@
 Explicitly stating the priors is important to demonstrate that our choice are reasonable and physically motivated since they could affect the marginal posteriors strongly, and thus the inferred physical parameters.
-We therefore decide to keep them in the lens modeling (Sec 4.1) and SED fitting sections (Sec 4.5).
+We therefore decided to keep them in the lens modeling (Section 4.1) and SED fitting sections (Section 4.5).
 
@@
 # RESPONSE:
-We updated f_gas and f_mol using M_gas and M_dyn of both RXJ1131+companion , i.e., as a merger system.
+We have updated f_gas and f_mol considering RXJ1131 and the companion as one system.
+That is, we have used the total M_gas obtained by summing up M_gas of RXJ1131 and of the companion in deriving f_gas, and the total M_dyn obtained by summing up M_gas of RXJ1131 and of the companion in deriving f_mol.
 
@@
 # RESPONSE:
-Indeed, the plot on the left is to demonstrate that while the observed 1st moment map is distorted due to a combination of differential lensing and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kinematic components.
+Indeed, the plot on the left is to demonstrate that while the observed 1st moment map is distorted due to a combination of differential lensing and beam smearing effects, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane positions for different kinematic components.
 Therefore, we show the source-plane positions atop of the observed 1st moment map.
-To address the referee's concern, we have added some additional description in the caption to clarify what is being shown in the left panel.
+To address the referee's concern, we have added some additional description to the caption to clarify what is being shown in the left panel.
 
-The reconstructed source-plane positions display a clear velocity gradient.
+The reconstructed source-plane positions display a clear velocity gradient that is reminiscent of a rotating disk-like object.
 Taken together with previous results from literature (C06) and the intrinsically symmetric line profile (Fig.
-5), we carried out dynamical modeling in Sec 4.3 assuming RXJ1131 is a disk galaxy.
+5), we carried out dynamical modeling in Section 4.3 assuming RXJ1131 is a disk galaxy.
 
 PV: 
-We have detailed the reasons for why we interpret RXJ1131 as a disk galaxy in Sec 4.1.1.
-Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraph of Sec 4.3).
+We have detailed the reasons for why we interpret RXJ1131 as a disk galaxy in Section 4.1.1.
+Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraph of Section 4.3).
 
-To address the referee's concern and to improve the clarity of this section, we have re-iterate in the beginning of Sec 4.3 that we assume RXJ1131 to be a disk galaxy for dynamical modeling.
+To address the referee's concern and to improve the clarity of this section, we have added the following at the beginning of Section 4.3 to remind the reader that we are assuming RXJ1131 to be a disk galaxy for dynamical modeling.
+
+"As discussed in §4.1.1, we interpret RXJ1131 as a disk galaxy as it displays evidence of a source-plane velocity gradient in the CO emission, a symmetric double-horned line profile (Figure 5, Figure 6 and, left panel of Figure 9), and a disk-like morphology in the source-plane reconstruction of optical-NIR emission (C06)"
 
 Size:
-As explained in para.
-3 of Sec 4.3, we use the maximum observed velocity (i.e.
-corresponding to the redmost channel along the disk major axis) at 6+/-3kpc as a proxy for the rotation velocity.
+As explained in paragraph 3 of Section 4.3, we use the maximum observed velocity (i.e.
+corresponding to the red-most channel along the disk major axis) at 6+/-3 kpc as a proxy for the rotation velocity.
 Thus the quoted CO disk radius corresponds to the extent of this velocity component, as measured from the centroid position at zero velocity.

### 2016-12-08 WRITEUP/ms.tex
ready for DR again

@@
 \input{preamble}
-\slugcomment{To be submitted to the ApJ}
+\slugcomment{To be submitted to the ApJ, with changes from the referee report }
  \makeatletter
@@
 \begin{document}
-%{\tiny  \RevisionInfo}
-
-\title{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
+
+\title{Molecular Gas Kinematics and Spectral Energy Distribution Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 Observations of the \cco rotational line 
-($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
-towards RXJ1131 at $z_{\rm QSO}$\eq0.658 
+($\nu_{\rm rest}$\,=\,345.79599\,GHz) towards RXJ1131 at $z_{\rm s, QSO}$\eq0.658 
 were carried out with the \carma (CARMA;
-Program ID: cf0098; PI: D. Riechers) in the D array configuration. They were carried out
+Program ID: cf0098; PI: D. Riechers) in the D array configuration. 
+The line frequency is redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz at the quasar redshift.
+Observations were carried out
 on 2014 February 02 under poor 1.5\,mm
@@
 imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
-beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
+beam size of 3\farcs2 $\times$ 1\farcs9 at a position angle (PA) of 8\degr for the lower sideband
 image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
@@
 ($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
-redshifted to $\nu_{\rm obs}$\eq139.256\,GHz towards RXJ1131
-at the
-CARMA \cco redshift of $z_{\rm CO(3-2)}$\eq0.655
+towards RXJ1131
 were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
 Riechers).
+Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
+the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
 Two observing runs were carried out on 2014 December 06 and 2015
@@
 \end{figure}
-\vspace{.2em}
+
 % moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
@@
 
-The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
-to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  % In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
-consistent with that obtained by $uv$-plane fitting within the uncertainties. 
+The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian 
+to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  
+% In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
+which is consistent with that obtained by visibility-plane fitting within the uncertainties. 
 % UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
-The spatial distribution of the observed CO emission is unlikely to be fully 
-encapsulated by a simple Gaussian 
-given its skewed emission, which also appears to be a superposition of two components (\Fig{CO21mom}). 
-% To better capture the spatial distribution of the line emission, we 
-We therefore also fit a model of two Gaussians which yeilds deconvolved source sizes of 
+Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
+and appears to be a superposition of two components (top left panel of \Fig{CO21mom}), 
+we also fit two Gaussians to the intensity map. 
+This yields deconvolved source sizes of 
 3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
-The deconvolved source size together with
-% complex morphology of a partial ``Einstein ring'' with 
-% structures along the arc and knots 
-% seen in optical and \nir emission (see \Fig{CO21mom}). %that were observed at higher resolution, 
-the spatially more extended blue wing compared to the optical 
-``Einstein ring" of diameter $\sim$3\farcs6 (top right panel of \Fig{CO21mom}) suggest that 
-the CO-emitting region in RXJ1131 is more extended than its stellar and quasar emission.
+The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended 
+than the optical 
+``Einstein ring'', which has a diameter of $\sim$3\farcs6
+(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one). 
+This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image, 
+and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
+Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.
 
@@
 are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
-The contours in both top panels start at 3$\sigma$ and increment at steps of
+The contours in both top panels start at 3$\sigma$ and increment in steps of
 $\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
@@
 % indicating a $\sim$\,6$\sigma$ detection. 
-We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing,
+We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing,
 indicating a $\sim$\,6$\sigma$ detection. 
 We estimate a line intensity of 35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop}) by summing up fluxes over the FWZI
-linewidth used to infer the \bco line intensity ($\sim$700 \kms).
-
-Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
+linewidth used to infer the \bco line intensity.
+
+Assuming that the spatial extent of \bco and \cco is similar and therefore the emission is
 magnified by the same amount, the measured line intensities
 correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.37, where this error bar includes 
-the uncertainties in absolute flux calibration.
-This ratio is consistent with
+$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.37.
+The quoted error bar is derived by adding the uncertainties associated with the CO line intensities 
+and those from absolute flux calibrations in quadrature.
+This brightness temperature ratio is consistent with
 thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
-nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
-with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
+nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, Riechers11b, CW13}, but also
+with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13, Daddi15a}.
 % see DANNERBAUER09 intro
@@
 emission is marginally resolved along its major axis.
-We subtract a point source model in the $uv$-plane to remove the unresolved part of the
-emission, which we here assume to be dominated by the foreground galaxy. The peak emission
-in the residual map coincides with the lensed arc, with a flux density 
-of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy. 
-This peak flux is consistent with
-the difference between the integrated and the peak flux in the
+We subtract a point source model in the visibility-plane to remove the unresolved part of the
+emission, which we here assume to be dominated by the foreground galaxy. The emission
+in the residual map coincides spatially with the lensed arc. We measure a flux density 
+of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
+This flux density is consistent with
+the difference between the integrated and the peak flux density measured in the
 original continuum map ($\sim$0.4 mJy). 
-We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the 2\,mm continuum flux measurement for 
+We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the best estimate for the 2\,mm continuum flux of 
 the background galaxy (RXJ1131). 
-The quoted uncertainty is derived by adding those associated with the flux density of the 
+We here quote a conservative uncertainty, which is derived by adding those associated with the flux density of the 
 point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
 the peak flux in the residual map (0.08\,mJy) 
-in quadrature, and does not account for that in the 
+in quadrature. We caution that this does not account for that in the 
 de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
@@
 \caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
-Contours start and increment at steps of
+Contours start and increment in steps of
 $\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
-Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
+Bottom: overlay of the VLA 5\,GHz continuum emission on the optical image.
 Contours correspond to $\pm2^n\sigma$, where 
 $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne 
-and $n$ is an integer starting from 2 to 5. 
-Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$.
+and $n$ is an integer running from 2 to 5. 
+Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.
 The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
@@
 for the background galaxy by fitting
-power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum emission at
+power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
 5\,GHz and 2\,mm. 
-The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; ][]{Andreani93a}, suggesting 
-that a fraction of the observed 2\,mm emission arises from thermal dust and free-free emission. 
+The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}.
+This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
+that a fraction of the observed 2\,mm emission arises from thermal dust  emission. 
 This spectral slope would be even shallower 
-if the background source has a contribution in the
-2\,mm flux of the point-source model used
-in the deblending process. This would also 
-explain the flat spectrum found for the foreground galaxy that is atypical of elliptical galaxies. 
-Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we find
+if the background source contributes to the unresolved fraction of the
+2\,mm flux. This would also 
+explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
+Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we would expect
 a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm      % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
-for the background source based on its 5\,GHz flux,
-and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy that arises from thermal dust emission.
+for the background source due to synchrotron radiation,
+and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
+likely arises due to thermal dust emission.
 
@@
 \includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
-\caption{The full resolution \bco spectrum (yellow histogram) and
+\caption{Top: the full resolution \bco spectrum (yellow histogram) and
 the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The
-blue histogram shows the ``intrinsic'' line profile of RXJ1131
+light blue histogram shows the ``intrinsic'' line profile of RXJ1131
 after subtracting a contribution from its companion galaxy and
@@
 above each respective model channel.
+Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
+The y-axis is shown on log scale (top) and linear scale (bottom).
 \label{fig:delensed}}
@@
 \caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
-Top: each panel corresponds to a channel map of width 107.5\,\kms around the labelled central velocity where
-the observed emission (red contours) is over-plotted atop the best-fit model (grayscale). 
+Top: each panel corresponds to a channel map of width 107.5\,\kms centered on the indicated velocity.
+The observed emission (red contours) is over-plotted atop the best-fit model (grayscale). 
 % the velocity annotated in each panel is the center velocity of each of the seven channels used in lens modelling.
@@
 Contours start
-at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
+at $\pm$3$\sigma$ and increment in steps of 3$\times$2$^n\sigma$,
 where $n$ is a positive integer.
@@
 In the image-plane integrated line map shown in \Fig{CO21mom}, the redshifted component is
-cospatial with the Einstein ring seen in the
-optical image, with most of its apparent flux originating from the lensed arc
-in the southeast, whereas the blue component is predominately coming from
-solely the lensed arc. To further illustrate this, we show the
+cospatial with the Einstein ring that is seen in the
+optical image, with most of its apparent flux originating along the lensed arc, 
+whereas centroid of the blueshifted emission is offset to the SE of
+the lensed arc. This suggests that the CO-emitting region in RXJ1131 is extended.
+To further illustrate this, we show the
 channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
@@
 Central velocities are shown at the top of each map.
-Contours start and increment at steps of
+Contours start and increment in steps of
 $\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
@@
 the {\it HST} $V$-, $I$-, and $H$-bands, where the
-magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}, indicating that
-the spatial positions and extents of different stellar populations within the host galaxy are dissimilar with respect
-to the caustic.
-Here, 
-the best-fit lens models obtained for different CO channel slices show that differential lensing also plays 
+magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
+This indicates that the spatial positions and extents of different stellar populations 
+within the host galaxy are dissimilar with respect to the caustic which may be a result of dust extinction and reddening.
+The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays 
 an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
@@
 blueshifted component due to a higher magnification factor.
-A secondary effect contributing to the asymmetry is likely caused by 
-the CO emission in the companion at the reddest velocities.
+A secondary effect is likely a result of including the CO emission from the companion in the most redshifted velocity channels.
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
@@
 As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy as it displays
-evidence of a source-plane velocity gradient in the CO emission,
+a kinematically-ordered velocity gradient in the source-plane velocity map of CO emission,
 a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}), 
@@
 \citepalias{Claeskens06a}.
-We extract a one dimensional PV profile as shown in the right panel of \Fig{PV}
-by assuming the velocities of the respective channels used in
-lens modeling correspond to solely the tangential component of the
+We extract a one dimensional position-velocity (PV) profile 
+by assuming that the source-plane centroids of different velocity components
+obtained from dynamical lens modeling
+are dominated by the tangential component of the
 true velocity vector of a rotating disk, i.e., each velocity component would 
-be seen lying along the major axis of a rotating disk if observed with sufficiently high angular resolution.
+be seen as lying along the major axis of a rotating disk if observed with sufficiently high angular resolution 
+(see right panel of \Fig{PV}).
 In this process, the positions for each velocity component (plotted as data points in the right panel of \Fig{PV})
@@
 \includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
-\caption{Left: Source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown 
+\caption{Velocity gradient of the \bco emission observed in RXJ1131 and the de-lensed velocity gradient obtained from lens modeling.
+Left: source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown 
 as markers color-coded by their velocities
 atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). 
-The contours are at steps of 50\,\kms. 
+The contours are in steps of 50\,\kms. 
 Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
@@
 emission of warm and small dust grains.
-The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak and 
-an uncertainty from absolute flux calibration of $\sim$15\% is added in quadrature 
-% to obtain the total uncertainties 
-for the PdBI 2\,mm continuum photometry in our fitting procedure. 
+The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak.
 Here, we use a flux density of $S_{\rm 2mm}$\eq0.27\pmm0.08 mJy derived in \Sec{deblend} 
-instead of the deblended 0.39\,mJy listed in \Tab{photometry} 
-to exclude synchrotron emission (see \Sec{deblend}) in dust SED modeling.
+instead of the deblended flux listed in \Tab{photometry} 
+to exclude a potential contribution due to synchrotron emission (see \Sec{deblend}) in the dust SED modeling.
+An uncertainty from absolute flux calibration of $\sim$15\% is added in quadrature 
+to the PdBI 2\,mm continuum photometry in our fitting procedure.
 
@@
 3.81\petm{1.92}{1.97}\E{12}\,\Lsun, and a
-dust mass of 16\petm{5}{12}\E{8}\,\Msun, all of which are not lensing-corrected.
+dust mass of 16\petm{5}{12}\E{8}\,\Msun, all of which are not corrected for lensing magnification.
 For the mass absorption coefficient, we adopt
@@
 with (without) MIR constraint at 24\,$\micron$.
-The solid black line shows the best-fit SED model with dust attenuation obtained using the \ncode{magphys} code, whereas
-the light blue solid line shows the unattenuated stellar emission. 
+The solid black line shows the best-fit SED model obtained using the \ncode{magphys} code.
+The light blue solid line shows the unattenuated stellar emission. 
 \label{fig:SED}}
@@
 \section{Discussion} \label{sec:diss}
-The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}.
 \input{table_propRXJ}
@@
 On the other hand, we would also obtain a higher gas mass if
-we assumed sub-thermal excitation between \bco and \aco emission.
+we were to assume sub-thermal excitation between \bco and \aco emission.
 % but this may be a minor effect as CO emission in local ULIRGs is typically thermalized up to $J$ = 3 or 4 \citep{,CW13}.
@@
 % \mgii & Hbeta: outer part of the BLR (Goad12a) compared to high-ionization lines (\eg CIV)
+% \oiii is forbidden, must be from low-density region (further out)
 % Hbeta can also come from NLR
@@
 \citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
-The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and the \mgii emission line.
+The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at 
+$z_{\rm s, QSO}$\ssim0.658, including the broad component of the Balmer lines and the \mgii emission line.
 Using the CO line center redshift as the systemic redshift,
@@
 On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
-Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature, e.g., 
-\citet{Richards02a} find a
-median of 97\kms and a dispersion of 269\,\kms in the distribution of
-offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in a
+Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature.
+\citet{Richards02a} find an offset of 
+% median of 97\kms and a dispersion of 269\,\kms in the distribution of offset
+$\sim$100\pmm270\,\kms 
+between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in a
 sample of $>$3800 quasars,
-and \citet{Bonning07a} find a mean offset of 100\,\kms with a dispersion of 212\,\kms
+and \citet{Bonning07a} report
+an offset of 
+% a mean offset of 
+% 100\,\kms with a dispersion of 212\,\kms
 %FWHM = 500
+$\sim$100\pmm210\,\kms
 between the broad component of
 H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
-where only $\lesssim$20 of them are found to have offset $>$800\,\kms.
+where only $\lesssim$20 of them ((i.e., $<$1\%) are found to have offsets $>$800\,\kms.
 Thus, large velocity offsets between BLR and NLR lines 
@@
 a recoiling black hole (BH), 
-where its BLR is moving at high velocity relative to the bulk of its host galaxy
+where the BLR is moving at high velocity relative to the bulk of its host galaxy
 \citep{Madau04a, Bonning07a, Loeb07a}.
@@
 Depending on their initial conditions (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
-numerical relativity simulations have shown that the recoil velocity can reach up to 
+numerical relativity simulations have shown that recoil velocities can reach up to 
 $v_{\rm kick}$\ssim4000\,\kms for spinning BHs, 
-with a typical offset recoil velocity of $v_{\rm kick}$\ssim100\,$-$\,500\,\kms 
+with typical recoil velocities of $v_{\rm kick}$\ssim100\,$-$\,500\,\kms 
 \citep[\eg][]{Libeskind06a,Campanelli07a}.
-Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a},
-SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}, and
-SDSS J0927+2943 at $z$\,$\sim$\,0.713.
-In the case of SDSS J0927+2943, the black hole recoil scenario was proposed based on
-the velocity offset between a set of redshifted narrow lines and a second set of 
-blueshifted broad AGN lines \citep{Komossa08a}.
-However, this was recently refuted by \citet{Decarli14a}, who find that the
-BLR lines in SDSSJ0927+2943 are indeed consistent with its CO systemic redshift.
-This is in contrast with RXJ1131, where our CO observations confirm the redshifted BLR lines.
+Several sources have been proposed as recoiling BH candidates \citep[][]{Komossa08a, Civano10a, Steinhardt12a}.
+% For the candidate SDSS J0927+2943 at $z$\,$\sim$\,0.713 \citep{Komossa08a}, 
+However, \citet{Decarli14a} have recently refuted 
+such scenario for one of the candidates --- SDSS J0927+2943 --- by finding that the redshift of its
+BLR lines is indeed consistent with its CO systemic redshift.
+This is in contrast with RXJ1131, where our CO observations confirm 
+the redshifted BLR lines compared to the CO systemic redshift.
 Since this scenario requires a coalesced BH, it would imply that RXJ1131 
@@
 Alternative scenarios 
-e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing angle towards the accretion disk, and 
-inclination effect together with a clumpy accretion disk
+e.g., outflow/inflow of gas in the BLR, viewing angle towards the accretion disk, and 
+obscuration in the clumpy accretion disk
 are more commonly invoked to explain velocity offsets between BLR and systemic redshift. 
-% , in which clumps in the accretion disk may block emission towards the far side of the disk, and thus the observed BLR emission is only originating from
-% the redshifted inflowing gas component in the near side of the accretion disk of RXJ1131.
-In the context of the last scenario, 
+Since the BLR lines of RXJ1131 show positive velocity offsets with respect to its systemic redshift, it may imply that 
+obscuration may be causing the observed 
+BLR line emission to be dominated by gas that is flowing into the central BH or the receding component of
+the accretion disk.
 \citet{Sluse07a} report a covering factor of 20\% for the accretion disk in RXJ1131
@@
 magnified the redshifted component of the compact BLR more strongly than its blueshifted component.
-
-With the existing data, we do not favor a particular scenario mentioned above as the interpretation for 
-the observed velocity offset.
+% gas motion (Woo+15, 16).
 
@@
 Based on our lens modeling analysis of different \bco velocity channels,
-we find a secondary CO-emitting source near RXJ1131 whose coordinates
-are consistent with those of an optically faint companion reported in previous optical studies
+we find a secondary CO-emitting source near RXJ1131 whose spatial position
+is consistent with those of an optically faint companion reported in previous optical studies
 \citepalias{Claeskens06a,Brewer08a}.
@@
 This together with a symmetric source-plane velocity gradient argues for a rotating disk in RXJ1131, in good agreement with previous findings \citepalias{Claeskens06a}.
-We find a lensing-corrected gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
+Physical quantities derived for RXJ1131 and the companion throughout this paper are summarized in \Tab{prop}.
+
+Based on the lensing-corrected \bco line intensities, 
+we find an intrinsic gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
 for RXJ1131
@@
 that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are redshifted by $\sim$715\,\kms. 
+but that the BLR lines are redshifted by $\sim$715\,\kms. 
 We raise several plausible scenarios that may explain the observed velocity offset, \eg
@@
 microlensing, and a recoiling black hole.
-The latter scenario might also explain the high black hole spin parameter reported by \citet[$a$\ssim0.9][]{Reis14a}.
-With the available data, 
-we do not favor a particular scenario mentioned above as the interpretation for the observed velocity offset.
+The latter scenario would also explain the high black hole spin parameter reported by \citet[$a$\ssim0.9][]{Reis14a}, but 
+further evidence is needed to confirm or rule out this scenario.
+% spin up scenario: 
+% Wang+16: """ The spin of a BH is widely believed to play a crucial role in
+% determining the radio emission from SMBHs. The scenario that
+% an energy is extracted from an SMBH being spun up by a BH?
+% BH merger (e.g., Chiaberge & Marconi 2011) is favored for
+% high-mass SMBHs. This spin-up scenario is, however, almost
+% infeasible for low-mass SMBHs because they are believed to
+% largely build from secular evolution driven by internal
+% dynamical processes in the disk growth rather than from two
+% BHs merging (e.g., Kormendy & Ho 2013).
 

### 2016-12-08 WRITEUP/diff.tex
ready for DR

@@
 \newcommand{\new}[1]{\textcolor{blue}{\uwave{#1}}}
-\newcommand{\old}[1]{\textcolor{red}{\st{#1}}} % {\textcolor{green!55!blue}{\bf #1}} or  {\textcolor{OliveGreen}{\bf #1}}
+\newcommand{\old}[1]{\textcolor{red}{\st{#1}}} % 
 % -----------------------------------------------------------------------------------------------
@@
 
-\title{Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
+\title{Molecular Gas \old{Dynamics} \new{Kinematics and Spectral Energy Distribution Properties} of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
-at $z_\textrm{s, QSO}$\eq$0.658$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
+at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
 studying the evolution of molecular gas properties in quasar host galaxies and the
@@
 $\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
-% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
 \defcitealias{Claeskens06a}{C06}
 
-%--------------------------------------------------------------------------
-%                          Observations details
-%--------------------------------------------------------------------------
 \section{Observations} \label{sec:obs}
 \subsection{CARMA \cco}
-Observations of the \cco rotational line \old{in RXJ1131} ($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz \new{towards RXJ1131 at $z_{\rm QSO}$\eq0.658}
-were carried out with the \carma (CARMA;
+\old{Observations of the \mbox{\cco} rotational line in RXJ1131
+($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
+were carried out with the \mbox{\carma} (CARMA;
 Program ID: cf0098; PI: D. Riechers)
-in the D array configuration\new{. They were carried out} on 2014 February 02 under poor 1.5\,mm
+in the D array configuration on 2014 February 02 under poor 1.5\,mm
 weather conditions and on 2014 February 17 under good 1.5\,mm
-weather conditions.
+weather conditions.}
+\new{Observations of the \cco rotational line 
+($\nu_{\rm rest}$\,=\,345.79599\,GHz) towards RXJ1131 at $z_{\rm s, QSO}$\eq0.658 
+were carried out with the \mbox{\carma} (CARMA;
+Program ID: cf0098; PI: D. Riechers) in the D array configuration. 
+The line frequency is redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz at the quasar redshift.
+Observations were carried out
+on 2014 February 02 under poor 1.5\,mm
+weather conditions and on 2014 February 17 under good 1.5\,mm
+weather conditions.}
 This resulted in a total on-source time of 2.94 hours after flagging poor
@@
 imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
-beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
+beam size of 3\farcs2 $\times$ 1\farcs9 \old{(PA\,=\,8\degr)} \new{at a position angle (PA) of 8\degr} for the lower sideband
 image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
@@
 \subsection{PdBI \bco}
-Observations of the \bco rotational line
+\old{Observations of the \mbox{\bco} rotational line
 ($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
-\old{at the $\nu_{\rm LO}$\eq139.256\,GHz}
-\new{redshifted to $\nu_{\rm obs}$\eq139.256\,GHz towards RXJ1131 at the CARMA \cco redshift of 
-$z_{\rm CO(3-2)}$\eq0.655}
-were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
+at the $\nu_{\rm LO}$\eq139.256\,GHz
+were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
 Riechers). Two observing runs were carried out on 2014 December 06 and 2015
 February 05 under good weather conditions in the C and D array configurations,
-respectively.
+respectively.}
+\new{Observations of the \bco rotational line
+($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
+towards RXJ1131
+were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
+Riechers).
+Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
+the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
+}
 This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
@@
 is produced by averaging over 3.16\,GHz of line-free bandwidth. This
-yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15
+yields an rms noise of 0.082 mJy\,beam$^{-1}$.
 
 \subsection{VLA (Archival)}
-Our analysis also uses archival data of the 4.885\,GHz %4.88510 GHz
+Our analysis also uses archival data of the 4.885\,GHz
 radio continuum obtained with the
@@
 \subsection{\bco Emission} \label{sec:CO21}
-We detect \bco line emission toward the background source in the PdBI data
-at $\gtrsim$\,27$\sigma$ \old{significance, confirming} \new{significance. Based on this measurement, we refine} the redshift \old{at} \new{of RXJ1131 to} \old{$z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.}
-\new{$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to
-the de-lensed spectrum, which is shown in \Fig{delensed}
+We detect \bco line emission towards the background source RXJ1131 in the PdBI data
+at $\gtrsim$\,27$\sigma$ significance\old{, confirming the redshift at $z_{\rm CO}$ =
+0.6537\,$\pm$\,0.0005.} 
+\new{. Based on this measurement, we refine the redshift of RXJ1131 to
+$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to 
+the de-lensed spectrum (\Fig{delensed}) 
 instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
 redshift determination 
-due to differential lensing (see \Sec{differential})}.}}
-\old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
+due to differential lensing (see \Sec{differential}).
+}.}}
+The emission is spatially and \old{dynamically}\new{kinematically} resolved
 with a highly asymmetric double-horned line profile
@@
 179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
-$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms} \new{20.3\,$\pm$\,0.6 Jy \kms}. % see 15May16/
+$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms}\new{20.3\,$\pm$\,0.6 Jy \kms}.
 
@@
 22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
-The velocity scale is with respect to \old{$z$\,=\,0.6537, which is approximately the line center considering the asymmetry resulting from differential lensing.} \new{$z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
-the de-lensed line profile (\Fig{delensed})}.
+\old{The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
+considering the asymmetry resulting from differential lensing.}
+\new{The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
+the de-lensed line profile (\Fig{delensed}).}
 A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
@@
 The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
-in the intensity map.
-
-\old{
-The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
+in the intensity map. \new{Observed properties of the \bco emission line are summarized in \Tab{obsprop}.}
+
+\old{The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
 the image plane
@@
 wavelengths, the lensed emission would be more accurately described by an
-annulus, enclosing the partially complete ``Einstein ring'' and}
-\old{\mbox{the lensed knots (see \Fig{CO21mom}).}}
-\new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
-to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  % In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
-consistent with that obtained by $uv$-plane fitting within the uncertainties. 
-% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
-The spatial distribution of the observed CO emission is unlikely to be fully 
-encapsulated by a simple Gaussian 
-given its skewed emission, which also appears to be a superposition of two components (\Fig{CO21mom}). 
-% To better capture the spatial distribution of the line emission, we 
-We therefore also fit a model of two Gaussians which yeilds deconvolved source sizes of 
+annulus, enclosing the partially complete ``Einstein ring'' and
+the lensed knots \mbox{(see \Fig{CO21mom}).}}
+\new{The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian 
+to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  
+which is consistent with that obtained by visibility-plane fitting within the uncertainties. 
+Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
+and appears to be a superposition of two components (top left panel of \Fig{CO21mom}), 
+we also fit two Gaussians to the intensity map. 
+This yields deconvolved source sizes of 
 3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
-The deconvolved source size together with
-% complex morphology of a partial ``Einstein ring'' with 
-% structures along the arc and knots 
-% seen in optical and \nir emission (see \Fig{CO21mom}). %that were observed at higher resolution, 
-the spatially more extended blue wing compared to the optical 
-``Einstein ring" of diameter $\sim$3\farcs6 (top right panel of \Fig{CO21mom}) suggest that 
-the CO-emitting region in RXJ1131 is more extended than its stellar and quasar emission.}
+The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended 
+than the optical 
+``Einstein ring'', which has a diameter of $\sim$3\farcs6
+(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one). 
+This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image, 
+and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
+Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.}
 
@@
 \hspace{0.5em}
-% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
-% 126-144 (Red)
-% ~ delta V ~410 km/s
-% from [409, 0] km/s
-%  144-160 (Blue)
-% ~ 365 km/s
-% [-324.88, 0] km/s
 \includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
@@
 \new{\mbox{are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.}}
-The contours in both top panels start at 3$\sigma$ and increment at steps of
+The contours in both top panels start at 3$\sigma$ and increment in steps of
 $\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
@@
 \subsection{\cco Emission}
-We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
+We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
 \old{The spectrum is shown in \mbox{\Fig{co32spec}} and appears to be consistent with a
 double-peaked profile. }
-\new{The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where we over-plot spectra of the \bco and \cco lines.}
-\new{We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
-We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, 
-indicating a $\gtrsim$3$\sigma$ detection for this component, and a peak line 
-flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing, indicating a $\sim$\,6$\sigma$ detection. 
-}
+\new{The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \mbox{\Fig{co32spec}}, where
+we over-plot spectra of the \bco and \cco lines.
+We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
+We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing,
+indicating a $\sim$\,6$\sigma$ detection. }
 We estimate a line intensity of 
-\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop})} by summing up fluxes over the FWZI
-linewidth used to infer the \bco line intensity ($\sim$700 \kms).
-
-Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
+\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\mbox{\Tab{obsprop}})}
+by summing up fluxes over the FWZI
+linewidth used to infer the \bco line intensity.
+
+Assuming that the spatial extent of \bco and \cco is similar and therefore the emission is
 magnified by the same amount, the measured line intensities
@@
 $r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,\old{0.66\,$\pm$\,0.41. Taking into account the large phase errors associated with \cco, this is consistent with}
-\new{0.78\,$\pm$\,0.37, where this uncertainty includes
-the uncertainties in absolute flux calibration.
-This ratio is consistent with}
+\new{0.78\,$\pm$\,0.37. The quoted error bar is derived by adding the uncertainties associated with the CO line intensities 
+and those from absolute flux calibrations in quadrature.
+This brightness temperature ratio is consistent with} 
 thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
-nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
-with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
-% see DANNERBAUER09 intro
-% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.
+nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, Riechers11b, CW13}, but also
+with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13, Daddi15a}.
 
 \begin{figure}[!htbp]
-%\centering
 \includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-The velocity scale is \old{with respect to \mbox{$z$=0.6537, which corresponds to the
-dynamical center of the \bco line.}} \new{same as in \Fig{CO21spec}).} The spectral resolution for \cco and \bco
+\old{\mbox{The velocity scale is with respect to $z$=0.6537, which corresponds to the
+dynamical center of the \bco line.}}\new{\mbox{The velocity scale is the same as in \Fig{CO21spec}.}} The spectral resolution for \cco and \bco
 is 36 \kms and 22 \kms, respectively.
@@
 \subsection{Continuum Emission} \label{sec:deblend}
-No \old{1.5\,mm} \new{1.4\,mm} continuum emission is detected at the position of \cco
+No \old{1.5\,mm}\new{1.4\,mm} continuum emission is detected at the position of \cco
 down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
@@
 
-We detect \old{2\,mm} \new{2.2\,mm} continuum emission at an
+We detect \old{2\,mm}\new{2.2\,mm} continuum emission at an
 integrated flux density of
@@
 $S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
-centered on the lensing galaxy (\Fig{cont}).
-Slightly extended emission
+centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
 along the lensed arc is also detected.
 This suggests that we detect emission in both
-the foreground and the background galaxy and that the
+the foreground galaxy and the background galaxy and that the
 emission is marginally resolved along its major axis.
-We subtract a point source model in the $uv$-plane to remove the unresolved part of the
-emission, which we here assume to be dominated by the foreground galaxy. The peak 
-\old{flux (0.39\,$\pm$\,0.08\,mJy)}
-\new{emission}
-in the residual map coincides with the lensed arc, \old{and} \new{with 
-a flux density of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy.}
-\new{This peak flux} is consistent with
+We subtract a point source model in the visibility-plane to remove the unresolved part of the
+emission, which we here assume to be dominated by the foreground galaxy. 
+\old{The peak flux (0.39\,$\pm$\,0.08\,mJy)
+in the residual map coincides with the lensed arc, and is consistent with
 the difference between the integrated and the peak flux in the
+original continuum map ($\sim$0.4 mJy). We therefore adopt
+$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
+the background galaxy (RXJ1131).
+The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.}
+\new{The emission
+in the residual map coincides spatially with the lensed arc. We measure a flux density 
+of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
+This flux density is consistent with
+the difference between the integrated and the peak flux density measured in the
 original continuum map ($\sim$0.4 mJy). 
-We therefore adopt \old{$S_{\nu}$ = 0.39\pmm0.08 mJy} \new{$S_{\nu}$\eq0.39\pmm0.12 mJy} as the 2\,mm continuum \old{emission towards} \new{flux measurement for}
+We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the best estimate for the 2\,mm continuum flux of 
 the background galaxy (RXJ1131). 
-The quoted uncertainty is \old{from the flux measurement in the residual map, }
-\new{derived by adding those associated with the flux density of the
-point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and the peak flux in the residual map (0.08 mJy) in 
-quadrature,}
-and does not account for that in the
-de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
+We here quote a conservative uncertainty, which is derived by adding those associated with the flux density of the 
+point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
+the peak flux in the residual map (0.08\,mJy) 
+in quadrature. We caution that this does not account for that in the 
+de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.}
 We report the peak flux in the original map
@@
 \begin{figure}[!htbp]
-%\centering
 \includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
@@
 \caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
-Contours start and increment at steps of
+Contours start and increment in steps of
 $\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
@@
 and $n$ is an integer starting from 2 to 5.
-Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$.}
+Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.}
 The central crosses in both panels indicate the centroid of the foreground galaxy,
@@
 We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
-We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.024}\new{0.02\pmm0.07}
-for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.345}\new{0.35\pmm0.21}
+\old{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
+for the foreground
+galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
+for the background galaxy by fitting a
+power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
+5\,GHz and 2\,mm.}
+\new{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
+for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21 % differential
 for the background galaxy by fitting
-power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum emission at
+power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
 5\,GHz and 2\,mm. 
-\new{The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; ][]{Andreani93a}}, suggesting 
-that a fraction of the observed 2\,mm emission arises from thermal dust and free-free emission. 
+The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}}.
+This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
+that a fraction of the observed 2\,mm emission arises from thermal dust  emission. 
 This spectral slope would be even shallower 
-if the background source has a contribution in the
-2\,mm flux of the point-source model used
-in the deblending process. This would also 
-explain the flat spectrum found for the foreground galaxy that is atypical of elliptical galaxies. 
-Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we find
-a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm      % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
-for the background source based on its 5\,GHz flux,
-and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy that arises from thermal dust emission.}
-
-\subsection{Photometry} \label{sec:photometry} %DONE
+if the background source contributes to the unresolved fraction of the
+2\,mm flux. This would also 
+explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
+Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we would expect
+a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm
+and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
+likely arises due to thermal dust emission.
+}
+
+\subsection{Photometry} \label{sec:photometry}
 We compile \mir (MIR) to \fir broadband photometry from various
@@
 obtained from both methods are consistent within the uncertainties.
-
-\input{table_photometry_AAScustomized}
-
-%--------------------------------------------------------------------------
-%                                Analysis
-%--------------------------------------------------------------------------
+\input{table_photometry_AAScustomized.tex}
+
 \section{Analysis} \label{sec:anal}
-%\subsection{Stellar Mass and BH-Bulge Mass Correlation}
-%Rest-frame $K$-band (NIR) photometry has been proposed as a reliable proxy to
-%the underlying total stellar mass. Using the decomposed IRAC photometry at 3.6$\micron$ (rest-frame $K$-band),
-%we find a stellar mass of BLAH, using the BLAH.
-%This implies a $M_{\rm BH}$$/$$M^*$ = BLAH (cf. $\sim$0.1\% found in local galaxies).
-%
-%The AGN-starburst connection has become a central issue with the discovery of the relation
-%between stellar velocity dispersion and mass of the central black hole in spheroidal stellar
-%systems (Magorrian et al. 1998, Ferrarese & Merritt 2000, Gebhardt et al. 2000). Given that
-%elliptical galaxies are mainly old, this relation has to be put in place at their formation history.
-%
-%This implies that RXJ1131 is in the BLAH stage of the evolution, in which the BH ?.
 
@@
 this implies that we do not resolve
-structures (e.g. knots and arcs) of the lensed emission
+structures (e.g., knots and arcs) of the lensed emission
 in our \bco data.
 Nevertheless, the high spectral
-resolution of these data provides \old{dynamical} \new{kinematic} information on
+resolution of these data provides \old{dynamical}\new{kinematic} information on
 spatial scales smaller than the beam (see \Fig{CO21mom}).
-Hence, we reconstruct the intrinsic \old{dynamics} \new{line profile and source-plane velocity structure }
-% - morphology of different kinematic components - velocity structure
+Hence, we reconstruct the \old{intrinsic gas dynamics}\new{intrinsic line profile and source-plane velocity structure}
 by carrying out a parametric lens modeling over different
@@
 \includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
-\caption{The full resolution \bco spectrum (yellow histogram) and
-the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The
+\caption{Top: the full resolution \bco spectrum (yellow histogram) and
+the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The light
 blue histogram shows the ``intrinsic'' line profile of RXJ1131
@@
 above each respective model channel.
+\new{Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
+The y-axis is shown on log scale (top) and linear scale (bottom).}
 \label{fig:delensed}}
@@
 Top: each panel corresponds to a channel map of width 107.5\,\kms \old{of the observed
-emission (red) overlaid on} \new{around the labelled central velocity where
-the observed emission (red contours) is over-plotted atop} the best-fit model (grayscale).
-% the velocity annotated in each panel is the center velocity of each of the seven channels used in lens modelling.
+emission (red) overlaid on the best-fit models (grayscale).} \new{centered on the indicated velocity.
+The observed emission (red contours) is over-plotted atop the best-fit model (grayscale). }
 Bottom: residual images obtained by
@@
 Contours start
-at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
+at $\pm$3$\sigma$ and increment in steps of 3$\times$2$^n\sigma$,
 where $n$ is a positive integer.
-The beam of the PdBI observations is shown in the bottom right corner. % of each panel.
+The beam of the PdBI observations is shown in the bottom right corner.
 The reconstructed source-plane positions, as represented by the magenta ellipses, demonstrate an intrinsic velocity gradient of the \bco emission in RXJ1131.
-The best-fit model of the red-most channel (top left panel) contains two source components \new{--- RXJ1131 and its companion galaxy.}
+The best-fit model of the red-most channel (top left panel) contains two source components  --- RXJ1131 and its companion galaxy.
 \label{fig:model}}
@@
 In the image-plane integrated line map shown in \Fig{CO21mom}, the redshifted component is
-cospatial with the Einstein ring seen in the
-optical image, with most of its apparent flux originating from the lensed arc
-in the southeast, whereas the blue component is predominately coming from
-solely the lensed arc. To further illustrate this, we show the
+cospatial with the Einstein ring that is seen in the
+optical image, with most of its apparent flux originating along the lensed arc, 
+whereas centroid of the blueshifted emission is offset to the southeast of
+ the lensed arc. 
+ \new{This suggests that the CO-emitting region in RXJ1131 is extended.}
+ To further illustrate this, we show the
 channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
@@
 
-\input{table_magFactor}
-
-\old{
-Similar to previous studies of RXJ1131, where
+\input{table_magFactor.tex}
+
+\old{Similar to previous studies of RXJ1131, where
 differential lensing across the {\it HST}
@@
 blueshifted component.
-This can be explained by the difference in magnification factor \mbox{$(\mu_{\rm L})$} which
+This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
 varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
-\new{
-Previous studies of RXJ1131 find evidence for differential lensing across 
+\new{Previous studies of RXJ1131 find evidence for differential lensing across 
 the {\it HST} $V$-, $I$-, and $H$-bands, where the
-magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}, indicating that
-the spatial positions and extents of different stellar populations within the host galaxy are dissimilar with respect
-to the caustic.
-Here, 
-the best-fit lens models obtained for different CO channel slices show that differential lensing also plays 
+magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
+This indicates that the spatial positions and extents of different stellar populations 
+within the host galaxy are dissimilar with respect to the caustic which may be a result of dust extinction and reddening.
+The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays 
 an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
-from 8.7 to 3.1 across different kinematic components (\Tab{model}).
+from 8.7 to 3.1 across different kinematic components (\mbox{\Tab{model}}).
 The asymmetry in the line profile is therefore predominantly a result of differential lensing, where 
@@
 blueshifted component due to a higher magnification factor.
-A secondary effect contributing to the asymmetry is likely caused by 
-the CO emission in the companion at the reddest velocities.}
+A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.}
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
@@
 we extract a one dimensional PV diagram in \mbox{\Fig{PV}}
-by slicing across their source plane positions (PA: 121\degr).
+by slicing across their source plane positions (PA: 121\degr).}
+\new{As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy as it displays
+a kinematically-ordered velocity gradient in the source-plane velocity map of CO emission,
+a symmetric double-horned line profile (\mbox{\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}}), 
+and a disk-like morphology in the source-plane reconstruction of optical-NIR emission
+\citepalias{Claeskens06a}.
+We extract a one dimensional position-velocity (PV) profile 
+by assuming that the source-plane centroids of different velocity components
+obtained from dynamical lens modeling
+are dominated by the tangential component of the
+true velocity vector of a rotating disk, i.e., each velocity component would 
+be seen as lying along the major axis of a rotating disk if observed with sufficiently high angular resolution 
+(see right panel of \Fig{PV}).
+In this process, the positions for each velocity component (plotted as data points in the right panel of \Fig{PV})
+are extracted along the best-fitted major axis, which is along a PA of 121\degr.
 }
-\new{As discussed in \mbox{\Sec{caveat}}, we interpret RXJ1131 as a disk galaxy as it displays
-evidence of a source-plane velocity gradient in the CO emission,
-a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}), 
-and a disk-like morphology in the source-plane reconstruction of optical-NIR emission
-\mbox{\citepalias{Claeskens06a}}.
-We extract a one dimensional PV profile as shown in the right panel of \Fig{PV}
-by assuming the velocities of the respective channels used in
-lens modeling correspond to solely the tangential component of the
-true velocity vector of a rotating disk, i.e., each velocity component would 
-be seen lying along the major axis of a rotating disk if observed with sufficiently high angular resolution.
-In this process, the positions for each velocity component (plotted as data points in the right panel of \Fig{PV})
-are extracted along the best-fitted major axis, which is along a PA of 121\degr.}
 
@@
 and the ``turnover'' radius are poorly constrained.
-In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
-Pearson coefficient $R$\,=\,0.998, and $-$0.400 between $V_{a}$ and $V_0$. % beam smearing --> not resolving velocity info. within the beam
+\old{In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
+Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.}
+\new{In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
+Pearson coefficient $R$\,=\,0.998, and $-$0.400 between $V_{a}$ and $V_0$. }
 
@@
 \includegraphics[width=0.525\textwidth]{../Figures/bestfit_PV.eps}
-\caption{Left: 
-\old{Source-plane positions from best-fit \mbox{\bco} lens models are indicated with their associated uncertainties atop
-the observed first moment map}
-\new{Source-plane positions obtained from the best-fit lens models (presented in \mbox{\Sec{lensmodel}}) are shown
+\caption{\old{Left: Source-plane positions from best-fit \mbox{\bco} lens models are indicated with their associated uncertainties atop
+the observed first moment map. The contours are at steps of 50\,\kms.
+Right: PV slice along the major axis in the source plane at PA\,=\,121\degr.
+Dashed line shows the best-fit ``rotation curve'' using an arctangent model.}
+%
+\new{Velocity gradient of the \mbox{\bco} emission observed in RXJ1131 and the de-lensed velocity gradient obtained from lens modeling.
+Left: source-plane positions obtained from the best-fit lens models (presented in \mbox{\Sec{lensmodel}}) are shown 
 as markers color-coded by their velocities
-atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). }
-The contours are at steps of 50\,\kms.
+atop the observed first moment map (i.e., in the image-plane; see \mbox{\Fig{CO21mom}}). 
+The contours are in steps of 50\,\kms. 
 Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
 RXJ1131 is intrinsically a kinematically-ordered disk.
-Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr \new{based on
+Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr based on 
 the reconstructed source-plane velocity gradient.}
-Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
 The vertical error bars show the channel width for
@@
 terminology), since this corresponds to the radius at which the velocity
-of a pure exponential disk peaks \citep{Courteau97b}. % \ie commonly use Vmax (taken at R2.2) as V_rot
-% Due to the large correlation
+of a pure exponential disk peaks \citep{Courteau97b}.
 Here, we adopt the maximum {\em observed} velocity
-$V_{\rm rot}$\,=\,\old{345}\new{303}\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc
-from the % line center velo of the reddest channel slice, unc = slice width
+$V_{\rm rot}$\,=\,\old{345}\new{303}\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
 dynamical center as a proxy to the rotation velocity.
@@
 $($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
-Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,\old{345}\new{303}\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
+Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,\old{345}\new{303}\,\kms (see \Sec{dynamics}),
 we find a dynamical mass of
@@
 
-%%% using disk model, should use FWHM of single Gauss fit then (Fu+13)
-%Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
-% \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as
-%$v_{\rm FWHM}$, we find a dynamical mass of
-%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
-%within the CO-emitting region.
-%If we instead consider the
-%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
-%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
-%To correct for the inclination effect, we
-%infer an inclination angle of 56.4$\degr$ using
-%the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25)
-%from the reconstructed image (Figure~3 in \citetalias{Claeskens06a}). This inclination angle
-%is consistent with the
-%observed unobscured AGN and an observable double peak line profile.
-%The dynamical mass is then
-%1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
-%% the systematic uncertainty on the inclination angle may cause this estimate to differ by
-%% a factor of $\sim$2.
-%Our estimate is likely a lower limit given the presence of a companion. In a merger model,
-%the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.
-
 \subsection{SED Modeling} \label{sec:SED}
@@
 emission of warm and small dust grains.
-The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak \new{and
-an uncertainty from absolute flux calibration of $\sim$15\% is added in quadrature
-% to obtain the total uncertainties
-for the PdBI 2\,mm continuum in our fitting procedure.
-Here, we use a flux density of $S_{\rm 2mm}$\eq0.27\pmm0.08mJy derived in \Sec{deblend}
-instead of the deblended 0.39\,mJy listed in \Tab{photometry}
-to exclude synchrotron emission (see \Sec{deblend}) in dust SED modeling}.
+The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak.
+\new{Here, we use a flux density of $S_{\rm 2mm}$\eq0.27\pmm0.08 mJy derived in \Sec{deblend} 
+instead of the deblended flux listed in \Tab{photometry} 
+to exclude a potential contribution due to synchrotron emission (see \Sec{deblend}) in the dust SED modeling.
+An uncertainty from absolute flux calibration of $\sim$15\% is added in quadrature 
+to the PdBI 2\,mm continuum photometry in our fitting procedure. }
 
@@
 response curves to perform color correction.
-% Previous studies find that in the absence of mid-IR data, a powerlaw slope
-% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
-%
 The model is described by five free parameters: the rest-frame characteristic dust
@@
 taken for the burn-in phase (which are then discarded).
-Here we report the statistical means % modes in log file
-% summary statistics (global mode (where min. chi),
-% marginal mode (in log file), posterior median (instead of posterior means;
-% need to compute)
+Here we report the statistical means
 and the 68\% confidence intervals in the marginal PDFs
@@
 The best-fit models are shown in \Fig{SED} along with the broadband photometry that is listed in \Tab{photometry}.
-
-\input{table_mbb}
+\input{table_mbb.tex}
+
 In the first model, we attempt to constrain the power-law index by including
@@
 \fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
-\old{\mbox{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}} \new{\mbox{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
-dust mass of 16\petm{5}{12}\E{8}\,\Msun, \old{uncorrected for lensing} \new{all of which are not lensing-corrected}.
+\old{\mbox{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}}\new{\mbox{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
+\old{\mbox{dust mass of 22\petm{5}{18}\E{8}\,\Msun}}\new{\mbox{dust mass of 16\petm{5}{12}\E{8}\,\Msun}}, all of which are not corrected for lensing magnification.
 For the mass absorption coefficient, we adopt
@@
 for this model, we find a total IR luminosity
-\LIR (rest-frame 8\,$-$\,1000\,\micron) of \old{\mbox{9.71\petm{6.14}{-6.05}\E{12}\,\Lsun}} \new{\mbox{8.67\petm{5.27}{5.27}\E{12}\,\Lsun}},
-a \fir luminosity \LFIR of \old{\mbox{4.72\petm{2.54}{2.26}\E{12}\,\Lsun}} \new{\mbox{4.24\petm{2.17}{2.00}\E{12}\,\Lsun}} and a
-dust mass $M_{\rm dust}$ of \old{\mbox{11\petm{5}{6}\E{8}\,\Msun}} \new{\mbox{14\petm{5}{7}\E{8}\,\Msun}}, all of which are \old{uncorrected for lensing}\new{not lensing-corrected}.
+\old{\mbox{\LIR} (rest-frame 8\,$-$\,1000\,\micron) of \mbox{9.71\petm{6.14}{-6.05}\E{12}\,\Lsun},
+a \mbox{\fir} luminosity \mbox{\LFIR} of \mbox{4.72\petm{2.54}{2.26}\E{12}\,\Lsun} and a
+dust mass $M_{\rm dust}$ of \mbox{11\petm{5}{6}\E{8}\,\Msun,} all of which are uncorrected for lensing.}
+\new{\LIR (rest-frame 8\,$-$\,1000\,\micron) of \mbox{8.67\petm{5.27}{5.27}\E{12}\,\Lsun},
+a \fir luminosity \LFIR of \mbox{4.24\petm{2.17}{2.00}\E{12}\,\Lsun} and a
+dust mass $M_{\rm dust}$ of \mbox{14\petm{5}{7}\E{8}\,\Msun,} all of which are not lensing-corrected.}
 Taken at face value, this implies an FIR-to-IR luminosity ratio
-of \old{$\sim$58\pmm35\%} \new{$\sim$49\pmm38\%}.
+\old{of $\sim$58\pmm35\%.}
+\new{of $\sim$49\pmm38\%.}
 
@@
 The choice of SED model does not affect
-the derived star formation rate (SFR) given the similar \fir luminosity\old{.Yet, the dust mass is higher by a factor of $\sim$2 in the former but consistent within the uncertainties.}{\new, and
-their dust masses are consistent within the uncertainties.}
+the derived star formation rate (SFR) given the similar \fir luminosity,
+and their dust masses are consistent within the uncertainties.
+% Yet, the dust mass is higher by a factor of $\sim$2 in the former but consistent within the
+% uncertainties.
 We correct for lensing using the median magnification
@@
 The consistency may be attributed to the large uncertainties arising from the lack of photometric constraints on the models and the fact that the best-fit parameters from the MBB method are similar to those of the \ncode{magphys} method.
-%  Mdust 8.427   8.522   8.617
-% Ldust  1.191E+001  1.204E+001  1.219E+001; but from 3-1000 \micron; should compare with our \LIR.
-%
-% Salpeter M* ~ 1.8 * Chabrier
-% Assuming a \citet{Salpeter55a} IMF, we find a ``stellar mass build-up'' time (aka mass-doubling timescale) of $M^*$$/$SFR\eq sSFR\pmOne\ssim440 Myr for RXJ1131.
-
-% -------
-% WISE flux is slightly higher than the IRAC point, probably due to a smaller
-% aperture used in IRAC extraction (both from archive).
+
 \begin{figure}[!htbp]
@@
 with (without) MIR constraint at 24\,$\micron$.
-The solid black line shows the best-fit SED model with dust attenuation \old{\mbox{(light blue solid line)
-obtained using the \ncode{magphys} code.}}\new{obtained using the \mbox{\ncode{magphys}} code, whereas
-the light blue solid line shows the unattenuated stellar emission. }
+The solid black line shows the best-fit SED model obtained using the \ncode{magphys} code.
+The light blue solid line shows the unattenuated stellar emission. 
 \label{fig:SED}}
@@
 
-%--------------------------------------------------------------------------
-%                                Discussion
-%--------------------------------------------------------------------------
 \section{Discussion} \label{sec:diss}
-\new{The properties of RXJ1131 and the companion derived in this section are summarized in \Tab{prop}}.
 \input{table_propRXJ}
@@
 
-% ------------- gas fraction --------------
-% Locally, the baryonic gas fraction for giant disks is ~7-10% (Leroy et al. 2008, Saintonge et al. 2011a), while
-% at z~1.2 it increases to 34±5% and at z~2.3 to 44±6% (Tacconi
-% et al. 2010, Daddi et al. 2010).
-We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq\old{19\pmm5\%}\new{18\pmm4\%}
-% , where the uncertainty is based on that of the gas mass.
-and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq\old{\mbox{32\petm{7}{12}\% for RXJ1131}}\new{\mbox{34\pmm16\%} for the merger system (i.e., RXJ1131 and companion)}.
-% The derived gas fraction of suggests that $\sim$70\% of the available baryonic mass has already been converted into stars.
+We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\old{\eq19\pmm5\%}\new{\eq18\pmm4\%}
+and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\old{\mbox{\eq32\petm{7}{12}\% for RXJ1131.}} \new{\mbox{\eq34\pmm16\%} for the merger system (i.e., RXJ1131 and companion).}
 Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
-% On the other hand,
-% the baryonic gas mass fraction ranges from $\sim$10$-$30\% with an average of 0.21\pmm0.03 in normal ``star-forming'' galaxies at $z$\ssim0.4 \citep{Geach11a}, and $\sim$5 at $z$\ssim0 \citep{Saintonge11a}.
 and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
-``normal star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
+``normal'' star-forming galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
 \alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
-Both the dynamical and baryonic gas mass fractions of RXJ1131\new{+companion} are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2 %(e.g., \citealt{Lagos11a, Popping12a, Genzel15a})
+Both the dynamical and baryonic gas mass fractions of RXJ1131+companion are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2
 which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% gas to dust ratio:
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Solomon+97: GDR ~ 100
-% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
-% our galaxy MW ~150 (Draine+07)
-% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
-% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
-%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Using the lensing-corrected dust mass, we find a galactic-scale %galaxy-wide
+
+Using the lensing-corrected dust mass, we find a galactic-scale
 gas-to-dust ratio (GDR) of
-\old{40\pmm34}\new{54\pmm13}.   %  (1.38e2+0.192e2)/16*5.5 +/- ((0.33/1.38)**2+(0.09/1.92)**2 + (12/16)**2)**.5*54
-\old{This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.}
+\old{40\pmm34.}\new{54\pmm13}
+This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
 This GDR is lower than the statistical average of 206
@@
 On the other hand, we would also obtain a higher gas mass if
-we assumed sub-thermal excitation between \bco and \aco emission.
-% but this may be a minor effect as CO emission in local ULIRGs is typically thermalized up to $J$ = 3 or 4 \citep{,CW13}.
+we assumed to assume sub-thermal excitation between \bco and \aco emission.
 We also note that the gas-to-dust ratio derived for RXJ1131 may be biased low as the gas is likely to
@@
 
-% ================================================
-%local ULIRGs are in the majority starbursts caused by
-%galaxy major mergers (e.g. Sanders & Mirabel 1996, Veilleux
-%et al. 2009). The overall gas fraction in those systems is not high,
-%and they are expected to sustain such a high rate of star formation
-%for only a short duration, on the order of 100Myr. The depletion
-%time scale of massive star-forming galaxies, with a high gas
-%fraction but low star formation efficiency (SFE), is on the other
-%hand on the order of one Gyr or more (Leroy et al. 2008, Bigiel
-%et al. 2008). These galaxies are dubbed as falling on the ?main
-%sequence? of star-forming galaxies (Noeske
-%et al. 2007), or in a ?normal? star formation phase.
-% =================================================
-
-%====================================================================
-%While the \alphaco conversion factor is commonly assumed to be 0.8\,\alphaU for
-%for ULIRGs/starbursts, its numerical value depends on the ISM environment
-% \citep[\eg][]{Narayanan11a}.
-% For instance, it could be different in a
-% dynamically turbulent galaxy, where the gas is warmer, more excited,
-% and denser, than in a quiescent galaxy.
-% In addition, the physical basis for deriving the gas mass from the CO luminosity is
-% by assuming the ISM only consists of virialized, non-overlapping gas clouds,
-% which is often not true in ULIRGs \citep[][\citetalias{Solomon97, Downes98a}]{Downes93a}.
-% % the CO emitting gas in the centers of ULIRGs is unlikely to be virialized, but instead bound by the potential of the galaxy or from molecular gas in pressure equilibrium rather than gravitational equilibrium.
-
-% % DS98: lower alphaCO for objects with extended surface gas densities, where gas temperature and velocity dispersion are higher; Mgas derived from radiative transfer model instead of using standard conversion factor, which yields the \alphaco = 0.8 UNIT for local ULIRGs.
-% % Also see Scoville+97
-
- %As discussed in Solomon \& Vanden
- %Bout (2005), low-$z$ studies of ULIRGs have led to the
- %suggestion that the conversion factor could be several times
- %smaller (Downes et al. 1993; Bryant \& Scoville 1999, DS98). This can
- %arise in ULIRGs if the gas is concentrated in the nuclear
- %regions (as a result of dissipative galaxy merging) and the
- %molecular emission linewidths can be broadened by the galactic
- %dynamics associated with the stellar mass, not just the self-gravitating
- %gas mass as in individual GMCs in which the
- %standard conversion factor was derived. In addition, the mean
- %gas temperature and density may be different in the ULIRG
- %nuclei as a result of the intense star formation activity and since AlphaCO
- %should vary as density and temperature e.g. (Dickman et al. 1986).
- % Also should be a continuous distribution instead of a bimodal value (Narayanan+12).
- % Yet, from numerical models, it is found that mergers have lower alphaCO than
- % disk galaxies, thus we can derive an upper limit on the gas mass in the RXJ1131 merger system using a disk alphaCO factor.
-% In a minor merger, the rise in gas temperatures and velocity dispersions are not as extreme as in major mergers.
-Hence, the rise in velocity-integrated CO intensity is not as large, and the X-factor (and thus alphaco) does not decrease as much {Narayana11a}.
-
-%====================================================================
-
-% \subsection{Fate of RXS J1131$-$1231}
-%Results from theoretical simulations have suggested that
-%the disk component of a gas-rich progenitor galaxy can
-%survive merging if it has a low star formation efficiency, which in turn
-%reduces the gravitational torque available to
-%remove the angular momentum of the gas, thereby allowing
-%a higher gas fraction to be retained and redistributed over a large extent in
-%the merged galaxy \citep{Hopkins09a}. In this scenario, it is plausible that RXJ1131
-%will retain its a disk component upon merging
-%with a small bulge component
-%given its low SFE and the extended disk.
-%%since there is little/no significant stellar material % (collisionless)
-%%available to torque away the cold gas in the disc, thus little/no angular momentum is lost,
-%%and gas will rapidly reform a cold disc in the background
-%%of the relaxing stellar potential.
-%% --> suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
-%% the final product will have a low bulge mass fraction.
-%%
-%%i.e. small bulge disc can also form from minor merger or major merger (if gas fraction is sufficiently large).
-%% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
 Given that the host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger
@@
 
-% (bulge dominated; Springel05a, Robertson06a)
-% and disc with low B/D ratio ($\sim$0.1$-$0.2; Hopkins09a).
-%
-%In systems that are sufficiently gas-rich, it is possible to
-%suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
-%since there is little/no significant stellar material % (collisionless)
-%available to torque away the cold gas in the disc, thus little/no angular momentum is lost,
-%and gas will rapidly reform a cold disc in the background
-%of the relaxing stellar potential.
-%Gas, being collisional, cannot violently relax, but must
-%have its angular momentum torqued away in order to dissipate and
-%build a bulge by forming stars in a central starburst
-%(\ie gas loses angular momentum to stars in the
-%perturbed disk and fall toward center).
-% In a merger,
-%this torque is primarily internal, from stars in the same disc: the
-%passages and merger of the secondary induce a non-axisymmetric
-%distortion in the primary stellar and gas disc. The stellar distortion
-%(in a trailing resonance and close proximity to the gas response)
-%efficiently removes angular momentum from the gas and allows it
-%to fall to the center and form a bulge  (see also Barnes \& Hernquist
-% 1996).
-% A bulge will form because cold gas with no angular momentum
-% will be largely unable to form any sort of disk, and that a galaxy?s
-% worth of gas compressed to high densities and small
-% radii will inevitably form a large mass in stars).
-%
-% unlikely RXJ1131 will evolve into present-day massive
-% ellipticals (M$\gtrsim$1\E{12}\,\Msun),
-% gas-poor mergers: --> present-day massive elliticals
-% (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
-
 \subsection{\texorpdfstring{\st{Velocity Offset and a Recoiling Black Hole}}{ } Systemic Redshift and Velocity Offset}
-%Outflow:
-% Not AGN outflows because require different velocity offsets in Balmer and forbidden lines (Zamanov02a)
-% line origins:
-% \mgii & Hbeta: outer part of the BLR (Goad12a) compared to high-ionization lines (\eg CIV)
-% Hbeta can also come from NLR
-
 \citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
-The first set of lines is at $z$\ssim\old{0.653}\new{0.654}, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
+The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z_{\rm s, QSO}$\ssim0.658, including the broad component of the Balmer lines and
 the \mgii emission line.
 Using the CO line center redshift as the systemic redshift,
-we find that the redshift of the first set is fully consistent with the \old{systematic} \new{systemic} redshift. This
+we find that the redshift of the first set is fully consistent with the \old{systematic}\new{systemic} redshift. This
 supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
@@
 to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
-\old{On the other hand, the second set of lines is blueshifted by $\sim$780\,\kms, indicating that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.}
-\new{On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.}
+On the other hand, the second set of lines is \old{blueshifted by $\sim$780\,\kms, indicating that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.}
+\new{redshifted by $\sim$715\,\kms.}
+
 \old{One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
 the central AGN, whereas this condition is not necessary for NLRs.
-From an SDSS sample of $>$3800 quasars, \mbox{\citet{Richards02a}} find a}
-\new{Offset between BLR and NLR lines have been reported in literature, e.g., 
-\mbox{\citet{Richards02a}} find a}
- median of 97\kms and a dispersion of \mbox{269\,\kms} in the distribution of
-\old{the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
+From an SDSS sample of $>$3800 quasars, \mbox{\citet{Richards02a}} find a
+median of \mbox{97\kms} and a dispersion of \mbox{269\,\kms} in the distribution of
+the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
 that large offsets are uncommon. Nevertheless,
 offsets as large as \mbox{$\sim$\,500\,\kms} have been observed in some cases.}
-\new{the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in an SDSS sample of $>$3800 quasars, 
-and \mbox{\citet{Bonning07a}} find a mean offset of \mbox{100\,\kms} with a dispersion of \mbox{212\,\kms} %FWHM = 500
+\new{Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature.
+\mbox{\citet{Richards02a}} find an offset of 
+% median of 97\kms and a dispersion of 269\,\kms in the distribution of offset
+$\sim$100\pmm270\,\kms 
+between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in a
+sample of $>$3800 quasars,
+and \mbox{\citet{Bonning07a}} report
+an offset of 
+% a mean offset of 
+% 100\,\kms with a dispersion of 212\,\kms
+%FWHM = 500
+$\sim$100\pmm210\,\kms
 between the broad component of
-\mbox{H$\beta$ and [O\,{\scriptsize III}]} lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.81,
-where only $\lesssim$20 of them are found to have offset $>$800\,\kms.
-Thus, large velocity offsets between BLR and NLR lines comparable to that of RXJ1131 are uncommon but 
-have been observed in some cases.}
+H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
+where only $\lesssim$20 of them ((i.e., $<$1\%) are found to have offsets $>$800\,\kms.
+Thus, large velocity offsets between BLR and NLR lines 
+comparable to that of RXJ1131 are uncommon but have been observed in some cases.
+}
 
 \old{Alternatively, large velocity offsets between emission lines of the
-BLR and the NLR may arise in a recoiling black hole (BH),}
-\new{The observed velocity offset between the BLR and NLR lines may be explained
-by a recoiling black hole (BH),}
+BLR and the NLR may arise in a recoiling black hole (BH),
 where its BLR is moving at high velocity relative to the bulk of its host galaxy
-\mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.
-A recoiling black hole is expected
+\mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.}
+\old{A recoiling black hole is expected
 when a pair of uneven mass BH coalesce, during which their orbital energy is being released
@@
 non-zero net angular momentum is being carried away.
-Depending on their initial conditions \new{(e.g., black hole mass ratio, spin-orbit orientation, spin magnitude)}, numerical relativity simulations have shown that
-the recoil velocity can reach up to \mbox{$\sim$4000\,\kms} for spinning BHs\old{\mbox{\citep[\eg][]{Campanelli07a}}}\new{,with a typical offset recoil velocity of $v_{\rm kick}$\ssim100\,$-$\,500\,\kms
-\mbox{\citep[\eg][]{Libeskind06a,Campanelli07a}}}.
-Several sources have been proposed as recoiling BH candidates, such as CID-42 at \mbox{$z$\,=\,0.359 \citep{Civano10a}} and
-SDSS 0956+5127 at \mbox{$z$\,$\sim$\,0.714 \citep{Steinhardt12a}}\old{. One notable system is}\new{, and} SDSSJ0927+2943 at \mbox{$z$\,$\sim$\,0.713}\old{, where}\new{In the case of 
-SDSSJ0927+2943, the black hole recoil scenario was proposed based on the 
-velocity offset between}
+Depending on their initial conditions, numerical relativity simulations have shown that
+the recoil velocity can reach up to \mbox{$\sim$4000\,\kms for} }
+\old{spinning BHs \mbox{\citep[e.g.,][]{Campanelli07a}}.}
+\old{Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \mbox{\citep{Civano10a}} and
+SDSS 0956+5127 at $z$\,$\sim$\,0.714 \mbox{\citep{Steinhardt12a}}.
+One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
 a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
-\old{have been observed} \mbox{\citep{Komossa08a}}\old{, similar to the case for RXJ1131}.
-However, this \old{scenario} was recently refuted by \mbox{\citet{Decarli14a}}, who find that the
-BLR lines in SDSSJ0927+2943 are indeed consistent with its CO systemic redshift.
+have been observed \mbox{\citep{Komossa08a}},  similar to the case for RXJ1131.
+However, this scenario was recently refuted by \mbox{\citet{Decarli14a}}, who confirm that the
+BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.} 
+\new{The observed velocity offset between the BLR and NLR lines may be explained by
+a recoiling black hole (BH), 
+where the BLR is moving at high velocity relative to the bulk of its host galaxy
+\mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.}
+\new{A recoiling black hole is expected
+when a pair of uneven mass BH coalesce, during which their orbital energy is being released
+as gravitational wave and a non-zero net angular momentum is being carried away.
+Depending on their initial conditions (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
+numerical relativity simulations have shown that recoil velocities can reach up to }
+\new{\mbox{$v_{\rm kick}$\ssim4000\,\kms} for spinning BHs, 
+with typical recoil velocities of \mbox{$v_{\rm kick}$\ssim100\,$-$\,500\,\kms }}
+\new{\mbox{\citep[\eg][]{Libeskind06a,Campanelli07a}}.}
+\new{Several sources have been proposed as recoiling BH candidates} 
+\new{\mbox{\citep[][]{Komossa08a, Civano10a, Steinhardt12a}}}.
+% For the candidate SDSS J0927+2943 at $z$\,$\sim$\,0.713 \citep{Komossa08a}, }
+\new{However, \mbox{\citet{Decarli14a}} have recently refuted 
+such scenario for one of the candidates --- SDSS J0927+2943 --- by finding that the redshift of its
+BLR lines is indeed consistent with its CO systemic redshift.
+}
 This is in contrast with RXJ1131, where our CO observations confirm the \old{blueshifted}\new{redshifted} BLR.
@@
 \new{Alternative scenarios 
-e.g., outflow/inflow of gas in the BLR, rotation of the accretion disk, viewing 
-angle towards the accretion disk, and 
-inclination effect together with a clumpy accretion disk
+e.g., outflow/inflow of gas in the BLR, viewing angle towards the accretion disk, and 
+obscuration in the clumpy accretion disk
 are more commonly invoked to explain velocity offsets between BLR and systemic redshift. 
-In the context of the last scenario, 
-\mbox{\citet{Sluse07a}} report a covering factor of 20\% for the accretion disk in RXJ1131
+Since the BLR lines of RXJ1131 show positive velocity offsets with respect to its systemic redshift, it may imply that 
+obscuration may be causing the observed 
+BLR line emission to be dominated by the gas that is flowing into the central BH, or the receding component of
+the accretion disk.}
+\new{\mbox{\citet{Sluse07a}} report a covering factor of 20\% for the accretion disk in RXJ1131
 based on its broad \mgii absorption line at $z$\eq0.654.
@@
 microlensing \mbox{\citep[\eg][]{Sluse07a, Sluse12a}}, which may have
-magnified the redshifted component of the compact BLR more strongly than its blueshifted component.}
-
-\new{With the existing data, we do not favor a particular scenario mentioned above as the interpretation for 
-the observed velocity offset.}
+magnified the redshifted component of the compact BLR more strongly than its blueshifted component.
+% gas motion (Woo+15, 16).
+}
 
 \subsection{The $M_{\rm BH}$$-$\mbulge Relation}
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\mbox{$>$0.27\petm{11}{8}\%}} \new{\mbox{$>$0.27\petm{0.11}{0.08}\%}}
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\%
 using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
@@
 Based on our lens modeling analysis of different \bco velocity channels,
-we find a secondary CO-emitting source near RXJ1131 whose coordinates
-are consistent with those of an optically faint companion reported in previous optical studies
+we find a secondary CO-emitting source near RXJ1131 whose spatial position is
+consistent with those of an optically faint companion reported in previous optical studies
 \citepalias{Claeskens06a,Brewer08a}.
-%The source-plane positions form a symmetric velocity field,
-% which is consistent with a kinematically-ordered disk galaxy.
 The magnification factor inferred for the CO emission in RXJ1131 is found to
@@
 This together with a symmetric source-plane velocity gradient argues for a rotating disk in RXJ1131, in good agreement with previous findings \citepalias{Claeskens06a}.
-We find a lensing-corrected gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
+\new{Physical quantities derived for RXJ1131 and the companion throughout this paper are summarized in \Tab{prop}. }
+
+\old{We find a lensing-corrected gas mass} \new{Based on the lensing-corrected \bco line intensities, 
+we find an intrinsic gas mass}
+of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
 for RXJ1131
@@
 Using the source-plane \bco size of $R$\ssim6\,kpc, we find a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun for RXJ1131.
-%  and $\sim$(4)\E{9}\,\Msun for the companion.
-The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim\old{19}\new{18}\% and baryonic gas mass fraction of
-$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\ssim\old{32}\new{34}\% are consistent with the trend of decreasing molecular gas
+The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$ssim\old{19}\new{18}\% and baryonic gas mass fraction of
+$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\old{32}\new{34}\% are consistent with the trend of decreasing molecular gas
 content since $z$\ssim2 \citep[e.g.,][;\citetalias{Combes13a}]{Lagos11a,Tacconi13a}
@@
 We also derive a stellar mass of $M_{*}$\ssim3\E{10}\,\Msun by fitting SED models to the
-rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit to account for differential lensing effect.
-
+rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit to
+account for differential lensing effect.
 The source-plane distribution of the gas and stellar populations of different ages
@@
 
-Using the CO redshift as systemic redshift for the host galaxy of RXJ1131, we find
-that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are redshifted by \old{$\sim$780\,\kms}\new{$\sim$715\,\kms}.\old{This implies that the AGN is offset from the dynamical center of its host galaxy.
+Using the CO redshift as the systemic redshift for the host galaxy of RXJ1131, we find
+that the redshift inferred from the NLR lines reported in previous studies are consistent with this systemic redshift
+but the optical BLR lines are blueshifted by \old{$\sim$780\,\kms.
+This implies that the AGN is offset from the dynamical center of its host galaxy.
 One explanation could be that the
@@
 Since the velocity offset between emission lines of the BLR and the NLR
-is typically \mbox{$\sim$100\pmm270\,\kms},
+is typically $\sim$100\pmm270\,\kms,
 we thus raise an alternative explanation of a recoiling black hole in RXJ1131, which
-would also explain the high spin parameter reported by \mbox{\citet{Reis14a}}.}\new{
-Using the CO redshift as systemic redshift for the host galaxy of RXJ1131, we find
-that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are redshifted by $\sim$715\,\kms. 
+would also explain the high spin parameter reported by \mbox{\citet{Reis14a}.}}
+\new{$\sim$715\,\kms. 
 We raise several plausible scenarios that may explain the observed velocity offset, \eg
@@
 microlensing, and a recoiling black hole.
-The latter scenario might also explain the high black hole spin parameter reported by 
-\mbox{\citet[$a$\ssim0.9][]{Reis14a}}.
-With the available data, 
-we do not favor a particular scenario mentioned above as the interpretation for the observed velocity offset.
-}
+The latter scenario would also explain the high black hole spin parameter reported by 
+\mbox{\citet[$a$\ssim0.9][]{Reis14a}}, but 
+further evidence is needed to confirm or rule out this scenario.}
 
 Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$>$\old{\mbox{0.27\petm{11}{8}\%}}\new{\mbox{0.27\petm{0.11}{0.08}\%}} for RXJ1131, providing
+$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{0.11}{0.08}\% for RXJ1131, providing
 a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
@@
 
-%==============================================================================
-%                                Back matters
-%==============================================================================
-% ACKNOWLEDGEMENTS
-%-----------------
 \acknowledgments
-
 We thank the referee for providing detailed and constructive comments that helped improved the clarify of this manuscript.

### 2016-12-08 WRITEUP/ms.tex
ready for DR

@@
 blueshifted component due to a higher magnification factor.
-A secondary effect is likely a result of including the CO emission from the companion in the most redshifted velocity channels.
+A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
@@
 obscuration may be causing the observed 
-BLR line emission to be dominated by gas that is flowing into the central BH or the receding component of
+BLR line emission to be dominated by the gas that is flowing into the central BH, or the receding component of
 the accretion disk.

### 2016-12-08 WRITEUP/diff.tex
after proof-reading by myself, will give to DR

@@
 were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
-Riechers). Two observing runs were carried out on 2014 December 06 and 2015
-February 05 under good weather conditions in the C and D array configurations,
-respectively.}
+Riechers).} 
 \new{Observations of the \bco rotational line
@@
 Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
-the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
-}
+the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.}
+Two observing runs were carried out on 2014 December 06 and 2015
+February 05 under good weather conditions in the C and D array configurations,
+respectively.
 This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-\old{\mbox{The velocity scale is with respect to $z$=0.6537, which corresponds to the
-dynamical center of the \bco line.}}\new{\mbox{The velocity scale is the same as in \Fig{CO21spec}.}} The spectral resolution for \cco and \bco
+\old{The velocity scale is with respect to $z$=0.6537, which corresponds to the
+dynamical center of the \mbox{\bco} line.} \new{The velocity scale is the same as in \mbox{\Fig{CO21spec}.}} The spectral resolution for \cco and \bco
 is 36 \kms and 22 \kms, respectively.
@@
 the background galaxy (RXJ1131). 
-We here quote a conservative uncertainty, which is derived by adding those associated with the flux density of the 
-point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
-the peak flux in the residual map (0.08\,mJy) 
-in quadrature. We caution that this does not account for that in the 
+We here quote a conservative error bar, which is derived by adding the uncertainty 
+associated with the flux density of the 
+point-source model ($\delta S_{\nu}$\eq0.088\,mJy) with
+that of the peak flux in the residual map (0.08\,mJy) 
+in quadrature. We caution that this does not account for the systematic uncertainties of the 
 de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.}
@@
 a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm
-and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
+and thus an excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
 likely arises due to thermal dust emission.
@@
 Spatially, the red velocity component of the CO emission
-also coincides with this component F. It is therefore likely that we
+also consistent with this component F. It is therefore likely that we
 detect \bco emission in a companion galaxy.
@@
 \caption{
-Channel maps of the PdBI \bco data cube toward RXJ1131 at 22\,\kms resolution.
+Channel maps of the PdBI \bco data at 22\,\kms resolution.
 Black crosses indicate the positions of the lensed knots (AGN emission,
-which correspond to components ABCD in \citetalias{Claeskens06a}). The central white-filled
+which correspond to components ABCD in \citetalias{Claeskens06a}). The white-filled
 star indicates the position of the foreground lensing galaxy (component G
@@
 magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
-This indicates that the spatial positions and extents of different stellar populations 
-within the host galaxy are dissimilar with respect to the caustic which may be a result of dust extinction and reddening.
-The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays 
+This indicates that emission from different stellar populations 
+within the host galaxy are dissimilar with respect to the caustic. 
+%This imply that different stellar populations in the host galaxy are not co-spatial, and have  
+%different spatial extents, or
+%may be a result of dust extinction and reddening.
+The best-fit lens models obtained here for different CO channels show that differential lensing also plays 
 an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
 from 8.7 to 3.1 across different kinematic components (\mbox{\Tab{model}}).
-The asymmetry in the line profile is therefore predominantly a result of differential lensing, where 
-the redshifted CO-emitting gas is only apparently much brighter than the
-blueshifted component due to a higher magnification factor.
+The asymmetry in the line profile (\Fig{CO21spec} and \Fig{delensed}) is therefore predominantly a result of
+the redshifted CO-emitting gas being more strongly-magnified 
+than the 
+blueshifted component.
 A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.}
-The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
+The variation in $\mu_{\rm L}$ found across channels is consistent with the source-plane
 positions relative to the caustics in \Fig{model}, where the red wing
@@
 Left: source-plane positions obtained from the best-fit lens models (presented in \mbox{\Sec{lensmodel}}) are shown 
-as markers color-coded by their velocities
+as markers
 atop the observed first moment map (i.e., in the image-plane; see \mbox{\Fig{CO21mom}}). 
+The markers are color-coded by their centroid velocities.
 The contours are in steps of 50\,\kms. 
@@
 We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\old{\eq19\pmm5\%}\new{\eq18\pmm4\%}
-and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\old{\mbox{\eq32\petm{7}{12}\% for RXJ1131.}} \new{\mbox{\eq34\pmm16\%} for the merger system (i.e., RXJ1131 and companion).}
+and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\old{\mbox{\eq32\petm{7}{12}\% for RXJ1131.}} \new{\mbox{\eq34\pmm16\%} for the merger system (i.e., RXJ1131 and companion).}
 Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
@@
 \mbox{\citep{Madau04a, Bonning07a, Loeb07a}}.}
-\new{A recoiling black hole is expected
-when a pair of uneven mass BH coalesce, during which their orbital energy is being released
-as gravitational wave and a non-zero net angular momentum is being carried away.
-Depending on their initial conditions (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
+\new{Depending on the initial conditions of the black hole pair 
+(e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
 numerical relativity simulations have shown that recoil velocities can reach up to }
@@
 This ratio is consistent with those of other intermediate-$z$ radio-loud AGNs \citep{McLure06a}
-but is higher than those of nearby AGNs \citep{HR04a}, supporting
+but is higher than those of nearby AGNs \citep{HR04a}.
+Our results therefore support
 the emerging picture that quasars
@@
 $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\old{32}\new{34}\% are consistent with the trend of decreasing molecular gas
-content since $z$\ssim2 \citep[e.g.,][;\citetalias{Combes13a}]{Lagos11a,Tacconi13a}
+content since $z$\ssim2 \citep[e.g.,][\citetalias{Combes13a}]{Lagos11a,Tacconi13a}
 which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
@@
 that the \SF in RXJ1131 could form a
-larger stellar bulge in the merger remnant upon coalescing.
+larger stellar bulge in the remnant disk galaxy upon coalescing.
 
@@
 that the redshift inferred from the NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are blueshifted by \old{$\sim$780\,\kms.
+but that the optical BLR lines are blueshifted by \old{$\sim$780\,\kms.
 This implies that the AGN is offset from the dynamical center of its host galaxy.

### 2016-12-08 WRITEUP/ms.tex
after proof-reading by myself, will give to DR

@@
 the background galaxy (RXJ1131). 
-We here quote a conservative uncertainty, which is derived by adding those associated with the flux density of the 
-point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
-the peak flux in the residual map (0.08\,mJy) 
-in quadrature. We caution that this does not account for that in the 
+We here quote a conservative error bar, which is derived by adding the uncertainty 
+associated with the flux density of the 
+point-source model ($\delta S_{\nu}$\eq0.088\,mJy) with
+that of the peak flux in the residual map (0.08\,mJy) 
+in quadrature. We caution that this does not account for the systematic uncertainties of the 
 de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
@@
 for the background source due to synchrotron radiation,
-and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
+and thus an excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
 likely arises due to thermal dust emission.
@@
 magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
-This indicates that the spatial positions and extents of different stellar populations 
-within the host galaxy are dissimilar with respect to the caustic which may be a result of dust extinction and reddening.
+This indicates that emission from different stellar populations 
+within the host galaxy are dissimilar with respect to the caustic. 
+%This imply that different stellar populations in the host galaxy are not co-spatial, and have  
+%different spatial extents, or
+%may be a result of dust extinction and reddening.
 The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays 
@@
 from 8.7 to 3.1 across different kinematic components (\Tab{model}).
-The asymmetry in the line profile is therefore predominantly a result of differential lensing, where 
-the redshifted CO-emitting gas is only apparently much brighter than the
-blueshifted component due to a higher magnification factor.
+The asymmetry in the line profile (\Fig{co21spec} and \Fig{delensed}) is therefore predominantly a result of
+the redshifted CO-emitting gas being more strongly-magnified 
+than the 
+blueshifted component.
 A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.
@@
 Left: source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown 
-as markers color-coded by their velocities
+as markers 
 atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}). 
+The markers are color-coded by their centroid velocities.
 The contours are in steps of 50\,\kms. 
@@
 \citep{Madau04a, Bonning07a, Loeb07a}.
-A recoiling black hole is expected
-when a pair of uneven mass BH coalesce, during which their orbital energy is being released
-as gravitational wave and a non-zero net angular momentum is being carried away.
-Depending on their initial conditions (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
+Depending on the initial conditions of the black hole pair (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude), 
 numerical relativity simulations have shown that recoil velocities can reach up to 

### 2016-12-12 WRITEUP/response.md
w/ DR's minor fix

@@
 # RESPONSE:
-We have addressed this comment by changing "dynamically resolved" to "kinematically resolved". to minimize potential confusion.
+We have addressed this comment by changing "dynamically resolved" to "kinematically resolved" to minimize potential confusion.
 
@@
 Rather than saying the differential lensing effect in CO is *similar* to what is seen in the optical, we point out that different magnification factors have been reported in previous studies using optical images.
-This is done to illustrate the prominence of differential lensing effect in this source, and to demonstrate that the CO gas traces a different region in the source plane and has a different spatial distribution compared to the stellar populations.
+This is done to illustrate the prominence of the differential lensing effect in this source, and to demonstrate that the CO gas traces a different region in the source plane and has a different spatial distribution compared to the stellar populations.
 
@@
 Since the lensing-corrected M_gas for both RXJ1131 and the companion are derived by first summing up the flux density of each channel within the FWZI, and then dividing by their respective magnification factors.
-This revision in the CO line intensity does not change our conclusion of this paper.
+This revision in the CO line intensity does not change the conclusions of this paper.
 
@@
 We addressed the referee's comment on the *deconvolved* CO source size by fitting a single Gaussian in uv-plane, which corresponds to 4.5" +/- 0.1" x 3.5" +/- 0.2", consistent with the reported CO size based on image-plane fitting within the uncertainties.
-We additionally report the source sizes by fitting two Gaussians to provide further evidence that the CO(2-1) emission is spatially resolved.
+We additionally report the source sizes obtained by fitting two Gaussians to provide further evidence that the CO(2-1) emission is spatially resolved.
 We have updated Section 3.1 to clarify the discussion.
@@
 
-The term "deblending" is a broadly used in photometry, and it is clear that it refers to the flux subtraction within the same paragraph. We therefore make no changes to the wording.
+The term "deblending" is a broadly used in photometry, and it is clear that it refers to the flux subtraction within the same paragraph.
+We therefore have seriously considered the referee's suggestions, but have decided to keep the wording as is.
 
@@
 Flat spectrum of foreground galaxy:
-We have also added a statement in the paper stating that if the background source has a contribution in the point-source model assumed in our deblending procedure, such that its flux density would be higher than derived here (0.39 +/- 0.12 mJy), then the derived spectral index (-0.35) would be even shallower.
+We have also added in the paper that if the background source has a contribution in the point-source model assumed in our deblending procedure, such that its flux density would be higher than derived here (0.39 +/- 0.12 mJy), then the derived spectral index (-0.35) would be even shallower.
 In this case, the 2mm flux inferred for the foreground galaxy would lower, and thus steepening its spectral slope.
@@
 We agree with the referee that it is unlikely that all offsets in AGN lines are caused by black hole recoil.
-Considering the referee's comments, we have updated this section to as well discuss other possible scenarios.
-We only discuss the possibility of a recoil black hole as one of the interpretations for the velocity offset, given that
-    i) the magnitude of the offset in RXJ1131 (>700 km/s) appears to be an outlier in the distribution of offset found for large samples of QSOs (Richards+02, Bonning+07)
-    ii) RXJ1131 appears to have a high BH spin parameter (a > 0.9; Reis+14)    iii) recoiling BHs are expected theoretically from hierarchical model of galaxy evolution.
+Considering the referee's comments, we have updated this section to discuss other possible scenarios as well.
+We only discuss the recoiling black hole as one of the possibility interpretations for the velocity offset, given that
+i) the magnitude of the offset in RXJ1131 (>700 km/s) appears to be an outlier in the distribution of offset found for large samples of QSOs (Richards+02, Bonning+07).
+ii) RXJ1131 appears to have a high BH spin parameter (a > 0.9; Reis+14). 
+iii) recoiling BHs are expected theoretically from hierarchical model of galaxy evolution.
 
@@
 The BH displacement estimated by the referee (~few 10kpc) has been shown to be theoretically possible in the absence of dynamical friction (Bonning+07, Loeb 2007).
-However, Loeb 2007 has showed that at low ejection speeds of a few hundred km/s, the recoil is expected to be damped by the external gravitational potential of the galaxy, dynamical friction against background stars, dark matter, and gas, thereby limiting the BH displacement and is likely to bring it back to the center of its host galaxy within a few dynamical times (Madau & Quataert 04, Boylan-Kolchin+04, Guedes+11).
+However, Loeb 2007 has shown that at low ejection speeds of a few hundred km/s, the recoil is expected to be damped by the external gravitational potential of the galaxy, dynamical friction against background stars, dark matter, and gas, thereby limiting the BH displacement and is likely to bring it back to the center of its host galaxy within a few dynamical times (Madau & Quataert 04, Boylan-Kolchin+04, Guedes+11).
 

### 2016-12-12 WRITEUP/diff.tex
with DR's comment and changed focus of conclusion to feedback

@@
 The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
-and \eq(2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
-The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
-We find lensing-corrected stellar and dust masses, an IR luminosity, and a
+and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
+The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
+\old{We find lensing-corrected stellar and dust masses, an IR luminosity, and a
 star formation rate of
-$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU for RXS\,J1131$-$1231.
+\mbox{$M_{*}$\eq(3\pmm1)\E{10}\,\Msun}, \mbox{$M_{\rm dust}$\ssim3\E{8}\,\Msun}, \mbox{$L_{\rm IR}$\ssim1.5\E{12}\,\Lsun}, and \mbox{SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU} for RXS\,J1131$-$1231.
 The source-plane morphologies of its gas and stellar populations
 indicate that the star-formation activity may be as extended as the molecular gas reservoir.
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\mbox{$>$0.27\petm{11}{8}\%}} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
+We find a \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} which is higher
 than the
-local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
+local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.}
+\new{We find a lensing-corrected stellar mass of
+$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU, and
+a star formation efficiency and specific SFR comparable to non-quasar host galaxies at $z$\ssim1.
+This together with a gas mass fraction consistent with the trend of evolution indicate 
+that no quenching of star formation is seen in RXJ1131.
+Our results therefore suggest that 
+the decrease in molecular gas mass fraction towards lower redshift 
+plays a dominant role 
+in the decline of cosmic star formation history even in quasar host galaxies.}
 \end{abstract}
@@
 at the $\nu_{\rm LO}$\eq139.256\,GHz
-were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
+were carried out using the IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
 Riechers).} 
@@
 \new{. Based on this measurement, we refine the redshift of RXJ1131 to
-$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to 
+$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002}\footnote{This redshift is derived by fitting a double-Gaussian to 
 the de-lensed spectrum (\Fig{delensed}) 
@@
 redshift determination 
-due to differential lensing (see \Sec{differential}).
-}.}}
+due to differential lensing (see \Sec{differential}).}
 The emission is spatially and \old{dynamically}\new{kinematically} resolved
@@
 Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
-and appears to be a superposition of two components (top left panel of \Fig{CO21mom}), 
+and appears to be a superposition of at least two components (top left panel of \Fig{CO21mom}), 
 we also fit two Gaussians to the intensity map. 
 This yields deconvolved source sizes of 
-3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
+3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, separated 
+by $\sim$2\farcs2 in RA and $\sim$1\farcs7 in Dec.  % ((3-0.76)^2+(2.49-.78)^2)^.5
 The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended 
@@
 indicating a $\sim$\,6$\sigma$ detection. }
-We estimate a line intensity of 
+We measure a line intensity of 
 \old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\mbox{\Tab{obsprop}})}
@@
 5\,GHz and 2\,mm. 
-The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}}.
-This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
-that a fraction of the observed 2\,mm emission arises from thermal dust  emission. 
+The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}}. This likely suggests 
+that at least a fraction of the observed 2\,mm emission arises from thermal dust emission. 
 This spectral slope would be even shallower 
 if the background source contributes to the unresolved fraction of the
-2\,mm flux. This would also 
-explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
-Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we would expect
-a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm
-and thus an excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
-likely arises due to thermal dust emission.
+2\,mm flux. 
+In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and yield a steeper slope.
+This would also explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
+Assuming a spectral slope of $\alpha$\ssim$-$0.7 for synchrotron radiation in RXJ1131, we expect
+a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm. 
+The flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy therefore likely arises due to thermal dust emission.
 }
@@
 \new{Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
-The y-axis is shown on log scale (top) and linear scale (bottom).}
+The y-axes are shown on a log scale.}
 \label{fig:delensed}}
@@
 magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
-This indicates that emission from different stellar populations 
-within the host galaxy are dissimilar with respect to the caustic. 
+This indicates that the emission from different stellar populations 
+within the host galaxy 
+have various spatial extents and positions with respect to the caustic. 
 %This imply that different stellar populations in the host galaxy are not co-spatial, and have  
@@
 blueshifted component.
-A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.}
+A secondary reason is likely due to 
+the inclusion of the emission of the companion in the most redshifted velocity channels.}
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source-plane
@@
 \old{\mbox{3.81\petm{2.04}{1.92}\E{12}\,\Lsun}}\new{\mbox{3.81\petm{1.92}{1.97}\E{12}\,\Lsun}}, and a
-\old{\mbox{dust mass of 22\petm{5}{18}\E{8}\,\Msun}}\new{\mbox{dust mass of 16\petm{5}{12}\E{8}\,\Msun}}, all of which are not corrected for lensing magnification.
+\old{\mbox{dust mass of 22\petm{5}{18}\E{8}\,\Msun}}\new{\mbox{dust mass of 16\petm{5}{12}\E{8}\,\Msun}}, none of which are corrected for lensing magnification.
 For the mass absorption coefficient, we adopt
@@
 
-\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio}
+\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio} \label{sec:frac}
 
@@
 that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
-
-Given that the host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger
-system, the removal of angular momentum of the gas via gravitational torque is likely inefficient to convert the
+\new{In addition, a SFE and a sSFR similar to those of high-$z$ disk 
+galaxies, which are not known to host an AGN,
+together with a molecular gas mass fraction that follows the reported trend of evolution (\Sec{frac})
+suggest that no quenching of star formation is observed in RXJ1131, despite 
+that fact that it is hosting a quasar.
+Hence, the decline in star formation history since $z$\ssim2 even for AGN host galaxies is likely
+a manifestation of the evolution in the molecular gas content rather than negative feedback driven by their central AGNs.
+% The decrease in molecular gas mass fraction may be due to 
+% decrease in intergalactic cold gas accretion (flows of cold gas/cold gas accretion from the IGM).
+}
+
+The host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger
+system. Therefore, removal of angular momentum of the gas via gravitational torque is likely inefficient to convert the
 entire gas disk into a massive stellar bulge.
-Hence, the disk component may be retained upon merging with the companion.
+In this case, the disk component may be retained upon merging with the companion.
 This scenario is consistent with the results from recent simulations, which suggest that bulge formation maybe
@@
 offsets as large as \mbox{$\sim$\,500\,\kms} have been observed in some cases.}
-\new{Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature.
-\mbox{\citet{Richards02a}} find an offset of 
+\new{Velocity offsets between broad line region (BLR) and NLR lines have been reported for other 
+AGNs in the literature.
+\mbox{\citet{Richards02a}} find a median offset of 
 % median of 97\kms and a dispersion of 269\,\kms in the distribution of offset
@@
 and \mbox{\citet{Bonning07a}} report
-an offset of 
+a mean offset of 
 % a mean offset of 
@@
 H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
-where only $\lesssim$20 of them ((i.e., $<$1\%) are found to have offsets $>$800\,\kms.
+where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms and $\sim$1\% 
+are found to have offsets $>$500\,\kms}\footnote{\citet{Bonning07a} report the fraction of objects with offset velocities greater 
+than 500, 800, 1000, 1500, 2000, and 2500\,\kms. We therefore quote the two fractions corresponding to 
+offset velocities closest 
+to that of RXJ1131 in this discussion.}.\new{
 Thus, large velocity offsets between BLR and NLR lines 
@@
 }
-This is in contrast with RXJ1131, where our CO observations confirm the \old{blueshifted}\new{redshifted} BLR.
+This is in contrast with RXJ1131, where our CO observations confirm that the BLR is \old{blueshifted}\new{redshifted}
+relative to the systemic redshift.
 \old{Since this model requires a merged BH, it would imply that RXJ1131 might
@@
 Since the BLR lines of RXJ1131 show positive velocity offsets with respect to its systemic redshift, it may imply that 
-obscuration may be causing the observed 
-BLR line emission to be dominated by the gas that is flowing into the central BH, or the receding component of
-the accretion disk.}
+the observed 
+BLR line emission is dominated by the gas that is flowing into the central BH, or by the receding component of
+the accretion disk, owing to the viewing angle or the obscuration in the accretion disk.}
 \new{\mbox{\citet{Sluse07a}} report a covering factor of 20\% for the accretion disk in RXJ1131
@@
 Additionally, the centroids of the BLR lines in RXJ1131 may be biased towards longer wavelengths due to
-microlensing \mbox{\citep[\eg][]{Sluse07a, Sluse12a}}, which may have
-magnified the redshifted component of the compact BLR more strongly than its blueshifted component.
+microlensing of the compact BLR \mbox{\citep[\eg][]{Sluse07a, Sluse12a}}, where
+the redshifted component may have magnified more strongly than the blueshifted component.
 % gas motion (Woo+15, 16).
@@
 and a far-IR luminosity that corresponds to a SFR$_{\rm FIR}$\ssim120\,\sfrU.
-These physical properties suggest that the merger system is dusty in nature with on-going \SF activity occuring
+These physical properties suggest that the merger system is dusty in nature with on-going \SF activity occurring
 at a rate comparable to local ULIRGs/mergers and high-$z$ massive disk galaxies \citep{dacunha10a, Daddi10a}.
@@
 account for differential lensing effect.
+
 The source-plane distribution of the gas and stellar populations of different ages
@@
 reservoir.
+
 While properties such as CO linewidth, SFR, and gas mass found in RXJ1131
@@
 larger stellar bulge in the remnant disk galaxy upon coalescing.
+\new{This picture is in agreement with that based on the \mbox{$M_{\rm BH}$$-$$M_{\rm bulge}$} relation,
+where we find an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of $>$0.27\petm{0.11}{0.08}\% for 
+RXJ1131 compared to the local value.
+This suggests that the stellar bulge of RXJ1131 is still assembling in order to evolve onto the local relation.}
+% The elevated ratio compared to nearby AGN host galaxies is also consistent the  other studies of high-$z$ AGNs
+% reported in the literature
+% \mbox{\citep[e.g.,][]{Walter04a, Peng06a,McLure06a}}.}
+
+\new{Theoretical studies have suggested that the negative feedback from an AGN may remove a 
+large fraction of molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
+In this study, we find that the SFE and sSFR derived for RXJ1131 are comparable to those of 
+non-AGN host galaxies at $z$\ssim1$-$1.5, and that the 
+derived molecular gas mass fraction is consistent with the expected trend of evolution reported in other studies. 
+We thus conclude that no negative feedback from the AGN is seen on the molecular gas content 
+and on the star formation activity in RXJ1131, albeit hosting a quasar. % at the resolution of our \obs 
+% Therefore, we propose that the decline in star formation history since $z$\ssim2 even for AGN host galaxies is 
+% a manifestation of the evolution in the molecular gas content 
+% rather than
+% due to negative feedback driven by their central AGNs.
+This suggests that even for AGN host galaxies, 
+the decrease in molecular gas mass fraction towards lower redshift
+is the main reason for the decline in cosmic star formation history since $z$\ssim2.}
 
@@
 microlensing, and a recoiling black hole.
-The latter scenario would also explain the high black hole spin parameter reported by 
-\mbox{\citet[$a$\ssim0.9][]{Reis14a}}, but 
+The latter scenario would also explain the high black hole spin parameter of 
+$a$\eq0.87\petm{0.08}{0.15}
+reported by 
+\mbox{\citet[][]{Reis14a}}, but 
 further evidence is needed to confirm or rule out this scenario.}
 
-Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{0.11}{0.08}\% for RXJ1131, providing
-a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
-The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio compared to the local relation suggests that the
+\old{Adopting the stellar mass as an upper limit to the bulge mass, we find a
+\mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{0.11}{0.08}\%} for RXJ1131, providing
+a direct constraint on the empirical \mbox{$M_{\rm BH}$$-$\mbulge} relation at $z$\ssim0.65.
+The elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio compared to the local relation suggests that the
 black hole in RXJ1131 has grown faster or earlier than its host galaxy than nearby AGN host galaxies,
 consistent with the results from existing studies of the evolution in the growth of SMBHs and their host galaxies
-\citep[e.g.,][]{Walter04a, Peng06a,McLure06a}.
-The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
+\mbox{\citep[e.g.,][]{Walter04a, Peng06a,McLure06a}}.
+The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local \mbox{$M_{\rm BH}$$-$$M_{\rm bulge}$ relation}.}
 

### 2016-12-12 WRITEUP/ms.tex
with DR's comment and changed focus of conclusion to feedback

@@
 The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
-We find lensing-corrected stellar and dust masses, an IR luminosity, and a
-star formation rate of
-$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU for RXS\,J1131$-$1231.
-The source-plane morphologies of its gas and stellar populations
-indicate that the star-formation activity may be as extended as the molecular gas reservoir.
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\% which is higher
-than the 
-local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
+We find a lensing-corrected stellar mass of
+$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU, and
+a star formation efficiency and specific SFR comparable to non-quasar host galaxies at $z$\ssim1.
+This together with a gas mass fraction consistent with the trend of evolution indicate 
+that no quenching of star formation is seen in RXJ1131.
+Our results therefore suggest that 
+the decrease in molecular gas mass fraction towards lower redshift 
+plays a dominant role 
+in the decline of cosmic star formation history even in quasar host galaxies.
 \end{abstract}
@@
 towards RXJ1131
-were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
+were carried out using the IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
 Riechers).
@@
 Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
-and appears to be a superposition of two components (top left panel of \Fig{CO21mom}), 
+and appears to be a superposition of at least two components (top left panel of \Fig{CO21mom}),
 we also fit two Gaussians to the intensity map.
 This yields deconvolved source sizes of
-3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
+3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, separated by $\sim$2\farcs2 in RA and $\sim$1\farcs7 in Dec.  % RA: 3-0.76; Dec: 2.49-.78
 The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended
@@
 indicating a $\sim$\,6$\sigma$ detection.
-We estimate a line intensity of 35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop}) by summing up fluxes over the FWZI
+We measure a line intensity of 35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop}) by summing up fluxes over the FWZI
 linewidth used to infer the \bco line intensity.
@@
 Slightly extended emission
-along the lensed arc is also detected.
+along the lensing arc is also detected.
 This suggests that we detect emission in both
@@
 emission, which we here assume to be dominated by the foreground galaxy. The emission
-in the residual map coincides spatially with the lensed arc. We measure a flux density 
+in the residual map coincides spatially with the lensing arc. We measure a flux density
 of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
@@
 This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
-that a fraction of the observed 2\,mm emission arises from thermal dust  emission. 
+that at least a fraction of the observed 2\,mm emission arises from thermal dust  emission.
 This spectral slope would be even shallower
 if the background source contributes to the unresolved fraction of the
-2\,mm flux. This would also 
+2\,mm flux. 
+In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and yield a steeper slope.
+This would also
 explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies.
-Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we would expect
-a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm      % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
-for the background source due to synchrotron radiation,
-and thus an excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
-likely arises due to thermal dust emission.
-
+Assuming a spectral slope of $\alpha$\ssim$-$0.7 for synchrotron radiation in RXJ1131, we expect
+a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm.     % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
+The flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy therefore likely arises due to thermal dust emission.
 % We thus adopt the flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy as
@@
 Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
-The y-axis is shown on log scale (top) and linear scale (bottom).
+The y-axes are shown on a log scale.
 \label{fig:delensed}}
@@
 cospatial with the Einstein ring that is seen in the
-optical image, with most of its apparent flux originating along the lensed arc, 
+optical image, with most of its apparent flux originating along the lensing arc,
 whereas centroid of the blueshifted emission is offset to the SE of
-the lensed arc. This suggests that the CO-emitting region in RXJ1131 is extended.
+the lensing arc. This suggests that the CO-emitting region in RXJ1131 is extended.
 To further illustrate this, we show the
@@
 blueshifted component.
-A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.
+A secondary reason is likely due to 
+the inclusion of the emission of the companion in the most redshifted velocity channels.
 The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
@@
 As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy as it displays
-a kinematically-ordered velocity gradient in the source-plane velocity map of CO emission,
+a kinematically-ordered velocity gradient in the source-plane velocity map of the CO emission,
 a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}),
-and a disk-like morphology in the source-plane reconstruction of optical-NIR emission
+and a disk-like morphology in the source-plane reconstruction of the optical-NIR emission
 \citepalias{Claeskens06a}.
@@
 3.81\petm{1.92}{1.97}\E{12}\,\Lsun, and a
-dust mass of 16\petm{5}{12}\E{8}\,\Msun, all of which are not corrected for lensing magnification.
+dust mass of 16\petm{5}{12}\E{8}\,\Msun, none of which are corrected for lensing magnification.
 For the mass absorption coefficient, we adopt
@@
 that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
+In addition, a SFE and a sSFR similar to those of high-$z$ disk 
+galaxies, which are not known to host an AGN,
+together with a molecular gas mass fraction that follows the reported trend of evolution (\Sec{frac})
+suggest that no quenching of star formation is observed in RXJ1131, despite 
+that fact that it is hosting a quasar.
+Hence, the decline in star formation history since $z$\ssim2 even for AGN host galaxies is likely
+a manifestation of the evolution in the molecular gas content rather than negative feedback driven by their central AGNs.
 
@@
 %% 1:1 gas-riich mergers can yield disc-dominated remnants, and 1:3-1:4 ratio major mergers can yield B/T < 0.2.
-Given that the host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger
-system, the removal of angular momentum of the gas via gravitational torque is likely inefficient to convert the
+The host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger
+system. Therefore, removal of angular momentum of the gas via gravitational torque is likely inefficient to convert the
 entire gas disk into a massive stellar bulge.
-Hence, the disk component may be retained upon merging with the companion.
+In this case, the disk component may be retained upon merging with the companion.
 This scenario is consistent with the results from recent simulations, which suggest that bulge formation maybe
@@
 Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature.
-\citet{Richards02a} find an offset of 
+\citet{Richards02a} find a median offset of
 % median of 97\kms and a dispersion of 269\,\kms in the distribution of offset
@@
 and \citet{Bonning07a} report
-an offset of 
+a mean offset of
 % a mean offset of
@@
 H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
-where only $\lesssim$20 of them ((i.e., $<$1\%) are found to have offsets $>$800\,\kms.
+where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms.
 Thus, large velocity offsets between BLR and NLR lines
@@
 Since the BLR lines of RXJ1131 show positive velocity offsets with respect to its systemic redshift, it may imply that 
-obscuration may be causing the observed 
-BLR line emission to be dominated by the gas that is flowing into the central BH, or the receding component of
-the accretion disk.
+the observed 
+BLR line emission is dominated by the gas that is flowing into the central BH, or by the receding component of
+the accretion disk, owing to the viewing angle or the obscuration in the accretion disk.
 \citet{Sluse07a} report a covering factor of 20\% for the accretion disk in RXJ1131
@@
 larger stellar bulge in the remnant disk galaxy upon coalescing.
+This picture is in agreement with that based on the \mbox{$M_{\rm BH}$$-$$M_{\rm bulge}$} relation,
+where we find an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of $>$0.27\petm{0.11}{0.08}\% for 
+RXJ1131 compared to the local value.
+This suggests that the stellar bulge of RXJ1131 is still assembling in order to evolve onto the local relation.
+
+Theoretical studies have suggested that the negative feedback from an AGN may remove a 
+large fraction of molecular gas from its host galaxy, thereby quenching 
+its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
+In this study, we find that the SFE and sSFR derived for RXJ1131 are comparable to those of 
+non-AGN host galaxies at $z$\ssim1$-$1.5, and that the 
+derived molecular gas mass fraction is consistent with the expected trend of evolution reported in other studies. 
+We thus conclude that no negative feedback from the AGN is seen on the molecular gas content 
+and on the star formation activity in RXJ1131, albeit hosting a quasar. % at the resolution of our \obs 
+% Therefore, we propose that the decline in star formation history since $z$\ssim2 even for AGN host galaxies is 
+% a manifestation of the evolution in the molecular gas content 
+% rather than
+% due to negative feedback driven by their central AGNs.
+This suggests that even for AGN host galaxies, 
+the decrease in molecular gas mass fraction towards lower redshift
+is the main reason for the decline in cosmic star formation history since $z$\ssim2.
 
@@
 outflow/inflow of gas in the BLR, kinematics of the accretion disk, geometric effects,
-microlensing, and a recoiling black hole.
-The latter scenario would also explain the high black hole spin parameter reported by \citet[$a$\ssim0.9][]{Reis14a}, but 
+microlensing, and a recoiling black hole from merger event.
+The latter scenario might also explain the high black hole spin parameter of 
+$a$\eq0.87\petm{0.08}{0.15} reported by \citet[][]{Reis14a}, but
 further evidence is needed to confirm or rule out this scenario.
@@
 
-Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{0.11}{0.08}\% for RXJ1131, providing
-a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
-The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio compared to the local relation suggests that the
-black hole in RXJ1131 has grown faster or earlier than its host galaxy than nearby AGN host galaxies,
-consistent with the results from existing studies of the evolution in the growth of SMBHs and their host galaxies
- \citep[e.g.,][]{Walter04a, Peng06a,McLure06a}.
- The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
+%Adopting the stellar mass as an upper limit to the bulge mass, we find a
+%$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{0.11}{0.08}\% for RXJ1131, providing
+%a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
+%The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio compared to the local relation suggests that the
+%black hole in RXJ1131 has grown faster or earlier than its host galaxy than nearby AGN host galaxies,
+%consistent with the results from existing studies of the evolution in the growth of SMBHs and their host galaxies
+% \citep[e.g.,][]{Walter04a, Peng06a,McLure06a}.
+% The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
 

### 2016-12-13 WRITEUP/diff.tex
change the tone on feedback

@@
 \input{preamble}
-\slugcomment{To be submitted to the ApJ}
+\slugcomment{With changes from the referee report}
  \makeatletter
@@
 
-\title{Molecular Gas \old{Dynamics} \new{Kinematics and Spectral Energy Distribution Properties} of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
+\title{Molecular Gas \old{Dynamics} \new{Kinematics and Star Formation Properties} of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 \new{We find a lensing-corrected stellar mass of
-$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU, and
-a star formation efficiency and specific SFR comparable to non-quasar host galaxies at $z$\ssim1.
-This together with a gas mass fraction consistent with the trend of evolution indicate 
-that no quenching of star formation is seen in RXJ1131.
-Our results therefore suggest that 
-the decrease in molecular gas mass fraction towards lower redshift 
-plays a dominant role 
-in the decline of cosmic star formation history even in quasar host galaxies.}
+$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
+corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
+disk galaxies at $z$\ssim1.
+This together with a gas mass fraction following the redshift evolution indicates
+that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
+This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
+local value, suggesting that the bulk of the black hole 
+mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.}
 \end{abstract}
@@
 2\,mm flux. 
-In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and yield a steeper slope.
-This would also explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
-Assuming a spectral slope of $\alpha$\ssim$-$0.7 for synchrotron radiation in RXJ1131, we expect
+In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and  
+lead to a slope steeper than $\alpha^{\rm 2mm}_{\rm 6cm}$\ssim$-$0.02, which is flatter than 
+that typical of elliptical galaxies. 
+Assuming a spectral slope of $\alpha$\ssim$-$0.7 to account for synchrotron radiation in RXJ1131, we expect
 a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm. 
@@
 that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
-\new{In addition, a SFE and a sSFR similar to those of high-$z$ disk 
-galaxies, which are not known to host an AGN,
-together with a molecular gas mass fraction that follows the reported trend of evolution (\Sec{frac})
+\new{In addition, a SFE and sSFR comparable to those of high-$z$ disk 
+galaxies, which are not known to host AGNs,
+together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
 suggest that no quenching of star formation is observed in RXJ1131, despite 
 that fact that it is hosting a quasar.
-Hence, the decline in star formation history since $z$\ssim2 even for AGN host galaxies is likely
-a manifestation of the evolution in the molecular gas content rather than negative feedback driven by their central AGNs.
-% The decrease in molecular gas mass fraction may be due to 
-% decrease in intergalactic cold gas accretion (flows of cold gas/cold gas accretion from the IGM).
+Hence, the decline in star formation history since $z$\ssim2 
+for at least a subset of AGN host galaxies 
+may be mainly
+a manifestation of the evolution in the molecular gas content rather than a result of 
+the negative feedback driven by their central AGNs.
 }
@@
 offset velocities closest 
-to that of RXJ1131 in this discussion.}.\new{
+to that of RXJ1131 ($\sim$715\,\kms) in this discussion.}.\new{
 Thus, large velocity offsets between BLR and NLR lines 
@@
 larger stellar bulge in the remnant disk galaxy upon coalescing.
-\new{This picture is in agreement with that based on the \mbox{$M_{\rm BH}$$-$$M_{\rm bulge}$} relation,
+\new{This picture is in agreement with the one based on the \mbox{$M_{\rm BH}$$-$$M_{\rm bulge}$} relation,
 where we find an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of $>$0.27\petm{0.11}{0.08}\% for 
@@
 
-\new{Theoretical studies have suggested that the negative feedback from an AGN may remove a 
-large fraction of molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
-In this study, we find that the SFE and sSFR derived for RXJ1131 are comparable to those of 
-non-AGN host galaxies at $z$\ssim1$-$1.5, and that the 
-derived molecular gas mass fraction is consistent with the expected trend of evolution reported in other studies. 
-We thus conclude that no negative feedback from the AGN is seen on the molecular gas content 
-and on the star formation activity in RXJ1131, albeit hosting a quasar. % at the resolution of our \obs 
-% Therefore, we propose that the decline in star formation history since $z$\ssim2 even for AGN host galaxies is 
-% a manifestation of the evolution in the molecular gas content 
-% rather than
-% due to negative feedback driven by their central AGNs.
-This suggests that even for AGN host galaxies, 
-the decrease in molecular gas mass fraction towards lower redshift
-is the main reason for the decline in cosmic star formation history since $z$\ssim2.}
+\new{Theoretical studies have suggested that negative feedback from an AGN may remove a 
+large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
+In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
+non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
+derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
+We thus find no evidence of negative AGN feedback on the molecular gas content 
+and on the star formation activity in RXJ1131 at the resolution of our data.
+Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
+their contribution to the decline in cosmic star formation history since $z$\ssim2 
+may be mainly
+a manifestation of the redshift evolution in the molecular gas content rather than a result of 
+negative feedback driven by their central AGNs.
+}
 

### 2016-12-13 WRITEUP/ms.tex
change the tone on feedback

@@
 
-\title{Molecular Gas Kinematics and Spectral Energy Distribution Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
+\title{Molecular Gas Kinematics and Star Formation Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 We find a lensing-corrected stellar mass of
-$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU, and
-a star formation efficiency and specific SFR comparable to non-quasar host galaxies at $z$\ssim1.
-This together with a gas mass fraction consistent with the trend of evolution indicate 
-that no quenching of star formation is seen in RXJ1131.
-Our results therefore suggest that 
-the decrease in molecular gas mass fraction towards lower redshift 
-plays a dominant role 
-in the decline of cosmic star formation history even in quasar host galaxies.
+$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
+corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
+disk galaxies at $z$\ssim1.
+This together with a gas mass fraction following the redshift evolution indicates
+that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
+This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
+local value, suggesting that the bulk of the black hole 
+mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
 \end{abstract}
@@
 5\,GHz and 2\,mm.
-The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}.
-This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
+The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}. This likely suggests 
 that at least a fraction of the observed 2\,mm emission arises from thermal dust emission. 
@@
 2\,mm flux. 
-In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and yield a steeper slope.
-This would also
-explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies.
-Assuming a spectral slope of $\alpha$\ssim$-$0.7 for synchrotron radiation in RXJ1131, we expect
+In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and  
+lead to a slope steeper than $\alpha^{\rm 2mm}_{\rm 6cm}$\ssim$-$0.02, which is flatter than 
+that typical of elliptical galaxies. 
+Assuming a spectral slope of $\alpha$\ssim$-$0.7 to account for synchrotron radiation in RXJ1131, we expect
 a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm.  % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
@@
 that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
-In addition, a SFE and a sSFR similar to those of high-$z$ disk 
-galaxies, which are not known to host an AGN,
-together with a molecular gas mass fraction that follows the reported trend of evolution (\Sec{frac})
+In addition, a SFE and sSFR comparable to those of high-$z$ disk 
+galaxies, which are not known to host AGNs,
+together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
 suggest that no quenching of star formation is observed in RXJ1131, despite 
 that fact that it is hosting a quasar.
-Hence, the decline in star formation history since $z$\ssim2 even for AGN host galaxies is likely
-a manifestation of the evolution in the molecular gas content rather than negative feedback driven by their central AGNs.
+Hence, the decline in star formation history since $z$\ssim2 
+for at least a subset of AGN host galaxies 
+may be mainly
+a manifestation of the evolution in the molecular gas content rather than a result of 
+the negative feedback driven by their central AGNs.
 
@@
 H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
-where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms.
+where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms
+and $\sim$1\% 
+are found to have offsets $>$500\,\kms \footnote{\citet{Bonning07a} report the fraction of objects with offset velocities greater 
+than 500, 800, 1000, 1500, 2000, and 2500\,\kms. We therefore quote the two fractions corresponding to 
+offset velocities closest 
+to that of RXJ1131 ($\sim$715\,\kms) in this discussion.}
 Thus, large velocity offsets between BLR and NLR lines
@@
 larger stellar bulge in the remnant disk galaxy upon coalescing.
-This picture is in agreement with that based on the \mbox{$M_{\rm BH}$$-$$M_{\rm bulge}$} relation,
+This picture is in agreement with the one based on the \mbox{$M_{\rm BH}$$-$$M_{\rm bulge}$} relation,
 where we find an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of $>$0.27\petm{0.11}{0.08}\% for 
@@
 
-Theoretical studies have suggested that the negative feedback from an AGN may remove a 
-large fraction of molecular gas from its host galaxy, thereby quenching 
-its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
-In this study, we find that the SFE and sSFR derived for RXJ1131 are comparable to those of 
-non-AGN host galaxies at $z$\ssim1$-$1.5, and that the 
-derived molecular gas mass fraction is consistent with the expected trend of evolution reported in other studies. 
-We thus conclude that no negative feedback from the AGN is seen on the molecular gas content 
-and on the star formation activity in RXJ1131, albeit hosting a quasar. % at the resolution of our \obs 
-% Therefore, we propose that the decline in star formation history since $z$\ssim2 even for AGN host galaxies is 
-% a manifestation of the evolution in the molecular gas content 
-% rather than
-% due to negative feedback driven by their central AGNs.
-This suggests that even for AGN host galaxies, 
-the decrease in molecular gas mass fraction towards lower redshift
-is the main reason for the decline in cosmic star formation history since $z$\ssim2.
+Theoretical studies have suggested that negative feedback from an AGN may remove a 
+large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
+In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
+non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
+derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
+We thus find no evidence of negative AGN feedback on the molecular gas content 
+and on the star formation activity in RXJ1131 at the resolution of our data.
+Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
+their contribution to the decline in cosmic star formation history since $z$\ssim2 
+may be mainly
+a manifestation of the redshift evolution in the molecular gas content rather than a result of 
+negative feedback driven by their central AGNs.
 

### 2016-12-13 WRITEUP/response.md
update tone

@@
 # RESPONSE:
-1a) To take the referee's point into account, we have changed the title to "Molecular gas kinematics and spectral energy distribution properties of the strongly lensed quasar host galaxy RXSJ1131-1231".
+1a) To take the referee's point into account, we have changed the title to "Molecular gas kinematics and star formation properties of the strongly lensed quasar host galaxy RXSJ1131-1231".
 We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (including lens modeling) on which we thus place an emphasis.
@@
 
-We have updated the number of decimals in the spectral indices indexes reported in Section 3.3, as suggested by the referee.
+We have updated the number of decimals in the spectral indices reported in Section 3.3, as suggested by the referee.
 

### 2016-12-13 WRITEUP/diff.tex
update tone

@@
 that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
-This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
-local value, suggesting that the bulk of the black hole 
-mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.}
+This is in agreement with its elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
+local value, suggesting that the bulk of its black hole 
+mass is largely in place while its stellar bulge is still assembling.}
 \end{abstract}
@@
 that fact that it is hosting a quasar.
-Hence, the decline in star formation history since $z$\ssim2 
-for at least a subset of AGN host galaxies 
-may be mainly
-a manifestation of the evolution in the molecular gas content rather than a result of 
-the negative feedback driven by their central AGNs.
+This is suggestive that for some AGN host galaxies at intermediate redshift, 
+their contribution to the decline in the cosmic star formation history since $z$\ssim2 is mainly a 
+manifestation of the redshift evolution in the molecular gas content 
+rather than a result of the negative feedback driven by their central AGNs.
 }
@@
 and on the star formation activity in RXJ1131 at the resolution of our data.
-Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
-their contribution to the decline in cosmic star formation history since $z$\ssim2 
-may be mainly
-a manifestation of the redshift evolution in the molecular gas content rather than a result of 
-negative feedback driven by their central AGNs.
+Our results suggest that for some AGN host galaxies at intermediate redshift, 
+their contribution to the decline in the cosmic star formation history since $z$\ssim2 is mainly a 
+manifestation of the redshift evolution in the molecular gas content 
+rather than a result of the negative feedback driven by their central AGNs.
 }

### 2016-12-13 WRITEUP/ms.tex
update tone

@@
 that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
-This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
-local value, suggesting that the bulk of the black hole 
-mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
+This is in agreement with its elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
+local value, suggesting that the bulk of its black hole 
+mass is largely in place while its stellar bulge is still assembling.
 \end{abstract}
@@
 that fact that it is hosting a quasar.
-Hence, the decline in star formation history since $z$\ssim2 
-for at least a subset of AGN host galaxies 
-may be mainly
-a manifestation of the evolution in the molecular gas content rather than a result of 
-the negative feedback driven by their central AGNs.
+This is suggestive that for some AGN host galaxies at intermediate redshift, 
+their contribution to the decline in the cosmic star formation history since $z$\ssim2 is mainly a 
+manifestation of the redshift evolution in the molecular gas content 
+rather than a result of the negative feedback driven by their central AGNs.
 
@@
 and on the star formation activity in RXJ1131 at the resolution of our data.
-Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
-their contribution to the decline in cosmic star formation history since $z$\ssim2 
-may be mainly
-a manifestation of the redshift evolution in the molecular gas content rather than a result of 
-negative feedback driven by their central AGNs.
+Our results suggest that for some AGN host galaxies at intermediate redshift, 
+their contribution to the decline in the cosmic star formation history since $z$\ssim2 is mainly a 
+manifestation of the redshift evolution in the molecular gas content 
+rather than a result of the negative feedback driven by their central AGNs.
 

### 2017-01-10 src/HSTVLA.py
zoom in

@@ -1,12 +1,16 @@
 """
 Author: Daisy Leung
 
-Last edited: 21 Nov 2016
+Last edited: 9 Jan 2016
 
 Purpose:
 - Plot single panel 5GHz VLA continuum on HST F555W, investigate continuum offset
 
 History:
+Jan 9 2016:
+    - zoom in
+    - use np.sort() w/ contour level, to satisfy mpl version > 1.5.3
+    - change contour color
 Nov 21 2016:
     - add inverted HST
     - update contour color
@@ -37,6 +41,7 @@ import glob
 import matplotlib.pyplot as plt
 import matplotlib as mpl
 from APLpySetup import *
+import numpy as np
 
 path = '../HST/'
 Plotpath = '../Figures/'
@@ -72,7 +77,7 @@ figC = plt.figure(1)
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.0018
+sizep = 0.0014
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
@@ -113,7 +118,7 @@ if inverted_HSTleft: fig1.set_theme('publication')
 # Contours
 ########################################
 # fig1.show_contour(label_vla['C_R0'][0], colors="green", levels=sigma_contour_tenpercent(Smax), linewidths=1.0)#, layer='fg')
-fig1.show_contour(label_vla['C_R0'][0], colors="#17C336", levels=sigma_contour_VLA(sigma), linewidths=1.0)#, layer='fg')
+fig1.show_contour(label_vla['C_R0'][0], colors="red", levels=np.sort(sigma_contour_VLA(sigma)), linewidths=1.2)#, layer='fg')
 
 # figred.show_contour(label_vla['red'][0], colors="lime", levels=sigma_contour_array(sigma_red), linewidths=2)
 

### 2017-01-10 src/plotCont.py

@@ -1,12 +1,15 @@
 """
 Author: Daisy Leung
 
-Last edited: 21 Nov 2016
+Last edited: 9 Jan 2016
 
 Purpose:
 - Overlay 2mm Cont contour on HST
 
 History:
+Jan 9 2016:
+    - zoom in
+    - use np.sort() w/ contour level, to satisfy mpl version > 1.5.3
 Nov 21 2016:
     - add inverted HST
     - no marker, zoom in
@@ -32,6 +35,7 @@ log.setLevel('ERROR')
 import glob
 import matplotlib.pyplot as plt
 import matplotlib as mpl
+import numpy as np
 from APLpySetup import *
 
 path = '../HST/'
@@ -63,14 +67,14 @@ for k in label_pdbi.iterkeys():
     label_pdbi[k] = file_pdBI
 # print label_pdbi
 
-figC = plt.figure(1)
+figC = plt.figure(1, figsize=(12, 8))
 # figRed = plt.figure(2, figsize=(12, 7))
 ########################################
 # user define area
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.0018 # 0.002058066
+sizep = 0.0015 # 0.002058066
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
@@ -109,7 +113,7 @@ if inverted_HSTleft: fig1.set_theme('publication')
 ########################################
 # Contours
 ########################################
-fig1.show_contour(label_pdbi['cont'][0], colors="black", levels=sigma_contour_array(sigma), linewidths=1.62)#, layer='fg')
+fig1.show_contour(label_pdbi['cont'][0], colors="black", levels=np.sort(sigma_contour_array(sigma)), linewidths=1.62)#, layer='fg')
 
 # figred.show_contour(label_pdbi['red'][0], colors="lime", levels=sigma_contour_array(sigma_red), linewidths=2)
 

### 2017-01-10 src/HSTVLA.py
shift label

@@ -70,7 +70,7 @@ for k in label_vla.iterkeys():
     label_vla[k] = file_vla
 # print label_vla
 
-figC = plt.figure(1)
+figC = plt.figure(1, figsize=(12, 8))
 # figRed = plt.figure(2, figsize=(12, 7))
 ########################################
 # user define area
@@ -161,8 +161,8 @@ standard_plot_setup(fig1, ra_center, dec_center, sizep, tickc=tickcolor)
 # if '_' in sym[:-1]: symf = sym.replace('_', ' ')
 
 # put_label(fig1, 0.20, 0.95, 'HST F555W', 'titleBand')
-put_label(fig1, 0.38, 0.9, 'HST F555W, 5GHz Continuum', 'titleBand', c=tickcolor)
-put_label(fig1, 0.15725, 0.95, 'RXJ1131', 'titleObj', c=tickcolor)
+put_label(fig1, 0.295, 0.87, 'HST F555W, 5GHz Continuum', 'titleBand', c=tickcolor)
+put_label(fig1, 0.15725, 0.92, 'RXJ1131', 'titleObj', c=tickcolor)
 # put_label(figHST, 0.20, 0.95, 'HST F555W', 'titleBand')
 # put_label(figHST, 0.1825, 0.9, 'RXJ1131', 'titleObj')
 # put_label(figred, 0.40, 0.95, 'HST F555W, CO Red wing', 'titleBand')

### 2017-01-10 src/plotCont.py

@@ -74,7 +74,7 @@ figC = plt.figure(1, figsize=(12, 8))
 ########################################
 ra_center = 172.96434563888
 dec_center = -12.5328629
-sizep = 0.0015 # 0.002058066
+sizep = 0.0014
 
 ra_cross, dec_cross = ra_center, dec_center
 row_a = 0.1
@@ -155,8 +155,8 @@ standard_plot_setup(fig1, ra_center, dec_center, sizep, tickc=tickcolor)
 ########################################
 # if '_' in sym[:-1]: symf = sym.replace('_', ' ')
 
-put_label(fig1, 0.15725, 0.95, 'RXJ1131', 'titleObj', c=tickcolor)
-put_label(fig1, 0.38, 0.9, 'HST F555W, 2 mm Continuum', 'titleBand', c=tickcolor)
+put_label(fig1, 0.15725, 0.92, 'RXJ1131', 'titleObj', c=tickcolor)
+put_label(fig1, 0.295, 0.87, 'HST F555W, 2 mm Continuum', 'titleBand', c=tickcolor)
 # put_label(figHST, 0.20, 0.95, 'HST F555W', 'titleBand')
 # put_label(figHST, 0.1825, 0.9, 'RXJ1131', 'titleObj')
 # put_label(figred, 0.40, 0.95, 'HST F555W, CO Red wing', 'titleBand')

### 2017-01-10 WRITEUP/diff.tex
resubmit

--- 2016-12-13 WRITEUP/diff.tex
@@
 different kinematic components.
-The intrinsically symmetric line profile with a conspicuous source-plane velocity
-gradient suggests that
+The intrinsically symmetric line profile and a smooth source-plane velocity
+gradient suggest that
 the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
 a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
-In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
+We also find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
 consistent with the optically-faint companion reported in previous studies.
@@
 and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
-The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
-\old{We find lensing-corrected stellar and dust masses, an IR luminosity, and a
+\old{The gas mass fraction of 
+% $f_{\rm gas}$\eq\old{$\sim$19\% } \new{$\sim$18\pmm4\%} 
+\mbox{$f_{\rm gas}$\eq$\sim$19\%}
+is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
+We find lensing-corrected stellar and dust masses, an IR luminosity, and a
 star formation rate of
@@
 $M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
-corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
-disk galaxies at $z$\ssim1.
-This together with a gas mass fraction following the redshift evolution indicates
-that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
-This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
-local value, suggesting that the bulk of the black hole 
-mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.}
+corresponding to a specific SFR and star formation efficiency comparable to 
+$z$\ssim1 disk galaxies not hosting quasars.
+The implied gas mass fraction of $\sim$18\pmm4\% is consistent with the previously-observed cosmic decline since $z$\ssim2.
+We thus find no evidence for quenching of star formation in RXS\,J1131$-$1231.
+This agrees with our finding of an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
+local value, suggesting that the bulk of its black hole 
+mass is largely in place while its stellar bulge is still assembling.}
 \end{abstract}
@@
 \new{Contours correspond to $\pm2^n\sigma$, where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
-and $n$ is an integer starting from 2 to 5.
+and $n$ is an integer running from 2 to 5.
 Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.}
-The central crosses in both panels indicate the centroid of the foreground galaxy,
-as detected in the optical image.
 The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
@@
 the observed first moment map. The contours are at steps of 50\,\kms.
-Right: PV slice along the major axis in the source plane at PA\,=\,121\degr.
-Dashed line shows the best-fit ``rotation curve'' using an arctangent model.}
+Right: PV slice along the major axis in the source plane at PA\,=\,121\degr.}
 %
@@
 the reconstructed source-plane velocity gradient.}
+Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
 The vertical error bars show the channel width for
@@
 \citep[\citetalias{Solomon97a};][]{Combes11a} but consistent with those of
-low-$z$ spiral galaxies \citepalias[$z$\,$<$\,0.1;][]{SV05a} and high-$z$ disk-like
+low-$z$ spiral galaxies \citep[$z$\,$<$\,0.1;][]{SV05a} and high-$z$ disk-like
 galaxies, which are also IR luminous galaxies with \LIR$\sim$10$^{12}$\,\Msun \citep{Daddi08a, Daddi10a}.
@@
 the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
-Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
+Given that RXJ1131 shares similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
 the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
 that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
-\new{In addition, a SFE and sSFR comparable to those of high-$z$ disk 
-galaxies, which are not known to host AGNs,
-together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
-suggest that no quenching of star formation is observed in RXJ1131, despite 
-that fact that it is hosting a quasar.
-Hence, the decline in star formation history since $z$\ssim2 
-for at least a subset of AGN host galaxies 
-may be mainly
-a manifestation of the evolution in the molecular gas content rather than a result of 
-the negative feedback driven by their central AGNs.
-}
 
@@
 we find that the redshift of the first set is fully consistent with the \old{systematic}\new{systemic} redshift. This
-supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
+supports previous claims that [O{\scriptsize III}] lines, tracing the narrow line region (NLR),
 are good proxies
@@
 median of \mbox{97\kms} and a dispersion of \mbox{269\,\kms} in the distribution of
-the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
+the offset between [Mg{\scriptsize II}] and [O{\scriptsize III}] lines, suggesting
 that large offsets are uncommon. Nevertheless,
@@
 $\sim$100\pmm270\,\kms 
-between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in a
+between [Mg{\scriptsize II}] and [O{\scriptsize III}] lines in a
 sample of $>$3800 quasars,
@@
 between the broad component of
-H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
+H$\beta$ and [O{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
 where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms and $\sim$1\% 
@@
 
-\new{Theoretical studies have suggested that negative feedback from an AGN may remove a 
-large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
-In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
-non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
-derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
-We thus find no evidence of negative AGN feedback on the molecular gas content 
-and on the star formation activity in RXJ1131 at the resolution of our data.
-Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
-their contribution to the decline in cosmic star formation history since $z$\ssim2 
-may be mainly
-a manifestation of the redshift evolution in the molecular gas content rather than a result of 
-negative feedback driven by their central AGNs.
-}
-
-Using the CO redshift as the systemic redshift for the host galaxy of RXJ1131, we find
-that the redshift inferred from the NLR lines reported in previous studies are consistent with this systemic redshift
+We find that the redshift inferred from the NLR lines reported in previous studies are consistent with the  systemic redshift as measured
+from the CO line, 
 but that the optical BLR lines are blueshifted by \old{$\sim$780\,\kms.
@@
 
+\new{Theoretical studies have suggested that negative feedback from an AGN may remove a 
+large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
+In this study, we find that the star formation efficiency and specific SFR of RXJ1131 are comparable to those of 
+$z$\ssim1$-$1.5 disk galaxies, which are not known to host quasars, and that its
+molecular gas mass fraction is consistent with the observed cosmic decline for star-forming 
+galaxies since $z$\ssim2$-$3.
+Hence, we find no evidence of negative AGN feedback on the cold molecular gas fraction 
+and on the star formation activity in RXJ1131.
+Future observations at higher resolution will allow us to better constrain the molecular gas kinematics and dynamics of
+RXJ1131 to investigate any potential interplay with the quasar on smaller scales.
+More broadly, systematic studies of the correlations between the molecular gas fraction, stellar mass, and AGN luminosity 
+at different redshifts 
+will enable us to better understand the relative importance of AGN feedback and of the 
+evolution in the molecular gas mass fraction on the decline of star formation history and black hole accretion history.}
+
 \acknowledgments
-We thank the referee for providing detailed and constructive comments that helped improved the clarify of this manuscript.
+We thank the referee for providing detailed and constructive comments that helped to improve the clarity of this manuscript.
 DR and RP acknowledge support from the National Science Foundation

### 2017-01-10 WRITEUP/ms.tex
resubmit

--- 2016-12-13 WRITEUP/ms.tex
@@
 \input{preamble}
-\slugcomment{To be submitted to the ApJ, with changes from the referee report }
+\slugcomment{With changes from the referee report}
  \makeatletter
@@
 and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
-The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
 We find a lensing-corrected stellar mass of
 $M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
-corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
-disk galaxies at $z$\ssim1.
-This together with a gas mass fraction following the redshift evolution indicates
-that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
-This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
-local value, suggesting that the bulk of the black hole 
-mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
+corresponding to a specific SFR and star formation efficiency comparable to  
+$z$\ssim1 disk galaxies not hosting quasars.
+The implied gas mass fraction of $\sim$18\pmm4\% is consistent with the previously-observed cosmic decline since $z$\ssim2.
+We thus find no evidence for quenching of star formation in RXS\,J1131$-$1231.
+This agrees with our finding of an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
+local value, suggesting that the bulk of its black hole 
+mass is largely in place while its stellar bulge is still assembling.
 \end{abstract}
@@
 \section{Results} \label{sec:results}
-\input{table_obsprop}
-
 \subsection{\bco Emission} \label{sec:CO21}
@@
 $\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/
+
+\input{table_obsprop}
 
@@
 \begin{figure}[!htbp]
-%\centering
-\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
-\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
+\includegraphics[trim=12 27 0 1, clip, width=0.47\textwidth]{../Figures/F555W_ContPdBI.eps}
+\includegraphics[trim=10 5 0 0, clip, width=0.47\textwidth]{../Figures/F555W_ContVLA.eps}
 \caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
@@
 that cover the full linewidth of $\sim$750\,\kms.
+\input{table_medianLens}
 
@@
 median and the 68\% confidence intervals in the marginal PDFs.
-\input{table_medianLens}
 
@@
 magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
-This indicates that emission from different stellar populations
-within the host galaxy are dissimilar with respect to the caustic.
-%This imply that different stellar populations in the host galaxy are not co-spatial, and have
-%different spatial extents, or
+This indicates that the emission from different stellar populations
+within the host galaxy have various spatial extents and positions with respect to the caustic.
 %may be a result of dust extinction and reddening.
-The best-fit lens models obtained here for different CO channel slices show that differential lensing also plays
+The best-fit lens models obtained here for different CO channels show that differential lensing also plays
 an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
 from 8.7 to 3.1 across different kinematic components (\Tab{model}).
-The asymmetry in the line profile (\Fig{co21spec} and \Fig{delensed}) is therefore predominantly a result of
+The asymmetry in the line profile (\Fig{CO21spec} and \Fig{delensed}) is therefore predominantly a result of
 the redshifted CO-emitting gas being more strongly-magnified
@@
 54\pmm13.   %  (1.38e2+0.192e2)/16*5.5 +/- ((0.33/1.38)**2+(0.09/1.92)**2 + (12/16)**2)**.5*54
+This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
 This GDR is lower than the statistical average of 206
@@
 %  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
-Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
+Given that RXJ1131 shares similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
 the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
 that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
-In addition, a SFE and sSFR comparable to those of high-$z$ disk 
-galaxies, which are not known to host AGNs,
-together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
-suggest that no quenching of star formation is observed in RXJ1131, despite 
-that fact that it is hosting a quasar.
-Hence, the decline in star formation history since $z$\ssim2 
-for at least a subset of AGN host galaxies 
-may be mainly
-a manifestation of the evolution in the molecular gas content rather than a result of 
-the negative feedback driven by their central AGNs.
 
@@
 we find that the redshift of the first set is fully consistent with the systemic redshift. This
-supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
+supports previous claims that [O{\scriptsize III}] lines, tracing the narrow line region (NLR),
 are good proxies
@@
 On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
+
 Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature.
@@
 $\sim$100\pmm270\,\kms
-between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines in a
+between [Mg{\scriptsize II}] and [O{\scriptsize III}] lines in a
 sample of $>$3800 quasars,
@@
 between the broad component of
-H$\beta$ and [O\,{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
+H$\beta$ and [O{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
 where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms
@@
 
-Theoretical studies have suggested that negative feedback from an AGN may remove a 
-large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
-In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
-non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
-derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
-We thus find no evidence of negative AGN feedback on the molecular gas content 
-and on the star formation activity in RXJ1131 at the resolution of our data.
-Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
-their contribution to the decline in cosmic star formation history since $z$\ssim2 
-may be mainly
-a manifestation of the redshift evolution in the molecular gas content rather than a result of 
-negative feedback driven by their central AGNs.
-
-Using the CO redshift as systemic redshift for the host galaxy of RXJ1131, we find
-that the redshift inferred from NLR lines reported in previous studies are consistent with this systemic redshift
+We find that the redshift inferred from the NLR lines reported in previous studies are consistent with the  systemic redshift as measured
+from the CO line,
 but that the BLR lines are redshifted by $\sim$715\,\kms.
@@
 
+Theoretical studies have suggested that negative feedback from an AGN may remove a 
+large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
+In this study, we find that the star formation efficiency and specific SFR of RXJ1131 are comparable to those of 
+$z$\ssim1$-$1.5 disk galaxies, which are not known to host quasars, and that its
+molecular gas mass fraction is consistent with the observed cosmic decline for star-forming 
+galaxies since $z$\ssim2$-$3.
+Hence, we find no evidence of negative AGN feedback on the cold molecular gas fraction 
+and on the star formation activity in RXJ1131.
+Future observations at higher resolution will allow us to better constrain the molecular gas kinematics and dynamics of
+RXJ1131 to investigate any potential interplay with the quasar on smaller scales.
+More broadly, systematic studies of the correlations between the molecular gas fraction, stellar mass, and AGN luminosity 
+at different redshifts 
+% constraining the molecular gas fraction
+% as a function of stellar mass together with 
+% the molecular gas fraction as a function of AGN luminosity normalized 
+% by the stellar mass ($L_{\rm QSO}$$/$M$_*$) for a sample of AGN host galaxies at different redshifts
+% between 0$<$\,$z$\,$<$2 % at a given galaxy mass 
+will enable us to better understand the relative importance of AGN feedback and of the 
+evolution in the molecular gas mass fraction on the decline of star formation history and black hole accretion history.
+
 %==============================================================================
@@
 
-We thank the referee for providing detailed and constructive comments that helped improved the clarify of this manuscript.
+We thank the referee for providing detailed and constructive comments that helped to improve the clarity of this manuscript.
 DR and RP acknowledge support from the National Science Foundation

### 2017-01-21 src/HSTVLA.py
update contour color

@@ -1,12 +1,14 @@
 """
 Author: Daisy Leung
 
-Last edited: 9 Jan 2016
+Last edited: 21 Jan 2016
 
 Purpose:
 - Plot single panel 5GHz VLA continuum on HST F555W, investigate continuum offset
 
 History:
+Jan 21 2016:
+    - update contour color
 Jan 9 2016:
     - zoom in
     - use np.sort() w/ contour level, to satisfy mpl version > 1.5.3
@@ -118,7 +120,8 @@ if inverted_HSTleft: fig1.set_theme('publication')
 # Contours
 ########################################
 # fig1.show_contour(label_vla['C_R0'][0], colors="green", levels=sigma_contour_tenpercent(Smax), linewidths=1.0)#, layer='fg')
-fig1.show_contour(label_vla['C_R0'][0], colors="red", levels=np.sort(sigma_contour_VLA(sigma)), linewidths=1.2)#, layer='fg')
+fig1.show_contour(label_vla['C_R0'][0], colors="#99ff00", levels=np.sort(sigma_contour_VLA(sigma)), linewidths=1.2)#, layer='fg')
+# fig1.show_contour(label_vla['C_R0'][0], colors="#ffff00", levels=np.sort(sigma_contour_VLA(sigma)), linewidths=1.2)#, layer='fg')
 
 # figred.show_contour(label_vla['red'][0], colors="lime", levels=sigma_contour_array(sigma_red), linewidths=2)
 

### 2017-01-21 WRITEUP/ms_apj/ms.tex
accepted version

@@
 
-\slugcomment{To be submitted to the ApJ}
+\slugcomment{Accepted to the ApJ}
 \makeatletter
@@
 \citestyle{aa}
-\shorttitle{Molecular Gas Dynamics in the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
+\shorttitle{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXJ1131$-$1231}
 \shortauthors{Leung, Riechers \& Pavesi}
@@
 
-\title{Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
+\title{Molecular Gas Kinematics and Star Formation Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
 \author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
@@
 different kinematic components.
-The intrinsically symmetric line profile with a conspicuous source-plane velocity
-gradient suggests that
+The intrinsically symmetric line profile and a smooth source-plane velocity
+gradient suggest that
 the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
 a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
-In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
+We also find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
 consistent with the optically-faint companion reported in previous studies.
-The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
-and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
-The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
-We find lensing-corrected stellar and dust masses, an IR luminosity, and a
-star formation rate of
-$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
-The source-plane morphologies of its gas and stellar populations
-indicate that the star-formation activity may be as extended as the molecular gas reservoir.
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
-than the
-local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
+The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
+and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
+We find a lensing-corrected stellar mass of
+$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
+corresponding to a specific SFR and star formation efficiency comparable to
+$z$\ssim1 disk galaxies not hosting quasars.
+The implied gas mass fraction of $\sim$18\pmm4\% is consistent with the previously-observed cosmic decline since $z$\ssim2.
+We thus find no evidence for quenching of star formation in RXS\,J1131$-$1231.
+This agrees with our finding of an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
+local value, suggesting that the bulk of its black hole
+mass is largely in place while its stellar bulge is still assembling.
 \end{abstract}
@@
 \section{Observations} \label{sec:obs}
+
+\subsection{CARMA \cco}
+Observations of the \cco rotational line
+($\nu_{\rm rest}$\,=\,345.79599\,GHz) towards RXJ1131 at $z_{\rm s, QSO}$\eq0.658
+were carried out with the \carma (CARMA;
+Program ID: cf0098; PI: D. Riechers) in the D array configuration.
+The line frequency is redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz at the quasar redshift.
+Observations were carried out
+on 2014 February 02 under poor 1.5\,mm
+weather conditions and on 2014 February 17 under good 1.5\,mm
+weather conditions.
+This resulted in a
+total on-source time of 2.94 hours after flagging poor
+visibility data.
+The correlator setup provides a bandwidth of 3.75 GHz in
+each sideband and a
+spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
+line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
+(second track) were observed
+every 15 minutes for pointing, amplitude, and phase calibration. Mars was
+observed as the primary absolute flux calibrator and 3C279 was observed as
+the bandpass calibrator for both tracks.
+
+Given that the phase calibrator used for the first track was faint and was
+observed under poor weather conditions and that the phase calibrator used for
+the second track was far from our target source, the phase calibration is
+subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
+We thus conservatively estimate
+a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35
+the gain variations over time, and the phase scatter on the calibrated data. We
+therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
+of this system and the conclusion of this paper do not rely on this quantity.
+
+The \ncode{miriad} package was used to calibrate the visibility data.
+The calibrated visibility data were
+imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
+beam size of 3\farcs2 $\times$ 1\farcs9 at a position angle (PA) of 8\degr for the lower sideband
+image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
+over a channel width of 25\,MHz. An rms noise of
+$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
+line-free channels in both sidebands.
+
 \subsection{PdBI \bco}
@@
 ($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
-at the $\nu_{\rm LO}$\eq139.256\,GHz
-were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
-Riechers). Two observing runs were carried out on 2014 December 06 and 2015
+towards RXJ1131
+were carried out using the IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
+Riechers).
+Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
+the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
+Two observing runs were carried out on 2014 December 06 and 2015
 February 05 under good weather conditions in the C and D array configurations,
@@
 yields an rms noise of 0.082 mJy\,beam$^{-1}$.
-
-\subsection{CARMA \cco}
-Observations of the \cco rotational line in RXJ1131
-($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
-were carried out with the \carma (CARMA;
-Program ID: cf0098; PI: D. Riechers)
-in the D array configuration on 2014 February 02 under poor 1.5\,mm
-weather conditions and on 2014 February 17 under good 1.5\,mm
-weather conditions.
-This resulted in a total on-source time of 2.94 hours after flagging poor
-visibility data.
-The correlator setup provides a bandwidth of 3.75 GHz in
-each sideband and a
-spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
-line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
-(second track) were observed
-every 15 minutes for pointing, amplitude, and phase calibration. Mars was
-observed as the primary absolute flux calibrator and 3C279 was observed as
-the bandpass calibrator for both tracks.
-
-Given that the phase calibrator used for the first track was faint and was
-observed under poor weather conditions and that the phase calibrator used for
-the second track was far from our target source, the phase calibration is
-subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
-We thus conservatively estimate
-a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35
-the gain variations over time, and the phase scatter on the calibrated data. We
-therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
-of this system and the conclusion of this paper do not rely on this quantity.
-
-The \ncode{miriad} package was used to calibrate the visibility data.
-The calibrated visibility data were
-imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
-beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
-image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
-over a channel width of 25\,MHz. An rms noise of
-$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
-line-free channels in both sidebands.
 
@@
 \subsection{\bco Emission} \label{sec:CO21}
-We detect \bco line emission toward the background source in the PdBI data
-at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
-0.6537\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
+We detect \bco line emission towards the background source RXJ1131 in the PdBI data
+at $\gtrsim$\,27$\sigma$ significance. Based on this measurement, we refine the redshift of RXJ1131 to
+$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to
+the de-lensed spectrum (\Fig{delensed})
+instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our
+redshift determination
+due to differential lensing (see \Sec{differential}).
+}. The emission is spatially and kinematically resolved
 with a highly asymmetric double-horned line profile
@@
 179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
-$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms.
+$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms.
+
+\begin{deluxetable}{lcc}[!htbp]
+\tabletypesize{\scriptsize}
+\tablecolumns{3}
+\tablecaption{Observed Properties of RXJ1131 and its companion}
+\tablehead{
+\colhead{Parameter} &
+\colhead{Unit} &
+\colhead{Value}
+}
+\startdata
+$z_{\rm CO(2-1)}$   &                          & 0.6541\pmm0.0002 \\ [0.5ex]
+$I_{\rm CO(2-1)}$     & Jy\,km s\pmOne           & 20.3\pmm0.6 \\ [0.5ex]
+$S_{\rm CO(2-1)}$\tna     & Jy km s\pmOne beam\pmOne & 8.12\pmm0.30 \\ [0.5ex]
+FWHM$_{\rm CO(2-1)}$ \tnb & km s\pmOne               & 179\pmm9, 255\pmm28 \\ [0.5ex]
+FWHM$_{\rm CO(2-1)}$\tnc        & km s\pmOne               & 220\pmm72 \\ [0.5ex]
+$I_{\rm CO(3-2)}$     & Jy\,km s\pmOne           & 35.7\pmm6.9
+\enddata
+\label{tab:obsprop}
+%\tablecomments{}
+\tablenotetext{a}{Peak flux density in the intensity map.}
+\tablenotetext{b}{From fitting a double Gaussian to the observed \bco spectrum (\Fig{CO21spec}).}
+\tablenotetext{c}{From fitting a double Gaussian with a common FWHM to the de-lensed \bco spectrum (\Fig{delensed}).}
+\end{deluxetable}
 
@@
 \includegraphics[width=0.45\textwidth]{f1.eps}
-\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of
-21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
-The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
-considering the asymmetry resulting from differential lensing.
+\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
+22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
+The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
+the de-lensed line profile (\Fig{delensed}).
 A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
 \end{figure}
-\vspace{.2em}
+
 We construct a zeroth order moment map, red/blue channel maps, and
@@
 in the intensity map.
-
-The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
-the image plane
-is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
-and thus, the emission is resolved over $\sim$2.2 beams.
-While the lensed emission is not strictly distributed as a two-dimensional
-Gaussian;
-the fit recovers the line intensity enclosed by the emitting
-region, therefore we take this as an estimate on the full extent of the lensed
-emission. On the other hand, if we assume that the spatial distribution of
-the lensed molecular gas emission is similar to that in the optical to \nir
-wavelengths, the lensed emission would be more accurately described by an
-annulus, enclosing the partially complete ``Einstein ring'' and
-the lensed knots (see \Fig{CO21mom}).
+Observed properties of the \bco emission line are summarized in \Tab{obsprop}.
+
+The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian
+to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,
+which is consistent with that obtained by visibility-plane fitting within the uncertainties.
+Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
+and appears to be a superposition of at least two components (top left panel of \Fig{CO21mom}),
+we also fit two Gaussians to the intensity map.
+This yields deconvolved source sizes of
+3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, separated by $\sim$2\farcs2 in RA and $\sim$1\farcs7 in Dec.
+The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended
+than the optical
+``Einstein ring'', which has a diameter of $\sim$3\farcs6
+(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one).
+This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image,
+and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
+Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.
 
@@
 Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
-are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
-The contours in both top panels start at 3$\sigma$ and increment at steps of
+are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
+The contours in both top panels start at 3$\sigma$ and increment in steps of
 $\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
@@
 \subsection{\cco Emission}
-We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
-The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
-double-peaked profile. We estimate a line intensity of
-35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
-linewidth used to infer the \bco line intensity ($\sim$700 \kms).
-Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
+We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
+The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where
+we over-plot spectra of the \bco and \cco lines.
+We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
+We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing,
+indicating a $\sim$\,6$\sigma$ detection.
+We measure a line intensity of 35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop}) by summing up fluxes over the FWZI
+linewidth used to infer the \bco line intensity.
+
+Assuming that the spatial extent of \bco and \cco is similar and therefore the emission is
 magnified by the same amount, the measured line intensities
 correspond to a brightness temperature ratio of
-$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
-Taking into account the large phase errors associated with \cco, this is consistent with
+$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.37.
+The quoted error bar is derived by adding the uncertainties associated with the CO line intensities
+and those from absolute flux calibrations in quadrature.
+This brightness temperature ratio is consistent with
 thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
-nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
-with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
+nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, Riechers11b, CW13}, but also
+with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13, Daddi15a}.
 
@@
 over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
-The velocity scale is with respect to $z$=0.6537, which corresponds to the
-dynamical center of the \bco line. The spectral resolution for \cco and \bco
-is 35.8 \kms and 21.5 \kms, respectively.
+The velocity scale is the same as in \Fig{CO21spec}.
+The spectral resolution for \cco and \bco
+is 36 \kms and 22 \kms, respectively.
 \label{fig:co32spec}}
@@
 
-We detect 2\,mm continuum emission at an
+We detect 2.2\,mm continuum emission at an
 integrated flux density of
@@
 $S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
-centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
-along the lensed arc is also detected.
+centered on the lensing galaxy (\Fig{cont}).
+Slightly extended emission
+along the lensing arc is also detected.
 This suggests that we detect emission in both
-the foreground galaxy and the background galaxy and that the
+the foreground and the background galaxy and that the
 emission is marginally resolved along its major axis.
-We subtract a point source model in the $uv$-plane to remove the unresolved part of the
-emission, which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
-in the residual map coincides with the lensed arc, and is consistent with
-the difference between the integrated and the peak flux in the
-original continuum map ($\sim$0.4 mJy). We therefore adopt
-$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
+We subtract a point source model in the visibility-plane to remove the unresolved part of the
+emission, which we here assume to be dominated by the foreground galaxy. The emission
+in the residual map coincides spatially with the lensing arc. We measure a flux density
+of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy for this residual component.
+This flux density is consistent with
+the difference between the integrated and the peak flux density measured in the
+original continuum map ($\sim$0.4 mJy).
+We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the best estimate for the 2\,mm continuum flux of
 the background galaxy (RXJ1131).
-The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
+We here quote a conservative error bar, which is derived by adding the uncertainty
+associated with the flux density of the
+point-source model ($\delta S_{\nu}$\eq0.088\,mJy) with
+that of the peak flux in the residual map (0.08\,mJy)
+in quadrature. We caution that this does not account for the systematic uncertainties of the
+de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
 We report the peak flux in the original map
@@
 \begin{figure}[!htbp]
-\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{f4a.eps}
-\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{f4b.eps}
-\caption{Top: overlay of the 2\,mm continuum emission on the optical image.
-Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
-Contours in both images start and increment at steps of
-$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and
-$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the top and bottom panel, respectively.
-The central crosses indicate the centroid of the foreground galaxy,
-as detected in the optical image.
+\includegraphics[trim=12 27 0 1, clip, width=0.47\textwidth]{f4a.eps}
+\includegraphics[trim=10 5 0 0, clip, width=0.47\textwidth]{f4b.eps}
+\caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
+Contours start and increment in steps of
+$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
+Bottom: overlay of the VLA 5\,GHz continuum emission on the optical image.
+Contours correspond to $\pm2^n\sigma$, where
+$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
+and $n$ is an integer running from 2 to 5.
+Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$ significance.
 The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
@@
 We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
-We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
-for the foreground
-galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
-for the background galaxy by fitting a
-power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
+We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
+for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21
+for the background galaxy by fitting
+power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
 5\,GHz and 2\,mm.
+The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}. This likely suggests
+that at least a fraction of the observed 2\,mm emission arises from thermal dust emission.
+This spectral slope would be even shallower
+if the background source contributes to the unresolved fraction of the
+2\,mm flux.
+In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and
+lead to a slope steeper than $\alpha^{\rm 2mm}_{\rm 6cm}$\ssim$-$0.02, which is flatter than
+that typical of elliptical galaxies.
+Assuming a spectral slope of $\alpha$\ssim$-$0.7 to account for synchrotron radiation in RXJ1131, we expect
+a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm.
+The flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy therefore likely arises due to thermal dust emission.
 
@@
 \startdata
-1.25    & 239834  & 1.009 $\pm$ 0.09    & CTIO/J-Band \\
-1.65    & 181692  & 1.448 $\pm$ 0.12    & CTIO/H-Band \\
-2.17    & 138153  & 2.064 $\pm$ 0.16    & CTIO/Ks-Band \\
-3.4     & 88174.2 & 7.027 $\pm$ 0.14    & {\it WISE}/W1 \\
-3.6     & 83275.7 & 5.618 $\pm$ 0.0021  & {\em Spitzer}/IRAC \\
-4.5     & 66620.5 & 7.803 $\pm$ 0.0021  & {\em Spitzer}/IRAC \\
-4.6     & 65172.3 & 8.872 $\pm$ 0.16    & {\it WISE}/W2 \\
-5.8     & 51688.4 & 10.720 $\pm$ 0.0051 & {\it Spitzer}/IRAC \\
-8.0     & 37474.1 & 14.470 $\pm$ 0.0041 & {\it Spitzer}/IRAC \\
-12      & 24982.7 & 21.960 $\pm$ 0.42   & {\it WISE}/W3 \\
+1.25    & 239834  & 1.009 $\pm$ 0.090    & CTIO/J-Band \\
+1.65    & 181692  & 1.448 $\pm$ 0.121    & CTIO/H-Band \\
+2.17    & 138153  & 2.064 $\pm$ 0.160    & CTIO/Ks-Band \\
+3.4     & 88174.2 & 7.027 $\pm$ 0.142    & {\it WISE}/W1 \\
+3.6     & 83275.7 & 5.618 $\pm$ 0.002   & {\em Spitzer}/IRAC \\
+4.5     & 66620.5 & 7.803 $\pm$ 0.002   & {\em Spitzer}/IRAC \\
+4.6     & 65172.3 & 8.872 $\pm$ 0.163   & {\it WISE}/W2 \\
+5.8     & 51688.4 & 10.720 $\pm$ 0.005  & {\it Spitzer}/IRAC \\
+8.0     & 37474.1 & 14.470 $\pm$ 0.004  & {\it Spitzer}/IRAC \\
+12      & 24982.7 & 21.960 $\pm$ 0.425  & {\it WISE}/W3 \\
 12      & 24982.7 & $<$400              & {\it IRAS} \\
-22      & 13626.9 & 55.110 $\pm$ 1.9    & {\it WISE}/W4 \\
+22      & 13626.9 & 55.110 $\pm$ 1.878  & {\it WISE}/W4 \\
 24      & 12491.4 & 70.204 $\pm$ 0.026  & {\it Spitzer}/MIPS \\
@@
 500     & 599.585 & 56.8 $\pm$ 8.8      & {\it Herschel}/SPIRE \\
-1387.93 & 216     & $<$2.492            & CARMA \\
-2152.82 & 139.256 & 1.230 $\pm$ 0.220   & PdBI \\
+1387.93 & 216     & $<$2.49             & CARMA \\
+2152.82 & 139.256 & 1.23 $\pm$ 0.22   & PdBI \\
 \cutinhead{Foreground Lensing Galaxy (deblended bands)} \\ [-1.5ex]
@@
 3.6     & 83275.7 & 0.585 $\pm$ 0.003\tna   & {\em Spitzer}/IRAC \\
-4.5     & 66620.5 & 1.794 $\pm$ 0.0027\tna  & {\em Spitzer}/IRAC \\
-5.8     & 51688.4 & 3.163 $\pm$ 0.0059\tna  & {\it Spitzer}/IRAC \\
-8.0     & 37474.1 & 4.589 $\pm$ 0.0057\tna  & {\it Spitzer}/IRAC \\
+4.5     & 66620.5 & 1.794 $\pm$ 0.003\tna  & {\em Spitzer}/IRAC \\
+5.8     & 51688.4 & 3.163 $\pm$ 0.006\tna  & {\it Spitzer}/IRAC \\
+8.0     & 37474.1 & 4.589 $\pm$ 0.006\tna  & {\it Spitzer}/IRAC \\
 2152.82 & 139.256 & 0.799 $\pm$ 0.082   & PdBI \\
@@
 \cutinhead{Background Galaxy RXJ1131 (deblended bands)}
-0.555   & 540167  & 0.009 $\pm$ 0.0041\tnb  & {\it HST}-ACS/V-Band \\
-0.814   & 368295  & 0.041 $\pm$ 0.0054\tnb  & {\it HST}-ACS/I-Band \\
+0.555   & 540167  & 0.009 $\pm$ 0.004\tnb  & {\it HST}-ACS/V-Band \\
+0.814   & 368295  & 0.041 $\pm$ 0.005\tnb  & {\it HST}-ACS/I-Band \\
 1.6     & 187370  & 0.133 $\pm$ 0.004\tnb   & {\it HST}-NICMOS(NIC2)/H-Band \\
-3.6     & 83275.7 & 5.034 $\pm$ 0.0021  & {\em Spitzer}/IRAC \\
-4.5     & 66620.5 & 6.009 $\pm$ 0.0017  & {\em Spitzer}/IRAC \\
+3.6     & 83275.7 & 5.034 $\pm$ 0.002  & {\em Spitzer}/IRAC \\
+4.5     & 66620.5 & 6.009 $\pm$ 0.002  & {\em Spitzer}/IRAC \\
 5.8     & 51688.4 & 7.557 $\pm$ 0.003   & {\it Spitzer}/IRAC \\
-8.0     & 37474.1 & 9.881 $\pm$ 0.0039  & {\it Spitzer}/IRAC\\
-2152.82 & 139.256 & 0.400 $\pm$ 0.082\tnc   & PdBI \\
+8.0     & 37474.1 & 9.881 $\pm$ 0.004  & {\it Spitzer}/IRAC\\
+2152.82 & 139.256 & 0.39 $\pm$ 0.12\tnc   & PdBI \\
 61414   & 4.8815  & 1.273 $\pm$ 0.042   & VLA
@@
 \tablecomments{The IRAC photometry for channel 1 (3.6\,$\micron$) is extracted directly from the image and
-from the Spitzer Heritage Archive for channels 2$-$4 (4.5, 5.8, and 8.0\,$\micron$). All upper limits are 3$\sigma$.}
+from the Spitzer Heritage Archive for channels 2$-$4 (4.5, 5.8, and 8.0\,$\micron$).
+The flux uncertainties quoted for radio and mm observations (PdBI, CARMA, and VLA) do not include those from absolute flux calibration.
+All upper limits are 3$\sigma$.}
 \tablenotetext{a}{Flux obtained using aperture photometry after subtracting the emission of RXJ1131 from the total emission.}
 \tablenotetext{b}{A contribution from the quasar has been removed (see C06), and thus the flux density corresponds to the host galaxy only.}
-\tablenotetext{c}{Flux extracted from the residual map after subtracting a point-source model.}
+\tablenotetext{c}{Flux extracted from the residual map after subtracting a point-source model.
+For SED modeling, we use $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy to exclude synchrotron emission (see \Sec{deblend}).}
 \tablerefs{The {\it HST} photometry is adopted from C06.}
@@
 Nevertheless, the high spectral
-resolution of these data provides dynamical information on
+resolution of these data provides kinematic information on
 spatial scales smaller than the beam (see \Fig{CO21mom}).
-Hence, we reconstruct the intrinsic gas dynamics
+Hence, we reconstruct the intrinsic line profile and source-plane velocity structure
 by carrying out a parametric lens modeling over different
@@
 that cover the full linewidth of $\sim$750\,\kms.
+\begin{deluxetable}{lcc}[htbp]
+\tabletypesize{\scriptsize}
+\tablecolumns{3}
+\tablecaption{Lens parameters constrained by models of seven velocity channels}
+\tablehead{
+\multicolumn{2}{c}{Parameters} &
+\colhead{Median values} % weighted-mean of median of each
+}
+\startdata
+Offset in RA    & (\arcsec)   &  0.004$\pm$0.027\\
+Offset in Dec    & (\arcsec)   & 0.003$\pm$0.027\\
+Axial Ratio      &             & 0.56$\pm$0.16\\
+Position Angle   & (deg)       & 103$\pm$22\\
+Einstein Radius\tna  & (\arcsec)   & 1.833$\pm$0.002
+\enddata
+\label{tab:lens}
+\tablenotetext{a}{This corresponds to mass of $M(\theta$\,$<$\,$\theta_{\rm E})$\eq(7.42\pmm0.02)\E{11}\Msun within the Einstein radius.}
+\tablecomments{Parameters describing the foreground lens are
+obtained based on the median in the preliminary models (see text for details).
+All angular offsets are with respect to
+$\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
+$\delta$\,=\,$-$12\degr31\arcmin58\farcs3 (J2000).}
+\end{deluxetable}
 
@@
 \includegraphics[width=0.45\textwidth]{f5.eps}
-\caption{The full resolution \bco spectrum (yellow histogram) and
+\caption{Top: the full resolution \bco spectrum (yellow histogram) and
 the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The
-blue histogram shows the ``intrinsic'' line profile of RXJ1131
+light blue histogram shows the ``intrinsic'' line profile of RXJ1131
 after subtracting a contribution from its companion galaxy and
@@
 above each respective model channel.
+Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
+The y-axes are shown on a log scale.
 \label{fig:delensed}}
@@
 median and the 68\% confidence intervals in the marginal PDFs.
-\begin{deluxetable}{lcc}[!htbp]
-\tabletypesize{\scriptsize}
-\tablecolumns{3}
-\tablecaption{Lens parameters constrained by models of seven velocity channels}
-\tablehead{
-\multicolumn{2}{c}{Parameters} &
-\colhead{Median values} % weighted-mean of median of each
-}
-\startdata
-Offset in RA    & (\arcsec)   &  0.004$\pm$0.027\\
-Offset in Dec    & (\arcsec)   & 0.003$\pm$0.027\\
-Axial Ratio      &             & 0.56$\pm$0.16\\
-Position Angle   & (deg)       & 103$\pm$22\\
-Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002
-\enddata
-\label{tab:lens}
-\tablecomments{Parameters describing the foreground lens are
-obtained based on the median in the preliminary models (see text for details).
-All angular offsets are with respect to
-$\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
-$\delta$\,=\,$-$12\degr31\arcmin58\farcs3 (J2000).}
-\end{deluxetable}
 
@@
 \caption{Best-fit lens models of the PdBI \bco data in different velocity channels, as listed in \Tab{model}.
-Top: each panel corresponds to a channel map of width 107.5\,\kms of the observed
-emission (red) overlaid on the best-fit models (grayscale).
+Top: each panel corresponds to a channel map of width 107.5\,\kms centered on the indicated velocity.
+The observed emission (red contours) is over-plotted atop the best-fit model (grayscale).
 Bottom: residual images obtained by
@@
 In the image-plane integrated line map shown in \Fig{CO21mom}, the redshifted component is
-cospatial with the Einstein ring seen in the
-optical image, with most of its apparent flux originating from the lensed arc
-in the southeast, whereas the blue component is predominately coming from
-solely the lensed arc. To further illustrate this, we show the
+cospatial with the Einstein ring that is seen in the
+optical image, with most of its apparent flux originating along the lensing arc,
+whereas centroid of the blueshifted emission is offset to the SE of
+the lensing arc. This suggests that the CO-emitting region in RXJ1131 is extended.
+To further illustrate this, we show the
 channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
@@
 \caption{
-Channel maps of the PdBI \bco data cube toward RXJ1131 at 21.5\,\kms resolution.
+Channel maps of the PdBI \bco data at 22\,\kms resolution.
 Black crosses indicate the positions of the lensed knots (AGN emission,
-which correspond to components ABCD in \citetalias{Claeskens06a}). The central white-filled
+which correspond to components ABCD in \citetalias{Claeskens06a}). The white-filled
 star indicates the position of the foreground lensing galaxy (component G
@@
 \tablehead{
-\colhead{Velocity Range (\kms)} & % see 22May16/intensity30Apr16.spec; or channel map in paper
+\colhead{Velocity Range (\kms)} & % see 02July16/velo_res_obs.txt (2nd column), which corresponds to rest-frame velocity at z=0.6541, taken from the central of each bin
 \colhead{Source 1 $\mu_{\rm L}$} &
@@
 \startdata
--366\,$-$\,-258 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
--237\,$-$\,-151 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
--129\,$-$\,-43  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
--21.5\,$-$\,65    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
-86\,$-$\,172        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
-194\,$-$\,280       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
-301\,$-$\,388       & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ [0.5ex]
-weighted average & 4.4 & \\ [0.5ex]
+346\,$-$\,260       & 6.7 $\pm$ 2.5 &  7.2 $\pm$ 5.6 \\
+238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
+131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
+24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
+-84\,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
+-191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
+-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.7ex]\hline
+weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]
 median & 5.5 &
@@
 \label{tab:model}
-\tablecomments{Velocity is taken from the center of each (native) channel
-without any binning. Each row corresponds to a channel slice used for
+\tablecomments{First column corresponds to the rest-frame velocity ranges taken from the center of an unbinned channel
+(see \Fig{delensed}). Each row corresponds to a (binned) channel slice used for
 lens modeling. Source 1 is RXJ1131 and source 2 is its companion. }
@@
 
-Similar to previous studies of RXJ1131, where
-differential lensing across the {\it HST}
-$V$-, $I$-, and $H$-bands has been detected with a
-magnification factor decreasing from 10.9 to 7.8 \citepalias{Claeskens06a},
-the highly asymmetric \bco line profile suggests that
-differential lensing is also non-negligible for CO,
-causing the redshifted emission to be apparently much brighter than the
+Previous studies of RXJ1131 find evidence for differential lensing across
+the {\it HST} $V$-, $I$-, and $H$-bands, where the
+magnification factor varies from 10.9 to 7.8 \citepalias{Claeskens06a}.
+This indicates that the emission from different stellar populations
+within the host galaxy have various spatial extents and positions with respect to the caustic.
+The best-fit lens models obtained here for different CO channels show that differential lensing also plays
+an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
+from 8.7 to 3.1 across different kinematic components (\Tab{model}).
+The asymmetry in the line profile (\Fig{CO21spec} and \Fig{delensed}) is therefore predominantly a result of
+the redshifted CO-emitting gas being more strongly-magnified
+than the
 blueshifted component.
-This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
-varies from 8.7 to 3.1 across the \bco line (\Tab{model}) and also partly due to a contribution from the companion in the redshifted velocity channels.
-The variation in $\mu_{\rm L}$ across channels is consistent with the source plane
+A secondary reason is likely due to
+the inclusion of the emission of the companion in the most redshifted velocity channels.
+The variation in $\mu_{\rm L}$ found across channels is consistent with the source plane
 positions relative to the caustics in \Fig{model}, where the red wing
@@
 \subsection{\bco Dynamical Modeling} \label{sec:dynamics}
-Assuming the velocities of the respective channels used in the
-lens modeling correspond to solely the tangential component of the
-true velocity vector of a rotating disk (i.e., along the major axis),
-we extract a one dimensional PV diagram in \Fig{PV}
-by slicing across their source plane positions (PA: 121\degr).
+As discussed in \Sec{caveat}, we interpret RXJ1131 as a disk galaxy as it displays
+a kinematically-ordered velocity gradient in the source-plane velocity map of the CO emission,
+a symmetric double-horned line profile (\Fig{delensed}, \Fig{model} and, left panel of \Fig{PV}),
+and a disk-like morphology in the source-plane reconstruction of the optical-NIR emission
+\citepalias{Claeskens06a}.
+We extract a one dimensional position-velocity (PV) profile
+by assuming that the source-plane centroids of different velocity components
+obtained from dynamical lens modeling
+are dominated by the tangential component of the
+true velocity vector of a rotating disk, i.e., each velocity component would
+be seen as lying along the major axis of a rotating disk if observed with sufficiently high angular resolution
+(see right panel of \Fig{PV}).
+In this process, the positions for each velocity component (plotted as data points in the right panel of \Fig{PV})
+are extracted along the best-fitted major axis, which is along a PA of 121\degr.
 
@@
 In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
-Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.
+Pearson coefficient $R$\,=\,0.998, and $-$0.400 between $V_{a}$ and $V_0$.
 
@@
 \includegraphics[width=0.525\textwidth]{f9b.eps}
-\caption{Left: Source-plane positions from best-fit \bco lens models are indicated with their associated uncertainties atop
-the observed first moment map. The contours are at steps of 50\,\kms.
-Right: PV slice along the major axis in the source plane at PA\,=\,121\degr.
-Dashed line shows the best-fit rotation curve using an arctangent model.
+\caption{Velocity gradient of the \bco emission observed in RXJ1131 and the de-lensed velocity gradient obtained from lens modeling.
+Left: source-plane positions obtained from the best-fit lens models (presented in \Sec{lensmodel}) are shown
+as markers
+atop the observed first moment map (i.e., in the image-plane; see \Fig{CO21mom}).
+The markers are color-coded by their centroid velocities.
+The contours are in steps of 50\,\kms.
+Despite the distorted first moment map in the image-plane due to differential lensing and beam smearing effects, the source-plane velocity gradient reconstructed from dynamical lens modeling suggests that
+RXJ1131 is intrinsically a kinematically-ordered disk.
+Right: PV slice extracted along the fitted major axis at PA\,=\,121\degr based on
+the reconstructed source-plane velocity gradient.
+Dashed line shows the best-fit ``rotation curve'' using an arctangent model.
 The vertical error bars show the channel width for
 each model and the horizontal error bars are the
-1$\sigma$ uncertainties on the source plane positions.
+1$\sigma$ uncertainties on the source-plane positions along the major axis.
 \label{fig:PV}}
@@
 Here, we adopt the maximum {\em observed} velocity
-$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
+$V_{\rm rot}$\,=\,303\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc
+from the
 dynamical center as a proxy to the rotation velocity.
@@
 $($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
-Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),
+Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,303\,\kms (see \Sec{dynamics}),
 we find a dynamical mass of
-$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1.7\E{11}\,\Msun enclosed
+$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1.3\E{11}\,\Msun enclosed
 within the CO-emitting region in RXJ1131.
@@
 The IRAS 60\,$\micron$ and 100\,$\micron$ upper limits are included to constrain the dust peak.
+Here, we use a flux density of $S_{\rm 2mm}$\eq0.27\pmm0.08 mJy derived in \Sec{deblend}
+instead of the deblended flux listed in \Tab{photometry}
+to exclude a potential contribution due to synchrotron emission (see \Sec{deblend}) in the dust SED modeling.
+An uncertainty from absolute flux calibration of $\sim$15\% is added in quadrature
+to the PdBI 2\,mm continuum photometry in our fitting procedure.
+
 The fit is performed using the code
@@
 Here we report the statistical means
-and the 1$\sigma$ confidence interval in the marginal PDFs
+and the 68\% confidence intervals in the marginal PDFs
 as the best-fit parameters, as listed in \Tab{SED}.
@@
 \startdata
-$T_d$                           & (K)                & 52.0\petm{4.0}{4.1}   & 58.2\petm{14.5}{14.4}  \\ [1.05ex]
-$\beta$                         &                    & 1.8\petm{0.5}{0.6}    & 2.1\petm{0.3}{0.3}  \\ [1.05ex]
-$\alpha$                        &                    & 1.6\petm{0.5}{0.5}    & 8.9\petm{6.9}{6.3}   \\ [1.05ex]
-$\lambda_0$\tna                 & ($\micron$)        & 548\petm{285}{307}    & 367\petm{125}{145}  \\ [1.05ex]
-$\lambda_{\rm peak}$\tnb        & ($\micron$)        & 162\petm{16}{30}      & 146\petm{39}{44}  \\ [1.05ex]
-$f_{\rm norm,\ 500\micron}$\tnc & (mJy)              & 59\petm{14}{13} & 60\petm{5}{5} \\ [1.05ex]
-\LFIR\tnd                       & (10$^{12}$\,\Lsun) & 3.81\petm{2.04}{1.92} & 4.72\petm{2.54}{2.26}      \\ [1.05ex]
-$M_{\rm d}$\tne                 & (10$^8$\,\Msun)    & 22\petm{5}{18}        & 11\petm{5}{6}
+$T_d$                           & (K)                & 54\petm{8}{10}   &
+55\petm{21}{20}  \\ [1.05ex]
+$\beta$                         &                    & 1.6\petm{0.5}{0.4}    & 2.2\petm{0.3}{0.3}  \\ [1.05ex]
+$\alpha$                        &                    & 1.6\petm{0.5}{0.6}    & 8.5\petm{7.0}{6.2}   \\ [1.05ex]
+$\lambda_0$\tna                 & ($\micron$)        & 559\petm{278}{324}    & 365\petm{111}{120}  \\ [1.05ex]
+$\lambda_{\rm peak}$\tnb        & ($\micron$)        & 159\petm{19}{40}      & 155\petm{38}{43}  \\ [1.05ex]
+$f_{\rm norm,\ 500\micron}$\tnc & (mJy)              & 55\petm{13}{13} & 59\petm{6}{6} \\ [1.05ex]
+\LFIR\tnd                       & (10$^{12}$\,\Lsun) & 3.81\petm{1.92}{1.97} & 4.24\petm{2.17}{2.00}      \\ [1.05ex]
+$M_{\rm d}$\tne                 & (10$^8$\,\Msun)    & 16\petm{5}{12}        & 14\petm{5}{7}
 \enddata
@@
 the 24\,$\micron$ data. Based on the resulting posterior PDFs, we find an apparent
+IR luminosity (rest-frame 8\,$-$\,1000\,$\micron$) of 8.22\petm{2.75}{2.98}\E{12} \Lsun, a
 \fir luminosity (rest-frame 42.5\,$-$\,122.5\,$\micron$) of
-3.81\petm{2.04}{1.92}\E{12}\,\Lsun and a
-dust mass of 22\petm{5}{18}\E{8}\,\Msun, uncorrected for lensing.
+3.81\petm{1.92}{1.97}\E{12}\,\Lsun, and a
+dust mass of 16\petm{5}{12}\E{8}\,\Msun, none of which are corrected for lensing magnification.
 For the mass absorption coefficient, we adopt
@@
 for this model, we find a total IR luminosity
-\LIR (rest-frame 8\,$-$\,1000\,\micron) of 9.71\petm{6.14}{-6.05}\E{12}\,\Lsun,
-a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
-dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun, all of which are uncorrected for lensing.
+\LIR (rest-frame 8\,$-$\,1000\,\micron) of 8.67\petm{5.27}{5.27}\E{12}\,\Lsun,
+a \fir luminosity \LFIR of 4.24\petm{2.17}{2.00}\E{12}\,\Lsun and a
+dust mass $M_{\rm dust}$ of 14\petm{5}{7}\E{8}\,\Msun, all of which are not lensing-corrected.
 Taken at face value, this implies an FIR-to-IR luminosity ratio
-of $\sim$58\pmm35\%.
+of $\sim$49\pmm38\%.
 
@@
 The choice of SED model does not affect
-the derived star formation rate (SFR) given the similar \fir luminosity.
-Yet, the dust mass is higher by a factor of $\sim$2 in the former but consistent within the
-uncertainties.
+the derived star formation rate (SFR) given the similar \fir luminosity, and
+their dust masses are consistent within the uncertainties.
 We correct for lensing using the median magnification
@@
 with (without) MIR constraint at 24\,$\micron$.
-The solid black line shows the best-fit SED model with dust attenuation (light blue solid line)
-obtained using the \ncode{magphys} code.
+The solid black line shows the best-fit SED model obtained using the \ncode{magphys} code.
+The light blue solid line shows the unattenuated stellar emission.
 \label{fig:SED}}
@@
 \section{Discussion} \label{sec:diss}
+\begin{deluxetable}{lcc}[!htbp]
+\tabletypesize{\scriptsize}
+\tablecolumns{3}
+\tablecaption{Physical properties of RXJ1131 and its companion}
+\tablehead{
+\colhead{Parameter} &
+\colhead{Unit} &
+\colhead{Value}
+}
+\startdata
+$r_{\rm 32}$                        &                & 0.78\pmm0.37\\ [0.5ex]
+FWHM$_{\rm CO(2-1), RXJ1131}$\tna   & \kms           & 220\pmm72 \\ [0.5ex]
+FWHM$_{\rm CO(2-1), RXJ1131}$\tnb   & \kms           & 600\pmm160 \\ [0.5ex]
+FWHM$_{\rm CO(2-1), companion}$\tnb & \kms           & 73\pmm43 \\ [0.5ex]
+$M_{\rm gas,\ RXJ1131}$             & $10^{10}$\Msun & 1.38\pmm0.33\\[0.5ex]
+$M_{\rm gas,\ companion}$           & $10^{9}$\Msun  & 1.92\pmm0.09 \\ [0.5ex]
+$R_{\rm CO,\ RXJ1131}$              & kpc            & 6.2\pmm3.0\\ [0.5ex]
+$R_{\rm CO,\ companion}$            & kpc            & 4.2\pmm2.8 \\ [0.5ex]
+$M_{\rm dyn,\ RXJ1131}$             & $10^{10}$\Msun & 8.3\pmm1.9\tnc \\ [0.5ex]
+$M_{\rm dyn,\ companion}$           & $10^{9}$\Msun  & 3.5\pmm2.3\tnc \\[0.5ex]
+$f_{\rm gas}$                       & \%             & 18\pmm4\tnd    \\ [0.5ex]
+$f_{\rm mol}$                       & \%             & 34\pmm16 \\ [0.5ex]     % (1.38 + 0.192) / (1.38 + 0.192 + 3) +/- 0.34*(2*(0.33/1.38)**2+2*(0.09/1.92)**2+(1.0/3)**2)**.5
+$L_{\rm IR}$                        & $10^{12}$\Lsun & $\sim$1.5\\ [0.5ex]
+$L_{\rm FIR}$                       & $10^{11}$\Lsun & 6.9\pmm3.6\\ [0.5ex]
+SFR$_{\rm FIR}$                     & \Msun yr\pmOne & 120\pmm63\\ [0.5ex]
+$M_{\rm dust}$                      & $10^{8}$\Msun  & $\sim$3\\ [0.5ex] % 16/5.5
+GDR                                 &                & 54\pmm13 \\ [0.5ex]
+$\tau_{\rm depl}$                   & Myr            & 102\pmm25  \\ [0.5ex]
+$M_*$                               & $10^{10}$\Msun & 3.0\pmm1.0  \\ [0.5ex]
+$M_{\rm BH}$\tne                    & $10^7$\Msun    & $\sim$\,8 \\ [0.5ex]
+$M_{\rm BH}/M_{\rm bulge}$          & \%             & $>$0.27\petm{0.11}{0.08}
+\enddata
+\label{tab:prop}
+\tablecomments{All the parameters have been corrected for lensing magnification. The physical parameters are derived for RXJ1131 and the companion as a single system unless otherwise stated.}
+\tablenotetext{a}{From fitting a double Gaussian with a common FWHM to the de-lensed spectrum.}
+\tablenotetext{b}{From fitting a single Gaussian to the de-lensed spectrum.}
+\tablenotetext{c}{Excluding systematic uncertainties.}
+\tablenotetext{d}{Excluding uncertainties in the dynamical masses.}
+\tablenotetext{e}{\citet{Sluse12a}.}
+\end{deluxetable}
+
 \subsection{ISM Properties} \label{sec:properties}
@@
 
-\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio}
-
-We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq19\pmm5\%
-and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\eq32\petm{7}{12}\% for RXJ1131.
+\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio} \label{sec:frac}
+
+We find a dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\eq18\pmm4\%
+and a baryonic gas mass fraction of $f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\eq34\pmm16\% for the merger system (i.e., RXJ1131 and companion).
 Recent studies find that the baryonic gas fraction of starburst galaxies has decreased from $f_{\rm mol}$\ssim40\% to $\lesssim$10\% between $z$\ssim2 and $z$\ssim0 \citep[\citetalias{Solomon97a};][]{GS04a, Tacconi06a},
 and from $f_\textrm{mol}$\ssim50\% to $\sim$5\% between the same redshift range for
-normal ``star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
+``normal star-forming'' galaxies \citep{Geach11a, Saintonge11a, Tacconi13a}\footnote{These authors use the ``Galactic'' value of
 \alphaco\eq4.6\,\alphaU to compute the molecular gas mass.}.
-Both the dynamical and baryonic gas mass fractions of RXJ1131 are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2
+Both the dynamical and baryonic gas mass fractions of RXJ1131+companion are thus consistent with the trend of decreasing molecular gas content since $z$\ssim2
 which has been suggested as the cause for the decline in sSFR and cosmic \SF history towards $z$\ssim0 \citep[e.g.,][]{Tacconi13a,CW13,Genzel15a}.
@@
 gas-to-dust ratio (GDR) of
-40\pmm34.
+54\pmm13.
 This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
@@
 On the other hand, we would also obtain a higher gas mass if
-we assumed sub-thermal excitation between \bco and \aco emission.
+we were to assume sub-thermal excitation between \bco and \aco emission.
 We also note that the gas-to-dust ratio derived for RXJ1131 may be biased low as the gas is likely to
@@
 the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
-Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
+Given that RXJ1131 shares similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
 the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
@@
 
-\subsection{Fate of RXS J1131$-$1231}
-Given that the host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger
-system, the removal of angular momentum of the gas via gravitational torque is likely inefficient to convert the
+The host galaxy of RXJ1131 is an extended disk with low star formation efficiency in a minor merger
+system. Therefore, removal of angular momentum of the gas via gravitational torque is likely inefficient to convert the
 entire gas disk into a massive stellar bulge.
-Hence, the disk component may be retained upon merging with the companion.
+In this case, the disk component may be retained upon merging with the companion.
 This scenario is consistent with the results from recent simulations, which suggest that bulge formation maybe
@@
 
-\subsection{Velocity Offset and a Recoiling Black Hole}
+\subsection{Systemic Redshift and Velocity Offset}
 
 \citet[]{Sluse07a} report two sets of AGN lines observed in RXJ1131.
-The first set of lines is at $z$\ssim0.653, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at $z$\ssim0.658, including the broad component of the Balmer lines and
-the \mgii emission line.
+The first set of lines is at $z$\ssim0.654, including the narrow component of the Balmer lines, the \oiii lines, and the \mgii absorption line; the second set is at
+$z_{\rm s, QSO}$\ssim0.658, including the broad component of the Balmer lines and the \mgii emission line.
 Using the CO line center redshift as the systemic redshift,
-we find that the redshift of the first set is fully consistent with the systematic redshift. This
-supports previous claims that [O\,{\scriptsize III}] lines, tracing the narrow line region (NLR),
+we find that the redshift of the first set is fully consistent with the systemic redshift. This
+supports previous claims that [O{\scriptsize III}] lines, tracing the narrow line region (NLR),
 are good proxies
 to the true systemic redshift \citep[e.g.,][]{Vrtilek85a, Nelson00a}.
-On the other hand, the second set of lines is blueshifted by $\sim$780\,\kms, indicating that the broad line region (BLR) of the AGN is dynamically offset from the centroid of its host galaxy.
-
-One explanation for the offset may arise from the fact that BLRs are gravitationally bound to
-the central AGN, whereas this condition is not necessary for NLRs.
-From an SDSS sample of $>$3800 quasars, \citet{Richards02a} find a
-median of 97\kms and a dispersion of 269\,\kms in the distribution of
-the offset between [Mg\,{\scriptsize II}] and [O\,{\scriptsize III}] lines, suggesting
-that large offsets are uncommon. Nevertheless,
-offsets as large as $\sim$\,500\,\kms have been observed in some cases.
-
-Alternatively, large velocity offsets between emission lines of the
-BLR and the NLR may arise in a recoiling black hole (BH),
-where its BLR is moving at high velocity relative to the bulk of its host galaxy
+On the other hand, the second set of lines is redshifted by $\sim$715\,\kms.
+
+Velocity offsets between broad line region (BLR) and NLR lines have been reported in literature.
+\citet{Richards02a} find a median offset of
+$\sim$100\pmm270\,\kms
+between [Mg{\scriptsize II}] and [O{\scriptsize III}] lines in a
+sample of $>$3800 quasars,
+and \citet{Bonning07a} report
+a mean offset of
+$\sim$100\pmm210\,\kms
+between the broad component of
+H$\beta$ and [O{\scriptsize III}] lines in a sample of $\sim$2600 quasars at 0.1$<$$z$$<$0.8,
+where only $\lesssim$20 of them (i.e., $<$1\%) are found to have offsets $>$800\,\kms
+and $\sim$1\%
+are found to have offsets $>$500\,\kms \footnote{\citet{Bonning07a} report the fraction of objects with offset velocities greater
+than 500, 800, 1000, 1500, 2000, and 2500\,\kms. We therefore quote the two fractions corresponding to
+offset velocities closest
+to that of RXJ1131 ($\sim$715\,\kms) in this discussion.}
+Thus, large velocity offsets between BLR and NLR lines
+comparable to that of RXJ1131 are uncommon but have been observed in some cases.
+
+The observed velocity offset between the BLR and NLR lines may be explained by
+a recoiling black hole (BH),
+where the BLR is moving at high velocity relative to the bulk of its host galaxy
 \citep{Madau04a, Bonning07a, Loeb07a}.
-A recoiling black hole is expected
-when a pair of uneven mass BH coalesce, during which their orbital energy is being released
-as gravitational wave and a
-non-zero net angular momentum is being carried away.
-Depending on their initial conditions, numerical relativity simulations have shown that
-the recoil velocity can reach up to $\sim$4000\,\kms for spinning BHs \citep[\eg][]{Campanelli07a}.
-Several sources have been proposed as recoiling BH candidates, such as CID-42 at $z$\,=\,0.359 \citep{Civano10a} and
-SDSS 0956+5127 at $z$\,$\sim$\,0.714 \citep{Steinhardt12a}.
-One notable system is SDSSJ0927+2943 at $z$\,$\sim$\,0.713, where
-a set of redshifted narrow lines and a second set of blueshifted broad AGN lines
-have been observed \citep{Komossa08a},  similar to the case for RXJ1131.
-However, this scenario was recently refuted by \citet{Decarli14a}, who confirm that the
-BLR lines in SDSSJ0927+2943 are consistent with the CO systemic redshift.
-This is in contrast with RXJ1131, where our CO observations confirm the blueshifted BLR.
-Since this model requires a merged BH, it would imply that RXJ1131 might
-have been in a previous merger, which would also explain
-the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
+Depending on the initial conditions of the black hole pair (e.g., black hole mass ratio, spin-orbit orientation, spin magnitude),
+numerical relativity simulations have shown that recoil velocities can reach up to
+$v_{\rm kick}$\ssim4000\,\kms for spinning BHs,
+with typical recoil velocities of $v_{\rm kick}$\ssim100\,$-$\,500\,\kms
+\citep[\eg][]{Libeskind06a,Campanelli07a}.
+Several sources have been proposed as recoiling BH candidates \citep[][]{Komossa08a, Civano10a, Steinhardt12a}.
+However, \citet{Decarli14a} have recently refuted
+such scenario for one of the candidates --- SDSS J0927+2943 --- by finding that the redshift of its
+BLR lines is indeed consistent with its CO systemic redshift.
+This is in contrast with RXJ1131, where our CO observations confirm
+the redshifted BLR lines compared to the CO systemic redshift.
+Since this scenario requires a coalesced BH, it would imply that RXJ1131
+is a product of a previous merger, which is not implausible and
+might also explain the highly spinning BH in RX1131 \citep[$a$\ssim0.9;][]{Reis14a}.
+
+Alternative scenarios
+e.g., outflow/inflow of gas in the BLR, viewing angle towards the accretion disk, and
+obscuration in the clumpy accretion disk
+are more commonly invoked to explain velocity offsets between BLR and systemic redshift.
+Since the BLR lines of RXJ1131 show positive velocity offsets with respect to its systemic redshift, it may imply that
+the observed
+BLR line emission is dominated by the gas that is flowing into the central BH, or by the receding component of
+the accretion disk, owing to the viewing angle or the obscuration in the accretion disk.
+\citet{Sluse07a} report a covering factor of 20\% for the accretion disk in RXJ1131
+based on its broad \mgii absorption line at $z$\eq0.654.
+Additionally, the centroids of the BLR lines in RXJ1131 may be biased towards longer wavelengths due to
+microlensing \citep[\eg][]{Sluse07a, Sluse12a}, which may have
+magnified the redshifted component of the compact BLR more strongly than its blueshifted component.
 
 \subsection{The $M_{\rm BH}$$-$\mbulge Relation}
-We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\%
+We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\%
 using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
@@
 resolved CO study at intermediate redshift.
-Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.66\,\pm\,0.41$
+Using the CO line intensities, we find a brightness temperature ratio of $r_{32}$\eq$0.78\,\pm\,0.37$
 between the \bco and \cco lines,
@@
 This together with a symmetric source-plane velocity gradient argues for a rotating disk in RXJ1131, in good agreement with previous findings \citepalias{Claeskens06a}.
-We find a lensing-corrected gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
+Physical quantities derived for RXJ1131 and the companion throughout this paper are summarized in \Tab{prop}.
+
+Based on the lensing-corrected \bco line intensities,
+we find an intrinsic gas mass of $M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun
 for RXJ1131
@@
 Using the source-plane \bco size of $R$\ssim6\,kpc, we find a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun for RXJ1131.
-The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim19\% and baryonic gas mass fraction of
-$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M^*$)\ssim32\% are consistent with the trend of decreasing molecular gas
+The dynamical gas mass fraction of $f_{\rm gas}$\eq$M_{\rm gas}$/$M_{\rm dyn}$\ssim18\% and baryonic gas mass fraction of
+$f_\textrm{mol}$\eq$M_{\rm gas}$/($M_{\rm gas} + M_*$)\ssim34\% are consistent with the trend of decreasing molecular gas
 content since $z$\ssim2 \citep[e.g.,][;\citetalias{Combes13a}]{Lagos11a,Tacconi13a}
@@
 that the \SF in RXJ1131 could form a
-larger stellar bulge in the merger remnant upon coalescing.
-
-Using the CO redshift as the systemic redshift for the host galaxy of RXJ1131, we find
-that the redshift inferred from the NLR lines reported in previous studies are consistent with this systemic redshift
-but the optical BLR lines are blueshifted by $\sim$780\,\kms.
-This implies that the AGN is offset from the dynamical center of its host galaxy.
-One explanation could be that the
-BLRs are gravitationally bound to the central AGN, whereas this condition is not necessary for NLRs.
-Since the velocity offset between emission lines of the BLR and the NLR
-is typically $\sim$100\pmm270\,\kms,
-we thus raise an alternative explanation of a recoiling black hole in RXJ1131, which
-would also explain the high spin parameter reported by \citet{Reis14a}.
-
-Adopting the stellar mass as an upper limit to the bulge mass, we find a
-$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{11}{8}\% for RXJ1131, providing
-a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
-The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio compared to the local relation suggests that the
-black hole in RXJ1131 has grown faster or earlier than its host galaxy than nearby AGN host galaxies,
-consistent with the results from existing studies of the evolution in the growth of SMBHs and their host galaxies
-\citep[e.g.,][]{Walter04a, Peng06a,McLure06a}.
-The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
+larger stellar bulge in the remnant disk galaxy upon coalescing.
+This picture is in agreement with the one based on the \mbox{$M_{\rm BH}$$-$$M_{\rm bulge}$} relation,
+where we find an elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of $>$0.27\petm{0.11}{0.08}\% for
+RXJ1131 compared to the local value.
+This suggests that the stellar bulge of RXJ1131 is still assembling in order to evolve onto the local relation.
+
+We find that the redshift inferred from the NLR lines reported in previous studies are consistent with the  systemic redshift as measured
+from the CO line,
+but that the BLR lines are redshifted by $\sim$715\,\kms.
+We raise several plausible scenarios that may explain the observed velocity offset, \eg
+outflow/inflow of gas in the BLR, kinematics of the accretion disk, geometric effects,
+microlensing, and a recoiling black hole from merger event.
+The latter scenario might also explain the high black hole spin parameter of
+$a$\eq0.87\petm{0.08}{0.15} reported by \citet[][]{Reis14a}, but
+further evidence is needed to confirm or rule out this scenario.
+
+Theoretical studies have suggested that negative feedback from an AGN may remove a
+large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
+In this study, we find that the star formation efficiency and specific SFR of RXJ1131 are comparable to those of
+$z$\ssim1$-$1.5 disk galaxies, which are not known to host quasars, and that its
+molecular gas mass fraction is consistent with the observed cosmic decline for star-forming
+galaxies since $z$\ssim2$-$3.
+Hence, we find no evidence of negative AGN feedback on the cold molecular gas fraction
+and on the star formation activity in RXJ1131.
+Future observations at higher resolution will allow us to better constrain the molecular gas kinematics and dynamics of
+RXJ1131 to investigate any potential interplay with the quasar on smaller scales.
+More broadly, systematic studies of the correlations between the molecular gas fraction, stellar mass, and AGN luminosity
+at different redshifts
+will enable us to better understand the relative importance of AGN feedback and of the
+evolution in the molecular gas mass fraction on the decline of star formation history and black hole accretion history.
 
@@
 
+We thank the referee for providing detailed and constructive comments that helped to improve the clarity of this manuscript.
 DR and RP acknowledge support from the National Science Foundation

### 2017-01-21 WRITEUP/ms_arxiv/ms.tex
arvix version (lossy figures), work with ArXIV

--- 2017-01-21 WRITEUP/ms_apj/ms.tex
@@
 \documentclass[]{emulateapj}
-\usepackage{amsmath}
-
-\usepackage[normalem]{ulem}
-\usepackage[usenames]{xcolor}
-\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
-\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
-\newcommand{\new}[1]{\textcolor{red}{\bf #1}}
-\newcommand{\old}[1]{\sout{\textcolor{airforceblue}{\bf #1}}}
-
-\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=blue]{hyperref}
+ \usepackage[colorlinks,citecolor=blue,linkcolor=blue]{hyperref}
 \usepackage{etoolbox}
@@
 \usepackage{apjfonts}
-\usepackage{amssymb, amsmath} % for e.g. \lesssim
+\usepackage{amssymb, amsmath}
 \usepackage{natbibspacing, natbib}
-\usepackage{aas_macros} % for understanding Journal in bib
-\usepackage{graphics,graphicx}
+\usepackage{aas_macros}
+%\usepackage{graphics,graphicx}
 %
@@
 
-\citestyle{aa}
 \shorttitle{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXJ1131$-$1231}
@@
 We thus conservatively estimate
-a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35
+a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,
 the gain variations over time, and the phase scatter on the calibrated data. We
@@
 \centering
-\includegraphics[width=0.45\textwidth]{f1.eps}
+\includegraphics[width=0.45\textwidth]{f1.pdf}
 \caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
@@
 \hspace{0.5em}
-\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{f2a.eps}
-\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{f2b.eps}
+\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{f2a.pdf}
+\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{f2b.pdf}
 \\
-\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{f2c.eps}
+\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{f2c.pdf}
 \vspace{0.1em}
@@
 \begin{figure}[!htbp]
-\includegraphics[width=0.455\textwidth]{f3.eps}
+\includegraphics[width=0.455\textwidth]{f3.pdf}
 \caption{CARMA \cco line profile (solid) without continuum subtraction is
@@
 \begin{figure}[!htbp]
-\includegraphics[trim=12 27 0 1, clip, width=0.47\textwidth]{f4a.eps}
-\includegraphics[trim=10 5 0 0, clip, width=0.47\textwidth]{f4b.eps}
+\includegraphics[trim=12 27 0 1, clip, width=0.47\textwidth]{f4a.pdf}
+\includegraphics[trim=10 5 0 0, clip, width=0.47\textwidth]{f4b.pdf}
 \caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
@@
 \begin{figure}[!htbp]
-\includegraphics[width=0.45\textwidth]{f5.eps}
+\includegraphics[width=0.45\textwidth]{f5.pdf}
 \caption{Top: the full resolution \bco spectrum (yellow histogram) and
@@
 \begin{tabular}{c}
-\includegraphics[trim=0 0 0 0, clip, width=1.0\textwidth]{f6a.eps} \\
-\includegraphics[width=0.98\textwidth]{f6b.eps}
+\includegraphics[trim=0 0 0 0, clip, width=1.0\textwidth]{f6a.pdf} \\
+\includegraphics[width=0.98\textwidth]{f6b.pdf}
 \end{tabular}
@@
 \centering
-\includegraphics[width=1.0\textwidth]{f7.eps}
+\includegraphics[width=1.0\textwidth]{f7.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=0.9\textwidth]{f8.eps}
+\includegraphics[width=0.9\textwidth]{f8.pdf}
 \caption{
@@
 \tablehead{
-\colhead{Velocity Range (\kms)} & % see 02July16/velo_res_obs.txt (2nd column), which corresponds to rest-frame velocity at z=0.6541, taken from the central of each bin
+\colhead{Velocity Range (\kms)} &
 \colhead{Source 1 $\mu_{\rm L}$} &
@@
 \includegraphics[trim=0 0 30 0, clip, width=0.4\textwidth]{f9a.pdf}
-\includegraphics[width=0.525\textwidth]{f9b.eps}
+\includegraphics[width=0.525\textwidth]{f9b.pdf}
 \caption{Velocity gradient of the \bco emission observed in RXJ1131 and the de-lensed velocity gradient obtained from lens modeling.
@@
 $f_{\rm gas}$                       & \%             & 18\pmm4\tnd    \\ [0.5ex]
-$f_{\rm mol}$                       & \%             & 34\pmm16 \\ [0.5ex]     % (1.38 + 0.192) / (1.38 + 0.192 + 3) +/- 0.34*(2*(0.33/1.38)**2+2*(0.09/1.92)**2+(1.0/3)**2)**.5
+$f_{\rm mol}$                       & \%             & 34\pmm16 \\ [0.5ex]
 $L_{\rm IR}$                        & $10^{12}$\Lsun & $\sim$1.5\\ [0.5ex]
@@
 SFR$_{\rm FIR}$                     & \Msun yr\pmOne & 120\pmm63\\ [0.5ex]
-$M_{\rm dust}$                      & $10^{8}$\Msun  & $\sim$3\\ [0.5ex] % 16/5.5
+$M_{\rm dust}$                      & $10^{8}$\Msun  & $\sim$3\\ [0.5ex]
 GDR                                 &                & 54\pmm13 \\ [0.5ex]
@@
 
-\acknowledgments
-
+\begin{acknowledgments}
 We thank the referee for providing detailed and constructive comments that helped to improve the clarity of this manuscript.
@@
 Facilities: IRAM PdBI, CARMA, VLA, Herschel(SPIRE), WISE, IRAS, 2MASS, Spitzer(IRAC, MIPS), HST(ACS, NICMOS)
-
-\input{ms.bbl}
+\end{acknowledgments}
+
+\bibliographystyle{yahapj}
+\bibliography{RXJ}
 \end{document}

### 2017-01-25 WRITEUP/ms_arxiv/ms.tex
fingers messing around?\!
updated to Karl G Jansky

@@
 
-\subsection{VLA (Archival)}
+\subsection{Karl G. Jansky Very Large Array (Archival)}
 Our analysis also uses archival data of the 4.885\,GHz
 radio continuum obtained with the
-VLA (Program ID: AW741; PI: Wucknitz).
+Karl G. Jansky Very Large Array (VLA; Program ID: AW741; PI: Wucknitz).
 Observations were carried out on 2008 December 29 under excellent weather

### 2017-01-28 Radio/VLA_OH/VLA_proposal2017B.tex
superseeded by VLA_2.tex

% abstract:
% An exceptionally rare lensing configuration ?, providing a unique opportunity to explore the ISM conditions in this important but thus far unobservable(unexplored?unexploited?) regime of galaxy evolution. We propose to take advantage of the magnification of the lensed galaxy RXJ1131, a gas-rich merger with prodigious star formation rate of 120 \Msun yr\pmOne to search for OHM at intermediate-$z$, when the merger rate and ... . By combining this information with existing ?, we will ? These observations will ...

%% Suggested LaTeX template for the scientific justification
%% to be submitted as part of an NRAO observing proposal
%%
%% Version for GBT/VLA/VLBA/HSA dated 2013 July 23

\documentclass[letterpaper,11pt]{article}
\usepackage{graphics,graphicx}
\usepackage{cprotect}
\usepackage{subcaption}
\usepackage{amssymb, amsmath}
\usepackage{xspace}
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros}
\usepackage{wrapfig}
\usepackage{floatrow}
\usepackage{sidecap}
%% In the graphics and graphicx packages, Postscript and eps figures
%% can be included using the \includegraphics command. The graphics
%% package is part of standard LaTeX2e and provides a basic way of
%% including a figure. The graphicx package is not standard, but
%% extends the \includegraphics command to make it more user-friendly.
%% If graphicx is not available on your system please remove it from
%% the list of included packages above.

%% Syntax:
%% In the graphics package:
%%
%% \begin{figure}
%% \includegraphics[llx,lly][urx,ury]{file}
%% \end{figure}
%%
%% where ll denotes 'lower left' and ur 'upper right' and the x and y
%% values are the coordinates of the PostScript bounding box in
%% points. There are 72 points in an inch.
%%
%% In the graphicx package:
%%
%% \begin{figure}
%% \includegraphics[key=val,key=val,...]{file}
%% \end{figure}
%%
%% where some of the useful keys are: angle, width, height,
%% keepaspectratio (='true' or 'false') and scale. Bounding box values
%% can be given as [bb=llx lly urx ury].
%%
%% In either case you have to use LaTeX figure placement commands to
%% position the figure on the page; \includegraphics will not do
%% that. Both these commands also have other options that are listed
%% in the LaTeX manual (for the graphics package) and in ``The LaTeX
%% Graphics Companion'' (for the graphicx package).

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
\newcommand{\LOH}{$L_{\rm OH}$\xspace}
\newcommand{\rarr}{$\rightarrow$}
% \newcommand{\civ}{C{\scriptsize IV}}
% \newcommand{\heii}{He{\scriptsize II}}
\newcommand{\bco}{\mbox{CO(2-1)}\xspace}
\newcommand{\cco}{\mbox{CO(3-2)}\xspace}
\newcommand{\lohmax}{$L_{\rm OH}^{\rm max}$\xspace}
\newcommand{\lohpred}{$L_{\rm OH}^{\rm pred}$\xspace}
\newcommand{\lohlfir}{$L_{\rm OH}-L{\rm FIR}$\xspace}

% \newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}}
% \newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\kms}{km\,s$^{-1}$\xspace}
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
\newcommand{\Fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
%
\newcommand{\E}[1]{\mbox{$\times10^{#1}$}}
\newcommand{\eq}{\,=\,}
\newcommand{\ssim}{\,$\sim$\,}
\newcommand{\pmm}{\,$\pm$\,}
%
\newcommand{\SF}{star formation\xspace}
\newcommand{\highz}{high-$z$\space}
\newcommand{\athighz}{at high redshifts\xspace}
\newcommand{\atinterz}{at intermediate redshifts\xspace}
\newcommand{\SB}{starburst\xspace}
\newcommand{\bh}{black hole\xspace}
\newcommand{\hr}{high resolution\xspace}
\newcommand{\obs}{observations\xspace}
\newcommand{\stu}{studies\xspace}
\newcommand{\galpop}{galaxy populations\xspace}
\newcommand{\qsohosts}{quasar host galaxies\xspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

% compact bib
\citestyle{aa}
\bibliographystyle{apj_w_etal_3auth}
\usepackage{paralist}
\renewenvironment{thebibliography}[1]{%
%\section*{\refname}%
%  {\normalsize {\textbf{References:}}}
  \let\par\relax\let\newblock\relax%
  \inparaitem[{[}1{]}]}{\endinparaitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Page dimensions %%%%%
%%%%%  DO NOT CHANGE  %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\textwidth}{6.5in} \setlength{\textheight}{9in}
\setlength{\topmargin}{-0.0625in} \setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in} \setlength{\headheight}{0in}
\setlength{\headsep}{0in} \setlength{\hoffset}{0in}
\setlength{\voffset}{0in}
\setlength{\parskip}{0.5em}

% added by D. Leung
\setlength{\intextsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\textfloatsep}{10pt plus 1.0pt minus2.0pt}
\setlength{\floatsep}{10pt plus 1.0pt minus 2.0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Section heading format %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatletter
\renewcommand{\section}{\@startsection%
{section}{1}{0mm}{-0.4\baselineskip}%
{0.1\baselineskip}{\normalfont\fontsize{11}{11}\bfseries}}%
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Start of document %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{plain}
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Title of proposal %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\large{\bf{Probing OH Megamaser in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
\end{center}
\vspace{-.8em}
\textbf{Current understanding of OH megamasers and galaxy evolution} \\
% point
% - OHM <-> ULIRGs <-> mergers <-> gas rich 
% - conditions for OHM
\indent Almost all ($>$95\%) OH ``megamasers" (OHMs) known to date are associated with 
(ultra)-luminous infrared galaxies (U)LIRGs (\LIR$>10^{11}$\,\Lsun; see \citealt[]{Lo05a} for a review), 
which are undergoing extreme bursts of star formation triggered by merger events
\citep[e.g.,][]{Sanders96a, Hopkins06b}.
Theoretically, the intense IR radiation field and the large column of molecular gas 
found in (U)LIRGs/mergers
are the required conditions for generating OHMs \citep[e.g.][]{Baan89a}.
%Since the necessary excitation of OHMs can be provided by 
%IR pumping (for pop. inversion) with large molecular column density \citep{Baan89a}, where 
%the required radiation is believed to be coming from dust absorbing starlight from 
%SB that are thought to be merger-driven (and AGN), and the high density at center easily reached in mergers.
Thus, starburst galaxies (IR-luminous) and mergers appear to be the most probable galaxy populations for hosting OHMs.

% point:
% - using OHM to trace distant merger
% - future survey using number density of OHM to constraint galaxy evolution models / merger history
% - currently no new detections beyond z>0.3, despite great efforts over the last two decades
% - our source is cheap to do, reasonable to expect OHM, we are probing deeper than previous attempts
The scaling relation of $L_{\rm OH}$$\propto L_{\rm FIR}^{2}$ 
\citep[or  $L_{\rm OH}$$\propto L_{\rm FIR}^{1.2}$ with Malmquist bias correction; \Fig{model}a; ][hereafter DG02]{Baan89a, Darling02b_LF} 
suggests that the number density of OHM is expected to increase towards $z$\ssim3,
when (U)LIRGs/mergers are more common \citep[e.g.,][]{LeFloch05a, Magnelli09a}.
OHMs have therefore been proposed as one of the most promising avenues for tracing mergers beyond the nearby universe
and for constraining the merger history of galaxies 
independent of IR luminosity function (\citealt{Briggs98a}, DG02). 
These models predict%  based on the commonly observed \LFIR$>$1\E{12}\Lsun at $z$\,$\gtrsim$\,1
that we should be able to detect OHMs out to at least $z$\ssim3 with current facilities 
(e.g. the GBT; \Fig{model}b). Yet, 
the most distant OHM host galaxy known-to-date is at $z$\eq0.265, which was 
discovered over two decades ago \citep{Baan92a}.
In addition, the null detections and unexpectedly low detection rate 
reported in the latest OHM studies (over half a decade ago) 
by \citet{Ivison06a} in a $z$\ssim4 galaxy % with an IR luminosity of \LIR$\gtrsim$1\E{14}\Lsun, 
and by \citet{Willett12a} in a sample of (U)LIRGs at $z$\,$\lesssim$\,1.5 (7\% detection rate, \Fig{model}) --- % only detected 9/121 
suggest a potential redshift evolution in the \LOH-\LFIR relation, which may hint at a different 
OHM triggering mechanism at earlier epochs that reflects the different physical conditions between
low- and high-$z$ (U)LIRGs.
The null detections in these studies also indicate also suggests that the 
classical model for OH pumping (pumped radiatively) in megamasers may not be universal (i.e., not all OHMs are unsaturated).
% only a radiative pumping mechanism for OH megamasers based on weak, unsaturated gain has been considered \citep{Henkel90a,Randell95a}.
%In these papers it was assumed that the maser cloud amplifies 
% radio emission from a source lying behind the cloud. 
However, since a purely radiative pumping mechanism is possible only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$). 
Theoretically, at relatively high OH densities, collisional processes may predominate. 
In addition, at high densities saturated amplification can be important \citep{Field94a}.
Detecting OHM beyond $z$\eq0.265 is therefore crucial to 
enable a better understanding of OHM and to 
improve existing predictions used for planning future OHM surveys with upcoming facilities 
\citep[e.g., FAST, APERTIF/WSRT, ASKAP;][]{Zhang14b}.
Here we propose to observe OH 1667 MHz line emission in the 
gravitationally-lensed starbursting galaxy merger
RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.

\noindent \textbf{An ideal target --- a lensed gas-rich, starbursting merger at $z$\,$>$\,0.6}\\ 
\indent High-resolution imaging and spectroscopy in optical wavelength show that RXJ1131 is 
lensed by a foreground galaxy at $z$\ssim0.3 (\Fig{hst}; \citealt{Sluse03a}). 
By exploiting the effect of lensing magnification, 
our proposed detection experiment requires {\bf an on-source time of  % sigma scales as 1/root(t) --> t scales as 1/sigma^2
$\sim$30 times less} than otherwise needed to reach the same sensitivity. 
The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}; e.g.,][]{Claeskens06a, Sluse07a, Pooley07a, Reis14a, Leung17a}, 
making it one of the best-studied galaxies at $z$$>$0.5 and 
the only source at 0.2$<$$z$$<$1 with spatially-resolved imaging of the molecular gas distribution \citep{Leung17a}. 
The lensed nature of this target provides an excellent 
opportunity to study the innermost regions around a black hole at a cosmological distance.
In fact, X-ray studies constrained the X-ray emitting region a highly compact source of emission 
($\sim$20\,AU; constraining the optical and X-ray emitting region near the accretion disk down to pc-scale) \citep{Dai10a},
demonstrating the how much we already know about this target.
Features in the X-ray spectrum finds 
%  A fraction of this hard X-ray emission is reflected by cold gas in the accretion disk, producing an observed spectrum imprinted with the features of photoelectric absorption, fluorescent 6.4 keV Fe K$\alpha$ line emission, and a Compton backscattered reflection continuum that produces a bump in the spectrum above 10 keV (George & Fabian 1991).
 % The continuum is strongly absorbed at soft energies by a 
a neutral gas of column density $N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ near the accretion disk. % w.in the X-ray emitting region
The spectrum at lower energies is heavily absorbed by neutral gas with a hydrogen column density $N_{\rm H}$.
% Soft X-ray continuum suggest the presence of a substantial amount of gas.
Our best-fit spectral energy distribution (SED) model indicates
a strong apparent far-IR luminosity of \LFIR$>$4\E{12}\,\Lsun, which corresponds to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
These properties together with the evidence of recent star formation (as traced by rest-frame UV \obs),
the presence of a nearby companion at $\sim$2.4\,kpc away, and a large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}) 
are favourable for generating OHMs, suggesting RXJ1131 is an ideal candidate 
to search for OHM beyond the nearby universe.

In addition, the redshift of RXJ1131 has been spectroscopically confirmed with CO lines down to a precision of 
$\Delta z$\eq0.0002, indicating that the proposed OH line is redshifted to a fortuitous region 
free of RFI at the low-end of the L-band. 
This together with the high fringe rate of the B-array configuration will 
reach a sensitivity deeper than previous high-$z$ OHM searches beyond $z$$>$0.4, which were carried out 
with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.

%--- added
% what can OHM help us understand the physical conditions of high-z galaxies. 
% what can't we learn from local OHM but can at high-z.
% difference between local and high-z; why care about doing OHM at high-z
The number density of IR-luminous galaxies and their molecular gas fractions and SFRs
are higher towards $z$\ssim2,
indicating a different physical conditions between low- and high-$z$ galaxies.
Such a different physical conditions can potentially be reflected in the OHM phenomenon, given that OHM are more strongly amplified in 
large column of molecular gas and the more intense IR radiation field.
Given that OHMs originate from central region, detecting OHM in high-$z$ galaxies and comparing them against those in the local, which are 
relatively more quiescent, would allow us to directly probe the physical conditions (and dynamics) in the inner few hundred pc
as galaxies evolve. {\bf justify the masing, pumping mechanism in science goals}
% foreground amplification of background radio continuum, this quadratic relationship may be expected, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud
In fact, the null detection of OHM in a $z$\ssim4 galaxy with \LIR$>$1\E{13}\,\Lsun already hints at a different 
excitation mechanism that may be a result of their different physical conditions (e.g. more dense, higher optical depth \citet{Ivision06a}).

% X-ray and LOH -- why RXJ1131
Because OHMs are associated with the most luminous galaxy in the nearby universe, it is reasonable to speculate a possible connection
between OHMs and quasars, where both are driven by mergers (increasing \LFIR, and molecular gas into central region) 
since recent high-$z$ studies find evidence that AGN activity and mergers are connected (growth of SMBHs may be partly driven by 
mergers) \citep{DiMatteo05a}.
pumping and density, saturated:
 A purely radiative pumping mechanism is possible only at relatively low densities
($n_{\rm OH}$\ssim10$^{-4}$ cm$^{-3}$). At relatively high OH densities, collisional processes may predominate. In addition, at high densities
saturated amplification can be important.
While in the nearby universe (z\ssim0), OHMs appear to be unsaturated. But this may not be the case at high-$z$, where
 the physical environment is very different, more violent star formation, the ISM is more turbulent, and when there are more gas 
 available on average.
Further \obs of OHM are needed to elucidate the role of collisional processes in 
producing population inversions over the observed radiative transitions of OH.
% while locally, not all OHM are AGN hosts, suggesting the FIR radiation from the SB is the dominant pumping source, but the non-detection based on local extrapolation and such maser model may suggest a different energy source/powering mechanism/ at higher-z, where quasars are more active, and may indicate that something about AGN/radio pumping? saturated amplification?

%-------

\noindent \textbf{Science goals} \\

\indent The proposed \obs will establish the first measurement of an OHM in a {\it bona-fide} high-$z$ merger, thereby
demonstrating the feasibility of using it as a tracer of distant galaxy mergers and
testing the long-envisaged hypothesis of using the number density of OHM to constrain 
the redshift evolution of merger rate. 
Such a
high-$z$ (non-)detection will also allow us to better constrain the \LOH-\LFIR scaling relation and its redshift evolution,
and thus improve 
% current models used to predict OHM detection rate 
predictions on the detection threshold needed  
% model predictions for designing 
% when designing
% future surveys to search for 
to carry out systematic searches of high-$z$ OHMs with upcoming facilities.  
% because if we find a shallower relation, then it would mean the surveys need to go deeper to reach the same \LOH.
Since our target is a merger, 
a null detection would also indicate that the notion of 
using the OHM number density to constrain the merger history needs to be revised before designing future OHM surveys.

% --  host properties ---
% to further understand the relationship between OHM and the types of galaxies hosting them at an earlier epoch.
In addition, regardless of whether the OH line emission is detected or not, the amount of data we have already acquired 
for this potential OHM host galaxy will allow us to compare its (host) galaxy properties 
(e.g., SFR or \LFIR, \LIR, \LOH, $L_{\rm radio}$, molecular and dust content)
against those of local OHM hosts to better understand 
% the nature of OHM.
% the pumping and masing mechanism of OHM. % the condition needed for generating OHM
% the required conditions for triggering OHM at an earlier epoch.
the relationship between the maser emission and the environment of its (host) galaxy. 
{\bf  Is there some
detailed prediction that they should be found in things above a
certain SFR or merger state or something? Any more details you can
provide there would be better. But 2-3 sentences about this would be good.
LFIR, LRadio.. LOH.. 
}
% --- to better understanding the pumping and masing mechanism --
To blah... saturated maser and collisional pumping. % saturated gain mechanism
% The T/density of the masing material? 
% Maybe you could do some of that with
% certain reasonable assumptions? Similarly 2-3 sentences would be good.
% 
Because of the required condition to excite and generate OHM, and because they originate from the central few pc to few hundred pc 
in the nuclear regions of galaxies \citep{Diamond99a},
OHM is a powerful diagnostics of the physical 
conditions in the innermost regions of galaxies. 
% foreground amplification of background radio continuum, this quadratic relationship may be expected, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud
Classical model of OHMs suggest that low-gain amplification (i.e., unsaturated gain) and IR pumping 
is the dominant mechanism for producing OHM. However, the null detections of OHM at $z$$>$0.3
\citep{Ivison06a, Willet12a} may suggest different pumping efficiency (\LOH/\LFIR) at high-z, due to the different physical conditions (e.g. 
optical depth is higher at high-z due to the higher LFIR). 
% 
% Since FIR radiation field can invert the OH population via the ``pumping lines'' at 35 and 53$\mu$m
% Masing can then be stimulated by 18 cm (i.e. $\sim$1.6GHz).
% With the additional constraint on the \LOH-\LFIR relation at $z$$>$0.3 provided by this experiment, we will 
% investigate the pumping efficiency at higher redshift than currently studies, %% but presumable can already do so with upper limits from Willett+12
% by comparing to local OHM hosts and as a function of \LFIR through the \LOH-\LFIR scaling relation. % (look for potential discrepancy in this relation based on nearby studies)% (already seen a discrepancy at z=3, see also Darling02b find evidence of a mixture of saturated and
% unsaturated masers). 
% For instance, a slope shallower than $<$2 %  (i.e, deviations from the quadrature) 
% would suggest that the amplification process is less efficient at higher FIR luminosity. %, where the optical depth is higher.
% Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
% (i.e., unsaturated masing) found to be consistent with local OHMs
% will likely break down resulting in deviations from the quadratic relation 
% implying the simple picture of low-gain amplification (i.e., unsaturated masing) 
% found to be consistent with local OHMs will likely break down
% and indicate saturated masing at high redshift.
% Darling02b: find evidence of a mixture of saturated and unsaturated masers. 
% 
A non-detection would therefore still be meaningful in advancing our knowledge.

% --- procedure
%Existing lens modeling of RXJ1131 have been carried out from rest-frame X-ray through submm, indicating BLAH component is strongly-lensed by a factor of $\mu$\ssim10. 
%Since the OHM is expected to originate from the few hundred pc from the central quasar \citep[e.g.][]{Darling07a}, thus 
%we will correct for lensing using the magnification factor based on X-ray, MIR lens model \citep{}.

With the aid of lensing and the rich multi-wavelength data 
% probing a wide range of properties 
available for this potential OHM host, RXJ1131 is an exceptional target
for obtaining a better understanding of OHM in IR-luminous galaxies beyond the nearby universe out to
a lookback time of $\sim$6 Gyr.
% The detection of a OHM at redshift higher than already known 
% may also open up/demonstrate the possibility of use OHM as a tool for studying the 
% properties (dynamics) of the molecular nuclei at high redshifts when observed at high resolution with the VLBI.
In the case of a detection, we will future carry out follow-up \obs % at higher-resolution 
with the VLBI to study the physical conditions of the nuclear molecular torus
% and to better understand the energy source and the nature of OHM at high redshift.
% ($<$ few hundred pc) 
responsible for the OH line emission, where the velocity structure of the 
currently highest-$z$ OHM already suggests a different dynamic structure 
than those at lower-$z$ \citep{Baan92a}. % . e..g IRAS F14070+0525 has a total line width of ~2400 km/s 
% OHM may be useful for studying dynamical and molecular properties of nuclei at high-z. <-- well, but APM is not detected.. so OHM may not be so reliable.
The proposed investigation will therefore serve as an
important benchmark for future studies of high-$z$ OHM out to earlier epochs,
when extremely IR-luminous sources are much more common.
%  inform future systematic searches of high-$z$ OHMs 
% Thus, a detection/non-detection at this redshift is crucial for development of this technique for future OHM studies.

%\noindent \textbf{Technical Justification}
%We estimate the required sensitivity based on the \LFIR of 4\E{12}\,\Lsun found for RXJ1131 
%together with the \LOH$\propto$\LFIR$^{1.2}$ relation reported by (DG02), and 
%the typical FWHM line width of $\sim$600\,\kms of the highest-$z$ sources ($z$$>$0.2; DG02).
%These yield a line intensity of 330 mJy\,\kms, and a peak flux density of $S_\nu$\eq0.55\,mJy.
%To secure a 5$\sigma$ detection, we therefore require $\sigma$\eq0.11\,mJy beam\pmOne over the line FWHM. 
%Since extragalactic OHMs originate from the central few hundred pc, we expect the emission to 
%remain spatially-unresolved at the B-array configuration.
%We thus require an on-source time of 4.3 hours (total time of 5.5 hours).
%% \vspace{-0.25em}

%% ------------------------------------------------------------
%% REFERENCES
%% ------------------------------------------------------------
\noindent \textbf{References}
{\fontsize{10pt}{12pt}\selectfont
    \bibliography{master_cleanup}
}
% \vspace{-1.25em}

\begin{figure}[ptbh]
\includegraphics[trim=10 305 270 0, clip, scale=0.825]{Fig/OHFIR} \hspace{-1.25em}
% \includegraphics[trim=0 400 200 0, clip, scale=0.85]{Fig/Darling02b_distribution}
%  \includegraphics[trim=0 0 0 0, clip, scale=0.625]{Fig/Willett11_distribution}\\ \vspace{1.5em}
% \includegraphics[trim=0 0 0 0, clip, scale=0.42]{Fig/Darling02_predictionf4}
\includegraphics[trim=0 -20 155 0, clip, scale=0.41]{Fig/willett12_fig1_mod.pdf}
\caption{{\bf \LOH-\LFIR correlation and existing OHMs measurements}
{\it Left}: The super-linear correlation found between \LOH and \LFIR in local studies indicates
the connection between OHM generation and IR radiation field,
and thus suggests that OHM is a powerful tool for tracing distant mergers (bright IR emitters)
and constraining the cosmic merger history (DG02).
{\it Right}: 
The highest-$z$ OHM known to date (at $z$\eq0.265) was 
detected over two decades ago \citep{Baan92a}.
3$\sigma$ sensitivity predicted to be necessary for OHM detection at different $z$, 
derived based on existing OHM detections (i.e., assuming some $\Delta v$). 
Subsequent OHM \obs yielded very low detection rate ($\sim$7\%;  black and green) \citep[figure modified from][]{Willett12a}. 
The lower than expected detection rate indicates that current prediction based on local measurements need to be revised, or that the previous 
high-z OHM survey are not sensitive enough, or that the assumption of $\Delta v$ is too small (the $z$$>$0.2 sources have wider FWHM by at least a factor of 2). 
Our proposed \obs will push beyond these sensitivity to $5\sigma$\eq0.55 mJy...
 (since RFI is better in interferometer, because higher fringe rate, increase baselines so that RFIs are decorrelated via geometric delay.)
{\bf also can reach to lower rms than previous study which are affected by RFIs.}
Here we propose to observe OH 1667 MHz line emission in the gravitationally-lensed starbursting 
galaxy merger RXJ1131 at $z$\eq0.65. 
In contrast to the \citet{Willett12a} sample, which does not include any active galactic nucleus (AGN) host 
galaxies, 
our target hosts an optically bright AGN, and thus may offer an alternate view to high-$z$ OHM hosts. 
The proposed \obs will better constrain the \LOH-\LFIR scaling relation and its redshift evolution, and thus 
improve % current models used to predict OHM detection rate 
model predictions for designing 
future surveys to search for high-$z$ OHMs with upcoming facilities.
{\bf look for discrepancy in \LOH-\LFIR between low and high-$z$ mergers/potential OHM hosts, which
 would indicate different OH excitation mechanism.} % foreground amplification of background radio continuum, this quadratic relationship may be expected, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud
The proposed sensitivity together with the aid of lensing magnification 
allow us to probe deeper than previous OHM high-z searches, and to fainter intrinsic \LOH beyond $z$$\gtrsim$0.2.
\label{fig:model}}
\end{figure}

\begin{figure}[ptbh]
% \hspace{-1.6em}
\includegraphics[trim=0 0 50 0, clip, scale=.275]{Fig/Manipulate_figs} 
\includegraphics[scale=.3]{Fig/F555WCO21_mom0_single_invertedgray}
\includegraphics[scale=0.23]{Fig/SpecCO21}
\includegraphics[scale=.2]{Fig/F555W_ContVLA}
\includegraphics[trim=0 0 0 30, clip, scale=0.36]{Fig/SED_mani} \vspace{-0.25em}
\caption{
{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\,$>$\,0.6 with a well-sampled spectral energy distribution (SED) spanning rest-frame UV to radio.} 
{\em Top left:} Source-plane reconstruction of {\it HST} images shows the
emission from recent star-formation in this AGN host galaxy and
the presence of a nearby companion (\citealt{Claeskens06a}).
{\em Top right:} 
CO line emission overlaid on an {\it HST} image, which shows BLAH BLAH
that RXJ1131 is lensed into an Einstein ring of diameter $\sim$3.6".
{\em Middle left:}
Our recent study finds a large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 and 
confirmed the presence of its companion, with a gas mass ratio of 7:1 \citep{Leung17a}. 
{\em Middle right:}
We have previously detected radio continuum emission at 5\,GHz towards this target.
The proposed \obs will provide an additional constraint on the radio continuum at 1\,GHz.
{\em Bottom:} Our best-fit model to the well-sampled SED 
indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
The large molecular gas reservoir, on-going star formation, and the high \LFIR together
are favourable for generating OHM, and thus RXJ1131 is an
ideal candidate for high-$z$ OHM search.
The proposed \obs together with our existing data acquired for this target will allow us to 
compare its (host) properties against those of local OHM hosts to better understand 
the physical environment that triggers OHM out to a look-back time of 6 Gyr.
\label{fig:hst}}
\end{figure}

\end{document}

### 2017-01-28 Radio/VLA_OH/VLA_2.tex
text in there, need to finish captions

% abstract:
% An exceptionally rare lensing configuration ?, providing a unique opportunity to explore the ISM conditions in this important but thus far unobservable(unexplored?unexploited?) regime of galaxy evolution. We propose to take advantage of the magnification of the lensed galaxy RXJ1131, a gas-rich merger with prodigious star formation rate of 120 \Msun yr\pmOne to search for OHM at intermediate-$z$, when the merger rate and ... . By combining this information with existing ?, we will ? These observations will ...
% inform future systematic searches of high-$z$ OHMs 
% OH maser emission at 1.67 GHz is known to be associated with regions of intense star formation within ULIRGs. As these galaxies are formed through violent mergers, studying the co-moving density of OH maser galaxies across cosmic time will allow the merger rate of the Universe to be determined in an independent way. This merger rate is an important parameter in galaxy formation and evolution scenarios.

%% Suggested LaTeX template for the scientific justification
%% to be submitted as part of an NRAO observing proposal
%%
%% Version for GBT/VLA/VLBA/HSA dated 2013 July 23

\documentclass[letterpaper,11pt]{article}
\usepackage{graphics,graphicx}
\usepackage{cprotect}
\usepackage{subcaption}
\usepackage{amssymb, amsmath}
\usepackage{xspace}
\usepackage{natbibspacing, natbib}
\usepackage{aas_macros}
\usepackage{wrapfig}
\usepackage{floatrow}
\usepackage{sidecap}
%% In the graphics and graphicx packages, Postscript and eps figures
%% can be included using the \includegraphics command. The graphics
%% package is part of standard LaTeX2e and provides a basic way of
%% including a figure. The graphicx package is not standard, but
%% extends the \includegraphics command to make it more user-friendly.
%% If graphicx is not available on your system please remove it from
%% the list of included packages above.

%% Syntax:
%% In the graphics package:
%%
%% \begin{figure}
%% \includegraphics[llx,lly][urx,ury]{file}
%% \end{figure}
%%
%% where ll denotes 'lower left' and ur 'upper right' and the x and y
%% values are the coordinates of the PostScript bounding box in
%% points. There are 72 points in an inch.
%%
%% In the graphicx package:
%%
%% \begin{figure}
%% \includegraphics[key=val,key=val,...]{file}
%% \end{figure}
%%
%% where some of the useful keys are: angle, width, height,
%% keepaspectratio (='true' or 'false') and scale. Bounding box values
%% can be given as [bb=llx lly urx ury].
%%
%% In either case you have to use LaTeX figure placement commands to
%% position the figure on the page; \includegraphics will not do
%% that. Both these commands also have other options that are listed
%% in the LaTeX manual (for the graphics package) and in ``The LaTeX
%% Graphics Companion'' (for the graphicx package).

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
\newcommand{\LOH}{$L_{\rm OH}$\xspace}
\newcommand{\rarr}{$\rightarrow$}
% \newcommand{\civ}{C{\scriptsize IV}}
% \newcommand{\heii}{He{\scriptsize II}}
\newcommand{\bco}{\mbox{CO(2-1)}\xspace}
\newcommand{\cco}{\mbox{CO(3-2)}\xspace}
\newcommand{\lohmax}{$L_{\rm OH}^{\rm max}$\xspace}
\newcommand{\lohpred}{$L_{\rm OH}^{\rm pred}$\xspace}
\newcommand{\lohlfir}{$L_{\rm OH}$-$L_{\rm FIR}$\xspace}

% \newcommand{\Lp}[1][CO]{\mbox{$L^{\prime}_\textrm{\fontsize{8pt}{12pt}\selectfont{#1}}$}}
% \newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\kms}{km\,s$^{-1}$\xspace}
\newcommand{\pmOne}{\mbox{$^{-1}$}\xspace}
\newcommand{\Fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Eq}[1]{Equation~\ref{eq:#1}}
%
\newcommand{\E}[1]{\mbox{$\times10^{#1}$}}
\newcommand{\eq}{\,=\,}
\newcommand{\ssim}{\,$\sim$\,}
\newcommand{\pmm}{\,$\pm$\,}
%
\newcommand{\SF}{star formation\xspace}
\newcommand{\highz}{high-$z$\space}
\newcommand{\athighz}{at high redshifts\xspace}
\newcommand{\atinterz}{at intermediate redshifts\xspace}
\newcommand{\SB}{starburst\xspace}
\newcommand{\bh}{black hole\xspace}
\newcommand{\hr}{high resolution\xspace}
\newcommand{\obs}{observations\xspace}
\newcommand{\stu}{studies\xspace}
\newcommand{\galpop}{galaxy populations\xspace}
\newcommand{\qsohosts}{quasar host galaxies\xspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

% compact bib
\citestyle{aa}
\bibliographystyle{apj_w_etal_3auth}
\usepackage{paralist}
\renewenvironment{thebibliography}[1]{%
%\section*{\refname}%
%  {\normalsize {\textbf{References:}}}
  \let\par\relax\let\newblock\relax%
  \inparaitem[{[}1{]}]}{\endinparaitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Page dimensions %%%%%
%%%%%  DO NOT CHANGE  %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\textwidth}{6.5in} \setlength{\textheight}{9in}
\setlength{\topmargin}{-0.0625in} \setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in} \setlength{\headheight}{0in}
\setlength{\headsep}{0in} \setlength{\hoffset}{0in}
\setlength{\voffset}{0in}
\setlength{\parskip}{0.5em}

% added by D. Leung
\setlength{\intextsep}{10pt plus 1.0pt minus 2.0pt}
\setlength{\textfloatsep}{10pt plus 1.0pt minus2.0pt}
\setlength{\floatsep}{10pt plus 1.0pt minus 2.0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Section heading format %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatletter
\renewcommand{\section}{\@startsection%
{section}{1}{0mm}{-0.4\baselineskip}%
{0.1\baselineskip}{\normalfont\fontsize{11}{11}\bfseries}}%
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Start of document %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{plain}
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Title of proposal %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\large{\bf{Probing OH Megamaser in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
\end{center}
\vspace{-.8em}
\textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
% Galaxy evolution and the history of galaxy mergers} 
Studying the properties of high-redshift ($z$) galaxies is crucial to understand the formation and evolution of present-day galaxies.
High-$z$ galaxies are IR-luminous due to their intense bursts 
of obscured star formation and/or their central active galactic nuclei (AGNs),
which are sustained by their massive molecular gas reservoirs ($M_{\rm gas}$$>$10$^{10}$\,\Msun; see \citet{CW13} for a review).
The gas-rich and starbursting nature of high-$z$ galaxies may be a result of galaxy mergers
\citep{Riechers11a, Hayward12a, Riechers13b}, 
consistent with the notion that galaxies grow through hierarchical merging \citep{White91a}.
%  merging in the hierarchical model of galaxy formation \citep{White91a}.
The merger rate is thus expected to increase towards higher redshift \citep[e.g.,][]{LeFloch05a, Magnelli09a}, and constraining 
its evolution allows us to track the origin and evolution of present-day populations. % emergence of current day populations.

\noindent The steep dependence between OH and FIR luminosities ($L_{\rm OH}^2\propto L_{\rm FIR}^2$; \Fig{model}a) 
found in local OH ``megamasers'' (OHMs;  see \citealt[]{Lo05a} for a review) and 
the ubiquity of strong IR-emitting galaxies found at high $z$ suggest that
the number density of OHM may improve current constraints on
the cosmic merger history \citep[hereafter DG02]{Darling02b_LF}.
Existing models predict that detections of  
OHMs out to at least $z$\ssim3 are possible with current facilities (e.g. the GBT; \Fig{model}b).
Yet, despite several attempts, 
the most distant OHM known-to-date was discovered over two decades ago, at $z$\eq0.265 \citep{Baan92a}.
The null detection in a $z$\ssim4 extremely IR-bright galaxy (\LIR$>10^{14}$\Lsun; \citealt{Ivison06a}) and 
the remarkably low detection rate (7\%) from a sample of $>$120 IR-luminous galaxies 
at $z$\,$\lesssim$\,1.5 ($L_{\rm IR}>10^{11}$\Lsun; \Fig{model}b; \citealt{Willett12a}) 
suggest a potential redshift evolution in the \LOH-\LFIR relation.
Detecting OHM beyond $z$\eq0.265 is therefore needed to enable a better understanding of the 
OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies,
and to improve existing predictions to plan for future OHM surveys with upcoming facilities 
\citep[e.g., FAST, APERTIF/WSRT, ASKAP;][]{Zhang14b}.
Here we propose to observe OH 1667 MHz line emission in the 
gravitationally-lensed starbursting galaxy merger
RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.

\noindent \textbf{An ideal target --- a lensed gas-rich, starbursting merger at $z$\,$>$\,0.6}\\
\noindent High-resolution imaging and spectroscopy in optical wavelength show that RXJ1131 is 
lensed by a foreground galaxy at $z$\ssim0.3 (\Fig{hst}; \citealt{Sluse03a}).
By exploiting the effect of lensing magnification, 
our proposed detection experiment requires {\bf an on-source time of  % sigma scales as 1/root(t) --> t scales as 1/sigma^2
$\sim$30 times less} than otherwise needed to reach the same sensitivity. 
The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}e; e.g.,][]{Claeskens06a, Sluse07a, Leung17a}, 
making it one of the best-studied galaxies at $z$$>$0.5 and 
the only source at 0.2$<$$z$$<$1 with spatially-resolved imaging of the molecular gas distribution \citep{Leung17a}. 
% X-ray studies  a highly compact source of emission 
% in the innermost region near the accretion disk down to pc-scale
% \citep[$\sim$20\,AU][]{Dai10a}.
Modeling of the X-ray spectrum reveals substantial amount of neutral gas with column density of
 % The continuum is strongly absorbed at soft energies by a 
$N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ in the innermost region near % the accretion disk % w.in the X-ray emitting region
% The spectrum at lower energies is heavily absorbed by neutral gas with a hydrogen column density $N_{\rm H}$.
% Soft X-ray continuum suggest the presence of a substantial amount of gas.
the $L_X$$\gtrsim$10$^{45}$\,\Lsun AGN \citep{Pooley07a, Reis14a}. 
Our best-fit spectral energy distribution (SED) model indicates
a strong apparent far-IR luminosity of \LFIR$\sim$5\E{12}\Lsun, which corresponds to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
The large column density together with the strong FIR radiation field % of $\sim$10$^{12}$\Lsun (lensing-corrected),
% recent star formation (as traced by rest-frame UV emission), 
% presence of a nearby companion, and % at $\sim$2.4\,kpc away, and 
and the large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}b, c) 
are favourable for generating OH masers, making RXJ1131 an ideal candidate 
to search for OHMs beyond the nearby universe. Assuming the Malmquist-bias corrected relation
($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}b).

\noindent In addition, the redshift of RXJ1131 has been spectroscopically confirmed with CO lines down to a precision of 
$\Delta z$\eq0.0002, indicating that the proposed OH line is redshifted to a fortuitous region 
free of RFI at the low-end of the L-band. 
Together with the high fringe rate of the B-array configuration, the proposed \obs will
reach a sensitivity deeper than previous high-$z$ OHM searches beyond $z$$>$0.4, which were carried out 
with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.

\noindent \textbf{Science goals}
\vspace{.2em}\\
\indent {\bf Testing OHM as a tracer of merger}
The proposed \obs will establish the first OHM measurement in a {\it bona-fide} high-$z$ merger, thereby
demonstrating the feasibility of using it as a tracer of distant mergers and 
testing the long-envisaged hypothesis of using its number density to constrain 
the redshift evolution of merger rate. 
Such a detection will also allow us to better constrain the
\LOH-\LFIR relation out to higher $z$, % which may provide a handle on the pumping efficiency (\LOH/\LFIR) 
% that may be closer to other high-$z$ galaxies if their physical conditions are more similar than compared to low-z (\LOH/\LFIR)
and thus improve predictions on the required sensitivity needed for future searches of high-$z$ OHMs.
Since our target is a merger, 
a null detection would also indicate that the notion of 
using the OHM number density to constrain the merger history requires revision before designing future OHM surveys.

%
% OHM help us understand the physical conditions of high-z galaxies: different circumnuclear environment, optical depth? - likely already know about the cirucmnuclear env part from X-ray, but then could be use for other high-z sources w/o detailed characterization?
{\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies}
% Classical model: foreground amplification of background radio continuum, expect quadratic relationship, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud.
Null detections in previous high-$z$ OHM searches suggest a shallower \LOH-\LFIR dependence, which may be
reflecting the different physical conditions of the inner few hundred pc (where OHMs are generated) 
between low- and high-$z$ IR-luminous galaxies.
The lower \LOH/\LFIR indicate that the OH amplification is less efficient at the same FIR luminosity 
and that collisional pumping (e.g. due to the strong AGN, and high gas mass and density; \citealt{Field94a}) % volume density 
% while locally, not all OHM are AGN hosts, suggesting the FIR radiation from the SB is the dominant pumping source, but the non-detection based on local extrapolation and such maser model may suggest a different energy source/powering mechanism at higher-z, where quasars are more active, and may indicate that something about AGN/radio pumping
%
% Since a purely radiative pumping mechanism is possible 
% only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$), and collisional processes can theoretically predominate at high OH densities, and saturated amplification can become important \citep{Field94a}.
may play a dominant role in these gas-rich \highz systems.
Obtaining a definitive OHM measurement in RXJ1131 will provide a handle on the OH pumping efficiency (\LOH/\LFIR) out to higher $z$.
This together with the detailed properties derived for our target (e.g., \LFIR, \LIR, SFR, $L_{\rm radio}$, molecular and dust content)
will elucidate the role of collisional over radiative pumping
that may be prevalent in \highz galaxies given their physical properties, which are more similar to RXJ1131 than 
local starbursts. % more violent star formation in a more gas-rich turbulent ISM.
	% [NOT applicable] Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
	% (i.e., unsaturated masing) found to be consistent with local OHMs...
	%
% % implying the simple picture of low-gain amplification (i.e., unsaturated masing, quadrature, low density)  \citep{Henkel90a,Randell95a} found to be consistent with local OHMs will likely break down; (i.e., not all OHMs are unsaturated). 
% While in the nearby universe (z\ssim0), OHMs appear to be unsaturated.

{\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies}
The much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$\eq0 already indicate 
different dynamical properties in the innermost regions of their hosts \citep{Baan92a,Darling02a}.
Detecting the OHM in RXJ1131 will therefore demonstrate the feasibility of 
using it as a trace of the kinematics in the circumnuclear regions of \highz galaxies, which will improve 
our understanding of the internal dynamics of IR-luminous, starbursting galaxies at high $z$.

{\bf Radio continuum}
In addition, the proposed \obs will provide an additional constraint on the radio continuum emission at 1\,GHz 
towards RXJ1131 (\Fig{hst}e).

% --- finally ----
\noindent 
With the aid of lensing and the rich multi-wavelength data available for this potential OHM host, RXJ1131 is an exceptional target
for high-$z$ OHM search. 
Detecting the OHM will provide a handle on the pumping efficiency (\LOH/\LFIR)
and enable a better understanding of the OHM triggering mechanism at $z$\ssim0.65, which 
would reflect the different physical conditions between low- and high-$z$ IR-luminous galaxies.
The detection will also demonstrate the utility of OHMs as tracers of distant mergers, and
of the kinematics in the inner few hundred pc 
of starburst galaxies beyond the nearby universe. %, out to a lookback time of $\sim$6 Gyr.
The proposed investigation will therefore serve as an
important benchmark for future studies of high-$z$ OHMs out to earlier epochs,
when extremely IR-luminous sources are much more common.

%% ------------------------------------------------------------
%% REFERENCES
%% ------------------------------------------------------------
\noindent \textbf{References}
{\fontsize{10pt}{12pt}\selectfont
    \bibliography{master_cleanup}
}
% \vspace{-1.25em}

\begin{figure}[ptbh]
\includegraphics[trim=10 305 270 0, clip, scale=0.825]{Fig/OHFIR} \hspace{-1.25em}
% \includegraphics[trim=0 400 200 0, clip, scale=0.85]{Fig/Darling02b_distribution}
%  \includegraphics[trim=0 0 0 0, clip, scale=0.625]{Fig/Willett11_distribution}\\ \vspace{1.5em}
% \includegraphics[trim=0 0 0 0, clip, scale=0.42]{Fig/Darling02_predictionf4}
\includegraphics[trim=0 -20 155 0, clip, scale=0.41]{Fig/willett12_fig1_mod.pdf}
\caption{{\bf \LOH-\LFIR correlation and existing OHMs measurements}
{\it (a):} Since the OH line strength increases with \LFIR,
the ubiquity of IR-luminous galaxies at high $z$ suggest that OHM can be used to trace distant mergers 
($L_{\rm IR}$$\gtrsim$10$^{12}$\Lsun; DG02).
{\it (b):} The highest-$z$ OHM known ($z$\eq0.265) was discovered over two decades ago. 
A remarkably low detection rate of $\sim$7\% was reported in subsequent surveys (black and green symbols), 
suggesting a potential redshift evolution in the \LOH/\LFIR relation
due to the different physical properties between low- and high-$z$ IR-luminous galaxies.
Assuming $L_{\rm OH}\propto L_{\rm FIR}^{1.2}$ (Malmquist-bias corrected; DG02), 
we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun in our target (orange marker). (Figure adopted from 
\citealt{Willett12a})
Here we propose to observe OH 1667 MHz line emission in the gravitationally-lensed starbursting 
galaxy merger RXJ1131 at $z$\eq0.65.
The proposed sensitivity will
probe deeper than existing OHM surveys, and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.2.
The proposed \obs will measure the \LOH/\LFIR 
and its redshift evolution, and thus improve model predictions for designing 
future surveys to search for high-$z$ OHMs with upcoming facilities. 
\label{fig:model}}
\end{figure}

\begin{figure}[ptbh]
% \hspace{-1.6em}
\centering
\includegraphics[trim=0 0 300 0, clip, scale=.75]{Fig/Fig2} 
\vspace{-0.25em}
\caption{
{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\,$>$\,0.6 with a well-sampled spectral energy distribution (SED) spanning rest-frame UV to radio.} 
{\em (a):} Source-plane reconstruction of {\it HST} images shows recent star formation in our target and
the presence of a nearby companion (\citealt{Claeskens06a}).
{\em (b):} 
CO line emission overlaid on an {\it HST} image, which shows BLAH BLAH
that RXJ1131 is lensed into an Einstein ring of diameter $\sim$3.6".
{\em (c):}
Our CO \obs reveal large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 and 
confirmed the presence of the nearby companion, with a gas mass ratio of 7:1 \citep{Leung17a}. 
{\em (d):}
Our VLA radio continuum image at 5\,GHz in this target. 
The proposed \obs will provide an additional constraint on the radio continuum at 1\,GHz.
{\em (e):} Our best-fit model to the well-sampled SED 
indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
The large molecular gas reservoir, on-going star formation, and the high \LFIR together
are favourable for generating OHM, and thus RXJ1131 is an
ideal candidate for high-$z$ OHM search.
The proposed \obs together with our existing data acquired for this target will allow us to 
compare its (host) properties against those of local OHM hosts to better understand 
the physical environment that triggers OHM out to a look-back time of 6 Gyr.
\label{fig:hst}}
\end{figure}

\end{document}

### 2017-01-28 Radio/VLA_OH/VLA_2.tex
added captions, send to DR

@@
 \vspace{.2em}\\
-\indent {\bf Testing OHM as a tracer of merger}
+$\bullet$ {\bf Testing OHM as a tracer of merger}
 The proposed \obs will establish the first OHM measurement in a {\it bona-fide} high-$z$ merger, thereby
@@
 - likely already know about the cirucmnuclear env part from X-ray, but then could be use for other high-z sources w/o detailed characterization?
-{\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies}
+\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies}
 % Classical model: foreground amplification of background radio continuum, expect quadratic relationship, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud.
@@
 
-{\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies}
+\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies}
 The much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$\eq0 already indicate 
@@
 
-{\bf Radio continuum}
+\noindent $\bullet$ {\bf Radio continuum}
 In addition, the proposed \obs will provide an additional constraint on the radio continuum emission at 1\,GHz 
@@
 probe deeper than existing OHM surveys, and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.2.
-The proposed \obs will measure the \LOH/\LFIR 
-and its redshift evolution, and thus improve model predictions for designing 
-future surveys to search for high-$z$ OHMs with upcoming facilities. 
+Detecting the OHM in RXJ1131 will provide the first measurement beyond $z$$>$0.265,
+which will improve predictions on the sensitivity needed for future high-$z$ OHM surveys with upcoming facilities.
 \label{fig:model}}
@@
 {\em (b):} 
-CO line emission overlaid on an {\it HST} image, which shows BLAH BLAH
-that RXJ1131 is lensed into an Einstein ring of diameter $\sim$3.6".
+The UV starlight in RXJ1131 is lensed into an Einstein ring (diameter $\sim$3.6") and the central AGN is 
+quadruply-lensed in the {\it HST} image (grayscale). Both star formation and AGN are sustained 
+by the extended CO gas reservoir \citep[contours; ][]{Leung17a}. 
 {\em (c):}
-Our CO \obs reveal large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 and 
+Our CO \obs reveal a massive molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 and 
 confirmed the presence of the nearby companion, with a gas mass ratio of 7:1 \citep{Leung17a}. 
 {\em (d):}
-Our VLA radio continuum image at 5\,GHz in this target. 
-The proposed \obs will provide an additional constraint on the radio continuum at 1\,GHz.
-{\em (e):} Our best-fit model to the well-sampled SED 
-indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
+We have detected strong radio continuum at 5\,GHz towards this target. 
+The proposed \obs will provide an additional constraint at 1\,GHz (orange marker in \Fig{hst}e).
+{\em (e):} Our best-fit SED model indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
 an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
-The large molecular gas reservoir, on-going star formation, and the high \LFIR together
-are favourable for generating OHM, and thus RXJ1131 is an
-ideal candidate for high-$z$ OHM search.
-The proposed \obs together with our existing data acquired for this target will allow us to 
-compare its (host) properties against those of local OHM hosts to better understand 
-the physical environment that triggers OHM out to a look-back time of 6 Gyr.
+The massive gas reservoir, on-going star formation with high \LFIR, and the large gas column density
+are favourable for generating OHM, making RXJ1131 an
+ideal candidate to search for OHM beyond the nearby universe.
+Here we aim to detect the OHM in RXJ1131, and thus obtain a handle on the pumping efficiency
+to better understand the triggering mechanism at a look-back time of 6 Gyr, which 
+would reflect the different physical conditions of the innermost regions between low- and high-$z$ IR-luminous galaxies.
+The proposed \obs is thus an important step towards understanding the evolution of the inner few hundred pc of
+IR-luminous galaxies.
 \label{fig:hst}}

### 2017-01-29 Radio/VLA_OH/VLA_2.tex
citation parentheses

@@
-% abstract:
-% An exceptionally rare lensing configuration ?, providing a unique opportunity to explore the ISM conditions in this important but thus far unobservable(unexplored?unexploited?) regime of galaxy evolution.
-We propose to take advantage of the magnification of the lensed galaxy RXJ1131, a gas-rich merger with prodigious star formation rate of 120 \Msun yr\pmOne to search for OHM at intermediate-$z$, when the merger rate and ...
-.
-By combining this information with existing ?, we will ?
-These observations will ...
-% inform future systematic searches of high-$z$ OHMs 
-% OH maser emission at 1.67 GHz is known to be associated with regions of intense star formation within ULIRGs.
-As these galaxies are formed through violent mergers, studying the co-moving density of OH maser galaxies across cosmic time will allow the merger rate of the Universe to be determined in an independent way.
-This merger rate is an important parameter in galaxy formation and evolution scenarios.
-
 %% Suggested LaTeX template for the scientific justification
@@
 of obscured star formation and/or their central active galactic nuclei (AGNs),
-which are sustained by their massive molecular gas reservoirs ($M_{\rm gas}$$>$10$^{10}$\,\Msun; see \citet{CW13} for a review).
+which are sustained by their massive molecular gas reservoirs ($M_{\rm gas}$$>$10$^{10}$\,\Msun; see \citealt{CW13} for a review).
 The gas-rich and starbursting nature of high-$z$ galaxies may be a result of galaxy mergers

### 2017-01-29 Radio/VLA_OH/VLA_2.tex
replace hierarchical with cold gas accretion

@@
 \textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
-% Galaxy evolution and the history of galaxy mergers}
 Studying the properties of high-redshift ($z$) galaxies is crucial to understand the formation and evolution of present-day galaxies.
@@
 which are sustained by their massive molecular gas reservoirs ($M_{\rm gas}$$>$10$^{10}$\,\Msun; see \citealt{CW13} for a review).
+% Their high IR luminosity imply that they are responsible for building most of the stellar mass in the universe.
 The gas-rich and starbursting nature of high-$z$ galaxies may be a result of galaxy mergers
-\citep{Riechers11a, Hayward12a, Riechers13b},
-consistent with the notion that galaxies grow through hierarchical merging \citep{White91a}.
-%  merging in the hierarchical model of galaxy formation \citep{White91a}.
-The merger rate is thus expected to increase towards higher redshift \citep[e.g.,][]{LeFloch05a, Magnelli09a}, and constraining
+\citep{Riechers11a, Hayward12a, Riechers13b}, or cold gas accretion from the cosmic web \citep[e.g.,][]{Dekel09b}.
+% , consistent with the notion that galaxies grow through hierarchical merging \citep{White91a}.
+Since the merger rate is expected to increase towards higher redshift \citep[e.g.,][]{LeFloch05a, Magnelli09a}, constraining
 its evolution allows us to track the origin and evolution of present-day populations. % emergence of current day populations.
+
+%Galaxies with high IR-luminous and intense star formation are important for the build-up of stellar mass in the universe. 
+%While IR-luminous galaxies are found in both nearby and at high $z$, studies find that they display different properties and 
+%are different galaxy populations. Low-$z$ ULIRGs are predominantly more compact,
+%mostly merger-triggered starbursts, with lower molecular 
+%gas mass fractions \citep{Veilleux02a, Hopkins10a, Rujopakarn11a, Rujopakarn13a}, whereas 
+%\highz galaxies are a combination of mergers and cold gas accretion.
 
@@
 the number density of OHM may improve current constraints on
-the cosmic merger history \citep[hereafter DG02]{Darling02b_LF}.
+the cosmic merger history \citep[hereafter DG02]{Darling02b_LF}. % but that's assuming IR-luminous must be driven by mergers....
 Existing models predict that detections of
@@
 lensed by a foreground galaxy at $z$\ssim0.3 (\Fig{hst}; \citealt{Sluse03a}).
-By exploiting the effect of lensing magnification,
-our proposed detection experiment requires {\bf an on-source time of  % sigma scales as 1/root(t) --> t scales as 1/sigma^2
-$\sim$30 times less} than otherwise needed to reach the same sensitivity.
 The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}e; e.g.,][]{Claeskens06a, Sluse07a, Leung17a},
@@
 are favourable for generating OH masers, making RXJ1131 an ideal candidate
-to search for OHMs beyond the nearby universe. Assuming the Malmquist-bias corrected relation
-($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}b).
+to search for OHMs beyond the nearby universe.
 
@@
 with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.
+Assuming the Malmquist-bias corrected relation
+($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}b). 
+We here aim to detect the OHM in RXJ1131 at 5$\sigma$. 
+By exploiting the effect of lensing magnification, we require an {\bf on-source time of 4.3 hours}, which
+is {\bf $\sim$30 times cheaper}
+ % sigma scales as 1/root(t) --> t scales as 1/sigma^2
+than otherwise possible.
 
-\noindent \textbf{Science goals}
+\noindent \underline{\textbf{Science goals}}
 \vspace{.2em}\\
-$\bullet$ {\bf Testing OHM as a tracer of merger}
+$\bullet$ {\bf Testing OHM as a tracer of merger.}
 The proposed \obs will establish the first OHM measurement in a {\it bona-fide} high-$z$ merger, thereby
@@
 - likely already know about the cirucmnuclear env part from X-ray, but then could be use for other high-z sources w/o detailed characterization?
-\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies}
+\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies.}
 % Classical model: foreground amplification of background radio continuum, expect quadratic relationship, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud.
@@
 
-\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies}
+\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies.}
 The much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$\eq0 already indicate
@@
 
-\noindent $\bullet$ {\bf Radio continuum}
+\noindent $\bullet$ {\bf Radio continuum.}
 In addition, the proposed \obs will provide an additional constraint on the radio continuum emission at 1\,GHz

### 2017-01-29 Radio/VLA_OH/VLA_2.tex
fix typo

@@
 
-\noindent The steep dependence between OH and FIR luminosities ($L_{\rm OH}^2\propto L_{\rm FIR}^2$; \Fig{model}a)
+\noindent The steep dependence between OH and FIR luminosities ($L_{\rm OH}\propto L_{\rm FIR}^2$; \Fig{model}a)
 found in local OH ``megamasers'' (OHMs;  see \citealt[]{Lo05a} for a review) and

### 2017-01-31 Radio/VLA_OH/VLA_3.tex
with some DR's comments

--- 2017-01-29 Radio/VLA_OH/VLA_2.tex
@@
 \begin{center}
-{\large{\bf{Probing OH Megamaser in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
+{\large{\bf{OH Megamaser Emission in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
 \end{center}
@@
 \textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
-% Galaxy evolution and the history of galaxy mergers}
-Studying the properties of high-redshift ($z$) galaxies is crucial to understand the formation and evolution of present-day galaxies.
-High-$z$ galaxies are IR-luminous due to their intense bursts
-of obscured star formation and/or their central active galactic nuclei (AGNs),
-which are sustained by their massive molecular gas reservoirs ($M_{\rm gas}$$>$10$^{10}$\,\Msun; see \citealt{CW13} for a review).
-The gas-rich and starbursting nature of high-$z$ galaxies may be a result of galaxy mergers
-\citep{Riechers11a, Hayward12a, Riechers13b},
-consistent with the notion that galaxies grow through hierarchical merging \citep{White91a}.
-%  merging in the hierarchical model of galaxy formation \citep{White91a}.
-The merger rate is thus expected to increase towards higher redshift \citep[e.g.,][]{LeFloch05a, Magnelli09a}, and constraining
-its evolution allows us to track the origin and evolution of present-day populations. % emergence of current day populations.
+Galaxies with high IR-luminousity and thus intense star formation rates are important for the build-up of stellar mass in the universe. 
+While IR-luminous galaxies ($\gtrsim10^{12}$\Lsun; ULIRGs) 
+exist at both low and high redshift ($z$), recent studies indicate that they are not the same population. 
+Low-$z$ ULIRGs are mostly merger-triggered starbursts which are more compact and contain
+less molecular gas compared to their \highz counterparts \citep{Veilleux02a, Hopkins10a, Rujopakarn11a, Rujopakarn13a},
+where \highz starbursts are driven by cold gas accretion \citep[e.g.,][]{Dekel09b} 
+and/or galaxy mergers \citep{Riechers11a, Riechers13b, Hayward12a}.
+Probing the kinematics, dynamical structures, and physical conditions of the inner regions of \highz ULIRGs 
+and comparing them to those observed at low $z$ 
+are necessary to enable a better understanding of starbursting galaxies at different epochs.
+% a comparison with their local analogs are important to enable a better understanding of the nature of these \galpop and
+% to shed light on their formation and evolution processes.
+% improve our understanding of the formation and evolution of low- and \highz starburts.
+However, measuring these properties at high $z$ (e.g., $\sim$8\,kpc/$''$ at $z$=1)
+% measuring the kinematics in the inner regions of high-$z$ galaxies 
+require sub-arcsec resolution or better with typical line tracers. On the other hand, a 
+steep relation ($L_{\rm OH}\propto L_{\rm FIR}^{1.2-2}$; \Fig{model}a) has been found in nearby OH ``megamasers'' 
+(OHMs), which are generated in the inner few hundred pc of U/LIRGs (see \citealt[]{Lo05a} for a review).
+Given the ubiquity of IR-bright galaxies at high-$z$, we propose that OHM may be used as a tracer to 
+study the kinematics of the inner regions of \highz galaxies.
+In fact, the much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$=0 already hint at the feasibility of 
+this diagnostic \citep[hereafter DG02]{Baan92a, Darling02a}.
 
-\noindent The steep dependence between OH and FIR luminosities ($L_{\rm OH}^2\propto L_{\rm FIR}^2$; \Fig{model}a)
-found in local OH ``megamasers'' (OHMs;  see \citealt[]{Lo05a} for a review) and
-the ubiquity of strong IR-emitting galaxies found at high $z$ suggest that
-the number density of OHM may improve current constraints on
-the cosmic merger history \citep[hereafter DG02]{Darling02b_LF}.
-Existing models predict that detections of
-OHMs out to at least $z$\ssim3 are possible with current facilities (e.g. the GBT; \Fig{model}b).
+\noindent Existing models predict that detections of
+OHMs out to at least $z$\ssim3 are possible with current facilities (e.g. the GBT; \Fig{model}b; \citealt{Darling02b_LF}).
 Yet, despite several attempts,
@@
 OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies,
-and to improve existing predictions to plan for future OHM surveys with upcoming facilities
-\citep[e.g., FAST, APERTIF/WSRT, ASKAP;][]{Zhang14b}.
+to demonstrate the utility of using it a tracer of the kinematics in the inner regions of high-$z$ galaxies (with upcoming facilities,
+e.g., FAST, APERTIF/WSRT, ASKAP; \citealt[][]{Zhang14b}),
+and to improve existing predictions for future OHM surveys with these facilities.
 Here we propose to observe OH 1667 MHz line emission in the
@@
 the only source at 0.2$<$$z$$<$1 with spatially-resolved imaging of the molecular gas distribution \citep{Leung17a}.
-% X-ray studies  a highly compact source of emission
-% in the innermost region near the accretion disk down to pc-scale
-% \citep[$\sim$20\,AU][]{Dai10a}.
 Modeling of the X-ray spectrum reveals substantial amount of neutral gas with column density of
- % The continuum is strongly absorbed at soft energies by a
-$N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ in the innermost region near % the accretion disk % w.in the X-ray emitting region
-% The spectrum at lower energies is heavily absorbed by neutral gas with a hydrogen column density $N_{\rm H}$.
-% Soft X-ray continuum suggest the presence of a substantial amount of gas.
+$N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ in the innermost region near 
 the $L_X$$\gtrsim$10$^{45}$\,\Lsun AGN \citep{Pooley07a, Reis14a}.
@@
 a strong apparent far-IR luminosity of \LFIR$\sim$5\E{12}\Lsun, which corresponds to
-an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
+an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected), and a cold dust temperature of $T_{d}$\eq55K
+(i.e., based on FIR/submm photometry).
 The large column density together with the strong FIR radiation field % of $\sim$10$^{12}$\Lsun (lensing-corrected),
 % recent star formation (as traced by rest-frame UV emission),
-% presence of a nearby companion, and % at $\sim$2.4\,kpc away, and
 and the large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}b, c)
 are favourable for generating OH masers, making RXJ1131 an ideal candidate
-to search for OHMs beyond the nearby universe. Assuming the Malmquist-bias corrected relation
-($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}b).
+to search for OHMs beyond the nearby universe.
 
@@
 with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.
+Assuming the Malmquist-bias corrected relation
+($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), 
+we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}).
+Since Mrk 231 --- the only OHM host with an AGN and starburst, and thus the most similar to RXJ1131 ---
+falls above this relation, our assumption and estimation of the required sensitivity are reasonable.
+We here aim at a 7$\sigma$ detection.
+By exploiting the effect of lensing magnification, we require an {\bf on-source time of 8 hours}, which
+is {\bf $\gtrsim$30 times cheaper}
+ % sigma scales as 1/root(t) --> t scales as 1/sigma^2
+than otherwise possible.
 
-\noindent \textbf{Science goals}
+\noindent \underline{\textbf{Science goals}}
 \vspace{.2em}\\
-$\bullet$ {\bf Testing OHM as a tracer of merger}
+\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies.}
+Null detections in previous high-$z$ OHM searches suggest a shallower \LOH-\LFIR dependence, which may be
+reflecting the different physical conditions of the inner few hundred pc (where OHMs are generated)
+between low- and high-$z$ IR-luminous galaxies.
+The lower \LOH/\LFIR indicate that the OH amplification is less efficient at the same FIR luminosity
+and that collisional pumping (e.g. due to the strong AGN, and high gas mass and density; \citealt{Field94a}) % volume density
+%
+% Since a purely radiative pumping mechanism is possible
+% only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$), and collisional processes can theoretically predominate at high OH densities, and saturated amplification can become important \citep{Field94a}.
+may play a dominant role in these \highz gas-rich systems.
+Obtaining a definitive OHM measurement in RXJ1131 will provide a handle on the OH pumping efficiency (\LOH/\LFIR) out to higher $z$.
+This together with the detailed properties derived for our target (e.g., \LFIR, \LIR, SFR, $L_{\rm radio}$, $T_{d}$, molecular and dust content)
+will elucidate the role of collisional over radiative pumping
+that may be prevalent in \highz galaxies, given that their physical properties are more similar to RXJ1131 than
+local starbursts. % more violent star formation in a more gas-rich turbulent ISM.
+%	% [NOT applicable] Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
+%	% (i.e., unsaturated masing) found to be consistent with local OHMs...
+%	%
+%% % implying the simple picture of low-gain amplification (i.e., unsaturated masing, quadrature, low density)  \citep{Henkel90a,Randell95a} found to be consistent with local OHMs will likely break down; (i.e., not all OHMs are unsaturated).
+%% While in the nearby universe (z\ssim0), OHMs appear to be unsaturated.
+
+\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies.}
+The much broader linewidths found in $z$$>$0.2 OHMs \citep[typically at least a factor of $>$2 in FWHM;][DG02]{Baan92a}
+compared to those at $z$\eq0 already indicate
+different dynamical properties in the innermost regions of low- and high-$z$ OHM hosts.
+Detecting the OHM in RXJ1131 will therefore demonstrate the feasibility of
+using it as a tracer of the kinematics in the circumnuclear regions of \highz galaxies, thereby improving
+our understanding of the internal dynamics of IR-luminous, gas-rich, starbursting galaxies at high $z$.
+
+\noindent $\bullet$ {\bf Testing OHM as a tracer of mergers.}
 The proposed \obs will establish the first OHM measurement in a {\it bona-fide} high-$z$ merger, thereby
@@
 testing the long-envisaged hypothesis of using its number density to constrain
-the redshift evolution of merger rate.
+the redshift evolution of merger rate (DG02).
 Such a detection will also allow us to better constrain the
@@
 
-%
-% OHM help us understand the physical conditions of high-z galaxies: different circumnuclear environment, optical depth?
-- likely already know about the cirucmnuclear env part from X-ray, but then could be use for other high-z sources w/o detailed characterization?
-\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies}
-% Classical model: foreground amplification of background radio continuum, expect quadratic relationship, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud.
-Null detections in previous high-$z$ OHM searches suggest a shallower \LOH-\LFIR dependence, which may be
-reflecting the different physical conditions of the inner few hundred pc (where OHMs are generated)
-between low- and high-$z$ IR-luminous galaxies.
-The lower \LOH/\LFIR indicate that the OH amplification is less efficient at the same FIR luminosity
-and that collisional pumping (e.g. due to the strong AGN, and high gas mass and density; \citealt{Field94a}) % volume density
-% while locally, not all OHM are AGN hosts, suggesting the FIR radiation from the SB is the dominant pumping source, but the non-detection based on local extrapolation and such maser model may suggest a different energy source/powering mechanism at higher-z, where quasars are more active, and may indicate that something about AGN/radio pumping
-%
-% Since a purely radiative pumping mechanism is possible
-% only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$), and collisional processes can theoretically predominate at high OH densities, and saturated amplification can become important \citep{Field94a}.
-may play a dominant role in these gas-rich \highz systems.
-Obtaining a definitive OHM measurement in RXJ1131 will provide a handle on the OH pumping efficiency (\LOH/\LFIR) out to higher $z$.
-This together with the detailed properties derived for our target (e.g., \LFIR, \LIR, SFR, $L_{\rm radio}$, molecular and dust content)
-will elucidate the role of collisional over radiative pumping
-that may be prevalent in \highz galaxies given their physical properties, which are more similar to RXJ1131 than
-local starbursts. % more violent star formation in a more gas-rich turbulent ISM.
-	% [NOT applicable] Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
-	% (i.e., unsaturated masing) found to be consistent with local OHMs...
-	%
-% % implying the simple picture of low-gain amplification (i.e., unsaturated masing, quadrature, low density)  \citep{Henkel90a,Randell95a} found to be consistent with local OHMs will likely break down; (i.e., not all OHMs are unsaturated).
-% While in the nearby universe (z\ssim0), OHMs appear to be unsaturated.
-
-\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies}
-The much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$\eq0 already indicate
-different dynamical properties in the innermost regions of their hosts \citep{Baan92a,Darling02a}.
-Detecting the OHM in RXJ1131 will therefore demonstrate the feasibility of
-using it as a trace of the kinematics in the circumnuclear regions of \highz galaxies, which will improve
-our understanding of the internal dynamics of IR-luminous, starbursting galaxies at high $z$.
-
-\noindent $\bullet$ {\bf Radio continuum}
-In addition, the proposed \obs will provide an additional constraint on the radio continuum emission at 1\,GHz
-towards RXJ1131 (\Fig{hst}e).
+\noindent $\bullet$ {\bf Radio continuum.}
+The proposed \obs will also constrain the 1\,GHz radio continuum emission
+towards RXJ1131 (\Fig{hst}e), providing a useful estimate for future observations with the A-array configuration to
+constrain the spectral index and synchrotron emission in the foreground radio galaxy 
+and in the background quasar (our target RXJ1131; \Fig{hst}d, e).
 
@@
 important benchmark for future studies of high-$z$ OHMs out to earlier epochs,
-when extremely IR-luminous sources are much more common.
+when extremely IR-luminous starbursting sources are much more common.
 
@@
 \begin{figure}[ptbh]
-\includegraphics[trim=10 305 270 0, clip, scale=0.825]{Fig/OHFIR} \hspace{-1.25em}
-% \includegraphics[trim=0 400 200 0, clip, scale=0.85]{Fig/Darling02b_distribution}
-%  \includegraphics[trim=0 0 0 0, clip, scale=0.625]{Fig/Willett11_distribution}\\ \vspace{1.5em}
-% \includegraphics[trim=0 0 0 0, clip, scale=0.42]{Fig/Darling02_predictionf4}
+\includegraphics[trim=0 0 0 0, clip, scale=0.82]{Fig/OHFIR_RXJ} % \hspace{-1.25em}
 \includegraphics[trim=0 -20 155 0, clip, scale=0.41]{Fig/willett12_fig1_mod.pdf}
@@
 {\it (a):} Since the OH line strength increases with \LFIR,
-the ubiquity of IR-luminous galaxies at high $z$ suggest that OHM can be used to trace distant mergers
-($L_{\rm IR}$$\gtrsim$10$^{12}$\Lsun; DG02).
+the ubiquity of IR-luminous galaxies at high $z$ suggest that OHM may be a used as a proxy for
+studying the kinematics of the inner regions of distant galaxies.
+(Figure modified from DG02).
 {\it (b):} The highest-$z$ OHM known ($z$\eq0.265) was discovered over two decades ago.
-A remarkably low detection rate of $\sim$7\% was reported in subsequent surveys (black and green symbols),
-suggesting a potential redshift evolution in the \LOH/\LFIR relation
-due to the different physical properties between low- and high-$z$ IR-luminous galaxies.
-Assuming $L_{\rm OH}\propto L_{\rm FIR}^{1.2}$ (Malmquist-bias corrected; DG02),
-we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun in our target (orange marker). (Figure adopted from
-\citealt{Willett12a})
+Subsequent surveys (black and green symbols) suggest a potential redshift evolution in the \LOH/\LFIR relation
+due to the different physical properties between low- and high-$z$ IR-luminous galaxies, but 
+severe RFI contaminations at $\nu_{\rm obs}$$<$1\,GHz inhibit a definitive conclusion. (Figure adopted from
+\citealt{Willett12a}).
 Here we propose to observe OH 1667 MHz line emission in the gravitationally-lensed starbursting
 galaxy merger RXJ1131 at $z$\eq0.65.
-The proposed sensitivity will
-probe deeper than existing OHM surveys, and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.2.
+Assuming $L_{\rm OH}\propto L_{\rm FIR}^{1.2}$ (Malmquist-bias corrected; DG02),
+we expect an apparent \LOH= 3.3\E{3}\,\Lsun in our target (orange marker). The proposed sensitivity will
+probe deeper than existing OHM surveys (we do not expect RFI contamination at the 
+redshifted line frequency), 
+and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.2.
 Detecting the OHM in RXJ1131 will provide the first measurement beyond $z$$>$0.265,
@@
 \centering
-\includegraphics[trim=0 0 300 0, clip, scale=.75]{Fig/Fig2}
-\vspace{-0.25em}
+\includegraphics[trim=0 190 0 0, clip, scale=.77]{Fig/Fig2}
+\vspace{-0.85em}
 \caption{
-{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\,$>$\,0.6 with a well-sampled spectral energy distribution (SED) spanning rest-frame UV to radio.}
+{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\,$>$\,0.6}
 {\em (a):} Source-plane reconstruction of {\it HST} images shows recent star formation in our target and
@@
 The UV starlight in RXJ1131 is lensed into an Einstein ring (diameter $\sim$3.6") and the central AGN is
-quadruply-lensed in the {\it HST} image (grayscale). Both star formation and AGN are sustained
+quadruply-lensed in the {\it HST} image (grayscale). Both star formation and the AGN are sustained
 by the extended CO gas reservoir \citep[contours; ][]{Leung17a}.
 {\em (c):}
-Our CO \obs reveal a massive molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 and
-confirmed the presence of the nearby companion, with a gas mass ratio of 7:1 \citep{Leung17a}.
+Lens modeling of our CO data (yellow) 
+reveals a massive gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 
+(cyan; magnification factors $\mu_{L}$ are annotated above the respective channels) and
+confirmed the presence of a CO-emitting companion, with a gas mass ratio of 7:1 \citep[bottom panel;][]{Leung17a}.
 {\em (d):}
@@
 ideal candidate to search for OHM beyond the nearby universe.
-Here we aim to detect the OHM in RXJ1131, and thus obtain a handle on the pumping efficiency
+Here we aim to detect the OHM in RXJ1131, and thus to obtain a handle on the pumping efficiency
 to better understand the triggering mechanism at a look-back time of 6 Gyr, which
 would reflect the different physical conditions of the innermost regions between low- and high-$z$ IR-luminous galaxies.
-The proposed \obs is thus an important step towards understanding the evolution of the inner few hundred pc of
-IR-luminous galaxies.
+The proposed study is therefore an important step towards understanding 
+% the evolution of the inner few hundred pc of
+the internal structure and kinematics of
+starbursting galaxies at earlier epochs.
 \label{fig:hst}}

### 2017-01-31 Radio/VLA_OH/VLA_3.tex
proof read

@@
 \textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
-Galaxies with high IR-luminousity and thus intense star formation rates are important for the build-up of stellar mass in the universe. 
+Galaxies with high IR luminousity and thus intense star formation rate are important for the build-up of stellar mass in the universe. 
 While IR-luminous galaxies ($\gtrsim10^{12}$\Lsun; ULIRGs) 
-exist at both low and high redshift ($z$), recent studies indicate that they are not the same population. 
+exist at both low and high redshifts ($z$), recent studies indicate that they are not the same population. 
 Low-$z$ ULIRGs are mostly merger-triggered starbursts which are more compact and contain
 less molecular gas compared to their \highz counterparts \citep{Veilleux02a, Hopkins10a, Rujopakarn11a, Rujopakarn13a},
-where \highz starbursts are driven by cold gas accretion \citep[e.g.,][]{Dekel09b} 
+whereas \highz starbursts are driven by cold gas accretion \citep[e.g.,][]{Dekel09b} 
 and/or galaxy mergers \citep{Riechers11a, Riechers13b, Hayward12a}.
-Probing the kinematics, dynamical structures, and physical conditions of the inner regions of \highz ULIRGs 
+Probing the kinematics, dynamical structures, and physical conditions of the inner regions of \highz ULIRGs, 
 and comparing them to those observed at low $z$ 
-are necessary to enable a better understanding of starbursting galaxies at different epochs.
+are necessary to better understand the internal structures of starbursting galaxies at different epochs.
 % a comparison with their local analogs are important to enable a better understanding of the nature of these \galpop and
@@
 Given the ubiquity of IR-bright galaxies at high-$z$, we propose that OHM may be used as a tracer to 
-study the kinematics of the inner regions of \highz galaxies.
+study the kinematics and dynamics of the inner regions of \highz galaxies.
 In fact, the much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$=0 already hint at the feasibility of 
@@
 \noindent Existing models predict that detections of
-OHMs out to at least $z$\ssim3 are possible with current facilities (e.g. the GBT; \Fig{model}b; \citealt{Darling02b_LF}).
+OHMs out to at least $z$\ssim3 are possible with current facilities (e.g., the GBT; \Fig{model}b; \citealt{Darling02b_LF}).
 Yet, despite several attempts,
@@
 suggest a potential redshift evolution in the \LOH-\LFIR relation.
-Detecting OHM beyond $z$\eq0.265 is therefore needed to enable a better understanding of the
-OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies,
-to demonstrate the utility of using it a tracer of the kinematics in the inner regions of high-$z$ galaxies (with upcoming facilities,
-e.g., FAST, APERTIF/WSRT, ASKAP; \citealt[][]{Zhang14b}),
+Detecting OHM beyond $z$\eq0.265 is therefore necessary to enable a better understanding of the
+OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies;
+to demonstrate the utility of using it as a tracer of the kinematics in the inner regions of high-$z$ galaxies (with upcoming facilities,
+e.g., FAST, APERTIF/WSRT, ASKAP; \citealt[][]{Zhang14b});
 and to improve existing predictions for future OHM surveys with these facilities.
@@
 gravitationally-lensed starbursting galaxy merger
-RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.
+RXJ1131 at $z$\ssim0.65 (\Fig{hst}) using the VLA's B-array configuration.
 
@@
 Our best-fit spectral energy distribution (SED) model indicates
-a strong apparent far-IR luminosity of \LFIR$\sim$5\E{12}\Lsun, which corresponds to
+a strong apparent far-IR luminosity of \LFIR$\sim$5\E{12}\Lsun, corresponding to
 an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected), and a cold dust temperature of $T_{d}$\eq55K
 (i.e., based on FIR/submm photometry).
-The large column density together with the strong FIR radiation field % of $\sim$10$^{12}$\Lsun (lensing-corrected),
+The large column density together with the strong FIR radiation field
+% of $\sim$10$^{12}$\Lsun (lensing-corrected),
 % recent star formation (as traced by rest-frame UV emission),
@@
 Together with the high fringe rate of the B-array configuration, the proposed \obs will
-reach a sensitivity deeper than previous high-$z$ OHM searches beyond $z$$>$0.4, which were carried out
+probe deeper than previous OHM searches beyond $z$$\gtrsim$0.3, which were carried out
 with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.
@@
 we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}).
-Since Mrk 231 --- the only OHM host with an AGN and starburst, and thus the most similar to RXJ1131 ---
-falls above this relation, our assumption and estimation of the required sensitivity are reasonable.
+Since Mrk 231 --- an OHM host with both an AGN and starburst, and thus the most similar to RXJ1131 ---
+falls above this relation, our assumption and the required sensitivity are reasonable for our target.
 We here aim at a 7$\sigma$ detection.
-By exploiting the effect of lensing magnification, we require an {\bf on-source time of 8 hours}, which
+By exploiting the effect of lensing magnification, we require an {\bf on-source time of 8.0 hours}, which
 is {\bf $\gtrsim$30 times cheaper}
@@
 The lower \LOH/\LFIR indicate that the OH amplification is less efficient at the same FIR luminosity
-and that collisional pumping (e.g. due to the strong AGN, and high gas mass and density; \citealt{Field94a}) % volume density
+and that collisional pumping (e.g., due to higher gas mass and density, and 
+AGN heating; \citealt{Field94a}) % volume density
 %
@@
 Detecting the OHM in RXJ1131 will therefore demonstrate the feasibility of
-using it as a tracer of the kinematics in the circumnuclear regions of \highz galaxies, thereby improving
-our understanding of the internal dynamics of IR-luminous, gas-rich, starbursting galaxies at high $z$.
+using it as a tracer of the circumnuclear kinematics of \highz galaxies, which contain higher 
+gas fractions and are much more turbulent than local galaxies, thereby improving
+our understanding of the internal dynamics of violently star-forming galaxies at high $z$.
 
@@
 constrain the spectral index and synchrotron emission in the foreground radio galaxy 
-and in the background quasar (our target RXJ1131; \Fig{hst}d, e).
+and in the background AGN (our target RXJ1131; \Fig{hst}d, e).
 
@@
 }
-% \vspace{-1.25em}
+\vspace{-0.9em}
 
 \begin{figure}[ptbh]
-\includegraphics[trim=0 0 0 0, clip, scale=0.82]{Fig/OHFIR_RXJ} % \hspace{-1.25em}
-\includegraphics[trim=0 -20 155 0, clip, scale=0.41]{Fig/willett12_fig1_mod.pdf}
+\includegraphics[trim=0 0 0 0, clip, scale=0.8]{Fig/OHFIR_RXJ} % \hspace{-1.25em}
+\includegraphics[trim=0 -20 155 0, clip, scale=0.39]{Fig/willett12_fig1_mod.pdf}
+\vspace{-0.5em}
 \caption{{\bf \LOH-\LFIR correlation and existing OHMs measurements}
@@
 we expect an apparent \LOH= 3.3\E{3}\,\Lsun in our target (orange marker). The proposed sensitivity will
-probe deeper than existing OHM surveys (we do not expect RFI contamination at the 
+probe deeper than existing OHM surveys (we do not expect RFI at the 
 redshifted line frequency), 
-and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.2.
+and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.3.
 Detecting the OHM in RXJ1131 will provide the first measurement beyond $z$$>$0.265,
@@
 \caption{
-{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\,$>$\,0.6}
+{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\ssim0.65}
 {\em (a):} Source-plane reconstruction of {\it HST} images shows recent star formation in our target and
@@
 {\em (d):}
-We have detected strong radio continuum at 5\,GHz towards this target.
+We have detected strong radio continuum emission at 5\,GHz towards this target.
 The proposed \obs will provide an additional constraint at 1\,GHz (orange marker in \Fig{hst}e).
 {\em (e):} Our best-fit SED model indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
-an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
-The massive gas reservoir, on-going star formation with high \LFIR, and the large gas column density
+an intense SFR\ssim120 \Msun yr\pmOne (lensing-corrected), and a dust temperature of $T_{d}$\eq55 K.
+The massive gas reservoir, on-going star formation with high \LFIR and $T_{d}$, and the large gas column density
 are favourable for generating OHM, making RXJ1131 an

### 2017-01-31 Radio/VLA_OH/VLA_proposal2017B.tex
remove future obs w/ A array part

@@
-% abstract:
-% An exceptionally rare lensing configuration ?, providing a unique opportunity to explore the ISM conditions in this important but thus far unobservable(unexplored?unexploited?) regime of galaxy evolution.
-We propose to take advantage of the magnification of the lensed galaxy RXJ1131, a gas-rich merger with prodigious star formation rate of 120 \Msun yr\pmOne to search for OHM at intermediate-$z$, when the merger rate and ...
-.
-By combining this information with existing ?, we will ?
-These observations will ...
-
 %% Suggested LaTeX template for the scientific justification
@@
 \newcommand{\lohpred}{$L_{\rm OH}^{\rm pred}$\xspace}
-\newcommand{\lohlfir}{$L_{\rm OH}-L{\rm FIR}$\xspace}
+\newcommand{\lohlfir}{$L_{\rm OH}$-$L_{\rm FIR}$\xspace}
 
@@
 \begin{center}
-{\large{\bf{Probing OH Megamaser in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
+{\large{\bf{OH Megamaser Emission in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
 \end{center}
 \vspace{-.8em}
-\textbf{Current understanding of OH megamasers and galaxy evolution} \\
-% point
-% - OHM <-> ULIRGs <-> mergers <-> gas rich 
-% - conditions for OHM
-\indent Almost all ($>$95\%) OH ``megamasers" (OHMs) known to date are associated with 
-(ultra)-luminous infrared galaxies (U)LIRGs (\LIR$>10^{11}$\,\Lsun; see \citealt[]{Lo05a} for a review), 
-which are undergoing extreme bursts of star formation triggered by merger events
-\citep[e.g.,][]{Sanders96a, Hopkins06b}.
-Theoretically, the intense IR radiation field and the large column of molecular gas 
-found in (U)LIRGs/mergers
-are the required conditions for generating OHMs \citep[e.g.][]{Baan89a}.
-%Since the necessary excitation of OHMs can be provided by 
-%IR pumping (for pop. inversion) with large molecular column density \citep{Baan89a}, where 
-%the required radiation is believed to be coming from dust absorbing starlight from 
-%SB that are thought to be merger-driven (and AGN), and the high density at center easily reached in mergers.
-Thus, starburst galaxies (IR-luminous) and mergers appear to be the most probable galaxy populations for hosting OHMs.
+\textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
+Galaxies with high IR luminousity and thus intense star formation rate are important for the build-up of stellar mass in the universe. 
+While IR-luminous galaxies ($\gtrsim10^{12}$\Lsun; ULIRGs) 
+exist at both low and high redshifts ($z$), recent studies indicate that they are not the same population. 
+Low-$z$ ULIRGs are mostly merger-triggered starbursts which are more compact and contain
+less molecular gas compared to their \highz counterparts \citep{Veilleux02a, Hopkins10a, Rujopakarn11a, Rujopakarn13a},
+whereas \highz starbursts are driven by cold gas accretion \citep[e.g.,][]{Dekel09b} 
+and/or galaxy mergers \citep{Riechers11a, Riechers13b, Hayward12a}.
+Probing the kinematics, dynamical structures, and physical conditions of the inner regions of \highz ULIRGs, 
+and comparing them to those observed at low $z$ 
+are necessary to better understand the internal structures of starbursting galaxies at different epochs.
+% a comparison with their local analogs are important to enable a better understanding of the nature of these \galpop and
+% to shed light on their formation and evolution processes.
+% improve our understanding of the formation and evolution of low- and \highz starburts.
+However, measuring these properties at high $z$ (e.g., $\sim$8\,kpc/$''$ at $z$=1)
+% measuring the kinematics in the inner regions of high-$z$ galaxies 
+require sub-arcsec resolution or better with typical line tracers. On the other hand, a 
+steep relation ($L_{\rm OH}\propto L_{\rm FIR}^{1.2-2}$; \Fig{model}a) has been found in nearby OH ``megamasers'' 
+(OHMs), which are generated in the inner few hundred pc of U/LIRGs (see \citealt[]{Lo05a} for a review).
+Given the ubiquity of IR-bright galaxies at high-$z$, we propose that OHM may be used as a tracer to 
+study the kinematics and dynamics of the inner regions of \highz galaxies.
+In fact, the much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$=0 already hint at the feasibility of 
+this diagnostic \citep[hereafter DG02]{Baan92a, Darling02a}.
 
-% point:
-% - using OHM to trace distant merger
-% - future survey using number density of OHM to constraint galaxy evolution models / merger history
-% - currently no new detections beyond z>0.3, despite great efforts over the last two decades
-% - our source is cheap to do, reasonable to expect OHM, we are probing deeper than previous attempts
-The scaling relation of $L_{\rm OH}$$\propto L_{\rm FIR}^{2}$ 
-\citep[or  $L_{\rm OH}$$\propto L_{\rm FIR}^{1.2}$ with Malmquist bias correction; \Fig{model}a; ][hereafter DG02]{Baan89a, Darling02b_LF} 
-suggests that the number density of OHM is expected to increase towards $z$\ssim3,
-when (U)LIRGs/mergers are more common \citep[e.g.,][]{LeFloch05a, Magnelli09a}.
-OHMs have therefore been proposed as one of the most promising avenues for tracing mergers beyond the nearby universe
-and for constraining the merger history of galaxies 
-independent of IR luminosity function (\citealt{Briggs98a}, DG02). 
-These models predict%  based on the commonly observed \LFIR$>$1\E{12}\Lsun at $z$\,$\gtrsim$\,1
-that we should be able to detect OHMs out to at least $z$\ssim3 with current facilities 
-(e.g. the GBT; \Fig{model}b). Yet, 
-the most distant OHM host galaxy known-to-date is at $z$\eq0.265, which was 
-discovered over two decades ago \citep{Baan92a}.
-In addition, the null detections and unexpectedly low detection rate 
-reported in the latest OHM studies (over half a decade ago) 
-by \citet{Ivison06a} in a $z$\ssim4 galaxy % with an IR luminosity of \LIR$\gtrsim$1\E{14}\Lsun, 
-and by \citet{Willett12a} in a sample of (U)LIRGs at $z$\,$\lesssim$\,1.5 (7\% detection rate, \Fig{model}) --- % only detected 9/121 
-suggest a potential redshift evolution in the \LOH-\LFIR relation, which may hint at a different 
-OHM triggering mechanism at earlier epochs that reflects the different physical conditions between
-low- and high-$z$ (U)LIRGs.
-The null detections in these studies also indicate also suggests that the 
-classical model for OH pumping (pumped radiatively) in megamasers may not be universal (i.e., not all OHMs are unsaturated).
-% only a radiative pumping mechanism for OH megamasers based on weak, unsaturated gain has been considered \citep{Henkel90a,Randell95a}.
-%In these papers it was assumed that the maser cloud amplifies 
-% radio emission from a source lying behind the cloud. 
-However, since a purely radiative pumping mechanism is possible only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$). 
-Theoretically, at relatively high OH densities, collisional processes may predominate. 
-In addition, at high densities saturated amplification can be important \citep{Field94a}.
-Detecting OHM beyond $z$\eq0.265 is therefore crucial to 
-enable a better understanding of OHM and to 
-improve existing predictions used for planning future OHM surveys with upcoming facilities 
-\citep[e.g., FAST, APERTIF/WSRT, ASKAP;][]{Zhang14b}.
+\noindent Existing models predict that detections of
+OHMs out to at least $z$\ssim3 are possible with current facilities (e.g., the GBT; \Fig{model}b; \citealt{Darling02b_LF}).
+Yet, despite several attempts,
+the most distant OHM known-to-date was discovered over two decades ago, at $z$\eq0.265 \citep{Baan92a}.
+The null detection in a $z$\ssim4 extremely IR-bright galaxy (\LIR$>10^{14}$\Lsun; \citealt{Ivison06a}) and
+the remarkably low detection rate (7\%) from a sample of $>$120 IR-luminous galaxies
+at $z$\,$\lesssim$\,1.5 ($L_{\rm IR}>10^{11}$\Lsun; \Fig{model}b; \citealt{Willett12a})
+suggest a potential redshift evolution in the \LOH-\LFIR relation.
+Detecting OHM beyond $z$\eq0.265 is therefore necessary to enable a better understanding of the
+OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies;
+to demonstrate the utility of using it as a tracer of the kinematics in the inner regions of high-$z$ galaxies (with upcoming facilities,
+e.g., FAST, APERTIF/WSRT, ASKAP; \citealt[][]{Zhang14b});
+and to improve existing predictions for future OHM surveys with these facilities.
 Here we propose to observe OH 1667 MHz line emission in the
 gravitationally-lensed starbursting galaxy merger
-RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.
+RXJ1131 at $z$\ssim0.65 (\Fig{hst}) using the VLA's B-array configuration.
 
 \noindent \textbf{An ideal target --- a lensed gas-rich, starbursting merger at $z$\,$>$\,0.6}\\
-\indent High-resolution imaging and spectroscopy in optical wavelength show that RXJ1131 is 
+\noindent High-resolution imaging and spectroscopy in optical wavelength show that RXJ1131 is
 lensed by a foreground galaxy at $z$\ssim0.3 (\Fig{hst}; \citealt{Sluse03a}).
-By exploiting the effect of lensing magnification, 
-our proposed detection experiment requires {\bf an on-source time of  % sigma scales as 1/root(t) --> t scales as 1/sigma^2
-$\sim$30 times less} than otherwise needed to reach the same sensitivity. 
-The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}; e.g.,][]{Claeskens06a, Sluse07a, Pooley07a, Reis14a, Leung17a}, 
+The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}e; e.g.,][]{Claeskens06a, Sluse07a, Leung17a},
 making it one of the best-studied galaxies at $z$$>$0.5 and
 the only source at 0.2$<$$z$$<$1 with spatially-resolved imaging of the molecular gas distribution \citep{Leung17a}.
-The lensed nature of this target provides an excellent 
-opportunity to study the innermost regions around a black hole at a cosmological distance.
-In fact, X-ray studies constrained the X-ray emitting region a highly compact source of emission 
-($\sim$20\,AU; constraining the optical and X-ray emitting region near the accretion disk down to pc-scale) \citep{Dai10a},
-demonstrating the how much we already know about this target.
-Features in the X-ray spectrum finds 
-%  A fraction of this hard X-ray emission is reflected by cold gas in the accretion disk, producing an observed spectrum imprinted with the features of photoelectric absorption, fluorescent 6.4 keV Fe K$\alpha$ line emission, and a Compton backscattered reflection continuum that produces a bump in the spectrum above 10 keV (George & Fabian 1991).
- % The continuum is strongly absorbed at soft energies by a 
-a neutral gas of column density $N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ near the accretion disk. % w.in the X-ray emitting region
-The spectrum at lower energies is heavily absorbed by neutral gas with a hydrogen column density $N_{\rm H}$.
-% Soft X-ray continuum suggest the presence of a substantial amount of gas.
+Modeling of the X-ray spectrum reveals substantial amount of neutral gas with column density of
+$N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ in the innermost region near 
+the $L_X$$\gtrsim$10$^{45}$\,\Lsun AGN \citep{Pooley07a, Reis14a}.
 Our best-fit spectral energy distribution (SED) model indicates
-a strong apparent far-IR luminosity of \LFIR$>$4\E{12}\,\Lsun, which corresponds to
-an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
-These properties together with the evidence of recent star formation (as traced by rest-frame UV \obs),
-the presence of a nearby companion at $\sim$2.4\,kpc away, and a large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}) 
-are favourable for generating OHMs, suggesting RXJ1131 is an ideal candidate 
-to search for OHM beyond the nearby universe.
+a strong apparent far-IR luminosity of \LFIR$\sim$5\E{12}\Lsun, corresponding to
+an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected), and a cold dust temperature of $T_{d}$\eq55K
+(i.e., based on FIR/submm photometry).
+The large column density together with the strong FIR radiation field
+% of $\sim$10$^{12}$\Lsun (lensing-corrected),
+% recent star formation (as traced by rest-frame UV emission),
+and the large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}b, c)
+are favourable for generating OH masers, making RXJ1131 an ideal candidate
+to search for OHMs beyond the nearby universe.
 
-In addition, the redshift of RXJ1131 has been spectroscopically confirmed with CO lines down to a precision of 
+\noindent In addition, the redshift of RXJ1131 has been spectroscopically confirmed with CO lines down to a precision of
 $\Delta z$\eq0.0002, indicating that the proposed OH line is redshifted to a fortuitous region
 free of RFI at the low-end of the L-band.
-This together with the high fringe rate of the B-array configuration will 
-reach a sensitivity deeper than previous high-$z$ OHM searches beyond $z$$>$0.4, which were carried out 
+Together with the high fringe rate of the B-array configuration, the proposed \obs will
+probe deeper than previous OHM searches beyond $z$$\gtrsim$0.3, which were carried out
 with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.
+Assuming the Malmquist-bias corrected relation
+($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), 
+we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}).
+Since Mrk 231 --- an OHM host with both an AGN and starburst, and thus the most similar to RXJ1131 ---
+falls above this relation, our assumption and the required sensitivity are reasonable for our target.
+We here aim at a 7$\sigma$ detection.
+By exploiting the effect of lensing magnification, we require an {\bf on-source time of 8.0 hours}, which
+is {\bf $\gtrsim$30 times cheaper}
+ % sigma scales as 1/root(t) --> t scales as 1/sigma^2
+than otherwise possible.
 
-%--- added
-% what can OHM help us understand the physical conditions of high-z galaxies. 
-% what can't we learn from local OHM but can at high-z.
-% difference between local and high-z; why care about doing OHM at high-z
-The number density of IR-luminous galaxies and their molecular gas fractions and SFRs
-are higher towards $z$\ssim2,
-indicating a different physical conditions between low- and high-$z$ galaxies.
-Such a different physical conditions can potentially be reflected in the OHM phenomenon, given that OHM are more strongly amplified in 
-large column of molecular gas and the more intense IR radiation field.
-Given that OHMs originate from central region, detecting OHM in high-$z$ galaxies and comparing them against those in the local, which are 
-relatively more quiescent, would allow us to directly probe the physical conditions (and dynamics) in the inner few hundred pc
-as galaxies evolve. {\bf justify the masing, pumping mechanism in science goals}
-% foreground amplification of background radio continuum, this quadratic relationship may be expected, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud
-In fact, the null detection of OHM in a $z$\ssim4 galaxy with \LIR$>$1\E{13}\,\Lsun already hints at a different 
-excitation mechanism that may be a result of their different physical conditions (e.g. more dense, higher optical depth \citet{Ivision06a}).
+\noindent \underline{\textbf{Science goals}}
+\vspace{.2em}\\
+\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies.}
+Null detections in previous high-$z$ OHM searches suggest a shallower \LOH-\LFIR dependence, which may be
+reflecting the different physical conditions of the inner few hundred pc (where OHMs are generated)
+between low- and high-$z$ IR-luminous galaxies.
+The lower \LOH/\LFIR indicate that the OH amplification is less efficient at the same FIR luminosity
+and that collisional pumping (e.g., due to higher gas mass and density, and 
+AGN heating; \citealt{Field94a}) % volume density
+%
+% Since a purely radiative pumping mechanism is possible
+% only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$), and collisional processes can theoretically predominate at high OH densities, and saturated amplification can become important \citep{Field94a}.
+may play a dominant role in these \highz gas-rich systems.
+Obtaining a definitive OHM measurement in RXJ1131 will provide a handle on the OH pumping efficiency (\LOH/\LFIR) out to higher $z$.
+This together with the detailed properties derived for our target (e.g., \LFIR, \LIR, SFR, $L_{\rm radio}$, $T_{d}$, molecular and dust content)
+will elucidate the role of collisional over radiative pumping
+that may be prevalent in \highz galaxies, given that their physical properties are more similar to RXJ1131 than
+local starbursts. % more violent star formation in a more gas-rich turbulent ISM.
+%	% [NOT applicable] Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
+%	% (i.e., unsaturated masing) found to be consistent with local OHMs...
+%	%
+%% % implying the simple picture of low-gain amplification (i.e., unsaturated masing, quadrature, low density)  \citep{Henkel90a,Randell95a} found to be consistent with local OHMs will likely break down; (i.e., not all OHMs are unsaturated).
+%% While in the nearby universe (z\ssim0), OHMs appear to be unsaturated.
 
-% X-ray and LOH -- why RXJ1131
-Because OHMs are associated with the most luminous galaxy in the nearby universe, it is reasonable to speculate a possible connection
-between OHMs and quasars, where both are driven by mergers (increasing \LFIR, and molecular gas into central region) 
-since recent high-$z$ studies find evidence that AGN activity and mergers are connected (growth of SMBHs may be partly driven by 
-mergers) \citep{DiMatteo05a}.
-pumping and density, saturated:
- A purely radiative pumping mechanism is possible only at relatively low densities
-($n_{\rm OH}$\ssim10$^{-4}$ cm$^{-3}$). At relatively high OH densities, collisional processes may predominate. In addition, at high densities
-saturated amplification can be important.
-While in the nearby universe (z\ssim0), OHMs appear to be unsaturated. But this may not be the case at high-$z$, where
- the physical environment is very different, more violent star formation, the ISM is more turbulent, and when there are more gas 
- available on average.
-Further \obs of OHM are needed to elucidate the role of collisional processes in 
-producing population inversions over the observed radiative transitions of OH.
-% while locally, not all OHM are AGN hosts, suggesting the FIR radiation from the SB is the dominant pumping source, but the non-detection based on local extrapolation and such maser model may suggest a different energy source/powering mechanism/ at higher-z, where quasars are more active, and may indicate that something about AGN/radio pumping?
-saturated amplification?
+\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies.}
+The much broader linewidths found in $z$$>$0.2 OHMs \citep[typically at least a factor of $>$2 in FWHM;][DG02]{Baan92a}
+compared to those at $z$\eq0 already indicate
+different dynamical properties in the innermost regions of low- and high-$z$ OHM hosts.
+Detecting the OHM in RXJ1131 will therefore demonstrate the feasibility of
+using it as a tracer of the circumnuclear kinematics of \highz galaxies, which contain higher 
+gas fractions and are much more turbulent than local galaxies, thereby improving
+our understanding of the internal dynamics of violently star-forming galaxies at high $z$.
 
-%-------
-
-\noindent \textbf{Science goals} \\
-
-\indent The proposed \obs will establish the first measurement of an OHM in a {\it bona-fide} high-$z$ merger, thereby
-demonstrating the feasibility of using it as a tracer of distant galaxy mergers and
-testing the long-envisaged hypothesis of using the number density of OHM to constrain 
-the redshift evolution of merger rate. 
-Such a
-high-$z$ (non-)detection will also allow us to better constrain the \LOH-\LFIR scaling relation and its redshift evolution,
-and thus improve 
-% current models used to predict OHM detection rate 
-predictions on the detection threshold needed  
-% model predictions for designing 
-% when designing
-% future surveys to search for 
-to carry out systematic searches of high-$z$ OHMs with upcoming facilities.  
-% because if we find a shallower relation, then it would mean the surveys need to go deeper to reach the same \LOH.
+\noindent $\bullet$ {\bf Testing OHM as a tracer of mergers.}
+The proposed \obs will establish the first OHM measurement in a {\it bona-fide} high-$z$ merger, thereby
+demonstrating the feasibility of using it as a tracer of distant mergers and
+testing the long-envisaged hypothesis of using its number density to constrain
+the redshift evolution of merger rate (DG02).
+Such a detection will also allow us to better constrain the
+\LOH-\LFIR relation out to higher $z$, % which may provide a handle on the pumping efficiency (\LOH/\LFIR)
+% that may be closer to other high-$z$ galaxies if their physical conditions are more similar than compared to low-z (\LOH/\LFIR)
+and thus improve predictions on the required sensitivity needed for future searches of high-$z$ OHMs.
 Since our target is a merger,
 a null detection would also indicate that the notion of
-using the OHM number density to constrain the merger history needs to be revised before designing future OHM surveys.
+using the OHM number density to constrain the merger history requires revision before designing future OHM surveys.
 
-% --  host properties ---
-% to further understand the relationship between OHM and the types of galaxies hosting them at an earlier epoch.
-In addition, regardless of whether the OH line emission is detected or not, the amount of data we have already acquired 
-for this potential OHM host galaxy will allow us to compare its (host) galaxy properties 
-(e.g., SFR or \LFIR, \LIR, \LOH, $L_{\rm radio}$, molecular and dust content)
-against those of local OHM hosts to better understand 
-% the nature of OHM.
-% the pumping and masing mechanism of OHM. % the condition needed for generating OHM
-% the required conditions for triggering OHM at an earlier epoch.
-the relationship between the maser emission and the environment of its (host) galaxy. 
-{\bf  Is there some
-detailed prediction that they should be found in things above a
-certain SFR or merger state or something? Any more details you can
-provide there would be better. But 2-3 sentences about this would be good.
-LFIR, LRadio.. LOH.. 
-}
-% --- to better understanding the pumping and masing mechanism --
-To blah... saturated maser and collisional pumping. % saturated gain mechanism
-% The T/density of the masing material? 
-% Maybe you could do some of that with
-% certain reasonable assumptions? Similarly 2-3 sentences would be good.
-% 
-Because of the required condition to excite and generate OHM, and because they originate from the central few pc to few hundred pc 
-in the nuclear regions of galaxies \citep{Diamond99a},
-OHM is a powerful diagnostics of the physical 
-conditions in the innermost regions of galaxies. 
-% foreground amplification of background radio continuum, this quadratic relationship may be expected, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud
-Classical model of OHMs suggest that low-gain amplification (i.e., unsaturated gain) and IR pumping 
-is the dominant mechanism for producing OHM. However, the null detections of OHM at $z$$>$0.3
-\citep{Ivison06a, Willet12a} may suggest different pumping efficiency (\LOH/\LFIR) at high-z, due to the different physical conditions (e.g. 
-optical depth is higher at high-z due to the higher LFIR). 
-% 
-% Since FIR radiation field can invert the OH population via the ``pumping lines'' at 35 and 53$\mu$m
-% Masing can then be stimulated by 18 cm (i.e. $\sim$1.6GHz).
-% With the additional constraint on the \LOH-\LFIR relation at $z$$>$0.3 provided by this experiment, we will 
-% investigate the pumping efficiency at higher redshift than currently studies, %% but presumable can already do so with upper limits from Willett+12
-% by comparing to local OHM hosts and as a function of \LFIR through the \LOH-\LFIR scaling relation.
-% (look for potential discrepancy in this relation based on nearby studies)% (already seen a discrepancy at z=3, see also Darling02b find evidence of a mixture of saturated and
-% unsaturated masers). 
-% For instance, a slope shallower than $<$2 %  (i.e, deviations from the quadrature) 
-% would suggest that the amplification process is less efficient at higher FIR luminosity. %, where the optical depth is higher.
-% Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
-% (i.e., unsaturated masing) found to be consistent with local OHMs
-% will likely break down resulting in deviations from the quadratic relation 
-% implying the simple picture of low-gain amplification (i.e., unsaturated masing) 
-% found to be consistent with local OHMs will likely break down
-% and indicate saturated masing at high redshift.
-% Darling02b: find evidence of a mixture of saturated and unsaturated masers. 
-% 
-A non-detection would therefore still be meaningful in advancing our knowledge.
+\noindent $\bullet$ {\bf Radio continuum.}
+The proposed \obs will also provide an additional constraint on the radio continuum emission at 1\,GHz 
+towards RXJ1131, and thus to constrain the radio spectral index (\Fig{hst}e).
 
-% --- procedure
-%Existing lens modeling of RXJ1131 have been carried out from rest-frame X-ray through submm, indicating BLAH component is strongly-lensed by a factor of $\mu$\ssim10. 
-%Since the OHM is expected to originate from the few hundred pc from the central quasar \citep[e.g.][]{Darling07a}, thus 
-%we will correct for lensing using the magnification factor based on X-ray, MIR lens model \citep{}.
-
-With the aid of lensing and the rich multi-wavelength data 
-% probing a wide range of properties 
-available for this potential OHM host, RXJ1131 is an exceptional target
-for obtaining a better understanding of OHM in IR-luminous galaxies beyond the nearby universe out to
-a lookback time of $\sim$6 Gyr.
-% The detection of a OHM at redshift higher than already known 
-% may also open up/demonstrate the possibility of use OHM as a tool for studying the 
-% properties (dynamics) of the molecular nuclei at high redshifts when observed at high resolution with the VLBI.
-In the case of a detection, we will future carry out follow-up \obs % at higher-resolution 
-with the VLBI to study the physical conditions of the nuclear molecular torus
-% and to better understand the energy source and the nature of OHM at high redshift.
-% ($<$ few hundred pc) 
-responsible for the OH line emission, where the velocity structure of the 
-currently highest-$z$ OHM already suggests a different dynamic structure 
-than those at lower-$z$ \citep{Baan92a}. % . e..g IRAS F14070+0525 has a total line width of ~2400 km/s 
-% OHM may be useful for studying dynamical and molecular properties of nuclei at high-z. <-- well, but APM is not detected.. so OHM may not be so reliable.
+% --- finally ----
+\noindent
+With the aid of lensing and the rich multi-wavelength data available for this potential OHM host, RXJ1131 is an exceptional target
+for high-$z$ OHM search. 
+Detecting the OHM will provide a handle on the pumping efficiency (\LOH/\LFIR)
+and enable a better understanding of the OHM triggering mechanism at $z$\ssim0.65, which
+would reflect the different physical conditions between low- and high-$z$ IR-luminous galaxies.
+The detection will also demonstrate the utility of OHMs as tracers of distant mergers, and
+of the kinematics in the inner few hundred pc
+of starburst galaxies beyond the nearby universe. %, out to a lookback time of $\sim$6 Gyr.
 The proposed investigation will therefore serve as an
-important benchmark for future studies of high-$z$ OHM out to earlier epochs,
-when extremely IR-luminous sources are much more common.
-%  inform future systematic searches of high-$z$ OHMs 
-% Thus, a detection/non-detection at this redshift is crucial for development of this technique for future OHM studies.
-
-%\noindent \textbf{Technical Justification}
-%We estimate the required sensitivity based on the \LFIR of 4\E{12}\,\Lsun found for RXJ1131 
-%together with the \LOH$\propto$\LFIR$^{1.2}$ relation reported by (DG02), and 
-%the typical FWHM line width of $\sim$600\,\kms of the highest-$z$ sources ($z$$>$0.2; DG02).
-%These yield a line intensity of 330 mJy\,\kms, and a peak flux density of $S_\nu$\eq0.55\,mJy.
-%To secure a 5$\sigma$ detection, we therefore require $\sigma$\eq0.11\,mJy beam\pmOne over the line FWHM. 
-%Since extragalactic OHMs originate from the central few hundred pc, we expect the emission to 
-%remain spatially-unresolved at the B-array configuration.
-%We thus require an on-source time of 4.3 hours (total time of 5.5 hours).
-%% \vspace{-0.25em}
+important benchmark for future studies of high-$z$ OHMs out to earlier epochs,
+when extremely IR-luminous starbursting sources are much more common.
 
@@
 }
-% \vspace{-1.25em}
+\vspace{-0.9em}
 
 \begin{figure}[ptbh]
-\includegraphics[trim=10 305 270 0, clip, scale=0.825]{Fig/OHFIR} \hspace{-1.25em}
-% \includegraphics[trim=0 400 200 0, clip, scale=0.85]{Fig/Darling02b_distribution}
-%  \includegraphics[trim=0 0 0 0, clip, scale=0.625]{Fig/Willett11_distribution}\\ \vspace{1.5em}
-% \includegraphics[trim=0 0 0 0, clip, scale=0.42]{Fig/Darling02_predictionf4}
-\includegraphics[trim=0 -20 155 0, clip, scale=0.41]{Fig/willett12_fig1_mod.pdf}
+\includegraphics[trim=0 0 0 0, clip, scale=0.8]{Fig/OHFIR_RXJ} % \hspace{-1.25em}
+\includegraphics[trim=0 -20 155 0, clip, scale=0.39]{Fig/willett12_fig1_mod.pdf}
+\vspace{-0.5em}
 \caption{{\bf \LOH-\LFIR correlation and existing OHMs measurements}
-{\it Left}: The super-linear correlation found between \LOH and \LFIR in local studies indicates
-the connection between OHM generation and IR radiation field,
-and thus suggests that OHM is a powerful tool for tracing distant mergers (bright IR emitters)
-and constraining the cosmic merger history (DG02).
-{\it Right}: 
-The highest-$z$ OHM known to date (at $z$\eq0.265) was 
-detected over two decades ago \citep{Baan92a}.
-3$\sigma$ sensitivity predicted to be necessary for OHM detection at different $z$, 
-derived based on existing OHM detections (i.e., assuming some $\Delta v$). 
-Subsequent OHM \obs yielded very low detection rate ($\sim$7\%;  black and green) \citep[figure modified from][]{Willett12a}. 
-The lower than expected detection rate indicates that current prediction based on local measurements need to be revised, or that the previous 
-high-z OHM survey are not sensitive enough, or that the assumption of $\Delta v$ is too small (the $z$$>$0.2 sources have wider FWHM by at least a factor of 2). 
-Our proposed \obs will push beyond these sensitivity to $5\sigma$\eq0.55 mJy...
- (since RFI is better in interferometer, because higher fringe rate, increase baselines so that RFIs are decorrelated via geometric delay.)
-{\bf also can reach to lower rms than previous study which are affected by RFIs.}
+{\it (a):} Since the OH line strength increases with \LFIR,
+the ubiquity of IR-luminous galaxies at high $z$ suggest that OHM may be a used as a proxy for
+studying the kinematics of the inner regions of distant galaxies.
+(Figure modified from DG02).
+{\it (b):} The highest-$z$ OHM known ($z$\eq0.265) was discovered over two decades ago.
+Subsequent surveys (black and green symbols) suggest a potential redshift evolution in the \LOH/\LFIR relation
+due to the different physical properties between low- and high-$z$ IR-luminous galaxies, but 
+severe RFI contaminations at $\nu_{\rm obs}$$<$1\,GHz inhibit a definitive conclusion. (Figure adopted from
+\citealt{Willett12a}).
 Here we propose to observe OH 1667 MHz line emission in the gravitationally-lensed starbursting
 galaxy merger RXJ1131 at $z$\eq0.65.
-In contrast to the \citet{Willett12a} sample, which does not include any active galactic nucleus (AGN) host 
-galaxies, 
-our target hosts an optically bright AGN, and thus may offer an alternate view to high-$z$ OHM hosts. 
-The proposed \obs will better constrain the \LOH-\LFIR scaling relation and its redshift evolution, and thus 
-improve % current models used to predict OHM detection rate 
-model predictions for designing 
-future surveys to search for high-$z$ OHMs with upcoming facilities.
-{\bf look for discrepancy in \LOH-\LFIR between low and high-$z$ mergers/potential OHM hosts, which
- would indicate different OH excitation mechanism.} % foreground amplification of background radio continuum, this quadratic relationship may be expected, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud
-The proposed sensitivity together with the aid of lensing magnification 
-allow us to probe deeper than previous OHM high-z searches, and to fainter intrinsic \LOH beyond $z$$\gtrsim$0.2.
+Assuming $L_{\rm OH}\propto L_{\rm FIR}^{1.2}$ (Malmquist-bias corrected; DG02),
+we expect an apparent \LOH= 3.3\E{3}\,\Lsun in our target (orange marker). The proposed sensitivity will
+probe deeper than existing OHM surveys (we do not expect RFI at the 
+redshifted line frequency), 
+and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.3.
+Detecting the OHM in RXJ1131 will provide the first measurement beyond $z$$>$0.265,
+which will improve predictions on the sensitivity needed for future high-$z$ OHM surveys with upcoming facilities.
 \label{fig:model}}
@@
 % \hspace{-1.6em}
-\includegraphics[trim=0 0 50 0, clip, scale=.275]{Fig/Manipulate_figs} 
-\includegraphics[scale=.3]{Fig/F555WCO21_mom0_single_invertedgray}
-\includegraphics[scale=0.23]{Fig/SpecCO21}
-\includegraphics[scale=.2]{Fig/F555W_ContVLA}
-\includegraphics[trim=0 0 0 30, clip, scale=0.36]{Fig/SED_mani} \vspace{-0.25em}
+\centering
+\includegraphics[trim=0 190 0 0, clip, scale=.77]{Fig/Fig2}
+\vspace{-0.85em}
 \caption{
-{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\,$>$\,0.6 with a well-sampled spectral energy distribution (SED) spanning rest-frame UV to radio.} 
-{\em Top left:} Source-plane reconstruction of {\it HST} images shows the
-emission from recent star-formation in this AGN host galaxy and
+{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\ssim0.65}
+{\em (a):} Source-plane reconstruction of {\it HST} images shows recent star formation in our target and
 the presence of a nearby companion (\citealt{Claeskens06a}).
-{\em Top right:} 
-CO line emission overlaid on an {\it HST} image, which shows BLAH BLAH
-that RXJ1131 is lensed into an Einstein ring of diameter $\sim$3.6".
-{\em Middle left:}
-Our recent study finds a large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 and 
-confirmed the presence of its companion, with a gas mass ratio of 7:1 \citep{Leung17a}. 
-{\em Middle right:}
-We have previously detected radio continuum emission at 5\,GHz towards this target.
-The proposed \obs will provide an additional constraint on the radio continuum at 1\,GHz.
-{\em Bottom:} Our best-fit model to the well-sampled SED 
-indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
-an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
-The large molecular gas reservoir, on-going star formation, and the high \LFIR together
-are favourable for generating OHM, and thus RXJ1131 is an
-ideal candidate for high-$z$ OHM search.
-The proposed \obs together with our existing data acquired for this target will allow us to 
-compare its (host) properties against those of local OHM hosts to better understand 
-the physical environment that triggers OHM out to a look-back time of 6 Gyr.
+{\em (b):}
+The UV starlight in RXJ1131 is lensed into an Einstein ring (diameter $\sim$3.6") and the central AGN is
+quadruply-lensed in the {\it HST} image (grayscale). Both star formation and the AGN are sustained
+by the extended CO gas reservoir \citep[contours; ][]{Leung17a}.
+{\em (c):}
+Lens modeling of our CO data (yellow) 
+reveals a massive gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 
+(cyan; magnification factors $\mu_{L}$ are annotated above the respective channels) and
+confirmed the presence of a CO-emitting companion, with a gas mass ratio of 7:1 \citep[bottom panel;][]{Leung17a}.
+{\em (d):}
+We have detected strong radio continuum emission at 5\,GHz towards this target.
+The proposed \obs will provide an additional constraint at 1\,GHz (orange marker in \Fig{hst}e).
+{\em (e):} Our best-fit SED model indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
+an intense SFR\ssim120 \Msun yr\pmOne (lensing-corrected), and a dust temperature of $T_{d}$\eq55 K.
+The massive gas reservoir, on-going star formation with high \LFIR and $T_{d}$, and the large gas column density
+are favourable for generating OHM, making RXJ1131 an
+ideal candidate to search for OHM beyond the nearby universe.
+Here we aim to detect the OHM in RXJ1131, and thus to obtain a handle on the pumping efficiency
+to better understand the triggering mechanism at a look-back time of 6 Gyr, which
+would reflect the different physical conditions of the innermost regions between low- and high-$z$ IR-luminous galaxies.
+The proposed study is therefore an important step towards understanding 
+% the evolution of the inner few hundred pc of
+the internal structure and kinematics of
+starbursting galaxies at earlier epochs.
 \label{fig:hst}}
